### 2020-06-03 paper.Rnw
added documents for shortened paper

\documentclass[AMS,STIX2COL]{WileyNJD-v2}

% Packages
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{natbib}
\usepackage{subcaption}
\usepackage{xcolor}

% Commands
\definecolor{orange}{rgb}{0.94, 0.59, 0.19}
\definecolor{purple}{rgb}{0.5, 0.0, 0.5}
\definecolor{teal}{rgb}{0, 0.502, 0.502}
\newcommand{\hh}[1]{\textcolor{orange}{#1}}
\newcommand{\kgc}[1]{\textcolor{purple}{#1}}
\newcommand{\kge}[1]{\textcolor{teal}{#1}}
\newcommand{\data}{sine data}

% Set up for ASA data science journal
\articletype{Article Type}
\received{26 April 2016}
\revised{6 June 2016}
\accepted{6 June 2016}
\raggedbottom

\begin{document}

% Paper header (title and authors)
\title{Visual Diagnostics of a Model Explainer -- Tools for the Assessment of LIME Explanations}
\author[1]{Katherine Goode*}
\author[1,2]{Heike Hofmann}
\authormark{Goode and Hofmann}
\address[1]{\orgdiv{Department of Statistics}, \orgname{Iowa State University}, \orgaddress{\state{Iowa}, \country{United States}}}
\address[2]{\orgdiv{Center for Statistics and Applications in Forensic Evidence (CSAFE)}, \orgname{Iowa State University}, \orgaddress{\state{Iowa}, \country{United States}}}
\corres{*Corresponding author. \email{kgoode@iastate.edu}}
\presentaddress{This is sample for present address text this is sample for present address text}

% Abstract and keywords
\abstract[Summary]{The importance of providing explanations for predictions made by black-box models has led to the development of model explainer methods such as LIME (local interpretable model-agnostic explanations) \citep{ribeiro:2016}. LIME uses a surrogate model to explain the relationship between predictor variables from a black-box model and the black-box model predictions in a local region around a prediction of interest. However, the quality of the resulting explanations relies on how well the explainer model captures the black-box model in a specified local region. Here we introduce four visual diagnostics to assess the quality of LIME explanations: (1) explanation scatterplot, (2) prediction comparison plot, (3) assessment metric plot, and (4) feature heatmap. We apply the visual diagnostics to a forensics bullet matching dataset to show examples where LIME explanations depend on the tuning parameters and the explainer model oversimplifies the black-box model. Our examples raise concerns about claims made about LIME \citep{ribeiro:2016} that are similar to other criticism found in the literature (\citet{alvarezmelis:2018}, \citet{laugel:2018}, and \citet{molnar:2019}).}
\keywords{LIME, black-box models, interpretability, diagnostics}

% Citation information
\jnlcitation{
\cname{\author{Goode K.}, \author{H. Hofmann}, }
\cyear{2019},
\ctitle{Visual Diagnostics of a Model Explainer -- Tools for the Assessment of LIME Explanations},
\cjournal{Stat Anal Data Min: The ASA Data Sci Journal},
\cvol{volume, number and page}.}

\maketitle

<<setup, echo = FALSE, include = FALSE>>=

# Specify global options
knitr::opts_chunk$set(echo = FALSE,
                      fig.keep = 'high',
                      message = FALSE)

# Load packages
library(caret)
library(cowplot)
library(dplyr)
library(forcats)
library(ggforce)
library(ggplot2)
library(ggpcp)
library(glmnet)
library(gower)
library(graphics)
library(gretchenalbrecht)
library(latex2exp)
library(lime) #devtools::install_github("goodekat/lime")
library(limeaid) #devtools::install_github("goodekat/limeaid")
library(purrr)
library(randomForest)
library(stringr)
library(tidyr)

@

\section{Introduction}

In the field of statistics, there are two main uses for models: inference and prediction. Machine learning models are often used for the latter purpose. These models have proven to perform well in a wide range of prediction problems, but the accuracy of many machine learning models comes at the cost of interpretability due to their algorithmic complexity (hence the phrase "black-box models"). Model interpretability allows for the assessment and understanding of how the model produces predictions. In application, the ability to assess and understand model is crucial in important and crutial in areas areas with high stakes decisions such as health care and forensics science. The increased use of machine learning models and the introduction of the General Data Protection Regulation (GDPR) in 2018 \citep{goodman:2016} has resulted in a dramatic increase in research in the area of explainable machine learning that focuses on developing ways to explain output from machine learning algorithms.

Throughout this paper, we will make a distinction between interpretability and explanability of models. We define {\it interpretability} as the ability to directly use model parameters to understand the relationships in the data captured by the model: e.g., a linear model coefficient associated with a predictor variable indicates the amount the response variable changes based on a change in the predictor variable. In contrast, {\it explanability} is defined as the ability to use the model in an indirect manner to understand the relationships in the data captured by the model: e.g., partial dependence plots depict the marginal relationship between model predictions and predictor variables \citep{friedman:2001}.

Numerous methods have been proposed to provide explanations for black-box model predictions \citep{guidotti:2018, mohseni:2018, molnar:2019}. Some are specific to one type of model (e.g. \citep{bau:2017} and \citep{hara:2016}), and others are model-agnostic (e.g. \citep{greenwell:2018} and \citep{strumbelj:2014}). In this paper, we focus on the model-agnostic method of LIME (local interpretable model-agnostic explanations) \citep{ribeiro:2016}.

<<concept-data>>=
# Simulate example data
set.seed(20190624)
lime_data <-
  data.frame(
    feature1 = sort(runif(250, 0, 1)),
    feature2 = sample(x = 1:250, size = 250, replace = FALSE)) %>%
  mutate(
    feature1_stnd = (feature1 - mean(feature1)) / sd(feature1),
    feature2_stnd = (feature2 - mean(feature2)) / sd(feature2),
    prediction = if_else(feature1 >= 0 & feature1 < 0.1,
                         (0.3 * feature1) + rnorm(n(), 0, 0.01),
                 if_else(feature1 >= 0.1 & feature1 < 0.3,
                         rbeta(n(), 1, 0.5),
                 if_else(feature1 >= 0.3 & feature1 < 0.5,
                         sin(pi* feature1) + rnorm(n(), 0, 0.5),
                 if_else(feature1 >= 0.5 & feature1 < 0.8,
                         -(sin(pi* feature1) + rnorm(n(), 0, 0.1)) + 1,
                 if_else(feature1 >= 0.8 & feature1 < 0.9,
                         0.5 + runif(n(), -0.5, 0.5),
                         0.5 + rnorm(n(), 0, 0.3))))))) %>%
  bind_rows(
    data.frame(feature1 = rep(1, 30) + rnorm(5, 0, 0.05),
           feature2 = rep(245, 30) + rnorm(5, 0, 1),
           prediction = rep(0, 30) + rnorm(5, 0, 0.05)) %>%
  mutate(feature1_stnd = (feature1 - mean(feature1)) / sd(feature1),
         feature2_stnd = (feature2 - mean(feature2)) / sd(feature2)))

# Specify a prediction of interest
prediction_of_interest <-
  data.frame(feature1 = 0.07, feature2 = 200) %>%
  mutate(feature1_stnd = (feature1 - mean(lime_data$feature1)) /
           sd(lime_data$feature1),
         feature2_stnd = (feature2 - mean(lime_data$feature2)) /
           sd(lime_data$feature2),
         prediction = 0.05,
         color = factor("Prediction \nof Interest"))

# Specify the gower exponents
good_gower_power <- 50
bad_gower_power <- 1

# Compute the good distances between the prediction of interest
# and all other observations
lime_data$distance_good <-
  (1 - gower_dist(x = prediction_of_interest %>%
                    select(feature1_stnd, feature2_stnd),
                  y = lime_data %>%
                    select(feature1_stnd,
                           feature2_stnd)))^good_gower_power

# Compute the bad distances between the prediction of interest
# and all other observations
lime_data$distance_bad <-
  (1 - gower_dist(x = prediction_of_interest %>%
                    select(feature1_stnd, feature2_stnd),
                  y = lime_data %>%
                    select(feature1_stnd,
                           feature2_stnd)))^bad_gower_power

# Prepare the data for plotting
lime_data_gathered <- lime_data %>%
  gather(feature, feature_stnd_value,
         feature1_stnd:feature2_stnd) %>%
  gather(distance, distance_value, distance_good:distance_bad) %>%
  mutate(distance = fct_recode(distance,
                               "good" = "distance_good",
                               "bad" = "distance_bad"),
         feature = fct_recode(feature,
                              "Feature 1" = "feature1_stnd",
                              "Feature 2" = "feature2_stnd"))

# Prepare the prediction of interest data for plotting
prediction_of_interest_gathered <- prediction_of_interest %>%
  select(-feature1, -feature2) %>%
  gather(feature, feature_value, feature1_stnd, feature2_stnd) %>%
  mutate(feature = fct_recode(feature,
                              "Feature 1" = "feature1_stnd",
                              "Feature 2" = "feature2_stnd"))

@

<<concept-explainers>>=

# Fit the good interpretable explainer model
explainer_good <-
  glmnet(x = lime_data %>% select(feature1_stnd, feature2_stnd)
         %>% as.matrix(),
         y = lime_data$prediction,
         alpha = 0,
         lambda = 1,
         weights = lime_data$distance_good)

# Fit the bad interpretable explainer model
explainer_bad <-
  glmnet(x = lime_data %>% select(feature1_stnd, feature2_stnd)
         %>% as.matrix(),
         y = lime_data$prediction,
         alpha = 0,
         lambda = 1,
         weights = lime_data$distance_bad)

# Join the coefficients from the explainer model into a dataframe
coefs_data <- data.frame(case = c("good", "bad"),
                         b0 = c(coef(explainer_good)[1],
                                coef(explainer_bad)[1]),
                         b1 = c(coef(explainer_good)[2],
                                coef(explainer_bad)[2]),
                         b2 = c(coef(explainer_good)[3],
                                coef(explainer_bad)[3])) %>%
  mutate(feature1 = b0 + b2*prediction_of_interest$feature2_stnd,
         feature2 = b0 + b1*prediction_of_interest$feature1_stnd) %>%
  gather(key = feature, value = int, feature1:feature2) %>%
  mutate(slope = c(coef(explainer_good)[2],
                   coef(explainer_good)[3],
                   coef(explainer_bad)[2],
                   coef(explainer_bad)[3]),
         feature = fct_recode(feature,
                              "Feature 1" = "feature1",
                              "Feature 2" = "feature2"))

@

\begin{figure*}[!htbp]
<<concept-plot-good, out.width = '\\textwidth', fig.width = 7.95, fig.height = 3.75, warning = FALSE>>=

# Plot of good explainer model
ggplot() +
  facet_grid(. ~ feature, switch = "x") +
  geom_point(data = lime_data_gathered,
             mapping = aes(x = feature_stnd_value,
                           y = prediction,
                           size = distance_value,
                           alpha = distance_value,
                           color = distance)) +
  geom_abline(data = coefs_data %>% filter(case == "good"),
              mapping = aes(intercept = int, slope = slope),
              size = 1) +
  scale_alpha(range = c(0.3, 1)) +
  scale_color_manual(values = c(NA, "grey30"), guide = FALSE) +
  geom_point(data = prediction_of_interest_gathered,
             mapping = aes(x = feature_value,
                           y = prediction,
                           fill = color),
             color = "black",
             size = 5,
             shape = 23,
             alpha = 0.75) +
  scale_fill_manual(values = "#FAAA72") +
  geom_text(
    data = data.frame(feature_stnd_value = 1.2,
                      prediction = 1.6,
                      feature = c("Feature 1", "Feature 2"),
                      slope = c(paste("Slope:",
                                      coefs_data %>%
                                        filter(case == "good",
                                               feature == "Feature 1") %>%
                                        pull(slope) %>%
                                        round(3)),
                                paste("Slope:",
                                      coefs_data %>%
                                        filter(case == "good",
                                               feature == "Feature 2") %>%
                                        pull(slope) %>%
                                        round(3)))),
    mapping = aes(x = feature_stnd_value,
                  y = prediction,
                  label = slope),
    family = "Times",
    size = 4) +
  labs(x = "",
       y = "Black-Box Prediction",
       title = "Conceptual Depiction of a Faithful Local Explainer Model",
       subtitle = paste("Gower Distance Metric Exponent:", good_gower_power),
       fill = "",
       alpha = "Weight",
       size = "Weight") +
  theme_linedraw(base_family = "Times", base_size = 10) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        strip.placement = "outside",
        strip.background = element_rect(color = "white", fill = "white"),
        strip.text = element_text(color = 'black', size = 10)) +
  guides(fill = guide_legend(order = 1),
         size = guide_legend(order = 2),
         alpha = guide_legend(order = 2))

@
\caption{A conceptual depiction of a faithful LIME explainer model in the immediate neighborhood of a prediction of interest. The predictions from a hypothetical black-box model are plotted against the standardized values of the two predictor variables used to fit the hypothetical model. The diamond shaped points represent the location of a prediction of interest. The size and opacity of the circular points indicate the weight assigned based on the distance to the point of interest computed using the inverse of the Gower distance metric raised to the power of \Sexpr{good_gower_power}. The black lines are a weighted ridge regression model used as an explainer model that reasonably captures the relationship between the black-box predictions and the features in a local region around the point of interest. That is, it is faithful to the complex model and produces a reasonable explanation that Feature 1 plays a more important role in the prediction of interest than Feature 2 since the magnitude of the slope associated with Feature 1 is larger.}
\label{fig:concept-plot-good}

\vspace*{\floatsep}

<<concept-plot-bad, out.width = '\\textwidth', fig.width = 7.95, fig.height = 3.75, warning = FALSE>>=

# Plot of good explainer model
ggplot() +
  facet_grid(. ~ feature, switch = "x") +
  geom_point(data = lime_data_gathered,
             mapping = aes(x = feature_stnd_value,
                           y = prediction,
                           size = distance_value,
                           alpha = distance_value,
                           color = distance)) +
  geom_abline(data = coefs_data %>% filter(case == "bad"),
              mapping = aes(intercept = int, slope = slope),
              size = 1) +
  scale_alpha(range = c(0.3, 1)) +
  scale_color_manual(values = c("grey30", NA), guide = FALSE) +
  geom_point(data = prediction_of_interest_gathered,
             mapping = aes(x = feature_value,
                           y = prediction,
                           fill = color),
             color = "black",
             size = 5,
             shape = 23,
             alpha = 0.75) +
  scale_fill_manual(values = "#FAAA72") +
  geom_text(
    data = data.frame(feature_stnd_value = 1.2,
                      prediction = 1.6,
                      feature = c("Feature 1", "Feature 2"),
                      slope = c(paste("Slope:",
                                      coefs_data %>%
                                        filter(case == "bad",
                                               feature == "Feature 1") %>%
                                        pull(slope) %>%
                                        round(3)),
                                paste("Slope:",
                                      coefs_data %>%
                                        filter(case == "bad",
                                               feature == "Feature 2") %>%
                                        pull(slope) %>%
                                        round(3)))),
    mapping = aes(x = feature_stnd_value,
                  y = prediction,
                  label = slope),
    family = "Times",
    size = 4) +
  labs(x = "",
       y = "Black-Box Prediction",
       title = "Conceptual Depiction of an Unfaithful Local Explainer Model",
       subtitle = paste("Gower Distance Metric Exponent:", bad_gower_power),
       fill = "",
       alpha = "Weight",
       size = "Weight") +
  theme_linedraw(base_family = "Times", base_size = 10) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        strip.placement = "outside",
        strip.background = element_rect(color = "white", fill = "white"),
        strip.text = element_text(color = 'black', size = 10)) +
  guides(fill = guide_legend(order = 1),
         size = guide_legend(order = 2),
         alpha = guide_legend(order = 2))

@
\caption{A conceptual depiction of an unfaithful local explainer model in the immediate neighborhood of a prediction of interest. A ridge regression model is fit to the same black-box model predictions and predictor variables as in \autoref{fig:concept-plot-good}, but the weights are computed using a Gower exponent of 1. The explainer model provides a global approximation of the complex model in regards to the prediction of interest.}
\label{fig:concept-plot-bad}
\end{figure*}

\subsection{LIME}

LIME falls under the category of model explainers \citep{ribeiro:2016} \citep{mohseni:2018}. A model explainer is a method that uses a surrogate model to relate the predictor variables to the black-box model predictions. We will distinguish between the terms of model explainer and explainer model: by \emph{model explainer} we denote the method for explaining a complex model using a surrogate model, while the \emph{explainer model}, or simply the \emph{explainer}, is the surrogate model.

While some model explainers are focused on understanding a model at the global level, LIME claims to provide local explanations. Additionally, LIME is designed to work with any model and to produce easily understandable explanations \citep{ribeiro:2016}. Conceptually, LIME fits a simple interpretable model, the explainer model,  meant to capture the behavior of the (complex) black-box model in a local region around a prediction of interest. The  simple model then provides interpretable estimates for variables that most influenced the prediction made by the complex model.

\autoref{fig:concept-plot-good} provides a visualization of this conceptual understanding of LIME. The two plots show the predictions from a hypothetical black-box model plotted against the two predictor variables used to fit the hypothetical model. The diamond shaped points represent a prediction of interest. A Gower distance metric \citep{gower:1971} is used to define locality: the size of the points represent the inverse of the Gower distance as a reflection of the proximity to the prediction of interest. Here, an exponent of \Sexpr{good_gower_power} is used to emphasize interest in a very local region around the point of interest. A ridge regression model weighted by the proximity values is used as the explainer model. The black-box predictions are used as the response variable, standardized versions of Features 1 and 2 are included as predictor variables. Standardized features allow direct comparisons of the model coefficients. The explainer model is depicted by the black lines in the figure.

The plot on the left of \autoref{fig:concept-plot-good} shows the relationship between the black-box predictions and Feature 1. Here, the explainer model is plotted with Feature 2 fixed at the observed value of Feature 2 for the prediction of interest. The explainer model captures the relationship in the immediate neighborhood around the prediction of interest  with a slope of \Sexpr{coefs_data %>% filter(case == "good", feature == "Feature 1") %>% pull(slope) %>% round(3)}. The plot on the right shows that there is no global or local relationship between the black-box predictions and Feature 2. Here, the explainer model is plotted with Feature 1 set to be the observed value of Feature 1 for the prediction of interest, and it has a small slope of \Sexpr{coefs_data %>% filter(case == "good", feature == "Feature 2") %>% pull(slope) %>% round(3)}. The magnitude of the slope associated with Feature 1 is larger than the slope of Feature 2, resulting LIME to report that Feature 1 plays a more important role in the prediction made by the black-box model.

\subsection{Motivation for Diagnosing LIME}

Explainer models are meant to provide clarity to the process of predictive modeling, but since the explainer model is an approximation of the complex model and not a direct interpretation, explanations produced by an explainer model are subject to the quality of the approximation. Thus, explainer models add another layer of complexity to predictive models by requiring yet another model that needs to be assessed.

The choice of exponent in the scenario depicted in \autoref{fig:concept-plot-good} is crucial. High values ensure an up-weight of observations closer to the prediction of interest. Consider the example depicted in \autoref{fig:concept-plot-bad}. The plots show the same data as \autoref{fig:concept-plot-good}, but the Gower distance metric exponent was decreased to \Sexpr{bad_gower_power} (the default exponented in the \emph{lime} R package). This causes the observations that are further away from the prediction of interest to be given larger weights than before. In \autoref{fig:concept-plot-good}, the explainer model captures the relationship between the black-box predictions in the immediate neighborhood of the prediction of interest. This cannot be said of the explainer model in \autoref{fig:concept-plot-bad}. In addition, the magnitude of the slope (\Sexpr{coefs_data %>% filter(case == "bad", feature == "Feature 2") %>% pull(slope) %>% round(3) %>% abs()}) associated with Feature 2 is larger than that of Feature 1 (\Sexpr{coefs_data %>% filter(case == "bad", feature == "Feature 1") %>% pull(slope) %>% round(3) %>% abs()}). Thus, this explainer model actually provides a misleading explanation that Feature 2 plays a more important role in predicting the observation of interest.

There are various ways in which LIME can fail. One of the biggest difficulties with LIME is determining how to specify a local region \citep{molnar:2019} due to an unclear definition of what a local region means and how to apply LIME to achieve an appropriate local region. \autoref{fig:concept-plot-bad} demonstrates an explainer model that provides misleading explanations due to poorly specified weights. \citet{laugel:2018} show additional examples of undesirable explanations produced by LIME when the local region was chosen inadequately. \citet{alvarezmelis:2018} raise another concern pertaining to the robustness of explanations from LIME and other post-hoc explainers: they find that even small changes in predictor variables can lead to very different LIME explanations. Additionally, LIME relies on a good approximation of the explainer model to the complex model. \citet{ribeiro:2016} acknowledge that ``if the underlying model is highly non-linear even in the locality of the prediction, there may not be a faithful explanation" with a linear regression model as the explainer model.

As a result of the various ways LIME explanations can fail, it is important to assess LIME explanations. In this paper, we lay out the set of claims about LIME made by \citet{ribeiro:2016} and propose four visualizations for the assessment of these claims: (1) \emph{explanation scatterplot}, (2) \emph{prediction comparison plot}, (3) \emph{feature heatmap}, (4) \emph{assessment metric plot}.

While LIME has been implemented for image, tabular, and text data, we will only focus on tabular data. For additional simplicity, we will only discuss classification prediction models with a dichotomous response variable and continuous predictor variables. However, the proposed diagnostics may be extended to a wider range of situations.

\subsection{Overview of Paper}

The reminder of the paper is structured as follows. Section \ref{background} provides background and the claims made by \citet{ribeiro:2016} about LIME. In Section \ref{diagnostics}, we introduce the suggested diagnostic plots. Then in Section \ref{application}, we demonstrate the use of the diagnostics to assess LIME explanations for a random forest model fit to a forensics bullet matching dataset. Section \ref{discussion} concludes with a discussion on extenstion and limitations of the diagnostic plots and concerns about LIME in regards to the claims made by \citet{ribeiro:2016} brought about by the visualization examples in this paper that agree with \citet{alvarezmelis:2018}, \citet{laugel:2018}, and \citet{molnar:2019}.

\section{Background on LIME} \label{background}

LIME was introduced in 2016 by \citet{ribeiro:2016}. LIME is presented as a model explainer that produces easily understandable explanations for individual predictions from any predictive model \citep{ribeiro:2016}. As described by \citet{laugel:2018}, the general form of the LIME algorithm can be divided into three steps:

\begin{enumerate}

\item \emph{Data Simulation and Interpretable Transformation}: Simulate a dataset from the original data used to fit the black-box model. Apply a transformation to the simulated data and the prediction of interest that will allow for interpretable explanations.

\item \emph{Explainer Model Fitting}: Apply the black-box model to the simulated data to obtain predictions. Compute the distance between each of the simulated observations and the prediction of interest. Fit an interpretable model with the black-box predictions from the simulated data as the response, the transformed simulated data as the predictors, and the distances as weights. This model is the explainer model.

\item \emph{Explainer Model Interpretation}: Interpret the explainer model to determine which features played the most important role in the prediction of interest.

\end{enumerate}

\citet{ribeiro:2016} make the following set of claims regarding the performance of LIME:

\begin{itemize}
\item \emph{Interpretability}: The explainer model can be easily interpreted to provide meaningful explanations.
\item \emph{Faithfulness}: The explainer model sufficiently captures the relationship between the complex model predictions and the features in the local region around a prediction of interest to produce explanations that are faithful to the complex model.
\item \emph{Linearity}: By using a ridge regression model as the explainer model, it is assumed that there is a linear relationship between complex model predictions and the features in the local region around a prediction of interest.
\item \emph{Localness}: The explanations produced by LIME are local in regards to a prediction of interest.
\end{itemize}

The assumption of interpretability only depends on the complexity of the model used as explainer model. If the model is too complex to provide meaningful explanations (e.g. there are too many variables in the model), it is clear that the assumption of interpretability is violated. The other three assumptions are not as easy to assess -- for those we suggest the use of diagnostic plots.

LIME was initially implemented in a Python package\footnote{https://github.com/marcotcr/lime} by the original authors. The adaption to an R package is by Thomas Lin-Pedersen\footnote{https://github.com/thomasp85/lime}. In this paper, we use a forked version\footnote{https://github.com/goodekat/lime} of the development version of the R package \emph{lime} (\Sexpr{packageVersion("lime")}) \citep{pedersen:2020}. The forked version of \emph{lime} allows us to export internal values of the procedure not already exported by \emph{lime}.

\section{Visual Diagnostics for LIME} \label{diagnostics}

<<sine-data, echo = FALSE, include = FALSE>>=

# Functions for rotating the data
rot_x <- function(x, y, theta) (x * cos(theta)) - (y * sin(theta))
rot_y <- function(x, y, theta) (x * sin(theta)) + (y * cos(theta))

# Generate the data
theta = -0.9
min = -10
max = 10
set.seed(20190913)
sine_data <- data.frame(x1 = runif(600, min, max),
                        x2 = sort(runif(600, min, max))) %>%
  mutate(x1new = rot_x(x1, x2, theta),
         x2new = rot_y(x1, x2, theta),
         y = ifelse(x2new > 5 * sin(x1new), "blue", "red")) %>%
  slice(sample(1:n())) %>%
  mutate(x3 = rnorm(600),
         case = 1:600) %>%
  select(case, everything())

# Separte the data into training and testing parts
set.seed(20191003)
rs <- sample(1:600, 500, replace = FALSE)
sine_data_train <- sine_data[rs,]
sine_data_test <- sine_data[-rs,]

# Fit a random forest
set.seed(20191003)
rfsine <- randomForest(x = sine_data_train %>% select(x1, x2, x3),
                       y = factor(sine_data_train$y))

# Obtain predictions on the training and testing data
sine_data_train$rfpred <- predict(rfsine)
sine_data_train <- cbind(sine_data_train, predict(rfsine, type = "prob"))
sine_data_train <- sine_data_train %>% 
  rename(rfprob_blue = blue, rfprob_red = red)
sine_data_test$rfpred <- predict(rfsine, sine_data_test %>% select(x1, x2, x3))
sine_data_test <- cbind(sine_data_test,
                        predict(rfsine, sine_data_test
                                %>% select(x1, x2, x3),
                                type = "prob"))
sine_data_test <- sine_data_test %>% 
  rename(rfprob_blue = blue, rfprob_red = red)

# Extract the prediction of interest from the sine test data
sine_poi <- sine_data_test %>% filter(y != rfpred, x1 > 0, x1 < 5, x2 > 5)

@

\begin{figure*}[!t]
\centering
<<sine-plot-data, out.width = '\\textwidth', fig.width = 8, fig.height = 3.1>>=

# Create points represting the rotated since curve
sinefun_data <- data.frame(xnew = seq(min(sine_data$x1new),
                                      max(sine_data$x1new),
                                      by = 0.01)) %>%
  mutate(ynew = 5 * sin(xnew)) %>%
  mutate(x = rot_x(xnew, ynew, -theta),
         y = rot_y(xnew, ynew, -theta)) %>%
  filter(y >= -10, y <= 10)

# Specify colors for predictions
sinecolor_red = "firebrick"
sinecolor_blue = "steelblue"

# Plot the training data observed classes
sine_plot_obs <- ggplot(sine_data_train, aes(x = x1, y = x2, color = y)) +
  geom_point(alpha = 0.8) +
  geom_path(data = sinefun_data, aes(x = x, y = y),
            color = "black") +
  scale_colour_manual(values = c(sinecolor_blue, sinecolor_red)) +
  theme_bw(base_family = "Times", base_size = 10) +
  labs(x = TeX("$x_1$"),
       y = TeX("$x_2$"),
       color = TeX("y"),
       title = "Training Data")

# Plot the testing data rf predictions
sine_plot_pred <- ggplot() +
  geom_point(data = sine_poi %>%
               mutate(shape = "Prediction \nof Interest"),
             mapping = aes(x = x1,
                           y = x2,
                           #fill = rfprob_blue,
                           shape = shape),
             size = 5,
             alpha = 0.8,
             color = "black") +
  geom_point(data = sine_data_test %>% filter(y != rfpred),
             mapping = aes(x = x1, y = x2),
             shape = 1,
             size = 3,
             color = "black") +
  geom_point(data = sine_data_test,
             mapping =  aes(x = x1,
                            y = x2,
                            color = rfprob_blue,
                            fill = rfprob_blue),
             shape = 21,
             alpha = 0.8) +
  geom_path(data = sinefun_data, aes(x = x, y = y),
            color = "black") +
  scale_color_gradient2(low = sinecolor_red,
                        mid = '#f7f7f7',
                        high = sinecolor_blue,
                        midpoint = 0.5) +
  scale_fill_gradient2(low = sinecolor_red,
                        mid = '#f7f7f7',
                        high = sinecolor_blue,
                        midpoint = 0.5) +
  scale_shape_manual(values = 23) +
  theme_bw(base_family = "Times", base_size = 10) +
  labs(x = TeX("$x_1$"),
       y = TeX("$x_2$"),
       color = "Random \nForest \nProbability \nfor 'blue'",
       fill = "Random \nForest \nProbability \nfor 'blue'",
       title = "Testing Data",
       shape = "") +
  guides(shape = guide_legend(order = 1))

# Join the plots
plot_grid(sine_plot_obs, sine_plot_pred,
          nrow = 1,
          rel_widths = c(0.4825, 0.5175))

@
\caption{Plots of $x_2$ versus $x_1$ from the training (left) and testing (right) set of the \data \ introduced in Section \ref{procedure}. The true classification boundary is shown as the solid black line in both plots. The color of the training data points represents the value of the observed response variable ($y$). The color of the testing data points represents the random forest probability that an observation belongs to the category of blue ($\hat{y}$). The \Sexpr{dim(sine_data_test %>% filter(y != rfpred))[1]} cases that are misclassified by the random forest are identified by black circles. The prediction of interest to explain is indicated by a diamond.}
\label{fig:sine-plot-data}
\end{figure*}

At a high level, the concept of LIME is relatively simple: an interpretable model is used to approximate a complex model in a local region. In practice, the implementation of LIME is not straightforward, and there is research is being done to improve the procedure \citep{laugel:2018}. As described in \autoref{background}, there are various parameter choices that have to be made when applying LIME: the simulation method, the feature selection method, and how weights are calculated.  We will refer to these choices as tuning parameters. Without an assessment of the explainer model, it is not clear if the tuning parameters selected when applying LIME resulted in a useful explanation and LIME becomes a black-box procedure of its own. To counteract the black-box nature, we suggest the use of visualizations of each step of the LIME algorithm. In this section, we introduce four suggested visual diagnostic plots for the assessment of LIME. The diagnostic plots focus on assessing the LIME claims at different levels of application:

\begin{enumerate}
\item Explanation scatterplot (Section \ref{plot1}): Comparison of the explainer and complex models for an individual prediction of interest.
\item Prediction comparison plot (Section \ref{plot1}): Comparison of explainer and complex model predictions for a set of predictions.
\item Feature Heatmap: Comparison of features selected by LIME across applications of LIME with different tuning parameters.k
\item Assessment metric plot: Comparison of performance metrics for LIME across applications of LIME with different tuning parameters. 
\end{enumerate}

\paragraph{The \data}

To demonstrate the visualizations, we generate an example dataset that will be referred to as the \data. The \data \ contains \Sexpr{dim(sine_data)[1]} observations with three features and one response variable. The features, $x_1$, $x_2$, and $x_3$, are randomly sampled from Unif(\Sexpr{min}, \Sexpr{max}), Unif(\Sexpr{min}, \Sexpr{max}), and $\mbox{N}(0,1)$ distributions, respectively. A binary response variable $y$ is  created using a rotated sine curve. In particular, let $x'_1=x_1\cos(\theta)-x_2\sin(\theta)$ and $x'_2=x_1\sin(\theta)+x_2\cos(\theta)$ where $\theta=-0.9$. Then $y$ is defined as
\begin{eqnarray}\label{eq:data}
  y=\begin{cases}
  \mbox{blue} & \mbox{ if } x'_2 > \sin\left(x'_1\right) \\
  \mbox{red} & \mbox{ if } x'_2 \le \sin\left(x'_1\right) \ . %\nolabel
  \end{cases}
\end{eqnarray}
Note that due to the creation of $y$ in this manner, $y$ is dependent on $x_1$ and $x_2$ and independent of $x_3$.

The dataset is divided into a training set of \Sexpr{dim(sine_data_train)[1]} observations and a testing set of \Sexpr{dim(sine_data_test)[1]} observations. A random forest model is fit using the R package \emph{randomForest} (version \Sexpr{packageVersion("randomForest")}) \citep{liaw:2002} with the default settings. The model is applied to the testing set to obtain predictions. \autoref{fig:sine-plot-data} shows scatterplots of $x_2$ versus $x_1$ from the training data (left) and the testing data (right). Both plots include the true classification boundary of the rotated sine function plotted as the solid black line. The training data are colored by the observed response variable ($y$), and the testing data are colored by the prediction probabilities from the random forest model ($\hat{y}$).

The random forest model misclassifies \Sexpr{dim(sine_data_test %>% filter(y != rfpred))[1]} points on the classification boundary. These are identified by circles in \autoref{fig:sine-plot-data}. For the diagnostic plot presented in Section \ref{plot1}, we focus on one of these points: the observation with $(x_1, x_2, x_3)$ coordinates of (\Sexpr{round(sine_poi$x1, 2)}, \Sexpr{round(sine_poi$x2, 2)}, \Sexpr{round(sine_poi$x3, 2)}) indicated by a diamond in \autoref{fig:sine-plot-data}.

<<sine-lime>>=

# Apply LIME with various tuning parameters to the sine data
if (!file.exists("../data/sine_lime_explain.rds")) {

    # Apply lime with various input options
    sine_lime_explain <- apply_lime(
      train = sine_data_train %>% select(x1, x2, x3),
      test = sine_data_test %>% select(x1, x2, x3),
      model = rfsine,
      label = "blue",
      n_features = 2,
      sim_method = c('quantile_bins', "kernel_density"),
      nbins = 2:6,
      feature_select = "auto",
      dist_fun = "gower",
      kernel_width = NULL,
      gower_pow = 1,
      return_perms = TRUE,
      all_fs = TRUE,
      seed = 20190914)

    saveRDS(sine_lime_explain, "../data/sine_lime_explain.rds")

  } else {

    sine_lime_explain <- readRDS("../data/sine_lime_explain.rds")

  }

@

<<sine-lime-default>>=

# Extract the explanations from the default lime implementation
sine_lime_default <- sine_lime_explain$explain %>% filter(nbins == 4)

# Extract the explanations from the default lime implementation
# for the prediction of interest only
sine_poi_lime_default <- sine_lime_default %>%
  filter(case == sine_poi %>% pull(case)) %>%
  mutate(case = c("Prediction of Interest", "Prediction of Interest"))

@

We apply LIME to the \data \ using \emph{lime} with the default settings. The user is asked to specify the number of features shown in the explanations. Here, we set this value to two, because we expect that $x_1$ and $x_2$ will be the main drivers in the prediction. Note that the complexity of an explanation goes hand in hand with the number of features selected to be included in the explanation. Setting the number of features to a small number will make the explanation simpler but not necessarily more correct.

To demonstrate the proposed diagnostic plots, we applied six different implementations of LIME to the sine data to select the top two features associated with each of the random forest predictions in the testing dataset. This was done using six different sets of tuning parameters via \sout{our} R package \emph{limeaid} \footnote{Available on GitHub at https://github.com/goodekat/limeaid}. Quantile bins were used for five of the implementations, and the number of bins for these implementations was varied from 2 to 6. The sixth implementation of LIME used the kernel density estimates. The feature selection method and the computation of the weights were set to the default options in \emph{lime} of forward selection and Gower distance raised to an exponent of 1.

\subsection{Explanation Scatterplots} \label{plot1}

<<warning = FALSE>>=
# Obtain the simulated data associated with the poi
sine_poi_perms <- sine_poi_lime_default %>%
  slice(1) %>%
  select(perms_raw, perms_pred_complex, perms_numerified, weights) %>%
  mutate(perms_numerified =
           map(perms_numerified,
               .f = function(x) rename(x,
                                       "x1num" = "x1",
                                       "x2num" = "x2",
                                       "x3num" = "x3"))) %>%
  unnest(cols = c(perms_raw, perms_pred_complex, perms_numerified, weights)) %>%
  select(-red) %>%
  rename(rfpred = blue) %>%
  mutate(case = factor(1:n())) %>%
  select(case, everything())

# Determine the bin cuts for the default lime implementation
sine_lime_default_bin_cuts <- sine_lime_default %>%
  select(feature, feature_desc) %>%
  unique() %>%
  separate(feature_desc, c("other", "bin_cut"), sep = " <= ") %>%
  select(-other) %>%
  na.omit() %>%
  mutate(bin_cut = as.numeric(bin_cut)) %>%
  arrange(feature) %>%
  mutate(case = rep(1:3, 2)) %>%
  spread(feature, bin_cut)
@

<<sine-poi-explainer, warning = FALSE>>=

# Determine the lime explanation cutoffs
sine_poi_bounds <- sine_poi_lime_default %>%
  select(case, feature, feature_value, feature_desc) %>%
  separate(feature_desc, c("other", "upper"), sep = " <= ") %>%
  separate(other, c("lower", "feature2"), sep = " < ") %>%
  mutate(upper = ifelse(is.na(upper), "Inf", upper)) %>%
  select(-feature2) %>%
  mutate_at(.vars = c("lower", "upper"), .funs = as.numeric)

# Extract the coefficients from the explainer
sine_b0 <- sine_poi_lime_default$model_intercept[1]
sine_b1 <- sine_poi_lime_default$feature_weight[2]
sine_b2 <- sine_poi_lime_default$feature_weight[1]

# Extract the bounds of the bins
x1_lower <- sine_poi_bounds %>% filter(feature == "x1") %>% pull(lower)
x1_upper <- sine_poi_bounds %>% filter(feature == "x1") %>% pull(upper)
x2_lower <- sine_poi_bounds %>% filter(feature == "x2") %>% pull(lower)
x2_upper <- sine_poi_bounds %>% filter(feature == "x2") %>% pull(upper)

# Function for computing the predicted value via the explainer model
sine_explainer <- function(z1, z2) sine_b0 + sine_b1 * z1 + sine_b2 * z2

@

<<sine-perms-subset>>=
# Subset the simulated data to the region where the poi is located
sine_poi_region_perms <- sine_poi_perms %>%
  filter(x2 >= sine_poi_bounds %>% filter(feature == "x2") %>% pull(lower),
         x1 >= sine_poi_bounds %>% filter(feature == "x1") %>% pull(lower),
         x1 < sine_poi_bounds %>% filter(feature == "x1") %>% pull(upper))
@

\begin{figure*}[!htp]
<<sine-plot1, out.width = '\\textwidth', fig.width = 10, fig.height = 4, warning = FALSE>>=

sine_poi_exp <- sine_poi_lime_default %>% plot_features()

plot1 <- ggplot() +
  geom_point(data = sine_poi_perms,
             mapping = aes(x = x1,
                           y = x2,
                           color = rfpred,
                           size = weights),
             alpha = 0.8,
             shape = 20) +
  scale_size(range = c(0.1, 3)) +
  geom_rect(data = sine_poi_bounds %>% filter(feature == "x1"),
            mapping = aes(xmin = lower,
                          xmax = upper,
                          ymin = -Inf,
                          ymax = Inf),
            alpha = 0.25,
            fill = "grey90",
            color = "firebrick") +
  geom_rect(data = sine_poi_bounds %>% 
              filter(feature == "x2"),
            mapping = aes(xmin = -Inf,
                          xmax = Inf,
                          ymin = lower,
                          ymax = upper,
                          color = coef),
            alpha = 0.25,
            fill = "grey90",
            color = "steelblue") +
  geom_point(data = sine_poi %>%
               mutate(shape = "Prediction \nof Interest"),
             mapping = aes(x = x1, y = x2, shape = shape, fill = rfprob_blue),
             size = 7,
             alpha = 0.8) +
  scale_shape_manual(values = 23) +
  scale_fill_gradient2(low = sinecolor_red,
                        mid = '#f7f7f7',
                        high = sinecolor_blue,
                        midpoint = 0.5,
                        limits = c(0, 1)) +
  scale_color_gradient2(low = sinecolor_red,
                        mid = '#f7f7f7',
                        high = sinecolor_blue,
                        midpoint = 0.5,
                        limits = c(0, 1)) +
  theme_bw(base_family = "Times", base_size = 10) +
  labs(x = TeX("x'_1"),
       y = TeX("x'_2"),
       size = "Weight",
       shape = "",
       fill = "Random \nForest \nProbability \nfor 'blue'",
       color = "Random \nForest \nProbability \nfor 'blue'",
       title = "Complex and Explainer Model Comparison Plot") + 
  guides(shape = guide_legend(order = 1)) + 
  theme(aspect.ratio = 1)

plot_grid(sine_poi_exp, plot1, align = "h")
@
\caption{\kgc{Edit...} (right) The explanation plot depicts the estimated parameters from the explainer model. The lengths of the bars represent the absolute values of the coefficients, and the colors of the bars represent the coefficient values. Since the magnitude of the coefficient associated with $x_2$ is longer than that of $x_1$, the explanation suggests that $x_2$ has more of an effect on the random forest prediction of interest than $x_1$ does. The explainer model comparison plot shows the simulated data colored by the random forest probabilities and sized by the assigned LIME weights. The prediction of interest is shown as the diamond shaped point. The quantile bins associated with $x_1$ and $x_2$ are depicted by the solid lines. The color of the line indicates whether the explainer model supports a prediction of 'blue' (blue line) or supports a prediction of 'red' (red lines). This figure shows that the quantile bins are not flexible enough to capture the relationship between the random forest predictions and the $x_1$ and $x_2$ values.}
\label{fig:sine-plot-step3ab}
\end{figure*}

\kgc{Add intro paragraph and edit text as necessary in this subsection}

\autoref{fig:sine-plot-poi} shows the visualization of the explanation produced by \emph{lime} for the prediction of interest. The figure shows that the random forest returned a probability of \Sexpr{sine_poi_lime_default$label_prob[1]} that the observation of interest belongs to category blue {(denoted as the ``label" in the figure). The colored bars indicate the features chosen by LIME and whether they support or contradict a random forest classification of blue. \kgc{Add explanation for bins in the plot.}

The explanation for the prediction of interest depicted in Figure \ref{fig:sine-plot-poi} can be interpreted as follows. A random forest classification of blue is supported by the prediction of interest having a value of $x_2$ that is greater than \Sexpr{str_split(sine_poi_lime_default$feature_desc[[1]], pattern = " ")[[1]][1]}, but the prediction of interest having a value of $x_1$ that is greater than \Sexpr{str_split(sine_poi_lime_default$feature_desc[[2]], pattern = " ")[[1]][1]} and less than or equal to \Sexpr{str_split(sine_poi_lime_default$feature_desc[[2]], pattern = " ")[[1]][5]} provides support against a classification of blue. Since the weight associated with $x_2$ has a larger magnitude than the weight associated with $x_1$, LIME explains that the $x_1$ and $x_2$ locations of the prediction of interest provide more support for a random forest classification of blue over red. This explanation agrees with the random forest probability of \Sexpr{sine_poi_lime_default$label_prob[1]} for blue, even though both classify the observation incorrectly.

\autoref{fig:sine-plot-poi} also includes an "explanation fit" value. This value corresponds to the deviance ratio from the R package \emph{glmnet} \citep{simon:2011} for a ridge regression model, or in other words, this is the $R^2$ value associated with the explainer model. In this case, it is \Sexpr{round(sine_poi_lime_default$model_r2[1], 2)} suggesting that the explainer model is not a good linear fit. However, it is commonly accepted that $R^2$ has limitations for accessing the quality of fit of a model \citep{sapra:2014}, and it should not be the only metric used for assessment of a model. Based on this metric or this plot, it is not yet possible to make an informed assessment of the trustworthiness of the explanation.

The plot on the right of Figure \ref{fig:sine-plot-step3ab} is the complex and explainer model comparison plot for the prediction of interest from the \data. This figure shows the relationship between the random forest model and the LIME explainer model. The random forest model is represented by the simulated values of $x'_2$ versus $x'_1$ colored by the random forest predictions. The explainer model is represented by the solid horizontal and vertical line identify the boundaries of the quantiles that contain the prediction of interest. The color of the lines represents whether the coefficient of the corresponding indicator variable in the explainer model supports a random forest prediction of 'blue' (blue lines) or not (red lines). Additionally, the size of the simulated data points represents the proximity weight used to fit the ridge regression explainer model. The prediction of interest is represented by the diamond shaped point.

By juxtaposing the random forest predictions and the explainer model boundaries, we are able to assess the faithfulness and localness of the explainer model. First consider the claim of localness. The weights remain relatively high  outside of the intersection of the two quantile bins suggesting that the LIME explanation is highly influenced by points outside of the bin containing the prediction of interest. While it is still difficult to say whether or not the claim of localness has been violated, it is possible to say that the weights assigned to the simulated data do not agree with the local region assigned by the intersection of the quantile bins. Next, let us consider the claim of faithfulness.

Within the intersection of the $x'_1$ and $x'_2$ quantile bins, there appears to be more random forest probabilities above 0.5. This indicates why the magnitude of the coefficient associated with $x_2$ is larger than that of $x_1$. However, the pattern of the random forest predictions in this plot suggest that a better explanations for this prediction exist. One example of a better explanation would be to say that the prediction of interest received a random forest prediction greater than 0.5 since the observation of interest falls in the region where $x_1$ is less than 2.5 and $x_2$ is greater 4.5. Another more localized explanation would be to say that  the region around the prediction of interest shows that observations with $-0.3 < x_1 <= 2.5$ and $4.8 < x_2 <= 8.75$ are all assigned probabilities greater than 0.5. The procedure implemented by LIME is not flexible enough to capture either of these explanations.

The explanation scatterplot shows issues with a definition of locality and an oversimplification of the random forest model. LIME does provide an explanation for the prediction of interest, which makes sense based on the quantile bins used. However, the visualization of the complex and explainer model comparison plot solidifies the understanding that better explanations for the prediction of interest exist.

\subsection{Prediction Comparison Plot} \label{plot2}

<<sine-mid-explainer-pred>>=
# Determine the explainer model predictions with the
# random forest predictions are between 0.25 and 0.75
mid_expred <- sine_lime_default %>%
  group_by(case, sim_method) %>%
  ungroup() %>%
  filter(label_prob > 0.25, label_prob < 0.75) %>%
  select(label_prob, model_prediction)
@

\begin{figure}[!t]
<<sine-plot-compare-bins, warning = FALSE, out.width = '0.5\\textwidth', fig.width = 6.75, fig.height = 5.5>>=

# Compute the average explainer model predictions per bin
bin_mean_exp_pred <- sine_lime_default %>%
  select(case, model_prediction) %>%
  group_by(case) %>%
  slice(1) %>%
  ungroup() %>%
  full_join(sine_lime_default %>%
              select(case, feature, feature_desc) %>%
              spread(feature, feature_desc),
            by = "case") %>%
  group_by(x1, x2) %>%
  summarise(mean_exp_pred = mean(model_prediction)) %>%
  ungroup() %>%
  separate(x1, c("x1_other", "x1_upper"), sep = " <= ") %>%
  separate(x1_other, c("x1_almost_lower", "x1_other"), sep = "x1") %>%
  select(-x1_other) %>%
  separate(x1_almost_lower, c("x1_lower", "x1_other"), sep = " <") %>%
  select(-x1_other) %>%
  separate(x2, c("x2_other", "x2_upper"), sep = " <= ") %>%
  separate(x2_other, c("x2_almost_lower", "x2_other"), sep = "x2") %>%
  select(-x2_other) %>%
  separate(x2_almost_lower, c("x2_lower", "x2_other"), sep = " <") %>%
  select(-x2_other) %>%
  mutate(x1_lower = ifelse(x1_lower == "", "-Inf", x1_lower),
         x1_upper = ifelse(is.na(x1_upper), "Inf", x1_upper),
         x2_lower = ifelse(x2_lower == "", "-Inf", x2_lower),
         x2_upper = ifelse(is.na(x2_upper), "Inf", x2_upper)) %>%
  mutate_at(.vars = c("x1_lower", "x1_upper",
                      "x2_lower", "x2_upper"),
            .funs = as.numeric) %>%
  arrange(x1_lower)

# Compute the lower and upper limits of the explainer model predictions
pred_col_lower = min(bin_mean_exp_pred$mean_exp_pred)
pred_col_upper = max(bin_mean_exp_pred$mean_exp_pred)

# Plot of the average feature weights by bin
ggplot() +
  geom_rect(data = bin_mean_exp_pred,
            mapping = aes(xmin = x1_lower,
                          xmax = x1_upper,
                          ymin = x2_lower,
                          ymax = x2_upper,
                          fill = mean_exp_pred),
            alpha = 1) +
  geom_point(data = sine_lime_default %>%
               select(case, feature, feature_value,
                      label_prob, model_prediction) %>%
               spread(feature, feature_value),
             mapping =  aes(x = x1, y = x2, color = label_prob)) +
  geom_point(data = sine_lime_default %>%
               select(case, feature, feature_value,
                      label_prob, model_prediction) %>%
               spread(feature, feature_value) %>%
               mutate(rf1 = ifelse(label_prob > 0.5, TRUE, FALSE),
                      lime1 = ifelse(model_prediction > 0.5,
                                     TRUE, FALSE)) %>%
               mutate(diff = rf1 - lime1) %>%
               select(case, x1, x2, diff) %>%
               filter(diff != 0) %>%
               mutate(shape = "Random Forest \nMisclassified \nPredictions"),
             mapping =  aes(x = x1, y = x2, color = label_prob,
                            shape = shape),
             alpha = 1,
             size = 3,
             color = "black") +
  scale_color_gradient2(low = "firebrick",
                        mid = '#f7f7f7',
                        high = "steelblue",
                        midpoint = 0.5,
                        limits = c(pred_col_lower, pred_col_upper)) +
  scale_fill_gradient2(low = "firebrick",
                       mid = '#f7f7f7',
                       high = "steelblue",
                       midpoint = 0.5,
                       limits = c(pred_col_lower, pred_col_upper)) +
  scale_shape_manual(values = 1) +
  xlim(-10, 10) +
  ylim(-10, 10) +
  theme_bw(base_family = "Times", base_size = 14) +
  labs(x = TeX("$x_1$"),
       y = TeX("$x_2$"),
       shape = "",
       fill = "Average \nExplainer \nModel \nProbability \nfor 'blue'",
       color = "Random \nForest \nProbability \nfor 'blue'",
       title = "Quantile Grid Comparison of LIME Explainer \nModel Predictions to Random Forest \nPredictions") +
  guides(shape = guide_legend(order = 1),
         fill = guide_legend(order = 2, reverse = T),
         color = guide_legend(order = 3, reverse = T))

@
\caption{Plot comparing the LIME explainer models predictions to the random forest predictions in the context of the four $x_1$ and $x_2$ quantile bins. The intersection of the quantile bins are colored by the average of the test data explainer model probabilities located in the intersection. The points are the test set data and colored by the corresponding random forest probability. The observations misclassificed by the random forest are indicated by black open circles.}
\label{fig:sine-plot-compare-bins}
\end{figure}

\kgc{Add intro paragraph and edit text as necessary in this subsection}

\autoref{fig:sine-plot-compare-bins} provides a visualization of the comparison of the explainer model predictions to the random forest predictions in the context of the $x_1$ and $x_2$ quantile bins. The intersection of the bins are colored by the average explainer model prediction of the test set observation located in the region. The \data \ test set is plotted as the circles and colored by the corresponding random forest probability. The test points that the random forest misclassified are encompassed by a black open circles. The plot highlights that the explainer models are over-simplifying the random forest predictions on the diagonal (lower left to upper right) where the explainer model predictions are close to 0.5, but the random forest probabilities range from 0 to 1. It is also possible to see the locations where the explainer model is over or under estimating the random forest model predictions on the off diagonals.

\subsection{Feature Heatmap Diagnostic Plot} \label{feature-heatmap}

\begin{figure}[!b]
<<concept-heatmap, out.width = '0.5\\textwidth', fig.width = 6, fig.height = 3>>=
# Specify the number of cases and LIME input options
ncases = 10
ninputs = 5

# Create a good case of chosen feature example data
set.seed(20191008)
heatmap_data_good <- tibble(case = factor(rep(1:ncases, each = ninputs),
                                     levels = ncases:1),
                       input = factor(rep(1:ninputs, ncases)),
                       feature = factor(c(rep(1, 5),
                                          rep(2, 5),
                                          rep(3, 5),
                                          rep(1, 5),
                                          rep(1, 5),
                                          rep(4, 5),
                                          rep(1, 5),
                                          rep(3, 5),
                                          rep(1, 5),
                                          rep(4, 5)))) %>%
  mutate(input = forcats::fct_recode(input, "A" = "1", "B" = "2",
                                     "C" = "3", "D" = "4", "E" = "5"))

# Create the conceptual good heatmap
heatmap_plot_good <- ggplot(data = heatmap_data_good,
                            mapping = aes(x = input,
                                          y = case,
                                          fill = feature,
                                          color = feature)) +
  geom_tile() +
  labs(x = "Implementation Method",
       y = "Case",
       fill = "Feature",
       title = "Situation 1: \nConsistent Explanations") +
  theme_bw(base_family = "Times", base_size = 12) +
  scale_fill_grey() +
  scale_color_grey() +
  theme(legend.position = "none")

# Create a bad case of chosen feature example data
set.seed(20190627)
heatmap_data_bad <- tibble(case = factor(rep(1:ncases, ninputs),
                                     levels = ncases:1),
                       input = factor(rep(1:ninputs, each = ncases)),
                       feature = factor(rep(c(1, 2, 4, 3, 2), each = 10))) %>%
  mutate(input = forcats::fct_recode(input, "A" = "1", "B" = "2",
                                     "C" = "3", "D" = "4", "E" = "5"))

# Create the conceptual bad heatmap
heatmap_plot_bad <- ggplot(data = heatmap_data_bad,
                            mapping = aes(x = input,
                                          y = case,
                                          fill = feature,
                                          color = feature)) +
  geom_tile() +
  labs(x = "Implementation Method",
       y = "Case",
       fill = "Feature",
       title = "Situation 2: \nInconsistent Explanations") +
  theme_bw(base_family = "Times", base_size = 12) +
  scale_fill_grey() + 
  scale_color_grey()

heatmap_leg <- get_legend(heatmap_plot_bad)
heatmap_plot_bad <- heatmap_plot_bad + theme(legend.position = 'none')

# Join the plots
plot_grid(heatmap_plot_good, heatmap_plot_bad, heatmap_leg,
          nrow = 1,
          rel_widths = c(0.45, 0.45, 0.1))

@
\caption{Two hypothetical examples of feature heatmaps showing the top feature chosen for 10 cases across 5 different implementations of LIME (sets of tuning parameters). The color of the cell indicates the feature chosen by LIME. The plots represent two possible situations that may arise when applying LIME to a set of predictions.}
\label{fig:concept-heatmap}
\end{figure}

\begin{figure}[!t]
<<sine-feature-heatmap, out.width = '0.5\\textwidth', fig.width = 5, fig.height = 5.5>>=
feature_heatmap(sine_lime_explain$explain,
                order_method = "PCA") +
  theme_bw(base_family = "Times", base_size = 10) +
  theme(legend.position = "bottom",
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) +
  labs(y = "Case")
@
\caption{Feature heatmap of the various LIME implementations applied to the \data. The cases from the test set are plotted on the y-axis, and the implementation methods are included on the x-axis. The colors of the tiles indicate the feature selected by LIME for the corresponding case and implementation method. The top faceted row includes the first features selected by LIME, and the bottom faceted row includes the second features selected by LIME. The faceted columns separate the kernel density implementation method from the quantile bin implementations. The vertical striping seen in the plot indicates that LIME is not consistent in selecting features across implementation methods.}
\label{fig:sine-feature-heatmap}
\end{figure}

Explanations produced by LIME are likely affected by exact choice of tuning parameters. An example of this was shown by Figures \ref{fig:concept-plot-good} and \ref{fig:concept-plot-bad} where the method used to weight the observations influenced the explanation. As of the time of writing this manuscript, there are no recommendations or procedures provided for how to determine which method to use besides for the default settings in \emph{lime} \kgc{(confirm this)}. In order to compare the explanations produced by LIME using different tuning parameters, we view an overview of all the explanations in the feature heatmap.

We plot the features selected by LIME for all of the cases and tuning parameters in heatmaps separated by the position of importance assigned by LIME in a plot that will be referred to as a feature heatmap. That is, for LIME applied for $t$ sets of tuning parameters to $n$ cases to select the $f$ top features, create $f$ heatmaps (one for each of the positions of importance) with the cases on the y-axis, the tuning parameters on the x-axis, and the cells colored by the feature chosen for the corresponding case and tuning parameter. This plot will be used assess the locality of the explanations and to compare results from different input options.

Two hypothetical examples of feature heatmaps are included in \autoref{fig:concept-heatmap}. The plots were created with the assumption that LIME was applied to select the top feature out of $p=8$ features for $n=10$ cases with $t=5$ sets of tuning parameters. If LIME were producing local explanations, it would be expected that the top features selected by LIME would vary for predictions located in different regions of the feature space unless a feature or several features are the deterministic features throughout the entire feature space. Additionally, if the tuning parameters used when implementing LIME did not affect the feature selected by LIME, the selected feature would be the same across all implementations for a case.

The plots in \autoref{fig:concept-heatmap} depict two different situations that may arise when applying LIME. Situation 1 shows an example where the features selected across implementation methods within a case are consistent, and the features selected by vary across cases. This is the ideal situation, because regardless which implementation method is used, the LIME explanations do not vary, and the explanations appear to be local since the features vary between cases. Situation 2 shows an example where the features selected across implementation methods within a case vary, but the features selected within an implementation method across cases are the same. This situation \sout{is not ideal, because it} indicates that the features selected by LIME are dependent on the implementation method used, and the explanations are not local because the same feature is chosen regardless of the case. In practice, it is expected that the plot will exhibit a combination of these two situations.

\autoref{fig:sine-feature-heatmap} shows the feature heatmap for the LIME implementations applied to the \data. The top row of the plot contains the features selected as the most important by LIME, and the bottom row contains the second most important feature selected by LIME. For the quantile bin implementations, the original features prior to the interpretability transformation are plotted  since it is obvious that different features would be selected when the sizes of the bins change from one implementation to the next. This figure shows a clear difference in the explanations produced by LIME for the kernel density and two quantile bin methods and the other quantile bin methods. For both the kernel density and two quantile bin implementations, LIME selects $x_1$ as the most important feature and $x_2$ as the second most important feature across all cases in the test set. There is more variability in the features selected by LIME for the three to six quantile bin implementations. For these implementations, there is a mix of horizontal and vertical stripes, which suggests that LIME is not consistently providing the sample explanation across implementation methods. It is also interesting, that the implementations of 3 and 5 bins leads to the selection of the random noise variable of $x_3$ as an important variable in many predictions, which should not be the case.

\subsection{Assessment Metric Plot}

\begin{figure}[!t]
<<sine-metric-plot, out.width = '0.5\\textwidth', fig.width = 4.5, fig.height = 4, warning = FALSE>>=

# Create the metric plot
metric_plot(sine_lime_explain$explain) +
  theme_bw(base_family = "Times") +
  scale_color_gradient(low = "grey10", high = "grey90")

@
\caption{Example of a metric comparison plot using the \data. Each row of the plot corresponds to one of three metrics: average fidelity, average $R^2$, or MSEE. The tuning parameters from the different LIME implementations are plotted on the x-axis, and the metric values are shown on the y-axis. The points are colored by rank within a metric indicating best to worst (dark to light). The kernel density simulation methods performs well according to all three metrics.}
\label{fig:sine-metric-plot}
\end{figure}

The feature heatmap for the \data \ in the previous section showed an example of how LIME explanations are not always consistent across \hh{this sounds like R versus python implementation. It's not what you mean} implementation methods. As a result, it is necessary to choose \hh{tuning parameters} that produce reliable explanations. One way to do this, \sout{would be} to apply LIME using different implementations, and then compute assessment metrics to determine the optimal tuning parameters. We will discuss several metrics that could be used for this purpose and present a comparison of the metrics in a plot. \kgc{***Right now, I have not included any variability in these plots. I could add standard deviation bars or change these to box plot.}

\kgc{I have moved all notation to the appendix. I will explain the metrics here in words.}

\begin{itemize}
\item $R^2$: Once LIME has been applied to all observations of interest, an average $R^2$ can be computed from the explainer models within an implementation method. 
\item Fidelity metric: for measuring the faithfulness of the explainer model to the complex model. This is done by comparing the complex and simple model predictions for each of the values in the simulated dataset accounting for the assigned weight. 
\item MSEE: meant to measure the faithfulness of the explainer model to the complex model by comparing their predictions, but instead of computing a squared difference over all observations in the simulated data, we only consider the observation of interest and compute the average squared deviation over the observations in the test set for an implementation of LIME. 
\end{itemize}

In \autoref{fig:sine-metric-plot}, the average fidelity is lowest for the kernel density simulation method increases as the number of quantile bins increase. This would suggest that the LIME implementation using the kernel density estimate provides the best local approximation to the random forest model on average. Note that the points in the plot are colored such that darker indicates a better metric value and lighter indicates a worse metric value.

The 6 quantile bin simulation method has the lowest MSEE followed closely by the kernel density method, which suggests that these methods have explainer models that best approximate the complex model for the prediction of interest on average. The MSEE increases as the number of quantile bins increases.

The average $R^2$ value is highest for the kernel density simulation method and decreases as the number of quantile bins increase. This metric agrees with the average fidelity, and it suggests that the the kernel density method leads to the best fitting explainer models on average.

For the \data, the metrics of average fidelity and average $R^2$ are in perfect agreement \hh{what do you mean by perfect agreement? and how do you use the fidelity measure?} with which simulation methods lead to the recommended LIME methods. The MSEE is in agreement \hh{with ? } in terms of the kernel density method performing well in terms of faithfulness, but it orders the quantile bin methods in the opposite order from the average fidelity and $R^2$ values. This may be due to the MSEE only taking into account the prediction of interest and not the full simulated dataset.

The kernel density method performed well in regards to all three metrics. Recall that \autoref{fig:sine-feature-heatmap} indicated that the LIME kernel density method selected the same feature across all cases in the test dataset for both the first and second features. It appears that a global trend may be the best explanation for this example, which may be reasonable considering that we know that both $x_1$ and $x_2$ are the two features that should be the features used by the random forest to distinguish between response categories.

\section{Application to Bullet Matching Data} \label{application}

The \data \ is a relatively simple problem where the true decision boundary can be easily visualized and diagnostics for the performance of LIME can directly be compared to ground truth. In practice, we usually encounter more complicated situations. The remainder of this section provides a discussion of the visual diagnostics at the example of a practical data problem investigating the similarity of marks on fired bullets.

\subsection{Bullet Matching Data}

\begin{figure}[!t]
\centering
\includegraphics[width=1.5in]{./figure-static/gun.png}
\includegraphics[width=1.58in]{./figure-static/bullet.png}
\includegraphics[width=3in]{./figure-static/striae.png}
\caption{(Top left) Traditionally rifled gun barrel. Grooves and lands alternate to give bullets a spin during the firing process.
Barrel create markings (striations) on a bullet when fired.
(Top right) Image of a fired bullet. The vertical stripes along the lower half of the bullet show groove and land engraved areas. The land engraved areas contain the microscopic striations created when the bullet passed through the barrel of the gun. (Bottom) Zoomed in image of a land engraved area showing striations (vertical lines).}
\label{fig:bullet}
\end{figure}

In current practice, forensic firearm  examiners evaluate whether two bullets come from the same source (are fired from the same gun) or from different sources based on microscopic comparison of the striation patterns engraved on bullets during the firing process (see \autoref{fig:bullet}). This process is based on a visual and therefore subjective assessment of the evidence under a comparison microscope. The lack of objective evaluation and the associated absence of established error rates has first been criticized by the National Research Council \cite{nrc:2009} and later by the President's Council of Advisors on Science and Technology \cite{pcast:2016}.

In response, \citet{hare:2016} proposed an automated machine learning method for bullet matching to complement a visual inspection by firearm examiners. Based on high-resolution topological scans of land engraved areas \citet{hare:2016} obtain signatures of  striations from two bullet lands (\autoref{fig:signatures}). Nine features quantifying the similarity of signatures, such as the cross-correlation function, the distance between signatures, and the number of matching striae, are extracted and used to train a random forest model to determine the probability of a comparison resulting from the same source (matching signatures) or from different sources (non-matching signatures).

\begin{figure}[!t]
\centering
\includegraphics[width=3.5in]{./figure-static/signatures.png}
\label{fig:signatures}
\caption{Bullet signatures extracted from two bullets fired through the same barrel. The two signatures come from the same barrel-land and therefore have very similar patterns. The features used in the random forest from \citet{hare:2016} are different metrics that measure the similarity between two such signatures.}
\end{figure}

<<bullet-data>>=

# Load the hamby data
bullet_train <- read.csv("../data/hamby173and252_train.csv")
bullet_test <- read.csv("../data/hamby224_test.csv")

# Extract the features and order them based on feature importance
bullet_features <- rownames(bulletxtrctr::rtrees$importance)
bullet_features_ordered <-
  data.frame(feature = rownames(bulletxtrctr::rtrees$importance),
             MeanDecreaseGini = bulletxtrctr::rtrees$importance) %>%
  arrange(desc(MeanDecreaseGini)) %>%
  mutate(feature = fct_recode(feature,
                              "CCF" = "ccf",
                              "CMS" = "cms",
                              "Matches" = "matches",
                              "Mismatches" = "mismatches",
                              "Non-CMS" = "non_cms",
                              "Rough Correlation" = "rough_cor",
                              "Distance Std Dev" = "sd_D",
                              "Distance" = "D",
                              "Sum Peaks" = "sum_peaks"))

bullet_features_ordered <- bullet_features_ordered %>%
  mutate(feature = factor(feature, levels = bullet_features_ordered$feature))

@

The random forest model trained in \citet{hare:2016} is available as object rtrees from the \emph{bulletxtrctr} R package. rtrees is trained on a set of scans obtained from one set of bullets of the James Hamby Consecutively Rifled Ruger Barrel Study \citep{hamby:2009} and based on \Sexpr{dim(bullet_train)[1]} land-to-land comparisons.

\begin{figure*}[!b]
<<bullet-plot-rfpcp, out.width = '\\textwidth', warning = FALSE>>=

# Create (or load) the parallel coordinate plot
if (file.exists("./figure-static/bullet_pcp.png")) {

  # Load and print the plot
  knitr::include_graphics("./figure-static/bullet_pcp.png")

} else {

  # Create the plot
  bullet_pcp <- bullet_train %>%
    select(all_of(bullet_features), samesource, rfscore) %>%
    bind_rows(bullet_test %>%
                select(all_of(bullet_features), samesource, rfscore),
              .id = "set") %>%
    mutate(set = fct_recode(set,
                            "Training Set" = "1",
                            "Testing Set" = "2"),
           samesource = fct_recode(factor(samesource),
                                  "Same Source = TRUE" = "TRUE",
                                  "Same Source = FALSE" = "FALSE")) %>%
    rename("CCF" = "ccf", "CMS" = "cms", "Matches" = "matches",
           "Mismatches" = "mismatches", "Non-CMS" = "non_cms",
           "Rough Correlation" = "rough_cor", "Distance Std Dev" = "sd_D",
           "Distance" = "D", "Sum Peaks" = "sum_peaks") %>%
    na.omit() %>%
    ggplot(aes(color = rfscore)) +
    geom_pcp(aes(vars = vars(bullet_features_ordered$feature)),
             alpha = 0.2) +
    facet_grid(set ~ samesource) +
    scale_color_gradient2(low = "grey50",
                          high = "darkorange",
                          midpoint = 0.5) +
    theme_bw(base_family = "Times", base_size = 10) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          strip.placement = "outside",
          strip.background = element_rect(color = "white",
                                          fill = "white")) +
    labs(x = "Features Ordered by Random Forest Variable Importance \n(highest to lowest from left to right)",
         y = "Scaled Feature Values",
         color = "Random \nForest \nProbability")

  # Save the plot
  ggplot2::ggsave(plot = bullet_pcp,
                  filename = "./figure-static/bullet_pcp.png",
                  width = 7.5,
                  height = 3.5,
                  units = "in")
}

@
\caption{Parallel coordinate plots of rtrees training and testing data. The training data are included in the plots on the top row, and the testing data are included in the plots on the bottom row. The left column contains the observations which are know to be comparisons of lands that are not from the same gun, and the known same source comparisons are on the right. The y-axis shows the standardized feature values, and the x-axis shows the features used to fit the random forest (ordered by feature importance). Each line corresponds to a comparison, and the color of the line represents the associated random forest probability. These figures show a clear relationship between the feature values and the probability returned by the random forest.}
\label{fig:bullet-plot-rfpcp}
\end{figure*}

rtrees was tested on another set of bullets from the Hamby study with \Sexpr{dim(bullet_test)[1]} rows of land comparisons. \autoref{fig:bullet-plot-rfpcp} shows parallel coordinate plots of the rtrees training (top row) and testing (bottom row) datasets. The plots on the left contain comparisons know to be from from different sources, and the plots on the right contain comparisons know to be from the same source. Each line represents one observation in the data, and the color of the line represents the by the corresponding random forest probability. The standardized feature values are plotted on the y-axis, and the features are plotted on the x-axis, which are ordered from left to right from the highest to lowest random forest feature importance.

The majority of observations with random forest probabilities close to 1 have a clear pattern of corresponding feature values as can be seen in the plots where same source is known to be true. The observations where the random forest is wrong in returning high probabilities when same source is known to be true (i.e. same source is true but the random forest probabilities are between 0 and 0.5) have feature values that reflect those of observations where same source is known to be false as seen in the plots on the left. These plots provide insight into why the random forest is producing poor random forest probabilities for these observations.

Since firearm identification is commonly used as evidence for convictions in court cases, it is important to be able to understand and assess the model that is used to quantify the probability that a bullet was fired from a gun. An application of LIME to rtrees could provide an understanding of the key variables used by the random forest model to make a prediction. However, just as it is important to assess the random forest model for this high-stakes application, it is also important to assess the LIME explanations to make sure they are providing a trustworthiness understanding of the random forest model. We will apply LIME to rtrees and use our visual diagnostics to assess different implementations of LIME.

\subsection{Application of LIME to Bullet Matching Data}

<<bullet-lime>>=

# Apply LIME to all but two cases without returning the permutations
if (file.exists("../data/hamby_lime.rds")){

  # Load the files
  #bullet_lime_noperms <- readRDS("../data/hamby_lime.rds")
  bullet_explain_noperms <- readRDS("../data/hamby_explain.rds")

} else {

  # Apply lime with various input options to the hamby data
  bullet_lime_explain_noperms <- apply_lime(
    train = bullet_train %>% select(all_of(bullet_features)),
    test = bullet_test %>%
      select(all_of(bullet_features)) %>%
      na.omit(),
    model = bulletxtrctr::rtrees,
    label = as.character(TRUE),
    n_features = 3,
    sim_method = c('quantile_bins', 'equal_bins',
                   'kernel_density', 'normal_approx'),
    nbins = 2:6,
    feature_select = "auto",
    dist_fun = "gower",
    kernel_width = NULL,
    gower_pow = c(0.5, 1, 10),
    return_perms = FALSE,
    all_fs = FALSE,
    seed = 20190914)

  # Separate the lime and explain parts of the results
  bullet_lime_noperms <- bullet_lime_explain_noperms$lime
  bullet_explain_noperms <- bullet_lime_explain_noperms$explain

  # Save the output objects
  saveRDS(object = bullet_lime_noperms,
          file = "../data/hamby_lime.rds")
  saveRDS(object = bullet_explain_noperms,
          file = "../data/hamby_explain.rds")

}

@

<<bullet-lime-perms>>=

# Specify two cases of interest
bullet_poi_match <- unique(bullet_explain_noperms$case)[c(325)]
bullet_poi_nonmatch <- unique(bullet_explain_noperms$case)[c(20)]

# Apply LIME to two cases with the permutations returned
bullet_lime_explain_perms <- apply_lime(
  train = bullet_train %>% select(all_of(bullet_features)),
  test = bullet_test %>%
    filter(case %in% bullet_poi_match) %>%
    bind_rows(bullet_test %>%
    filter(case %in% bullet_poi_nonmatch)) %>%
    select(all_of(bullet_features)),
  model = bulletxtrctr::rtrees,
  label = as.character(TRUE),
  n_features = 3,
  sim_method = c('quantile_bins', 'equal_bins', 'kernel_density', 'normal_approx'),
  nbins = 3,
  feature_select = "auto",
  dist_fun = "gower",
  kernel_width = NULL,
  gower_pow = 0.5,
  return_perms = TRUE,
  all_fs = FALSE,
  seed = 20190914)

# Separate the lime and explain parts of the results
bullet_lime_perms <- bullet_lime_explain_perms$lime
bullet_explain_perms <- bullet_lime_explain_perms$explain %>%
  mutate(case = ifelse(case == 1,
                       bullet_poi_match,
                       bullet_poi_nonmatch))

@

<<bullet-lime-combined>>=

# Determine the implementation and case number of the poi
# in the no_perms data
poi_cases_no_perms <- bullet_explain_noperms %>%
  filter(case %in% c(bullet_poi_match, bullet_poi_nonmatch),
         nbins %in% c(3, NA),
         gower_pow == 0.5) %>%
  select(case, implementation) %>%
  unique()

# Join the no perms data (with poi removed) with the
# perms data (perms removed)
bullet_explain <- bullet_explain_noperms %>%
  anti_join(poi_cases_no_perms,
            by = c("implementation", "case")) %>%
  bind_rows(bullet_explain_perms %>%
              select(-perms_raw, -perms_numerified,
                     -perms_pred_simple, -perms_pred_complex,
                     -weights))

@

\begin{figure*}[!th]
<<bullet-feature-heatmap, out.width = '\\textwidth', fig.width = 18, fig.height = 10.5>>=

# Create a feature heatmap
feature_heatmap(bullet_explain %>%
                  mutate(label = as.factor(label)),
                facet_var = na.omit(bullet_test$samesource),
                order_method = "PCA") +
  scale_fill_gretchenalbrecht(palette = "last_rays",
                              discrete = TRUE) +
  theme_bw(base_family = "Times", base_size = 10) +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) +
  labs(y = "Case")

@
\caption{Feature heatmap of the 36 LIME implementations applied to the bullet comparison data test set. In addition to faceting the results by simulation method and order a feature was selected by LIME as done in \autoref{fig:sine-feature-heatmap}, this plot has been faceted by the Gower power and whether the the observation is from a match (TRUE) or non-match (FALSE). This plot shows several key insights about the LIME explanations. First, the features selected by LIME for the density simulation methods are mostly the same for all implementations and all cases. Second, the features selected by LIME for the bin based methods are affected by the number of bins but not the Gower power. Third, the explanations produced by LIME using bin based methods result in different important features for the matches and non-matches. \kgc{***Need to rotate the facet labels, so I can make the text bigger.}}
\label{fig:bullet-feature-heatmap}
\end{figure*}

We apply LIME to each prediction from the bullet test data obtained from the 'rtrees' random forest model for each of the four sampling methods (equally spaced bins, quantile bins, kernel density estimation, and normal approximation). For each of the bin based sampling methods, LIME was applied for 2 to 6 bins. It was decided to use 6 bins as the maximum, since the larger the number of bins, the more complex the explanation becomes. Each simulation method was implemented three times with Gower exponents of 0.5, 1, and 10. Thus, a total of $12\times 3=36$ different implementations of LIME were performed. These implementations of LIME were performed using our R package \emph{limeaid}. Each implementation was set to return 3 features by LIME and feature selection was performed using the highest weights method.

\subsection{LIME Assessment Visualizations}

To get an overview of the LIME explanations from the 36 implementations, we consider our heatmap diagnostic plot for comparing the LIME implementations first shown in \autoref{fig:bullet-feature-heatmap}. The plot facets the features selected in the LIME explanations by the simulation method, the Gower power, the order the feature was chosen, and whether the observation is from a known match or non-match of bullet signatures. This plot highlights several key features of the LIME explanations from the bullet matching dataset.

First of all, the density simulation methods produced the same explanations for almost all cases and LIME implementation methods. As a result, the LIME explanations for the density implementation methods are global and not local. Second, within a bin based simulation method, the features selected by LIME for an observation often vary based on the number of bins used but do not appear to vary based on the Gower power used. Especially with the equal bin explanations, there are vertical stripes that suggest a dependence of the LIME explanations on the number of bins used. The vertical stripes are not as apparent with the quantile bins. Lastly, there are clear differences between the LIME explanations for the cases that are matches and those that are not matches which are produced by the bin based simulation methods. This provides evidence that suggests that the features which the random forests uses to classify a match are different from the features used by the random forest to classify a non-match. The most important insight \autoref{fig:bullet-feature-heatmap} highlights is the dependence of the explanations on the LIME implementation method for many of the observations in the test data.

\begin{figure*}[!t]
<<bullet-metric-plot, out.width = '\\textwidth', warning = FALSE, fig.width = 10, fig.height = 4>>=

# Create a metric comparison plot
metric_plot(bullet_explain %>% mutate(label = as.factor(label))) +
  theme_bw(base_family = "Times") +
  scale_color_gradient(low = "grey10", high = "grey90") +
  labs(color = "Rank \n(within \na metric)")

@
\caption{Plot of LIME assessment metrics for the 36 different implementations of LIME applied to the bullet comparison data test set. The shape of the points represents the power used for the Gower distance calculation, and the color of the points represents the rank associated with that observation within a metric. The density simulation methods perform well for all metrics, but the bin based metrics often do not agree in terms of performance across metrics.}
\label{fig:bullet-metric-plot}
\end{figure*}

To try to identify the LIME implementation method with the most trustworthy set of explanations, we created an assessment metric plot shown in \autoref{fig:bullet-metric-plot}. The three metrics of average fidelity, average $R^2$, and MSEE were computed for each of the simulation methods and Gower power used to implement LIME. The plot is faceted by the simulation method, and the shape of a point represents the Gower power. The color of a point represents the rank within a metric. That is, the darker a point, the better performance of that implementation method based on the metric.

The density simulation methods performed well across all implementation methods. This is an interesting result, since \autoref{fig:bullet-feature-heatmap} shows that the density methods results in global explanations. The metric values for the bin based implementation methods do not agree across metrics. For example, 2 and 3 quantile bins performed well according to the average $R^2$ but poorly according to MSEE. As a result, with the bin based methods, it is difficult to know which method to recommend. When considering the metrics across the Gower power used, the implementations using a power of 0.5 perform best or as well as the other powers in across all simulation methods. This suggests that the power that leads to a more global explanation is preferred by LIME in this example.

Unfortunately, \autoref{fig:bullet-feature-heatmap} leaves us without a clear indication of which set of explanations to use to explain the random forest. Perhaps we can say that the kernel density method, 3 equal bins, and 3 quantile bins are some of the best performing methods. To better understand the explanations provided by these three methods, we take a closer look at explanations from these methods for two observations of interest where one is a known non-match (case \Sexpr{bullet_poi_nonmatch}) and the other is a known match (case \Sexpr{bullet_poi_match}).

Figures \ref{fig:bullet-eois-nonmatch} and \ref{fig:bullet-eois-match} contain plots that provide this closer look for the known non-match and match, respectively. The top row of plots in each figure are the explanation plots from \emph{lime}. The bottom row of plots show scatterplots of the features selected by LIME colored by the random forest model prediction. The location of the prediction of interest is indicated on the scatterplots by a diamond, and black solid lines are included on the plots representing the bin divisions for implementations using bins. The bottom row plots are created using \emph{limeaid}. The plots within a column are associated with one of the three implementation methods (kernel density, 3 equal bins, or 3 quantile bins).

The scatterplots provide a visualization that helps to explain the LIME explanation. For example, consider the explanation for case \Sexpr{bullet_poi_nonmatch} when 3 quantile bins were used. The explanation plot from \emph{lime} shows that case \Sexpr{bullet_poi_nonmatch} having an observed CCF value greater than 0.320 supports a random forest prediction in favor of a match. The scatter plots show that many of the simulated values with CCF greater then 0.320 have random forest predictions greater than 0.5. Additionally, the LIME explanation indicates that a value of matches less than or equal to 1.66 contradicts a prediction in favor of a match. The scatter plots shows that almost all simulated values with a value of matches less than or equal to 1.66 have random forest predictions close to 0. Similar statements can be made about the 3 equal bin explanation for this case and the bin based implementations for the known match observation explanations.

While the scatterplots provide visual explanations for the LIME explanations, some of them indicate that LIME falls short of a good explanation of the random forest predictions. Again, consider the explanation for case 325 when 3 quantile bins were used. From looking at the scatter plot of CCF versus matches, a better explanation for the random forest prediction would be to say that because the prediction of interest has a value of CCF less than 0.8 (approximately) and a value of matches less than 7 (approximately), the random forest is providing a prediction that supports a non-match. The relationship between ccf and rough correlation does not provide much evidence to support the random forest prediction one way or the other due to the mixture of random forest predictions ranging from 0 to 1 in most regressions, but there is a pentagon shaped region at the bottom of the scatter plot of matches versus rough correlation that the prediction of interest falls in that supports the random forest prediction of a non-match.

<<bullet-eoi-plots, message = FALSE>>=
bullet_explain_perms <- bullet_explain_perms %>%
  mutate(case = ifelse(case == bullet_poi_nonmatch,
                       paste(case, "(non-match)"),
                       paste(case, "(match)")))

eoi1_3qb <- eoi_plot(bullet_explain_perms[1:3,], alpha = 0.9, weights = FALSE) +
  scale_color_gradient2(low = "grey50",
                        high = "darkorange",
                        midpoint = 0.5,
                        limits = c(0, 1)) +
  scale_fill_gradient2(low = "grey50",
                        high = "darkorange",
                        midpoint = 0.5,
                        limits = c(0, 1)) +
  theme_bw(base_family = "Times", base_size = 8) +
  theme(strip.placement = "outside",
        strip.background = element_rect(color = "white",
                                        fill = "white"))

eoi2_3qb <- eoi_plot(bullet_explain_perms[4:6,], alpha = 0.9, weights = FALSE) +
  scale_color_gradient2(low = "grey50",
                        high = "darkorange",
                        midpoint = 0.5,
                        limits = c(0, 1)) +
  scale_fill_gradient2(low = "grey50",
                        high = "darkorange",
                        midpoint = 0.5,
                        limits = c(0, 1)) +
  theme_bw(base_family = "Times", base_size = 8) +
  theme(strip.placement = "outside",
        strip.background = element_rect(color = "white",
                                        fill = "white"))

eoi1_3eb <- eoi_plot(bullet_explain_perms[7:9,], alpha = 0.9, weights = FALSE) +
  scale_color_gradient2(low = "grey50",
                        high = "darkorange",
                        midpoint = 0.5,
                        limits = c(0, 1)) +
  scale_fill_gradient2(low = "grey50",
                        high = "darkorange",
                        midpoint = 0.5,
                        limits = c(0, 1)) +
  theme_bw(base_family = "Times", base_size = 8) +
  theme(strip.placement = "outside",
        strip.background = element_rect(color = "white",
                                        fill = "white"))

eoi2_3eb <- eoi_plot(bullet_explain_perms[10:12,], alpha = 0.9, weights = FALSE) +
  scale_color_gradient2(low = "grey50",
                        high = "darkorange",
                        midpoint = 0.5,
                        limits = c(0, 1)) +
  scale_fill_gradient2(low = "grey50",
                        high = "darkorange",
                        midpoint = 0.5,
                        limits = c(0, 1)) +
  theme_bw(base_family = "Times", base_size = 8) +
  theme(strip.placement = "outside",
        strip.background = element_rect(color = "white",
                                        fill = "white"))

eoi1_kd <- eoi_plot(bullet_explain_perms[13:15,], alpha = 0.9, weights = FALSE) +
  scale_color_gradient2(low = "grey50",
                        high = "darkorange",
                        midpoint = 0.5,
                        limits = c(0, 1)) +
  scale_fill_gradient2(low = "grey50",
                        high = "darkorange",
                        midpoint = 0.5,
                        limits = c(0, 1)) +
  theme_bw(base_family = "Times", base_size = 8) +
  theme(strip.placement = "outside",
        strip.background = element_rect(color = "white",
                                        fill = "white"))

eoi2_kd <- eoi_plot(bullet_explain_perms[16:18,], alpha = 0.9, weights = FALSE) +
  scale_color_gradient2(low = "grey45",
                        high = "darkorange",
                        midpoint = 0.5,
                        limits = c(0, 1)) +
  scale_fill_gradient2(low = "grey45",
                        high = "darkorange",
                        midpoint = 0.5,
                        limits = c(0, 1)) +
  theme_bw(base_family = "Times", base_size = 8) +
  theme(strip.placement = "outside",
        strip.background = element_rect(color = "white",
                                        fill = "white"))

pf1_3qb <- plot_features(bullet_explain_perms[1:3,]) +
  scale_fill_manual(values = c("darkorange", "grey50"))
pf2_3qb <- plot_features(bullet_explain_perms[4:6,]) +
  scale_fill_manual(values = c("darkorange", "grey50"))
pf1_3eb <- plot_features(bullet_explain_perms[7:9,]) +
  scale_fill_manual(values = c("darkorange", "grey50"))
pf2_3eb <- plot_features(bullet_explain_perms[10:12,]) +
  scale_fill_manual(values = c("darkorange", "grey50"))
pf1_kd <- plot_features(bullet_explain_perms[13:15,]) +
  scale_fill_manual(values = c("darkorange", "grey50"))
pf2_kd <- plot_features(bullet_explain_perms[16:18,]) +
  scale_fill_manual(values = c("darkorange", "grey50"))
@

\begin{figure*}[!htbp]
<<bullet-eois-nonmatch, out.width = '\\textwidth', fig.width = 12, fig.height = 6.25, message = FALSE>>=
# Join the plots
plot_grid(pf2_3qb, pf2_3eb, pf2_kd,
          eoi2_3qb, eoi2_3eb, eoi2_kd,
          nrow = 2,
          rel_heights = c(0.45, 0.55))
@
\caption{Plots of LIME explanations for one case in the test data that is a known non-match. Each column contains plots associated with a different implementation (3 quantile bins, 3 equal bins, or kernel density). The top row of plots are the explanation plots from \emph{lime}. The bottom row shows scatter plots of the simulated data associated with the prediction of interest. The features plotted are those chosen by LIME in the explanations, and the points are colored by the the random forest predictions. Lines showing the divisions created in the feature space by the bin based LIME methods are included as solid black lines. The scatter plots can be used to better understand the LIME explanation and assess if it is a good explanation.}
\label{fig:bullet-eois-nonmatch}

\vspace*{\floatsep}

<<bullet-eois-match, out.width = '\\textwidth', fig.width = 12, fig.height = 6.25, message = FALSE>>=
# Join the plots
plot_grid(pf1_3qb, pf1_3eb, pf1_kd,
          eoi1_3qb, eoi1_3eb, eoi1_kd,
          nrow = 2,
          rel_heights = c(0.45, 0.55))
@
\caption{Plots with the same structure as \ref{fig:bullet-eois-match} but for an observation from the test data that is a known match.}
\label{fig:bullet-eois-match}
\end{figure*}

The scatter plots of the kernel density implementations for both the match and non-match case show that almost all of the simulated values have random forest predictions less than 0.5, which provide evidence in favor of a non-match. It appears that simulation method is not providing enough values to cover the feature space that hit regions where the random forest provides predictions above 0.5. The training data has a much smaller amount of matches (\Sexpr{sum(bullet_train$samesource)}) than non-matches (\Sexpr{sum(bullet_train$samesource == FALSE)}), and this simulation method is clearly affected by this imbalance in the two classification categories. Furthermore, this may be the cause of the minimal amount of variability in the LIME explanations across all of the cases in the test data.

Without applying multiple implementations LIME to the bullet test data or viewing diagnostic plots of the LIME explanations, it may be very possible to formulate reasons why the LIME explanations make sense. However, the sequence of plots in this section (Figures \ref{fig:bullet-feature-heatmap}, \ref{fig:bullet-lime-expls}, \ref{fig:bullet-metric-plot}, \ref{fig:bullet-eois-match}, and \ref{fig:bullet-eois-nonmatch}) suggest that we should be cautious to trust any of these LIME explanations. While some of them provide an explanation that may be reasonable, there could be better explanations (as seen in the 3 quantile bin case of \autoref{fig:bullet-eois-match}), and some of them provide explanations that make no sense (as seen in \autoref{fig:bullet-lime-expls}). It appears that either LIME needs to be further tuned to provide trustworthy and good explanations, or a different approach may provide better insight. As glimpsed with the scatter plots in Figures \ref{fig:bullet-eois-match} and \ref{fig:bullet-eois-nonmatch}, the more traditional approach to explanation random forest predictions by plotting the random forest predictions over the feature space (partial dependence plots), could provide better insight into the complex model with no need to assess the explanation method if the sampling method is well chosen.

\section{Discussion} \label{discussion}

\kgc{Break into sections: (1) visualization limitations (2) future research (3) concerns about LIME}

%\kgc{Possible content to add here:} \kgc{Need to work this in}: \hh{In terms of limitations of the visualizations: first two features span the x and y axis, additional features can be used for faceting. four features is completely feasible, beyond that the visualization might not work as well. The number of bins should be in the single digits. A large number of small multiples \citep{Becker:1996gy} needs a strong signal in the data to be effective - otherwise the visualization might be affected by change blindness \citep{simonsChangeBlindness1997, review19}. }

%The \data \ provide a \kge{neat} \kge{very clean} example of how to use the proposed visualizations to assess a single LIME explanation \kge{with two features. Once the number of features is greater than 3, adjustments will need to be made to the plots. In this case, multiple plots will be required to visualize the majority of the steps in the LIME procedure. Reasonable extensions would be scatterplot matrices or the use of faceting. \hh{XXX this is too vague: when do you use scatterplot matrices, what is the advantage of faceting. Make your solutions more concrete by discussing them as well as their limitations. }

%In the case of faceting, the} \hh{first two features} \kge{can} \hh{span the x and y axis,} \kge{and} \hh{additional features can be} \kge{used as the facets.} We have included some examples of such plots in Appendix \ref{scatter-plots} that take into the feature $x_3$ from the \data \ in the visualization of the LIME procedure.

%\hh{\sout{In terms of limitations of the visualizations: first two features span the x and y axis, additional features can be used for faceting. four features is completely feasible, beyond that the visualization might not work as well. The number of bins should be in the single digits. A large number of small multiples (reference to Cleveland?) needs a strong signal in the data to be effective - otherwise the visualization might be affected by change blindness} \citet{simons:1997, vanderplas:2020}.}

%\hh{Both large number of observations and large number of features make visual assessments harder:} \kgc{I've decided to not discuss a large amount of data, because that really isn't a problem due to the size of the simulated dataset being chosen by the user, and there is not a need to go above 5000. Whereas, it is reasonable to expect that a user may select more than two features.} \hh{That the size of the data is chosen by the user is actually a good point to make. }

%\hh{the number of features can also be controlled by the user - lime is interested in a small number of features, as earlier mentioned, using faceting or scatterplot matrices we are able to deal with high single digits, low double digits of features. The limiting factors are screen space and cognitive load. }

%In situations with large amounts of data, it may become difficult to see the trends if the training or testing data due to over plotting. However, consider that the number of observations in the simulated data is chosen by the user, which allows the user to select a number that is large enough to get a visual of the full range of the observed data without running into issues of over plotting.

%Another possibly problematic situation is when it is of interest to include more than two features in the LIME explanation. In this situation, multiple plots will be required to visualize the LIME procedure, and if the number of features is really large, the number of plots may become too large to interpret well. However, if too many \hh{XXX what is too many? make this less abstract and give concrete suggestions on how to go beyond two dimensions.} features are chosen to be included in the LIME explanation, the explanation may no longer interpretable. It seems reasonable that the number of features to focus on in an explanation should be low enough that scatter plot matrices of the \sout{our} \hh{XXX not 'our' - that creates boundaries. you want the readers to use these plots as well.} diagnostic plots could be created.} \kgc{I decided I also didn't want to get into the discuss of "too many" features here.}}

\kgc{Need to add a discussion on using our visualizations in situations without tabular data or a dichotomous response variable.}\\

In this paper, we have presented visualizations that depict the steps in the LIME algorithm (\autoref{procedure}) and diagnose LIME explanations (Sections \ref{set-visuals} and \ref{implementation-visuals}). Our intentions with these visualizations were to provide insight on how LIME works, assess the ability of the explainer model to capture the complex predictive model, and compare LIME explanations produced by different tuning parameters. While the visualizations accomplish these tasks, they also expose examples of the failings of LIME. To address the discovered failings of LIME, we will reconsider each of the claims about the performance of LIME made by \citep{ribeiro:2016} (interpretability, faithfulness, linearity, and localness) in light of the insights gained from the diagnostic visualizations.

As previously discussed, the \textbf{interpretability} of the LIME explanations can be controlled by the complexity of the explainer model. For example, the number of bins selected for simulation can control the interpretability of the explanations. If too many bins are selected, the bin range that is reported in the LIME explanation will be too small to be meaningful in the context of the feature. An appropriate choice of the number of bins will keep the bin range meaningful. Thus, the claim of interpretability does not need to be assessed using the visualizations. However, diagnostic visualizations do present a different perspective on the meaning of interpretability.

\kgc{**Need to rework this paragraph and the next two. The ideas are here, but they are worded very poorly.} Even though an explanation will be interpretable as long as the complexity of the explainer model is appropriately chosen, the presentation of a LIME explanation in the key visual used by \citep{ribeiro:2016} (shown in \autoref{fig:sine-plot-poi}) could lead to an over simplified interpretation of the explainer model. Without a solid understanding of the details behind the fitting of the explainer model, the deeper meaning of the bars in the figure is lost.

It is customary to interpret this plot by stating that the direction of the bar supports or contradicts the classification in a certain category, and the length of the bar signifies the importance of the involvement of a feature in the prediction. While these interpretations are correct, the lengths of the bars represent the coefficients of the ridge regression model used as the explainer model, which contain more meaning than just the direction of support and importance of a feature. The bars indicate how much the average complex model prediction estimated by the linear explainer model changes based on a change in the feature. Furthermore, this interpretation changes depending on whether a bin based or density simulation method was used (i.e the change in the average complex model prediction between an observation in the same bin as the case of interest and an observation not in the same bin versus the change in the mean complex model prediction for a change in the feature by one standardized unit).

Thus, even though an explainer model may be interpretable, the explanation it produces may be under-interpreted or misinterpreted without an understanding of the process that produced the explanation. Supplementing \citep{ribeiro:2016}'s compact visualization of the explanation with visualizations of the explanation that depict the simulated data and the explainer model (such as Figures \ref{fig:sine-plot-step3ab} and \ref{fig:bullet-eois-match}) promotes a full interpretation of the explanation. This is done by providing reminders of the meaning of the lengths of the bars in addition to a visual connection between complex model predictions and the estimated coefficients of the explainer model.

Even with an explainer model that is interpreted correctly, the interpretation is worthless if the explainer model is not \textbf{faithful} to the complex model. This claim can be easily assessed using the diagnostic plots suggested in this paper. Many of the visualizations in this paper highlight problems with the faithfulness of the explainer models.

The visualizations that incorporate the bins along with the complex model predictions (Figures \ref{fig:fig:sine-plot-step1ab}, \ref{ fig:sine-plot-step1c}, \ref{fig:sine-plot-step3ab}, \ref{fig:sine-plot-compare-bins}, \ref{fig:bullet-eois-match}, and \ref{fig:bullet-eois-nonmatch}) highlight issues that accompany the choice to use bin based simulation methods. These visualizations allow for a comparison of the size of the bins to the complex model's decision boundaries. All of the examples in this paper show cases where the bins do not accurately capture the classification boundaries near the predictions of interest of the random forest models by oversimplifying the model. Using less bins would clearly not help improve the faithfulness of the explainer model in these examples, and while an increase in bins would lead to a finer resolution of the random forest classification boundaries, interpretability of the explainer model would quickly be lost. The bins used by LIME are not flexible enough to capture the different sized division boundaries of the random forests shown in this paper. Perhaps this could be improved by allowing the bin creation to account for the relationships between the features and response variable or a different number of bins for each feature.

The figures referenced in the previous paragraph from the \data \ example are all based on the implementation of LIME using a set of tuning parameters. From the use of the feature heatmap, we found that different sets of tuning parameters can produce different explanations. It makes sense that one set of tuning parameters could lead to a more faithful explainer model than another. As a result, we proposed a visual comparison of two faithfulness metrics (MSEE and average fidelity). The examples of faithfulness metric comparisons in this paper (Figures \ref{fig:sine-metric-plot} and \ref{fig:bullet-metric-plot}) both produced confusing results. In both examples, the density based simulation methods resulted in the best or close to the best performance even though the feature heatmaps (Figures \ref{fig:sine-feature-heatmap} and \ref{fig:bullet-feature-heatmap}) showed that the density simulation methods produced global explanations with no variation in features selected by LIME. For the bin based simulation methods, the two metrics often did not agree or contradicted one another, which makes it difficult to decide on a recommendation of a set of tuning parameters that produces the explanations with the most faithful explainer model.

The metric comparison plot also includes a comparison of average $R^2$ values, which is a metric that can be used to assess the claim of \textbf{linearity}. Most of the average $R^2$ values in the examples from this paper are below 0.5 suggesting a poor linear fit of the explainer models. The poor linear fit of the explainer model was also seen with the residual plot (\autoref{fig:sine-plot-step2cd}).

The final claim, \textbf{localness}, is also addressed by the feature heatmap and metric comparison plot. As stated, the feature heatmap revealed that the density simulation methods in the examples of this paper resulted in global explanations where the same features were repeatedly chosen across all (or almost all) observations in the set of explanations. This finding agrees with that of \citep{laugel:2019} who also found LIME produced global explanations with the normal approximation simulation method. For the bin based simulation methods in the bullet data example, the feature heatmap showed that the features chosen for the explanations varied between the two classification categories (match versus non-match). This is an interesting finding that suggests that different features can play a role in the predictions of observations in different response categories, but the patterns of features selected by LIME within a classification category do not vary. Again, this is a suggestion of global explanations. Furthermore, while the metric comparison plot in the bullet example did not provide agreement between metrics on a best bin based method, all metrics agree that a Gower power of 0.5 for computing the model weights associated with distance of a simulated data point from the prediction of interest was best. This suggests that a less local explanation provided a better explanation of the performance of the random forest.

Some of the visualizations in the paper generalize easily to any application of LIME such as the feature heatmap and metric plot. Other plots such as the visualizations of the LIME procedure would require extensions such as the use of scatterplot matrices to compare explanations with more than two features. The addition of interactivity to the diagnostic plots would provide additional enhancement of the assessment process. For example, a diagnostic plot that provides a summary of multiple LIME explanations, such as the feature heatmap, could be displayed and clicked on to reveal more detailed figures associated with individual predictions of interest, such as plots of the simulated data and explainer model.

While it would be ideal if LIME could be used as a method to provide easily understandable explanations for black-box models as \citep{ribeiro:2016} claim, that dream is not yet a reality. The examples using diagnostic plots to assess LIME in this paper show frequent issues with LIME. The practice of assessing the performance of methods has once again shown its importance. We hope that our plots provide motivation to assess LIME explanations, to not blindly use the default settings (even if it is not clear which tuning parameters to use), and perhaps to encourage work on improving LIME, so that it can be a lime and not a lemon.

\kgc{Need to work this into the discussion: We acknowledge that not all prediction problems will produce trends as easy to interpret as the visualizations we have shown in the section, but we still believe that visualizations of the procedure can provide insight into the quality of the LIME explanation. We hope these figures will provide a starting point (if not an ending point) for the assessment of a single LIME explanation. Perhaps the inability to interpret a plot is itself telling, or the act of creating extensions of these visualizations to work with a different scenarios will lead to an understanding of the trustworthiness of the explanation.}

\section*{Acknowledgments}

This is acknowledgment text. Provide text here.

\subsection*{Author contributions}

This is an author contribution text. This is an author contribution text. This is an author contribution text. This is an author contribution text. This is an author contribution text.

\subsection*{Financial disclosure}

None reported.

\subsection*{Conflict of interest}

The authors declare no potential conflict of interests.

\section*{Supporting information}

The following supporting information is available as part of the online article:

\appendix

\section{Details on Assessment Metrics}

\kgc{Placing the notation definitions here for now - need to make adjustments as necessary:} \kge{We first introduce notation for the scenario of tabular data with a binary response variable and continuous features. Let $\textbf{X}$ be an $n$ by $p$ data matrix with $p$ features and $n$ observations, and let $x_i\in\textbf{X}$ be a real-valued vector such that $x_i\in\mathbb{R}^p$ for $i=1,2,...,n$. Furthermore, let $y$ be a response variable of length $n$ with elements $y_i\in\{0, 1\}$ for $i=1,2,...,n$. Suppose that $f$ is a classification model where $f:\mathbb{R}^p\rightarrow[0,1]$ that is applied to $\textbf{X}$ and $y$. Let the vector of predictions made by $f$ applied to $\textbf{X}$ be denoted as $\hat{y}$. Note that $\hat{y}_i=f(x_i)\in\hat{y}$ for $i=1,..,n$. For both bin based methods, the interpretability transformation converts the generated observations to indicator variables, where a 1 indicates that the feature value for an observation is in the same bin as the feature value for the case of interest. That is
  $$z'_{i,j}=T\left(x'_{i,j}\right) = I\left[x'_{i,j} \mbox{ and } x^*_{i,j}\in b_{j,k} \right]$$
for $i=1,..,m$ and $j=1,..,p$ where $b_{j,k}$ is bin $k$ for feature $j$. Let observation $z'_i$ have weight $\omega_{x^*}(\textbf{x}'_i) = Gower(x^*, x'_i)^c$, where $Gower$ represents the computation of the Gower similarity and $c$ is some constant. This denotes a proximity measure between $x^*$ and $x'_i$ for each $i\in 1,...,m$. If the exponential kernel is used, the weights are computed after the interpretability transformation such that $z'_i$ has weight $\omega_{z^*}(\textbf{z}'_i)$.}

\citet{ribeiro:2016} present \hh{the following metric as a measure of fidelity:}
$$\mathcal{L}(f, g, \omega_{x^*}) = \sum_{i=1}^{m}\omega_{x^*}(x_i)\left(f(x_i)-g\left(z_i'\right)\right)^2,$$
\hh{where  ... }

This metric is computed as $$\mathcal{L}(f, g, \omega_{x^*}) = \sum_{i=1}^{m}\omega_{x^*}(x_i)\left(f(x_i)-g\left(z_i'\right)\right)^2.$$ Smaller values of $\mathcal{L}$ indicate a better local approximation of the explainer model to the complex model.

That is, let $$MSEE=\frac{1}{n}\sum_{i=1}^n\left(f\left(x^*\right)-g\left(z^*\right)\right)^2.$$ Again, smaller values of MSEE would suggest a better approximation of the explainer model.

\bibliography{references}

% Do I need to include this?
% \section*{Author Biography}
% \begin{biography}
% {\includegraphics[width=60pt,height=70pt,draft]{empty}}
% {\textbf{Author Name.} This is sample author biography text this is sample author biography text}
% \end{biography}

% \newpage
% 
% \textsc{\textbf{Ideas for describing proposed plots}}
% 
% \begin{itemize}
% \item start at the high level explanation (this is what we want to do and this is how we do it)
% \item go over a good and bad example
% \item include schematics of the plot first (good and bad) and then include the sine mini example version
% \item explain the expectation of the plot
% \end{itemize}
% 
% \textsc{\textbf{Comments for Editing}}
% 
% \begin{itemize}
% \item \hh{Generally: avoid 'can be'. Replace by 'is'.  }
% \item \hh{References like 'they', 'them' ... replace them by repeating the noun you are referring to to avoid any kind of ambiguity}
% \item \kgc{words to go back and make sure I am not using too often: ability, produce, understand}
% \item \kgc{decide on features or predictor variables}
% \item \hh{it's tuning parameters, not tunning} \kgc{Oops! I get that one wrong all of the time}
% \item \kgc{Adjust text sizes in plots so they all match}
% \item \kgc{Color scheme - comment from Heike:} \hh{I like the red-blue scheme for binary values, I also like the color scheme in the features heatmap. Generally papers and color don't go well together anyways, but we will solve that problem when we have to ... Most likely we will have to just pay the extra color fee}
% \item \kgc{Check that I am consistently referring to the perturbing as data simulation}
% \item \kgc{Clean up notation}
% \item \kgc{Referring to the linearity assumption:} \hh{Be a bit careful in the phrasing here - we can always approximate any function using a linear form (think Taylor expansion). The question is how big the error is.}
% \item \kgc{Make sure plots in the same figure are the same size}
% \item \kgc{Make sure I am distinguishing between RF predictions and probabilities correctly}
% \item \kgc{Use prediction of interest not case of interest}
% \item \kgc{Make sure I always treat the word 'data' as plural}
% \item \kgc{dataset or data set?}
% \item \kgc{scatterplot or scatter plot (check other plot names as well)}
% \item \kgc{choose whether to use the term feature or variable and make sure it is consistent throughout}
% \item \kgc{just include the details about LIME that are necessary to understand the plots and remove the rest to the appendix}
% \item \hh{avoid the use of implicit references like `this' and `that'. Make the reference explicit by adding what you are referring to, such as `this method', `that procedure'}
% \item \hh{make sure to use exact phrases. things like `LIME was developed in 2016' is factually questionable - but we know LIME was introduced in 2016. Also `the authors were interested in ...' implies that you know their intent. It's better to not guess any intent but stick to what we know.}
% \item \hh{`our` diagnostics ... you are using `our` quite often. It is good to claim work, but it is not good to claim things that we want others to use, because that is by definition excluding everybody but you. It's better to re-phrase with a focus on what you did. We introduce, we suggest, etc.}
% \item \hh{Try to give each of the diagnostics a name.}
% \item \kgc{check that I am always using present tense}
% \item \kgc{check that I am consistent in my use of the term black-box model}
% \end{itemize}
% 
% \textsc{\textbf{Ideas for Publishing}}
% 
% \begin{itemize}
% \item longer review article (emph on CS method in ML - we're translating the content into a stats language) (talk to Maitra and Wendy)
% \item review article would need a more extensive lit review:
% \begin{itemize}
% \item who has looked at LIME and found it not great
% \item who is using LIME for applications
% \item papers using LIME
% \end{itemize}
% \item the diagnostics plots could get put in a rapid research paper via DS journal
% \item could consider JOSS for publication of the limeaid package
% \item implement a hierarchical ordering method for the feature heatmap
% \end{itemize}
% 
% \textsc{\textbf{Other Ideas}}
% 
% \begin{itemize}
% \item Consider creating a plot to show the decay of the distance by Gower exponent in terms of standard deviations in the appendix.
% \end{itemize}

\end{document}

### 2020-06-04 paper.Rnw
edits through section 3.0 (almost)

@@
 Model interpretability allows for the assessment and understanding of how the model produces predictions.
-In application, the ability to assess and understand model is crucial in important and crutial in areas areas with high stakes decisions such as health care and forensics science.
-The increased use of machine learning models and the introduction of the General Data Protection Regulation (GDPR) in 2018 \citep{goodman:2016} has resulted in a dramatic increase in research in the area of explainable machine learning that focuses on developing ways to explain output from machine learning algorithms.
-
-Throughout this paper, we will make a distinction between interpretability and explanability of models.
+The lack of the ability to assess and understand a model makes it difficult to trust the model, especially in areas areas with high stakes decisions such as health care and forensics science.
+The increased use of machine learning models in applications and the introduction of the General Data Protection Regulation (GDPR) in 2018 \citep{goodman:2016} has resulted in a dramatic increase in research in an area known as explainable machine learning, which focuses on developing ways to explain output from machine learning algorithms.
+
+Throughout this paper, we make a distinction between interpretability and explanability of models.
 We define {\it interpretability} as the ability to directly use model parameters to understand the relationships in the data captured by the model: e.g., a linear model coefficient associated with a predictor variable indicates the amount the response variable changes based on a change in the predictor variable.
@@
 \citep{greenwell:2018} and \citep{strumbelj:2014}).
-In this paper, we focus on the model-agnostic method of LIME (local interpretable model-agnostic explanations) \citep{ribeiro:2016}.
+In this paper, we focus on the model-agnostic method of LIME \citep{ribeiro:2016}.
 
@@
 A ridge regression model is fit to the same black-box model predictions and predictor variables as in \autoref{fig:concept-plot-good}, but the weights are computed using a Gower exponent of 1.
-The explainer model provides a global approximation of the complex model in regards to the prediction of interest.}
+The explainer model is unfaithful to the complex model in the immediate neighborhood of the prediction of interest.}
 \label{fig:concept-plot-bad}
@@
 
-\subsection{LIME}
-
-LIME falls under the category of model explainers \citep{ribeiro:2016} \citep{mohseni:2018}.
-A model explainer is a method that uses a surrogate model to relate the predictor variables to the black-box model predictions.
-We will distinguish between the terms of model explainer and explainer model: by \emph{model explainer} we denote the method for explaining a complex model using a surrogate model, while the \emph{explainer model}, or simply the \emph{explainer}, is the surrogate model.
-
-While some model explainers are focused on understanding a model at the global level, LIME claims to provide local explanations.
-Additionally, LIME is designed to work with any model and to produce easily understandable explanations \citep{ribeiro:2016}.
-Conceptually, LIME fits a simple interpretable model, the explainer model,  meant to capture the behavior of the (complex) black-box model in a local region around a prediction of interest.
+\subsection{Conceptual Description of LIME}
+
+LIME (local interpretable model-agnostic explanations) is a method that uses a surrogate model to relate predictor variables to black-box model predictions (i.e.
+a model explainer) \citep{ribeiro:2016}.
+We distinguish between the terms of model explainer and explainer model: by \emph{model explainer} we denote the method for explaining a complex model using a surrogate model, while the \emph{explainer model}, or simply the \emph{explainer}, is the surrogate model.
+
+While some model explainers are focused on understanding a model at the global level, LIME claims to provide explanations for individual predictions (local).
+Additionally, LIME is designed to work with any model (model-agnostic) and to produce easily understandable results (explanations) \citep{ribeiro:2016}.
+Conceptually, LIME fits a simple (interpretable) model, the explainer model,  meant to capture the behavior of the (complex) black-box model in a local region around a prediction of interest.
 The  simple model then provides interpretable estimates for variables that most influenced the prediction made by the complex model.
@@
 Here, an exponent of \Sexpr{good_gower_power} is used to emphasize interest in a very local region around the point of interest.
-A ridge regression model weighted by the proximity values is used as the explainer model.
-The black-box predictions are used as the response variable, standardized versions of Features 1 and 2 are included as predictor variables.
+A ridge regression model weighted by the proximity values is used as the explainer model with the black-box predictions as the response variable and standardized versions of Features 1 and 2 as predictor variables.
 Standardized features allow direct comparisons of the model coefficients.
@@
 The plot on the right shows that there is no global or local relationship between the black-box predictions and Feature 2.
-Here, the explainer model is plotted with Feature 1 set to be the observed value of Feature 1 for the prediction of interest, and it has a small slope of \Sexpr{coefs_data %>% filter(case == "good", feature == "Feature 2") %>% pull(slope) %>% round(3)}.
-The magnitude of the slope associated with Feature 1 is larger than the slope of Feature 2, resulting LIME to report that Feature 1 plays a more important role in the prediction made by the black-box model.
+Here, the explainer model is plotted with Feature 1 set to be the observed value of Feature 1 for the prediction of interest, and it has an appropriately small slope of \Sexpr{coefs_data %>% filter(case == "good", feature == "Feature 2") %>% pull(slope) %>% round(3)}.
+The magnitude of the slope associated with Feature 1 is larger than the slope of Feature 2, which suggests that Feature 1 plays a more important role in the prediction made by the black-box model for the point of interest.
+This explanation agrees with a visual assessment of the relationships between the predictions and predictor variables.
 
@@
 
-Explainer models are meant to provide clarity to the process of predictive modeling, but since the explainer model is an approximation of the complex model and not a direct interpretation, explanations produced by an explainer model are subject to the quality of the approximation.
-Thus, explainer models add another layer of complexity to predictive models by requiring yet another model that needs to be assessed.
-
-The choice of exponent in the scenario depicted in \autoref{fig:concept-plot-good} is crucial.
-High values ensure an up-weight of observations closer to the prediction of interest.
-Consider the example depicted in \autoref{fig:concept-plot-bad}.
-The plots show the same data as \autoref{fig:concept-plot-good}, but the Gower distance metric exponent was decreased to \Sexpr{bad_gower_power} (the default exponented in the \emph{lime} R package).
+The concept of LIME is relatively simple: use an interpretable model to approximate a complex model in a local region.
+However, a practical implementation of LIME is not straightforward, and there is research is being done to improve the procedure \citep{laugel:2018}.
+The current implementations of LIME\footnote{https://github.com/thomasp85/lime} \footnote{https://github.com/goodekat/lime} offer various tuning parameters the user specifies when applying LIME (see Section \ref{background}) that affect the explainer model and ultimately, the explanation.
+Since the explainer model is an approximation of the complex model and not a direct interpretation, the explanations produced by an explainer model are subject to the quality of the approximation.
+Thus, in order to achieve accurate explanations, the tuning parameters selected need to be assessed.
+
+We consider an example where the choice of exponent used to specify the weights is crucial to the quality of the explanation.
+The plots in Figure \ref{fig:concept-plot-bad} show the same data as \autoref{fig:concept-plot-good}, but the Gower distance metric exponent was decreased to \Sexpr{bad_gower_power} (the default exponent in the \emph{lime} R package).
 This causes the observations that are further away from the prediction of interest to be given larger weights than before.
@@
 
-There are various ways in which LIME can fail.
-One of the biggest difficulties with LIME is determining how to specify a local region \citep{molnar:2019} due to an unclear definition of what a local region means and how to apply LIME to achieve an appropriate local region.
-\autoref{fig:concept-plot-bad} demonstrates an explainer model that provides misleading explanations due to poorly specified weights.
-\citet{laugel:2018} show additional examples of undesirable explanations produced by LIME when the local region was chosen inadequately.
-\citet{alvarezmelis:2018} raise another concern pertaining to the robustness of explanations from LIME and other post-hoc explainers: they find that even small changes in predictor variables can lead to very different LIME explanations.
-Additionally, LIME relies on a good approximation of the explainer model to the complex model.
-\citet{ribeiro:2016} acknowledge that ``if the underlying model is highly non-linear even in the locality of the prediction, there may not be a faithful explanation" with a linear regression model as the explainer model.
+Several sources in the literature discuss the performance of LIME.
+One of the biggest difficulties with LIME is determining how to specify a local region \citep{molnar:2019} \citet{laugel:2018}.
+This is due to an unclear definition of what a local region means and how to apply LIME to achieve an appropriate local region as demonstrated by \autoref{fig:concept-plot-bad}.
+\citet{alvarezmelis:2018} raise a concern pertaining to the robustness of explanations from LIME and other model explainers: they find that even small changes in predictor variables can lead to very different LIME explanations.
+Additionally, \citet{ribeiro:2016} acknowledge that if a linear models is used as the explainer, LIME relies on a linear approximation of the explainer model to the complex model and state ``if the underlying model is highly non-linear even in the locality of the prediction, there may not be a faithful explanation".
 
 As a result of the various ways LIME explanations can fail, it is important to assess LIME explanations.
+We suggest the use of visual diagnostics for assessment.
 In this paper, we lay out the set of claims about LIME made by \citet{ribeiro:2016} and propose four visualizations for the assessment of these claims: (1) \emph{explanation scatterplot}, (2) \emph{prediction comparison plot}, (3) \emph{feature heatmap}, (4) \emph{assessment metric plot}.
-
 While LIME has been implemented for image, tabular, and text data, we will only focus on tabular data.
@@
 
-\subsection{Overview of Paper}
-
-The reminder of the paper is structured as follows.
-Section \ref{background} provides background and the claims made by \citet{ribeiro:2016} about LIME.
-In Section \ref{diagnostics}, we introduce the suggested diagnostic plots.
+\subsection{Structure of Paper}
+
+The remainder of the paper is structured as follows.
+Section \ref{background} provides background and claims made by \citet{ribeiro:2016} about LIME.
+We introduce the suggested diagnostic plots in Section \ref{diagnostics}.
 Then in Section \ref{application}, we demonstrate the use of the diagnostics to assess LIME explanations for a random forest model fit to a forensics bullet matching dataset.
-Section \ref{discussion} concludes with a discussion on extenstion and limitations of the diagnostic plots and concerns about LIME in regards to the claims made by \citet{ribeiro:2016} brought about by the visualization examples in this paper that agree with \citet{alvarezmelis:2018}, \citet{laugel:2018}, and \citet{molnar:2019}.
+Section \ref{discussion} concludes with a discussion on extension and limitations of the diagnostic plots and concerns about LIME in regards to the claims made by \citet{ribeiro:2016} brought about by the visualization examples in this paper that agree with \citet{alvarezmelis:2018}, \citet{laugel:2018}, and \citet{molnar:2019}.
 
@@
 LIME was introduced in 2016 by \citet{ribeiro:2016}.
-LIME is presented as a model explainer that produces easily understandable explanations for individual predictions from any predictive model \citep{ribeiro:2016}.
+The original authors provide an implementation of LIME in a Python package\footnote{https://github.com/marcotcr/lime}.
+An adaption of the Python package in R is by Thomas Lin-Pedersen\footnote{https://github.com/thomasp85/lime}.
+In this paper, any details provided about the implementation of LIME are based on the R package.
+
 As described by \citet{laugel:2018}, the general form of the LIME algorithm can be divided into three steps:
@@
 Compute the distance between each of the simulated observations and the prediction of interest.
-Fit an interpretable model with the black-box predictions from the simulated data as the response, the transformed simulated data as the predictors, and the distances as weights.
+Perform feature selection.
+Fit an interpretable model with the black-box predictions from the simulated data as the response, the selected features from the transformed simulated data as the predictors, and the distances as weights.
 This model is the explainer model.
@@
 
-\citet{ribeiro:2016} make the following set of claims regarding the performance of LIME:
+During the application of LIME, the user must select various tuning parameter options: the number of features to return in the explanation, the simulation method, the feature selection method, and how the weights are computed.
+An overview of the options available for the tuning parameters is included in Appendix \ref{lime-details}.
+
+In the original paper, \citet{ribeiro:2016} make the following set of claims regarding the performance of LIME:
 
@@
 The other three assumptions are not as easy to assess -- for those we suggest the use of diagnostic plots.
-
-LIME was initially implemented in a Python package\footnote{https://github.com/marcotcr/lime} by the original authors.
-The adaption to an R package is by Thomas Lin-Pedersen\footnote{https://github.com/thomasp85/lime}.
-In this paper, we use a forked version\footnote{https://github.com/goodekat/lime} of the development version of the R package \emph{lime} (\Sexpr{packageVersion("lime")}) \citep{pedersen:2020}.
-The forked version of \emph{lime} allows us to export internal values of the procedure not already exported by \emph{lime}.
 
@@
 
-At a high level, the concept of LIME is relatively simple: an interpretable model is used to approximate a complex model in a local region.
-In practice, the implementation of LIME is not straightforward, and there is research is being done to improve the procedure \citep{laugel:2018}.
-As described in \autoref{background}, there are various parameter choices that have to be made when applying LIME: the simulation method, the feature selection method, and how weights are calculated.
-We will refer to these choices as tuning parameters.
-Without an assessment of the explainer model, it is not clear if the tuning parameters selected when applying LIME resulted in a useful explanation and LIME becomes a black-box procedure of its own.
-To counteract the black-box nature, we suggest the use of visualizations of each step of the LIME algorithm.
-In this section, we introduce four suggested visual diagnostic plots for the assessment of LIME.
-The diagnostic plots focus on assessing the LIME claims at different levels of application:
+In this section, we introduce four visual diagnostic plots for the assessment of LIME.
+The plots focus on different levels of application of LIME (e.g.
+on explanation versus a set of explanations) to assess the LIME claims from different perspectives:
 
 \begin{enumerate}
-\item Explanation scatterplot (Section \ref{plot1}): Comparison of the explainer and complex models for an individual prediction of interest.
-\item Prediction comparison plot (Section \ref{plot1}): Comparison of explainer and complex model predictions for a set of predictions.
-\item Feature Heatmap: Comparison of features selected by LIME across applications of LIME with different tuning parameters.k
-\item Assessment metric plot: Comparison of performance metrics for LIME across applications of LIME with different tuning parameters. 
+\item \emph{Explanation Scatterplot} (Section \ref{plot1}): Comparison of the explainer and complex models for an individual prediction of interest.
+\item \emph{Prediction Comparison Plot} (Section \ref{plot2}): Comparison of explainer and complex model predictions for a set of predictions.
+\item \emph{Feature Heatmap} (Section \ref{plot3}): Comparison of features selected by LIME across applications of LIME with different tuning parameters.k
+\item \emph{Assessment Metric Plot}: Comparison of performance metrics for LIME across applications of LIME with different tuning parameters. 
 \end{enumerate}
@@
 A random forest model is fit using the R package \emph{randomForest} (version \Sexpr{packageVersion("randomForest")}) \citep{liaw:2002} with the default settings.
-The model is applied to the testing set to obtain predictions.
+The model is applied to the test set to obtain predictions.
 \autoref{fig:sine-plot-data} shows scatterplots of $x_2$ versus $x_1$ from the training data (left) and the testing data (right).
@@
 The training data are colored by the observed response variable ($y$), and the testing data are colored by the prediction probabilities from the random forest model ($\hat{y}$).
-
 The random forest model misclassifies \Sexpr{dim(sine_data_test %>% filter(y != rfpred))[1]} points on the classification boundary.
 These are identified by circles in \autoref{fig:sine-plot-data}.
-For the diagnostic plot presented in Section \ref{plot1}, we focus on one of these points: the observation with $(x_1, x_2, x_3)$ coordinates of (\Sexpr{round(sine_poi$x1, 2)}, \Sexpr{round(sine_poi$x2, 2)}, \Sexpr{round(sine_poi$x3, 2)}) indicated by a diamond in \autoref{fig:sine-plot-data}.
+
+For the presentation of the explanation scatterplot, we focus on the misclassified point with $(x_1, x_2, x_3)$ coordinates of (\Sexpr{round(sine_poi$x1, 2)}, \Sexpr{round(sine_poi$x2, 2)}, \Sexpr{round(sine_poi$x3, 2)}) indicated by a diamond in \autoref{fig:sine-plot-data}.
+For the introduction of the other three plots, we use all observations in the \data test data as points of interest.
 
@@
 
-We apply LIME to the \data \ using \emph{lime} with the default settings.
+\kgc{This is where I left off with the editing:} We apply LIME to the \data \ using \emph{lime} with the default settings.
 The user is asked to specify the number of features shown in the explanations.
@@
 This was done using six different sets of tuning parameters via \sout{our} R package \emph{limeaid} \footnote{Available on GitHub at https://github.com/goodekat/limeaid}.
-Quantile bins were used for five of the implementations, and the number of bins for these implementations was varied from 2 to 6.
+\kge{(In this paper, we use a forked version\footnote{https://github.com/goodekat/lime} of the development version of the R package \emph{lime} (\Sexpr{packageVersion("lime")}) \citep{pedersen:2020}.
+The forked version of \emph{lime} allows us to export internal values of the procedure not already exported by \emph{lime}.)} Quantile bins were used for five of the implementations, and the number of bins for these implementations was varied from 2 to 6.
 The sixth implementation of LIME used the kernel density estimates.
@@
 
-\kgc{Add intro paragraph and edit text as necessary in this subsection}
-
 \autoref{fig:sine-plot-poi} shows the visualization of the explanation produced by \emph{lime} for the prediction of interest.
@@
 
-\kgc{Add intro paragraph and edit text as necessary in this subsection}
-
 \autoref{fig:sine-plot-compare-bins} provides a visualization of the comparison of the explainer model predictions to the random forest predictions in the context of the $x_1$ and $x_2$ quantile bins.
@@
 
-\subsection{Feature Heatmap Diagnostic Plot} \label{feature-heatmap}
+\subsection{Feature Heatmap Diagnostic Plot} \label{plot3}
 
@@
 
-\subsection{Assessment Metric Plot}
+\subsection{Assessment Metric Plot} \label{plot4}
 
@@
 
-\kgc{Break into sections: (1) visualization limitations (2) future research (3) concerns about LIME}
-
-%\kgc{Possible content to add here:} \kgc{Need to work this in}: \hh{In terms of limitations of the visualizations: first two features span the x and y axis, additional features can be used for faceting.
+This paper highlights that while an explainer model is meant to provide clarity, it actually adds another layer of complexity to predictive models by requiring yet another model that needs to be assessed.
+Without an assessment of the explainer model, LIME is a black-box procedure of its own.
+We suggest the use of visual diagnostics to counteract the black-box nature of LIME and provide four diagnostic plots.
+Here we discuss the limitations and possible extensions of the diagnostic plots and concerns about LIME raise by applications of the diagnostics plots in this paper.
+
+\subsection{Diagnostic Plot Limitations and Possible Extensions} \label{limit-exten}
+
+% We acknowledge that not all prediction problems will produce trends as easy to interpret as the visualizations we have shown in the section, but we still believe that visualizations of the procedure can provide insight into the quality of the LIME explanation.
+We hope these figures will provide a starting point (if not an ending point) for the assessment of a single LIME explanation.
+Perhaps the inability to interpret a plot is itself telling, or the act of creating extensions of these visualizations to work with a different scenarios will lead to an understanding of the trustworthiness of the explanation.
+
+%\hh{In terms of limitations of the visualizations: first two features span the x and y axis, additional features can be used for faceting.
 four features is completely feasible, beyond that the visualization might not work as well.
@@
 
-%In the case of faceting, the} \hh{first two features} \kge{can} \hh{span the x and y axis,} \kge{and} \hh{additional features can be} \kge{used as the facets.} We have included some examples of such plots in Appendix \ref{scatter-plots} that take into the feature $x_3$ from the \data \ in the visualization of the LIME procedure.
-
-%\hh{\sout{In terms of limitations of the visualizations: first two features span the x and y axis, additional features can be used for faceting.
-four features is completely feasible, beyond that the visualization might not work as well.
-The number of bins should be in the single digits.
-A large number of small multiples (reference to Cleveland?) needs a strong signal in the data to be effective - otherwise the visualization might be affected by change blindness} \citet{simons:1997, vanderplas:2020}.}
-
 %\hh{Both large number of observations and large number of features make visual assessments harder:} \kgc{I've decided to not discuss a large amount of data, because that really isn't a problem due to the size of the simulated dataset being chosen by the user, and there is not a need to go above 5000.
@@
 
-\kgc{Need to add a discussion on using our visualizations in situations without tabular data or a dichotomous response variable.}\\
-
-In this paper, we have presented visualizations that depict the steps in the LIME algorithm (\autoref{procedure}) and diagnose LIME explanations (Sections \ref{set-visuals} and \ref{implementation-visuals}).
-Our intentions with these visualizations were to provide insight on how LIME works, assess the ability of the explainer model to capture the complex predictive model, and compare LIME explanations produced by different tuning parameters.
+% Add a discussion on using our visualizations in situations without tabular data or a dichotomous response variable.
+
+\subsection{Concerns about LIME} \label{concerns}
+
+The visualizations are intended to provide insight on how LIME works, assess the ability of the explainer model to capture the complex predictive model, and compare LIME explanations produced by different tuning parameters.
 While the visualizations accomplish these tasks, they also expose examples of the failings of LIME.
@@
 
-\kgc{**Need to rework this paragraph and the next two.
-The ideas are here, but they are worded very poorly.} Even though an explanation will be interpretable as long as the complexity of the explainer model is appropriately chosen, the presentation of a LIME explanation in the key visual used by \citep{ribeiro:2016} (shown in \autoref{fig:sine-plot-poi}) could lead to an over simplified interpretation of the explainer model.
+Even though an explanation will be interpretable as long as the complexity of the explainer model is appropriately chosen, the presentation of a LIME explanation in the key visual used by \citep{ribeiro:2016} (shown in \autoref{fig:sine-plot-poi}) could lead to an over simplified interpretation of the explainer model.
 Without a solid understanding of the details behind the fitting of the explainer model, the deeper meaning of the bars in the figure is lost.
@@
 
-\kgc{Need to work this into the discussion: We acknowledge that not all prediction problems will produce trends as easy to interpret as the visualizations we have shown in the section, but we still believe that visualizations of the procedure can provide insight into the quality of the LIME explanation.
-We hope these figures will provide a starting point (if not an ending point) for the assessment of a single LIME explanation.
-Perhaps the inability to interpret a plot is itself telling, or the act of creating extensions of these visualizations to work with a different scenarios will lead to an understanding of the trustworthiness of the explanation.}
-
 \section*{Acknowledgments}
@@
 \appendix
+
+\section{LIME Tuning Parameter Options} \label{lime-details}
 

### 2020-06-04 paper.Rnw
edits through 3.0

@@
 However, a practical implementation of LIME is not straightforward, and there is research is being done to improve the procedure \citep{laugel:2018}.
-The current implementations of LIME\footnote{https://github.com/thomasp85/lime} \footnote{https://github.com/goodekat/lime} offer various tuning parameters the user specifies when applying LIME (see Section \ref{background}) that affect the explainer model and ultimately, the explanation.
+The current implementations of LIME\footnote{https://github.com/marcotcr/lime} \citep{pedersen:2020} offer various tuning parameters the user specifies when applying LIME (see Section \ref{background}) that affect the explainer model and ultimately, the explanation.
 Since the explainer model is an approximation of the complex model and not a direct interpretation, the explanations produced by an explainer model are subject to the quality of the approximation.
@@
 Several sources in the literature discuss the performance of LIME.
-One of the biggest difficulties with LIME is determining how to specify a local region \citep{molnar:2019} \citet{laugel:2018}.
-This is due to an unclear definition of what a local region means and how to apply LIME to achieve an appropriate local region as demonstrated by \autoref{fig:concept-plot-bad}.
+One of the biggest difficulties with LIME is determining how to specify a local region \citep{laugel:2018} \citep{molnar:2019}.
+This is due to an unclear definition of a "local region" and how to apply LIME to achieve an appropriate local region as demonstrated by \autoref{fig:concept-plot-bad}.
 \citet{alvarezmelis:2018} raise a concern pertaining to the robustness of explanations from LIME and other model explainers: they find that even small changes in predictor variables can lead to very different LIME explanations.
@@
 The original authors provide an implementation of LIME in a Python package\footnote{https://github.com/marcotcr/lime}.
-An adaption of the Python package in R is by Thomas Lin-Pedersen\footnote{https://github.com/thomasp85/lime}.
+An adaption of the Python package in R is by Thomas Lin-Pedersen \citep{pedersen:2020}.
 In this paper, any details provided about the implementation of LIME are based on the R package.
@@
 @
-\caption{Plots of $x_2$ versus $x_1$ from the training (left) and testing (right) set of the \data \ introduced in Section \ref{procedure}.
+\caption{Plots of $x_2$ versus $x_1$ from the training (left) and testing (right) sets of the \data \ introduced in Section \ref{diagnostics}.
 The true classification boundary is shown as the solid black line in both plots.
@@
 \end{figure*}
-
-In this section, we introduce four visual diagnostic plots for the assessment of LIME.
-The plots focus on different levels of application of LIME (e.g.
-on explanation versus a set of explanations) to assess the LIME claims from different perspectives:
-
-\begin{enumerate}
-\item \emph{Explanation Scatterplot} (Section \ref{plot1}): Comparison of the explainer and complex models for an individual prediction of interest.
-\item \emph{Prediction Comparison Plot} (Section \ref{plot2}): Comparison of explainer and complex model predictions for a set of predictions.
-\item \emph{Feature Heatmap} (Section \ref{plot3}): Comparison of features selected by LIME across applications of LIME with different tuning parameters.k
-\item \emph{Assessment Metric Plot}: Comparison of performance metrics for LIME across applications of LIME with different tuning parameters. 
-\end{enumerate}
-
-\paragraph{The \data}
-
-To demonstrate the visualizations, we generate an example dataset that will be referred to as the \data.
-The \data \ contains \Sexpr{dim(sine_data)[1]} observations with three features and one response variable.
-The features, $x_1$, $x_2$, and $x_3$, are randomly sampled from Unif(\Sexpr{min}, \Sexpr{max}), Unif(\Sexpr{min}, \Sexpr{max}), and $\mbox{N}(0,1)$ distributions, respectively.
-A binary response variable $y$ is  created using a rotated sine curve.
-In particular, let $x'_1=x_1\cos(\theta)-x_2\sin(\theta)$ and $x'_2=x_1\sin(\theta)+x_2\cos(\theta)$ where $\theta=-0.9$.
-Then $y$ is defined as
-\begin{eqnarray}\label{eq:data}
-  y=\begin{cases}
-  \mbox{blue} & \mbox{ if } x'_2 > \sin\left(x'_1\right) \\
-  \mbox{red} & \mbox{ if } x'_2 \le \sin\left(x'_1\right) \ . %\nolabel
-  \end{cases}
-\end{eqnarray}
-Note that due to the creation of $y$ in this manner, $y$ is dependent on $x_1$ and $x_2$ and independent of $x_3$.
-
-The dataset is divided into a training set of \Sexpr{dim(sine_data_train)[1]} observations and a testing set of \Sexpr{dim(sine_data_test)[1]} observations.
-A random forest model is fit using the R package \emph{randomForest} (version \Sexpr{packageVersion("randomForest")}) \citep{liaw:2002} with the default settings.
-The model is applied to the test set to obtain predictions.
-\autoref{fig:sine-plot-data} shows scatterplots of $x_2$ versus $x_1$ from the training data (left) and the testing data (right).
-Both plots include the true classification boundary of the rotated sine function plotted as the solid black line.
-The training data are colored by the observed response variable ($y$), and the testing data are colored by the prediction probabilities from the random forest model ($\hat{y}$).
-The random forest model misclassifies \Sexpr{dim(sine_data_test %>% filter(y != rfpred))[1]} points on the classification boundary.
-These are identified by circles in \autoref{fig:sine-plot-data}.
-
-For the presentation of the explanation scatterplot, we focus on the misclassified point with $(x_1, x_2, x_3)$ coordinates of (\Sexpr{round(sine_poi$x1, 2)}, \Sexpr{round(sine_poi$x2, 2)}, \Sexpr{round(sine_poi$x3, 2)}) indicated by a diamond in \autoref{fig:sine-plot-data}.
-For the introduction of the other three plots, we use all observations in the \data test data as points of interest.
 
@@
 
-\kgc{This is where I left off with the editing:} We apply LIME to the \data \ using \emph{lime} with the default settings.
-The user is asked to specify the number of features shown in the explanations.
-Here, we set this value to two, because we expect that $x_1$ and $x_2$ will be the main drivers in the prediction.
-Note that the complexity of an explanation goes hand in hand with the number of features selected to be included in the explanation.
-Setting the number of features to a small number will make the explanation simpler but not necessarily more correct.
-
-To demonstrate the proposed diagnostic plots, we applied six different implementations of LIME to the sine data to select the top two features associated with each of the random forest predictions in the testing dataset.
-This was done using six different sets of tuning parameters via \sout{our} R package \emph{limeaid} \footnote{Available on GitHub at https://github.com/goodekat/limeaid}.
-\kge{(In this paper, we use a forked version\footnote{https://github.com/goodekat/lime} of the development version of the R package \emph{lime} (\Sexpr{packageVersion("lime")}) \citep{pedersen:2020}.
-The forked version of \emph{lime} allows us to export internal values of the procedure not already exported by \emph{lime}.)} Quantile bins were used for five of the implementations, and the number of bins for these implementations was varied from 2 to 6.
-The sixth implementation of LIME used the kernel density estimates.
-The feature selection method and the computation of the weights were set to the default options in \emph{lime} of forward selection and Gower distance raised to an exponent of 1.
-
-\subsection{Explanation Scatterplots} \label{plot1}
+In this section, we introduce four visual diagnostic plots for the assessment of LIME.
+The plots focus on different levels of application of LIME (e.g.
+on explanation versus a set of explanations) to assess the LIME claims from different perspectives:
+
+\begin{enumerate}
+\item \emph{Explanation Scatterplot} (Section \ref{plot1}): Comparison of the explainer and complex models for an individual prediction of interest.
+\item \emph{Prediction Comparison Plot} (Section \ref{plot2}): Comparison of explainer and complex model predictions for a set of predictions.
+\item \emph{Feature Heatmap} (Section \ref{plot3}): Comparison of features selected by LIME across applications of LIME with different tuning parameters.k
+\item \emph{Assessment Metric Plot}: Comparison of performance metrics for LIME across applications of LIME with different tuning parameters. 
+\end{enumerate}
+
+\paragraph{The \data}
+
+To demonstrate the visualizations, we generate an example dataset that will be referred to as the \data.
+The \data \ contains \Sexpr{dim(sine_data)[1]} observations with three features and one response variable.
+The features, $x_1$, $x_2$, and $x_3$, are randomly sampled from Unif(\Sexpr{min}, \Sexpr{max}), Unif(\Sexpr{min}, \Sexpr{max}), and $\mbox{N}(0,1)$ distributions, respectively.
+A binary response variable $y$ is  created using a rotated sine curve.
+In particular, let $x'_1=x_1\cos(\theta)-x_2\sin(\theta)$ and $x'_2=x_1\sin(\theta)+x_2\cos(\theta)$ where $\theta=-0.9$.
+Then $y$ is defined as
+\begin{eqnarray}\label{eq:data}
+  y=\begin{cases}
+  \mbox{blue} & \mbox{ if } x'_2 > \sin\left(x'_1\right) \\
+  \mbox{red} & \mbox{ if } x'_2 \le \sin\left(x'_1\right) \ . %\nolabel
+  \end{cases}
+\end{eqnarray}
+Note that due to the creation of $y$ in this manner, $y$ is dependent on $x_1$ and $x_2$ and independent of $x_3$.
+
+The dataset is divided into a training set of \Sexpr{dim(sine_data_train)[1]} observations and a testing set of \Sexpr{dim(sine_data_test)[1]} observations.
+A random forest model is fit using the R package \emph{randomForest} (version \Sexpr{packageVersion("randomForest")}) \citep{liaw:2002} with the default settings.
+The model is applied to the test set to obtain predictions.
+\autoref{fig:sine-plot-data} shows scatterplots of $x_2$ versus $x_1$ from the training data (left) and the testing data (right).
+Both plots include the true classification boundary of the rotated sine function plotted as the solid black line.
+The training data are colored by the observed response variable ($y$), and the testing data are colored by the prediction probabilities from the random forest model ($\hat{y}$).
+The random forest model misclassifies \Sexpr{dim(sine_data_test %>% filter(y != rfpred))[1]} points on the classification boundary.
+These are identified by circles in \autoref{fig:sine-plot-data}.
+
+For the presentation of the explanation scatterplot, we focus on the misclassified point with $(x_1, x_2, x_3)$ coordinates of (\Sexpr{round(sine_poi$x1, 2)}, \Sexpr{round(sine_poi$x2, 2)}, \Sexpr{round(sine_poi$x3, 2)}) indicated by a diamond in \autoref{fig:sine-plot-data}.
+For the introduction of the other three plots, we use all observations in the \data test data as points of interest.
 
@@
 
-\begin{figure*}[!htp]
+\begin{figure*}[!tp]
 <<sine-plot1, out.width = '\\textwidth', fig.width = 10, fig.height = 4, warning = FALSE>>=
@@
 
+We perform six applications of LIME with different tuning parameters to the random forest predictions from all observations in the sine data test set.
+To do this, we use the R package \emph{limeaid} \footnote{Available on GitHub at https://github.com/goodekat/limeaid} (\Sexpr{packageVersion("limeaid")}), which applies a forked version\footnote{https://github.com/goodekat/lime} of the development version of the R package \emph{lime} (\Sexpr{packageVersion("lime")}) \citep{pedersen:2020}.
+The forked version allows us to export internal values from \emph{lime}.
+The tuning parameters are as follows.
+For each application, we specify that LIME returns the top two features in the explanation, because we expect $x_1$ and $x_2$ to be the important features.
+Note that the complexity of an explanation goes hand in hand with the number of features selected to be included in the explanation.
+Setting the number of features to a small number will make the explanation simpler but not necessarily more correct.
+A quantile bin based simulation method is used for five of the implementations with the number of bins varying from 2 to 6 by application.
+The sixth implementation of LIME uses a kernel density simulation method.
+The default methods for feature selection (forward selection) and the computation of the weights (Gower distance raised to an exponent of 1) are used for all applications.
+
+\subsection{Explanation Scatterplots} \label{plot1}
+
 \autoref{fig:sine-plot-poi} shows the visualization of the explanation produced by \emph{lime} for the prediction of interest.
@@
 \begin{figure}[!t]
-<<sine-feature-heatmap, out.width = '0.5\\textwidth', fig.width = 5, fig.height = 5.5>>=
+<<sine-feature-heatmap, out.width = '0.5\\textwidth', fig.width = 4, fig.height = 4>>=
 feature_heatmap(sine_lime_explain$explain,

### 2020-06-05 paper.Rnw
more edits

@@
 However, the quality of the resulting explanations relies on how well the explainer model captures the black-box model in a specified local region.
-Here we introduce four visual diagnostics to assess the quality of LIME explanations: (1) explanation scatterplot, (2) prediction comparison plot, (3) assessment metric plot, and (4) feature heatmap.
+Here we introduce three visual diagnostics to assess the quality of LIME explanations: (1) explanation scatterplot, (2) assessment metric plot, and (3) feature heatmap.
 We apply the visual diagnostics to a forensics bullet matching dataset to show examples where LIME explanations depend on the tuning parameters and the explainer model oversimplifies the black-box model.
@@
 We suggest the use of visual diagnostics for assessment.
-In this paper, we lay out the set of claims about LIME made by \citet{ribeiro:2016} and propose four visualizations for the assessment of these claims: (1) \emph{explanation scatterplot}, (2) \emph{prediction comparison plot}, (3) \emph{feature heatmap}, (4) \emph{assessment metric plot}.
+In this paper, we lay out the set of claims about LIME made by \citet{ribeiro:2016} and propose three visualizations for the assessment of these claims: (1) \emph{explanation scatterplot}, (2) \emph{feature heatmap}, (3) \emph{assessment metric plot}.
 While LIME has been implemented for image, tabular, and text data, we will only focus on tabular data.
@@
 
-In this section, we introduce four visual diagnostic plots for the assessment of LIME.
+In this section, we introduce three visual diagnostic plots for the assessment of LIME.
 The plots focus on different levels of application of LIME (e.g.
@@
 \begin{enumerate}
-\item \emph{Explanation Scatterplot} (Section \ref{plot1}): Comparison of the explainer and complex models for an individual prediction of interest.
-\item \emph{Prediction Comparison Plot} (Section \ref{plot2}): Comparison of explainer and complex model predictions for a set of predictions.
-\item \emph{Feature Heatmap} (Section \ref{plot3}): Comparison of features selected by LIME across applications of LIME with different tuning parameters.k
-\item \emph{Assessment Metric Plot}: Comparison of performance metrics for LIME across applications of LIME with different tuning parameters. 
+\item \emph{Explanation Scatterplot} (Section \ref{exp-scatter}): Comparison of the explainer and complex models for an individual prediction of interest.
+\item \emph{Feature Heatmap} (Section \ref{feat-heat}): Comparison of features selected by LIME across applications of LIME with different tuning parameters.
+\item \emph{Assessment Metric Plot} (Section \ref{assess-metric}): Comparison of performance metrics for LIME across applications of LIME with different tuning parameters. 
 \end{enumerate}
@@
 \begin{figure*}[!tp]
-<<sine-plot1, out.width = '\\textwidth', fig.width = 10, fig.height = 4, warning = FALSE>>=
+<<sine-exp-scatter, out.width = '\\textwidth', fig.width = 10, fig.height = 4, warning = FALSE>>=
 
@@
 
-plot1 <- ggplot() +
+exp_scatter <- ggplot() +
   geom_point(data = sine_poi_perms,
@@
 
-plot_grid(sine_poi_exp, plot1, align = "h")
-@
-\caption{\kgc{Edit...} (right) The explanation plot depicts the estimated parameters from the explainer model.
-The lengths of the bars represent the absolute values of the coefficients, and the colors of the bars represent the coefficient values.
-Since the magnitude of the coefficient associated with $x_2$ is longer than that of $x_1$, the explanation suggests that $x_2$ has more of an effect on the random forest prediction of interest than $x_1$ does.
-The explainer model comparison plot shows the simulated data colored by the random forest probabilities and sized by the assigned LIME weights.
+plot_grid(sine_poi_exp, exp_scatter, align = "h")
+@
+\caption{(left) Visualization from the \emph{lime} R package of the LIME explanation for the \data individual prediction of interest.
+The bars represent the explainer model coefficients.
+(right) \emph{Explanation Scatterplot} The points represent the simulated data colored by the random forest probabilities and sized by the assigned LIME weights.
 The prediction of interest is shown as the diamond shaped point.
-The quantile bins associated with $x_1$ and $x_2$ are depicted by the solid lines.
-The color of the line indicates whether the explainer model supports a prediction of 'blue' (blue line) or supports a prediction of 'red' (red lines).
+The explainer model indicator variables associated with $x_1$ and $x_2$ (quantile bins containing the prediction of interest) are depicted by the solid lines.
+The color of the lines indicates the explainer model explanation for whether the corresponding feature value supports a prediction of 'blue' (blue lines) or supports a prediction of 'red' (red lines).
 This figure shows that the quantile bins are not flexible enough to capture the relationship between the random forest predictions and the $x_1$ and $x_2$ values.}
-\label{fig:sine-plot-step3ab}
+\label{fig:sine-exp-scatter}
 \end{figure*}
@@
 
-\subsection{Explanation Scatterplots} \label{plot1}
-
-\autoref{fig:sine-plot-poi} shows the visualization of the explanation produced by \emph{lime} for the prediction of interest.
+\subsection{Explanation Scatterplots} \label{exp-scatter}
+
+The \emph{explanation scatterplot} is a visual diagnostic for assessing the LIME claims for an individual explanation by juxtaposing the complex and explainer models in one plot.
+The format of an explanation scatterplot depends on the LIME simulation method.
+We introduce the explanation scatterplot here under the default method in the \emph{lime} R package in which the data are simulated uniformly from four quantile bins.
+In this scenario, LIME converts continuous predictor variables to indicator variables identifying whether the variable value falls in the same quantile bin as the prediction of interest or not, and the indicator variables are used as the explainer model features.
+The explanation scatterplot achieves a juxtaposition of the complex and explainer models by plotting the LIME simulated data colored by the complex predictions overlaid by lines representing boundaries of the indicator variables used to fit the explainer model.
+The size of the points represents the weight assigned by LIME, and the color of the lines denote whether LIME indicates that a feature supports or contradicts a class prediction.
+A scatterplot is created for all pairwise combinations of features included in the LIME explanation.
+Appendix \ref{exp-scatter_plus} addresses the explanation scatterplot formats in other LIME simulation scenarios.
+
+To demonstrate an explanation scatterplot, we focus on the misclassified point indicated in Figure \ref{fig:sine-plot-data} by the diamond as the prediction of interest.
+The left plot in Figure \ref{fig:sine-exp-scatter} shows the visualization of the explanation produced by \emph{lime} for the prediction of interest.
 The figure shows that the random forest returned a probability of \Sexpr{sine_poi_lime_default$label_prob[1]} that the observation of interest belongs to category blue {(denoted as the ``label" in the figure).
 The colored bars indicate the features chosen by LIME and whether they support or contradict a random forest classification of blue.
-\kgc{Add explanation for bins in the plot.}
-
-The explanation for the prediction of interest depicted in Figure \ref{fig:sine-plot-poi} can be interpreted as follows.
+Note that the features are represented as regions in the figure.
+These are the indicator variable regions created by LIME.
+
+The explanation for the prediction of interest depicted in Figure \ref{fig:sine-exp-scatter} can be interpreted as follows.
 A random forest classification of blue is supported by the prediction of interest having a value of $x_2$ that is greater than \Sexpr{str_split(sine_poi_lime_default$feature_desc[[1]], pattern = " ")[[1]][1]}, but the prediction of interest having a value of $x_1$ that is greater than \Sexpr{str_split(sine_poi_lime_default$feature_desc[[2]], pattern = " ")[[1]][1]} and less than or equal to \Sexpr{str_split(sine_poi_lime_default$feature_desc[[2]], pattern = " ")[[1]][5]} provides support against a classification of blue.
@@
 
-\autoref{fig:sine-plot-poi} also includes an "explanation fit" value.
+\autoref{fig:sine-exp-scatter} also includes an "explanation fit" value.
 This value corresponds to the deviance ratio from the R package \emph{glmnet} \citep{simon:2011} for a ridge regression model, or in other words, this is the $R^2$ value associated with the explainer model.
@@
 
-The plot on the right of Figure \ref{fig:sine-plot-step3ab} is the complex and explainer model comparison plot for the prediction of interest from the \data.
+The plot on the right of Figure \ref{fig:sine-exp-scatter} is the complex and explainer model comparison plot for the prediction of interest from the \data.
 This figure shows the relationship between the random forest model and the LIME explainer model.
@@
 
-\subsection{Prediction Comparison Plot} \label{plot2}
-
-<<sine-mid-explainer-pred>>=
-# Determine the explainer model predictions with the
-# random forest predictions are between 0.25 and 0.75
-mid_expred <- sine_lime_default %>%
-  group_by(case, sim_method) %>%
-  ungroup() %>%
-  filter(label_prob > 0.25, label_prob < 0.75) %>%
-  select(label_prob, model_prediction)
-@
-
-\begin{figure}[!t]
-<<sine-plot-compare-bins, warning = FALSE, out.width = '0.5\\textwidth', fig.width = 6.75, fig.height = 5.5>>=
-
-# Compute the average explainer model predictions per bin
-bin_mean_exp_pred <- sine_lime_default %>%
-  select(case, model_prediction) %>%
-  group_by(case) %>%
-  slice(1) %>%
-  ungroup() %>%
-  full_join(sine_lime_default %>%
-              select(case, feature, feature_desc) %>%
-              spread(feature, feature_desc),
-            by = "case") %>%
-  group_by(x1, x2) %>%
-  summarise(mean_exp_pred = mean(model_prediction)) %>%
-  ungroup() %>%
-  separate(x1, c("x1_other", "x1_upper"), sep = " <= ") %>%
-  separate(x1_other, c("x1_almost_lower", "x1_other"), sep = "x1") %>%
-  select(-x1_other) %>%
-  separate(x1_almost_lower, c("x1_lower", "x1_other"), sep = " <") %>%
-  select(-x1_other) %>%
-  separate(x2, c("x2_other", "x2_upper"), sep = " <= ") %>%
-  separate(x2_other, c("x2_almost_lower", "x2_other"), sep = "x2") %>%
-  select(-x2_other) %>%
-  separate(x2_almost_lower, c("x2_lower", "x2_other"), sep = " <") %>%
-  select(-x2_other) %>%
-  mutate(x1_lower = ifelse(x1_lower == "", "-Inf", x1_lower),
-         x1_upper = ifelse(is.na(x1_upper), "Inf", x1_upper),
-         x2_lower = ifelse(x2_lower == "", "-Inf", x2_lower),
-         x2_upper = ifelse(is.na(x2_upper), "Inf", x2_upper)) %>%
-  mutate_at(.vars = c("x1_lower", "x1_upper",
-                      "x2_lower", "x2_upper"),
-            .funs = as.numeric) %>%
-  arrange(x1_lower)
-
-# Compute the lower and upper limits of the explainer model predictions
-pred_col_lower = min(bin_mean_exp_pred$mean_exp_pred)
-pred_col_upper = max(bin_mean_exp_pred$mean_exp_pred)
-
-# Plot of the average feature weights by bin
-ggplot() +
-  geom_rect(data = bin_mean_exp_pred,
-            mapping = aes(xmin = x1_lower,
-                          xmax = x1_upper,
-                          ymin = x2_lower,
-                          ymax = x2_upper,
-                          fill = mean_exp_pred),
-            alpha = 1) +
-  geom_point(data = sine_lime_default %>%
-               select(case, feature, feature_value,
-                      label_prob, model_prediction) %>%
-               spread(feature, feature_value),
-             mapping =  aes(x = x1, y = x2, color = label_prob)) +
-  geom_point(data = sine_lime_default %>%
-               select(case, feature, feature_value,
-                      label_prob, model_prediction) %>%
-               spread(feature, feature_value) %>%
-               mutate(rf1 = ifelse(label_prob > 0.5, TRUE, FALSE),
-                      lime1 = ifelse(model_prediction > 0.5,
-                                     TRUE, FALSE)) %>%
-               mutate(diff = rf1 - lime1) %>%
-               select(case, x1, x2, diff) %>%
-               filter(diff != 0) %>%
-               mutate(shape = "Random Forest \nMisclassified \nPredictions"),
-             mapping =  aes(x = x1, y = x2, color = label_prob,
-                            shape = shape),
-             alpha = 1,
-             size = 3,
-             color = "black") +
-  scale_color_gradient2(low = "firebrick",
-                        mid = '#f7f7f7',
-                        high = "steelblue",
-                        midpoint = 0.5,
-                        limits = c(pred_col_lower, pred_col_upper)) +
-  scale_fill_gradient2(low = "firebrick",
-                       mid = '#f7f7f7',
-                       high = "steelblue",
-                       midpoint = 0.5,
-                       limits = c(pred_col_lower, pred_col_upper)) +
-  scale_shape_manual(values = 1) +
-  xlim(-10, 10) +
-  ylim(-10, 10) +
-  theme_bw(base_family = "Times", base_size = 14) +
-  labs(x = TeX("$x_1$"),
-       y = TeX("$x_2$"),
-       shape = "",
-       fill = "Average \nExplainer \nModel \nProbability \nfor 'blue'",
-       color = "Random \nForest \nProbability \nfor 'blue'",
-       title = "Quantile Grid Comparison of LIME Explainer \nModel Predictions to Random Forest \nPredictions") +
-  guides(shape = guide_legend(order = 1),
-         fill = guide_legend(order = 2, reverse = T),
-         color = guide_legend(order = 3, reverse = T))
-
-@
-\caption{Plot comparing the LIME explainer models predictions to the random forest predictions in the context of the four $x_1$ and $x_2$ quantile bins.
-The intersection of the quantile bins are colored by the average of the test data explainer model probabilities located in the intersection.
-The points are the test set data and colored by the corresponding random forest probability.
-The observations misclassificed by the random forest are indicated by black open circles.}
-\label{fig:sine-plot-compare-bins}
-\end{figure}
-
-\autoref{fig:sine-plot-compare-bins} provides a visualization of the comparison of the explainer model predictions to the random forest predictions in the context of the $x_1$ and $x_2$ quantile bins.
-The intersection of the bins are colored by the average explainer model prediction of the test set observation located in the region.
-The \data \ test set is plotted as the circles and colored by the corresponding random forest probability.
-The test points that the random forest misclassified are encompassed by a black open circles.
-The plot highlights that the explainer models are over-simplifying the random forest predictions on the diagonal (lower left to upper right) where the explainer model predictions are close to 0.5, but the random forest probabilities range from 0 to 1.
-It is also possible to see the locations where the explainer model is over or under estimating the random forest model predictions on the off diagonals.
-
-\subsection{Feature Heatmap Diagnostic Plot} \label{plot3}
+The \data \ explanation only includes two features.
+In situations were more than two features are included in a LIME explanation, the explanation scatterplots can be extended to a generalized scatterplot matrix \kgc{(reference)} that includes all pairwise combinations of features.
+Generalized scatterplot matrices (and scatterplot matrices in general) fail to provide helpful information when the number of features becomes large \kgc{(reference)}.
+It is common in machine learning prediction problems for there to be a large number of features, and therefore, a generalized scatterplot matrix of explanation scatterplots would be ineffective.
+However, in the application of LIME, the user selects the number of features to return in the explanation (as previously mentioned).
+\citet{pedersen:2020} encourages users to select less than 10 features to include in the explanation \kgc{(need to check how to cite vignettes: https://cran.r-project.org/web/packages/lime/vignettes/Understanding\_lime.html)}.
+As a result, specifying a small number of features to include a LIME explanation leads to the feasibility of using generalized scatterplot matrices of explanation scatterplots to assess individual LIME explanations.
+
+\subsection{Feature Heatmap} \label{feat-heat}
 
@@
 \begin{figure}[!t]
-<<sine-feature-heatmap, out.width = '0.5\\textwidth', fig.width = 4, fig.height = 4>>=
+<<sine-feat-heat, out.width = '0.5\\textwidth', fig.width = 4, fig.height = 4>>=
 feature_heatmap(sine_lime_explain$explain,
@@
 The vertical striping seen in the plot indicates that LIME is not consistent in selecting features across implementation methods.}
-\label{fig:sine-feature-heatmap}
+\label{fig:sine-feat-heat}
 \end{figure}
 
-Explanations produced by LIME are likely affected by exact choice of tuning parameters.
+Explanations produced by LIME are likely to be affected by the choice of tuning parameters.
 An example of this was shown by Figures \ref{fig:concept-plot-good} and \ref{fig:concept-plot-bad} where the method used to weight the observations influenced the explanation.
 As of the time of writing this manuscript, there are no recommendations or procedures provided for how to determine which method to use besides for the default settings in \emph{lime} \kgc{(confirm this)}.
-In order to compare the explanations produced by LIME using different tuning parameters, we view an overview of all the explanations in the feature heatmap.
-
-We plot the features selected by LIME for all of the cases and tuning parameters in heatmaps separated by the position of importance assigned by LIME in a plot that will be referred to as a feature heatmap.
+In order to compare the explanations produced by LIME using different tuning parameters, we view an overview of all the explanations in the \emph{feature heatmap} visual diagnostic plot.
+
+The feature heatmap uses colors to identify the features selected by LIME for sets of predictions and tuning parameters faceted by the position of importance assigned by LIME.
 That is, for LIME applied for $t$ sets of tuning parameters to $n$ cases to select the $f$ top features, create $f$ heatmaps (one for each of the positions of importance) with the cases on the y-axis, the tuning parameters on the x-axis, and the cells colored by the feature chosen for the corresponding case and tuning parameter.
-This plot will be used assess the locality of the explanations and to compare results from different input options.
+This plot is used assess the locality of the explanations and to compare results from different input options.
 
@@
 The plots were created with the assumption that LIME was applied to select the top feature out of $p=8$ features for $n=10$ cases with $t=5$ sets of tuning parameters.
-If LIME were producing local explanations, it would be expected that the top features selected by LIME would vary for predictions located in different regions of the feature space unless a feature or several features are the deterministic features throughout the entire feature space.
-Additionally, if the tuning parameters used when implementing LIME did not affect the feature selected by LIME, the selected feature would be the same across all implementations for a case.
+If LIME produces local explanations, the top features selected by LIME will vary for predictions located in different regions of the feature space (unless a feature or several features are the deterministic features throughout the entire feature space).
+Additionally, if the tuning parameters did not affect the feature selected by LIME, the selected feature would be the same across all tuning parameters for a prediction.
 
@@
 
-\autoref{fig:sine-feature-heatmap} shows the feature heatmap for the LIME implementations applied to the \data.
+\autoref{fig:sine-feat-heat} shows the feature heatmap for the LIME implementations applied to the \data.
 The top row of the plot contains the features selected as the most important by LIME, and the bottom row contains the second most important feature selected by LIME.
@@
 
-\subsection{Assessment Metric Plot} \label{plot4}
+\subsection{Assessment Metric Plot} \label{assess-metric}
 
 \begin{figure}[!t]
-<<sine-metric-plot, out.width = '0.5\\textwidth', fig.width = 4.5, fig.height = 4, warning = FALSE>>=
+<<sine-assess-metric, out.width = '0.5\\textwidth', fig.width = 4.5, fig.height = 4, warning = FALSE>>=
 
@@
 The kernel density simulation methods performs well according to all three metrics.}
-\label{fig:sine-metric-plot}
+\label{fig:sine-assess-metric}
 \end{figure}
 
-The feature heatmap for the \data \ in the previous section showed an example of how LIME explanations are not always consistent across \hh{this sounds like R versus python implementation.
-It's not what you mean} implementation methods.
-As a result, it is necessary to choose \hh{tuning parameters} that produce reliable explanations.
-One way to do this, \sout{would be} to apply LIME using different implementations, and then compute assessment metrics to determine the optimal tuning parameters.
-We will discuss several metrics that could be used for this purpose and present a comparison of the metrics in a plot.
-\kgc{***Right now, I have not included any variability in these plots.
-I could add standard deviation bars or change these to box plot.}
-
-\kgc{I have moved all notation to the appendix. I will explain the metrics here in words.}
+The feature heatmap for the \data \ in the previous section showed an example inconsistent LIME explanations
+across tuning parameter applications.
+As a result, it is necessary to choose tuning parameters that produce reliable explanations.
+One way to do this is to apply LIME using different implementations, and compute assessment metrics to determine the optimal tuning parameters.
+We will discuss three metrics that could be used for this purpose and present a comparison of the metrics in a plot.
+
+Each metric presented below is computed on a set of LIME explanations associted with a set predictions of interest obtained using the the same tuning parameters.
 
 \begin{itemize}
-\item $R^2$: Once LIME has been applied to all observations of interest, an average $R^2$ can be computed from the explainer models within an implementation method. 
-\item Fidelity metric: for measuring the faithfulness of the explainer model to the complex model.
-This is done by comparing the complex and simple model predictions for each of the values in the simulated dataset accounting for the assigned weight.
-\item MSEE: meant to measure the faithfulness of the explainer model to the complex model by comparing their predictions, but instead of computing a squared difference over all observations in the simulated data, we only consider the observation of interest and compute the average squared deviation over the observations in the test set for an implementation of LIME.
+\item \emph{Average $R^2$}: A metric for the assessment of the model fit and linearity assumption computed as the average of ridge regression explainer models $R^2$ values (deviance ratios from the R package \emph{glmnet}).
+
+\item \emph{Average Fidelity}: Provides comparison of the complex and simple model predictions for each of the values in the simulated dataset accounting for the assigned weight computed as the average of the fidelity metric presented in \citet{ribeiro:2016} (weighted distance between explainer and complex model predictions for simulated data).
+
+\item \emph{Mean Squared Explanation Error (MSEE)}: Measures the faithfulness of the explainer model to the complex model by comparing their predictions similar to the average fidelity, but only the observation of interest is used to compute the average squared deviation over the observations in the test set.
 \end{itemize}
 
-In \autoref{fig:sine-metric-plot}, the average fidelity is lowest for the kernel density simulation method increases as the number of quantile bins increase.
+Notation and formulas for these metrics are included in Appendix \ref{metric-details}.
+
+\kgc{This is where I left off...}
+
+\kgc{***Right now, I have not included any variability in these plots. I could add standard deviation bars or change these to box plot.}
+
+In \autoref{fig:sine-assess-metric}, the average fidelity is lowest for the kernel density simulation method increases as the number of quantile bins increase.
 This would suggest that the LIME implementation using the kernel density estimate provides the best local approximation to the random forest model on average.
@@
 
-\begin{figure}[!t]
+\begin{figure}[!htp]
 \centering
-\includegraphics[width=1.5in]{./figure-static/gun.png}
-\includegraphics[width=1.58in]{./figure-static/bullet.png}
-\includegraphics[width=3in]{./figure-static/striae.png}
+\includegraphics[width=3in]{./figure-static/bullets.png}
 \caption{(Top left) Traditionally rifled gun barrel. Grooves and lands alternate to give bullets a spin during the firing process.
@@
 \label{fig:bullet}
-\end{figure}
-
-In current practice, forensic firearm  examiners evaluate whether two bullets come from the same source (are fired from the same gun) or from different sources based on microscopic comparison of the striation patterns engraved on bullets during the firing process (see \autoref{fig:bullet}).
-This process is based on a visual and therefore subjective assessment of the evidence under a comparison microscope.
-The lack of objective evaluation and the associated absence of established error rates has first been criticized by the National Research Council \cite{nrc:2009} and later by the President's Council of Advisors on Science and Technology \cite{pcast:2016}.
-
-In response, \citet{hare:2016} proposed an automated machine learning method for bullet matching to complement a visual inspection by firearm examiners.
-Based on high-resolution topological scans of land engraved areas \citet{hare:2016} obtain signatures of  striations from two bullet lands (\autoref{fig:signatures}).
-Nine features quantifying the similarity of signatures, such as the cross-correlation function, the distance between signatures, and the number of matching striae, are extracted and used to train a random forest model to determine the probability of a comparison resulting from the same source (matching signatures) or from different sources (non-matching signatures).
-
-\begin{figure}[!t]
-\centering
-\includegraphics[width=3.5in]{./figure-static/signatures.png}
+
+\vspace*{\floatsep}
+
+\includegraphics[width=3in]{./figure-static/signatures.png}
 \label{fig:signatures}
@@
 \end{figure}
+
+In current practice, forensic firearm  examiners evaluate whether two bullets come from the same source (are fired from the same gun) or from different sources based on microscopic comparison of the striation patterns engraved on bullets during the firing process (see \autoref{fig:bullet}).
+This process is based on a visual and therefore subjective assessment of the evidence under a comparison microscope.
+The lack of objective evaluation and the associated absence of established error rates has first been criticized by the National Research Council \cite{nrc:2009} and later by the President's Council of Advisors on Science and Technology \cite{pcast:2016}.
+
+In response, \citet{hare:2016} proposed an automated machine learning method for bullet matching to complement a visual inspection by firearm examiners.
+Based on high-resolution topological scans of land engraved areas \citet{hare:2016} obtain signatures of  striations from two bullet lands (\autoref{fig:signatures}).
+Nine features quantifying the similarity of signatures, such as the cross-correlation function, the distance between signatures, and the number of matching striae, are extracted and used to train a random forest model to determine the probability of a comparison resulting from the same source (matching signatures) or from different sources (non-matching signatures).
 
@@
 
-\begin{figure*}[!b]
+\begin{figure*}[!htp]
 <<bullet-plot-rfpcp, out.width = '\\textwidth', warning = FALSE>>=
@@
 \begin{figure*}[!t]
-<<bullet-metric-plot, out.width = '\\textwidth', warning = FALSE, fig.width = 10, fig.height = 4>>=
+<<bullet-assess-metric, out.width = '\\textwidth', warning = FALSE, fig.width = 10, fig.height = 4>>=
 
@@
 The density simulation methods perform well for all metrics, but the bin based metrics often do not agree in terms of performance across metrics.}
-\label{fig:bullet-metric-plot}
+\label{fig:bullet-assess-metric}
 \end{figure*}
 
-To try to identify the LIME implementation method with the most trustworthy set of explanations, we created an assessment metric plot shown in \autoref{fig:bullet-metric-plot}.
+To try to identify the LIME implementation method with the most trustworthy set of explanations, we created an assessment metric plot shown in \autoref{fig:bullet-assess-metric}.
 The three metrics of average fidelity, average $R^2$, and MSEE were computed for each of the simulation methods and Gower power used to implement LIME.
@@
 Without applying multiple implementations LIME to the bullet test data or viewing diagnostic plots of the LIME explanations, it may be very possible to formulate reasons why the LIME explanations make sense.
-However, the sequence of plots in this section (Figures \ref{fig:bullet-feature-heatmap}, \ref{fig:bullet-lime-expls}, \ref{fig:bullet-metric-plot}, \ref{fig:bullet-eois-match}, and \ref{fig:bullet-eois-nonmatch}) suggest that we should be cautious to trust any of these LIME explanations.
+However, the sequence of plots in this section (Figures \ref{fig:bullet-feature-heatmap}, \ref{fig:bullet-lime-expls}, \ref{fig:bullet-assess-metric}, \ref{fig:bullet-eois-match}, and \ref{fig:bullet-eois-nonmatch}) suggest that we should be cautious to trust any of these LIME explanations.
 While some of them provide an explanation that may be reasonable, there could be better explanations (as seen in the 3 quantile bin case of \autoref{fig:bullet-eois-match}), and some of them provide explanations that make no sense (as seen in \autoref{fig:bullet-lime-expls}).
@@
 Without an assessment of the explainer model, LIME is a black-box procedure of its own.
-We suggest the use of visual diagnostics to counteract the black-box nature of LIME and provide four diagnostic plots.
+We suggest the use of visual diagnostics to counteract the black-box nature of LIME and provide three diagnostic plots.
 Here we discuss the limitations and possible extensions of the diagnostic plots and concerns about LIME raise by applications of the diagnostics plots in this paper.
@@
 As a result, we proposed a visual comparison of two faithfulness metrics (MSEE and average fidelity).
-The examples of faithfulness metric comparisons in this paper (Figures \ref{fig:sine-metric-plot} and \ref{fig:bullet-metric-plot}) both produced confusing results.
+The examples of faithfulness metric comparisons in this paper (Figures \ref{fig:sine-assess-metric} and \ref{fig:bullet-assess-metric}) both produced confusing results.
 In both examples, the density based simulation methods resulted in the best or close to the best performance even though the feature heatmaps (Figures \ref{fig:sine-feature-heatmap} and \ref{fig:bullet-feature-heatmap}) showed that the density simulation methods produced global explanations with no variation in features selected by LIME.
@@
 
-\section{Details on Assessment Metrics}
+\section{Explanation Scatterplots Under Other Simulation Scenarios} \label{exp-scatter_plus}
+
+Section \ref{exp-scatter} introduces explanation scatterplots under the default simulation method in the \emph{lime} R package: four quantile bins.
+The structure of an explanation scatterplot remains the same for if any bin based simulation method is used to create the simulated data (any number of quantile or equally spaced bins).
+However, if the kernel density or normal approximation simulation methods are used as the simulation method, the format of the explanation scatterplot changes.
+In the density based simulation method scenarios, LIME uses the standardized versions of the predictor variables to fit the explainer model.
+Thus, the explainer model needs to be represented differently in the explanation scatterplot.
+
+When the kernel density or normal approximation simulation methods are applied, the explanation scatterplot depicts the complex model by plotting the complex model predictions versus a feature selected in LIME the explanation from the simulated data.
+The explainer model is included as a line on the figure where all features excluding the one plotted on the x-axis are set to the observed values of the prediction of interest.
+An explanation scatterplot is created for each feature included in the LIME explanation.
+As with the bin based simulation method, the size of the points represent the weight assigned by LIME.
+
+Figure ... provides example explanation scatterplots for each feature in the default LIME explanation for the \data individual prediction of interest indicated in Figure \ref{fig:sine-plot-data}.
+
+\kgc{Need to updated limeaid to create this plot and then add figure here.}
+
+\section{Details on Assessment Metrics} \ref{metric-details}
 

### 2020-06-05 paper.Rnw
edits through 3.2

@@
 
-Numerous methods have been proposed to provide explanations for black-box model predictions \citep{guidotti:2018, mohseni:2018, molnar:2019}.
+Numerous methods have been proposed to provide explanations for black-box model predictions \citep{gilpin:2018, guidotti:2018, ming:2017, mohseni:2018, molnar:2019}.
 Some are specific to one type of model (e.g.
-\citep{bau:2017} and \citep{hara:2016}), and others are model-agnostic (e.g.
-\citep{greenwell:2018} and \citep{strumbelj:2014}).
+\citep{simonyan:2013} and \citep{welling:2016}), and others are model-agnostic (e.g.
+\citep{fisher:2018} and \citep{strumbelj:2014}).
 In this paper, we focus on the model-agnostic method of LIME \citep{ribeiro:2016}.
@@
 
-\begin{figure*}[!htbp]
+\begin{figure*}[!thp]
 <<concept-plot-good, out.width = '\\textwidth', fig.width = 7.95, fig.height = 3.75, warning = FALSE>>=
@@
 
-\begin{figure*}[!t]
+\begin{figure*}[!thp]
 \centering
@@
 
-# Extract the explanations from the default lime implementation
+# Extract the explanations from the default lime application
 sine_lime_default <- sine_lime_explain$explain %>% filter(nbins == 4)
 
-# Extract the explanations from the default lime implementation
+# Extract the explanations from the default lime application
 # for the prediction of interest only
@@
 For the presentation of the explanation scatterplot, we focus on the misclassified point with $(x_1, x_2, x_3)$ coordinates of (\Sexpr{round(sine_poi$x1, 2)}, \Sexpr{round(sine_poi$x2, 2)}, \Sexpr{round(sine_poi$x3, 2)}) indicated by a diamond in \autoref{fig:sine-plot-data}.
+Misclassified points are often of interest to explain since they may provide information about ways to improve the model.
 For the introduction of the other three plots, we use all observations in the \data test data as points of interest.
+
+We perform six applications of LIME with different tuning parameters to the random forest predictions from all observations in the sine data test set.
+To do this, we use the R package \emph{limeaid} \footnote{Available on GitHub at https://github.com/goodekat/limeaid} (\Sexpr{packageVersion("limeaid")}), which applies a forked version\footnote{https://github.com/goodekat/lime} of the development version of the R package \emph{lime} (\Sexpr{packageVersion("lime")}) \citep{pedersen:2020}.
+The forked version allows us to export internal values from \emph{lime}.
+The tuning parameters are as follows.
+For each application, we specify that LIME returns the top two features in the explanation, because we expect $x_1$ and $x_2$ to be the important features.
+Note that the complexity of an explanation goes hand in hand with the number of features selected to be included in the explanation.
+Setting the number of features to a small number will make the explanation simpler but not necessarily more correct.
+A quantile bin based simulation method is used for five of the implementations with the number of bins varying from 2 to 6 by application.
+The sixth implementation of LIME uses a kernel density simulation method.
+The default methods for feature selection (forward selection) and the computation of the weights (Gower distance raised to an exponent of 1) are used for all applications.
+
+\subsection{Explanation Scatterplots} \label{exp-scatter}
 
@@
 
-\begin{figure*}[!tp]
+\begin{figure*}[!thp]
 <<sine-exp-scatter, out.width = '\\textwidth', fig.width = 10, fig.height = 4, warning = FALSE>>=
@@
   theme_bw(base_family = "Times", base_size = 10) +
-  labs(x = TeX("x'_1"),
-       y = TeX("x'_2"),
+  labs(x = TeX("x_1"),
+       y = TeX("x_2"),
        size = "Weight",
@@
        color = "Random \nForest \nProbability \nfor 'blue'",
-       title = "Complex and Explainer Model Comparison Plot") + 
+       title = "Explanation Scatterplot") + 
   guides(shape = guide_legend(order = 1)) + 
@@
 @
-\caption{(left) Visualization from the \emph{lime} R package of the LIME explanation for the \data individual prediction of interest.
+\caption{(left) Visualization from the \emph{lime} R package of the LIME explanation for the \data \ prediction of interest.
 The bars represent the explainer model coefficients.
-(right) \emph{Explanation Scatterplot} The points represent the simulated data colored by the random forest probabilities and sized by the assigned LIME weights.
+(right) \emph{Explanation Scatterplot}.
+The points represent the simulated data colored by the random forest probabilities and sized by the assigned LIME weights.
 The prediction of interest is shown as the diamond shaped point.
 The explainer model indicator variables associated with $x_1$ and $x_2$ (quantile bins containing the prediction of interest) are depicted by the solid lines.
-The color of the lines indicates the explainer model explanation for whether the corresponding feature value supports a prediction of 'blue' (blue lines) or supports a prediction of 'red' (red lines).
+The line colors represent the explainer model coefficient signs and indicate whether the feature supports a prediction of `blue' (blue lines) or supports a prediction of `red' (red lines).
 This figure shows that the quantile bins are not flexible enough to capture the relationship between the random forest predictions and the $x_1$ and $x_2$ values.}
@@
 
-We perform six applications of LIME with different tuning parameters to the random forest predictions from all observations in the sine data test set.
-To do this, we use the R package \emph{limeaid} \footnote{Available on GitHub at https://github.com/goodekat/limeaid} (\Sexpr{packageVersion("limeaid")}), which applies a forked version\footnote{https://github.com/goodekat/lime} of the development version of the R package \emph{lime} (\Sexpr{packageVersion("lime")}) \citep{pedersen:2020}.
-The forked version allows us to export internal values from \emph{lime}.
-The tuning parameters are as follows.
-For each application, we specify that LIME returns the top two features in the explanation, because we expect $x_1$ and $x_2$ to be the important features.
-Note that the complexity of an explanation goes hand in hand with the number of features selected to be included in the explanation.
-Setting the number of features to a small number will make the explanation simpler but not necessarily more correct.
-A quantile bin based simulation method is used for five of the implementations with the number of bins varying from 2 to 6 by application.
-The sixth implementation of LIME uses a kernel density simulation method.
-The default methods for feature selection (forward selection) and the computation of the weights (Gower distance raised to an exponent of 1) are used for all applications.
-
-\subsection{Explanation Scatterplots} \label{exp-scatter}
-
-The \emph{explanation scatterplot} is a visual diagnostic for assessing the LIME claims for an individual explanation by juxtaposing the complex and explainer models in one plot.
+The \emph{explanation scatterplot} is a visual diagnostic for assessing the LIME claims of locality and fidelity for an individual explanation by juxtaposing the complex and explainer models in one plot.
 The format of an explanation scatterplot depends on the LIME simulation method.
-We introduce the explanation scatterplot here under the default method in the \emph{lime} R package in which the data are simulated uniformly from four quantile bins.
-In this scenario, LIME converts continuous predictor variables to indicator variables identifying whether the variable value falls in the same quantile bin as the prediction of interest or not, and the indicator variables are used as the explainer model features.
-The explanation scatterplot achieves a juxtaposition of the complex and explainer models by plotting the LIME simulated data colored by the complex predictions overlaid by lines representing boundaries of the indicator variables used to fit the explainer model.
+We introduce the explanation scatterplot here under the \emph{lime} R package default method in which the data are simulated uniformly from four quantile bins.
+In this scenario, LIME converts continuous predictor variables to indicator variables identifying whether the variable value falls in the same quantile bin as the prediction of interest or not.
+The indicator variables are used as the explainer model features.
+The explanation scatterplot achieves a juxtaposition of the complex and explainer models by plotting the LIME simulated data for two features in an explanation colored by the complex predictions overlaid by lines representing boundaries of the indicator variables used to fit the explainer model.
 The size of the points represents the weight assigned by LIME, and the color of the lines denote whether LIME indicates that a feature supports or contradicts a class prediction.
-A scatterplot is created for all pairwise combinations of features included in the LIME explanation.
 Appendix \ref{exp-scatter_plus} addresses the explanation scatterplot formats in other LIME simulation scenarios.
@@
 To demonstrate an explanation scatterplot, we focus on the misclassified point indicated in Figure \ref{fig:sine-plot-data} by the diamond as the prediction of interest.
-The left plot in Figure \ref{fig:sine-exp-scatter} shows the visualization of the explanation produced by \emph{lime} for the prediction of interest.
-The figure shows that the random forest returned a probability of \Sexpr{sine_poi_lime_default$label_prob[1]} that the observation of interest belongs to category blue {(denoted as the ``label" in the figure).
-The colored bars indicate the features chosen by LIME and whether they support or contradict a random forest classification of blue.
-Note that the features are represented as regions in the figure.
-These are the indicator variable regions created by LIME.
+First, consider the left plot in Figure \ref{fig:sine-exp-scatter}, which shows the \emph{lime} R package visualization of the explanation for the prediction of interest.
+The figure shows that the random forest returned a probability of \Sexpr{round(sine_poi_lime_default$label_prob[1], 2)} that the observation of interest belongs to category blue {(denoted as the ``label" in the figure).The lengths of the bars represent the explainer model coefficients associated with the indicator variables chosen by LIME as important.
+The color of the bar denotes the sign of the coefficient and whether the feature supports or contradicts a random forest classification of `blue'.
+The "explanation fit" value is the deviance ratio from the R package \emph{glmnet} \citep{simon:2011} for a ridge regression model.
+In other words, this is the $R^2$ value associated with the explainer model.
+In this case, it is \Sexpr{round(sine_poi_lime_default$model_r2[1], 2)} suggesting that the explainer model is not a good linear fit.
+However, it is commonly accepted that $R^2$ has limitations for accessing the quality of fit of a model \citep{sapra:2014}, and it should not be the only metric used for assessment of a model.
 
@@
 Since the weight associated with $x_2$ has a larger magnitude than the weight associated with $x_1$, LIME explains that the $x_1$ and $x_2$ locations of the prediction of interest provide more support for a random forest classification of blue over red.
-This explanation agrees with the random forest probability of \Sexpr{sine_poi_lime_default$label_prob[1]} for blue, even though both classify the observation incorrectly.
-
-\autoref{fig:sine-exp-scatter} also includes an "explanation fit" value.
-This value corresponds to the deviance ratio from the R package \emph{glmnet} \citep{simon:2011} for a ridge regression model, or in other words, this is the $R^2$ value associated with the explainer model.
-In this case, it is \Sexpr{round(sine_poi_lime_default$model_r2[1], 2)} suggesting that the explainer model is not a good linear fit.
-However, it is commonly accepted that $R^2$ has limitations for accessing the quality of fit of a model \citep{sapra:2014}, and it should not be the only metric used for assessment of a model.
-Based on this metric or this plot, it is not yet possible to make an informed assessment of the trustworthiness of the explanation.
-
-The plot on the right of Figure \ref{fig:sine-exp-scatter} is the complex and explainer model comparison plot for the prediction of interest from the \data.
-This figure shows the relationship between the random forest model and the LIME explainer model.
-The random forest model is represented by the simulated values of $x'_2$ versus $x'_1$ colored by the random forest predictions.
-The explainer model is represented by the solid horizontal and vertical line identify the boundaries of the quantiles that contain the prediction of interest.
-The color of the lines represents whether the coefficient of the corresponding indicator variable in the explainer model supports a random forest prediction of 'blue' (blue lines) or not (red lines).
-Additionally, the size of the simulated data points represents the proximity weight used to fit the ridge regression explainer model.
+This explanation agrees with the random forest probability of \Sexpr{sine_poi_lime_default$label_prob[1]} for blue.
+Note that both models classify the observation incorrectly.
+Based on this plot alone, it is not possible to make an informed assessment of the explanation.
+
+To assess the explanation, we turn to an explanation scatterplot shown as the right plot in Figure \ref{fig:sine-exp-scatter}.
+The points are the simulated values of $x_2$ versus $x_1$ colored by the random forest predictions and sized by the proximity weight used to fit the ridge regression explainer model.
+The explainer model is represented by the solid horizontal and vertical lines identifying the boundaries of the quantiles that contain the prediction of interest.
+The color of the lines indicate whether the explainer model coefficient is positive (blue) or negative (red).
+Thus, the $x_2$ coefficient is positive, so the $x_2$ value of the prediction of interest supports a random forest prediction of `blue', and the $x_1$ coefficient is negative, so the $x_1$ value of the prediction of interest contradicts a random forest prediction of `blue'.
 The prediction of interest is represented by the diamond shaped point.
@@
 While it is still difficult to say whether or not the claim of localness has been violated, it is possible to say that the weights assigned to the simulated data do not agree with the local region assigned by the intersection of the quantile bins.
-Next, let us consider the claim of faithfulness.
-
-Within the intersection of the $x'_1$ and $x'_2$ quantile bins, there appears to be more random forest probabilities above 0.5.
+
+Now, consider the claim of faithfulness.
+Within the intersection of the $x_1$ and $x_2$ quantile bins, there are more random forest probabilities above 0.5.
 This indicates why the magnitude of the coefficient associated with $x_2$ is larger than that of $x_1$.
-However, the pattern of the random forest predictions in this plot suggest that a better explanations for this prediction exist.
-One example of a better explanation would be to say that the prediction of interest received a random forest prediction greater than 0.5 since the observation of interest falls in the region where $x_1$ is less than 2.5 and $x_2$ is greater 4.5.
-Another more localized explanation would be to say that  the region around the prediction of interest shows that observations with $-0.3 < x_1 <= 2.5$ and $4.8 < x_2 <= 8.75$ are all assigned probabilities greater than 0.5.
+However, the pattern of the random forest predictions in this plot suggest that better explanations for this prediction exist.
+One example of a better explanation is to say that the prediction of interest received a random forest prediction greater than 0.5 since the observation of interest falls in the region where $x_1$ is less than 2.5 and $x_2$ is greater 4.5.
+A more localized explanation is to say that the region around the prediction of interest shows that observations with $-0.3 < x_1 <= 2.5$ and $4.8 < x_2 <= 8.75$ are all assigned probabilities greater than 0.5.
 The procedure implemented by LIME is not flexible enough to capture either of these explanations.
@@
 LIME does provide an explanation for the prediction of interest, which makes sense based on the quantile bins used.
-However, the visualization of the complex and explainer model comparison plot solidifies the understanding that better explanations for the prediction of interest exist.
+However, the explanation scatterplot identifies that better explanations for the prediction of interest exist.
+It is difficult to assess linearity from an explanation scatterplot, but a residual plot of the explainer model could be used to check the linearity claim.
+See Appendix \ref{residual-plot} for the residual plot associated with the explanation considered in Figure \ref{fig:sine-exp-scatter} and shows a violation of the linearity claim.
 
@@
 Generalized scatterplot matrices (and scatterplot matrices in general) fail to provide helpful information when the number of features becomes large \kgc{(reference)}.
-It is common in machine learning prediction problems for there to be a large number of features, and therefore, a generalized scatterplot matrix of explanation scatterplots would be ineffective.
+It is common for machine learning models to have a large number of features, and therefore, a generalized scatterplot matrix of explanation scatterplots for all features would be ineffective.
 However, in the application of LIME, the user selects the number of features to return in the explanation (as previously mentioned).
-\citet{pedersen:2020} encourages users to select less than 10 features to include in the explanation \kgc{(need to check how to cite vignettes: https://cran.r-project.org/web/packages/lime/vignettes/Understanding\_lime.html)}.
-As a result, specifying a small number of features to include a LIME explanation leads to the feasibility of using generalized scatterplot matrices of explanation scatterplots to assess individual LIME explanations.
+\citet{pedersen:2020} encourage users to select less than 10 features to include in the explanation\footnote{https://cran.r-project.org/web/packages/lime/vignettes/Understanding\_lime.html}.
+As a result, specifying a small number of features to include in a LIME explanation makes it feasible to use generalized scatterplot matrices of explanation scatterplots.
 
@@
 
-\begin{figure}[!b]
-<<concept-heatmap, out.width = '0.5\\textwidth', fig.width = 6, fig.height = 3>>=
+\begin{figure}[!thp]
+<<concept-feat-heat, out.width = '0.48\\textwidth', fig.width = 6, fig.height = 3>>=
 # Specify the number of cases and LIME input options
@@
   geom_tile() +
-  labs(x = "Implementation Method",
+  labs(x = "Tuning Parameter",
        y = "Case",
        fill = "Feature",
+       color = "Feature",
        title = "Situation 1: \nConsistent Explanations") +
@@
   geom_tile() +
-  labs(x = "Implementation Method",
+  labs(x = "Tuning Parameter",
        y = "Case",
        fill = "Feature",
+       color = "Feature",
        title = "Situation 2: \nInconsistent Explanations") +
@@
 @
-\caption{Two hypothetical examples of feature heatmaps showing the top feature chosen for 10 cases across 5 different implementations of LIME (sets of tuning parameters).
-The color of the cell indicates the feature chosen by LIME.
-The plots represent two possible situations that may arise when applying LIME to a set of predictions.}
-\label{fig:concept-heatmap}
-\end{figure}
-
-\begin{figure}[!t]
-<<sine-feat-heat, out.width = '0.5\\textwidth', fig.width = 4, fig.height = 4>>=
+\caption{Hypothetical examples of feature heatmaps in two possible situations.
+The heatmaps show the top feature chosen for 10 cases across 5 different sets of LIME tuning parameters.
+The color of the cell indicates the feature chosen by LIME.}
+\label{fig:concept-feat-heat}
+
+\vspace*{\floatsep}
+
+<<sine-feat-heat, out.width = '0.45\\textwidth', fig.width = 4, fig.height = 4>>=
 feature_heatmap(sine_lime_explain$explain,
@@
 @
-\caption{Feature heatmap of the various LIME implementations applied to the \data.
-The cases from the test set are plotted on the y-axis, and the implementation methods are included on the x-axis.
-The colors of the tiles indicate the feature selected by LIME for the corresponding case and implementation method.
-The top faceted row includes the first features selected by LIME, and the bottom faceted row includes the second features selected by LIME.
-The faceted columns separate the kernel density implementation method from the quantile bin implementations.
-The vertical striping seen in the plot indicates that LIME is not consistent in selecting features across implementation methods.}
+\caption{\emph{Feature Heatmap}.
+An example feature heatmap of the explanations from the applications of LIME with different tuning parameters to the \data.
+The cases from the test set are plotted on the y-axis, and the tuning parameters (simulation methods in this example) are included on the x-axis.
+The colors of the tiles indicate the feature selected by LIME for the corresponding case and tuning parameter.
+The top facet includes the first features selected by LIME, and the second most important features are included in the bottom facet.
+The column facets separate the kernel density method from the quantile bin methods.
+The vertical striping seen in the plot indicates that the LIME explanations are not consistent across tuning parameters.}
 \label{fig:sine-feat-heat}
@@
 An example of this was shown by Figures \ref{fig:concept-plot-good} and \ref{fig:concept-plot-bad} where the method used to weight the observations influenced the explanation.
-As of the time of writing this manuscript, there are no recommendations or procedures provided for how to determine which method to use besides for the default settings in \emph{lime} \kgc{(confirm this)}.
-In order to compare the explanations produced by LIME using different tuning parameters, we view an overview of all the explanations in the \emph{feature heatmap} visual diagnostic plot.
-
-The feature heatmap uses colors to identify the features selected by LIME for sets of predictions and tuning parameters faceted by the position of importance assigned by LIME.
-That is, for LIME applied for $t$ sets of tuning parameters to $n$ cases to select the $f$ top features, create $f$ heatmaps (one for each of the positions of importance) with the cases on the y-axis, the tuning parameters on the x-axis, and the cells colored by the feature chosen for the corresponding case and tuning parameter.
+As of the time of writing this manuscript, we have encountered no recommendations for how to determine which method to use besides for the default settings in \emph{lime} \kgc{(confirm this)}.
+In order to compare the explanations produced by LIME using different tuning parameters, we visualize an overview the explanations in the \emph{feature heatmap} diagnostic plot.
+
+The feature heatmap uses colors to identify the features selected by LIME across tuning parameters for sets of explanations (referred to as cases here) faceted by the position of feature importance assigned by LIME.
+That is, for LIME applied with $t$ sets of tuning parameters to $n$ cases to select the $f$ top features, create $f$ heatmaps (one for each of the positions of importance determined by the magnitude of the explainer model coefficients) with the cases on the y-axis, the tuning parameters on the x-axis, and the cells colored by the feature chosen for the corresponding case and tuning parameter.
 This plot is used assess the locality of the explanations and to compare results from different input options.
 
-Two hypothetical examples of feature heatmaps are included in \autoref{fig:concept-heatmap}.
+Two hypothetical examples of feature heatmaps are included in \autoref{fig:concept-feat-heat}.
 The plots were created with the assumption that LIME was applied to select the top feature out of $p=8$ features for $n=10$ cases with $t=5$ sets of tuning parameters.
-If LIME produces local explanations, the top features selected by LIME will vary for predictions located in different regions of the feature space (unless a feature or several features are the deterministic features throughout the entire feature space).
-Additionally, if the tuning parameters did not affect the feature selected by LIME, the selected feature would be the same across all tuning parameters for a prediction.
-
-The plots in \autoref{fig:concept-heatmap} depict two different situations that may arise when applying LIME.
-Situation 1 shows an example where the features selected across implementation methods within a case are consistent, and the features selected by vary across cases.
-This is the ideal situation, because regardless which implementation method is used, the LIME explanations do not vary, and the explanations appear to be local since the features vary between cases.
-Situation 2 shows an example where the features selected across implementation methods within a case vary, but the features selected within an implementation method across cases are the same.
-This situation \sout{is not ideal, because it} indicates that the features selected by LIME are dependent on the implementation method used, and the explanations are not local because the same feature is chosen regardless of the case.
+Situation 1 shows an example where the features selected are consistent across tuning parameters within a case but vary across cases within a tuning parameter.
+This is the ideal situation, because the LIME explanations do not depend on the tuning parameters but do depend on the location of the observation in the feature space.
+Situation 2 shows an example where the features selected vary across tuning parameters within a case but are consistent across cases within a tuning parameter.
+This situation indicates that the features selected by LIME are dependent on the tuning parameters, and the explanations are not local because the same feature is chosen regardless of the case.
 In practice, it is expected that the plot will exhibit a combination of these two situations.
 
-\autoref{fig:sine-feat-heat} shows the feature heatmap for the LIME implementations applied to the \data.
-The top row of the plot contains the features selected as the most important by LIME, and the bottom row contains the second most important feature selected by LIME.
-For the quantile bin implementations, the original features prior to the interpretability transformation are plotted  since it is obvious that different features would be selected when the sizes of the bins change from one implementation to the next.
-This figure shows a clear difference in the explanations produced by LIME for the kernel density and two quantile bin methods and the other quantile bin methods.
-For both the kernel density and two quantile bin implementations, LIME selects $x_1$ as the most important feature and $x_2$ as the second most important feature across all cases in the test set.
-There is more variability in the features selected by LIME for the three to six quantile bin implementations.
-For these implementations, there is a mix of horizontal and vertical stripes, which suggests that LIME is not consistently providing the sample explanation across implementation methods.
-It is also interesting, that the implementations of 3 and 5 bins leads to the selection of the random noise variable of $x_3$ as an important variable in many predictions, which should not be the case.
+\autoref{fig:sine-feat-heat} shows the feature heatmap for the LIME applications to the 100 observations in the \data \ test set.
+The most important (top facet) and second most important (bottom facet) features are shown in this plot.
+For the quantile bins, the original features prior to the indicator variable transformation are included since it is obvious that different features would be selected when the sizes of the bins change.
+This figure shows that for the kernel density and 2 quantile bin implementations, LIME selects $x_1$ as the most important feature and $x_2$ as the second most important feature across all cases in the test set.
+These explanations are not local.
+There is variability in the features selected by LIME for 3 to 6 quantile bins.
+For these tuning parameters, there is a mix of horizontal and vertical stripes, which suggests a dependence on tuning parameters.
+Note that the explanations from 3 and 5 quantile bins include the selection of the random noise variable ($x_3$) as an important variable in many predictions, which should not be the case.
+The pattern seen in the explanations for 3 to 6 quantile bins may suggest local explanations, but the dependence on tuning parameter makes it unclear which set of explanations to use.
 
@@
 
-\begin{figure}[!t]
-<<sine-assess-metric, out.width = '0.5\\textwidth', fig.width = 4.5, fig.height = 4, warning = FALSE>>=
+\begin{figure}[!thp]
+<<sine-assess-metric, out.width = '0.49\\textwidth', fig.width = 4.5, fig.height = 4, warning = FALSE>>=
 
@@
 Each row of the plot corresponds to one of three metrics: average fidelity, average $R^2$, or MSEE.
-The tuning parameters from the different LIME implementations are plotted on the x-axis, and the metric values are shown on the y-axis.
+The LIME tuning parameters are plotted on the x-axis, and the metric values are shown on the y-axis.
 The points are colored by rank within a metric indicating best to worst (dark to light).
@@
 
-The feature heatmap for the \data \ in the previous section showed an example inconsistent LIME explanations
-across tuning parameter applications.
-As a result, it is necessary to choose tuning parameters that produce reliable explanations.
-One way to do this is to apply LIME using different implementations, and compute assessment metrics to determine the optimal tuning parameters.
-We will discuss three metrics that could be used for this purpose and present a comparison of the metrics in a plot.
-
-Each metric presented below is computed on a set of LIME explanations associted with a set predictions of interest obtained using the the same tuning parameters.
+The feature heatmap for the \data \ in the previous section shows an example of inconsistent LIME explanations across tuning parameters.
+In this situation, the user must determine which set of explanations to trust.
+One way to do this is to compute assessment metrics for each set of explanations to identify the optimal tuning parameters.
+We discuss three metrics for this purpose and present a visual comparison in an \emph{assessment metric plot}.
+
+Each metric presented below is computed on a set of LIME explanations associated with a set predictions of interest obtained using the the same tuning parameters.
+Here we provide a high level description of the metrics.
+Notation and formulas for these metrics are included in Appendix \ref{metric-details}.
 
@@
 
-Notation and formulas for these metrics are included in Appendix \ref{metric-details}.
-
-\kgc{This is where I left off...}
-
-\kgc{***Right now, I have not included any variability in these plots. I could add standard deviation bars or change these to box plot.}
-
-In \autoref{fig:sine-assess-metric}, the average fidelity is lowest for the kernel density simulation method increases as the number of quantile bins increase.
-This would suggest that the LIME implementation using the kernel density estimate provides the best local approximation to the random forest model on average.
-Note that the points in the plot are colored such that darker indicates a better metric value and lighter indicates a worse metric value.
-
-The 6 quantile bin simulation method has the lowest MSEE followed closely by the kernel density method, which suggests that these methods have explainer models that best approximate the complex model for the prediction of interest on average.
-The MSEE increases as the number of quantile bins increases.
-
-The average $R^2$ value is highest for the kernel density simulation method and decreases as the number of quantile bins increase.
-This metric agrees with the average fidelity, and it suggests that the the kernel density method leads to the best fitting explainer models on average.
-
-For the \data, the metrics of average fidelity and average $R^2$ are in perfect agreement \hh{what do you mean by perfect agreement?
-and how do you use the fidelity measure?} with which simulation methods lead to the recommended LIME methods.
-The MSEE is in agreement \hh{with ?
-} in terms of the kernel density method performing well in terms of faithfulness, but it orders the quantile bin methods in the opposite order from the average fidelity and $R^2$ values.
+\autoref{fig:sine-assess-metric} shows these metrics computed for each of the different tuning parameter applications of LIME to the \data.
+The simulation methods are listed on the x-axis.
+The plot is faceted by metric, and the metric values are plotted on the y-axis.
+The colors of the points represent the rank of the simulation methods performance based on a particular metric (darker indicates a better metric value and lighter indicates a worse metric value).
+Higher average $R^2$ values are better, and lower average fidelity and MSEE values are better.
+
+All three metrics suggest that the kernel density implementation performed well, but the metrics disagree for the quantile bins methods.
+Average $R^2$ values and average fidelity rank the performance of the number of quantile bins the same (2 quantile bins perform the best and 6 quantile bins perform the worst).
+In fact, these two metrics appear to have an inverse relationship in this example.
+MSEE provides different ranks of the simulation methods.
+MSEE suggests that 6 quantile bins perform the best, and 2 quantile bins perform the worst.
+This is the opposite of average $R^2$ and average fidelity.
+Since average fidelity and MSEE are similar metrics, it would be expected that they would agree, but that is so in this example.
 This may be due to the MSEE only taking into account the prediction of interest and not the full simulated dataset.
-
-The kernel density method performed well in regards to all three metrics.
+The contradiction between metrics makes it difficult to identify which simulation method explanations to trust.
+
 Recall that \autoref{fig:sine-feature-heatmap} indicated that the LIME kernel density method selected the same feature across all cases in the test dataset for both the first and second features.
 It appears that a global trend may be the best explanation for this example, which may be reasonable considering that we know that both $x_1$ and $x_2$ are the two features that should be the features used by the random forest to distinguish between response categories.
+At this point, the use of explanation scatterplots for individual predictions of interest may provide better insight into a selection of tuning parameters to use.
 
@@
 
-\begin{figure}[!htp]
+\begin{figure}[!thp]
 \centering
-\includegraphics[width=3in]{./figure-static/bullets.png}
+\includegraphics[width=2.5in]{./figure-static/bullets.png}
 \caption{(Top left) Traditionally rifled gun barrel. Grooves and lands alternate to give bullets a spin during the firing process.
@@
 
-\begin{figure*}[!htp]
+\begin{figure*}[!thp]
 <<bullet-plot-rfpcp, out.width = '\\textwidth', warning = FALSE>>=
@@
 
-\begin{figure*}[!th]
+\begin{figure*}[!thp]
 <<bullet-feature-heatmap, out.width = '\\textwidth', fig.width = 18, fig.height = 10.5>>=
@@
                 order_method = "PCA") +
-  scale_fill_gretchenalbrecht(palette = "last_rays",
-                              discrete = TRUE) +
+  scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) +
+  scale_color_gretchenalbrecht(palette = "last_rays", discrete = TRUE) +
   theme_bw(base_family = "Times", base_size = 10) +
@@
 
-\begin{figure*}[!t]
+\begin{figure*}[!thp]
 <<bullet-assess-metric, out.width = '\\textwidth', warning = FALSE, fig.width = 10, fig.height = 4>>=
@@
 
-\begin{figure*}[!htbp]
+\begin{figure*}[!thp]
 <<bullet-eois-nonmatch, out.width = '\\textwidth', fig.width = 12, fig.height = 6.25, message = FALSE>>=
@@
 
-\section{Details on Assessment Metrics} \ref{metric-details}
+\section{Explainer Model Residual Plot} \label{residual-plot}
+
+In order to assess the claim of linearity for the \data \ prediction of interest discussed in Section \ref{exp-scatter}, we use one of the most basic diagnostics in a statistician's tool box and draw a residual plot for the explainer model.
+This is shown in Figure \ref{fig:sine-plot-resids} with the explainer model residuals on the y-axis and explainer model predictions on the x-axis.
+The points along the x-axes have been jittered to ease the effect of the over-plotted points in the visualization.
+There is a clear increasing trend in the residuals as the explainer model predictions increase.
+This is a clear violation of the linearity assumption with the ridge regression model.
+
+\begin{figure}[!thp]
+<<sine-plot-resids, out.width = '0.5\\textwidth', fig.width = 4, fig.height = 3.25, warning = FALSE>>=
+
+# Calculate the residuals from the explainer model
+y <- sine_poi_perms$rfpred
+sine_poi_explainer <-
+  function(x1, x2) sine_b0 + (sine_b1 * x1) + (sine_b2 * x2)
+sine_poi_perms <- sine_poi_perms %>%
+  mutate(exppred = sine_poi_explainer(x1num, x2num)) %>%
+  mutate(resid = exppred - rfpred)
+
+# Create the residual plot
+ggplot(sine_poi_perms, aes(x = exppred, y = resid)) +
+  geom_jitter(alpha = 0.5, width = 0.02) +
+  geom_hline(yintercept = 0) +
+  theme_bw(base_family = "Times", base_size = 10) +
+  labs(x = "Explainer Model Predictions",
+       y = "Explainer Model Residuals",
+       title = "Explainer Model Residual Plot")
+@
+\caption{Residual plot of the explainer model associated with \data \ prediction of interest from Section \ref{exp-scatter}.
+The residuals are plotted against the predicted values.
+The points are jittered in the x-direction to alleviate the over-plotting of points.
+There is an upward trend in the residuals as the explainer model predictions increase, which suggests a violation of the linearity assumption.}
+\label{fig:sine-plot-resids}
+\end{figure}
+
+\section{Details on Assessment Metrics} \label{metric-details}
 
@@
 
-% \newpage
-% 
 % \textsc{\textbf{Ideas for describing proposed plots}}
@@
 % \end{itemize}
-% 
-% \textsc{\textbf{Ideas for Publishing}}
-% 
-% \begin{itemize}
-% \item longer review article (emph on CS method in ML - we're translating the content into a stats language) (talk to Maitra and Wendy)
-% \item review article would need a more extensive lit review:
-% \begin{itemize}
-% \item who has looked at LIME and found it not great
-% \item who is using LIME for applications
-% \item papers using LIME
-% \end{itemize}
-% \item the diagnostics plots could get put in a rapid research paper via DS journal
-% \item could consider JOSS for publication of the limeaid package
-% \item implement a hierarchical ordering method for the feature heatmap
-% \end{itemize}
-% 
-% \textsc{\textbf{Other Ideas}}
-% 
-% \begin{itemize}
-% \item Consider creating a plot to show the decay of the distance by Gower exponent in terms of standard deviations in the appendix.
-% \end{itemize}
 

### 2020-06-06 paper.Rnw
edits through sec 3

@@
 Setting the number of features to a small number will make the explanation simpler but not necessarily more correct.
-A quantile bin based simulation method is used for five of the implementations with the number of bins varying from 2 to 6 by application.
-The sixth implementation of LIME uses a kernel density simulation method.
+A quantile bin based simulation method is used for five of the LIME applications with the number of bins varying from 2 to 6 by application.
+The sixth application of LIME uses a kernel density simulation method.
 The default methods for feature selection (forward selection) and the computation of the weights (Gower distance raised to an exponent of 1) are used for all applications.
@@
 
-# Determine the bin cuts for the default lime implementation
+# Determine the bin cuts for the default lime application
 sine_lime_default_bin_cuts <- sine_lime_default %>%
@@
 The \data \ explanation only includes two features.
-In situations were more than two features are included in a LIME explanation, the explanation scatterplots can be extended to a generalized scatterplot matrix \kgc{(reference)} that includes all pairwise combinations of features.
-Generalized scatterplot matrices (and scatterplot matrices in general) fail to provide helpful information when the number of features becomes large \kgc{(reference)}.
-It is common for machine learning models to have a large number of features, and therefore, a generalized scatterplot matrix of explanation scatterplots for all features would be ineffective.
-However, in the application of LIME, the user selects the number of features to return in the explanation (as previously mentioned).
-\citet{pedersen:2020} encourage users to select less than 10 features to include in the explanation\footnote{https://cran.r-project.org/web/packages/lime/vignettes/Understanding\_lime.html}.
-As a result, specifying a small number of features to include in a LIME explanation makes it feasible to use generalized scatterplot matrices of explanation scatterplots.
+In situations were more than two features are included in a LIME explanation, the explanation scatterplots can be extended to a generalized pairs plot \citep{emerson:2013} that includes all pairwise combinations of features.
+Generalized pairs plots (and scatterplot matrices in general) fail to provide helpful information when the number of features becomes large.
+It is common for machine learning models to have a large number of features, and therefore, a generalized pairs plot of explanation scatterplots for all features would be ineffective.
+However, when applying LIME, the user selects the number of features to return in the explanation (as previously mentioned).
+In the \emph{lime} R package, \citet{pedersen:2020} encourage users to select less than 10 features to include in the explanation.
+As a result, specifying a small number of features to include in a LIME explanation makes it feasible to use generalized pairs plot of explanation scatterplots.
 
@@
 That is, for LIME applied with $t$ sets of tuning parameters to $n$ cases to select the $f$ top features, create $f$ heatmaps (one for each of the positions of importance determined by the magnitude of the explainer model coefficients) with the cases on the y-axis, the tuning parameters on the x-axis, and the cells colored by the feature chosen for the corresponding case and tuning parameter.
+Additional tuning parameters may also be included in the plot via facets.
 This plot is used assess the locality of the explanations and to compare results from different input options.
@@
 For the quantile bins, the original features prior to the indicator variable transformation are included since it is obvious that different features would be selected when the sizes of the bins change.
-This figure shows that for the kernel density and 2 quantile bin implementations, LIME selects $x_1$ as the most important feature and $x_2$ as the second most important feature across all cases in the test set.
+This figure shows that for kernel density and 2 quantile bins, LIME selects $x_1$ as the most important feature and $x_2$ as the second most important feature across all cases in the test set.
 These explanations are not local.
@@
 @
-\caption{Example of a metric comparison plot using the \data.
-Each row of the plot corresponds to one of three metrics: average fidelity, average $R^2$, or MSEE.
-The LIME tuning parameters are plotted on the x-axis, and the metric values are shown on the y-axis.
-The points are colored by rank within a metric indicating best to worst (dark to light).
+\caption{\emph{Assessment metric plot}.
+The assessment metrics computed on the applications of LIME to the \data \ test set are included in this example assessment metric plot.
+Each horizontal facet corresponds to one of three metrics: average $R^2$, average fidelity, or MSEE.
+The LIME tuning parameter (simulation methods in this example) is plotted on the x-axis, and the metric values are shown on the y-axis.
+The points are colored by rank (within a metric) indicating best to worst (dark to light).
 The kernel density simulation methods performs well according to all three metrics.}
@@
 
-Each metric presented below is computed on a set of LIME explanations associated with a set predictions of interest obtained using the the same tuning parameters.
+Each metric presented below is computed on a set of LIME explanations obtained using the the same tuning parameters.
 Here we provide a high level description of the metrics.
@@
 \begin{itemize}
-\item \emph{Average $R^2$}: A metric for the assessment of the model fit and linearity assumption computed as the average of ridge regression explainer models $R^2$ values (deviance ratios from the R package \emph{glmnet}).
-
-\item \emph{Average Fidelity}: Provides comparison of the complex and simple model predictions for each of the values in the simulated dataset accounting for the assigned weight computed as the average of the fidelity metric presented in \citet{ribeiro:2016} (weighted distance between explainer and complex model predictions for simulated data).
-
-\item \emph{Mean Squared Explanation Error (MSEE)}: Measures the faithfulness of the explainer model to the complex model by comparing their predictions similar to the average fidelity, but only the observation of interest is used to compute the average squared deviation over the observations in the test set.
+\item \emph{Average $R^2$}: Assess the model fit and linearity claim by computing the average of the explainer model $R^2$ values (deviance ratios from the R package \emph{glmnet}).
+
+\item \emph{Average Fidelity}: Measures the faithfulness of the explainer model to the complex model by comparing their predictions.
+Computed as the average of the explainer model fidelity metrics: a metric presented in \citet{ribeiro:2016} (the weighted distance between explainer and complex model predictions for all observations in the LIME simulated data associated with an individual prediction of interest).
+
+\item \emph{Mean Squared Explanation Error (MSEE)}: Also measures the faithfulness of the explainer model to the complex model by comparing their predictions, but only the prediction of interest is used to compute an average squared deviation between explainer and complex model predictions.
 \end{itemize}
 
-\autoref{fig:sine-assess-metric} shows these metrics computed for each of the different tuning parameter applications of LIME to the \data.
+\autoref{fig:sine-assess-metric} shows these metrics computed for each of the LIME applications to the \data \ test set.
 The simulation methods are listed on the x-axis.
@@
 Higher average $R^2$ values are better, and lower average fidelity and MSEE values are better.
-
-All three metrics suggest that the kernel density implementation performed well, but the metrics disagree for the quantile bins methods.
-Average $R^2$ values and average fidelity rank the performance of the number of quantile bins the same (2 quantile bins perform the best and 6 quantile bins perform the worst).
+This example only includes one tuning parameter: the simulation method.
+If more than one tuning parameter is considered, the assessment metric plot is extended by adding additional facets or levels to the x-axis.
+
+All three metrics suggest that the kernel density performed well, but the metrics disagree for the quantile bins methods.
+Average $R^2$ and average fidelity rank the performance of the number of quantile bins the same (2 quantile bins perform the best and 6 quantile bins perform the worst).
 In fact, these two metrics appear to have an inverse relationship in this example.
@@
 
-Recall that \autoref{fig:sine-feature-heatmap} indicated that the LIME kernel density method selected the same feature across all cases in the test dataset for both the first and second features.
+Recall that \autoref{fig:sine-feat-heat} indicated that the LIME kernel density method selected the same feature across all cases in the test set for both the first and second features.
 It appears that a global trend may be the best explanation for this example, which may be reasonable considering that we know that both $x_1$ and $x_2$ are the two features that should be the features used by the random forest to distinguish between response categories.
-At this point, the use of explanation scatterplots for individual predictions of interest may provide better insight into a selection of tuning parameters to use.
 
@@
 
-The \data \ is a relatively simple problem where the true decision boundary can be easily visualized and diagnostics for the performance of LIME can directly be compared to ground truth.
-In practice, we usually encounter more complicated situations.
-The remainder of this section provides a discussion of the visual diagnostics at the example of a practical data problem investigating the similarity of marks on fired bullets.
+In this section, we provide a discussion of the application of the visual diagnostics for LIME explanations to a practical data problem investigating the similarity of marks on fired bullets.
 
@@
 
-\begin{figure}[!thp]
+In current practice, forensic firearm  examiners evaluate whether two bullets come from the same source (are fired from the same gun) or from different sources based on microscopic comparison of the striation patterns engraved on bullets during the firing process (see \autoref{fig:bullet}).
+This process is based on a visual and therefore subjective assessment of the evidence under a comparison microscope.
+The lack of objective evaluation and the associated absence of established error rates has first been criticized by the National Research Council \cite{nrc:2009} and later by the President's Council of Advisors on Science and Technology \cite{pcast:2016}.
+
+In response, \citet{hare:2016} proposed an automated machine learning method for bullet matching to complement a visual inspection by firearm examiners.
+Based on high-resolution topological scans of land engraved areas \citet{hare:2016} obtain signatures of  striations from two bullet lands (\autoref{fig:signatures}).
+Nine features quantifying the similarity of signatures, such as the cross-correlation function, the distance between signatures, and the number of matching striae, are extracted and used to train a random forest model to determine the probability of a comparison resulting from the same source (matching signatures) or from different sources (non-matching signatures).
+
+\begin{figure}[!t]
 \centering
@@
 \end{figure}
-
-In current practice, forensic firearm  examiners evaluate whether two bullets come from the same source (are fired from the same gun) or from different sources based on microscopic comparison of the striation patterns engraved on bullets during the firing process (see \autoref{fig:bullet}).
-This process is based on a visual and therefore subjective assessment of the evidence under a comparison microscope.
-The lack of objective evaluation and the associated absence of established error rates has first been criticized by the National Research Council \cite{nrc:2009} and later by the President's Council of Advisors on Science and Technology \cite{pcast:2016}.
-
-In response, \citet{hare:2016} proposed an automated machine learning method for bullet matching to complement a visual inspection by firearm examiners.
-Based on high-resolution topological scans of land engraved areas \citet{hare:2016} obtain signatures of  striations from two bullet lands (\autoref{fig:signatures}).
-Nine features quantifying the similarity of signatures, such as the cross-correlation function, the distance between signatures, and the number of matching striae, are extracted and used to train a random forest model to determine the probability of a comparison resulting from the same source (matching signatures) or from different sources (non-matching signatures).
 
@@
 However, just as it is important to assess the random forest model for this high-stakes application, it is also important to assess the LIME explanations to make sure they are providing a trustworthiness understanding of the random forest model.
-We will apply LIME to rtrees and use our visual diagnostics to assess different implementations of LIME.
+We will apply LIME to rtrees and use our visual diagnostics to assess different LIME tuning parameters.
 
@@
 
-# Determine the implementation and case number of the poi
+# Determine the application and case number of the poi
 # in the no_perms data
@@
 @
-\caption{Feature heatmap of the 36 LIME implementations applied to the bullet comparison data test set.
+\caption{Feature heatmap of the 36 LIME applications to the bullet comparison data test set.
 In addition to faceting the results by simulation method and order a feature was selected by LIME as done in \autoref{fig:sine-feature-heatmap}, this plot has been faceted by the Gower power and whether the the observation is from a match (TRUE) or non-match (FALSE).
 This plot shows several key insights about the LIME explanations.
-First, the features selected by LIME for the density simulation methods are mostly the same for all implementations and all cases.
+First, the features selected by LIME for the density simulation methods are mostly the same for all tuning parameters and all cases.
 Second, the features selected by LIME for the bin based methods are affected by the number of bins but not the Gower power.
@@
 Each simulation method was implemented three times with Gower exponents of 0.5, 1, and 10.
-Thus, a total of $12\times 3=36$ different implementations of LIME were performed.
-These implementations of LIME were performed using our R package \emph{limeaid}.
-Each implementation was set to return 3 features by LIME and feature selection was performed using the highest weights method.
+Thus, a total of $12\times 3=36$ different applications of LIME were performed.
+These applications of LIME were performed using the R package \emph{limeaid}.
+Each application was set to return 3 features by LIME and feature selection was performed using the highest weights method.
 
@@
 
-To get an overview of the LIME explanations from the 36 implementations, we consider our heatmap diagnostic plot for comparing the LIME implementations first shown in \autoref{fig:bullet-feature-heatmap}.
+To get an overview of the LIME explanations from the 36 applications, we consider our heatmap diagnostic plot for comparing the LIME applications first shown in \autoref{fig:bullet-feature-heatmap}.
 The plot facets the features selected in the LIME explanations by the simulation method, the Gower power, the order the feature was chosen, and whether the observation is from a known match or non-match of bullet signatures.
@@
 
-First of all, the density simulation methods produced the same explanations for almost all cases and LIME implementation methods.
-As a result, the LIME explanations for the density implementation methods are global and not local.
+First of all, the density simulation methods produced the same explanations for almost all cases and LIME tuning parameters.
+As a result, the LIME explanations for the density methods are global and not local.
 Second, within a bin based simulation method, the features selected by LIME for an observation often vary based on the number of bins used but do not appear to vary based on the Gower power used.
@@
 This provides evidence that suggests that the features which the random forests uses to classify a match are different from the features used by the random forest to classify a non-match.
-The most important insight \autoref{fig:bullet-feature-heatmap} highlights is the dependence of the explanations on the LIME implementation method for many of the observations in the test data.
+The most important insight \autoref{fig:bullet-feature-heatmap} highlights is the dependence of the explanations on the LIME tuning parameter for many of the observations in the test data.
 
@@
 @
-\caption{Plot of LIME assessment metrics for the 36 different implementations of LIME applied to the bullet comparison data test set.
+\caption{Plot of LIME assessment metrics for the 36 different applications of LIME applied to the bullet comparison data test set.
 The shape of the points represents the power used for the Gower distance calculation, and the color of the points represents the rank associated with that observation within a metric.
@@
 
-To try to identify the LIME implementation method with the most trustworthy set of explanations, we created an assessment metric plot shown in \autoref{fig:bullet-assess-metric}.
+To try to identify the set of LIME tuning parameters with the most trustworthy set of explanations, we created an assessment metric plot shown in \autoref{fig:bullet-assess-metric}.
 The three metrics of average fidelity, average $R^2$, and MSEE were computed for each of the simulation methods and Gower power used to implement LIME.
@@
 The color of a point represents the rank within a metric.
-That is, the darker a point, the better performance of that implementation method based on the metric.
-
-The density simulation methods performed well across all implementation methods.
+That is, the darker a point, the better performance of that method based on the metric.
+
+The density simulation methods performed well across all tuning parameters.
 This is an interesting result, since \autoref{fig:bullet-feature-heatmap} shows that the density methods results in global explanations.
-The metric values for the bin based implementation methods do not agree across metrics.
+The metric values for the bin based methods do not agree across metrics.
 For example, 2 and 3 quantile bins performed well according to the average $R^2$ but poorly according to MSEE.
 As a result, with the bin based methods, it is difficult to know which method to recommend.
-When considering the metrics across the Gower power used, the implementations using a power of 0.5 perform best or as well as the other powers in across all simulation methods.
+When considering the metrics across the Gower power used, the applications using a power of 0.5 perform best or as well as the other powers in across all simulation methods.
 This suggests that the power that leads to a more global explanation is preferred by LIME in this example.
@@
 The bottom row of plots show scatterplots of the features selected by LIME colored by the random forest model prediction.
-The location of the prediction of interest is indicated on the scatterplots by a diamond, and black solid lines are included on the plots representing the bin divisions for implementations using bins.
+The location of the prediction of interest is indicated on the scatterplots by a diamond, and black solid lines are included on the plots representing the bin divisions for applications using bins.
 The bottom row plots are created using \emph{limeaid}.
-The plots within a column are associated with one of the three implementation methods (kernel density, 3 equal bins, or 3 quantile bins).
+The plots within a column are associated with one of the three simulation methods (kernel density, 3 equal bins, or 3 quantile bins).
 
@@
 The scatter plots shows that almost all simulated values with a value of matches less than or equal to 1.66 have random forest predictions close to 0.
-Similar statements can be made about the 3 equal bin explanation for this case and the bin based implementations for the known match observation explanations.
+Similar statements can be made about the 3 equal bin explanation for this case and the bin based methods for the known match observation explanations.
 
@@
 \caption{Plots of LIME explanations for one case in the test data that is a known non-match.
-Each column contains plots associated with a different implementation (3 quantile bins, 3 equal bins, or kernel density).
+Each column contains plots associated with a different application (3 quantile bins, 3 equal bins, or kernel density).
 The top row of plots are the explanation plots from \emph{lime}.
@@
 
-The scatter plots of the kernel density implementations for both the match and non-match case show that almost all of the simulated values have random forest predictions less than 0.5, which provide evidence in favor of a non-match.
+The scatter plots of the kernel density applications for both the match and non-match case show that almost all of the simulated values have random forest predictions less than 0.5, which provide evidence in favor of a non-match.
 It appears that simulation method is not providing enough values to cover the feature space that hit regions where the random forest provides predictions above 0.5.
@@
 
-Without applying multiple implementations LIME to the bullet test data or viewing diagnostic plots of the LIME explanations, it may be very possible to formulate reasons why the LIME explanations make sense.
+Without applying multiple applications LIME to the bullet test data or viewing diagnostic plots of the LIME explanations, it may be very possible to formulate reasons why the LIME explanations make sense.
 However, the sequence of plots in this section (Figures \ref{fig:bullet-feature-heatmap}, \ref{fig:bullet-lime-expls}, \ref{fig:bullet-assess-metric}, \ref{fig:bullet-eois-match}, and \ref{fig:bullet-eois-nonmatch}) suggest that we should be cautious to trust any of these LIME explanations.
@@
 
-The figures referenced in the previous paragraph from the \data \ example are all based on the implementation of LIME using a set of tuning parameters.
+The figures referenced in the previous paragraph from the \data \ example are all based on the application of LIME using a set of tuning parameters.
 From the use of the feature heatmap, we found that different sets of tuning parameters can produce different explanations.

### 2020-06-06 paper.Rnw
edits through 4.2

@@
 A quantile bin based simulation method is used for five of the LIME applications with the number of bins varying from 2 to 6 by application.
+We use 6 bins as the maximum, since the larger the number of bins, the more complex the explanation becomes.
 The sixth application of LIME uses a kernel density simulation method.
@@
 \begin{figure*}[!thp]
-<<sine-exp-scatter, out.width = '\\textwidth', fig.width = 10, fig.height = 4, warning = FALSE>>=
+<<sine-exp-scatter, out.width = '\\textwidth', fig.width = 10, fig.height = 3.9, warning = FALSE>>=
 
@@
 The \data \ explanation only includes two features.
-In situations were more than two features are included in a LIME explanation, the explanation scatterplots can be extended to a generalized pairs plot \citep{emerson:2013} that includes all pairwise combinations of features.
-Generalized pairs plots (and scatterplot matrices in general) fail to provide helpful information when the number of features becomes large.
-It is common for machine learning models to have a large number of features, and therefore, a generalized pairs plot of explanation scatterplots for all features would be ineffective.
-However, when applying LIME, the user selects the number of features to return in the explanation (as previously mentioned).
+In situations where more than two features are included in a LIME explanation, the explanation scatterplots can be extended to a generalized pairs plot \citep{emerson:2013} that includes all pairwise combinations of features.
+Generalized pairs plots (and scatterplot matrices in general) have diminishing value as the number of features increase \citep{jensen:2011} \citep{sweller:2011}.
+Machine learning models are commonly fit using a large number of features, and therefore, a generalized pairs plot of explanation scatterplots for all features would be ineffective.
+However, when applying LIME, the user selects the number of features to return in the explanation.
 In the \emph{lime} R package, \citet{pedersen:2020} encourage users to select less than 10 features to include in the explanation.
@@
 An example feature heatmap of the explanations from the applications of LIME with different tuning parameters to the \data.
-The cases from the test set are plotted on the y-axis, and the tuning parameters (simulation methods in this example) are included on the x-axis.
-The colors of the tiles indicate the feature selected by LIME for the corresponding case and tuning parameter.
-The top facet includes the first features selected by LIME, and the second most important features are included in the bottom facet.
+The cases from the test set are plotted on the y-axis, and the tuning parameter values (simulation methods here) are included on the x-axis.
+The colors of the tiles indicate the feature selected by LIME for the corresponding case and tuning parameter value.
+The plot is faceted by the first features selected by LIME (top facet) and the second most important features (bottom facet).
 The column facets separate the kernel density method from the quantile bin methods.
-The vertical striping seen in the plot indicates that the LIME explanations are not consistent across tuning parameters.}
+The vertical striping indicates that the LIME explanations are not consistent across tuning parameters.}
 \label{fig:sine-feat-heat}
@@
 \subsection{Bullet Matching Data}
-
-In current practice, forensic firearm  examiners evaluate whether two bullets come from the same source (are fired from the same gun) or from different sources based on microscopic comparison of the striation patterns engraved on bullets during the firing process (see \autoref{fig:bullet}).
-This process is based on a visual and therefore subjective assessment of the evidence under a comparison microscope.
-The lack of objective evaluation and the associated absence of established error rates has first been criticized by the National Research Council \cite{nrc:2009} and later by the President's Council of Advisors on Science and Technology \cite{pcast:2016}.
-
-In response, \citet{hare:2016} proposed an automated machine learning method for bullet matching to complement a visual inspection by firearm examiners.
-Based on high-resolution topological scans of land engraved areas \citet{hare:2016} obtain signatures of  striations from two bullet lands (\autoref{fig:signatures}).
-Nine features quantifying the similarity of signatures, such as the cross-correlation function, the distance between signatures, and the number of matching striae, are extracted and used to train a random forest model to determine the probability of a comparison resulting from the same source (matching signatures) or from different sources (non-matching signatures).
-
-\begin{figure}[!t]
-\centering
-\includegraphics[width=2.5in]{./figure-static/bullets.png}
-\caption{(Top left) Traditionally rifled gun barrel. Grooves and lands alternate to give bullets a spin during the firing process.
-Barrel create markings (striations) on a bullet when fired.
-(Top right) Image of a fired bullet.
-The vertical stripes along the lower half of the bullet show groove and land engraved areas.
-The land engraved areas contain the microscopic striations created when the bullet passed through the barrel of the gun.
-(Bottom) Zoomed in image of a land engraved area showing striations (vertical lines).}
-\label{fig:bullet}
-
-\vspace*{\floatsep}
-
-\includegraphics[width=3in]{./figure-static/signatures.png}
-\label{fig:signatures}
-\caption{Bullet signatures extracted from two bullets fired through the same barrel.
-The two signatures come from the same barrel-land and therefore have very similar patterns.
-The features used in the random forest from \citet{hare:2016} are different metrics that measure the similarity between two such signatures.}
-\end{figure}
 
@@
 
+# Create an ordered version of the data
 bullet_features_ordered <- bullet_features_ordered %>%
@@
 
-The random forest model trained in \citet{hare:2016} is available as object rtrees from the \emph{bulletxtrctr} R package.
-rtrees is trained on a set of scans obtained from one set of bullets of the James Hamby Consecutively Rifled Ruger Barrel Study \citep{hamby:2009} and based on \Sexpr{dim(bullet_train)[1]} land-to-land comparisons.
+In current practice, forensic firearm examiners evaluate whether two bullets are from the same source (fired from the same gun) or from different sources based on microscopic comparison of the striation patterns engraved on bullets during the firing process (see \autoref{fig:bullet}).
+The process is based on a visual and therefore subjective assessment of the evidence.
+The lack of objective evaluation and the associated absence of established error rates has first been criticized by the National Research Council \cite{nrc:2009} and later by the President's Council of Advisors on Science and Technology \cite{pcast:2016}.
+
+In response, \citet{hare:2016} proposed an automated machine learning method for bullet matching to complement a visual inspection by firearm examiners.
+Based on high-resolution topological scans of land engraved areas \citet{hare:2016} obtain signatures of striations from two bullet lands (\autoref{fig:signatures}).
+Nine features quantifying the similarity of signatures, such as the cross-correlation function, the distance between signatures, and the number of matching striae, are extracted and used to train a random forest model (available in the \emph{bulletxtrctr} R package) to determine the probability of a comparison resulting from the same source (matching signatures) or from different sources (non-matching signatures).
+The model was trained on a set of scans of bullets from the James Hamby Consecutively Rifled Ruger Barrel Study \citep{hamby:2009}, which includes \Sexpr{dim(bullet_train)[1]} land-to-land comparisons.
+
+\begin{figure}[!t]
+\centering
+\includegraphics[width=2.25in]{./figure-static/bullets.png}
+\caption{(Top left) Traditionally rifled gun barrel.
+The grooves and lands alternate to give bullets a spin during the firing process, which create markings (striations) on a bullet when fired.
+(Top right) Image of a fired bullet.
+The vertical stripes along the lower half of the bullet show groove and land engraved areas.
+The land engraved areas contain the microscopic striations created when the bullet passed through the barrel of the gun.
+(Bottom) Close up of a land engraved area showing striations (vertical lines).}
+\label{fig:bullet}
+
+\vspace*{\floatsep}
+
+\includegraphics[width=3.25in]{./figure-static/signatures.png}
+\label{fig:signatures}
+\caption{Example bullet signatures.
+The bullet signatures are from the same barrel-land and therefore have very similar patterns.
+The \citet{hare:2016} random forest uses features that measure the similarity between two such signatures.}
+\end{figure}
+
+\subsection{Application of LIME to Bullet Matching Data}
 
@@
 @
-\caption{Parallel coordinate plots of rtrees training and testing data.
-The training data are included in the plots on the top row, and the testing data are included in the plots on the bottom row.
-The left column contains the observations which are know to be comparisons of lands that are not from the same gun, and the known same source comparisons are on the right.
-The y-axis shows the standardized feature values, and the x-axis shows the features used to fit the random forest (ordered by feature importance).
-Each line corresponds to a comparison, and the color of the line represents the associated random forest probability.
-These figures show a clear relationship between the feature values and the probability returned by the random forest.}
+\caption{Parallel coordinate plots of the \citet{hare:2016} random forest predictions from the training (top facet) and testing (bottom facet) data.
+The observations are separated by same source (right column) and different source (left column) The y-axis shows the standardized feature values, and the x-axis shows the features used to fit the random forest (ordered by random forest impurity based feature importance).
+Each line corresponds to a comparison, and the line color represents the associated random forest probability.
+There are clear relationships between the feature values and the random forest probabilities.}
 \label{fig:bullet-plot-rfpcp}
@@
 
-rtrees was tested on another set of bullets from the Hamby study with \Sexpr{dim(bullet_test)[1]} rows of land comparisons.
-\autoref{fig:bullet-plot-rfpcp} shows parallel coordinate plots of the rtrees training (top row) and testing (bottom row) datasets.
-The plots on the left contain comparisons know to be from from different sources, and the plots on the right contain comparisons know to be from the same source.
-Each line represents one observation in the data, and the color of the line represents the by the corresponding random forest probability.
-The standardized feature values are plotted on the y-axis, and the features are plotted on the x-axis, which are ordered from left to right from the highest to lowest random forest feature importance.
-
-The majority of observations with random forest probabilities close to 1 have a clear pattern of corresponding feature values as can be seen in the plots where same source is known to be true.
-The observations where the random forest is wrong in returning high probabilities when same source is known to be true (i.e.
-same source is true but the random forest probabilities are between 0 and 0.5) have feature values that reflect those of observations where same source is known to be false as seen in the plots on the left.
-These plots provide insight into why the random forest is producing poor random forest probabilities for these observations.
-
-Since firearm identification is commonly used as evidence for convictions in court cases, it is important to be able to understand and assess the model that is used to quantify the probability that a bullet was fired from a gun.
-An application of LIME to rtrees could provide an understanding of the key variables used by the random forest model to make a prediction.
-However, just as it is important to assess the random forest model for this high-stakes application, it is also important to assess the LIME explanations to make sure they are providing a trustworthiness understanding of the random forest model.
-We will apply LIME to rtrees and use our visual diagnostics to assess different LIME tuning parameters.
-
-\subsection{Application of LIME to Bullet Matching Data}
+Since firearm identification is commonly used as evidence for convictions in court cases, it is important to be able to understand and assess a model used to quantify the probability that a bullet was fired from a gun.
+LIME explanations would provide a local explanation for an individual prediction, but just as it is important to assess the model for this high-stakes application, it is also important to assess the LIME explanations.
+We will demonstrate an assessment of LIME explanations using the visual diagnostics introduced in this paper.
+
+We apply the random forest model from \citet{hare:2016} to another set of bullets from the Hamby study with \Sexpr{dim(bullet_test)[1]} rows of land comparisons.
+We first consider a global visualization of the relationship between the random forest predictions and the model features by creating a parallel coordinate plot of the training data (top facet) and testing data (bottom facets) predictions (\autoref{fig:bullet-plot-rfpcp}).
+The majority of same source observations with random forest probabilities close to 1 have a clear pattern of corresponding feature values.
+The known same source observations where the random forest is wrong (does not return probabilities close to 1) have feature values that reflect those of observations where same source is known to be false.
+
+LIME is implemented using the R package \emph{limeaid} to apply LIME multiple times to all test set observations using different tuning parameters: 12 sampling methods (2-6 equally spaced bins, 2-6 quantile bins, kernel density estimation, and normal approximation) and 3 Gower exponents (0.5, 1, and 10).
+Thus, a total of $12\times 3=36$ different applications of LIME were performed.
+We specify that each LIME explanation return 3 features and feature selection was performed using the highest weights method (default option).
 
@@
 
+\subsection{LIME Assessment Visualizations}
+
+To get an overview of the LIME explanations from the 36 applications, we consider a feature heatmap (\autoref{fig:bullet-feature-heatmap}).
+The plot is faceted vertically by simulation method and the Gower power and horizontally by the order the feature was chosen and whether the observation is a known same source or different source comparison.
+\kgc{This is where I left off...} This plot highlights several key features of the LIME explanations from the bullet matching dataset.
+
+First of all, the density simulation methods produced the same explanations for almost all cases and LIME tuning parameters.
+As a result, the LIME explanations for the density methods are global and not local.
+Second, within a bin based simulation method, the features selected by LIME for an observation often vary based on the number of bins used but do not appear to vary based on the Gower power used.
+Especially with the equal bin explanations, there are vertical stripes that suggest a dependence of the LIME explanations on the number of bins used.
+The vertical stripes are not as apparent with the quantile bins.
+Lastly, there are clear differences between the LIME explanations for the cases that are matches and those that are not matches which are produced by the bin based simulation methods.
+This provides evidence that suggests that the features which the random forests uses to classify a match are different from the features used by the random forest to classify a non-match.
+The most important insight \autoref{fig:bullet-feature-heatmap} highlights is the dependence of the explanations on the LIME tuning parameter for many of the observations in the test data.
+
 \begin{figure*}[!thp]
@@
 \label{fig:bullet-feature-heatmap}
-\end{figure*}
-
-We apply LIME to each prediction from the bullet test data obtained from the 'rtrees' random forest model for each of the four sampling methods (equally spaced bins, quantile bins, kernel density estimation, and normal approximation).
-For each of the bin based sampling methods, LIME was applied for 2 to 6 bins.
-It was decided to use 6 bins as the maximum, since the larger the number of bins, the more complex the explanation becomes.
-Each simulation method was implemented three times with Gower exponents of 0.5, 1, and 10.
-Thus, a total of $12\times 3=36$ different applications of LIME were performed.
-These applications of LIME were performed using the R package \emph{limeaid}.
-Each application was set to return 3 features by LIME and feature selection was performed using the highest weights method.
-
-\subsection{LIME Assessment Visualizations}
-
-To get an overview of the LIME explanations from the 36 applications, we consider our heatmap diagnostic plot for comparing the LIME applications first shown in \autoref{fig:bullet-feature-heatmap}.
-The plot facets the features selected in the LIME explanations by the simulation method, the Gower power, the order the feature was chosen, and whether the observation is from a known match or non-match of bullet signatures.
-This plot highlights several key features of the LIME explanations from the bullet matching dataset.
-
-First of all, the density simulation methods produced the same explanations for almost all cases and LIME tuning parameters.
-As a result, the LIME explanations for the density methods are global and not local.
-Second, within a bin based simulation method, the features selected by LIME for an observation often vary based on the number of bins used but do not appear to vary based on the Gower power used.
-Especially with the equal bin explanations, there are vertical stripes that suggest a dependence of the LIME explanations on the number of bins used.
-The vertical stripes are not as apparent with the quantile bins.
-Lastly, there are clear differences between the LIME explanations for the cases that are matches and those that are not matches which are produced by the bin based simulation methods.
-This provides evidence that suggests that the features which the random forests uses to classify a match are different from the features used by the random forest to classify a non-match.
-The most important insight \autoref{fig:bullet-feature-heatmap} highlights is the dependence of the explanations on the LIME tuning parameter for many of the observations in the test data.
-
-\begin{figure*}[!thp]
+
+\vspace*{\floatsep}
+
 <<bullet-assess-metric, out.width = '\\textwidth', warning = FALSE, fig.width = 10, fig.height = 4>>=

### 2020-06-09 paper.Rnw
updates to paper after updating limeaid

@@
 
-<<sine-feat-heat, out.width = '0.45\\textwidth', fig.width = 4, fig.height = 4>>=
-feature_heatmap(sine_lime_explain$explain,
+<<sine-feat-heat, out.width = '0.45\\textwidth', fig.width = 4, fig.height = 3.5>>=
+plot_feature_heatmap(sine_lime_explain$explain,
                 order_method = "PCA") +
@@
         axis.text.y = element_blank(),
-        axis.ticks.y = element_blank()) +
+        axis.ticks.y = element_blank(),
+        strip.background = element_rect(color = "white", fill = "white")) +
   labs(y = "Case")
@@
 \begin{figure}[!thp]
-<<sine-assess-metric, out.width = '0.49\\textwidth', fig.width = 4.5, fig.height = 4, warning = FALSE>>=
+<<sine-assess-metric, out.width = '0.49\\textwidth', fig.width = 4.5, fig.height = 3.75, warning = FALSE>>=
 
 # Create the metric plot
-metric_plot(sine_lime_explain$explain) +
+plot_metrics(sine_lime_explain$explain, rank_legend = "discrete") +
   theme_bw(base_family = "Times") + 
-  scale_color_gradient(low = "grey10", high = "grey90")
+  theme(strip.background = element_rect(color = "white", fill = "white"))
 
@@
 # Create a feature heatmap
-feature_heatmap(bullet_explain %>%
+plot_feature_heatmap(bullet_explain %>%
                   mutate(label = as.factor(label)),
@@
   scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) +
-  scale_color_gretchenalbrecht(palette = "last_rays", discrete = TRUE) +
-  theme_bw(base_family = "Times", base_size = 10) +
+  scale_color_gretchenalbrecht(palette = "last_rays", discrete = TRUE, reverse = TRUE) +
+  theme_bw(base_family = "Times", base_size = 16) +
   theme(axis.text.y = element_blank(),
-        axis.ticks.y = element_blank()) +
-  labs(y = "Case")
+        axis.ticks.y = element_blank(),
+        strip.background = element_rect(color = "white", fill = "white"),
+        strip.text.y.right = element_text(angle = 0), 
+        legend.position = "bottom",
+        axis.text.x = element_text(angle = 45, hjust = 1)) +
+  guides(fill = guide_legend(nrow = 1)) + 
+  labs(y = "Case", color = "Complex Model Feature", fill = "Complex Model Feature")
 
@@
 Second, the features selected by LIME for the bin based methods are affected by the number of bins but not the Gower power.
-Third, the explanations produced by LIME using bin based methods result in different important features for the matches and non-matches.
-\kgc{***Need to rotate the facet labels, so I can make the text bigger.}}
+Third, the explanations produced by LIME using bin based methods result in different important features for the matches and non-matches.}
 \label{fig:bullet-feature-heatmap}
@@
 # Create a metric comparison plot
-metric_plot(bullet_explain %>% mutate(label = as.factor(label))) +
+plot_metrics(bullet_explain %>% mutate(label = as.factor(label)), add_lines = TRUE) +
   theme_bw(base_family = "Times") +
-  scale_color_gradient(low = "grey10", high = "grey90") +
-  labs(color = "Rank \n(within \na metric)")
-
+  theme(strip.background = element_rect(color = "white", fill = "white"))
 @
@@
 The shape of the points represents the power used for the Gower distance calculation, and the color of the points represents the rank associated with that observation within a metric.
-The density simulation methods perform well for all metrics, but the bin based metrics often do not agree in terms of performance across metrics.}
+The density simulation methods perform well for all metrics, but the bin based metrics often do not agree in terms of performance across metrics.
+\kgc{Something is wrong here.
+Right now, there are repetitions of some tuning parameter combinations.}}
 \label{fig:bullet-assess-metric}
@@
 
-eoi1_3qb <- eoi_plot(bullet_explain_perms[1:3,], alpha = 0.9, weights = FALSE) +
+eoi1_3qb <- plot_explain_scatter(bullet_explain_perms[1:3,], alpha = 0.9, weights = FALSE) +
   scale_color_gradient2(low = "grey50",
@@
 
-eoi2_3qb <- eoi_plot(bullet_explain_perms[4:6,], alpha = 0.9, weights = FALSE) +
+eoi2_3qb <- plot_explain_scatter(bullet_explain_perms[4:6,], alpha = 0.9, weights = FALSE) +
   scale_color_gradient2(low = "grey50",
@@
 
-eoi1_3eb <- eoi_plot(bullet_explain_perms[7:9,], alpha = 0.9, weights = FALSE) +
+eoi1_3eb <- plot_explain_scatter(bullet_explain_perms[7:9,], alpha = 0.9, weights = FALSE) +
   scale_color_gradient2(low = "grey50",
@@
 
-eoi2_3eb <- eoi_plot(bullet_explain_perms[10:12,], alpha = 0.9, weights = FALSE) +
+eoi2_3eb <- plot_explain_scatter(bullet_explain_perms[10:12,], alpha = 0.9, weights = FALSE) +
   scale_color_gradient2(low = "grey50",
@@
 
-eoi1_kd <- eoi_plot(bullet_explain_perms[13:15,], alpha = 0.9, weights = FALSE) +
+eoi1_kd <- plot_explain_scatter(bullet_explain_perms[13:15,], alpha = 0.9, weights = FALSE) +
   scale_color_gradient2(low = "grey50",
@@
 
-eoi2_kd <- eoi_plot(bullet_explain_perms[16:18,], alpha = 0.9, weights = FALSE) +
+eoi2_kd <- plot_explain_scatter(bullet_explain_perms[16:18,], alpha = 0.9, weights = FALSE) +
   scale_color_gradient2(low = "grey45",

### 2020-06-10 paper.Rnw
updates after updating limeaid (but something is not working with the explanation scatterplot)

@@
             by = c("implementation", "case")) %>%
-  bind_rows(bullet_explain_perms %>%
-              select(-perms_raw, -perms_numerified,
-                     -perms_pred_simple, -perms_pred_complex,
-                     -weights))
-
+  bind_rows(
+    bullet_explain_perms %>%
+      mutate(
+        implementation = fct_recode(
+          implementation,
+          "2" = "1",
+          "7" = "2",
+          "31" = "3",
+          "32" = "4"
+        )
+      ) %>%
+      select(
+        -perms_raw,
+        -perms_numerified,-perms_pred_simple,
+        -perms_pred_complex,-weights
+      )
+  )
 @
@@
 # Create a metric comparison plot
-plot_metrics(bullet_explain %>% mutate(label = as.factor(label)), add_lines = TRUE) +
+plot_metrics(bullet_explain %>% 
+               mutate(label = as.factor(label)), 
+             add_lines = TRUE) +
   theme_bw(base_family = "Times") +
@@
 The shape of the points represents the power used for the Gower distance calculation, and the color of the points represents the rank associated with that observation within a metric.
-The density simulation methods perform well for all metrics, but the bin based metrics often do not agree in terms of performance across metrics.
-\kgc{Something is wrong here.
-Right now, there are repetitions of some tuning parameter combinations.}}
+The density simulation methods perform well for all metrics, but the bin based metrics often do not agree in terms of performance across metrics.}
 \label{fig:bullet-assess-metric}
@@
 eoi1_3qb <- plot_explain_scatter(bullet_explain_perms[1:3,], alpha = 0.9, weights = FALSE) +
-  scale_color_gradient2(low = "grey50",
-                        high = "darkorange",
-                        midpoint = 0.5,
-                        limits = c(0, 1)) +
+  scale_color_manual(values = c("grey50", "darkorange")) +
   scale_fill_gradient2(low = "grey50",
@@
 eoi2_3qb <- plot_explain_scatter(bullet_explain_perms[4:6,], alpha = 0.9, weights = FALSE) +
-  scale_color_gradient2(low = "grey50",
-                        high = "darkorange",
-                        midpoint = 0.5,
-                        limits = c(0, 1)) +
+  scale_color_manual(values = c("grey50", "darkorange")) +
   scale_fill_gradient2(low = "grey50",
@@
 eoi1_3eb <- plot_explain_scatter(bullet_explain_perms[7:9,], alpha = 0.9, weights = FALSE) +
-  scale_color_gradient2(low = "grey50",
-                        high = "darkorange",
-                        midpoint = 0.5,
-                        limits = c(0, 1)) +
+  scale_color_manual(values = c("grey50", "darkorange")) +
   scale_fill_gradient2(low = "grey50",
@@
 eoi2_3eb <- plot_explain_scatter(bullet_explain_perms[10:12,], alpha = 0.9, weights = FALSE) +
-  scale_color_gradient2(low = "grey50",
-                        high = "darkorange",
-                        midpoint = 0.5,
-                        limits = c(0, 1)) +
+  scale_color_manual(values = c("grey50", "darkorange")) +
   scale_fill_gradient2(low = "grey50",
@@
 eoi1_kd <- plot_explain_scatter(bullet_explain_perms[13:15,], alpha = 0.9, weights = FALSE) +
-  scale_color_gradient2(low = "grey50",
-                        high = "darkorange",
-                        midpoint = 0.5,
-                        limits = c(0, 1)) +
+  scale_color_manual(values = c("grey50", "darkorange")) +
   scale_fill_gradient2(low = "grey50",
@@
 eoi2_kd <- plot_explain_scatter(bullet_explain_perms[16:18,], alpha = 0.9, weights = FALSE) +
-  scale_color_gradient2(low = "grey45",
-                        high = "darkorange",
-                        midpoint = 0.5,
-                        limits = c(0, 1)) +
+  scale_color_manual(values = c("grey50", "darkorange")) +
   scale_fill_gradient2(low = "grey45",

### 2020-06-10 paper.Rnw
updated paper after fixing limeaid issue with the point colors

@@
 
-exp_scatter <- ggplot() +
-  geom_point(data = sine_poi_perms,
-             mapping = aes(x = x1,
-                           y = x2,
-                           color = rfpred,
-                           size = weights),
-             alpha = 0.8,
-             shape = 20) +
-  scale_size(range = c(0.1, 3)) +
-  geom_rect(data = sine_poi_bounds %>% filter(feature == "x1"),
-            mapping = aes(xmin = lower,
-                          xmax = upper,
-                          ymin = -Inf,
-                          ymax = Inf),
-            alpha = 0.25,
-            fill = "grey90",
-            color = "firebrick") +
-  geom_rect(data = sine_poi_bounds %>%
-              filter(feature == "x2"),
-            mapping = aes(xmin = -Inf,
-                          xmax = Inf,
-                          ymin = lower,
-                          ymax = upper,
-                          color = coef),
-            alpha = 0.25,
-            fill = "grey90",
-            color = "steelblue") +
-  geom_point(data = sine_poi %>%
-               mutate(shape = "Prediction \nof Interest"),
-             mapping = aes(x = x1, y = x2, shape = shape, fill = rfprob_blue),
-             size = 7,
-             alpha = 0.8) +
-  scale_shape_manual(values = 23) +
-  scale_fill_gradient2(low = sinecolor_red,
-                        mid = '#f7f7f7',
-                        high = sinecolor_blue,
-                        midpoint = 0.5,
-                        limits = c(0, 1)) +
-  scale_color_gradient2(low = sinecolor_red,
-                        mid = '#f7f7f7',
-                        high = sinecolor_blue,
-                        midpoint = 0.5,
-                        limits = c(0, 1)) +
-  theme_bw(base_family = "Times", base_size = 10) +
+exp_scatter <- 
+  plot_explain_scatter(sine_poi_lime_default) +
+  facet_grid(switch = "both") +
   labs(x = TeX("x_1"),
@@
        color = "Random \nForest \nProbability \nfor 'blue'",
+       linetype = "",
        title = "Explanation Scatterplot") +
+  theme_bw(base_family = "Times", base_size = 10) +
   guides(shape = guide_legend(order = 1)) +
@@
 bullet_explain_perms <- bullet_explain_perms %>%
-  mutate(case = ifelse(case == bullet_poi_nonmatch,
+  mutate(case = ifelse(
+    case == bullet_poi_nonmatch,
     paste(case, "(non-match)"),
-                       paste(case, "(match)")))
-
-eoi1_3qb <- plot_explain_scatter(bullet_explain_perms[1:3,], alpha = 0.9, weights = FALSE) +
-  scale_color_manual(values = c("grey50", "darkorange")) +
-  scale_fill_gradient2(low = "grey50",
+    paste(case, "(match)")
+  ))
+
+eoi1_3qb <-
+  plot_explain_scatter(bullet_explain_perms[1:3, ], alpha = 0.9, weights = TRUE) +
+  scale_color_gradient2(
+    low = "grey50",
     high = "darkorange",
     midpoint = 0.5,
-                        limits = c(0, 1)) +
-  theme_bw(base_family = "Times", base_size = 8) +
-  theme(strip.placement = "outside",
-        strip.background = element_rect(color = "white",
-                                        fill = "white"))
-
-eoi2_3qb <- plot_explain_scatter(bullet_explain_perms[4:6,], alpha = 0.9, weights = FALSE) +
-  scale_color_manual(values = c("grey50", "darkorange")) +
-  scale_fill_gradient2(low = "grey50",
+    limits = c(0, 1)
+  ) +
+  scale_fill_gradient2(
+    low = "grey50",
     high = "darkorange",
     midpoint = 0.5,
-                        limits = c(0, 1)) +
+    limits = c(0, 1)
+  ) +
   theme_bw(base_family = "Times", base_size = 8) +
-  theme(strip.placement = "outside",
+  theme(
+    strip.placement = "outside",
     strip.background = element_rect(color = "white",
-                                        fill = "white"))
-
-eoi1_3eb <- plot_explain_scatter(bullet_explain_perms[7:9,], alpha = 0.9, weights = FALSE) +
-  scale_color_manual(values = c("grey50", "darkorange")) +
-  scale_fill_gradient2(low = "grey50",
+                                    fill = "white")
+  ) + 
+  guides(linetype = guide_legend(override.aes = list(color = c("darkorange"))))
+
+eoi2_3qb <-
+  plot_explain_scatter(bullet_explain_perms[4:6, ], alpha = 0.9, weights = TRUE) +
+  scale_color_gradient2(
+    low = "grey50",
     high = "darkorange",
     midpoint = 0.5,
-                        limits = c(0, 1)) +
-  theme_bw(base_family = "Times", base_size = 8) +
-  theme(strip.placement = "outside",
-        strip.background = element_rect(color = "white",
-                                        fill = "white"))
-
-eoi2_3eb <- plot_explain_scatter(bullet_explain_perms[10:12,], alpha = 0.9, weights = FALSE) +
-  scale_color_manual(values = c("grey50", "darkorange")) +
-  scale_fill_gradient2(low = "grey50",
+    limits = c(0, 1)
+  ) +
+  scale_fill_gradient2(
+    low = "grey50",
     high = "darkorange",
     midpoint = 0.5,
-                        limits = c(0, 1)) +
+    limits = c(0, 1)
+  ) +
   theme_bw(base_family = "Times", base_size = 8) +
-  theme(strip.placement = "outside",
+  theme(
+    strip.placement = "outside",
     strip.background = element_rect(color = "white",
-                                        fill = "white"))
-
-eoi1_kd <- plot_explain_scatter(bullet_explain_perms[13:15,], alpha = 0.9, weights = FALSE) +
-  scale_color_manual(values = c("grey50", "darkorange")) +
-  scale_fill_gradient2(low = "grey50",
+                                    fill = "white")
+  ) + 
+  guides(linetype = guide_legend(override.aes = list(color = c("grey50", "darkorange"))))
+
+eoi1_3eb <-
+  plot_explain_scatter(bullet_explain_perms[7:9, ], alpha = 0.9, weights = TRUE) +
+  scale_color_gradient2(
+    low = "grey50",
     high = "darkorange",
     midpoint = 0.5,
-                        limits = c(0, 1)) +
-  theme_bw(base_family = "Times", base_size = 8) +
-  theme(strip.placement = "outside",
-        strip.background = element_rect(color = "white",
-                                        fill = "white"))
-
-eoi2_kd <- plot_explain_scatter(bullet_explain_perms[16:18,], alpha = 0.9, weights = FALSE) +
-  scale_color_manual(values = c("grey50", "darkorange")) +
-  scale_fill_gradient2(low = "grey45",
+    limits = c(0, 1)
+  ) +
+  scale_fill_gradient2(
+    low = "grey50",
     high = "darkorange",
     midpoint = 0.5,
-                        limits = c(0, 1)) +
+    limits = c(0, 1)
+  ) +
   theme_bw(base_family = "Times", base_size = 8) +
-  theme(strip.placement = "outside",
+  theme(
+    strip.placement = "outside",
     strip.background = element_rect(color = "white",
-                                        fill = "white"))
+                                    fill = "white")
+  ) + 
+  guides(linetype = guide_legend(override.aes = list(color = c("grey50", "darkorange"))))
+
+eoi2_3eb <-
+  plot_explain_scatter(bullet_explain_perms[10:12, ], alpha = 0.9, weights = TRUE) +
+  scale_color_gradient2(
+    low = "grey50",
+    high = "darkorange",
+    midpoint = 0.5,
+    limits = c(0, 1)
+  ) +
+  scale_fill_gradient2(
+    low = "grey50",
+    high = "darkorange",
+    midpoint = 0.5,
+    limits = c(0, 1)
+  ) +
+  theme_bw(base_family = "Times", base_size = 8) +
+  theme(
+    strip.placement = "outside",
+    strip.background = element_rect(color = "white",
+                                    fill = "white")
+  ) + 
+  guides(linetype = guide_legend(override.aes = list(color = c("grey50", "darkorange"))))
+
+eoi1_kd <-
+  plot_explain_scatter(bullet_explain_perms[13:15, ], alpha = 0.9, weights = TRUE) +
+  scale_color_gradient2(
+    low = "grey50",
+    high = "darkorange",
+    midpoint = 0.5,
+    limits = c(0, 1)
+  ) +
+  scale_fill_gradient2(
+    low = "grey50",
+    high = "darkorange",
+    midpoint = 0.5,
+    limits = c(0, 1)
+  ) +
+  theme_bw(base_family = "Times", base_size = 8) +
+  theme(
+    strip.placement = "outside",
+    strip.background = element_rect(color = "white",
+                                    fill = "white")
+  )
+
+eoi2_kd <-
+  plot_explain_scatter(bullet_explain_perms[16:18, ], alpha = 0.9, weights = TRUE) +
+  scale_color_gradient2(
+    low = "grey50",
+    high = "darkorange",
+    midpoint = 0.5,
+    limits = c(0, 1)
+  ) +
+  scale_fill_gradient2(
+    low = "grey45",
+    high = "darkorange",
+    midpoint = 0.5,
+    limits = c(0, 1)
+  ) +
+  theme_bw(base_family = "Times", base_size = 8) +
+  theme(
+    strip.placement = "outside",
+    strip.background = element_rect(color = "white",
+                                    fill = "white")
+  )
 
@@
 \begin{figure*}[!thp]
-<<bullet-eois-nonmatch, out.width = '\\textwidth', fig.width = 12, fig.height = 6.25, message = FALSE>>=
+<<bullet-eois-nonmatch, out.width = '\\textwidth', fig.width = 15, fig.height = 7.8125, message = FALSE>>=
 # Join the plots
@@
 
-<<bullet-eois-match, out.width = '\\textwidth', fig.width = 12, fig.height = 6.25, message = FALSE>>=
+<<bullet-eois-match, out.width = '\\textwidth', fig.width = 15, fig.height = 7.8125, message = FALSE>>=
 # Join the plots

### 2020-07-15 paper.Rnw
added comment about where to add sentence about limeaid
start on limitations - overplotting

@@
 
-Throughout this paper, we make a distinction between interpretability and explanability of models.
+Throughout this paper, we distinguish between interpretability and explanability of models.
 We define {\it interpretability} as the ability to directly use model parameters to understand the relationships in the data captured by the model: e.g., a linear model coefficient associated with a predictor variable indicates the amount the response variable changes based on a change in the predictor variable.
@@
 Section \ref{discussion} concludes with a discussion on extension and limitations of the diagnostic plots and concerns about LIME in regards to the claims made by \citet{ribeiro:2016} brought about by the visualization examples in this paper that agree with \citet{alvarezmelis:2018}, \citet{laugel:2018}, and \citet{molnar:2019}.
+\kgc{Add sentence here about limeaid...}
 
@@
 \section{Discussion} \label{discussion}
+\hh{The discussion should not have subsection ... but we can keep them for now for structural purposes.}
 
@@
 Without an assessment of the explainer model, LIME is a black-box procedure of its own.
-We suggest the use of visual diagnostics to counteract the black-box nature of LIME and provide three diagnostic plots.
-Here we discuss the limitations and possible extensions of the diagnostic plots and concerns about LIME raise by applications of the diagnostics plots in this paper.
+\hh{XXX what is the implication?
+bring it to a punch: asking the user to trust into explainer  ...} We suggest the use of visual diagnostics to counteract the black-box nature of LIME and provide three diagnostic plots.
+%Here we discuss the limitations and possible extensions of the diagnostic plots and concerns about LIME raise by applications of the diagnostics plots in this paper.
 
@@
 
+The largest limitation to visualizations is the dimensionality of the data shown, both in the number of dimensions or features as well as the number of observations. 
+Fortunately, in the situation of LIME, both of these aspects are rather well controlled: 
+LIME relies heavily on simulations to generate data scenarios that are close to the data observed but exhibits variability.
+Effects from overplotting should be relatively mild, because output from simulations is shown, which is expected to be (relatively) continuous.
+In that respect, the diagnostics shown for the \data\ and  in the bullet example  are representative of what is expected.
+But in cases where overplotting does become problematic, the user could either simply reduce the size of the simulations or use some well-studied binning techniques in the visualizations, as discussed in \citet{Carr:1987hi} \hh{reference to Millions book}
+
+% talking points: 
 % We acknowledge that not all prediction problems will produce trends as easy to interpret as the visualizations we have shown in the section, but we still believe that visualizations of the procedure can provide insight into the quality of the LIME explanation.

### 2020-07-25 paper.Rnw
finished "cutting" of paper and wrote appendices (minus updated explanation scatterplot which is the next task)

--- 2020-06-10 paper.Rnw
@@
 
-sine_poi_exp <- sine_poi_lime_default %>% plot_features()
+sine_poi_exp <- sine_poi_lime_default %>% plot_features() + theme(text = element_text(family = "Times", size = 10))
 
@@
 \centering
-\includegraphics[width=2.25in]{./figure-static/bullets.png}
+\includegraphics[width=2in]{./figure-static/bullets.png}
 \caption{(Top left) Traditionally rifled gun barrel.
@@
            samesource = fct_recode(factor(samesource),
-                                  "Same Source = TRUE" = "TRUE",
-                                  "Same Source = FALSE" = "FALSE")) %>%
+                                  "Match" = "TRUE",
+                                  "Non-Match" = "FALSE")) %>%
     rename("CCF" = "ccf", "CMS" = "cms", "Matches" = "matches",
@@
 \caption{Parallel coordinate plots of the \citet{hare:2016} random forest predictions from the training (top facet) and testing (bottom facet) data.
-The observations are separated by same source (right column) and different source (left column) The y-axis shows the standardized feature values, and the x-axis shows the features used to fit the random forest (ordered by random forest impurity based feature importance).
-Each line corresponds to a comparison, and the line color represents the associated random forest probability.
+The observations are separated by known matching (right column) and non-matching (left column) signatures.
+The y-axis shows the standardized feature values, and the x-axis shows the features used to fit the random forest (ordered by random forest impurity based feature importance).
+Each line corresponds to an observation, and the line color represents the associated random forest probability.
 There are clear relationships between the feature values and the random forest probabilities.}
@@
 To get an overview of the LIME explanations from the 36 applications, we consider a feature heatmap (\autoref{fig:bullet-feature-heatmap}).
-The plot is faceted vertically by simulation method and the Gower power and horizontally by the order the feature was chosen and whether the observation is a known same source or different source comparison.
-\kgc{This is where I left off...} This plot highlights several key features of the LIME explanations from the bullet matching dataset.
-
-First of all, the density simulation methods produced the same explanations for almost all cases and LIME tuning parameters.
-As a result, the LIME explanations for the density methods are global and not local.
-Second, within a bin based simulation method, the features selected by LIME for an observation often vary based on the number of bins used but do not appear to vary based on the Gower power used.
-Especially with the equal bin explanations, there are vertical stripes that suggest a dependence of the LIME explanations on the number of bins used.
+In addition to facets for simulation method and order of feature selected by LIME, this plot includes a vertical facet for Gower power and a horizontal facet for whether the observation is a known match or non-match.
+This plot highlights several key features of the LIME explanations from the bullet matching dataset.
+
+First, the density simulation methods produce the same explanations for almost all cases and LIME tuning parameters suggesting the LIME explanations are global and not local.
+Second, within a bin based simulation method, the features selected by LIME for an observation often vary by the number of bins but do not appear to vary by the Gower power.
+With the equal bins, there are vertical stripes that suggest a dependence of the LIME explanations on the number of bins.
 The vertical stripes are not as apparent with the quantile bins.
-Lastly, there are clear differences between the LIME explanations for the cases that are matches and those that are not matches which are produced by the bin based simulation methods.
-This provides evidence that suggests that the features which the random forests uses to classify a match are different from the features used by the random forest to classify a non-match.
-The most important insight \autoref{fig:bullet-feature-heatmap} highlights is the dependence of the explanations on the LIME tuning parameter for many of the observations in the test data.
+Lastly, there are clear differences between the LIME explanations produced by the bin based simulation methods for the matches and non-matches.
+This suggests that the features the random forest uses to classify a match or non-match are different.
 
 \begin{figure*}[!thp]
-<<bullet-feature-heatmap, out.width = '\\textwidth', fig.width = 18, fig.height = 10.5>>=
-
+<<bullet-feature-heatmap, out.width = '\\textwidth', fig.width = 18, fig.height = 12>>=
 # Create a feature heatmap
-plot_feature_heatmap(bullet_explain %>%
-                  mutate(label = as.factor(label)),
-                facet_var = na.omit(bullet_test$samesource),
-                order_method = "PCA") +
+plot_feature_heatmap(
+  bullet_explain %>%
+    mutate(
+      label = as.factor(label),
+      feature = fct_recode(
+        feature,
+        "Rough Correlation" = "rough_cor",
+        "Consecutively Matching Striae" = "cms",
+        "Distance" = "D",
+        "Matches" = "matches",
+        "Mismatches" = "mismatches",
+        "Non-Consecutively Matching Striae" = "non_cms",
+        "Cross Correlation Function" = "ccf",
+        "Sum of Peaks" = "sum_peaks",
+        "Distance Standard Deviation" = "sd_D"
+      )
+    ),
+  facet_var = bullet_test %>%
+    mutate(samesource = fct_recode(
+      factor(samesource),
+      "Match" = "TRUE",
+      "Non-Match" = "FALSE"
+    )) %>%
+    pull(samesource) %>%
+    na.omit(),
+  order_method = "PCA"
+) +
   scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) +
-  scale_color_gretchenalbrecht(palette = "last_rays", discrete = TRUE, reverse = TRUE) +
+  scale_color_gretchenalbrecht(palette = "last_rays",
+                               discrete = TRUE,
+                               reverse = TRUE) +
   theme_bw(base_family = "Times", base_size = 16) +
-  theme(axis.text.y = element_blank(),
+  theme(
+    axis.text.y = element_blank(),
     axis.ticks.y = element_blank(),
@@
     legend.position = "bottom",
-        axis.text.x = element_text(angle = 45, hjust = 1)) +
-  guides(fill = guide_legend(nrow = 1)) + 
+    axis.text.x = element_text(angle = 45, hjust = 1)
+  ) +
+  guides(fill = guide_legend(nrow = 3)) +
   labs(y = "Case", color = "Complex Model Feature", fill = "Complex Model Feature")
@@
 \caption{Feature heatmap of the 36 LIME applications to the bullet comparison data test set.
-In addition to faceting the results by simulation method and order a feature was selected by LIME as done in \autoref{fig:sine-feature-heatmap}, this plot has been faceted by the Gower power and whether the the observation is from a match (TRUE) or non-match (FALSE).
-This plot shows several key insights about the LIME explanations.
-First, the features selected by LIME for the density simulation methods are mostly the same for all tuning parameters and all cases.
-Second, the features selected by LIME for the bin based methods are affected by the number of bins but not the Gower power.
-Third, the explanations produced by LIME using bin based methods result in different important features for the matches and non-matches.}
+In addition to faceting the results by simulation method and LIME feature selection order, facets for the Gower power and whether the observation is a match or non-match are included.
+The vertical stripes of features selected indicate a dependence between the LIME explanations and tuning parameters.}
 \label{fig:bullet-feature-heatmap}
@@
 @
-\caption{Plot of LIME assessment metrics for the 36 different applications of LIME applied to the bullet comparison data test set.
-The shape of the points represents the power used for the Gower distance calculation, and the color of the points represents the rank associated with that observation within a metric.
-The density simulation methods perform well for all metrics, but the bin based metrics often do not agree in terms of performance across metrics.}
+\caption{Plot of LIME assessment metrics for the applications of LIME on the bullet comparison data test set.
+The density simulation methods perform well for all metrics.
+The bin based metrics often do not agree in terms of performance across metrics.}
 \label{fig:bullet-assess-metric}
@@
 
-To try to identify the set of LIME tuning parameters with the most trustworthy set of explanations, we created an assessment metric plot shown in \autoref{fig:bullet-assess-metric}.
-The three metrics of average fidelity, average $R^2$, and MSEE were computed for each of the simulation methods and Gower power used to implement LIME.
-The plot is faceted by the simulation method, and the shape of a point represents the Gower power.
-The color of a point represents the rank within a metric.
-That is, the darker a point, the better performance of that method based on the metric.
-
-The density simulation methods performed well across all tuning parameters.
+To try to identify a set of LIME tuning parameters with the most trustworthy set of explanations, an assessment metric plot is considered (\autoref{fig:bullet-assess-metric}).
+All density simulation methods performed well based on the three metrics.
 This is an interesting result, since \autoref{fig:bullet-feature-heatmap} shows that the density methods results in global explanations.
@@
 As a result, with the bin based methods, it is difficult to know which method to recommend.
-When considering the metrics across the Gower power used, the applications using a power of 0.5 perform best or as well as the other powers in across all simulation methods.
-This suggests that the power that leads to a more global explanation is preferred by LIME in this example.
-
-Unfortunately, \autoref{fig:bullet-feature-heatmap} leaves us without a clear indication of which set of explanations to use to explain the random forest.
-Perhaps we can say that the kernel density method, 3 equal bins, and 3 quantile bins are some of the best performing methods.
-To better understand the explanations provided by these three methods, we take a closer look at explanations from these methods for two observations of interest where one is a known non-match (case \Sexpr{bullet_poi_nonmatch}) and the other is a known match (case \Sexpr{bullet_poi_match}).
-
-Figures \ref{fig:bullet-eois-nonmatch} and \ref{fig:bullet-eois-match} contain plots that provide this closer look for the known non-match and match, respectively.
-The top row of plots in each figure are the explanation plots from \emph{lime}.
-The bottom row of plots show scatterplots of the features selected by LIME colored by the random forest model prediction.
-The location of the prediction of interest is indicated on the scatterplots by a diamond, and black solid lines are included on the plots representing the bin divisions for applications using bins.
-The bottom row plots are created using \emph{limeaid}.
-The plots within a column are associated with one of the three simulation methods (kernel density, 3 equal bins, or 3 quantile bins).
-
-The scatterplots provide a visualization that helps to explain the LIME explanation.
-For example, consider the explanation for case \Sexpr{bullet_poi_nonmatch} when 3 quantile bins were used.
-The explanation plot from \emph{lime} shows that case \Sexpr{bullet_poi_nonmatch} having an observed CCF value greater than 0.320 supports a random forest prediction in favor of a match.
-The scatter plots show that many of the simulated values with CCF greater then 0.320 have random forest predictions greater than 0.5.
-Additionally, the LIME explanation indicates that a value of matches less than or equal to 1.66 contradicts a prediction in favor of a match.
-The scatter plots shows that almost all simulated values with a value of matches less than or equal to 1.66 have random forest predictions close to 0.
-Similar statements can be made about the 3 equal bin explanation for this case and the bin based methods for the known match observation explanations.
-
-While the scatterplots provide visual explanations for the LIME explanations, some of them indicate that LIME falls short of a good explanation of the random forest predictions.
-Again, consider the explanation for case 325 when 3 quantile bins were used.
-From looking at the scatter plot of CCF versus matches, a better explanation for the random forest prediction would be to say that because the prediction of interest has a value of CCF less than 0.8 (approximately) and a value of matches less than 7 (approximately), the random forest is providing a prediction that supports a non-match.
-The relationship between ccf and rough correlation does not provide much evidence to support the random forest prediction one way or the other due to the mixture of random forest predictions ranging from 0 to 1 in most regressions, but there is a pentagon shaped region at the bottom of the scatter plot of matches versus rough correlation that the prediction of interest falls in that supports the random forest prediction of a non-match.
+The applications using a power of 0.5 perform the best or as well as the other powers across all simulation methods suggesting that the power that leads to a more global explanation is preferred by LIME.
+
+Perhaps we can say that the kernel density method, 3 equal bins, or 3 quantile bins are some of the better performing methods, but unfortunately, \autoref{fig:bullet-assess-metric} leaves us without a clear indication of which set of explanations to use to explain the random forest.
+To better understand the explanations provided by these three methods, we take a closer look at explanations from these methods for two observations of interest, which will be referred to as case M (a known match) and case NM (a known non-match).
+
+Figure \ref{fig:bullet-eois} include the explanation plots (from \emph{lime}) and explanation scatterplots for cases M and NM.
+Plots for 3 equal bins and 3 quantile bins are included.
+The scatterplots provide several insights into the LIME explanations.
+Here we focus on the explanation for case NM with 3 quantile bins, but similar statements can be made about the other plots.
+
+The explanation plot from \emph{lime} for case NM with 3 quantile bins shows that an observed CCF value greater than 0.320 supports a random forest prediction in favor of a match, and the scatter plots show that many of the simulated values with CCF greater then 0.320 have random forest predictions greater than 0.5.
+Additionally, the LIME explanation indicates that a value of matches less than or equal to 1.66 contradicts a prediction in favor of a match, and the scatter plots show that almost all simulated values with a value of matches less than or equal to 1.66 have random forest predictions close to 0.
+While the LIME explanation makes sense based on the observations made from the explanation scatter plot, the plot also indicates that LIME falls short of providing a good explanation of the random forest prediction for case NM.
+Based on the scatter plot of CCF versus matches, a better explanation would be that because case NM has a value of CCF less than 0.8 and a value of matches less than 7, the random forest provides a prediction supporting a non-match.
+The relationship between CCF and rough correlation does not provide much evidence to support the random forest prediction one way or the other, but there is a pentagon shaped region at the bottom of the scatter plot of matches versus rough correlation with mostly predictions close to 0 that case NM falls and supports the random forest prediction of a non-match.
 
@@
   ) +
-  theme_bw(base_family = "Times", base_size = 8) +
+  theme_bw(base_family = "Times", base_size = 10) +
   theme(
@@
 
-eoi1_kd <-
-  plot_explain_scatter(bullet_explain_perms[13:15, ], alpha = 0.9, weights = TRUE) +
-  scale_color_gradient2(
-    low = "grey50",
-    high = "darkorange",
-    midpoint = 0.5,
-    limits = c(0, 1)
-  ) +
-  scale_fill_gradient2(
-    low = "grey50",
-    high = "darkorange",
-    midpoint = 0.5,
-    limits = c(0, 1)
-  ) +
-  theme_bw(base_family = "Times", base_size = 8) +
-  theme(
-    strip.placement = "outside",
-    strip.background = element_rect(color = "white",
-                                    fill = "white")
+# eoi1_kd <-
+#   plot_explain_scatter(bullet_explain_perms[13:15, ], alpha = 0.9, weights = TRUE) +
+#   scale_color_gradient2(
+#     low = "grey50",
+#     high = "darkorange",
+#     midpoint = 0.5,
+#     limits = c(0, 1)
+#   ) +
+#   scale_fill_gradient2(
+#     low = "grey50",
+#     high = "darkorange",
+#     midpoint = 0.5,
+#     limits = c(0, 1)
+#   ) +
+#   theme_bw(base_family = "Times", base_size = 8) +
+#   theme(
+#     strip.placement = "outside",
+#     strip.background = element_rect(color = "white",
+#                                     fill = "white")
+#   )
+# 
+# eoi2_kd <-
+#   plot_explain_scatter(bullet_explain_perms[16:18, ], alpha = 0.9, weights = TRUE) +
+#   scale_color_gradient2(
+#     low = "grey50",
+#     high = "darkorange",
+#     midpoint = 0.5,
+#     limits = c(0, 1)
+#   ) +
+#   scale_fill_gradient2(
+#     low = "grey45",
+#     high = "darkorange",
+#     midpoint = 0.5,
+#     limits = c(0, 1)
+#   ) +
+#   theme_bw(base_family = "Times", base_size = 8) +
+#   theme(
+#     strip.placement = "outside",
+#     strip.background = element_rect(color = "white",
+#                                     fill = "white")
+#   )
+
+pf1_3qb <- plot_features(bullet_explain_perms[1:3,]) +
+  scale_fill_manual(values = c("darkorange", "grey50")) +
+  theme(text = element_text(family = "Times", size = 10))
+pf2_3qb <- plot_features(bullet_explain_perms[4:6,]) +
+  scale_fill_manual(values = c("darkorange", "grey50")) + 
+  theme(text = element_text(family = "Times", size = 10))
+pf1_3eb <- plot_features(bullet_explain_perms[7:9,]) +
+  scale_fill_manual(values = c("darkorange", "grey50")) +
+  theme(text = element_text(family = "Times", size = 10))
+pf2_3eb <- plot_features(bullet_explain_perms[10:12,]) +
+  scale_fill_manual(values = c("darkorange", "grey50")) +
+  theme(text = element_text(family = "Times", size = 10))
+# pf1_kd <- plot_features(bullet_explain_perms[13:15,]) +
+#   scale_fill_manual(values = c("darkorange", "grey50"))
+# pf2_kd <- plot_features(bullet_explain_perms[16:18,]) +
+#   scale_fill_manual(values = c("darkorange", "grey50"))
+@
+
+\begin{figure*}[!thp]
+<<bullet-eois-nonmatch, out.width = '\\textwidth', fig.width = 12, fig.height = 17, fig.align = "center", out.width="90%", message = FALSE>>=
+# Join the plots
+plot_grid(
+  pf2_3qb,
+  pf2_3eb,
+  eoi2_3qb,
+  eoi2_3eb,
+  pf1_3qb,
+  pf1_3eb,
+  eoi1_3qb,
+  eoi1_3eb,
+  nrow = 4,
+  rel_heights = c(0.2, 0.3, 0.2, 0.3)
 )
-
-eoi2_kd <-
-  plot_explain_scatter(bullet_explain_perms[16:18, ], alpha = 0.9, weights = TRUE) +
-  scale_color_gradient2(
-    low = "grey50",
-    high = "darkorange",
-    midpoint = 0.5,
-    limits = c(0, 1)
-  ) +
-  scale_fill_gradient2(
-    low = "grey45",
-    high = "darkorange",
-    midpoint = 0.5,
-    limits = c(0, 1)
-  ) +
-  theme_bw(base_family = "Times", base_size = 8) +
-  theme(
-    strip.placement = "outside",
-    strip.background = element_rect(color = "white",
-                                    fill = "white")
-  )
-
-pf1_3qb <- plot_features(bullet_explain_perms[1:3,]) +
-  scale_fill_manual(values = c("darkorange", "grey50"))
-pf2_3qb <- plot_features(bullet_explain_perms[4:6,]) +
-  scale_fill_manual(values = c("darkorange", "grey50"))
-pf1_3eb <- plot_features(bullet_explain_perms[7:9,]) +
-  scale_fill_manual(values = c("darkorange", "grey50"))
-pf2_3eb <- plot_features(bullet_explain_perms[10:12,]) +
-  scale_fill_manual(values = c("darkorange", "grey50"))
-pf1_kd <- plot_features(bullet_explain_perms[13:15,]) +
-  scale_fill_manual(values = c("darkorange", "grey50"))
-pf2_kd <- plot_features(bullet_explain_perms[16:18,]) +
-  scale_fill_manual(values = c("darkorange", "grey50"))
-@
-
-\begin{figure*}[!thp]
-<<bullet-eois-nonmatch, out.width = '\\textwidth', fig.width = 15, fig.height = 7.8125, message = FALSE>>=
-# Join the plots
-plot_grid(pf2_3qb, pf2_3eb, pf2_kd,
-          eoi2_3qb, eoi2_3eb, eoi2_kd,
-          nrow = 2,
-          rel_heights = c(0.45, 0.55))
-@
-\caption{Plots of LIME explanations for one case in the test data that is a known non-match.
-Each column contains plots associated with a different application (3 quantile bins, 3 equal bins, or kernel density).
-The top row of plots are the explanation plots from \emph{lime}.
-The bottom row shows scatter plots of the simulated data associated with the prediction of interest.
-The features plotted are those chosen by LIME in the explanations, and the points are colored by the the random forest predictions.
-Lines showing the divisions created in the feature space by the bin based LIME methods are included as solid black lines.
-The scatter plots can be used to better understand the LIME explanation and assess if it is a good explanation.}
-\label{fig:bullet-eois-nonmatch}
-
-\vspace*{\floatsep}
-
-<<bullet-eois-match, out.width = '\\textwidth', fig.width = 15, fig.height = 7.8125, message = FALSE>>=
-# Join the plots
-plot_grid(pf1_3qb, pf1_3eb, pf1_kd,
-          eoi1_3qb, eoi1_3eb, eoi1_kd,
-          nrow = 2,
-          rel_heights = c(0.45, 0.55))
-@
-\caption{Plots with the same structure as \ref{fig:bullet-eois-match} but for an observation from the test data that is a known match.}
-\label{fig:bullet-eois-match}
+@
+\caption{Plots of LIME explanations and explanation scatterplots for one case M and NM in the bullet test data.
+The first column contains plots associated with 3 quantile bins and the second with 3 equally spaced bins.
+The plots provide insights into the LIME explanations and allow for the assessment of the explanation quality.}
+\label{fig:bullet-eois}
 \end{figure*}
 
-The scatter plots of the kernel density applications for both the match and non-match case show that almost all of the simulated values have random forest predictions less than 0.5, which provide evidence in favor of a non-match.
-It appears that simulation method is not providing enough values to cover the feature space that hit regions where the random forest provides predictions above 0.5.
-The training data has a much smaller amount of matches (\Sexpr{sum(bullet_train$samesource)}) than non-matches (\Sexpr{sum(bullet_train$samesource == FALSE)}), and this simulation method is clearly affected by this imbalance in the two classification categories.
-Furthermore, this may be the cause of the minimal amount of variability in the LIME explanations across all of the cases in the test data.
-
-Without applying multiple applications LIME to the bullet test data or viewing diagnostic plots of the LIME explanations, it may be very possible to formulate reasons why the LIME explanations make sense.
-However, the sequence of plots in this section (Figures \ref{fig:bullet-feature-heatmap}, \ref{fig:bullet-lime-expls}, \ref{fig:bullet-assess-metric}, \ref{fig:bullet-eois-match}, and \ref{fig:bullet-eois-nonmatch}) suggest that we should be cautious to trust any of these LIME explanations.
-While some of them provide an explanation that may be reasonable, there could be better explanations (as seen in the 3 quantile bin case of \autoref{fig:bullet-eois-match}), and some of them provide explanations that make no sense (as seen in \autoref{fig:bullet-lime-expls}).
+Without applying LIME with multiple tuning parameters to the bullet test data or viewing diagnostic plots of the LIME explanations, it may be very possible to formulate reasons why the LIME explanations make sense.
+However, the sequence of plots in this section (Figures \ref{fig:bullet-feature-heatmap}, \ref{fig:bullet-assess-metric}, and \ref{fig:bullet-eois}) suggest that we should be cautious to trust any of these LIME explanations.
 It appears that either LIME needs to be further tuned to provide trustworthy and good explanations, or a different approach may provide better insight.
-As glimpsed with the scatter plots in Figures \ref{fig:bullet-eois-match} and \ref{fig:bullet-eois-nonmatch}, the more traditional approach to explanation random forest predictions by plotting the random forest predictions over the feature space (partial dependence plots), could provide better insight into the complex model with no need to assess the explanation method if the sampling method is well chosen.
 
@@
 
+%\hh{The discussion should not have subsection ... but we can keep them for now for structural purposes.} \kg{Okay. I took them out.}
+
 This paper highlights that while an explainer model is meant to provide clarity, it actually adds another layer of complexity to predictive models by requiring yet another model that needs to be assessed.
-Without an assessment of the explainer model, LIME is a black-box procedure of its own.
+Without an assessment of the explainer model, LIME is a black-box procedure of its own requiring blind trust in the explainer model.
+%\hh{XXX what is the implication?
+bring it to a punch: asking the user to trust into explainer...}
 We suggest the use of visual diagnostics to counteract the black-box nature of LIME and provide three diagnostic plots.
-Here we discuss the limitations and possible extensions of the diagnostic plots and concerns about LIME raise by applications of the diagnostics plots in this paper.
-
-\subsection{Diagnostic Plot Limitations and Possible Extensions} \label{limit-exten}
-
-% We acknowledge that not all prediction problems will produce trends as easy to interpret as the visualizations we have shown in the section, but we still believe that visualizations of the procedure can provide insight into the quality of the LIME explanation.
-We hope these figures will provide a starting point (if not an ending point) for the assessment of a single LIME explanation.
-Perhaps the inability to interpret a plot is itself telling, or the act of creating extensions of these visualizations to work with a different scenarios will lead to an understanding of the trustworthiness of the explanation.
-
-%\hh{In terms of limitations of the visualizations: first two features span the x and y axis, additional features can be used for faceting.
-four features is completely feasible, beyond that the visualization might not work as well.
-The number of bins should be in the single digits.
-A large number of small multiples \citep{Becker:1996gy} needs a strong signal in the data to be effective - otherwise the visualization might be affected by change blindness \citep{simonsChangeBlindness1997, review19}.
-}
-
-%The \data \ provide a \kge{neat} \kge{very clean} example of how to use the proposed visualizations to assess a single LIME explanation \kge{with two features.
-Once the number of features is greater than 3, adjustments will need to be made to the plots.
-In this case, multiple plots will be required to visualize the majority of the steps in the LIME procedure.
-Reasonable extensions would be scatterplot matrices or the use of faceting.
-\hh{XXX this is too vague: when do you use scatterplot matrices, what is the advantage of faceting.
-Make your solutions more concrete by discussing them as well as their limitations.
-}
-
-%\hh{Both large number of observations and large number of features make visual assessments harder:} \kgc{I've decided to not discuss a large amount of data, because that really isn't a problem due to the size of the simulated dataset being chosen by the user, and there is not a need to go above 5000.
-Whereas, it is reasonable to expect that a user may select more than two features.} \hh{That the size of the data is chosen by the user is actually a good point to make.
-}
-
-%\hh{the number of features can also be controlled by the user - lime is interested in a small number of features, as earlier mentioned, using faceting or scatterplot matrices we are able to deal with high single digits, low double digits of features.
-The limiting factors are screen space and cognitive load.
-}
-
-%In situations with large amounts of data, it may become difficult to see the trends if the training or testing data due to over plotting.
-However, consider that the number of observations in the simulated data is chosen by the user, which allows the user to select a number that is large enough to get a visual of the full range of the observed data without running into issues of over plotting.
-
-%Another possibly problematic situation is when it is of interest to include more than two features in the LIME explanation.
-In this situation, multiple plots will be required to visualize the LIME procedure, and if the number of features is really large, the number of plots may become too large to interpret well.
-However, if too many \hh{XXX what is too many?
-make this less abstract and give concrete suggestions on how to go beyond two dimensions.} features are chosen to be included in the LIME explanation, the explanation may no longer interpretable.
-It seems reasonable that the number of features to focus on in an explanation should be low enough that scatter plot matrices of the \sout{our} \hh{XXX not 'our' - that creates boundaries.
-you want the readers to use these plots as well.} diagnostic plots could be created.} \kgc{I decided I also didn't want to get into the discuss of "too many" features here.}}
-
-% Add a discussion on using our visualizations in situations without tabular data or a dichotomous response variable.
-
-\subsection{Concerns about LIME} \label{concerns}
 
@@
 While the visualizations accomplish these tasks, they also expose examples of the failings of LIME.
-To address the discovered failings of LIME, we will reconsider each of the claims about the performance of LIME made by \citep{ribeiro:2016} (interpretability, faithfulness, linearity, and localness) in light of the insights gained from the diagnostic visualizations.
+To address the discovered failings of LIME, we will reconsider each of the claims about the performance of LIME made by \citet{ribeiro:2016} in light of the insights gained from the diagnostic visualizations.
 
@@
 
-Even though an explanation will be interpretable as long as the complexity of the explainer model is appropriately chosen, the presentation of a LIME explanation in the key visual used by \citep{ribeiro:2016} (shown in \autoref{fig:sine-plot-poi}) could lead to an over simplified interpretation of the explainer model.
-Without a solid understanding of the details behind the fitting of the explainer model, the deeper meaning of the bars in the figure is lost.
-
-It is customary to interpret this plot by stating that the direction of the bar supports or contradicts the classification in a certain category, and the length of the bar signifies the importance of the involvement of a feature in the prediction.
-While these interpretations are correct, the lengths of the bars represent the coefficients of the ridge regression model used as the explainer model, which contain more meaning than just the direction of support and importance of a feature.
-The bars indicate how much the average complex model prediction estimated by the linear explainer model changes based on a change in the feature.
-Furthermore, this interpretation changes depending on whether a bin based or density simulation method was used (i.e the change in the average complex model prediction between an observation in the same bin as the case of interest and an observation not in the same bin versus the change in the mean complex model prediction for a change in the feature by one standardized unit).
-
-Thus, even though an explainer model may be interpretable, the explanation it produces may be under-interpreted or misinterpreted without an understanding of the process that produced the explanation.
-Supplementing \citep{ribeiro:2016}'s compact visualization of the explanation with visualizations of the explanation that depict the simulated data and the explainer model (such as Figures \ref{fig:sine-plot-step3ab} and \ref{fig:bullet-eois-match}) promotes a full interpretation of the explanation.
-This is done by providing reminders of the meaning of the lengths of the bars in addition to a visual connection between complex model predictions and the estimated coefficients of the explainer model.
+Even though an explanation will be interpretable as long as the complexity of the explainer model is appropriately chosen, a lack of understanding of the process used to create the explanation could lead to an incorrect interpretation of the explanation.
+For example, the visualization of a LIME explanation available from the \emph{lime} R package \citep{pedersen:2020} (shown in Figures \ref{fig:sine-exp-scatter} and \ref{fig:bullet-eois}) is a major simplification of the explainer model, which could lead to under-interpreted or misinterpreted LIME explanation.
+Supplementing \citet{pedersen:2020}'s compact visualization of the explanation with an explanation scatterplot that shows a more detailed visualization of the explainer model (such as Figures \ref{fig:sine-exp-scatter} and \ref{fig:bullet-eois}) promotes a full interpretation of the explanation.
 
 Even with an explainer model that is interpreted correctly, the interpretation is worthless if the explainer model is not \textbf{faithful} to the complex model.
-This claim can be easily assessed using the diagnostic plots suggested in this paper.
+This claim can be assessed using the diagnostic plots suggested in this paper.
 Many of the visualizations in this paper highlight problems with the faithfulness of the explainer models.
-
-The visualizations that incorporate the bins along with the complex model predictions (Figures \ref{fig:fig:sine-plot-step1ab}, \ref{ fig:sine-plot-step1c}, \ref{fig:sine-plot-step3ab}, \ref{fig:sine-plot-compare-bins}, \ref{fig:bullet-eois-match}, and \ref{fig:bullet-eois-nonmatch}) highlight issues that accompany the choice to use bin based simulation methods.
-These visualizations allow for a comparison of the size of the bins to the complex model's decision boundaries.
-All of the examples in this paper show cases where the bins do not accurately capture the classification boundaries near the predictions of interest of the random forest models by oversimplifying the model.
+The explanation scatterplots allow for a comparison of the explainer model to the complex model.
+The examples in this paper show cases where the explainer model bins do not accurately capture the classification boundaries near the predictions of interest of the random forest models by oversimplifying the model (Figures \ref{fig:sine-exp-scatter} and \ref{fig:bullet-eois}).
 Using less bins would clearly not help improve the faithfulness of the explainer model in these examples, and while an increase in bins would lead to a finer resolution of the random forest classification boundaries, interpretability of the explainer model would quickly be lost.
-The bins used by LIME are not flexible enough to capture the different sized division boundaries of the random forests shown in this paper.
 Perhaps this could be improved by allowing the bin creation to account for the relationships between the features and response variable or a different number of bins for each feature.
 
-The figures referenced in the previous paragraph from the \data \ example are all based on the application of LIME using a set of tuning parameters.
-From the use of the feature heatmap, we found that different sets of tuning parameters can produce different explanations.
-It makes sense that one set of tuning parameters could lead to a more faithful explainer model than another.
-As a result, we proposed a visual comparison of two faithfulness metrics (MSEE and average fidelity).
+In addition to assessing faithfulness by visually comparing the complex and explainer model, we propose a visual comparison of two faithfulness metrics (MSEE and average fidelity).
 The examples of faithfulness metric comparisons in this paper (Figures \ref{fig:sine-assess-metric} and \ref{fig:bullet-assess-metric}) both produced confusing results.
-In both examples, the density based simulation methods resulted in the best or close to the best performance even though the feature heatmaps (Figures \ref{fig:sine-feature-heatmap} and \ref{fig:bullet-feature-heatmap}) showed that the density simulation methods produced global explanations with no variation in features selected by LIME.
+The density based simulation methods resulted in the best or close to the best performance even though the feature heatmaps (Figures \ref{fig:sine-feat-heat} and \ref{fig:bullet-feature-heatmap}) showed that the density simulation methods produced global explanations with no variation in features selected by LIME.
 For the bin based simulation methods, the two metrics often did not agree or contradicted one another, which makes it difficult to decide on a recommendation of a set of tuning parameters that produces the explanations with the most faithful explainer model.
@@
 Most of the average $R^2$ values in the examples from this paper are below 0.5 suggesting a poor linear fit of the explainer models.
-The poor linear fit of the explainer model was also seen with the residual plot (\autoref{fig:sine-plot-step2cd}).
-
-The final claim, \textbf{localness}, is also addressed by the feature heatmap and metric comparison plot.
+The poor linear fit of the explainer model was also seen with the residual plot (\autoref{fig:sine-plot-resids}).
+
+The final claim, \textbf{localness}, is addressed by the feature heatmap and metric comparison plot.
 As stated, the feature heatmap revealed that the density simulation methods in the examples of this paper resulted in global explanations where the same features were repeatedly chosen across all (or almost all) observations in the set of explanations.
-This finding agrees with that of \citep{laugel:2019} who also found LIME produced global explanations with the normal approximation simulation method.
+This finding agrees with that of \citep{laugel:2018} who found LIME produced global explanations with the normal approximation simulation method.
 For the bin based simulation methods in the bullet data example, the feature heatmap showed that the features chosen for the explanations varied between the two classification categories (match versus non-match).
@@
 
+The largest limitation to the diagnostic visualizations is the dimensionality of the data shown, both in the number of dimensions or features as well as the number of observations.
+Fortunately, in the situation of LIME, both of these aspects are rather well controlled: LIME relies heavily on simulations to generate data scenarios that are close to the data observed but exhibits variability.
+Effects from overplotting should be relatively mild, because output from simulations is shown, which is expected to be (relatively) continuous \kgc{What do you mean by continuous here?}.
+In that respect, the diagnostics shown for the \data\ and in the bullet example are representative of what is expected.
+But in cases where overplotting does become problematic, the user could either simply reduce the size of the simulations or use some well-studied binning techniques in the visualizations, as discussed in \citet{carr:1987} \hh{reference to Millions book}
+
 While it would be ideal if LIME could be used as a method to provide easily understandable explanations for black-box models as \citep{ribeiro:2016} claim, that dream is not yet a reality.
 The examples using diagnostic plots to assess LIME in this paper show frequent issues with LIME.
-The practice of assessing the performance of methods has once again shown its importance.
-We hope that our plots provide motivation to assess LIME explanations, to not blindly use the default settings (even if it is not clear which tuning parameters to use), and perhaps to encourage work on improving LIME, so that it can be a lime and not a lemon.
+We hope that our plots provide motivation to assess LIME explanations, to not blindly use the default settings (even if it is not clear which tuning parameters to use), and to encourage work on improving LIME, so that it can be a lime and not a lemon.
 
@@
 \section{LIME Tuning Parameter Options} \label{lime-details}
+
+The following tuning parameters for the LIME algorithm are available in the \emph{lime} R package.
+
+\begin{itemize}
+
+\item Data simulation methods:
+
+\begin{itemize}
+\item Equally spaced bins: observations are uniformly sampled from equally spaced bins (number of bins may be specified)
+\item Quantile bins: observations are uniformly sampled from quantile bins (number of bins may be specified)
+\item Normal density approximation: observations are sampled from a normal distribution with mean and standard deviation computed from the corresponding feature
+\item Kernel density approximation: observations are sampled from an kernel density approximation of the corresponding feature
+\end{itemize}
+
+\item Number of observations to simulate
+
+\item Distance metric for determining proximity to the prediction of interest: Gower distance (where the power may be specified) or exponential kernel (where the kernel width may be specified)
+
+\item Number of features to return in an explanation
+
+\item Feature selection method for determining the features to return in an explanation: forward selection applied to a ridge regression, heighest weights in ridge regression, LASSO, classification/regression tree splits
+
+\end{itemize}
 
@@
 
-Figure ... provides example explanation scatterplots for each feature in the default LIME explanation for the \data individual prediction of interest indicated in Figure \ref{fig:sine-plot-data}.
-
+Figure ...
+provides example explanation scatterplots for each feature in the default LIME explanation for the \data \ prediction of interest indicated in Figure \ref{fig:sine-plot-data}.
 \kgc{Need to updated limeaid to create this plot and then add figure here.}
@@
 
-\kgc{Placing the notation definitions here for now - need to make adjustments as necessary:} \kge{We first introduce notation for the scenario of tabular data with a binary response variable and continuous features.
-Let $\textbf{X}$ be an $n$ by $p$ data matrix with $p$ features and $n$ observations, and let $x_i\in\textbf{X}$ be a real-valued vector such that $x_i\in\mathbb{R}^p$ for $i=1,2,...,n$.
-Furthermore, let $y$ be a response variable of length $n$ with elements $y_i\in\{0, 1\}$ for $i=1,2,...,n$.
-Suppose that $f$ is a classification model where $f:\mathbb{R}^p\rightarrow[0,1]$ that is applied to $\textbf{X}$ and $y$.
-Let the vector of predictions made by $f$ applied to $\textbf{X}$ be denoted as $\hat{y}$.
-Note that $\hat{y}_i=f(x_i)\in\hat{y}$ for $i=1,..,n$.
-For both bin based methods, the interpretability transformation converts the generated observations to indicator variables, where a 1 indicates that the feature value for an observation is in the same bin as the feature value for the case of interest.
-That is
-  $$z'_{i,j}=T\left(x'_{i,j}\right) = I\left[x'_{i,j} \mbox{ and } x^*_{i,j}\in b_{j,k} \right]$$
-for $i=1,..,m$ and $j=1,..,p$ where $b_{j,k}$ is bin $k$ for feature $j$.
-Let observation $z'_i$ have weight $\omega_{x^*}(\textbf{x}'_i) = Gower(x^*, x'_i)^c$, where $Gower$ represents the computation of the Gower similarity and $c$ is some constant.
-This denotes a proximity measure between $x^*$ and $x'_i$ for each $i\in 1,...,m$.
-If the exponential kernel is used, the weights are computed after the interpretability transformation such that $z'_i$ has weight $\omega_{z^*}(\textbf{z}'_i)$.}
-
-\citet{ribeiro:2016} present \hh{the following metric as a measure of fidelity:}
-$$\mathcal{L}(f, g, \omega_{x^*}) = \sum_{i=1}^{m}\omega_{x^*}(x_i)\left(f(x_i)-g\left(z_i'\right)\right)^2,$$
-\hh{where  ... }
-
-This metric is computed as $$\mathcal{L}(f, g, \omega_{x^*}) = \sum_{i=1}^{m}\omega_{x^*}(x_i)\left(f(x_i)-g\left(z_i'\right)\right)^2.$$ Smaller values of $\mathcal{L}$ indicate a better local approximation of the explainer model to the complex model.
-
-That is, let $$MSEE=\frac{1}{n}\sum_{i=1}^n\left(f\left(x^*\right)-g\left(z^*\right)\right)^2.$$ Again, smaller values of MSEE would suggest a better approximation of the explainer model.
+Suppose $f$ is a complex model, and let $\textbf{X}$ be a matrix of observed data with $K$ features and $E$ observations where $x_e$ is an observed feature vector for observation $e$.
+Let $f(x_e)$ be the complex model prediction for observation $e$.
+It is of interest to explain the predictions made by $f$ applied to $X$ using LIME.
+
+For $x_e$ and set of tuning parameters $t$, let $\textbf{X}_{e,t}'$ be the LIME simulated dataset with $K$ features and $S$ observations such that $x'_{e,t,s}$ is the feature vector for simulated data observation $s$.
+Let $\textbf{Z}'_{e,t}$ be the matrix of interpretability transformed simulated data with $K$ features and $S$ observations such that $z'_{e,t,s}$ is the interpretability transformed feature vector for observation/explanation $e$, tuning parameter $t$, and simulated data observation $s$.
+Note that $z_{e,t}$ will represent the interpretability transformed version of $x_e$.
+
+Next, let $\omega_t$ represent a proximity distance metric.
+Then $\omega_t\left(x_e, x'_{e,t,s}\right)$ is the weight assigned to $x'_{e,t,s}$, which is the proximity between $x_e$ and $x'_{e,t,s}$.
+Allow $g_{e,t}$ to be the explainer model for an explanation $e$ and tuning parameter $t$.
+Thus, $g_{e,t}\left(z'_{e,s,t}\right)$ is the explainer model prediction for the interpretability transformed simulated data observation $s$.
+
+For a set of $E$ explanations and a set of tuning parameters $t$, we define the assessment metrics as follows:\\
+\\
+\emph{Average $R^2$} is denoted as $R^2_{\mbox{ave}}$ and computed as
+
+  $$R^2_{\mbox{ave}} = \frac{1}{E}\sum_{e=1}^E R_{e,t}^2$$
+
+where $R_{e,t}^2$ is the $R^2$ value for $g_{e,t}$.\\
+\\
+\emph{Average fidelity} is denoted by $\mathcal{L}_{\mbox{ave}}$ and computed as
+
+\begin{eqnarray*} \mathcal{L}_{\mbox{ave}} & = & \frac{1}{E}\sum_{e=1}^E\mathcal{L}(f, \ g_{e,t}, \ \pi_{t}) \\ & = & \frac{1}{E}\sum_{e=1}^E\sum_{s=1}^{S}\omega_{t}\left(x_e, x'_{e,t,s}\right)\left(f\left(x'_{e,t,s}\right)-g_{e,t}\left(z_{e,t,s}'\right)\right)^2.
+\end{eqnarray*}\\
+\\
+\emph{Mean squared explanation error} is denoted by MSEE and computed as
+
+$$MSEE=\frac{1}{E}\sum_{e=1}^E\left(f\left(x_e\right)-g_{e,t}\left(z_{e,t}\right)\right)^2.$$
 
@@
 We introduce, we suggest, etc.}
-% \item \hh{Try to give each of the diagnostics a name.}
 % \item \kgc{check that I am always using present tense}

### 2020-07-26 paper.Rnw
updated based on limeaid updates

@@
   mutate(case = c("Prediction of Interest", "Prediction of Interest"))
-
 @
@@
 
-Figure ...
-provides example explanation scatterplots for each feature in the default LIME explanation for the \data \ prediction of interest indicated in Figure \ref{fig:sine-plot-data}.
-\kgc{Need to updated limeaid to create this plot and then add figure here.}
+Figure \ref{fig:sine-expl-scat-density} provides example explanation scatterplots for each feature in the default LIME explanation obtained using the kernel density simulation method for the \data \ prediction of interest.
+
+\begin{figure*}[!thp]
+<<sine-expl-scat-density, out.width = '\\textwidth', fig.width = 12, fig.height = 4.5, fig.align = "center">>=
+plot_explain_scatter(
+  sine_lime_explain$explain %>%
+    filter(sim_method == "kernel_density", case == sine_poi %>% pull(case)),
+  alpha = 0.75, title.opt = FALSE
+) + 
+  theme_bw(base_family = "Times") +
+  theme(strip.background = element_rect(fill = "white", color = "white"),
+        strip.placement = "outside")
+@
+\caption{Explanation scatterplots for the \data \ prediction of interest with the kernel density simulation method.}
+\label{fig:sine-expl-scat-density}
+\end{figure*}
 
@@
 \begin{figure}[!thp]
-<<sine-plot-resids, out.width = '0.5\\textwidth', fig.width = 4, fig.height = 3.25, warning = FALSE>>=
+<<sine-plot-resids, out.width = '0.5\\textwidth', fig.width = 5, fig.height = 4, warning = FALSE>>=
 

### 2020-07-26 paper.Rnw
updated explanation scatterplot
more updates after limeaid updates to the explanation scatterplot

@@
 
-\subsection{LIME Assessment Visualizations}
+\subsection{LIME Assessment Visualizations} \label{bullet-assess-ex}
 
@@
 Plots for 3 equal bins and 3 quantile bins are included.
+Plots for the kernel density simulation method are included in Figure \ref{fig:bullet-expl-scat-density}.
 The scatterplots provide several insights into the LIME explanations.
@@
 \begin{figure*}[!thp]
-<<bullet-eois-nonmatch, out.width = '\\textwidth', fig.width = 12, fig.height = 17, fig.align = "center", out.width="90%", message = FALSE>>=
+<<bullet-eois, out.width = '\\textwidth', fig.width = 12, fig.height = 17, fig.align = "center", out.width="90%", message = FALSE>>=
 # Join the plots
@@
 
-\item Feature selection method for determining the features to return in an explanation: forward selection applied to a ridge regression, heighest weights in ridge regression, LASSO, classification/regression tree splits
+\item Feature selection method for determining the features to return in an explanation: forward selection applied to a ridge regression, highest weights in ridge regression, LASSO, classification/regression tree splits
 
@@
 \label{fig:sine-expl-scat-density}
+\end{figure*}
+
+Figure \ref{fig:bullet-expl-scat-density} includes explanation scatterplots for the explanations generated using kernel density simulation for the bullet example cases M and NM discussed in Section \ref{bullet-assess-ex}.
+
+\begin{figure*}[!thp]
+<<bullet-expl-scat-density, out.width = '\\textwidth', fig.width = 12, fig.height = 9, fig.align = "center">>=
+bullet_es_NM <-
+  plot_explain_scatter(
+  bullet_explain_perms[13:15, ] %>% mutate(case = "M"),
+  alpha = 0.75, title.opt = TRUE
+) +
+  theme_bw(base_family = "Times") +
+  theme(strip.background = element_rect(fill = "white", color = "white"),
+        strip.placement = "outside")
+
+bullet_es_M <-
+  plot_explain_scatter(
+  bullet_explain_perms[16:18, ] %>% mutate(case = "NM"),
+  alpha = 0.75, title.opt = TRUE
+) +
+  theme_bw(base_family = "Times") +
+  theme(strip.background = element_rect(fill = "white", color = "white"),
+        strip.placement = "outside")
+
+plot_grid(bullet_es_NM, bullet_es_M, nrow = 2)
+@
+\caption{Explanation scatterplots for LIME explanations using kernel density simulation for the cases M and NM of the bullet comparison.}
+\label{fig:bullet-expl-scat-density}
 \end{figure*}

### 2020-08-19 paper.Rnw
proof read section 1

@@
 \corres{*Corresponding author. \email{kgoode@iastate.edu}}
-\presentaddress{This is sample for present address text this is sample for present address text}
 
@@
 \abstract[Summary]{The importance of providing explanations for predictions made by black-box models has led to the development of model explainer methods such as LIME (local interpretable model-agnostic explanations) \citep{ribeiro:2016}.
-LIME uses a surrogate model to explain the relationship between predictor variables from a black-box model and the black-box model predictions in a local region around a prediction of interest.
+LIME uses a surrogate model to explain the relationship between predictor variables and predictions from a black-box model in a local region around a prediction of interest.
 However, the quality of the resulting explanations relies on how well the explainer model captures the black-box model in a specified local region.
@@
 We apply the visual diagnostics to a forensics bullet matching dataset to show examples where LIME explanations depend on the tuning parameters and the explainer model oversimplifies the black-box model.
-Our examples raise concerns about claims made about LIME \citep{ribeiro:2016} that are similar to other criticism found in the literature (\citet{alvarezmelis:2018}, \citet{laugel:2018}, and \citet{molnar:2019}).}
+Our examples raise concerns about claims made about LIME \citep{ribeiro:2016} that are similar to other criticisms in the literature (\citet{alvarezmelis:2018}, \citet{laugel:2018}, and \citet{molnar:2019}).}
 \keywords{LIME, black-box models, interpretability, diagnostics}
@@
 These models have proven to perform well in a wide range of prediction problems, but the accuracy of many machine learning models comes at the cost of interpretability due to their algorithmic complexity (hence the phrase "black-box models").
-Model interpretability allows for the assessment and understanding of how the model produces predictions.
-The lack of the ability to assess and understand a model makes it difficult to trust the model, especially in areas areas with high stakes decisions such as health care and forensics science.
-The increased use of machine learning models in applications and the introduction of the General Data Protection Regulation (GDPR) in 2018 \citep{goodman:2016} has resulted in a dramatic increase in research in an area known as explainable machine learning, which focuses on developing ways to explain output from machine learning algorithms.
+Model interpretability allows for the understanding and assessment of how a model produces predictions.
+The lack of the ability to understand and assess a model makes it difficult to trust the model, especially in areas with high stakes decisions such as health care and forensics science.
+The increased use of machine learning models in applications and the introduction of the General Data Protection Regulation (GDPR) in 2018 \citep{goodman:2016} has resulted in a dramatic increase in explainable machine learning research, which focuses on developing ways to explain output from machine learning algorithms.
 
@@
 We define {\it interpretability} as the ability to directly use model parameters to understand the relationships in the data captured by the model: e.g., a linear model coefficient associated with a predictor variable indicates the amount the response variable changes based on a change in the predictor variable.
-In contrast, {\it explanability} is defined as the ability to use the model in an indirect manner to understand the relationships in the data captured by the model: e.g., partial dependence plots depict the marginal relationship between model predictions and predictor variables \citep{friedman:2001}.
+In contrast, define {\it explanability} as the ability to use the model in an indirect manner to understand the relationships in the data captured by the model: e.g., partial dependence plots depict the marginal relationship between model predictions and predictor variables \citep{friedman:2001}.
 
@@
 In this paper, we focus on the model-agnostic method of LIME \citep{ribeiro:2016}.
+
+\subsection{Conceptual Description of LIME}
+
+LIME (local interpretable model-agnostic explanations) is a method that uses a surrogate model to relate predictor variables to black-box model predictions (i.e.
+a model explainer) \citep{ribeiro:2016}.
+We distinguish between the terms of model explainer and explainer model: by \emph{model explainer} we denote the method for explaining a complex model using a surrogate model, while the \emph{explainer model}, or simply the \emph{explainer}, is the surrogate model.
+
+While some model explainers focus on understanding a model at the global level, LIME claims to provide explanations for individual predictions (local).
+Additionally, LIME is designed to work with any model (model-agnostic) and to produce easily understandable results (explanations) \citep{ribeiro:2016}.
+Conceptually, LIME fits a simple (interpretable) model, the explainer model,  meant to capture the behavior of the (complex) black-box model in a local region around a prediction of interest.
+The  simple model then provides interpretable estimates for variables that most influenced the prediction made by the complex model.
 
@@
 \caption{A conceptual depiction of a faithful LIME explainer model in the immediate neighborhood of a prediction of interest.
-The predictions from a hypothetical black-box model are plotted against the standardized values of the two predictor variables used to fit the hypothetical model.
+The predictions from a hypothetical black-box model are plotted against the standardized values of the two hypothetical predictor variables.
 The diamond shaped points represent the location of a prediction of interest.
-The size and opacity of the circular points indicate the weight assigned based on the distance to the point of interest computed using the inverse of the Gower distance metric raised to the power of \Sexpr{good_gower_power}.
-The black lines are a weighted ridge regression model used as an explainer model that reasonably captures the relationship between the black-box predictions and the features in a local region around the point of interest.
-That is, it is faithful to the complex model and produces a reasonable explanation that Feature 1 plays a more important role in the prediction of interest than Feature 2 since the magnitude of the slope associated with Feature 1 is larger.}
+The size and opacity of the circular points indicate the weight assigned based on the distance to the prediction of interest computed using the inverse of the Gower distance metric raised to the power of \Sexpr{good_gower_power}.
+The black lines are a weighted ridge regression model used as an explainer model that reasonably captures the relationship between the black-box predictions and the features in a local region around the prediction of interest.
+That is, the explainer is faithful to the complex model and produces a reasonable explanation that Feature 1 plays a more important role in the prediction of interest than Feature 2 since the magnitude of the slope associated with Feature 1 is larger.}
 \label{fig:concept-plot-good}
@@
 \caption{A conceptual depiction of an unfaithful local explainer model in the immediate neighborhood of a prediction of interest.
-A ridge regression model is fit to the same black-box model predictions and predictor variables as in \autoref{fig:concept-plot-good}, but the weights are computed using a Gower exponent of 1.
+A ridge regression model is fit to the same hypothetical black-box model predictions and predictor variables as in \autoref{fig:concept-plot-good}, but the weights are computed using a Gower exponent of 1.
 The explainer model is unfaithful to the complex model in the immediate neighborhood of the prediction of interest.}
@@
 
-\subsection{Conceptual Description of LIME}
-
-LIME (local interpretable model-agnostic explanations) is a method that uses a surrogate model to relate predictor variables to black-box model predictions (i.e.
-a model explainer) \citep{ribeiro:2016}.
-We distinguish between the terms of model explainer and explainer model: by \emph{model explainer} we denote the method for explaining a complex model using a surrogate model, while the \emph{explainer model}, or simply the \emph{explainer}, is the surrogate model.
-
-While some model explainers are focused on understanding a model at the global level, LIME claims to provide explanations for individual predictions (local).
-Additionally, LIME is designed to work with any model (model-agnostic) and to produce easily understandable results (explanations) \citep{ribeiro:2016}.
-Conceptually, LIME fits a simple (interpretable) model, the explainer model,  meant to capture the behavior of the (complex) black-box model in a local region around a prediction of interest.
-The  simple model then provides interpretable estimates for variables that most influenced the prediction made by the complex model.
-
 \autoref{fig:concept-plot-good} provides a visualization of this conceptual understanding of LIME.
@@
 The diamond shaped points represent a prediction of interest.
-A Gower distance metric \citep{gower:1971} is used to define locality: the size of the points represent the inverse of the Gower distance as a reflection of the proximity to the prediction of interest.
-Here, an exponent of \Sexpr{good_gower_power} is used to emphasize interest in a very local region around the point of interest.
+A Gower distance metric \citep{gower:1971} is used to define locality such that the size of the points represent the inverse of the Gower distance raised to some value and indicate the proximity to the prediction of interest.
+Here, an exponent of \Sexpr{good_gower_power} is used to emphasize a very local region around the prediction of interest.
 A ridge regression model weighted by the proximity values is used as the explainer model with the black-box predictions as the response variable and standardized versions of Features 1 and 2 as predictor variables.
@@
 The plot on the left of \autoref{fig:concept-plot-good} shows the relationship between the black-box predictions and Feature 1.
-Here, the explainer model is plotted with Feature 2 fixed at the observed value of Feature 2 for the prediction of interest.
+Here, the explainer model is plotted with Feature 2 fixed at the observed value of the prediction of interest.
 The explainer model captures the relationship in the immediate neighborhood around the prediction of interest  with a slope of \Sexpr{coefs_data %>% filter(case == "good", feature == "Feature 1") %>% pull(slope) %>% round(3)}.
-The plot on the right shows that there is no global or local relationship between the black-box predictions and Feature 2.
-Here, the explainer model is plotted with Feature 1 set to be the observed value of Feature 1 for the prediction of interest, and it has an appropriately small slope of \Sexpr{coefs_data %>% filter(case == "good", feature == "Feature 2") %>% pull(slope) %>% round(3)}.
-The magnitude of the slope associated with Feature 1 is larger than the slope of Feature 2, which suggests that Feature 1 plays a more important role in the prediction made by the black-box model for the point of interest.
+The plot on the right shows no global or local relationship between the black-box predictions and Feature 2.
+Here, the explainer model is plotted with Feature 1 set as the observed value of the prediction of interest, and it has an appropriately small slope of \Sexpr{coefs_data %>% filter(case == "good", feature == "Feature 2") %>% pull(slope) %>% round(3)}.
+The magnitude of the slope associated with Feature 1 is larger than the slope of Feature 2, which suggests that Feature 1 plays a more important role in the prediction made by the black-box model for the prediction of interest.
 This explanation agrees with a visual assessment of the relationships between the predictions and predictor variables.
@@
 The concept of LIME is relatively simple: use an interpretable model to approximate a complex model in a local region.
-However, a practical implementation of LIME is not straightforward, and there is research is being done to improve the procedure \citep{laugel:2018}.
-The current implementations of LIME\footnote{https://github.com/marcotcr/lime} \citep{pedersen:2020} offer various tuning parameters the user specifies when applying LIME (see Section \ref{background}) that affect the explainer model and ultimately, the explanation.
+However, a practical implementation of LIME is not straightforward, and research is being done to improve the procedure \citep{laugel:2018}.
+The current implementations of LIME\footnote{https://github.com/marcotcr/lime} \citep{pedersen:2020} offer various tuning parameters (see Section \ref{background}) that affect the explainer model and ultimately, the explanation.
 Since the explainer model is an approximation of the complex model and not a direct interpretation, the explanations produced by an explainer model are subject to the quality of the approximation.
@@
 
-We consider an example where the choice of exponent used to specify the weights is crucial to the quality of the explanation.
-The plots in Figure \ref{fig:concept-plot-bad} show the same data as \autoref{fig:concept-plot-good}, but the Gower distance metric exponent was decreased to \Sexpr{bad_gower_power} (the default exponent in the \emph{lime} R package).
+We consider an example where the choice of exponent for the weights is crucial to the quality of the explanation.
+The plots in Figure \ref{fig:concept-plot-bad} show the same data as \autoref{fig:concept-plot-good}, but the Gower distance metric exponent is decreased to \Sexpr{bad_gower_power} (the default exponent in the \emph{lime} R package).
 This causes the observations that are further away from the prediction of interest to be given larger weights than before.
@@
 \citet{alvarezmelis:2018} raise a concern pertaining to the robustness of explanations from LIME and other model explainers: they find that even small changes in predictor variables can lead to very different LIME explanations.
-Additionally, \citet{ribeiro:2016} acknowledge that if a linear models is used as the explainer, LIME relies on a linear approximation of the explainer model to the complex model and state ``if the underlying model is highly non-linear even in the locality of the prediction, there may not be a faithful explanation".
-
-As a result of the various ways LIME explanations can fail, it is important to assess LIME explanations.
+Additionally, \citet{ribeiro:2016} acknowledge that if a linear model is used as the explainer, LIME relies on a linear approximation of the explainer model to the complex model and state ``if the underlying model is highly non-linear even in the locality of the prediction, there may not be a faithful explanation".
+
+As a result of the various ways LIME can fail, it is important to assess LIME explanations.
 We suggest the use of visual diagnostics for assessment.
 In this paper, we lay out the set of claims about LIME made by \citet{ribeiro:2016} and propose three visualizations for the assessment of these claims: (1) \emph{explanation scatterplot}, (2) \emph{feature heatmap}, (3) \emph{assessment metric plot}.
-While LIME has been implemented for image, tabular, and text data, we will only focus on tabular data.
-For additional simplicity, we will only discuss classification prediction models with a dichotomous response variable and continuous predictor variables.
+While LIME is implemented for image, tabular, and text data, we only focus on tabular data.
+For additional simplicity, we only discuss classification prediction models with a dichotomous response variable and continuous predictor variables.
 However, the proposed diagnostics may be extended to a wider range of situations.
@@
 Then in Section \ref{application}, we demonstrate the use of the diagnostics to assess LIME explanations for a random forest model fit to a forensics bullet matching dataset.
-Section \ref{discussion} concludes with a discussion on extension and limitations of the diagnostic plots and concerns about LIME in regards to the claims made by \citet{ribeiro:2016} brought about by the visualization examples in this paper that agree with \citet{alvarezmelis:2018}, \citet{laugel:2018}, and \citet{molnar:2019}.
-\kgc{Add sentence here about limeaid...}
+Section \ref{discussion} concludes with a discussion on extensions and limitations of the diagnostic plots and concerns about LIME in regards to the claims made by \citet{ribeiro:2016} brought about by the visualization examples in this paper that agree with \citet{alvarezmelis:2018}, \citet{laugel:2018}, and \citet{molnar:2019}.
+The diagnostic plots included in this paper are created using the R package \emph{limeaid} \citep{goode:2020}.
+\kgc{(Would you like me to add you as an author on the limeaid package?)}
 
@@
 Explanations produced by LIME are likely to be affected by the choice of tuning parameters.
-An example of this was shown by Figures \ref{fig:concept-plot-good} and \ref{fig:concept-plot-bad} where the method used to weight the observations influenced the explanation.
+An example of this is shown by Figures \ref{fig:concept-plot-good} and \ref{fig:concept-plot-bad} where the method used to weight the observations influenced the explanation.
 As of the time of writing this manuscript, we have encountered no recommendations for how to determine which method to use besides for the default settings in \emph{lime} \kgc{(confirm this)}.
@@
 Two hypothetical examples of feature heatmaps are included in \autoref{fig:concept-feat-heat}.
-The plots were created with the assumption that LIME was applied to select the top feature out of $p=8$ features for $n=10$ cases with $t=5$ sets of tuning parameters.
+The plots were created with the assumption that LIME is applied to select the top feature out of $p=8$ features for $n=10$ cases with $t=5$ sets of tuning parameters.
 Situation 1 shows an example where the features selected are consistent across tuning parameters within a case but vary across cases within a tuning parameter.
@@
 
-Since firearm identification is commonly used as evidence for convictions in court cases, it is important to be able to understand and assess a model used to quantify the probability that a bullet was fired from a gun.
+Since firearm identification is commonly used as evidence for convictions in court cases, it is important to be able to understand and assess a model used to quantify the probability that a bullet is fired from a gun.
 LIME explanations would provide a local explanation for an individual prediction, but just as it is important to assess the model for this high-stakes application, it is also important to assess the LIME explanations.
@@
 Thus, a total of $12\times 3=36$ different applications of LIME were performed.
-We specify that each LIME explanation return 3 features and feature selection was performed using the highest weights method (default option).
+We specify that each LIME explanation return 3 features and feature selection is performed using the highest weights method (default option).
 
@@
 Most of the average $R^2$ values in the examples from this paper are below 0.5 suggesting a poor linear fit of the explainer models.
-The poor linear fit of the explainer model was also seen with the residual plot (\autoref{fig:sine-plot-resids}).
+The poor linear fit of the explainer model is also seen with the residual plot (\autoref{fig:sine-plot-resids}).
 
@@
 Again, this is a suggestion of global explanations.
-Furthermore, while the metric comparison plot in the bullet example did not provide agreement between metrics on a best bin based method, all metrics agree that a Gower power of 0.5 for computing the model weights associated with distance of a simulated data point from the prediction of interest was best.
+Furthermore, while the metric comparison plot in the bullet example did not provide agreement between metrics on a best bin based method, all metrics agree that a Gower power of 0.5 for computing the model weights associated with distance of a simulated data point from the prediction of interest is best.
 This suggests that a less local explanation provided a better explanation of the performance of the random forest.

### 2020-08-21 paper.Rnw
small series of edits

@@
 \citep{fisher:2018} and \citep{strumbelj:2014}).
-In this paper, we focus on the model-agnostic method of LIME \citep{ribeiro:2016}.
-
-\subsection{Conceptual Description of LIME}
+In this paper, we focus on \hh{one specific} model-agnostic method: LIME \citet{ribeiro:2016} \hh{introduced by Ribeiro, Singh, and Guestrin in 2016}.
+
+%\subsection{Conceptual Description of LIME}
 
@@
 A Gower distance metric \citep{gower:1971} is used to define locality such that the size of the points represent the inverse of the Gower distance raised to some value and indicate the proximity to the prediction of interest.
-Here, an exponent of \Sexpr{good_gower_power} is used to emphasize a very local region around the prediction of interest.
-A ridge regression model weighted by the proximity values is used as the explainer model with the black-box predictions as the response variable and standardized versions of Features 1 and 2 as predictor variables.
-Standardized features allow direct comparisons of the model coefficients.
-The explainer model is depicted by the black lines in the figure.
+\hh{In the example of \autoref{fig:concept-plot-good}} an exponent of \Sexpr{good_gower_power} is used to emphasize a very local region around the prediction of interest.
+A ridge regression model weighted by the proximity values is used as the explainer model with the black-box predictions as the response variable and standardized versions of \hh{two features in the data} % features Features 1 and~2
+as predictor variables. Standardized features allow direct comparisons of the model coefficients. The explainer model is depicted by the black lines in the figure.
 
@@
 
-\subsection{Motivation for Diagnosing LIME}
+%\subsection{Motivation for Diagnosing LIME}
 
@@
 
-\subsection{Structure of Paper}
+%\subsection{Structure of Paper}
 
@@
 The diagnostic plots included in this paper are created using the R package \emph{limeaid} \citep{goode:2020}.
-\kgc{(Would you like me to add you as an author on the limeaid package?)}
+%\kgc{(Would you like me to add you as an author on the limeaid package?)}\hh{I appreciated your offer, but limeaid is your package - I haven't written a single line :)}
 
@@
 LIME was introduced in 2016 by \citet{ribeiro:2016}.
-The original authors provide an implementation of LIME in a Python package\footnote{https://github.com/marcotcr/lime}.
-An adaption of the Python package in R is by Thomas Lin-Pedersen \citep{pedersen:2020}.
-In this paper, any details provided about the implementation of LIME are based on the R package.
-
-As described by \citet{laugel:2018}, the general form of the LIME algorithm can be divided into three steps:
+The  authors provide an implementation of LIME in a Python package\footnote{https://github.com/marcotcr/lime}.
+An adaption of the Python package in R has been implemented and made available by Thomas Lin-Pedersen \citep{pedersen:2020}.
+The discussion of parameter choices and implementation details of LIME in this paper are based on the R package.
+
+The general form of the LIME algorithm can be divided into three steps (see also \citep{laugel:2018}):
 
@@
 
-During the application of LIME, the user must select various tuning parameter options: the number of features to return in the explanation, the simulation method, the feature selection method, and how the weights are computed.
-An overview of the options available for the tuning parameters is included in Appendix \ref{lime-details}.
+During the application of LIME, the user is asked to select various tuning parameter options: the number of features to return in the explanation, the simulation method, the feature selection method, and how the weights are computed.
+An overview of the options available for the tuning parameters is included in Appendix~\ref{lime-details}.
 
@@
 Note that due to the creation of $y$ in this manner, $y$ is dependent on $x_1$ and $x_2$ and independent of $x_3$.
+\hh{From the plots in \autoref{sine-plot-data} we see that the global relationship between response $y$ and features $x_1$ and $x_2$ is linear: the probability for label blue increases with the difference between features $x_2$ and $x_1$.
+Locally, the relationship between $y$ and features $x_2$ and $x_1$ varies a lot more around the line of identity.
+Here, the relationship  is determined by the sine waves.
+However, the sine is a good-natured function that can be approximated well linearly.
+}
 
@@
 
-We perform six applications of LIME with different tuning parameters to the random forest predictions from all observations in the sine data test set.
-To do this, we use the R package \emph{limeaid} \footnote{Available on GitHub at https://github.com/goodekat/limeaid} (\Sexpr{packageVersion("limeaid")}), which applies a forked version\footnote{https://github.com/goodekat/lime} of the development version of the R package \emph{lime} (\Sexpr{packageVersion("lime")}) \citep{pedersen:2020}.
-The forked version allows us to export internal values from \emph{lime}.
-The tuning parameters are as follows.
-For each application, we specify that LIME returns the top two features in the explanation, because we expect $x_1$ and $x_2$ to be the important features.
-Note that the complexity of an explanation goes hand in hand with the number of features selected to be included in the explanation.
-Setting the number of features to a small number will make the explanation simpler but not necessarily more correct.
-A quantile bin based simulation method is used for five of the LIME applications with the number of bins varying from 2 to 6 by application.
-We use 6 bins as the maximum, since the larger the number of bins, the more complex the explanation becomes.
-The sixth application of LIME uses a kernel density simulation method.
-The default methods for feature selection (forward selection) and the computation of the weights (Gower distance raised to an exponent of 1) are used for all applications.
-
-\subsection{Explanation Scatterplots} \label{exp-scatter}
+\hh{All runs of LIME in this paper are executed in}
+a forked version\footnote{https://github.com/goodekat/lime} of the development version of the R package \emph{lime} (\Sexpr{packageVersion("lime")}) \citep{pedersen:2020}. 
+The forked version \hh{is functionally indistinguishable from Pedersen's implementation but it} allows us to export internal values \hh{relevant for an assessment of the explainer}. 
+The R package \emph{limeaid} \footnote{Available on GitHub at https://github.com/goodekat/limeaid} (\Sexpr{packageVersion("limeaid")}) implements diagnostic plots based on the output of the altered version of `lime`.
 
@@
 The points represent the simulated data colored by the random forest probabilities and sized by the assigned LIME weights.
-The prediction of interest is shown as the diamond shaped point.
+\hh{XXX could you make the complex prediction **much** lighter for this example?
+The diamond and the lines are hard to see, but should be the focus.} The prediction of interest is shown as the diamond shaped point.
 The explainer model indicator variables associated with $x_1$ and $x_2$ (quantile bins containing the prediction of interest) are depicted by the solid lines.
@@
 
-The \emph{explanation scatterplot} is a visual diagnostic for assessing the LIME claims of locality and fidelity for an individual explanation by juxtaposing the complex and explainer models in one plot.
-The format of an explanation scatterplot depends on the LIME simulation method.
-We introduce the explanation scatterplot here under the \emph{lime} R package default method in which the data are simulated uniformly from four quantile bins.
-In this scenario, LIME converts continuous predictor variables to indicator variables identifying whether the variable value falls in the same quantile bin as the prediction of interest or not.
-The indicator variables are used as the explainer model features.
-The explanation scatterplot achieves a juxtaposition of the complex and explainer models by plotting the LIME simulated data for two features in an explanation colored by the complex predictions overlaid by lines representing boundaries of the indicator variables used to fit the explainer model.
-The size of the points represents the weight assigned by LIME, and the color of the lines denote whether LIME indicates that a feature supports or contradicts a class prediction.
-Appendix \ref{exp-scatter_plus} addresses the explanation scatterplot formats in other LIME simulation scenarios.
-
-To demonstrate an explanation scatterplot, we focus on the misclassified point indicated in Figure \ref{fig:sine-plot-data} by the diamond as the prediction of interest.
-First, consider the left plot in Figure \ref{fig:sine-exp-scatter}, which shows the \emph{lime} R package visualization of the explanation for the prediction of interest.
+A quantile bin based simulation method is used for five of the LIME applications with the number of bins varying from 2 to 6 by application.
+We use 6 bins as the maximum, \hh{because the complexity of the explanations increases with  the number of bins.} The sixth application of LIME uses a kernel density simulation method.
+The default methods for feature selection (forward selection) and the computation of the weights (Gower distance raised to an exponent of 1) are used for all applications.
+
+\subsection{A LIME explanation}
+\hh{XXX I've just pulled the description of the left hand side of figure 4 out of the next section.}
+To demonstrate a LIME explanation, we focus on the misclassified point indicated in Figure \ref{fig:sine-plot-data} by the diamond as the prediction of interest.
+The left plot in Figure \ref{fig:sine-exp-scatter} shows a visualization of the explanation for the prediction of interest as suggested by Ribeiro et al and implemented in the \emph{lime} R package.
 The figure shows that the random forest returned a probability of \Sexpr{round(sine_poi_lime_default$label_prob[1], 2)} that the observation of interest belongs to category blue {(denoted as the ``label" in the figure).The lengths of the bars represent the explainer model coefficients associated with the indicator variables chosen by LIME as important.
@@
 In this case, it is \Sexpr{round(sine_poi_lime_default$model_r2[1], 2)} suggesting that the explainer model is not a good linear fit.
-However, it is commonly accepted that $R^2$ has limitations for accessing the quality of fit of a model \citep{sapra:2014}, and it should not be the only metric used for assessment of a model.
+However, it is commonly accepted that $R^2$ has limitations for assessing the quality of fit of a model \citep{sapra:2014}, and it should not be used as the only metric in a model assessment.
 
@@
 A random forest classification of blue is supported by the prediction of interest having a value of $x_2$ that is greater than \Sexpr{str_split(sine_poi_lime_default$feature_desc[[1]], pattern = " ")[[1]][1]}, but the prediction of interest having a value of $x_1$ that is greater than \Sexpr{str_split(sine_poi_lime_default$feature_desc[[2]], pattern = " ")[[1]][1]} and less than or equal to \Sexpr{str_split(sine_poi_lime_default$feature_desc[[2]], pattern = " ")[[1]][5]} provides support against a classification of blue.
-Since the weight associated with $x_2$ has a larger magnitude than the weight associated with $x_1$, LIME explains that the $x_1$ and $x_2$ locations of the prediction of interest provide more support for a random forest classification of blue over red.
+\hh{Because the support for blue by the value of feature $x_1$ outweighs the support for red by the value of feature $x_2$, the overall LIME explanation favors a label of blue for the prediction of interest.} %Since the weight associated with $x_2$ has a larger magnitude than the weight associated with $x_1$, LIME explains that the $x_1$ and $x_2$ locations of the prediction of interest provide more support for a random forest classification of blue over red.
 This explanation agrees with the random forest probability of \Sexpr{sine_poi_lime_default$label_prob[1]} for blue.
 Note that both models classify the observation incorrectly.
-Based on this plot alone, it is not possible to make an informed assessment of the explanation.
-
-To assess the explanation, we turn to an explanation scatterplot shown as the right plot in Figure \ref{fig:sine-exp-scatter}.
+Based on the plot \hh{on the left of \autoref{fig:sine-exp-scatter}} alone, it is not possible to make an informed assessment of the explanation.
+
+\subsection{Explanation Scatterplots} \label{exp-scatter}
+\hh{XXX I think we could reduce some of the example for the specific example a bit, now that the LIME explanation is moved out, there is not that much need to repeat the general ideas.}
+
+\hh{For a further assessment of the explainer model}, we turn to an \emph{explanation scatterplot}:
+the \emph{explanation scatterplot} is a visual diagnostic for assessing the LIME claims of locality and fidelity for an individual explanation by juxtaposing the complex and explainer models in one plot.
+The format of an explanation scatterplot depends on the LIME simulation method.
+We introduce the explanation scatterplot here under the \emph{lime} R package default method in which the data are simulated uniformly from four quantile bins.
+In this scenario, LIME converts continuous predictor variables to indicator variables identifying whether the variable value falls in the same quantile bin as the prediction of interest or not.
+The indicator variables are used as the explainer model features.
+
+The explanation scatterplot is built by plotting the LIME simulated data for the top two features identified by the explanation in a scatterplot and coloring these points by the  predictions from the complex model.
+The size of the points represents the weight assigned by LIME.
+\hh{In order to show the LIME results for the observation of interest, }
+ lines \hh{are drawn on top of the points.
+These lines } represent the boundaries of the indicator variables used to fit the explainer model.
+The color of the lines denote whether LIME indicates that a feature supports or contradicts a class prediction.
+Appendix \ref{exp-scatter_plus} addresses the explanation scatterplot formats in other LIME simulation scenarios.
+
+\hh{An explanation scatterplot for the example of the previous section is shown on the right hand side of \autoref{fig:sine-exp-scatter}.}
  The points are the simulated values of $x_2$ versus $x_1$ colored by the random forest predictions and sized by the proximity weight used to fit the ridge regression explainer model.
@@
 
-<<sine-feat-heat, out.width = '0.45\\textwidth', fig.width = 4, fig.height = 3.5>>=
+<<sine-feat-heat, out.width = '0.45\\textwidth', fig.width = 4, fig.height = 4>>=
 plot_feature_heatmap(sine_lime_explain$explain,
@@
 Fortunately, in the situation of LIME, both of these aspects are rather well controlled: LIME relies heavily on simulations to generate data scenarios that are close to the data observed but exhibits variability.
-Effects from overplotting should be relatively mild, because output from simulations is shown, which is expected to be (relatively) continuous \kgc{What do you mean by continuous here?}.
-In that respect, the diagnostics shown for the \data\ and in the bullet example are representative of what is expected.
-But in cases where overplotting does become problematic, the user could either simply reduce the size of the simulations or use some well-studied binning techniques in the visualizations, as discussed in \citet{carr:1987} \hh{reference to Millions book}
+Effects from overplotting should be relatively mild, because output from simulations is shown, which is expected to be (relatively) continuous \hh{such that overplotting only occurs for points with (relatively) similar values.} \kgc{What do you mean by continuous here?}.
+\hh{XXX Does that extra explanation help?} In that respect, the diagnostics shown for the \data\ and in the bullet example are representative of what is expected.
+But in cases where overplotting does become problematic, the user could either simply reduce the size of the simulations or use some well-studied binning techniques in the visualizations, as discussed for example in \citet{carr:1987} or \citet{gold}.
 
@@
 \section*{Acknowledgments}
-
-This is acknowledgment text. Provide text here.
+HH was partially funded by the Center for Statistics and Applications in Forensic Evidence (CSAFE) through Cooperative Agreement 70NANB20H019 between NIST and Iowa State University, which includes activities carried out at Carnegie Mellon University, Duke University, University of California Irvine, University of Virginia, West Virginia University, University of Pennsylvania, Swarthmore College and University of Nebraska, Lincoln.
 
@@
 
-This is an author contribution text. This is an author contribution text. This is an author contribution text. This is an author contribution text. This is an author contribution text.
+\hh{A taxonomy of author contributions is suggested by Elsevier - I put the link in an email
+}
+
+{\bf Katherine Goode, Heike Hofmann}: Conceptualization, Methodology, Investigation, Writing- Reviewing and Editing.
+{\bf Katherine Goode}: Writing Initial Draft, Software.
 
@@
 The following supporting information is available as part of the online article:
-
-\appendix
-
-\section{LIME Tuning Parameter Options} \label{lime-details}
-
-The following tuning parameters for the LIME algorithm are available in the \emph{lime} R package.
-
-\begin{itemize}
-
-\item Data simulation methods:
-
-\begin{itemize}
-\item Equally spaced bins: observations are uniformly sampled from equally spaced bins (number of bins may be specified)
-\item Quantile bins: observations are uniformly sampled from quantile bins (number of bins may be specified)
-\item Normal density approximation: observations are sampled from a normal distribution with mean and standard deviation computed from the corresponding feature
-\item Kernel density approximation: observations are sampled from an kernel density approximation of the corresponding feature
-\end{itemize}
-
-\item Number of observations to simulate
-
-\item Distance metric for determining proximity to the prediction of interest: Gower distance (where the power may be specified) or exponential kernel (where the kernel width may be specified)
-
-\item Number of features to return in an explanation
-
-\item Feature selection method for determining the features to return in an explanation: forward selection applied to a ridge regression, highest weights in ridge regression, LASSO, classification/regression tree splits
-
-\end{itemize}
-
-\section{Explanation Scatterplots Under Other Simulation Scenarios} \label{exp-scatter_plus}
-
-Section \ref{exp-scatter} introduces explanation scatterplots under the default simulation method in the \emph{lime} R package: four quantile bins.
-The structure of an explanation scatterplot remains the same for if any bin based simulation method is used to create the simulated data (any number of quantile or equally spaced bins).
-However, if the kernel density or normal approximation simulation methods are used as the simulation method, the format of the explanation scatterplot changes.
-In the density based simulation method scenarios, LIME uses the standardized versions of the predictor variables to fit the explainer model.
-Thus, the explainer model needs to be represented differently in the explanation scatterplot.
-
-When the kernel density or normal approximation simulation methods are applied, the explanation scatterplot depicts the complex model by plotting the complex model predictions versus a feature selected in LIME the explanation from the simulated data.
-The explainer model is included as a line on the figure where all features excluding the one plotted on the x-axis are set to the observed values of the prediction of interest.
-An explanation scatterplot is created for each feature included in the LIME explanation.
-As with the bin based simulation method, the size of the points represent the weight assigned by LIME.
-
-Figure \ref{fig:sine-expl-scat-density} provides example explanation scatterplots for each feature in the default LIME explanation obtained using the kernel density simulation method for the \data \ prediction of interest.
-
-\begin{figure*}[!thp]
-<<sine-expl-scat-density, out.width = '\\textwidth', fig.width = 12, fig.height = 4.5, fig.align = "center">>=
-plot_explain_scatter(
-  sine_lime_explain$explain %>%
-    filter(sim_method == "kernel_density", case == sine_poi %>% pull(case)),
-  alpha = 0.75, title.opt = FALSE
-) + 
-  theme_bw(base_family = "Times") +
-  theme(strip.background = element_rect(fill = "white", color = "white"),
-        strip.placement = "outside")
-@
-\caption{Explanation scatterplots for the \data \ prediction of interest with the kernel density simulation method.}
-\label{fig:sine-expl-scat-density}
-\end{figure*}
-
-Figure \ref{fig:bullet-expl-scat-density} includes explanation scatterplots for the explanations generated using kernel density simulation for the bullet example cases M and NM discussed in Section \ref{bullet-assess-ex}.
-
-\begin{figure*}[!thp]
-<<bullet-expl-scat-density, out.width = '\\textwidth', fig.width = 12, fig.height = 9, fig.align = "center">>=
-bullet_es_NM <-
-  plot_explain_scatter(
-  bullet_explain_perms[13:15, ] %>% mutate(case = "M"),
-  alpha = 0.75, title.opt = TRUE
-) +
-  theme_bw(base_family = "Times") +
-  theme(strip.background = element_rect(fill = "white", color = "white"),
-        strip.placement = "outside")
-
-bullet_es_M <-
-  plot_explain_scatter(
-  bullet_explain_perms[16:18, ] %>% mutate(case = "NM"),
-  alpha = 0.75, title.opt = TRUE
-) +
-  theme_bw(base_family = "Times") +
-  theme(strip.background = element_rect(fill = "white", color = "white"),
-        strip.placement = "outside")
-
-plot_grid(bullet_es_NM, bullet_es_M, nrow = 2)
-@
-\caption{Explanation scatterplots for LIME explanations using kernel density simulation for the cases M and NM of the bullet comparison.}
-\label{fig:bullet-expl-scat-density}
-\end{figure*}
-
-\section{Explainer Model Residual Plot} \label{residual-plot}
-
-In order to assess the claim of linearity for the \data \ prediction of interest discussed in Section \ref{exp-scatter}, we use one of the most basic diagnostics in a statistician's tool box and draw a residual plot for the explainer model.
-This is shown in Figure \ref{fig:sine-plot-resids} with the explainer model residuals on the y-axis and explainer model predictions on the x-axis.
-The points along the x-axes have been jittered to ease the effect of the over-plotted points in the visualization.
-There is a clear increasing trend in the residuals as the explainer model predictions increase.
-This is a clear violation of the linearity assumption with the ridge regression model.
-
-\begin{figure}[!thp]
-<<sine-plot-resids, out.width = '0.5\\textwidth', fig.width = 5, fig.height = 4, warning = FALSE>>=
-
-# Calculate the residuals from the explainer model
-y <- sine_poi_perms$rfpred
-sine_poi_explainer <-
-  function(x1, x2) sine_b0 + (sine_b1 * x1) + (sine_b2 * x2)
-sine_poi_perms <- sine_poi_perms %>%
-  mutate(exppred = sine_poi_explainer(x1num, x2num)) %>%
-  mutate(resid = exppred - rfpred)
-
-# Create the residual plot
-ggplot(sine_poi_perms, aes(x = exppred, y = resid)) +
-  geom_jitter(alpha = 0.5, width = 0.02) +
-  geom_hline(yintercept = 0) +
-  theme_bw(base_family = "Times", base_size = 10) +
-  labs(x = "Explainer Model Predictions",
-       y = "Explainer Model Residuals",
-       title = "Explainer Model Residual Plot")
-@
-\caption{Residual plot of the explainer model associated with \data \ prediction of interest from Section \ref{exp-scatter}.
-The residuals are plotted against the predicted values.
-The points are jittered in the x-direction to alleviate the over-plotting of points.
-There is an upward trend in the residuals as the explainer model predictions increase, which suggests a violation of the linearity assumption.}
-\label{fig:sine-plot-resids}
-\end{figure}
-
-\section{Details on Assessment Metrics} \label{metric-details}
-
-Suppose $f$ is a complex model, and let $\textbf{X}$ be a matrix of observed data with $K$ features and $E$ observations where $x_e$ is an observed feature vector for observation $e$.
-Let $f(x_e)$ be the complex model prediction for observation $e$.
-It is of interest to explain the predictions made by $f$ applied to $X$ using LIME.
-
-For $x_e$ and set of tuning parameters $t$, let $\textbf{X}_{e,t}'$ be the LIME simulated dataset with $K$ features and $S$ observations such that $x'_{e,t,s}$ is the feature vector for simulated data observation $s$.
-Let $\textbf{Z}'_{e,t}$ be the matrix of interpretability transformed simulated data with $K$ features and $S$ observations such that $z'_{e,t,s}$ is the interpretability transformed feature vector for observation/explanation $e$, tuning parameter $t$, and simulated data observation $s$.
-Note that $z_{e,t}$ will represent the interpretability transformed version of $x_e$.
-
-Next, let $\omega_t$ represent a proximity distance metric.
-Then $\omega_t\left(x_e, x'_{e,t,s}\right)$ is the weight assigned to $x'_{e,t,s}$, which is the proximity between $x_e$ and $x'_{e,t,s}$.
-Allow $g_{e,t}$ to be the explainer model for an explanation $e$ and tuning parameter $t$.
-Thus, $g_{e,t}\left(z'_{e,s,t}\right)$ is the explainer model prediction for the interpretability transformed simulated data observation $s$.
-
-For a set of $E$ explanations and a set of tuning parameters $t$, we define the assessment metrics as follows:\\
-\\
-\emph{Average $R^2$} is denoted as $R^2_{\mbox{ave}}$ and computed as
-
-  $$R^2_{\mbox{ave}} = \frac{1}{E}\sum_{e=1}^E R_{e,t}^2$$
-
-where $R_{e,t}^2$ is the $R^2$ value for $g_{e,t}$.\\
-\\
-\emph{Average fidelity} is denoted by $\mathcal{L}_{\mbox{ave}}$ and computed as
-
-\begin{eqnarray*} \mathcal{L}_{\mbox{ave}} & = & \frac{1}{E}\sum_{e=1}^E\mathcal{L}(f, \ g_{e,t}, \ \pi_{t}) \\ & = & \frac{1}{E}\sum_{e=1}^E\sum_{s=1}^{S}\omega_{t}\left(x_e, x'_{e,t,s}\right)\left(f\left(x'_{e,t,s}\right)-g_{e,t}\left(z_{e,t,s}'\right)\right)^2.
-\end{eqnarray*}\\
-\\
-\emph{Mean squared explanation error} is denoted by MSEE and computed as
-
-$$MSEE=\frac{1}{E}\sum_{e=1}^E\left(f\left(x_e\right)-g_{e,t}\left(z_{e,t}\right)\right)^2.$$
 
@@
 % \end{itemize}
+\newpage
+\appendix
+
+\section{LIME Tuning Parameter Options} \label{lime-details}
+
+The following tuning parameters for the LIME algorithm are available in the \emph{lime} R package.
+
+\begin{itemize}
+
+\item Data simulation methods:
+
+\begin{itemize}
+\item Equally spaced bins: observations are uniformly sampled from equally spaced bins (number of bins may be specified)
+\item Quantile bins: observations are uniformly sampled from quantile bins (number of bins may be specified)
+\item Normal density approximation: observations are sampled from a normal distribution with mean and standard deviation computed from the corresponding feature
+\item Kernel density approximation: observations are sampled from an kernel density approximation of the corresponding feature
+\end{itemize}
+
+\item Number of observations to simulate
+
+\item Distance metric for determining proximity to the prediction of interest: Gower distance (where the power may be specified) or exponential kernel (where the kernel width may be specified)
+
+\item Number of features to return in an explanation
+
+\item Feature selection method for determining the features to return in an explanation: forward selection applied to a ridge regression, highest weights in ridge regression, LASSO, classification/regression tree splits
+
+\end{itemize}
+
+\section{Explanation Scatterplots Under Other Simulation Scenarios} \label{exp-scatter_plus}
+
+Section \ref{exp-scatter} introduces explanation scatterplots under the default simulation method in the \emph{lime} R package: four quantile bins.
+The structure of an explanation scatterplot remains the same for if any bin based simulation method is used to create the simulated data (any number of quantile or equally spaced bins).
+However, if the kernel density or normal approximation simulation methods are used as the simulation method, the format of the explanation scatterplot changes.
+In the density based simulation method scenarios, LIME uses the standardized versions of the predictor variables to fit the explainer model.
+Thus, the explainer model needs to be represented differently in the explanation scatterplot.
+
+When the kernel density or normal approximation simulation methods are applied, the explanation scatterplot depicts the complex model by plotting the complex model predictions versus a feature selected in LIME the explanation from the simulated data.
+The explainer model is included as a line on the figure where all features excluding the one plotted on the x-axis are set to the observed values of the prediction of interest.
+An explanation scatterplot is created for each feature included in the LIME explanation.
+As with the bin based simulation method, the size of the points represent the weight assigned by LIME.
+
+Figure \ref{fig:sine-expl-scat-density} provides example explanation scatterplots for each feature in the default LIME explanation obtained using the kernel density simulation method for the \data \ prediction of interest.
+
+\begin{figure*}[!thp]
+<<sine-expl-scat-density, out.width = '\\textwidth', fig.width = 12, fig.height = 4.5, fig.align = "center">>=
+plot_explain_scatter(
+  sine_lime_explain$explain %>%
+    filter(sim_method == "kernel_density", case == sine_poi %>% pull(case)),
+  alpha = 0.75, title.opt = FALSE
+) + 
+  theme_bw(base_family = "Times") +
+  theme(strip.background = element_rect(fill = "white", color = "white"),
+        strip.placement = "outside")
+@
+\caption{Explanation scatterplots for the \data \ prediction of interest with the kernel density simulation method.}
+\label{fig:sine-expl-scat-density}
+\end{figure*}
+
+Figure \ref{fig:bullet-expl-scat-density} includes explanation scatterplots for the explanations generated using kernel density simulation for the bullet example cases M and NM discussed in Section \ref{bullet-assess-ex}.
+
+\begin{figure*}[!thp]
+<<bullet-expl-scat-density, out.width = '\\textwidth', fig.width = 12, fig.height = 9, fig.align = "center">>=
+bullet_es_NM <-
+  plot_explain_scatter(
+  bullet_explain_perms[13:15, ] %>% mutate(case = "M"),
+  alpha = 0.75, title.opt = TRUE
+) +
+  theme_bw(base_family = "Times") +
+  theme(strip.background = element_rect(fill = "white", color = "white"),
+        strip.placement = "outside")
+
+bullet_es_M <-
+  plot_explain_scatter(
+  bullet_explain_perms[16:18, ] %>% mutate(case = "NM"),
+  alpha = 0.75, title.opt = TRUE
+) +
+  theme_bw(base_family = "Times") +
+  theme(strip.background = element_rect(fill = "white", color = "white"),
+        strip.placement = "outside")
+
+plot_grid(bullet_es_NM, bullet_es_M, nrow = 2)
+@
+\caption{Explanation scatterplots for LIME explanations using kernel density simulation for the cases M and NM of the bullet comparison.}
+\label{fig:bullet-expl-scat-density}
+\end{figure*}
+
+\section{Explainer Model Residual Plot} \label{residual-plot}
+
+In order to assess the claim of linearity for the \data \ prediction of interest discussed in Section \ref{exp-scatter}, we use one of the most basic diagnostics in a statistician's tool box and draw a residual plot for the explainer model.
+This is shown in Figure \ref{fig:sine-plot-resids} with the explainer model residuals on the y-axis and explainer model predictions on the x-axis.
+The points along the x-axes have been jittered to ease the effect of the over-plotted points in the visualization.
+There is a clear increasing trend in the residuals as the explainer model predictions increase.
+This is a clear violation of the linearity assumption with the ridge regression model.
+
+\begin{figure}[!thp]
+<<sine-plot-resids, out.width = '0.5\\textwidth', fig.width = 5, fig.height = 4, warning = FALSE>>=
+
+# Calculate the residuals from the explainer model
+y <- sine_poi_perms$rfpred
+sine_poi_explainer <-
+  function(x1, x2) sine_b0 + (sine_b1 * x1) + (sine_b2 * x2)
+sine_poi_perms <- sine_poi_perms %>%
+  mutate(exppred = sine_poi_explainer(x1num, x2num)) %>%
+  mutate(resid = exppred - rfpred)
+
+# Create the residual plot
+ggplot(sine_poi_perms, aes(x = exppred, y = resid)) +
+  geom_jitter(alpha = 0.5, width = 0.02) +
+  geom_hline(yintercept = 0) +
+  theme_bw(base_family = "Times", base_size = 10) +
+  labs(x = "Explainer Model Predictions",
+       y = "Explainer Model Residuals",
+       title = "Explainer Model Residual Plot")
+@
+\caption{Residual plot of the explainer model associated with \data \ prediction of interest from Section \ref{exp-scatter}.
+The residuals are plotted against the predicted values.
+The points are jittered in the x-direction to alleviate the over-plotting of points.
+There is an upward trend in the residuals as the explainer model predictions increase, which suggests a violation of the linearity assumption.}
+\label{fig:sine-plot-resids}
+\end{figure}
+
+\section{Details on Assessment Metrics} \label{metric-details}
+
+Suppose $f$ is a complex model, and let $\textbf{X}$ be a matrix of observed data with $K$ features and $E$ observations where $x_e$ is an observed feature vector for observation $e$.
+Let $f(x_e)$ be the complex model prediction for observation $e$.
+It is of interest to explain the predictions made by $f$ applied to $X$ using LIME.
+
+For $x_e$ and set of tuning parameters $t$, let $\textbf{X}_{e,t}'$ be the LIME simulated dataset with $K$ features and $S$ observations such that $x'_{e,t,s}$ is the feature vector for simulated data observation $s$.
+Let $\textbf{Z}'_{e,t}$ be the matrix of interpretability transformed simulated data with $K$ features and $S$ observations such that $z'_{e,t,s}$ is the interpretability transformed feature vector for observation/explanation $e$, tuning parameter $t$, and simulated data observation $s$.
+Note that $z_{e,t}$ will represent the interpretability transformed version of $x_e$.
+
+Next, let $\omega_t$ represent a proximity distance metric.
+Then $\omega_t\left(x_e, x'_{e,t,s}\right)$ is the weight assigned to $x'_{e,t,s}$, which is the proximity between $x_e$ and $x'_{e,t,s}$.
+Allow $g_{e,t}$ to be the explainer model for an explanation $e$ and tuning parameter $t$.
+Thus, $g_{e,t}\left(z'_{e,s,t}\right)$ is the explainer model prediction for the interpretability transformed simulated data observation $s$.
+
+For a set of $E$ explanations and a set of tuning parameters $t$, we define the assessment metrics as follows:\\
+\\
+\emph{Average $R^2$} is denoted as $R^2_{\mbox{ave}}$ and computed as
+
+  $$R^2_{\mbox{ave}} = \frac{1}{E}\sum_{e=1}^E R_{e,t}^2$$
+
+where $R_{e,t}^2$ is the $R^2$ value for $g_{e,t}$.\\
+\\
+\emph{Average fidelity} is denoted by $\mathcal{L}_{\mbox{ave}}$ and computed as
+
+\begin{eqnarray*} \mathcal{L}_{\mbox{ave}} & = & \frac{1}{E}\sum_{e=1}^E\mathcal{L}(f, \ g_{e,t}, \ \pi_{t}) \\ & = & \frac{1}{E}\sum_{e=1}^E\sum_{s=1}^{S}\omega_{t}\left(x_e, x'_{e,t,s}\right)\left(f\left(x'_{e,t,s}\right)-g_{e,t}\left(z_{e,t,s}'\right)\right)^2.
+\end{eqnarray*}\\
+\\
+\emph{Mean squared explanation error} is denoted by MSEE and computed as
+
+$$MSEE=\frac{1}{E}\sum_{e=1}^E\left(f\left(x_e\right)-g_{e,t}\left(z_{e,t}\right)\right)^2.$$
 

### 2020-08-23 paper.Rnw
mini edits from the meeting

@@
 The forked version \hh{is functionally indistinguishable from Pedersen's implementation but it} allows us to export internal values \hh{relevant for an assessment of the explainer}. 
-The R package \emph{limeaid} \footnote{Available on GitHub at https://github.com/goodekat/limeaid} (\Sexpr{packageVersion("limeaid")}) implements diagnostic plots based on the output of the altered version of `lime`.
+The R package \emph{limeaid} \footnote{Available on GitHub at https://github.com/goodekat/limeaid} (\Sexpr{packageVersion("limeaid")}) implements diagnostic plots based on the output of the altered version of \emph{lime}.
 

### 2020-08-25 paper.Rnw
updates based on comments from Heike - I'll work on proof reading next

@@
 library(ggplot2)
-library(ggpcp)
+library(ggpcp) #devtools::install_github("yaweige/ggpcp", build_vignettes = TRUE)
 library(glmnet)
@@
 library(graphics)
-library(gretchenalbrecht)
+library(gretchenalbrecht) #devtools::install_github("dicook/gretchenalbrecht")
 library(latex2exp)
@@
   scale_alpha(range = c(0.3, 1)) +
-  scale_color_manual(values = c(NA, "grey30"), guide = FALSE) +
+  scale_color_manual(values = c(NA, "grey30"), guide = "none") +
   geom_point(data = prediction_of_interest_gathered,
@@
   scale_alpha(range = c(0.3, 1)) +
-  scale_color_manual(values = c("grey30", NA), guide = FALSE) +
+  scale_color_manual(values = c("grey30", NA), guide = "none") +
   geom_point(data = prediction_of_interest_gathered,
@@
 A Gower distance metric \citep{gower:1971} is used to define locality such that the size of the points represent the inverse of the Gower distance raised to some value and indicate the proximity to the prediction of interest.
-\hh{In the example of \autoref{fig:concept-plot-good}} an exponent of \Sexpr{good_gower_power} is used to emphasize a very local region around the prediction of interest.
+\hh{In the example of \autoref{fig:concept-plot-good}}, an exponent of \Sexpr{good_gower_power} is used to emphasize a very local region around the prediction of interest.
 A ridge regression model weighted by the proximity values is used as the explainer model with the black-box predictions as the response variable and standardized versions of \hh{two features in the data} % features Features 1 and~2
@@
 Note that due to the creation of $y$ in this manner, $y$ is dependent on $x_1$ and $x_2$ and independent of $x_3$.
-\hh{From the plots in \autoref{sine-plot-data} we see that the global relationship between response $y$ and features $x_1$ and $x_2$ is linear: the probability for label blue increases with the difference between features $x_2$ and $x_1$.
+\hh{From the plots in \autoref{sine-plot-data}}\kge{,} \hh{we see that the global relationship between response $y$ and features $x_1$ and $x_2$ is linear: the probability for label blue increases with the difference between features $x_2$ and $x_1$.
 Locally, the relationship between $y$ and features $x_2$ and $x_1$ varies a lot more around the line of identity.
 Here, the relationship is determined by the sine waves.
-However, the sine is a good-natured function that can be approximated well linearly.
-}
+However, the sine is a good-natured function that can be approximated well linearly} \kge{in local regions}.
 
@@
 a forked version\footnote{https://github.com/goodekat/lime} of the development version of the R package \emph{lime} (\Sexpr{packageVersion("lime")}) \citep{pedersen:2020}. 
-The forked version \hh{is functionally indistinguishable from Pedersen's implementation but it} allows us to export internal values \hh{relevant for an assessment of the explainer}. 
+The forked version \hh{is functionally indistinguishable from Pedersen's implementation}\kge{,} \hh{but it} allows us to export internal values \hh{relevant for an assessment of the explainer}. 
 The R package \emph{limeaid} \footnote{Available on GitHub at https://github.com/goodekat/limeaid} (\Sexpr{packageVersion("limeaid")}) implements diagnostic plots based on the output of the altered version of \emph{lime}.
@@
 \begin{figure*}[!thp]
-<<sine-exp-scatter, out.width = '\\textwidth', fig.width = 10, fig.height = 3.9, warning = FALSE>>=
+<<sine-exp-scatter, out.width = '\\textwidth', fig.width = 12, fig.height = 4.68, warning = FALSE>>=
 
@@
 exp_scatter <- 
-  plot_explain_scatter(sine_poi_lime_default) +
+  plot_explain_scatter(sine_poi_lime_default, alpha = 0.4) +
   facet_grid(switch = "both") +
@@
   theme_bw(base_family = "Times", base_size = 10) +
-  guides(shape = guide_legend(order = 1)) +
+  guides(shape = guide_legend(order = 1),
+         size = guide_legend(nrow = 2, byrow = T)) +
   theme(aspect.ratio = 1)
 
-plot_grid(sine_poi_exp, exp_scatter, align = "h") 
+plot_grid(sine_poi_exp, exp_scatter) 
 @
@@
 \hh{XXX could you make the complex prediction **much** lighter for this example?
-The diamond and the lines are hard to see, but should be the focus.} The prediction of interest is shown as the diamond shaped point.
+The diamond and the lines are hard to see, but should be the focus.} \kgc{Is that light enough?
+Feel free to edit the alpha value in the plot\_explain\_scatter function as you feel necessary.
+I also made the lines depicting the explainer model wider in limeaid, and there is an option 'line\_size' that can be adjusted.} The prediction of interest is shown as the diamond shaped point.
 The explainer model indicator variables associated with $x_1$ and $x_2$ (quantile bins containing the prediction of interest) are depicted by the solid lines.
@@
 \subsection{A LIME explanation}
-\hh{XXX I've just pulled the description of the left hand side of figure 4 out of the next section.}
-To demonstrate a LIME explanation, we focus on the misclassified point indicated in Figure \ref{fig:sine-plot-data} by the diamond as the prediction of interest.
+\hh{XXX I've just pulled the description of the left hand side of figure 4 out of the next section.} \kgc{Okay.} To demonstrate a LIME explanation, we focus on the misclassified point indicated in Figure \ref{fig:sine-plot-data} by the diamond as the prediction of interest.
 The left plot in Figure \ref{fig:sine-exp-scatter} shows a visualization of the explanation for the prediction of interest as suggested by Ribeiro et al and implemented in the \emph{lime} R package.
@@
 \subsection{Explanation Scatterplots} \label{exp-scatter}
-\hh{XXX I think we could reduce some of the example for the specific example a bit, now that the LIME explanation is moved out, there is not that much need to repeat the general ideas.}
-
-\hh{For a further assessment of the explainer model}, we turn to an \emph{explanation scatterplot}:
-the \emph{explanation scatterplot} is a visual diagnostic for assessing the LIME claims of locality and fidelity for an individual explanation by juxtaposing the complex and explainer models in one plot.
+\hh{XXX I think we could reduce some of the example for the specific example a bit, now that the LIME explanation is moved out, there is not that much need to repeat the general ideas.} \kgc{I commented out the text that I think you were referring to.
+See what you think.}
+
+\hh{For a further assessment of the explainer model}, we turn to an \emph{explanation scatterplot}: the \emph{explanation scatterplot} is a visual diagnostic for assessing the LIME claims of locality and fidelity for an individual explanation by juxtaposing the complex and explainer models in one plot.
 The format of an explanation scatterplot depends on the LIME simulation method.
@@
 
-\hh{An explanation scatterplot for the example of the previous section is shown on the right hand side of \autoref{fig:sine-exp-scatter}.}
- The points are the simulated values of $x_2$ versus $x_1$ colored by the random forest predictions and sized by the proximity weight used to fit the ridge regression explainer model.
+\hh{An explanation scatterplot} \sout{for the} \kge{associated with the LIME explanation depicted on the left in \autoref{fig:sine-exp-scatter}} \sout{example of the previous section} \hh{is shown on the right hand side of \autoref{fig:sine-exp-scatter}.} %The points are the simulated values of $x_2$ versus $x_1$ colored by the random forest predictions and sized by the proximity weight used to fit the ridge regression explainer model.
 The explainer model is represented by the solid horizontal and vertical lines identifying the boundaries of the quantiles that contain the prediction of interest.
@@
 The prediction of interest is represented by the diamond shaped point.
-
 By juxtaposing the random forest predictions and the explainer model boundaries, we are able to assess the faithfulness and localness of the explainer model.
@@
 Effects from overplotting should be relatively mild, because output from simulations is shown, which is expected to be (relatively) continuous \hh{such that overplotting only occurs for points with (relatively) similar values.} \kgc{What do you mean by continuous here?}.
-\hh{XXX Does that extra explanation help?} In that respect, the diagnostics shown for the \data\ and in the bullet example are representative of what is expected.
+\hh{XXX Does that extra explanation help?} \kgc{Yes.
+I see what you mean now.} In that respect, the diagnostics shown for the \data\ and in the bullet example are representative of what is expected.
 But in cases where overplotting does become problematic, the user could either simply reduce the size of the simulations or use some well-studied binning techniques in the visualizations, as discussed for example in \citet{carr:1987} or \citet{gold}.

### 2020-08-26 paper.Rnw
proof reading edits through the description of the sine data in Section 3

@@
 % Set up for ASA data science journal
-\articletype{Article Type}
-\received{26 April 2016}
-\revised{6 June 2016}
-\accepted{6 June 2016}
+\articletype{\kge{Research Article}}
+\received{\kge{XX August 2020}}
+\revised{\kge{XX XX XXXX}}
+\accepted{\kge{XX XX XXXX}}
 \raggedbottom
@@
 However, the quality of the resulting explanations relies on how well the explainer model captures the black-box model in a specified local region.
-Here we introduce three visual diagnostics to assess the quality of LIME explanations: (1) explanation scatterplot, (2) assessment metric plot, and (3) feature heatmap.
+Here we introduce three visual diagnostics to assess the quality of LIME explanations: (1) explanation scatterplot\kge{s}, (2) assessment metric plot\kge{s}, and (3) feature heatmap\kge{s}.
 We apply the visual diagnostics to a forensics bullet matching dataset to show examples where LIME explanations depend on the tuning parameters and the explainer model oversimplifies the black-box model.
-Our examples raise concerns about claims made about LIME \citep{ribeiro:2016} that are similar to other criticisms in the literature (\citet{alvarezmelis:2018}, \citet{laugel:2018}, and \citet{molnar:2019}).}
+Our examples raise concerns about claims made \kge{of \sout{about}} LIME \citep{ribeiro:2016} that are similar to other criticisms in the literature (\citet{alvarezmelis:2018}, \citet{laugel:2018}, and \citet{molnar:2019}).}
 \keywords{LIME, black-box models, interpretability, diagnostics}
@@
 Model interpretability allows for the understanding and assessment of how a model produces predictions.
-The lack of the ability to understand and assess a model makes it difficult to trust the model, especially in areas with high stakes decisions such as health care and forensics science.
+The lack of the ability to understand and assess a model makes it difficult to trust the model, especially in areas with high stakes decisions such as \kge{medical \sout{health care}} and forensics science\kge{s}.
 The increased use of machine learning models in applications and the introduction of the General Data Protection Regulation (GDPR) in 2018 \citep{goodman:2016} has resulted in a dramatic increase in explainable machine learning research, which focuses on developing ways to explain output from machine learning algorithms.
@@
 
-Numerous methods have been proposed to provide explanations for black-box model predictions \citep{gilpin:2018, guidotti:2018, ming:2017, mohseni:2018, molnar:2019}.
-Some are specific to one type of model (e.g.
-\citep{simonyan:2013} and \citep{welling:2016}), and others are model-agnostic (e.g.
+Numerous methods have been proposed to provide explanations for black-box model predictions \citep{gilpin:2018, guidotti:2018, ming:2017, molnar:2019}.
+\kgc{I just took out the Mohseni reference since it is not peer reviewed.
+I think the other four should give enough of an idea of places to look for overviews on EML.
+Does that seem okay to you?} Some are specific to one type of model (e.g.
+\citep{simonyan:2013} and \citep{urbanek:2008}), \kgc{I switched to a reference to Urbanek's visualizations since the Welling paper was not peer reviewed.
+Is this better?} %\citep{welling:2016}),
+and others are model-agnostic (e.g.
 \citep{fisher:2018} and \citep{strumbelj:2014}).
-In this paper, we focus on \hh{one specific} model-agnostic method: LIME \citet{ribeiro:2016} \hh{introduced by Ribeiro, Singh, and Guestrin in 2016}.
-
-%\subsection{Conceptual Description of LIME}
+In this paper, we focus on \hh{one specific} model-agnostic method: LIME \citep{ribeiro:2016} \kge{(}\hh{introduced by Ribeiro, Singh, and Guestrin in 2016}\kge{)}.
+\kgc{Do we need the addition of when the paper was introduced here since the statement is made at the beginning of Section 2, or did you intend to remove that sentence?}
 
@@
 The size and opacity of the circular points indicate the weight assigned based on the distance to the prediction of interest computed using the inverse of the Gower distance metric raised to the power of \Sexpr{good_gower_power}.
-The black lines are a weighted ridge regression model used as an explainer model that reasonably captures the relationship between the black-box predictions and the features in a local region around the prediction of interest.
+The black lines \kge{represent \sout{are}} a weighted ridge regression model used as an explainer model that reasonably captures the relationship between the black-box predictions and the features in a local region around the prediction of interest.
 That is, the explainer is faithful to the complex model and produces a reasonable explanation that Feature 1 plays a more important role in the prediction of interest than Feature 2 since the magnitude of the slope associated with Feature 1 is larger.}
@@
 A ridge regression model is fit to the same hypothetical black-box model predictions and predictor variables as in \autoref{fig:concept-plot-good}, but the weights are computed using a Gower exponent of 1.
-The explainer model is unfaithful to the complex model in the immediate neighborhood of the prediction of interest.}
+The explainer model is unfaithful to the complex model in \kge{any \sout{the}} immediate neighborhood of the prediction of interest.}
 \label{fig:concept-plot-bad}
@@
 \autoref{fig:concept-plot-good} provides a visualization of this conceptual understanding of LIME.
-The two plots show the predictions from a hypothetical black-box model plotted against the two predictor variables used to fit the hypothetical model.
-The diamond shaped points represent a prediction of interest.
+The two plots show the predictions from a hypothetical black-box model plotted against the two \kge{hypothetical model} predictor variables \kge{\sout{used to fit the hypothetical model}}.
+The diamond shaped points represent \kge{\sout{a} the location of the} prediction of interest.
 A Gower distance metric \citep{gower:1971} is used to define locality such that the size of the points represent the inverse of the Gower distance raised to some value and indicate the proximity to the prediction of interest.
 \hh{In the example of \autoref{fig:concept-plot-good}}, an exponent of \Sexpr{good_gower_power} is used to emphasize a very local region around the prediction of interest.
-A ridge regression model weighted by the proximity values is used as the explainer model with the black-box predictions as the response variable and standardized versions of \hh{two features in the data} % features Features 1 and~2
-as predictor variables. Standardized features allow direct comparisons of the model coefficients. The explainer model is depicted by the black lines in the figure.
+A ridge regression model weighted by the proximity values is used as the explainer model with the black-box predictions as the response variable and standardized versions of \hh{two features in the data} as predictor variables.
+Standardized features allow direct comparisons of the model coefficients.
+The explainer model is depicted by the black lines in the figure.
 
@@
 Here, the explainer model is plotted with Feature 2 fixed at the observed value of the prediction of interest.
-The explainer model captures the relationship in the immediate neighborhood around the prediction of interest  with a slope of \Sexpr{coefs_data %>% filter(case == "good", feature == "Feature 1") %>% pull(slope) %>% round(3)}.
-The plot on the right shows no global or local relationship between the black-box predictions and Feature 2.
+The explainer model captures the relationship in \kge{an \sout{the}} immediate neighborhood around the prediction of interest with a slope of \Sexpr{coefs_data %>% filter(case == "good", feature == "Feature 1") %>% pull(slope) %>% round(3)}.
+The plot on the right shows no global or local relationship\kge{s} between the black-box predictions and Feature 2.
 Here, the explainer model is plotted with Feature 1 set as the observed value of the prediction of interest, and it has an appropriately small slope of \Sexpr{coefs_data %>% filter(case == "good", feature == "Feature 2") %>% pull(slope) %>% round(3)}.
@@
 
-%\subsection{Motivation for Diagnosing LIME}
-
 The concept of LIME is relatively simple: use an interpretable model to approximate a complex model in a local region.
 However, a practical implementation of LIME is not straightforward, and research is being done to improve the procedure \citep{laugel:2018}.
-The current implementations of LIME\footnote{https://github.com/marcotcr/lime} \citep{pedersen:2020} offer various tuning parameters (see Section \ref{background}) that affect the explainer model and ultimately, the explanation.
+The current implementations of LIME\footnote{https://github.com/marcotcr/lime}\kgc{Is there a better way to cite a Python package?} \citep{pedersen:2020} offer various tuning parameters (see Section \ref{background}) that affect the explainer model and ultimately, the explanation.
 Since the explainer model is an approximation of the complex model and not a direct interpretation, the explanations produced by an explainer model are subject to the quality of the approximation.
@@
 This causes the observations that are further away from the prediction of interest to be given larger weights than before.
-In \autoref{fig:concept-plot-good}, the explainer model captures the relationship between the black-box predictions in the immediate neighborhood of the prediction of interest.
+In \autoref{fig:concept-plot-good}, the explainer model captures the relationship between the black-box predictions in \kge{an \sout{the}} immediate neighborhood of the prediction of interest.
 This cannot be said of the explainer model in \autoref{fig:concept-plot-bad}.
-In addition, the magnitude of the slope (\Sexpr{coefs_data %>% filter(case == "bad", feature == "Feature 2") %>% pull(slope) %>% round(3) %>% abs()}) associated with Feature 2 is larger than that of Feature 1 (\Sexpr{coefs_data %>% filter(case == "bad", feature == "Feature 1") %>% pull(slope) %>% round(3) %>% abs()}).
-Thus, this explainer model actually provides a misleading explanation that Feature 2 plays a more important role in predicting the observation of interest.
+In addition, the magnitude of the slope associated with Feature 2  (\Sexpr{coefs_data %>% filter(case == "bad", feature == "Feature 2") %>% pull(slope) %>% round(3) %>% abs()}) is larger than that of Feature 1 (\Sexpr{coefs_data %>% filter(case == "bad", feature == "Feature 1") %>% pull(slope) %>% round(3) %>% abs()}).
+Thus, this explainer model actually provides a misleading explanation that Feature 2 plays a more important role in \kge{the} predict\kge{ion\sout{ing the observation}} of interest.
 
@@
 \citet{alvarezmelis:2018} raise a concern pertaining to the robustness of explanations from LIME and other model explainers: they find that even small changes in predictor variables can lead to very different LIME explanations.
-Additionally, \citet{ribeiro:2016} acknowledge that if a linear model is used as the explainer, LIME relies on a linear approximation of the explainer model to the complex model and state ``if the underlying model is highly non-linear even in the locality of the prediction, there may not be a faithful explanation".
+Additionally, \citet{ribeiro:2016} acknowledge that if a linear model is used as the explainer, LIME relies on a linear approximation of the explainer model to the complex model and state "if the underlying model is highly non-linear even in the locality of the prediction, there may not be a faithful explanation".
 
@@
 
-%\subsection{Structure of Paper}
-
 The remainder of the paper is structured as follows.
@@
 We introduce the suggested diagnostic plots in Section \ref{diagnostics}.
-Then in Section \ref{application}, we demonstrate the use of the diagnostics to assess LIME explanations for a random forest model fit to a forensics bullet matching dataset.
+Then in Section \ref{application}, we demonstrate the use of the diagnostics to assess LIME explanations for a random forest \kge{\sout{model}} fit to a forensics bullet matching dataset.
 Section \ref{discussion} concludes with a discussion on extensions and limitations of the diagnostic plots and concerns about LIME in regards to the claims made by \citet{ribeiro:2016} brought about by the visualization examples in this paper that agree with \citet{alvarezmelis:2018}, \citet{laugel:2018}, and \citet{molnar:2019}.
+\kgc{I moved the following two sentences here from Section 2, so that it refers to the whole paper more clearly.} \hh{All runs of LIME in this paper are executed in} a forked version\footnote{https://github.com/goodekat/lime} of the development version of the R package \emph{lime} (\Sexpr{packageVersion("lime")}) \citep{pedersen:2020}.
+The forked version \hh{is functionally indistinguishable from Pedersen's implementation}\kge{,} \hh{but it} allows us to export internal values \hh{relevant for an assessment of the explainer}.
+%The R package \emph{limeaid} \footnote{Available on GitHub at https://github.com/goodekat/limeaid} (\Sexpr{packageVersion("limeaid")}) implements diagnostic plots based on the output of the altered version of \emph{lime}.
 The diagnostic plots included in this paper are created using the R package \emph{limeaid} \citep{goode:2020}.
-%\kgc{(Would you like me to add you as an author on the limeaid package?)}\hh{I appreciated your offer, but limeaid is your package - I haven't written a single line :)}
 
@@
 LIME was introduced in 2016 by \citet{ribeiro:2016}.
-The  authors provide an implementation of LIME in a Python package\footnote{https://github.com/marcotcr/lime}.
-An adaption of the Python package in R has been implemented and made available by Thomas Lin-Pedersen \citep{pedersen:2020}.
+\kgc{You added this sentence to Section 1.
+Do you want it removed from here or there?
+If it is removed here, the next sentence will need to be changed.} The authors provide an implementation of LIME in a Python package\footnote{https://github.com/marcotcr/lime}.
+\kgc{(Again, is there a better way to cite a Python package?)} An adaption of the Python package in R has been implemented and made available by Thomas Lin-Pedersen \citep{pedersen:2020}.
 The discussion of parameter choices and implementation details of LIME in this paper are based on the R package.
@@
 there are too many variables in the model), it is clear that the assumption of interpretability is violated.
-The other three assumptions are not as easy to assess -- for those we suggest the use of diagnostic plots.
+The other three assumptions are not as easy to assess\kge{, and} %--
+for those\kge{,} we suggest the use of diagnostic plots.
 
@@
 
-# Separte the data into training and testing parts
+# Separate the data into training and testing parts
 set.seed(20191003)
@@
 
-# Create points represting the rotated since curve
+# Create points representing the rotated since curve
 sinefun_data <- data.frame(xnew = seq(min(sine_data$x1new),
@@
 The true classification boundary is shown as the solid black line in both plots.
-The color of the training data points represents the value of the observed response variable ($y$).
-The color of the testing data points represents the random forest probability that an observation belongs to the category of blue ($\hat{y}$).
+The color of the training data \kge{\sout{points}} represents the value of the observed response variable ($y$).
+The color of the testing data \kge{\sout{points}} represents the random forest probability that an observation belongs to the category of blue \kge{\sout{($\hat{y}$)}}.
 The \Sexpr{dim(sine_data_test %>% filter(y != rfpred))[1]} cases that are misclassified by the random forest are identified by black circles.
@@
 
-To demonstrate the visualizations, we generate an example dataset that will be referred to as the \data.
+To demonstrate the \kge{visual diagnostics \sout{visualizations}}, we generate an example dataset that will be referred to as the \data.
 The \data \ contains \Sexpr{dim(sine_data)[1]} observations with three features and one response variable.
@@
 Note that due to the creation of $y$ in this manner, $y$ is dependent on $x_1$ and $x_2$ and independent of $x_3$.
-\hh{From the plots in \autoref{sine-plot-data}}\kge{,} \hh{we see that the global relationship between response $y$ and features $x_1$ and $x_2$ is linear: the probability for label blue increases with the difference between features $x_2$ and $x_1$.
+The dataset is divided into \kge{training and testing sets of \Sexpr{dim(sine_data_train)[1]} and \Sexpr{dim(sine_data_test)[1]} observations, respectively.
+\sout{a training set of \Sexpr{dim(sine_data_train)[1]} observations and a testing set of \Sexpr{dim(sine_data_test)[1]} observations.}} A random forest \kge{\sout{model}} is fit using the R package \emph{randomForest} (version \Sexpr{packageVersion("randomForest")}) \citep{liaw:2002} with the default settings.
+The model is applied to the test set to obtain predictions.
+
+\autoref{fig:sine-plot-data} shows scatterplots of $x_2$ versus $x_1$ from the training data (left) and the testing data (right).
+Both plots include the true classification boundary of the rotated sine function plotted as the solid black line.
+The training data are colored by the observed response variable ($y$), and the testing data are colored by \kge{random forest \sout{the}} prediction probabilities \kge{\sout{from the random forest model ($\hat{y}$)}}.
+The random forest \kge{\sout{model}} misclassifies \Sexpr{dim(sine_data_test %>% filter(y != rfpred))[1]} points\kge{, which are all located near \sout{on}} the classification boundary.
+These are identified by \kge{open} circles in \autoref{fig:sine-plot-data}.
+
+\kgc{I moved this paragraph.
+Figure 3 had not been introduced yet, so I think it fits better here.} \hh{From \kge{\sout{the plots in}} \autoref{fig:sine-plot-data}}\kge{,} \hh{we see that the global relationship between response $y$ and features $x_1$ and $x_2$ is linear: the probability for label blue increases with the difference between features $x_2$ and $x_1$.
 Locally, the relationship between $y$ and features $x_2$ and $x_1$ varies a lot more around the line of identity.
@@
 
-The dataset is divided into a training set of \Sexpr{dim(sine_data_train)[1]} observations and a testing set of \Sexpr{dim(sine_data_test)[1]} observations.
-A random forest model is fit using the R package \emph{randomForest} (version \Sexpr{packageVersion("randomForest")}) \citep{liaw:2002} with the default settings.
-The model is applied to the test set to obtain predictions.
-\autoref{fig:sine-plot-data} shows scatterplots of $x_2$ versus $x_1$ from the training data (left) and the testing data (right).
-Both plots include the true classification boundary of the rotated sine function plotted as the solid black line.
-The training data are colored by the observed response variable ($y$), and the testing data are colored by the prediction probabilities from the random forest model ($\hat{y}$).
-The random forest model misclassifies \Sexpr{dim(sine_data_test %>% filter(y != rfpred))[1]} points on the classification boundary.
-These are identified by circles in \autoref{fig:sine-plot-data}.
+\kgc{I moved some paragraphs around here.
+It didn't read smoothly to me.
+I also added a sentence similar to one I had written before and you removed that I had included as an exposition sentence.
+Without it, I think it's confusing to jump into listing the tuning parameters we use without an overview of what is done.
+See what you think of it now.} \kge{We apply LIME using six sets of tuning parameters to all observations in the \data \ test set to observe variability across tuning parameters.} A quantile bin based simulation method is used for five of the LIME applications with the number of bins varying from 2 to 6 by application.
+We use 6 bins as the maximum, \hh{because the complexity of the explanations increases with the number of bins.} The sixth application of LIME uses a kernel density simulation method.
+The default methods for feature selection (forward selection) and the computation of the weights (Gower distance raised to an exponent of 1) are used for all applications.
+\kge{(See Appendix~\ref{lime-details} for more details on the tuning parameters.)}
 
@@
 Misclassified points are often of interest to explain since they may provide information about ways to improve the model.
-For the introduction of the other three plots, we use all observations in the \data test data as points of interest.
-
-\hh{All runs of LIME in this paper are executed in}
-a forked version\footnote{https://github.com/goodekat/lime} of the development version of the R package \emph{lime} (\Sexpr{packageVersion("lime")}) \citep{pedersen:2020}. 
-The forked version \hh{is functionally indistinguishable from Pedersen's implementation}\kge{,} \hh{but it} allows us to export internal values \hh{relevant for an assessment of the explainer}. 
-The R package \emph{limeaid} \footnote{Available on GitHub at https://github.com/goodekat/limeaid} (\Sexpr{packageVersion("limeaid")}) implements diagnostic plots based on the output of the altered version of \emph{lime}.
+For the introduction of the other \kge{two \sout{three}} plots, we \kge{consider the LIME explanations for \sout{use}} all observations in the \data \ test data.
+\kge{\sout{as points of interest.}} \kgc{XXX This is where I left off XXX}
 
@@
 
-A quantile bin based simulation method is used for five of the LIME applications with the number of bins varying from 2 to 6 by application.
-We use 6 bins as the maximum, \hh{because the complexity of the explanations increases with  the number of bins.} The sixth application of LIME uses a kernel density simulation method.
-The default methods for feature selection (forward selection) and the computation of the weights (Gower distance raised to an exponent of 1) are used for all applications.
-
-\subsection{A LIME explanation}
-\hh{XXX I've just pulled the description of the left hand side of figure 4 out of the next section.} \kgc{Okay.} To demonstrate a LIME explanation, we focus on the misclassified point indicated in Figure \ref{fig:sine-plot-data} by the diamond as the prediction of interest.
+%\subsection{A LIME explanation}
+
+\paragraph{An Example LIME Explanation}
+
+\kgc{I really like the idea of separating the description of the \emph{lime} figure from the explanation scatterplot, but the more I think about it, I don't like that it get it's own sub-section.
+I think it would be nicer to allocate the sub-sections to the visual diagnostic plots.
+Instead, I switched to using a heading like you created for introducing the sine data.
+I also changed the wording of the heading a bit.
+What do you think?
+Another option would be to drop the heading altogether and just say, "Here is an example of a LIME explanation...but it is not enough..."}
+
+\hh{XXX I've just pulled the description of the left hand side of figure 4 out of the next section.} To demonstrate a LIME explanation, we focus on the misclassified point indicated in Figure \ref{fig:sine-plot-data} by the diamond as the prediction of interest.
 The left plot in Figure \ref{fig:sine-exp-scatter} shows a visualization of the explanation for the prediction of interest as suggested by Ribeiro et al and implemented in the \emph{lime} R package.
@@
 
-The explanation scatterplot shows issues with a definition of locality and an oversimplification of the random forest model.
+The explanation scatterplot shows issues with a definition of locality and an oversimplification of the random forest \kge{\sout{model}}.
 LIME does provide an explanation for the prediction of interest, which makes sense based on the quantile bins used.
@@
 Based on high-resolution topological scans of land engraved areas \citet{hare:2016} obtain signatures of striations from two bullet lands (\autoref{fig:signatures}).
-Nine features quantifying the similarity of signatures, such as the cross-correlation function, the distance between signatures, and the number of matching striae, are extracted and used to train a random forest model (available in the \emph{bulletxtrctr} R package) to determine the probability of a comparison resulting from the same source (matching signatures) or from different sources (non-matching signatures).
+Nine features quantifying the similarity of signatures, such as the cross-correlation function, the distance between signatures, and the number of matching striae, are extracted and used to train a random forest \kge{\sout{model}} (available in the \emph{bulletxtrctr} R package) to determine the probability of a comparison resulting from the same source (matching signatures) or from different sources (non-matching signatures).
 The model was trained on a set of scans of bullets from the James Hamby Consecutively Rifled Ruger Barrel Study \citep{hamby:2009}, which includes \Sexpr{dim(bullet_train)[1]} land-to-land comparisons.
@@
 
-We apply the random forest model from \citet{hare:2016} to another set of bullets from the Hamby study with \Sexpr{dim(bullet_test)[1]} rows of land comparisons.
+We apply the random forest \kge{\sout{model}} from \citet{hare:2016} to another set of bullets from the Hamby study with \Sexpr{dim(bullet_test)[1]} rows of land comparisons.
 We first consider a global visualization of the relationship between the random forest predictions and the model features by creating a parallel coordinate plot of the training data (top facet) and testing data (bottom facets) predictions (\autoref{fig:bullet-plot-rfpcp}).
@@
 The explanation scatterplots allow for a comparison of the explainer model to the complex model.
-The examples in this paper show cases where the explainer model bins do not accurately capture the classification boundaries near the predictions of interest of the random forest models by oversimplifying the model (Figures \ref{fig:sine-exp-scatter} and \ref{fig:bullet-eois}).
+The examples in this paper show cases where the explainer model bins do not accurately capture the classification boundaries near the predictions of interest of the random forest\kge{s \sout{models}} by oversimplifying the model (Figures \ref{fig:sine-exp-scatter} and \ref{fig:bullet-eois}).
 Using less bins would clearly not help improve the faithfulness of the explainer model in these examples, and while an increase in bins would lead to a finer resolution of the random forest classification boundaries, interpretability of the explainer model would quickly be lost.

### 2020-08-26 paper.Rnw
removing color

@@
 However, the quality of the resulting explanations relies on how well the explainer model captures the black-box model in a specified local region.
-Here we introduce three visual diagnostics to assess the quality of LIME explanations: (1) explanation scatterplot\kge{s}, (2) assessment metric plot\kge{s}, and (3) feature heatmap\kge{s}.
+Here we introduce three visual diagnostics to assess the quality of LIME explanations: (1) explanation scatterplots, (2) assessment metric plots, and (3) feature heatmaps.
 We apply the visual diagnostics to a forensics bullet matching dataset to show examples where LIME explanations depend on the tuning parameters and the explainer model oversimplifies the black-box model.
-Our examples raise concerns about claims made \kge{of \sout{about}} LIME \citep{ribeiro:2016} that are similar to other criticisms in the literature (\citet{alvarezmelis:2018}, \citet{laugel:2018}, and \citet{molnar:2019}).}
+Our examples raise concerns about claims made of LIME \citep{ribeiro:2016} that are similar to other criticisms in the literature \citep{alvarezmelis:2018, laugel:2018, molnar:2019}.}
 \keywords{LIME, black-box models, interpretability, diagnostics}
@@
 Model interpretability allows for the understanding and assessment of how a model produces predictions.
-The lack of the ability to understand and assess a model makes it difficult to trust the model, especially in areas with high stakes decisions such as \kge{medical \sout{health care}} and forensics science\kge{s}.
+The lack of the ability to understand and assess a model makes it difficult to trust the model, especially in areas with high stakes decisions such as medical and forensics sciences.
 The increased use of machine learning models in applications and the introduction of the General Data Protection Regulation (GDPR) in 2018 \citep{goodman:2016} has resulted in a dramatic increase in explainable machine learning research, which focuses on developing ways to explain output from machine learning algorithms.
@@
 Numerous methods have been proposed to provide explanations for black-box model predictions \citep{gilpin:2018, guidotti:2018, ming:2017, molnar:2019}.
-\kgc{I just took out the Mohseni reference since it is not peer reviewed.
+%\hh{sounds good!}\kgc{I just took out the Mohseni reference since it is not peer reviewed.
 I think the other four should give enough of an idea of places to look for overviews on EML.
-Does that seem okay to you?} Some are specific to one type of model (e.g.
-\citep{simonyan:2013} and \citep{urbanek:2008}), \kgc{I switched to a reference to Urbanek's visualizations since the Welling paper was not peer reviewed.
+Does that seem okay to you?}
+Some are specific to one type of model (e.g.
+\citep{simonyan:2013} and \citep{urbanek:2008}), %\hh{good!}\kgc{I switched to a reference to Urbanek's visualizations since the Welling paper was not peer reviewed.
 Is this better?} %\citep{welling:2016}),
@@
 \citep{fisher:2018} and \citep{strumbelj:2014}).
-In this paper, we focus on \hh{one specific} model-agnostic method: LIME \citep{ribeiro:2016} \kge{(}\hh{introduced by Ribeiro, Singh, and Guestrin in 2016}\kge{)}.
+In this paper, we focus on one specific model-agnostic method: LIME \citep{ribeiro:2016}.
+%introduced by Ribeiro, Singh, and Guestrin in 2016.
 \kgc{Do we need the addition of when the paper was introduced here since the statement is made at the beginning of Section 2, or did you intend to remove that sentence?}
@@
 The size and opacity of the circular points indicate the weight assigned based on the distance to the prediction of interest computed using the inverse of the Gower distance metric raised to the power of \Sexpr{good_gower_power}.
-The black lines \kge{represent \sout{are}} a weighted ridge regression model used as an explainer model that reasonably captures the relationship between the black-box predictions and the features in a local region around the prediction of interest.
+The black lines represent  a weighted ridge regression model used as an explainer model that reasonably captures the relationship between the black-box predictions and the features in a local region around the prediction of interest.
 That is, the explainer is faithful to the complex model and produces a reasonable explanation that Feature 1 plays a more important role in the prediction of interest than Feature 2 since the magnitude of the slope associated with Feature 1 is larger.}
@@
 A ridge regression model is fit to the same hypothetical black-box model predictions and predictor variables as in \autoref{fig:concept-plot-good}, but the weights are computed using a Gower exponent of 1.
-The explainer model is unfaithful to the complex model in \kge{any \sout{the}} immediate neighborhood of the prediction of interest.}
+The explainer model is unfaithful to the complex model in any immediate neighborhood of the prediction of interest.}
 \label{fig:concept-plot-bad}
@@
 \autoref{fig:concept-plot-good} provides a visualization of this conceptual understanding of LIME.
-The two plots show the predictions from a hypothetical black-box model plotted against the two \kge{hypothetical model} predictor variables \kge{\sout{used to fit the hypothetical model}}.
-The diamond shaped points represent \kge{\sout{a} the location of the} prediction of interest.
+The two plots show the predictions from a hypothetical black-box model plotted against the two hypothetical model predictor variables.
+The diamond shaped points represent  the location of the prediction of interest.
 A Gower distance metric \citep{gower:1971} is used to define locality such that the size of the points represent the inverse of the Gower distance raised to some value and indicate the proximity to the prediction of interest.
-\hh{In the example of \autoref{fig:concept-plot-good}}, an exponent of \Sexpr{good_gower_power} is used to emphasize a very local region around the prediction of interest.
-A ridge regression model weighted by the proximity values is used as the explainer model with the black-box predictions as the response variable and standardized versions of \hh{two features in the data} as predictor variables.
+In the example of \autoref{fig:concept-plot-good}, an exponent of \Sexpr{good_gower_power} is used to emphasize a very local region around the prediction of interest.
+A ridge regression model weighted by the proximity values is used as the explainer model with the black-box predictions as the response variable and standardized versions of two features in the data as predictor variables.
 Standardized features allow direct comparisons of the model coefficients.
@@
 Here, the explainer model is plotted with Feature 2 fixed at the observed value of the prediction of interest.
-The explainer model captures the relationship in \kge{an \sout{the}} immediate neighborhood around the prediction of interest with a slope of \Sexpr{coefs_data %>% filter(case == "good", feature == "Feature 1") %>% pull(slope) %>% round(3)}.
-The plot on the right shows no global or local relationship\kge{s} between the black-box predictions and Feature 2.
+The explainer model captures the relationship in an  immediate neighborhood around the prediction of interest with a slope of \Sexpr{coefs_data %>% filter(case == "good", feature == "Feature 1") %>% pull(slope) %>% round(3)}.
+The plot on the right shows no global or local relationships between the black-box predictions and Feature 2.
 Here, the explainer model is plotted with Feature 1 set as the observed value of the prediction of interest, and it has an appropriately small slope of \Sexpr{coefs_data %>% filter(case == "good", feature == "Feature 2") %>% pull(slope) %>% round(3)}.
@@
 However, a practical implementation of LIME is not straightforward, and research is being done to improve the procedure \citep{laugel:2018}.
-The current implementations of LIME\footnote{https://github.com/marcotcr/lime}\kgc{Is there a better way to cite a Python package?} \citep{pedersen:2020} offer various tuning parameters (see Section \ref{background}) that affect the explainer model and ultimately, the explanation.
+The current implementations of LIME\footnote{https://github.com/marcotcr/lime}\kgc{Is there a better way to cite a Python package?}\hh{might be good to model the python package reference after the R package references, have a loog at reference limepy}  \citep{pedersen:2020} offer various tuning parameters (see Section \ref{background}) that affect the explainer model and ultimately, the explanation.
 Since the explainer model is an approximation of the complex model and not a direct interpretation, the explanations produced by an explainer model are subject to the quality of the approximation.
@@
 This causes the observations that are further away from the prediction of interest to be given larger weights than before.
-In \autoref{fig:concept-plot-good}, the explainer model captures the relationship between the black-box predictions in \kge{an \sout{the}} immediate neighborhood of the prediction of interest.
+In \autoref{fig:concept-plot-good}, the explainer model captures the relationship between the black-box predictions in an immediate neighborhood of the prediction of interest.
 This cannot be said of the explainer model in \autoref{fig:concept-plot-bad}.
 In addition, the magnitude of the slope associated with Feature 2  (\Sexpr{coefs_data %>% filter(case == "bad", feature == "Feature 2") %>% pull(slope) %>% round(3) %>% abs()}) is larger than that of Feature 1 (\Sexpr{coefs_data %>% filter(case == "bad", feature == "Feature 1") %>% pull(slope) %>% round(3) %>% abs()}).
-Thus, this explainer model actually provides a misleading explanation that Feature 2 plays a more important role in \kge{the} predict\kge{ion\sout{ing the observation}} of interest.
+Thus, this explainer model actually provides a misleading explanation that Feature 2 plays a more important role in the prediction of interest.
 
@@
 We introduce the suggested diagnostic plots in Section \ref{diagnostics}.
-Then in Section \ref{application}, we demonstrate the use of the diagnostics to assess LIME explanations for a random forest \kge{\sout{model}} fit to a forensics bullet matching dataset.
+Then in Section \ref{application}, we demonstrate the use of the diagnostics to assess LIME explanations for a random forest  fit to a forensics bullet matching dataset.
 Section \ref{discussion} concludes with a discussion on extensions and limitations of the diagnostic plots and concerns about LIME in regards to the claims made by \citet{ribeiro:2016} brought about by the visualization examples in this paper that agree with \citet{alvarezmelis:2018}, \citet{laugel:2018}, and \citet{molnar:2019}.
-\kgc{I moved the following two sentences here from Section 2, so that it refers to the whole paper more clearly.} \hh{All runs of LIME in this paper are executed in} a forked version\footnote{https://github.com/goodekat/lime} of the development version of the R package \emph{lime} (\Sexpr{packageVersion("lime")}) \citep{pedersen:2020}.
-The forked version \hh{is functionally indistinguishable from Pedersen's implementation}\kge{,} \hh{but it} allows us to export internal values \hh{relevant for an assessment of the explainer}.
-%The R package \emph{limeaid} \footnote{Available on GitHub at https://github.com/goodekat/limeaid} (\Sexpr{packageVersion("limeaid")}) implements diagnostic plots based on the output of the altered version of \emph{lime}.
-The diagnostic plots included in this paper are created using the R package \emph{limeaid} \citep{goode:2020}.
+%\kgc{I moved the following two sentences here from Section 2, so that it refers to the whole paper more clearly.} \hh{I agree, that improves the flow!}
+
+All runs of LIME in this paper are executed in a forked version\footnote{https://github.com/goodekat/lime} of the development version of the R package \emph{lime} (\Sexpr{packageVersion("lime")}) \citep{pedersen:2020}.
+The forked version is functionally indistinguishable from Pedersen's implementation, but allows us to export internal values relevant for an assessment of the explainerThe diagnostic plots included in this paper are created using the R package \emph{limeaid} \citep{goode:2020}.
 
@@
 
-LIME was introduced in 2016 by \citet{ribeiro:2016}.
+%LIME was introduced in 2016 by \citet{ribeiro:2016}.
 \kgc{You added this sentence to Section 1.
 Do you want it removed from here or there?
-If it is removed here, the next sentence will need to be changed.} The authors provide an implementation of LIME in a Python package\footnote{https://github.com/marcotcr/lime}.
-\kgc{(Again, is there a better way to cite a Python package?)} An adaption of the Python package in R has been implemented and made available by Thomas Lin-Pedersen \citep{pedersen:2020}.
+If it is removed here, the next sentence will need to be changed.}
+\citet{ribeiro:2016} provide an implementation of LIME in a Python package \cite{limepy}.
+An adaption of the Python package in R has been implemented and made available by Thomas Lin-Pedersen \citep{pedersen:2020}.
 The discussion of parameter choices and implementation details of LIME in this paper are based on the R package.
 
-The general form of the LIME algorithm can be divided into three steps (see also \citep{laugel:2018}):
+The general form of the LIME algorithm can be divided into three steps  \citep[see also]{laugel:2018}:
 
@@
 there are too many variables in the model), it is clear that the assumption of interpretability is violated.
-The other three assumptions are not as easy to assess\kge{, and} %--
-for those\kge{,} we suggest the use of diagnostic plots.
+The other three assumptions are not as easy to assess, and %--
+for those, we suggest the use of diagnostic plots.
 
@@
 The true classification boundary is shown as the solid black line in both plots.
-The color of the training data \kge{\sout{points}} represents the value of the observed response variable ($y$).
-The color of the testing data \kge{\sout{points}} represents the random forest probability that an observation belongs to the category of blue \kge{\sout{($\hat{y}$)}}.
+The color of the training data  represents the value of the observed response variable ($y$).
+The color of the testing data  represents the random forest probability that an observation belongs to the category of blue.
 The \Sexpr{dim(sine_data_test %>% filter(y != rfpred))[1]} cases that are misclassified by the random forest are identified by black circles.
@@
 
-To demonstrate the \kge{visual diagnostics \sout{visualizations}}, we generate an example dataset that will be referred to as the \data.
+To demonstrate the visual diagnostics, we generate an example dataset that will be referred to as the \data.
 The \data \ contains \Sexpr{dim(sine_data)[1]} observations with three features and one response variable.
@@
 Note that due to the creation of $y$ in this manner, $y$ is dependent on $x_1$ and $x_2$ and independent of $x_3$.
-The dataset is divided into \kge{training and testing sets of \Sexpr{dim(sine_data_train)[1]} and \Sexpr{dim(sine_data_test)[1]} observations, respectively.
-\sout{a training set of \Sexpr{dim(sine_data_train)[1]} observations and a testing set of \Sexpr{dim(sine_data_test)[1]} observations.}} A random forest \kge{\sout{model}} is fit using the R package \emph{randomForest} (version \Sexpr{packageVersion("randomForest")}) \citep{liaw:2002} with the default settings.
+The dataset is divided into training and testing sets of \Sexpr{dim(sine_data_train)[1]} and \Sexpr{dim(sine_data_test)[1]} observations, respectively.
+A random forest  is fit using the R package \emph{randomForest} (version \Sexpr{packageVersion("randomForest")}) \citep{liaw:2002} with the default settings.
 The model is applied to the test set to obtain predictions.
@@
 Both plots include the true classification boundary of the rotated sine function plotted as the solid black line.
-The training data are colored by the observed response variable ($y$), and the testing data are colored by \kge{random forest \sout{the}} prediction probabilities \kge{\sout{from the random forest model ($\hat{y}$)}}.
-The random forest \kge{\sout{model}} misclassifies \Sexpr{dim(sine_data_test %>% filter(y != rfpred))[1]} points\kge{, which are all located near \sout{on}} the classification boundary.
-These are identified by \kge{open} circles in \autoref{fig:sine-plot-data}.
-
-\kgc{I moved this paragraph.
-Figure 3 had not been introduced yet, so I think it fits better here.} \hh{From \kge{\sout{the plots in}} \autoref{fig:sine-plot-data}}\kge{,} \hh{we see that the global relationship between response $y$ and features $x_1$ and $x_2$ is linear: the probability for label blue increases with the difference between features $x_2$ and $x_1$.
+The training data are colored by the observed response variable ($y$), and the testing data are colored by random forest  prediction probabilities.
+The random forest  misclassifies \Sexpr{dim(sine_data_test %>% filter(y != rfpred))[1]} points, which are all located near  the classification boundary.
+These are identified by open circles in \autoref{fig:sine-plot-data}.
+
+%\kgc{I moved this paragraph. Figure 3 had not been introduced yet, so I think it fits better here.}
+\hh{From these scatterplots we also} see that the global relationship between response $y$ and features $x_1$ and $x_2$ is linear: the probability for label blue increases with the difference between features $x_2$ and $x_1$.
 Locally, the relationship between $y$ and features $x_2$ and $x_1$ varies a lot more around the line of identity.
 Here, the relationship is determined by the sine waves.
-However, the sine is a good-natured function that can be approximated well linearly} \kge{in local regions}.
-
-\kgc{I moved some paragraphs around here.
+However, the sine is a good-natured function that can be approximated well linearly in local regions.
+
+%\kgc{I moved some paragraphs around here.
 It didn't read smoothly to me.
@@
 Without it, I think it's confusing to jump into listing the tuning parameters we use without an overview of what is done.
-See what you think of it now.} \kge{We apply LIME using six sets of tuning parameters to all observations in the \data \ test set to observe variability across tuning parameters.} A quantile bin based simulation method is used for five of the LIME applications with the number of bins varying from 2 to 6 by application.
-We use 6 bins as the maximum, \hh{because the complexity of the explanations increases with the number of bins.} The sixth application of LIME uses a kernel density simulation method.
+See what you think of it now.}
+We apply LIME using six sets of tuning parameters to all observations in the \data \ test set to observe variability across tuning parameters.
+A quantile bin based simulation method is used for five of the LIME applications with the number of bins varying from 2 to 6 by application.
+We use 6 bins as the maximum, because the complexity of the explanations increases with the number of bins.
+The sixth application of LIME uses a kernel density simulation method.
 The default methods for feature selection (forward selection) and the computation of the weights (Gower distance raised to an exponent of 1) are used for all applications.
-\kge{(See Appendix~\ref{lime-details} for more details on the tuning parameters.)}
+(See Appendix~\ref{lime-details} for more details on the tuning parameters.)
 
@@
 Misclassified points are often of interest to explain since they may provide information about ways to improve the model.
-For the introduction of the other \kge{two \sout{three}} plots, we \kge{consider the LIME explanations for \sout{use}} all observations in the \data \ test data.
-\kge{\sout{as points of interest.}} \kgc{XXX This is where I left off XXX}
+For the introduction of the other two  plots, we consider the LIME explanations for  all observations in the \data \ test data.
+\kgc{XXX This is where I left off XXX}
 

### 2020-08-26 paper.Rnw
small changes

@@
 Numerous methods have been proposed to provide explanations for black-box model predictions \citep{gilpin:2018, guidotti:2018, ming:2017, molnar:2019}.
-%\hh{sounds good!}\kgc{I just took out the Mohseni reference since it is not peer reviewed.
-I think the other four should give enough of an idea of places to look for overviews on EML.
-Does that seem okay to you?}
 Some are specific to one type of model (e.g.
-\citep{simonyan:2013} and \citep{urbanek:2008}), %\hh{good!}\kgc{I switched to a reference to Urbanek's visualizations since the Welling paper was not peer reviewed.
-Is this better?} %\citep{welling:2016}),
-and others are model-agnostic (e.g.
+\citep{simonyan:2013} and \citep{urbanek:2008}), and others are model-agnostic (e.g.
 \citep{fisher:2018} and \citep{strumbelj:2014}).
 In this paper, we focus on one specific model-agnostic method: LIME \citep{ribeiro:2016}.
-%introduced by Ribeiro, Singh, and Guestrin in 2016.
-\kgc{Do we need the addition of when the paper was introduced here since the statement is made at the beginning of Section 2, or did you intend to remove that sentence?}
 
@@
 However, a practical implementation of LIME is not straightforward, and research is being done to improve the procedure \citep{laugel:2018}.
-The current implementations of LIME\footnote{https://github.com/marcotcr/lime}\kgc{Is there a better way to cite a Python package?}\hh{might be good to model the python package reference after the R package references, have a loog at reference limepy}  \citep{pedersen:2020} offer various tuning parameters (see Section \ref{background}) that affect the explainer model and ultimately, the explanation.
+The current implementations of LIME \citep{ribeiro:2020} \kgc{Is there a better way to cite a Python package?} \hh{might be good to model the python package reference after the R package references, have a loog at reference limepy} \kgc{I kept thinking about this, and since the Python pakcgae doesn't have a manual, I ended up combining your limepy reference with the second second suggestion from https://academia.stackexchange.com/questions/14010/how-do-you-cite-a-github-repository.
+For now, I listed Ribeiro as the author, because he is the main contributor, but there are 40 other contributors to the package.
+Is it okay to just list Ribeiro?} \citep{pedersen:2020} offer various tuning parameters (see Section \ref{background}) that affect the explainer model and ultimately, the explanation.
 Since the explainer model is an approximation of the complex model and not a direct interpretation, the explanations produced by an explainer model are subject to the quality of the approximation.
@@
 Section \ref{discussion} concludes with a discussion on extensions and limitations of the diagnostic plots and concerns about LIME in regards to the claims made by \citet{ribeiro:2016} brought about by the visualization examples in this paper that agree with \citet{alvarezmelis:2018}, \citet{laugel:2018}, and \citet{molnar:2019}.
-%\kgc{I moved the following two sentences here from Section 2, so that it refers to the whole paper more clearly.} \hh{I agree, that improves the flow!}
-
-All runs of LIME in this paper are executed in a forked version\footnote{https://github.com/goodekat/lime} of the development version of the R package \emph{lime} (\Sexpr{packageVersion("lime")}) \citep{pedersen:2020}.
-The forked version is functionally indistinguishable from Pedersen's implementation, but allows us to export internal values relevant for an assessment of the explainerThe diagnostic plots included in this paper are created using the R package \emph{limeaid} \citep{goode:2020}.
+
+All runs of LIME in this paper are executed in a forked version\footnote{https://github.com/goodekat/lime} of the development version of the R package \emph{lime} (version \Sexpr{packageVersion("lime")}) by \kge{\citet{pedersen:2020}}.
+The forked version is functionally indistinguishable from \kge{\citeauthor{pedersen:2020}'s} implementation but allows us to export internal values relevant for an assessment of the explainer.
+The diagnostic plots included in this paper are created using the R package \emph{limeaid} \citep{goode:2020}.
 
@@
 
-%LIME was introduced in 2016 by \citet{ribeiro:2016}.
-\kgc{You added this sentence to Section 1.
-Do you want it removed from here or there?
-If it is removed here, the next sentence will need to be changed.}
 \citet{ribeiro:2016} provide an implementation of LIME in a Python package \cite{limepy}.
@@
 
-The general form of the LIME algorithm can be divided into three steps  \citep[see also]{laugel:2018}:
+The general form of the LIME algorithm can be divided into three steps \citep[see also][]{laugel:2018}:
 
@@
 there are too many variables in the model), it is clear that the assumption of interpretability is violated.
-The other three assumptions are not as easy to assess, and %--
-for those, we suggest the use of diagnostic plots.
+The other three assumptions are not as easy to assess, and for those, we suggest the use of diagnostic plots.
 
@@
 
-%\kgc{I moved this paragraph. Figure 3 had not been introduced yet, so I think it fits better here.}
-\hh{From these scatterplots we also} see that the global relationship between response $y$ and features $x_1$ and $x_2$ is linear: the probability for label blue increases with the difference between features $x_2$ and $x_1$.
+From these scatterplots, we also see that the global relationship between response $y$ and features $x_1$ and $x_2$ is linear: the probability for label blue increases with the difference between features $x_2$ and $x_1$.
 Locally, the relationship between $y$ and features $x_2$ and $x_1$ varies a lot more around the line of identity.
@@
 
-%\kgc{I moved some paragraphs around here.
-It didn't read smoothly to me.
-I also added a sentence similar to one I had written before and you removed that I had included as an exposition sentence.
-Without it, I think it's confusing to jump into listing the tuning parameters we use without an overview of what is done.
-See what you think of it now.}
 We apply LIME using six sets of tuning parameters to all observations in the \data \ test set to observe variability across tuning parameters.
@@
 For the introduction of the other two  plots, we consider the LIME explanations for  all observations in the \data \ test data.
-\kgc{XXX This is where I left off XXX}
 

### 2020-08-26 paper.Rnw
small rewording

@@
 
-All runs of LIME in this paper are executed in a forked version\footnote{https://github.com/goodekat/lime} of the development version of the R package \emph{lime} (version \Sexpr{packageVersion("lime")}) by \kge{\citet{pedersen:2020}}.
+All runs of LIME in this paper are executed in a forked version\footnote{https://github.com/goodekat/lime} of the R package \emph{lime} (version \Sexpr{packageVersion("lime")}) by \kge{\citet{pedersen:2020}}.
 The forked version is functionally indistinguishable from \kge{\citeauthor{pedersen:2020}'s} implementation but allows us to export internal values relevant for an assessment of the explainer.

### 2020-08-26 paper.Rnw
small changes to references

@@
 The default methods for feature selection (forward selection) and the computation of the weights (Gower distance raised to an exponent of 1) are used for all applications.
-(See Appendix~\ref{lime-details} for more details on the tuning parameters.)
+(See Appendix~\ref{lime-details} for descriptions of the tuning parameters.)
 
@@
 I see what you mean now.} In that respect, the diagnostics shown for the \data\ and in the bullet example are representative of what is expected.
-But in cases where overplotting does become problematic, the user could either simply reduce the size of the simulations or use some well-studied binning techniques in the visualizations, as discussed for example in \citet{carr:1987} or \citet{gold}.
+But in cases where overplotting does become problematic, the user could either simply reduce the size of the simulations or use some well-studied binning techniques in the visualizations, as discussed for example in \citet{carr:1987} or \citet{unwin:2006}.
 

### 2020-08-27 paper.Rnw
edits (many more to add that are on a printed out version of the paper)

@@
 We apply LIME using six sets of tuning parameters to all observations in the \data \ test set to observe variability across tuning parameters.
-A quantile bin based simulation method is used for five of the LIME applications with the number of bins varying from 2 to 6 by application.
+A quantile bin based simulation method \kge{(samples are simulated uniformly from a specified number of quantile bins)} is used for five of the LIME applications with the number of bins varying from 2 to 6 by application.
 We use 6 bins as the maximum, because the complexity of the explanations increases with the number of bins.
-The sixth application of LIME uses a kernel density simulation method.
+\kge{Note that 4 quantile bins are the default method in \emph{lime}.} The sixth application of LIME uses a kernel density simulation method \kge{(samples are drawn from kernel density approximations of the feature distributions)}.
 The default methods for feature selection (forward selection) and the computation of the weights (Gower distance raised to an exponent of 1) are used for all applications.
@@
 @
-\caption{(left) Visualization from the \emph{lime} R package of the LIME explanation for the \data \ prediction of interest.
-The bars represent the explainer model coefficients.
-(right) \emph{Explanation Scatterplot}.
+\caption{(left) Visualization from the \emph{lime} R package of \kge{a} \sout{the} LIME explanation for the \data \ prediction of interest \kge{identified in \autoref{fig:sine-plot-data}}.
+\sout{The bars represent the explainer model coefficients.} (right) \emph{Explanation Scatterplot}.
 The points represent the simulated data colored by the random forest probabilities and sized by the assigned LIME weights.
@@
 
-\paragraph{An Example LIME Explanation}
+\paragraph{A Visual Representation of a LIME Explanation}
 
@@
 What do you think?
-Another option would be to drop the heading altogether and just say, "Here is an example of a LIME explanation...but it is not enough..."}
-
-\hh{XXX I've just pulled the description of the left hand side of figure 4 out of the next section.} To demonstrate a LIME explanation, we focus on the misclassified point indicated in Figure \ref{fig:sine-plot-data} by the diamond as the prediction of interest.
-The left plot in Figure \ref{fig:sine-exp-scatter} shows a visualization of the explanation for the prediction of interest as suggested by Ribeiro et al and implemented in the \emph{lime} R package.
-The figure shows that the random forest returned a probability of \Sexpr{round(sine_poi_lime_default$label_prob[1], 2)} that the observation of interest belongs to category blue {(denoted as the ``label" in the figure).The lengths of the bars represent the explainer model coefficients associated with the indicator variables chosen by LIME as important.
-The color of the bar denotes the sign of the coefficient and whether the feature supports or contradicts a random forest classification of `blue'.
-The "explanation fit" value is the deviance ratio from the R package \emph{glmnet} \citep{simon:2011} for a ridge regression model.
+Another option would be to drop the heading altogether and flow into the next paragraph.} \hh{XXX I've just pulled the description of the left hand side of figure 4 out of the next section.}
+
+\kge{Before introducing the visual diagnostics, let us consider a commonly used visualization of a LIME explanation that is shown in Figure \ref{fig:sine-exp-scatter} (left).
+The plot is created using the \emph{lime} R package and provides a visual representation of a LIME explanation for the prediction of interest indicated in \autoref{fig:sine-plot-data} (when 4 quantile bins are used to simulate the data).} \sout{To demonstrate a LIME explanation, we focus on the misclassified point indicated in Figure \ref{fig:sine-plot-data} by the diamond as the prediction of interest.
+The left plot in Figure \ref{fig:sine-exp-scatter} shows a visualization of the explanation for the prediction of interest as suggested by Ribeiro et al and implemented in the \emph{lime} R package.}
+
+The \kge{plot} \sout{figure} \kge{reports \Sexpr{round(sine_poi_lime_default$label_prob[1], 2)} as} \sout{shows that} the random forest \sout{returned a} probability \sout{of \Sexpr{round(sine_poi_lime_default$label_prob[1], 2)}} that the observation of interest belongs to category blue {(denoted as the ``label" in the \kge{plot \sout{figure}}).
+The lengths of the bars represent the \kge{\sout{explainer model}} coefficients \kge{from a ridge regression model (the explainer model) fit using the R package \emph{glmnet} \citep{simon:2011}} associated with the indicator variables chosen \kge{via feature selection \sout{by LIME as important}}.
+The color of \kge{a \sout{the}} bar denotes the sign of the coefficient and whether the feature "supports" or "contradicts" a random forest classification of `blue'.
+The "explanation fit" \kge{\sout{value}} is the deviance ratio from \kge{\sout{the R package}} \emph{glmnet} \kge{\sout{\citep{simon:2011} for a ridge regression model}}.
 In other words, this is the $R^2$ value associated with the explainer model.
 In this case, it is \Sexpr{round(sine_poi_lime_default$model_r2[1], 2)} suggesting that the explainer model is not a good linear fit.
-However, it is commonly accepted that $R^2$ has limitations for assessing the quality of fit of a model \citep{sapra:2014}, and it should not be used as the only metric in a model assessment.
+However, it is commonly accepted that $R^2$ has limitations for assessing the quality of fit of a model \citep{sapra:2014}\kge{\sout{,}} and \kge{\sout{it}} should not be used as the only metric in a model assessment.
 
@@
 A random forest classification of blue is supported by the prediction of interest having a value of $x_2$ that is greater than \Sexpr{str_split(sine_poi_lime_default$feature_desc[[1]], pattern = " ")[[1]][1]}, but the prediction of interest having a value of $x_1$ that is greater than \Sexpr{str_split(sine_poi_lime_default$feature_desc[[2]], pattern = " ")[[1]][1]} and less than or equal to \Sexpr{str_split(sine_poi_lime_default$feature_desc[[2]], pattern = " ")[[1]][5]} provides support against a classification of blue.
-\hh{Because the support for blue by the value of feature $x_1$ outweighs the support for red by the value of feature $x_2$, the overall LIME explanation favors a label of blue for the prediction of interest.} %Since the weight associated with $x_2$ has a larger magnitude than the weight associated with $x_1$, LIME explains that the $x_1$ and $x_2$ locations of the prediction of interest provide more support for a random forest classification of blue over red.
-This explanation agrees with the random forest probability of \Sexpr{sine_poi_lime_default$label_prob[1]} for blue.
+\kge{Since the weight associated with $x_2$ has a larger magnitude than the weight associated with $x_1$, LIME explains that $x_2$ plays a more important role in the random forest prediction.} \kge{Additionally, consider that since the support for blue by $x_2$ outweights the support for red by $x_1$, the explainer model overall favors a label of blue for the prediction of interest, which} agrees with the random forest probability of \Sexpr{sine_poi_lime_default$label_prob[1]} for blue.
 Note that both models classify the observation incorrectly.
-Based on the plot \hh{on the left of \autoref{fig:sine-exp-scatter}} alone, it is not possible to make an informed assessment of the explanation.
+
+%\hh{Because the support for blue by the value of feature $x_1$ outweighs the support for red by the value of feature $x_2$, the overall LIME explanation favors a label of blue for the prediction of interest.} \kgc{I don't think this statement is quite right.}
+
+%Since the weight associated with $x_2$ has a larger magnitude than the weight associated with $x_1$, LIME explains that the $x_1$ and $x_2$ locations of the prediction of interest provide more support for a random forest classification of blue over red.
 
@@
 
+\kgc{I moved the next sentence here from the previous paragraph.} Based on the plot \hh{on the left of \autoref{fig:sine-exp-scatter}} alone, it is not possible to make an informed assessment of the explanation.
 \hh{For a further assessment of the explainer model}, we turn to an \emph{explanation scatterplot}: the \emph{explanation scatterplot} is a visual diagnostic for assessing the LIME claims of locality and fidelity for an individual explanation by juxtaposing the complex and explainer models in one plot.

### 2020-08-27 paper.Rnw
edits through 4.2

@@
 \kge{Before introducing the visual diagnostics, let us consider a commonly used visualization of a LIME explanation that is shown in Figure \ref{fig:sine-exp-scatter} (left).
-The plot is created using the \emph{lime} R package and provides a visual representation of a LIME explanation for the prediction of interest indicated in \autoref{fig:sine-plot-data} (when 4 quantile bins are used to simulate the data).} \sout{To demonstrate a LIME explanation, we focus on the misclassified point indicated in Figure \ref{fig:sine-plot-data} by the diamond as the prediction of interest.
+The plot is created using the \emph{lime} R package and provides a visual representation of a LIME explanation for the prediction of interest indicated in \autoref{fig:sine-plot-data}.
+In particular, the explanation was obtained using 4 quantile bins to simulate the data.} \kgc{I moved the next few sentences here from the sub-section.} In this scenario, LIME converts continuous predictor variables to indicator variables identifying whether the variable value falls in the same quantile bin as the prediction of interest or not.
+The indicator variables are used as the explainer model features.
+\sout{To demonstrate a LIME explanation, we focus on the misclassified point indicated in Figure \ref{fig:sine-plot-data} by the diamond as the prediction of interest.
 The left plot in Figure \ref{fig:sine-exp-scatter} shows a visualization of the explanation for the prediction of interest as suggested by Ribeiro et al and implemented in the \emph{lime} R package.}
@@
 \kgc{I moved the next sentence here from the previous paragraph.} Based on the plot \hh{on the left of \autoref{fig:sine-exp-scatter}} alone, it is not possible to make an informed assessment of the explanation.
-\hh{For a further assessment of the explainer model}, we turn to an \emph{explanation scatterplot}: the \emph{explanation scatterplot} is a visual diagnostic for assessing the LIME claims of locality and fidelity for an individual explanation by juxtaposing the complex and explainer models in one plot.
+\hh{For a further assessment of the explainer model}, we turn to an \emph{explanation scatterplot}: \sout{the \emph{explanation scatterplot} is} a visual diagnostic for assessing the LIME claims of locality and fidelity for an individual explanation by juxtaposing the complex and explainer models in one plot.
 The format of an explanation scatterplot depends on the LIME simulation method.
-We introduce the explanation scatterplot here under the \emph{lime} R package default method in which the data are simulated uniformly from four quantile bins.
-In this scenario, LIME converts continuous predictor variables to indicator variables identifying whether the variable value falls in the same quantile bin as the prediction of interest or not.
-The indicator variables are used as the explainer model features.
+We introduce the explanation scatterplot here under the \emph{lime} R package default method \kge{four quantile bins.} \sout{in which the data are simulated uniformly from four quantile bins.}
 
 The explanation scatterplot is built by plotting the LIME simulated data for the top two features identified by the explanation in a scatterplot and coloring these points by the  predictions from the complex model.
-The size of the points represents the weight assigned by LIME.
-\hh{In order to show the LIME results for the observation of interest, }
- lines \hh{are drawn on top of the points.
+The \kge{point} size \sout{of the points} represents the weight assigned by LIME.
+\hh{In order to show the LIME results for the observation of interest,} lines \hh{are drawn on top of the points.
 These lines } represent the boundaries of the indicator variables used to fit the explainer model.
-The color of the lines denote whether LIME indicates that a feature supports or contradicts a class prediction.
+The \kge{line} color \sout{of the lines} denote\kge{s} whether LIME indicates that a feature supports or contradicts a class prediction.
 Appendix \ref{exp-scatter_plus} addresses the explanation scatterplot formats in other LIME simulation scenarios.
 
-\hh{An explanation scatterplot} \sout{for the} \kge{associated with the LIME explanation depicted on the left in \autoref{fig:sine-exp-scatter}} \sout{example of the previous section} \hh{is shown on the right hand side of \autoref{fig:sine-exp-scatter}.} %The points are the simulated values of $x_2$ versus $x_1$ colored by the random forest predictions and sized by the proximity weight used to fit the ridge regression explainer model.
+\hh{An explanation scatterplot} \sout{for the} \kge{corresponding to the LIME explanation depicted on the left in \autoref{fig:sine-exp-scatter}} \sout{example of the previous section} \hh{is shown on the right hand side of \autoref{fig:sine-exp-scatter}.} %The points are the simulated values of $x_2$ versus $x_1$ colored by the random forest predictions and sized by the proximity weight used to fit the ridge regression explainer model.
 The explainer model is represented by the solid horizontal and vertical lines identifying the boundaries of the quantiles that contain the prediction of interest.
@@
 By juxtaposing the random forest predictions and the explainer model boundaries, we are able to assess the faithfulness and localness of the explainer model.
-First consider the claim of localness.
-The weights remain relatively high outside of the intersection of the two quantile bins suggesting that the LIME explanation is highly influenced by points outside of the bin containing the prediction of interest.
-While it is still difficult to say whether or not the claim of localness has been violated, it is possible to say that the weights assigned to the simulated data do not agree with the local region assigned by the intersection of the quantile bins.
-
-Now, consider the claim of faithfulness.
-Within the intersection of the $x_1$ and $x_2$ quantile bins, there are more random forest probabilities above 0.5.
+
+First, consider the claim of localness.
+The weights \kge{decay relatively slowly} \sout{remain relatively high} outside of the intersection of the two quantile bins suggesting that the LIME explanation is highly influenced by points outside of the bin\kge{s} containing the prediction of interest.
+\sout{While i} \kge{However,} it is \sout{still} difficult to say \kge{if} \sout{whether or not} the claim of localness has been violated\kge{, because a definition of a local region was not specified.
+Depending a the region a viewer considers to be local, an argument could be made in favor of or against a violation of localness.
+The explanation scatterplot raises awareness of the unclear definition of a local region with LIME.
+Nevertheless,} it is possible to say that the weights assigned to the simulated data do not \kge{capture} \sout{agree with} the local region \kge{identified} \sout{assigned} by the intersection of the quantile bins.
+
+\kgc{I tried rewriting this paragraph to make it less "technical".
+See what you think.} Now, consider the claim of faithfulness.
+\kge{It can be said that the majority of the points in the $x_2$ quantile support a prediction of blue, which is captured by the bar supporting a prediction of blue in LIME explanation, and a similar statement can be said about the $x_1$ quantile bin.
+These statements validate the explanation produced by LIME.
+However, the explanation scatterplot plot shows that the random forest does a good job of capturing the sine curve classification boundary by creating various sized rectangles with similar probabilities, which the LIME explanation does not pick up on.
+Thus, LIME does provide an explanation for the prediction, but it is a very poor explanation in terms of faithfulness to the random forest prediction regions.}
+
+\sout{Within the intersection of the $x_1$ and $x_2$ quantile bins, there are more random forest probabilities above 0.5 \kge{than below}.
 This indicates why the magnitude of the coefficient associated with $x_2$ is larger than that of $x_1$.
@@
 A more localized explanation is to say that the region around the prediction of interest shows that observations with $-0.3 < x_1 <= 2.5$ and $4.8 < x_2 <= 8.75$ are all assigned probabilities greater than 0.5.
-The procedure implemented by LIME is not flexible enough to capture either of these explanations.
-
-The explanation scatterplot shows issues with a definition of locality and an oversimplification of the random forest \kge{\sout{model}}.
+The procedure implemented by LIME is not flexible enough to capture either of these explanations.}
+
+\sout{The explanation scatterplot shows issues with a definition of locality and an oversimplification of the random forest \kge{\sout{model}}.
 LIME does provide an explanation for the prediction of interest, which makes sense based on the quantile bins used.
-However, the explanation scatterplot identifies that better explanations for the prediction of interest exist.
-It is difficult to assess linearity from an explanation scatterplot, but a residual plot of the explainer model could be used to check the linearity claim.
-See Appendix \ref{residual-plot} for the residual plot associated with the explanation considered in Figure \ref{fig:sine-exp-scatter} and shows a violation of the linearity claim.
-
-The \data \ explanation only includes two features.
+However, the explanation scatterplot identifies that better explanations for the prediction of interest exist.}
+
+It is difficult to assess linearity from \kge{this} \sout{an} explanation scatterplot, but a residual plot of the explainer model could be used to check the linearity claim.
+See Appendix \ref{residual-plot} for the residual plot associated with the explanation considered in Figure \ref{fig:sine-exp-scatter}, which shows a violation of the linearity claim.
+
+\kge{This example} \sout{The \data \ } explanation only includes two features.
 In situations where more than two features are included in a LIME explanation, the explanation scatterplots can be extended to a generalized pairs plot \citep{emerson:2013} that includes all pairwise combinations of features.
@@
 However, when applying LIME, the user selects the number of features to return in the explanation.
-In the \emph{lime} R package, \citet{pedersen:2020} encourage users to select less than 10 features to include in the explanation.
-As a result, specifying a small number of features to include in a LIME explanation makes it feasible to use generalized pairs plot of explanation scatterplots.
+In the \emph{lime} R package, \citet{pedersen:2020} encourage users to select less than 10 features \sout{to include in the explanation}.
+\kge{As long as a small number of features are returned in the LIME explanation,} \sout{As a result, specifying a small number of features to include in a LIME explanation makes} it \kge{is} feasible to use \kge{a} generalized pairs plot of explanation scatterplots.
+\kge{An example is shown in Section \ref{bullet-assess-ex}.}
 
@@
   geom_tile() +
-  labs(x = "Tuning Parameter",
+  labs(x = "Tuning Parameter Value",
        y = "Case",
@@
 \caption{Hypothetical examples of feature heatmaps in two possible situations.
-The heatmaps show the top feature chosen for 10 cases across 5 different sets of LIME tuning parameters.
-The color of the cell indicates the feature chosen by LIME.}
+The heatmaps show the top feature chosen for 10 cases across 5 different sets of \sout{LIME} tuning parameters.
+The color of the cell indicates the feature chosen by LIME.
+\kge{Situation 1 is the ideal, because the explanations are not dependent on tuning parameter values.}}
 \label{fig:concept-feat-heat}
@@
 \caption{\emph{Feature Heatmap}.
-An example feature heatmap of the explanations from the applications of LIME with different tuning parameters to the \data.
+An example feature heatmap of the explanations from the applications of LIME with different tuning parameters to the \data \ test set.
 The cases from the test set are plotted on the y-axis, and the tuning parameter values (simulation methods here) are included on the x-axis.
 The colors of the tiles indicate the feature selected by LIME for the corresponding case and tuning parameter value.
-The plot is faceted by the first features selected by LIME (top facet) and the second most important features (bottom facet).
-The column facets separate the kernel density method from the quantile bin methods.
+The plot is faceted by the first \kge{and second most important} features selected by LIME (top \kge{and bottom} facet\kge{s, respectively}) \sout{ and the second most important features (bottom facet).} \kge{The vertical facets separate the} \sout{The column facets separate the} kernel density method from the quantile bin methods.
 The vertical striping indicates that the LIME explanations are not consistent across tuning parameters.}
@@
 Explanations produced by LIME are likely to be affected by the choice of tuning parameters.
-An example of this is shown by Figures \ref{fig:concept-plot-good} and \ref{fig:concept-plot-bad} where the method used to weight the observations influenced the explanation.
-As of the time of writing this manuscript, we have encountered no recommendations for how to determine which method to use besides for the default settings in \emph{lime} \kgc{(confirm this)}.
-In order to compare the explanations produced by LIME using different tuning parameters, we visualize an overview the explanations in the \emph{feature heatmap} diagnostic plot.
-
-The feature heatmap uses colors to identify the features selected by LIME across tuning parameters for sets of explanations (referred to as cases here) faceted by the position of feature importance assigned by LIME.
+\sout{An} \kge{A hypothetical} example of this is shown by Figures \ref{fig:concept-plot-good} and \ref{fig:concept-plot-bad} where the method used to weight the observations influenced the explanation.
+As of the time of writing this manuscript, we have encountered no recommendations for how to \kge{specify the parameter values} \sout{determine which method to use} besides for the default settings in \emph{lime}.
+In order to compare the explanations produced by LIME using different tuning parameters \kge{and provide another perspective for assessing localness}, we visualize an overview \kge{of} the explanations \kge{with} \sout{in} the \emph{feature heatmap} diagnostic plot.
+
+The feature heatmap uses colors to identify the features selected by LIME \kge{across multiple predictions (referred to as cases here) and tuning paramter values} \sout{across tuning parameters for sets of explanations (referred to as cases here)} \kge{organized} \sout{faceted} by the \sout{position of} feature importance assigned by LIME.
 That is, for LIME applied with $t$ sets of tuning parameters to $n$ cases to select the $f$ top features, create $f$ heatmaps (one for each of the positions of importance determined by the magnitude of the explainer model coefficients) with the cases on the y-axis, the tuning parameters on the x-axis, and the cells colored by the feature chosen for the corresponding case and tuning parameter.
 Additional tuning parameters may also be included in the plot via facets.
-This plot is used assess the locality of the explanations and to compare results from different input options.
+\sout{This plot is used assess the locality of the explanations and to compare results from different input options.}
 
 Two hypothetical examples of feature heatmaps are included in \autoref{fig:concept-feat-heat}.
-The plots were created with the assumption that LIME is applied to select the top feature out of $p=8$ features for $n=10$ cases with $t=5$ sets of tuning parameters.
-Situation 1 shows an example where the features selected are consistent across tuning parameters within a case but vary across cases within a tuning parameter.
+The plots were created with the assumption that LIME is applied to select the top feature out of $p=\kge{4}$ \sout{8} features for $n=10$ cases with $t=5$ sets of tuning parameters.
+Situation 1 \kge{is} \sout{shows} an example where the features selected are consistent across tuning parameters within a case but vary across cases within a tuning parameter.
 This is the ideal situation, because the LIME explanations do not depend on the tuning parameters but do depend on the location of the observation in the feature space.
-Situation 2 shows an example where the features selected vary across tuning parameters within a case but are consistent across cases within a tuning parameter.
-This situation indicates that the features selected by LIME are dependent on the tuning parameters, and the explanations are not local because the same feature is chosen regardless of the case.
+Situation 2 \kge{is} \sout{shows} an example where the features selected vary across tuning parameters within a case but are consistent across cases within a tuning parameter.
+This situation indicates that the features selected by LIME are dependent on the tuning parameters, and the explanations \kge{may not be} \sout{are not} local, because the same feature is chosen regardless of the case.
 In practice, it is expected that the plot will exhibit a combination of these two situations.
 
-\autoref{fig:sine-feat-heat} shows the feature heatmap for the LIME applications to the 100 observations in the \data \ test set.
-The most important (top facet) and second most important (bottom facet) features are shown in this plot.
-For the quantile bins, the original features prior to the indicator variable transformation are included since it is obvious that different features would be selected when the sizes of the bins change.
+\autoref{fig:sine-feat-heat} shows \kge{a} \sout{the} feature heatmap for the LIME applications to the 100 observations in the \data \ test set.
+The most important \kge{and second most important features selected by lime are showin in the top and bottom facets, respectively.} \sout{(top facet) and second most important (bottom facet) features are shown in this plot.} For the quantile bins, the original features prior to the indicator variable transformation are included since it is obvious that different features would be selected when the sizes of the bins change.
 This figure shows that for kernel density and 2 quantile bins, LIME selects $x_1$ as the most important feature and $x_2$ as the second most important feature across all cases in the test set.
 These explanations are not local.
-There is variability in the features selected by LIME for 3 to 6 quantile bins.
-For these tuning parameters, there is a mix of horizontal and vertical stripes, which suggests a dependence on tuning parameters.
+There is variability in the features selected by LIME for 3 to 6 quantile bins \kge{suggesting more local explanations}.
+\sout{For these tuning parameters, there is a mix of horizontal and vertical stripes,} \kge{There are signs of vertical striping,} which suggests a dependence on tuning parameters.
 Note that the explanations from 3 and 5 quantile bins include the selection of the random noise variable ($x_3$) as an important variable in many predictions, which should not be the case.
@@
 Each horizontal facet corresponds to one of three metrics: average $R^2$, average fidelity, or MSEE.
-The LIME tuning parameter (simulation methods in this example) is plotted on the x-axis, and the metric values are shown on the y-axis.
+The LIME tuning parameter \kge{values} (simulation methods in this example) \kge{are} \sout{is} plotted on the x-axis, and the metric values are shown on the y-axis.
 The points are colored by rank (within a metric) indicating best to worst (dark to light).
-The kernel density simulation methods performs well according to all three metrics.}
+The kernel density simulation methods performs well \kge{across} \sout{according to} all three metrics.}
 \label{fig:sine-assess-metric}
@@
 
-Each metric presented below is computed on a set of LIME explanations obtained using the the same tuning parameters.
+Each metric presented below is computed on a \sout{set of} LIME explanations \kge{for a set of predictions} obtained using the \sout{the} same tuning parameters.
 Here we provide a high level description of the metrics.
@@
 
-\autoref{fig:sine-assess-metric} shows these metrics computed for each of the LIME applications to the \data \ test set.
+\autoref{fig:sine-assess-metric} shows \kge{an example assessment metric plot}.
+\sout{these} \kge{The three} metrics \kge{are} computed for each of the LIME applications to the \data \ test set.
 The simulation methods are listed on the x-axis.
@@
 
-All three metrics suggest that the kernel density performed well, but the metrics disagree for the quantile bins methods.
+All three metrics suggest that the kernel density \kge{method} performed well, but the metrics disagree for the quantile bins methods.
 Average $R^2$ and average fidelity rank the performance of the number of quantile bins the same (2 quantile bins perform the best and 6 quantile bins perform the worst).
-In fact, these two metrics appear to have an inverse relationship in this example.
-MSEE provides different ranks of the simulation methods.
-MSEE suggests that 6 quantile bins perform the best, and 2 quantile bins perform the worst.
-This is the opposite of average $R^2$ and average fidelity.
-Since average fidelity and MSEE are similar metrics, it would be expected that they would agree, but that is so in this example.
+In fact, these two metrics appear to have \kge{a mirrored} \sout{an inverse} relationship in this example.
+MSEE provides \kge{almost the exact opposite results with} \sout{different ranks of the simulation methods.
+MSEE suggests that} 6 quantile bins perform\kge{ing} the best\sout{,} and 2 quantile bins perform\kge{ing} the worst.
+\sout{This is the opposite of average $R^2$ and average fidelity.} Since average fidelity and MSEE are similar metrics, it would be expected that they would agree, but that is so in this example.
 This may be due to the MSEE only taking into account the prediction of interest and not the full simulated dataset.
-The contradiction between metrics makes it difficult to identify which simulation method explanations to trust.
-
-Recall that \autoref{fig:sine-feat-heat} indicated that the LIME kernel density method selected the same feature across all cases in the test set for both the first and second features.
+The contradiction between metrics makes it difficult to identify which simulation method \sout{explanations} to trust.
+
+Recall that \autoref{fig:sine-feat-heat} indicated that the \sout{LIME} kernel density method selected the same feature across all cases in the test set for both the first and second features.
 It appears that a global trend may be the best explanation for this example, which may be reasonable considering that we know that both $x_1$ and $x_2$ are the two features that should be the features used by the random forest to distinguish between response categories.
@@
 
-In current practice, forensic firearm examiners evaluate whether two bullets are from the same source (fired from the same gun) or from different sources based on microscopic comparison of the striation patterns engraved on bullets during the firing process (see \autoref{fig:bullet}).
+In current practice, forensic firearm examiners evaluate whether two bullets are from the same source (fired from the same gun) or from different sources based on \kge microscopic comparison of the striation patterns engraved on bullets during the firing process (see \autoref{fig:bullet}).
 The process is based on a visual and therefore subjective assessment of the evidence.
@@
 In response, \citet{hare:2016} proposed an automated machine learning method for bullet matching to complement a visual inspection by firearm examiners.
-Based on high-resolution topological scans of land engraved areas \citet{hare:2016} obtain signatures of striations from two bullet lands (\autoref{fig:signatures}).
+Based on high-resolution topological scans of land engraved areas\kge{,} \citet{hare:2016} obtain signatures of striations from two bullet lands (\autoref{fig:signatures}).
 Nine features quantifying the similarity of signatures, such as the cross-correlation function, the distance between signatures, and the number of matching striae, are extracted and used to train a random forest \kge{\sout{model}} (available in the \emph{bulletxtrctr} R package) to determine the probability of a comparison resulting from the same source (matching signatures) or from different sources (non-matching signatures).
@@
 \includegraphics[width=3.25in]{./figure-static/signatures.png}
+\caption{Example bullet signatures.
+The bullet signatures are from the same barrel \kge{and} land and therefore have very similar patterns.
+The \citet{hare:2016} random forest \kge{is fit using various} \sout{uses} features that measure the similarity between two such signatures.}
 \label{fig:signatures}
-\caption{Example bullet signatures.
-The bullet signatures are from the same barrel-land and therefore have very similar patterns.
-The \citet{hare:2016} random forest uses features that measure the similarity between two such signatures.}
 \end{figure}
@@
 We apply the random forest \kge{\sout{model}} from \citet{hare:2016} to another set of bullets from the Hamby study with \Sexpr{dim(bullet_test)[1]} rows of land comparisons.
-We first consider a global visualization of the relationship between the random forest predictions and the model features by creating a parallel coordinate plot of the training data (top facet) and testing data (bottom facets) predictions (\autoref{fig:bullet-plot-rfpcp}).
+We first consider a global visualization of the relationship between the random forest predictions and the model features \kge{with} \sout{by creating} a parallel coordinate plot of the training data (top facet) and testing data (bottom facets) predictions (\autoref{fig:bullet-plot-rfpcp}).
 The majority of same source observations with random forest probabilities close to 1 have a clear pattern of corresponding feature values.
@@
 
-LIME is implemented using the R package \emph{limeaid} to apply LIME multiple times to all test set observations using different tuning parameters: 12 sampling methods (2-6 equally spaced bins, 2-6 quantile bins, kernel density estimation, and normal approximation) and 3 Gower exponents (0.5, 1, and 10).
+LIME \sout{is implemented using the R package \emph{limeaid} to apply LIME} \kge{is applied} \sout{multiple times} to all test set observations using different tuning parameters: 12 sampling methods (2-6 equally spaced bins, 2-6 quantile bins, kernel density estimation, and normal approximation) and 3 Gower exponents (0.5, 1, and 10).
 Thus, a total of $12\times 3=36$ different applications of LIME were performed.
-We specify that each LIME explanation return 3 features and feature selection is performed using the highest weights method (default option).
+We specify that each LIME explanation return 3 features and feature selection is performed \kge{by selecting the features with the highest weights in a ridge regression model} \sout{using the highest weights method} (default option).
+\kgc{XXX THIS IS WHERE I LEFT OFF XXX}
 

### 2020-08-27 paper.Rnw
edits through the discussion

@@
 We specify that each LIME explanation return 3 features and feature selection is performed \kge{by selecting the features with the highest weights in a ridge regression model} \sout{using the highest weights method} (default option).
-\kgc{XXX THIS IS WHERE I LEFT OFF XXX}
 
@@
 To get an overview of the LIME explanations from the 36 applications, we consider a feature heatmap (\autoref{fig:bullet-feature-heatmap}).
-In addition to facets for simulation method and order of feature selected by LIME, this plot includes a vertical facet for Gower power and a horizontal facet for whether the observation is a known match or non-match.
+In addition to facets for simulation method and \kge{LIME feature importance} \sout{order of feature selected by LIME}, this plot includes a vertical facet for Gower power and a horizontal facet for whether the observation is a known match or non-match.
 This plot highlights several key features of the LIME explanations from the bullet matching dataset.
@@
 @
-\caption{Feature heatmap of the 36 LIME applications to the bullet comparison data test set.
+\caption{Feature heatmap of \sout{the} 36 LIME applications to the bullet comparison data test set.
 In addition to faceting the results by simulation method and LIME feature selection order, facets for the Gower power and whether the observation is a match or non-match are included.
@@
 @
-\caption{Plot of LIME assessment metrics for the applications of LIME on the bullet comparison data test set.
+\caption{\kge{Assessment metric plot} \sout{Plot of LIME assessment metrics} for the applications of LIME on the bullet comparison data test set.
 The density simulation methods perform well for all metrics.
@@
 
-Figure \ref{fig:bullet-eois} include the explanation plots (from \emph{lime}) and explanation scatterplots for cases M and NM.
+Figure \ref{fig:bullet-eois} include\kge{s} the \kge{visual representation plots of explanations} \sout{explanation plots} (from \emph{lime}) and explanation scatterplots for cases M and NM.
 Plots for 3 equal bins and 3 quantile bins are included.
-Plots for the kernel density simulation method are included in Figure \ref{fig:bullet-expl-scat-density}.
+Plots for the kernel density simulation method are included in \kge{Appendix \ref{exp-scatter_plus} (}Figure \ref{fig:bullet-expl-scat-density}\kge{)}.
 The scatterplots provide several insights into the LIME explanations.
 Here we focus on the explanation for case NM with 3 quantile bins, but similar statements can be made about the other plots.
+\kgc{I've been thinking about the examples I chose to include, and I have a couple of questions.
+First, is it okay to include all of these plots when I am only discussing one?
+Second, I'm not sure why I chose to list 3 quantile bins as a "good" tuning parameter value anymore based on the assessment metric plot.
+I don't know that I agree with that anymore.
+However, it does provide a nice example for where the explainer model goes wrong.
+I'm wondering if it would be better to just focus on the 3 equal bins plots for cases M and NM.
+They are not quite a dramatically bad as 3 quantile bins, but a case could be make for not really capturing the random forest prediction regions.}
 
@@
 Based on the scatter plot of CCF versus matches, a better explanation would be that because case NM has a value of CCF less than 0.8 and a value of matches less than 7, the random forest provides a prediction supporting a non-match.
-The relationship between CCF and rough correlation does not provide much evidence to support the random forest prediction one way or the other, but there is a pentagon shaped region at the bottom of the scatter plot of matches versus rough correlation with mostly predictions close to 0 that case NM falls and supports the random forest prediction of a non-match.
+The relationship between CCF and rough correlation does not provide much evidence to support the random forest prediction one way or the other, but there is a pentagon shaped region at the bottom of the scatter plot of matches versus rough correlation with mostly predictions close to 0 that case NM falls \kge{in} and supports the random forest prediction of a non-match.
 
@@
 
-# eoi1_kd <-
-#   plot_explain_scatter(bullet_explain_perms[13:15, ], alpha = 0.9, weights = TRUE) +
-#   scale_color_gradient2(
-#     low = "grey50",
-#     high = "darkorange",
-#     midpoint = 0.5,
-#     limits = c(0, 1)
-#   ) +
-#   scale_fill_gradient2(
-#     low = "grey50",
-#     high = "darkorange",
-#     midpoint = 0.5,
-#     limits = c(0, 1)
-#   ) +
-#   theme_bw(base_family = "Times", base_size = 8) +
-#   theme(
-#     strip.placement = "outside",
-#     strip.background = element_rect(color = "white",
-#                                     fill = "white")
-#   )
-# 
-# eoi2_kd <-
-#   plot_explain_scatter(bullet_explain_perms[16:18, ], alpha = 0.9, weights = TRUE) +
-#   scale_color_gradient2(
-#     low = "grey50",
-#     high = "darkorange",
-#     midpoint = 0.5,
-#     limits = c(0, 1)
-#   ) +
-#   scale_fill_gradient2(
-#     low = "grey45",
-#     high = "darkorange",
-#     midpoint = 0.5,
-#     limits = c(0, 1)
-#   ) +
-#   theme_bw(base_family = "Times", base_size = 8) +
-#   theme(
-#     strip.placement = "outside",
-#     strip.background = element_rect(color = "white",
-#                                     fill = "white")
-#   )
-
 pf1_3qb <- plot_features(bullet_explain_perms[1:3,]) +
@@
   theme(text = element_text(family = "Times", size = 10))
-# pf1_kd <- plot_features(bullet_explain_perms[13:15,]) +
-#   scale_fill_manual(values = c("darkorange", "grey50"))
-# pf2_kd <- plot_features(bullet_explain_perms[16:18,]) +
-#   scale_fill_manual(values = c("darkorange", "grey50"))
 @
@@
 @
-\caption{Plots of LIME explanations and explanation scatterplots for one case M and NM in the bullet test data.
-The first column contains plots associated with 3 quantile bins and the second with 3 equally spaced bins.
-The plots provide insights into the LIME explanations and allow for the assessment of the explanation quality.}
+\caption{Plots of LIME explanations \kge{(first and third rows)} and explanation scatterplots \kge{(second and fourth rows)} for \sout{one} case\kge{s} M and NM in the bullet test data \kge{for two tuning parameter values: 3 quantile bins (first column) and 3 equal bins (second column)}.
+\sout{The first column contains plots associated with 3 quantile bins and the second with 3 equally spaced bins.} The plots provide insights into the LIME explanations and allow for the assessment of the explanation quality.}
 \label{fig:bullet-eois}
@@
 
-Without applying LIME with multiple tuning parameters to the bullet test data or viewing diagnostic plots of the LIME explanations, it may be very possible to formulate reasons why the LIME explanations make sense.
+Without applying LIME with multiple tuning parameter\sout{s} \kge{values} to the bullet test data or viewing diagnostic plots of the LIME explanations, it may be very possible to formulate reasons why the LIME explanations make sense.
 However, the sequence of plots in this section (Figures \ref{fig:bullet-feature-heatmap}, \ref{fig:bullet-assess-metric}, and \ref{fig:bullet-eois}) suggest that we should be cautious to trust any of these LIME explanations.
@@
 
-%\hh{The discussion should not have subsection ... but we can keep them for now for structural purposes.} \kg{Okay. I took them out.}
-
 This paper highlights that while an explainer model is meant to provide clarity, it actually adds another layer of complexity to predictive models by requiring yet another model that needs to be assessed.
 Without an assessment of the explainer model, LIME is a black-box procedure of its own requiring blind trust in the explainer model.
-%\hh{XXX what is the implication?
-bring it to a punch: asking the user to trust into explainer...}
 We suggest the use of visual diagnostics to counteract the black-box nature of LIME and provide three diagnostic plots.
 
-The visualizations are intended to provide insight on how LIME works, assess the ability of the explainer model to capture the complex predictive model, and compare LIME explanations produced by different tuning parameters.
+The visualizations are intended to provide insight on how LIME works, assess the ability of the explainer model to capture the complex predictive model, and compare LIME explanations produced by different tuning parameter\sout{s} \kge{values}.
 While the visualizations accomplish these tasks, they also expose examples of the failings of LIME.
-To address the discovered failings of LIME, we will reconsider each of the claims about the performance of LIME made by \citet{ribeiro:2016} in light of the insights gained from the diagnostic visualizations.
-
-As previously discussed, the \textbf{interpretability} of the LIME explanations can be controlled by the complexity of the explainer model.
+To address the discovered failings of LIME, we \sout{will} reconsider each of the claims about the performance of LIME made by \citet{ribeiro:2016} in light of the insights gained from the diagnostic visualizations.
+
+As previously discussed, the \textbf{interpretability} of the LIME explanations \kge{is controllable} \sout{can be controlled} by the complexity of the explainer model.
 For example, the number of bins selected for simulation can control the interpretability of the explanations.
@@
 For example, the visualization of a LIME explanation available from the \emph{lime} R package \citep{pedersen:2020} (shown in Figures \ref{fig:sine-exp-scatter} and \ref{fig:bullet-eois}) is a major simplification of the explainer model, which could lead to under-interpreted or misinterpreted LIME explanation.
-Supplementing \citet{pedersen:2020}'s compact visualization of the explanation with an explanation scatterplot that shows a more detailed visualization of the explainer model (such as Figures \ref{fig:sine-exp-scatter} and \ref{fig:bullet-eois}) promotes a full interpretation of the explanation.
+Supplementing \citet{pedersen:2020}'s compact visualization of the explanation with an explanation scatterplot that shows a more detailed visualization of the explainer model (such as Figures \ref{fig:sine-exp-scatter} and \ref{fig:bullet-eois}) promotes a \kge{more complete understanding} \sout{full interpretation} of the explanation.
 
@@
 The explanation scatterplots allow for a comparison of the explainer model to the complex model.
-The examples in this paper show cases where the explainer model bins do not accurately capture the classification boundaries near the predictions of interest of the random forest\kge{s \sout{models}} by oversimplifying the model (Figures \ref{fig:sine-exp-scatter} and \ref{fig:bullet-eois}).
+The examples in this paper show cases where the explainer model bins do not accurately capture the \kge{regions with similar random forest probabilities that contain the prediction of interest} \sout{classification boundaries near the predictions of interest of the random forest\kge{s \sout{models}} by} \kge{and} oversimplify\sout{ing} the model (Figures \ref{fig:sine-exp-scatter} and \ref{fig:bullet-eois}).
 Using less bins would clearly not help improve the faithfulness of the explainer model in these examples, and while an increase in bins would lead to a finer resolution of the random forest classification boundaries, interpretability of the explainer model would quickly be lost.
@@
 The examples of faithfulness metric comparisons in this paper (Figures \ref{fig:sine-assess-metric} and \ref{fig:bullet-assess-metric}) both produced confusing results.
-The density based simulation methods resulted in the best or close to the best performance even though the feature heatmaps (Figures \ref{fig:sine-feat-heat} and \ref{fig:bullet-feature-heatmap}) showed that the density simulation methods produced global explanations with no variation in features selected by LIME.
-For the bin based simulation methods, the two metrics often did not agree or contradicted one another, which makes it difficult to decide on a recommendation of a set of tuning parameters that produces the explanations with the most faithful explainer model.
+The density based simulation methods result\sout{ed} in the best or close to the best performance even though the feature heatmaps (Figures \ref{fig:sine-feat-heat} and \ref{fig:bullet-feature-heatmap}) show\sout{ed} that the density simulation methods produce\sout{d} global explanations with \kge{minimal} \sout{no} variation in features selected by LIME.
+For the bin based simulation methods, the two metrics often \kge{do} \sout{did} not agree or contradict\sout{ed} one another, which makes it difficult to decide on a recommendation of a set of tuning parameters that produces the explanations with the most faithful explainer model.
 
@@
 
-The final claim, \textbf{localness}, is addressed by the feature heatmap and metric comparison plot.
-As stated, the feature heatmap revealed that the density simulation methods in the examples of this paper resulted in global explanations where the same features were repeatedly chosen across all (or almost all) observations in the set of explanations.
+The final claim, \textbf{localness}, is addressed by the feature heatmap and metric comparison plot\kge{s}.
+As stated, the feature heatmap reveal\kge{s}\sout{ed} that the density simulation methods in the examples of this paper result\kge{s}\sout{ed} in global explanations where the same features \kge{are} \sout{were} repeatedly chosen across all (or almost all) observations in the set of explanations.
 This finding agrees with that of \citep{laugel:2018} who found LIME produced global explanations with the normal approximation simulation method.
 For the bin based simulation methods in the bullet data example, the feature heatmap showed that the features chosen for the explanations varied between the two classification categories (match versus non-match).
-This is an interesting finding that suggests that different features can play a role in the predictions of observations in different response categories, but the patterns of features selected by LIME within a classification category do not vary.
-Again, this is a suggestion of global explanations.
-Furthermore, while the metric comparison plot in the bullet example did not provide agreement between metrics on a best bin based method, all metrics agree that a Gower power of 0.5 for computing the model weights associated with distance of a simulated data point from the prediction of interest is best.
+This is an interesting finding that suggests that different features can play a role in the predictions of observations in different response categories\kge{.} \sout{, but the patterns of features selected by LIME within a classification category do not vary.
+Again, this is a suggestion of global explanations.} \kgc{I'm not sure what I was trying to say there.} Furthermore, while the metric comparison plot in the bullet example did not provide agreement between metrics on a best bin based method, all metrics agree that a Gower power of 0.5 for computing the model weights associated with distance of a simulated data point from the prediction of interest is best.
 This suggests that a less local explanation provided a better explanation of the performance of the random forest.
@@
 The addition of interactivity to the diagnostic plots would provide additional enhancement of the assessment process.
-For example, a diagnostic plot that provides a summary of multiple LIME explanations, such as the feature heatmap, could be displayed and clicked on to reveal more detailed figures associated with individual predictions of interest, such as plots of the simulated data and explainer model.
+For example, a diagnostic plot that provides a summary of multiple LIME explanations, such as the feature heatmap, could be displayed and clicked on to reveal more detailed figures associated with individual predictions of interest, such as \kge{an explanation scatterplot.} \sout{plots of the simulated data and explainer model.}
 
@@
 \hh{XXX Does that extra explanation help?} \kgc{Yes.
-I see what you mean now.} In that respect, the diagnostics shown for the \data\ and in the bullet example are representative of what is expected.
+I see what you mean now.} In that respect, the diagnostics shown for the \data \ and \sout{in} the bullet example are representative of what is expected.
 But in cases where overplotting does become problematic, the user could either simply reduce the size of the simulations or use some well-studied binning techniques in the visualizations, as discussed for example in \citet{carr:1987} or \citet{unwin:2006}.
 
-While it would be ideal if LIME could be used as a method to provide easily understandable explanations for black-box models as \citep{ribeiro:2016} claim, that dream is not yet a reality.
+While it would be ideal if LIME could be used as a method to provide easily understandable explanations for black-box models as \citet{ribeiro:2016} claim, that dream is not yet a reality.
 The examples using diagnostic plots to assess LIME in this paper show frequent issues with LIME.
-We hope that our plots provide motivation to assess LIME explanations, to not blindly use the default settings (even if it is not clear which tuning parameters to use), and to encourage work on improving LIME, so that it can be a lime and not a lemon.
+We hope that our plots provide motivation to assess LIME explanations, to not blindly use the default settings (even if it is not clear \kge{how to tune the parameters} \sout{which tuning parameters to use}), and to encourage work on improving LIME, so that it can be a lime and not a lemon.
 
 \section*{Acknowledgments}
-HH was partially funded by the Center for Statistics and Applications in Forensic Evidence (CSAFE) through Cooperative Agreement 70NANB20H019 between NIST and Iowa State University, which includes activities carried out at Carnegie Mellon University, Duke University, University of California Irvine, University of Virginia, West Virginia University, University of Pennsylvania, Swarthmore College and University of Nebraska, Lincoln.
+
+\kge{Should this go under the financial disclosure section?
+Also, what is the financial disclosure section meant to contain?
+I couldn't find it described on the ASA data science journal author guidelines page.
+Should we remove it?} HH was partially funded by the Center for Statistics and Applications in Forensic Evidence (CSAFE) through Cooperative Agreement 70NANB20H019 between NIST and Iowa State University, which includes activities carried out at Carnegie Mellon University, Duke University, University of California Irvine, University of Virginia, West Virginia University, University of Pennsylvania, Swarthmore College and University of Nebraska, Lincoln.
 
@@
 
-\hh{A taxonomy of author contributions is suggested by Elsevier - I put the link in an email
-}
-
-{\bf Katherine Goode, Heike Hofmann}: Conceptualization, Methodology, Investigation, Writing- Reviewing and Editing.
+\hh{A taxonomy of author contributions is suggested by Elsevier - I put the link in an email}
+
+{\bf Katherine Goode, Heike Hofmann}: Conceptualization, Methodology, Investigation\kge{, Visualizations}, Writing- Reviewing and Editing.
 {\bf Katherine Goode}: Writing Initial Draft, Software.
@@
 
-The following supporting information is available as part of the online article:
+The following supporting information is available as part of the online article: \kgc{What should we list here?}
 
@@
 % \end{itemize}
+
 \newpage
+
 \appendix
+
+\kgc{XXX This is where I left off XXX}
 

### 2020-08-27 paper.Rnw
made it through the paper with edits! (I may clean up references a bit more.)

@@
 As stated, the feature heatmap reveal\kge{s}\sout{ed} that the density simulation methods in the examples of this paper result\kge{s}\sout{ed} in global explanations where the same features \kge{are} \sout{were} repeatedly chosen across all (or almost all) observations in the set of explanations.
-This finding agrees with that of \citep{laugel:2018} who found LIME produced global explanations with the normal approximation simulation method.
+This finding agrees with that of \citet{laugel:2018} who found LIME produced global explanations with the normal approximation simulation method.
 For the bin based simulation methods in the bullet data example, the feature heatmap showed that the features chosen for the explanations varied between the two classification categories (match versus non-match).
@@
 
-\kgc{XXX This is where I left off XXX}
-
 \section{LIME Tuning Parameter Options} \label{lime-details}
 
-The following tuning parameters for the LIME algorithm are available in the \emph{lime} R package.
+The following tuning parameters for the LIME algorithm are available in the \emph{lime} R package \citep[pedersen:2020].
 
@@
 
-\item Feature selection method for determining the features to return in an explanation: forward selection applied to a ridge regression, highest weights in ridge regression, LASSO, classification/regression tree splits
+\item Feature selection method for determining the features to return in an explanation: forward selection applied to a ridge regression, features with the largest magnitude coefficients in ridge regression, LASSO, classification/regression tree splits
 
@@
 Section \ref{exp-scatter} introduces explanation scatterplots under the default simulation method in the \emph{lime} R package: four quantile bins.
-The structure of an explanation scatterplot remains the same for if any bin based simulation method is used to create the simulated data (any number of quantile or equally spaced bins).
-However, if the kernel density or normal approximation simulation methods are used as the simulation method, the format of the explanation scatterplot changes.
+The structure of an explanation scatterplot remains the same \sout{for} if any bin based simulation method is used \sout{to create the simulated data}, i.e., any number of quantile or equally spaced bins.
+However, if the kernel density or normal approximation simulation methods are used \sout{as the simulation method}, the format of the explanation scatterplot changes.
 In the density based simulation method scenarios, LIME uses the standardized versions of the predictor variables to fit the explainer model.
@@
 Figure \ref{fig:sine-expl-scat-density} provides example explanation scatterplots for each feature in the default LIME explanation obtained using the kernel density simulation method for the \data \ prediction of interest.
+Figure \ref{fig:bullet-expl-scat-density} includes explanation scatterplots for the explanations generated using kernel density simulation for the bullet example cases M and NM discussed in Section \ref{bullet-assess-ex}.
 
@@
 
-Figure \ref{fig:bullet-expl-scat-density} includes explanation scatterplots for the explanations generated using kernel density simulation for the bullet example cases M and NM discussed in Section \ref{bullet-assess-ex}.
-
 \begin{figure*}[!thp]
@@
 This is shown in Figure \ref{fig:sine-plot-resids} with the explainer model residuals on the y-axis and explainer model predictions on the x-axis.
-The points along the x-axes have been jittered to ease the effect of the over-plotted points in the visualization.
+The points along the x-axis have been jittered to ease the effect of the over-plotted points in the visualization.
 There is a clear increasing trend in the residuals as the explainer model predictions increase.
@@
 
-For $x_e$ and set of tuning parameters $t$, let $\textbf{X}_{e,t}'$ be the LIME simulated dataset with $K$ features and $S$ observations such that $x'_{e,t,s}$ is the feature vector for simulated data observation $s$.
-Let $\textbf{Z}'_{e,t}$ be the matrix of interpretability transformed simulated data with $K$ features and $S$ observations such that $z'_{e,t,s}$ is the interpretability transformed feature vector for observation/explanation $e$, tuning parameter $t$, and simulated data observation $s$.
-Note that $z_{e,t}$ will represent the interpretability transformed version of $x_e$.
-
-Next, let $\omega_t$ represent a proximity distance metric.
+For $x_e$ and \kge{a} set of tuning parameters $t$, let $\textbf{X}_{e,t}'$ be the LIME simulated dataset with $K$ features and $S$ observations such that $x'_{e,t,s}$ is the feature vector for simulated data observation $s$ \kge{corresponding to observation/explanation $e$ and tuning parameters $t$}.
+Let $\textbf{Z}'_{e,t}$ be the matrix of \kge{simulated data transformed to bin indicator variables (for bin based simulation methods) or standardization (for density based simulation methods)} \sout{interpretability transformed simulated data} with $K$ features and $S$ observations such that $z'_{e,t,s}$ is the interpretability transformed feature vector for observation/explanation $e$, tuning parameter\kge{s} $t$, and simulated data observation $s$.
+Note that $z_{e,t}$ will represent the \sout{interpretability} transformed version of $x_e$.
+
+Next, let $\omega_t$ represent a proximity distance metric \kge{corresponding to tuning parameters $t$}.
 Then $\omega_t\left(x_e, x'_{e,t,s}\right)$ is the weight assigned to $x'_{e,t,s}$, which is the proximity between $x_e$ and $x'_{e,t,s}$.
@@
 
-where $R_{e,t}^2$ is the $R^2$ value for $g_{e,t}$.\\
+\noindent where $R_{e,t}^2$ is the $R^2$ value for $g_{e,t}$.\\
 \\
@@
 \begin{eqnarray*} \mathcal{L}_{\mbox{ave}} & = & \frac{1}{E}\sum_{e=1}^E\mathcal{L}(f, \ g_{e,t}, \ \pi_{t}) \\ & = & \frac{1}{E}\sum_{e=1}^E\sum_{s=1}^{S}\omega_{t}\left(x_e, x'_{e,t,s}\right)\left(f\left(x'_{e,t,s}\right)-g_{e,t}\left(z_{e,t,s}'\right)\right)^2.
-\end{eqnarray*}\\
+\end{eqnarray*}
+
+\noindent \kge{where $\mathcal{L}$ was originally defined in \citet{ribeiro:2016}.}\\
 \\

### 2020-08-27 paper.Rnw
changed a few past tense words to present tense

@@
 The plot is created using the \emph{lime} R package and provides a visual representation of a LIME explanation for the prediction of interest indicated in \autoref{fig:sine-plot-data}.
-In particular, the explanation was obtained using 4 quantile bins to simulate the data.} \kgc{I moved the next few sentences here from the sub-section.} In this scenario, LIME converts continuous predictor variables to indicator variables identifying whether the variable value falls in the same quantile bin as the prediction of interest or not.
+In particular, the explanation is obtained using 4 quantile bins to simulate the data.} \kgc{I moved the next few sentences here from the sub-section.} In this scenario, LIME converts continuous predictor variables to indicator variables identifying whether the variable value falls in the same quantile bin as the prediction of interest or not.
 The indicator variables are used as the explainer model features.
@@
 
-The explanation for the prediction of interest depicted in Figure \ref{fig:sine-exp-scatter} can be interpreted as follows.
+The explanation for the prediction of interest depicted in Figure \ref{fig:sine-exp-scatter} \kge{is} \sout{can be} interpreted as follows.
 A random forest classification of blue is supported by the prediction of interest having a value of $x_2$ that is greater than \Sexpr{str_split(sine_poi_lime_default$feature_desc[[1]], pattern = " ")[[1]][1]}, but the prediction of interest having a value of $x_1$ that is greater than \Sexpr{str_split(sine_poi_lime_default$feature_desc[[2]], pattern = " ")[[1]][1]} and less than or equal to \Sexpr{str_split(sine_poi_lime_default$feature_desc[[2]], pattern = " ")[[1]][5]} provides support against a classification of blue.
@@
 The weights \kge{decay relatively slowly} \sout{remain relatively high} outside of the intersection of the two quantile bins suggesting that the LIME explanation is highly influenced by points outside of the bin\kge{s} containing the prediction of interest.
-\sout{While i} \kge{However,} it is \sout{still} difficult to say \kge{if} \sout{whether or not} the claim of localness has been violated\kge{, because a definition of a local region was not specified.
+\sout{While i} \kge{However,} it is \sout{still} difficult to say \kge{if} \sout{whether or not} the claim of localness has been violated\kge{, because a definition of a local region is not specified.
 Depending a the region a viewer considers to be local, an argument could be made in favor of or against a violation of localness.
@@
 Two hypothetical examples of feature heatmaps are included in \autoref{fig:concept-feat-heat}.
-The plots were created with the assumption that LIME is applied to select the top feature out of $p=\kge{4}$ \sout{8} features for $n=10$ cases with $t=5$ sets of tuning parameters.
+The plots \kge{are} \sout{were} created with the assumption that LIME is applied to select the top feature out of $p=\kge{4}$ \sout{8} features for $n=10$ cases with $t=5$ sets of tuning parameters.
 Situation 1 \kge{is} \sout{shows} an example where the features selected are consistent across tuning parameters within a case but vary across cases within a tuning parameter.
@@
 LIME \sout{is implemented using the R package \emph{limeaid} to apply LIME} \kge{is applied} \sout{multiple times} to all test set observations using different tuning parameters: 12 sampling methods (2-6 equally spaced bins, 2-6 quantile bins, kernel density estimation, and normal approximation) and 3 Gower exponents (0.5, 1, and 10).
-Thus, a total of $12\times 3=36$ different applications of LIME were performed.
+Thus, a total of $12\times 3=36$ different applications of LIME \kge{are} \sout{were} performed.
 We specify that each LIME explanation return 3 features and feature selection is performed \kge{by selecting the features with the highest weights in a ridge regression model} \sout{using the highest weights method} (default option).
@@
 
-% Do I need to include this?
-% \section*{Author Biography}
-% \begin{biography}
-% {\includegraphics[width=60pt,height=70pt,draft]{empty}}
-% {\textbf{Author Name.} This is sample author biography text this is sample author biography text}
-% \end{biography}
-
-% \textsc{\textbf{Ideas for describing proposed plots}}
-% 
-% \begin{itemize}
-% \item start at the high level explanation (this is what we want to do and this is how we do it)
-% \item go over a good and bad example
-% \item include schematics of the plot first (good and bad) and then include the sine mini example version
-% \item explain the expectation of the plot
-% \end{itemize}
-% 
-% \textsc{\textbf{Comments for Editing}}
-% 
-% \begin{itemize}
-% \item \hh{Generally: avoid 'can be'. Replace by 'is'.  }
-% \item \hh{References like 'they', 'them' ... replace them by repeating the noun you are referring to to avoid any kind of ambiguity}
-% \item \kgc{words to go back and make sure I am not using too often: ability, produce, understand}
-% \item \kgc{decide on features or predictor variables}
-% \item \hh{it's tuning parameters, not tunning} \kgc{Oops! I get that one wrong all of the time}
-% \item \kgc{Adjust text sizes in plots so they all match}
-% \item \kgc{Color scheme - comment from Heike:} \hh{I like the red-blue scheme for binary values, I also like the color scheme in the features heatmap.
-Generally papers and color don't go well together anyways, but we will solve that problem when we have to ...
-Most likely we will have to just pay the extra color fee}
-% \item \kgc{Check that I am consistently referring to the perturbing as data simulation}
-% \item \kgc{Clean up notation}
-% \item \kgc{Referring to the linearity assumption:} \hh{Be a bit careful in the phrasing here - we can always approximate any function using a linear form (think Taylor expansion).
-The question is how big the error is.}
-% \item \kgc{Make sure plots in the same figure are the same size}
-% \item \kgc{Make sure I am distinguishing between RF predictions and probabilities correctly}
-% \item \kgc{Use prediction of interest not case of interest}
-% \item \kgc{Make sure I always treat the word 'data' as plural}
-% \item \kgc{dataset or data set?}
-% \item \kgc{scatterplot or scatter plot (check other plot names as well)}
-% \item \kgc{choose whether to use the term feature or variable and make sure it is consistent throughout}
-% \item \kgc{just include the details about LIME that are necessary to understand the plots and remove the rest to the appendix}
-% \item \hh{avoid the use of implicit references like `this' and `that'. Make the reference explicit by adding what you are referring to, such as `this method', `that procedure'}
-% \item \hh{make sure to use exact phrases.
-things like `LIME was developed in 2016' is factually questionable - but we know LIME was introduced in 2016.
-Also `the authors were interested in ...' implies that you know their intent.
-It's better to not guess any intent but stick to what we know.}
-% \item \hh{`our` diagnostics ...
-you are using `our` quite often.
-It is good to claim work, but it is not good to claim things that we want others to use, because that is by definition excluding everybody but you.
-It's better to re-phrase with a focus on what you did.
-We introduce, we suggest, etc.}
-% \item \kgc{check that I am always using present tense}
-% \item \kgc{check that I am consistent in my use of the term black-box model}
-% \end{itemize}
-
 \newpage

### 2020-08-28 paper.Rnw
resolving merge conflict

@@
 For now, I listed Ribeiro as the author, because he is the main contributor, but there are 40 other contributors to the package.
-Is it okay to just list Ribeiro?} \citep{pedersen:2020} offer various tuning parameters (see Section \ref{background}) that affect the explainer model and ultimately, the explanation.
+Is it okay to just list Ribeiro?}\hh{I would go with 'and contributors' - if we just cite Ribeiro people might not realize that it's truly not just him.} \citep{pedersen:2020} offer various tuning parameters (see Section \ref{background}) that affect the explainer model and ultimately, the explanation.
 Since the explainer model is an approximation of the complex model and not a direct interpretation, the explanations produced by an explainer model are subject to the quality of the approximation.
@@
 
-All runs of LIME in this paper are executed in a forked version\footnote{https://github.com/goodekat/lime} of the R package \emph{lime} (version \Sexpr{packageVersion("lime")}) by \kge{\citet{pedersen:2020}}.
-The forked version is functionally indistinguishable from \kge{\citeauthor{pedersen:2020}'s} implementation but allows us to export internal values relevant for an assessment of the explainer.
+All runs of LIME in this paper are executed in a forked version\footnote{https://github.com/goodekat/lime} of the R package \emph{lime} (version \Sexpr{packageVersion("lime")}) by \citet{pedersen:2020}.
+The forked version is functionally indistinguishable from \citeauthor{pedersen:2020}'s implementation but allows us to export internal values relevant for an assessment of the explainer.
 The diagnostic plots included in this paper are created using the R package \emph{limeaid} \citep{goode:2020}.
@@
 We apply LIME using six sets of tuning parameters to all observations in the \data \ test set to observe variability across tuning parameters.
-A quantile bin based simulation method \kge{(samples are simulated uniformly from a specified number of quantile bins)} is used for five of the LIME applications with the number of bins varying from 2 to 6 by application.
+A quantile bin based simulation method (samples are simulated uniformly from a specified number of quantile bins) is used for five of the LIME applications with the number of bins varying from 2 to 6 by application.
 We use 6 bins as the maximum, because the complexity of the explanations increases with the number of bins.
-\kge{Note that 4 quantile bins are the default method in \emph{lime}.} The sixth application of LIME uses a kernel density simulation method \kge{(samples are drawn from kernel density approximations of the feature distributions)}.
+Note that 4 quantile bins are the default method in \emph{lime}.
+The sixth application of LIME uses a kernel density simulation method (samples are drawn from kernel density approximations of the feature distributions).
 The default methods for feature selection (forward selection) and the computation of the weights (Gower distance raised to an exponent of 1) are used for all applications.
@@
 @
-\caption{(left) Visualization from the \emph{lime} R package of \kge{a} \sout{the} LIME explanation for the \data \ prediction of interest \kge{identified in \autoref{fig:sine-plot-data}}.
-\sout{The bars represent the explainer model coefficients.} (right) \emph{Explanation Scatterplot}.
+\caption{(left) Visualization from the \emph{lime} R package of a LIME explanation for the \data \ prediction of interest identified in \autoref{fig:sine-plot-data}.
+(right) \emph{Explanation Scatterplot}.
 The points represent the simulated data colored by the random forest probabilities and sized by the assigned LIME weights.
-\hh{XXX could you make the complex prediction **much** lighter for this example?
+%\hh{XXX could you make the complex prediction **much** lighter for this example?
 The diamond and the lines are hard to see, but should be the focus.} \kgc{Is that light enough?
 Feel free to edit the alpha value in the plot\_explain\_scatter function as you feel necessary.
-I also made the lines depicting the explainer model wider in limeaid, and there is an option 'line\_size' that can be adjusted.} The prediction of interest is shown as the diamond shaped point.
+I also made the lines depicting the explainer model wider in limeaid, and there is an option 'line\_size' that can be adjusted.} \hh{thank you!}
+The prediction of interest is shown as the diamond shaped point.
 The explainer model indicator variables associated with $x_1$ and $x_2$ (quantile bins containing the prediction of interest) are depicted by the solid lines.
@@
 
-\kgc{I really like the idea of separating the description of the \emph{lime} figure from the explanation scatterplot, but the more I think about it, I don't like that it get it's own sub-section.
+%\kgc{I really like the idea of separating the description of the \emph{lime} figure from the explanation scatterplot, but the more I think about it, I don't like that it get it's own sub-section.
 I think it would be nicer to allocate the sub-sections to the visual diagnostic plots.
@@
 Another option would be to drop the heading altogether and flow into the next paragraph.} \hh{XXX I've just pulled the description of the left hand side of figure 4 out of the next section.}
-
-\kge{Before introducing the visual diagnostics, let us consider a commonly used visualization of a LIME explanation that is shown in Figure \ref{fig:sine-exp-scatter} (left).
+\hh{XXX I like the idea of not giving this section an official header, but I like the way it looks like now with the bold header - that should help the reader what's going on.}
+
+Before introducing the visual diagnostics, let us consider a commonly used visualization of a LIME explanation that is shown in Figure \ref{fig:sine-exp-scatter} (left).
 The plot is created using the \emph{lime} R package and provides a visual representation of a LIME explanation for the prediction of interest indicated in \autoref{fig:sine-plot-data}.
-In particular, the explanation is obtained using 4 quantile bins to simulate the data.} \kgc{I moved the next few sentences here from the sub-section.} In this scenario, LIME converts continuous predictor variables to indicator variables identifying whether the variable value falls in the same quantile bin as the prediction of interest or not.
+In particular, the explanation is obtained using 4 quantile bins to simulate the data.
+%\kgc{I moved the next few sentences here from the sub-section.}
+In this scenario, LIME converts continuous predictor variables to indicator variables identifying whether the variable value falls in the same quantile bin as the prediction of interest or not.
 The indicator variables are used as the explainer model features.
-\sout{To demonstrate a LIME explanation, we focus on the misclassified point indicated in Figure \ref{fig:sine-plot-data} by the diamond as the prediction of interest.
-The left plot in Figure \ref{fig:sine-exp-scatter} shows a visualization of the explanation for the prediction of interest as suggested by Ribeiro et al and implemented in the \emph{lime} R package.}
-
-The \kge{plot} \sout{figure} \kge{reports \Sexpr{round(sine_poi_lime_default$label_prob[1], 2)} as} \sout{shows that} the random forest \sout{returned a} probability \sout{of \Sexpr{round(sine_poi_lime_default$label_prob[1], 2)}} that the observation of interest belongs to category blue {(denoted as the ``label" in the \kge{plot \sout{figure}}).
-The lengths of the bars represent the \kge{\sout{explainer model}} coefficients \kge{from a ridge regression model (the explainer model) fit using the R package \emph{glmnet} \citep{simon:2011}} associated with the indicator variables chosen \kge{via feature selection \sout{by LIME as important}}.
-The color of \kge{a \sout{the}} bar denotes the sign of the coefficient and whether the feature "supports" or "contradicts" a random forest classification of `blue'.
-The "explanation fit" \kge{\sout{value}} is the deviance ratio from \kge{\sout{the R package}} \emph{glmnet} \kge{\sout{\citep{simon:2011} for a ridge regression model}}.
+
+The plot  reports \Sexpr{round(sine_poi_lime_default$label_prob[1], 2)} as  the random forest  probability  that the observation of interest belongs to category blue (denoted as the ``label" in the plot).
+The lengths of the bars represent the  coefficients from a ridge regression model (the explainer model) fit using the R package \emph{glmnet} \citep{simon:2011} associated with the indicator variables chosen via feature selection.
+The color of a  bar denotes the sign of the coefficient and whether the feature "supports" or "contradicts" a random forest classification of `blue'.
+The "explanation fit" is the deviance ratio from  \emph{glmnet}.
 In other words, this is the $R^2$ value associated with the explainer model.
 In this case, it is \Sexpr{round(sine_poi_lime_default$model_r2[1], 2)} suggesting that the explainer model is not a good linear fit.
-However, it is commonly accepted that $R^2$ has limitations for assessing the quality of fit of a model \citep{sapra:2014}\kge{\sout{,}} and \kge{\sout{it}} should not be used as the only metric in a model assessment.
-
-The explanation for the prediction of interest depicted in Figure \ref{fig:sine-exp-scatter} \kge{is} \sout{can be} interpreted as follows.
+However, it is commonly accepted that $R^2$ has limitations for assessing the quality of fit of a model \citep{sapra:2014} and  should not be used as the only metric in a model assessment.
+
+The explanation for the prediction of interest depicted in Figure \ref{fig:sine-exp-scatter} is interpreted as follows.
 A random forest classification of blue is supported by the prediction of interest having a value of $x_2$ that is greater than \Sexpr{str_split(sine_poi_lime_default$feature_desc[[1]], pattern = " ")[[1]][1]}, but the prediction of interest having a value of $x_1$ that is greater than \Sexpr{str_split(sine_poi_lime_default$feature_desc[[2]], pattern = " ")[[1]][1]} and less than or equal to \Sexpr{str_split(sine_poi_lime_default$feature_desc[[2]], pattern = " ")[[1]][5]} provides support against a classification of blue.
-\kge{Since the weight associated with $x_2$ has a larger magnitude than the weight associated with $x_1$, LIME explains that $x_2$ plays a more important role in the random forest prediction.} \kge{Additionally, consider that since the support for blue by $x_2$ outweights the support for red by $x_1$, the explainer model overall favors a label of blue for the prediction of interest, which} agrees with the random forest probability of \Sexpr{sine_poi_lime_default$label_prob[1]} for blue.
+Since the weight associated with $x_2$ has a larger magnitude than the weight associated with $x_1$, LIME explains that $x_2$ plays a more important role in the random forest prediction.
+Additionally, consider that since the support for blue by $x_2$ outweights the support for red by $x_1$, the explainer model overall favors a label of blue for the prediction of interest, which agrees with the random forest probability of \Sexpr{sine_poi_lime_default$label_prob[1]} for blue.
 Note that both models classify the observation incorrectly.
@@
 \subsection{Explanation Scatterplots} \label{exp-scatter}
-\hh{XXX I think we could reduce some of the example for the specific example a bit, now that the LIME explanation is moved out, there is not that much need to repeat the general ideas.} \kgc{I commented out the text that I think you were referring to.
+%\hh{XXX I think we could reduce some of the example for the specific example a bit, now that the LIME explanation is moved out, there is not that much need to repeat the general ideas.} \kgc{I commented out the text that I think you were referring to.
 See what you think.}
 
-\kgc{I moved the next sentence here from the previous paragraph.} Based on the plot \hh{on the left of \autoref{fig:sine-exp-scatter}} alone, it is not possible to make an informed assessment of the explanation.
-\hh{For a further assessment of the explainer model}, we turn to an \emph{explanation scatterplot}: \sout{the \emph{explanation scatterplot} is} a visual diagnostic for assessing the LIME claims of locality and fidelity for an individual explanation by juxtaposing the complex and explainer models in one plot.
+%\kgc{I moved the next sentence here from the previous paragraph.} 
+Based on the plot on the left of \autoref{fig:sine-exp-scatter} alone, it is not possible to make an informed assessment of the explanation.
+For a further assessment of the explainer model, we turn to an \emph{explanation scatterplot}:  a visual diagnostic for assessing the LIME claims of locality and fidelity for an individual explanation by juxtaposing the complex and explainer models in one plot.
 The format of an explanation scatterplot depends on the LIME simulation method.
-We introduce the explanation scatterplot here under the \emph{lime} R package default method \kge{four quantile bins.} \sout{in which the data are simulated uniformly from four quantile bins.}
+We introduce the explanation scatterplot here under the \emph{lime} R package default method of four quantile bins.
 
 The explanation scatterplot is built by plotting the LIME simulated data for the top two features identified by the explanation in a scatterplot and coloring these points by the  predictions from the complex model.
-The \kge{point} size \sout{of the points} represents the weight assigned by LIME.
-\hh{In order to show the LIME results for the observation of interest,} lines \hh{are drawn on top of the points.
-These lines } represent the boundaries of the indicator variables used to fit the explainer model.
-The \kge{line} color \sout{of the lines} denote\kge{s} whether LIME indicates that a feature supports or contradicts a class prediction.
+The point size  represents the weight assigned by LIME.
+In order to show the LIME results for the observation of interest, lines are drawn on top of the points.
+These lines  represent the boundaries of the indicator variables used to fit the explainer model.
+The line color  denotes whether LIME indicates that a feature supports or contradicts a class prediction.
 Appendix \ref{exp-scatter_plus} addresses the explanation scatterplot formats in other LIME simulation scenarios.
 
-\hh{An explanation scatterplot} \sout{for the} \kge{corresponding to the LIME explanation depicted on the left in \autoref{fig:sine-exp-scatter}} \sout{example of the previous section} \hh{is shown on the right hand side of \autoref{fig:sine-exp-scatter}.} %The points are the simulated values of $x_2$ versus $x_1$ colored by the random forest predictions and sized by the proximity weight used to fit the ridge regression explainer model.
+An explanation scatterplot corresponding to the LIME explanation depicted on the left in \autoref{fig:sine-exp-scatter} is shown on the right hand side of \autoref{fig:sine-exp-scatter}.
+%The points are the simulated values of $x_2$ versus $x_1$ colored by the random forest predictions and sized by the proximity weight used to fit the ridge regression explainer model.
 The explainer model is represented by the solid horizontal and vertical lines identifying the boundaries of the quantiles that contain the prediction of interest.
@@
 First, consider the claim of localness.
-The weights \kge{decay relatively slowly} \sout{remain relatively high} outside of the intersection of the two quantile bins suggesting that the LIME explanation is highly influenced by points outside of the bin\kge{s} containing the prediction of interest.
-\sout{While i} \kge{However,} it is \sout{still} difficult to say \kge{if} \sout{whether or not} the claim of localness has been violated\kge{, because a definition of a local region is not specified.
-Depending a the region a viewer considers to be local, an argument could be made in favor of or against a violation of localness.
+The weights decay relatively slowly  outside of the intersection of the two quantile bins suggesting that the LIME explanation is highly influenced by points outside of the bins containing the prediction of interest.
+However, it is  difficult to say if the claim of localness has been violated, because a definition of a local region is not specified.
+Depending on what region a viewer considers to be local, an argument could be made in favor of or against a violation of localness.
 The explanation scatterplot raises awareness of the unclear definition of a local region with LIME.
-Nevertheless,} it is possible to say that the weights assigned to the simulated data do not \kge{capture} \sout{agree with} the local region \kge{identified} \sout{assigned} by the intersection of the quantile bins.
-
-\kgc{I tried rewriting this paragraph to make it less "technical".
-See what you think.} Now, consider the claim of faithfulness.
-\kge{It can be said that the majority of the points in the $x_2$ quantile support a prediction of blue, which is captured by the bar supporting a prediction of blue in LIME explanation, and a similar statement can be said about the $x_1$ quantile bin.
+Nevertheless, it is possible to say that the weights assigned to the simulated data do not capture  the local region identified by the intersection of the quantile bins.
+
+%\kgc{I tried rewriting this paragraph to make it less "technical". See what you think.}\hh{I like it - the arguments are also more to the point }
+Now, consider the claim of faithfulness: It can be said that the majority of the points in the $x_2$ quantile support a prediction of blue, which is captured by the bar supporting a prediction of blue in the LIME explanation, and a similar statement can be made about the $x_1$ quantile bin.
 These statements validate the explanation produced by LIME.
-However, the explanation scatterplot plot shows that the random forest does a good job of capturing the sine curve classification boundary by creating various sized rectangles with similar probabilities, which the LIME explanation does not pick up on.
-Thus, LIME does provide an explanation for the prediction, but it is a very poor explanation in terms of faithfulness to the random forest prediction regions.}
-
-\sout{Within the intersection of the $x_1$ and $x_2$ quantile bins, there are more random forest probabilities above 0.5 \kge{than below}.
+However, the explanation scatterplot plot shows that the random forest performs well at capturing the sine curve classification boundary by creating various sized rectangles consisting of predictions with similar probabilities, which the LIME explanation does not pick up on.
+Thus, LIME does provide an explanation for the prediction, but it is a very poor explanation in terms of faithfulness to the random forest prediction regions.
+
+%\sout{Within the intersection of the $x_1$ and $x_2$ quantile bins, there are more random forest probabilities above 0.5 \kge{than below}.
 This indicates why the magnitude of the coefficient associated with $x_2$ is larger than that of $x_1$.
@@
 
-\sout{The explanation scatterplot shows issues with a definition of locality and an oversimplification of the random forest \kge{\sout{model}}.
+%\sout{The explanation scatterplot shows issues with a definition of locality and an oversimplification of the random forest \kge{\sout{model}}.
 LIME does provide an explanation for the prediction of interest, which makes sense based on the quantile bins used.
@@
 
-It is difficult to assess linearity from \kge{this} \sout{an} explanation scatterplot, but a residual plot of the explainer model could be used to check the linearity claim.
-See Appendix \ref{residual-plot} for the residual plot associated with the explanation considered in Figure \ref{fig:sine-exp-scatter}, which shows a violation of the linearity claim.
-
-\kge{This example} \sout{The \data \ } explanation only includes two features.
+It is difficult to assess linearity from this explanation scatterplot, but a residual plot of the explainer model could be used to check the linearity claim.
+See Appendix~\ref{residual-plot} for the residual plot associated with the explanation considered in Figure \ref{fig:sine-exp-scatter}, which shows a violation of the linearity claim.
+
+This example explanation only includes two features.
 In situations where more than two features are included in a LIME explanation, the explanation scatterplots can be extended to a generalized pairs plot \citep{emerson:2013} that includes all pairwise combinations of features.
-Generalized pairs plots (and scatterplot matrices in general) have diminishing value as the number of features increase \citep{jensen:2011} \citep{sweller:2011}.
+Generalized pairs plots (and scatterplot matrices in general) have diminishing value when the number of features increase \citep{jensen:2011} \citep{sweller:2011}.
 Machine learning models are commonly fit using a large number of features, and therefore, a generalized pairs plot of explanation scatterplots for all features would be ineffective.
 However, when applying LIME, the user selects the number of features to return in the explanation.
-In the \emph{lime} R package, \citet{pedersen:2020} encourage users to select less than 10 features \sout{to include in the explanation}.
-\kge{As long as a small number of features are returned in the LIME explanation,} \sout{As a result, specifying a small number of features to include in a LIME explanation makes} it \kge{is} feasible to use \kge{a} generalized pairs plot of explanation scatterplots.
-\kge{An example is shown in Section \ref{bullet-assess-ex}.}
+In the \emph{lime} R package, \citet{pedersen:2020} encourage users to select less than 10 features.
+As long as a small number of features are returned in the LIME explanation,  it is feasible to use a generalized pairs plot of explanation scatterplots.
+An example is shown in Section~\ref{bullet-assess-ex}.
 
@@
 \caption{Hypothetical examples of feature heatmaps in two possible situations.
-The heatmaps show the top feature chosen for 10 cases across 5 different sets of \sout{LIME} tuning parameters.
+The heatmaps show the top feature chosen for 10 cases across 5 different sets of  tuning parameters.
 The color of the cell indicates the feature chosen by LIME.
-\kge{Situation 1 is the ideal, because the explanations are not dependent on tuning parameter values.}}
+Situation 1 is the ideal, because the explanations vary across cases but do not dependent on specific tuning parameter values.}
 \label{fig:concept-feat-heat}
@@
 The colors of the tiles indicate the feature selected by LIME for the corresponding case and tuning parameter value.
-The plot is faceted by the first \kge{and second most important} features selected by LIME (top \kge{and bottom} facet\kge{s, respectively}) \sout{ and the second most important features (bottom facet).} \kge{The vertical facets separate the} \sout{The column facets separate the} kernel density method from the quantile bin methods.
+The plot is faceted by the first and second most important features selected by LIME (top and bottom facets, respectively).
+The vertical facets separate the  kernel density method from the quantile bin methods.
 The vertical striping indicates that the LIME explanations are not consistent across tuning parameters.}
@@
 Explanations produced by LIME are likely to be affected by the choice of tuning parameters.
-\sout{An} \kge{A hypothetical} example of this is shown by Figures \ref{fig:concept-plot-good} and \ref{fig:concept-plot-bad} where the method used to weight the observations influenced the explanation.
-As of the time of writing this manuscript, we have encountered no recommendations for how to \kge{specify the parameter values} \sout{determine which method to use} besides for the default settings in \emph{lime}.
-In order to compare the explanations produced by LIME using different tuning parameters \kge{and provide another perspective for assessing localness}, we visualize an overview \kge{of} the explanations \kge{with} \sout{in} the \emph{feature heatmap} diagnostic plot.
-
-The feature heatmap uses colors to identify the features selected by LIME \kge{across multiple predictions (referred to as cases here) and tuning paramter values} \sout{across tuning parameters for sets of explanations (referred to as cases here)} \kge{organized} \sout{faceted} by the \sout{position of} feature importance assigned by LIME.
-That is, for LIME applied with $t$ sets of tuning parameters to $n$ cases to select the $f$ top features, create $f$ heatmaps (one for each of the positions of importance determined by the magnitude of the explainer model coefficients) with the cases on the y-axis, the tuning parameters on the x-axis, and the cells colored by the feature chosen for the corresponding case and tuning parameter.
+A hypothetical example of this is shown by Figures \ref{fig:concept-plot-good} and \ref{fig:concept-plot-bad} where the method used to weight the observations influenced the explanation.
+As of the time of writing this manuscript, we have encountered no recommendations for how to specify the parameter values besides for the default settings in \emph{lime}.
+In order to compare the explanations produced by LIME using different tuning parameters and provide another perspective for assessing localness, we visualize an overview of the explanations with the \emph{feature heatmap} diagnostic plot.
+
+The feature heatmap uses colors to identify the features selected by LIME across multiple predictions (referred to as cases here) and tuning paramter values organized by the  feature importance assigned by LIME.
+That is, for LIME applied with $t$ sets of tuning parameters to $n$ cases to select the $f$ top features, create $f$ heatmaps (one for each of the positions of importance determined by the magnitude of the explainer model coefficients) with the cases on the $y$-axis, the tuning parameters on the $x$-axis, and the cells colored by the feature chosen for the corresponding case and tuning parameter.
 Additional tuning parameters may also be included in the plot via facets.
-\sout{This plot is used assess the locality of the explanations and to compare results from different input options.}
 
 Two hypothetical examples of feature heatmaps are included in \autoref{fig:concept-feat-heat}.
-The plots \kge{are} \sout{were} created with the assumption that LIME is applied to select the top feature out of $p=\kge{4}$ \sout{8} features for $n=10$ cases with $t=5$ sets of tuning parameters.
-Situation 1 \kge{is} \sout{shows} an example where the features selected are consistent across tuning parameters within a case but vary across cases within a tuning parameter.
+The plots are created with the assumption that LIME is applied to select the top feature out of $p=\kge{4}$  features for $n=10$ cases with $t=5$ sets of tuning parameters.
+Situation 1 is  an example where the features selected are consistent across tuning parameters within a case but vary across cases within a tuning parameter.
 This is the ideal situation, because the LIME explanations do not depend on the tuning parameters but do depend on the location of the observation in the feature space.
-Situation 2 \kge{is} \sout{shows} an example where the features selected vary across tuning parameters within a case but are consistent across cases within a tuning parameter.
-This situation indicates that the features selected by LIME are dependent on the tuning parameters, and the explanations \kge{may not be} \sout{are not} local, because the same feature is chosen regardless of the case.
+Situation 2 is an example where the selected features  vary across tuning parameters within a case but are consistent across cases within a tuning parameter.
+This situation indicates that the features selected by LIME are dependent on the tuning parameters, and the explanations may not be  local, because the same feature is chosen regardless of the case.
 In practice, it is expected that the plot will exhibit a combination of these two situations.
 
-\autoref{fig:sine-feat-heat} shows \kge{a} \sout{the} feature heatmap for the LIME applications to the 100 observations in the \data \ test set.
-The most important \kge{and second most important features selected by lime are showin in the top and bottom facets, respectively.} \sout{(top facet) and second most important (bottom facet) features are shown in this plot.} For the quantile bins, the original features prior to the indicator variable transformation are included since it is obvious that different features would be selected when the sizes of the bins change.
+\autoref{fig:sine-feat-heat} shows a feature heatmap for the LIME applications to the 100 observations in the \data \ test set.
+The most important and second most important features selected by lime are showin in the top and bottom facets, respectively.
+For the quantile bins, the original features prior to the indicator variable transformation are included since it is obvious that different features would be selected when the sizes of the bins change.
 This figure shows that for kernel density and 2 quantile bins, LIME selects $x_1$ as the most important feature and $x_2$ as the second most important feature across all cases in the test set.
 These explanations are not local.
-There is variability in the features selected by LIME for 3 to 6 quantile bins \kge{suggesting more local explanations}.
-\sout{For these tuning parameters, there is a mix of horizontal and vertical stripes,} \kge{There are signs of vertical striping,} which suggests a dependence on tuning parameters.
+There is variability in the features selected by LIME for 3 to 6 quantile bins suggesting more local explanations.
+There are signs of vertical striping, which suggests a dependence on tuning parameters.
 Note that the explanations from 3 and 5 quantile bins include the selection of the random noise variable ($x_3$) as an important variable in many predictions, which should not be the case.
@@
 Each horizontal facet corresponds to one of three metrics: average $R^2$, average fidelity, or MSEE.
-The LIME tuning parameter \kge{values} (simulation methods in this example) \kge{are} \sout{is} plotted on the x-axis, and the metric values are shown on the y-axis.
+The LIME tuning parameter values (simulation methods in this example) are plotted on the x-axis, and the metric values are shown on the y-axis.
 The points are colored by rank (within a metric) indicating best to worst (dark to light).
-The kernel density simulation methods performs well \kge{across} \sout{according to} all three metrics.}
+The kernel density simulation methods performs well across all three metrics.}
 \label{fig:sine-assess-metric}
@@
 
-Each metric presented below is computed on a \sout{set of} LIME explanations \kge{for a set of predictions} obtained using the \sout{the} same tuning parameters.
+Each metric presented below is computed on  LIME explanations for a set of predictions obtained using the same tuning parameters.
 Here we provide a high level description of the metrics.
@@
 
-\autoref{fig:sine-assess-metric} shows \kge{an example assessment metric plot}.
-\sout{these} \kge{The three} metrics \kge{are} computed for each of the LIME applications to the \data \ test set.
+\autoref{fig:sine-assess-metric} shows an example assessment metric plot.
+The three metrics are computed for each of the LIME applications to the \data \ test set.
 The simulation methods are listed on the x-axis.
@@
 
-All three metrics suggest that the kernel density \kge{method} performed well, but the metrics disagree for the quantile bins methods.
+All three metrics suggest that the kernel density method performed well, but the metrics disagree for the quantile bins methods.
 Average $R^2$ and average fidelity rank the performance of the number of quantile bins the same (2 quantile bins perform the best and 6 quantile bins perform the worst).
-In fact, these two metrics appear to have \kge{a mirrored} \sout{an inverse} relationship in this example.
-MSEE provides \kge{almost the exact opposite results with} \sout{different ranks of the simulation methods.
-MSEE suggests that} 6 quantile bins perform\kge{ing} the best\sout{,} and 2 quantile bins perform\kge{ing} the worst.
-\sout{This is the opposite of average $R^2$ and average fidelity.} Since average fidelity and MSEE are similar metrics, it would be expected that they would agree, but that is so in this example.
-This may be due to the MSEE only taking into account the prediction of interest and not the full simulated dataset.
-The contradiction between metrics makes it difficult to identify which simulation method \sout{explanations} to trust.
-
-Recall that \autoref{fig:sine-feat-heat} indicated that the \sout{LIME} kernel density method selected the same feature across all cases in the test set for both the first and second features.
+In fact, these two metrics appear to have a mirrored  relationship in this example.
+MSEE provides almost the exact opposite results with  6 quantile bins performing the best and 2 quantile bins performing the worst.
+Average fidelity and MSEE are similar metrics, so it is not surprising that they would agree in this example.
+Another factor might be that MSEE only takes the prediction of interest  into account and not the full simulated dataset.
+The contradiction between metrics makes it difficult to identify which simulation method to trust.
+
+Recall that \autoref{fig:sine-feat-heat} indicated that the kernel density method selected the same feature across all cases in the test set for both the first and second features.
 It appears that a global trend may be the best explanation for this example, which may be reasonable considering that we know that both $x_1$ and $x_2$ are the two features that should be the features used by the random forest to distinguish between response categories.
@@
 
-In current practice, forensic firearm examiners evaluate whether two bullets are from the same source (fired from the same gun) or from different sources based on \kge microscopic comparison of the striation patterns engraved on bullets during the firing process (see \autoref{fig:bullet}).
+In current practice, forensic firearm examiners evaluate whether two bullets are from the same source (fired from the same gun) or from different sources based on microscopic comparison of the striation patterns engraved on bullets during the firing process (see \autoref{fig:bullet}).
 The process is based on a visual and therefore subjective assessment of the evidence.
@@
 In response, \citet{hare:2016} proposed an automated machine learning method for bullet matching to complement a visual inspection by firearm examiners.
-Based on high-resolution topological scans of land engraved areas\kge{,} \citet{hare:2016} obtain signatures of striations from two bullet lands (\autoref{fig:signatures}).
-Nine features quantifying the similarity of signatures, such as the cross-correlation function, the distance between signatures, and the number of matching striae, are extracted and used to train a random forest \kge{\sout{model}} (available in the \emph{bulletxtrctr} R package) to determine the probability of a comparison resulting from the same source (matching signatures) or from different sources (non-matching signatures).
+Based on high-resolution topological scans of land engraved areas, \citet{hare:2016} obtain signatures of striations from two bullet lands (\autoref{fig:signatures}).
+Nine features quantifying the similarity of signatures, such as the cross-correlation function, the distance between signatures, and the number of matching striae, are extracted and used to train a random forest  (available in the \emph{bulletxtrctr} R package) to determine the probability of a comparison resulting from the same source (matching signatures) or from different sources (non-matching signatures).
 The model was trained on a set of scans of bullets from the James Hamby Consecutively Rifled Ruger Barrel Study \citep{hamby:2009}, which includes \Sexpr{dim(bullet_train)[1]} land-to-land comparisons.
@@
 \caption{Example bullet signatures.
-The bullet signatures are from the same barrel \kge{and} land and therefore have very similar patterns.
-The \citet{hare:2016} random forest \kge{is fit using various} \sout{uses} features that measure the similarity between two such signatures.}
+The bullet signatures correspond to the same land \hh{XXX barrel land is actually a standing term, meaning the physical land in the barrel that created the striation.
+Obviously it is confusing, so I got rid of the 'barrel'.} and therefore have very similar patterns.
+The \citet{hare:2016} random forest is fit using various features that measure the similarity between two such signatures.}
 \label{fig:signatures}
@@
 
-We apply the random forest \kge{\sout{model}} from \citet{hare:2016} to another set of bullets from the Hamby study with \Sexpr{dim(bullet_test)[1]} rows of land comparisons.
-We first consider a global visualization of the relationship between the random forest predictions and the model features \kge{with} \sout{by creating} a parallel coordinate plot of the training data (top facet) and testing data (bottom facets) predictions (\autoref{fig:bullet-plot-rfpcp}).
+We apply the random forest  \kge{\sout{model}} \hh{XXX I would actually prefer to leave the model in here.
+applying a random forest sounds like you applied he methodology to the data.
+But you got predictions based on the model previously fitted by Eric.
+That's a difference} from \citet{hare:2016} to another set of bullets from the Hamby study with \Sexpr{dim(bullet_test)[1]} rows of land comparisons.
+We first consider a global visualization of the relationship between the random forest predictions and the model features with  a parallel coordinate plot of the training data (top facet) and testing data (bottom facets) predictions (\autoref{fig:bullet-plot-rfpcp}).
 The majority of same source observations with random forest probabilities close to 1 have a clear pattern of corresponding feature values.
@@
 
-LIME \sout{is implemented using the R package \emph{limeaid} to apply LIME} \kge{is applied} \sout{multiple times} to all test set observations using different tuning parameters: 12 sampling methods (2-6 equally spaced bins, 2-6 quantile bins, kernel density estimation, and normal approximation) and 3 Gower exponents (0.5, 1, and 10).
-Thus, a total of $12\times 3=36$ different applications of LIME \kge{are} \sout{were} performed.
-We specify that each LIME explanation return 3 features and feature selection is performed \kge{by selecting the features with the highest weights in a ridge regression model} \sout{using the highest weights method} (default option).
+LIME is applied to all test set observations using different tuning parameters: 12 sampling methods (2-6 equally spaced bins, 2-6 quantile bins, kernel density estimation, and normal approximation) and 3 Gower exponents (0.5, 1, and 10).
+Thus, a total of $12\times 3=36$ different applications of LIME are performed.
+We specify that each LIME explanation return 3 features and feature selection is performed by selecting the features with the highest weights in a ridge regression model (default option).
 
@@
 To get an overview of the LIME explanations from the 36 applications, we consider a feature heatmap (\autoref{fig:bullet-feature-heatmap}).
-In addition to facets for simulation method and \kge{LIME feature importance} \sout{order of feature selected by LIME}, this plot includes a vertical facet for Gower power and a horizontal facet for whether the observation is a known match or non-match.
+In addition to facets for simulation method and LIME feature importance, this plot includes a vertical facet for Gower power and a horizontal facet for whether the observation is a known match or non-match.
 This plot highlights several key features of the LIME explanations from the bullet matching dataset.
@@
 @
-\caption{Feature heatmap of \sout{the} 36 LIME applications to the bullet comparison data test set.
+\caption{Feature heatmap of  36 LIME applications to the bullet comparison data test set.
 In addition to faceting the results by simulation method and LIME feature selection order, facets for the Gower power and whether the observation is a match or non-match are included.
@@
 @
-\caption{\kge{Assessment metric plot} \sout{Plot of LIME assessment metrics} for the applications of LIME on the bullet comparison data test set.
+\caption{Assessment metric plot for the applications of LIME on the bullet comparison data test set.
 The density simulation methods perform well for all metrics.
@@
 
-Figure \ref{fig:bullet-eois} include\kge{s} the \kge{visual representation plots of explanations} \sout{explanation plots} (from \emph{lime}) and explanation scatterplots for cases M and NM.
+Figure \ref{fig:bullet-eois} includes the visual representation plots of explanations (from \emph{lime}) and explanation scatterplots for cases M and NM.
 Plots for 3 equal bins and 3 quantile bins are included.
-Plots for the kernel density simulation method are included in \kge{Appendix \ref{exp-scatter_plus} (}Figure \ref{fig:bullet-expl-scat-density}\kge{)}.
+Plots for the kernel density simulation method are included in Appendix~\ref{exp-scatter_plus} (Figure \ref{fig:bullet-expl-scat-density}).
 The scatterplots provide several insights into the LIME explanations.
-Here we focus on the explanation for case NM with 3 quantile bins, but similar statements can be made about the other plots.
+Here, we focus on the explanation for case NM with 3 quantile bins, but similar statements can be made about the other plots.
 \kgc{I've been thinking about the examples I chose to include, and I have a couple of questions.
 First, is it okay to include all of these plots when I am only discussing one?
-Second, I'm not sure why I chose to list 3 quantile bins as a "good" tuning parameter value anymore based on the assessment metric plot.
+\hh{What's the reason that you are not discussing the other ones?
+I can see a case in favor because of the similar structure - that makes the plots appear like from a template, which is the effect we are going after.} Second, I'm not sure why I chose to list 3 quantile bins as a "good" tuning parameter value \hh{I think the argument was to have something along the lines of low, medium, high} anymore based on the assessment metric plot.
 I don't know that I agree with that anymore.
@@
 Based on the scatter plot of CCF versus matches, a better explanation would be that because case NM has a value of CCF less than 0.8 and a value of matches less than 7, the random forest provides a prediction supporting a non-match.
-The relationship between CCF and rough correlation does not provide much evidence to support the random forest prediction one way or the other, but there is a pentagon shaped region at the bottom of the scatter plot of matches versus rough correlation with mostly predictions close to 0 that case NM falls \kge{in} and supports the random forest prediction of a non-match.
+The relationship between CCF and rough correlation does not provide much evidence to support the random forest prediction one way or the other, but there is a pentagon shaped region at the bottom of the scatter plot of matches versus rough correlation with mostly predictions close to 0 that case NM falls in and supports the random forest prediction of a non-match.
 
@@
 @
-\caption{Plots of LIME explanations \kge{(first and third rows)} and explanation scatterplots \kge{(second and fourth rows)} for \sout{one} case\kge{s} M and NM in the bullet test data \kge{for two tuning parameter values: 3 quantile bins (first column) and 3 equal bins (second column)}.
-\sout{The first column contains plots associated with 3 quantile bins and the second with 3 equally spaced bins.} The plots provide insights into the LIME explanations and allow for the assessment of the explanation quality.}
+\caption{Plots of LIME explanations (first and third rows) and explanation scatterplots (second and fourth rows) for  cases M and NM in the bullet test data for two tuning parameter values: 3 quantile bins (first column) and 3 equal bins (second column).
+The plots provide insights into the LIME explanations and allow for the assessment of the explanation quality.}
 \label{fig:bullet-eois}
@@
 
-Without applying LIME with multiple tuning parameter\sout{s} \kge{values} to the bullet test data or viewing diagnostic plots of the LIME explanations, it may be very possible to formulate reasons why the LIME explanations make sense.
+Without applying LIME with multiple tuning parameter values to the bullet test data or viewing diagnostic plots of the LIME explanations, it may be very possible to formulate reasons why the LIME explanations make sense.
 However, the sequence of plots in this section (Figures \ref{fig:bullet-feature-heatmap}, \ref{fig:bullet-assess-metric}, and \ref{fig:bullet-eois}) suggest that we should be cautious to trust any of these LIME explanations.
@@
 
-The visualizations are intended to provide insight on how LIME works, assess the ability of the explainer model to capture the complex predictive model, and compare LIME explanations produced by different tuning parameter\sout{s} \kge{values}.
+The visualizations are intended to provide insight on how LIME works, assess the ability of the explainer model to capture the complex predictive model, and compare LIME explanations produced by different tuning parameter values.
 While the visualizations accomplish these tasks, they also expose examples of the failings of LIME.
@@
 
-As previously discussed, the \textbf{interpretability} of the LIME explanations \kge{is controllable} \sout{can be controlled} by the complexity of the explainer model.
+As previously discussed, the \textbf{interpretability} of the LIME explanations is controllable  by the complexity of the explainer model.
 For example, the number of bins selected for simulation can control the interpretability of the explanations.
@@
 For example, the visualization of a LIME explanation available from the \emph{lime} R package \citep{pedersen:2020} (shown in Figures \ref{fig:sine-exp-scatter} and \ref{fig:bullet-eois}) is a major simplification of the explainer model, which could lead to under-interpreted or misinterpreted LIME explanation.
-Supplementing \citet{pedersen:2020}'s compact visualization of the explanation with an explanation scatterplot that shows a more detailed visualization of the explainer model (such as Figures \ref{fig:sine-exp-scatter} and \ref{fig:bullet-eois}) promotes a \kge{more complete understanding} \sout{full interpretation} of the explanation.
+Supplementing \citet{pedersen:2020}'s compact visualization of the explanation with an explanation scatterplot that shows a more detailed visualization of the explainer model (such as Figures~\ref{fig:sine-exp-scatter} and \ref{fig:bullet-eois}) promotes a more complete understanding of the explanation.
 
@@
 The explanation scatterplots allow for a comparison of the explainer model to the complex model.
-The examples in this paper show cases where the explainer model bins do not accurately capture the \kge{regions with similar random forest probabilities that contain the prediction of interest} \sout{classification boundaries near the predictions of interest of the random forest\kge{s \sout{models}} by} \kge{and} oversimplify\sout{ing} the model (Figures \ref{fig:sine-exp-scatter} and \ref{fig:bullet-eois}).
-Using less bins would clearly not help improve the faithfulness of the explainer model in these examples, and while an increase in bins would lead to a finer resolution of the random forest classification boundaries, interpretability of the explainer model would quickly be lost.
+The examples in this paper show cases where the explainer model bins do not accurately capture the regions with similar random forest probabilities that contain the prediction of interest and oversimplify the model (Figures \ref{fig:sine-exp-scatter} and \ref{fig:bullet-eois}).
+Using \hh{fewer \sout{less}} bins would clearly not help improve the faithfulness of the explainer model in these examples, and while an increase in \hh{the number of} bins would lead to a finer resolution of the random forest classification boundaries, interpretability of the explainer model would quickly be lost.
 Perhaps this could be improved by allowing the bin creation to account for the relationships between the features and response variable or a different number of bins for each feature.
@@
 In addition to assessing faithfulness by visually comparing the complex and explainer model, we propose a visual comparison of two faithfulness metrics (MSEE and average fidelity).
-The examples of faithfulness metric comparisons in this paper (Figures \ref{fig:sine-assess-metric} and \ref{fig:bullet-assess-metric}) both produced confusing results.
-The density based simulation methods result\sout{ed} in the best or close to the best performance even though the feature heatmaps (Figures \ref{fig:sine-feat-heat} and \ref{fig:bullet-feature-heatmap}) show\sout{ed} that the density simulation methods produce\sout{d} global explanations with \kge{minimal} \sout{no} variation in features selected by LIME.
-For the bin based simulation methods, the two metrics often \kge{do} \sout{did} not agree or contradict\sout{ed} one another, which makes it difficult to decide on a recommendation of a set of tuning parameters that produces the explanations with the most faithful explainer model.
+The examples of faithfulness metric comparisons in this paper (Figures \ref{fig:sine-assess-metric} and \ref{fig:bullet-assess-metric}) both produced confusing \hh{XX conflicting?} results.
+The density based simulation methods result in the best or close to the best performance even though the feature heatmaps (Figures \ref{fig:sine-feat-heat} and \ref{fig:bullet-feature-heatmap}) show that the density simulation methods produce global explanations with minimal variation in features selected by LIME.
+For the bin based simulation methods, the two metrics often do not agree or contradict one another, which makes it difficult to decide on a recommendation of a set of tuning parameters that produces the explanations with the most faithful explainer model.
 
@@
 
-The final claim, \textbf{localness}, is addressed by the feature heatmap and metric comparison plot\kge{s}.
-As stated, the feature heatmap reveal\kge{s}\sout{ed} that the density simulation methods in the examples of this paper result\kge{s}\sout{ed} in global explanations where the same features \kge{are} \sout{were} repeatedly chosen across all (or almost all) observations in the set of explanations.
-This finding agrees with that of \citet{laugel:2018} who found LIME produced global explanations with the normal approximation simulation method.
+The final claim, \textbf{localness}, is addressed by the feature heatmap and metric comparison plots.
+As stated, the feature heatmap reveals that the density simulation methods in the examples of this paper results in global explanations where the same features are repeatedly chosen across all (or almost all) observations in the set of explanations.
+This finding agrees with that of \citep{laugel:2018} who found LIME produced global explanations with the normal approximation simulation method.
 For the bin based simulation methods in the bullet data example, the feature heatmap showed that the features chosen for the explanations varied between the two classification categories (match versus non-match).
-This is an interesting finding that suggests that different features can play a role in the predictions of observations in different response categories\kge{.} \sout{, but the patterns of features selected by LIME within a classification category do not vary.
-Again, this is a suggestion of global explanations.} \kgc{I'm not sure what I was trying to say there.} Furthermore, while the metric comparison plot in the bullet example did not provide agreement between metrics on a best bin based method, all metrics agree that a Gower power of 0.5 for computing the model weights associated with distance of a simulated data point from the prediction of interest is best.
-This suggests that a less local explanation provided a better explanation of the performance of the random forest.
+This is an interesting finding that suggests that different features can play a role in the predictions of observations in different response categories.
+Furthermore, while the metric comparison plot in the bullet example does not provide agreement between metrics on a best bin based method, all metrics agree that a Gower power of 0.5 for computing the model weights associated with distance of a simulated data point from the prediction of interest is the best.
+This suggests that a less local explanation provides a better explanation of the performance of the random forest.
 
@@
 The addition of interactivity to the diagnostic plots would provide additional enhancement of the assessment process.
-For example, a diagnostic plot that provides a summary of multiple LIME explanations, such as the feature heatmap, could be displayed and clicked on to reveal more detailed figures associated with individual predictions of interest, such as \kge{an explanation scatterplot.} \sout{plots of the simulated data and explainer model.}
+For example, a diagnostic plot that provides a summary of multiple LIME explanations, such as the feature heatmap, could be displayed and clicked on to reveal more detailed figures associated with individual predictions of interest, such as an explanation scatterplot.
 
@@
 Fortunately, in the situation of LIME, both of these aspects are rather well controlled: LIME relies heavily on simulations to generate data scenarios that are close to the data observed but exhibits variability.
-Effects from overplotting should be relatively mild, because output from simulations is shown, which is expected to be (relatively) continuous \hh{such that overplotting only occurs for points with (relatively) similar values.} \kgc{What do you mean by continuous here?}.
+Effects from overplotting should be relatively mild, because output from simulations is shown, which is expected to be (relatively) continuous such that overplotting only occurs for points with (relatively) similar values.
+%\kgc{What do you mean by continuous here?}.
 \hh{XXX Does that extra explanation help?} \kgc{Yes.
-I see what you mean now.} In that respect, the diagnostics shown for the \data \ and \sout{in} the bullet example are representative of what is expected.
+I see what you mean now.}
+In that respect, the diagnostics shown for the \data \ and \sout{in} the bullet example are representative of what is expected.
 But in cases where overplotting does become problematic, the user could either simply reduce the size of the simulations or use some well-studied binning techniques in the visualizations, as discussed for example in \citet{carr:1987} or \citet{unwin:2006}.
@@
 The examples using diagnostic plots to assess LIME in this paper show frequent issues with LIME.
-We hope that our plots provide motivation to assess LIME explanations, to not blindly use the default settings (even if it is not clear \kge{how to tune the parameters} \sout{which tuning parameters to use}), and to encourage work on improving LIME, so that it can be a lime and not a lemon.
+We hope that our plots provide motivation to assess LIME explanations, to not blindly use the default settings (even if it is not clear how to tune the parameters), and to encourage work on improving LIME, so that it can be a lime and not a lemon.
 
@@
 
-\kge{Should this go under the financial disclosure section?
+%\kge{Should this go under the financial disclosure section?
 Also, what is the financial disclosure section meant to contain?
 I couldn't find it described on the ASA data science journal author guidelines page.
-Should we remove it?} HH was partially funded by the Center for Statistics and Applications in Forensic Evidence (CSAFE) through Cooperative Agreement 70NANB20H019 between NIST and Iowa State University, which includes activities carried out at Carnegie Mellon University, Duke University, University of California Irvine, University of Virginia, West Virginia University, University of Pennsylvania, Swarthmore College and University of Nebraska, Lincoln.
+Should we remove it?} \hh{financial disclosures are used to determine conflicts of interest -  like getting funded by the robacco industry and promoting the health benefits of smoking.
+}
+HH was partially funded by the Center for Statistics and Applications in Forensic Evidence (CSAFE) through Cooperative Agreement 70NANB20H019 between NIST and Iowa State University, which includes activities carried out at Carnegie Mellon University, Duke University, University of California Irvine, University of Virginia, West Virginia University, University of Pennsylvania, Swarthmore College and University of Nebraska, Lincoln.
 
 \subsection*{Author contributions}
-
-\hh{A taxonomy of author contributions is suggested by Elsevier - I put the link in an email}
 
@@
 The following supporting information is available as part of the online article: \kgc{What should we list here?}
+\hh{This is like a table of contents for the appendix.}
 

### 2020-08-28 paper.Rnw
changes based on discussion in meeting

@@
 % Set up for ASA data science journal
-\articletype{\kge{Research Article}}
-\received{\kge{XX August 2020}}
-\revised{\kge{XX XX XXXX}}
-\accepted{\kge{XX XX XXXX}}
+\articletype{Research Article}
+\received{XX XX 2020}
+\revised{XX XX XXXX}
+\accepted{XX XX XXXX}
 \raggedbottom
@@
 Here we introduce three visual diagnostics to assess the quality of LIME explanations: (1) explanation scatterplots, (2) assessment metric plots, and (3) feature heatmaps.
-We apply the visual diagnostics to a forensics bullet matching dataset to show examples where LIME explanations depend on the tuning parameters and the explainer model oversimplifies the black-box model.
+We apply the visual diagnostics to a forensics bullet matching dataset to show examples where LIME explanations depend on the tuning parameter values and the explainer model oversimplifies the black-box model.
 Our examples raise concerns about claims made of LIME \citep{ribeiro:2016} that are similar to other criticisms in the literature \citep{alvarezmelis:2018, laugel:2018, molnar:2019}.}
@@
 However, a practical implementation of LIME is not straightforward, and research is being done to improve the procedure \citep{laugel:2018}.
-The current implementations of LIME \citep{ribeiro:2020} \kgc{Is there a better way to cite a Python package?} \hh{might be good to model the python package reference after the R package references, have a loog at reference limepy} \kgc{I kept thinking about this, and since the Python pakcgae doesn't have a manual, I ended up combining your limepy reference with the second second suggestion from https://academia.stackexchange.com/questions/14010/how-do-you-cite-a-github-repository.
-For now, I listed Ribeiro as the author, because he is the main contributor, but there are 40 other contributors to the package.
-Is it okay to just list Ribeiro?}\hh{I would go with 'and contributors' - if we just cite Ribeiro people might not realize that it's truly not just him.} \citep{pedersen:2020} offer various tuning parameters (see Section \ref{background}) that affect the explainer model and ultimately, the explanation.
+The current implementations of LIME \citep{ribeiro:2020} \citep{pedersen:2020} offer various tuning parameters (see Section \ref{background}) that affect the explainer model and ultimately, the explanation.
 Since the explainer model is an approximation of the complex model and not a direct interpretation, the explanations produced by an explainer model are subject to the quality of the approximation.
-Thus, in order to achieve accurate explanations, the tuning parameters selected need to be assessed.
+Thus, in order to achieve accurate explanations, the tuning parameter values selected need to be assessed.
 
@@
 
-\citet{ribeiro:2016} provide an implementation of LIME in a Python package \cite{limepy}.
+\citet{ribeiro:2016} provide an implementation of LIME in a Python package \cite{ribeiro:2020}.
 An adaption of the Python package in R has been implemented and made available by Thomas Lin-Pedersen \citep{pedersen:2020}.
@@
 \item \emph{Explanation Scatterplot} (Section \ref{exp-scatter}): Comparison of the explainer and complex models for an individual prediction of interest.
-\item \emph{Feature Heatmap} (Section \ref{feat-heat}): Comparison of features selected by LIME across applications of LIME with different tuning parameters.
-\item \emph{Assessment Metric Plot} (Section \ref{assess-metric}): Comparison of performance metrics for LIME across applications of LIME with different tuning parameters. 
+\item \emph{Feature Heatmap} (Section \ref{feat-heat}): Comparison of features selected by LIME across applications of LIME with different tuning parameter values.
+\item \emph{Assessment Metric Plot} (Section \ref{assess-metric}): Comparison of performance metrics for LIME across applications of LIME with different tuning parameter values. 
 \end{enumerate}
@@
 
-We apply LIME using six sets of tuning parameters to all observations in the \data \ test set to observe variability across tuning parameters.
+We apply LIME using six sets of tuning parameter values to all observations in the \data \ test set to observe variability across tuning parameter values.
 A quantile bin based simulation method (samples are simulated uniformly from a specified number of quantile bins) is used for five of the LIME applications with the number of bins varying from 2 to 6 by application.
@@
 The points represent the simulated data colored by the random forest probabilities and sized by the assigned LIME weights.
-%\hh{XXX could you make the complex prediction **much** lighter for this example?
-The diamond and the lines are hard to see, but should be the focus.} \kgc{Is that light enough?
-Feel free to edit the alpha value in the plot\_explain\_scatter function as you feel necessary.
-I also made the lines depicting the explainer model wider in limeaid, and there is an option 'line\_size' that can be adjusted.} \hh{thank you!}
 The prediction of interest is shown as the diamond shaped point.
@@
 
-%\subsection{A LIME explanation}
-
 \paragraph{A Visual Representation of a LIME Explanation}
-
-%\kgc{I really like the idea of separating the description of the \emph{lime} figure from the explanation scatterplot, but the more I think about it, I don't like that it get it's own sub-section.
-I think it would be nicer to allocate the sub-sections to the visual diagnostic plots.
-Instead, I switched to using a heading like you created for introducing the sine data.
-I also changed the wording of the heading a bit.
-What do you think?
-Another option would be to drop the heading altogether and flow into the next paragraph.} \hh{XXX I've just pulled the description of the left hand side of figure 4 out of the next section.}
-\hh{XXX I like the idea of not giving this section an official header, but I like the way it looks like now with the bold header - that should help the reader what's going on.}
 
@@
 In particular, the explanation is obtained using 4 quantile bins to simulate the data.
-%\kgc{I moved the next few sentences here from the sub-section.}
 In this scenario, LIME converts continuous predictor variables to indicator variables identifying whether the variable value falls in the same quantile bin as the prediction of interest or not.
@@
 Since the weight associated with $x_2$ has a larger magnitude than the weight associated with $x_1$, LIME explains that $x_2$ plays a more important role in the random forest prediction.
-Additionally, consider that since the support for blue by $x_2$ outweights the support for red by $x_1$, the explainer model overall favors a label of blue for the prediction of interest, which agrees with the random forest probability of \Sexpr{sine_poi_lime_default$label_prob[1]} for blue.
+Additionally, consider that since the support for blue by $x_2$ outweighs the support for red by $x_1$, the explainer model overall favors a label of blue for the prediction of interest, which agrees with the random forest probability of \Sexpr{sine_poi_lime_default$label_prob[1]} for blue.
 Note that both models classify the observation incorrectly.
 
-%\hh{Because the support for blue by the value of feature $x_1$ outweighs the support for red by the value of feature $x_2$, the overall LIME explanation favors a label of blue for the prediction of interest.} \kgc{I don't think this statement is quite right.}
-
-%Since the weight associated with $x_2$ has a larger magnitude than the weight associated with $x_1$, LIME explains that the $x_1$ and $x_2$ locations of the prediction of interest provide more support for a random forest classification of blue over red.
-
 \subsection{Explanation Scatterplots} \label{exp-scatter}
-%\hh{XXX I think we could reduce some of the example for the specific example a bit, now that the LIME explanation is moved out, there is not that much need to repeat the general ideas.} \kgc{I commented out the text that I think you were referring to.
-See what you think.}
-
-%\kgc{I moved the next sentence here from the previous paragraph.} 
+
 Based on the plot on the left of \autoref{fig:sine-exp-scatter} alone, it is not possible to make an informed assessment of the explanation.
@@
 An explanation scatterplot corresponding to the LIME explanation depicted on the left in \autoref{fig:sine-exp-scatter} is shown on the right hand side of \autoref{fig:sine-exp-scatter}.
-%The points are the simulated values of $x_2$ versus $x_1$ colored by the random forest predictions and sized by the proximity weight used to fit the ridge regression explainer model.
-The explainer model is represented by the solid horizontal and vertical lines identifying the boundaries of the quantiles that contain the prediction of interest.
-The color of the lines indicate whether the explainer model coefficient is positive (blue) or negative (red).
-Thus, the $x_2$ coefficient is positive, so the $x_2$ value of the prediction of interest supports a random forest prediction of `blue', and the $x_1$ coefficient is negative, so the $x_1$ value of the prediction of interest contradicts a random forest prediction of `blue'.
-The prediction of interest is represented by the diamond shaped point.
 By juxtaposing the random forest predictions and the explainer model boundaries, we are able to assess the faithfulness and localness of the explainer model.
@@
 
-%\kgc{I tried rewriting this paragraph to make it less "technical". See what you think.}\hh{I like it - the arguments are also more to the point }
 Now, consider the claim of faithfulness: It can be said that the majority of the points in the $x_2$ quantile support a prediction of blue, which is captured by the bar supporting a prediction of blue in the LIME explanation, and a similar statement can be made about the $x_1$ quantile bin.
@@
 Thus, LIME does provide an explanation for the prediction, but it is a very poor explanation in terms of faithfulness to the random forest prediction regions.
-
-%\sout{Within the intersection of the $x_1$ and $x_2$ quantile bins, there are more random forest probabilities above 0.5 \kge{than below}.
-This indicates why the magnitude of the coefficient associated with $x_2$ is larger than that of $x_1$.
-However, the pattern of the random forest predictions in this plot suggest that better explanations for this prediction exist.
-One example of a better explanation is to say that the prediction of interest received a random forest prediction greater than 0.5 since the observation of interest falls in the region where $x_1$ is less than 2.5 and $x_2$ is greater 4.5.
-A more localized explanation is to say that the region around the prediction of interest shows that observations with $-0.3 < x_1 <= 2.5$ and $4.8 < x_2 <= 8.75$ are all assigned probabilities greater than 0.5.
-The procedure implemented by LIME is not flexible enough to capture either of these explanations.}
-
-%\sout{The explanation scatterplot shows issues with a definition of locality and an oversimplification of the random forest \kge{\sout{model}}.
-LIME does provide an explanation for the prediction of interest, which makes sense based on the quantile bins used.
-However, the explanation scatterplot identifies that better explanations for the prediction of interest exist.}
 
@@
 \caption{Hypothetical examples of feature heatmaps in two possible situations.
-The heatmaps show the top feature chosen for 10 cases across 5 different sets of  tuning parameters.
+The heatmaps show the top feature chosen for 10 cases across 5 different sets of tuning parameter values.
 The color of the cell indicates the feature chosen by LIME.
@@
 
-<<sine-feat-heat, out.width = '0.45\\textwidth', fig.width = 4, fig.height = 4>>=
+<<sine-feat-heat, out.width = '0.45\\textwidth', fig.width = 4, fig.height = 4.5>>=
 plot_feature_heatmap(sine_lime_explain$explain,
@@
 \caption{\emph{Feature Heatmap}.
-An example feature heatmap of the explanations from the applications of LIME with different tuning parameters to the \data \ test set.
+An example feature heatmap of the explanations from the applications of LIME with different tuning parameter values to the \data \ test set.
 The cases from the test set are plotted on the y-axis, and the tuning parameter values (simulation methods here) are included on the x-axis.
@@
 The vertical facets separate the  kernel density method from the quantile bin methods.
-The vertical striping indicates that the LIME explanations are not consistent across tuning parameters.}
+The vertical striping indicates that the LIME explanations are not consistent across tuning parameter values.}
 \label{fig:sine-feat-heat}
@@
 
-Explanations produced by LIME are likely to be affected by the choice of tuning parameters.
+Explanations produced by LIME are likely to be affected by the choice of tuning parameter values.
 A hypothetical example of this is shown by Figures \ref{fig:concept-plot-good} and \ref{fig:concept-plot-bad} where the method used to weight the observations influenced the explanation.
 As of the time of writing this manuscript, we have encountered no recommendations for how to specify the parameter values besides for the default settings in \emph{lime}.
-In order to compare the explanations produced by LIME using different tuning parameters and provide another perspective for assessing localness, we visualize an overview of the explanations with the \emph{feature heatmap} diagnostic plot.
-
-The feature heatmap uses colors to identify the features selected by LIME across multiple predictions (referred to as cases here) and tuning paramter values organized by the  feature importance assigned by LIME.
-That is, for LIME applied with $t$ sets of tuning parameters to $n$ cases to select the $f$ top features, create $f$ heatmaps (one for each of the positions of importance determined by the magnitude of the explainer model coefficients) with the cases on the $y$-axis, the tuning parameters on the $x$-axis, and the cells colored by the feature chosen for the corresponding case and tuning parameter.
+In order to compare the explanations produced by LIME using different tuning parameter values and provide another perspective for assessing localness, we visualize an overview of the explanations with the \emph{feature heatmap} diagnostic plot.
+
+The feature heatmap uses colors to identify the features selected by LIME across multiple predictions (referred to as cases here) and tuning parameter values organized by the  feature importance assigned by LIME.
+That is, for LIME applied with $t$ sets of tuning parameter values to $n$ cases to select the $f$ top features, create $f$ heatmaps (one for each of the positions of importance determined by the magnitude of the explainer model coefficients) with the cases on the $y$-axis, the tuning parameter values on the $x$-axis, and the cells colored by the feature chosen for the corresponding case and tuning parameter value.
 Additional tuning parameters may also be included in the plot via facets.
@@
 Two hypothetical examples of feature heatmaps are included in \autoref{fig:concept-feat-heat}.
-The plots are created with the assumption that LIME is applied to select the top feature out of $p=\kge{4}$  features for $n=10$ cases with $t=5$ sets of tuning parameters.
-Situation 1 is  an example where the features selected are consistent across tuning parameters within a case but vary across cases within a tuning parameter.
+The plots are created with the assumption that LIME is applied to select the top feature out of $p=4$  features for $n=10$ cases with $t=5$ sets of tuning parameter values.
+Situation 1 is  an example where the features selected are consistent across tuning parameter values within a case but vary across cases within a tuning parameter value.
 This is the ideal situation, because the LIME explanations do not depend on the tuning parameters but do depend on the location of the observation in the feature space.
-Situation 2 is an example where the selected features  vary across tuning parameters within a case but are consistent across cases within a tuning parameter.
+Situation 2 is an example where the selected features vary across tuning parameter values within a case but are consistent across cases within a tuning parameter value.
 This situation indicates that the features selected by LIME are dependent on the tuning parameters, and the explanations may not be  local, because the same feature is chosen regardless of the case.
@@
 \autoref{fig:sine-feat-heat} shows a feature heatmap for the LIME applications to the 100 observations in the \data \ test set.
-The most important and second most important features selected by lime are showin in the top and bottom facets, respectively.
+The most important and second most important features selected by lime are shown in in the top and bottom facets, respectively.
 For the quantile bins, the original features prior to the indicator variable transformation are included since it is obvious that different features would be selected when the sizes of the bins change.
@@
 Note that the explanations from 3 and 5 quantile bins include the selection of the random noise variable ($x_3$) as an important variable in many predictions, which should not be the case.
-The pattern seen in the explanations for 3 to 6 quantile bins may suggest local explanations, but the dependence on tuning parameter makes it unclear which set of explanations to use.
+The pattern seen in the explanations for 3 to 6 quantile bins may suggest local explanations, but the dependence on tuning parameters makes it unclear which set of explanations to use.
 
@@
 
-The feature heatmap for the \data \ in the previous section shows an example of inconsistent LIME explanations across tuning parameters.
+The feature heatmap for the \data \ in the previous section shows an example of inconsistent LIME explanations across tuning parameter values.
 In this situation, the user must determine which set of explanations to trust.
-One way to do this is to compute assessment metrics for each set of explanations to identify the optimal tuning parameters.
+One way to do this is to compute assessment metrics for each set of explanations to identify the optimal tuning parameter values.
 We discuss three metrics for this purpose and present a visual comparison in an \emph{assessment metric plot}.
 
-Each metric presented below is computed on  LIME explanations for a set of predictions obtained using the same tuning parameters.
+Each metric presented below is computed on  LIME explanations for a set of predictions obtained using the same tuning parameter values.
 Here we provide a high level description of the metrics.
@@
 \caption{Example bullet signatures.
-The bullet signatures correspond to the same land \hh{XXX barrel land is actually a standing term, meaning the physical land in the barrel that created the striation.
-Obviously it is confusing, so I got rid of the 'barrel'.} and therefore have very similar patterns.
+The bullet signatures correspond to the same land and therefore have very similar patterns.
 The \citet{hare:2016} random forest is fit using various features that measure the similarity between two such signatures.}
@@
 
-We apply the random forest  \kge{\sout{model}} \hh{XXX I would actually prefer to leave the model in here.
-applying a random forest sounds like you applied he methodology to the data.
-But you got predictions based on the model previously fitted by Eric.
-That's a difference} from \citet{hare:2016} to another set of bullets from the Hamby study with \Sexpr{dim(bullet_test)[1]} rows of land comparisons.
+We apply the \kge{trained} random forest \kge{model} from \citet{hare:2016} to another set of bullets from the Hamby study with \Sexpr{dim(bullet_test)[1]} rows of land comparisons.
 We first consider a global visualization of the relationship between the random forest predictions and the model features with a parallel coordinate plot of the training data (top facet) and testing data (bottom facets) predictions (\autoref{fig:bullet-plot-rfpcp}).
@@
 
-LIME is applied to all test set observations using different tuning parameters: 12 sampling methods (2-6 equally spaced bins, 2-6 quantile bins, kernel density estimation, and normal approximation) and 3 Gower exponents (0.5, 1, and 10).
+LIME is applied to all test set observations using different tuning parameter values: 12 sampling methods (2-6 equally spaced bins, 2-6 quantile bins, kernel density estimation, and normal approximation) and 3 Gower exponents (0.5, 1, and 10).
 Thus, a total of $12\times 3=36$ different applications of LIME are performed.
@@
 
-First, the density simulation methods produce the same explanations for almost all cases and LIME tuning parameters suggesting the LIME explanations are global and not local.
+First, the density simulation methods produce the same explanations for almost all cases and LIME tuning parameter values suggesting the LIME explanations are global and not local.
 Second, within a bin based simulation method, the features selected by LIME for an observation often vary by the number of bins but do not appear to vary by the Gower power.
@@
 In addition to faceting the results by simulation method and LIME feature selection order, facets for the Gower power and whether the observation is a match or non-match are included.
-The vertical stripes of features selected indicate a dependence between the LIME explanations and tuning parameters.}
+The vertical stripes of features selected indicate a dependence between the LIME explanations and tuning parameter values.}
 \label{fig:bullet-feature-heatmap}
@@
 
-To try to identify a set of LIME tuning parameters with the most trustworthy set of explanations, an assessment metric plot is considered (\autoref{fig:bullet-assess-metric}).
+To try to identify a set of LIME tuning parameter values with the most trustworthy set of explanations, an assessment metric plot is considered (\autoref{fig:bullet-assess-metric}).
 All density simulation methods performed well based on the three metrics.
@@
 The applications using a power of 0.5 perform the best or as well as the other powers across all simulation methods suggesting that the power that leads to a more global explanation is preferred by LIME.
-
-Perhaps we can say that the kernel density method, 3 equal bins, or 3 quantile bins are some of the better performing methods, but unfortunately, \autoref{fig:bullet-assess-metric} leaves us without a clear indication of which set of explanations to use to explain the random forest.
-To better understand the explanations provided by these three methods, we take a closer look at explanations from these methods for two observations of interest, which will be referred to as case M (a known match) and case NM (a known non-match).
-
+Perhaps we can say that the kernel density method \kge{or} 3 equal bins \sout{, or 3 quantile bins} are \kge{the best} \sout{some of the better} performing methods, but unfortunately, \autoref{fig:bullet-assess-metric} leaves us without a clear indication of which set of explanations to use to explain the random forest.
+
+\kge{To provide a more detailed view of explanations obtained using different tuning parameter values,} \sout{To better understand the explanations provided by these three methods,} we take a closer look at explanations \sout{from these methods} for two observations of interest, which will be referred to as case M (a known match) and case NM (a known non-match)\kge{, using explanation scatterplots}.
 Figure \ref{fig:bullet-eois} includes the visual representation plots of explanations (from \emph{lime}) and explanation scatterplots for cases M and NM.
-Plots for 3 equal bins and 3 quantile bins are included.
+Plots for 3 equal bins and 3 quantile bins are included \kge{to depict tuning parameter values with good (3 equal bins) and mediocre (3 quantile bins) performance based on the assessment metric plot}.
 Plots for the kernel density simulation method are included in Appendix~\ref{exp-scatter_plus} (Figure \ref{fig:bullet-expl-scat-density}).
-The scatterplots provide several insights into the LIME explanations.
-Here, we focus on the explanation for case NM with 3 quantile bins, but similar statements can be made about the other plots.
-\kgc{I've been thinking about the examples I chose to include, and I have a couple of questions.
-First, is it okay to include all of these plots when I am only discussing one?
-\hh{What's the reason that you are not discussing the other ones?
-I can see a case in favor because of the similar structure - that makes the plots appear like from a template, which is the effect we are going after.} Second, I'm not sure why I chose to list 3 quantile bins as a "good" tuning parameter value \hh{I think the argument was to have something along the lines of low, medium, high} anymore based on the assessment metric plot.
-I don't know that I agree with that anymore.
-However, it does provide a nice example for where the explainer model goes wrong.
-I'm wondering if it would be better to just focus on the 3 equal bins plots for cases M and NM.
-They are not quite a dramatically bad as 3 quantile bins, but a case could be make for not really capturing the random forest prediction regions.}
-
-The explanation plot from \emph{lime} for case NM with 3 quantile bins shows that an observed CCF value greater than 0.320 supports a random forest prediction in favor of a match, and the scatter plots show that many of the simulated values with CCF greater then 0.320 have random forest predictions greater than 0.5.
+\sout{The scatterplots provide several insights into the LIME explanations.
+Here, we focus on the explanation for case NM with 3 quantile bins, but similar statements can be made about the other plots.}
+
+\kge{First, focus on the explanation for case NM with 3 quantile bins.} The explanation plot from \emph{lime} \sout{for case NM with 3 quantile bins} shows that an observed CCF value greater than 0.320 supports a random forest prediction in favor of a match, and the scatter plots show that many of the simulated values with CCF greater then 0.320 have random forest predictions greater than 0.5.
 Additionally, the LIME explanation indicates that a value of matches less than or equal to 1.66 contradicts a prediction in favor of a match, and the scatter plots show that almost all simulated values with a value of matches less than or equal to 1.66 have random forest predictions close to 0.
@@
 The relationship between CCF and rough correlation does not provide much evidence to support the random forest prediction one way or the other, but there is a pentagon shaped region at the bottom of the scatter plot of matches versus rough correlation with mostly predictions close to 0 that case NM falls in and supports the random forest prediction of a non-match.
+
+\kge{The other explanation scatterplots can be interpreted in a similar manner.
+Overall, the plots identify that the 3 quantile bin explanations are not faithful to the random forest model predictions.
+The 3 equal bin explanations are more faithful to the random forest, but the regions captured by the bins still do not align with the regions with similar probabilities produced by the random forest.}
 
@@
 While the visualizations accomplish these tasks, they also expose examples of the failings of LIME.
-To address the discovered failings of LIME, we \sout{will} reconsider each of the claims about the performance of LIME made by \citet{ribeiro:2016} in light of the insights gained from the diagnostic visualizations.
+To address the discovered failings of LIME, we reconsider each of the claims about the performance of LIME made by \citet{ribeiro:2016} in light of the insights gained from the diagnostic visualizations.
 
@@
 The examples in this paper show cases where the explainer model bins do not accurately capture the regions with similar random forest probabilities that contain the prediction of interest and oversimplify the model (Figures \ref{fig:sine-exp-scatter} and \ref{fig:bullet-eois}).
-Using \hh{fewer \sout{less}} bins would clearly not help improve the faithfulness of the explainer model in these examples, and while an increase in \hh{the number of} bins would lead to a finer resolution of the random forest classification boundaries, interpretability of the explainer model would quickly be lost.
+Using fewer bins would clearly not help improve the faithfulness of the explainer model in these examples, and while an increase in the number of bins would lead to a finer resolution of the random forest classification boundaries, interpretability of the explainer model would quickly be lost.
 Perhaps this could be improved by allowing the bin creation to account for the relationships between the features and response variable or a different number of bins for each feature.
@@
 In addition to assessing faithfulness by visually comparing the complex and explainer model, we propose a visual comparison of two faithfulness metrics (MSEE and average fidelity).
-The examples of faithfulness metric comparisons in this paper (Figures \ref{fig:sine-assess-metric} and \ref{fig:bullet-assess-metric}) both produced confusing \hh{XX conflicting?} results.
+The examples of faithfulness metric comparisons in this paper (Figures \ref{fig:sine-assess-metric} and \ref{fig:bullet-assess-metric}) both produced conflicting results.
 The density based simulation methods result in the best or close to the best performance even though the feature heatmaps (Figures \ref{fig:sine-feat-heat} and \ref{fig:bullet-feature-heatmap}) show that the density simulation methods produce global explanations with minimal variation in features selected by LIME.
-For the bin based simulation methods, the two metrics often do not agree or contradict one another, which makes it difficult to decide on a recommendation of a set of tuning parameters that produces the explanations with the most faithful explainer model.
+For the bin based simulation methods, the two metrics often do not agree or contradict one another, which makes it difficult to decide on a recommendation of a set of tuning parameter values that produce the explanations with the most faithful explainer model.
 
@@
 Effects from overplotting should be relatively mild, because output from simulations is shown, which is expected to be (relatively) continuous such that overplotting only occurs for points with (relatively) similar values.
-%\kgc{What do you mean by continuous here?}.
-\hh{XXX Does that extra explanation help?} \kgc{Yes.
-I see what you mean now.}
-In that respect, the diagnostics shown for the \data \ and \sout{in} the bullet example are representative of what is expected.
+In that respect, the diagnostics shown for the \data \ and the bullet example are representative of what is expected.
 But in cases where overplotting does become problematic, the user could either simply reduce the size of the simulations or use some well-studied binning techniques in the visualizations, as discussed for example in \citet{carr:1987} or \citet{unwin:2006}.
@@
 
-%\kge{Should this go under the financial disclosure section?
-Also, what is the financial disclosure section meant to contain?
-I couldn't find it described on the ASA data science journal author guidelines page.
-Should we remove it?} \hh{financial disclosures are used to determine conflicts of interest -  like getting funded by the robacco industry and promoting the health benefits of smoking.
-}
 HH was partially funded by the Center for Statistics and Applications in Forensic Evidence (CSAFE) through Cooperative Agreement 70NANB20H019 between NIST and Iowa State University, which includes activities carried out at Carnegie Mellon University, Duke University, University of California Irvine, University of Virginia, West Virginia University, University of Pennsylvania, Swarthmore College and University of Nebraska, Lincoln.
@@
 
-{\bf Katherine Goode, Heike Hofmann}: Conceptualization, Methodology, Investigation\kge{, Visualizations}, Writing- Reviewing and Editing.
-{\bf Katherine Goode}: Writing Initial Draft, Software.
+{\bf Katherine Goode, Heike Hofmann}: Conceptualization, Methodology, Investigation, Visualizations, Writing - Reviewing and Editing. {\bf Katherine Goode}: Writing - Initial Draft, Software.
 
@@
 
-The following supporting information is available as part of the online article: \kgc{What should we list here?}
-\hh{This is like a table of contents for the appendix.}
+%The following supporting information is available as part of the online article:
 
@@
 
-For $x_e$ and \kge{a} set of tuning parameters $t$, let $\textbf{X}_{e,t}'$ be the LIME simulated dataset with $K$ features and $S$ observations such that $x'_{e,t,s}$ is the feature vector for simulated data observation $s$ \kge{corresponding to observation/explanation $e$ and tuning parameters $t$}.
-Let $\textbf{Z}'_{e,t}$ be the matrix of \kge{simulated data transformed to bin indicator variables (for bin based simulation methods) or standardization (for density based simulation methods)} \sout{interpretability transformed simulated data} with $K$ features and $S$ observations such that $z'_{e,t,s}$ is the interpretability transformed feature vector for observation/explanation $e$, tuning parameter\kge{s} $t$, and simulated data observation $s$.
+For $x_e$ and \kge{a} set of tuning parameter values $t$, let $\textbf{X}_{e,t}'$ be the LIME simulated dataset with $K$ features and $S$ observations such that $x'_{e,t,s}$ is the feature vector for simulated data observation $s$ \kge{corresponding to observation/explanation $e$ and tuning parameter values $t$}.
+Let $\textbf{Z}'_{e,t}$ be the matrix of \kge{simulated data transformed to bin indicator variables (for bin based simulation methods) or standardization (for density based simulation methods)} \sout{interpretability transformed simulated data} with $K$ features and $S$ observations such that $z'_{e,t,s}$ is the interpretability transformed feature vector for observation/explanation $e$, tuning parameter values $t$, and simulated data observation $s$.
 Note that $z_{e,t}$ will represent the \sout{interpretability} transformed version of $x_e$.
 
-Next, let $\omega_t$ represent a proximity distance metric \kge{corresponding to tuning parameters $t$}.
+Next, let $\omega_t$ represent a proximity distance metric \kge{corresponding to tuning parameter values $t$}.
 Then $\omega_t\left(x_e, x'_{e,t,s}\right)$ is the weight assigned to $x'_{e,t,s}$, which is the proximity between $x_e$ and $x'_{e,t,s}$.
-Allow $g_{e,t}$ to be the explainer model for an explanation $e$ and tuning parameter $t$.
+Allow $g_{e,t}$ to be the explainer model for an explanation $e$ and tuning parameter values $t$.
 Thus, $g_{e,t}\left(z'_{e,s,t}\right)$ is the explainer model prediction for the interpretability transformed simulated data observation $s$.
 
-For a set of $E$ explanations and a set of tuning parameters $t$, we define the assessment metrics as follows:\\
+For a set of $E$ explanations and a set of tuning parameter values $t$, we define the assessment metrics as follows:\\
 \\

### 2020-08-31 paper.Rnw
last edits - ready to go out!

@@
 
-We apply the \kge{trained} random forest \kge{model} from \citet{hare:2016} to another set of bullets from the Hamby study with \Sexpr{dim(bullet_test)[1]} rows of land comparisons.
+We apply the trained random forest model from \citet{hare:2016} to another set of bullets from the Hamby study with \Sexpr{dim(bullet_test)[1]} rows of land comparisons.
 We first consider a global visualization of the relationship between the random forest predictions and the model features with a parallel coordinate plot of the training data (top facet) and testing data (bottom facets) predictions (\autoref{fig:bullet-plot-rfpcp}).
@@
 The applications using a power of 0.5 perform the best or as well as the other powers across all simulation methods suggesting that the power that leads to a more global explanation is preferred by LIME.
-Perhaps we can say that the kernel density method \kge{or} 3 equal bins \sout{, or 3 quantile bins} are \kge{the best} \sout{some of the better} performing methods, but unfortunately, \autoref{fig:bullet-assess-metric} leaves us without a clear indication of which set of explanations to use to explain the random forest.
-
-\kge{To provide a more detailed view of explanations obtained using different tuning parameter values,} \sout{To better understand the explanations provided by these three methods,} we take a closer look at explanations \sout{from these methods} for two observations of interest, which will be referred to as case M (a known match) and case NM (a known non-match)\kge{, using explanation scatterplots}.
-Figure \ref{fig:bullet-eois} includes the visual representation plots of explanations (from \emph{lime}) and explanation scatterplots for cases M and NM.
-Plots for 3 equal bins and 3 quantile bins are included \kge{to depict tuning parameter values with good (3 equal bins) and mediocre (3 quantile bins) performance based on the assessment metric plot}.
+Perhaps we can say that the kernel density method or 3 equal bins  are the best performing methods, but unfortunately, \autoref{fig:bullet-assess-metric} leaves us without a clear indication of which set of explanations to use to explain the random forest.
+
+To provide a more detailed view of explanations obtained using different tuning parameter values, we take a closer look at explanations  for two observations of interest, which will be referred to as case M (a known match) and case NM (a known non-match), using explanation scatterplots.
+Figure~\ref{fig:bullet-eois} includes the visual representation plots of explanations (from \emph{lime}) and explanation scatterplots for cases M and NM.
+Plots for 3 equal bins and 3 quantile bins are included to depict tuning parameter values with good (3 equal bins) and mediocre (3 quantile bins) performance based on the assessment metric plot.
 Plots for the kernel density simulation method are included in Appendix~\ref{exp-scatter_plus} (Figure \ref{fig:bullet-expl-scat-density}).
-\sout{The scatterplots provide several insights into the LIME explanations.
-Here, we focus on the explanation for case NM with 3 quantile bins, but similar statements can be made about the other plots.}
-
-\kge{First, focus on the explanation for case NM with 3 quantile bins.} The explanation plot from \emph{lime} \sout{for case NM with 3 quantile bins} shows that an observed CCF value greater than 0.320 supports a random forest prediction in favor of a match, and the scatter plots show that many of the simulated values with CCF greater then 0.320 have random forest predictions greater than 0.5.
+
+First, focus on the explanation for case NM with 3 quantile bins.
+The explanation plot from \emph{lime} \sout{for case NM with 3 quantile bins} shows that an observed CCF value greater than 0.320 supports a random forest prediction in favor of a match, and the scatter plots show that many of the simulated values with CCF greater then 0.320 have random forest predictions greater than 0.5.
 Additionally, the LIME explanation indicates that a value of matches less than or equal to 1.66 contradicts a prediction in favor of a match, and the scatter plots show that almost all simulated values with a value of matches less than or equal to 1.66 have random forest predictions close to 0.
@@
 
-\kge{The other explanation scatterplots can be interpreted in a similar manner.
+The other explanation scatterplots can be interpreted in a similar manner.
 Overall, the plots identify that the 3 quantile bin explanations are not faithful to the random forest model predictions.
-The 3 equal bin explanations are more faithful to the random forest, but the regions captured by the bins still do not align with the regions with similar probabilities produced by the random forest.}
+The 3 equal bin explanations are more faithful to the random forest, but the regions captured by the bins still do not align with the regions with similar probabilities produced by the random forest.
 
@@
 
-For $x_e$ and \kge{a} set of tuning parameter values $t$, let $\textbf{X}_{e,t}'$ be the LIME simulated dataset with $K$ features and $S$ observations such that $x'_{e,t,s}$ is the feature vector for simulated data observation $s$ \kge{corresponding to observation/explanation $e$ and tuning parameter values $t$}.
-Let $\textbf{Z}'_{e,t}$ be the matrix of \kge{simulated data transformed to bin indicator variables (for bin based simulation methods) or standardization (for density based simulation methods)} \sout{interpretability transformed simulated data} with $K$ features and $S$ observations such that $z'_{e,t,s}$ is the interpretability transformed feature vector for observation/explanation $e$, tuning parameter values $t$, and simulated data observation $s$.
-Note that $z_{e,t}$ will represent the \sout{interpretability} transformed version of $x_e$.
-
-Next, let $\omega_t$ represent a proximity distance metric \kge{corresponding to tuning parameter values $t$}.
+For $x_e$ and a set of tuning parameter values $t$, let $\textbf{X}_{e,t}'$ be the LIME simulated dataset with $K$ features and $S$ observations such that $x'_{e,t,s}$ is the feature vector for simulated data observation $s$ corresponding to observation/explanation $e$ and tuning parameter values $t$.
+Let $\textbf{Z}'_{e,t}$ be the matrix of simulated data transformed to bin indicator variables (for bin based simulation methods) or standardization (for density based simulation methods)  with $K$ features and $S$ observations such that $z'_{e,t,s}$ is the interpretability transformed feature vector for observation/explanation $e$, tuning parameter values $t$, and simulated data observation $s$.
+Note that $z_{e,t}$ will represent the  transformed version of $x_e$.
+
+Next, let $\omega_t$ represent a proximity distance metric corresponding to tuning parameter values $t$.
 Then $\omega_t\left(x_e, x'_{e,t,s}\right)$ is the weight assigned to $x'_{e,t,s}$, which is the proximity between $x_e$ and $x'_{e,t,s}$.
@@
 
-\noindent \kge{where $\mathcal{L}$ was originally defined in \citet{ribeiro:2016}.}\\
+\noindent where $\mathcal{L}$ was originally defined in \citet{ribeiro:2016}.\\
 \\

### 2020-09-01 paper.Rnw
adjusted figure size to meet submission requirements

@@
 # Specify global options
-knitr::opts_chunk$set(echo = FALSE,
+knitr::opts_chunk$set(
+  echo = FALSE,
   fig.keep = 'high',
-                      message = FALSE)
+  message = FALSE,
+  dev = "tiff",
+  fig.align = 'center'
+)
 
@@
 \begin{figure*}[!thp]
-<<concept-plot-good, out.width = '\\textwidth', fig.width = 7.95, fig.height = 3.75, warning = FALSE>>=
+<<concept-plot-good, out.width = '6.5in', fig.width = 7.95, fig.height = 3.75, warning = FALSE>>=
 
@@
 
-<<concept-plot-bad, out.width = '\\textwidth', fig.width = 7.95, fig.height = 3.75, warning = FALSE>>=
+<<concept-plot-bad, out.width = '6.5in', fig.width = 7.95, fig.height = 3.75, warning = FALSE>>=
 
@@
 \centering
-<<sine-plot-data, out.width = '\\textwidth', fig.width = 8, fig.height = 3.1>>=
+<<sine-plot-data, out.width = '6.5in', fig.width = 8, fig.height = 3.1>>=
 
@@
 \begin{figure*}[!thp]
-<<sine-exp-scatter, out.width = '\\textwidth', fig.width = 12, fig.height = 4.68, warning = FALSE>>=
+<<sine-exp-scatter, out.width = '6.5in', fig.width = 12, fig.height = 4.68, warning = FALSE>>=
 
@@
 \begin{figure}[!thp]
-<<concept-feat-heat, out.width = '0.48\\textwidth', fig.width = 6, fig.height = 3>>=
+<<concept-feat-heat, out.width = '3.125in', fig.width = 6, fig.height = 3>>=
 # Specify the number of cases and LIME input options
@@
 
-<<sine-feat-heat, out.width = '0.45\\textwidth', fig.width = 4, fig.height = 4.5>>=
+<<sine-feat-heat, out.width = '3.125in', fig.width = 4, fig.height = 4.5>>=
 plot_feature_heatmap(sine_lime_explain$explain,
@@
 \begin{figure}[!thp]
-<<sine-assess-metric, out.width = '0.49\\textwidth', fig.width = 4.5, fig.height = 3.75, warning = FALSE>>=
+<<sine-assess-metric, out.width = '3.25in', fig.width = 4.5, fig.height = 3.75, warning = FALSE>>=
 
@@
 \centering
-\includegraphics[width=2in]{./figure-static/bullets.png}
+\includegraphics[width=2.75in]{./figure-static/bullets.png}
 \caption{(Top left) Traditionally rifled gun barrel.
@@
 
-\includegraphics[width=3.25in]{./figure-static/signatures.png}
+\includegraphics[width=3.125in]{./figure-static/signatures.png}
 \caption{Example bullet signatures.
@@
 \begin{figure*}[!thp]
-<<bullet-plot-rfpcp, out.width = '\\textwidth', warning = FALSE>>=
+<<bullet-plot-rfpcp, out.width = '6.5in', warning = FALSE>>=
 
@@
 \begin{figure*}[!thp]
-<<bullet-feature-heatmap, out.width = '\\textwidth', fig.width = 18, fig.height = 12>>=
+<<bullet-feature-heatmap, out.width = '6.5in', fig.width = 18, fig.height = 12>>=
 # Create a feature heatmap
@@
 
-<<bullet-assess-metric, out.width = '\\textwidth', warning = FALSE, fig.width = 10, fig.height = 4>>=
+<<bullet-assess-metric, out.width = '6.5in', warning = FALSE, fig.width = 10, fig.height = 4>>=
 
@@
 \begin{figure*}[!thp]
-<<bullet-eois, out.width = '\\textwidth', fig.width = 12, fig.height = 17, fig.align = "center", out.width="90%", message = FALSE>>=
+<<bullet-eois, out.width = '6.5in', fig.width = 12, fig.height = 17, out.width="90%", message = FALSE>>=
 # Join the plots
@@
 \begin{figure*}[!thp]
-<<sine-expl-scat-density, out.width = '\\textwidth', fig.width = 12, fig.height = 4.5, fig.align = "center">>=
+<<sine-expl-scat-density, out.width = '6.5in', fig.width = 12, fig.height = 4.5, fig.align = "center">>=
 plot_explain_scatter(
@@
 \begin{figure*}[!thp]
-<<bullet-expl-scat-density, out.width = '\\textwidth', fig.width = 12, fig.height = 9, fig.align = "center">>=
+<<bullet-expl-scat-density, out.width = '6.5in', fig.width = 12, fig.height = 9, fig.align = "center">>=
 bullet_es_NM <-
@@
 \begin{figure}[!thp]
-<<sine-plot-resids, out.width = '0.5\\textwidth', fig.width = 5, fig.height = 4, warning = FALSE>>=
+<<sine-plot-resids, out.width = '3.125in', fig.width = 5, fig.height = 4, warning = FALSE>>=
 

### 2020-09-01 paper.Rnw
working on preparing paper for submission

@@
 \address[2]{\orgdiv{Center for Statistics and Applications in Forensic Evidence (CSAFE)}, \orgname{Iowa State University}, \orgaddress{\state{Iowa}, \country{United States}}}
-\corres{*Corresponding author. \email{kgoode@iastate.edu}}
+\corres{*Katherine Goode, Department of Statistics, Iowa State University, Ames, IA. \email{kgoode@iastate.edu}}
 
 % Abstract and keywords
-\abstract[Summary]{The importance of providing explanations for predictions made by black-box models has led to the development of model explainer methods such as LIME (local interpretable model-agnostic explanations) \citep{ribeiro:2016}.
+\abstract[Abstract]{The importance of providing explanations for predictions made by black-box models has led to the development of model explainer methods such as LIME (local interpretable model-agnostic explanations).
 LIME uses a surrogate model to explain the relationship between predictor variables and predictions from a black-box model in a local region around a prediction of interest.
@@
 We apply the visual diagnostics to a forensics bullet matching dataset to show examples where LIME explanations depend on the tuning parameter values and the explainer model oversimplifies the black-box model.
-Our examples raise concerns about claims made of LIME \citep{ribeiro:2016} that are similar to other criticisms in the literature \citep{alvarezmelis:2018, laugel:2018, molnar:2019}.}
+Our examples raise concerns about claims made of LIME that are similar to other criticisms in the literature.}
 \keywords{LIME, black-box models, interpretability, diagnostics}
@@
 knitr::opts_chunk$set(
+  warning = FALSE,
+  message = FALSE,
   echo = FALSE,
   fig.keep = 'high',
-  message = FALSE,
-  dev = "tiff",
-  fig.align = 'center'
+  fig.align = 'center',
+  dev = c("cairo_pdf", "cairo_ps"),
+  dev.args = list(fallback_resolution = 800),
+  dpi = 800
 )
@@
 # Load packages
+library(Cairo)
 library(caret)
@@
        size = "Weight") +
-  theme_linedraw(base_family = "Times", base_size = 10) +
+  theme_linedraw(base_family = "Times", base_size = 8) +
   theme(panel.grid.major = element_blank(),
@@
   scale_colour_manual(values = c(sinecolor_blue, sinecolor_red)) +
-  theme_bw(base_family = "Times", base_size = 10) +
+  theme_bw(base_family = "Times", base_size = 8) +
   labs(x = TeX("$x_1$"),
@@
   scale_shape_manual(values = 23) +
-  theme_bw(base_family = "Times", base_size = 10) +
+  theme_bw(base_family = "Times", base_size = 8) +
   labs(x = TeX("$x_1$"),
@@
 
-sine_poi_exp <- sine_poi_lime_default %>% plot_features() + theme(text = element_text(family = "Times", size = 10))
+sine_poi_exp <- 
+  sine_poi_lime_default %>% 
+  plot_features() + 
+  theme(text = element_text(family = "Times", size = 12))
 
@@
        title = "Explanation Scatterplot") +
-  theme_bw(base_family = "Times", base_size = 10) +
+  theme_bw(base_family = "Times", base_size = 12) +
   guides(shape = guide_legend(order = 1),
@@
                 order_method = "PCA") +
-  theme_bw(base_family = "Times", base_size = 10) +
+  theme_bw(base_family = "Times", base_size = 12) +
   theme(legend.position = "bottom",
@@
 \begin{figure*}[!thp]
-<<bullet-eois, out.width = '6.5in', fig.width = 12, fig.height = 17, out.width="90%", message = FALSE>>=
+<<bullet-eois, out.width = '6.25in', fig.width = 12, fig.height = 17, message = FALSE>>=
 # Join the plots

### 2020-09-03 paper.Rnw
made adjustments to figures to meet minimum size (text and lines) requiements for submission

@@
   dev.args = list(fallback_resolution = 800),
-  dpi = 800
+  dpi = 1200
 )
@@
 library(limeaid) #devtools::install_github("goodekat/limeaid")
+library(magick)
 library(purrr)
@@
 
+# Specify the (base) font size for all plots
+fs = 7
 @
@@
 <<concept-data>>=
+
 # Simulate example data
@@
 \begin{figure*}[!thp]
-<<concept-plot-good, out.width = '6.5in', fig.width = 7.95, fig.height = 3.75, warning = FALSE>>=
+<<figure-01, out.width = '6.5in', fig.width = 7.95, fig.height = 3.75, warning = FALSE>>=
+
+# Specify the figure size (for determining font size)
+f1_ow = 6.5
+f1_fw = 7.95
+f1_fs = fs * (f1_fw / f1_ow)
 
@@
   facet_grid(. ~ feature, switch = "x") +
-  geom_point(data = lime_data_gathered,
-             mapping = aes(x = feature_stnd_value,
+  geom_point(
+    data = lime_data_gathered,
+    mapping = aes(
+      x = feature_stnd_value,
       y = prediction,
@@
       alpha = distance_value,
-                           color = distance)) +
-  geom_abline(data = coefs_data %>% filter(case == "good"),
+      color = distance
+    )
+  ) +
+  geom_abline(
+    data = coefs_data %>% filter(case == "good"),
     mapping = aes(intercept = int, slope = slope),
-              size = 1) +
+    size = 1
+  ) +
   scale_alpha(range = c(0.3, 1)) +
   scale_color_manual(values = c(NA, "grey30"), guide = "none") +
-  geom_point(data = prediction_of_interest_gathered,
+  geom_point(
+    data = prediction_of_interest_gathered,
     mapping = aes(x = feature_value,
@@
     shape = 23,
-             alpha = 0.75) +
+    alpha = 0.75
+  ) +
   scale_fill_manual(values = "#FAAA72") +
   geom_text(
-    data = data.frame(feature_stnd_value = 1.2,
+    data = data.frame(
+      feature_stnd_value = 1.2,
       prediction = 1.6,
       feature = c("Feature 1", "Feature 2"),
-                      slope = c(paste("Slope:",
+      slope = c(
+        paste(
+          "Slope:",
           coefs_data %>%
@@
             pull(slope) %>%
-                                        round(3)),
-                                paste("Slope:",
+            round(3)
+        ),
+        paste(
+          "Slope:",
           coefs_data %>%
@@
             pull(slope) %>%
-                                        round(3)))),
+            round(3)
+        )
+      )
+    ),
     mapping = aes(x = feature_stnd_value,
@@
     family = "Times",
-    size = 4) +
-  labs(x = "",
+    size = f1_fs / 2.85
+  ) +
+  labs(
+    x = "",
     y = "Black-Box Prediction",
@@
     alpha = "Weight",
-       size = "Weight") +
-  theme_linedraw(base_family = "Times", base_size = 8) +
-  theme(panel.grid.major = element_blank(),
+    size = "Weight"
+  ) +
+  theme_linedraw(base_family = "Times", base_size = f1_fs) +
+  theme(
+    panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
@@
     strip.background = element_rect(color = "white", fill = "white"),
-        strip.text = element_text(color = 'black', size = 10)) +
-  guides(fill = guide_legend(order = 1),
+    strip.text.x = element_text(size = f1_fs, color = "black"),
+    plot.title = element_text(size = f1_fs)
+  ) +
+  guides(
+    fill = guide_legend(order = 1),
     size = guide_legend(order = 2),
-         alpha = guide_legend(order = 2))
+    alpha = guide_legend(order = 2)
+  )
 
@@
 That is, the explainer is faithful to the complex model and produces a reasonable explanation that Feature 1 plays a more important role in the prediction of interest than Feature 2 since the magnitude of the slope associated with Feature 1 is larger.}
-\label{fig:concept-plot-good}
+\label{fig:figure-01}
 
@@
 
-<<concept-plot-bad, out.width = '6.5in', fig.width = 7.95, fig.height = 3.75, warning = FALSE>>=
+<<figure-02, out.width = '6.5in', fig.width = 7.95, fig.height = 3.75, warning = FALSE>>=
+
+# Specify the figure size (for determining font size)
+f2_ow = 6.5
+f2_fw = 7.95
+f2_fs = fs * (f2_fw / f2_ow)
 
@@
       alpha = distance_value,
-                           color = distance)) +
-  geom_abline(data = coefs_data %>% filter(case == "bad"),
+      color = distance
+    )
+  ) +
+  geom_abline(
+    data = coefs_data %>% filter(case == "bad"),
     mapping = aes(intercept = int, slope = slope),
-              size = 1) +
+    size = 1
+  ) +
   scale_alpha(range = c(0.3, 1)) +
   scale_color_manual(values = c("grey30", NA), guide = "none") +
-  geom_point(data = prediction_of_interest_gathered,
+  geom_point(
+    data = prediction_of_interest_gathered,
     mapping = aes(x = feature_value,
@@
     family = "Times",
-    size = 4) +
-  labs(x = "",
+    size = f2_fs / 3
+  ) +
+  labs(
+    x = "",
     y = "Black-Box Prediction",
@@
     alpha = "Weight",
-       size = "Weight") +
-  theme_linedraw(base_family = "Times", base_size = 8) +
-  theme(panel.grid.major = element_blank(),
+    size = "Weight"
+  ) +
+  theme_linedraw(base_family = "Times", base_size = f2_fs) +
+  theme(
+    panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
@@
     strip.background = element_rect(color = "white", fill = "white"),
-        strip.text = element_text(color = 'black', size = 10)) +
-  guides(fill = guide_legend(order = 1),
+    strip.text.x = element_text(size = f2_fs, color = "black"),
+    plot.title = element_text(size = f2_fs)
+  ) +
+  guides(
+    fill = guide_legend(order = 1),
     size = guide_legend(order = 2),
-         alpha = guide_legend(order = 2))
+    alpha = guide_legend(order = 2)
+  )
 
@@
 \caption{A conceptual depiction of an unfaithful local explainer model in the immediate neighborhood of a prediction of interest.
-A ridge regression model is fit to the same hypothetical black-box model predictions and predictor variables as in \autoref{fig:concept-plot-good}, but the weights are computed using a Gower exponent of 1.
+A ridge regression model is fit to the same hypothetical black-box model predictions and predictor variables as in \autoref{fig:figure-01}, but the weights are computed using a Gower exponent of 1.
 The explainer model is unfaithful to the complex model in any immediate neighborhood of the prediction of interest.}
-\label{fig:concept-plot-bad}
+\label{fig:figure-02}
 \end{figure*}
 
-\autoref{fig:concept-plot-good} provides a visualization of this conceptual understanding of LIME.
+\autoref{fig:figure-01} provides a visualization of this conceptual understanding of LIME.
 The two plots show the predictions from a hypothetical black-box model plotted against the two hypothetical model predictor variables.
@@
 A Gower distance metric \citep{gower:1971} is used to define locality such that the size of the points represent the inverse of the Gower distance raised to some value and indicate the proximity to the prediction of interest.
-In the example of \autoref{fig:concept-plot-good}, an exponent of \Sexpr{good_gower_power} is used to emphasize a very local region around the prediction of interest.
+In the example of \autoref{fig:figure-01}, an exponent of \Sexpr{good_gower_power} is used to emphasize a very local region around the prediction of interest.
 A ridge regression model weighted by the proximity values is used as the explainer model with the black-box predictions as the response variable and standardized versions of two features in the data as predictor variables.
@@
 
-The plot on the left of \autoref{fig:concept-plot-good} shows the relationship between the black-box predictions and Feature 1.
+The plot on the left of \autoref{fig:figure-01} shows the relationship between the black-box predictions and Feature 1.
 Here, the explainer model is plotted with Feature 2 fixed at the observed value of the prediction of interest.
@@
 We consider an example where the choice of exponent for the weights is crucial to the quality of the explanation.
-The plots in Figure \ref{fig:concept-plot-bad} show the same data as \autoref{fig:concept-plot-good}, but the Gower distance metric exponent is decreased to \Sexpr{bad_gower_power} (the default exponent in the \emph{lime} R package).
+The plots in Figure \ref{fig:figure-02} show the same data as \autoref{fig:figure-01}, but the Gower distance metric exponent is decreased to \Sexpr{bad_gower_power} (the default exponent in the \emph{lime} R package).
 This causes the observations that are further away from the prediction of interest to be given larger weights than before.
-In \autoref{fig:concept-plot-good}, the explainer model captures the relationship between the black-box predictions in an immediate neighborhood of the prediction of interest.
-This cannot be said of the explainer model in \autoref{fig:concept-plot-bad}.
+In \autoref{fig:figure-01}, the explainer model captures the relationship between the black-box predictions in an immediate neighborhood of the prediction of interest.
+This cannot be said of the explainer model in \autoref{fig:figure-02}.
 In addition, the magnitude of the slope associated with Feature 2  (\Sexpr{coefs_data %>% filter(case == "bad", feature == "Feature 2") %>% pull(slope) %>% round(3) %>% abs()}) is larger than that of Feature 1 (\Sexpr{coefs_data %>% filter(case == "bad", feature == "Feature 1") %>% pull(slope) %>% round(3) %>% abs()}).
@@
 One of the biggest difficulties with LIME is determining how to specify a local region \citep{laugel:2018} \citep{molnar:2019}.
-This is due to an unclear definition of a "local region" and how to apply LIME to achieve an appropriate local region as demonstrated by \autoref{fig:concept-plot-bad}.
+This is due to an unclear definition of a "local region" and how to apply LIME to achieve an appropriate local region as demonstrated by \autoref{fig:figure-02}.
 \citet{alvarezmelis:2018} raise a concern pertaining to the robustness of explanations from LIME and other model explainers: they find that even small changes in predictor variables can lead to very different LIME explanations.
@@
 \centering
-<<sine-plot-data, out.width = '6.5in', fig.width = 8, fig.height = 3.1>>=
+<<figure-03, out.width = '6.5in', fig.width = 8, fig.height = 3.1>>=
+
+# Specify the figure size (for determining font size)
+f3_ow = 6.5
+f3_fw = 8
+f3_fs = fs * (f3_fw / f3_ow)
+f3_ls = 0.5 * (f3_fw / f3_ow)
 
@@
   geom_path(data = sinefun_data, aes(x = x, y = y),
-            color = "black") +
+            color = "black", 
+            size = f3_ls) +
   scale_colour_manual(values = c(sinecolor_blue, sinecolor_red)) +
-  theme_bw(base_family = "Times", base_size = 8) +
+  theme_bw(base_family = "Times", base_size = f3_fs) +
+  theme(aspect.ratio = 1, 
+        plot.title = element_text(size = f3_fs)) +
   labs(x = TeX("$x_1$"),
@@
                            y = x2,
-                           #fill = rfprob_blue,
                            shape = shape),
@@
   geom_path(data = sinefun_data, aes(x = x, y = y),
-            color = "black") +
+            color = "black", 
+            size = f3_ls) +
   scale_color_gradient2(low = sinecolor_red,
@@
   scale_shape_manual(values = 23) +
-  theme_bw(base_family = "Times", base_size = 8) +
+  theme_bw(base_family = "Times", base_size = f3_fs) +
+  theme(aspect.ratio = 1,
+        plot.title = element_text(size = f3_fs)) +
   labs(x = TeX("$x_1$"),
@@
 The prediction of interest to explain is indicated by a diamond.}
-\label{fig:sine-plot-data}
+\label{fig:figure-03}
 \end{figure*}
@@
   mutate(case = c("Prediction of Interest", "Prediction of Interest"))
+
 @
@@
 
-\autoref{fig:sine-plot-data} shows scatterplots of $x_2$ versus $x_1$ from the training data (left) and the testing data (right).
+\autoref{fig:figure-03} shows scatterplots of $x_2$ versus $x_1$ from the training data (left) and the testing data (right).
 Both plots include the true classification boundary of the rotated sine function plotted as the solid black line.
@@
 The random forest  misclassifies \Sexpr{dim(sine_data_test %>% filter(y != rfpred))[1]} points, which are all located near  the classification boundary.
-These are identified by open circles in \autoref{fig:sine-plot-data}.
+These are identified by open circles in \autoref{fig:figure-03}.
 
@@
 
-For the presentation of the explanation scatterplot, we focus on the misclassified point with $(x_1, x_2, x_3)$ coordinates of (\Sexpr{round(sine_poi$x1, 2)}, \Sexpr{round(sine_poi$x2, 2)}, \Sexpr{round(sine_poi$x3, 2)}) indicated by a diamond in \autoref{fig:sine-plot-data}.
+For the presentation of the explanation scatterplot, we focus on the misclassified point with $(x_1, x_2, x_3)$ coordinates of (\Sexpr{round(sine_poi$x1, 2)}, \Sexpr{round(sine_poi$x2, 2)}, \Sexpr{round(sine_poi$x3, 2)}) indicated by a diamond in \autoref{fig:figure-03}.
 Misclassified points are often of interest to explain since they may provide information about ways to improve the model.
@@
 <<warning = FALSE>>=
+
 # Obtain the simulated data associated with the poi
@@
   spread(feature, bin_cut)
+
 @
@@
 
-<<sine-perms-subset>>=
-# Subset the simulated data to the region where the poi is located
-sine_poi_region_perms <- sine_poi_perms %>%
-  filter(x2 >= sine_poi_bounds %>% filter(feature == "x2") %>% pull(lower),
-         x1 >= sine_poi_bounds %>% filter(feature == "x1") %>% pull(lower),
-         x1 < sine_poi_bounds %>% filter(feature == "x1") %>% pull(upper))
-@
-
 \begin{figure*}[!thp]
-<<sine-exp-scatter, out.width = '6.5in', fig.width = 12, fig.height = 4.68, warning = FALSE>>=
-
+<<figure-04, out.width = '6.5in', fig.width = 12, fig.height = 5, warning = FALSE>>=
+
+# Specify the figure size (for determining font size)
+f4_ow = 6.5
+f4_fw = 12
+f4_fs = fs * (f4_fw / f4_ow)
+f4_ls = 0.5 * (f4_fw / f4_ow)
+
+# Create the lime R package explanation visualization for the sine data
 sine_poi_exp <- 
@@
   plot_features() + 
-  theme(text = element_text(family = "Times", size = 12))
-
+  theme(text = element_text(family = "Times", size = f4_fs),
+        strip.text = element_text(size = f4_fs, face = "plain"))
+
+# Create the explanation scatterplot for the lime explanation for the sine data
 exp_scatter <-
-  plot_explain_scatter(sine_poi_lime_default, alpha = 0.4) +
+  plot_explain_scatter(
+    sine_poi_lime_default,
+    alpha = 0.4,
+    line_size = f4_ls
+  ) +
   facet_grid(switch = "both") +
-  labs(x = TeX("x_1"),
+  labs(
+    x = TeX("x_1"),
     y = TeX("x_2"),
@@
     linetype = "",
-       title = "Explanation Scatterplot") +
-  theme_bw(base_family = "Times", base_size = 12) +
+    title = "Explanation Scatterplot"
+  ) +
+  theme_bw(base_family = "Times", base_size = f4_fs) +
   guides(shape = guide_legend(order = 1),
-         size = guide_legend(nrow = 2, byrow = T)) +
-  theme(aspect.ratio = 1)
-
+         size = guide_legend(
+           nrow = 2,
+           byrow = T,
+           override.aes = list(alpha = 1)
+         )) +
+  theme(aspect.ratio = 1,
+        plot.title = element_text(size = f4_fs))
+
+# Join the plots
 plot_grid(sine_poi_exp, exp_scatter)
-@
-\caption{(left) Visualization from the \emph{lime} R package of a LIME explanation for the \data \ prediction of interest identified in \autoref{fig:sine-plot-data}.
+
+@
+\caption{(left) Visualization from the \emph{lime} R package of a LIME explanation for the \data \ prediction of interest identified in \autoref{fig:figure-03}.
 (right) \emph{Explanation Scatterplot}.
@@
 This figure shows that the quantile bins are not flexible enough to capture the relationship between the random forest predictions and the $x_1$ and $x_2$ values.}
-\label{fig:sine-exp-scatter}
+\label{fig:figure-04}
 \end{figure*}
@@
 
-Before introducing the visual diagnostics, let us consider a commonly used visualization of a LIME explanation that is shown in Figure \ref{fig:sine-exp-scatter} (left).
-The plot is created using the \emph{lime} R package and provides a visual representation of a LIME explanation for the prediction of interest indicated in \autoref{fig:sine-plot-data}.
+Before introducing the visual diagnostics, let us consider a commonly used visualization of a LIME explanation that is shown in Figure \ref{fig:figure-04} (left).
+The plot is created using the \emph{lime} R package and provides a visual representation of a LIME explanation for the prediction of interest indicated in \autoref{fig:figure-03}.
 In particular, the explanation is obtained using 4 quantile bins to simulate the data.
@@
 
-The explanation for the prediction of interest depicted in Figure \ref{fig:sine-exp-scatter} is interpreted as follows.
+The explanation for the prediction of interest depicted in Figure \ref{fig:figure-04} is interpreted as follows.
 A random forest classification of blue is supported by the prediction of interest having a value of $x_2$ that is greater than \Sexpr{str_split(sine_poi_lime_default$feature_desc[[1]], pattern = " ")[[1]][1]}, but the prediction of interest having a value of $x_1$ that is greater than \Sexpr{str_split(sine_poi_lime_default$feature_desc[[2]], pattern = " ")[[1]][1]} and less than or equal to \Sexpr{str_split(sine_poi_lime_default$feature_desc[[2]], pattern = " ")[[1]][5]} provides support against a classification of blue.
@@
 
-Based on the plot on the left of \autoref{fig:sine-exp-scatter} alone, it is not possible to make an informed assessment of the explanation.
+Based on the plot on the left of \autoref{fig:figure-04} alone, it is not possible to make an informed assessment of the explanation.
 For a further assessment of the explainer model, we turn to an \emph{explanation scatterplot}: a visual diagnostic for assessing the LIME claims of locality and fidelity for an individual explanation by juxtaposing the complex and explainer models in one plot.
@@
 
-An explanation scatterplot corresponding to the LIME explanation depicted on the left in \autoref{fig:sine-exp-scatter} is shown on the right hand side of \autoref{fig:sine-exp-scatter}.
+An explanation scatterplot corresponding to the LIME explanation depicted on the left in \autoref{fig:figure-04} is shown on the right hand side of \autoref{fig:figure-04}.
 By juxtaposing the random forest predictions and the explainer model boundaries, we are able to assess the faithfulness and localness of the explainer model.
@@
 It is difficult to assess linearity from this explanation scatterplot, but a residual plot of the explainer model could be used to check the linearity claim.
-See Appendix~\ref{residual-plot} for the residual plot associated with the explanation considered in Figure \ref{fig:sine-exp-scatter}, which shows a violation of the linearity claim.
+See Appendix~\ref{residual-plot} for the residual plot associated with the explanation considered in Figure \ref{fig:figure-04}, which shows a violation of the linearity claim.
 
@@
 \begin{figure}[!thp]
-<<concept-feat-heat, out.width = '3.125in', fig.width = 6, fig.height = 3>>=
+<<figure-05, out.width = '3.125in', fig.width = 6, fig.height = 3>>=
+
+# Specify the figure size (for determining font size)
+f5_ow = 3.125
+f5_fw = 6
+f5_fs = fs * (f5_fw / f5_ow)
+
 # Specify the number of cases and LIME input options
@@
 set.seed(20191008)
-heatmap_data_good <- tibble(case = factor(rep(1:ncases, each = ninputs),
+heatmap_data_good <-
+  tibble(
+    case = factor(rep(1:ncases, each = ninputs),
                   levels = ncases:1),
     input = factor(rep(1:ninputs, ncases)),
-                       feature = factor(c(rep(1, 5),
+    feature = factor(c(
+      rep(1, 5),
       rep(2, 5),
@@
       rep(1, 5),
-                                          rep(4, 5)))) %>%
-  mutate(input = forcats::fct_recode(input, "A" = "1", "B" = "2",
-                                     "C" = "3", "D" = "4", "E" = "5"))
+      rep(4, 5)
+    ))
+  ) %>%
+  mutate(input = forcats::fct_recode(
+    input,
+    "A" = "1",
+    "B" = "2",
+    "C" = "3",
+    "D" = "4",
+    "E" = "5"
+  ))
 
@@
 heatmap_plot_good <- ggplot(data = heatmap_data_good,
-                            mapping = aes(x = input,
+                            mapping = aes(
+                              x = input,
                               y = case,
                               fill = feature,
-                                          color = feature)) +
+                              color = feature
+                            )) +
   geom_tile() +
-  labs(x = "Tuning Parameter Value",
+  labs(
+    x = "Tuning Parameter Value",
     y = "Case",
@@
     color = "Feature",
-       title = "Situation 1: \nConsistent Explanations") +
-  theme_bw(base_family = "Times", base_size = 12) +
+    title = "Situation 1",
+    subtitle = "Consistent Explanations"
+  ) +
+  theme_bw(base_family = "Times", base_size = f5_fs) +
   scale_fill_grey() +
   scale_color_grey() +
-  theme(legend.position = "none")
+  theme(legend.position = "none", 
+        plot.title = element_text(size = f5_fs))
 
@@
 set.seed(20190627)
-heatmap_data_bad <- tibble(case = factor(rep(1:ncases, ninputs),
+heatmap_data_bad <- tibble(
+  case = factor(rep(1:ncases, ninputs),
                 levels = ncases:1),
   input = factor(rep(1:ninputs, each = ncases)),
-                       feature = factor(rep(c(1, 2, 4, 3, 2), each = 10))) %>%
-  mutate(input = forcats::fct_recode(input, "A" = "1", "B" = "2",
-                                     "C" = "3", "D" = "4", "E" = "5"))
+  feature = factor(rep(c(1, 2, 4, 3, 2), each = 10))
+) %>%
+  mutate(input = forcats::fct_recode(
+    input,
+    "A" = "1",
+    "B" = "2",
+    "C" = "3",
+    "D" = "4",
+    "E" = "5"
+  ))
 
@@
 heatmap_plot_bad <- ggplot(data = heatmap_data_bad,
-                            mapping = aes(x = input,
+                           mapping = aes(
+                             x = input,
                              y = case,
                              fill = feature,
-                                          color = feature)) +
+                             color = feature
+                           )) +
   geom_tile() +
-  labs(x = "Tuning Parameter Value",
+  labs(
+    x = "Tuning Parameter Value",
     y = "Case",
@@
     color = "Feature",
-       title = "Situation 2: \nInconsistent Explanations") +
-  theme_bw(base_family = "Times", base_size = 12) +
+    title = "Situation 2",
+    subtitle = "Inconsistent Explanations"
+  ) +
+  theme_bw(base_family = "Times", base_size = f5_fs) +
+  theme(plot.title = element_text(size = f5_fs)) +
   scale_fill_grey() +
@@
 heatmap_leg <- get_legend(heatmap_plot_bad)
-heatmap_plot_bad <- heatmap_plot_bad + theme(legend.position = 'none')
+heatmap_plot_bad <-
+  heatmap_plot_bad + theme(legend.position = 'none')
 
 # Join the plots
-plot_grid(heatmap_plot_good, heatmap_plot_bad, heatmap_leg,
+plot_grid(
+  heatmap_plot_good,
+  heatmap_plot_bad,
+  heatmap_leg,
   nrow = 1,
-          rel_widths = c(0.45, 0.45, 0.1))
+  rel_widths = c(0.45, 0.45, 0.1)
+)
 
@@
 Situation 1 is the ideal, because the explanations vary across cases but do not dependent on specific tuning parameter values.}
-\label{fig:concept-feat-heat}
+\label{fig:figure-05}
 
@@
 
-<<sine-feat-heat, out.width = '3.125in', fig.width = 4, fig.height = 4.5>>=
+<<figure-06, out.width = '3.125in', fig.width = 4, fig.height = 4.5>>=
+
+# Specify the figure size (for determining font size)
+f6_ow = 3.125
+f6_fw = 4
+f6_fs = fs * (f6_fw / f6_ow)
+
+# Create the example feature heatmap with the sine data
 plot_feature_heatmap(sine_lime_explain$explain,
                      order_method = "PCA") +
-  theme_bw(base_family = "Times", base_size = 12) +
-  theme(legend.position = "bottom",
+  theme_bw(base_family = "Times", base_size = f6_fs) +
+  theme(
+    legend.position = "bottom",
     axis.text.y = element_blank(),
     axis.ticks.y = element_blank(),
-        strip.background = element_rect(color = "white", fill = "white")) +
+    strip.background = element_rect(color = "white", fill = "white")
+  ) +
   labs(y = "Case")
+
 @
@@
 The vertical striping indicates that the LIME explanations are not consistent across tuning parameter values.}
-\label{fig:sine-feat-heat}
+\label{fig:figure-06}
 \end{figure}
@@
 Explanations produced by LIME are likely to be affected by the choice of tuning parameter values.
-A hypothetical example of this is shown by Figures \ref{fig:concept-plot-good} and \ref{fig:concept-plot-bad} where the method used to weight the observations influenced the explanation.
+A hypothetical example of this is shown by Figures \ref{fig:figure-01} and \ref{fig:figure-02} where the method used to weight the observations influenced the explanation.
 As of the time of writing this manuscript, we have encountered no recommendations for how to specify the parameter values besides for the default settings in \emph{lime}.
@@
 
-Two hypothetical examples of feature heatmaps are included in \autoref{fig:concept-feat-heat}.
+Two hypothetical examples of feature heatmaps are included in \autoref{fig:figure-05}.
 The plots are created with the assumption that LIME is applied to select the top feature out of $p=4$  features for $n=10$ cases with $t=5$ sets of tuning parameter values.
@@
 
-\autoref{fig:sine-feat-heat} shows a feature heatmap for the LIME applications to the 100 observations in the \data \ test set.
+\autoref{fig:figure-06} shows a feature heatmap for the LIME applications to the 100 observations in the \data \ test set.
 The most important and second most important features selected by lime are shown in in the top and bottom facets, respectively.
@@
 \begin{figure}[!thp]
-<<sine-assess-metric, out.width = '3.25in', fig.width = 4.5, fig.height = 3.75, warning = FALSE>>=
+<<figure-07, out.width = '3.25in', fig.width = 4.5, fig.height = 3.75, warning = FALSE>>=
+
+# Specify the figure size (for determining font size)
+f7_ow = 3.25
+f7_fw = 4.5
+f7_fs = fs * (f7_fw / f7_ow)
 
@@
 plot_metrics(sine_lime_explain$explain, rank_legend = "discrete") +
-  theme_bw(base_family = "Times") + 
-  theme(strip.background = element_rect(color = "white", fill = "white"))
+  theme_bw(base_family = "Times", base_size = f7_fs) +
+  theme(
+    strip.background = element_rect(color = "white", fill = "white"),
+    strip.placement = "outside",
+    strip.text.y = element_text(size = f7_fs)
+  )
 
@@
 The kernel density simulation methods performs well across all three metrics.}
-\label{fig:sine-assess-metric}
+\label{fig:figure-07}
 \end{figure}
@@
 
-\autoref{fig:sine-assess-metric} shows an example assessment metric plot.
+\autoref{fig:figure-07} shows an example assessment metric plot.
 The three metrics are computed for each of the LIME applications to the \data \ test set.
@@
 
-Recall that \autoref{fig:sine-feat-heat} indicated that the kernel density method selected the same feature across all cases in the test set for both the first and second features.
+Recall that \autoref{fig:figure-06} indicated that the kernel density method selected the same feature across all cases in the test set for both the first and second features.
 It appears that a global trend may be the best explanation for this example, which may be reasonable considering that we know that both $x_1$ and $x_2$ are the two features that should be the features used by the random forest to distinguish between response categories.
@@
 bullet_features_ordered <-
-  data.frame(feature = rownames(bulletxtrctr::rtrees$importance),
-             MeanDecreaseGini = bulletxtrctr::rtrees$importance) %>%
+  data.frame(
+    feature = rownames(bulletxtrctr::rtrees$importance),
+    MeanDecreaseGini = bulletxtrctr::rtrees$importance
+  ) %>%
   arrange(desc(MeanDecreaseGini)) %>%
-  mutate(feature = fct_recode(feature,
+  mutate(
+    feature = fct_recode(
+      feature,
       "CCF" = "ccf",
@@
       "Distance" = "D",
-                              "Sum Peaks" = "sum_peaks"))
+      "Sum Peaks" = "sum_peaks"
+    )
+  )
 
@@
 
-In current practice, forensic firearm examiners evaluate whether two bullets are from the same source (fired from the same gun) or from different sources based on microscopic comparison of the striation patterns engraved on bullets during the firing process (see \autoref{fig:bullet}).
+In current practice, forensic firearm examiners evaluate whether two bullets are from the same source (fired from the same gun) or from different sources based on microscopic comparison of the striation patterns engraved on bullets during the firing process (see \autoref{fig:figure-08}).
 The process is based on a visual and therefore subjective assessment of the evidence.
@@
 In response, \citet{hare:2016} proposed an automated machine learning method for bullet matching to complement a visual inspection by firearm examiners.
-Based on high-resolution topological scans of land engraved areas, \citet{hare:2016} obtain signatures of striations from two bullet lands (\autoref{fig:signatures}).
+Based on high-resolution topological scans of land engraved areas, \citet{hare:2016} obtain signatures of striations from two bullet lands (\autoref{fig:figure-09}).
 Nine features quantifying the similarity of signatures, such as the cross-correlation function, the distance between signatures, and the number of matching striae, are extracted and used to train a random forest (available in the \emph{bulletxtrctr} R package) to determine the probability of a comparison resulting from the same source (matching signatures) or from different sources (non-matching signatures).
@@
 
+<<converting-static-figs-to-eps>>=
+
+# Convert the bullet figure to eps (if needed)
+if (!file.exists("./figure-static/figure-08.eps")) {
+  bullets <- image_read("./figure-static/figure-08.png")
+  image_write(bullets, path = "./figure-static/figure-08.eps", format = "eps")
+}
+
+# Convert the signature figure to eps (if needed)
+if (!file.exists("./figure-static/figure-09.eps")) {
+  signatures <- image_read("./figure-static/figure-09.png")
+  image_write(signatures, path = "./figure-static/figure-09.eps", format = "eps")
+}
+
+@
+
 \begin{figure}[!t]
 \centering
-\includegraphics[width=2.75in]{./figure-static/bullets.png}
+\includegraphics[width=2.25in]{./figure-static/figure-08.eps}
 \caption{(Top left) Traditionally rifled gun barrel.
@@
 (Bottom) Close up of a land engraved area showing striations (vertical lines).}
-\label{fig:bullet}
+\label{fig:figure-08}
 
@@
 
-\includegraphics[width=3.125in]{./figure-static/signatures.png}
+\includegraphics[width=2.25in]{./figure-static/figure-09.eps}
 \caption{Example bullet signatures.
@@
 The \citet{hare:2016} random forest is fit using various features that measure the similarity between two such signatures.}
-\label{fig:signatures}
+\label{fig:figure-09}
 \end{figure}
@@
 \begin{figure*}[!thp]
-<<bullet-plot-rfpcp, out.width = '6.5in', warning = FALSE>>=
+<<figure-10, out.width = '6.5in', warning = FALSE>>=
 
 # Create (or load) the parallel coordinate plot
-if (file.exists("./figure-static/bullet_pcp.png")) {
+if (file.exists("./figure-static/figure-10.eps")) {
 
   # Load and print the plot
-  knitr::include_graphics("./figure-static/bullet_pcp.png")
+  knitr::include_graphics("./figure-static/figure-10.eps")
 
 } else {
+
+  # Specify the figure size (for determining font size)
+  f10_ow = 6.5
+  f10_fw = 7.5
+  f10_fs = 7 * (f10_fw / f10_ow)
+  f10_ls = 0.5 * (f10_fw / f10_ow)
 
@@
               .id = "set") %>%
-    mutate(set = fct_recode(set,
+    mutate(
+      set = fct_recode(set,
                        "Training Set" = "1",
                        "Testing Set" = "2"),
-           samesource = fct_recode(factor(samesource),
+      samesource = fct_recode(
+        factor(samesource),
         "Match" = "TRUE",
-                                  "Non-Match" = "FALSE")) %>%
-    rename("CCF" = "ccf", "CMS" = "cms", "Matches" = "matches",
-           "Mismatches" = "mismatches", "Non-CMS" = "non_cms",
-           "Rough Correlation" = "rough_cor", "Distance Std Dev" = "sd_D",
-           "Distance" = "D", "Sum Peaks" = "sum_peaks") %>%
+        "Non-Match" = "FALSE"
+      )
+    ) %>%
+    rename(
+      "CCF" = "ccf",
+      "CMS" = "cms",
+      "Matches" = "matches",
+      "Mismatches" = "mismatches",
+      "Non-CMS" = "non_cms",
+      "Rough Correlation" = "rough_cor",
+      "Distance Std Dev" = "sd_D",
+      "Distance" = "D",
+      "Sum Peaks" = "sum_peaks"
+    ) %>%
     na.omit() %>%
     ggplot(aes(color = rfscore)) +
-    geom_pcp(aes(vars = vars(bullet_features_ordered$feature)),
-             alpha = 0.2) +
+    geom_pcp(
+      mapping = aes(vars = vars(bullet_features_ordered$feature)),
+      alpha = 0.2,
+      size = f10_ls
+    ) +
     facet_grid(set ~ samesource) +
@@
                           midpoint = 0.5) +
-    theme_bw(base_family = "Times", base_size = 10) +
-    theme(axis.text.x = element_text(angle = 45, hjust = 1),
+    theme_bw(base_family = "Times", base_size = f10_fs) +
+    theme(
+      axis.text.x = element_text(angle = 45, hjust = 1),
       strip.placement = "outside",
       strip.background = element_rect(color = "white",
-                                          fill = "white")) +
+                                      fill = "white")
+    ) +
     labs(x = "Features Ordered by Random Forest Variable Importance \n(highest to lowest from left to right)",
@@
   # Save the plot
-  ggplot2::ggsave(plot = bullet_pcp,
-                  filename = "./figure-static/bullet_pcp.png",
+  ggplot2::ggsave(
+    plot = bullet_pcp,
+    filename = "./figure-static/figure-10.png",
     width = 7.5,
     height = 3.5,
-                  units = "in")
+    units = "in",
+    dpi = 1200
+  )
+
+  # Load the figure and then save as an eps file
+  bullet_pcp <- image_read("./figure-static/figure-10.png")
+  image_write(bullet_pcp, path = "./figure-static/figure-10.eps", format = "eps")
+
 }
@@
 There are clear relationships between the feature values and the random forest probabilities.}
-\label{fig:bullet-plot-rfpcp}
+\label{fig:figure-10}
 \end{figure*}
@@
 We apply the trained random forest model from \citet{hare:2016} to another set of bullets from the Hamby study with \Sexpr{dim(bullet_test)[1]} rows of land comparisons.
-We first consider a global visualization of the relationship between the random forest predictions and the model features with a parallel coordinate plot of the training data (top facet) and testing data (bottom facets) predictions (\autoref{fig:bullet-plot-rfpcp}).
+We first consider a global visualization of the relationship between the random forest predictions and the model features with a parallel coordinate plot of the training data (top facet) and testing data (bottom facets) predictions (\autoref{fig:figure-10}).
 The majority of same source observations with random forest probabilities close to 1 have a clear pattern of corresponding feature values.
@@
   # Load the files
-  #bullet_lime_noperms <- readRDS("../data/hamby_lime.rds")
   bullet_explain_noperms <- readRDS("../data/hamby_explain.rds")
@@
   n_features = 3,
-  sim_method = c('quantile_bins', 'equal_bins', 'kernel_density', 'normal_approx'),
+  sim_method = c(
+    'quantile_bins',
+    'equal_bins',
+    'kernel_density',
+    'normal_approx'
+  ),
   nbins = 3,
@@
   all_fs = FALSE,
-  seed = 20190914)
+  seed = 20190914
+)
 
@@
   )
+
 @
@@
 
-To get an overview of the LIME explanations from the 36 applications, we consider a feature heatmap (\autoref{fig:bullet-feature-heatmap}).
+To get an overview of the LIME explanations from the 36 applications, we consider a feature heatmap (\autoref{fig:figure-11}).
 In addition to facets for simulation method and LIME feature importance, this plot includes a vertical facet for Gower power and a horizontal facet for whether the observation is a known match or non-match.
@@
 \begin{figure*}[!thp]
-<<bullet-feature-heatmap, out.width = '6.5in', fig.width = 18, fig.height = 12>>=
+<<figure-11, out.width = '6.5in', fig.width = 18, fig.height = 14>>=
+
+# Specify the figure size (for determining font size)
+f11_ow = 6.5
+f11_fw = 18
+f11_fs = fs * (f11_fw / f11_ow)
+
 # Create a feature heatmap
@@
                                reverse = TRUE) +
-  theme_bw(base_family = "Times", base_size = 16) +
+  theme_bw(base_family = "Times", base_size = f11_fs) +
   theme(
@@
 The vertical stripes of features selected indicate a dependence between the LIME explanations and tuning parameter values.}
-\label{fig:bullet-feature-heatmap}
+\label{fig:figure-11}
 
@@
 
-<<bullet-assess-metric, out.width = '6.5in', warning = FALSE, fig.width = 10, fig.height = 4>>=
+<<figure-12, out.width = '6.5in', warning = FALSE, fig.width = 10, fig.height = 4>>=
+
+# Specify the figure size (for determining font size)
+f12_ow = 6.5
+f12_fw = 10
+f12_fs = fs * (f12_fw / f12_ow)
+f12_ls = 0.5 * (f12_fw / f12_ow)
 
 # Create a metric comparison plot
-plot_metrics(bullet_explain %>% 
+plot_metrics(
+  bullet_explain %>%
     mutate(label = as.factor(label)),
-             add_lines = TRUE) +
-  theme_bw(base_family = "Times") +
-  theme(strip.background = element_rect(color = "white", fill = "white"))
+  add_lines = TRUE,
+  line_alpha = 0.75,
+  line_size = f12_ls
+) +
+  theme_bw(base_family = "Times", base_size = f12_fs) +
+  theme(
+    strip.background = element_rect(color = "white", fill = "white"),
+    strip.placement = "outside",
+    strip.text.y = element_text(size = f12_fs)
+  )
+
 @
@@
 The bin based metrics often do not agree in terms of performance across metrics.}
-\label{fig:bullet-assess-metric}
+\label{fig:figure-12}
 \end{figure*}
 
-To try to identify a set of LIME tuning parameter values with the most trustworthy set of explanations, an assessment metric plot is considered (\autoref{fig:bullet-assess-metric}).
+To try to identify a set of LIME tuning parameter values with the most trustworthy set of explanations, an assessment metric plot is considered (\autoref{fig:figure-12}).
 All density simulation methods performed well based on the three metrics.
-This is an interesting result, since \autoref{fig:bullet-feature-heatmap} shows that the density methods results in global explanations.
+This is an interesting result, since \autoref{fig:figure-11} shows that the density methods results in global explanations.
 The metric values for the bin based methods do not agree across metrics.
@@
 The applications using a power of 0.5 perform the best or as well as the other powers across all simulation methods suggesting that the power that leads to a more global explanation is preferred by LIME.
-Perhaps we can say that the kernel density method or 3 equal bins  are the best performing methods, but unfortunately, \autoref{fig:bullet-assess-metric} leaves us without a clear indication of which set of explanations to use to explain the random forest.
+Perhaps we can say that the kernel density method or 3 equal bins  are the best performing methods, but unfortunately, \autoref{fig:figure-12} leaves us without a clear indication of which set of explanations to use to explain the random forest.
 
 To provide a more detailed view of explanations obtained using different tuning parameter values, we take a closer look at explanations  for two observations of interest, which will be referred to as case M (a known match) and case NM (a known non-match), using explanation scatterplots.
-Figure~\ref{fig:bullet-eois} includes the visual representation plots of explanations (from \emph{lime}) and explanation scatterplots for cases M and NM.
+Figure~\ref{fig:figure-13} includes the visual representation plots of explanations (from \emph{lime}) and explanation scatterplots for cases M and NM.
 Plots for 3 equal bins and 3 quantile bins are included to depict tuning parameter values with good (3 equal bins) and mediocre (3 quantile bins) performance based on the assessment metric plot.
-Plots for the kernel density simulation method are included in Appendix~\ref{exp-scatter_plus} (Figure \ref{fig:bullet-expl-scat-density}).
+Plots for the kernel density simulation method are included in Appendix~\ref{exp-scatter_plus} (Figure \ref{fig:figure-B2}).
 
 First, focus on the explanation for case NM with 3 quantile bins.
-The explanation plot from \emph{lime} \sout{for case NM with 3 quantile bins} shows that an observed CCF value greater than 0.320 supports a random forest prediction in favor of a match, and the scatter plots show that many of the simulated values with CCF greater then 0.320 have random forest predictions greater than 0.5.
+The explanation plot from \emph{lime} shows that an observed CCF value greater than 0.320 supports a random forest prediction in favor of a match, and the scatter plots show that many of the simulated values with CCF greater then 0.320 have random forest predictions greater than 0.5.
 Additionally, the LIME explanation indicates that a value of matches less than or equal to 1.66 contradicts a prediction in favor of a match, and the scatter plots show that almost all simulated values with a value of matches less than or equal to 1.66 have random forest predictions close to 0.
@@
 
-<<bullet-eoi-plots, message = FALSE>>=
+\begin{figure*}[!thp]
+<<figure-13, out.width = '6.25in', fig.width = 13, fig.height = 17, message = FALSE>>=
+
+# Specify the figure size (for determining font size)
+f13_ow = 6.25
+f13_fw = 13
+f13_fs = fs * (f13_fw / f13_ow)
+f13_ls = 0.5 * (f13_fw / f13_ow)
+
+# Adjust names of the cases
 bullet_explain_perms <- bullet_explain_perms %>%
-  mutate(case = ifelse(
-    case == bullet_poi_nonmatch,
-    paste(case, "(non-match)"),
-    paste(case, "(match)")
-  ))
-
-eoi1_3qb <-
-  plot_explain_scatter(bullet_explain_perms[1:3, ], alpha = 0.9, weights = TRUE) +
+  mutate(case = ifelse(case == bullet_poi_nonmatch, "NM", "M"))
+
+# Create the explanation scatterplot: case M, 3 quantile bins
+eoiM_3qb <-
+  plot_explain_scatter(
+    bullet_explain_perms[1:3,],
+    alpha = 0.9,
+    weights = TRUE,
+    line_size = f13_ls
+  ) +
   scale_color_gradient2(
@@
   ) +
-  theme_bw(base_family = "Times", base_size = 10) +
+  theme_bw(base_family = "Times", base_size = f13_fs) +
   theme(
+    aspect.ratio = 1,
+    plot.title = element_text(size = f13_fs),
+    strip.text.x = element_text(size = f13_fs),
+    strip.text.y = element_text(size = f13_fs),
     strip.placement = "outside",
-    strip.background = element_rect(color = "white",
-                                    fill = "white")
-  ) + 
-  guides(linetype = guide_legend(override.aes = list(color = c("darkorange"))))
-
-eoi2_3qb <-
-  plot_explain_scatter(bullet_explain_perms[4:6, ], alpha = 0.9, weights = TRUE) +
+    strip.background = element_rect(color = "white", fill = "white")
+  ) +
+  guides(linetype = guide_legend(override.aes = list(color = c("darkorange"))),
+         size = guide_legend(nrow = 2, byrow = T))
+
+# Create the explanation scatterplot: case MM, 3 quantile bins
+eoiNM_3qb <-
+  plot_explain_scatter(
+    bullet_explain_perms[4:6, ],
+    alpha = 0.9,
+    weights = TRUE,
+    line_size = f13_ls
+  ) +
   scale_color_gradient2(
@@
   ) +
-  theme_bw(base_family = "Times", base_size = 10) +
+  theme_bw(base_family = "Times", base_size = f13_fs) +
   theme(
+    aspect.ratio = 1,
+    plot.title = element_text(size = f13_fs),
     strip.placement = "outside",
-    strip.background = element_rect(color = "white",
-                                    fill = "white")
-  ) + 
-  guides(linetype = guide_legend(override.aes = list(color = c("grey50", "darkorange"))))
-
-eoi1_3eb <-
-  plot_explain_scatter(bullet_explain_perms[7:9, ], alpha = 0.9, weights = TRUE) +
+    strip.background = element_rect(color = "white", fill = "white"),
+    strip.text.x = element_text(size = f13_fs),
+    strip.text.y = element_text(size = f13_fs)
+  ) +
+  guides(linetype = guide_legend(override.aes = list(color = c(
+    "grey50", "darkorange"
+  ))),
+  size = guide_legend(nrow = 2, byrow = T))
+
+# Create the explanation scatterplot: case M, 3 equal bins
+eoiM_3eb <-
+  plot_explain_scatter(
+    bullet_explain_perms[7:9,],
+    alpha = 0.9,
+    weights = TRUE,
+    line_size = f13_ls
+  ) +
   scale_color_gradient2(
@@
   ) +
-  theme_bw(base_family = "Times", base_size = 10) +
+  theme_bw(base_family = "Times", base_size = f13_fs) +
   theme(
+    aspect.ratio = 1,
+    plot.title = element_text(size = f13_fs),
     strip.placement = "outside",
-    strip.background = element_rect(color = "white",
-                                    fill = "white")
-  ) + 
-  guides(linetype = guide_legend(override.aes = list(color = c("grey50", "darkorange"))))
-
-eoi2_3eb <-
-  plot_explain_scatter(bullet_explain_perms[10:12, ], alpha = 0.9, weights = TRUE) +
+    strip.background = element_rect(color = "white", fill = "white"),
+    strip.text.x = element_text(size = f13_fs),
+    strip.text.y = element_text(size = f13_fs)
+  ) +
+  guides(linetype = guide_legend(override.aes = list(color = c(
+    "grey50", "darkorange"
+  ))),
+  size = guide_legend(nrow = 2, byrow = T))
+
+# Create the explanation scatterplot: case NM, 3 equal bins
+eoiNM_3eb <-
+  plot_explain_scatter(
+    bullet_explain_perms[10:12,],
+    alpha = 0.9,
+    weights = TRUE,
+    line_size = f13_ls
+  ) +
   scale_color_gradient2(
@@
   ) +
-  theme_bw(base_family = "Times", base_size = 10) +
+  theme_bw(base_family = "Times", base_size = f13_fs) +
   theme(
+    aspect.ratio = 1,
+    plot.title = element_text(size = f13_fs),
     strip.placement = "outside",
-    strip.background = element_rect(color = "white",
-                                    fill = "white")
-  ) + 
-  guides(linetype = guide_legend(override.aes = list(color = c("grey50", "darkorange"))))
-
-pf1_3qb <- plot_features(bullet_explain_perms[1:3,]) +
+    strip.background = element_rect(color = "white", fill = "white"),
+    strip.text.x = element_text(size = f13_fs),
+    strip.text.y = element_text(size = f13_fs)
+  ) +
+  guides(linetype = guide_legend(override.aes = list(color = c(
+    "grey50", "darkorange"
+  ))),
+  size = guide_legend(nrow = 2, byrow = T))
+
+# Create the lime explanation visualization: case M, 3 quantile bins
+pfM_3qb <- plot_features(bullet_explain_perms[1:3,]) +
   scale_fill_manual(values = c("darkorange", "grey50")) +
-  theme(text = element_text(family = "Times", size = 10))
-pf2_3qb <- plot_features(bullet_explain_perms[4:6,]) +
+  theme(text = element_text(family = "Times", size = f13_fs),
+        strip.text.x = element_text(face = "plain", size = f13_fs))
+
+# Create the lime explanation visualization: case NM, 3 quantile bins
+pfNM_3qb <- plot_features(bullet_explain_perms[4:6,]) +
   scale_fill_manual(values = c("darkorange", "grey50")) + 
-  theme(text = element_text(family = "Times", size = 10))
-pf1_3eb <- plot_features(bullet_explain_perms[7:9,]) +
+  theme(text = element_text(family = "Times", size = f13_fs),
+        strip.text.x = element_text(face = "plain", size = f13_fs))
+
+# Create the lime explanation visualization: case M, 3 equal bins
+pfM_3eb <- plot_features(bullet_explain_perms[7:9,]) +
   scale_fill_manual(values = c("darkorange", "grey50")) +
-  theme(text = element_text(family = "Times", size = 10))
-pf2_3eb <- plot_features(bullet_explain_perms[10:12,]) +
+  theme(text = element_text(family = "Times", size = f13_fs),
+        strip.text.x = element_text(face = "plain", size = f13_fs))
+
+# Create the lime explanation visualization: case NM, 3 equal bins
+pfNM_3eb <- plot_features(bullet_explain_perms[10:12,]) +
   scale_fill_manual(values = c("darkorange", "grey50")) +
-  theme(text = element_text(family = "Times", size = 10))
-@
-
-\begin{figure*}[!thp]
-<<bullet-eois, out.width = '6.25in', fig.width = 12, fig.height = 17, message = FALSE>>=
+  theme(text = element_text(family = "Times", size = f13_fs),
+        strip.text.x = element_text(face = "plain", size = f13_fs))
+
 # Join the plots
 plot_grid(
-  pf2_3qb,
-  pf2_3eb,
-  eoi2_3qb,
-  eoi2_3eb,
-  pf1_3qb,
-  pf1_3eb,
-  eoi1_3qb,
-  eoi1_3eb,
+  pfNM_3qb,
+  pfNM_3eb,
+  eoiNM_3qb,
+  eoiNM_3eb,
+  pfM_3qb,
+  pfM_3eb,
+  eoiM_3qb,
+  eoiM_3eb,
   nrow = 4,
@@
 )
+
 @
@@
 The plots provide insights into the LIME explanations and allow for the assessment of the explanation quality.}
-\label{fig:bullet-eois}
+\label{fig:figure-13}
 \end{figure*}
@@
 Without applying LIME with multiple tuning parameter values to the bullet test data or viewing diagnostic plots of the LIME explanations, it may be very possible to formulate reasons why the LIME explanations make sense.
-However, the sequence of plots in this section (Figures \ref{fig:bullet-feature-heatmap}, \ref{fig:bullet-assess-metric}, and \ref{fig:bullet-eois}) suggest that we should be cautious to trust any of these LIME explanations.
+However, the sequence of plots in this section (Figures \ref{fig:figure-11}, \ref{fig:figure-12}, and \ref{fig:figure-13}) suggest that we should be cautious to trust any of these LIME explanations.
 It appears that either LIME needs to be further tuned to provide trustworthy and good explanations, or a different approach may provide better insight.
@@
 Even though an explanation will be interpretable as long as the complexity of the explainer model is appropriately chosen, a lack of understanding of the process used to create the explanation could lead to an incorrect interpretation of the explanation.
-For example, the visualization of a LIME explanation available from the \emph{lime} R package \citep{pedersen:2020} (shown in Figures \ref{fig:sine-exp-scatter} and \ref{fig:bullet-eois}) is a major simplification of the explainer model, which could lead to under-interpreted or misinterpreted LIME explanation.
-Supplementing \citet{pedersen:2020}'s compact visualization of the explanation with an explanation scatterplot that shows a more detailed visualization of the explainer model (such as Figures~\ref{fig:sine-exp-scatter} and \ref{fig:bullet-eois}) promotes a more complete understanding of the explanation.
+For example, the visualization of a LIME explanation available from the \emph{lime} R package \citep{pedersen:2020} (shown in Figures \ref{fig:figure-04} and \ref{fig:figure-13}) is a major simplification of the explainer model, which could lead to under-interpreted or misinterpreted LIME explanation.
+Supplementing \citet{pedersen:2020}'s compact visualization of the explanation with an explanation scatterplot that shows a more detailed visualization of the explainer model (such as Figures~\ref{fig:figure-04} and \ref{fig:figure-13}) promotes a more complete understanding of the explanation.
 
@@
 The explanation scatterplots allow for a comparison of the explainer model to the complex model.
-The examples in this paper show cases where the explainer model bins do not accurately capture the regions with similar random forest probabilities that contain the prediction of interest and oversimplify the model (Figures \ref{fig:sine-exp-scatter} and \ref{fig:bullet-eois}).
+The examples in this paper show cases where the explainer model bins do not accurately capture the regions with similar random forest probabilities that contain the prediction of interest and oversimplify the model (Figures \ref{fig:figure-04} and \ref{fig:figure-13}).
 Using fewer bins would clearly not help improve the faithfulness of the explainer model in these examples, and while an increase in the number of bins would lead to a finer resolution of the random forest classification boundaries, interpretability of the explainer model would quickly be lost.
@@
 In addition to assessing faithfulness by visually comparing the complex and explainer model, we propose a visual comparison of two faithfulness metrics (MSEE and average fidelity).
-The examples of faithfulness metric comparisons in this paper (Figures \ref{fig:sine-assess-metric} and \ref{fig:bullet-assess-metric}) both produced conflicting results.
-The density based simulation methods result in the best or close to the best performance even though the feature heatmaps (Figures \ref{fig:sine-feat-heat} and \ref{fig:bullet-feature-heatmap}) show that the density simulation methods produce global explanations with minimal variation in features selected by LIME.
+The examples of faithfulness metric comparisons in this paper (Figures \ref{fig:figure-07} and \ref{fig:figure-12}) both produced conflicting results.
+The density based simulation methods result in the best or close to the best performance even though the feature heatmaps (Figures \ref{fig:figure-06} and \ref{fig:figure-11}) show that the density simulation methods produce global explanations with minimal variation in features selected by LIME.
 For the bin based simulation methods, the two metrics often do not agree or contradict one another, which makes it difficult to decide on a recommendation of a set of tuning parameter values that produce the explanations with the most faithful explainer model.
@@
 Most of the average $R^2$ values in the examples from this paper are below 0.5 suggesting a poor linear fit of the explainer models.
-The poor linear fit of the explainer model is also seen with the residual plot (\autoref{fig:sine-plot-resids}).
+The poor linear fit of the explainer model is also seen with the residual plot (\autoref{fig:figure-C3}).
 
@@
 
-The following tuning parameters for the LIME algorithm are available in the \emph{lime} R package \citep[pedersen:2020].
+The following tuning parameters for the LIME algorithm are available in the \emph{lime} R package \citep{pedersen:2020}.
 
@@
 Section \ref{exp-scatter} introduces explanation scatterplots under the default simulation method in the \emph{lime} R package: four quantile bins.
-The structure of an explanation scatterplot remains the same \sout{for} if any bin based simulation method is used \sout{to create the simulated data}, i.e., any number of quantile or equally spaced bins.
-However, if the kernel density or normal approximation simulation methods are used \sout{as the simulation method}, the format of the explanation scatterplot changes.
+The structure of an explanation scatterplot remains the same if any bin based simulation method is used, i.e., any number of quantile or equally spaced bins.
+However, if the kernel density or normal approximation simulation methods are used, the format of the explanation scatterplot changes.
 In the density based simulation method scenarios, LIME uses the standardized versions of the predictor variables to fit the explainer model.
@@
 
-Figure \ref{fig:sine-expl-scat-density} provides example explanation scatterplots for each feature in the default LIME explanation obtained using the kernel density simulation method for the \data \ prediction of interest.
-Figure \ref{fig:bullet-expl-scat-density} includes explanation scatterplots for the explanations generated using kernel density simulation for the bullet example cases M and NM discussed in Section \ref{bullet-assess-ex}.
+Figure \ref{fig:figure-B1} provides example explanation scatterplots for each feature in the default LIME explanation obtained using the kernel density simulation method for the \data \ prediction of interest.
+Figure \ref{fig:figure-B2} includes explanation scatterplots for the explanations generated using kernel density simulation for the bullet example cases M and NM discussed in Section \ref{bullet-assess-ex}.
 
 \begin{figure*}[!thp]
-<<sine-expl-scat-density, out.width = '6.5in', fig.width = 12, fig.height = 4.5, fig.align = "center">>=
+<<figure-B1, out.width = '6.5in', fig.width = 12, fig.height = 5, fig.align = "center">>=
+
+# Specify the figure size (for determining font size and line size)
+fb1_ow = 6.5
+fb1_fw = 12
+fb1_fs = fs * (fb1_fw / fb1_ow)
+fb1_ls = 0.5 * (fb1_fw / fb1_ow)
+
+# Create the explanation scatterplot
 plot_explain_scatter(
@@
     filter(sim_method == "kernel_density", case == sine_poi %>% pull(case)),
-  alpha = 0.75, title.opt = FALSE
-) + 
-  theme_bw(base_family = "Times") +
-  theme(strip.background = element_rect(fill = "white", color = "white"),
-        strip.placement = "outside")
+  alpha = 0.75,
+  title.opt = FALSE, 
+  line_size = fb1_ls 
+) +
+  theme_bw(base_family = "Times", base_size = fb1_fs) +
+  theme(
+    strip.background = element_rect(fill = "white", color = "white"),
+    strip.placement = "outside",
+    strip.text.x = element_text(size = fb1_fs)
+  )
+
 @
 \caption{Explanation scatterplots for the \data \ prediction of interest with the kernel density simulation method.}
-\label{fig:sine-expl-scat-density}
+\label{fig:figure-B1}
 \end{figure*}
@@
 \begin{figure*}[!thp]
-<<bullet-expl-scat-density, out.width = '6.5in', fig.width = 12, fig.height = 9, fig.align = "center">>=
+<<figure-B2, out.width = '6.5in', fig.width = 12, fig.height = 10, fig.align = "center">>=
+
+# Specify the figure size (for determining font size and line size)
+fb2_ow = 6.5
+fb2_fw = 12
+fb2_fs = fs * (fb2_fw / fb2_ow)
+fb2_ls = 0.5 * (fb2_fw / fb2_ow)
+
+# Create the explanation scatterplot: case M, kernel density
+bullet_es_M <-
+  plot_explain_scatter(
+    bullet_explain_perms[16:18,] %>% mutate(case = "NM"),
+    alpha = 0.75,
+    title.opt = TRUE, 
+    line_size = fb2_ls
+  ) +
+  theme_bw(base_family = "Times", base_size = fb2_fs) +
+  theme(
+    aspect.ratio = 1,
+    strip.background = element_rect(fill = "white", color = "white"),
+    strip.placement = "outside",
+    strip.text.x = element_text(size = fb2_fs),
+    plot.title = element_text(size = fb2_fs)
+  )
+
+# Create the explanation scatterplot: case NM, kernel density
 bullet_es_NM <-
@@
     bullet_explain_perms[13:15, ] %>% mutate(case = "M"),
-  alpha = 0.75, title.opt = TRUE
-) +
-  theme_bw(base_family = "Times") +
-  theme(strip.background = element_rect(fill = "white", color = "white"),
-        strip.placement = "outside")
-
-bullet_es_M <-
-  plot_explain_scatter(
-  bullet_explain_perms[16:18, ] %>% mutate(case = "NM"),
-  alpha = 0.75, title.opt = TRUE
-) +
-  theme_bw(base_family = "Times") +
-  theme(strip.background = element_rect(fill = "white", color = "white"),
-        strip.placement = "outside")
-
+    alpha = 0.75,
+    title.opt = TRUE, 
+    line_size = fb2_ls
+  ) +
+  theme_bw(base_family = "Times", base_size = fb2_fs) +
+  theme(
+    aspect.ratio = 1,
+    strip.background = element_rect(fill = "white", color = "white"),
+    strip.placement = "outside",
+    strip.text.x = element_text(size = fb2_fs), 
+    plot.title = element_text(size = fb2_fs)
+  )
+
+# Join the plots
 plot_grid(bullet_es_NM, bullet_es_M, nrow = 2)
+
 @
 \caption{Explanation scatterplots for LIME explanations using kernel density simulation for the cases M and NM of the bullet comparison.}
-\label{fig:bullet-expl-scat-density}
+\label{fig:figure-B2}
 \end{figure*}
@@
 In order to assess the claim of linearity for the \data \ prediction of interest discussed in Section \ref{exp-scatter}, we use one of the most basic diagnostics in a statistician's tool box and draw a residual plot for the explainer model.
-This is shown in Figure \ref{fig:sine-plot-resids} with the explainer model residuals on the y-axis and explainer model predictions on the x-axis.
+This is shown in Figure \ref{fig:figure-C3} with the explainer model residuals on the y-axis and explainer model predictions on the x-axis.
 The points along the x-axis have been jittered to ease the effect of the over-plotted points in the visualization.
@@
 \begin{figure}[!thp]
-<<sine-plot-resids, out.width = '3.125in', fig.width = 5, fig.height = 4, warning = FALSE>>=
+<<figure-C3, out.width = '3.125in', fig.width = 5, fig.height = 4, warning = FALSE>>=
+
+# Specify the figure size (for determining font size and line size)
+fc3_ow = 3.125
+fc3_fw = 5
+fc3_fs = fs * (fc3_fw / fc3_ow)
+fc3_ls = 0.5 * (fc3_fw / fc3_ow)
 
@@
 sine_poi_explainer <-
-  function(x1, x2) sine_b0 + (sine_b1 * x1) + (sine_b2 * x2)
+  function(x1, x2)
+    sine_b0 + (sine_b1 * x1) + (sine_b2 * x2)
 sine_poi_perms <- sine_poi_perms %>%
@@
 ggplot(sine_poi_perms, aes(x = exppred, y = resid)) +
+  geom_hline(yintercept = 0, size = fc3_ls) +
   geom_jitter(alpha = 0.5, width = 0.02) +
-  geom_hline(yintercept = 0) +
-  theme_bw(base_family = "Times", base_size = 10) +
+  theme_bw(base_family = "Times", base_size = fc3_fs) +
+  theme(plot.title = element_text(size = fc3_fs)) +
   labs(x = "Explainer Model Predictions",
@@
        title = "Explainer Model Residual Plot")
+
 @
@@
 There is an upward trend in the residuals as the explainer model predictions increase, which suggests a violation of the linearity assumption.}
-\label{fig:sine-plot-resids}
+\label{fig:figure-C3}
 \end{figure}

### 2020-09-03 paper.Rnw
updated code for creating/loading static figures

@@
 
-<<converting-static-figs-to-eps>>=
-
-# Convert the bullet figure to eps (if needed)
-if (!file.exists("./figure-static/figure-08.eps")) {
-  bullets <- image_read("./figure-static/figure-08.png")
-  image_write(bullets, path = "./figure-static/figure-08.eps", format = "eps")
-}
-
-# Convert the signature figure to eps (if needed)
-if (!file.exists("./figure-static/figure-09.eps")) {
-  signatures <- image_read("./figure-static/figure-09.png")
-  image_write(signatures, path = "./figure-static/figure-09.eps", format = "eps")
-}
-
-@
-
 \begin{figure}[!t]
 \centering
-\includegraphics[width=2.25in]{./figure-static/figure-08.eps}
+<<figure-08, out.width = '2.25in', fig.width = 6, fig.height = 3, warning = FALSE>>=
+
+# Convert the bullet figure to eps (if needed)
+if (!file.exists("./figure-static/figure-08-1.eps")) {
+  bullets <- image_read("./figure-static/figure-08-1.png")
+  image_write(bullets, path = "./figure-static/figure-08-1.eps", format = "eps")
+}
+
+# Load and print the plot
+knitr::include_graphics("./figure-static/figure-08-1.eps")
+
+@
 \caption{(Top left) Traditionally rifled gun barrel.
@@
 
-\includegraphics[width=2.25in]{./figure-static/figure-09.eps}
+<<figure-09, out.width = '3.125in', fig.width = 6, fig.height = 3, warning = FALSE>>=
+
+# Specify the figure size (for determining font size)
+f9_ow = 3.125
+f9_fw = 6
+f9_fs = fs * (f9_fw / f9_ow)
+
+# Load the signatures data
+signatures <- readRDS("../data/signatures.rds")
+
+# Create plot of the signatures
+signatures %>%
+  mutate(land = c("Signature 1", "Signature 2")[as.factor(source)]) %>%
+  ggplot(aes(x = x/1000)) + 
+  geom_line(aes(y = sig), colour = "grey30") +
+  facet_grid(land~.) +
+  ylim(c(-4,6)) +
+  theme_bw(base_family = "Times", base_size = f9_fs) +
+  theme(strip.background = element_blank()) +
+  ylab("Surface measurement (in microns)") +
+  xlab("Relative Location (in millimeters)")
+
+@
 \caption{Example bullet signatures.
@@
 # Create (or load) the parallel coordinate plot
-if (file.exists("./figure-static/figure-10.eps")) {
-
-  # Load and print the plot
-  knitr::include_graphics("./figure-static/figure-10.eps")
-
-} else {
+if (!file.exists("./figure-static/figure-10-1.png")) {
 
@@
 
+}
+
+# Create (or load) the parallel coordinate plot
+if (file.exists("./figure-static/figure-10-1.eps")) {
+
+  # Load and print the plot
+  knitr::include_graphics("./figure-static/figure-10-1.eps")
+
+} else {
+
   # Load the figure and then save as an eps file
-  bullet_pcp <- image_read("./figure-static/figure-10.png")
-  image_write(bullet_pcp, path = "./figure-static/figure-10.eps", format = "eps")
+  bullet_pcp <- image_read("./figure-static/figure-10-1.png")
+  image_write(bullet_pcp, path = "./figure-static/figure-10-1.eps", format = "eps")
 

### 2020-09-03 submission/paper-submission.Rnw
adding the paper files and code for submission

--- 2020-09-03 paper.Rnw
@@
   dev.args = list(fallback_resolution = 800),
-  dpi = 1200
+  dpi = 1200,
+  fig.path = ""
 )
@@
 # Apply LIME with various tuning parameters to the sine data
-if (!file.exists("../data/sine_lime_explain.rds")) {
+if (!file.exists("sine_lime_explain.rds")) {
 
@@
 
-    saveRDS(sine_lime_explain, "../data/sine_lime_explain.rds")
+    saveRDS(sine_lime_explain, "sine_lime_explain.rds")
 
@@
 
-    sine_lime_explain <- readRDS("../data/sine_lime_explain.rds")
+    sine_lime_explain <- readRDS("sine_lime_explain.rds")
 
@@
 # Load the hamby data
-bullet_train <- read.csv("../data/hamby173and252_train.csv")
-bullet_test <- read.csv("../data/hamby224_test.csv")
+bullet_train <- read.csv("hamby173and252_train.csv")
+bullet_test <- read.csv("hamby224_test.csv")
 
@@
 # Convert the bullet figure to eps (if needed)
-if (!file.exists("./figure-static/figure-08-1.eps")) {
-  bullets <- image_read("./figure-static/figure-08-1.png")
-  image_write(bullets, path = "./figure-static/figure-08-1.eps", format = "eps")
+if (!file.exists("figure-08-1.eps")) {
+  bullets <- image_read("figure-08-1.png")
+  image_write(bullets, path = "figure-08-1.eps", format = "eps")
 }
@@
 # Load and print the plot
-knitr::include_graphics("./figure-static/figure-08-1.eps")
+knitr::include_graphics("figure-08-1.eps")
 
@@
 # Load the signatures data
-signatures <- readRDS("../data/signatures.rds")
+signatures <- readRDS("signatures.rds")
 
@@
 # Create (or load) the parallel coordinate plot
-if (!file.exists("./figure-static/figure-10-1.png")) {
+if (!file.exists("figure-10-1.png")) {
 
@@
     plot = bullet_pcp,
-    filename = "./figure-static/figure-10.png",
+    filename = "figure-10.png",
     width = 7.5,
@@
 # Create (or load) the parallel coordinate plot
-if (file.exists("./figure-static/figure-10-1.eps")) {
+if (file.exists("figure-10-1.eps")) {
 
   # Load and print the plot
-  knitr::include_graphics("./figure-static/figure-10-1.eps")
-
-} else {
+  knitr::include_graphics("figure-10-1.eps")
+
+} else {on
 
   # Load the figure and then save as an eps file
-  bullet_pcp <- image_read("./figure-static/figure-10-1.png")
-  image_write(bullet_pcp, path = "./figure-static/figure-10-1.eps", format = "eps")
+  bullet_pcp <- image_read("figure-10-1.png")
+  image_write(bullet_pcp, path = "figure-10-1.eps", format = "eps")
 
@@
 # Apply LIME to all but two cases without returning the permutations
-if (file.exists("../data/hamby_lime.rds")){
+if (file.exists("hamby_lime.rds")){
 
   # Load the files
-  bullet_explain_noperms <- readRDS("../data/hamby_explain.rds")
+  bullet_explain_noperms <- readRDS("hamby_explain.rds")
 
@@
   saveRDS(object = bullet_lime_noperms,
-          file = "../data/hamby_lime.rds")
+          file = "hamby_lime.rds")
   saveRDS(object = bullet_explain_noperms,
-          file = "../data/hamby_explain.rds")
+          file = "hamby_explain.rds")
 

### 2020-09-03 submission/code.R

@@ -1,0 +1,1454 @@
+## ----setup, echo = FALSE, include = FALSE------------------------
+
+# Specify global options
+knitr::opts_chunk$set(
+  warning = FALSE,
+  message = FALSE,
+  echo = FALSE,
+  fig.keep = 'high',
+  fig.align = 'center',
+  dev = c("cairo_pdf", "cairo_ps"),
+  dev.args = list(fallback_resolution = 800),
+  dpi = 1200,
+  fig.path = ""
+)
+
+# Load packages
+library(Cairo)
+library(caret)
+library(cowplot)
+library(dplyr)
+library(forcats)
+library(ggforce)
+library(ggplot2)
+library(ggpcp) #devtools::install_github("yaweige/ggpcp", build_vignettes = TRUE)
+library(glmnet)
+library(gower)
+library(graphics)
+library(gretchenalbrecht) #devtools::install_github("dicook/gretchenalbrecht")
+library(latex2exp)
+library(lime) #devtools::install_github("goodekat/lime")
+library(limeaid) #devtools::install_github("goodekat/limeaid")
+library(magick)
+library(purrr)
+library(randomForest)
+library(stringr)
+library(tidyr)
+
+# Specify the (base) font size for all plots
+fs = 7
+
+
+## ----concept-data------------------------------------------------
+
+# Simulate example data
+set.seed(20190624)
+lime_data <-
+  data.frame(
+    feature1 = sort(runif(250, 0, 1)),
+    feature2 = sample(x = 1:250, size = 250, replace = FALSE)) %>%
+  mutate(
+    feature1_stnd = (feature1 - mean(feature1)) / sd(feature1),
+    feature2_stnd = (feature2 - mean(feature2)) / sd(feature2),
+    prediction = if_else(feature1 >= 0 & feature1 < 0.1,
+                         (0.3 * feature1) + rnorm(n(), 0, 0.01),
+                 if_else(feature1 >= 0.1 & feature1 < 0.3,
+                         rbeta(n(), 1, 0.5),
+                 if_else(feature1 >= 0.3 & feature1 < 0.5,
+                         sin(pi* feature1) + rnorm(n(), 0, 0.5),
+                 if_else(feature1 >= 0.5 & feature1 < 0.8,
+                         -(sin(pi* feature1) + rnorm(n(), 0, 0.1)) + 1,
+                 if_else(feature1 >= 0.8 & feature1 < 0.9,
[…]

### 2020-09-04 paper.tex
added tex files

--- 2020-09-03 paper.Rnw
@@
-\documentclass[AMS,STIX2COL]{WileyNJD-v2}
+\documentclass[AMS,STIX2COL]{WileyNJD-v2}\usepackage[]{graphicx}\usepackage[]{color}
+% maxwidth is the original width if it is less than linewidth
+% otherwise use linewidth (to make sure the graphics do not exceed the margin)
+\makeatletter
+\def\maxwidth{ %
+  \ifdim\Gin@nat@width>\linewidth
+    \linewidth
+  \else
+    \Gin@nat@width
+  \fi
+}
+\makeatother
+
+\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
+\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
+\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
+\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
+\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
+\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
+\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
+\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
+\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
+\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%
+\let\hlipl\hlkwb
+
+\usepackage{framed}
+\makeatletter
+\newenvironment{kframe}{%
+ \def\at@end@of@kframe{}%
+ \ifinner\ifhmode%
+  \def\at@end@of@kframe{\end{minipage}}%
+  \begin{minipage}{\columnwidth}%
+ \fi\fi%
+ \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
+ \colorbox{shadecolor}{##1}\hskip-\fboxsep
+     % There is no \\@totalrightmargin, so:
+     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
+ \MakeFramed {\advance\hsize-\width
+   \@totalleftmargin\z@ \linewidth\hsize
+   \@setminipage}}%
+ {\par\unskip\endMakeFramed%
+ \at@end@of@kframe}
+\makeatother
+
+\definecolor{shadecolor}{rgb}{.97, .97, .97}
+\definecolor{messagecolor}{rgb}{0, 0, 0}
+\definecolor{warningcolor}{rgb}{1, 0, 1}
+\definecolor{errorcolor}{rgb}{1, 0, 0}
+\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX
+
+\usepackage{alltt}
 
@@
 \raggedbottom
-
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
 \begin{document}
@@
 
-<<setup, echo = FALSE, include = FALSE>>=
-
-# Specify global options
-knitr::opts_chunk$set(
-  warning = FALSE,
-  message = FALSE,
-  echo = FALSE,
-  fig.keep = 'high',
-  fig.align = 'center',
-  dev = c("cairo_pdf", "cairo_ps"),
-  dev.args = list(fallback_resolution = 800),
-  dpi = 1200
-)
-
-# Load packages
-library(Cairo)
-library(caret)
-library(cowplot)
-library(dplyr)
-library(forcats)
-library(ggforce)
-library(ggplot2)
-library(ggpcp) #devtools::install_github("yaweige/ggpcp", build_vignettes = TRUE)
-library(glmnet)
-library(gower)
-library(graphics)
-library(gretchenalbrecht) #devtools::install_github("dicook/gretchenalbrecht")
-library(latex2exp)
-library(lime) #devtools::install_github("goodekat/lime")
-library(limeaid) #devtools::install_github("goodekat/limeaid")
-library(magick)
-library(purrr)
-library(randomForest)
-library(stringr)
-library(tidyr)
-
-# Specify the (base) font size for all plots
-fs = 7
-@
-
 \section{Introduction}
@@
 
-<<concept-data>>=
-
-# Simulate example data
-set.seed(20190624)
-lime_data <-
-  data.frame(
-    feature1 = sort(runif(250, 0, 1)),
-    feature2 = sample(x = 1:250, size = 250, replace = FALSE)) %>%
-  mutate(
-    feature1_stnd = (feature1 - mean(feature1)) / sd(feature1),
-    feature2_stnd = (feature2 - mean(feature2)) / sd(feature2),
-    prediction = if_else(feature1 >= 0 & feature1 < 0.1,
-                         (0.3 * feature1) + rnorm(n(), 0, 0.01),
-                 if_else(feature1 >= 0.1 & feature1 < 0.3,
-                         rbeta(n(), 1, 0.5),
-                 if_else(feature1 >= 0.3 & feature1 < 0.5,
-                         sin(pi* feature1) + rnorm(n(), 0, 0.5),
-                 if_else(feature1 >= 0.5 & feature1 < 0.8,
-                         -(sin(pi* feature1) + rnorm(n(), 0, 0.1)) + 1,
-                 if_else(feature1 >= 0.8 & feature1 < 0.9,
-                         0.5 + runif(n(), -0.5, 0.5),
-                         0.5 + rnorm(n(), 0, 0.3))))))) %>%
-  bind_rows(
-    data.frame(feature1 = rep(1, 30) + rnorm(5, 0, 0.05),
-           feature2 = rep(245, 30) + rnorm(5, 0, 1),
-           prediction = rep(0, 30) + rnorm(5, 0, 0.05)) %>%
-  mutate(feature1_stnd = (feature1 - mean(feature1)) / sd(feature1),
-         feature2_stnd = (feature2 - mean(feature2)) / sd(feature2)))
-
-# Specify a prediction of interest
-prediction_of_interest <-
-  data.frame(feature1 = 0.07, feature2 = 200) %>%
-  mutate(feature1_stnd = (feature1 - mean(lime_data$feature1)) /
-           sd(lime_data$feature1),
-         feature2_stnd = (feature2 - mean(lime_data$feature2)) /
-           sd(lime_data$feature2),
-         prediction = 0.05,
-         color = factor("Prediction \nof Interest"))
-
-# Specify the gower exponents
-good_gower_power <- 50
-bad_gower_power <- 1
-
-# Compute the good distances between the prediction of interest
-# and all other observations
-lime_data$distance_good <-
-  (1 - gower_dist(x = prediction_of_interest %>%
-                    select(feature1_stnd, feature2_stnd),
-                  y = lime_data %>%
-                    select(feature1_stnd,
-                           feature2_stnd)))^good_gower_power
-
-# Compute the bad distances between the prediction of interest
-# and all other observations
-lime_data$distance_bad <-
-  (1 - gower_dist(x = prediction_of_interest %>%
-                    select(feature1_stnd, feature2_stnd),
-                  y = lime_data %>%
-                    select(feature1_stnd,
-                           feature2_stnd)))^bad_gower_power
-
-# Prepare the data for plotting
-lime_data_gathered <- lime_data %>%
-  gather(feature, feature_stnd_value,
-         feature1_stnd:feature2_stnd) %>%
-  gather(distance, distance_value, distance_good:distance_bad) %>%
-  mutate(distance = fct_recode(distance,
-                               "good" = "distance_good",
-                               "bad" = "distance_bad"),
-         feature = fct_recode(feature,
-                              "Feature 1" = "feature1_stnd",
-                              "Feature 2" = "feature2_stnd"))
-
-# Prepare the prediction of interest data for plotting
-prediction_of_interest_gathered <- prediction_of_interest %>%
-  select(-feature1, -feature2) %>%
-  gather(feature, feature_value, feature1_stnd, feature2_stnd) %>%
-  mutate(feature = fct_recode(feature,
-                              "Feature 1" = "feature1_stnd",
-                              "Feature 2" = "feature2_stnd"))
-
-@
-
-<<concept-explainers>>=
-
-# Fit the good interpretable explainer model
-explainer_good <-
-  glmnet(x = lime_data %>% select(feature1_stnd, feature2_stnd)
-         %>% as.matrix(),
-         y = lime_data$prediction,
-         alpha = 0,
-         lambda = 1,
-         weights = lime_data$distance_good)
-
-# Fit the bad interpretable explainer model
-explainer_bad <-
-  glmnet(x = lime_data %>% select(feature1_stnd, feature2_stnd)
-         %>% as.matrix(),
-         y = lime_data$prediction,
-         alpha = 0,
-         lambda = 1,
-         weights = lime_data$distance_bad)
-
-# Join the coefficients from the explainer model into a dataframe
-coefs_data <- data.frame(case = c("good", "bad"),
-                         b0 = c(coef(explainer_good)[1],
-                                coef(explainer_bad)[1]),
-                         b1 = c(coef(explainer_good)[2],
-                                coef(explainer_bad)[2]),
-                         b2 = c(coef(explainer_good)[3],
-                                coef(explainer_bad)[3])) %>%
-  mutate(feature1 = b0 + b2*prediction_of_interest$feature2_stnd,
-         feature2 = b0 + b1*prediction_of_interest$feature1_stnd) %>%
-  gather(key = feature, value = int, feature1:feature2) %>%
-  mutate(slope = c(coef(explainer_good)[2],
-                   coef(explainer_good)[3],
-                   coef(explainer_bad)[2],
-                   coef(explainer_bad)[3]),
-         feature = fct_recode(feature,
-                              "Feature 1" = "feature1",
-                              "Feature 2" = "feature2"))
-
-@
-
 \begin{figure*}[!thp]
-<<figure-01, out.width = '6.5in', fig.width = 7.95, fig.height = 3.75, warning = FALSE>>=
-
-# Specify the figure size (for determining font size)
-f1_ow = 6.5
-f1_fw = 7.95
-f1_fs = fs * (f1_fw / f1_ow)
-
-# Plot of good explainer model
-ggplot() +
-  facet_grid(. ~ feature, switch = "x") +
-  geom_point(
-    data = lime_data_gathered,
-    mapping = aes(
-      x = feature_stnd_value,
-      y = prediction,
-      size = distance_value,
-      alpha = distance_value,
-      color = distance
-    )
-  ) +
-  geom_abline(
-    data = coefs_data %>% filter(case == "good"),
-    mapping = aes(intercept = int, slope = slope),
-    size = 1
-  ) +
-  scale_alpha(range = c(0.3, 1)) +
-  scale_color_manual(values = c(NA, "grey30"), guide = "none") +
-  geom_point(
-    data = prediction_of_interest_gathered,
-    mapping = aes(x = feature_value,
-                  y = prediction,
-                  fill = color),
-    color = "black",
-    size = 5,
-    shape = 23,
-    alpha = 0.75
-  ) +
-  scale_fill_manual(values = "#FAAA72") +
-  geom_text(
-    data = data.frame(
-      feature_stnd_value = 1.2,
-      prediction = 1.6,
-      feature = c("Feature 1", "Feature 2"),
-      slope = c(
-        paste(
-          "Slope:",
-          coefs_data %>%
-            filter(case == "good",
-                   feature == "Feature 1") %>%
-            pull(slope) %>%
-            round(3)
-        ),
-        paste(
-          "Slope:",
-          coefs_data %>%
-            filter(case == "good",
-                   feature == "Feature 2") %>%
-            pull(slope) %>%
-            round(3)
-        )
-      )
-    ),
-    mapping = aes(x = feature_stnd_value,
-                  y = prediction,
-                  label = slope),
-    family = "Times",
-    size = f1_fs / 2.85
-  ) +
-  labs(
-    x = "",
-    y = "Black-Box Prediction",
-    title = "Conceptual Depiction of a Faithful Local Explainer Model",
-    subtitle = paste("Gower Distance Metric Exponent:", good_gower_power),
-    fill = "",
-    alpha = "Weight",
-    size = "Weight"
-  ) +
-  theme_linedraw(base_family = "Times", base_size = f1_fs) +
-  theme(
-    panel.grid.major = element_blank(),
-    panel.grid.minor = element_blank(),
-    axis.text.x = element_blank(),
-    axis.ticks.x = element_blank(),
-    axis.text.y = element_blank(),
-    axis.ticks.y = element_blank(),
-    strip.placement = "outside",
-    strip.background = element_rect(color = "white", fill = "white"),
-    strip.text.x = element_text(size = f1_fs, color = "black"),
-    plot.title = element_text(size = f1_fs)
-  ) +
-  guides(
-    fill = guide_legend(order = 1),
-    size = guide_legend(order = 2),
-    alpha = guide_legend(order = 2)
-  )
-
-@
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+
+{\centering \includegraphics[width=6.5in]{figure/figure-01-1}
+
+}
+
+\end{knitrout}
 \caption{A conceptual depiction of a faithful LIME explainer model in the immediate neighborhood of a prediction of interest.
@@
 The diamond shaped points represent the location of a prediction of interest.
-The size and opacity of the circular points indicate the weight assigned based on the distance to the prediction of interest computed using the inverse of the Gower distance metric raised to the power of \Sexpr{good_gower_power}.
+The size and opacity of the circular points indicate the weight assigned based on the distance to the prediction of interest computed using the inverse of the Gower distance metric raised to the power of 50.
 The black lines represent  a weighted ridge regression model used as an explainer model that reasonably captures the relationship between the black-box predictions and the features in a local region around the prediction of interest.
@@
 
-<<figure-02, out.width = '6.5in', fig.width = 7.95, fig.height = 3.75, warning = FALSE>>=
-
-# Specify the figure size (for determining font size)
-f2_ow = 6.5
-f2_fw = 7.95
-f2_fs = fs * (f2_fw / f2_ow)
-
-# Plot of good explainer model
-ggplot() +
-  facet_grid(. ~ feature, switch = "x") +
-  geom_point(
-    data = lime_data_gathered,
-    mapping = aes(
-      x = feature_stnd_value,
-      y = prediction,
-      size = distance_value,
-      alpha = distance_value,
-      color = distance
-    )
-  ) +
-  geom_abline(
-    data = coefs_data %>% filter(case == "bad"),
-    mapping = aes(intercept = int, slope = slope),
-    size = 1
-  ) +
-  scale_alpha(range = c(0.3, 1)) +
-  scale_color_manual(values = c("grey30", NA), guide = "none") +
-  geom_point(
-    data = prediction_of_interest_gathered,
-    mapping = aes(x = feature_value,
-                  y = prediction,
-                  fill = color),
-    color = "black",
-    size = 5,
-    shape = 23,
-    alpha = 0.75
-  ) +
-  scale_fill_manual(values = "#FAAA72") +
-  geom_text(
-    data = data.frame(
-      feature_stnd_value = 1.2,
-      prediction = 1.6,
-      feature = c("Feature 1", "Feature 2"),
-      slope = c(
-        paste(
-          "Slope:",
-          coefs_data %>%
-            filter(case == "bad",
-                   feature == "Feature 1") %>%
-            pull(slope) %>%
-            round(3)
-        ),
-        paste(
-          "Slope:",
-          coefs_data %>%
-            filter(case == "bad",
-                   feature == "Feature 2") %>%
-            pull(slope) %>%
-            round(3)
-        )
-      )
-    ),
-    mapping = aes(x = feature_stnd_value,
-                  y = prediction,
-                  label = slope),
-    family = "Times",
-    size = f2_fs / 3
-  ) +
-  labs(
-    x = "",
-    y = "Black-Box Prediction",
-    title = "Conceptual Depiction of an Unfaithful Local Explainer Model",
-    subtitle = paste("Gower Distance Metric Exponent:", bad_gower_power),
-    fill = "",
-    alpha = "Weight",
-    size = "Weight"
-  ) +
-  theme_linedraw(base_family = "Times", base_size = f2_fs) +
-  theme(
-    panel.grid.major = element_blank(),
-    panel.grid.minor = element_blank(),
-    axis.text.x = element_blank(),
-    axis.ticks.x = element_blank(),
-    axis.text.y = element_blank(),
-    axis.ticks.y = element_blank(),
-    strip.placement = "outside",
-    strip.background = element_rect(color = "white", fill = "white"),
-    strip.text.x = element_text(size = f2_fs, color = "black"),
-    plot.title = element_text(size = f2_fs)
-  ) +
-  guides(
-    fill = guide_legend(order = 1),
-    size = guide_legend(order = 2),
-    alpha = guide_legend(order = 2)
-  )
-
-@
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+
+{\centering \includegraphics[width=6.5in]{figure/figure-02-1}
+
+}
+
+\end{knitrout}
 \caption{A conceptual depiction of an unfaithful local explainer model in the immediate neighborhood of a prediction of interest.
@@
 A Gower distance metric \citep{gower:1971} is used to define locality such that the size of the points represent the inverse of the Gower distance raised to some value and indicate the proximity to the prediction of interest.
-In the example of \autoref{fig:figure-01}, an exponent of \Sexpr{good_gower_power} is used to emphasize a very local region around the prediction of interest.
+In the example of \autoref{fig:figure-01}, an exponent of 50 is used to emphasize a very local region around the prediction of interest.
 A ridge regression model weighted by the proximity values is used as the explainer model with the black-box predictions as the response variable and standardized versions of two features in the data as predictor variables.
@@
 Here, the explainer model is plotted with Feature 2 fixed at the observed value of the prediction of interest.
-The explainer model captures the relationship in an  immediate neighborhood around the prediction of interest with a slope of \Sexpr{coefs_data %>% filter(case == "good", feature == "Feature 1") %>% pull(slope) %>% round(3)}.
+The explainer model captures the relationship in an  immediate neighborhood around the prediction of interest with a slope of 0.068.
 The plot on the right shows no global or local relationships between the black-box predictions and Feature 2.
-Here, the explainer model is plotted with Feature 1 set as the observed value of the prediction of interest, and it has an appropriately small slope of \Sexpr{coefs_data %>% filter(case == "good", feature == "Feature 2") %>% pull(slope) %>% round(3)}.
+Here, the explainer model is plotted with Feature 1 set as the observed value of the prediction of interest, and it has an appropriately small slope of -0.001.
 The magnitude of the slope associated with Feature 1 is larger than the slope of Feature 2, which suggests that Feature 1 plays a more important role in the prediction made by the black-box model for the prediction of interest.
@@
 We consider an example where the choice of exponent for the weights is crucial to the quality of the explanation.
-The plots in Figure \ref{fig:figure-02} show the same data as \autoref{fig:figure-01}, but the Gower distance metric exponent is decreased to \Sexpr{bad_gower_power} (the default exponent in the \emph{lime} R package).
+The plots in Figure \ref{fig:figure-02} show the same data as \autoref{fig:figure-01}, but the Gower distance metric exponent is decreased to 1 (the default exponent in the \emph{lime} R package).
 This causes the observations that are further away from the prediction of interest to be given larger weights than before.
@@
 This cannot be said of the explainer model in \autoref{fig:figure-02}.
-In addition, the magnitude of the slope associated with Feature 2  (\Sexpr{coefs_data %>% filter(case == "bad", feature == "Feature 2") %>% pull(slope) %>% round(3) %>% abs()}) is larger than that of Feature 1 (\Sexpr{coefs_data %>% filter(case == "bad", feature == "Feature 1") %>% pull(slope) %>% round(3) %>% abs()}).
+In addition, the magnitude of the slope associated with Feature 2  (0.011) is larger than that of Feature 1 (0.005).
 Thus, this explainer model actually provides a misleading explanation that Feature 2 plays a more important role in the prediction of interest.
@@
 
-All runs of LIME in this paper are executed in a forked version\footnote{https://github.com/goodekat/lime} of the R package \emph{lime} (version \Sexpr{packageVersion("lime")}) by \citet{pedersen:2020}.
+All runs of LIME in this paper are executed in a forked version\footnote{https://github.com/goodekat/lime} of the R package \emph{lime} (version 0.5.1) by \citet{pedersen:2020}.
 The forked version is functionally indistinguishable from \citeauthor{pedersen:2020}'s implementation but allows us to export internal values relevant for an assessment of the explainer.
@@
 
-<<sine-data, echo = FALSE, include = FALSE>>=
-
-# Functions for rotating the data
-rot_x <- function(x, y, theta) (x * cos(theta)) - (y * sin(theta))
-rot_y <- function(x, y, theta) (x * sin(theta)) + (y * cos(theta))
-
-# Generate the data
-theta = -0.9
-min = -10
-max = 10
-set.seed(20190913)
-sine_data <- data.frame(x1 = runif(600, min, max),
-                        x2 = sort(runif(600, min, max))) %>%
-  mutate(x1new = rot_x(x1, x2, theta),
-         x2new = rot_y(x1, x2, theta),
-         y = ifelse(x2new > 5 * sin(x1new), "blue", "red")) %>%
-  slice(sample(1:n())) %>%
-  mutate(x3 = rnorm(600),
-         case = 1:600) %>%
-  select(case, everything())
-
-# Separate the data into training and testing parts
-set.seed(20191003)
-rs <- sample(1:600, 500, replace = FALSE)
-sine_data_train <- sine_data[rs,]
-sine_data_test <- sine_data[-rs,]
-
-# Fit a random forest
-set.seed(20191003)
-rfsine <- randomForest(x = sine_data_train %>% select(x1, x2, x3),
-                       y = factor(sine_data_train$y))
-
-# Obtain predictions on the training and testing data
-sine_data_train$rfpred <- predict(rfsine)
-sine_data_train <- cbind(sine_data_train, predict(rfsine, type = "prob"))
-sine_data_train <- sine_data_train %>% 
-  rename(rfprob_blue = blue, rfprob_red = red)
-sine_data_test$rfpred <- predict(rfsine, sine_data_test %>% select(x1, x2, x3))
-sine_data_test <- cbind(sine_data_test,
-                        predict(rfsine, sine_data_test
-                                %>% select(x1, x2, x3),
-                                type = "prob"))
-sine_data_test <- sine_data_test %>% 
-  rename(rfprob_blue = blue, rfprob_red = red)
-
-# Extract the prediction of interest from the sine test data
-sine_poi <- sine_data_test %>% filter(y != rfpred, x1 > 0, x1 < 5, x2 > 5)
-
-@
-
 \begin{figure*}[!thp]
 \centering
-<<figure-03, out.width = '6.5in', fig.width = 8, fig.height = 3.1>>=
-
-# Specify the figure size (for determining font size)
-f3_ow = 6.5
-f3_fw = 8
-f3_fs = fs * (f3_fw / f3_ow)
-f3_ls = 0.5 * (f3_fw / f3_ow)
-
-# Create points representing the rotated since curve
-sinefun_data <- data.frame(xnew = seq(min(sine_data$x1new),
-                                      max(sine_data$x1new),
-                                      by = 0.01)) %>%
-  mutate(ynew = 5 * sin(xnew)) %>%
-  mutate(x = rot_x(xnew, ynew, -theta),
-         y = rot_y(xnew, ynew, -theta)) %>%
-  filter(y >= -10, y <= 10)
-
-# Specify colors for predictions
-sinecolor_red = "firebrick"
-sinecolor_blue = "steelblue"
-
-# Plot the training data observed classes
-sine_plot_obs <- ggplot(sine_data_train, aes(x = x1, y = x2, color = y)) +
-  geom_point(alpha = 0.8) +
-  geom_path(data = sinefun_data, aes(x = x, y = y),
-            color = "black", 
-            size = f3_ls) +
-  scale_colour_manual(values = c(sinecolor_blue, sinecolor_red)) +
-  theme_bw(base_family = "Times", base_size = f3_fs) +
-  theme(aspect.ratio = 1, 
-        plot.title = element_text(size = f3_fs)) +
-  labs(x = TeX("$x_1$"),
-       y = TeX("$x_2$"),
-       color = TeX("y"),
-       title = "Training Data")
-
-# Plot the testing data rf predictions
-sine_plot_pred <- ggplot() +
-  geom_point(data = sine_poi %>%
-               mutate(shape = "Prediction \nof Interest"),
-             mapping = aes(x = x1,
-                           y = x2,
-                           shape = shape),
-             size = 5,
-             alpha = 0.8,
-             color = "black") +
-  geom_point(data = sine_data_test %>% filter(y != rfpred),
-             mapping = aes(x = x1, y = x2),
-             shape = 1,
-             size = 3,
-             color = "black") +
-  geom_point(data = sine_data_test,
-             mapping =  aes(x = x1,
-                            y = x2,
-                            color = rfprob_blue,
-                            fill = rfprob_blue),
-             shape = 21,
-             alpha = 0.8) +
-  geom_path(data = sinefun_data, aes(x = x, y = y),
-            color = "black", 
-            size = f3_ls) +
-  scale_color_gradient2(low = sinecolor_red,
-                        mid = '#f7f7f7',
-                        high = sinecolor_blue,
-                        midpoint = 0.5) +
-  scale_fill_gradient2(low = sinecolor_red,
-                        mid = '#f7f7f7',
-                        high = sinecolor_blue,
-                        midpoint = 0.5) +
-  scale_shape_manual(values = 23) +
-  theme_bw(base_family = "Times", base_size = f3_fs) +
-  theme(aspect.ratio = 1,
-        plot.title = element_text(size = f3_fs)) +
-  labs(x = TeX("$x_1$"),
-       y = TeX("$x_2$"),
-       color = "Random \nForest \nProbability \nfor 'blue'",
-       fill = "Random \nForest \nProbability \nfor 'blue'",
-       title = "Testing Data",
-       shape = "") +
-  guides(shape = guide_legend(order = 1))
-
-# Join the plots
-plot_grid(sine_plot_obs, sine_plot_pred,
-          nrow = 1,
-          rel_widths = c(0.4825, 0.5175))
-
-@
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+
+{\centering \includegraphics[width=6.5in]{figure/figure-03-1}
+
+}
+
+\end{knitrout}
 \caption{Plots of $x_2$ versus $x_1$ from the training (left) and testing (right) sets of the \data \ introduced in Section \ref{diagnostics}.
@@
 The color of the testing data  represents the random forest probability that an observation belongs to the category of blue.
-The \Sexpr{dim(sine_data_test %>% filter(y != rfpred))[1]} cases that are misclassified by the random forest are identified by black circles.
+The 18 cases that are misclassified by the random forest are identified by black circles.
 The prediction of interest to explain is indicated by a diamond.}
@@
 \end{figure*}
-
-<<sine-lime>>=
-
-# Apply LIME with various tuning parameters to the sine data
-if (!file.exists("../data/sine_lime_explain.rds")) {
-
-    # Apply lime with various input options
-    sine_lime_explain <- apply_lime(
-      train = sine_data_train %>% select(x1, x2, x3),
-      test = sine_data_test %>% select(x1, x2, x3),
-      model = rfsine,
-      label = "blue",
-      n_features = 2,
-      sim_method = c('quantile_bins', "kernel_density"),
-      nbins = 2:6,
-      feature_select = "auto",
-      dist_fun = "gower",
-      kernel_width = NULL,
-      gower_pow = 1,
-      return_perms = TRUE,
-      all_fs = TRUE,
-      seed = 20190914)
-
-    saveRDS(sine_lime_explain, "../data/sine_lime_explain.rds")
-
-  } else {
-
-    sine_lime_explain <- readRDS("../data/sine_lime_explain.rds")
-
-  }
-
-@
-
-<<sine-lime-default>>=
-
-# Extract the explanations from the default lime application
-sine_lime_default <- sine_lime_explain$explain %>% filter(nbins == 4)
-
-# Extract the explanations from the default lime application
-# for the prediction of interest only
-sine_poi_lime_default <- sine_lime_default %>%
-  filter(case == sine_poi %>% pull(case)) %>%
-  mutate(case = c("Prediction of Interest", "Prediction of Interest"))
-
-@
 
@@
 To demonstrate the visual diagnostics, we generate an example dataset that will be referred to as the \data.
-The \data \ contains \Sexpr{dim(sine_data)[1]} observations with three features and one response variable.
-The features, $x_1$, $x_2$, and $x_3$, are randomly sampled from Unif(\Sexpr{min}, \Sexpr{max}), Unif(\Sexpr{min}, \Sexpr{max}), and $\mbox{N}(0,1)$ distributions, respectively.
+The \data \ contains 600 observations with three features and one response variable.
+The features, $x_1$, $x_2$, and $x_3$, are randomly sampled from Unif(-10, 10), Unif(-10, 10), and $\mbox{N}(0,1)$ distributions, respectively.
 A binary response variable $y$ is  created using a rotated sine curve.
@@
 Note that due to the creation of $y$ in this manner, $y$ is dependent on $x_1$ and $x_2$ and independent of $x_3$.
-The dataset is divided into training and testing sets of \Sexpr{dim(sine_data_train)[1]} and \Sexpr{dim(sine_data_test)[1]} observations, respectively.
-A random forest  is fit using the R package \emph{randomForest} (version \Sexpr{packageVersion("randomForest")}) \citep{liaw:2002} with the default settings.
+The dataset is divided into training and testing sets of 500 and 100 observations, respectively.
+A random forest  is fit using the R package \emph{randomForest} (version 4.6.14) \citep{liaw:2002} with the default settings.
 The model is applied to the test set to obtain predictions.
@@
 The training data are colored by the observed response variable ($y$), and the testing data are colored by random forest  prediction probabilities.
-The random forest  misclassifies \Sexpr{dim(sine_data_test %>% filter(y != rfpred))[1]} points, which are all located near  the classification boundary.
+The random forest  misclassifies 18 points, which are all located near  the classification boundary.
 These are identified by open circles in \autoref{fig:figure-03}.
@@
 
-For the presentation of the explanation scatterplot, we focus on the misclassified point with $(x_1, x_2, x_3)$ coordinates of (\Sexpr{round(sine_poi$x1, 2)}, \Sexpr{round(sine_poi$x2, 2)}, \Sexpr{round(sine_poi$x3, 2)}) indicated by a diamond in \autoref{fig:figure-03}.
+For the presentation of the explanation scatterplot, we focus on the misclassified point with $(x_1, x_2, x_3)$ coordinates of (1.23, 8.47, -0.99) indicated by a diamond in \autoref{fig:figure-03}.
 Misclassified points are often of interest to explain since they may provide information about ways to improve the model.
@@
 
-<<warning = FALSE>>=
-
-# Obtain the simulated data associated with the poi
-sine_poi_perms <- sine_poi_lime_default %>%
-  slice(1) %>%
-  select(perms_raw, perms_pred_complex, perms_numerified, weights) %>%
-  mutate(perms_numerified =
-           map(perms_numerified,
-               .f = function(x) rename(x,
-                                       "x1num" = "x1",
-                                       "x2num" = "x2",
-                                       "x3num" = "x3"))) %>%
-  unnest(cols = c(perms_raw, perms_pred_complex, perms_numerified, weights)) %>%
-  select(-red) %>%
-  rename(rfpred = blue) %>%
-  mutate(case = factor(1:n())) %>%
-  select(case, everything())
-
-# Determine the bin cuts for the default lime application
-sine_lime_default_bin_cuts <- sine_lime_default %>%
-  select(feature, feature_desc) %>%
-  unique() %>%
-  separate(feature_desc, c("other", "bin_cut"), sep = " <= ") %>%
-  select(-other) %>%
-  na.omit() %>%
-  mutate(bin_cut = as.numeric(bin_cut)) %>%
-  arrange(feature) %>%
-  mutate(case = rep(1:3, 2)) %>%
-  spread(feature, bin_cut)
-
-@
-
-<<sine-poi-explainer, warning = FALSE>>=
-
-# Determine the lime explanation cutoffs
-sine_poi_bounds <- sine_poi_lime_default %>%
-  select(case, feature, feature_value, feature_desc) %>%
-  separate(feature_desc, c("other", "upper"), sep = " <= ") %>%
-  separate(other, c("lower", "feature2"), sep = " < ") %>%
-  mutate(upper = ifelse(is.na(upper), "Inf", upper)) %>%
-  select(-feature2) %>%
-  mutate_at(.vars = c("lower", "upper"), .funs = as.numeric)
-
-# Extract the coefficients from the explainer
-sine_b0 <- sine_poi_lime_default$model_intercept[1]
-sine_b1 <- sine_poi_lime_default$feature_weight[2]
-sine_b2 <- sine_poi_lime_default$feature_weight[1]
-
-# Extract the bounds of the bins
-x1_lower <- sine_poi_bounds %>% filter(feature == "x1") %>% pull(lower)
-x1_upper <- sine_poi_bounds %>% filter(feature == "x1") %>% pull(upper)
-x2_lower <- sine_poi_bounds %>% filter(feature == "x2") %>% pull(lower)
-x2_upper <- sine_poi_bounds %>% filter(feature == "x2") %>% pull(upper)
-
-# Function for computing the predicted value via the explainer model
-sine_explainer <- function(z1, z2) sine_b0 + sine_b1 * z1 + sine_b2 * z2
-
-@
-
 \begin{figure*}[!thp]
-<<figure-04, out.width = '6.5in', fig.width = 12, fig.height = 5, warning = FALSE>>=
-
-# Specify the figure size (for determining font size)
-f4_ow = 6.5
-f4_fw = 12
-f4_fs = fs * (f4_fw / f4_ow)
-f4_ls = 0.5 * (f4_fw / f4_ow)
-
-# Create the lime R package explanation visualization for the sine data
-sine_poi_exp <- 
-  sine_poi_lime_default %>% 
-  plot_features() + 
-  theme(text = element_text(family = "Times", size = f4_fs),
-        strip.text = element_text(size = f4_fs, face = "plain"))
-
-# Create the explanation scatterplot for the lime explanation for the sine data
-exp_scatter <-
-  plot_explain_scatter(
-    sine_poi_lime_default,
-    alpha = 0.4,
-    line_size = f4_ls
-  ) +
-  facet_grid(switch = "both") +
-  labs(
-    x = TeX("x_1"),
-    y = TeX("x_2"),
-    size = "Weight",
-    shape = "",
-    fill = "Random \nForest \nProbability \nfor 'blue'",
-    color = "Random \nForest \nProbability \nfor 'blue'",
-    linetype = "",
-    title = "Explanation Scatterplot"
-  ) +
-  theme_bw(base_family = "Times", base_size = f4_fs) +
-  guides(shape = guide_legend(order = 1),
-         size = guide_legend(
-           nrow = 2,
-           byrow = T,
-           override.aes = list(alpha = 1)
-         )) +
-  theme(aspect.ratio = 1,
-        plot.title = element_text(size = f4_fs))
-
-# Join the plots
-plot_grid(sine_poi_exp, exp_scatter)
-
-@
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+
+{\centering \includegraphics[width=6.5in]{figure/figure-04-1}
+
+}
+
+\end{knitrout}
 \caption{(left) Visualization from the \emph{lime} R package of a LIME explanation for the \data \ prediction of interest identified in \autoref{fig:figure-03}.
@@
 
-The plot reports \Sexpr{round(sine_poi_lime_default$label_prob[1], 2)} as  the random forest  probability  that the observation of interest belongs to category blue (denoted as the ``label" in the plot).
+The plot reports 0.74 as  the random forest  probability  that the observation of interest belongs to category blue (denoted as the ``label" in the plot).
 The lengths of the bars represent the  coefficients from a ridge regression model (the explainer model) fit using the R package \emph{glmnet} \citep{simon:2011} associated with the indicator variables chosen via feature selection.
@@
 In other words, this is the $R^2$ value associated with the explainer model.
-In this case, it is \Sexpr{round(sine_poi_lime_default$model_r2[1], 2)} suggesting that the explainer model is not a good linear fit.
+In this case, it is 0.21 suggesting that the explainer model is not a good linear fit.
 However, it is commonly accepted that $R^2$ has limitations for assessing the quality of fit of a model \citep{sapra:2014} and  should not be used as the only metric in a model assessment.
@@
 The explanation for the prediction of interest depicted in Figure \ref{fig:figure-04} is interpreted as follows.
-A random forest classification of blue is supported by the prediction of interest having a value of $x_2$ that is greater than \Sexpr{str_split(sine_poi_lime_default$feature_desc[[1]], pattern = " ")[[1]][1]}, but the prediction of interest having a value of $x_1$ that is greater than \Sexpr{str_split(sine_poi_lime_default$feature_desc[[2]], pattern = " ")[[1]][1]} and less than or equal to \Sexpr{str_split(sine_poi_lime_default$feature_desc[[2]], pattern = " ")[[1]][5]} provides support against a classification of blue.
+A random forest classification of blue is supported by the prediction of interest having a value of $x_2$ that is greater than 4.834, but the prediction of interest having a value of $x_1$ that is greater than -0.302 and less than or equal to 4.844 provides support against a classification of blue.
 Since the weight associated with $x_2$ has a larger magnitude than the weight associated with $x_1$, LIME explains that $x_2$ plays a more important role in the random forest prediction.
-Additionally, consider that since the support for blue by $x_2$ outweighs the support for red by $x_1$, the explainer model overall favors a label of blue for the prediction of interest, which agrees with the random forest probability of \Sexpr{sine_poi_lime_default$label_prob[1]} for blue.
+Additionally, consider that since the support for blue by $x_2$ outweighs the support for red by $x_1$, the explainer model overall favors a label of blue for the prediction of interest, which agrees with the random forest probability of 0.744 for blue.
 Note that both models classify the observation incorrectly.
@@
 \begin{figure}[!thp]
-<<figure-05, out.width = '3.125in', fig.width = 6, fig.height = 3>>=
-
-# Specify the figure size (for determining font size)
-f5_ow = 3.125
-f5_fw = 6
-f5_fs = fs * (f5_fw / f5_ow)
-
-# Specify the number of cases and LIME input options
-ncases = 10
-ninputs = 5
-
-# Create a good case of chosen feature example data
-set.seed(20191008)
-heatmap_data_good <-
-  tibble(
-    case = factor(rep(1:ncases, each = ninputs),
-                  levels = ncases:1),
-    input = factor(rep(1:ninputs, ncases)),
-    feature = factor(c(
-      rep(1, 5),
-      rep(2, 5),
-      rep(3, 5),
-      rep(1, 5),
-      rep(1, 5),
-      rep(4, 5),
-      rep(1, 5),
-      rep(3, 5),
-      rep(1, 5),
-      rep(4, 5)
-    ))
-  ) %>%
-  mutate(input = forcats::fct_recode(
-    input,
-    "A" = "1",
-    "B" = "2",
-    "C" = "3",
-    "D" = "4",
-    "E" = "5"
-  ))
-
-# Create the conceptual good heatmap
-heatmap_plot_good <- ggplot(data = heatmap_data_good,
-                            mapping = aes(
-                              x = input,
-                              y = case,
-                              fill = feature,
-                              color = feature
-                            )) +
-  geom_tile() +
-  labs(
-    x = "Tuning Parameter Value",
-    y = "Case",
-    fill = "Feature",
-    color = "Feature",
-    title = "Situation 1",
-    subtitle = "Consistent Explanations"
-  ) +
-  theme_bw(base_family = "Times", base_size = f5_fs) +
-  scale_fill_grey() +
-  scale_color_grey() +
-  theme(legend.position = "none", 
-        plot.title = element_text(size = f5_fs))
-
-# Create a bad case of chosen feature example data
-set.seed(20190627)
-heatmap_data_bad <- tibble(
-  case = factor(rep(1:ncases, ninputs),
-                levels = ncases:1),
-  input = factor(rep(1:ninputs, each = ncases)),
-  feature = factor(rep(c(1, 2, 4, 3, 2), each = 10))
-) %>%
-  mutate(input = forcats::fct_recode(
-    input,
-    "A" = "1",
-    "B" = "2",
-    "C" = "3",
-    "D" = "4",
-    "E" = "5"
-  ))
-
-# Create the conceptual bad heatmap
-heatmap_plot_bad <- ggplot(data = heatmap_data_bad,
-                           mapping = aes(
-                             x = input,
-                             y = case,
-                             fill = feature,
-                             color = feature
-                           )) +
-  geom_tile() +
-  labs(
-    x = "Tuning Parameter Value",
-    y = "Case",
-    fill = "Feature",
-    color = "Feature",
-    title = "Situation 2",
-    subtitle = "Inconsistent Explanations"
-  ) +
-  theme_bw(base_family = "Times", base_size = f5_fs) +
-  theme(plot.title = element_text(size = f5_fs)) +
-  scale_fill_grey() +
-  scale_color_grey()
-
-heatmap_leg <- get_legend(heatmap_plot_bad)
-heatmap_plot_bad <-
-  heatmap_plot_bad + theme(legend.position = 'none')
-
-# Join the plots
-plot_grid(
-  heatmap_plot_good,
-  heatmap_plot_bad,
-  heatmap_leg,
-  nrow = 1,
-  rel_widths = c(0.45, 0.45, 0.1)
-)
-
-@
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+
+{\centering \includegraphics[width=3.125in]{figure/figure-05-1}
+
+}
+
+\end{knitrout}
 \caption{Hypothetical examples of feature heatmaps in two possible situations.
@@
 
-<<figure-06, out.width = '3.125in', fig.width = 4, fig.height = 4.5>>=
-
-# Specify the figure size (for determining font size)
-f6_ow = 3.125
-f6_fw = 4
-f6_fs = fs * (f6_fw / f6_ow)
-
-# Create the example feature heatmap with the sine data
-plot_feature_heatmap(sine_lime_explain$explain,
-                     order_method = "PCA") +
-  theme_bw(base_family = "Times", base_size = f6_fs) +
-  theme(
-    legend.position = "bottom",
-    axis.text.y = element_blank(),
-    axis.ticks.y = element_blank(),
-    strip.background = element_rect(color = "white", fill = "white")
-  ) +
-  labs(y = "Case")
-
-@
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+
+{\centering \includegraphics[width=3.125in]{figure/figure-06-1}
+
+}
+
+\end{knitrout}
 \caption{\emph{Feature Heatmap}.
@@
 \begin{figure}[!thp]
-<<figure-07, out.width = '3.25in', fig.width = 4.5, fig.height = 3.75, warning = FALSE>>=
-
-# Specify the figure size (for determining font size)
-f7_ow = 3.25
-f7_fw = 4.5
-f7_fs = fs * (f7_fw / f7_ow)
-
-# Create the metric plot
-plot_metrics(sine_lime_explain$explain, rank_legend = "discrete") +
-  theme_bw(base_family = "Times", base_size = f7_fs) +
-  theme(
-    strip.background = element_rect(color = "white", fill = "white"),
-    strip.placement = "outside",
-    strip.text.y = element_text(size = f7_fs)
-  )
-
-@
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+
+{\centering \includegraphics[width=3.25in]{figure/figure-07-1}
+
+}
+
+\end{knitrout}
 \caption{\emph{Assessment metric plot}.
@@
 
-<<bullet-data>>=
-
-# Load the hamby data
-bullet_train <- read.csv("../data/hamby173and252_train.csv")
-bullet_test <- read.csv("../data/hamby224_test.csv")
-
-# Extract the features and order them based on feature importance
-bullet_features <- rownames(bulletxtrctr::rtrees$importance)
-bullet_features_ordered <-
-  data.frame(
-    feature = rownames(bulletxtrctr::rtrees$importance),
-    MeanDecreaseGini = bulletxtrctr::rtrees$importance
-  ) %>%
-  arrange(desc(MeanDecreaseGini)) %>%
-  mutate(
-    feature = fct_recode(
-      feature,
-      "CCF" = "ccf",
-      "CMS" = "cms",
-      "Matches" = "matches",
-      "Mismatches" = "mismatches",
-      "Non-CMS" = "non_cms",
-      "Rough Correlation" = "rough_cor",
-      "Distance Std Dev" = "sd_D",
-      "Distance" = "D",
-      "Sum Peaks" = "sum_peaks"
-    )
-  )
-
-# Create an ordered version of the data
-bullet_features_ordered <- bullet_features_ordered %>%
-  mutate(feature = factor(feature, levels = bullet_features_ordered$feature))
-
-@
-
 In current practice, forensic firearm examiners evaluate whether two bullets are from the same source (fired from the same gun) or from different sources based on microscopic comparison of the striation patterns engraved on bullets during the firing process (see \autoref{fig:figure-08}).
@@
 Nine features quantifying the similarity of signatures, such as the cross-correlation function, the distance between signatures, and the number of matching striae, are extracted and used to train a random forest (available in the \emph{bulletxtrctr} R package) to determine the probability of a comparison resulting from the same source (matching signatures) or from different sources (non-matching signatures).
-The model was trained on a set of scans of bullets from the James Hamby Consecutively Rifled Ruger Barrel Study \citep{hamby:2009}, which includes \Sexpr{dim(bullet_train)[1]} land-to-land comparisons.
-
-<<converting-static-figs-to-eps>>=
-
-# Convert the bullet figure to eps (if needed)
-if (!file.exists("./figure-static/figure-08.eps")) {
-  bullets <- image_read("./figure-static/figure-08.png")
-  image_write(bullets, path = "./figure-static/figure-08.eps", format = "eps")
-}
-
-# Convert the signature figure to eps (if needed)
-if (!file.exists("./figure-static/figure-09.eps")) {
-  signatures <- image_read("./figure-static/figure-09.png")
-  image_write(signatures, path = "./figure-static/figure-09.eps", format = "eps")
-}
-
-@
+The model was trained on a set of scans of bullets from the James Hamby Consecutively Rifled Ruger Barrel Study \citep{hamby:2009}, which includes 83028 land-to-land comparisons.
 
@@
 \centering
-\includegraphics[width=2.25in]{./figure-static/figure-08.eps}
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+
+{\centering \includegraphics[width=2.25in]{./figure-static/figure-08-1}
+
+}
+
+\end{knitrout}
 \caption{(Top left) Traditionally rifled gun barrel.
@@
 
-\includegraphics[width=2.25in]{./figure-static/figure-09.eps}
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+
+{\centering \includegraphics[width=3.125in]{figure/figure-09-1}
+
+}
+
+\end{knitrout}
 \caption{Example bullet signatures.
@@
 \begin{figure*}[!thp]
-<<figure-10, out.width = '6.5in', warning = FALSE>>=
-
-# Create (or load) the parallel coordinate plot
-if (file.exists("./figure-static/figure-10.eps")) {
-
-  # Load and print the plot
-  knitr::include_graphics("./figure-static/figure-10.eps")
-
-} else {
-
-  # Specify the figure size (for determining font size)
-  f10_ow = 6.5
-  f10_fw = 7.5
-  f10_fs = 7 * (f10_fw / f10_ow)
-  f10_ls = 0.5 * (f10_fw / f10_ow)
-
-  # Create the plot
-  bullet_pcp <- bullet_train %>%
-    select(all_of(bullet_features), samesource, rfscore) %>%
-    bind_rows(bullet_test %>%
-                select(all_of(bullet_features), samesource, rfscore),
-              .id = "set") %>%
-    mutate(
-      set = fct_recode(set,
-                       "Training Set" = "1",
-                       "Testing Set" = "2"),
-      samesource = fct_recode(
-        factor(samesource),
-        "Match" = "TRUE",
-        "Non-Match" = "FALSE"
-      )
-    ) %>%
-    rename(
-      "CCF" = "ccf",
-      "CMS" = "cms",
-      "Matches" = "matches",
-      "Mismatches" = "mismatches",
-      "Non-CMS" = "non_cms",
-      "Rough Correlation" = "rough_cor",
-      "Distance Std Dev" = "sd_D",
-      "Distance" = "D",
-      "Sum Peaks" = "sum_peaks"
-    ) %>%
-    na.omit() %>%
-    ggplot(aes(color = rfscore)) +
-    geom_pcp(
-      mapping = aes(vars = vars(bullet_features_ordered$feature)),
-      alpha = 0.2,
-      size = f10_ls
-    ) +
-    facet_grid(set ~ samesource) +
-    scale_color_gradient2(low = "grey50",
-                          high = "darkorange",
-                          midpoint = 0.5) +
-    theme_bw(base_family = "Times", base_size = f10_fs) +
-    theme(
-      axis.text.x = element_text(angle = 45, hjust = 1),
-      strip.placement = "outside",
-      strip.background = element_rect(color = "white",
-                                      fill = "white")
-    ) +
-    labs(x = "Features Ordered by Random Forest Variable Importance \n(highest to lowest from left to right)",
-         y = "Scaled Feature Values",
-         color = "Random \nForest \nProbability")
-
-  # Save the plot
-  ggplot2::ggsave(
-    plot = bullet_pcp,
-    filename = "./figure-static/figure-10.png",
-    width = 7.5,
-    height = 3.5,
-    units = "in",
-    dpi = 1200
-  )
-
-  # Load the figure and then save as an eps file
-  bullet_pcp <- image_read("./figure-static/figure-10.png")
-  image_write(bullet_pcp, path = "./figure-static/figure-10.eps", format = "eps")
-
-}
-
-@
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+
+{\centering \includegraphics[width=6.5in]{./figure-static/figure-10-1}
+
+}
+
+\end{knitrout}
 \caption{Parallel coordinate plots of the \citet{hare:2016} random forest predictions from the training (top facet) and testing (bottom facet) data.
@@
 
-We apply the trained random forest model from \citet{hare:2016} to another set of bullets from the Hamby study with \Sexpr{dim(bullet_test)[1]} rows of land comparisons.
+We apply the trained random forest model from \citet{hare:2016} to another set of bullets from the Hamby study with 432 rows of land comparisons.
 We first consider a global visualization of the relationship between the random forest predictions and the model features with a parallel coordinate plot of the training data (top facet) and testing data (bottom facets) predictions (\autoref{fig:figure-10}).
@@
 We specify that each LIME explanation return 3 features and feature selection is performed by selecting the features with the highest weights in a ridge regression model (default option).
-
-<<bullet-lime>>=
-
-# Apply LIME to all but two cases without returning the permutations
-if (file.exists("../data/hamby_lime.rds")){
-
-  # Load the files
-  bullet_explain_noperms <- readRDS("../data/hamby_explain.rds")
-
-} else {
-
-  # Apply lime with various input options to the hamby data
-  bullet_lime_explain_noperms <- apply_lime(
-    train = bullet_train %>% select(all_of(bullet_features)),
-    test = bullet_test %>%
-      select(all_of(bullet_features)) %>%
-      na.omit(),
-    model = bulletxtrctr::rtrees,
-    label = as.character(TRUE),
-    n_features = 3,
-    sim_method = c('quantile_bins', 'equal_bins',
-                   'kernel_density', 'normal_approx'),
-    nbins = 2:6,
-    feature_select = "auto",
-    dist_fun = "gower",
-    kernel_width = NULL,
-    gower_pow = c(0.5, 1, 10),
-    return_perms = FALSE,
-    all_fs = FALSE,
-    seed = 20190914)
-
-  # Separate the lime and explain parts of the results
-  bullet_lime_noperms <- bullet_lime_explain_noperms$lime
-  bullet_explain_noperms <- bullet_lime_explain_noperms$explain
-
-  # Save the output objects
-  saveRDS(object = bullet_lime_noperms,
-          file = "../data/hamby_lime.rds")
-  saveRDS(object = bullet_explain_noperms,
-          file = "../data/hamby_explain.rds")
-
-}
-
-@
-
-<<bullet-lime-perms>>=
-
-# Specify two cases of interest
-bullet_poi_match <- unique(bullet_explain_noperms$case)[c(325)]
-bullet_poi_nonmatch <- unique(bullet_explain_noperms$case)[c(20)]
-
-# Apply LIME to two cases with the permutations returned
-bullet_lime_explain_perms <- apply_lime(
-  train = bullet_train %>% select(all_of(bullet_features)),
-  test = bullet_test %>%
-    filter(case %in% bullet_poi_match) %>%
-    bind_rows(bullet_test %>%
-                filter(case %in% bullet_poi_nonmatch)) %>%
-    select(all_of(bullet_features)),
-  model = bulletxtrctr::rtrees,
-  label = as.character(TRUE),
-  n_features = 3,
-  sim_method = c(
-    'quantile_bins',
-    'equal_bins',
-    'kernel_density',
-    'normal_approx'
-  ),
-  nbins = 3,
-  feature_select = "auto",
-  dist_fun = "gower",
-  kernel_width = NULL,
-  gower_pow = 0.5,
-  return_perms = TRUE,
-  all_fs = FALSE,
-  seed = 20190914
-)
-
-# Separate the lime and explain parts of the results
-bullet_lime_perms <- bullet_lime_explain_perms$lime
-bullet_explain_perms <- bullet_lime_explain_perms$explain %>%
-  mutate(case = ifelse(case == 1,
-                       bullet_poi_match,
-                       bullet_poi_nonmatch))
-
-@
-
-<<bullet-lime-combined>>=
-
-# Determine the application and case number of the poi
-# in the no_perms data
-poi_cases_no_perms <- bullet_explain_noperms %>%
-  filter(case %in% c(bullet_poi_match, bullet_poi_nonmatch),
-         nbins %in% c(3, NA),
-         gower_pow == 0.5) %>%
-  select(case, implementation) %>%
-  unique()
-
-# Join the no perms data (with poi removed) with the
-# perms data (perms removed)
-bullet_explain <- bullet_explain_noperms %>%
-  anti_join(poi_cases_no_perms,
-            by = c("implementation", "case")) %>%
-  bind_rows(
-    bullet_explain_perms %>%
-      mutate(
-        implementation = fct_recode(
-          implementation,
-          "2" = "1",
-          "7" = "2",
-          "31" = "3",
-          "32" = "4"
-        )
-      ) %>%
-      select(
-        -perms_raw,
-        -perms_numerified,-perms_pred_simple,
-        -perms_pred_complex,-weights
-      )
-  )
-
-@
 
@@
 \begin{figure*}[!thp]
-<<figure-11, out.width = '6.5in', fig.width = 18, fig.height = 14>>=
-
-# Specify the figure size (for determining font size)
-f11_ow = 6.5
-f11_fw = 18
-f11_fs = fs * (f11_fw / f11_ow)
-
-# Create a feature heatmap
-plot_feature_heatmap(
-  bullet_explain %>%
-    mutate(
-      label = as.factor(label),
-      feature = fct_recode(
-        feature,
-        "Rough Correlation" = "rough_cor",
-        "Consecutively Matching Striae" = "cms",
-        "Distance" = "D",
-        "Matches" = "matches",
-        "Mismatches" = "mismatches",
-        "Non-Consecutively Matching Striae" = "non_cms",
-        "Cross Correlation Function" = "ccf",
-        "Sum of Peaks" = "sum_peaks",
-        "Distance Standard Deviation" = "sd_D"
-      )
-    ),
-  facet_var = bullet_test %>%
-    mutate(samesource = fct_recode(
-      factor(samesource),
-      "Match" = "TRUE",
-      "Non-Match" = "FALSE"
-    )) %>%
-    pull(samesource) %>%
-    na.omit(),
-  order_method = "PCA"
-) +
-  scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) +
-  scale_color_gretchenalbrecht(palette = "last_rays",
-                               discrete = TRUE,
-                               reverse = TRUE) +
-  theme_bw(base_family = "Times", base_size = f11_fs) +
-  theme(
-    axis.text.y = element_blank(),
-    axis.ticks.y = element_blank(),
-    strip.background = element_rect(color = "white", fill = "white"),
-    strip.text.y.right = element_text(angle = 0),
-    legend.position = "bottom",
-    axis.text.x = element_text(angle = 45, hjust = 1)
-  ) +
-  guides(fill = guide_legend(nrow = 3)) +
-  labs(y = "Case", color = "Complex Model Feature", fill = "Complex Model Feature")
-
-@
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+
+{\centering \includegraphics[width=6.5in]{figure/figure-11-1}
+
+}
+
+\end{knitrout}
 \caption{Feature heatmap of  36 LIME applications to the bullet comparison data test set.
@@
 
-<<figure-12, out.width = '6.5in', warning = FALSE, fig.width = 10, fig.height = 4>>=
-
-# Specify the figure size (for determining font size)
-f12_ow = 6.5
-f12_fw = 10
-f12_fs = fs * (f12_fw / f12_ow)
-f12_ls = 0.5 * (f12_fw / f12_ow)
-
-# Create a metric comparison plot
-plot_metrics(
-  bullet_explain %>%
-    mutate(label = as.factor(label)),
-  add_lines = TRUE,
-  line_alpha = 0.75,
-  line_size = f12_ls
-) +
-  theme_bw(base_family = "Times", base_size = f12_fs) +
-  theme(
-    strip.background = element_rect(color = "white", fill = "white"),
-    strip.placement = "outside",
-    strip.text.y = element_text(size = f12_fs)
-  )
-
-@
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+
+{\centering \includegraphics[width=6.5in]{figure/figure-12-1}
+
+}
+
+\end{knitrout}
 \caption{Assessment metric plot for the applications of LIME on the bullet comparison data test set.
@@
 \begin{figure*}[!thp]
-<<figure-13, out.width = '6.25in', fig.width = 13, fig.height = 17, message = FALSE>>=
-
-# Specify the figure size (for determining font size)
-f13_ow = 6.25
-f13_fw = 13
-f13_fs = fs * (f13_fw / f13_ow)
-f13_ls = 0.5 * (f13_fw / f13_ow)
-
-# Adjust names of the cases
-bullet_explain_perms <- bullet_explain_perms %>%
-  mutate(case = ifelse(case == bullet_poi_nonmatch, "NM", "M"))
-
-# Create the explanation scatterplot: case M, 3 quantile bins
-eoiM_3qb <-
-  plot_explain_scatter(
-    bullet_explain_perms[1:3,],
-    alpha = 0.9,
-    weights = TRUE,
-    line_size = f13_ls
-  ) +
-  scale_color_gradient2(
-    low = "grey50",
-    high = "darkorange",
-    midpoint = 0.5,
-    limits = c(0, 1)
-  ) +
-  scale_fill_gradient2(
-    low = "grey50",
-    high = "darkorange",
-    midpoint = 0.5,
-    limits = c(0, 1)
-  ) +
-  theme_bw(base_family = "Times", base_size = f13_fs) +
-  theme(
-    aspect.ratio = 1,
-    plot.title = element_text(size = f13_fs),
-    strip.text.x = element_text(size = f13_fs),
-    strip.text.y = element_text(size = f13_fs),
-    strip.placement = "outside",
-    strip.background = element_rect(color = "white", fill = "white")
-  ) +
-  guides(linetype = guide_legend(override.aes = list(color = c("darkorange"))),
-         size = guide_legend(nrow = 2, byrow = T))
-
-# Create the explanation scatterplot: case MM, 3 quantile bins
-eoiNM_3qb <-
-  plot_explain_scatter(
-    bullet_explain_perms[4:6, ],
-    alpha = 0.9,
-    weights = TRUE,
-    line_size = f13_ls
-  ) +
-  scale_color_gradient2(
-    low = "grey50",
-    high = "darkorange",
-    midpoint = 0.5,
-    limits = c(0, 1)
-  ) +
-  scale_fill_gradient2(
-    low = "grey50",
-    high = "darkorange",
-    midpoint = 0.5,
-    limits = c(0, 1)
-  ) +
-  theme_bw(base_family = "Times", base_size = f13_fs) +
-  theme(
-    aspect.ratio = 1,
-    plot.title = element_text(size = f13_fs),
-    strip.placement = "outside",
-    strip.background = element_rect(color = "white", fill = "white"),
-    strip.text.x = element_text(size = f13_fs),
-    strip.text.y = element_text(size = f13_fs)
-  ) +
-  guides(linetype = guide_legend(override.aes = list(color = c(
-    "grey50", "darkorange"
-  ))),
-  size = guide_legend(nrow = 2, byrow = T))
-
-# Create the explanation scatterplot: case M, 3 equal bins
-eoiM_3eb <-
-  plot_explain_scatter(
-    bullet_explain_perms[7:9,],
-    alpha = 0.9,
-    weights = TRUE,
-    line_size = f13_ls
-  ) +
-  scale_color_gradient2(
-    low = "grey50",
-    high = "darkorange",
-    midpoint = 0.5,
-    limits = c(0, 1)
-  ) +
-  scale_fill_gradient2(
-    low = "grey50",
-    high = "darkorange",
-    midpoint = 0.5,
-    limits = c(0, 1)
-  ) +
-  theme_bw(base_family = "Times", base_size = f13_fs) +
-  theme(
-    aspect.ratio = 1,
-    plot.title = element_text(size = f13_fs),
-    strip.placement = "outside",
-    strip.background = element_rect(color = "white", fill = "white"),
-    strip.text.x = element_text(size = f13_fs),
-    strip.text.y = element_text(size = f13_fs)
-  ) +
-  guides(linetype = guide_legend(override.aes = list(color = c(
-    "grey50", "darkorange"
-  ))),
-  size = guide_legend(nrow = 2, byrow = T))
-
-# Create the explanation scatterplot: case NM, 3 equal bins
-eoiNM_3eb <-
-  plot_explain_scatter(
-    bullet_explain_perms[10:12,],
-    alpha = 0.9,
-    weights = TRUE,
-    line_size = f13_ls
-  ) +
-  scale_color_gradient2(
-    low = "grey50",
-    high = "darkorange",
-    midpoint = 0.5,
-    limits = c(0, 1)
-  ) +
-  scale_fill_gradient2(
-    low = "grey50",
-    high = "darkorange",
-    midpoint = 0.5,
-    limits = c(0, 1)
-  ) +
-  theme_bw(base_family = "Times", base_size = f13_fs) +
-  theme(
-    aspect.ratio = 1,
-    plot.title = element_text(size = f13_fs),
-    strip.placement = "outside",
-    strip.background = element_rect(color = "white", fill = "white"),
-    strip.text.x = element_text(size = f13_fs),
-    strip.text.y = element_text(size = f13_fs)
-  ) +
-  guides(linetype = guide_legend(override.aes = list(color = c(
-    "grey50", "darkorange"
-  ))),
-  size = guide_legend(nrow = 2, byrow = T))
-
-# Create the lime explanation visualization: case M, 3 quantile bins
-pfM_3qb <- plot_features(bullet_explain_perms[1:3,]) +
-  scale_fill_manual(values = c("darkorange", "grey50")) +
-  theme(text = element_text(family = "Times", size = f13_fs),
-        strip.text.x = element_text(face = "plain", size = f13_fs))
-
-# Create the lime explanation visualization: case NM, 3 quantile bins
-pfNM_3qb <- plot_features(bullet_explain_perms[4:6,]) +
-  scale_fill_manual(values = c("darkorange", "grey50")) + 
-  theme(text = element_text(family = "Times", size = f13_fs),
-        strip.text.x = element_text(face = "plain", size = f13_fs))
-
-# Create the lime explanation visualization: case M, 3 equal bins
-pfM_3eb <- plot_features(bullet_explain_perms[7:9,]) +
-  scale_fill_manual(values = c("darkorange", "grey50")) +
-  theme(text = element_text(family = "Times", size = f13_fs),
-        strip.text.x = element_text(face = "plain", size = f13_fs))
-
-# Create the lime explanation visualization: case NM, 3 equal bins
-pfNM_3eb <- plot_features(bullet_explain_perms[10:12,]) +
-  scale_fill_manual(values = c("darkorange", "grey50")) +
-  theme(text = element_text(family = "Times", size = f13_fs),
-        strip.text.x = element_text(face = "plain", size = f13_fs))
-
-# Join the plots
-plot_grid(
-  pfNM_3qb,
-  pfNM_3eb,
-  eoiNM_3qb,
-  eoiNM_3eb,
-  pfM_3qb,
-  pfM_3eb,
-  eoiM_3qb,
-  eoiM_3eb,
-  nrow = 4,
-  rel_heights = c(0.2, 0.3, 0.2, 0.3)
-)
-
-@
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+
+{\centering \includegraphics[width=6.25in]{figure/figure-13-1}
+
+}
+
+\end{knitrout}
 \caption{Plots of LIME explanations (first and third rows) and explanation scatterplots (second and fourth rows) for  cases M and NM in the bullet test data for two tuning parameter values: 3 quantile bins (first column) and 3 equal bins (second column).
@@
 \begin{figure*}[!thp]
-<<figure-B1, out.width = '6.5in', fig.width = 12, fig.height = 5, fig.align = "center">>=
-
-# Specify the figure size (for determining font size and line size)
-fb1_ow = 6.5
-fb1_fw = 12
-fb1_fs = fs * (fb1_fw / fb1_ow)
-fb1_ls = 0.5 * (fb1_fw / fb1_ow)
-
-# Create the explanation scatterplot
-plot_explain_scatter(
-  sine_lime_explain$explain %>%
-    filter(sim_method == "kernel_density", case == sine_poi %>% pull(case)),
-  alpha = 0.75,
-  title.opt = FALSE, 
-  line_size = fb1_ls 
-) +
-  theme_bw(base_family = "Times", base_size = fb1_fs) +
-  theme(
-    strip.background = element_rect(fill = "white", color = "white"),
-    strip.placement = "outside",
-    strip.text.x = element_text(size = fb1_fs)
-  )
-
-@
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+
+{\centering \includegraphics[width=6.5in]{figure/figure-B1-1}
+
+}
+
+\end{knitrout}
 \caption{Explanation scatterplots for the \data \ prediction of interest with the kernel density simulation method.}
@@
 \begin{figure*}[!thp]
-<<figure-B2, out.width = '6.5in', fig.width = 12, fig.height = 10, fig.align = "center">>=
-
-# Specify the figure size (for determining font size and line size)
-fb2_ow = 6.5
-fb2_fw = 12
-fb2_fs = fs * (fb2_fw / fb2_ow)
-fb2_ls = 0.5 * (fb2_fw / fb2_ow)
-
-# Create the explanation scatterplot: case M, kernel density
-bullet_es_M <-
-  plot_explain_scatter(
-    bullet_explain_perms[16:18,] %>% mutate(case = "NM"),
-    alpha = 0.75,
-    title.opt = TRUE, 
-    line_size = fb2_ls
-  ) +
-  theme_bw(base_family = "Times", base_size = fb2_fs) +
-  theme(
-    aspect.ratio = 1,
-    strip.background = element_rect(fill = "white", color = "white"),
-    strip.placement = "outside",
-    strip.text.x = element_text(size = fb2_fs),
-    plot.title = element_text(size = fb2_fs)
-  )
-
-# Create the explanation scatterplot: case NM, kernel density
-bullet_es_NM <-
-  plot_explain_scatter(
-    bullet_explain_perms[13:15, ] %>% mutate(case = "M"),
-    alpha = 0.75,
-    title.opt = TRUE, 
-    line_size = fb2_ls
-  ) +
-  theme_bw(base_family = "Times", base_size = fb2_fs) +
-  theme(
-    aspect.ratio = 1,
-    strip.background = element_rect(fill = "white", color = "white"),
-    strip.placement = "outside",
-    strip.text.x = element_text(size = fb2_fs), 
-    plot.title = element_text(size = fb2_fs)
-  )
-
-# Join the plots
-plot_grid(bullet_es_NM, bullet_es_M, nrow = 2)
-
-@
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+
+{\centering \includegraphics[width=6.5in]{figure/figure-B2-1}
+
+}
+
+\end{knitrout}
 \caption{Explanation scatterplots for LIME explanations using kernel density simulation for the cases M and NM of the bullet comparison.}
@@
 \begin{figure}[!thp]
-<<figure-C3, out.width = '3.125in', fig.width = 5, fig.height = 4, warning = FALSE>>=
-
-# Specify the figure size (for determining font size and line size)
-fc3_ow = 3.125
-fc3_fw = 5
-fc3_fs = fs * (fc3_fw / fc3_ow)
-fc3_ls = 0.5 * (fc3_fw / fc3_ow)
-
-# Calculate the residuals from the explainer model
-y <- sine_poi_perms$rfpred
-sine_poi_explainer <-
-  function(x1, x2)
-    sine_b0 + (sine_b1 * x1) + (sine_b2 * x2)
-sine_poi_perms <- sine_poi_perms %>%
-  mutate(exppred = sine_poi_explainer(x1num, x2num)) %>%
-  mutate(resid = exppred - rfpred)
-
-# Create the residual plot
-ggplot(sine_poi_perms, aes(x = exppred, y = resid)) +
-  geom_hline(yintercept = 0, size = fc3_ls) +
-  geom_jitter(alpha = 0.5, width = 0.02) +
-  theme_bw(base_family = "Times", base_size = fc3_fs) +
-  theme(plot.title = element_text(size = fc3_fs)) +
-  labs(x = "Explainer Model Predictions",
-       y = "Explainer Model Residuals",
-       title = "Explainer Model Residual Plot")
-
-@
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+
+{\centering \includegraphics[width=3.125in]{figure/figure-C3-1}
+
+}
+
+\end{knitrout}
 \caption{Residual plot of the explainer model associated with \data \ prediction of interest from Section \ref{exp-scatter}.

### 2020-09-04 old-version/paper.Rnw
added the old (long) version of the paper

\documentclass[AMS,STIX2COL]{WileyNJD-v2}

% Packages
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{natbib}
\usepackage{subcaption}
\usepackage{xcolor}

% Commands
\definecolor{orange}{rgb}{0.94, 0.59, 0.19}
\definecolor{purple}{rgb}{0.5, 0.0, 0.5}
\definecolor{teal}{rgb}{0, 0.502, 0.502}
\newcommand{\hh}[1]{\textcolor{orange}{#1}}
\newcommand{\kgc}[1]{\textcolor{purple}{#1}}
\newcommand{\kge}[1]{\textcolor{teal}{#1}}
\newcommand{\data}{sine data}

% Set up for ASA data science journal
\articletype{Article Type}
\received{26 April 2016}
\revised{6 June 2016}
\accepted{6 June 2016}
\raggedbottom

\begin{document}

% Paper header (title and authors)
\title{Visual Diagnostics of a Model Explainer -- Tools for the Assessment of LIME Explanations}
\author[1]{Katherine Goode*}
\author[1,2]{Heike Hofmann}
\authormark{Goode and Hofmann}
\address[1]{\orgdiv{Department of Statistics}, \orgname{Iowa State University}, \orgaddress{\state{Iowa}, \country{United States}}}
\address[2]{\orgdiv{Center for Statistics and Applications in Forensic Evidence (CSAFE)}, \orgname{Iowa State University}, \orgaddress{\state{Iowa}, \country{United States}}}
\corres{*Corresponding author. \email{kgoode@iastate.edu}}
\presentaddress{This is sample for present address text this is sample for present address text}

% Abstract and keywords
\abstract[Summary]{The importance of providing explanations for predictions made by black-box models has led to the development of model explainer methods such as LIME (local interpretable model-agnostic explanations) \citep{ribeiro:2016}. LIME uses a surrogate model to explain the relationship between predictor variables from a black-box model and the black-box model predictions in a local region around a prediction of interest. However, the quality of the resulting explanations relies on how well the explainer model captures the black-box model in a specified local region. Here we introduce visual diagnostics to assess the quality of LIME explanations. We propose visualizations for individual explanations, sets of explanations, and comparisons LIME applications with different tuning parameters. We apply the visual diagnostics to a forensics bullet matching dataset to show examples where LIME explanations depend on the tuning parameters and the explainer model oversimplifies the black-box model. Our examples raise concerns about claims made about LIME \citep{ribeiro:2016} that are similar to other criticism found in the literature (\citet{alvarezmelis:2018}, \citet{laugel:2018}, and \citet{molnar:2019}).}
\keywords{LIME, black-box models, interpretability, diagnostics}

% Citation information
\jnlcitation{
\cname{\author{Goode K.}, \author{H. Hofmann}, }
\cyear{2019},
\ctitle{Visual Diagnostics of a Model Explainer -- Tools for the Assessment of LIME Explanations},
\cjournal{Stat Anal Data Min: The ASA Data Sci Journal},
\cvol{volume, number and page}.}

\maketitle

<<setup, echo = FALSE, include = FALSE>>=

# Specify global options
knitr::opts_chunk$set(echo = FALSE,
                      fig.keep = 'high',
                      message = FALSE)

# Load packages
library(caret)
library(cowplot)
library(dplyr)
library(forcats)
library(ggforce)
library(ggplot2)
library(ggpcp)
library(glmnet)
library(gower)
library(graphics)
library(gretchenalbrecht)
library(latex2exp)
library(lime) #devtools::install_github("goodekat/lime")
library(limeaid) #devtools::install_github("goodekat/limeaid")
library(purrr)
library(randomForest)
library(stringr)
library(tidyr)

@

\section{Introduction}

In the field of statistics, there are two main uses for models: inference and prediction. Machine learning models are often used for the latter purpose. While these models have proven to perform well in a wide range of prediction problems, their accuracy generally comes at the cost of interpretability. Most machine learning models are complex algorithms that are good at identifying patterns in the data but lack a simple functional form. The absence of a functional form makes a direct interpretation impractical, and as a result, these models become ``black-box models". Even models with a functional form become difficult to interpret beyond a certain complexity, such as e.g. three-way or higher interactions in logistic regression models.

Throughout this paper, we will make a distinction between interpretability and explanability of models. We define {\it interpretability} as the ability to directly use model parameters to understand the relationships in the data captured by the model: e.g., a linear model coefficient associated with a predictor variable indicates the amount the response variable changes based on a change in the predictor variable. In contrast, {\it explanability} is defined as the ability to use the model in an indirect manner to understand the relationships in the data captured by the model: e.g., partial dependence plots depict the marginal relationship between model predictions and predictor variables \citep{friedman:2001}.

Various methods have been proposed to provide explanations for black-box model predictions \citep{guidotti:2018, mohseni:2018, molnar:2019}. Some are specific to one type of model (e.g. \citep{bau:2017} and \citep{hara:2016}), and others are model-agnostic (e.g. \citep{greenwell:2018} and \citep{strumbelj:2014}). In this paper, we focus on the model-agnostic method of LIME (local interpretable model-agnostic explanations) \citep{ribeiro:2016}.

\subsection{The Importance of Explanability}

The ability to explain a model serves multiple purposes. When a model is fit, explanations help to diagnose the model by checking for relationships between the response and predictor variables. Depending on the training set, some models might pick up on spurious features in the data that are unrelated to the model outcome such as an example described by \citet{ribeiro:2016} where the distinction between huskies and wolves is based on whether there is snow in the background rather than features of the animals.

After a model has been diagnosed, the explanations for the predictions are used to understand the underlying mechanism that produced the data and provide an argument for why the predictions should be trusted. In some areas of application, the ability to be able to explain the results from a model is critical.

The forensics sciences and the heath care industry are two areas that have benefited from machine learning but have an obvious need for explainable predictions. For example, \citet{hare:2016} discuss the use of a random forest model in the forensics sciences to determine whether two bullets were fired from the same gun. \citet{yu:2018} describe how healthcare has advanced through the use of machine learning in ways such as using neural networks to automate medical image diagnoses and implementing Bayesian networks to predict clinical outcomes. In both of these fields, the decisions made based on the results of the machine learning models can greatly impact people's lives. If it is not possible to explain the output from a model, it becomes questionable whether to rely on the predictions to make important decisions.

The European Union has taken the desire to provide explanations for machine learning model predictions a step further. In May 2018, the General Data Protection Regulation (GDPR) went into effect \footnote{https://eugdpr.org/the-regulation/gdpr-faqs/}. The regulation includes a policy that gives the right for individuals affected by decisions made via automated algorithms to understand the logic behind the decisions being made. As \citet{goodman:2016} point out, this regulation has a great effect on the way that machine learning algorithms are used to make decisions. The wording of the policy leaves room for interpretation, but  \citet{goodman:2016} state, ``It is reasonable to suppose that any adequate explanation would, at a minimum, provide an account of how input features relate to predictions, allowing one to answer questions such as: Is the model more or less likely to recommend a loan if the applicant is a minority?"

<<concept-data>>=
# Simulate example data
set.seed(20190624)
lime_data <-
  data.frame(
    feature1 = sort(runif(250, 0, 1)),
    feature2 = sample(x = 1:250, size = 250, replace = FALSE)) %>%
  mutate(
    feature1_stnd = (feature1 - mean(feature1)) / sd(feature1),
    feature2_stnd = (feature2 - mean(feature2)) / sd(feature2),
    prediction = if_else(feature1 >= 0 & feature1 < 0.1,
                         (0.3 * feature1) + rnorm(n(), 0, 0.01),
                 if_else(feature1 >= 0.1 & feature1 < 0.3,
                         rbeta(n(), 1, 0.5),
                 if_else(feature1 >= 0.3 & feature1 < 0.5,
                         sin(pi* feature1) + rnorm(n(), 0, 0.5),
                 if_else(feature1 >= 0.5 & feature1 < 0.8,
                         -(sin(pi* feature1) + rnorm(n(), 0, 0.1)) + 1,
                 if_else(feature1 >= 0.8 & feature1 < 0.9,
                         0.5 + runif(n(), -0.5, 0.5),
                         0.5 + rnorm(n(), 0, 0.3))))))) %>%
  bind_rows(
    data.frame(feature1 = rep(1, 30) + rnorm(5, 0, 0.05),
           feature2 = rep(245, 30) + rnorm(5, 0, 1),
           prediction = rep(0, 30) + rnorm(5, 0, 0.05)) %>%
  mutate(feature1_stnd = (feature1 - mean(feature1)) / sd(feature1),
         feature2_stnd = (feature2 - mean(feature2)) / sd(feature2)))

# Specify a prediction of interest
prediction_of_interest <-
  data.frame(feature1 = 0.07, feature2 = 200) %>%
  mutate(feature1_stnd = (feature1 - mean(lime_data$feature1)) /
           sd(lime_data$feature1),
         feature2_stnd = (feature2 - mean(lime_data$feature2)) /
           sd(lime_data$feature2),
         prediction = 0.05,
         color = factor("Prediction \nof Interest"))

# Specify the gower exponents
good_gower_power <- 50
bad_gower_power <- 1

# Compute the good distances between the prediction of interest
# and all other observations
lime_data$distance_good <-
  (1 - gower_dist(x = prediction_of_interest %>%
                    select(feature1_stnd, feature2_stnd),
                  y = lime_data %>%
                    select(feature1_stnd,
                           feature2_stnd)))^good_gower_power

# Compute the bad distances between the prediction of interest
# and all other observations
lime_data$distance_bad <-
  (1 - gower_dist(x = prediction_of_interest %>%
                    select(feature1_stnd, feature2_stnd),
                  y = lime_data %>%
                    select(feature1_stnd,
                           feature2_stnd)))^bad_gower_power

# Prepare the data for plotting
lime_data_gathered <- lime_data %>%
  gather(feature, feature_stnd_value,
         feature1_stnd:feature2_stnd) %>%
  gather(distance, distance_value, distance_good:distance_bad) %>%
  mutate(distance = fct_recode(distance,
                               "good" = "distance_good",
                               "bad" = "distance_bad"),
         feature = fct_recode(feature,
                              "Feature 1" = "feature1_stnd",
                              "Feature 2" = "feature2_stnd"))

# Prepare the prediction of interest data for plotting
prediction_of_interest_gathered <- prediction_of_interest %>%
  select(-feature1, -feature2) %>%
  gather(feature, feature_value, feature1_stnd, feature2_stnd) %>%
  mutate(feature = fct_recode(feature,
                              "Feature 1" = "feature1_stnd",
                              "Feature 2" = "feature2_stnd"))

@

<<concept-explainers>>=

# Fit the good interpretable explainer model
explainer_good <-
  glmnet(x = lime_data %>% select(feature1_stnd, feature2_stnd)
         %>% as.matrix(),
         y = lime_data$prediction,
         alpha = 0,
         lambda = 1,
         weights = lime_data$distance_good)

# Fit the bad interpretable explainer model
explainer_bad <-
  glmnet(x = lime_data %>% select(feature1_stnd, feature2_stnd)
         %>% as.matrix(),
         y = lime_data$prediction,
         alpha = 0,
         lambda = 1,
         weights = lime_data$distance_bad)

# Join the coefficients from the explainer model into a dataframe
coefs_data <- data.frame(case = c("good", "bad"),
                         b0 = c(coef(explainer_good)[1],
                                coef(explainer_bad)[1]),
                         b1 = c(coef(explainer_good)[2],
                                coef(explainer_bad)[2]),
                         b2 = c(coef(explainer_good)[3],
                                coef(explainer_bad)[3])) %>%
  mutate(feature1 = b0 + b2*prediction_of_interest$feature2_stnd,
         feature2 = b0 + b1*prediction_of_interest$feature1_stnd) %>%
  gather(key = feature, value = int, feature1:feature2) %>%
  mutate(slope = c(coef(explainer_good)[2],
                   coef(explainer_good)[3],
                   coef(explainer_bad)[2],
                   coef(explainer_bad)[3]),
         feature = fct_recode(feature,
                              "Feature 1" = "feature1",
                              "Feature 2" = "feature2"))

@

\begin{figure*}[!htbp]
<<concept-plot-good, out.width = '\\textwidth', fig.width = 7.95, fig.height = 3.75, warning = FALSE>>=

# Plot of good explainer model
ggplot() +
  facet_grid(. ~ feature, switch = "x") +
  geom_point(data = lime_data_gathered,
             mapping = aes(x = feature_stnd_value,
                           y = prediction,
                           size = distance_value,
                           alpha = distance_value,
                           color = distance)) +
  geom_abline(data = coefs_data %>% filter(case == "good"),
              mapping = aes(intercept = int, slope = slope),
              size = 1) +
  scale_alpha(range = c(0.3, 1)) +
  scale_color_manual(values = c(NA, "grey30"), guide = FALSE) +
  geom_point(data = prediction_of_interest_gathered,
             mapping = aes(x = feature_value,
                           y = prediction,
                           fill = color),
             color = "black",
             size = 5,
             shape = 23,
             alpha = 0.75) +
  scale_fill_manual(values = "#FAAA72") +
  geom_text(
    data = data.frame(feature_stnd_value = 1.2,
                      prediction = 1.6,
                      feature = c("Feature 1", "Feature 2"),
                      slope = c(paste("Slope:",
                                      coefs_data %>%
                                        filter(case == "good",
                                               feature == "Feature 1") %>%
                                        pull(slope) %>%
                                        round(3)),
                                paste("Slope:",
                                      coefs_data %>%
                                        filter(case == "good",
                                               feature == "Feature 2") %>%
                                        pull(slope) %>%
                                        round(3)))),
    mapping = aes(x = feature_stnd_value,
                  y = prediction,
                  label = slope),
    family = "Times",
    size = 4) +
  labs(x = "",
       y = "Black-Box Prediction",
       title = "Conceptual Depiction of a Faithful Local Explainer Model",
       subtitle = paste("Gower Distance Metric Exponent:", good_gower_power),
       fill = "",
       alpha = "Weight",
       size = "Weight") +
  theme_linedraw(base_family = "Times", base_size = 10) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        strip.placement = "outside",
        strip.background = element_rect(color = "white", fill = "white"),
        strip.text = element_text(color = 'black', size = 10)) +
  guides(fill = guide_legend(order = 1),
         size = guide_legend(order = 2),
         alpha = guide_legend(order = 2))

@
\caption{A conceptual depiction of a faithful LIME explainer model in the immediate neighborhood of a prediction of interest. The predictions from a hypothetical black-box model are plotted against the standardized values of the two predictor variables used to fit the hypothetical model. The diamond shaped points represent the location of a prediction of interest. The size and opacity of the circular points indicate the weight assigned based on the distance to the point of interest computed using the inverse of the Gower distance metric raised to the power of \Sexpr{good_gower_power}. The black lines are a weighted ridge regression model used as an explainer model that reasonably captures the relationship between the black-box predictions and the features in a local region around the point of interest. That is, it is faithful to the complex model and produces a reasonable explanation that Feature 1 plays a more important role in the prediction of interest than Feature 2 since the magnitude of the slope associated with Feature 1 is larger.}
\label{fig:concept-plot-good}

\vspace*{\floatsep}

<<concept-plot-bad, out.width = '\\textwidth', fig.width = 7.95, fig.height = 3.75, warning = FALSE>>=

# Plot of good explainer model
ggplot() +
  facet_grid(. ~ feature, switch = "x") +
  geom_point(data = lime_data_gathered,
             mapping = aes(x = feature_stnd_value,
                           y = prediction,
                           size = distance_value,
                           alpha = distance_value,
                           color = distance)) +
  geom_abline(data = coefs_data %>% filter(case == "bad"),
              mapping = aes(intercept = int, slope = slope),
              size = 1) +
  scale_alpha(range = c(0.3, 1)) +
  scale_color_manual(values = c("grey30", NA), guide = FALSE) +
  geom_point(data = prediction_of_interest_gathered,
             mapping = aes(x = feature_value,
                           y = prediction,
                           fill = color),
             color = "black",
             size = 5,
             shape = 23,
             alpha = 0.75) +
  scale_fill_manual(values = "#FAAA72") +
  geom_text(
    data = data.frame(feature_stnd_value = 1.2,
                      prediction = 1.6,
                      feature = c("Feature 1", "Feature 2"),
                      slope = c(paste("Slope:",
                                      coefs_data %>%
                                        filter(case == "bad",
                                               feature == "Feature 1") %>%
                                        pull(slope) %>%
                                        round(3)),
                                paste("Slope:",
                                      coefs_data %>%
                                        filter(case == "bad",
                                               feature == "Feature 2") %>%
                                        pull(slope) %>%
                                        round(3)))),
    mapping = aes(x = feature_stnd_value,
                  y = prediction,
                  label = slope),
    family = "Times",
    size = 4) +
  labs(x = "",
       y = "Black-Box Prediction",
       title = "Conceptual Depiction of an Unfaithful Local Explainer Model",
       subtitle = paste("Gower Distance Metric Exponent:", bad_gower_power),
       fill = "",
       alpha = "Weight",
       size = "Weight") +
  theme_linedraw(base_family = "Times", base_size = 10) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        strip.placement = "outside",
        strip.background = element_rect(color = "white", fill = "white"),
        strip.text = element_text(color = 'black', size = 10)) +
  guides(fill = guide_legend(order = 1),
         size = guide_legend(order = 2),
         alpha = guide_legend(order = 2))

@
\caption{A conceptual depiction of an unfaithful local explainer model in the immediate neighborhood of a prediction of interest. A ridge regression model is fit to the same black-box model predictions and predictor variables as in \autoref{fig:concept-plot-good}, but the weights are computed using a Gower exponent of 1. The explainer model provides a global approximation of the complex model in regards to the prediction of interest.}
\label{fig:concept-plot-bad}
\end{figure*}

\subsection{Explainer Models}

As a result of the movement to produce explainable predictions, an area of research has emerged on developing ways to explain output from machine learning algorithms \citep{guidotti:2018} \citep{mohseni:2018} \citep{molnar:2019}. Model explainers are one commonly used approach \citep{mohseni:2018}. A model explainer is a method that uses a surrogate model to relate the predictor variables to the black-box model predictions. We will distinguish between the terms of model explainer and explainer model: by \emph{model explainer} we denote the  method for explaining a complex model using a surrogate model, while the \emph{explainer model}, or simply the \emph{explainer}, is the surrogate model.

LIME is one such model explainer \citep{ribeiro:2016}. While some model explainers are focused on understanding a model at the global level, LIME claims to provide local explanations. Additionally, LIME is designed to work with any model and to produce easily understandable explanations \citep{ribeiro:2016}. Conceptually, LIME fits a simple interpretable model, the explainer model,  meant to capture the behavior of the (complex) black-box model in a local region around a prediction of interest. The  simple model then provides interpretable estimates for variables that most influenced the prediction made by the complex model.

\autoref{fig:concept-plot-good} provides a visualization of this conceptual understanding of LIME. The two plots show the predictions from a hypothetical black-box model plotted against the two predictor variables used to fit the hypothetical model. The diamond shaped points represent a prediction  of interest. A Gower distance metric \citep{gower:1971} is used to define locality: the size of the points represent the inverse of the Gower distance as a reflection of the proximity to the prediction of interest. Here, an exponent of \Sexpr{good_gower_power} is used to emphasize interest in a very local region around the point of interest. A ridge regression model weighted by the proximity values is used as the explainer model. The black-box predictions are used as the response variable, standardized versions of Features 1 and 2 are included as predictor variables. Standardized features allow direct comparisons of the model coefficients. The explainer model is depicted by the black lines in the figure.

The plot on the left of \autoref{fig:concept-plot-good} shows the relationship between the black-box predictions and Feature 1.  Here, the explainer model is plotted with Feature 2 fixed at the observed value of Feature 2 for the prediction of interest. The explainer model captures the relationship in the immediate neighborhood around the prediction of interest  with a slope of \Sexpr{coefs_data %>% filter(case == "good", feature == "Feature 1") %>% pull(slope) %>% round(3)}. The plot on the right shows that there is no global or local relationship between the black-box predictions and Feature 2. Here, the explainer model is plotted with Feature 1 set to be the observed value of Feature 1 for the prediction of interest, and it has a small slope of \Sexpr{coefs_data %>% filter(case == "good", feature == "Feature 2") %>% pull(slope) %>% round(3)}. The magnitude of the slope associated with Feature 1 is larger than the slope of Feature 2, resulting LIME to report that Feature 1 plays a more important role in the prediction made by the black-box model.

\subsection{Motivation for Diagnosing LIME}

Explainer models are meant to provide clarity to the process of predictive modeling. However, explainer models are an approximation of the complex models and not a direct interpretation. The explanations produced by an explainer model are subject to the quality of the approximation of the explainer to the complex model. This means that explainer models add another layer of complexity to predictive models by requiring yet another model that needs to be relied on for its accuracy.

The choice of exponent in the scenario depicted in \autoref{fig:concept-plot-good} is crucial. High values ensure an up-weight of observations closer to the prediction of interest. Now consider the example depicted in \autoref{fig:concept-plot-bad}. The plots show the same data as \autoref{fig:concept-plot-good}, but the Gower distance metric was raised to the default power used by the \emph{lime} R package of \Sexpr{bad_gower_power}. This causes the observations that are further away from the prediction of interest to be given larger weights than before. In \autoref{fig:concept-plot-good}, the explainer model captures the relationship between the black-box predictions in the immediate neighborhood of the prediction of interest. This cannot be said of the explainer model in \autoref{fig:concept-plot-bad}. In addition, the magnitude of the slope (\Sexpr{coefs_data %>% filter(case == "bad", feature == "Feature 2") %>% pull(slope) %>% round(3) %>% abs()}) associated with Feature 2 is larger than that of Feature 1 (\Sexpr{coefs_data %>% filter(case == "bad", feature == "Feature 1") %>% pull(slope) %>% round(3) %>% abs()}). Thus, this explainer model actually provides a misleading explanation that Feature 2 plays a more important role in predicting the observation of interest.

There are various ways in which LIME can fail. One of the biggest difficulties with LIME is determining how to specify a local region \citep{molnar:2019} due to an unclear definition of what a local region means and how to apply LIME to achieve an appropriate local region. \autoref{fig:concept-plot-bad} demonstrates an explainer model that provides misleading explanations due to poorly specified weights. \citet{laugel:2018} show additional examples of undesirable explanations produced by LIME when the local region was chosen inadequately. \citet{alvarezmelis:2018} raise another concern pertaining to the robustness of explanations from LIME and other post-hoc explainers: they find that even small changes in predictor variables can lead to very different LIME explanations. Additionally, LIME relies on a good approximation of the explainer model to the complex model. \citet{ribeiro:2016} acknowledge that ``if the underlying model is highly non-linear even in the locality of the prediction, there may not be a faithful explanation" with a linear regression model as the explainer model.

As a result of the various ways LIME explanations can fail, it is important to assess LIME explanations. In this paper, we lay out the set of claims about LIME made by \citet{ribeiro:2016} and propose visualizations for the assessment of these claims. We have organized our visualizations into three categories:

\begin{itemize}
\item Diagnostics for \emph{Individual Explanations}: Following advice by \citet{wickham:2015}, we visualize the steps taken by LIME to fit the explainer model and plot the model in data space to get a better understanding of the LIME algorithm and an assessment of the claims made at various stages in the creation of the explanation.
\item Diagnostics for \emph{Sets of Explanations}: We visualize a set of explanations associated with a set of predictions to gain insight into the variability in LIME explanations across the feature space and assess the approximations of the explainer models.
\item Diagnostics for \emph{Comparisons of Tuning Parameters}: To assess the tuning parameters used to produce LIME explanations, we visualize sets of explanations associated with the same predictions across applications of LIME using different tuning parameters as defined in \autoref{implementation-visuals}.
\end{itemize}

While LIME has been implemented for image, tabular, and text data, we will only focus on tabular data. For additional simplicity, we will only discuss classification prediction models with a dichotomous response variable and continuous predictor variables. However, the proposed diagnostics are applicable in a wider range of situations.

\subsection{Overview of Paper}

\autoref{background} provides background on LIME including an overview of the LIME algorithm, currently available implementations of LIME, and the claims \citet{ribeiro:2016} make about LIME. We introduce the suggested diagnostic plots in Sections \ref{procedure}, \ref{set-visuals}, and \ref{implementation-visuals}. In \autoref{application}, we  demonstrate the use of the diagnostics to assess LIME explanations for a random forest model fit to a forensics bullet matching dataset. \autoref{discussion} concludes with a discussion on how the examples of the visualizations in this paper find concerns with LIME in regards to the claims made by \citet{ribeiro:2016} that agree with \citet{alvarezmelis:2018}, \citet{laugel:2018}, and \citet{molnar:2019}. Additionally, extensions of the visual diagnostics are discussed.

\section{Background on LIME} \label{background}

LIME was introduced in 2016 by \citet{ribeiro:2016} in an attempt to create a model explainer that produced easily understandable explanations for individual predictions from any predictive model \citep{ribeiro:2016}. The general idea of LIME is to provide an explanation of how a black-box model arrived at a specific prediction for a given observation.

As described by \citet{laugel:2018}, the process performed by LIME can be divided into three steps:

\begin{enumerate}

\item \emph{Data Simulation and Interpretable Transformation}: Simulate a dataset from the original data used to fit the black-box model. Apply a transformation to the simulated data and the prediction of interest that will allow for  interpretable explanations.

\item \emph{Explainer Model Fitting}: Apply the black-box model to the simulated data to obtain predictions. Compute the distance between each of the simulated observations and the prediction of interest. Fit an interpretable model with the black-box predictions from the simulated data as the response, the transformed simulated data as the predictors, and the distances as weights. This model is the explainer model.

\item \emph{Explainer Model Interpretation}: Interpret the explainer model to determine which features played the most important role in the prediction of interest.

\end{enumerate}

\citet{ribeiro:2016} make the following set of claims regarding the performance of LIME:

\begin{itemize}
\item \emph{Interpretability}: The explainer model can be easily interpreted to provide meaningful explanations.
\item \emph{Faithfulness}: The explainer model sufficiently captures the relationship between the complex model predictions and the features in the local region around a prediction of interest to produce explanations that are faithful to the complex model.
\item \emph{Linearity}: By using a ridge regression model as the explainer model, it is assumed that there is a linear relationship between complex model predictions and the features in the local region around a prediction of interest.
\item \emph{Localness}: The explanations produced by LIME are local in regards to a prediction of interest.
\end{itemize}

The assumption of interpretability only depends on the complexity of the model used as explainer model. If the model is too complex to provide meaningful explanations (e.g. there are too many variables in the model), it is clear that the assumption of interpretability is violated. The other three assumptions are not as easy to assess -- for those we suggest the use of diagnostic plots.

LIME was initially implemented in a Python package\footnote{https://github.com/marcotcr/lime} by the original authors. The adaption to an R package is by Thomas Lin-Pedersen\footnote{https://github.com/thomasp85/lime}. In this paper, we use a forked version\footnote{https://github.com/goodekat/lime} of the development version of the R package \emph{lime} (\Sexpr{packageVersion("lime")}) \citep{pedersen:2020}. The forked version of \emph{lime} allows us to export internal values of the procedure not already exported by \emph{lime}.

\section{Visualizations of an Individual LIME Explanation} \label{procedure}

<<sine-data, echo = FALSE, include = FALSE>>=

# Functions for rotating the data
rot_x <- function(x, y, theta) (x * cos(theta)) - (y * sin(theta))
rot_y <- function(x, y, theta) (x * sin(theta)) + (y * cos(theta))

# Generate the data
theta = -0.9
min = -10
max = 10
set.seed(20190913)
sine_data <- data.frame(x1 = runif(600, min, max),
                        x2 = sort(runif(600, min, max))) %>%
  mutate(x1new = rot_x(x1, x2, theta),
         x2new = rot_y(x1, x2, theta),
         y = ifelse(x2new > 5 * sin(x1new), "blue", "red")) %>%
  slice(sample(1:n())) %>%
  mutate(x3 = rnorm(600),
         case = 1:600) %>%
  select(case, everything())

# Separte the data into training and testing parts
set.seed(20191003)
rs <- sample(1:600, 500, replace = FALSE)
sine_data_train <- sine_data[rs,]
sine_data_test <- sine_data[-rs,]

# Fit a random forest
set.seed(20191003)
rfsine <- randomForest(x = sine_data_train %>% select(x1, x2, x3),
                       y = factor(sine_data_train$y))

# Obtain predictions on the training and testing data
sine_data_train$rfpred <- predict(rfsine)
sine_data_train <- cbind(sine_data_train, predict(rfsine, type = "prob"))
sine_data_train <- sine_data_train %>% 
  rename(rfprob_blue = blue, rfprob_red = red)
sine_data_test$rfpred <- predict(rfsine, sine_data_test %>% select(x1, x2, x3))
sine_data_test <- cbind(sine_data_test,
                        predict(rfsine, sine_data_test
                                %>% select(x1, x2, x3),
                                type = "prob"))
sine_data_test <- sine_data_test %>% 
  rename(rfprob_blue = blue, rfprob_red = red)

# Extract the prediction of interest from the sine test data
sine_poi <- sine_data_test %>% filter(y != rfpred, x1 > 0, x1 < 5, x2 > 5)

@

\begin{figure*}[!t]
\centering
<<sine-plot-data, out.width = '\\textwidth', fig.width = 8, fig.height = 3.1>>=

# Create points represting the rotated since curve
sinefun_data <- data.frame(xnew = seq(min(sine_data$x1new),
                                      max(sine_data$x1new),
                                      by = 0.01)) %>%
  mutate(ynew = 5 * sin(xnew)) %>%
  mutate(x = rot_x(xnew, ynew, -theta),
         y = rot_y(xnew, ynew, -theta)) %>%
  filter(y >= -10, y <= 10)

# Specify colors for predictions
sinecolor_red = "firebrick"
sinecolor_blue = "steelblue"

# Plot the training data observed classes
sine_plot_obs <- ggplot(sine_data_train, aes(x = x1, y = x2, color = y)) +
  geom_point(alpha = 0.8) +
  geom_path(data = sinefun_data, aes(x = x, y = y),
            color = "black") +
  scale_colour_manual(values = c(sinecolor_blue, sinecolor_red)) +
  theme_bw(base_family = "Times", base_size = 10) +
  labs(x = TeX("$x_1$"),
       y = TeX("$x_2$"),
       color = TeX("y"),
       title = "Training Data")

# Plot the testing data rf predictions
sine_plot_pred <- ggplot() +
  geom_point(data = sine_poi %>%
               mutate(shape = "Prediction \nof Interest"),
             mapping = aes(x = x1,
                           y = x2,
                           #fill = rfprob_blue,
                           shape = shape),
             size = 5,
             alpha = 0.8,
             color = "black") +
  geom_point(data = sine_data_test %>% filter(y != rfpred),
             mapping = aes(x = x1, y = x2),
             shape = 1,
             size = 3,
             color = "black") +
  geom_point(data = sine_data_test,
             mapping =  aes(x = x1,
                            y = x2,
                            color = rfprob_blue,
                            fill = rfprob_blue),
             shape = 21,
             alpha = 0.8) +
  geom_path(data = sinefun_data, aes(x = x, y = y),
            color = "black") +
  scale_color_gradient2(low = sinecolor_red,
                        mid = '#f7f7f7',
                        high = sinecolor_blue,
                        midpoint = 0.5) +
  scale_fill_gradient2(low = sinecolor_red,
                        mid = '#f7f7f7',
                        high = sinecolor_blue,
                        midpoint = 0.5) +
  scale_shape_manual(values = 23) +
  theme_bw(base_family = "Times", base_size = 10) +
  labs(x = TeX("$x_1$"),
       y = TeX("$x_2$"),
       color = "Random \nForest \nProbability \nfor 'blue'",
       fill = "Random \nForest \nProbability \nfor 'blue'",
       title = "Testing Data",
       shape = "") +
  guides(shape = guide_legend(order = 1))

# Join the plots
plot_grid(sine_plot_obs, sine_plot_pred,
          nrow = 1,
          rel_widths = c(0.4825, 0.5175))

@
\caption{Plots of $x_2$ versus $x_1$ from the training (left) and testing (right) set of the \data \ introduced in Section \ref{procedure}. The true classification boundary is shown as the solid black line in both plots. The color of the training data points represents the value of the observed response variable ($y$). The color of the testing data points represents the random forest probability that an observation belongs to the category of blue ($\hat{y}$). The \Sexpr{dim(sine_data_test %>% filter(y != rfpred))[1]} cases that are misclassified by the random forest are identified by black circles. The prediction of interest to explain is indicated by a diamond.}
\label{fig:sine-plot-data}
\end{figure*}

At a high level, the concept of LIME is relatively simple: an interpretable model is used to approximate a complex model in a local region. In practice, the implementation of LIME is not straightforward, and research is being done to improve the procedure \citep{laugel:2018}. At each step, various decisions have to be made such as the type of distribution to use when simulating data and which distance metric to use to assign weights to the simulated values. It is possible for the procedure to go wrong at any of the internal steps. Without an understanding of or a way to assess the steps, LIME becomes a black-box procedure of its own. To counteract the black-box nature, we suggest the use of visualizations of each step of the LIME algorithm. In this section, we provide example visualizations of the LIME procedure for the creation of an individual explanation.

\paragraph{The \data}

To demonstrate the visualizations, we generate an example dataset that will be referred to as the \data. The \data \ contains \Sexpr{dim(sine_data)[1]} observations with three features and one response variable. The features, $x_1$, $x_2$, and $x_3$, are randomly sampled from Unif(\Sexpr{min}, \Sexpr{max}), Unif(\Sexpr{min}, \Sexpr{max}), and $\mbox{N}(0,1)$ distributions, respectively. A binary response variable $y$ is  created using a rotated sine curve. In particular, let $x'_1=x_1\cos(\theta)-x_2\sin(\theta)$ and $x'_2=x_1\sin(\theta)+x_2\cos(\theta)$ where $\theta=-0.9$. Then $y$ is defined as
\begin{eqnarray}\label{eq:data}
  y=\begin{cases}
  \mbox{blue} & \mbox{ if } x'_2 > \sin\left(x'_1\right) \\
  \mbox{red} & \mbox{ if } x'_2 \le \sin\left(x'_1\right) \ . %\nolabel
  \end{cases}
\end{eqnarray}
Note that due to the creation of $y$ in this manner, $y$ is dependent on $x_1$ and $x_2$ and independent of $x_3$.

The dataset is divided into a training set of \Sexpr{dim(sine_data_train)[1]} observations and a testing set of \Sexpr{dim(sine_data_test)[1]} observations. A random forest model is fit using the R package \emph{randomForest} (version \Sexpr{packageVersion("randomForest")}) \citep{liaw:2002} with the default settings. The model is applied to the testing set to obtain predictions. \autoref{fig:sine-plot-data} shows scatterplots of $x_2$ versus $x_1$ from the training data (left) and the testing data (right). Both plots include the true classification boundary of the rotated sine function plotted as the solid black line. The training data are colored by the observed response variable ($y$), and the testing data are colored by the prediction probabilities from the random forest model ($\hat{y}$).

The random forest model misclassifies \Sexpr{dim(sine_data_test %>% filter(y != rfpred))[1]} points on the classification boundary. These are identified by circles in \autoref{fig:sine-plot-data}. For the visualizations of the steps of the LIME algorithm, we focus on one of these points: the observation with $(x_1, x_2, x_3)$ coordinates of (\Sexpr{round(sine_poi$x1, 2)}, \Sexpr{round(sine_poi$x2, 2)}, \Sexpr{round(sine_poi$x3, 2)}) and indicated in \autoref{fig:sine-plot-data} by a diamond.

<<sine-lime>>=

# Apply LIME with various tuning parameters to the sine data
if (!file.exists("../data/sine_lime_explain.rds")) {

    # Apply lime with various input options
    sine_lime_explain <- apply_lime(
      train = sine_data_train %>% select(x1, x2, x3),
      test = sine_data_test %>% select(x1, x2, x3),
      model = rfsine,
      label = "blue",
      n_features = 2,
      sim_method = c('quantile_bins', "kernel_density"),
      nbins = 2:6,
      feature_select = "auto",
      dist_fun = "gower",
      kernel_width = NULL,
      gower_pow = 1,
      return_perms = TRUE,
      all_fs = TRUE,
      seed = 20190914)

    saveRDS(sine_lime_explain, "../data/sine_lime_explain.rds")

  } else {

    sine_lime_explain <- readRDS("../data/sine_lime_explain.rds")

  }

@

<<sine-lime-default>>=

# Extract the explanations from the default lime implementation
sine_lime_default <- sine_lime_explain$explain %>% filter(nbins == 4)

# Extract the explanations from the default lime implementation
# for the prediction of interest only
sine_poi_lime_default <- sine_lime_default %>%
  filter(case == sine_poi %>% pull(case)) %>%
  mutate(case = c("Prediction of Interest", "Prediction of Interest"))

@

We apply LIME to the \data \ using \emph{lime} with the default settings. The user is asked to specify the number of features shown in the explanations. Here, we set this value to two, because we expect that $x_1$ and $x_2$ will be the main drivers in the prediction. Note that the complexity of an explanation goes hand in hand with the number of features selected to be included in the explanation. Setting the number of features to a small number will make the explanation simpler but not necessarily more correct.

\autoref{fig:sine-plot-poi} shows the visualization of the explanation produced by \emph{lime} for the prediction of interest. The figure shows that the random forest returned a probability of \Sexpr{sine_poi_lime_default$label_prob[1]} that the observation of interest belongs to category blue {(denoted as the ``label" in the figure). The colored bars indicate the features chosen by LIME and whether they support or contradict a random forest classification of blue. Note that the LIME explanation provides its explanations in form of intervals surrounding the observation of interest. We will discuss this aspect in more detail in Section \ref{step1}.

The explanation for the prediction of interest depicted in Figure \ref{fig:sine-plot-poi} can be interpreted as follows. A random forest classification of blue is supported by the prediction of interest having a value of $x_2$ that is greater than \Sexpr{str_split(sine_poi_lime_default$feature_desc[[1]], pattern = " ")[[1]][1]}, but the prediction of interest having a value of $x_1$ that is greater than \Sexpr{str_split(sine_poi_lime_default$feature_desc[[2]], pattern = " ")[[1]][1]} and less than or equal to \Sexpr{str_split(sine_poi_lime_default$feature_desc[[2]], pattern = " ")[[1]][5]} provides support against a classification of blue. Since the weight associated with $x_2$ has a larger magnitude than the weight associated with $x_1$, LIME explains that the $x_1$ and $x_2$ locations of the prediction of interest provide more support for a random forest classification of blue over red. This explanation agrees with the random forest probability of \Sexpr{sine_poi_lime_default$label_prob[1]} for blue, even though both classify the observation incorrectly.

\autoref{fig:sine-plot-poi} also includes an "explanation fit" value. This value corresponds to the deviance ratio from the R package \emph{glmnet} \citep{simon:2011} for a ridge regression model, or in other words, this is the $R^2$ value associated with the explainer model. In this case, it is \Sexpr{round(sine_poi_lime_default$model_r2[1], 2)} suggesting that the explainer model is not a good linear fit. However, it is commonly accepted that $R^2$ has limitations for accessing the quality of fit of a model \citep{sapra:2014}, and it should not be the only metric used for assessment of a model. Based on this metric or this plot, it is not yet possible to make an informed assessment of the trustworthiness of the explanation.

We will visualize the steps taken by LIME in creating this explanation to provide insight on why this explanation is returned and to assess its quality. Since the explanation chose the two features, $x_1$ and $x_2$, all of our visualizations will focus on these two features, but they could be extended to include $x_3$ or more features if available. A discussion on the extension of the visualizations to more than two features is included in Section \ref{limitations}. Furthermore, while presenting the visualizations of the procedure, we describe the default procedure options used by \emph{lime} and briefly mention the other available options. More information on the other \emph{lime} options is included in Appendix \ref{lime}.

\begin{figure}[!htbp]
\centering
<<sine-plot-poi, out.width = '0.5\\textwidth', fig.width = 4, fig.height = 3.25>>=
sine_poi_exp <- sine_poi_lime_default %>% plot_features()
sine_poi_exp
@
\caption{Visualization from \emph{lime} of the explanation associated with the prediction of interest from the \data \ produced by the default settings. The probability of \Sexpr{sine_poi_lime_default$label_prob[1]} is the random forest probability in support of a classification of blue. The colored bars indicate that $\Sexpr{str_split(sine_poi_lime_default$feature_desc[[1]], pattern = " ")[[1]][1]} < x_2$ supports a random forest prediction of 1 and $\Sexpr{str_split(sine_poi_lime_default$feature_desc[[2]], pattern = " ")[[1]][1]}<x_1\le \Sexpr{str_split(sine_poi_lime_default$feature_desc[[2]], pattern = " ")[[1]][5]}$ contradicts a random forest prediction of 0. The explanation fit of \Sexpr{round(sine_poi_lime_default$model_r2[1], 2)} is the $R^2$ value of the explainer model, which indicates that the explainer model has a poor linear fit. Aside of some evidence from the $R^2$ value, it is not clear whether this explanation is reasonable.}
\label{fig:sine-plot-poi}
\end{figure}

\begin{figure*}[!htbp]
\centering
<<sine-plot-step1ab, out.width = '\\textwidth', fig.width = 8.25, fig.height = 3.25, warning = FALSE>>=

# Determine the bin cuts for the default lime implementation
sine_lime_default_bin_cuts <- sine_lime_default %>%
  select(feature, feature_desc) %>%
  unique() %>%
  separate(feature_desc, c("other", "bin_cut"), sep = " <= ") %>%
  select(-other) %>%
  na.omit() %>%
  mutate(bin_cut = as.numeric(bin_cut)) %>%
  arrange(feature) %>%
  mutate(case = rep(1:3, 2)) %>%
  spread(feature, bin_cut)

# Plot the training data with observed classes and the
# four quantile bins associated with each feature
sine_plot_bins <- ggplot() +
  geom_point(data = sine_data_train,
             mapping = aes(x = x1, y = x2, color = y),
             alpha = 0.8) +
  geom_vline(xintercept = sine_lime_default_bin_cuts$x1) +
  geom_hline(yintercept = sine_lime_default_bin_cuts$x2) +
  scale_color_manual(values = c(sinecolor_blue, sinecolor_red)) +
  scale_fill_manual(values = c(sinecolor_blue, sinecolor_red)) +
  scale_shape_manual(values = 23) +
  theme_bw(base_family = "Times", base_size = 10) +
  labs(x = TeX("$x_1$"),
       y = TeX("$x_2$"),
       color = TeX("y"),
       fill = TeX("y"),
       shape = "",
       title = "Training Data Plot") +
  guides(shape = guide_legend(order = 1),
         fill = FALSE)

# Obtain the simulated data associated with the poi
sine_poi_perms <- sine_poi_lime_default %>%
  slice(1) %>%
  select(perms_raw, perms_pred_complex, perms_numerified, weights) %>%
  mutate(perms_numerified =
           map(perms_numerified,
               .f = function(x) rename(x,
                                       "x1num" = "x1",
                                       "x2num" = "x2",
                                       "x3num" = "x3"))) %>%
  unnest(cols = c(perms_raw, perms_pred_complex, perms_numerified, weights)) %>%
  select(-red) %>%
  rename(rfpred = blue) %>%
  mutate(case = factor(1:n())) %>%
  select(case, everything())

# Plot the permutations associated with the prediction of interest
sine_plot_sims <- ggplot() +
  geom_point(data = sine_poi_perms,
             mapping = aes(x = x1,
                           y = x2,
                           fill = rfpred,
                           color = rfpred),
             alpha = 0.8,
             shape = 21,
             size = 0.75) +
  geom_vline(xintercept = sine_lime_default_bin_cuts$x1) +
  geom_hline(yintercept = sine_lime_default_bin_cuts$x2) +
  geom_point(data = sine_poi %>% mutate(shape = "Prediction \nof Interest"),
             mapping = aes(x = x1,
                           y = x2,
                           fill = rfprob_blue,
                           shape = shape),
             color = "black",
             size = 5,
             alpha = 0.8) +
  scale_fill_gradient2(low = sinecolor_red,
                        mid = '#f7f7f7',
                        high = sinecolor_blue,
                        midpoint = 0.5) +
  scale_color_gradient2(low = sinecolor_red,
                        mid = '#f7f7f7',
                        high = sinecolor_blue,
                        midpoint = 0.5) +
  scale_shape_manual(values = 23) +
  theme_bw(base_family = "Times", base_size = 10) +
  labs(x = TeX("$x'_1$"),
       y = TeX("$x'_2$"),
       fill = "Random \nForest \nProbability \nfor 'blue'",
       color = "Random \nForest \nProbability \nfor 'blue'",
       shape = "",
       title = "Untransformed Simulated Data Plot") +
  guides(shape = guide_legend(order = 1)) + 
  theme(aspect.ratio = 1)

# Join the plots
plot_grid(sine_plot_bins, sine_plot_sims,
          nrow = 1,
          rel_widths = c(0.47, 0.53))

@
\caption{\emph{Training data plot} (left) and \emph{untransformed simulated data plot} (right). Both plots show the 4 quantile bins for $x_1$ and $x_2$ as the vertical and horizontal lines, respectively, overlaid on the \data \ training set colored by the response values (left) and the simulated data colored by the random forest probabilities for category blue (right). The depiction of the random forest predictions for the simulated data shows that the feature space is divided into rectangles of various sizes within which the random forest returns similar probabilities. The intersection of the quantile bins creates a grid that divides the feature space into 16 cells, which is too simple to capture the rectangular pattern of the predictions made by the random forest.}
\label{fig:sine-plot-step1ab}
\end{figure*}

<<sine-poi-explainer, warning = FALSE>>=

# Determine the lime explanation cutoffs
sine_poi_bounds <- sine_poi_lime_default %>%
  select(case, feature, feature_value, feature_desc) %>%
  separate(feature_desc, c("other", "upper"), sep = " <= ") %>%
  separate(other, c("lower", "feature2"), sep = " < ") %>%
  mutate(upper = ifelse(is.na(upper), "Inf", upper)) %>%
  select(-feature2) %>%
  mutate_at(.vars = c("lower", "upper"), .funs = as.numeric)

# Extract the coefficients from the explainer
sine_b0 <- sine_poi_lime_default$model_intercept[1]
sine_b1 <- sine_poi_lime_default$feature_weight[2]
sine_b2 <- sine_poi_lime_default$feature_weight[1]

# Extract the bounds of the bins
x1_lower <- sine_poi_bounds %>% filter(feature == "x1") %>% pull(lower)
x1_upper <- sine_poi_bounds %>% filter(feature == "x1") %>% pull(upper)
x2_lower <- sine_poi_bounds %>% filter(feature == "x2") %>% pull(lower)
x2_upper <- sine_poi_bounds %>% filter(feature == "x2") %>% pull(upper)

# Function for computing the predicted value via the explainer model
sine_explainer <- function(z1, z2) sine_b0 + sine_b1 * z1 + sine_b2 * z2

@

\begin{figure}[!htbp]
\centering
<<sine-plot-step1c, out.width = '0.5\\textwidth', fig.width = 4.25, fig.height = 3.25, warning = FALSE>>=

# Create a dataset with the rectangles that make up the four categories
sine_exp_rect <-
  data.frame(rect = factor(1:6),
             z1 = c(0, 1, 0, 0, 1, 0),
             z2 = c(1, 1, 1, 0, 0, 0),
             case = factor(c(01, 11, 01, 00, 10, 00)),
             x1 = c(-10, x1_lower, x1_upper, -10, x1_lower, x1_upper),
             x2 = c(x1_lower, x1_upper, 10, x1_lower, x1_upper, 10),
             y1 = c(x2_lower, x2_lower, x2_lower, -10, -10, -10),
             y2 = c(10, 10, 10, x2_lower, x2_lower, x2_lower)) %>%
  mutate(empred = sine_explainer(z1, z2),
         case_names = ifelse(case == "11", "\nx'1 same bin \nx'2 same bin\n",
                      ifelse(case == "10", "\nx'1 same bin \nx'2 diff bin\n",
                      ifelse(case == "1", "\nx'1 diff bin \nx'2 same bin\n",
                      "\nx'1 diff bin \nx'2 diff bin\n"))))

# Plot of the numerified perturbations
ggplot() +
  geom_point(data = sine_poi_perms,
             mapping = aes(x = x1,
                           y = x2,
                           color = rfpred),
             alpha = 0.5,
             shape = 20) +
  geom_rect(data = sine_exp_rect,
            mapping = aes(xmin = x1,
                          xmax = x2,
                          ymin = y1,
                          ymax = y2,
                          fill = case_names),
            alpha = 0.7,
            color = "black") +
  geom_point(data = sine_poi,
             mapping = aes(x = x1, y = x2, color = rfprob_blue),
             size = 5,
             shape = 18,
             alpha = 0.8) +
  geom_point(data = sine_poi %>% mutate(shape = "Prediction \nof Interest"),
             mapping = aes(x = x1, y = x2, shape = shape),
             size = 5,
             alpha = 0.8) +
  scale_color_gradient2(low = sinecolor_red,
                        mid = '#f7f7f7',
                        high = sinecolor_blue,
                        midpoint = 0.5) +
  scale_fill_manual(values = c("grey90", "grey25", "grey70", "grey1")) +
  scale_shape_manual(values = 23) +
  theme_bw(base_family = "Times", base_size = 10) +
  labs(x = TeX("$x'_1$"),
       y = TeX("$x'_2$"),
       fill = "Interpretability \nTransformed \nFeature Value",
       title = "Transformed Simulated Data Plot",
       shape = "") +
  guides(shape = guide_legend(order = 1),
         size = FALSE,
         color = FALSE) + 
  theme(aspect.ratio = 1)

@
\caption{\emph{Transformed simulated data plot.} The values of $x'_2$ and $x'_1$ from the simulated data, colored by the random forest probabilities, are plotted behind rectangles representing the interpretability transformed values. The shades of the rectangles represent whether the observation values of $x'_1$ and/or $x'_2$ share the same bin as the prediction of interest. The location of the prediction of interest is denoted by a diamond. This plot shows how the features are simplified by LIME during the interpretability transformation from continuous features to categorical features with two categories each.}
\label{fig:sine-plot-step1c}
\end{figure}

\subsection{Data Simulation and Interpretable Transformation} \label{step1}

The data simulation process involves generating a new set of features based on the training data, applying the complex model to the simulated data to obtain predictions, and transforming the simulated features for ease of interpretation of the explainer model. To understand the progression from the training data to the transformed simulated data that LIME ultimately uses for the explanation, we visualize the three stages in the process. The visualizations corresponding to these stages will be referred to as (a) the \emph{training data plot}, (b) the \emph{untransformed simulated data plot}, and (c) the \emph{transformed simulated data plot}. Examples of these plots with the \data \ prediction of interest are shown in Figures \ref{fig:sine-plot-step1ab} and \ref{fig:sine-plot-step1c}.

The plot on the left in \autoref{fig:sine-plot-step1ab} is the training data plot for the \data \ prediction of interest, which depicts $x_2$ versus $x_1$ from the \data \ training set. The points are colored by the observed response value. The default data simulation in \emph{lime} is done by first dividing each feature in the training data into 4 quantile bins. The black lines in the left plot of \autoref{fig:sine-plot-step1ab} depict the 4 quantile bins for $x_1$ (vertical lines) and $x_2$ (horizontal lines). The quantile bins create a grid that divides the feature space of $x_1$ and $x_2$ into 16 cells. With the inclusion of $x_3$, the quantile bins divide the feature space into 64 cells. In general, the number of cells increases exponentially in the number of features and polynomially in the number of bins. % number of bins to the number of features: $b^f$ that's a polynomial relationship in b
This increase prohibits working with a large number of features or bins. Additionally, an increase in the number of bins may lead to an issue with visualizations of the LIME algorithm due to change blindness. See a further discussion on this issue in Section \ref{limitations}.

By default, \emph{lime} samples 4999 observations for each feature with a probability of 0.25 that an observation is drawn from a quantile bin. The observed feature values of the prediction of interest are appended to the simulated data to create a dataset with 5000 rows. The complex model is applied to the simulated data to obtain predictions. The plot on the right in \autoref{fig:sine-plot-step1ab} is the untransformed simulated data plot, which shows the simulated values of $x_1$ and $x_2$ from the \data \ example denotes as $x'_1$ and $x'_2$. The 4 quantile bin grid used to simulate the data is again depicted by the black vertical and horizontal lines. The points are colored by the random forest prediction probability that an observation is in category blue. The diamond shaped point indicates the location of the prediction of interest in the simulated data.

The simulated data provide a dense cover of the feature space, which gives insight on how the random forest model creates a prediction based on the $x_1$ and $x_2$ coordinates similar to a partial dependence plot \citep{friedman:2001}. The random forest appears to split the feature space into rectangles of different sizes within which the observations receive similar probabilities. For example, observations with $x_1\in[-10,-2.5)$ and $x_2\in[0,10)$ all have probabilities close to 1. The result is an image of predictions that looks like the rotated sine curve made up of rectangles of varying sizes. The predictions closest to the classification boundary of the curve have random forest probabilities around 0.5.

The random forest predictions depicted with the grid of quantile bins shows how the bins relate to the random forest probabilities. By simulating data using quantile bins, LIME only accounts for the feature space and not the relationship between the features and the response variable. As a result, some of the rectangles created by the quantile bins contain simulated values with similar random forest probabilities, but many of them contain a mixture of probabilities. The quantile bin rectangles are the wrong size to capture the rectangular pattern of random forest predictions. For example, the intersection of quantile bins where $x'_1\in[-5 ,0)$ and $x'_2\in[-5,0)$ is too large to capture the smaller rectangular areas with similar random forest predictions, and the region created by the quantile bins where $x'_1\in[-10,-5)$ and $x'_2\in[5,10)$ is too small to capture the rectangular region in the upper left corner of $x'_1\in[-10,-2.5]$ and $x'_2\in[0,10)$ where the random forest predictions are all approximately 1. The discrepancy between the quantile bin rectangles and the rectangular regions created by the random forest predictions highlights an issue with the LIME claim of faithfulness in this example that will lead to an issue in the interpretation in the explainer model discussed in Section \ref{step3}.

Before the simulated data is used to fit the explainer model, a transformation is applied to the features in the simulated data in an attempt to achieve a representation that will allow for an easy interpretation of the explainer model. We will refer to this as the \emph{interpretability transformation}. With the quantile bin simulation method, the interpretability transformation converts the generated features to binary variables based on whether an observation falls in the same bin as the prediction of interest or not. This transformation is what leads to the intervals used in the LIME explanation shown in Figure \ref{fig:sine-plot-poi}.

The transformed simulated data plot is shown in \autoref{fig:sine-plot-step1c}. The plot shows the simulated values of $x'_2$ versus $x'_1$ as in \autoref{fig:sine-plot-step1ab}, but they are overlaid by rectangles that represent the regions where observations share the same interpretability transformed values. The plot shows two intersecting strips where observations are in the same bin as the prediction of interest for either $x'_1$, $x'_2$, or both. With this transformation, the grid created by the four quantile bins is reduced to 4 categories in the case of two features (or 8 categories accounting for $x_3$).

Overlaying the simulated data with the interpretability transformed values highlights the simplification imposed by the transformation. The rectangle where the prediction of interest is located contains a wide range of random forest predictions from \Sexpr{sine_poi_perms %>% filter(x1num == 1, x2num == 1) %>% summarise(min(rfpred)) %>% round(2)} to \Sexpr{sine_poi_perms %>% filter(x1num == 1, x2num == 1) %>% summarise(max(rfpred)) %>% round(2)}, but the interpretability transformation groups all of these values into one category. While this transformation  provides easily understandable interpretations, it leads to an extreme over-simplification of the random forest model. This simplification may be one of the reasons underlying the low $R^2$ value associated with the final explainer model and provides further evidence against the LIME claim of faithfulness for this explainer model.

The other simulation methods available in \emph{lime} include quantile bins with a different number of bins, a specified number of equally spaced bins, a kernel density approximation, and a normal distribution approximation. Each of these simulation methods has a corresponding interpretability transformation. See Appendix \ref{lime} for additional information on these other methods. The plots created here are applicable to the other simulation methods.

\subsection{Explainer Model Fitting} \label{step2}

\begin{figure*}[!htp]
\centering
<<sine-plot-step2ab, out.width = '\\textwidth', fig.width = 8, fig.height = 3.25>>=

# Hex plot of the mean weights of the simulated values
step2a <- ggplot() +
  stat_summary_hex(data = sine_poi_perms,
             mapping = aes(x = x1,
                           y = x2,
                           z = weights),
             fun = mean,
             bins = 20) +
  geom_vline(xintercept = sine_poi_bounds %>% 
               filter(feature == "x1") %>% 
               select (lower, upper) %>% 
               as.numeric()) +
  geom_hline(yintercept = sine_poi_bounds %>% 
               filter(feature == "x2") %>% 
               select (lower, upper) %>% 
               as.numeric()) +
  geom_point(data = sine_poi %>%
               mutate(shape = "Prediction \nof Interest"),
             mapping = aes(x = x1, y = x2, shape = shape),
             fill = sinecolor_blue,
             size = 5,
             alpha = 0.8) +
  scale_fill_gradient(low = "grey90", high = "grey10") +
  scale_shape_manual(values = 23) +
  theme_bw(base_family = "Times", base_size = 10) +
  labs(x = TeX("x'_1"),
       y = TeX("x'_2"),
       shape = "",
       title = "Proximity Weights Plot",
       fill = "Weight") +
  guides(shape = guide_legend(order = 1)) + 
  theme(aspect.ratio = 1)

# Plot of features selected via all feture selection methods
step2b <- sine_poi_lime_default %>%
  slice(1) %>%
  select(fs, hw, lp, tree) %>%
  unnest(cols = c(fs, hw, lp, tree)) %>%
  gather(method, feature) %>%
  mutate(method = fct_recode(method,
                             "Feature \nSelection \n(default)" = "fs",
                             "Highest \nWeights" = "hw",
                             "Lasso \nPath" = "lp",
                             "Tree" = "tree"),
         feature = factor(feature, levels = c("x3", "x2", "x1"))) %>%
  ggplot(aes(x = method, y = feature, fill = feature)) +
  geom_tile() +
  scale_y_discrete(drop = FALSE) +
  theme_bw(base_family = "Times", base_size = 10) +
  labs(x = "Feature Selection Method",
       y = "Feature",
       fill = "Selected",
       title = "Feature Selection Comparison Plot") +
  scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) +
  guides(fill = guide_legend(reverse = TRUE)) + 
  theme(aspect.ratio = 1)

plot_grid(step2a, step2b, rel_widths = c(0.55, 0.45))
@
\caption{\kge{(Left) \emph{Proximity weights plot}.}\sout{Plots of the weight assignments and feature selection.} The plot \kge{is} \sout{on the left shows} a hex plot \kge{depicting the distribution} of the default \emph{lime} weights (Gower distances raised to the power of 1) assigned to the simulated data prior to the interpretability transformation. \kge{The color of a hexagon represents} \sout{Each hexagon contains} the average of the weights of the observations located within the hexagon. The location of the prediction of interest is \kge{indicated by} \sout{included as} the diamond shaped point. \kge{The black vertical and horizontal lines represent the interpretability transformation boundaries.} The plot shows that the weights increase as the observations approach the prediction of interest, but it is not clear if the region with the largest weights is small enough to provide a valid local interpretation. \sout{Note that the change in weights is not a smooth gradient, which is the result of the value of $x_3$ being taken into account in the calculation of the weight.} \kge{(Right) \emph{Feature selection comparison plot}.} The plot \sout{on the right} shows the features selected by the four feature selection methods in \emph{lime} for the prediction of interest from the \data. The methods produce consistent results since the features of $x_1$ and $x_2$ are chosen by all methods.}
\label{fig:sine-plot-step2ab}
\end{figure*}

\kge{The process of obtaining the explainer model in \emph{lime} involves assigning weights to the interpretability transformed simulated data based on proximity to the prediction of interest, performing feature selection to identify the features to include in the explainer model, and finally, fitting the explainer model. We visualize this process in a series of four plots: (a) \emph{proximity weights plot}, (b) \emph{feature selection comparison plot}, (c) \emph{explainer model prediction plot}, and (d) \emph{explainer model residual plot}. Examples of these plots with the \data \ prediction of interest are shown in Figures \ref{fig:sine-plot-step2ab} and \ref{fig:sine-plot-step2cd}.}

The proximity weights plot for the \data prediction of interest is shown on the left in \autoref{fig:sine-plot-step2ab}. By default, \emph{lime} computes the weights %\sout{for each of the observations in the simulated data}
based on the proximity of the simulated data features prior to the interpretability transformation to the prediction of interest using a Gower distance metric \citep{gower:1971} raised to an exponent of 1. %\kgc{Should I include more details about the Gower distance metric?} \hh{more details here might help with explaining what is going on in the figure below XXX}
The closer an observation is to the prediction of interest, the higher the assigned weight is. \autoref{fig:sine-plot-step2ab} shows a hexplot of the weights assigned to the simulated values from the \data \ for features $x_1$ and $x_2$ with the location of the prediction of interest included as the diamond shaped point. The color shading in each of the hexagons represents the average of the weights for observations located in the hexagon with darker shades representing larger weights. The black lines represent the interpretability transformation boundaries indicating the quantile bins that contain the prediction of interest.

\kgc{Can we talk about the interpretation of this figure? I made some adjustments, but I find this to be a difficult plot to talk about.} \hh{XXX It might become easier if you describe what you are personally looking for in this kind of plot. What would be a surprise, what would be something to react on?}
\sout{Weights are larger the closer an observation is to the prediction of interest, but \hh{interestingly}} \sout{the weights do not decrease in a \sout{smooth}} \hh{\sout{XXX smooth has a mathematical definition. I don't think you are using it that way. What exactly do you mean? decrease consistently in $x_1^2 + x_2^2$? Slow down and explain it precisely.}} \sout{gradient.} \hh{\sout{XXX some of these sentences are very long. They are more effective when shortened.}}, \sout{which is the result of the feature $x_3$ being included in the calculation of the weights.} 
The hexagons in \autoref{fig:sine-plot-step2ab} closer to the prediction of interest have darker shades than those further away, but the weights do not appear to create a tight local region around the prediction of interest in comparison to the ranges of $x_1$ and $x_2$. The darkest shades extend outside of the interpretability transformation region that contains the prediction of interest. This suggests a possible violation of the LIME claim of localness. However, determining whether the assumption of localness is met is difficult, because of a lack of a definition of a local region, and this plot does not include the response variable. The relationship between the response variable and the features would provide a better understanding of a local region that is both large enough for a practical interpretation and small enough to not oversimplify the pattern of the complex model. Since LIME does not account for the response variable in the computation of the weights, we chose to exclude it from our visualization to highlight the ambiguity in a local region. \kgc{I included this last sentence, because otherwise, the sentence before it suggests that we should really include the response variable in the visualization. I can't figure out a good way to include the response variable without the figure becoming too overwhelming.} \hh{sure, it sounds good}

\hh{XXX how do these plots survive a move to higher dimensions? Given that even in the sine example the weights don't seem to show a 2d relationship, I am doubtful.} \kgc{I don't really understand your comment here. Especially since I created visualizations of the weights in "higher dimensions" in the appendix (\autoref{fig:app-plot-step2a}).} \hh{I think this ties into what the purpose of the plots is - once that is clear, it's easier to determine how well the plots keep their purpose in higher dimensions.}

\hh{A point of criticism for LIME might also be that the weights do not regard importance of features, but are determined ahead of time. If weights were included in the modelling process in form of a parameter better local regions might be achievable.} \kgc{This is an interesting thought. However, would it be reasonable to perform feature selection without the weights? Then feature selection would be done without trying to account for the local region.}

After the weights are computed, feature selection is performed. \autoref{fig:sine-plot-step2ab} is the feature selection comparison plot for the \data \ example. \emph{lime} offers several ways to perform feature selection. If the user has requested 6 or less features be selected, \emph{lime} performs feature selection by first fitting a weighted ridge regression model with the complex model predictions from the simulated data as the response variable, the interpretability transformed simulated data features as the predictor variables, and the proximity measures as the weights. Then forward selection is used to select the features. The feature selection comparison plot includes the features selected by the default \emph{lime} method and three other methods to determine if the features selected are dependent on the method.
%\sout{used for the \data \ prediction of interest, we applied all four feature selection methods to the prediction of interest in the \data. for each of the methods.}

In the case of the \data \ prediction of interest, all methods selected features $x_1$ and $x_2$. This indicates that the methods are consistent in selecting the same features for the prediction of interest. If the selected features were not the same across methods, additional work may be required to determine which method should be used to return the LIME explanation. The application of LIME to the \data \ example will proceed with the default feature selection method of forward selection.

<<sine-perms-subset>>=
# Subset the simulated data to the region where the poi is located
sine_poi_region_perms <- sine_poi_perms %>%
  filter(x2 >= sine_poi_bounds %>% filter(feature == "x2") %>% pull(lower),
         x1 >= sine_poi_bounds %>% filter(feature == "x1") %>% pull(lower),
         x1 < sine_poi_bounds %>% filter(feature == "x1") %>% pull(upper))
@

\begin{figure*}[!htbp]
<<sine-plot-step2cd, out.width = '\\textwidth', fig.width = 8, fig.height = 3.25, warning = FALSE>>=

# Plot of the predictions in the four categories
step2c <- ggplot() +
  geom_rect(data = sine_exp_rect,
            mapping = aes(xmin = x1,
                          xmax = x2,
                          ymin = y1,
                          ymax = y2,
                          fill = empred)) +
    geom_point(data = sine_poi %>%
               mutate(shape = "Prediction \nof Interest",
                      exp_pred = sine_poi_lime_default$model_prediction[[1]]),
             mapping = aes(x = x1, y = x2, fill = exp_pred, shape = shape),
             size = 5,
             alpha = 0.8) +
  xlim(-10, 10) +
  ylim(-10, 10) +
  scale_shape_manual(values = 23) +
  scale_fill_gradient2(low = sinecolor_red,
                       mid = '#f7f7f7',
                       high = sinecolor_blue,
                       midpoint = 0.5,
                       limits = c(0, 1)) +
  guides(shape = guide_legend(order = 1)) +
  theme_bw(base_family = "Times", base_size = 10) +
  labs(x = TeX("x_1"),
       y = TeX("x_2"),
       fill = "Explainer \nModel \nPrediction \nfor 'blue'",
       title = "Explainer Model Prediction Plot",
       shape = "")

# Calculate the residuals from the explainer model
y <- sine_poi_perms$rfpred
sine_poi_explainer <-
  function(x1, x2) sine_b0 + (sine_b1 * x1) + (sine_b2 * x2)
sine_poi_perms <- sine_poi_perms %>%
  mutate(exppred = sine_poi_explainer(x1num, x2num)) %>%
  mutate(resid = exppred - rfpred)

# Create the residual plot
step2d <- ggplot(sine_poi_perms, aes(x = exppred, y = resid)) +
  geom_jitter(alpha = 0.5, width = 0.02) +
  geom_hline(yintercept = 0) +
  theme_bw(base_family = "Times", base_size = 10) +
  labs(x = "Explainer Model Predictions",
       y = "Residuals",
       title = "Explainer Model Residual Plot")

plot_grid(step2c, step2d, rel_widths = c(0.51, 0.49))
@
\caption{(Left) \emph{Explainer model prediction plot}. The explainer model divides the feature space associated with $x_1$ and $x_2$ into four categories. This plot shows the four categories and the prediction from the explainer model associated with each category. The division of the feature space into four prediction regions  is clearly a major simplification of the random forest model. (Right) \emph{Explainer model residual plot}. The plot shows the residuals versus the predicted values  from the \kge{prediction of interest} explainer model. \hh{XXX Jitter is not added - points are jittered} Jitter has been added to the x-direction. There is an upward trend in the residuals as the explainer model predictions increase, which suggests a violation of the linearity assumption of the ridge regression model.}
\label{fig:sine-plot-step2cd}
\end{figure*}

Finally, the explainer model is fit. \emph{lime} uses a weighted ridge regression model as the explainer model. Similar to the feature selection step, the complex model predictions from the simulated data are the response variability and the proximity measures are the weights, but only the interpretability transformed features identified during feature selection are used as the predictor variables. In the case of the \data, the explainer model predictor variables are the interpretability transformed versions of $x_1$ and $x_2$. The predictions from the explainer model associated with the \data \ prediction of interest are visualized in the explainer model prediction plot shown in \autoref{fig:sine-plot-step2cd} \kge{(left)}. Recall that the interpretability transformed features are binary variables. In the ridge regression model, the transformed features act as indicator variables for whether an observation falls in the same quantile bin. Since the \data \ explainer model contains 2 features, the explainer model prediction plot shows four colored regions indicating the four possible predictions produced by the model. In general, the \emph{lime} explainer model would produce $2^k$ prediction regions for $k$ indicator variables. \hh{XXX generally it would be $2^k$ for $k$ indicator functions - this is very small until it becomes unfeasible. So generally, it is doubtful that it is ever actually useful. XXX} \kgc{I'm not quite sure what you are getting at here: the visualizations or the explainer model in general? Is the last sentence I added enough to address your comment?} \hh{We can talk about this - my comment is again along the lines of bins being too large and too small at the same time. to only have 2 predictions for each variable is ridiculously simple until the number of features is large and $2^k$ becomes computationally unfeasible to manage.}

%\sout{The explainer model predictions mimic the random forest prediction.} \hh{\sout{XXX given that the random forest predictions are used, that is what the explainer model is supposed to do? You could put a bit more opinion in this paragraph.  XXX}}

%\sout{For example, the region where $5\le x_2$ has a prediction of approximately 0.8, which is reasonable considering that many of the observations from the simulated data in this region have a random forest prediction between 0.75 and 1 as seen in} \autoref{fig:sine-plot-step1ab}. \sout{However, by providing only one prediction,}

Compared to the relationship between the random forest predictions and the features of $x_1$ and $x_2$ shown in Figure \ref{fig:sine-plot-step1ab}, the explainer model is a major simplification of the random forest model. Consider the region where the prediction of interest is located. The explainer model provides a single prediction of \Sexpr{round(sine_poi_lime_default$model_prediction[[1]],2)} for the entire region as a summary of random forest predictions ranging from \Sexpr{round(min(sine_poi_region_perms$rfpred), 2)} to \Sexpr{round(max(sine_poi_region_perms$rfpred), 2)} with a mean and standard deviation \Sexpr{round(mean(sine_poi_region_perms$rfpred), 2)} and \Sexpr{round(sd(sine_poi_region_perms$rfpred), 2)}, respectively. The random forest prediction for the prediction of interest is \Sexpr{round(sine_poi$rfprob_blue,2)}. Consider that the mean prediction from the random forest (\Sexpr{round(mean(sine_poi_region_perms$rfpred), 2)}) agrees with the explainer model prediction (\Sexpr{round(sine_poi_lime_default$model_prediction[[1]],2)}) as is expected due to the nature of the explainer model used, but the random forest prediction associated with the case of interest (\Sexpr{round(sine_poi$rfprob_blue,2)}) is about a half \sout{1} standard deviation away from the mean. \kgc{After reading the previous sentence again, I'm wondering if the next sentence is too dramatic. (Especially since I had made a mistake with the standard deviation.)} \hh{XXX how about we put a 'suggest' into it?} The difference between the explainer model and random forest predictions for the case of interest along with the amount of variability in the random forest predictions in this region makes it clear that the explainer model is simplifying the random forest model too much and violating the assumption of faithfulness.

%\hh{\sout{avoid these parenthetic intros ... people listen/reader see the beginning of a sentence. Put emphasis on the important ideas you want to get across.}} \sout{With the explainer model fit, we are able to assess the linearity assumption. To do this, we consider a residual plot shown in} \autoref{fig:sine-plot-step2cd} (right).

In order to assess the claim of linearity, we use one of the most basic diagnostics in a statistician's tool box and draw a residual plot for the explainer model. The right plot in \autoref{fig:sine-plot-step2cd} shows residuals on the y axis and explainer model predictions on the x axis. \hh{The points along the $x$ axes have been jittered} to \hh{ease the effect of} the over-plotted points in the visualization. The discretization of the feature space to four categories can again be see in this plot. There is a clear increasing trend in the residuals as the explainer model predictions increase. \hh{XXX the `clear' is repeated} This \kge{is a clear of} \sout{suggests} \hh{\sout{suggests is very nice to lime ... clear indication?}} a violation of the linearity assumption with the ridge regression model.

\kgc{Do you think there is anything else that should be said about the figures in this section? It feels like we need something else, but I'm not quite sure what.}\hh{I'm not sure what else there could be said about these visualizations in particular, but a paragraph on limitations/general use would be good.}

\emph{lime} offers several other options for fitting the explainer model. Instead of a Gower distance to compute the weights, an exponential kernel can be used. As touched on in Figure \ref{fig:sine-plot-step2ab}, \emph{lime} offers the methods of highest weights, LASSO path, and tree for feature selection, and a different default method is used if more that 6 features are specified to be selected. More details about these options are included in Appendix \ref{lime}.

\begin{figure*}[!htp]
<<sine-plot-step3ab, out.width = '\\textwidth', fig.width = 10, fig.height = 4, warning = FALSE>>=

# My lime explanation plot
step3a <- sine_poi_lime_default %>% 
  select(feature_weight, feature_desc) %>%
  bind_rows(data.frame(feature_weight = 
                         sine_poi_lime_default$model_intercept[1],
                       feature_desc = "Intercept")) %>%
  mutate(feature_magnitude = abs(feature_weight)) %>%
  ggplot(aes(x = feature_desc, 
             y = feature_magnitude,
             fill = feature_weight)) + 
  geom_col() + 
  coord_flip() + 
  labs(y = "Explainer Model Coefficient Magnitude",
       x = "Explainer Model Feature",
       fill = "Explainer \nModel \nCoefficient \nValue",
       title = "Explanation Plot") + 
  scale_fill_gradient2(low = sinecolor_red,
                        mid = '#f7f7f7',
                        high = sinecolor_blue,
                        midpoint = 0,
                        limits = c(-1, 1)) +
  theme_bw(base_family = "Times", base_size = 10)

# My plot of lime explanation boundaries
step3b <- ggplot() +
  geom_point(data = sine_poi_perms,
             mapping = aes(x = x1,
                           y = x2,
                           color = rfpred,
                           size = weights),
             alpha = 0.8,
             shape = 20) +
  scale_size(range = c(0.1, 3)) +
  geom_rect(data = sine_poi_bounds %>% filter(feature == "x1"),
            mapping = aes(xmin = lower,
                          xmax = upper,
                          ymin = -Inf,
                          ymax = Inf),
            alpha = 0.25,
            fill = "grey90",
            color = "firebrick") +
  geom_rect(data = sine_poi_bounds %>% 
              filter(feature == "x2"),
            mapping = aes(xmin = -Inf,
                          xmax = Inf,
                          ymin = lower,
                          ymax = upper,
                          color = coef),
            alpha = 0.25,
            fill = "grey90",
            color = "steelblue") +
  geom_point(data = sine_poi %>%
               mutate(shape = "Prediction \nof Interest"),
             mapping = aes(x = x1, y = x2, shape = shape, fill = rfprob_blue),
             size = 7,
             alpha = 0.8) +
  scale_shape_manual(values = 23) +
  scale_fill_gradient2(low = sinecolor_red,
                        mid = '#f7f7f7',
                        high = sinecolor_blue,
                        midpoint = 0.5,
                        limits = c(0, 1)) +
  scale_color_gradient2(low = sinecolor_red,
                        mid = '#f7f7f7',
                        high = sinecolor_blue,
                        midpoint = 0.5,
                        limits = c(0, 1)) +
  theme_bw(base_family = "Times", base_size = 10) +
  labs(x = TeX("x'_1"),
       y = TeX("x'_2"),
       size = "Weight",
       shape = "",
       fill = "Random \nForest \nProbability \nfor 'blue'",
       color = "Random \nForest \nProbability \nfor 'blue'",
       title = "Complex and Explainer Model Comparison Plot") + 
  guides(shape = guide_legend(order = 1)) + 
  theme(aspect.ratio = 1)

# # My plot of lime explanation boundaries
# zoomedin <- ggplot() +
#   geom_rect(data = sine_poi_bounds %>% filter(feature == "x1"),
#             mapping = aes(xmin = lower,
#                           xmax = upper,
#                           ymin = -Inf,
#                           ymax = Inf),
#             alpha = 0.25,
#             fill = NA,
#             color = "firebrick") +
#   geom_rect(data = sine_poi_bounds %>% filter(feature == "x2"),
#             mapping = aes(xmin = -Inf,
#                           xmax = Inf,
#                           ymin = lower,
#                           ymax = upper),
#             alpha = 0.25,
#             fill = NA,
#             color = "steelblue") +
#   geom_point(data = sine_poi_region_perms,
#              mapping = aes(x = x1,
#                            y = x2,
#                            color = rfpred,
#                            size = weights),
#              alpha = 0.8) +
#   geom_point(data = sine_poi %>%
#                mutate(shape = "Prediction \nof Interest"),
#              mapping = aes(x = x1, y = x2, fill = rfprob_blue, shape = shape),
#              size = 7,
#              alpha = 0.8) +
#   scale_size(range = c(1, 3)) +
#   scale_shape_manual(values = 23) +
#   scale_fill_gradient2(low = sinecolor_red,
#                         mid = '#f7f7f7',
#                         high = sinecolor_blue,
#                         midpoint = 0.5,
#                         limits = c(0, 1)) +
#   scale_color_gradient2(low = sinecolor_red,
#                         mid = '#f7f7f7',
#                         high = sinecolor_blue,
#                         midpoint = 0.5,
#                         limits = c(0, 1)) +
#   theme_bw(base_family = "Times", base_size = 10) +
#   labs(x = TeX("x'_1"),
#        y = TeX("x'_2"),
#        color = "Random \nForest \nProbability \nfor 'blue'",
#        fill = "Random \nForest \nProbability \nfor 'blue'",
#        fill = "",
#        size = "Weight",
#        shape = "") +
#   guides(shape = guide_legend(order = 1)) +
#   xlim(sine_poi_bounds$lower[2], sine_poi_bounds$upper[2]) +
#   ylim(sine_poi_bounds$lower[1], max(sine_poi_perms$x2))
# 
# # Legend steps
# full_weight_legend <- get_legend(full)
# full_noleg <- full + theme(legend.position = "none")
# sine_exp_legend <- get_legend(zoomedin + guides(size = FALSE))
# zoomedin_weight_legend <- get_legend(zoomedin +
#   guides(color = FALSE, fill = FALSE, shape = FALSE) +
#   theme(legend.position = "bottom"))
# zoomedin_noleg <- zoomedin + theme(legend.position = "none")
# blank <- ggplot() + theme_void()
#
# # Join plots and legends
# step3a_plots <- plot_grid(full_noleg, zoomedin_noleg, sine_exp_legend,
#           nrow = 1,
#           rel_widths = c(0.43, 0.42, 0.15))
# step3a_weights <- plot_grid(full_weight_legend, zoomedin_weight_legend, blank,
#           nrow = 1,
#           rel_widths = c(0.425, 0.425, 0.15))
# plot_grid(step3a_plots, step3a_weights,
#           nrow = 2,
#           rel_heights = c(0.925, 0.075))

plot_grid(step3a, step3b)
@
\caption{\emph{Explanation plot} (left) \hh{I very much like the explanation plot. but is there a way to get rid of the actual values of the features for the interval and describe instead what it is? 2nd quartile, 3rd quartile? Visually, if the plots don't have the same height you would emphasize that the left and the right plot show different things. You could e.g. move the legend on the left side underneath the bars. That squishes the bars to a different size from the quantiles on the right.} and \emph{complex and explainer model comparison plot} (right). The explanation plot depicts the estimated parameters from the explainer model. The lengths of the bars represent the absolute values of the coefficients, and the colors of the bars represent the coefficient values. Since the magnitude of the coefficient associated with $x_2$ is longer than that of $x_1$, the explanation suggests that $x_2$ has more of an effect on the random forest prediction of interest than $x_1$ does. The explainer model comparison plot shows the simulated data colored by the random forest probabilities and sized by the assigned LIME weights. The prediction of interest is shown as the diamond shaped point. The quantile bins associated with $x_1$ and $x_2$ are depicted by the solid lines. The color of the line indicates whether the explainer model supports a prediction of 'blue' (blue line) or supports a prediction of 'red' (red lines). This figure shows that the quantile bins are not flexible enough to capture the relationship between the random forest predictions and the $x_1$ and $x_2$ values.}
\label{fig:sine-plot-step3ab}
\end{figure*}

\subsection{Explainer Model Interpretation} \label{step3}

\kgc{I made a handful of adjustments to this section including switching out the zoomed in plot for my preferred version of the \emph{lime} plot of the explanation. I also tried to adjust the interpretations based on your comments. See what you think...}

\hh{XXX one thing that the reader should be reminded of is that LIME is actually fitting an explainer model for each observation of interest, i.e. we have not just an explainer model $g$ but a whole family of models. In the example we have 16 possible structures, one of which you are investigating more closely.} \kgc{I'm not sure that we need to remind them of this here. The whole point of this section is that we are focusing on the explainer model for one observation. I'm hoping by this point, they have it locked in their mind that all of this section is focused on one explanation. If not, maybe we need to go back and make it more clear through it. I it would be better to include this reminder at the start of the next section. That could be a really nice was to set up the scenario of diagnostic plots for a set of explanations.} 
\hh{I can see your point, but I still think that it is important to keep it in the back of the readers mind that an explainer model is only valid for a single prediction and any interpretation needs to be repeated. }

The main idea behind LIME, is to interpret the coefficients of the explainer model  to identify the feature(s) of importance in the prediction of interest. To aid in the interpretation and ultimately the assessment of the explainer model, we visualize the coefficients from the explainer model and alongside a visualization of the complex model predictions with the explainer model. We will refer to these plots as (a) the \emph{explanation plot} and (b) the \emph{complex and explainer model comparison plot}, respectively. Examples of these plots with the explanation for the \data \ prediction of interest are included in Figure \ref{fig:sine-plot-step3ab}.

The plot on the left in Figure \ref{fig:sine-plot-step3ab} is the explanation plot for the prediction of interest from the \data. This plot is an extension of the visualization of the LIME explanation from the \emph{lime} R package shown in Figure \ref{fig:sine-plot-poi}. Similar to the plot from \emph{lime}, we include the coefficients from the explainer model for the interpretability transformed features of $x_1$ and $x_2$, but we depict the magnitude of the coefficients by the length of the bars as opposed to the coefficient value for ease of comparison between the lengths of the bars. We represent the coefficient value by the colors of the bar, so that it is still possible to understand which . We also include the intercept to remind the viewer of its role in the ridge regression model. The axis labels we use are meant to be more informative than those of the \emph{lime} plot such as "explainer model coefficient magnitude" as opposed to "weight". \hh{XXX I like the changed plots!}

We can use the explanation plot to interpret the explainer model in terms of a ridge regression coefficients. The intercept, \Sexpr{round(sine_poi_lime_default$model_intercept[1], 2)}, is the predicted random forest probability for observations that are not in the same $x_1$ or $x_2$ quantile bins as the prediction of interest. The coefficients are interpreted as the amount that the average random forest probability increases/decreases if an observation falls in the same bin as the prediction of interest. In this example, the average random forest probability that an observation is in category 'blue' increases by \Sexpr{sine_poi_lime_default %>% filter(feature == "x2") %>% select(feature_weight) %>% round(2)} if an observation falls in the same $x_2$ quantile bin as the prediction of interest (i.e. the third quantile), and the average random forest probability that an observation is in category 'blue' decreases by \Sexpr{sine_poi_lime_default %>% filter(feature == "x1") %>% select(feature_weight) %>% round(2) %>% abs()} if an observation falls in the same $x_1$ quantile bin as the prediction of interest (i.e. the fourth quantile). Because the magnitude of the coefficient associated with $x_2$ is larger, it indicates that $x_2$ affects the random forest prediction more than $x_1$. Note that if a different simulation method is used when applying LIME, the interpretation of the explainer model can change. See Appendix \ref{lime} for more details.

%\sout{\hh{In a} ridge regression model, the interpretation of the coefficients  depends on the interpretability transformation applied.} \hh{\sout{XXX something went wrong in the previous sentence ... of the transformation?}} \hh{\sout{XXX this would be a good place to tie in the example.}} \sout{In the case of bin based samples, $z'_{j,i}=1$ if feature $j$ is in the same bin as $x^*_j$.} \sout{Thus, the coefficient $\hat{\beta}_j$ can be interpreted as the amount that the response probability increases/decreases if an observation falls in the same bin as $x^*_j$. Thus, the magnitude of the coefficient \hh{XXX is supposed to describe}  the importance of the feature. \hh{XXX write this out in words} That is, $\left|\hat{\beta}_j\right|>\left|\hat{\beta}_{j'}\right|$ indicates that feature $j$ has more effect on the prediction than feature $j'$. \hh{XXX This can go into the appendix?} The magnitudes of the coefficients are used to order the $P$ features in terms of importance in the prediction associated with $x^*$.}

%\sout{In the case of the prediction of interest from the \data, we can interpret the explainer model as follows. \hh{XXX Instead of writing out numbers, I would suggest to describe the bins in words lowest quartile, third, second, top quartile, ...  XXX} For an observation that has a value of $x_1$ that is greater than \Sexpr{round(x1_lower, 1)} and less than or equal to \Sexpr{round(x1_upper, 1)}, the probability that the observation is predicted to be in category blue decreases by \Sexpr{abs(round(sine_b1, 1))}, and if an observation has a value of $x_2$ greater than \Sexpr{round(x2_lower, 1)}, the probability that the observation is predicted to be in category blue increases by \Sexpr{abs(round(sine_b2, 1))}. Since the magnitude of the coefficient associated with $x_2$ is larger, it indicates that $x_2$ plays a more important role of the random forest prediction than $x_1$. The figure produced by \emph{lime} shown in} \autoref{fig:sine-plot-poi} \sout{shows a visualization of the coefficients from the explainer model to provide a high level visualization of the LIME explanation.}

The plot on the right of Figure \ref{fig:sine-plot-step3ab} is the complex and explainer model comparison plot for the prediction of interest from the \data. This figure shows the relationship between the random forest model and the LIME explainer model. The random forest model is represented by the simulated values of $x'_2$ versus $x'_1$ colored by the random forest predictions. The explainer model is represented by the solid horizontal and vertical line identify the boundaries of the quantiles that contain the prediction of interest. The color of the lines represents whether the coefficient of the corresponding indicator variable in the explainer model supports a random forest prediction of 'blue' (blue lines) or not (red lines). Additionally, the size of the simulated data points represents the proximity weight used to fit the ridge regression explainer model. The prediction of interest is represented by the diamond shaped point.

%\hh{\sout{XXX tighten by focusing on the results rather than the process}}
%To provide insight into this explainer model produced by \emph{lime}, we created an additional visualization that incorporates the simulated data
%\sout{To provide a direct comparison of the explanation produced by the explainer model with the complex model. The plot on the left in} \autoref{fig:sine-plot-step3ab} \sout{is a plot of the simulated values of $x'_2$ versus $x'_1$ colored by the associated random forest probability and sized by weight \hh{XXX define weight more precisely }.  This part \hh{do you mean the weights by 'this part'? } of the visualization represents the complex model. The prediction of interest is shown by the diamond shaped point. The explainer model is represented by the red and blue solid lines \hh{XXX how do you come up with the colors for the lines?}, which are the bins from the ridge regression model associated with $x'_1$ and $x'_2$. A close up of the intersection of the bins is included as the plot on the right.}

%\sout{These figures show the relationship between the random forest model and the LIME explainer model.} 
By juxtaposing the random forest predictions and the explainer model boundaries, we are able to assess the faithfulness and localness of the explainer model. First consider the claim of localness. The weights remain relatively high  outside of the intersection of the two quantile bins suggesting that the LIME explanation is highly influenced by points outside of the bin containing the prediction of interest. While it is still difficult to say whether or not the claim of localness has been violated, it is possible to say that the weights assigned to the simulated data do not agree with the local region assigned by the intersection of the quantile bins. Next, let us consider the claim of faithfulness.

%\sout{The $x_2$ bin contains a majority of random forest probabilities greater than 0.5, whereas the $x_1$ bin contains mostly random forest probabilities less than 0.5.}
Within the intersection of the $x'_1$ and $x'_2$ quantile bins, there appears to be more random forest probabilities above 0.5. This indicates why the magnitude of the coefficient associated with $x_2$ is larger than that of $x_1$. However, the pattern of the random forest predictions in this plot suggest that a better explanations for this prediction exist. One example of a better explanation would be to say that the prediction of interest received a random forest prediction greater than 0.5 since the observation of interest falls in the region where $x_1$ is less than 2.5 and $x_2$ is greater 4.5. Another more localized explanation would be to say that  the region around the prediction of interest shows that observations with $-0.3 < x_1 <= 2.5$ and $4.8 < x_2 <= 8.75$ are all assigned probabilities greater than 0.5. The procedure implemented by LIME is not flexible enough to capture either of these explanations. %\sout{The LIME algorithm overlooked this region, which provides a more detailed explanation of the prediction made by the random forest for the case of interest. This explainer model} \hh{\sout{is too simplistic to meet the criteria of faithfulness or localness.}}

The visualizations within this section have repeatedly shown issues with a definition of locality and an oversimplification of the random forest model. LIME does provide an explanation for the prediction of interest, which makes sense based on the quantile bins used. However, the visualization of the complex and explainer model comparison plot solidifies the understanding that better explanations for the prediction of interest exist. \kgc{What do you think of this conclusion? I'd like to neatly wrap up the procedure visualizations in some way like this, but I'm not quite sure what to say.}\hh{that sounds good}

\subsection{\kge{Visualizations in Higher Dimensions}} \label{limitations}

\kgc{Help! I don't know how much information to include here. Right now I have it down to one paragraph...}

\hh{By tightening the work I did not mean to cut paragraphs or ideas. The ideas are good, but they need tighter, in the sense of sharper, arguments. }

\kgc{Need to work this in}: \hh{In terms of limitations of the visualizations: first two features span the x and y axis, additional features can be used for faceting. four features is completely feasible, beyond that the visualization might not work as well. The number of bins should be in the single digits. A large number of small multiples \citep{Becker:1996gy} needs a strong signal in the data to be effective - otherwise the visualization might be affected by change blindness \citep{simonsChangeBlindness1997, review19}. }

The \data \ provide a \kge{neat} \kge{very clean} example of how to use the proposed visualizations to assess a single LIME explanation \kge{with two features. Once the number of features is greater than 3, adjustments will need to be made to the plots. In this case, multiple plots will be required to visualize the majority of the steps in the LIME procedure. Reasonable extensions would be scatterplot matrices or the use of faceting. \hh{XXX this is too vague: when do you use scatterplot matrices, what is the advantage of faceting. Make your solutions more concrete by discussing them as well as their limitations. }
In the case of faceting, the} \hh{first two features} \kge{can} \hh{span the x and y axis,} \kge{and} \hh{additional features can be} \kge{used as the facets.} We have included some examples of such plots in Appendix \ref{scatter-plots} that take into the feature $x_3$ from the \data \ in the visualization of the LIME procedure.

\hh{\sout{In terms of limitations of the visualizations: first two features span the x and y axis, additional features can be used for faceting. four features is completely feasible, beyond that the visualization might not work as well. The number of bins should be in the single digits. A large number of small multiples (reference to Cleveland?) needs a strong signal in the data to be effective - otherwise the visualization might be affected by change blindness} \citet{simons:1997, vanderplas:2020}.}

\hh{Both large number of observations and large number of features make visual assessments harder:} \kgc{I've decided to not discuss a large amount of data, because that really isn't a problem due to the size of the simulated dataset being chosen by the user, and there is not a need to go above 5000. Whereas, it is reasonable to expect that a user may select more than two features.} \hh{That the size of the data is chosen by the user is actually a good point to make. }

\hh{the number of features can also be controlled by the user - lime is interested in a small number of features, as earlier mentioned, using faceting or scatterplot matrices we are able to deal with high single digits, low double digits of features. The limiting factors are screen space and cognitive load. }
\hh{XXX the ideas are good, but tighten the paragraphs XXX}

\sout{In situations with large amounts of data, it may become difficult to see the trends if the training or testing data due to over plotting. However, consider that the number of observations in the simulated data is chosen by the user, which allows the user to select a number that is large enough to get a visual of the full range of the observed data without running into issues of over plotting.}

\sout{Another possibly problematic situation is when it is of interest to include more than two features in the LIME explanation. In this situation, multiple plots will be required to visualize the LIME procedure, and if the number of features is really large, the number of plots may become too large to interpret well. However, if too many \hh{XXX what is too many? make this less abstract and give concrete suggestions on how to go beyond two dimensions.} features are chosen to be included in the LIME explanation, the explanation may no longer interpretable. It seems reasonable that the number of features to focus on in an explanation should be low enough that scatter plot matrices of the \sout{our} \hh{XXX not 'our' - that creates boundaries. you want the readers to use these plots as well.} diagnostic plots could be created.} \kgc{I decided I also didn't want to get into the discuss of "too many" features here.}

\section{Visualizations of a Set of LIME Explanations} \label{set-visuals}

The previous section visualized a LIME explanation for one prediction of interest. \hh{XX also to understand the model explainer.} In practice, it will often be of interest to provide explanations for more than one prediction. While visualizations of the LIME procedure for each explanation may provide insight, the creation of a series of visualizations for each prediction explanation may not be feasible. \hh{XXX more precision: we can create the visualizations, but looking at them individually is not generally going to help with a summary.} In this section, we visualize LIME explanations for a set of predictions of interest.
\sout{Our} visualizations consider the explanations from two viewpoints. \hh{XXX focus on results, not process. } \sout{First, we create} visualizations of the explanations to understand the pattern of the explanations across the set of predictions (\autoref{understand-set}).
Second, we use visualizations to assess the quality of the explanations by comparing the explainer model predictions to the complex model predictions (\autoref{assess-set}). Again, we use the \data \ to demonstrate our visualizations. \hh{In all of these diagnostics default settings of LIME were applied to produce explanations.}
%We applied LIME using the default setting in \emph{lime} to each of the observations in the test set.

\begin{figure*}[!htbp]
<<sine-plot-selected-features, out.width = "\\textwidth", fig.width = 8, fig.height = 3.25>>=

# Determining order for cases based on group explanations
sine_lime_default_case_order <- sine_lime_default %>%
  select(case, feature, feature_desc) %>%
  spread(key = feature, value = feature_desc) %>%
  mutate(x1 = factor(x1, levels = c("x1 <= -4.884",
                                    "-4.884 < x1 <= -0.302",
                                    "-0.302 < x1 <= 4.844",
                                    "4.844 < x1")),
         x2 = factor(x2, levels = c("x2 <= -4.681",
                                    "-4.681 < x2 <= -0.283",
                                    "-0.283 < x2 <= 4.834",
                                    "4.834 < x2"))) %>%
  arrange(x1, x2, case)

# Plot of all explanations from the default and kernel density cases
sine_lime_default %>%
  mutate(case = factor(case, levels = sine_lime_default_case_order$case),
         feature_desc = factor(feature_desc,
                               levels = c("x1 <= -4.884",
                                    "-4.884 < x1 <= -0.302",
                                    "-0.302 < x1 <= 4.844",
                                    "4.844 < x1",
                                    "x2 <= -4.681",
                                    "-4.681 < x2 <= -0.283",
                                    "-0.283 < x2 <= 4.834",
                                    "4.834 < x2",
                                    "x1", "x2")),
         sim_method = factor(sim_method,
                             levels = c("quantile_bins", "kernel_density")),
         sim_method = fct_recode(sim_method,
                                 "Four Quantile Bins" = "quantile_bins",
                                 "Kernel Density" = "kernel_density")) %>%
  ggplot(aes(x = case,
             y = feature_desc,
             fill = feature_weight,
             color = feature_weight)) +
  geom_tile() +
  facet_grid(feature ~ ., scales = "free", space = "free") +
  scale_fill_gradient2(low = 'firebrick',
                       mid = '#f7f7f7',
                       high = 'steelblue') +
  scale_color_gradient2(low = 'firebrick',
                        mid = '#f7f7f7',
                        high = 'steelblue') +
  theme_bw(base_family = "Times", base_size = 10) +
  theme(axis.text.x = element_blank()) +
  labs(x = "Case",
       y = "Feature",
       fill = "Feature \nWeight",
       color = "Feature \nWeight")

@
\caption{Heatmap of the ridge regression coefficients from the LIME explanations for each of the cases in the \data \ test set for the application of LIME with 4 quantile bins. This figure is an extension of a plot available in the \emph{lime} R package. The features selected by LIME are on the y-axis (faceted by the untransformed feature), and the cases are represented by the columns on the x-axis. The colors represent the ridge regression coefficients (feature weights). The cases are ordered so that cases within the same $x_1$ and $x_2$ are grouped. This highlights the 16 distinct groups of explanations that LIME produces with the 4 quantile bins simulation method.}
\label{fig:sine-plot-selected-features}
\end{figure*}

\subsection{Overview of Explanations} \label{understand-set}

When LIME is applied to a set of predictions, it is of interest to understand how the explanations vary across the set of predictions. Since LIME is assumed to produce local explanations, it would be expected that the explanations will vary depending on an observation's location in the feature space. However, it is possible that the same features could be the most influential in the predictions across the entire feature space, which would lead to the same features selected by LIME for all cases in the set of predictions. Visualizations incorporating all explanations provide insight into how the features driving predictions by the complex model change across the features space.

\autoref{fig:sine-plot-selected-features} shows an overview of the LIME explanations from the \data \ test set. The figure is an extension of a plot available from \emph{lime} that depicts the ridge regression coefficients associated with the features chosen by LIME.\hh{You are very generous to call your plot an extension of figure 4. There are similarities - describe them. That is going to make it more obvious that your plot is similar to Figure 4, but only in the sense that the same information is used.}

The features selected by LIME are plotted on the y-axis. Note that these are written as bins due to the discretization of the features, and they have been faceted by \hh{feature}. %whether they correspond to $x_1$ or $x_2$.
Each of the columns in the plot refers to a\hh{n individual} case in the testing dataset. Each case has two corresponding colored cells, which indicates the two features selected by LIME as important. \hh{Similar to figure 4 the color hue represents support for one of the two outcomes.} The \hh{intensity of the} color of the cell represents the value of the coefficient from the ridge regression associated with the feature (referred to as the feature weight in the figure to mimic the terminology used by \emph{lime}). Cases that are located within the same $x_1$ and $x_2$ bin are grouped together. \hh{This ordering visually emphasizes that} There are 16 = $k^2$ groups resulting from \hh{binning} features into $k=4$ quantile bins as discussed in \autoref{procedure}.

The plot shows that only features associated with $x_1$ and $x_2$ were selected by LIME. This is as \sout{hoped} \hh{expected} since $x_3$ is random noise and should not play an important role in prediction. There is variability in the explanations across the cases, but within each of the 16 bin categories, the ridge regression coefficients vary only slightly. The variability within an intersection of $x_1$ and $x_2$ bins is due to the randomness in the datasets simulated for each prediction of interest and the different weights used in the ridge regression model based on the location of the prediction of interest. However, in a practical sense, the explainer models provide the same explanations for predictions within the same $x_1$ and $x_2$ bin.

\hh{XXX I know what you mean by '$x_1$ and $x_2$ bin' - could you give this a name and refer to that? It sounds a bit clunky}

\begin{figure*}[!htbp]
<<sine-plot-agg-exp, warning = FALSE, out.width = '\\textwidth', fig.width = 10, fig.height = 3.25>>=

# Compute the coef averages in each bin
mean_coefs <- sine_lime_default %>%
  select(case, feature, feature_weight) %>%
  spread(feature, feature_weight) %>%
  rename("x1_coef" = "x1", "x2_coef" = "x2") %>%
  full_join(sine_lime_default %>%
              select(case, feature, feature_desc) %>%
              spread(feature, feature_desc),
            by = "case") %>%
  group_by(x1, x2) %>%
  summarise(mean_coef_x1 = mean(x1_coef),
            mean_coef_x2 = mean(x2_coef)) %>%
  ungroup() %>%
  separate(x1, c("x1_other", "x1_upper"), sep = " <= ") %>%
  separate(x1_other, c("x1_almost_lower", "x1_other"), sep = "x1") %>%
  select(-x1_other) %>%
  separate(x1_almost_lower, c("x1_lower", "x1_other"), sep = " <") %>%
  select(-x1_other) %>%
  separate(x2, c("x2_other", "x2_upper"), sep = " <= ") %>%
  separate(x2_other, c("x2_almost_lower", "x2_other"), sep = "x2") %>%
  select(-x2_other) %>%
  separate(x2_almost_lower, c("x2_lower", "x2_other"), sep = " <") %>%
  select(-x2_other) %>%
  mutate(x1_lower = ifelse(x1_lower == "", "-Inf", x1_lower),
         x1_upper = ifelse(is.na(x1_upper), "Inf", x1_upper),
         x2_lower = ifelse(x2_lower == "", "-Inf", x2_lower),
         x2_upper = ifelse(is.na(x2_upper), "Inf", x2_upper)) %>%
  mutate_at(.vars = c("x1_lower", "x1_upper",
                      "x2_lower", "x2_upper"),
            .funs = as.numeric) %>%
  arrange(x1_lower)

# Compute the average of beta1 + beta2 in each bin
mean_coefs_added <- sine_lime_default %>%
  select(case, feature, feature_weight) %>%
  spread(feature, feature_weight) %>%
  mutate(coef_x1_plus_x2 = x1 + x2) %>%
  select(-x1, -x2) %>%
  full_join(sine_lime_default %>%
              select(case, feature, feature_desc) %>%
              spread(feature, feature_desc),
            by = "case") %>%
  group_by(x1, x2) %>%
  summarise(mean_coef_x1_plus_x2 = mean(coef_x1_plus_x2)) %>%
  ungroup() %>%
  separate(x1, c("x1_other", "x1_upper"), sep = " <= ") %>%
  separate(x1_other, c("x1_almost_lower", "x1_other"), sep = "x1") %>%
  select(-x1_other) %>%
  separate(x1_almost_lower, c("x1_lower", "x1_other"), sep = " <") %>%
  select(-x1_other) %>%
  separate(x2, c("x2_other", "x2_upper"), sep = " <= ") %>%
  separate(x2_other, c("x2_almost_lower", "x2_other"), sep = "x2") %>%
  select(-x2_other) %>%
  separate(x2_almost_lower, c("x2_lower", "x2_other"), sep = " <") %>%
  select(-x2_other) %>%
  mutate(x1_lower = ifelse(x1_lower == "", "-Inf", x1_lower),
         x1_upper = ifelse(is.na(x1_upper), "Inf", x1_upper),
         x2_lower = ifelse(x2_lower == "", "-Inf", x2_lower),
         x2_upper = ifelse(is.na(x2_upper), "Inf", x2_upper)) %>%
  mutate_at(.vars = c("x1_lower", "x1_upper",
                      "x2_lower", "x2_upper"),
            .funs = as.numeric) %>%
  arrange(x1_lower)

coef_ext <- max(abs(min(mean_coefs_added$mean_coef_x1_plus_x2)),
                abs(max(mean_coefs_added$mean_coef_x1_plus_x2)))

lower_coef_col <- -coef_ext - 0.05
upper_coef_col <- coef_ext + 0.05

# Plot the x1 averaged coefficients
plot_x1coefs <- ggplot() +
  geom_rect(data = mean_coefs,
            mapping = aes(xmin = x1_lower,
                          xmax = x1_upper,
                          ymin = x2_lower,
                          ymax = x2_upper,
                          fill = mean_coef_x1)) +
  xlim(-10, 10) +
  ylim(-10, 10) +
  scale_fill_gradient2(low = "firebrick",
                       mid = "white",
                       high = "steelblue",
                       midpoint = 0,
                       limits = c(lower_coef_col, upper_coef_col)) +
  theme_bw(base_family = "Times", base_size = 12) +
  labs(x = TeX("$x_1$"),
       y = TeX("$x_2$"),
       fill = TeX('Ave $\\hat{\\beta}_1$'),
       color = "RF Prob",
       title = TeX("Average $\\hat{\\beta}_1$ by Quantile Bins")) +
  theme(legend.position = "none")

# Plot the x2 averaged coefficients
plot_x2coefs <- ggplot() +
  geom_rect(data = mean_coefs,
            mapping = aes(xmin = x1_lower,
                          xmax = x1_upper,
                          ymin = x2_lower,
                          ymax = x2_upper,
                          fill = mean_coef_x2)) +
  xlim(-10, 10) +
  ylim(-10, 10) +
  scale_fill_gradient2(low = "firebrick",
                       mid = "white",
                       high = "steelblue",
                       midpoint = 0,
                       limits = c(lower_coef_col, upper_coef_col)) +
  theme_bw(base_family = "Times", base_size = 12) +
  labs(x = TeX("$x_1$"),
       y = TeX("$x_2$"),
       fill = TeX('Ave $\\hat{\\beta}_2$'),
       color = "RF Prob",
       title = TeX("Average $\\hat{\\beta}_2$ by Quantile Bins")) +
  theme(legend.position = "none")

# Plot the x1 + x2 averaged coefficients
plot_x1plusx2coefs <- ggplot() +
  geom_rect(data = mean_coefs_added,
            mapping = aes(xmin = x1_lower,
                          xmax = x1_upper,
                          ymin = x2_lower,
                          ymax = x2_upper,
                          fill = mean_coef_x1_plus_x2)) +
  xlim(-10, 10) +
  ylim(-10, 10) +
  scale_fill_gradient2(low = "firebrick",
                       mid = "white",
                       high = "steelblue",
                       midpoint = 0,
                       limits = c(lower_coef_col, upper_coef_col)) +
  theme_bw(base_family = "Times", base_size = 12) +
  labs(x = TeX("$x_1$"),
       y = TeX("$x_2$"),
       fill = "Coefficient \nAverage",
       color = "RF Prob",
       title = TeX("Average $\\hat{\\beta}_1+\\hat{\\beta}_2$ by Quantile Bins"))

# Get legend and remove legend from addedplot
ave_coef_leg <- get_legend(plot_x1plusx2coefs)
plot_x1plusx2coefs <- plot_x1plusx2coefs +
  theme(legend.position = "none")

# Join the plots
plot_grid(plot_x1coefs, plot_x2coefs, plot_x1plusx2coefs, ave_coef_leg,
          nrow = 1, rel_widths = c(0.3, 0.3, 0.3, 0.1))

@
\caption{Plots of the four quantile bin grids of $x_1$ and $x_2$ colored by averaged explainer model coefficient values. The cells in the left and right plots are colored by the average of the ridge regression coefficients for $x_1$ $\left(\hat{\beta}_1\right)$ and $x_2$ $\left(\hat{\beta}_2\right)$, respectively, of the test set observations located within the cell. The plot on the right is colored by the average of the addition of the $x_1$ and $x_2$ ridge regression coefficients $\left(\hat{\beta}_1+\hat{\beta}_2\right)$ of the test set observations located within the cell. These plots are an overview of LIME explanations in a format that allows for easy interpretation based on the location of $x_1$ and $x_2$ values. \kgc{**Change the discussion to interpretation of the third plot as the overall contrasts (based on the combinations of the two features) and reduce the amount of time spent talking about the two possible ways and interpret the plot**} \kgc{**Add an implementation with 10 bins - could include in the appendix and add a discussion on how the more bins could lead to a more localized explanation (or not)**} \kgc{**Perform a test for whether a cell is "significantly" on one side or the other based on the within and between variability (var within a point, var between points within a bin) (could look at a ratio) (local versus global structure)}** **\kgc{Connect this figure to figure 13}**}
\label{fig:sine-plot-agg-exp}
\end{figure*}

As a result, it is possible to create aggregated explanations by averaging over the coefficients within an $x_1$ and $x_2$ bin intersections. Since this example has the same two features chosen for all cases in the test data, it is also possible to visualize the aggregated explanations as shown in \autoref{fig:sine-plot-agg-exp}. Each plot shows the grid of the 16 cells created by the 4 quantile bins for $x_1$ and $x_2$.
\hh{XXX Nice!}

The cells of the plot on the left in \autoref{fig:sine-plot-agg-exp} are colored by average of the coefficients for $x_1$ $\left(\hat{\beta}_1\right)$ associated with all of the test data points located within the cell. This shows that within an $x_1$ quantile bin, there is little variability in the average explainer model coefficients across the $x_2$ quantile bins. However, as the value of $x_1$ ranges from -10 to 10, the direction of the coefficient changes from being in support of a label of 1 to being in support of a label of 0.

The middle plot of \autoref{fig:sine-plot-agg-exp} is colored by the average of the coefficients for $x_2$ $\left(\hat{\beta}_2\right)$ associated with all of the test data points located within the cell. In this case, there are horizontal stripes showing that there is little variability in average $x_2$ coefficient within an $x_2$ quantile bin across the $x_1$ bins, but lots of variability across the $x_2$ quantile bins. Opposite from $x_1$, as the value of $x_2$ ranges from -10 to 10, the direction of the coefficient changes from being in support of a label of 0 to being in support of a label of 1.

Finally, the cells in the plot on right of \autoref{fig:sine-plot-agg-exp} are colored by the average of the sum of the $x_1$ and $x_2$ coefficients $\left(\hat{\beta}_1+\hat{\beta}_2\right)$ corresponding to the test points located within the cell. This plot allows for an explanation of a prediction within the $x_1$ and $x_2$ range based on the combination of the two features.
\hh{XXX Why wouldn't we be able to interpret the color directly? The 16 bins are colored by the (overall) predominant feature. The overall pattern the lime explanations find is the strong overall pattern for the diagonal. Nothing in the individual cases suggest that lime picks up on any of the local patterns of the sine curve beyond the diagonal. }

\hh{XXX I really don't think you have to discuss the plot in so much detail. It distracts from the main finding that lime, yet, again, is not locally faithful.}
By just viewing the colors of the cells, this plot can not be interpreted since the color could be the result of different of various scenarios of $\hat{\beta}_1$ and $\hat{\beta}_1$, but by considering the colors of the corresponding cells in the left and middle plot, the colors of the cells in the right plot can be interpreted. For example, consider the top left cell, which is dark blue. The same cells in the other two plots are both blue, so the combination of $x_1$ and $x_2$ leads to strong support that an observation in this region will be predicted to be in category blue by the random forest model. The bottom right cell is dark red, which indicates that the LIME explainer models suggest that observations in this cell have strong support of a random forest prediction of category red based on both $x_1$ and $x_2$ since the cells in the left and middle figures are also red. Overall, the right plot shows that the LIME explainer models indicated that as the location of an observation ranges from $x_1$ values near -10 and $x_2$ values near 10 to $x_1$ values near 10 and $x_2$ values near 10, there is an explanation gradient from both variables supporting a prediction of 1 to both variables supporting a prediction 0 with contrasting support between predictions of 0 and 1 from the two variables on the diagonal.

While the left and middle plots of \autoref{fig:sine-plot-agg-exp} are similar to \autoref{fig:sine-plot-selected-features}, by displaying the averaged coefficients as the grid of $x_2$ versus $x_1$, it is easier to interpret the LIME explanation pattern in the context of the feature values. With the addition of the right plot of \autoref{fig:sine-plot-agg-exp}, the visualization of the aggregated explanations provide a simplified and more intuitive method to view the explainer model explanations across the feature space.

\subsection{Explainer Model Assessment} \label{assess-set}

<<sine-mid-explainer-pred>>=
# Determine the explainer model predictions with the
# random forest predictions are between 0.25 and 0.75
mid_expred <- sine_lime_default %>%
  group_by(case, sim_method) %>%
  ungroup() %>%
  filter(label_prob > 0.25, label_prob < 0.75) %>%
  select(label_prob, model_prediction)
@

Both figures in \autoref{understand-set} display a set of the LIME explanations to provide a holistic understanding of the explanations, but neither provide any way to assess the explanations for trustworthiness. We will now introduce some diagnostic visualizations of a set of LIME explanations.

\hh{Lead into this paragraph by stating the goal. The scatterplot is the tool to get there, i.e. start by saying that you want to compare predictions with important features.}
A scatterplot of the predictions from the explainer models for important features \sout{can be} \hh{are} compared with a plot of predictions from the complex model to determine if the bins are appropriately capturing the pattern from the complex model.
\autoref{fig:sine-plot-grid} shows the $x_1$ and $x_2$ values of the observations in the test set of the \data \ colored by the prediction made by the corresponding LIME explainer model. The grid created by the quantile bins is overlaid by the solid black lines. Note that the predictions within each cell of the grid are visually \hh{very similar values}. \hh{Describe this pattern without using numbers ... how about: This plot shows that the explainer model captures the big picture relationship between features $x_1$ and $x_2$ of high values in the top left corner and low values in the bottom right. } This plot shows that the explainer models return predictions close to 0 when $x_1$ is near 10 and $x_2$ is near -10 (bottom right corner) and predictions close to 1 when $x_1$ is near -10 and $x_2$ is near 10 (upper left corner). Agreeing with the pattern seen in \autoref{fig:sine-plot-agg-exp}, there is a gradient in predictions from one of these locations to the other with a diagonal of predictions close to 0.5 in the middle. The gradient is a clear representation of true rotated sine decision boundary. However, the random forest captures the more complex relationship on the diagonal as seen in \autoref{fig:sine-plot-step1ab} with prediction \hh{region}s \sout{close to 0 and 1 in this region that} mimic\hh{ing} the true decision boundary. While LIME selects features  $x_1$ and $x_2$ as most important, by using just four  bins the explanations appear to have oversimplified the complex model predictions, and return explanations that are not accurate descriptors of the random forest model predictions. \kgc{KG: To address the complaint of how to handle more than two features with \autoref{fig:sine-plot-grid}, I could create a biplot of sorts that could be one extension or a scatterplot matrix. This could be included here or in the appendix.}
\hh{Here would be a good place to get into a discussion about how to go beyond two dimensions. }

\begin{figure}[!t]
<<sine-plot-grid, warning = FALSE, out.width = '0.5\\textwidth', fig.width = 4, fig.height = 3.2>>=

sine_chosen_errors <- sine_data_test %>%
  filter(y != rfpred, x1 > 0, x1 < 5, x2 > 0)

sine_error_bounds <- sine_lime_default %>%
  filter(case %in% sine_chosen_errors$case) %>%
  select(case, feature, feature_value, feature_desc) %>%
  separate(feature_desc, c("other", "upper"), sep = " <= ") %>%
  separate(other, c("lower", "feature2"), sep = " < ") %>%
  mutate(upper = ifelse(is.na(upper), "Inf", upper)) %>%
  select(-feature2) %>%
  mutate_at(.vars = c("lower", "upper"), .funs = as.numeric)

# Determine the bin cuts
sine_lime_default_bin_cuts <- sine_lime_default %>%
  select(feature, feature_desc) %>%
  unique() %>%
  separate(feature_desc, c("other", "bin_cut"), sep = " <= ") %>%
  select(-other) %>%
  na.omit() %>%
  mutate(bin_cut = as.numeric(bin_cut)) %>%
  arrange(feature) %>%
  mutate(case = rep(1:3, 2)) %>%
  spread(feature, bin_cut)

# Plot the LIME explainer model predictions for the
# testing data with the 4 quantile bins
ggplot() +
  geom_vline(xintercept = sine_lime_default_bin_cuts$x1) +
  geom_hline(yintercept = sine_lime_default_bin_cuts$x1) +
  geom_point(data = sine_lime_default %>%
               select(case, feature, feature_value, model_prediction) %>%
               spread(feature, feature_value),
             mapping = aes(x = x1,
                           y = x2,
                           color = model_prediction),
             alpha = 0.8) +
  scale_color_gradient2(low = sinecolor_red,
                        mid = '#f7f7f7',
                        high = sinecolor_blue,
                        midpoint = 0.5) +
  scale_fill_gradient2(low = "firebrick",
                       mid = '#f7f7f7',
                       high = "steelblue",
                       midpoint = 0) +
  theme_bw(base_family = "Times", base_size = 10) +
  labs(x = TeX("$x_1$"),
       y = TeX("$x_2$"),
       color = "LIME \nExplainer \nModel \nPrediction",
       title = "Test Data Colored by Explainer Prediction")

@
\caption{Plot of the test \data \ colored by the predictions from the LIME explainer model. The solid black lines represent the grid created by the 4 quantile bin simulation method. Predictions within a cell are visually indistinguishable. This plots shows a diagonal gradient of predictions near 1 in the top left corner to predictions of 0 in the bottom right corner. While this trend mimics the random forest predictions, it could be argued to be an oversimplification of the random forest prediction mechanism.}
\label{fig:sine-plot-grid}
\end{figure}

\hh{XXX add a subsection with a name for the diagnostic}

\hh{This is a good lead into the paragraph: you start by stating the objective and follow up with the figure.}
Both the complex and explainer models return a prediction for an observation. One way to assess the faithfulness of the explainer model to the complex model is to compare the two predictions. \autoref{fig:sine-plot-compare-preds} shows a plot of the explainer model predictions versus the random forest predictions from the observations in the \data \ test set. The solid line is a loess smoother fit to the points, and the dashed line is \hh{the identity} line. If the predictions from the explainer models were in perfect agreement with the random forest model, they would follow this line exactly. This is not the case. The curve in the loess suggests that the explainer model performs differently in terms of faithfulness depending on the value of the random forest prediction. When the random forest prediction is low, the explainer model is overestimating the random forest prediction, and when the random forest prediction is high, the explainer model is underestimating the prediction. When the random forest prediction is close to 0.5, the explainer model predictions \hh{cover a wide} range (from \Sexpr{round(min(mid_expred$model_prediction), 2)} to \Sexpr{round(max(mid_expred$model_prediction), 2)}). This plot \hh{clearly indicates} that there is an issue with the faithfulness of the explainer models in terms of their ability to produce predictions similar to the random forest.

\hh{XXX $R^2$ is not our standard $R^2$ and needs to be explained. You could go into the math here.}
Additionally, the points in \autoref{fig:sine-plot-compare-preds} are colored by the $R^2$ value from the corresponding explainer model. This shows that the $R^2$ values of the explainer models from the test set range from \Sexpr{round(min(sine_lime_default$model_r2), 2)} to \Sexpr{round(max(sine_lime_default$model_r2), 2)}. These are all low $R^2$ values.  \hh{XXX If LIME actually did fit nice local models, a low R2 wouldn't be so bad.} This suggest that the explainer models \sout{are doing a poor job} of explaining the relationship between the random forest predictions and the model features.

\begin{figure}[!t]
<<sine-plot-compare-preds, out.width = '0.5\\textwidth', fig.width = 4, fig.height = 3.25>>=
sine_lime_default %>%
  group_by(case, sim_method) %>%
  slice(1) %>%
  ungroup() %>%
  mutate(sim_method = fct_recode(sim_method,
                                 "Quantile Bins" = "quantile_bins",
                                 "Kernel Density" = "kernel_density")) %>%
  ggplot(aes(x = label_prob, y = model_prediction, color = model_r2)) +
  geom_point() +
  geom_smooth(se = FALSE, method = "loess", color = "black") +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed") +
  theme_bw(base_family = "Times", base_size = 10) +
  labs(x = "Random Forest Prediction",
       y = "Explainer Model Prediction",
       color = "Explainer \nModel \nR2",
       title = "Complex and Explainer Model \nPrediction Comparison") +
  scale_color_gradient(low = "grey90", high = "grey40")
@
\caption{Plot of the explainer model predictions versus the random forest predictions for each observation in the \data \ test set. Each point is colored by the $R^2$ value from the associated explainer model. The solid line is a loess smoother fit to the points, and the dashed line is a 1-1 line included for reference.}
\label{fig:sine-plot-compare-preds}
\end{figure}

\hh{\autoref{fig:sine-plot-compare-bins} goes back to Fig 13 and before. Move this back.}
To supplement the information gained from \autoref{fig:sine-plot-compare-preds}, \autoref{fig:sine-plot-compare-bins} provides a visualization of the comparison of the explainer model predictions to the random forest predictions in the context of the $x_1$ and $x_2$ quantile bins. The intersection of the bins are colored by the average explainer model prediction of the test set observation located in the region. The \data \ test set is plotted as the circles and colored by the corresponding random forest probability. The test points that the random forest misclassified are encompassed by a black open circles. The plot highlights that the explainer models are over-simplifying the random forest predictions on the diagonal (lower left to upper right) where the explainer model predictions are close to 0.5, but the random forest probabilities range from 0 to 1. It is also possible to see the locations where the explainer model is over or under estimating the random forest model predictions on the off diagonals.

\hh{XXX Good! This plot would also work in higher dimensions by including faceting.}
\begin{figure}[!t]
<<sine-plot-compare-bins, warning = FALSE, out.width = '0.5\\textwidth', fig.width = 6.75, fig.height = 5.5>>=

# Compute the average explainer model predictions per bin
bin_mean_exp_pred <- sine_lime_default %>%
  select(case, model_prediction) %>%
  group_by(case) %>%
  slice(1) %>%
  ungroup() %>%
  full_join(sine_lime_default %>%
              select(case, feature, feature_desc) %>%
              spread(feature, feature_desc),
            by = "case") %>%
  group_by(x1, x2) %>%
  summarise(mean_exp_pred = mean(model_prediction)) %>%
  ungroup() %>%
  separate(x1, c("x1_other", "x1_upper"), sep = " <= ") %>%
  separate(x1_other, c("x1_almost_lower", "x1_other"), sep = "x1") %>%
  select(-x1_other) %>%
  separate(x1_almost_lower, c("x1_lower", "x1_other"), sep = " <") %>%
  select(-x1_other) %>%
  separate(x2, c("x2_other", "x2_upper"), sep = " <= ") %>%
  separate(x2_other, c("x2_almost_lower", "x2_other"), sep = "x2") %>%
  select(-x2_other) %>%
  separate(x2_almost_lower, c("x2_lower", "x2_other"), sep = " <") %>%
  select(-x2_other) %>%
  mutate(x1_lower = ifelse(x1_lower == "", "-Inf", x1_lower),
         x1_upper = ifelse(is.na(x1_upper), "Inf", x1_upper),
         x2_lower = ifelse(x2_lower == "", "-Inf", x2_lower),
         x2_upper = ifelse(is.na(x2_upper), "Inf", x2_upper)) %>%
  mutate_at(.vars = c("x1_lower", "x1_upper",
                      "x2_lower", "x2_upper"),
            .funs = as.numeric) %>%
  arrange(x1_lower)

# Compute the lower and upper limits of the explainer model predictions
pred_col_lower = min(bin_mean_exp_pred$mean_exp_pred)
pred_col_upper = max(bin_mean_exp_pred$mean_exp_pred)

# Plot of the average feature weights by bin
ggplot() +
  geom_rect(data = bin_mean_exp_pred,
            mapping = aes(xmin = x1_lower,
                          xmax = x1_upper,
                          ymin = x2_lower,
                          ymax = x2_upper,
                          fill = mean_exp_pred),
            alpha = 1) +
  geom_point(data = sine_lime_default %>%
               select(case, feature, feature_value,
                      label_prob, model_prediction) %>%
               spread(feature, feature_value),
             mapping =  aes(x = x1, y = x2, color = label_prob)) +
  geom_point(data = sine_lime_default %>%
               select(case, feature, feature_value,
                      label_prob, model_prediction) %>%
               spread(feature, feature_value) %>%
               mutate(rf1 = ifelse(label_prob > 0.5, TRUE, FALSE),
                      lime1 = ifelse(model_prediction > 0.5,
                                     TRUE, FALSE)) %>%
               mutate(diff = rf1 - lime1) %>%
               select(case, x1, x2, diff) %>%
               filter(diff != 0) %>%
               mutate(shape = "Random Forest \nMisclassified \nPredictions"),
             mapping =  aes(x = x1, y = x2, color = label_prob,
                            shape = shape),
             alpha = 1,
             size = 3,
             color = "black") +
  scale_color_gradient2(low = "firebrick",
                        mid = '#f7f7f7',
                        high = "steelblue",
                        midpoint = 0.5,
                        limits = c(pred_col_lower, pred_col_upper)) +
  scale_fill_gradient2(low = "firebrick",
                       mid = '#f7f7f7',
                       high = "steelblue",
                       midpoint = 0.5,
                       limits = c(pred_col_lower, pred_col_upper)) +
  scale_shape_manual(values = 1) +
  xlim(-10, 10) +
  ylim(-10, 10) +
  theme_bw(base_family = "Times", base_size = 14) +
  labs(x = TeX("$x_1$"),
       y = TeX("$x_2$"),
       shape = "",
       fill = "Average \nExplainer \nModel \nProbability \nfor 'blue'",
       color = "Random \nForest \nProbability \nfor 'blue'",
       title = "Quantile Grid Comparison of LIME Explainer \nModel Predictions to Random Forest \nPredictions") +
  guides(shape = guide_legend(order = 1),
         fill = guide_legend(order = 2, reverse = T),
         color = guide_legend(order = 3, reverse = T))

@
\caption{Plot comparing the LIME explainer models predictions to the random forest predictions in the context of the four $x_1$ and $x_2$ quantile bins. The intersection of the quantile bins are colored by the average of the test data explainer model probabilities located in the intersection. The points are the test set data and colored by the corresponding random forest probability. The observations misclassificed by the random forest are indicated by black open circles.}
\label{fig:sine-plot-compare-bins}
\end{figure}

\section{Visualizations for the Comparison of LIME \kge{Tuning Parameters}}  \label{implementation-visuals}

Define an observation of interest as $x^*\in\mathbb{R}^p$. $x^*$ \hh{can} be an element of $\textbf{X}$ or a separate testing dataset. Let $y^*\in\{0,1\}$ be the response value associated with $x^*$. %Note that if $x^*\in\textbf{X}$, then $y^*$ is observed and is an element of $y$. Otherwise, $y^*$ is not observed.
LIME will be used to identify the key features involved in the prediction $f(x^*)$.

In terms of the \data, $\textbf{X}$ is a 500 by 3 matrix containing the features $x_1$, $x_2$, and $x_3$, and $y$ is a vector of length 500 of 0s and 1s. The complex model $f$ is the random forest model, and $\hat{y}$ are the probability predictions produced by the random forest model applied to $\textbf{X}$. The prediction of interest %we would like to provide an explanation for has 
\hh{is} $x^*=$ (\Sexpr{round(sine_poi$x1, 2)}, \Sexpr{round(sine_poi$x2, 2)}, \Sexpr{round(sine_poi$x3, 2)}) \hh{with} $f(x^*)=0.83$.

As described in \autoref{background}, there are \sout{many adjustments} \hh{various parameter choices}  that \sout{can} \hh{have to} be made when \sout{implementing} \hh{applying} LIME: the simulation method, the feature selection method, and how weights are calculated.  We will refer to these choices as tuning parameters.
Explanations produced by LIME are likely affected by exact choice of tuning parameters. An example of this was shown by Figures \ref{fig:concept-plot-good} and \ref{fig:concept-plot-bad} where the method used to weight the observations influenced the explanation. As of the time of writing this manuscript, there are no recommendations or procedures provided for how to determine which method to use besides for the default settings in \emph{lime} \kgc{(confirm this)}.

\hh{no woulds, shoulds, coulds, can bes or any other modals XXX get the next paragraph out of the realm of the hypothetical}
One approach to visually comparing the LIME explanations across different tuning parameters would be to extend the visualizations in \autoref{set-visuals}. Each graphic could be created for each implementation. However, as the number of tuning parameters increase, the number of graphics will also increase, and it may be difficult to identify patterns across implementations. In this section, we propose visualizations for the comparison and assessment of LIME explanations produced by different tuning parameters for a set of predictions that aggregate the results into a single graphic.

\hh{In the following section, we compare six different settings of tuning parameters and their impact on explanations given by LIME.}
\hh{XXX Move this paragraph to the beginning of section 6}
To demonstrate \sout{our} proposed diagnostic plots, we applied six different implementations of LIME to the sine data to select the top two features associated with each of the random forest predictions in the testing dataset. This was done using six different sets of tuning parameters via \sout{our} R package \emph{limeaid} \footnote{Available on GitHub at https://github.com/goodekat/limeaid}. Quantile bins were used for five of the implementations, and the number of bins for these implementations was varied from 2 to 6. The sixth implementation of LIME used the kernel density estimates. The feature selection method and the computation of the weights were set to the default options in \emph{lime} of forward selection and Gower distance raised to an exponent of 1.

\subsection{Feature Heatmap Diagnostic Plot} \label{feature-heatmap}

\begin{figure}[!b]
<<concept-heatmap, out.width = '0.5\\textwidth', fig.width = 6, fig.height = 3>>=
# Specify the number of cases and LIME input options
ncases = 10
ninputs = 5

# Create a good case of chosen feature example data
set.seed(20191008)
heatmap_data_good <- tibble(case = factor(rep(1:ncases, each = ninputs),
                                     levels = ncases:1),
                       input = factor(rep(1:ninputs, ncases)),
                       feature = factor(c(rep(1, 5),
                                          rep(2, 5),
                                          rep(3, 5),
                                          rep(1, 5),
                                          rep(1, 5),
                                          rep(4, 5),
                                          rep(1, 5),
                                          rep(3, 5),
                                          rep(1, 5),
                                          rep(4, 5)))) %>%
  mutate(input = forcats::fct_recode(input, "A" = "1", "B" = "2",
                                     "C" = "3", "D" = "4", "E" = "5"))

# Create the conceptual good heatmap
heatmap_plot_good <- ggplot(data = heatmap_data_good,
                            mapping = aes(x = input,
                                          y = case,
                                          fill = feature,
                                          color = feature)) +
  geom_tile() +
  labs(x = "Implementation Method",
       y = "Case",
       fill = "Feature",
       title = "Situation 1: \nConsistent Explanations") +
  theme_bw(base_family = "Times", base_size = 12) +
  scale_fill_grey() +
  scale_color_grey() +
  theme(legend.position = "none")

# Create a bad case of chosen feature example data
set.seed(20190627)
heatmap_data_bad <- tibble(case = factor(rep(1:ncases, ninputs),
                                     levels = ncases:1),
                       input = factor(rep(1:ninputs, each = ncases)),
                       feature = factor(rep(c(1, 2, 4, 3, 2), each = 10))) %>%
  mutate(input = forcats::fct_recode(input, "A" = "1", "B" = "2",
                                     "C" = "3", "D" = "4", "E" = "5"))

# Create the conceptual bad heatmap
heatmap_plot_bad <- ggplot(data = heatmap_data_bad,
                            mapping = aes(x = input,
                                          y = case,
                                          fill = feature,
                                          color = feature)) +
  geom_tile() +
  labs(x = "Implementation Method",
       y = "Case",
       fill = "Feature",
       title = "Situation 2: \nInconsistent Explanations") +
  theme_bw(base_family = "Times", base_size = 12) +
  scale_fill_grey() + 
  scale_color_grey()

heatmap_leg <- get_legend(heatmap_plot_bad)
heatmap_plot_bad <- heatmap_plot_bad + theme(legend.position = 'none')

# Join the plots
plot_grid(heatmap_plot_good, heatmap_plot_bad, heatmap_leg,
          nrow = 1,
          rel_widths = c(0.45, 0.45, 0.1))

@
\caption{Two hypothetical examples of feature heatmaps showing the top feature chosen for 10 cases across 5 different implementations of LIME (sets of tuning parameters). The color of the cell indicates the feature chosen by LIME. The plots represent two possible situations that may arise when applying LIME to a set of predictions.}
\label{fig:concept-heatmap}
\end{figure}

\begin{figure}[!t]
<<sine-feature-heatmap, out.width = '0.5\\textwidth', fig.width = 5, fig.height = 5.5>>=
feature_heatmap(sine_lime_explain$explain,
                order_method = "PCA") +
  theme_bw(base_family = "Times", base_size = 10) +
  theme(legend.position = "bottom",
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) +
  labs(y = "Case")
@
\caption{Feature heatmap of the various LIME implementations applied to the \data. The cases from the test set are plotted on the y-axis, and the implementation methods are included on the x-axis. The colors of the tiles indicate the feature selected by LIME for the corresponding case and implementation method. The top faceted row includes the first features selected by LIME, and the bottom faceted row includes the second features selected by LIME. The faceted columns separate the kernel density implementation method from the quantile bin implementations. The vertical striping seen in the plot indicates that LIME is not consistent in selecting features across implementation methods.}
\label{fig:sine-feature-heatmap}
\end{figure}

\kgc{**Refer back to the earlier use of a heatmap to compare implementations in this section**} In order to compare the explanations produced by LIME using different tuning parameters, we \sout{would like to} view an overview of all the explanations.
\sout{To do this,} we \sout{will} plot the features selected by LIME for all of the cases and tuning parameters in heatmaps separated by the position of importance assigned by LIME in a plot that will be referred to as a feature heatmap. That is, for LIME applied for $t$ sets of tuning parameters to $n$ cases to select the $f$ top features, create $f$ heatmaps (one for each of the positions of importance) with the cases on the y-axis, the tuning parameters on the x-axis, and the cells colored by the feature chosen for the corresponding case and tuning parameter. This plot will be used assess the locality of the explanations and to compare results from different input options.

Two hypothetical examples of feature heatmaps are included in \autoref{fig:concept-heatmap}. The plots were created with the assumption that LIME was applied to select the top feature out of $p=8$ features for $n=10$ cases with $t=5$ sets of tuning parameters. If LIME were producing local explanations, it would be expected that the top features selected by LIME would vary for predictions located in different regions of the feature space unless a feature or several features are the deterministic features throughout the entire feature space. Additionally, if the tuning parameters used when implementing LIME did not affect the feature selected by LIME, the selected feature would be the same across all implementations for a case.

The plots in \autoref{fig:concept-heatmap} depict two different situations that may arise when applying LIME. Situation 1 shows an example where the features selected across implementation methods within a case are consistent, and the features selected by vary across cases. This is the ideal situation, because regardless which implementation method is used, the LIME explanations do not vary, and the explanations appear to be local since the features vary between cases. Situation 2 shows an example where the features selected across implementation methods within a case vary, but the features selected within an implementation method across cases are the same. This situation \sout{is not ideal, because it} indicates that the features selected by LIME are dependent on the implementation method used, and the explanations are not local because the same feature is chosen regardless of the case. In practice, it is expected that the plot will exhibit a combination of these two situations.

\autoref{fig:sine-feature-heatmap} shows the feature heatmap for the LIME implementations applied to the \data. The top row of the plot contains the features selected as the most important by LIME, and the bottom row contains the second most important feature selected by LIME. For the quantile bin implementations, the original features prior to the interpretability transformation are plotted  since it is obvious that different features would be selected when the sizes of the bins change from one implementation to the next. This figure shows a clear difference in the explanations produced by LIME for the kernel density and two quantile bin methods and the other quantile bin methods. For both the kernel density and two quantile bin implementations, LIME selects $x_1$ as the most important feature and $x_2$ as the second most important feature across all cases in the test set. There is more variability in the features selected by LIME for the three to six quantile bin implementations. For these implementations, there is a mix of horizontal and vertical stripes, which suggests that LIME is not consistently providing the sample explanation across implementation methods. It is also interesting, that the implementations of 3 and 5 bins leads to the selection of the random noise variable of $x_3$ as an important variable in many predictions, which should not be the case. \kgc{At some point, I still need to look into the ordering of the tiles.}

\subsection{Assessment Metric Plot}

\begin{figure}[!t]
<<sine-metric-plot, out.width = '0.5\\textwidth', fig.width = 4.5, fig.height = 4, warning = FALSE>>=

# Create the metric plot
metric_plot(sine_lime_explain$explain) +
  theme_bw(base_family = "Times") +
  scale_color_gradient(low = "grey10", high = "grey90")

@
\caption{Example of a metric comparison plot using the \data. Each row of the plot corresponds to one of three metrics: average fidelity, average $R^2$, or MSEE. The tuning parameters from the different LIME implementations are plotted on the x-axis, and the metric values are shown on the y-axis. The points are colored by rank within a metric indicating best to worst (dark to light). The kernel density simulation methods performs well according to all three metrics.}
\label{fig:sine-metric-plot}
\end{figure}

The feature heatmap for the \data \ in the previous section showed an example of how LIME explanations are not always consistent across \hh{this sounds like R versus python implementation. It's not what you mean} implementation methods. As a result, it is necessary to choose \hh{tuning parameters} that produce reliable explanations. One way to do this, \sout{would be} to apply LIME using different implementations, and then compute assessment metrics to determine the optimal tuning parameters. We will discuss several metrics that could be used for this purpose and present a comparison of the metrics in a plot. \kgc{***Right now, I have not included any variability in these plots. I could add standard deviation bars or change these to box plot.} \kgc{***Also, I still haven't tried implementing the anova complexity parameter.}

\kgc{Placing the notation definitions here for now - need to make adjustments as necessary:} \kge{We first introduce notation for the scenario of tabular data with a binary response variable and continuous features. Let $\textbf{X}$ be an $n$ by $p$ data matrix with $p$ features and $n$ observations, and let $x_i\in\textbf{X}$ be a real-valued vector such that $x_i\in\mathbb{R}^p$ for $i=1,2,...,n$. Furthermore, let $y$ be a response variable of length $n$ with elements $y_i\in\{0, 1\}$ for $i=1,2,...,n$. Suppose that $f$ is a classification model where $f:\mathbb{R}^p\rightarrow[0,1]$ that is applied to $\textbf{X}$ and $y$. Let the vector of predictions made by $f$ applied to $\textbf{X}$ be denoted as $\hat{y}$. Note that $\hat{y}_i=f(x_i)\in\hat{y}$ for $i=1,..,n$. For both bin based methods, the interpretability transformation converts the generated observations to indicator variables, where a 1 indicates that the feature value for an observation is in the same bin as the feature value for the case of interest. That is
  $$z'_{i,j}=T\left(x'_{i,j}\right) = I\left[x'_{i,j} \mbox{ and } x^*_{i,j}\in b_{j,k} \right]$$
for $i=1,..,m$ and $j=1,..,p$ where $b_{j,k}$ is bin $k$ for feature $j$. Let observation $z'_i$ have weight $\omega_{x^*}(\textbf{x}'_i) = Gower(x^*, x'_i)^c$, where $Gower$ represents the computation of the Gower similarity and $c$ is some constant. This denotes a proximity measure between $x^*$ and $x'_i$ for each $i\in 1,...,m$. If the exponential kernel is used, the weights are computed after the interpretability transformation such that $z'_i$ has weight $\omega_{z^*}(\textbf{z}'_i)$.}

\citet{ribeiro:2016} present \hh{the following metric as a measure of fidelity:}
$$\mathcal{L}(f, g, \omega_{x^*}) = \sum_{i=1}^{m}\omega_{x^*}(x_i)\left(f(x_i)-g\left(z_i'\right)\right)^2,$$
\hh{where  ... }
%\hh{XXX please connect the symbols and the words. }

a fidelity metric for measuring the faithfulness of the explainer model to the complex model. This is done by comparing the complex and simple model predictions for each of the values in the simulated dataset accounting for the assigned weight. This metric is computed as $$\mathcal{L}(f, g, \omega_{x^*}) = \sum_{i=1}^{m}\omega_{x^*}(x_i)\left(f(x_i)-g\left(z_i'\right)\right)^2.$$ Smaller values of $\mathcal{L}$ indicate a better local approximation of the explainer model to the complex model.

\hh{Focus on results, not chronological order}
We computed $\mathcal{L}$ in \emph{limeaid} for each observation in the test \data \ and each implementation of LIME. We then computed the average value fidelity metric over the test dataset within a LIME implementation. These values have been plotted in the top facet of \autoref{fig:sine-metric-plot}. The average fidelity is lowest for the kernel density simulation method increases as the number of quantile bins increase. This would suggest that the LIME implementation using the kernel density estimate provides the best local approximation to the random forest model on average. Note that the points in the plot are colored such that darker indicates a better metric value and lighter indicates a worse metric value. \kgc{***I'm not sure what I think about this result. Can we talk through my code for computing this value together to make sure I didn't make any mistakes? Note that it appears to return a pattern that is perfectly symmetric to the average fidelity (agrees with R2), but it disagrees with the MSEE with the quantile bins???}

We propose a similar metric we will call the mean squared explanation error (MSEE). Again, this metric is meant to measure the faithfulness of the explainer model to the complex model by comparing their predictions, but instead of computing a squared difference over all observations in the simulated data, we only consider the observation of interest and compute the average squared deviation over the observations in the test set for an implementation of LIME. That is, let $$MSEE=\frac{1}{n}\sum_{i=1}^n\left(f\left(x^*\right)-g\left(z^*\right)\right)^2.$$ Again, smaller values of MSEE would suggest a better approximation of the explainer model.

%\hh{XXX Again, connect the symbols in the equation and the words. aren't you missing an index $i$?}

\hh{It's not important to have the values computed - the important part is the comparison. The beginning of the sentence is emphasized. Make sure to use that.}
We computed the MSEE for each implementation of LIME, and these values are plotted in the bottom facet of \autoref{fig:sine-metric-plot}. Again, the color gradient of the points indicates the MSEE ranks from best to worst (darkest to lightest). The 6 quantile bin simulation method has the lowest MSEE followed closely by the kernel density method, which suggests that these methods have explainer models that best approximate the complex model for the prediction of interest on average. The MSEE increases as the number of quantile bins increases.

\hh{XXX again, focus less on the chronological order and more on the results. }
\hh{XXX Somewhere in the paper define $R^2$ in detail, with a numbered equation - then you can refer to it very efficiently: "$R^2$ as defined in eq. X"  }
Another metric discussed earlier in the paper is $R^2$. This can be used to assess the fit of each individual explainer model. Once LIME has been applied to all observations of interest, an average $R^2$ can be computed from the explainer models within an implementation method. We computed the average $R^2$ value for each implementation of LIME with the \data, and these values have been plotted in the middle facet of \autoref{fig:sine-metric-plot} colored by rank from best to worst (darkest to lightest). The average $R^2$ value is highest for the kernel density simulation method and decreases as the number of quantile bins increase. This metric agrees with the average fidelity, and it suggests that the the kernel density method leads to the best fitting explainer models on average.

For the \data, the metrics of average fidelity and average $R^2$ are in perfect agreement \hh{what do you mean by perfect agreement? and how do you use the fidelity measure?} with which simulation methods lead to the recommended LIME methods. The MSEE is in agreement \hh{with ? } in terms of the kernel density method performing well in terms of faithfulness, but it orders the quantile bin methods in the opposite order from the average fidelity and $R^2$ values. This may be due to the MSEE only taking into account the prediction of interest and not the full simulated dataset.

The kernel density method performed well in regards to all three metrics. Recall that \autoref{fig:sine-feature-heatmap} indicated that the LIME kernel density method selected the same feature across all cases in the test dataset for both the first and second features. It appears that a global trend may be the best explanation for this example, which may be reasonable considering that we know that both $x_1$ and $x_2$ are the two features that should be the features used by the random forest to distinguish between response categories.

\section{Application to Bullet Matching Data} \label{application}

\hh{The \data \ is a relatively simple problem where the true decision boundary can be easily visualized and diagnostics for the performance of LIME can directly be compared to ground truth.}
%The \data \ provided a clean example to demonstrate visualizations for diagnosing LIME where we knew the true decision boundary.
\hh{In practice, we usually encounter more complicated situations. The remainder of this section provides a discussion of the visual diagnostics at the example of a practical data problem investigating the similarity of marks on fired bullets.}

\subsection{Bullet Matching Data}

\begin{figure}[!t]
\centering
\includegraphics[width=1.5in]{./figure-static/gun.png}
\includegraphics[width=1.58in]{./figure-static/bullet.png}
\includegraphics[width=3in]{./figure-static/striae.png}
\caption{%Photos depicting markings found on fired bullets.
(Top left) Traditionally rifled gun barrel. Grooves and lands alternate to give bullets a spin during the firing process.
Barrel create markings (striations) on a bullet when fired.
(Top right) Image of a fired bullet. The vertical stripes along the lower half of the bullet show groove and land engraved areas. The land engraved areas contain the microscopic striations created when the bullet passed through the barrel of the gun. (Bottom) Zoom into a land engraved area showing striations (vertical lines). }
\label{fig:bullet}
\end{figure}

\hh{In current practice, forensic firearm  examiners evaluate whether two bullets come from the same source (are fired from the same gun) or from different sources based on microscopic comparison of the striation patterns engraved on bullets during the firing process (see \autoref{fig:bullet}). }
\hh{This process is based on a visual and therefore subjective assessment of the evidence under a comparison microscope. }
%The discipline of firearm identification examines bullets to determine the likelihood that a bullet found in a criminal case was fired from a particular gun. To do this, the bullet from the crime will be compared with a bullet that was known to be fired from the gun under evaluation. When the bullet passes through the gun barrel, microscopic striations are created on the bullet as shown in \autoref{fig:bullet}. The dark vertical striped sections are called lands and are the regions where the striations are located. All of the bullets discussed in this paper have six lands. Markings on bullets fired from the same gun will have similar patterns, so these markings can be compared to determine if two bullets were fired from the same gun. Traditionally, this is a procedure that has been performed by hand. Specially trained examiners visually compare the bullet striations using a comparison microscope that allows the examiners to view both bullets at the same time \citep{nrc:2009}.
\hh{The lack of objective evaluation and the associated absence of established error rates has first been criticized by the National Research Council \cite{nrc:2009} and later by the President's Council of Advisors on Science and Technology \cite{pcast:2016}.}

%The scientific community has encouraged the inclusion of more data driven techniques to be used in forensic investigations \citet{nrc:2009}. These methods would allow for the reporting of a measure of uncertainty in addition to the conclusion drawn from the analysis. This led
In response \citet{hare:2016} proposed an automated machine learning method for bullet matching to complement a visual inspection by  firearm examiners.

\hh{Based on high-resolution topological scans of land engraved areas}
\citet{hare:2016} obtain signatures of  striations from   two bullet lands (\autoref{fig:signatures}). \hh{Features quantifying the similarity of signatures, such as the cross-correlation function, the distance between signatures, and the number of matching striae, are extracted and used to %variables that measure the similarity of the two signatures, and use a
train a random forest model to determine the probability of a comparison resulting from the same source (matching signatures) or from different sources (non-matching signatures).}

\begin{figure}[!t]
\centering
\includegraphics[width=3.5in]{./figure-static/signatures.png}
\label{fig:signatures}
\caption{Bullet signatures extracted from two bullets fired through the same barrel. The two signatures come from the same barrel-land and therefore have very similar patterns. The features used in the random forest from \citet{hare:2016} are different metrics that measure the similarity between two such signatures.}
\end{figure}

<<bullet-data>>=

# Load the hamby data
bullet_train <- read.csv("../data/hamby173and252_train.csv")
bullet_test <- read.csv("../data/hamby224_test.csv")

# Extract the features and order them based on feature importance
bullet_features <- rownames(bulletxtrctr::rtrees$importance)
bullet_features_ordered <-
  data.frame(feature = rownames(bulletxtrctr::rtrees$importance),
             MeanDecreaseGini = bulletxtrctr::rtrees$importance) %>%
  arrange(desc(MeanDecreaseGini)) %>%
  mutate(feature = fct_recode(feature,
                              "CCF" = "ccf",
                              "CMS" = "cms",
                              "Matches" = "matches",
                              "Mismatches" = "mismatches",
                              "Non-CMS" = "non_cms",
                              "Rough Correlation" = "rough_cor",
                              "Distance Std Dev" = "sd_D",
                              "Distance" = "D",
                              "Sum Peaks" = "sum_peaks"))

bullet_features_ordered <- bullet_features_ordered %>%
  mutate(feature = factor(feature, levels = bullet_features_ordered$feature))

@

\hh{The random forest model trained in \citet{hare:2016} is available as object rtrees from the \emph{bulletxtrctr} R package. rtrees is trained on a set of scans obtained from one set of bullets of the James Hamby Consecutively Rifled Ruger Barrel Study \citep{hamby:2009} and based on \Sexpr{dim(bullet_train)[1]} land-to-land comparisons.}
The model was fit using nine features from the training data that measure the similarity between two bullet signatures (CCF, CMS, distance, distance standard deviation, matches, mismatches, non-CMS, rough correlation, sum of peaks), and the response variable (same source) is a binary variable indicating whether the two bullets were fired from the same gun (same source = TRUE) or not (same source = FALSE). Additional details about rtrees and definitions of the features are included in Appendix \ref{hamby-rf}.
\hh{XXX State the problem: we want to know how the model comes up with predictions. Random forest models are relatively simple for a Machine Learning method, but do not have readily available interpretations. RF models also are able to capture local and non-linear structures in the data.
XXX What are diagnostics statisticians would use in this case?
Generally, any method exploring multivariate relationships, such as a (generalized) scatterplot matrix would be a valid route.
Specific to Random Forest models would e.g. be importance of features and parallel coordinate plots.  }

\autoref{fig:bullet-plot-train} shows plots of the distribution of the proportion of same source across the range of each of the nine features. Many of the plots show a location within the range of the feature where the proportion land comparisons from the same source switches from FALSE to TRUE. This suggests that most of the variables are good predictors for determining whether two bullets are from the same source.

\begin{figure}[!t]
<<bullet-plot-train, out.width = '0.5\\textwidth', fig.width = 5, fig.height = 5, warning = FALSE>>=
bullet_train %>%
  select(all_of(bullet_features), samesource) %>%
  pivot_longer(names_to = "feature",
               values_to = "value",
               all_of(bullet_features)) %>%
  select(feature, value, samesource) %>%
  mutate(feature = fct_recode(feature,
                              "CCF" = "ccf",
                              "CMS" = "cms",
                              "Matches" = "matches",
                              "Mismatches" = "mismatches",
                              "Non-CMS" = "non_cms",
                              "Rough Correlation" = "rough_cor",
                              "Distance" = "D",
                              "Distance Std Dev" = "sd_D",
                              "Sum Peaks" = "sum_peaks")) %>%
  ggplot(aes(x = value, fill = samesource, color = samesource)) +
  geom_histogram(position = "fill", bins = 30) +
  facet_wrap( ~ feature, scales = "free", strip.position = "bottom") +
  labs(x = "",
       y = "Proportion",
       fill = "Same Source?",
       color = "Same Source?",
       title = "Hamby Bullet Training Data") +
  theme_bw(base_family = "Times", base_size = 10) +
  theme(legend.position = "bottom",
        strip.placement = "outside",
        strip.background = element_rect(color = "white",
                                        fill = "white")) +
  scale_color_manual(values = c("grey50", "darkorange")) +
  scale_fill_manual(values = c("grey50", "darkorange"))
@
\caption{Distribution of the response variable \hh{explain the spine plots \cite{hummel:1996} a bit - they are non-standard}, same source, for the features used to fit the random forest rtrees. Each bin shows the proportion of land comparisons in the bin that are from the same source indicated by the color. Many of these variables have large ranges where the proportion of same source is either close to 0 or 1, which suggests that these features are good predictors of for determining whether two bullets are from the same source.}
\label{fig:bullet-plot-train}
\end{figure}

Another perspective of the rtrees training data is shown in \autoref{fig:bullet-plot-scatter}. The plots on the diagonal are histograms showing the univariate distributions of the variables. The plots on the off diagonal show the bivariate distribution of the response variable of same source. The feature space has been divided into a grid, and each cell is colored by the proportion of observations in the grid that are a comparison from the same source. Even in the bivariate perspective, there appears to be clear divisions between the bullet comparisons from the same source and different sources.

\begin{figure}[!t]
<<bullet-plot-scatter, out.width = '0.5\\textwidth', fig.width = 9, fig.height = 9, warning = FALSE>>=
ggplot(data = bullet_train %>%
         mutate(samesource = as.numeric(samesource)) %>%
         rename("CCF" = "ccf", "CMS" = "cms", "Matches" = "matches",
           "Mismatches" = "mismatches", "Non-CMS" = "non_cms",
           "Rough Correlation" = "rough_cor", "Distance Std Dev" = "sd_D",
           "Distance" = "D", "Sum Peaks" = "sum_peaks")) +
  stat_summary_2d(mapping = aes(x = .panel_x,
                                y = .panel_y,
                                z = samesource),
                  bins = 50,
                  fun = mean) +
  geom_autohistogram() +
  facet_matrix(vars(bullet_features_ordered$feature),
               layer.diag = 2,
               switch = "both") +
  scale_fill_gradient2(low = "grey50",
                       high = "darkorange",
                       midpoint = 0.5) +
  theme_bw(base_family = "Times", base_size = 10) +
  theme(strip.placement = "outside",
        strip.background = element_rect(color = "white",
                                        fill = "white"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.position = "bottom") +
  labs(fill = "Proportion of Same Source Observations")
@
\caption{Bivariate visualizations of the rtrees training data. The plots on the off diagonal were created by dividing the feature space into a grid, and the color of each cell represents the proportion of observations in the cell that are from the same source. This shows clear divisions in the bivariate perspective between same source and different source comparisons based on the feature values. Additionally, histograms of the features are shown in the plots on the diagonal that depict the univariate distributions of the features.}
\label{fig:bullet-plot-scatter}
\end{figure}

\begin{figure}[!b]
<<bullet-plot-rfvi, out.width = '0.5\\textwidth', fig.width = 3.5, fig.height = 1.5>>=
ggplot(bullet_features_ordered %>%
         mutate(feature = factor(feature, levels = rev(levels(feature)))),
       aes(x = MeanDecreaseGini, y = feature)) +
  geom_col() +
  labs(y = "Feature",
       x = "Variable Importance") +
  theme_bw(base_size = 10, base_family = "Times")
@
\caption{Variable importance plot for the random forest fit to the bullet matching dataset. The variables of rough correlation and CCF have the highest variable importance values followed by matches and mismatches.}
\label{fig:bullet-plot-rfvi}
\end{figure}

\begin{figure*}[!b]
<<bullet-plot-rfpcp, out.width = '\\textwidth', warning = FALSE>>=

# Create (or load) the parallel coordinate plot
if (file.exists("./figure-static/bullet_pcp.png")) {

  # Load and print the plot
  knitr::include_graphics("./figure-static/bullet_pcp.png")

} else {

  # Create the plot
  bullet_pcp <- bullet_train %>%
    select(all_of(bullet_features), samesource, rfscore) %>%
    bind_rows(bullet_test %>%
                select(all_of(bullet_features), samesource, rfscore),
              .id = "set") %>%
    mutate(set = fct_recode(set,
                            "Training Set" = "1",
                            "Testing Set" = "2"),
           samesource = fct_recode(factor(samesource),
                                  "Same Source = TRUE" = "TRUE",
                                  "Same Source = FALSE" = "FALSE")) %>%
    rename("CCF" = "ccf", "CMS" = "cms", "Matches" = "matches",
           "Mismatches" = "mismatches", "Non-CMS" = "non_cms",
           "Rough Correlation" = "rough_cor", "Distance Std Dev" = "sd_D",
           "Distance" = "D", "Sum Peaks" = "sum_peaks") %>%
    na.omit() %>%
    ggplot(aes(color = rfscore)) +
    geom_pcp(aes(vars = vars(bullet_features_ordered$feature)),
             alpha = 0.2) +
    facet_grid(set ~ samesource) +
    scale_color_gradient2(low = "grey50",
                          high = "darkorange",
                          midpoint = 0.5) +
    theme_bw(base_family = "Times", base_size = 10) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          strip.placement = "outside",
          strip.background = element_rect(color = "white",
                                          fill = "white")) +
    labs(x = "Features Ordered by Random Forest Variable Importance \n(highest to lowest from left to right)",
         y = "Scaled Feature Values",
         color = "Random \nForest \nProbability")

  # Save the plot
  ggplot2::ggsave(plot = bullet_pcp,
                  filename = "./figure-static/bullet_pcp.png",
                  width = 7.5,
                  height = 3.5,
                  units = "in")
}

@
\caption{Parallel coordinate plots of rtrees training and testing data. The training data are included in the plots on the top row, and the testing data are included in the plots on the bottom row. The left column contains the observations which are know to be comparisons of lands that are not from the same gun, and the known same source comparisons are on the right. The y-axis shows the standardized feature values, and the x-axis shows the features used to fit the random forest (ordered by feature importance). Each line corresponds to a comparison, and the color of the line represents the associated random forest probability. These figures show a clear relationship between the feature values and the probability returned by the random forest.}
\label{fig:bullet-plot-rfpcp}
\end{figure*}

\autoref{fig:bullet-plot-rfvi} shows the variable importance values produced by the rtrees. \kgc{KG: Look up what value is being used as the importance and describe it here.} Rough correlation and CCF have the highest variable importance values, and non-CMS and CMS have the lowest variable importance values.

rtrees was tested on another set of bullets from the Hamby study with \Sexpr{dim(bullet_test)[1]} rows of land comparisons. \autoref{fig:bullet-plot-rfpcp} shows parallel coordinate plots of the rtrees training (top row) and testing (bottom row) datasets. The plots on the left contain comparisons know to be from from different sources, and the plots on the right contain comparisons know to be from the same source. Each line represents one observation in the data, and the color of the line represents the by the corresponding random forest probability. The standardized feature values are plotted on the y-axis, and the features are plotted on the x-axis, which are ordered from left to right from the highest to lowest random forest feature importance.

The majority of observations with random forest probabilities close to 1 have a clear pattern of corresponding feature values as can be seen in the plots where same source is known to be true. The observations where the random forest is wrong in returning high probabilities when same source is known to be true (i.e. same source is true but the random forest probabilities are between 0 and 0.5) have feature values that reflect those of observations where same source is known to be false as seen in the plots on the left. These plots provide insight into why the random forest is producing poor random forest probabilities for these observations.

Since firearm identification is commonly used as evidence for convictions in court cases, it is important to be able to understand and assess the model that is used to quantify the probability that a bullet was fired from a gun. An application of LIME to rtrees could provide an understanding of the key variables used by the random forest model to make a prediction. However, just as it is important to assess the random forest model for this high-stakes application, it is also important to assess the LIME explanations to make sure they are providing a trustworthiness understanding of the random forest model. We will apply LIME to rtrees and use our visual diagnostics to assess different implementations of LIME.

\subsection{Application of LIME to Bullet Matching Data}

<<bullet-lime>>=

# Apply LIME to all but two cases without returning the permutations
if (file.exists("../data/hamby_lime.rds")){

  # Load the files
  #bullet_lime_noperms <- readRDS("../data/hamby_lime.rds")
  bullet_explain_noperms <- readRDS("../data/hamby_explain.rds")

} else {

  # Apply lime with various input options to the hamby data
  bullet_lime_explain_noperms <- apply_lime(
    train = bullet_train %>% select(all_of(bullet_features)),
    test = bullet_test %>%
      select(all_of(bullet_features)) %>%
      na.omit(),
    model = bulletxtrctr::rtrees,
    label = as.character(TRUE),
    n_features = 3,
    sim_method = c('quantile_bins', 'equal_bins',
                   'kernel_density', 'normal_approx'),
    nbins = 2:6,
    feature_select = "auto",
    dist_fun = "gower",
    kernel_width = NULL,
    gower_pow = c(0.5, 1, 10),
    return_perms = FALSE,
    all_fs = FALSE,
    seed = 20190914)

  # Separate the lime and explain parts of the results
  bullet_lime_noperms <- bullet_lime_explain_noperms$lime
  bullet_explain_noperms <- bullet_lime_explain_noperms$explain

  # Save the output objects
  saveRDS(object = bullet_lime_noperms,
          file = "../data/hamby_lime.rds")
  saveRDS(object = bullet_explain_noperms,
          file = "../data/hamby_explain.rds")

}

@

<<bullet-lime-perms>>=

# Specify two cases of interest
bullet_poi_match <- unique(bullet_explain_noperms$case)[c(325)]
bullet_poi_nonmatch <- unique(bullet_explain_noperms$case)[c(20)]

# Apply LIME to two cases with the permutations returned
bullet_lime_explain_perms <- apply_lime(
  train = bullet_train %>% select(all_of(bullet_features)),
  test = bullet_test %>%
    filter(case %in% bullet_poi_match) %>%
    bind_rows(bullet_test %>%
    filter(case %in% bullet_poi_nonmatch)) %>%
    select(all_of(bullet_features)),
  model = bulletxtrctr::rtrees,
  label = as.character(TRUE),
  n_features = 3,
  sim_method = c('quantile_bins', 'equal_bins', 'kernel_density', 'normal_approx'),
  nbins = 3,
  feature_select = "auto",
  dist_fun = "gower",
  kernel_width = NULL,
  gower_pow = 0.5,
  return_perms = TRUE,
  all_fs = FALSE,
  seed = 20190914)

# Separate the lime and explain parts of the results
bullet_lime_perms <- bullet_lime_explain_perms$lime
bullet_explain_perms <- bullet_lime_explain_perms$explain %>%
  mutate(case = ifelse(case == 1,
                       bullet_poi_match,
                       bullet_poi_nonmatch))

@

<<bullet-lime-combined>>=

# Determine the implementation and case number of the poi
# in the no_perms data
poi_cases_no_perms <- bullet_explain_noperms %>%
  filter(case %in% c(bullet_poi_match, bullet_poi_nonmatch),
         nbins %in% c(3, NA),
         gower_pow == 0.5) %>%
  select(case, implementation) %>%
  unique()

# Join the no perms data (with poi removed) with the
# perms data (perms removed)
bullet_explain <- bullet_explain_noperms %>%
  anti_join(poi_cases_no_perms,
            by = c("implementation", "case")) %>%
  bind_rows(bullet_explain_perms %>%
              select(-perms_raw, -perms_numerified,
                     -perms_pred_simple, -perms_pred_complex,
                     -weights))

@

\begin{figure*}[!th]
<<bullet-feature-heatmap, out.width = '\\textwidth', fig.width = 18, fig.height = 10.5>>=

# Create a feature heatmap
feature_heatmap(bullet_explain %>%
                  mutate(label = as.factor(label)),
                facet_var = na.omit(bullet_test$samesource),
                order_method = "PCA") +
  scale_fill_gretchenalbrecht(palette = "last_rays",
                              discrete = TRUE) +
  theme_bw(base_family = "Times", base_size = 10) +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) +
  labs(y = "Case")

@
\caption{Feature heatmap of the 36 LIME implementations applied to the bullet comparison data test set. In addition to faceting the results by simulation method and order a feature was selected by LIME as done in \autoref{fig:sine-feature-heatmap}, this plot has been faceted by the Gower power and whether the the observation is from a match (TRUE) or non-match (FALSE). This plot shows several key insights about the LIME explanations. First, the features selected by LIME for the density simulation methods are mostly the same for all implementations and all cases. Second, the features selected by LIME for the bin based methods are affected by the number of bins but not the Gower power. Third, the explanations produced by LIME using bin based methods result in different important features for the matches and non-matches. \kgc{***Need to rotate the facet labels, so I can make the text bigger.}}
\label{fig:bullet-feature-heatmap}
\end{figure*}

It was of interest to see how the explanations from LIME varied across the all sampling methods with different Gower exponents when applied to the bullet matching data. LIME was applied to each prediction from the bullet test data obtained from the 'rtrees' random forest model for each of the four sampling methods (equally spaced bins, quantile bins, kernel density estimation, and normal approximation). For each of the bin based sampling methods, LIME was applied for 2 to 6 bins. It was decided to use 6 bins as the maximum, since the larger the number of bins, the more complex the explanation becomes. Each simulation method was implemented three times with Gower exponents of 0.5, 1, and 10. Thus, a total of $12\times 3=36$ different implementations of LIME were performed. These implementations of LIME were performed using our R package \emph{limeaid}. Each implementation was set to return 3 features by LIME and feature selection was performed using the highest weights method.

\subsection{LIME Assessment Visualizations}

\begin{figure*}[!t]
<<bullet-lime-expls, out.width = '\\textwidth', warning = FALSE, fig.width = 12, fig.height = 5.5>>=

bullet_poi_nonmatch_exps <- bullet_explain %>%
  filter(sim_method == "quantile_bins",
         gower_pow == 1,
         case == bullet_poi_nonmatch) %>%
  mutate(case = paste0(case, ", ", nbins, " Quantile Bins"))

nb2 <- plot_features(bullet_poi_nonmatch_exps %>% filter(nbins == 2)) +
  scale_fill_manual(values = c("darkorange", "grey50"))
nb3 <- plot_features(bullet_poi_nonmatch_exps %>% filter(nbins == 3)) +
  scale_fill_manual(values = c("darkorange", "grey50"))
nb4 <- plot_features(bullet_poi_nonmatch_exps%>% filter(nbins == 4)) +
  scale_fill_manual(values = c("darkorange", "grey50"))
nb5 <- plot_features(bullet_poi_nonmatch_exps %>% filter(nbins == 5)) +
  scale_fill_manual(values = c("darkorange", "grey50"))
nb6 <- plot_features(bullet_poi_nonmatch_exps %>% filter(nbins == 6)) +
  scale_fill_manual(values = c("darkorange", "grey50"))

feat_ord <- bullet_poi_nonmatch_exps %>%
  count(feature) %>%
  arrange(n) %>%
  pull(feature)

bc <- bullet_poi_nonmatch_exps %>%
  mutate(feature = factor(feature, levels = feat_ord)) %>%
  mutate(feature = fct_recode(feature,
         "Rough Correlation" = "rough_cor",
         "Non-CMS" = "non_cms",
         "Sum of Peaks" = "sum_peaks",
         "Matches" = "matches",
         "CCF" = "ccf",
         "Mismatches" = "mismatches",
         "CMS" = "cms")) %>%
  ggplot(aes(feature)) +
  geom_bar() +
  coord_flip() +
  theme_bw(base_family = "Times") +
  labs(x = "Feature",
       y = "Number of Implementations \nwith Feature Selected",
       title = "Features Selected by LIME \nfor 2 to 6 Quantile Bins")

plot_grid(nb2, nb3, nb4, nb5, nb6, bc, nrow = 2)
@
\caption{Plots of the LIME explanations associated with one observation in the bullet comparison test data from the implementations using 2 to 6 quantile bins. A bar chart showing the number of times a feature was selected by LIME in these five explanations is also included in the bottom right corner.}
\label{fig:bullet-lime-expls}
\end{figure*}

To get an overview of the LIME explanations from the 36 implementations, we consider our heatmap diagnostic plot for comparing the LIME implementations first shown in \autoref{fig:bullet-feature-heatmap}. The plot facets the features selected in the LIME explanations by the simulation method, the Gower power, the order the feature was chosen, and whether the observation is from a known match or non-match of bullet signatures. This plot highlights several key features of the LIME explanations from the bullet matching dataset.

First of all, the density simulation methods produced the same explanations for almost all cases and LIME implementation methods. As a result, the LIME explanations for the density implementation methods are global and not local. Second, within a bin based simulation method, the features selected by LIME for an observation often vary based on the number of bins used but do not appear to vary based on the Gower power used. Especially with the equal bin explanations, there are vertical stripes that suggest a dependence of the LIME explanations on the number of bins used. The vertical stripes are not as apparent with the quantile bins. Lastly, there are clear differences between the LIME explanations for the cases that are matches and those that are not matches which are produced by the bin based simulation methods. This provides evidence that suggests that the features which the random forests uses to classify a match are different from the features used by the random forest to classify a non-match.

The most important insight \autoref{fig:bullet-feature-heatmap} highlights is the dependence of the explanations on the LIME implementation method for many of the observations in the test data. To better understand how an explanation can vary based on the implementation method, we consider the explanations for one observation across several LIME implementations. The observation we consider from the bullet comparison test data is known \Sexpr{ifelse(bullet_test %>% filter(case == unique(bullet_explain$case)[20]) %>% pull(samesource) == FALSE, print("to not be a match"), print("to be a match"))} and has a random forest score of \Sexpr{bullet_test %>% filter(case == unique(bullet_explain$case)[20]) %>% pull(rfscore)}. \autoref{fig:bullet-lime-expls} shows the explanation plots from \emph{lime} for the LIME implementations using 2 to 6 quantile bins associated with this case from the test data. A bar chart showing the number of times a feature was chosen by one of these implementations is also included.

Rough correlation is the feature that appears the most in the explanations (4 out of 5 implementations). Distance and distance standard deviation are never selected. As the bar chart shows, 7 of the 9 features used to fit the random forest were selected at least once.by LIME. The set of features selected by LIME are different for each implementation except for 4 and 5 bins. However, the order in which the features are selected for the 4 and 5 bins differ, but the lengths of the bars for rough correlation and sum of peaks are very similar for both explanations. The $R^2$ values (indicated as the explanation fit in the figure) range from 0.032 (6 bins) to 0.35 (2 bins). The implementation with 2 bins has the best $R^2$ value, and this is the only explanation where the top feature contradicts a prediction of a match, which agrees with the random forest prediction that provides evidence that that two bullets are not a match. All of the other explanations have a top feature that supports a match, which does not agree with the random forest prediction. However, the second and third feature selected by LIME in the 2 bin case, support a match. Based on the variation in explanations across implementation and the features selected that support a match, which disagree with the random forest prediction, it is not clear which explanation to trust, if any.

\begin{figure*}[!t]
<<bullet-metric-plot, out.width = '\\textwidth', warning = FALSE, fig.width = 10, fig.height = 4>>=

# Create a metric comparison plot
metric_plot(bullet_explain %>% mutate(label = as.factor(label))) +
  theme_bw(base_family = "Times") +
  scale_color_gradient(low = "grey10", high = "grey90") +
  labs(color = "Rank \n(within \na metric)")

@
\caption{Plot of LIME assessment metrics for the 36 different implementations of LIME applied to the bullet comparison data test set. The shape of the points represents the power used for the Gower distance calculation, and the color of the points represents the rank associated with that observation within a metric. The density simulation methods perform well for all metrics, but the bin based metrics often do not agree in terms of performance across metrics.}
\label{fig:bullet-metric-plot}
\end{figure*}

To try to identify the LIME implementation method with the most trustworthy set of explanations, we created an assessment metric plot shown in \autoref{fig:bullet-metric-plot}. The three metrics of average fidelity, average $R^2$, and MSEE were computed for each of the simulation methods and Gower power used to implement LIME. The plot is faceted by the simulation method, and the shape of a point represents the Gower power. The color of a point represents the rank within a metric. That is, the darker a point, the better performance of that implementation method based on the metric.

The density simulation methods performed well across all implementation methods. This is an interesting result, since \autoref{fig:bullet-feature-heatmap} shows that the density methods results in global explanations. The metric values for the bin based implementation methods do not agree across metrics. For example, 2 and 3 quantile bins performed well according to the average $R^2$ but poorly according to MSEE. As a result, with the bin based methods, it is difficult to know which method to recommend. When considering the metrics across the Gower power used, the implementations using a power of 0.5 perform best or as well as the other powers in across all simulation methods. This suggests that the power that leads to a more global explanation is preferred by LIME in this example.

Unfortunately, \autoref{fig:bullet-feature-heatmap} leaves us without a clear indication of which set of explanations to use to explain the random forest. Perhaps we can say that the kernel density method, 3 equal bins, and 3 quantile bins are some of the best performing methods. To better understand the explanations provided by these three methods, we take a closer look at explanations from these methods for two observations of interest where one is a known non-match (case \Sexpr{bullet_poi_nonmatch}) and the other is a known match (case \Sexpr{bullet_poi_match}).

Figures \ref{fig:bullet-eois-nonmatch} and \ref{fig:bullet-eois-match} contain plots that provide this closer look for the known non-match and match, respectively. The top row of plots in each figure are the explanation plots from \emph{lime}. The bottom row of plots show scatterplots of the features selected by LIME colored by the random forest model prediction. The location of the prediction of interest is indicated on the scatterplots by a diamond, and black solid lines are included on the plots representing the bin divisions for implementations using bins. The bottom row plots are created using \emph{limeaid}. The plots within a column are associated with one of the three implementation methods (kernel density, 3 equal bins, or 3 quantile bins).

The scatterplots provide a visualization that helps to explain the LIME explanation. For example, consider the explanation for case \Sexpr{bullet_poi_nonmatch} when 3 quantile bins were used. The explanation plot from \emph{lime} shows that case \Sexpr{bullet_poi_nonmatch} having an observed CCF value greater than 0.320 supports a random forest prediction in favor of a match. The scatter plots show that many of the simulated values with CCF greater then 0.320 have random forest predictions greater than 0.5. Additionally, the LIME explanation indicates that a value of matches less than or equal to 1.66 contradicts a prediction in favor of a match. The scatter plots shows that almost all simulated values with a value of matches less than or equal to 1.66 have random forest predictions close to 0. Similar statements can be made about the 3 equal bin explanation for this case and the bin based implementations for the known match observation explanations. \kgc{**Consider creating a different set of plots for the kernel density (and normal approximation) methods that plot the rfscores versus the features and include the model.}

While the scatterplots provide visual explanations for the LIME explanations, some of them indicate that LIME falls short of a good explanation of the random forest predictions. Again, consider the explanation for case 325 when 3 quantile bins were used. From looking at the scatter plot of CCF versus matches, a better explanation for the random forest prediction would be to say that because the prediction of interest has a value of CCF less than 0.8 (approximately) and a value of matches less than 7 (approximately), the random forest is providing a prediction that supports a non-match. The relationship between ccf and rough correlation does not provide much evidence to support the random forest prediction one way or the other due to the mixture of random forest predictions ranging from 0 to 1 in most regressions, but there is a pentagon shaped region at the bottom of the scatter plot of matches versus rough correlation that the prediction of interest falls in that supports the random forest prediction of a non-match.

<<bullet-eoi-plots, message = FALSE>>=
bullet_explain_perms <- bullet_explain_perms %>%
  mutate(case = ifelse(case == bullet_poi_nonmatch,
                       paste(case, "(non-match)"),
                       paste(case, "(match)")))

eoi1_3qb <- eoi_plot(bullet_explain_perms[1:3,], alpha = 0.9, weights = FALSE) +
  scale_color_gradient2(low = "grey50",
                        high = "darkorange",
                        midpoint = 0.5,
                        limits = c(0, 1)) +
  scale_fill_gradient2(low = "grey50",
                        high = "darkorange",
                        midpoint = 0.5,
                        limits = c(0, 1)) +
  theme_bw(base_family = "Times", base_size = 8) +
  theme(strip.placement = "outside",
        strip.background = element_rect(color = "white",
                                        fill = "white"))

eoi2_3qb <- eoi_plot(bullet_explain_perms[4:6,], alpha = 0.9, weights = FALSE) +
  scale_color_gradient2(low = "grey50",
                        high = "darkorange",
                        midpoint = 0.5,
                        limits = c(0, 1)) +
  scale_fill_gradient2(low = "grey50",
                        high = "darkorange",
                        midpoint = 0.5,
                        limits = c(0, 1)) +
  theme_bw(base_family = "Times", base_size = 8) +
  theme(strip.placement = "outside",
        strip.background = element_rect(color = "white",
                                        fill = "white"))

eoi1_3eb <- eoi_plot(bullet_explain_perms[7:9,], alpha = 0.9, weights = FALSE) +
  scale_color_gradient2(low = "grey50",
                        high = "darkorange",
                        midpoint = 0.5,
                        limits = c(0, 1)) +
  scale_fill_gradient2(low = "grey50",
                        high = "darkorange",
                        midpoint = 0.5,
                        limits = c(0, 1)) +
  theme_bw(base_family = "Times", base_size = 8) +
  theme(strip.placement = "outside",
        strip.background = element_rect(color = "white",
                                        fill = "white"))

eoi2_3eb <- eoi_plot(bullet_explain_perms[10:12,], alpha = 0.9, weights = FALSE) +
  scale_color_gradient2(low = "grey50",
                        high = "darkorange",
                        midpoint = 0.5,
                        limits = c(0, 1)) +
  scale_fill_gradient2(low = "grey50",
                        high = "darkorange",
                        midpoint = 0.5,
                        limits = c(0, 1)) +
  theme_bw(base_family = "Times", base_size = 8) +
  theme(strip.placement = "outside",
        strip.background = element_rect(color = "white",
                                        fill = "white"))

eoi1_kd <- eoi_plot(bullet_explain_perms[13:15,], alpha = 0.9, weights = FALSE) +
  scale_color_gradient2(low = "grey50",
                        high = "darkorange",
                        midpoint = 0.5,
                        limits = c(0, 1)) +
  scale_fill_gradient2(low = "grey50",
                        high = "darkorange",
                        midpoint = 0.5,
                        limits = c(0, 1)) +
  theme_bw(base_family = "Times", base_size = 8) +
  theme(strip.placement = "outside",
        strip.background = element_rect(color = "white",
                                        fill = "white"))

eoi2_kd <- eoi_plot(bullet_explain_perms[16:18,], alpha = 0.9, weights = FALSE) +
  scale_color_gradient2(low = "grey45",
                        high = "darkorange",
                        midpoint = 0.5,
                        limits = c(0, 1)) +
  scale_fill_gradient2(low = "grey45",
                        high = "darkorange",
                        midpoint = 0.5,
                        limits = c(0, 1)) +
  theme_bw(base_family = "Times", base_size = 8) +
  theme(strip.placement = "outside",
        strip.background = element_rect(color = "white",
                                        fill = "white"))

pf1_3qb <- plot_features(bullet_explain_perms[1:3,]) +
  scale_fill_manual(values = c("darkorange", "grey50"))
pf2_3qb <- plot_features(bullet_explain_perms[4:6,]) +
  scale_fill_manual(values = c("darkorange", "grey50"))
pf1_3eb <- plot_features(bullet_explain_perms[7:9,]) +
  scale_fill_manual(values = c("darkorange", "grey50"))
pf2_3eb <- plot_features(bullet_explain_perms[10:12,]) +
  scale_fill_manual(values = c("darkorange", "grey50"))
pf1_kd <- plot_features(bullet_explain_perms[13:15,]) +
  scale_fill_manual(values = c("darkorange", "grey50"))
pf2_kd <- plot_features(bullet_explain_perms[16:18,]) +
  scale_fill_manual(values = c("darkorange", "grey50"))
@

\begin{figure*}[!htbp]
<<bullet-eois-nonmatch, out.width = '\\textwidth', fig.width = 12, fig.height = 6.25, message = FALSE>>=
# Join the plots
plot_grid(pf2_3qb, pf2_3eb, pf2_kd,
          eoi2_3qb, eoi2_3eb, eoi2_kd,
          nrow = 2,
          rel_heights = c(0.45, 0.55))
@
\caption{Plots of LIME explanations for one case in the test data that is a known non-match. Each column contains plots associated with a different implementation (3 quantile bins, 3 equal bins, or kernel density). The top row of plots are the explanation plots from \emph{lime}. The bottom row shows scatter plots of the simulated data associated with the prediction of interest. The features plotted are those chosen by LIME in the explanations, and the points are colored by the the random forest predictions. Lines showing the divisions created in the feature space by the bin based LIME methods are included as solid black lines. The scatter plots can be used to better understand the LIME explanation and assess if it is a good explanation.}
\label{fig:bullet-eois-nonmatch}

\vspace*{\floatsep}

<<bullet-eois-match, out.width = '\\textwidth', fig.width = 12, fig.height = 6.25, message = FALSE>>=
# Join the plots
plot_grid(pf1_3qb, pf1_3eb, pf1_kd,
          eoi1_3qb, eoi1_3eb, eoi1_kd,
          nrow = 2,
          rel_heights = c(0.45, 0.55))
@
\caption{Plots with the same structure as \ref{fig:bullet-eois-match} but for an observation from the test data that is a known match.}
\label{fig:bullet-eois-match}
\end{figure*}

The scatter plots of the kernel density implementations for both the match and non-match case show that almost all of the simulated values have random forest predictions less than 0.5, which provide evidence in favor of a non-match. It appears that simulation method is not providing enough values to cover the feature space that hit regions where the random forest provides predictions above 0.5. The training data has a much smaller amount of matches (\Sexpr{sum(bullet_train$samesource)}) than non-matches (\Sexpr{sum(bullet_train$samesource == FALSE)}), and this simulation method is clearly affected by this imbalance in the two classification categories. Furthermore, this may be the cause of the minimal amount of variability in the LIME explanations across all of the cases in the test data.

Without applying multiple implementations LIME to the bullet test data or viewing diagnostic plots of the LIME explanations, it may be very possible to formulate reasons why the LIME explanations make sense. However, the sequence of plots in this section (Figures \ref{fig:bullet-feature-heatmap}, \ref{fig:bullet-lime-expls}, \ref{fig:bullet-metric-plot}, \ref{fig:bullet-eois-match}, and \ref{fig:bullet-eois-nonmatch}) suggest that we should be cautious to trust any of these LIME explanations. While some of them provide an explanation that may be reasonable, there could be better explanations (as seen in the 3 quantile bin case of \autoref{fig:bullet-eois-match}), and some of them provide explanations that make no sense (as seen in \autoref{fig:bullet-lime-expls}). It appears that either LIME needs to be further tuned to provide trustworthy and good explanations, or a different approach may provide better insight. As glimpsed with the scatter plots in Figures \ref{fig:bullet-eois-match} and \ref{fig:bullet-eois-nonmatch}, the more traditional approach to explanation random forest predictions by plotting the random forest predictions over the feature space (partial dependence plots), could provide better insight into the complex model with no need to assess the explanation method if the sampling method is well chosen.

\section{Discussion} \label{discussion}

\kgc{Need to add a discussion on using our visualizations in situations without tabular data or a dichotomous response variable.}\\
\\
In this paper, we have presented visualizations that depict the steps in the LIME algorithm (\autoref{procedure}) and diagnose LIME explanations (Sections \ref{set-visuals} and \ref{implementation-visuals}). Our intentions with these visualizations were to provide insight on how LIME works, assess the ability of the explainer model to capture the complex predictive model, and compare LIME explanations produced by different tuning parameters. While the visualizations accomplish these tasks, they also expose examples of the failings of LIME. To address the discovered failings of LIME, we will reconsider each of the claims about the performance of LIME made by \citep{ribeiro:2016} (interpretability, faithfulness, linearity, and localness) in light of the insights gained from the diagnostic visualizations.

As previously discussed, the \textbf{interpretability} of the LIME explanations can be controlled by the complexity of the explainer model. For example, the number of bins selected for simulation can control the interpretability of the explanations. If too many bins are selected, the bin range that is reported in the LIME explanation will be too small to be meaningful in the context of the feature. An appropriate choice of the number of bins will keep the bin range meaningful. Thus, the claim of interpretability does not need to be assessed using the visualizations. However, diagnostic visualizations do present a different perspective on the meaning of interpretability.

\kgc{**Need to rework this paragraph and the next two. The ideas are here, but they are worded very poorly.} Even though an explanation will be interpretable as long as the complexity of the explainer model is appropriately chosen, the presentation of a LIME explanation in the key visual used by \citep{ribeiro:2016} (shown in \autoref{fig:sine-plot-poi}) could lead to an over simplified interpretation of the explainer model. Without a solid understanding of the details behind the fitting of the explainer model, the deeper meaning of the bars in the figure is lost.

It is customary to interpret this plot by stating that the direction of the bar supports or contradicts the classification in a certain category, and the length of the bar signifies the importance of the involvement of a feature in the prediction. While these interpretations are correct, the lengths of the bars represent the coefficients of the ridge regression model used as the explainer model, which contain more meaning than just the direction of support and importance of a feature. The bars indicate how much the average complex model prediction estimated by the linear explainer model changes based on a change in the feature. Furthermore, this interpretation changes depending on whether a bin based or density simulation method was used (i.e the change in the average complex model prediction between an observation in the same bin as the case of interest and an observation not in the same bin versus the change in the mean complex model prediction for a change in the feature by one standardized unit).

Thus, even though an explainer model may be interpretable, the explanation it produces may be under-interpreted or misinterpreted without an understanding of the process that produced the explanation. Supplementing \citep{ribeiro:2016}'s compact visualization of the explanation with visualizations of the explanation that depict the simulated data and the explainer model (such as Figures \ref{fig:sine-plot-step3ab} and \ref{fig:bullet-eois-match}) promotes a full interpretation of the explanation. This is done by providing reminders of the meaning of the lengths of the bars in addition to a visual connection between complex model predictions and the estimated coefficients of the explainer model.

Even with an explainer model that is interpreted correctly, the interpretation is worthless if the explainer model is not \textbf{faithful} to the complex model. This claim can be easily assessed using the diagnostic plots suggested in this paper. Many of the visualizations in this paper highlight problems with the faithfulness of the explainer models.

The visualizations that incorporate the bins along with the complex model predictions (Figures \ref{fig:fig:sine-plot-step1ab}, \ref{ fig:sine-plot-step1c}, \ref{fig:sine-plot-step3ab}, \ref{fig:sine-plot-compare-bins}, \ref{fig:bullet-eois-match}, and \ref{fig:bullet-eois-nonmatch}) highlight issues that accompany the choice to use bin based simulation methods. These visualizations allow for a comparison of the size of the bins to the complex model's decision boundaries. All of the examples in this paper show cases where the bins do not accurately capture the classification boundaries near the predictions of interest of the random forest models by oversimplifying the model. Using less bins would clearly not help improve the faithfulness of the explainer model in these examples, and while an increase in bins would lead to a finer resolution of the random forest classification boundaries, interpretability of the explainer model would quickly be lost. The bins used by LIME are not flexible enough to capture the different sized division boundaries of the random forests shown in this paper. Perhaps this could be improved by allowing the bin creation to account for the relationships between the features and response variable or a different number of bins for each feature.

The figures referenced in the previous paragraph from the \data \ example are all based on the implementation of LIME using a set of tuning parameters. From the use of the feature heatmap, we found that different sets of tuning parameters can produce different explanations. It makes sense that one set of tuning parameters could lead to a more faithful explainer model than another. As a result, we proposed a visual comparison of two faithfulness metrics (MSEE and average fidelity). The examples of faithfulness metric comparisons in this paper (Figures \ref{fig:sine-metric-plot} and \ref{fig:bullet-metric-plot}) both produced confusing results. In both examples, the density based simulation methods resulted in the best or close to the best performance even though the feature heatmaps (Figures \ref{fig:sine-feature-heatmap} and \ref{fig:bullet-feature-heatmap}) showed that the density simulation methods produced global explanations with no variation in features selected by LIME. For the bin based simulation methods, the two metrics often did not agree or contradicted one another, which makes it difficult to decide on a recommendation of a set of tuning parameters that produces the explanations with the most faithful explainer model.

The metric comparison plot also includes a comparison of average $R^2$ values, which is a metric that can be used to assess the claim of \textbf{linearity}. Most of the average $R^2$ values in the examples from this paper are below 0.5 suggesting a poor linear fit of the explainer models. The poor linear fit of the explainer model was also seen with the residual plot (\autoref{fig:sine-plot-step2cd}).

The final claim, \textbf{localness}, is also addressed by the feature heatmap and metric comparison plot. As stated, the feature heatmap revealed that the density simulation methods in the examples of this paper resulted in global explanations where the same features were repeatedly chosen across all (or almost all) observations in the set of explanations. This finding agrees with that of \citep{laugel:2019} who also found LIME produced global explanations with the normal approximation simulation method. For the bin based simulation methods in the bullet data example, the feature heatmap showed that the features chosen for the explanations varied between the two classification categories (match versus non-match). This is an interesting finding that suggests that different features can play a role in the predictions of observations in different response categories, but the patterns of features selected by LIME within a classification category do not vary. Again, this is a suggestion of global explanations. Furthermore, while the metric comparison plot in the bullet example did not provide agreement between metrics on a best bin based method, all metrics agree that a Gower power of 0.5 for computing the model weights associated with distance of a simulated data point from the prediction of interest was best. This suggests that a less local explanation provided a better explanation of the performance of the random forest.

Some of the visualizations in the paper generalize easily to any application of LIME such as the feature heatmap and metric plot. Other plots such as the visualizations of the LIME procedure would require extensions such as the use of scatterplot matrices to compare explanations with more than two features. The addition of interactivity to the diagnostic plots would provide additional enhancement of the assessment process. For example, a diagnostic plot that provides a summary of multiple LIME explanations, such as the feature heatmap, could be displayed and clicked on to reveal more detailed figures associated with individual predictions of interest, such as plots of the simulated data and explainer model.

While it would be ideal if LIME could be used as a method to provide easily understandable explanations for black-box models as \citep{ribeiro:2016} claim, that dream is not yet a reality. The examples using diagnostic plots to assess LIME in this paper show frequent issues with LIME. The practice of assessing the performance of methods has once again shown its importance. We hope that our plots provide motivation to assess LIME explanations, to not blindly use the default settings (even if it is not clear which tuning parameters to use), and perhaps to encourage work on improving LIME, so that it can be a lime and not a lemon.

\kgc{Need to work this into the discussion: We acknowledge that not all prediction problems will produce trends as easy to interpret as the visualizations we have shown in the section, but we still believe that visualizations of the procedure can provide insight into the quality of the LIME explanation. We hope these figures will provide a starting point (if not an ending point) for the assessment of a single LIME explanation. Perhaps the inability to interpret a plot is itself telling, or the act of creating extensions of these visualizations to work with a different scenarios will lead to an understanding of the trustworthiness of the explanation.}

\section*{Acknowledgments}

This is acknowledgment text. Provide text here.

\subsection*{Author contributions}

This is an author contribution text. This is an author contribution text. This is an author contribution text. This is an author contribution text. This is an author contribution text.

\subsection*{Financial disclosure}

None reported.

\subsection*{Conflict of interest}

The authors declare no potential conflict of interests.

\section*{Supporting information}

The following supporting information is available as part of the online article:

\appendix

\section{Additional Details on the LIME Procedure as Implemented in R} \label{lime}

\kgc{Just copying text here for now...}\\
\\
\textbf{Data Simulation}\\
\\
The density approximation method leaves the continuous features in their original form and then approximates the density of each feature using either a kernel density estimator or a normal distribution with mean and standard deviation equal to the sample mean and standard deviation of the observed feature values. The density approximation methods will be referred to as kernel density approximation and normal approximation, respectively. For both methods, observations for $\textbf{X}^*$ are sampled from the estimated distributions.\\
\\
\textbf{Interpretable Transformation}\\
\\
The interpretability transformation that corresponds to the density approximation simulation methods standardizes all of the observations by subtracting the feature sample mean and dividing by the feature sample standard deviation.\\
\\
\textbf{Explainer Model}\\
\\
\hh{XXX The next couple of paragraphs are hard to read - they are quite abstract and and full of technical details. You could try to show the visualization first, and then go into a precise discussion of why the weights are not decreasing as you'd expect by going into this discussion. That has the benefit of motivating the reader to actually read through the details and highlights your work over LIME.  XXX}

For the computation of the weights, \emph{lime} allows for the use of the Gower distance \citep{gower:1971} or an exponential kernel. If the Gower distance is used, the weights are computed prior to the interpretability transformation by computing the Gower similarity metric raised to some power. That is, let observation $z'_i$ have weight $\omega_{x^*}(\textbf{x}'_i) = Gower(x^*, x'_i)^c$, where $Gower$ represents the computation of the Gower similarity and $c$ is some constant. This denotes a proximity measure between $x^*$ and $x'_i$ for each $i\in 1,...,m$. If the exponential kernel is used, the weights are computed after the interpretability transformation such that $z'_i$ has weight $\omega_{z^*}(\textbf{z}'_i)$. \kgc{Could change weight notation to $|| \cdot ||$.}

The process to obtain the explainer model involves two steps. First, feature selection is performed to identify the $P$ most important variables in the local region where $P$ is specified. \emph{lime} offers several options for performing feature selection. These options are as follows where all methods are applied to $\textbf{Z}'$ with weights of $\omega_{z^*}(\textbf{z}'_i)$.
\begin{itemize}
\item Forward Selection: Forward selection is performed using a ridge regression model with a shrinkage parameter of $\lambda=0$ to select $P$ features.
\item Highest Weights: A ridge regression model with a shrinkage parameter of $\lambda=0$ is fit using all $p$ features. The $P$ features with the largest coefficients in the ridge regression are selected.
\item LASSO: A LASSO model is used to select the $P$ features.
\item Classification Tree: A classification tree is fit. The first $P$ features used as breaks in the tree are selected.
\end{itemize}
The ridge regression and LASSO models are fit using the \emph{glmnet} package in R \citep{simon:2011}. By default, \emph{glmnet} standardizes all predictor variables prior to fitting a model, but the coefficients are returned on the original scale.

\hh{shorten}
Both the proximity metric and the type of feature selection \sout{used could} have an effect on the LIME explanation, so it is of interest to visualize this part of the LIME process. By default, \emph{lime} uses the Gower distance with $c=1$.
\hh{shorten-end}

The second \hh{and final} step in fitting the explainer model is to fit a ridge regression model to the selected features.

\hh{XXX results first, then the technical details. There's actually more indices in the model than different prediction results. LIME hides this simplicity behind a wall of technical details. Don't help them with it.}

Define the subset of $\textbf{Z}'$ containing the chosen $P$ features as $\textbf{Z}'_P$. A ridge regression model is fit using \emph{glmnet} to $\textbf{Z}'_P$ with $f\left(\textbf{X}'_P\right)$ as the response vector, a shrinkage parameter of $\lambda=2/n$ \kgc{(KG: Note that *lime* updated lambda in ridge regression final model)}, and weights of $\omega_{x^*}(\textbf{x}'_i)$ or $\omega_{z^*}(\textbf{z}'_i)$ depending on the simulation method used as discussed in \autoref{step1}. This ridge regression is used as the explainer model $g$. For the remainder of the paper, let
  $$g\left(\textbf{Z}'_{P}\right)=\hat{\beta}_0+\hat{\beta}_1z'_{1}+\cdots+\hat{\beta}_Pz'_{P}$$
where $\hat{\beta}_0, \hat{\beta}_1,...,\hat{\beta}_P$ are the estimated coefficients from the ridge regression.

The explainer model fit by \emph{lime} for the prediction of interest from the \data \ example is written as

$$g\left(\textbf{Z}'_{2}\right) = \Sexpr{round(sine_b0, 1)}\Sexpr{round(sine_b1, 1)}I\left[x_1\in (\Sexpr{round(x1_lower, 1)}, \Sexpr{round(x1_upper, 1)}] \right]+\Sexpr{round(sine_b2, 1)}I\left[x_2\in (\Sexpr{round(x2_lower, 1)}, \Sexpr{round(x2_upper, 1)})\right].$$

In terms of feature selection, \emph{lime} performs forward selection by default if the number of features requested to be selected is 6 or less, as in the case of the \data. If more than 6 features are specified to be selected, then the highest weights method is used. \\
\\
\textbf{Interpretation}\\
\\
 In the case of density approximation samples, the features used to fit $g$ have been standardized. Again the magnitudes of the coefficients indicate the importance of the features, but a coefficient can be interpreted as the amount the response probability increases/decreases for an increase in one unit of feature $j$.

\section{Procedure Visualizations with Three Features} \label{scatter-plots}

Section \ref{procedure} describes visualizations of the LIME procedure for the features of $x_1$ and $x_2$ of the \data. The feature of $x_3$ was excluded from visualizations since it was not one of the two features selected by LIME for the explanation of the prediction of interest. However, it may be of interest to incorporate $x_3$ in the visualizations of the the steps of the LIME procedure that include. These visualizations are shown in Figures \ref{fig:app-plot-step0} through \ref{fig:app-plot-step2a}. Note that the inclusion of $x_3$ in visualizations after feature selection is not necessary, and the visualizations would remain the same as shown in Section \ref{procedure}, so they are not included here. Figures \ref{fig:app-plot-step0} and \ref{fig:app-plot-step1a} show plots of the training and testing data that make it clear that there is a relationship between the response variable and $x_1$ and $x_2$ but no relationship between the response and $x_3$. \autoref{fig:app-plot-step1b} shows the discretization of the features from the interpretability transformation. Lastly, \autoref{fig:app-plot-step2a} highlights that the value of $x_3$ is taken into account when assigning weights to the simulated data.

\begin{figure*}[!t]
<<app-plot-step0, out.width = "\\textwidth", fig.width = 8, fig.height = 4.4>>=

# Scatterplots of training data
x1x2 <- ggplot(sine_data_train, aes(x = x1, y = x2, color = y)) +
  geom_point(alpha = 0.8) +
  scale_colour_manual(values = c(sinecolor_blue, sinecolor_red)) +
  theme_bw(base_family = "Times", base_size = 10) +
  labs(x = TeX("$x_1$"),
       y = TeX("$x_2$"),
       color = TeX("y"),
       title = "Training Data") +
  theme(legend.position = "none",
        plot.title = element_text(size = 10))
x1x3 <- ggplot(sine_data_train, aes(x = x1, y = x3, color = y)) +
  geom_point(alpha = 0.8) +
  scale_colour_manual(values = c(sinecolor_blue, sinecolor_red)) +
  theme_bw(base_family = "Times", base_size = 10) +
  labs(x = TeX("$x_1$"),
       y = TeX("$x_3$"),
       color = TeX("y"),
       title = "") +
  theme(legend.position = "none")
x2x3 <- ggplot(sine_data_train, aes(x = x2, y = x3, color = y)) +
  geom_point(alpha = 0.8) +
  scale_colour_manual(values = c(sinecolor_blue, sinecolor_red)) +
  theme_bw(base_family = "Times", base_size = 10) +
  labs(x = TeX("$x_2$"),
       y = TeX("$x_3$"),
       color = TeX("y"),
       title = "") +
  theme(legend.title = element_text(size = 8))
train_legend <- get_legend(x2x3)
x2x3 <- x2x3 + theme(legend.position = "none")

# Plot the testing data rf predictions
x1x2test <- ggplot() +
  geom_point(data = sine_poi %>%
               mutate(shape = "Prediction \nof Interest"),
             mapping = aes(x = x1,
                           y = x2,
                           #fill = rfprob_blue,
                           shape = shape),
             size = 5,
             alpha = 0.8,
             color = "black") +
  geom_point(data = sine_data_test,
             mapping =  aes(x = x1,
                            y = x2,
                            color = rfprob_blue,
                            fill = rfprob_blue),
             shape = 21,
             alpha = 0.8) +
  scale_color_gradient2(low = sinecolor_red,
                        mid = '#f7f7f7',
                        high = sinecolor_blue,
                        midpoint = 0.5) +
  scale_fill_gradient2(low = sinecolor_red,
                        mid = '#f7f7f7',
                        high = sinecolor_blue,
                        midpoint = 0.5) +
  scale_shape_manual(values = 23) +
  theme_bw(base_family = "Times", base_size = 10) +
  labs(x = TeX("$x_1$"),
       y = TeX("$x_2$"),
       color = "Random \nForest \nProbability",
       fill = "Random \nForest \nProbability",
       title = "Testing Data",
       shape = "") +
  guides(shape = guide_legend(order = 1)) +
  theme(legend.position = "none",
        plot.title = element_text(size = 10))
x1x3test <- ggplot() +
  geom_point(data = sine_poi %>%
               mutate(shape = "Prediction \nof Interest"),
             mapping = aes(x = x1,
                           y = x3,
                           #fill = rfprob_blue,
                           shape = shape),
             size = 5,
             alpha = 0.8,
             color = "black") +
  geom_point(data = sine_data_test,
             mapping =  aes(x = x1,
                            y = x3,
                            color = rfprob_blue,
                            fill = rfprob_blue),
             shape = 21,
             alpha = 0.8) +
  scale_color_gradient2(low = sinecolor_red,
                        mid = '#f7f7f7',
                        high = sinecolor_blue,
                        midpoint = 0.5) +
  scale_fill_gradient2(low = sinecolor_red,
                        mid = '#f7f7f7',
                        high = sinecolor_blue,
                        midpoint = 0.5) +
  scale_shape_manual(values = 23) +
  theme_bw(base_family = "Times", base_size = 10) +
  labs(x = TeX("$x_1$"),
       y = TeX("$x_3$"),
       color = "Random \nForest \nProbability",
       fill = "Random \nForest \nProbability",
       shape = "",
       title = "") +
  guides(shape = guide_legend(order = 1)) +
  theme(legend.position = "none")
x2x3test <- ggplot() +
  geom_point(data = sine_poi %>%
               mutate(shape = "Prediction \nof Interest"),
             mapping = aes(x = x2,
                           y = x3,
                           #fill = rfprob_blue,
                           shape = shape),
             size = 5,
             alpha = 0.8,
             color = "black") +
  geom_point(data = sine_data_test,
             mapping =  aes(x = x2,
                            y = x3,
                            color = rfprob_blue,
                            fill = rfprob_blue),
             shape = 21,
             alpha = 0.8) +
  scale_color_gradient2(low = sinecolor_red,
                        mid = '#f7f7f7',
                        high = sinecolor_blue,
                        midpoint = 0.5) +
  scale_fill_gradient2(low = sinecolor_red,
                        mid = '#f7f7f7',
                        high = sinecolor_blue,
                        midpoint = 0.5) +
  scale_shape_manual(values = 23) +
  theme_bw(base_family = "Times", base_size = 10) +
  labs(x = TeX("$x_2$"),
       y = TeX("$x_3$"),
       color = "Random \nForest \nProbability",
       fill = "Random \nForest \nProbability",
       title = "",
       shape = "") +
  guides(shape = guide_legend(order = 1)) +
  theme(legend.title = element_text(size = 8))
test_legend <- get_legend(x2x3test)
x2x3test <- x2x3test + theme(legend.position = "none")

# Join the plots
plot_grid(x1x2, x1x3, x2x3, train_legend,
          x1x2test, x1x3test, x2x3test, test_legend,
          nrow = 2,
          rel_widths = c(0.29, 0.29, 0.29, 0.13))

@
\caption{Scatter plots of all features from the \data \ training (top) and testing (bottom) sets. The points are colored by the observed response and the random forest probability, respectively. The prediction of interest is indicated by a diamond. There is a clear relationship between the response and $x_1$ and $x_2$ but no relationship between the response and $x_3$.}
\label{fig:app-plot-step0}
\end{figure*}

\begin{figure*}[!t]
\centering
<<app-plot-step1a, out.width = '\\textwidth', fig.width = 8, fig.height = 4.4>>=

# Plot of the training and simulated data with bins

sine_lime_default_bin_cuts$x3 <- sine_lime_explain$lime[[3]]$bin_cuts$x3[2:4]

bins_x1x2 <- ggplot() +
  geom_point(data = sine_data_train,
             mapping = aes(x = x1, y = x2, color = y),
             alpha = 0.8) +
  geom_vline(xintercept = sine_lime_default_bin_cuts$x1) +
  geom_hline(yintercept = sine_lime_default_bin_cuts$x2) +
  scale_color_manual(values = c(sinecolor_blue, sinecolor_red)) +
  scale_fill_manual(values = c(sinecolor_blue, sinecolor_red)) +
  scale_shape_manual(values = 23) +
  theme_bw(base_family = "Times", base_size = 10) +
  labs(x = TeX("$x_1$"),
       y = TeX("$x_2$"),
       color = TeX("y"),
       fill = TeX("y"),
       shape = "",
       title = "Training Data with Quantile Bins") +
  guides(shape = guide_legend(order = 1),
         fill = FALSE) +
  theme(legend.position = "none",
        plot.title = element_text(size = 10))

bins_x1x3 <- ggplot() +
  geom_point(data = sine_data_train,
             mapping = aes(x = x1, y = x3, color = y),
             alpha = 0.8) +
  geom_vline(xintercept = sine_lime_default_bin_cuts$x1) +
  geom_hline(yintercept = sine_lime_default_bin_cuts$x3) +
  scale_color_manual(values = c(sinecolor_blue, sinecolor_red)) +
  scale_fill_manual(values = c(sinecolor_blue, sinecolor_red)) +
  scale_shape_manual(values = 23) +
  theme_bw(base_family = "Times", base_size = 10) +
  labs(x = TeX("$x_1$"),
       y = TeX("$x_3$"),
       color = TeX("y"),
       fill = TeX("y"),
       shape = "",
       title = "") +
  guides(shape = guide_legend(order = 1),
         fill = FALSE) +
  theme(legend.position = "none")

bins_x2x3 <- ggplot() +
  geom_point(data = sine_data_train,
             mapping = aes(x = x2, y = x3, color = y),
             alpha = 0.8) +
  geom_vline(xintercept = sine_lime_default_bin_cuts$x2) +
  geom_hline(yintercept = sine_lime_default_bin_cuts$x3) +
  scale_color_manual(values = c(sinecolor_blue, sinecolor_red)) +
  scale_fill_manual(values = c(sinecolor_blue, sinecolor_red)) +
  scale_shape_manual(values = 23) +
  theme_bw(base_family = "Times", base_size = 10) +
  labs(x = TeX("$x_2$"),
       y = TeX("$x_3$"),
       color = TeX("y"),
       fill = TeX("y"),
       shape = "",
       title = "") +
  guides(shape = guide_legend(order = 1),
         fill = FALSE) +
  theme(legend.title = element_text(size = 8))

bins_leg <- get_legend(bins_x2x3)
bins_x2x3 <- bins_x2x3 + theme(legend.position = "none")

bins_sim_x1x2 <- ggplot() +
  geom_point(data = sine_poi_perms,
             mapping = aes(x = x1,
                           y = x2,
                           fill = rfpred,
                           color = rfpred),
             alpha = 0.8,
             shape = 21) +
  geom_vline(xintercept = sine_lime_default_bin_cuts$x1) +
  geom_hline(yintercept = sine_lime_default_bin_cuts$x2) +
  geom_point(data = sine_poi %>% mutate(shape = "Prediction \nof Interest"),
             mapping = aes(x = x1,
                           y = x2,
                           fill = rfprob_blue,
                           shape = shape),
             color = "black",
             size = 5,
             alpha = 0.8) +
  scale_fill_gradient2(low = sinecolor_red,
                        mid = '#f7f7f7',
                        high = sinecolor_blue,
                        midpoint = 0.5) +
  scale_color_gradient2(low = sinecolor_red,
                        mid = '#f7f7f7',
                        high = sinecolor_blue,
                        midpoint = 0.5) +
  scale_shape_manual(values = 23) +
  theme_bw(base_family = "Times", base_size = 10) +
  labs(x = TeX("$x'_1$"),
       y = TeX("$x'_2$"),
       fill = "Random \nForest \nProbability",
       color = "Random \nForest \nProbability",
       shape = "",
       title = "Quantile Bin Simulated Data") +
  guides(shape = guide_legend(order = 1)) +
  theme(legend.position = "none",
        plot.title = element_text(size = 10))

bins_sim_x1x3 <- ggplot() +
  geom_point(data = sine_poi_perms,
             mapping = aes(x = x1,
                           y = x3,
                           fill = rfpred,
                           color = rfpred),
             alpha = 0.8,
             shape = 21) +
  geom_vline(xintercept = sine_lime_default_bin_cuts$x1) +
  geom_hline(yintercept = sine_lime_default_bin_cuts$x3) +
  geom_point(data = sine_poi %>% mutate(shape = "Prediction \nof Interest"),
             mapping = aes(x = x1,
                           y = x3,
                           fill = rfprob_blue,
                           shape = shape),
             color = "black",
             size = 5,
             alpha = 0.8) +
  scale_fill_gradient2(low = sinecolor_red,
                        mid = '#f7f7f7',
                        high = sinecolor_blue,
                        midpoint = 0.5) +
  scale_color_gradient2(low = sinecolor_red,
                        mid = '#f7f7f7',
                        high = sinecolor_blue,
                        midpoint = 0.5) +
  scale_shape_manual(values = 23) +
  theme_bw(base_family = "Times", base_size = 10) +
  labs(x = TeX("$x'_1$"),
       y = TeX("$x'_3$"),
       fill = "Random \nForest \nProbability",
       color = "Random \nForest \nProbability",
       shape = "",
       title = "") +
  guides(shape = guide_legend(order = 1)) +
  theme(legend.position = "none")

bins_sim_x2x3 <- ggplot() +
  geom_point(data = sine_poi_perms,
             mapping = aes(x = x2,
                           y = x3,
                           fill = rfpred,
                           color = rfpred),
             alpha = 0.8,
             shape = 21) +
  geom_vline(xintercept = sine_lime_default_bin_cuts$x2) +
  geom_hline(yintercept = sine_lime_default_bin_cuts$x3) +
  geom_point(data = sine_poi %>% mutate(shape = "Prediction \nof Interest"),
             mapping = aes(x = x2,
                           y = x3,
                           fill = rfprob_blue,
                           shape = shape),
             color = "black",
             size = 5,
             alpha = 0.8) +
  scale_fill_gradient2(low = sinecolor_red,
                        mid = '#f7f7f7',
                        high = sinecolor_blue,
                        midpoint = 0.5) +
  scale_color_gradient2(low = sinecolor_red,
                        mid = '#f7f7f7',
                        high = sinecolor_blue,
                        midpoint = 0.5) +
  scale_shape_manual(values = 23) +
  theme_bw(base_family = "Times", base_size = 10) +
  labs(x = TeX("$x'_2$"),
       y = TeX("$x'_3$"),
       fill = "Random \nForest \nProbability",
       color = "Random \nForest \nProbability",
       shape = "",
       title = "") +
  guides(shape = guide_legend(order = 1)) +
  theme(legend.title = element_text(size = 8))

bins_sim_leg <- get_legend(bins_sim_x2x3)
bins_sim_x2x3 <- bins_sim_x2x3 + theme(legend.position = "none")

plot_grid(bins_x1x2, bins_x1x3, bins_x2x3, bins_leg,
          bins_sim_x1x2, bins_sim_x1x3, bins_sim_x2x3, bins_sim_leg,
          nrow = 2,
          rel_widths = c(0.29, 0.29, 0.29, 0.13))

@
\caption{Scatter plots of all features from the \data \ training set (top) and the four quantile bin simulated data (bottom). All sets are overlaid with black lines depicting the four quantile bins.}
\label{fig:app-plot-step1a}
\end{figure*}

\begin{figure*}[!t]
\centering
<<app-plot-step1b, out.width = '\\textwidth', fig.width = 14, fig.height = 4>>=

# Create a dataset with the rectangles that make up the four categories
rect_x1x2 <-
  data.frame(rect = factor(1:6),
             z1 = c(0, 1, 0, 0, 1, 0),
             z2 = c(1, 1, 1, 0, 0, 0),
             case = factor(c(01, 11, 01, 00, 10, 00)),
             x1 = c(-10, x1_lower, x1_upper, -10, x1_lower, x1_upper),
             x2 = c(x1_lower, x1_upper, 10, x1_lower, x1_upper, 10),
             y1 = c(x2_lower, x2_lower, x2_lower, -10, -10, -10),
             y2 = c(10, 10, 10, x2_lower, x2_lower, x2_lower)) %>%
  mutate(empred = sine_explainer(z1, z2),
         case_names = ifelse(case == "11", "\nz'1 = 1 \nz'2 = 1\n",
                      ifelse(case == "10", "\nz'1 = 1 \nz'2 = 0\n",
                      ifelse(case == "1", "\nz'1 = 0 \nz'2 = 1\n",
                      "\nz'1 = 0 \nz'2 = 0\n"))))

# Plot of the numerified perturbations
num_x1x2 <- ggplot() +
  geom_point(data = sine_poi_perms,
             mapping = aes(x = x1,
                           y = x2,
                           color = rfpred),
             alpha = 0.5,
             shape = 20) +
  geom_rect(data = rect_x1x2,
            mapping = aes(xmin = x1,
                          xmax = x2,
                          ymin = y1,
                          ymax = y2,
                          fill = case_names),
            alpha = 0.7,
            color = "black") +
  geom_point(data = sine_poi,
             mapping = aes(x = x1, y = x2, color = rfprob_blue),
             size = 5,
             shape = 18,
             alpha = 0.8) +
  geom_point(data = sine_poi %>% mutate(shape = "Prediction \nof Interest"),
             mapping = aes(x = x1, y = x2, shape = shape),
             size = 5,
             alpha = 0.8) +
  scale_color_gradient2(low = sinecolor_red,
                        mid = '#f7f7f7',
                        high = sinecolor_blue,
                        midpoint = 0.5) +
  scale_fill_manual(values = c("grey90", "grey25", "grey70", "grey1")) +
  scale_shape_manual(values = 23) +
  theme_bw(base_family = "Times", base_size = 12) +
  labs(x = TeX("$x'_1$"),
       y = TeX("$x'_2$"),
       fill = "Numerified \nFeature Value",
       title = "Interpretability Transformed Simulated Data",
       shape = "") +
  guides(shape = FALSE,
         size = FALSE,
         color = FALSE)

x3_min <- min(sine_poi_perms$x3)
x3_upper <- sine_lime_default_bin_cuts$x3[[2]]
x3_max <- max(sine_poi_perms$x3)

# Create a dataset with the rectangles that make up the four categories
rect_x1x3 <-
  data.frame(rect = factor(1:6),
             z1 = c(0, 1, 0, 0, 1, 0),
             z2 = c(1, 1, 1, 0, 0, 0),
             case = factor(c(01, 11, 01, 00, 10, 00)),
             x1 = c(-10, x1_lower, x1_upper, -10, x1_lower, x1_upper),
             x2 = c(x1_lower, x1_upper, 10, x1_lower, x1_upper, 10),
             y1 = c(x3_min, x3_min, x3_min,
                    x3_upper, x3_upper, x3_upper),
             y2 = c(x3_upper, x3_upper, x3_upper,
                    x3_max, x3_max, x3_max)) %>%
  mutate(empred = sine_explainer(z1, z2),
         case_names = ifelse(case == "11", "\nz'1 = 1 \nz'3 = 1\n",
                      ifelse(case == "10", "\nz'1 = 1 \nz'3 = 0\n",
                      ifelse(case == "1", "\nz'1 = 0 \nz'3 = 1\n",
                      "\nz'1 = 0 \nz'3 = 0\n"))))

# Plot of the numerified perturbations
num_x1x3 <- ggplot() +
  geom_point(data = sine_poi_perms,
             mapping = aes(x = x1,
                           y = x3,
                           color = rfpred),
             alpha = 0.5,
             shape = 20) +
  geom_rect(data = rect_x1x3,
            mapping = aes(xmin = x1,
                          xmax = x2,
                          ymin = y1,
                          ymax = y2,
                          fill = case_names),
            alpha = 0.7,
            color = "black") +
  geom_point(data = sine_poi,
             mapping = aes(x = x1, y = x3, color = rfprob_blue),
             size = 5,
             shape = 18,
             alpha = 0.8) +
  geom_point(data = sine_poi %>% mutate(shape = "Prediction \nof Interest"),
             mapping = aes(x = x1, y = x3, shape = shape),
             size = 5,
             alpha = 0.8) +
  scale_color_gradient2(low = sinecolor_red,
                        mid = '#f7f7f7',
                        high = sinecolor_blue,
                        midpoint = 0.5) +
  scale_fill_manual(values = c("grey90", "grey25", "grey70", "grey1")) +
  scale_shape_manual(values = 23) +
  theme_bw(base_family = "Times", base_size = 12) +
  labs(x = TeX("$x'_1$"),
       y = TeX("$x'_3$"),
       fill = "Numerified \nFeature Value",
       title = "",
       shape = "") +
  guides(shape = FALSE,
         size = FALSE,
         color = FALSE)

# Create a dataset with the rectangles that make up the four categories
rect_x2x3 <-
  data.frame(rect = factor(1:4),
             z1 = c(0, 1, 0, 1),
             z2 = c(0, 0, 1, 1),
             case = factor(c(00, 10, 01, 11)),
             x1 = c(-10, x2_lower, -10, x2_lower),
             x2 = c(x2_lower, 10, x2_lower, 10),
             y1 = c(x3_upper, x3_upper, x3_min, x3_min),
             y2 = c(x3_max, x3_max, x3_upper, x3_upper)) %>%
  mutate(empred = sine_explainer(z1, z2),
         case_names = ifelse(case == "11", "\nz'2 = 1 \nz'3 = 1\n",
                      ifelse(case == "10", "\nz'2 = 1 \nz'3 = 0\n",
                      ifelse(case == "1", "\nz'2 = 0 \nz'3 = 1\n",
                      "\nz'2 = 0 \nz'3 = 0\n"))))

# Plot of the numerified perturbations
num_x2x3 <- ggplot() +
  geom_point(data = sine_poi_perms,
             mapping = aes(x = x2,
                           y = x3,
                           color = rfpred),
             alpha = 0.5,
             shape = 20) +
  geom_rect(data = rect_x2x3,
            mapping = aes(xmin = x1,
                          xmax = x2,
                          ymin = y1,
                          ymax = y2,
                          fill = case_names),
            alpha = 0.7,
            color = "black") +
  geom_point(data = sine_poi,
             mapping = aes(x = x2, y = x3, color = rfprob_blue),
             size = 5,
             shape = 18,
             alpha = 0.8) +
  geom_point(data = sine_poi %>% mutate(shape = "Prediction \nof Interest"),
             mapping = aes(x = x2, y = x3, shape = shape),
             size = 5,
             alpha = 0.8) +
  scale_color_gradient2(low = sinecolor_red,
                        mid = '#f7f7f7',
                        high = sinecolor_blue,
                        midpoint = 0.5) +
  scale_fill_manual(values = c("grey90",  "grey25", "grey70", "grey1")) +
  scale_shape_manual(values = 23) +
  theme_bw(base_family = "Times", base_size = 12) +
  labs(x = TeX("$x'_2$"),
       y = TeX("$x'_3$"),
       fill = "Numerified \nFeature Value",
       title = "",
       shape = "") +
  guides(size = FALSE,
         color = FALSE)

num_legend <- get_legend(num_x2x3 + guides(fill = FALSE))
num_x2x3 <- num_x2x3 + guides(shape = FALSE)

plot_grid(num_x1x2, num_x1x3, num_x2x3, nrow = 1) %>%
  plot_grid(num_legend, nrow = 2, rel_heights = c(0.85, 0.15))

@
\caption{\kgc{I'm still thinking about how to visualize all three features for the discretization step, but here is my starting point.}}
\label{fig:app-plot-step1b}
\end{figure*}

\begin{figure*}[!t]
\centering
<<app-plot-step2a, out.width = '\\textwidth', fig.width = 8, fig.height = 2.25>>=

# Hex plots of the mean weights of the simulated values
weights_x1x2 <- ggplot() +
  stat_summary_hex(data = sine_poi_perms,
             mapping = aes(x = x1,
                           y = x2,
                           z = weights),
             fun = mean,
             bins = 20) +
  geom_point(data = sine_poi %>%
               mutate(shape = "Prediction \nof Interest"),
             mapping = aes(x = x1, y = x2, shape = shape),
             fill = sinecolor_blue,
             size = 5,
             alpha = 0.8) +
  scale_fill_gradient(low = "grey90", high = "grey10") +
  scale_shape_manual(values = 23) +
  theme_bw(base_family = "Times", base_size = 10) +
  labs(x = TeX("x'_1"),
       y = TeX("x'_2"),
       shape = "",
       title = "Simulated Data Weights",
       fill = "Weight") +
  guides(shape = guide_legend(order = 1)) +
  theme(legend.position = "none",
        plot.title = element_text(size = 10))

weights_x1x3 <- ggplot() +
  stat_summary_hex(data = sine_poi_perms,
             mapping = aes(x = x1,
                           y = x3,
                           z = weights),
             fun = mean,
             bins = 20) +
  geom_point(data = sine_poi %>%
               mutate(shape = "Prediction \nof Interest"),
             mapping = aes(x = x1, y = x3, shape = shape),
             fill = sinecolor_blue,
             size = 5,
             alpha = 0.8) +
  scale_fill_gradient(low = "grey90", high = "grey10") +
  scale_shape_manual(values = 23) +
  theme_bw(base_family = "Times", base_size = 10) +
  labs(x = TeX("x'_1"),
       y = TeX("x'_3"),
       shape = "",
       title = "",
       fill = "Weight") +
  guides(shape = guide_legend(order = 1)) +
  theme(legend.position = "none")

weights_x2x3 <- ggplot() +
  stat_summary_hex(data = sine_poi_perms,
             mapping = aes(x = x2,
                           y = x3,
                           z = weights),
             fun = mean,
             bins = 20) +
  geom_point(data = sine_poi %>%
               mutate(shape = "Prediction \nof Interest"),
             mapping = aes(x = x2, y = x3, shape = shape),
             fill = sinecolor_blue,
             size = 5,
             alpha = 0.8) +
  scale_fill_gradient(low = "grey90", high = "grey10") +
  scale_shape_manual(values = 23) +
  theme_bw(base_family = "Times", base_size = 10) +
  labs(x = TeX("x'_2"),
       y = TeX("x'_3"),
       shape = "",
       title = "",
       fill = "Weight") +
  guides(shape = guide_legend(order = 1)) +
  theme(legend.title = element_text(size = 8))

weights_legend <- get_legend(weights_x2x3)
weights_x2x3 <- weights_x2x3 + theme(legend.position = "none")

plot_grid(weights_x1x2, weights_x1x3, weights_x2x3, weights_legend,
          nrow = 1,
          rel_widths = c(0.29, 0.29, 0.29, 0.13))
@
\caption{Hex plots of the weights assigned to the observations in the simulated data for each pair of features in the \data. The color of each hexagon represents the average weight of the points located within that region.}
\label{fig:app-plot-step2a}
\end{figure*}

\section{Details of the Bullet Matching Random Forest Model} \label{hamby-rf}

\bibliography{references}

% Do I need to include this?
% \section*{Author Biography}
% \begin{biography}
% {\includegraphics[width=60pt,height=70pt,draft]{empty}}
% {\textbf{Author Name.} This is sample author biography text this is sample author biography text}
% \end{biography}

% \newpage
% 
% \textsc{\textbf{Ideas for describing proposed plots}}
% 
% \begin{itemize}
% \item start at the high level explanation (this is what we want to do and this is how we do it)
% \item go over a good and bad example
% \item include schematics of the plot first (good and bad) and then include the sine mini example version
% \item explain the expectation of the plot
% \end{itemize}
% 
% \textsc{\textbf{Comments for Editing}}
% 
% \begin{itemize}
% \item \hh{Generally: avoid 'can be'. Replace by 'is'.  }
% \item \hh{References like 'they', 'them' ... replace them by repeating the noun you are referring to to avoid any kind of ambiguity}
% \item \kgc{words to go back and make sure I am not using too often: ability, produce, understand}
% \item \kgc{decide on features or predictor variables}
% \item \hh{it's tuning parameters, not tunning} \kgc{Oops! I get that one wrong all of the time}
% \item \kgc{Adjust text sizes in plots so they all match}
% \item \kgc{Color scheme - comment from Heike:} \hh{I like the red-blue scheme for binary values, I also like the color scheme in the features heatmap. Generally papers and color don't go well together anyways, but we will solve that problem when we have to ... Most likely we will have to just pay the extra color fee}
% \item \kgc{Check that I am consistently referring to the perturbing as data simulation}
% \item \kgc{Clean up notation}
% \item \kgc{Referring to the linearity assumption:} \hh{Be a bit careful in the phrasing here - we can always approximate any function using a linear form (think Taylor expansion). The question is how big the error is.}
% \item \kgc{Make sure plots in the same figure are the same size}
% \item \kgc{Make sure I am distinguishing between RF predictions and probabilities correctly}
% \item \kgc{Use prediction of interest not case of interest}
% \item \kgc{Make sure I always treat the word 'data' as plural}
% \item \kgc{dataset or data set?}
% \item \kgc{scatterplot or scatter plot (check other plot names as well)}
% \item \kgc{choose whether to use the term feature or variable and make sure it is consistent throughout}
% \item \kgc{just include the details about LIME that are necessary to understand the plots and remove the rest to the appendix}
% \item \hh{avoid the use of implicit references like `this' and `that'. Make the reference explicit by adding what you are referring to, such as `this method', `that procedure'}
% \item \hh{make sure to use exact phrases. things like `LIME was developed in 2016' is factually questionable - but we know LIME was introduced in 2016. Also `the authors were interested in ...' implies that you know their intent. It's better to not guess any intent but stick to what we know.}
% \item \hh{`our` diagnostics ... you are using `our` quite often. It is good to claim work, but it is not good to claim things that we want others to use, because that is by definition excluding everybody but you. It's better to re-phrase with a focus on what you did. We introduce, we suggest, etc.}
% \item \hh{Try to give each of the diagnostics a name.}
% \item \kgc{check that I am always using present tense}
% \item \kgc{check that I am consistent in my use of the term black-box model}
% \end{itemize}
% 
% \textsc{\textbf{Ideas for Publishing}}
% 
% \begin{itemize}
% \item longer review article (emph on CS method in ML - we're translating the content into a stats language) (talk to Maitra and Wendy)
% \item review article would need a more extensive lit review:
% \begin{itemize}
% \item who has looked at LIME and found it not great
% \item who is using LIME for applications
% \item papers using LIME
% \end{itemize}
% \item the diagnostics plots could get put in a rapid research paper via DS journal
% \item could consider JOSS for publication of the limeaid package
% \item implement a hierarchical ordering method for the feature heatmap
% \end{itemize}
% 
% \textsc{\textbf{Other Ideas}}
% 
% \begin{itemize}
% \item Consider creating a plot to show the decay of the distance by Gower exponent in terms of standard deviations in the appendix.
% \end{itemize}

\end{document}

### 2020-09-04 old-version/paper.tex
added the old (long) version of the paper

--- 2020-09-04 old-version/paper.Rnw
@@
 
-<<setup, echo = FALSE, include = FALSE>>=
-
-# Specify global options
-knitr::opts_chunk$set(echo = FALSE,
-                      fig.keep = 'high',
-                      message = FALSE)
-
-# Load packages
-library(caret)
-library(cowplot)
-library(dplyr)
-library(forcats)
-library(ggforce)
-library(ggplot2)
-library(ggpcp)
-library(glmnet)
-library(gower)
-library(graphics)
-library(gretchenalbrecht)
-library(latex2exp)
-library(lime) #devtools::install_github("goodekat/lime")
-library(limeaid) #devtools::install_github("goodekat/limeaid")
-library(purrr)
-library(randomForest)
-library(stringr)
-library(tidyr)
-
-@
-
 \section{Introduction}
@@
 
-<<concept-data>>=
-# Simulate example data
-set.seed(20190624)
-lime_data <-
-  data.frame(
-    feature1 = sort(runif(250, 0, 1)),
-    feature2 = sample(x = 1:250, size = 250, replace = FALSE)) %>%
-  mutate(
-    feature1_stnd = (feature1 - mean(feature1)) / sd(feature1),
-    feature2_stnd = (feature2 - mean(feature2)) / sd(feature2),
-    prediction = if_else(feature1 >= 0 & feature1 < 0.1,
-                         (0.3 * feature1) + rnorm(n(), 0, 0.01),
-                 if_else(feature1 >= 0.1 & feature1 < 0.3,
-                         rbeta(n(), 1, 0.5),
-                 if_else(feature1 >= 0.3 & feature1 < 0.5,
-                         sin(pi* feature1) + rnorm(n(), 0, 0.5),
-                 if_else(feature1 >= 0.5 & feature1 < 0.8,
-                         -(sin(pi* feature1) + rnorm(n(), 0, 0.1)) + 1,
-                 if_else(feature1 >= 0.8 & feature1 < 0.9,
-                         0.5 + runif(n(), -0.5, 0.5),
-                         0.5 + rnorm(n(), 0, 0.3))))))) %>%
-  bind_rows(
-    data.frame(feature1 = rep(1, 30) + rnorm(5, 0, 0.05),
-           feature2 = rep(245, 30) + rnorm(5, 0, 1),
-           prediction = rep(0, 30) + rnorm(5, 0, 0.05)) %>%
-  mutate(feature1_stnd = (feature1 - mean(feature1)) / sd(feature1),
-         feature2_stnd = (feature2 - mean(feature2)) / sd(feature2)))
-
-# Specify a prediction of interest
-prediction_of_interest <-
-  data.frame(feature1 = 0.07, feature2 = 200) %>%
-  mutate(feature1_stnd = (feature1 - mean(lime_data$feature1)) /
-           sd(lime_data$feature1),
-         feature2_stnd = (feature2 - mean(lime_data$feature2)) /
-           sd(lime_data$feature2),
-         prediction = 0.05,
-         color = factor("Prediction \nof Interest"))
-
-# Specify the gower exponents
-good_gower_power <- 50
-bad_gower_power <- 1
-
-# Compute the good distances between the prediction of interest
-# and all other observations
-lime_data$distance_good <-
-  (1 - gower_dist(x = prediction_of_interest %>%
-                    select(feature1_stnd, feature2_stnd),
-                  y = lime_data %>%
-                    select(feature1_stnd,
-                           feature2_stnd)))^good_gower_power
-
-# Compute the bad distances between the prediction of interest
-# and all other observations
-lime_data$distance_bad <-
-  (1 - gower_dist(x = prediction_of_interest %>%
-                    select(feature1_stnd, feature2_stnd),
-                  y = lime_data %>%
-                    select(feature1_stnd,
-                           feature2_stnd)))^bad_gower_power
-
-# Prepare the data for plotting
-lime_data_gathered <- lime_data %>%
-  gather(feature, feature_stnd_value,
-         feature1_stnd:feature2_stnd) %>%
-  gather(distance, distance_value, distance_good:distance_bad) %>%
-  mutate(distance = fct_recode(distance,
-                               "good" = "distance_good",
-                               "bad" = "distance_bad"),
-         feature = fct_recode(feature,
-                              "Feature 1" = "feature1_stnd",
-                              "Feature 2" = "feature2_stnd"))
-
-# Prepare the prediction of interest data for plotting
-prediction_of_interest_gathered <- prediction_of_interest %>%
-  select(-feature1, -feature2) %>%
-  gather(feature, feature_value, feature1_stnd, feature2_stnd) %>%
-  mutate(feature = fct_recode(feature,
-                              "Feature 1" = "feature1_stnd",
-                              "Feature 2" = "feature2_stnd"))
-
-@
-
-<<concept-explainers>>=
-
-# Fit the good interpretable explainer model
-explainer_good <-
-  glmnet(x = lime_data %>% select(feature1_stnd, feature2_stnd)
-         %>% as.matrix(),
-         y = lime_data$prediction,
-         alpha = 0,
-         lambda = 1,
-         weights = lime_data$distance_good)
-
-# Fit the bad interpretable explainer model
-explainer_bad <-
-  glmnet(x = lime_data %>% select(feature1_stnd, feature2_stnd)
-         %>% as.matrix(),
-         y = lime_data$prediction,
-         alpha = 0,
-         lambda = 1,
-         weights = lime_data$distance_bad)
-
-# Join the coefficients from the explainer model into a dataframe
-coefs_data <- data.frame(case = c("good", "bad"),
-                         b0 = c(coef(explainer_good)[1],
-                                coef(explainer_bad)[1]),
-                         b1 = c(coef(explainer_good)[2],
-                                coef(explainer_bad)[2]),
-                         b2 = c(coef(explainer_good)[3],
-                                coef(explainer_bad)[3])) %>%
-  mutate(feature1 = b0 + b2*prediction_of_interest$feature2_stnd,
-         feature2 = b0 + b1*prediction_of_interest$feature1_stnd) %>%
-  gather(key = feature, value = int, feature1:feature2) %>%
-  mutate(slope = c(coef(explainer_good)[2],
-                   coef(explainer_good)[3],
-                   coef(explainer_bad)[2],
-                   coef(explainer_bad)[3]),
-         feature = fct_recode(feature,
-                              "Feature 1" = "feature1",
-                              "Feature 2" = "feature2"))
-
-@
-
 \begin{figure*}[!htbp]
-<<concept-plot-good, out.width = '\\textwidth', fig.width = 7.95, fig.height = 3.75, warning = FALSE>>=
-
-# Plot of good explainer model
-ggplot() +
-  facet_grid(. ~ feature, switch = "x") +
-  geom_point(data = lime_data_gathered,
-             mapping = aes(x = feature_stnd_value,
-                           y = prediction,
-                           size = distance_value,
-                           alpha = distance_value,
-                           color = distance)) +
-  geom_abline(data = coefs_data %>% filter(case == "good"),
-              mapping = aes(intercept = int, slope = slope),
-              size = 1) +
-  scale_alpha(range = c(0.3, 1)) +
-  scale_color_manual(values = c(NA, "grey30"), guide = FALSE) +
-  geom_point(data = prediction_of_interest_gathered,
-             mapping = aes(x = feature_value,
-                           y = prediction,
-                           fill = color),
-             color = "black",
-             size = 5,
-             shape = 23,
-             alpha = 0.75) +
-  scale_fill_manual(values = "#FAAA72") +
-  geom_text(
-    data = data.frame(feature_stnd_value = 1.2,
-                      prediction = 1.6,
-                      feature = c("Feature 1", "Feature 2"),
-                      slope = c(paste("Slope:",
-                                      coefs_data %>%
-                                        filter(case == "good",
-                                               feature == "Feature 1") %>%
-                                        pull(slope) %>%
-                                        round(3)),
-                                paste("Slope:",
-                                      coefs_data %>%
-                                        filter(case == "good",
-                                               feature == "Feature 2") %>%
-                                        pull(slope) %>%
-                                        round(3)))),
-    mapping = aes(x = feature_stnd_value,
-                  y = prediction,
-                  label = slope),
-    family = "Times",
-    size = 4) +
-  labs(x = "",
-       y = "Black-Box Prediction",
-       title = "Conceptual Depiction of a Faithful Local Explainer Model",
-       subtitle = paste("Gower Distance Metric Exponent:", good_gower_power),
-       fill = "",
-       alpha = "Weight",
-       size = "Weight") +
-  theme_linedraw(base_family = "Times", base_size = 10) +
-  theme(panel.grid.major = element_blank(),
-        panel.grid.minor = element_blank(),
-        axis.text.x = element_blank(),
-        axis.ticks.x = element_blank(),
-        axis.text.y = element_blank(),
-        axis.ticks.y = element_blank(),
-        strip.placement = "outside",
-        strip.background = element_rect(color = "white", fill = "white"),
-        strip.text = element_text(color = 'black', size = 10)) +
-  guides(fill = guide_legend(order = 1),
-         size = guide_legend(order = 2),
-         alpha = guide_legend(order = 2))
-
-@
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\textwidth]{figure/concept-plot-good-1}
+
+\end{knitrout}
 \caption{A conceptual depiction of a faithful LIME explainer model in the immediate neighborhood of a prediction of interest.
@@
 The diamond shaped points represent the location of a prediction of interest.
-The size and opacity of the circular points indicate the weight assigned based on the distance to the point of interest computed using the inverse of the Gower distance metric raised to the power of \Sexpr{good_gower_power}.
+The size and opacity of the circular points indicate the weight assigned based on the distance to the point of interest computed using the inverse of the Gower distance metric raised to the power of 50.
 The black lines are a weighted ridge regression model used as an explainer model that reasonably captures the relationship between the black-box predictions and the features in a local region around the point of interest.
@@
 
-<<concept-plot-bad, out.width = '\\textwidth', fig.width = 7.95, fig.height = 3.75, warning = FALSE>>=
-
-# Plot of good explainer model
-ggplot() +
-  facet_grid(. ~ feature, switch = "x") +
-  geom_point(data = lime_data_gathered,
-             mapping = aes(x = feature_stnd_value,
-                           y = prediction,
-                           size = distance_value,
-                           alpha = distance_value,
-                           color = distance)) +
-  geom_abline(data = coefs_data %>% filter(case == "bad"),
-              mapping = aes(intercept = int, slope = slope),
-              size = 1) +
-  scale_alpha(range = c(0.3, 1)) +
-  scale_color_manual(values = c("grey30", NA), guide = FALSE) +
-  geom_point(data = prediction_of_interest_gathered,
-             mapping = aes(x = feature_value,
-                           y = prediction,
-                           fill = color),
-             color = "black",
-             size = 5,
-             shape = 23,
-             alpha = 0.75) +
-  scale_fill_manual(values = "#FAAA72") +
-  geom_text(
-    data = data.frame(feature_stnd_value = 1.2,
-                      prediction = 1.6,
-                      feature = c("Feature 1", "Feature 2"),
-                      slope = c(paste("Slope:",
-                                      coefs_data %>%
-                                        filter(case == "bad",
-                                               feature == "Feature 1") %>%
-                                        pull(slope) %>%
-                                        round(3)),
-                                paste("Slope:",
-                                      coefs_data %>%
-                                        filter(case == "bad",
-                                               feature == "Feature 2") %>%
-                                        pull(slope) %>%
-                                        round(3)))),
-    mapping = aes(x = feature_stnd_value,
-                  y = prediction,
-                  label = slope),
-    family = "Times",
-    size = 4) +
-  labs(x = "",
-       y = "Black-Box Prediction",
-       title = "Conceptual Depiction of an Unfaithful Local Explainer Model",
-       subtitle = paste("Gower Distance Metric Exponent:", bad_gower_power),
-       fill = "",
-       alpha = "Weight",
-       size = "Weight") +
-  theme_linedraw(base_family = "Times", base_size = 10) +
-  theme(panel.grid.major = element_blank(),
-        panel.grid.minor = element_blank(),
-        axis.text.x = element_blank(),
-        axis.ticks.x = element_blank(),
-        axis.text.y = element_blank(),
-        axis.ticks.y = element_blank(),
-        strip.placement = "outside",
-        strip.background = element_rect(color = "white", fill = "white"),
-        strip.text = element_text(color = 'black', size = 10)) +
-  guides(fill = guide_legend(order = 1),
-         size = guide_legend(order = 2),
-         alpha = guide_legend(order = 2))
-
-@
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\textwidth]{figure/concept-plot-bad-1}
+
+\end{knitrout}
 \caption{A conceptual depiction of an unfaithful local explainer model in the immediate neighborhood of a prediction of interest.
@@
 A Gower distance metric \citep{gower:1971} is used to define locality: the size of the points represent the inverse of the Gower distance as a reflection of the proximity to the prediction of interest.
-Here, an exponent of \Sexpr{good_gower_power} is used to emphasize interest in a very local region around the point of interest.
+Here, an exponent of 50 is used to emphasize interest in a very local region around the point of interest.
 A ridge regression model weighted by the proximity values is used as the explainer model.
@@
 Here, the explainer model is plotted with Feature 2 fixed at the observed value of Feature 2 for the prediction of interest.
-The explainer model captures the relationship in the immediate neighborhood around the prediction of interest  with a slope of \Sexpr{coefs_data %>% filter(case == "good", feature == "Feature 1") %>% pull(slope) %>% round(3)}.
+The explainer model captures the relationship in the immediate neighborhood around the prediction of interest  with a slope of 0.068.
 The plot on the right shows that there is no global or local relationship between the black-box predictions and Feature 2.
-Here, the explainer model is plotted with Feature 1 set to be the observed value of Feature 1 for the prediction of interest, and it has a small slope of \Sexpr{coefs_data %>% filter(case == "good", feature == "Feature 2") %>% pull(slope) %>% round(3)}.
+Here, the explainer model is plotted with Feature 1 set to be the observed value of Feature 1 for the prediction of interest, and it has a small slope of -0.001.
 The magnitude of the slope associated with Feature 1 is larger than the slope of Feature 2, resulting LIME to report that Feature 1 plays a more important role in the prediction made by the black-box model.
@@
 Now consider the example depicted in \autoref{fig:concept-plot-bad}.
-The plots show the same data as \autoref{fig:concept-plot-good}, but the Gower distance metric was raised to the default power used by the \emph{lime} R package of \Sexpr{bad_gower_power}.
+The plots show the same data as \autoref{fig:concept-plot-good}, but the Gower distance metric was raised to the default power used by the \emph{lime} R package of 1.
 This causes the observations that are further away from the prediction of interest to be given larger weights than before.
@@
 This cannot be said of the explainer model in \autoref{fig:concept-plot-bad}.
-In addition, the magnitude of the slope (\Sexpr{coefs_data %>% filter(case == "bad", feature == "Feature 2") %>% pull(slope) %>% round(3) %>% abs()}) associated with Feature 2 is larger than that of Feature 1 (\Sexpr{coefs_data %>% filter(case == "bad", feature == "Feature 1") %>% pull(slope) %>% round(3) %>% abs()}).
+In addition, the magnitude of the slope (0.011) associated with Feature 2 is larger than that of Feature 1 (0.005).
 Thus, this explainer model actually provides a misleading explanation that Feature 2 plays a more important role in predicting the observation of interest.
@@
 The adaption to an R package is by Thomas Lin-Pedersen\footnote{https://github.com/thomasp85/lime}.
-In this paper, we use a forked version\footnote{https://github.com/goodekat/lime} of the development version of the R package \emph{lime} (\Sexpr{packageVersion("lime")}) \citep{pedersen:2020}.
+In this paper, we use a forked version\footnote{https://github.com/goodekat/lime} of the development version of the R package \emph{lime} (0.5.1) \citep{pedersen:2020}.
 The forked version of \emph{lime} allows us to export internal values of the procedure not already exported by \emph{lime}.
@@
 \section{Visualizations of an Individual LIME Explanation} \label{procedure}
-
-<<sine-data, echo = FALSE, include = FALSE>>=
-
-# Functions for rotating the data
-rot_x <- function(x, y, theta) (x * cos(theta)) - (y * sin(theta))
-rot_y <- function(x, y, theta) (x * sin(theta)) + (y * cos(theta))
-
-# Generate the data
-theta = -0.9
-min = -10
-max = 10
-set.seed(20190913)
-sine_data <- data.frame(x1 = runif(600, min, max),
-                        x2 = sort(runif(600, min, max))) %>%
-  mutate(x1new = rot_x(x1, x2, theta),
-         x2new = rot_y(x1, x2, theta),
-         y = ifelse(x2new > 5 * sin(x1new), "blue", "red")) %>%
-  slice(sample(1:n())) %>%
-  mutate(x3 = rnorm(600),
-         case = 1:600) %>%
-  select(case, everything())
-
-# Separte the data into training and testing parts
-set.seed(20191003)
-rs <- sample(1:600, 500, replace = FALSE)
-sine_data_train <- sine_data[rs,]
-sine_data_test <- sine_data[-rs,]
-
-# Fit a random forest
-set.seed(20191003)
-rfsine <- randomForest(x = sine_data_train %>% select(x1, x2, x3),
-                       y = factor(sine_data_train$y))
-
-# Obtain predictions on the training and testing data
-sine_data_train$rfpred <- predict(rfsine)
-sine_data_train <- cbind(sine_data_train, predict(rfsine, type = "prob"))
-sine_data_train <- sine_data_train %>% 
-  rename(rfprob_blue = blue, rfprob_red = red)
-sine_data_test$rfpred <- predict(rfsine, sine_data_test %>% select(x1, x2, x3))
-sine_data_test <- cbind(sine_data_test,
-                        predict(rfsine, sine_data_test
-                                %>% select(x1, x2, x3),
-                                type = "prob"))
-sine_data_test <- sine_data_test %>% 
-  rename(rfprob_blue = blue, rfprob_red = red)
-
-# Extract the prediction of interest from the sine test data
-sine_poi <- sine_data_test %>% filter(y != rfpred, x1 > 0, x1 < 5, x2 > 5)
-
-@
 
@@
 \centering
-<<sine-plot-data, out.width = '\\textwidth', fig.width = 8, fig.height = 3.1>>=
-
-# Create points represting the rotated since curve
-sinefun_data <- data.frame(xnew = seq(min(sine_data$x1new),
-                                      max(sine_data$x1new),
-                                      by = 0.01)) %>%
-  mutate(ynew = 5 * sin(xnew)) %>%
-  mutate(x = rot_x(xnew, ynew, -theta),
-         y = rot_y(xnew, ynew, -theta)) %>%
-  filter(y >= -10, y <= 10)
-
-# Specify colors for predictions
-sinecolor_red = "firebrick"
-sinecolor_blue = "steelblue"
-
-# Plot the training data observed classes
-sine_plot_obs <- ggplot(sine_data_train, aes(x = x1, y = x2, color = y)) +
-  geom_point(alpha = 0.8) +
-  geom_path(data = sinefun_data, aes(x = x, y = y),
-            color = "black") +
-  scale_colour_manual(values = c(sinecolor_blue, sinecolor_red)) +
-  theme_bw(base_family = "Times", base_size = 10) +
-  labs(x = TeX("$x_1$"),
-       y = TeX("$x_2$"),
-       color = TeX("y"),
-       title = "Training Data")
-
-# Plot the testing data rf predictions
-sine_plot_pred <- ggplot() +
-  geom_point(data = sine_poi %>%
-               mutate(shape = "Prediction \nof Interest"),
-             mapping = aes(x = x1,
-                           y = x2,
-                           #fill = rfprob_blue,
-                           shape = shape),
-             size = 5,
-             alpha = 0.8,
-             color = "black") +
-  geom_point(data = sine_data_test %>% filter(y != rfpred),
-             mapping = aes(x = x1, y = x2),
-             shape = 1,
-             size = 3,
-             color = "black") +
-  geom_point(data = sine_data_test,
-             mapping =  aes(x = x1,
-                            y = x2,
-                            color = rfprob_blue,
-                            fill = rfprob_blue),
-             shape = 21,
-             alpha = 0.8) +
-  geom_path(data = sinefun_data, aes(x = x, y = y),
-            color = "black") +
-  scale_color_gradient2(low = sinecolor_red,
-                        mid = '#f7f7f7',
-                        high = sinecolor_blue,
-                        midpoint = 0.5) +
-  scale_fill_gradient2(low = sinecolor_red,
-                        mid = '#f7f7f7',
-                        high = sinecolor_blue,
-                        midpoint = 0.5) +
-  scale_shape_manual(values = 23) +
-  theme_bw(base_family = "Times", base_size = 10) +
-  labs(x = TeX("$x_1$"),
-       y = TeX("$x_2$"),
-       color = "Random \nForest \nProbability \nfor 'blue'",
-       fill = "Random \nForest \nProbability \nfor 'blue'",
-       title = "Testing Data",
-       shape = "") +
-  guides(shape = guide_legend(order = 1))
-
-# Join the plots
-plot_grid(sine_plot_obs, sine_plot_pred,
-          nrow = 1,
-          rel_widths = c(0.4825, 0.5175))
-
-@
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\textwidth]{figure/sine-plot-data-1}
+
+\end{knitrout}
 \caption{Plots of $x_2$ versus $x_1$ from the training (left) and testing (right) set of the \data \ introduced in Section \ref{procedure}.
@@
 The color of the testing data points represents the random forest probability that an observation belongs to the category of blue ($\hat{y}$).
-The \Sexpr{dim(sine_data_test %>% filter(y != rfpred))[1]} cases that are misclassified by the random forest are identified by black circles.
+The 18 cases that are misclassified by the random forest are identified by black circles.
 The prediction of interest to explain is indicated by a diamond.}
@@
 To demonstrate the visualizations, we generate an example dataset that will be referred to as the \data.
-The \data \ contains \Sexpr{dim(sine_data)[1]} observations with three features and one response variable.
-The features, $x_1$, $x_2$, and $x_3$, are randomly sampled from Unif(\Sexpr{min}, \Sexpr{max}), Unif(\Sexpr{min}, \Sexpr{max}), and $\mbox{N}(0,1)$ distributions, respectively.
+The \data \ contains 600 observations with three features and one response variable.
+The features, $x_1$, $x_2$, and $x_3$, are randomly sampled from Unif(-10, 10), Unif(-10, 10), and $\mbox{N}(0,1)$ distributions, respectively.
 A binary response variable $y$ is  created using a rotated sine curve.
@@
 
-The dataset is divided into a training set of \Sexpr{dim(sine_data_train)[1]} observations and a testing set of \Sexpr{dim(sine_data_test)[1]} observations.
-A random forest model is fit using the R package \emph{randomForest} (version \Sexpr{packageVersion("randomForest")}) \citep{liaw:2002} with the default settings.
+The dataset is divided into a training set of 500 observations and a testing set of 100 observations.
+A random forest model is fit using the R package \emph{randomForest} (version 4.6.14) \citep{liaw:2002} with the default settings.
 The model is applied to the testing set to obtain predictions.
@@
 
-The random forest model misclassifies \Sexpr{dim(sine_data_test %>% filter(y != rfpred))[1]} points on the classification boundary.
+The random forest model misclassifies 18 points on the classification boundary.
 These are identified by circles in \autoref{fig:sine-plot-data}.
-For the visualizations of the steps of the LIME algorithm, we focus on one of these points: the observation with $(x_1, x_2, x_3)$ coordinates of (\Sexpr{round(sine_poi$x1, 2)}, \Sexpr{round(sine_poi$x2, 2)}, \Sexpr{round(sine_poi$x3, 2)}) and indicated in \autoref{fig:sine-plot-data} by a diamond.
-
-<<sine-lime>>=
-
-# Apply LIME with various tuning parameters to the sine data
-if (!file.exists("../data/sine_lime_explain.rds")) {
-
-    # Apply lime with various input options
-    sine_lime_explain <- apply_lime(
-      train = sine_data_train %>% select(x1, x2, x3),
-      test = sine_data_test %>% select(x1, x2, x3),
-      model = rfsine,
-      label = "blue",
-      n_features = 2,
-      sim_method = c('quantile_bins', "kernel_density"),
-      nbins = 2:6,
-      feature_select = "auto",
-      dist_fun = "gower",
-      kernel_width = NULL,
-      gower_pow = 1,
-      return_perms = TRUE,
-      all_fs = TRUE,
-      seed = 20190914)
-
-    saveRDS(sine_lime_explain, "../data/sine_lime_explain.rds")
-
-  } else {
-
-    sine_lime_explain <- readRDS("../data/sine_lime_explain.rds")
-
-  }
-
-@
-
-<<sine-lime-default>>=
-
-# Extract the explanations from the default lime implementation
-sine_lime_default <- sine_lime_explain$explain %>% filter(nbins == 4)
-
-# Extract the explanations from the default lime implementation
-# for the prediction of interest only
-sine_poi_lime_default <- sine_lime_default %>%
-  filter(case == sine_poi %>% pull(case)) %>%
-  mutate(case = c("Prediction of Interest", "Prediction of Interest"))
-
-@
+For the visualizations of the steps of the LIME algorithm, we focus on one of these points: the observation with $(x_1, x_2, x_3)$ coordinates of (1.23, 8.47, -0.99) and indicated in \autoref{fig:sine-plot-data} by a diamond.
 
@@
 \autoref{fig:sine-plot-poi} shows the visualization of the explanation produced by \emph{lime} for the prediction of interest.
-The figure shows that the random forest returned a probability of \Sexpr{sine_poi_lime_default$label_prob[1]} that the observation of interest belongs to category blue {(denoted as the ``label" in the figure).
+The figure shows that the random forest returned a probability of 0.744 that the observation of interest belongs to category blue {(denoted as the ``label" in the figure).
 The colored bars indicate the features chosen by LIME and whether they support or contradict a random forest classification of blue.
@@
 The explanation for the prediction of interest depicted in Figure \ref{fig:sine-plot-poi} can be interpreted as follows.
-A random forest classification of blue is supported by the prediction of interest having a value of $x_2$ that is greater than \Sexpr{str_split(sine_poi_lime_default$feature_desc[[1]], pattern = " ")[[1]][1]}, but the prediction of interest having a value of $x_1$ that is greater than \Sexpr{str_split(sine_poi_lime_default$feature_desc[[2]], pattern = " ")[[1]][1]} and less than or equal to \Sexpr{str_split(sine_poi_lime_default$feature_desc[[2]], pattern = " ")[[1]][5]} provides support against a classification of blue.
+A random forest classification of blue is supported by the prediction of interest having a value of $x_2$ that is greater than 4.834, but the prediction of interest having a value of $x_1$ that is greater than -0.302 and less than or equal to 4.844 provides support against a classification of blue.
 Since the weight associated with $x_2$ has a larger magnitude than the weight associated with $x_1$, LIME explains that the $x_1$ and $x_2$ locations of the prediction of interest provide more support for a random forest classification of blue over red.
-This explanation agrees with the random forest probability of \Sexpr{sine_poi_lime_default$label_prob[1]} for blue, even though both classify the observation incorrectly.
+This explanation agrees with the random forest probability of 0.744 for blue, even though both classify the observation incorrectly.
 
@@
 This value corresponds to the deviance ratio from the R package \emph{glmnet} \citep{simon:2011} for a ridge regression model, or in other words, this is the $R^2$ value associated with the explainer model.
-In this case, it is \Sexpr{round(sine_poi_lime_default$model_r2[1], 2)} suggesting that the explainer model is not a good linear fit.
+In this case, it is 0.21 suggesting that the explainer model is not a good linear fit.
 However, it is commonly accepted that $R^2$ has limitations for accessing the quality of fit of a model \citep{sapra:2014}, and it should not be the only metric used for assessment of a model.
@@
 \centering
-<<sine-plot-poi, out.width = '0.5\\textwidth', fig.width = 4, fig.height = 3.25>>=
-sine_poi_exp <- sine_poi_lime_default %>% plot_features()
-sine_poi_exp
-@
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=0.5\textwidth]{figure/sine-plot-poi-1}
+
+\end{knitrout}
 \caption{Visualization from \emph{lime} of the explanation associated with the prediction of interest from the \data \ produced by the default settings.
-The probability of \Sexpr{sine_poi_lime_default$label_prob[1]} is the random forest probability in support of a classification of blue.
-The colored bars indicate that $\Sexpr{str_split(sine_poi_lime_default$feature_desc[[1]], pattern = " ")[[1]][1]} < x_2$ supports a random forest prediction of 1 and $\Sexpr{str_split(sine_poi_lime_default$feature_desc[[2]], pattern = " ")[[1]][1]}<x_1\le \Sexpr{str_split(sine_poi_lime_default$feature_desc[[2]], pattern = " ")[[1]][5]}$ contradicts a random forest prediction of 0.
-The explanation fit of \Sexpr{round(sine_poi_lime_default$model_r2[1], 2)} is the $R^2$ value of the explainer model, which indicates that the explainer model has a poor linear fit.
+The probability of 0.744 is the random forest probability in support of a classification of blue.
+The colored bars indicate that $4.834 < x_2$ supports a random forest prediction of 1 and $-0.302<x_1\le 4.844$ contradicts a random forest prediction of 0.
+The explanation fit of 0.21 is the $R^2$ value of the explainer model, which indicates that the explainer model has a poor linear fit.
 Aside of some evidence from the $R^2$ value, it is not clear whether this explanation is reasonable.}
@@
 \centering
-<<sine-plot-step1ab, out.width = '\\textwidth', fig.width = 8.25, fig.height = 3.25, warning = FALSE>>=
-
-# Determine the bin cuts for the default lime implementation
-sine_lime_default_bin_cuts <- sine_lime_default %>%
-  select(feature, feature_desc) %>%
-  unique() %>%
-  separate(feature_desc, c("other", "bin_cut"), sep = " <= ") %>%
-  select(-other) %>%
-  na.omit() %>%
-  mutate(bin_cut = as.numeric(bin_cut)) %>%
-  arrange(feature) %>%
-  mutate(case = rep(1:3, 2)) %>%
-  spread(feature, bin_cut)
-
-# Plot the training data with observed classes and the
-# four quantile bins associated with each feature
-sine_plot_bins <- ggplot() +
-  geom_point(data = sine_data_train,
-             mapping = aes(x = x1, y = x2, color = y),
-             alpha = 0.8) +
-  geom_vline(xintercept = sine_lime_default_bin_cuts$x1) +
-  geom_hline(yintercept = sine_lime_default_bin_cuts$x2) +
-  scale_color_manual(values = c(sinecolor_blue, sinecolor_red)) +
-  scale_fill_manual(values = c(sinecolor_blue, sinecolor_red)) +
-  scale_shape_manual(values = 23) +
-  theme_bw(base_family = "Times", base_size = 10) +
-  labs(x = TeX("$x_1$"),
-       y = TeX("$x_2$"),
-       color = TeX("y"),
-       fill = TeX("y"),
-       shape = "",
-       title = "Training Data Plot") +
-  guides(shape = guide_legend(order = 1),
-         fill = FALSE)
-
-# Obtain the simulated data associated with the poi
-sine_poi_perms <- sine_poi_lime_default %>%
-  slice(1) %>%
-  select(perms_raw, perms_pred_complex, perms_numerified, weights) %>%
-  mutate(perms_numerified =
-           map(perms_numerified,
-               .f = function(x) rename(x,
-                                       "x1num" = "x1",
-                                       "x2num" = "x2",
-                                       "x3num" = "x3"))) %>%
-  unnest(cols = c(perms_raw, perms_pred_complex, perms_numerified, weights)) %>%
-  select(-red) %>%
-  rename(rfpred = blue) %>%
-  mutate(case = factor(1:n())) %>%
-  select(case, everything())
-
-# Plot the permutations associated with the prediction of interest
-sine_plot_sims <- ggplot() +
-  geom_point(data = sine_poi_perms,
-             mapping = aes(x = x1,
-                           y = x2,
-                           fill = rfpred,
-                           color = rfpred),
-             alpha = 0.8,
-             shape = 21,
-             size = 0.75) +
-  geom_vline(xintercept = sine_lime_default_bin_cuts$x1) +
-  geom_hline(yintercept = sine_lime_default_bin_cuts$x2) +
-  geom_point(data = sine_poi %>% mutate(shape = "Prediction \nof Interest"),
-             mapping = aes(x = x1,
-                           y = x2,
-                           fill = rfprob_blue,
-                           shape = shape),
-             color = "black",
-             size = 5,
-             alpha = 0.8) +
-  scale_fill_gradient2(low = sinecolor_red,
-                        mid = '#f7f7f7',
-                        high = sinecolor_blue,
-                        midpoint = 0.5) +
-  scale_color_gradient2(low = sinecolor_red,
-                        mid = '#f7f7f7',
-                        high = sinecolor_blue,
-                        midpoint = 0.5) +
-  scale_shape_manual(values = 23) +
-  theme_bw(base_family = "Times", base_size = 10) +
-  labs(x = TeX("$x'_1$"),
-       y = TeX("$x'_2$"),
-       fill = "Random \nForest \nProbability \nfor 'blue'",
-       color = "Random \nForest \nProbability \nfor 'blue'",
-       shape = "",
-       title = "Untransformed Simulated Data Plot") +
-  guides(shape = guide_legend(order = 1)) + 
-  theme(aspect.ratio = 1)
-
-# Join the plots
-plot_grid(sine_plot_bins, sine_plot_sims,
-          nrow = 1,
-          rel_widths = c(0.47, 0.53))
-
-@
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\textwidth]{figure/sine-plot-step1ab-1}
+
+\end{knitrout}
 \caption{\emph{Training data plot} (left) and \emph{untransformed simulated data plot} (right).
@@
 
-<<sine-poi-explainer, warning = FALSE>>=
-
-# Determine the lime explanation cutoffs
-sine_poi_bounds <- sine_poi_lime_default %>%
-  select(case, feature, feature_value, feature_desc) %>%
-  separate(feature_desc, c("other", "upper"), sep = " <= ") %>%
-  separate(other, c("lower", "feature2"), sep = " < ") %>%
-  mutate(upper = ifelse(is.na(upper), "Inf", upper)) %>%
-  select(-feature2) %>%
-  mutate_at(.vars = c("lower", "upper"), .funs = as.numeric)
-
-# Extract the coefficients from the explainer
-sine_b0 <- sine_poi_lime_default$model_intercept[1]
-sine_b1 <- sine_poi_lime_default$feature_weight[2]
-sine_b2 <- sine_poi_lime_default$feature_weight[1]
-
-# Extract the bounds of the bins
-x1_lower <- sine_poi_bounds %>% filter(feature == "x1") %>% pull(lower)
-x1_upper <- sine_poi_bounds %>% filter(feature == "x1") %>% pull(upper)
-x2_lower <- sine_poi_bounds %>% filter(feature == "x2") %>% pull(lower)
-x2_upper <- sine_poi_bounds %>% filter(feature == "x2") %>% pull(upper)
-
-# Function for computing the predicted value via the explainer model
-sine_explainer <- function(z1, z2) sine_b0 + sine_b1 * z1 + sine_b2 * z2
-
-@
-
 \begin{figure}[!htbp]
 \centering
-<<sine-plot-step1c, out.width = '0.5\\textwidth', fig.width = 4.25, fig.height = 3.25, warning = FALSE>>=
-
-# Create a dataset with the rectangles that make up the four categories
-sine_exp_rect <-
-  data.frame(rect = factor(1:6),
-             z1 = c(0, 1, 0, 0, 1, 0),
-             z2 = c(1, 1, 1, 0, 0, 0),
-             case = factor(c(01, 11, 01, 00, 10, 00)),
-             x1 = c(-10, x1_lower, x1_upper, -10, x1_lower, x1_upper),
-             x2 = c(x1_lower, x1_upper, 10, x1_lower, x1_upper, 10),
-             y1 = c(x2_lower, x2_lower, x2_lower, -10, -10, -10),
-             y2 = c(10, 10, 10, x2_lower, x2_lower, x2_lower)) %>%
-  mutate(empred = sine_explainer(z1, z2),
-         case_names = ifelse(case == "11", "\nx'1 same bin \nx'2 same bin\n",
-                      ifelse(case == "10", "\nx'1 same bin \nx'2 diff bin\n",
-                      ifelse(case == "1", "\nx'1 diff bin \nx'2 same bin\n",
-                      "\nx'1 diff bin \nx'2 diff bin\n"))))
-
-# Plot of the numerified perturbations
-ggplot() +
-  geom_point(data = sine_poi_perms,
-             mapping = aes(x = x1,
-                           y = x2,
-                           color = rfpred),
-             alpha = 0.5,
-             shape = 20) +
-  geom_rect(data = sine_exp_rect,
-            mapping = aes(xmin = x1,
-                          xmax = x2,
-                          ymin = y1,
-                          ymax = y2,
-                          fill = case_names),
-            alpha = 0.7,
-            color = "black") +
-  geom_point(data = sine_poi,
-             mapping = aes(x = x1, y = x2, color = rfprob_blue),
-             size = 5,
-             shape = 18,
-             alpha = 0.8) +
-  geom_point(data = sine_poi %>% mutate(shape = "Prediction \nof Interest"),
-             mapping = aes(x = x1, y = x2, shape = shape),
-             size = 5,
-             alpha = 0.8) +
-  scale_color_gradient2(low = sinecolor_red,
-                        mid = '#f7f7f7',
-                        high = sinecolor_blue,
-                        midpoint = 0.5) +
-  scale_fill_manual(values = c("grey90", "grey25", "grey70", "grey1")) +
-  scale_shape_manual(values = 23) +
-  theme_bw(base_family = "Times", base_size = 10) +
-  labs(x = TeX("$x'_1$"),
-       y = TeX("$x'_2$"),
-       fill = "Interpretability \nTransformed \nFeature Value",
-       title = "Transformed Simulated Data Plot",
-       shape = "") +
-  guides(shape = guide_legend(order = 1),
-         size = FALSE,
-         color = FALSE) + 
-  theme(aspect.ratio = 1)
-
-@
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=0.5\textwidth]{figure/sine-plot-step1c-1}
+
+\end{knitrout}
 \caption{\emph{Transformed simulated data plot.} The values of $x'_2$ and $x'_1$ from the simulated data, colored by the random forest probabilities, are plotted behind rectangles representing the interpretability transformed values.
@@
 Overlaying the simulated data with the interpretability transformed values highlights the simplification imposed by the transformation.
-The rectangle where the prediction of interest is located contains a wide range of random forest predictions from \Sexpr{sine_poi_perms %>% filter(x1num == 1, x2num == 1) %>% summarise(min(rfpred)) %>% round(2)} to \Sexpr{sine_poi_perms %>% filter(x1num == 1, x2num == 1) %>% summarise(max(rfpred)) %>% round(2)}, but the interpretability transformation groups all of these values into one category.
+The rectangle where the prediction of interest is located contains a wide range of random forest predictions from 0.09 to 0.98, but the interpretability transformation groups all of these values into one category.
 While this transformation  provides easily understandable interpretations, it leads to an extreme over-simplification of the random forest model.
@@
 \centering
-<<sine-plot-step2ab, out.width = '\\textwidth', fig.width = 8, fig.height = 3.25>>=
-
-# Hex plot of the mean weights of the simulated values
-step2a <- ggplot() +
-  stat_summary_hex(data = sine_poi_perms,
-             mapping = aes(x = x1,
-                           y = x2,
-                           z = weights),
-             fun = mean,
-             bins = 20) +
-  geom_vline(xintercept = sine_poi_bounds %>% 
-               filter(feature == "x1") %>% 
-               select (lower, upper) %>% 
-               as.numeric()) +
-  geom_hline(yintercept = sine_poi_bounds %>% 
-               filter(feature == "x2") %>% 
-               select (lower, upper) %>% 
-               as.numeric()) +
-  geom_point(data = sine_poi %>%
-               mutate(shape = "Prediction \nof Interest"),
-             mapping = aes(x = x1, y = x2, shape = shape),
-             fill = sinecolor_blue,
-             size = 5,
-             alpha = 0.8) +
-  scale_fill_gradient(low = "grey90", high = "grey10") +
-  scale_shape_manual(values = 23) +
-  theme_bw(base_family = "Times", base_size = 10) +
-  labs(x = TeX("x'_1"),
-       y = TeX("x'_2"),
-       shape = "",
-       title = "Proximity Weights Plot",
-       fill = "Weight") +
-  guides(shape = guide_legend(order = 1)) + 
-  theme(aspect.ratio = 1)
-
-# Plot of features selected via all feture selection methods
-step2b <- sine_poi_lime_default %>%
-  slice(1) %>%
-  select(fs, hw, lp, tree) %>%
-  unnest(cols = c(fs, hw, lp, tree)) %>%
-  gather(method, feature) %>%
-  mutate(method = fct_recode(method,
-                             "Feature \nSelection \n(default)" = "fs",
-                             "Highest \nWeights" = "hw",
-                             "Lasso \nPath" = "lp",
-                             "Tree" = "tree"),
-         feature = factor(feature, levels = c("x3", "x2", "x1"))) %>%
-  ggplot(aes(x = method, y = feature, fill = feature)) +
-  geom_tile() +
-  scale_y_discrete(drop = FALSE) +
-  theme_bw(base_family = "Times", base_size = 10) +
-  labs(x = "Feature Selection Method",
-       y = "Feature",
-       fill = "Selected",
-       title = "Feature Selection Comparison Plot") +
-  scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) +
-  guides(fill = guide_legend(reverse = TRUE)) + 
-  theme(aspect.ratio = 1)
-
-plot_grid(step2a, step2b, rel_widths = c(0.55, 0.45))
-@
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\textwidth]{figure/sine-plot-step2ab-1}
+
+\end{knitrout}
 \caption{\kge{(Left) \emph{Proximity weights plot}.}\sout{Plots of the weight assignments and feature selection.} The plot \kge{is} \sout{on the left shows} a hex plot \kge{depicting the distribution} of the default \emph{lime} weights (Gower distances raised to the power of 1) assigned to the simulated data prior to the interpretability transformation.
@@
 
-<<sine-perms-subset>>=
-# Subset the simulated data to the region where the poi is located
-sine_poi_region_perms <- sine_poi_perms %>%
-  filter(x2 >= sine_poi_bounds %>% filter(feature == "x2") %>% pull(lower),
-         x1 >= sine_poi_bounds %>% filter(feature == "x1") %>% pull(lower),
-         x1 < sine_poi_bounds %>% filter(feature == "x1") %>% pull(upper))
-@
-
 \begin{figure*}[!htbp]
-<<sine-plot-step2cd, out.width = '\\textwidth', fig.width = 8, fig.height = 3.25, warning = FALSE>>=
-
-# Plot of the predictions in the four categories
-step2c <- ggplot() +
-  geom_rect(data = sine_exp_rect,
-            mapping = aes(xmin = x1,
-                          xmax = x2,
-                          ymin = y1,
-                          ymax = y2,
-                          fill = empred)) +
-    geom_point(data = sine_poi %>%
-               mutate(shape = "Prediction \nof Interest",
-                      exp_pred = sine_poi_lime_default$model_prediction[[1]]),
-             mapping = aes(x = x1, y = x2, fill = exp_pred, shape = shape),
-             size = 5,
-             alpha = 0.8) +
-  xlim(-10, 10) +
-  ylim(-10, 10) +
-  scale_shape_manual(values = 23) +
-  scale_fill_gradient2(low = sinecolor_red,
-                       mid = '#f7f7f7',
-                       high = sinecolor_blue,
-                       midpoint = 0.5,
-                       limits = c(0, 1)) +
-  guides(shape = guide_legend(order = 1)) +
-  theme_bw(base_family = "Times", base_size = 10) +
-  labs(x = TeX("x_1"),
-       y = TeX("x_2"),
-       fill = "Explainer \nModel \nPrediction \nfor 'blue'",
-       title = "Explainer Model Prediction Plot",
-       shape = "")
-
-# Calculate the residuals from the explainer model
-y <- sine_poi_perms$rfpred
-sine_poi_explainer <-
-  function(x1, x2) sine_b0 + (sine_b1 * x1) + (sine_b2 * x2)
-sine_poi_perms <- sine_poi_perms %>%
-  mutate(exppred = sine_poi_explainer(x1num, x2num)) %>%
-  mutate(resid = exppred - rfpred)
-
-# Create the residual plot
-step2d <- ggplot(sine_poi_perms, aes(x = exppred, y = resid)) +
-  geom_jitter(alpha = 0.5, width = 0.02) +
-  geom_hline(yintercept = 0) +
-  theme_bw(base_family = "Times", base_size = 10) +
-  labs(x = "Explainer Model Predictions",
-       y = "Residuals",
-       title = "Explainer Model Residual Plot")
-
-plot_grid(step2c, step2d, rel_widths = c(0.51, 0.49))
-@
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\textwidth]{figure/sine-plot-step2cd-1}
+
+\end{knitrout}
 \caption{(Left) \emph{Explainer model prediction plot}.
@@
 Consider the region where the prediction of interest is located.
-The explainer model provides a single prediction of \Sexpr{round(sine_poi_lime_default$model_prediction[[1]],2)} for the entire region as a summary of random forest predictions ranging from \Sexpr{round(min(sine_poi_region_perms$rfpred), 2)} to \Sexpr{round(max(sine_poi_region_perms$rfpred), 2)} with a mean and standard deviation \Sexpr{round(mean(sine_poi_region_perms$rfpred), 2)} and \Sexpr{round(sd(sine_poi_region_perms$rfpred), 2)}, respectively.
-The random forest prediction for the prediction of interest is \Sexpr{round(sine_poi$rfprob_blue,2)}.
-Consider that the mean prediction from the random forest (\Sexpr{round(mean(sine_poi_region_perms$rfpred), 2)}) agrees with the explainer model prediction (\Sexpr{round(sine_poi_lime_default$model_prediction[[1]],2)}) as is expected due to the nature of the explainer model used, but the random forest prediction associated with the case of interest (\Sexpr{round(sine_poi$rfprob_blue,2)}) is about a half \sout{1} standard deviation away from the mean.
+The explainer model provides a single prediction of 0.65 for the entire region as a summary of random forest predictions ranging from 0.09 to 0.98 with a mean and standard deviation 0.68 and 0.2, respectively.
+The random forest prediction for the prediction of interest is 0.74.
+Consider that the mean prediction from the random forest (0.68) agrees with the explainer model prediction (0.65) as is expected due to the nature of the explainer model used, but the random forest prediction associated with the case of interest (0.74) is about a half \sout{1} standard deviation away from the mean.
 \kgc{After reading the previous sentence again, I'm wondering if the next sentence is too dramatic.
@@
 \begin{figure*}[!htp]
-<<sine-plot-step3ab, out.width = '\\textwidth', fig.width = 10, fig.height = 4, warning = FALSE>>=
-
-# My lime explanation plot
-step3a <- sine_poi_lime_default %>% 
-  select(feature_weight, feature_desc) %>%
-  bind_rows(data.frame(feature_weight = 
-                         sine_poi_lime_default$model_intercept[1],
-                       feature_desc = "Intercept")) %>%
-  mutate(feature_magnitude = abs(feature_weight)) %>%
-  ggplot(aes(x = feature_desc, 
-             y = feature_magnitude,
-             fill = feature_weight)) + 
-  geom_col() + 
-  coord_flip() + 
-  labs(y = "Explainer Model Coefficient Magnitude",
-       x = "Explainer Model Feature",
-       fill = "Explainer \nModel \nCoefficient \nValue",
-       title = "Explanation Plot") + 
-  scale_fill_gradient2(low = sinecolor_red,
-                        mid = '#f7f7f7',
-                        high = sinecolor_blue,
-                        midpoint = 0,
-                        limits = c(-1, 1)) +
-  theme_bw(base_family = "Times", base_size = 10)
-
-# My plot of lime explanation boundaries
-step3b <- ggplot() +
-  geom_point(data = sine_poi_perms,
-             mapping = aes(x = x1,
-                           y = x2,
-                           color = rfpred,
-                           size = weights),
-             alpha = 0.8,
-             shape = 20) +
-  scale_size(range = c(0.1, 3)) +
-  geom_rect(data = sine_poi_bounds %>% filter(feature == "x1"),
-            mapping = aes(xmin = lower,
-                          xmax = upper,
-                          ymin = -Inf,
-                          ymax = Inf),
-            alpha = 0.25,
-            fill = "grey90",
-            color = "firebrick") +
-  geom_rect(data = sine_poi_bounds %>% 
-              filter(feature == "x2"),
-            mapping = aes(xmin = -Inf,
-                          xmax = Inf,
-                          ymin = lower,
-                          ymax = upper,
-                          color = coef),
-            alpha = 0.25,
-            fill = "grey90",
-            color = "steelblue") +
-  geom_point(data = sine_poi %>%
-               mutate(shape = "Prediction \nof Interest"),
-             mapping = aes(x = x1, y = x2, shape = shape, fill = rfprob_blue),
-             size = 7,
-             alpha = 0.8) +
-  scale_shape_manual(values = 23) +
-  scale_fill_gradient2(low = sinecolor_red,
-                        mid = '#f7f7f7',
-                        high = sinecolor_blue,
-                        midpoint = 0.5,
-                        limits = c(0, 1)) +
-  scale_color_gradient2(low = sinecolor_red,
-                        mid = '#f7f7f7',
-                        high = sinecolor_blue,
-                        midpoint = 0.5,
-                        limits = c(0, 1)) +
-  theme_bw(base_family = "Times", base_size = 10) +
-  labs(x = TeX("x'_1"),
-       y = TeX("x'_2"),
-       size = "Weight",
-       shape = "",
-       fill = "Random \nForest \nProbability \nfor 'blue'",
-       color = "Random \nForest \nProbability \nfor 'blue'",
-       title = "Complex and Explainer Model Comparison Plot") + 
-  guides(shape = guide_legend(order = 1)) + 
-  theme(aspect.ratio = 1)
-
-# # My plot of lime explanation boundaries
-# zoomedin <- ggplot() +
-#   geom_rect(data = sine_poi_bounds %>% filter(feature == "x1"),
-#             mapping = aes(xmin = lower,
-#                           xmax = upper,
-#                           ymin = -Inf,
-#                           ymax = Inf),
-#             alpha = 0.25,
-#             fill = NA,
-#             color = "firebrick") +
-#   geom_rect(data = sine_poi_bounds %>% filter(feature == "x2"),
-#             mapping = aes(xmin = -Inf,
-#                           xmax = Inf,
-#                           ymin = lower,
-#                           ymax = upper),
-#             alpha = 0.25,
-#             fill = NA,
-#             color = "steelblue") +
-#   geom_point(data = sine_poi_region_perms,
-#              mapping = aes(x = x1,
-#                            y = x2,
-#                            color = rfpred,
-#                            size = weights),
-#              alpha = 0.8) +
-#   geom_point(data = sine_poi %>%
-#                mutate(shape = "Prediction \nof Interest"),
-#              mapping = aes(x = x1, y = x2, fill = rfprob_blue, shape = shape),
-#              size = 7,
-#              alpha = 0.8) +
-#   scale_size(range = c(1, 3)) +
-#   scale_shape_manual(values = 23) +
-#   scale_fill_gradient2(low = sinecolor_red,
-#                         mid = '#f7f7f7',
-#                         high = sinecolor_blue,
-#                         midpoint = 0.5,
-#                         limits = c(0, 1)) +
-#   scale_color_gradient2(low = sinecolor_red,
-#                         mid = '#f7f7f7',
-#                         high = sinecolor_blue,
-#                         midpoint = 0.5,
-#                         limits = c(0, 1)) +
-#   theme_bw(base_family = "Times", base_size = 10) +
-#   labs(x = TeX("x'_1"),
-#        y = TeX("x'_2"),
-#        color = "Random \nForest \nProbability \nfor 'blue'",
-#        fill = "Random \nForest \nProbability \nfor 'blue'",
-#        fill = "",
-#        size = "Weight",
-#        shape = "") +
-#   guides(shape = guide_legend(order = 1)) +
-#   xlim(sine_poi_bounds$lower[2], sine_poi_bounds$upper[2]) +
-#   ylim(sine_poi_bounds$lower[1], max(sine_poi_perms$x2))
-# 
-# # Legend steps
-# full_weight_legend <- get_legend(full)
-# full_noleg <- full + theme(legend.position = "none")
-# sine_exp_legend <- get_legend(zoomedin + guides(size = FALSE))
-# zoomedin_weight_legend <- get_legend(zoomedin +
-#   guides(color = FALSE, fill = FALSE, shape = FALSE) +
-#   theme(legend.position = "bottom"))
-# zoomedin_noleg <- zoomedin + theme(legend.position = "none")
-# blank <- ggplot() + theme_void()
-#
-# # Join plots and legends
-# step3a_plots <- plot_grid(full_noleg, zoomedin_noleg, sine_exp_legend,
-#           nrow = 1,
-#           rel_widths = c(0.43, 0.42, 0.15))
-# step3a_weights <- plot_grid(full_weight_legend, zoomedin_weight_legend, blank,
-#           nrow = 1,
-#           rel_widths = c(0.425, 0.425, 0.15))
-# plot_grid(step3a_plots, step3a_weights,
-#           nrow = 2,
-#           rel_heights = c(0.925, 0.075))
-
-plot_grid(step3a, step3b)
-@
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\textwidth]{figure/sine-plot-step3ab-1}
+
+\end{knitrout}
 \caption{\emph{Explanation plot} (left) \hh{I very much like the explanation plot.
@@
 We can use the explanation plot to interpret the explainer model in terms of a ridge regression coefficients.
-The intercept, \Sexpr{round(sine_poi_lime_default$model_intercept[1], 2)}, is the predicted random forest probability for observations that are not in the same $x_1$ or $x_2$ quantile bins as the prediction of interest.
+The intercept, 0.47, is the predicted random forest probability for observations that are not in the same $x_1$ or $x_2$ quantile bins as the prediction of interest.
 The coefficients are interpreted as the amount that the average random forest probability increases/decreases if an observation falls in the same bin as the prediction of interest.
-In this example, the average random forest probability that an observation is in category 'blue' increases by \Sexpr{sine_poi_lime_default %>% filter(feature == "x2") %>% select(feature_weight) %>% round(2)} if an observation falls in the same $x_2$ quantile bin as the prediction of interest (i.e.
-the third quantile), and the average random forest probability that an observation is in category 'blue' decreases by \Sexpr{sine_poi_lime_default %>% filter(feature == "x1") %>% select(feature_weight) %>% round(2) %>% abs()} if an observation falls in the same $x_1$ quantile bin as the prediction of interest (i.e.
+In this example, the average random forest probability that an observation is in category 'blue' increases by 0.31 if an observation falls in the same $x_2$ quantile bin as the prediction of interest (i.e.
+the third quantile), and the average random forest probability that an observation is in category 'blue' decreases by 0.13 if an observation falls in the same $x_1$ quantile bin as the prediction of interest (i.e.
 the fourth quantile).
@@
 \hh{XXX Instead of writing out numbers, I would suggest to describe the bins in words lowest quartile, third, second, top quartile, ...
-XXX} For an observation that has a value of $x_1$ that is greater than \Sexpr{round(x1_lower, 1)} and less than or equal to \Sexpr{round(x1_upper, 1)}, the probability that the observation is predicted to be in category blue decreases by \Sexpr{abs(round(sine_b1, 1))}, and if an observation has a value of $x_2$ greater than \Sexpr{round(x2_lower, 1)}, the probability that the observation is predicted to be in category blue increases by \Sexpr{abs(round(sine_b2, 1))}.
+XXX} For an observation that has a value of $x_1$ that is greater than round(x1_lower, 1) and less than or equal to round(x1_upper, 1), the probability that the observation is predicted to be in category blue decreases by abs(round(sine_b1, 1)), and if an observation has a value of $x_2$ greater than round(x2_lower, 1), the probability that the observation is predicted to be in category blue increases by abs(round(sine_b2, 1)).
 Since the magnitude of the coefficient associated with $x_2$ is larger, it indicates that $x_2$ plays a more important role of the random forest prediction than $x_1$.
@@
 \begin{figure*}[!htbp]
-<<sine-plot-selected-features, out.width = "\\textwidth", fig.width = 8, fig.height = 3.25>>=
-
-# Determining order for cases based on group explanations
-sine_lime_default_case_order <- sine_lime_default %>%
-  select(case, feature, feature_desc) %>%
-  spread(key = feature, value = feature_desc) %>%
-  mutate(x1 = factor(x1, levels = c("x1 <= -4.884",
-                                    "-4.884 < x1 <= -0.302",
-                                    "-0.302 < x1 <= 4.844",
-                                    "4.844 < x1")),
-         x2 = factor(x2, levels = c("x2 <= -4.681",
-                                    "-4.681 < x2 <= -0.283",
-                                    "-0.283 < x2 <= 4.834",
-                                    "4.834 < x2"))) %>%
-  arrange(x1, x2, case)
-
-# Plot of all explanations from the default and kernel density cases
-sine_lime_default %>%
-  mutate(case = factor(case, levels = sine_lime_default_case_order$case),
-         feature_desc = factor(feature_desc,
-                               levels = c("x1 <= -4.884",
-                                    "-4.884 < x1 <= -0.302",
-                                    "-0.302 < x1 <= 4.844",
-                                    "4.844 < x1",
-                                    "x2 <= -4.681",
-                                    "-4.681 < x2 <= -0.283",
-                                    "-0.283 < x2 <= 4.834",
-                                    "4.834 < x2",
-                                    "x1", "x2")),
-         sim_method = factor(sim_method,
-                             levels = c("quantile_bins", "kernel_density")),
-         sim_method = fct_recode(sim_method,
-                                 "Four Quantile Bins" = "quantile_bins",
-                                 "Kernel Density" = "kernel_density")) %>%
-  ggplot(aes(x = case,
-             y = feature_desc,
-             fill = feature_weight,
-             color = feature_weight)) +
-  geom_tile() +
-  facet_grid(feature ~ ., scales = "free", space = "free") +
-  scale_fill_gradient2(low = 'firebrick',
-                       mid = '#f7f7f7',
-                       high = 'steelblue') +
-  scale_color_gradient2(low = 'firebrick',
-                        mid = '#f7f7f7',
-                        high = 'steelblue') +
-  theme_bw(base_family = "Times", base_size = 10) +
-  theme(axis.text.x = element_blank()) +
-  labs(x = "Case",
-       y = "Feature",
-       fill = "Feature \nWeight",
-       color = "Feature \nWeight")
-
-@
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\textwidth]{figure/sine-plot-selected-features-1}
+
+\end{knitrout}
 \caption{Heatmap of the ridge regression coefficients from the LIME explanations for each of the cases in the \data \ test set for the application of LIME with 4 quantile bins.
@@
 \begin{figure*}[!htbp]
-<<sine-plot-agg-exp, warning = FALSE, out.width = '\\textwidth', fig.width = 10, fig.height = 3.25>>=
-
-# Compute the coef averages in each bin
-mean_coefs <- sine_lime_default %>%
-  select(case, feature, feature_weight) %>%
-  spread(feature, feature_weight) %>%
-  rename("x1_coef" = "x1", "x2_coef" = "x2") %>%
-  full_join(sine_lime_default %>%
-              select(case, feature, feature_desc) %>%
-              spread(feature, feature_desc),
-            by = "case") %>%
-  group_by(x1, x2) %>%
-  summarise(mean_coef_x1 = mean(x1_coef),
-            mean_coef_x2 = mean(x2_coef)) %>%
-  ungroup() %>%
-  separate(x1, c("x1_other", "x1_upper"), sep = " <= ") %>%
-  separate(x1_other, c("x1_almost_lower", "x1_other"), sep = "x1") %>%
-  select(-x1_other) %>%
-  separate(x1_almost_lower, c("x1_lower", "x1_other"), sep = " <") %>%
-  select(-x1_other) %>%
-  separate(x2, c("x2_other", "x2_upper"), sep = " <= ") %>%
-  separate(x2_other, c("x2_almost_lower", "x2_other"), sep = "x2") %>%
-  select(-x2_other) %>%
-  separate(x2_almost_lower, c("x2_lower", "x2_other"), sep = " <") %>%
-  select(-x2_other) %>%
-  mutate(x1_lower = ifelse(x1_lower == "", "-Inf", x1_lower),
-         x1_upper = ifelse(is.na(x1_upper), "Inf", x1_upper),
-         x2_lower = ifelse(x2_lower == "", "-Inf", x2_lower),
-         x2_upper = ifelse(is.na(x2_upper), "Inf", x2_upper)) %>%
-  mutate_at(.vars = c("x1_lower", "x1_upper",
-                      "x2_lower", "x2_upper"),
-            .funs = as.numeric) %>%
-  arrange(x1_lower)
-
-# Compute the average of beta1 + beta2 in each bin
-mean_coefs_added <- sine_lime_default %>%
-  select(case, feature, feature_weight) %>%
-  spread(feature, feature_weight) %>%
-  mutate(coef_x1_plus_x2 = x1 + x2) %>%
-  select(-x1, -x2) %>%
-  full_join(sine_lime_default %>%
-              select(case, feature, feature_desc) %>%
-              spread(feature, feature_desc),
-            by = "case") %>%
-  group_by(x1, x2) %>%
-  summarise(mean_coef_x1_plus_x2 = mean(coef_x1_plus_x2)) %>%
-  ungroup() %>%
-  separate(x1, c("x1_other", "x1_upper"), sep = " <= ") %>%
-  separate(x1_other, c("x1_almost_lower", "x1_other"), sep = "x1") %>%
-  select(-x1_other) %>%
-  separate(x1_almost_lower, c("x1_lower", "x1_other"), sep = " <") %>%
-  select(-x1_other) %>%
-  separate(x2, c("x2_other", "x2_upper"), sep = " <= ") %>%
-  separate(x2_other, c("x2_almost_lower", "x2_other"), sep = "x2") %>%
-  select(-x2_other) %>%
-  separate(x2_almost_lower, c("x2_lower", "x2_other"), sep = " <") %>%
-  select(-x2_other) %>%
-  mutate(x1_lower = ifelse(x1_lower == "", "-Inf", x1_lower),
-         x1_upper = ifelse(is.na(x1_upper), "Inf", x1_upper),
-         x2_lower = ifelse(x2_lower == "", "-Inf", x2_lower),
-         x2_upper = ifelse(is.na(x2_upper), "Inf", x2_upper)) %>%
-  mutate_at(.vars = c("x1_lower", "x1_upper",
-                      "x2_lower", "x2_upper"),
-            .funs = as.numeric) %>%
-  arrange(x1_lower)
-
-coef_ext <- max(abs(min(mean_coefs_added$mean_coef_x1_plus_x2)),
-                abs(max(mean_coefs_added$mean_coef_x1_plus_x2)))
-
-lower_coef_col <- -coef_ext - 0.05
-upper_coef_col <- coef_ext + 0.05
-
-# Plot the x1 averaged coefficients
-plot_x1coefs <- ggplot() +
-  geom_rect(data = mean_coefs,
-            mapping = aes(xmin = x1_lower,
-                          xmax = x1_upper,
-                          ymin = x2_lower,
-                          ymax = x2_upper,
-                          fill = mean_coef_x1)) +
-  xlim(-10, 10) +
-  ylim(-10, 10) +
-  scale_fill_gradient2(low = "firebrick",
-                       mid = "white",
-                       high = "steelblue",
-                       midpoint = 0,
-                       limits = c(lower_coef_col, upper_coef_col)) +
-  theme_bw(base_family = "Times", base_size = 12) +
-  labs(x = TeX("$x_1$"),
-       y = TeX("$x_2$"),
-       fill = TeX('Ave $\\hat{\\beta}_1$'),
-       color = "RF Prob",
-       title = TeX("Average $\\hat{\\beta}_1$ by Quantile Bins")) +
-  theme(legend.position = "none")
-
-# Plot the x2 averaged coefficients
-plot_x2coefs <- ggplot() +
-  geom_rect(data = mean_coefs,
-            mapping = aes(xmin = x1_lower,
-                          xmax = x1_upper,
-                          ymin = x2_lower,
-                          ymax = x2_upper,
-                          fill = mean_coef_x2)) +
-  xlim(-10, 10) +
-  ylim(-10, 10) +
-  scale_fill_gradient2(low = "firebrick",
-                       mid = "white",
-                       high = "steelblue",
-                       midpoint = 0,
-                       limits = c(lower_coef_col, upper_coef_col)) +
-  theme_bw(base_family = "Times", base_size = 12) +
-  labs(x = TeX("$x_1$"),
-       y = TeX("$x_2$"),
-       fill = TeX('Ave $\\hat{\\beta}_2$'),
-       color = "RF Prob",
-       title = TeX("Average $\\hat{\\beta}_2$ by Quantile Bins")) +
-  theme(legend.position = "none")
-
-# Plot the x1 + x2 averaged coefficients
-plot_x1plusx2coefs <- ggplot() +
-  geom_rect(data = mean_coefs_added,
-            mapping = aes(xmin = x1_lower,
-                          xmax = x1_upper,
-                          ymin = x2_lower,
-                          ymax = x2_upper,
-                          fill = mean_coef_x1_plus_x2)) +
-  xlim(-10, 10) +
-  ylim(-10, 10) +
-  scale_fill_gradient2(low = "firebrick",
-                       mid = "white",
-                       high = "steelblue",
-                       midpoint = 0,
-                       limits = c(lower_coef_col, upper_coef_col)) +
-  theme_bw(base_family = "Times", base_size = 12) +
-  labs(x = TeX("$x_1$"),
-       y = TeX("$x_2$"),
-       fill = "Coefficient \nAverage",
-       color = "RF Prob",
-       title = TeX("Average $\\hat{\\beta}_1+\\hat{\\beta}_2$ by Quantile Bins"))
-
-# Get legend and remove legend from addedplot
-ave_coef_leg <- get_legend(plot_x1plusx2coefs)
-plot_x1plusx2coefs <- plot_x1plusx2coefs +
-  theme(legend.position = "none")
-
-# Join the plots
-plot_grid(plot_x1coefs, plot_x2coefs, plot_x1plusx2coefs, ave_coef_leg,
-          nrow = 1, rel_widths = c(0.3, 0.3, 0.3, 0.1))
-
-@
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\textwidth]{figure/sine-plot-agg-exp-1}
+
+\end{knitrout}
 \caption{Plots of the four quantile bin grids of $x_1$ and $x_2$ colored by averaged explainer model coefficient values.
@@
 \subsection{Explainer Model Assessment} \label{assess-set}
-
-<<sine-mid-explainer-pred>>=
-# Determine the explainer model predictions with the
-# random forest predictions are between 0.25 and 0.75
-mid_expred <- sine_lime_default %>%
-  group_by(case, sim_method) %>%
-  ungroup() %>%
-  filter(label_prob > 0.25, label_prob < 0.75) %>%
-  select(label_prob, model_prediction)
-@
 
@@
 \begin{figure}[!t]
-<<sine-plot-grid, warning = FALSE, out.width = '0.5\\textwidth', fig.width = 4, fig.height = 3.2>>=
-
-sine_chosen_errors <- sine_data_test %>%
-  filter(y != rfpred, x1 > 0, x1 < 5, x2 > 0)
-
-sine_error_bounds <- sine_lime_default %>%
-  filter(case %in% sine_chosen_errors$case) %>%
-  select(case, feature, feature_value, feature_desc) %>%
-  separate(feature_desc, c("other", "upper"), sep = " <= ") %>%
-  separate(other, c("lower", "feature2"), sep = " < ") %>%
-  mutate(upper = ifelse(is.na(upper), "Inf", upper)) %>%
-  select(-feature2) %>%
-  mutate_at(.vars = c("lower", "upper"), .funs = as.numeric)
-
-# Determine the bin cuts
-sine_lime_default_bin_cuts <- sine_lime_default %>%
-  select(feature, feature_desc) %>%
-  unique() %>%
-  separate(feature_desc, c("other", "bin_cut"), sep = " <= ") %>%
-  select(-other) %>%
-  na.omit() %>%
-  mutate(bin_cut = as.numeric(bin_cut)) %>%
-  arrange(feature) %>%
-  mutate(case = rep(1:3, 2)) %>%
-  spread(feature, bin_cut)
-
-# Plot the LIME explainer model predictions for the
-# testing data with the 4 quantile bins
-ggplot() +
-  geom_vline(xintercept = sine_lime_default_bin_cuts$x1) +
-  geom_hline(yintercept = sine_lime_default_bin_cuts$x1) +
-  geom_point(data = sine_lime_default %>%
-               select(case, feature, feature_value, model_prediction) %>%
-               spread(feature, feature_value),
-             mapping = aes(x = x1,
-                           y = x2,
-                           color = model_prediction),
-             alpha = 0.8) +
-  scale_color_gradient2(low = sinecolor_red,
-                        mid = '#f7f7f7',
-                        high = sinecolor_blue,
-                        midpoint = 0.5) +
-  scale_fill_gradient2(low = "firebrick",
-                       mid = '#f7f7f7',
-                       high = "steelblue",
-                       midpoint = 0) +
-  theme_bw(base_family = "Times", base_size = 10) +
-  labs(x = TeX("$x_1$"),
-       y = TeX("$x_2$"),
-       color = "LIME \nExplainer \nModel \nPrediction",
-       title = "Test Data Colored by Explainer Prediction")
-
-@
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=0.5\textwidth]{figure/sine-plot-grid-1}
+
+\end{knitrout}
 \caption{Plot of the test \data \ colored by the predictions from the LIME explainer model.
@@
 When the random forest prediction is low, the explainer model is overestimating the random forest prediction, and when the random forest prediction is high, the explainer model is underestimating the prediction.
-When the random forest prediction is close to 0.5, the explainer model predictions \hh{cover a wide} range (from \Sexpr{round(min(mid_expred$model_prediction), 2)} to \Sexpr{round(max(mid_expred$model_prediction), 2)}).
+When the random forest prediction is close to 0.5, the explainer model predictions \hh{cover a wide} range (from 0.28 to 0.72).
 This plot \hh{clearly indicates} that there is an issue with the faithfulness of the explainer models in terms of their ability to produce predictions similar to the random forest.
@@
 Additionally, the points in \autoref{fig:sine-plot-compare-preds} are colored by the $R^2$ value from the corresponding explainer model.
-This shows that the $R^2$ values of the explainer models from the test set range from \Sexpr{round(min(sine_lime_default$model_r2), 2)} to \Sexpr{round(max(sine_lime_default$model_r2), 2)}.
+This shows that the $R^2$ values of the explainer models from the test set range from 0.04 to 0.49.
 These are all low $R^2$ values.
@@
 \begin{figure}[!t]
-<<sine-plot-compare-preds, out.width = '0.5\\textwidth', fig.width = 4, fig.height = 3.25>>=
-sine_lime_default %>%
-  group_by(case, sim_method) %>%
-  slice(1) %>%
-  ungroup() %>%
-  mutate(sim_method = fct_recode(sim_method,
-                                 "Quantile Bins" = "quantile_bins",
-                                 "Kernel Density" = "kernel_density")) %>%
-  ggplot(aes(x = label_prob, y = model_prediction, color = model_r2)) +
-  geom_point() +
-  geom_smooth(se = FALSE, method = "loess", color = "black") +
-  geom_abline(intercept = 0, slope = 1, linetype = "dashed") +
-  theme_bw(base_family = "Times", base_size = 10) +
-  labs(x = "Random Forest Prediction",
-       y = "Explainer Model Prediction",
-       color = "Explainer \nModel \nR2",
-       title = "Complex and Explainer Model \nPrediction Comparison") +
-  scale_color_gradient(low = "grey90", high = "grey40")
-@
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=0.5\textwidth]{figure/sine-plot-compare-preds-1}
+
+\end{knitrout}
 \caption{Plot of the explainer model predictions versus the random forest predictions for each observation in the \data \ test set.
@@
 \begin{figure}[!t]
-<<sine-plot-compare-bins, warning = FALSE, out.width = '0.5\\textwidth', fig.width = 6.75, fig.height = 5.5>>=
-
-# Compute the average explainer model predictions per bin
-bin_mean_exp_pred <- sine_lime_default %>%
-  select(case, model_prediction) %>%
-  group_by(case) %>%
-  slice(1) %>%
-  ungroup() %>%
-  full_join(sine_lime_default %>%
-              select(case, feature, feature_desc) %>%
-              spread(feature, feature_desc),
-            by = "case") %>%
-  group_by(x1, x2) %>%
-  summarise(mean_exp_pred = mean(model_prediction)) %>%
-  ungroup() %>%
-  separate(x1, c("x1_other", "x1_upper"), sep = " <= ") %>%
-  separate(x1_other, c("x1_almost_lower", "x1_other"), sep = "x1") %>%
-  select(-x1_other) %>%
-  separate(x1_almost_lower, c("x1_lower", "x1_other"), sep = " <") %>%
-  select(-x1_other) %>%
-  separate(x2, c("x2_other", "x2_upper"), sep = " <= ") %>%
-  separate(x2_other, c("x2_almost_lower", "x2_other"), sep = "x2") %>%
-  select(-x2_other) %>%
-  separate(x2_almost_lower, c("x2_lower", "x2_other"), sep = " <") %>%
-  select(-x2_other) %>%
-  mutate(x1_lower = ifelse(x1_lower == "", "-Inf", x1_lower),
-         x1_upper = ifelse(is.na(x1_upper), "Inf", x1_upper),
-         x2_lower = ifelse(x2_lower == "", "-Inf", x2_lower),
-         x2_upper = ifelse(is.na(x2_upper), "Inf", x2_upper)) %>%
-  mutate_at(.vars = c("x1_lower", "x1_upper",
-                      "x2_lower", "x2_upper"),
-            .funs = as.numeric) %>%
-  arrange(x1_lower)
-
-# Compute the lower and upper limits of the explainer model predictions
-pred_col_lower = min(bin_mean_exp_pred$mean_exp_pred)
-pred_col_upper = max(bin_mean_exp_pred$mean_exp_pred)
-
-# Plot of the average feature weights by bin
-ggplot() +
-  geom_rect(data = bin_mean_exp_pred,
-            mapping = aes(xmin = x1_lower,
-                          xmax = x1_upper,
-                          ymin = x2_lower,
-                          ymax = x2_upper,
-                          fill = mean_exp_pred),
-            alpha = 1) +
-  geom_point(data = sine_lime_default %>%
-               select(case, feature, feature_value,
-                      label_prob, model_prediction) %>%
-               spread(feature, feature_value),
-             mapping =  aes(x = x1, y = x2, color = label_prob)) +
-  geom_point(data = sine_lime_default %>%
-               select(case, feature, feature_value,
-                      label_prob, model_prediction) %>%
-               spread(feature, feature_value) %>%
-               mutate(rf1 = ifelse(label_prob > 0.5, TRUE, FALSE),
-                      lime1 = ifelse(model_prediction > 0.5,
-                                     TRUE, FALSE)) %>%
-               mutate(diff = rf1 - lime1) %>%
-               select(case, x1, x2, diff) %>%
-               filter(diff != 0) %>%
-               mutate(shape = "Random Forest \nMisclassified \nPredictions"),
-             mapping =  aes(x = x1, y = x2, color = label_prob,
-                            shape = shape),
-             alpha = 1,
-             size = 3,
-             color = "black") +
-  scale_color_gradient2(low = "firebrick",
-                        mid = '#f7f7f7',
-                        high = "steelblue",
-                        midpoint = 0.5,
-                        limits = c(pred_col_lower, pred_col_upper)) +
-  scale_fill_gradient2(low = "firebrick",
-                       mid = '#f7f7f7',
-                       high = "steelblue",
-                       midpoint = 0.5,
-                       limits = c(pred_col_lower, pred_col_upper)) +
-  scale_shape_manual(values = 1) +
-  xlim(-10, 10) +
-  ylim(-10, 10) +
-  theme_bw(base_family = "Times", base_size = 14) +
-  labs(x = TeX("$x_1$"),
-       y = TeX("$x_2$"),
-       shape = "",
-       fill = "Average \nExplainer \nModel \nProbability \nfor 'blue'",
-       color = "Random \nForest \nProbability \nfor 'blue'",
-       title = "Quantile Grid Comparison of LIME Explainer \nModel Predictions to Random Forest \nPredictions") +
-  guides(shape = guide_legend(order = 1),
-         fill = guide_legend(order = 2, reverse = T),
-         color = guide_legend(order = 3, reverse = T))
-
-@
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=0.5\textwidth]{figure/sine-plot-compare-bins-1}
+
+\end{knitrout}
 \caption{Plot comparing the LIME explainer models predictions to the random forest predictions in the context of the four $x_1$ and $x_2$ quantile bins.
@@
 The prediction of interest %we would like to provide an explanation for has
-\hh{is} $x^*=$ (\Sexpr{round(sine_poi$x1, 2)}, \Sexpr{round(sine_poi$x2, 2)}, \Sexpr{round(sine_poi$x3, 2)}) \hh{with} $f(x^*)=0.83$.
+\hh{is} $x^*=$ (1.23, 8.47, -0.99) \hh{with} $f(x^*)=0.83$.
 
@@
 \begin{figure}[!b]
-<<concept-heatmap, out.width = '0.5\\textwidth', fig.width = 6, fig.height = 3>>=
-# Specify the number of cases and LIME input options
-ncases = 10
-ninputs = 5
-
-# Create a good case of chosen feature example data
-set.seed(20191008)
-heatmap_data_good <- tibble(case = factor(rep(1:ncases, each = ninputs),
-                                     levels = ncases:1),
-                       input = factor(rep(1:ninputs, ncases)),
-                       feature = factor(c(rep(1, 5),
-                                          rep(2, 5),
-                                          rep(3, 5),
-                                          rep(1, 5),
-                                          rep(1, 5),
-                                          rep(4, 5),
-                                          rep(1, 5),
-                                          rep(3, 5),
-                                          rep(1, 5),
-                                          rep(4, 5)))) %>%
-  mutate(input = forcats::fct_recode(input, "A" = "1", "B" = "2",
-                                     "C" = "3", "D" = "4", "E" = "5"))
-
-# Create the conceptual good heatmap
-heatmap_plot_good <- ggplot(data = heatmap_data_good,
-                            mapping = aes(x = input,
-                                          y = case,
-                                          fill = feature,
-                                          color = feature)) +
-  geom_tile() +
-  labs(x = "Implementation Method",
-       y = "Case",
-       fill = "Feature",
-       title = "Situation 1: \nConsistent Explanations") +
-  theme_bw(base_family = "Times", base_size = 12) +
-  scale_fill_grey() +
-  scale_color_grey() +
-  theme(legend.position = "none")
-
-# Create a bad case of chosen feature example data
-set.seed(20190627)
-heatmap_data_bad <- tibble(case = factor(rep(1:ncases, ninputs),
-                                     levels = ncases:1),
-                       input = factor(rep(1:ninputs, each = ncases)),
-                       feature = factor(rep(c(1, 2, 4, 3, 2), each = 10))) %>%
-  mutate(input = forcats::fct_recode(input, "A" = "1", "B" = "2",
-                                     "C" = "3", "D" = "4", "E" = "5"))
-
-# Create the conceptual bad heatmap
-heatmap_plot_bad <- ggplot(data = heatmap_data_bad,
-                            mapping = aes(x = input,
-                                          y = case,
-                                          fill = feature,
-                                          color = feature)) +
-  geom_tile() +
-  labs(x = "Implementation Method",
-       y = "Case",
-       fill = "Feature",
-       title = "Situation 2: \nInconsistent Explanations") +
-  theme_bw(base_family = "Times", base_size = 12) +
-  scale_fill_grey() + 
-  scale_color_grey()
-
-heatmap_leg <- get_legend(heatmap_plot_bad)
-heatmap_plot_bad <- heatmap_plot_bad + theme(legend.position = 'none')
-
-# Join the plots
-plot_grid(heatmap_plot_good, heatmap_plot_bad, heatmap_leg,
-          nrow = 1,
-          rel_widths = c(0.45, 0.45, 0.1))
-
-@
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=0.5\textwidth]{figure/concept-heatmap-1}
+
+\end{knitrout}
 \caption{Two hypothetical examples of feature heatmaps showing the top feature chosen for 10 cases across 5 different implementations of LIME (sets of tuning parameters).
@@
 \begin{figure}[!t]
-<<sine-feature-heatmap, out.width = '0.5\\textwidth', fig.width = 5, fig.height = 5.5>>=
-feature_heatmap(sine_lime_explain$explain,
-                order_method = "PCA") +
-  theme_bw(base_family = "Times", base_size = 10) +
-  theme(legend.position = "bottom",
-        axis.text.y = element_blank(),
-        axis.ticks.y = element_blank()) +
-  labs(y = "Case")
-@
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=0.5\textwidth]{figure/sine-feature-heatmap-1}
+
+\end{knitrout}
 \caption{Feature heatmap of the various LIME implementations applied to the \data.
@@
 \begin{figure}[!t]
-<<sine-metric-plot, out.width = '0.5\\textwidth', fig.width = 4.5, fig.height = 4, warning = FALSE>>=
-
-# Create the metric plot
-metric_plot(sine_lime_explain$explain) +
-  theme_bw(base_family = "Times") +
-  scale_color_gradient(low = "grey10", high = "grey90")
-
-@
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=0.5\textwidth]{figure/sine-metric-plot-1}
+
+\end{knitrout}
 \caption{Example of a metric comparison plot using the \data.
@@
 
-<<bullet-data>>=
-
-# Load the hamby data
-bullet_train <- read.csv("../data/hamby173and252_train.csv")
-bullet_test <- read.csv("../data/hamby224_test.csv")
-
-# Extract the features and order them based on feature importance
-bullet_features <- rownames(bulletxtrctr::rtrees$importance)
-bullet_features_ordered <-
-  data.frame(feature = rownames(bulletxtrctr::rtrees$importance),
-             MeanDecreaseGini = bulletxtrctr::rtrees$importance) %>%
-  arrange(desc(MeanDecreaseGini)) %>%
-  mutate(feature = fct_recode(feature,
-                              "CCF" = "ccf",
-                              "CMS" = "cms",
-                              "Matches" = "matches",
-                              "Mismatches" = "mismatches",
-                              "Non-CMS" = "non_cms",
-                              "Rough Correlation" = "rough_cor",
-                              "Distance Std Dev" = "sd_D",
-                              "Distance" = "D",
-                              "Sum Peaks" = "sum_peaks"))
-
-bullet_features_ordered <- bullet_features_ordered %>%
-  mutate(feature = factor(feature, levels = bullet_features_ordered$feature))
-
-@
-
 \hh{The random forest model trained in \citet{hare:2016} is available as object rtrees from the \emph{bulletxtrctr} R package.
-rtrees is trained on a set of scans obtained from one set of bullets of the James Hamby Consecutively Rifled Ruger Barrel Study \citep{hamby:2009} and based on \Sexpr{dim(bullet_train)[1]} land-to-land comparisons.}
+rtrees is trained on a set of scans obtained from one set of bullets of the James Hamby Consecutively Rifled Ruger Barrel Study \citep{hamby:2009} and based on 83028 land-to-land comparisons.}
 The model was fit using nine features from the training data that measure the similarity between two bullet signatures (CCF, CMS, distance, distance standard deviation, matches, mismatches, non-CMS, rough correlation, sum of peaks), and the response variable (same source) is a binary variable indicating whether the two bullets were fired from the same gun (same source = TRUE) or not (same source = FALSE).
@@
 \begin{figure}[!t]
-<<bullet-plot-train, out.width = '0.5\\textwidth', fig.width = 5, fig.height = 5, warning = FALSE>>=
-bullet_train %>%
-  select(all_of(bullet_features), samesource) %>%
-  pivot_longer(names_to = "feature",
-               values_to = "value",
-               all_of(bullet_features)) %>%
-  select(feature, value, samesource) %>%
-  mutate(feature = fct_recode(feature,
-                              "CCF" = "ccf",
-                              "CMS" = "cms",
-                              "Matches" = "matches",
-                              "Mismatches" = "mismatches",
-                              "Non-CMS" = "non_cms",
-                              "Rough Correlation" = "rough_cor",
-                              "Distance" = "D",
-                              "Distance Std Dev" = "sd_D",
-                              "Sum Peaks" = "sum_peaks")) %>%
-  ggplot(aes(x = value, fill = samesource, color = samesource)) +
-  geom_histogram(position = "fill", bins = 30) +
-  facet_wrap( ~ feature, scales = "free", strip.position = "bottom") +
-  labs(x = "",
-       y = "Proportion",
-       fill = "Same Source?",
-       color = "Same Source?",
-       title = "Hamby Bullet Training Data") +
-  theme_bw(base_family = "Times", base_size = 10) +
-  theme(legend.position = "bottom",
-        strip.placement = "outside",
-        strip.background = element_rect(color = "white",
-                                        fill = "white")) +
-  scale_color_manual(values = c("grey50", "darkorange")) +
-  scale_fill_manual(values = c("grey50", "darkorange"))
-@
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=0.5\textwidth]{figure/bullet-plot-train-1}
+
+\end{knitrout}
 \caption{Distribution of the response variable \hh{explain the spine plots \cite{hummel:1996} a bit - they are non-standard}, same source, for the features used to fit the random forest rtrees.
@@
 \begin{figure}[!t]
-<<bullet-plot-scatter, out.width = '0.5\\textwidth', fig.width = 9, fig.height = 9, warning = FALSE>>=
-ggplot(data = bullet_train %>%
-         mutate(samesource = as.numeric(samesource)) %>%
-         rename("CCF" = "ccf", "CMS" = "cms", "Matches" = "matches",
-           "Mismatches" = "mismatches", "Non-CMS" = "non_cms",
-           "Rough Correlation" = "rough_cor", "Distance Std Dev" = "sd_D",
-           "Distance" = "D", "Sum Peaks" = "sum_peaks")) +
-  stat_summary_2d(mapping = aes(x = .panel_x,
-                                y = .panel_y,
-                                z = samesource),
-                  bins = 50,
-                  fun = mean) +
-  geom_autohistogram() +
-  facet_matrix(vars(bullet_features_ordered$feature),
-               layer.diag = 2,
-               switch = "both") +
-  scale_fill_gradient2(low = "grey50",
-                       high = "darkorange",
-                       midpoint = 0.5) +
-  theme_bw(base_family = "Times", base_size = 10) +
-  theme(strip.placement = "outside",
-        strip.background = element_rect(color = "white",
-                                        fill = "white"),
-        panel.grid.major = element_blank(),
-        panel.grid.minor = element_blank(),
-        legend.position = "bottom") +
-  labs(fill = "Proportion of Same Source Observations")
-@
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=0.5\textwidth]{figure/bullet-plot-scatter-1}
+
+\end{knitrout}
 \caption{Bivariate visualizations of the rtrees training data.
@@
 \begin{figure}[!b]
-<<bullet-plot-rfvi, out.width = '0.5\\textwidth', fig.width = 3.5, fig.height = 1.5>>=
-ggplot(bullet_features_ordered %>%
-         mutate(feature = factor(feature, levels = rev(levels(feature)))),
-       aes(x = MeanDecreaseGini, y = feature)) +
-  geom_col() +
-  labs(y = "Feature",
-       x = "Variable Importance") +
-  theme_bw(base_size = 10, base_family = "Times")
-@
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=0.5\textwidth]{figure/bullet-plot-rfvi-1}
+
+\end{knitrout}
 \caption{Variable importance plot for the random forest fit to the bullet matching dataset.
@@
 \begin{figure*}[!b]
-<<bullet-plot-rfpcp, out.width = '\\textwidth', warning = FALSE>>=
-
-# Create (or load) the parallel coordinate plot
-if (file.exists("./figure-static/bullet_pcp.png")) {
-
-  # Load and print the plot
-  knitr::include_graphics("./figure-static/bullet_pcp.png")
-
-} else {
-
-  # Create the plot
-  bullet_pcp <- bullet_train %>%
-    select(all_of(bullet_features), samesource, rfscore) %>%
-    bind_rows(bullet_test %>%
-                select(all_of(bullet_features), samesource, rfscore),
-              .id = "set") %>%
-    mutate(set = fct_recode(set,
-                            "Training Set" = "1",
-                            "Testing Set" = "2"),
-           samesource = fct_recode(factor(samesource),
-                                  "Same Source = TRUE" = "TRUE",
-                                  "Same Source = FALSE" = "FALSE")) %>%
-    rename("CCF" = "ccf", "CMS" = "cms", "Matches" = "matches",
-           "Mismatches" = "mismatches", "Non-CMS" = "non_cms",
-           "Rough Correlation" = "rough_cor", "Distance Std Dev" = "sd_D",
-           "Distance" = "D", "Sum Peaks" = "sum_peaks") %>%
-    na.omit() %>%
-    ggplot(aes(color = rfscore)) +
-    geom_pcp(aes(vars = vars(bullet_features_ordered$feature)),
-             alpha = 0.2) +
-    facet_grid(set ~ samesource) +
-    scale_color_gradient2(low = "grey50",
-                          high = "darkorange",
-                          midpoint = 0.5) +
-    theme_bw(base_family = "Times", base_size = 10) +
-    theme(axis.text.x = element_text(angle = 45, hjust = 1),
-          strip.placement = "outside",
-          strip.background = element_rect(color = "white",
-                                          fill = "white")) +
-    labs(x = "Features Ordered by Random Forest Variable Importance \n(highest to lowest from left to right)",
-         y = "Scaled Feature Values",
-         color = "Random \nForest \nProbability")
-
-  # Save the plot
-  ggplot2::ggsave(plot = bullet_pcp,
-                  filename = "./figure-static/bullet_pcp.png",
-                  width = 7.5,
-                  height = 3.5,
-                  units = "in")
-}
-
-@
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\textwidth]{./figure-static/bullet_pcp}
+
+\end{knitrout}
 \caption{Parallel coordinate plots of rtrees training and testing data.
@@
 
-rtrees was tested on another set of bullets from the Hamby study with \Sexpr{dim(bullet_test)[1]} rows of land comparisons.
+rtrees was tested on another set of bullets from the Hamby study with 432 rows of land comparisons.
 \autoref{fig:bullet-plot-rfpcp} shows parallel coordinate plots of the rtrees training (top row) and testing (bottom row) datasets.
@@
 
-<<bullet-lime>>=
-
-# Apply LIME to all but two cases without returning the permutations
-if (file.exists("../data/hamby_lime.rds")){
-
-  # Load the files
-  #bullet_lime_noperms <- readRDS("../data/hamby_lime.rds")
-  bullet_explain_noperms <- readRDS("../data/hamby_explain.rds")
-
-} else {
-
-  # Apply lime with various input options to the hamby data
-  bullet_lime_explain_noperms <- apply_lime(
-    train = bullet_train %>% select(all_of(bullet_features)),
-    test = bullet_test %>%
-      select(all_of(bullet_features)) %>%
-      na.omit(),
-    model = bulletxtrctr::rtrees,
-    label = as.character(TRUE),
-    n_features = 3,
-    sim_method = c('quantile_bins', 'equal_bins',
-                   'kernel_density', 'normal_approx'),
-    nbins = 2:6,
-    feature_select = "auto",
-    dist_fun = "gower",
-    kernel_width = NULL,
-    gower_pow = c(0.5, 1, 10),
-    return_perms = FALSE,
-    all_fs = FALSE,
-    seed = 20190914)
-
-  # Separate the lime and explain parts of the results
-  bullet_lime_noperms <- bullet_lime_explain_noperms$lime
-  bullet_explain_noperms <- bullet_lime_explain_noperms$explain
-
-  # Save the output objects
-  saveRDS(object = bullet_lime_noperms,
-          file = "../data/hamby_lime.rds")
-  saveRDS(object = bullet_explain_noperms,
-          file = "../data/hamby_explain.rds")
-
-}
-
-@
-
-<<bullet-lime-perms>>=
-
-# Specify two cases of interest
-bullet_poi_match <- unique(bullet_explain_noperms$case)[c(325)]
-bullet_poi_nonmatch <- unique(bullet_explain_noperms$case)[c(20)]
-
-# Apply LIME to two cases with the permutations returned
-bullet_lime_explain_perms <- apply_lime(
-  train = bullet_train %>% select(all_of(bullet_features)),
-  test = bullet_test %>%
-    filter(case %in% bullet_poi_match) %>%
-    bind_rows(bullet_test %>%
-    filter(case %in% bullet_poi_nonmatch)) %>%
-    select(all_of(bullet_features)),
-  model = bulletxtrctr::rtrees,
-  label = as.character(TRUE),
-  n_features = 3,
-  sim_method = c('quantile_bins', 'equal_bins', 'kernel_density', 'normal_approx'),
-  nbins = 3,
-  feature_select = "auto",
-  dist_fun = "gower",
-  kernel_width = NULL,
-  gower_pow = 0.5,
-  return_perms = TRUE,
-  all_fs = FALSE,
-  seed = 20190914)
-
-# Separate the lime and explain parts of the results
-bullet_lime_perms <- bullet_lime_explain_perms$lime
-bullet_explain_perms <- bullet_lime_explain_perms$explain %>%
-  mutate(case = ifelse(case == 1,
-                       bullet_poi_match,
-                       bullet_poi_nonmatch))
-
-@
-
-<<bullet-lime-combined>>=
-
-# Determine the implementation and case number of the poi
-# in the no_perms data
-poi_cases_no_perms <- bullet_explain_noperms %>%
-  filter(case %in% c(bullet_poi_match, bullet_poi_nonmatch),
-         nbins %in% c(3, NA),
-         gower_pow == 0.5) %>%
-  select(case, implementation) %>%
-  unique()
-
-# Join the no perms data (with poi removed) with the
-# perms data (perms removed)
-bullet_explain <- bullet_explain_noperms %>%
-  anti_join(poi_cases_no_perms,
-            by = c("implementation", "case")) %>%
-  bind_rows(bullet_explain_perms %>%
-              select(-perms_raw, -perms_numerified,
-                     -perms_pred_simple, -perms_pred_complex,
-                     -weights))
-
-@
-
 \begin{figure*}[!th]
-<<bullet-feature-heatmap, out.width = '\\textwidth', fig.width = 18, fig.height = 10.5>>=
-
-# Create a feature heatmap
-feature_heatmap(bullet_explain %>%
-                  mutate(label = as.factor(label)),
-                facet_var = na.omit(bullet_test$samesource),
-                order_method = "PCA") +
-  scale_fill_gretchenalbrecht(palette = "last_rays",
-                              discrete = TRUE) +
-  theme_bw(base_family = "Times", base_size = 10) +
-  theme(axis.text.y = element_blank(),
-        axis.ticks.y = element_blank()) +
-  labs(y = "Case")
-
-@
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\textwidth]{figure/bullet-feature-heatmap-1}
+
+\end{knitrout}
 \caption{Feature heatmap of the 36 LIME implementations applied to the bullet comparison data test set.
@@
 \begin{figure*}[!t]
-<<bullet-lime-expls, out.width = '\\textwidth', warning = FALSE, fig.width = 12, fig.height = 5.5>>=
-
-bullet_poi_nonmatch_exps <- bullet_explain %>%
-  filter(sim_method == "quantile_bins",
-         gower_pow == 1,
-         case == bullet_poi_nonmatch) %>%
-  mutate(case = paste0(case, ", ", nbins, " Quantile Bins"))
-
-nb2 <- plot_features(bullet_poi_nonmatch_exps %>% filter(nbins == 2)) +
-  scale_fill_manual(values = c("darkorange", "grey50"))
-nb3 <- plot_features(bullet_poi_nonmatch_exps %>% filter(nbins == 3)) +
-  scale_fill_manual(values = c("darkorange", "grey50"))
-nb4 <- plot_features(bullet_poi_nonmatch_exps%>% filter(nbins == 4)) +
-  scale_fill_manual(values = c("darkorange", "grey50"))
-nb5 <- plot_features(bullet_poi_nonmatch_exps %>% filter(nbins == 5)) +
-  scale_fill_manual(values = c("darkorange", "grey50"))
-nb6 <- plot_features(bullet_poi_nonmatch_exps %>% filter(nbins == 6)) +
-  scale_fill_manual(values = c("darkorange", "grey50"))
-
-feat_ord <- bullet_poi_nonmatch_exps %>%
-  count(feature) %>%
-  arrange(n) %>%
-  pull(feature)
-
-bc <- bullet_poi_nonmatch_exps %>%
-  mutate(feature = factor(feature, levels = feat_ord)) %>%
-  mutate(feature = fct_recode(feature,
-         "Rough Correlation" = "rough_cor",
-         "Non-CMS" = "non_cms",
-         "Sum of Peaks" = "sum_peaks",
-         "Matches" = "matches",
-         "CCF" = "ccf",
-         "Mismatches" = "mismatches",
-         "CMS" = "cms")) %>%
-  ggplot(aes(feature)) +
-  geom_bar() +
-  coord_flip() +
-  theme_bw(base_family = "Times") +
-  labs(x = "Feature",
-       y = "Number of Implementations \nwith Feature Selected",
-       title = "Features Selected by LIME \nfor 2 to 6 Quantile Bins")
-
-plot_grid(nb2, nb3, nb4, nb5, nb6, bc, nrow = 2)
-@
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\textwidth]{figure/bullet-lime-expls-1}
+
+\end{knitrout}
 \caption{Plots of the LIME explanations associated with one observation in the bullet comparison test data from the implementations using 2 to 6 quantile bins.
@@
 To better understand how an explanation can vary based on the implementation method, we consider the explanations for one observation across several LIME implementations.
-The observation we consider from the bullet comparison test data is known \Sexpr{ifelse(bullet_test %>% filter(case == unique(bullet_explain$case)[20]) %>% pull(samesource) == FALSE, print("to not be a match"), print("to be a match"))} and has a random forest score of \Sexpr{bullet_test %>% filter(case == unique(bullet_explain$case)[20]) %>% pull(rfscore)}.
+The observation we consider from the bullet comparison test data is known to not be a match and has a random forest score of 0.05.
 \autoref{fig:bullet-lime-expls} shows the explanation plots from \emph{lime} for the LIME implementations using 2 to 6 quantile bins associated with this case from the test data.
@@
 \begin{figure*}[!t]
-<<bullet-metric-plot, out.width = '\\textwidth', warning = FALSE, fig.width = 10, fig.height = 4>>=
-
-# Create a metric comparison plot
-metric_plot(bullet_explain %>% mutate(label = as.factor(label))) +
-  theme_bw(base_family = "Times") +
-  scale_color_gradient(low = "grey10", high = "grey90") +
-  labs(color = "Rank \n(within \na metric)")
-
-@
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\textwidth]{figure/bullet-metric-plot-1}
+
+\end{knitrout}
 \caption{Plot of LIME assessment metrics for the 36 different implementations of LIME applied to the bullet comparison data test set.
@@
 Perhaps we can say that the kernel density method, 3 equal bins, and 3 quantile bins are some of the best performing methods.
-To better understand the explanations provided by these three methods, we take a closer look at explanations from these methods for two observations of interest where one is a known non-match (case \Sexpr{bullet_poi_nonmatch}) and the other is a known match (case \Sexpr{bullet_poi_match}).
+To better understand the explanations provided by these three methods, we take a closer look at explanations from these methods for two observations of interest where one is a known non-match (case 20) and the other is a known match (case 325).
 
@@
 The scatterplots provide a visualization that helps to explain the LIME explanation.
-For example, consider the explanation for case \Sexpr{bullet_poi_nonmatch} when 3 quantile bins were used.
-The explanation plot from \emph{lime} shows that case \Sexpr{bullet_poi_nonmatch} having an observed CCF value greater than 0.320 supports a random forest prediction in favor of a match.
+For example, consider the explanation for case 20 when 3 quantile bins were used.
+The explanation plot from \emph{lime} shows that case 20 having an observed CCF value greater than 0.320 supports a random forest prediction in favor of a match.
 The scatter plots show that many of the simulated values with CCF greater then 0.320 have random forest predictions greater than 0.5.
@@
 
-<<bullet-eoi-plots, message = FALSE>>=
-bullet_explain_perms <- bullet_explain_perms %>%
-  mutate(case = ifelse(case == bullet_poi_nonmatch,
-                       paste(case, "(non-match)"),
-                       paste(case, "(match)")))
-
-eoi1_3qb <- eoi_plot(bullet_explain_perms[1:3,], alpha = 0.9, weights = FALSE) +
-  scale_color_gradient2(low = "grey50",
-                        high = "darkorange",
-                        midpoint = 0.5,
-                        limits = c(0, 1)) +
-  scale_fill_gradient2(low = "grey50",
-                        high = "darkorange",
-                        midpoint = 0.5,
-                        limits = c(0, 1)) +
-  theme_bw(base_family = "Times", base_size = 8) +
-  theme(strip.placement = "outside",
-        strip.background = element_rect(color = "white",
-                                        fill = "white"))
-
-eoi2_3qb <- eoi_plot(bullet_explain_perms[4:6,], alpha = 0.9, weights = FALSE) +
-  scale_color_gradient2(low = "grey50",
-                        high = "darkorange",
-                        midpoint = 0.5,
-                        limits = c(0, 1)) +
-  scale_fill_gradient2(low = "grey50",
-                        high = "darkorange",
-                        midpoint = 0.5,
-                        limits = c(0, 1)) +
-  theme_bw(base_family = "Times", base_size = 8) +
-  theme(strip.placement = "outside",
-        strip.background = element_rect(color = "white",
-                                        fill = "white"))
-
-eoi1_3eb <- eoi_plot(bullet_explain_perms[7:9,], alpha = 0.9, weights = FALSE) +
-  scale_color_gradient2(low = "grey50",
-                        high = "darkorange",
-                        midpoint = 0.5,
-                        limits = c(0, 1)) +
-  scale_fill_gradient2(low = "grey50",
-                        high = "darkorange",
-                        midpoint = 0.5,
-                        limits = c(0, 1)) +
-  theme_bw(base_family = "Times", base_size = 8) +
-  theme(strip.placement = "outside",
-        strip.background = element_rect(color = "white",
-                                        fill = "white"))
-
-eoi2_3eb <- eoi_plot(bullet_explain_perms[10:12,], alpha = 0.9, weights = FALSE) +
-  scale_color_gradient2(low = "grey50",
-                        high = "darkorange",
-                        midpoint = 0.5,
-                        limits = c(0, 1)) +
-  scale_fill_gradient2(low = "grey50",
-                        high = "darkorange",
-                        midpoint = 0.5,
-                        limits = c(0, 1)) +
-  theme_bw(base_family = "Times", base_size = 8) +
-  theme(strip.placement = "outside",
-        strip.background = element_rect(color = "white",
-                                        fill = "white"))
-
-eoi1_kd <- eoi_plot(bullet_explain_perms[13:15,], alpha = 0.9, weights = FALSE) +
-  scale_color_gradient2(low = "grey50",
-                        high = "darkorange",
-                        midpoint = 0.5,
-                        limits = c(0, 1)) +
-  scale_fill_gradient2(low = "grey50",
-                        high = "darkorange",
-                        midpoint = 0.5,
-                        limits = c(0, 1)) +
-  theme_bw(base_family = "Times", base_size = 8) +
-  theme(strip.placement = "outside",
-        strip.background = element_rect(color = "white",
-                                        fill = "white"))
-
-eoi2_kd <- eoi_plot(bullet_explain_perms[16:18,], alpha = 0.9, weights = FALSE) +
-  scale_color_gradient2(low = "grey45",
-                        high = "darkorange",
-                        midpoint = 0.5,
-                        limits = c(0, 1)) +
-  scale_fill_gradient2(low = "grey45",
-                        high = "darkorange",
-                        midpoint = 0.5,
-                        limits = c(0, 1)) +
-  theme_bw(base_family = "Times", base_size = 8) +
-  theme(strip.placement = "outside",
-        strip.background = element_rect(color = "white",
-                                        fill = "white"))
-
-pf1_3qb <- plot_features(bullet_explain_perms[1:3,]) +
-  scale_fill_manual(values = c("darkorange", "grey50"))
-pf2_3qb <- plot_features(bullet_explain_perms[4:6,]) +
-  scale_fill_manual(values = c("darkorange", "grey50"))
-pf1_3eb <- plot_features(bullet_explain_perms[7:9,]) +
-  scale_fill_manual(values = c("darkorange", "grey50"))
-pf2_3eb <- plot_features(bullet_explain_perms[10:12,]) +
-  scale_fill_manual(values = c("darkorange", "grey50"))
-pf1_kd <- plot_features(bullet_explain_perms[13:15,]) +
-  scale_fill_manual(values = c("darkorange", "grey50"))
-pf2_kd <- plot_features(bullet_explain_perms[16:18,]) +
-  scale_fill_manual(values = c("darkorange", "grey50"))
-@
-
 \begin{figure*}[!htbp]
-<<bullet-eois-nonmatch, out.width = '\\textwidth', fig.width = 12, fig.height = 6.25, message = FALSE>>=
-# Join the plots
-plot_grid(pf2_3qb, pf2_3eb, pf2_kd,
-          eoi2_3qb, eoi2_3eb, eoi2_kd,
-          nrow = 2,
-          rel_heights = c(0.45, 0.55))
-@
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\textwidth]{figure/bullet-eois-nonmatch-1}
+
+\end{knitrout}
 \caption{Plots of LIME explanations for one case in the test data that is a known non-match.
@@
 
-<<bullet-eois-match, out.width = '\\textwidth', fig.width = 12, fig.height = 6.25, message = FALSE>>=
-# Join the plots
-plot_grid(pf1_3qb, pf1_3eb, pf1_kd,
-          eoi1_3qb, eoi1_3eb, eoi1_kd,
-          nrow = 2,
-          rel_heights = c(0.45, 0.55))
-@
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\textwidth]{figure/bullet-eois-match-1}
+
+\end{knitrout}
 \caption{Plots with the same structure as \ref{fig:bullet-eois-match} but for an observation from the test data that is a known match.}
@@
 It appears that simulation method is not providing enough values to cover the feature space that hit regions where the random forest provides predictions above 0.5.
-The training data has a much smaller amount of matches (\Sexpr{sum(bullet_train$samesource)}) than non-matches (\Sexpr{sum(bullet_train$samesource == FALSE)}), and this simulation method is clearly affected by this imbalance in the two classification categories.
+The training data has a much smaller amount of matches (1221) than non-matches (81807), and this simulation method is clearly affected by this imbalance in the two classification categories.
 Furthermore, this may be the cause of the minimal amount of variability in the LIME explanations across all of the cases in the test data.
@@
 
-$$g\left(\textbf{Z}'_{2}\right) = \Sexpr{round(sine_b0, 1)}\Sexpr{round(sine_b1, 1)}I\left[x_1\in (\Sexpr{round(x1_lower, 1)}, \Sexpr{round(x1_upper, 1)}] \right]+\Sexpr{round(sine_b2, 1)}I\left[x_2\in (\Sexpr{round(x2_lower, 1)}, \Sexpr{round(x2_upper, 1)})\right].$$
+$$g\left(\textbf{Z}'_{2}\right) = 0.5-0.1I\left[x_1\in (-0.3, 4.8] \right]+0.3I\left[x_2\in (4.8, \ensuremath{\infty{}})\right].$$
 
@@
 \begin{figure*}[!t]
-<<app-plot-step0, out.width = "\\textwidth", fig.width = 8, fig.height = 4.4>>=
-
-# Scatterplots of training data
-x1x2 <- ggplot(sine_data_train, aes(x = x1, y = x2, color = y)) +
-  geom_point(alpha = 0.8) +
-  scale_colour_manual(values = c(sinecolor_blue, sinecolor_red)) +
-  theme_bw(base_family = "Times", base_size = 10) +
-  labs(x = TeX("$x_1$"),
-       y = TeX("$x_2$"),
-       color = TeX("y"),
-       title = "Training Data") +
-  theme(legend.position = "none",
-        plot.title = element_text(size = 10))
-x1x3 <- ggplot(sine_data_train, aes(x = x1, y = x3, color = y)) +
-  geom_point(alpha = 0.8) +
-  scale_colour_manual(values = c(sinecolor_blue, sinecolor_red)) +
-  theme_bw(base_family = "Times", base_size = 10) +
-  labs(x = TeX("$x_1$"),
-       y = TeX("$x_3$"),
-       color = TeX("y"),
-       title = "") +
-  theme(legend.position = "none")
-x2x3 <- ggplot(sine_data_train, aes(x = x2, y = x3, color = y)) +
-  geom_point(alpha = 0.8) +
-  scale_colour_manual(values = c(sinecolor_blue, sinecolor_red)) +
-  theme_bw(base_family = "Times", base_size = 10) +
-  labs(x = TeX("$x_2$"),
-       y = TeX("$x_3$"),
-       color = TeX("y"),
-       title = "") +
-  theme(legend.title = element_text(size = 8))
-train_legend <- get_legend(x2x3)
-x2x3 <- x2x3 + theme(legend.position = "none")
-
-# Plot the testing data rf predictions
-x1x2test <- ggplot() +
-  geom_point(data = sine_poi %>%
-               mutate(shape = "Prediction \nof Interest"),
-             mapping = aes(x = x1,
-                           y = x2,
-                           #fill = rfprob_blue,
-                           shape = shape),
-             size = 5,
-             alpha = 0.8,
-             color = "black") +
-  geom_point(data = sine_data_test,
-             mapping =  aes(x = x1,
-                            y = x2,
-                            color = rfprob_blue,
-                            fill = rfprob_blue),
-             shape = 21,
-             alpha = 0.8) +
-  scale_color_gradient2(low = sinecolor_red,
-                        mid = '#f7f7f7',
-                        high = sinecolor_blue,
-                        midpoint = 0.5) +
-  scale_fill_gradient2(low = sinecolor_red,
-                        mid = '#f7f7f7',
-                        high = sinecolor_blue,
-                        midpoint = 0.5) +
-  scale_shape_manual(values = 23) +
-  theme_bw(base_family = "Times", base_size = 10) +
-  labs(x = TeX("$x_1$"),
-       y = TeX("$x_2$"),
-       color = "Random \nForest \nProbability",
-       fill = "Random \nForest \nProbability",
-       title = "Testing Data",
-       shape = "") +
-  guides(shape = guide_legend(order = 1)) +
-  theme(legend.position = "none",
-        plot.title = element_text(size = 10))
-x1x3test <- ggplot() +
-  geom_point(data = sine_poi %>%
-               mutate(shape = "Prediction \nof Interest"),
-             mapping = aes(x = x1,
-                           y = x3,
-                           #fill = rfprob_blue,
-                           shape = shape),
-             size = 5,
-             alpha = 0.8,
-             color = "black") +
-  geom_point(data = sine_data_test,
-             mapping =  aes(x = x1,
-                            y = x3,
-                            color = rfprob_blue,
-                            fill = rfprob_blue),
-             shape = 21,
-             alpha = 0.8) +
-  scale_color_gradient2(low = sinecolor_red,
-                        mid = '#f7f7f7',
-                        high = sinecolor_blue,
-                        midpoint = 0.5) +
-  scale_fill_gradient2(low = sinecolor_red,
-                        mid = '#f7f7f7',
-                        high = sinecolor_blue,
-                        midpoint = 0.5) +
-  scale_shape_manual(values = 23) +
-  theme_bw(base_family = "Times", base_size = 10) +
-  labs(x = TeX("$x_1$"),
-       y = TeX("$x_3$"),
-       color = "Random \nForest \nProbability",
-       fill = "Random \nForest \nProbability",
-       shape = "",
-       title = "") +
-  guides(shape = guide_legend(order = 1)) +
-  theme(legend.position = "none")
-x2x3test <- ggplot() +
-  geom_point(data = sine_poi %>%
-               mutate(shape = "Prediction \nof Interest"),
-             mapping = aes(x = x2,
-                           y = x3,
-                           #fill = rfprob_blue,
-                           shape = shape),
-             size = 5,
-             alpha = 0.8,
-             color = "black") +
-  geom_point(data = sine_data_test,
-             mapping =  aes(x = x2,
-                            y = x3,
-                            color = rfprob_blue,
-                            fill = rfprob_blue),
-             shape = 21,
-             alpha = 0.8) +
-  scale_color_gradient2(low = sinecolor_red,
-                        mid = '#f7f7f7',
-                        high = sinecolor_blue,
-                        midpoint = 0.5) +
-  scale_fill_gradient2(low = sinecolor_red,
-                        mid = '#f7f7f7',
-                        high = sinecolor_blue,
-                        midpoint = 0.5) +
-  scale_shape_manual(values = 23) +
-  theme_bw(base_family = "Times", base_size = 10) +
-  labs(x = TeX("$x_2$"),
-       y = TeX("$x_3$"),
-       color = "Random \nForest \nProbability",
-       fill = "Random \nForest \nProbability",
-       title = "",
-       shape = "") +
-  guides(shape = guide_legend(order = 1)) +
-  theme(legend.title = element_text(size = 8))
-test_legend <- get_legend(x2x3test)
-x2x3test <- x2x3test + theme(legend.position = "none")
-
-# Join the plots
-plot_grid(x1x2, x1x3, x2x3, train_legend,
-          x1x2test, x1x3test, x2x3test, test_legend,
-          nrow = 2,
-          rel_widths = c(0.29, 0.29, 0.29, 0.13))
-
-@
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\textwidth]{figure/app-plot-step0-1}
+
+\end{knitrout}
 \caption{Scatter plots of all features from the \data \ training (top) and testing (bottom) sets.
@@
 \centering
-<<app-plot-step1a, out.width = '\\textwidth', fig.width = 8, fig.height = 4.4>>=
-
-# Plot of the training and simulated data with bins
-
-sine_lime_default_bin_cuts$x3 <- sine_lime_explain$lime[[3]]$bin_cuts$x3[2:4]
-
-bins_x1x2 <- ggplot() +
-  geom_point(data = sine_data_train,
-             mapping = aes(x = x1, y = x2, color = y),
-             alpha = 0.8) +
-  geom_vline(xintercept = sine_lime_default_bin_cuts$x1) +
-  geom_hline(yintercept = sine_lime_default_bin_cuts$x2) +
-  scale_color_manual(values = c(sinecolor_blue, sinecolor_red)) +
-  scale_fill_manual(values = c(sinecolor_blue, sinecolor_red)) +
-  scale_shape_manual(values = 23) +
-  theme_bw(base_family = "Times", base_size = 10) +
-  labs(x = TeX("$x_1$"),
-       y = TeX("$x_2$"),
-       color = TeX("y"),
-       fill = TeX("y"),
-       shape = "",
-       title = "Training Data with Quantile Bins") +
-  guides(shape = guide_legend(order = 1),
-         fill = FALSE) +
-  theme(legend.position = "none",
-        plot.title = element_text(size = 10))
-
-bins_x1x3 <- ggplot() +
-  geom_point(data = sine_data_train,
-             mapping = aes(x = x1, y = x3, color = y),
-             alpha = 0.8) +
-  geom_vline(xintercept = sine_lime_default_bin_cuts$x1) +
-  geom_hline(yintercept = sine_lime_default_bin_cuts$x3) +
-  scale_color_manual(values = c(sinecolor_blue, sinecolor_red)) +
-  scale_fill_manual(values = c(sinecolor_blue, sinecolor_red)) +
-  scale_shape_manual(values = 23) +
-  theme_bw(base_family = "Times", base_size = 10) +
-  labs(x = TeX("$x_1$"),
-       y = TeX("$x_3$"),
-       color = TeX("y"),
-       fill = TeX("y"),
-       shape = "",
-       title = "") +
-  guides(shape = guide_legend(order = 1),
-         fill = FALSE) +
-  theme(legend.position = "none")
-
-bins_x2x3 <- ggplot() +
-  geom_point(data = sine_data_train,
-             mapping = aes(x = x2, y = x3, color = y),
-             alpha = 0.8) +
-  geom_vline(xintercept = sine_lime_default_bin_cuts$x2) +
-  geom_hline(yintercept = sine_lime_default_bin_cuts$x3) +
-  scale_color_manual(values = c(sinecolor_blue, sinecolor_red)) +
-  scale_fill_manual(values = c(sinecolor_blue, sinecolor_red)) +
-  scale_shape_manual(values = 23) +
-  theme_bw(base_family = "Times", base_size = 10) +
-  labs(x = TeX("$x_2$"),
-       y = TeX("$x_3$"),
-       color = TeX("y"),
-       fill = TeX("y"),
-       shape = "",
-       title = "") +
-  guides(shape = guide_legend(order = 1),
-         fill = FALSE) +
-  theme(legend.title = element_text(size = 8))
-
-bins_leg <- get_legend(bins_x2x3)
-bins_x2x3 <- bins_x2x3 + theme(legend.position = "none")
-
-bins_sim_x1x2 <- ggplot() +
-  geom_point(data = sine_poi_perms,
-             mapping = aes(x = x1,
-                           y = x2,
-                           fill = rfpred,
-                           color = rfpred),
-             alpha = 0.8,
-             shape = 21) +
-  geom_vline(xintercept = sine_lime_default_bin_cuts$x1) +
-  geom_hline(yintercept = sine_lime_default_bin_cuts$x2) +
-  geom_point(data = sine_poi %>% mutate(shape = "Prediction \nof Interest"),
-             mapping = aes(x = x1,
-                           y = x2,
-                           fill = rfprob_blue,
-                           shape = shape),
-             color = "black",
-             size = 5,
-             alpha = 0.8) +
-  scale_fill_gradient2(low = sinecolor_red,
-                        mid = '#f7f7f7',
-                        high = sinecolor_blue,
-                        midpoint = 0.5) +
-  scale_color_gradient2(low = sinecolor_red,
-                        mid = '#f7f7f7',
-                        high = sinecolor_blue,
-                        midpoint = 0.5) +
-  scale_shape_manual(values = 23) +
-  theme_bw(base_family = "Times", base_size = 10) +
-  labs(x = TeX("$x'_1$"),
-       y = TeX("$x'_2$"),
-       fill = "Random \nForest \nProbability",
-       color = "Random \nForest \nProbability",
-       shape = "",
-       title = "Quantile Bin Simulated Data") +
-  guides(shape = guide_legend(order = 1)) +
-  theme(legend.position = "none",
-        plot.title = element_text(size = 10))
-
-bins_sim_x1x3 <- ggplot() +
-  geom_point(data = sine_poi_perms,
-             mapping = aes(x = x1,
-                           y = x3,
-                           fill = rfpred,
-                           color = rfpred),
-             alpha = 0.8,
-             shape = 21) +
-  geom_vline(xintercept = sine_lime_default_bin_cuts$x1) +
-  geom_hline(yintercept = sine_lime_default_bin_cuts$x3) +
-  geom_point(data = sine_poi %>% mutate(shape = "Prediction \nof Interest"),
-             mapping = aes(x = x1,
-                           y = x3,
-                           fill = rfprob_blue,
-                           shape = shape),
-             color = "black",
-             size = 5,
-             alpha = 0.8) +
-  scale_fill_gradient2(low = sinecolor_red,
-                        mid = '#f7f7f7',
-                        high = sinecolor_blue,
-                        midpoint = 0.5) +
-  scale_color_gradient2(low = sinecolor_red,
-                        mid = '#f7f7f7',
-                        high = sinecolor_blue,
-                        midpoint = 0.5) +
-  scale_shape_manual(values = 23) +
-  theme_bw(base_family = "Times", base_size = 10) +
-  labs(x = TeX("$x'_1$"),
-       y = TeX("$x'_3$"),
-       fill = "Random \nForest \nProbability",
-       color = "Random \nForest \nProbability",
-       shape = "",
-       title = "") +
-  guides(shape = guide_legend(order = 1)) +
-  theme(legend.position = "none")
-
-bins_sim_x2x3 <- ggplot() +
-  geom_point(data = sine_poi_perms,
-             mapping = aes(x = x2,
-                           y = x3,
-                           fill = rfpred,
-                           color = rfpred),
-             alpha = 0.8,
-             shape = 21) +
-  geom_vline(xintercept = sine_lime_default_bin_cuts$x2) +
-  geom_hline(yintercept = sine_lime_default_bin_cuts$x3) +
-  geom_point(data = sine_poi %>% mutate(shape = "Prediction \nof Interest"),
-             mapping = aes(x = x2,
-                           y = x3,
-                           fill = rfprob_blue,
-                           shape = shape),
-             color = "black",
-             size = 5,
-             alpha = 0.8) +
-  scale_fill_gradient2(low = sinecolor_red,
-                        mid = '#f7f7f7',
-                        high = sinecolor_blue,
-                        midpoint = 0.5) +
-  scale_color_gradient2(low = sinecolor_red,
-                        mid = '#f7f7f7',
-                        high = sinecolor_blue,
-                        midpoint = 0.5) +
-  scale_shape_manual(values = 23) +
-  theme_bw(base_family = "Times", base_size = 10) +
-  labs(x = TeX("$x'_2$"),
-       y = TeX("$x'_3$"),
-       fill = "Random \nForest \nProbability",
-       color = "Random \nForest \nProbability",
-       shape = "",
-       title = "") +
-  guides(shape = guide_legend(order = 1)) +
-  theme(legend.title = element_text(size = 8))
-
-bins_sim_leg <- get_legend(bins_sim_x2x3)
-bins_sim_x2x3 <- bins_sim_x2x3 + theme(legend.position = "none")
-
-plot_grid(bins_x1x2, bins_x1x3, bins_x2x3, bins_leg,
-          bins_sim_x1x2, bins_sim_x1x3, bins_sim_x2x3, bins_sim_leg,
-          nrow = 2,
-          rel_widths = c(0.29, 0.29, 0.29, 0.13))
-
-@
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\textwidth]{figure/app-plot-step1a-1}
+
+\end{knitrout}
 \caption{Scatter plots of all features from the \data \ training set (top) and the four quantile bin simulated data (bottom). All sets are overlaid with black lines depicting the four quantile bins.}
@@
 \centering
-<<app-plot-step1b, out.width = '\\textwidth', fig.width = 14, fig.height = 4>>=
-
-# Create a dataset with the rectangles that make up the four categories
-rect_x1x2 <-
-  data.frame(rect = factor(1:6),
-             z1 = c(0, 1, 0, 0, 1, 0),
-             z2 = c(1, 1, 1, 0, 0, 0),
-             case = factor(c(01, 11, 01, 00, 10, 00)),
-             x1 = c(-10, x1_lower, x1_upper, -10, x1_lower, x1_upper),
-             x2 = c(x1_lower, x1_upper, 10, x1_lower, x1_upper, 10),
-             y1 = c(x2_lower, x2_lower, x2_lower, -10, -10, -10),
-             y2 = c(10, 10, 10, x2_lower, x2_lower, x2_lower)) %>%
-  mutate(empred = sine_explainer(z1, z2),
-         case_names = ifelse(case == "11", "\nz'1 = 1 \nz'2 = 1\n",
-                      ifelse(case == "10", "\nz'1 = 1 \nz'2 = 0\n",
-                      ifelse(case == "1", "\nz'1 = 0 \nz'2 = 1\n",
-                      "\nz'1 = 0 \nz'2 = 0\n"))))
-
-# Plot of the numerified perturbations
-num_x1x2 <- ggplot() +
-  geom_point(data = sine_poi_perms,
-             mapping = aes(x = x1,
-                           y = x2,
-                           color = rfpred),
-             alpha = 0.5,
-             shape = 20) +
-  geom_rect(data = rect_x1x2,
-            mapping = aes(xmin = x1,
-                          xmax = x2,
-                          ymin = y1,
-                          ymax = y2,
-                          fill = case_names),
-            alpha = 0.7,
-            color = "black") +
-  geom_point(data = sine_poi,
-             mapping = aes(x = x1, y = x2, color = rfprob_blue),
-             size = 5,
-             shape = 18,
-             alpha = 0.8) +
-  geom_point(data = sine_poi %>% mutate(shape = "Prediction \nof Interest"),
-             mapping = aes(x = x1, y = x2, shape = shape),
-             size = 5,
-             alpha = 0.8) +
-  scale_color_gradient2(low = sinecolor_red,
-                        mid = '#f7f7f7',
-                        high = sinecolor_blue,
-                        midpoint = 0.5) +
-  scale_fill_manual(values = c("grey90", "grey25", "grey70", "grey1")) +
-  scale_shape_manual(values = 23) +
-  theme_bw(base_family = "Times", base_size = 12) +
-  labs(x = TeX("$x'_1$"),
-       y = TeX("$x'_2$"),
-       fill = "Numerified \nFeature Value",
-       title = "Interpretability Transformed Simulated Data",
-       shape = "") +
-  guides(shape = FALSE,
-         size = FALSE,
-         color = FALSE)
-
-x3_min <- min(sine_poi_perms$x3)
-x3_upper <- sine_lime_default_bin_cuts$x3[[2]]
-x3_max <- max(sine_poi_perms$x3)
-
-# Create a dataset with the rectangles that make up the four categories
-rect_x1x3 <-
-  data.frame(rect = factor(1:6),
-             z1 = c(0, 1, 0, 0, 1, 0),
-             z2 = c(1, 1, 1, 0, 0, 0),
-             case = factor(c(01, 11, 01, 00, 10, 00)),
-             x1 = c(-10, x1_lower, x1_upper, -10, x1_lower, x1_upper),
-             x2 = c(x1_lower, x1_upper, 10, x1_lower, x1_upper, 10),
-             y1 = c(x3_min, x3_min, x3_min,
-                    x3_upper, x3_upper, x3_upper),
-             y2 = c(x3_upper, x3_upper, x3_upper,
-                    x3_max, x3_max, x3_max)) %>%
-  mutate(empred = sine_explainer(z1, z2),
-         case_names = ifelse(case == "11", "\nz'1 = 1 \nz'3 = 1\n",
-                      ifelse(case == "10", "\nz'1 = 1 \nz'3 = 0\n",
-                      ifelse(case == "1", "\nz'1 = 0 \nz'3 = 1\n",
-                      "\nz'1 = 0 \nz'3 = 0\n"))))
-
-# Plot of the numerified perturbations
-num_x1x3 <- ggplot() +
-  geom_point(data = sine_poi_perms,
-             mapping = aes(x = x1,
-                           y = x3,
-                           color = rfpred),
-             alpha = 0.5,
-             shape = 20) +
-  geom_rect(data = rect_x1x3,
-            mapping = aes(xmin = x1,
-                          xmax = x2,
-                          ymin = y1,
-                          ymax = y2,
-                          fill = case_names),
-            alpha = 0.7,
-            color = "black") +
-  geom_point(data = sine_poi,
-             mapping = aes(x = x1, y = x3, color = rfprob_blue),
-             size = 5,
-             shape = 18,
-             alpha = 0.8) +
-  geom_point(data = sine_poi %>% mutate(shape = "Prediction \nof Interest"),
-             mapping = aes(x = x1, y = x3, shape = shape),
-             size = 5,
-             alpha = 0.8) +
-  scale_color_gradient2(low = sinecolor_red,
-                        mid = '#f7f7f7',
-                        high = sinecolor_blue,
-                        midpoint = 0.5) +
-  scale_fill_manual(values = c("grey90", "grey25", "grey70", "grey1")) +
-  scale_shape_manual(values = 23) +
-  theme_bw(base_family = "Times", base_size = 12) +
-  labs(x = TeX("$x'_1$"),
-       y = TeX("$x'_3$"),
-       fill = "Numerified \nFeature Value",
-       title = "",
-       shape = "") +
-  guides(shape = FALSE,
-         size = FALSE,
-         color = FALSE)
-
-# Create a dataset with the rectangles that make up the four categories
-rect_x2x3 <-
-  data.frame(rect = factor(1:4),
-             z1 = c(0, 1, 0, 1),
-             z2 = c(0, 0, 1, 1),
-             case = factor(c(00, 10, 01, 11)),
-             x1 = c(-10, x2_lower, -10, x2_lower),
-             x2 = c(x2_lower, 10, x2_lower, 10),
-             y1 = c(x3_upper, x3_upper, x3_min, x3_min),
-             y2 = c(x3_max, x3_max, x3_upper, x3_upper)) %>%
-  mutate(empred = sine_explainer(z1, z2),
-         case_names = ifelse(case == "11", "\nz'2 = 1 \nz'3 = 1\n",
-                      ifelse(case == "10", "\nz'2 = 1 \nz'3 = 0\n",
-                      ifelse(case == "1", "\nz'2 = 0 \nz'3 = 1\n",
-                      "\nz'2 = 0 \nz'3 = 0\n"))))
-
-# Plot of the numerified perturbations
-num_x2x3 <- ggplot() +
-  geom_point(data = sine_poi_perms,
-             mapping = aes(x = x2,
-                           y = x3,
-                           color = rfpred),
-             alpha = 0.5,
-             shape = 20) +
-  geom_rect(data = rect_x2x3,
-            mapping = aes(xmin = x1,
-                          xmax = x2,
-                          ymin = y1,
-                          ymax = y2,
-                          fill = case_names),
-            alpha = 0.7,
-            color = "black") +
-  geom_point(data = sine_poi,
-             mapping = aes(x = x2, y = x3, color = rfprob_blue),
-             size = 5,
-             shape = 18,
-             alpha = 0.8) +
-  geom_point(data = sine_poi %>% mutate(shape = "Prediction \nof Interest"),
-             mapping = aes(x = x2, y = x3, shape = shape),
-             size = 5,
-             alpha = 0.8) +
-  scale_color_gradient2(low = sinecolor_red,
-                        mid = '#f7f7f7',
-                        high = sinecolor_blue,
-                        midpoint = 0.5) +
-  scale_fill_manual(values = c("grey90",  "grey25", "grey70", "grey1")) +
-  scale_shape_manual(values = 23) +
-  theme_bw(base_family = "Times", base_size = 12) +
-  labs(x = TeX("$x'_2$"),
-       y = TeX("$x'_3$"),
-       fill = "Numerified \nFeature Value",
-       title = "",
-       shape = "") +
-  guides(size = FALSE,
-         color = FALSE)
-
-num_legend <- get_legend(num_x2x3 + guides(fill = FALSE))
-num_x2x3 <- num_x2x3 + guides(shape = FALSE)
-
-plot_grid(num_x1x2, num_x1x3, num_x2x3, nrow = 1) %>%
-  plot_grid(num_legend, nrow = 2, rel_heights = c(0.85, 0.15))
-
-@
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\textwidth]{figure/app-plot-step1b-1}
+
+\end{knitrout}
 \caption{\kgc{I'm still thinking about how to visualize all three features for the discretization step, but here is my starting point.}}
@@
 \centering
-<<app-plot-step2a, out.width = '\\textwidth', fig.width = 8, fig.height = 2.25>>=
-
-# Hex plots of the mean weights of the simulated values
-weights_x1x2 <- ggplot() +
-  stat_summary_hex(data = sine_poi_perms,
-             mapping = aes(x = x1,
-                           y = x2,
-                           z = weights),
-             fun = mean,
-             bins = 20) +
-  geom_point(data = sine_poi %>%
-               mutate(shape = "Prediction \nof Interest"),
-             mapping = aes(x = x1, y = x2, shape = shape),
-             fill = sinecolor_blue,
-             size = 5,
-             alpha = 0.8) +
-  scale_fill_gradient(low = "grey90", high = "grey10") +
-  scale_shape_manual(values = 23) +
-  theme_bw(base_family = "Times", base_size = 10) +
-  labs(x = TeX("x'_1"),
-       y = TeX("x'_2"),
-       shape = "",
-       title = "Simulated Data Weights",
-       fill = "Weight") +
-  guides(shape = guide_legend(order = 1)) +
-  theme(legend.position = "none",
-        plot.title = element_text(size = 10))
-
-weights_x1x3 <- ggplot() +
-  stat_summary_hex(data = sine_poi_perms,
-             mapping = aes(x = x1,
-                           y = x3,
-                           z = weights),
-             fun = mean,
-             bins = 20) +
-  geom_point(data = sine_poi %>%
-               mutate(shape = "Prediction \nof Interest"),
-             mapping = aes(x = x1, y = x3, shape = shape),
-             fill = sinecolor_blue,
-             size = 5,
-             alpha = 0.8) +
-  scale_fill_gradient(low = "grey90", high = "grey10") +
-  scale_shape_manual(values = 23) +
-  theme_bw(base_family = "Times", base_size = 10) +
-  labs(x = TeX("x'_1"),
-       y = TeX("x'_3"),
-       shape = "",
-       title = "",
-       fill = "Weight") +
-  guides(shape = guide_legend(order = 1)) +
-  theme(legend.position = "none")
-
-weights_x2x3 <- ggplot() +
-  stat_summary_hex(data = sine_poi_perms,
-             mapping = aes(x = x2,
-                           y = x3,
-                           z = weights),
-             fun = mean,
-             bins = 20) +
-  geom_point(data = sine_poi %>%
-               mutate(shape = "Prediction \nof Interest"),
-             mapping = aes(x = x2, y = x3, shape = shape),
-             fill = sinecolor_blue,
-             size = 5,
-             alpha = 0.8) +
-  scale_fill_gradient(low = "grey90", high = "grey10") +
-  scale_shape_manual(values = 23) +
-  theme_bw(base_family = "Times", base_size = 10) +
-  labs(x = TeX("x'_2"),
-       y = TeX("x'_3"),
-       shape = "",
-       title = "",
-       fill = "Weight") +
-  guides(shape = guide_legend(order = 1)) +
-  theme(legend.title = element_text(size = 8))
-
-weights_legend <- get_legend(weights_x2x3)
-weights_x2x3 <- weights_x2x3 + theme(legend.position = "none")
-
-plot_grid(weights_x1x2, weights_x1x3, weights_x2x3, weights_legend,
-          nrow = 1,
-          rel_widths = c(0.29, 0.29, 0.29, 0.13))
-@
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\includegraphics[width=\textwidth]{figure/app-plot-step2a-1}
+
+\end{knitrout}
 \caption{Hex plots of the weights assigned to the observations in the simulated data for each pair of features in the \data.

### 2020-09-04 paper.Rnw
small updates to paper

@@
 
-# Specify the (base) font size for all plots
+# Specify the (base) font size (fs) and font (ff) for all plots
 fs = 7
+ff = "Helvetica"
 @
@@
                   label = slope),
-    family = "Times",
+    family = ff,
     size = f1_fs / 2.85
@@
   ) +
-  theme_linedraw(base_family = "Times", base_size = f1_fs) +
+  theme_linedraw(base_family = ff, base_size = f1_fs) +
   theme(
@@
                   label = slope),
-    family = "Times",
+    family = ff,
     size = f2_fs / 3
@@
   ) +
-  theme_linedraw(base_family = "Times", base_size = f2_fs) +
+  theme_linedraw(base_family = ff, base_size = f2_fs) +
   theme(
@@
   scale_colour_manual(values = c(sinecolor_blue, sinecolor_red)) +
-  theme_bw(base_family = "Times", base_size = f3_fs) +
+  theme_bw(base_family = ff, base_size = f3_fs) +
   theme(aspect.ratio = 1, 
@@
   scale_shape_manual(values = 23) +
-  theme_bw(base_family = "Times", base_size = f3_fs) +
+  theme_bw(base_family = ff, base_size = f3_fs) +
   theme(aspect.ratio = 1,
@@
   plot_features() + 
-  theme(text = element_text(family = "Times", size = f4_fs),
+  theme(text = element_text(family = ff, size = f4_fs),
         strip.text = element_text(size = f4_fs, face = "plain"))
@@
   ) +
-  theme_bw(base_family = "Times", base_size = f4_fs) +
+  theme_bw(base_family = ff, base_size = f4_fs) +
   guides(shape = guide_legend(order = 1),
@@
   ) +
-  theme_bw(base_family = "Times", base_size = f5_fs) +
+  theme_bw(base_family = ff, base_size = f5_fs) +
   scale_fill_grey() +
@@
 
-# Create the conceptual bad heatmap
+# Create the conceptual bad heat map
 heatmap_plot_bad <- ggplot(data = heatmap_data_bad,
@@
   ) +
-  theme_bw(base_family = "Times", base_size = f5_fs) +
+  theme_bw(base_family = ff, base_size = f5_fs) +
   theme(plot.title = element_text(size = f5_fs)) +
@@
   nrow = 1,
-  rel_widths = c(0.45, 0.45, 0.1)
+  rel_widths = c(0.43, 0.43, 0.14)
 )
@@
                      order_method = "PCA") +
-  theme_bw(base_family = "Times", base_size = f6_fs) +
+  theme_bw(base_family = ff, base_size = f6_fs) +
   theme(
@@
 plot_metrics(sine_lime_explain$explain, rank_legend = "discrete") +
-  theme_bw(base_family = "Times", base_size = f7_fs) +
+  theme_bw(base_family = ff, base_size = f7_fs) +
   theme(
@@
 
-<<figure-09, out.width = '3.125in', fig.width = 6, fig.height = 3, warning = FALSE>>=
+<<figure-09, out.width = '3.125in', fig.width = 6, fig.height = 3.5, warning = FALSE>>=
 
@@
   ylim(c(-4,6)) +
-  theme_bw(base_family = "Times", base_size = f9_fs) +
+  theme_bw(base_family = ff, base_size = f9_fs) +
   theme(strip.background = element_blank()) +
@@
                           midpoint = 0.5) +
-    theme_bw(base_family = "Times", base_size = f10_fs) +
+    theme_bw(base_family = ff, base_size = f10_fs) +
     theme(
@@
     plot = bullet_pcp,
-    filename = "./figure-static/figure-10.png",
+    filename = "./figure-static/figure-10-1.png",
     width = 7.5,
@@
 
-  # Load the figure and then save as an eps file
+  # Load the figure and then save as an EPS file
   bullet_pcp <- image_read("./figure-static/figure-10-1.png")
@@
                                reverse = TRUE) +
-  theme_bw(base_family = "Times", base_size = f11_fs) +
+  theme_bw(base_family = ff, base_size = f11_fs) +
   theme(
@@
 
-<<figure-12, out.width = '6.5in', warning = FALSE, fig.width = 10, fig.height = 4>>=
+<<figure-12, out.width = '6.5in', warning = FALSE, fig.width = 10, fig.height = 4.25>>=
 
@@
 ) +
-  theme_bw(base_family = "Times", base_size = f12_fs) +
+  theme_bw(base_family = ff, base_size = f12_fs) +
   theme(
@@
 \begin{figure*}[!thp]
-<<figure-13, out.width = '6.25in', fig.width = 13, fig.height = 17, message = FALSE>>=
+<<figure-13, out.width = '6.25in', fig.width = 13, fig.height = 17.5, message = FALSE>>=
 
@@
   ) +
-  theme_bw(base_family = "Times", base_size = f13_fs) +
+  theme_bw(base_family = ff, base_size = f13_fs) +
   theme(
@@
   scale_fill_manual(values = c("darkorange", "grey50")) +
-  theme(text = element_text(family = "Times", size = f13_fs),
+  theme(text = element_text(family = ff, size = f13_fs),
         strip.text.x = element_text(face = "plain", size = f13_fs))
@@
   scale_fill_manual(values = c("darkorange", "grey50")) + 
-  theme(text = element_text(family = "Times", size = f13_fs),
+  theme(text = element_text(family = ff, size = f13_fs),
         strip.text.x = element_text(face = "plain", size = f13_fs))
@@
 
-%The following supporting information is available as part of the online article:
+The following supporting information is available:
+
+\kge{\begin{itemize}
+\item \textbf{Paper GitHub Repository}: The R markdown document and code used to produce the paper are available in the following GitHub Repository: \href{https://github.com/goodekat/LIME-diagnostics-paper-short-sweet}{https://github.com/goodekat/LIME-diagnostics-paper-short-sweet}.
+\kgc{Need to update this link after I change the name of the repository.}
+\item \textbf{Data}: The data used for the examples in Section \ref{application} are available at \kgc{need to fill in once Heike has the data published.}
+\end{itemize}}
 
@@
 ) +
-  theme_bw(base_family = "Times", base_size = fb1_fs) +
+  theme_bw(base_family = ff, base_size = fb1_fs) +
   theme(
@@
   ) +
-  theme_bw(base_family = "Times", base_size = fb2_fs) +
+  theme_bw(base_family = ff, base_size = fb2_fs) +
   theme(
@@
   geom_jitter(alpha = 0.5, width = 0.02) +
-  theme_bw(base_family = "Times", base_size = fc3_fs) +
+  theme_bw(base_family = ff, base_size = fc3_fs) +
   theme(plot.title = element_text(size = fc3_fs)) +

### 2020-09-07 paper.Rnw
small updates to improve pcp

@@
   mutate(
-    feature = fct_recode(
-      feature,
-      "CCF" = "ccf",
-      "CMS" = "cms",
+    feature = fct_recode(feature,
+      "Cross Correlation Function" = "ccf",
+      "Consecutively Matching Striae" = "cms",
       "Matches" = "matches",
       "Mismatches" = "mismatches",
-      "Non-CMS" = "non_cms",
+      "Non-Consecutively Matching Striae" = "non_cms",
       "Rough Correlation" = "rough_cor",
-      "Distance Std Dev" = "sd_D",
+      "Distance Standard Deviation" = "sd_D",
       "Distance" = "D",
-      "Sum Peaks" = "sum_peaks"
+      "Sum of Peaks" = "sum_peaks"
     )
@@
 Nine features quantifying the similarity of signatures, such as the cross-correlation function, the distance between signatures, and the number of matching striae, are extracted and used to train a random forest (available in the \emph{bulletxtrctr} R package) to determine the probability of a comparison resulting from the same source (matching signatures) or from different sources (non-matching signatures).
-The model was trained on a set of scans of bullets from the James Hamby Consecutively Rifled Ruger Barrel Study \citep{hamby:2009}, which includes \Sexpr{dim(bullet_train)[1]} land-to-land comparisons.
+\kge{See the supporting information for additional information on the data.} The model was trained on a set of scans of bullets from the James Hamby Consecutively Rifled Ruger Barrel Study \citep{hamby:2009}, which includes \Sexpr{dim(bullet_train)[1]} land-to-land comparisons.
 
@@
   theme(strip.background = element_blank()) +
-  ylab("Surface measurement (in microns)") +
+  ylab("Surface Measurement (in microns)") +
   xlab("Relative Location (in millimeters)")
@@
 
-# Create (or load) the parallel coordinate plot
+# Create or load the parallel coordinate plot
 if (!file.exists("./figure-static/figure-10-1.png")) {
@@
     rename(
-      "CCF" = "ccf",
-      "CMS" = "cms",
+      "Cross Correlation Function" = "ccf",
+      "Consecutively Matching Striae" = "cms",
       "Matches" = "matches",
       "Mismatches" = "mismatches",
-      "Non-CMS" = "non_cms",
+      "Non-Consecutively Matching Striae" = "non_cms",
       "Rough Correlation" = "rough_cor",
-      "Distance Std Dev" = "sd_D",
+      "Distance Standard Deviation" = "sd_D",
       "Distance" = "D",
-      "Sum Peaks" = "sum_peaks"
+      "Sum of Peaks" = "sum_peaks"
     ) %>%
@@
 
-}
-
-# Create (or load) the parallel coordinate plot
-if (file.exists("./figure-static/figure-10-1.eps")) {
-
-  # Load and print the plot
-  knitr::include_graphics("./figure-static/figure-10-1.eps")
-
-} else {
-
   # Load the figure and then save as an EPS file
@@
   image_write(bullet_pcp, path = "./figure-static/figure-10-1.eps", format = "eps")
+
+} else {
+
+   # Load and print the plot
+  knitr::include_graphics("./figure-static/figure-10-1.eps")
 
@@
 # Adjust names of the cases
-bullet_explain_perms <- bullet_explain_perms %>%
+bullet_explain_perms_clean <- bullet_explain_perms %>%
   mutate(case = ifelse(case == bullet_poi_nonmatch, "NM", "M"))
 
-# Create the explanation scatterplot: case M, 3 quantile bins
-eoiM_3qb <-
-  plot_explain_scatter(
-    bullet_explain_perms[1:3,],
-    alpha = 0.9,
-    weights = TRUE,
-    line_size = f13_ls
-  ) +
+# Create a theme for the lime explanation visualizations
+bullet_explain_plot_theme <-
+  list(
+    scale_fill_manual(values = c("darkorange", "grey50")),
+    theme(
+      text = element_text(family = ff, size = f13_fs),
+      strip.text.x = element_text(face = "plain", size = f13_fs)
+    )
+  )
+
+# Create the lime explanation visualizations
+pfM_3qb <- plot_features(bullet_explain_perms_clean[1:3,]) + bullet_explain_plot_theme
+pfNM_3qb <- plot_features(bullet_explain_perms_clean[4:6,]) + bullet_explain_plot_theme
+pfM_3eb <- plot_features(bullet_explain_perms_clean[7:9,]) + bullet_explain_plot_theme
+pfNM_3eb <- plot_features(bullet_explain_perms_clean[10:12,]) + bullet_explain_plot_theme
+
+# Create theme for explanation scatterplots
+bullet_eoi_plot_theme <-
+  list(
     scale_color_gradient2(
@@
       limits = c(0, 1)
-  ) +
+    ),
     scale_fill_gradient2(
@@
       limits = c(0, 1)
-  ) +
-  theme_bw(base_family = ff, base_size = f13_fs) +
+    ),
+    theme_bw(base_family = ff, base_size = f13_fs),
     theme(
@@
       strip.background = element_rect(color = "white", fill = "white")
-  ) +
-  guides(linetype = guide_legend(override.aes = list(color = c("darkorange"))),
-         size = guide_legend(nrow = 2, byrow = T))
-
-# Create the explanation scatterplot: case MM, 3 quantile bins
-eoiNM_3qb <-
+    ),
+    guides(size = guide_legend(nrow = 2, byrow = T), 
+           linetype = guide_legend(override.aes = list(color = c("grey50", "darkorange"))))
+  )
+
+# Create the explanation scatterplots
+eoiM_3qb <-
   plot_explain_scatter(
-    bullet_explain_perms[4:6, ],
+    bullet_explain_perms_clean[1:3, ],
     alpha = 0.9,
@@
   ) +
-  scale_color_gradient2(
-    low = "grey50",
-    high = "darkorange",
-    midpoint = 0.5,
-    limits = c(0, 1)
-  ) +
-  scale_fill_gradient2(
-    low = "grey50",
-    high = "darkorange",
-    midpoint = 0.5,
-    limits = c(0, 1)
-  ) +
-  theme_bw(base_family = ff, base_size = f13_fs) +
-  theme(
-    aspect.ratio = 1,
-    plot.title = element_text(size = f13_fs),
-    strip.placement = "outside",
-    strip.background = element_rect(color = "white", fill = "white"),
-    strip.text.x = element_text(size = f13_fs),
-    strip.text.y = element_text(size = f13_fs)
-  ) +
-  guides(linetype = guide_legend(override.aes = list(color = c(
-    "grey50", "darkorange"
-  ))),
-  size = guide_legend(nrow = 2, byrow = T))
-
-# Create the explanation scatterplot: case M, 3 equal bins
-eoiM_3eb <-
+  bullet_eoi_plot_theme +
+  guides(linetype = guide_legend(override.aes = list(color = c("darkorange"))))
+eoiNM_3qb <-
   plot_explain_scatter(
-    bullet_explain_perms[7:9,],
+    bullet_explain_perms_clean[4:6, ],
     alpha = 0.9,
@@
   ) +
-  scale_color_gradient2(
-    low = "grey50",
-    high = "darkorange",
-    midpoint = 0.5,
-    limits = c(0, 1)
-  ) +
-  scale_fill_gradient2(
-    low = "grey50",
-    high = "darkorange",
-    midpoint = 0.5,
-    limits = c(0, 1)
-  ) +
-  theme_bw(base_family = ff, base_size = f13_fs) +
-  theme(
-    aspect.ratio = 1,
-    plot.title = element_text(size = f13_fs),
-    strip.placement = "outside",
-    strip.background = element_rect(color = "white", fill = "white"),
-    strip.text.x = element_text(size = f13_fs),
-    strip.text.y = element_text(size = f13_fs)
-  ) +
-  guides(linetype = guide_legend(override.aes = list(color = c(
-    "grey50", "darkorange"
-  ))),
-  size = guide_legend(nrow = 2, byrow = T))
-
-# Create the explanation scatterplot: case NM, 3 equal bins
-eoiNM_3eb <-
+  bullet_eoi_plot_theme
+eoiM_3eb <-
   plot_explain_scatter(
-    bullet_explain_perms[10:12,],
+    bullet_explain_perms_clean[7:9, ],
     alpha = 0.9,
@@
   ) +
-  scale_color_gradient2(
-    low = "grey50",
-    high = "darkorange",
-    midpoint = 0.5,
-    limits = c(0, 1)
-  ) +
-  scale_fill_gradient2(
-    low = "grey50",
-    high = "darkorange",
-    midpoint = 0.5,
-    limits = c(0, 1)
-  ) +
-  theme_bw(base_family = ff, base_size = f13_fs) +
-  theme(
-    aspect.ratio = 1,
-    plot.title = element_text(size = f13_fs),
-    strip.placement = "outside",
-    strip.background = element_rect(color = "white", fill = "white"),
-    strip.text.x = element_text(size = f13_fs),
-    strip.text.y = element_text(size = f13_fs)
-  ) +
-  guides(linetype = guide_legend(override.aes = list(color = c(
-    "grey50", "darkorange"
-  ))),
-  size = guide_legend(nrow = 2, byrow = T))
-
-# Create the lime explanation visualization: case M, 3 quantile bins
-pfM_3qb <- plot_features(bullet_explain_perms[1:3,]) +
-  scale_fill_manual(values = c("darkorange", "grey50")) +
-  theme(text = element_text(family = ff, size = f13_fs),
-        strip.text.x = element_text(face = "plain", size = f13_fs))
-
-# Create the lime explanation visualization: case NM, 3 quantile bins
-pfNM_3qb <- plot_features(bullet_explain_perms[4:6,]) +
-  scale_fill_manual(values = c("darkorange", "grey50")) + 
-  theme(text = element_text(family = ff, size = f13_fs),
-        strip.text.x = element_text(face = "plain", size = f13_fs))
-
-# Create the lime explanation visualization: case M, 3 equal bins
-pfM_3eb <- plot_features(bullet_explain_perms[7:9,]) +
-  scale_fill_manual(values = c("darkorange", "grey50")) +
-  theme(text = element_text(family = ff, size = f13_fs),
-        strip.text.x = element_text(face = "plain", size = f13_fs))
-
-# Create the lime explanation visualization: case NM, 3 equal bins
-pfNM_3eb <- plot_features(bullet_explain_perms[10:12,]) +
-  scale_fill_manual(values = c("darkorange", "grey50")) +
-  theme(text = element_text(family = ff, size = f13_fs),
-        strip.text.x = element_text(face = "plain", size = f13_fs))
+  bullet_eoi_plot_theme
+eoiNM_3eb <-
+  plot_explain_scatter(
+    bullet_explain_perms_clean[10:12,],
+    alpha = 0.9,
+    weights = TRUE,
+    line_size = f13_ls
+  ) +
+  bullet_eoi_plot_theme
 
@@
 
-The following supporting information is available:
-
-\kge{\begin{itemize}
-\item \textbf{Paper GitHub Repository}: The R markdown document and code used to produce the paper are available in the following GitHub Repository: \href{https://github.com/goodekat/LIME-diagnostics-paper-short-sweet}{https://github.com/goodekat/LIME-diagnostics-paper-short-sweet}.
-\kgc{Need to update this link after I change the name of the repository.}
-\item \textbf{Data}: The data used for the examples in Section \ref{application} are available at \kgc{need to fill in once Heike has the data published.}
-\end{itemize}}
+\kge{The code used to produce the manuscript and the data from examples in Section \ref{application} are available in the following GitHub Repository: \href{https://github.com/goodekat/LIME-diagnostics-paper}{https://github.com/goodekat/LIME-diagnostics-paper}.
+Additional information about the bullet matching data are available at \kgc{XXX}.}
 

### 2020-09-07 paper.tex
small updates to improve pcp

--- 2020-09-04 paper.tex
@@
 Nine features quantifying the similarity of signatures, such as the cross-correlation function, the distance between signatures, and the number of matching striae, are extracted and used to train a random forest (available in the \emph{bulletxtrctr} R package) to determine the probability of a comparison resulting from the same source (matching signatures) or from different sources (non-matching signatures).
-The model was trained on a set of scans of bullets from the James Hamby Consecutively Rifled Ruger Barrel Study \citep{hamby:2009}, which includes 83028 land-to-land comparisons.
+\kge{See the supporting information for additional information on the data.} The model was trained on a set of scans of bullets from the James Hamby Consecutively Rifled Ruger Barrel Study \citep{hamby:2009}, which includes 83028 land-to-land comparisons.
 
@@
 
-%The following supporting information is available as part of the online article:
+\kge{The code used to produce the manuscript and the data from examples in Section \ref{application} are available in the following GitHub Repository: \href{https://github.com/goodekat/LIME-diagnostics-paper}{https://github.com/goodekat/LIME-diagnostics-paper}.
+Additional information about the bullet matching data are available at \kgc{XXX}.}
 

### 2020-09-07 code-extract-paper-code.R
added a file with code for extracting R code from the paper

@@ -1,0 +1,4 @@
+## Code for extracting the R code from the file paper.Rnw to be used for submission
+## Created: September 9, 2020
+
+knitr::purl("paper.Rnw", output = "code-paper.R")

### 2020-09-07 code-paper.R

@@ -1,0 +1,1370 @@
+## ----setup, echo = FALSE, include = FALSE----------------
+
+# Specify global options
+knitr::opts_chunk$set(
+  warning = FALSE,
+  message = FALSE,
+  echo = FALSE,
+  fig.keep = 'high',
+  fig.align = 'center',
+  dev = c("cairo_pdf", "cairo_ps"),
+  dev.args = list(fallback_resolution = 800),
+  dpi = 1200
+)
+
+# Load packages
+library(Cairo)
+library(caret)
+library(cowplot)
+library(dplyr)
+library(forcats)
+library(ggforce)
+library(ggplot2)
+library(ggpcp) #devtools::install_github("yaweige/ggpcp", build_vignettes = TRUE)
+library(glmnet)
+library(gower)
+library(graphics)
+library(gretchenalbrecht) #devtools::install_github("dicook/gretchenalbrecht")
+library(latex2exp)
+library(lime) #devtools::install_github("goodekat/lime")
+library(limeaid) #devtools::install_github("goodekat/limeaid")
+library(magick)
+library(purrr)
+library(randomForest)
+library(stringr)
+library(tidyr)
+
+# Specify the (base) font size (fs) and font (ff) for all plots
+fs = 7
+ff = "Helvetica"
+
+
+## ----concept-data----------------------------------------
+
+# Simulate example data
+set.seed(20190624)
+lime_data <-
+  data.frame(
+    feature1 = sort(runif(250, 0, 1)),
+    feature2 = sample(x = 1:250, size = 250, replace = FALSE)) %>%
+  mutate(
+    feature1_stnd = (feature1 - mean(feature1)) / sd(feature1),
+    feature2_stnd = (feature2 - mean(feature2)) / sd(feature2),
+    prediction = if_else(feature1 >= 0 & feature1 < 0.1,
+                         (0.3 * feature1) + rnorm(n(), 0, 0.01),
+                 if_else(feature1 >= 0.1 & feature1 < 0.3,
+                         rbeta(n(), 1, 0.5),
+                 if_else(feature1 >= 0.3 & feature1 < 0.5,
+                         sin(pi* feature1) + rnorm(n(), 0, 0.5),
+                 if_else(feature1 >= 0.5 & feature1 < 0.8,
+                         -(sin(pi* feature1) + rnorm(n(), 0, 0.1)) + 1,
[…]

### 2020-09-07 paper.Rnw
working on updating to the training dataset Heike is publishing

@@
 
-# Load the hamby data
+# Load the bullet matching training data and make some adjustments:
+#   1. filter out observations know to have tank rash
+#   2. exclude features not used to train the rtrees random forest 
+#   3. add a variable with the random forest probability in support of a match
+#   4. change the name of the same_source variable to match the test data
+#   5. reorder the variables
+bullet_train_temp <- read.csv("data-bullet-train.csv") %>%
+  #filter(land_id1 == "Hamby173-BrUnk-B2-L1")
+  select(-lag,-abs_lag,-signature_length) %>%
+  mutate(
+    case = factor(1:n()),
+    rfscore = predict(rtrees, bullet_train_temp %>% select(rownames(rtrees$importance)), type = "prob")[, 2]
+  ) %>%
+  rename("samesource" = "same_source") %>%
+  select(case, land_id1, land_id2, everything())
+
+# Load the bullet test data
 bullet_train <- read.csv("../data/hamby173and252_train.csv")
-bullet_test <- read.csv("../data/hamby224_test.csv")
+bullet_test <- read.csv("data-bullet-test.csv")
 

### 2020-09-07 paper.tex
working on updating to the training dataset Heike is publishing

@@
 Nine features quantifying the similarity of signatures, such as the cross-correlation function, the distance between signatures, and the number of matching striae, are extracted and used to train a random forest (available in the \emph{bulletxtrctr} R package) to determine the probability of a comparison resulting from the same source (matching signatures) or from different sources (non-matching signatures).
-\kge{See the supporting information for additional information on the data.} The model was trained on a set of scans of bullets from the James Hamby Consecutively Rifled Ruger Barrel Study \citep{hamby:2009}, which includes 83028 land-to-land comparisons.
+\kge{See the supporting information for additional information on the data.} The model was trained on a set of scans of bullets from the James Hamby Consecutively Rifled Ruger Barrel Study \citep{hamby:2009}, which includes 83436 land-to-land comparisons.
 

### 2020-09-07 submission/code.R
removed files that are no longer up to date and started a README file

@@ -1,1454 +1,0 @@
-## ----setup, echo = FALSE, include = FALSE------------------------
-
-# Specify global options
-knitr::opts_chunk$set(
-  warning = FALSE,
-  message = FALSE,
-  echo = FALSE,
-  fig.keep = 'high',
-  fig.align = 'center',
-  dev = c("cairo_pdf", "cairo_ps"),
-  dev.args = list(fallback_resolution = 800),
-  dpi = 1200,
-  fig.path = ""
-)
-
-# Load packages
-library(Cairo)
-library(caret)
-library(cowplot)
-library(dplyr)
-library(forcats)
-library(ggforce)
-library(ggplot2)
-library(ggpcp) #devtools::install_github("yaweige/ggpcp", build_vignettes = TRUE)
-library(glmnet)
-library(gower)
-library(graphics)
-library(gretchenalbrecht) #devtools::install_github("dicook/gretchenalbrecht")
-library(latex2exp)
-library(lime) #devtools::install_github("goodekat/lime")
-library(limeaid) #devtools::install_github("goodekat/limeaid")
-library(magick)
-library(purrr)
-library(randomForest)
-library(stringr)
-library(tidyr)
-
-# Specify the (base) font size for all plots
-fs = 7
-
-
-## ----concept-data------------------------------------------------
-
-# Simulate example data
-set.seed(20190624)
-lime_data <-
-  data.frame(
-    feature1 = sort(runif(250, 0, 1)),
-    feature2 = sample(x = 1:250, size = 250, replace = FALSE)) %>%
-  mutate(
-    feature1_stnd = (feature1 - mean(feature1)) / sd(feature1),
-    feature2_stnd = (feature2 - mean(feature2)) / sd(feature2),
-    prediction = if_else(feature1 >= 0 & feature1 < 0.1,
-                         (0.3 * feature1) + rnorm(n(), 0, 0.01),
-                 if_else(feature1 >= 0.1 & feature1 < 0.3,
-                         rbeta(n(), 1, 0.5),
-                 if_else(feature1 >= 0.3 & feature1 < 0.5,
-                         sin(pi* feature1) + rnorm(n(), 0, 0.5),
-                 if_else(feature1 >= 0.5 & feature1 < 0.8,
-                         -(sin(pi* feature1) + rnorm(n(), 0, 0.1)) + 1,
-                 if_else(feature1 >= 0.8 & feature1 < 0.9,
[…]

### 2020-09-07 code-extract-paper-code.R
created an R script with code for organzing the manuscript files

@@ -1,4 +1,0 @@
-## Code for extracting the R code from the file paper.Rnw to be used for submission
-## Created: September 9, 2020
-
-knitr::purl("paper.Rnw", output = "code-paper.R")

### 2020-09-07 code-file-organization.R

@@ -1,0 +1,19 @@
+## Code for organizing files associated with the paper
+## Last Run: September 7, 2020
+
+# Compressing files for GitHub ------------------------------------------
+
+# Save the static figure that is used in the paper as a zip file
+zip::zip("figure-08-1.png.zip", "figure-08-1.png")
+
+# Save the bullet training and testing datasets a zip files
+zip::zip("data-bullet-train.csv.zip", "data-bullet-train.csv")
+zip::zip("data-bullet-test.csv.zip", "data-bullet-test.csv")
+
+# Save the dataset with two example matching signatures as a zip file
+zip::zip("data-example-signatures.csv.zip", "data-example-signatures.csv")
+
+# Preparing files for submission ----------------------------------------
+
+# Extract the R code from the file paper.Rnw to be used for submission
+knitr::purl("paper.Rnw", output = "code-paper.R")

### 2020-09-07 code-file-organization.R
add tank rash to zip code

@@ -13,6 +13,9 @@ zip::zip("data-bullet-test.csv.zip", "data-bullet-test.csv")
 # Save the dataset with two example matching signatures as a zip file
 zip::zip("data-example-signatures.csv.zip", "data-example-signatures.csv")
 
+# Save the dataset with observations with tank rash as a zip file
+zip::zip("data-no-tank-rash.csv.zip", "data-no-tank-rash.csv")
+
 # Preparing files for submission ----------------------------------------
 
 # Extract the R code from the file paper.Rnw to be used for submission

### 2020-09-07 README.Rmd
working on updating the readme and converted to an Rmd file

---
output: rmarkdown::github_document
always_allow_html: yes
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

# LIME Diagnostics Paper

This repository contains the files associated with the paper "Visual Diagnostics of a Model Explainer -- Tools for the Assessment of LIME Explanations" by Katherine Goode and Heike Hofmann. The rest of this readme contains information about the files in the repository, instructions for knitting the paper, descriptions of the bullet data used in the paper, and information on the font sizes used for the figures in the manuscript.

### Description of Items in Repository

**Folders**

- `figure-static` contains the figures in the paper that are not generated by R.
- `old-version` contains the files associated with an old version of the paper that is much longer the the submitted version.
- `submission` contains all of the files submitted to the ASA data science journal.
  - Note that the paper is specified slightly different in this folder in order to meet the requirements of the ASA data science journal. For example, the figure path in the .Rnw saves the generated figures in the main folder (instead of a figures folder), and the paths in the .Rnw file are different. It also contains additional files such as data (whereas the data used by the .Rnw file in the main folder is stored elsewhere).

**Files**

- `.gitignore` contains objects to be ignored by git.
- `paper.Rnw` and `paper.pdf` are the manuscript.
- `references.bib` contains the bibtex information for the 
- `WileyNJG-AMS.bst` and `WileyNJG-v2.cls` contain the latex formatting specifications for the ASA data science journal.

### Instructions for Knitting Paper

**Note**: When the paper is knit, various files will be generated (such as data-bullet-explain.rds and figure-10-1.png). The first time the paper is knit, it will take approximately an hour to run. Once these files have been generated during the first knit, the paper will take much less time to knit (approximately 1 minute).

Follow these instructions to knit the paper:

1. Pull the repository from GitHub.
2. Unzip all .zip files in the repository (data-bullet-train.csv.zip, data-bullet-test.csv.zip, data-example-signatures.csv.zip, and figure-08-1.png.zip).
3. Install R packages goodekat/lime and goodekat/limeaid R from GitHub using devtools.

```{r eval = FALSE}
devtools::install_github("goodekat/lime")
devtools::install_github("goodekat/limeaid")
```

4. Knit paper (via the paper.Rnw file).

### Figure Font Size Information

The font sizes in the figures are calculated based on how the figures are scaled due to the specification of both fig.width and out.width in the Rnw file to ensure that they are consistent across figures. The text sizes are either set to 7 pt or 5.5 pt as indicated by the table below. Note that the text in the manuscript is 9 pt and a similar approach was used to ensure that line sizes are larger than 0.5 pt.

| Part of Graphic | Font Size |
| --------------- | --------- | 
| Title | 7 pt |
| Subtitle | 7 pt |
| Axis labels | 7 pt |
| Facet labels that act as x-axis or y-axis labels | 7 pt |
| Facet labels that act as titles for lime R package plots | 7 pt |
| Legend titles | 7 pt |
| Interior labels (such as those created using geom_text) | 7 pt |
| Axis tick labels | 5.5 pt |
| Facet labels (general) | 5.5 pt |
| Legend labels | 5.5 pt |

### Steps for Preparing Submission Folder

Follow these steps to make sure all guidelines are met for submission.

1. Knit paper (to make sure everything is up to date).
2. Run the code in the file code-extract-paper-code.R to produce an R script with all of the code from the manuscript (paper.Rnw).
3.

### Additional Information on Bullet Data

### 2020-09-07 paper.Rnw
knit paper after changing file names

--- 2020-09-07 paper.Rnw
@@
 # Apply LIME with various tuning parameters to the sine data
-if (!file.exists("../data/sine_lime_explain.rds")) {
+if (!file.exists("data-sine-lime-explain.rds")) {
 
@@
 
-    saveRDS(sine_lime_explain, "../data/sine_lime_explain.rds")
+    saveRDS(sine_lime_explain, "data-sine-lime-explain.rds")
 
@@
 
-    sine_lime_explain <- readRDS("../data/sine_lime_explain.rds")
+    sine_lime_explain <- readRDS("data-sine-lime-explain.rds")
 
@@
 
-# Load the hamby data
-bullet_train <- read.csv("../data/hamby173and252_train.csv")
-bullet_test <- read.csv("../data/hamby224_test.csv")
-
-# Extract the features and order them based on feature importance
+# Files that will need to be removed once I know how to 
+#bullet_train <- read.csv("../data/hamby173and252_train.csv")
+no_tank_rash = read.csv("data-no-tank-rash.csv")
+
+# Load the bullet matching training data and make some adjustments:
+#   1. filter out observations know to have tank rash
+#   2. exclude features not used to train the rtrees random forest 
+#   3. change the name of the same_source variable to match the test data
+#   4. reorder the variables
+bullet_train <-
+  read.csv("data-bullet-train.csv") %>%
+  slice(no_tank_rash$case) %>%
+  #filter(land_id1 == "Hamby173-BrUnk-B2-L1")
+  select(-lag,-abs_lag,-signature_length) %>%
+  mutate(case = factor(1:n())) %>%
+  rename("samesource" = "same_source") %>%
+  select(case, land_id1, land_id2, everything())
+
+# Load the bullet test data
+bullet_test <- read.csv("data-bullet-test.csv")
+
+# Extract the features
 bullet_features <- rownames(bulletxtrctr::rtrees$importance)
+
+# Add a variable to the training data with the random forest probability
+# in support of a match
+bullet_train$rfscore <- 
+  bulletxtrctr::rtrees %>%
+  predict(bullet_train %>% select(all_of(bullet_features)), type = "prob") %>%
+  data.frame() %>%
+  pull(TRUE.)
+
+# Order the features based on feature importance
 bullet_features_ordered <-
@@
   mutate(feature = factor(feature, levels = bullet_features_ordered$feature))
-
 @
@@
 # Load the signatures data
-signatures <- readRDS("../data/signatures.rds")
+signatures <- read.csv("data-example-signatures.csv")
 
@@
 # Create or load the parallel coordinate plot
-if (!file.exists("./figure-static/figure-10-1.png")) {
+if (!file.exists("figure-10-1.png")) {
 
@@
     plot = bullet_pcp,
-    filename = "./figure-static/figure-10-1.png",
+    filename = "figure-10-1.png",
     width = 7.5,
@@
   # Load the figure and then save as an EPS file
-  bullet_pcp <- image_read("./figure-static/figure-10-1.png")
-  image_write(bullet_pcp, path = "./figure-static/figure-10-1.eps", format = "eps")
+  bullet_pcp <- image_read("figure-10-1.png")
+  image_write(bullet_pcp, path = "figure-10-1.eps", format = "eps")
 
@@
    # Load and print the plot
-  knitr::include_graphics("./figure-static/figure-10-1.eps")
+  knitr::include_graphics("figure-10-1.eps")
 
@@
 # Apply LIME to all but two cases without returning the permutations
-if (file.exists("../data/hamby_lime.rds")){
-
-  # Load the files
-  bullet_explain_noperms <- readRDS("../data/hamby_explain.rds")
-
-} else {
+if (!file.exists("data-bullet-lime.rds") | !file.exists("data-bullet-explain.rds")){
 
@@
   # Save the output objects
-  saveRDS(object = bullet_lime_noperms,
-          file = "../data/hamby_lime.rds")
-  saveRDS(object = bullet_explain_noperms,
-          file = "../data/hamby_explain.rds")
+  saveRDS(object = bullet_lime_noperms, file = "data-bullet-lime.rds")
+  saveRDS(object = bullet_explain_noperms, file = "data-bullet-explain.rds")
+
+} else {
+
+  # Load the files
+  bullet_explain_noperms <- readRDS("data-bullet-explain.rds")
 

### 2020-09-08 README.Rmd
added an image
worked on updating the readme

@@
 
+```{r echo = FALSE}
+knitr::include_graphics("figure-readme.png")
+```
+
 This repository contains the files associated with the paper "Visual Diagnostics of a Model Explainer -- Tools for the Assessment of LIME Explanations" by Katherine Goode and Heike Hofmann.
-The rest of this readme contains information about the files in the repository, instructions for knitting the paper, descriptions of the bullet data used in the paper, and information on the font sizes used for the figures in the manuscript.
+The rest of this readme contains:
+
+- information about the files in the repository,
+- instructions for knitting the paper,
+- descriptions of the bullet data used in the paper, 
+- information on the font sizes used for the figures in the manuscript, 
+- and the steps taken to create the `submission` folder.
 
@@
 
-- `figure-static` contains the figures in the paper that are not generated by R.
 - `old-version` contains the files associated with an old version of the paper that is much longer the the submitted version.
 - `submission` contains all of the files submitted to the ASA data science journal.
-  - Note that the paper is specified slightly different in this folder in order to meet the requirements of the ASA data science journal.
-For example, the figure path in the .Rnw saves the generated figures in the main folder (instead of a figures folder), and the paths in the .Rnw file are different.
-It also contains additional files such as data (whereas the data used by the .Rnw file in the main folder is stored elsewhere).
+Note that the paper is specified slightly different in this folder in order to meet the requirements of the ASA data science journal.
+These are as follows:
+  - The figure path in the .Rnw saves the generated figures in the main folder (instead of a figures folder).
 
@@
 
+- `code-file-organization.R` contains R code for organizing the files to be added to the GitHub repository and generating a file with code for submission.
+- `code-paper.R` contains the R code extracted from `paper.Rnw` using code in `code-file-organization.R`.
+- `data-bullet-test.csv.zip` and `data-bullet-test.csv.zip` contain the data used for the bullet examples in the paper.
+Additional information about these files is included below under the heading "Additional Information on Bullet Data".
+- `data-example-signatures.csv.zip` contains signature data from two matching bullet lands that is used to generate a figure in the manuscript.
+- **`data-no-tank-rash.csv.zip` is a temporary fix file and needs to be deleted eventually!!!!**
+- `figure-08-1.png.zip` is the one figure in the manuscript that is not generated using R code.
 - `.gitignore` contains objects to be ignored by git.
-- `paper.Rnw` and `paper.pdf` are the manuscript.
+- `paper.Rnw`, `paper.pdf`, and `paper.tex` are the manuscript. Note that `paper.pdf` and `paper.tex` are generated by `paper.Rnw`.
+- `README.Rmd` and `README.md` are the readme files that generated this output. :)
 - `references.bib` contains the bibtex information for the 
@@
 
-**Note**: When the paper is knit, various files will be generated (such as data-bullet-explain.rds and figure-10-1.png).
-The first time the paper is knit, it will take approximately an hour to run.
-Once these files have been generated during the first knit, the paper will take much less time to knit (approximately 1 minute).
+When the paper is knit, various files will be generated (such as `data-bullet-explain.rds` and `figure-10-1.png`).
+The first time the paper is knit, it will take a while (approximately 45 minutes on Katherine's computer).
+Once these files have been generated during the first knit, the paper will take much less time to knit (approximately 1 minute on Katherine's computer).
 
@@
 1. Pull the repository from GitHub.
-2. Unzip all .zip files in the repository (data-bullet-train.csv.zip, data-bullet-test.csv.zip, data-example-signatures.csv.zip, and figure-08-1.png.zip).
+2. Unzip all .zip files in the repository (`data-bullet-train.csv.zip`, `data-bullet-test.csv.zip`, `data-example-signatures.csv.zip`, **`data-no-tank-rash.csv.zip`**, and `figure-08-1.png.zip`).
 3. Install R packages goodekat/lime and goodekat/limeaid R from GitHub using devtools.
@@
 4. Knit paper (via the paper.Rnw file).
+
+### Additional Information on Bullet Data
 
@@
 
-### Steps for Preparing Submission Folder
+### Steps Followed to Create the Submission Folder
 
@@
 3.
-
-### Additional Information on Bullet Data

### 2020-09-08 code-file-organization.R
got rid of anything relating to the tank rash identification data that is no longer needed

@@ -13,9 +13,6 @@ zip::zip("data-bullet-test.csv.zip", "data-bullet-test.csv")
 # Save the dataset with two example matching signatures as a zip file
 zip::zip("data-example-signatures.csv.zip", "data-example-signatures.csv")
 
-# Save the dataset with observations with tank rash as a zip file
-zip::zip("data-no-tank-rash.csv.zip", "data-no-tank-rash.csv")
-
 # Preparing files for submission ----------------------------------------
 
 # Extract the R code from the file paper.Rnw to be used for submission

### 2020-09-08 paper.Rnw
reknit paper after small changes
knit paper after filtering out tank rash bullets

@@
 
+# Save the figure to use in the GitHub repo readme
+# ggsave(
+#   filename = "figure-readme.png",
+#   plot = plot_grid(sine_poi_exp, exp_scatter),
+#   width = 12,
+#   height = 5
+# )
+
 @
@@
 
-# Files that will need to be removed once I know how to 
-#bullet_train <- read.csv("../data/hamby173and252_train.csv")
-no_tank_rash = read.csv("data-no-tank-rash.csv")
-
 # Load the bullet matching training data and make some adjustments:
-#   1. filter out observations know to have tank rash
+#   1. filter out observations known to have tank rash
 #   2. exclude features not used to train the rtrees random forest 
-#   3. change the name of the same_source variable to match the test data
-#   4. reorder the variables
+#   3. add a case variable
+#   4. change the name of the same_source variable to match the test data
+#   5. reorder the variables
 bullet_train <-
   read.csv("data-bullet-train.csv") %>%
-  slice(no_tank_rash$case) %>%
-  #filter(land_id1 == "Hamby173-BrUnk-B2-L1")
-  select(-lag,-abs_lag,-signature_length) %>%
+  filter(!(
+    land_id1 %in% c(
+      "Hamby173-Br6-B2-L1",
+      "Hamby173-Br9-B2-L4",
+      "Hamby173-BrUnk-BB-L2",
+      "Hamby173-BrUnk-B!-L4"
+    ) |
+      land_id2 %in% c(
+        "Hamby173-Br6-B2-L1",
+        "Hamby173-Br9-B2-L4",
+        "Hamby173-BrUnk-BB-L2",
+        "Hamby173-BrUnk-B!-L4"
+      )
+  )) %>%
+  select(-lag, -abs_lag, -signature_length) %>%
   mutate(case = factor(1:n())) %>%

### 2020-09-08 README.Rmd
moved location of the figure
adjusted figure in readme again
updated readme

@@
 - `data-example-signatures.csv.zip` contains signature data from two matching bullet lands that is used to generate a figure in the manuscript.
-- **`data-no-tank-rash.csv.zip` is a temporary fix file and needs to be deleted eventually!!!!**
 - `figure-08-1.png.zip` is the one figure in the manuscript that is not generated using R code.
+- `figure-readme.png` is a figure used in the readme.
 - `.gitignore` contains objects to be ignored by git.
@@
 1. Pull the repository from GitHub.
-2. Unzip all .zip files in the repository (`data-bullet-train.csv.zip`, `data-bullet-test.csv.zip`, `data-example-signatures.csv.zip`, **`data-no-tank-rash.csv.zip`**, and `figure-08-1.png.zip`).
+2. Unzip all .zip files in the repository (`data-bullet-train.csv.zip`, `data-bullet-test.csv.zip`, `data-example-signatures.csv.zip`, and `figure-08-1.png.zip`).
 3. Install R packages goodekat/lime and goodekat/limeaid R from GitHub using devtools.
@@
 ### Additional Information on Bullet Data
+
+**Need to write still**
 
@@
 2. Run the code in the file code-extract-paper-code.R to produce an R script with all of the code from the manuscript (paper.Rnw).
-3.
+3. **Need to finish...**

### 2020-09-08 README.Rmd
format change

@@
 - descriptions of the bullet data used in the paper, 
-- information on the font sizes used for the figures in the manuscript, 
-- and the steps taken to create the `submission` folder.
+- information on the font sizes used for the figures in the manuscript, and
+- the steps taken to create the `submission` folder.
 
-### Description of Items in Repository
+## Description of Items in Repository
 
@@
 
-### Instructions for Knitting Paper
+## Instructions for Knitting Paper
 
@@
 
-### Additional Information on Bullet Data
+## Additional Information on Bullet Data
 
@@
 
-### Figure Font Size Information
+## Figure Font Size Information
 
@@
 
-### Steps Followed to Create the Submission Folder
+## Steps Followed to Create the Submission Folder
 

### 2020-09-08 paper.Rnw
knit paper after adjusting parallel coordinate plot

@@
 library(ggplot2)
-library(ggpcp) #devtools::install_github("yaweige/ggpcp", build_vignettes = TRUE)
+library(ggpcp) #devtools::install_github("goodekat/ggpcp")
 library(glmnet)
@@
     feature = fct_recode(feature,
-      "Cross Correlation Function" = "ccf",
-      "Consecutively Matching Striae" = "cms",
+      "Cross Correlation\nFunction" = "ccf",
+      "Consecutively\nMatching Striae" = "cms",
       "Matches" = "matches",
       "Mismatches" = "mismatches",
-      "Non-Consecutively Matching Striae" = "non_cms",
-      "Rough Correlation" = "rough_cor",
-      "Distance Standard Deviation" = "sd_D",
+      "Non-Consecutively\nMatching Striae" = "non_cms",
+      "Rough\nCorrelation" = "rough_cor",
+      "Distance Standard\nDeviation" = "sd_D",
       "Distance" = "D",
@@
   # Create the plot
-  bullet_pcp <- bullet_train %>%
+  bullet_pcp <- 
+    bullet_train %>%
     select(all_of(bullet_features), samesource, rfscore) %>%
@@
     rename(
-      "Cross Correlation Function" = "ccf",
-      "Consecutively Matching Striae" = "cms",
+      "Cross Correlation\nFunction" = "ccf",
+      "Consecutively\nMatching Striae" = "cms",
       "Matches" = "matches",
       "Mismatches" = "mismatches",
-      "Non-Consecutively Matching Striae" = "non_cms",
-      "Rough Correlation" = "rough_cor",
-      "Distance Standard Deviation" = "sd_D",
+      "Non-Consecutively\nMatching Striae" = "non_cms",
+      "Rough\nCorrelation" = "rough_cor",
+      "Distance Standard\nDeviation" = "sd_D",
       "Distance" = "D",
@@
     theme(
-      axis.text.x = element_text(angle = 45, hjust = 1),
+      axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
       strip.placement = "outside",

### 2020-09-08 paper.Rnw
fixed a typo

@@
       "Hamby173-BrUnk-BB-L2",
-      "Hamby173-BrUnk-B!-L4"
+      "Hamby173-BrUnk-BQ-L4"
     ) |
@@
         "Hamby173-BrUnk-BB-L2",
-        "Hamby173-BrUnk-B!-L4"
+        "Hamby173-BrUnk-BQ-L4"
       )

### 2020-09-08 README.Rmd
small change
added forked ggpcp installation instructions

@@
 2. Unzip all .zip files in the repository (`data-bullet-train.csv.zip`, `data-bullet-test.csv.zip`, `data-example-signatures.csv.zip`, and `figure-08-1.png.zip`).
-3. Install R packages goodekat/lime and goodekat/limeaid R from GitHub using devtools.
+3.
+Install R packages goodekat/lime, goodekat/limeaid, and goodekat/ggpcp from GitHub using devtools.
+(Note that goodekat/lime and goodekat/ggpcp are forked versions of thomasp85/lime and yaweige/ggpcp, respectively with minor changes to meet the needs of the manuscript.)
 
@@
 devtools::install_github("goodekat/limeaid")
+devtools::install_github("goodekat/ggpcp")
 ```
@@
 
-**Need to write still**
+**Need to write...**
 

### 2020-09-08 README.Rmd
added to list back (so I don't forget anything)

@@
 - the steps taken to create the `submission` folder.
+
+## To Do
+
+- Figure out discrepancies with old and new versions of the training data
+- Rerun the lime explanations with the finalized training data
+- Write up dataset descriptions in README and convert to a txt document for the submission
+- Write up steps for creating the submission folder
+- Update all files in the submission folder
+- Consider getting rid of CyBox folder
+- Delete old repo with long version
+- Upload the files for submission, finish filling in questions, and submit!
 

### 2020-09-08 README.Rmd
updates now that Yawei updated ggpcp to allow for spaces

@@
 3.
-Install R packages goodekat/lime, goodekat/limeaid, and goodekat/ggpcp from GitHub using devtools.
-(Note that goodekat/lime and goodekat/ggpcp are forked versions of thomasp85/lime and yaweige/ggpcp, respectively with minor changes to meet the needs of the manuscript.)
+Install R packages goodekat/lime and goodekat/limeaid from GitHub using devtools.
+(Note that goodekat/lime is a forked versions of thomasp85/lime with minor changes to extract objects for the analysis in the manuscript.)
 
@@
 devtools::install_github("goodekat/limeaid")
-devtools::install_github("goodekat/ggpcp")
 ```

### 2020-09-08 paper.Rnw
one more update to pcp after yawei updated ggpcp

@@
 library(ggplot2)
-library(ggpcp) #devtools::install_github("goodekat/ggpcp")
+library(ggpcp) #devtools::install_github("yaweige/ggpcp")
 library(glmnet)

### 2020-09-08 README.Rmd
updated readme

@@
 ```
+
+## To Do
+
+- Figure out discrepancies with old and new versions of the training data
+- Rerun the lime explanations with the finalized training data
+- Edit dataset descriptions in README and add to the readme.txt document for submission
+- Update all files in the submission folder
+- Finish filling in questions in ASA submission document
+- Upload the files for submission and submit
 
@@
 
-## To Do
-
-- Figure out discrepancies with old and new versions of the training data
-- Rerun the lime explanations with the finalized training data
-- Write up dataset descriptions in README and convert to a txt document for the submission
-- Write up steps for creating the submission folder
-- Update all files in the submission folder
-- Consider getting rid of CyBox folder
-- Delete old repo with long version
-- Upload the files for submission, finish filling in questions, and submit!
-
 ## Description of Items in Repository
@@
 - `code-paper.R` contains the R code extracted from `paper.Rnw` using code in `code-file-organization.R`.
+- `code-trim-sig-data.R` contains R code for preparing the data in the file `data-example-signatures.csv.zip` based on data provided by Heike (that are not included in this directory).
 - `data-bullet-test.csv.zip` and `data-bullet-test.csv.zip` contain the data used for the bullet examples in the paper.
@@
 
-**Need to write...**
+The data used in the manuscript for the bullet comparison examples is described below.
+
+`data-bullet-train`: Contains comparison features from the Hamby 173 and 252 sets.
+
+`data-bullet-test`: Contains comparison features from the Hamby 224 Clone sets.
+As with all Hamby sets, Hamby set 224, is a collection of 35 bullets, organized as 20 known bullets and 15 questioned bullets.
+The known bullets are fired in pairs of two through one of ten consecutively manufactures P-85 barrels.
+Clone set 224 is arranged as a test set of fifteen tests, one for each questioned bullet.
+Each test set is arranged as a combination of three bullets: two known bullets and a questioned bullet.
+The test asks for a decision on whether the questioned bullet comes from the same source as the two known bullets or from a different source.
+This situation is similar to what a firearms and toolmarks examiner might encounter in case work.
+
+`data-example-signatures`: Contains the signature data from two bullet-lands that are a match. The variables in the data are as follows:
+
+  - land = Indicates where the observation corresponds to 'Signature 1' or 'Signature 2'
+  - x = The x position of the signature
+  - sig = The y position of the signature
 
@@
 
-1. Knit paper (to make sure everything is up to date).
-2. Run the code in the file code-extract-paper-code.R to produce an R script with all of the code from the manuscript (paper.Rnw).
-3. **Need to finish...**
+1. Knit the file `paper.Rnw` (to make sure everything is up to date).
+2. Run the code in the file `code-file-organization.R` for producing an R script with all of the code from the manuscript (paper.Rnw).
+3. Move the following files to the `submission` folder:
+    - `code-paper.R`
+    - `data-bullet-test.csv`
+    - `data-bullet-train.csv`
+    - `data-example-signatures.csv`
+    - `figure/figure-XX-1.eps` (for XX = 01-07, 09, 11-13, B1, B2, and C3)
+    - `figure-08-1.eps`
+    - `figure-10-1.eps`
+    - `paper.tex`
+    - `readme.txt`
+    - `references.bib`
+    - `WileyNJD-AMS.bst`
+    - `WileyNJD-v1.csl`
+4. Change the name of `paper.tex` to `paper-submission.tex`.
+5. Delete `figure/` from the figure file paths in `paper-submission.tex`. For example, change \includegraphics[width=6.5in]{figure/figure-01-1} to \includegraphics[width=6.5in]{figure-01-1}.
+6. Compile the file `paper-submission.tex` (using LaTex, then bibTex, then LaTeX twice more) to make sure it compiles correctly. 
+7. Besides for `paper-submission.pdf`, delete all other files generated when `paper-sumbission.tex` was compiled. This includes other `paper-submission` files and pdf versions of the figures.
+8. Convert the following files in the submission folder to a zip file, call it `code-and-data.zip`, and then delete the unzipped versions of the files:
+    - `code-paper.R`
+    - `data-bullet-test.csv`
+    - `data-bullet-train.csv`
+    - `data-example-signatures.csv`
+    - `readme.txt`
+9. Upload all remaining files to ASA data science journal submission page (except for `paper-submission.Rnw`) which should be:
+    - `code-and-data.zip`
+    - `figure-01-1.eps` through `figure-C3-1.eps`
+    - `paper-sumbission.pdf`
+    - `paper-sumbission.tex`
+    - `references.bib`
+    - `WileyNJD-AMS.bst`
+    - `WileyNJD-v2.cls`

### 2020-09-08 code-paper.R
extracted R code from the updated paper

@@ -1,4 +1,4 @@
-## ----setup, echo = FALSE, include = FALSE----------------
+## ----setup, echo = FALSE, include = FALSE---------------------
 
 # Specify global options
 knitr::opts_chunk$set(
@@ -20,7 +20,7 @@ library(dplyr)
 library(forcats)
 library(ggforce)
 library(ggplot2)
-library(ggpcp) #devtools::install_github("yaweige/ggpcp", build_vignettes = TRUE)
+library(ggpcp) #devtools::install_github("yaweige/ggpcp")
 library(glmnet)
 library(gower)
 library(graphics)
@@ -39,7 +39,7 @@ fs = 7
 ff = "Helvetica"
 
 
-## ----concept-data----------------------------------------
+## ----concept-data---------------------------------------------
 
 # Simulate example data
 set.seed(20190624)
@@ -122,7 +122,7 @@ prediction_of_interest_gathered <- prediction_of_interest %>%
 
 
 
-## ----concept-explainers----------------------------------
+## ----concept-explainers---------------------------------------
 
 # Fit the good interpretable explainer model
 explainer_good <-
@@ -359,7 +359,7 @@ ggplot() +
 
 
 
-## ----sine-data, echo = FALSE, include = FALSE------------
+## ----sine-data, echo = FALSE, include = FALSE-----------------
 
 # Functions for rotating the data
 rot_x <- function(x, y, theta) (x * cos(theta)) - (y * sin(theta))
@@ -497,10 +497,10 @@ plot_grid(sine_plot_obs, sine_plot_pred,
 
 
 
-## ----sine-lime-------------------------------------------
+## ----sine-lime------------------------------------------------
 
 # Apply LIME with various tuning parameters to the sine data
-if (!file.exists("../data/sine_lime_explain.rds")) {
+if (!file.exists("data-sine-lime-explain.rds")) {
 
     # Apply lime with various input options
     sine_lime_explain <- apply_lime(
@@ -519,17 +519,17 @@ if (!file.exists("../data/sine_lime_explain.rds")) {
       all_fs = TRUE,
       seed = 20190914)
 
-    saveRDS(sine_lime_explain, "../data/sine_lime_explain.rds")
+    saveRDS(sine_lime_explain, "data-sine-lime-explain.rds")
+  
+    } else {
 
-  } else {
-
-    sine_lime_explain <- readRDS("../data/sine_lime_explain.rds")
[…]

### 2020-09-08 code-trim-sig-data.R
added a file for trimming the signature data

@@ -1,0 +1,13 @@
+# The code in this script trims the data provided by Heike of two matching bullet signatures
+
+# Import the data
+signatures <- readRDS("../data/signatures.rds")
+
+# Create a land variable based on the source variable and select only variables 
+# necessary for the manuscfript
+signatures_trimmed <- signatures %>% 
+  mutate(land = c("Signature 1", "Signature 2")[as.factor(source)]) %>%
+  select(land, x, sig)
+
+# Export the trimmed data as a csv file into the manuscript directory
+write.csv(signatures_trimmed, "../diagnostics-paper/data-example-signatures.csv", row.names = FALSE)

### 2020-09-08 paper.Rnw
changed the signature data code

@@
 signatures %>%
-  mutate(land = c("Signature 1", "Signature 2")[as.factor(source)]) %>%
-  ggplot(aes(x = x/1000)) + 
-  geom_line(aes(y = sig), colour = "grey30") +
-  facet_grid(land~.) +
+  ggplot(aes(x = x/1000, y = sig)) + 
+  geom_line() +
+  facet_grid(land ~ .) +
   ylim(c(-4,6)) +
@@
 
-# Create or load the parallel coordinate plot
+# Create the parallel coordinate plot (if needed)
 if (!file.exists("figure-10-1.png")) {
@@
 
-} else {
+}
 
@@
 knitr::include_graphics("figure-10-1.eps")
-
-}
 

### 2020-09-08 submission/paper-submission.tex
added tex files
updated the submission folder with the current version of the paper (but will need to be updated again)

--- 2020-09-04 paper.tex
@@
 
-{\centering \includegraphics[width=6.5in]{figure/figure-01-1}
+{\centering \includegraphics[width=6.5in]{figure-01-1}
 
@@
 
-{\centering \includegraphics[width=6.5in]{figure/figure-02-1}
+{\centering \includegraphics[width=6.5in]{figure-02-1}
 
@@
 
-{\centering \includegraphics[width=6.5in]{figure/figure-03-1}
+{\centering \includegraphics[width=6.5in]{figure-03-1}
 
@@
 
-{\centering \includegraphics[width=6.5in]{figure/figure-04-1}
+{\centering \includegraphics[width=6.5in]{figure-04-1}
 
@@
 
-{\centering \includegraphics[width=3.125in]{figure/figure-05-1}
+{\centering \includegraphics[width=3.125in]{figure-05-1}
 
@@
 
-{\centering \includegraphics[width=3.125in]{figure/figure-06-1}
+{\centering \includegraphics[width=3.125in]{figure-06-1}
 
@@
 
-{\centering \includegraphics[width=3.25in]{figure/figure-07-1}
+{\centering \includegraphics[width=3.25in]{figure-07-1}
 
@@
 Nine features quantifying the similarity of signatures, such as the cross-correlation function, the distance between signatures, and the number of matching striae, are extracted and used to train a random forest (available in the \emph{bulletxtrctr} R package) to determine the probability of a comparison resulting from the same source (matching signatures) or from different sources (non-matching signatures).
-The model was trained on a set of scans of bullets from the James Hamby Consecutively Rifled Ruger Barrel Study \citep{hamby:2009}, which includes 83028 land-to-land comparisons.
+\kge{See the supporting information for additional information on the data.} The model was trained on a set of scans of bullets from the James Hamby Consecutively Rifled Ruger Barrel Study \citep{hamby:2009}, which includes 83436 land-to-land comparisons.
 
@@
 
-{\centering \includegraphics[width=2.25in]{./figure-static/figure-08-1}
+{\centering \includegraphics[width=2.25in]{figure-08-1}
 
@@
 
-{\centering \includegraphics[width=3.125in]{figure/figure-09-1}
+{\centering \includegraphics[width=3.125in]{figure-09-1}
 
@@
 
-{\centering \includegraphics[width=6.5in]{./figure-static/figure-10-1}
+{\centering \includegraphics[width=6.5in]{figure-10-1}
 
@@
 
-{\centering \includegraphics[width=6.5in]{figure/figure-11-1}
+{\centering \includegraphics[width=6.5in]{figure-11-1}
 
@@
 
-{\centering \includegraphics[width=6.5in]{figure/figure-12-1}
+{\centering \includegraphics[width=6.5in]{figure-12-1}
 
@@
 
-{\centering \includegraphics[width=6.25in]{figure/figure-13-1}
+{\centering \includegraphics[width=6.25in]{figure-13-1}
 
@@
 
-{\centering \includegraphics[width=6.5in]{figure/figure-B1-1}
+{\centering \includegraphics[width=6.5in]{figure-B1-1}
 
@@
 
-{\centering \includegraphics[width=6.5in]{figure/figure-B2-1}
+{\centering \includegraphics[width=6.5in]{figure-B2-1}
 
@@
 
-{\centering \includegraphics[width=3.125in]{figure/figure-C3-1}
+{\centering \includegraphics[width=3.125in]{figure-C3-1}
 

### 2020-09-08 paper.Rnw
found a small mistake in the code

@@
   )) %>%
-  select(-lag, -abs_lag, -signature_length) %>%
+  select(-lag, -abs_lag, -overlap, -signature_length) %>%
   mutate(case = factor(1:n())) %>%

### 2020-09-08 code-comparing-training-data.R
added some code for comparing the two files

@@ -1,0 +1,32 @@
+
+library(dplyr)
+
+train_new = read.csv("../data/hamby-comparisons.csv") %>%
+  select(-lag, -abs_lag, -overlap, -signature_length) %>%
+  rename("samesource" = "same_source")
+
+train_old = read.csv("../data/hamby173and252_train.csv") %>%
+  mutate(barrel1 = paste0("Br", barrel1),
+         bullet1 = paste0("B", bullet1),
+         land1 = paste0("L", land1),
+         barrel2 = paste0("Br", barrel2),
+         bullet2 = paste0("B", bullet2),
+         land2 = paste0("L", land2)) %>%
+  mutate(land_id1 = paste(study1, barrel1, bullet1, land1, sep = "-"),
+         land_id2 = paste(study2, barrel2, bullet2, land2, sep = "-")) %>%
+  select(land_id1, land_id2, ccf:samesource)
+
+dim(train_new)
+dim(train_new %>% filter(flag == FALSE))
+dim(train_old)
+
+names(train_new[-13]) == names(train_old)
+
+anti_join(train_old %>% select(land_id1, land_id2), train_new %>% 
+  select(land_id1, land_id2)) %>% dim()
+
+left_join(train_old %>% select(land_id1, land_id2), train_new %>% 
+            select(land_id1, land_id2)) %>% dim()
+
+unique(train_old$land_id1)
+unique(train_new$land_id1)

### 2020-09-09 README.Rmd
added an item to the to do list

@@
 - Upload the files for submission and submit
+- Make the repository public
 

### 2020-09-09 README.Rmd
small updates after meeting

@@
 1. Pull the repository from GitHub.
-2. Unzip all .zip files in the repository (`data-bullet-train.csv.zip`, `data-bullet-test.csv.zip`, `data-example-signatures.csv.zip`, and `figure-08-1.png.zip`).
-3.
-Install R packages goodekat/lime and goodekat/limeaid from GitHub using devtools.
+2.
+Install R packages goodekat/lime and goodekat/limeaid from GitHub using the remotes R package.
 (Note that goodekat/lime is a forked versions of thomasp85/lime with minor changes to extract objects for the analysis in the manuscript.)
@@
 ```{r eval = FALSE}
-devtools::install_github("goodekat/lime")
-devtools::install_github("goodekat/limeaid")
+remotes::install_github("goodekat/lime")
+remotes::install_github("goodekat/limeaid")
 ```
 
-4. Knit paper (via the paper.Rnw file).
-
+3. Knit paper (via the paper.Rnw file).
+et
 ## Additional Information on Bullet Data

### 2020-09-09 paper.Rnw
small updates after meeting

--- 2020-09-08 paper.Rnw
@@
 Our examples raise concerns about claims made of LIME that are similar to other criticisms in the literature.}
-\keywords{LIME, black-box models, interpretability, diagnostics}
+\keywords{explainable machine learning, black-box models, interpretability, statistical graphics, data science}
 
@@
 library(ggplot2)
-library(ggpcp) #devtools::install_github("yaweige/ggpcp")
+library(ggpcp) #remotes::install_github("yaweige/ggpcp")
 library(glmnet)
@@
 library(graphics)
-library(gretchenalbrecht) #devtools::install_github("dicook/gretchenalbrecht")
+library(gretchenalbrecht) #remotes::install_github("dicook/gretchenalbrecht")
 library(latex2exp)
-library(lime) #devtools::install_github("goodekat/lime")
-library(limeaid) #devtools::install_github("goodekat/limeaid")
+library(lime) #remotes::install_github("goodekat/lime")
+library(limeaid) #remotes::install_github("goodekat/limeaid")
 library(magick)
@@
 \item \emph{Explainer Model Fitting}: Apply the black-box model to the simulated data to obtain predictions.
-Compute the distance between each of the simulated observations and the prediction of interest.
+Compute the distance between each of the simulated data points and the prediction of interest.
 Perform feature selection.
@@
 bullet_train <-
-  read.csv("data-bullet-train.csv") %>%
+  readr::read_csv("data-bullet-train.csv.zip") %>%
   filter(!(
@@
 # Load the bullet test data
-bullet_test <- read.csv("data-bullet-test.csv")
+bullet_test <- readr::read_csv("data-bullet-test.csv.zip")
 
@@
 Nine features quantifying the similarity of signatures, such as the cross-correlation function, the distance between signatures, and the number of matching striae, are extracted and used to train a random forest (available in the \emph{bulletxtrctr} R package) to determine the probability of a comparison resulting from the same source (matching signatures) or from different sources (non-matching signatures).
-\kge{See the supporting information for additional information on the data.} The model was trained on a set of scans of bullets from the James Hamby Consecutively Rifled Ruger Barrel Study \citep{hamby:2009}, which includes \Sexpr{dim(bullet_train)[1]} land-to-land comparisons.
+See the supporting information for additional information on the data.
+The model was trained on a set of scans of bullets from the James Hamby Consecutively Rifled Ruger Barrel Study \citep{hamby:2009}, which includes over 80,000 land-to-land comparisons.
 
@@
 if (!file.exists("figure-08-1.eps")) {
+  unzip("figure-08-1.png.zip")
   bullets <- image_read("figure-08-1.png")
@@
 # Load the signatures data
-signatures <- read.csv("data-example-signatures.csv")
+signatures <- readr::read_csv("data-example-signatures.csv.zip")
 
@@
 
-\kge{The code used to produce the manuscript and the data from examples in Section \ref{application} are available in the following GitHub Repository: \href{https://github.com/goodekat/LIME-diagnostics-paper}{https://github.com/goodekat/LIME-diagnostics-paper}.
-Additional information about the bullet matching data are available at \kgc{XXX}.}
+The code used to produce the manuscript and the data from examples in Section \ref{application} are available in the following GitHub Repository: \href{https://github.com/goodekat/LIME-diagnostics-paper}{https://github.com/goodekat/LIME-diagnostics-paper}.
+Additional information about the bullet matching data are available at XXX.
 
@@
 
-For $x_e$ and a set of tuning parameter values $t$, let $\textbf{X}_{e,t}'$ be the LIME simulated dataset with $K$ features and $S$ observations such that $x'_{e,t,s}$ is the feature vector for simulated data observation $s$ corresponding to observation/explanation $e$ and tuning parameter values $t$.
-Let $\textbf{Z}'_{e,t}$ be the matrix of simulated data transformed to bin indicator variables (for bin based simulation methods) or standardization (for density based simulation methods)  with $K$ features and $S$ observations such that $z'_{e,t,s}$ is the interpretability transformed feature vector for observation/explanation $e$, tuning parameter values $t$, and simulated data observation $s$.
+For $x_e$ and a set of tuning parameter values $t$, let $\textbf{X}_{e,t}'$ be the LIME simulated dataset with $K$ features and $S$ rows such that $x'_{e,t,s}$ is the feature vector for simulated data point $s$ corresponding to explanation $e$ and tuning parameter values $t$.
+Let $\textbf{Z}'_{e,t}$ be the matrix of simulated data transformed to bin indicator variables (for bin based simulation methods) or standardization (for density based simulation methods) with $K$ features and $S$ observations such that $z'_{e,t,s}$ is the interpretability transformed feature vector for explanation $e$, tuning parameter values $t$, and simulated data point $s$.
 Note that $z_{e,t}$ will represent the  transformed version of $x_e$.
@@
 Allow $g_{e,t}$ to be the explainer model for an explanation $e$ and tuning parameter values $t$.
-Thus, $g_{e,t}\left(z'_{e,s,t}\right)$ is the explainer model prediction for the interpretability transformed simulated data observation $s$.
+Thus, $g_{e,t}\left(z'_{e,s,t}\right)$ is the explainer model prediction for the interpretability transformed simulated data point $s$.
 
@@
 
-\noindent where $\mathcal{L}$ was originally defined in \citet{ribeiro:2016}.\\
+\noindent where $\mathcal{L}$ is the fidelity metric originally defined in \citet{ribeiro:2016}.\\
 \\

### 2020-09-09 paper.tex
knit paper after changing file names
small updates after meeting

@@
 Nine features quantifying the similarity of signatures, such as the cross-correlation function, the distance between signatures, and the number of matching striae, are extracted and used to train a random forest (available in the \emph{bulletxtrctr} R package) to determine the probability of a comparison resulting from the same source (matching signatures) or from different sources (non-matching signatures).
-\kge{See the supporting information for additional information on the data.} The model was trained on a set of scans of bullets from the James Hamby Consecutively Rifled Ruger Barrel Study \citep{hamby:2009}, which includes 83436 land-to-land comparisons.
+See the supporting information for additional information on the data.
+The model was trained on a set of scans of bullets from the James Hamby Consecutively Rifled Ruger Barrel Study \citep{hamby:2009}, which includes over 80,000 land-to-land comparisons.
 

### 2020-09-09 code-comparing-training-data.R
removed data that is no longer necessary

@@ -1,32 +1,0 @@
-
-library(dplyr)
-
-train_new = read.csv("../data/hamby-comparisons.csv") %>%
-  select(-lag, -abs_lag, -overlap, -signature_length) %>%
-  rename("samesource" = "same_source")
-
-train_old = read.csv("../data/hamby173and252_train.csv") %>%
-  mutate(barrel1 = paste0("Br", barrel1),
-         bullet1 = paste0("B", bullet1),
-         land1 = paste0("L", land1),
-         barrel2 = paste0("Br", barrel2),
-         bullet2 = paste0("B", bullet2),
-         land2 = paste0("L", land2)) %>%
-  mutate(land_id1 = paste(study1, barrel1, bullet1, land1, sep = "-"),
-         land_id2 = paste(study2, barrel2, bullet2, land2, sep = "-")) %>%
-  select(land_id1, land_id2, ccf:samesource)
-
-dim(train_new)
-dim(train_new %>% filter(flag == FALSE))
-dim(train_old)
-
-names(train_new[-13]) == names(train_old)
-
-anti_join(train_old %>% select(land_id1, land_id2), train_new %>% 
-  select(land_id1, land_id2)) %>% dim()
-
-left_join(train_old %>% select(land_id1, land_id2), train_new %>% 
-            select(land_id1, land_id2)) %>% dim()
-
-unique(train_old$land_id1)
-unique(train_new$land_id1)

### 2020-09-09 README.Rmd
updated to do

@@
 
+- Look into using renev
+- Remove NAs from test data
 - Figure out discrepancies with old and new versions of the training data
@@
 - Upload the files for submission and submit
-- Make the repository public
 

### 2020-09-09 README.Rmd
reorganized to do list

--- 2020-09-09 README.Rmd
@@
 
+- Remove NAs from test data
+- Finish filling in questions in ASA submission document
 - Figure out discrepancies with old and new versions of the training data
@@
 - Update all files in the submission folder
-- Finish filling in questions in ASA submission document
 - Upload the files for submission and submit
-- Make the repository public
+- Look into using renev
 

### 2020-09-11 paper.Rnw
reorganized again and wrote code for moving the files to the submission folder

@@
 # Apply LIME with various tuning parameters to the sine data
-if (!file.exists("data-sine-lime-explain.rds")) {
+if (!file.exists("data/sine-lime-explain.rds")) {
 
@@
 
-    saveRDS(sine_lime_explain, "data-sine-lime-explain.rds")
+    saveRDS(sine_lime_explain, "data/sine-lime-explain.rds")
 
@@
 
-    sine_lime_explain <- readRDS("data-sine-lime-explain.rds")
+    sine_lime_explain <- readRDS("data/sine-lime-explain.rds")
 
@@
 #   5. reorder the variables
-bullet_train <-
-  readr::read_csv("data-bullet-train.csv.zip") %>%
-  filter(!(
-    land_id1 %in% c(
-      "Hamby173-Br6-B2-L1",
-      "Hamby173-Br9-B2-L4",
-      "Hamby173-BrUnk-BB-L2",
-      "Hamby173-BrUnk-BQ-L4"
-    ) |
-      land_id2 %in% c(
-        "Hamby173-Br6-B2-L1",
-        "Hamby173-Br9-B2-L4",
-        "Hamby173-BrUnk-BB-L2",
-        "Hamby173-BrUnk-BQ-L4"
-      )
-  )) %>%
-  select(-lag, -abs_lag, -overlap, -signature_length) %>%
-  mutate(case = factor(1:n())) %>%
-  rename("samesource" = "same_source") %>%
-  select(case, land_id1, land_id2, everything())
+bullet_train <- readr::read_csv("data/bullet-train.csv.zip") %>%
 
 # Load the bullet test data
-bullet_test <- readr::read_csv("data-bullet-test.csv.zip")
+bullet_test <- readr::read_csv("data/bullet-test.csv.zip")
 
@@
 # Convert the bullet figure to eps (if needed)
-if (!file.exists("figure-08-1.eps")) {
-  unzip("figure-08-1.png.zip")
-  bullets <- image_read("figure-08-1.png")
-  image_write(bullets, path = "figure-08-1.eps", format = "eps")
+if (!file.exists("figure-static/figure-08-1.eps")) {
+  unzip("figure-static/figure-08-1.png.zip")
+  bullets <- image_read("figure-static/figure-08-1.png")
+  image_write(bullets, path = "figure-static/figure-08-1.eps", format = "eps")
 }
@@
 # Load and print the plot
-knitr::include_graphics("figure-08-1.eps")
+knitr::include_graphics("figure-static/figure-08-1.eps")
 
@@
 # Load the signatures data
-signatures <- readr::read_csv("data-example-signatures.csv.zip")
+signatures <- readr::read_csv("data/example-signatures.csv.zip")
 
@@
 # Create the parallel coordinate plot (if needed)
-if (!file.exists("figure-10-1.png")) {
+if (!file.exists("figure-static/figure-10-1.png")) {
 
@@
   # Load the figure and then save as an EPS file
-  bullet_pcp <- image_read("figure-10-1.png")
-  image_write(bullet_pcp, path = "figure-10-1.eps", format = "eps")
+  bullet_pcp <- image_read("figure-static/figure-10-1.png")
+  image_write(bullet_pcp, path = "figure-static/figure-10-1.eps", format = "eps")
 
@@
 # Load and print the plot
-knitr::include_graphics("figure-10-1.eps")
+knitr::include_graphics("figure-static/figure-10-1.eps")
 
@@
 # Apply LIME to all but two cases without returning the permutations
-if (!file.exists("data-bullet-lime.rds") | !file.exists("data-bullet-explain.rds")){
+if (!file.exists("data/bullet-lime.rds") | !file.exists("data/bullet-explain.rds")){
 
@@
   # Save the output objects
-  saveRDS(object = bullet_lime_noperms, file = "data-bullet-lime.rds")
-  saveRDS(object = bullet_explain_noperms, file = "data-bullet-explain.rds")
+  saveRDS(object = bullet_lime_noperms, file = "data/bullet-lime.rds")
+  saveRDS(object = bullet_explain_noperms, file = "data/bullet-explain.rds")
 
@@
   # Load the files
-  bullet_explain_noperms <- readRDS("data-bullet-explain.rds")
+  bullet_explain_noperms <- readRDS("data/bullet-explain.rds")
 

### 2020-09-11 code-file-organization.R

@@ -1,19 +1,0 @@
-## Code for organizing files associated with the paper
-## Last Run: September 7, 2020
-
-# Compressing files for GitHub ------------------------------------------
-
-# Save the static figure that is used in the paper as a zip file
-zip::zip("figure-08-1.png.zip", "figure-08-1.png")
-
-# Save the bullet training and testing datasets a zip files
-zip::zip("data-bullet-train.csv.zip", "data-bullet-train.csv")
-zip::zip("data-bullet-test.csv.zip", "data-bullet-test.csv")
-
-# Save the dataset with two example matching signatures as a zip file
-zip::zip("data-example-signatures.csv.zip", "data-example-signatures.csv")
-
-# Preparing files for submission ----------------------------------------
-
-# Extract the R code from the file paper.Rnw to be used for submission
-knitr::purl("paper.Rnw", output = "code-paper.R")

### 2020-09-11 code-paper.R

@@ -1,1409 +1,0 @@
-## ----setup, echo = FALSE, include = FALSE---------------------
-
-# Specify global options
-knitr::opts_chunk$set(
-  warning = FALSE,
-  message = FALSE,
-  echo = FALSE,
-  fig.keep = 'high',
-  fig.align = 'center',
-  dev = c("cairo_pdf", "cairo_ps"),
-  dev.args = list(fallback_resolution = 800),
-  dpi = 1200
-)
-
-# Load packages
-library(Cairo)
-library(caret)
-library(cowplot)
-library(dplyr)
-library(forcats)
-library(ggforce)
-library(ggplot2)
-library(ggpcp) #devtools::install_github("yaweige/ggpcp")
-library(glmnet)
-library(gower)
-library(graphics)
-library(gretchenalbrecht) #devtools::install_github("dicook/gretchenalbrecht")
-library(latex2exp)
-library(lime) #devtools::install_github("goodekat/lime")
-library(limeaid) #devtools::install_github("goodekat/limeaid")
-library(magick)
-library(purrr)
-library(randomForest)
-library(stringr)
-library(tidyr)
-
-# Specify the (base) font size (fs) and font (ff) for all plots
-fs = 7
-ff = "Helvetica"
-
-
-## ----concept-data---------------------------------------------
-
-# Simulate example data
-set.seed(20190624)
-lime_data <-
-  data.frame(
-    feature1 = sort(runif(250, 0, 1)),
-    feature2 = sample(x = 1:250, size = 250, replace = FALSE)) %>%
-  mutate(
-    feature1_stnd = (feature1 - mean(feature1)) / sd(feature1),
-    feature2_stnd = (feature2 - mean(feature2)) / sd(feature2),
-    prediction = if_else(feature1 >= 0 & feature1 < 0.1,
-                         (0.3 * feature1) + rnorm(n(), 0, 0.01),
-                 if_else(feature1 >= 0.1 & feature1 < 0.3,
-                         rbeta(n(), 1, 0.5),
-                 if_else(feature1 >= 0.3 & feature1 < 0.5,
-                         sin(pi* feature1) + rnorm(n(), 0, 0.5),
-                 if_else(feature1 >= 0.5 & feature1 < 0.8,
-                         -(sin(pi* feature1) + rnorm(n(), 0, 0.1)) + 1,
-                 if_else(feature1 >= 0.8 & feature1 < 0.9,
[…]

### 2020-09-11 code-trim-sig-data.R

@@ -1,13 +1,0 @@
-# The code in this script trims the data provided by Heike of two matching bullet signatures
-
-# Import the data
-signatures <- readRDS("../data/signatures.rds")
-
-# Create a land variable based on the source variable and select only variables 
-# necessary for the manuscfript
-signatures_trimmed <- signatures %>% 
-  mutate(land = c("Signature 1", "Signature 2")[as.factor(source)]) %>%
-  select(land, x, sig)
-
-# Export the trimmed data as a csv file into the manuscript directory
-write.csv(signatures_trimmed, "../diagnostics-paper/data-example-signatures.csv", row.names = FALSE)

### 2020-09-11 code/data-preparation.R

@@ -1,0 +1,120 @@
+
+library(dplyr)
+
+# The code in this script trims the data provided by Heike of two matching bullet signatures
+
+# Import the data
+signatures <- readRDS("data/signatures.rds")
+
+# Create a land variable based on the source variable and select only variables 
+# necessary for the manuscript
+signatures_trimmed <- signatures %>% 
+  mutate(land = c("Signature 1", "Signature 2")[as.factor(source)]) %>%
+  select(land, x, sig)
+
+# Export the trimmed data as a csv file into the manuscript directory
+write.csv(signatures_trimmed, "../diagnostics-paper/data-example-signatures.csv", row.names = FALSE)
+
+bullet_train <- 
+  read.csv("data/raw/hamby-comparisons.csv") %>%
+  filter(!(
+  land_id1 %in% c(
+    "Hamby173-Br6-B2-L1",
+    "Hamby173-Br9-B2-L4",
+    "Hamby173-BrUnk-BB-L2",
+    "Hamby173-BrUnk-BQ-L4"
+  ) |
+    land_id2 %in% c(
+      "Hamby173-Br6-B2-L1",
+      "Hamby173-Br9-B2-L4",
+      "Hamby173-BrUnk-BB-L2",
+      "Hamby173-BrUnk-BQ-L4"
+    )
+)) %>%
+  select(-lag, -abs_lag, -overlap, -signature_length) %>%
+  mutate(case = factor(1:n())) %>%
+  rename("samesource" = "same_source") %>%
+  select(case, land_id1, land_id2, everything())
+
+write.csv(bullet_train, "data/bullet-train.csv.zip")
+
+
+# Load in the Hamby 224 datasets
+hamby224_set1 <- readRDS("data/raw/h224-set1-features.rds")
+hamby224_set11 <- readRDS("data/raw/h224-set11-features.rds")
+
+
+
+The code below cleans the data from both sets 1 and 11. This involves:
+  
+  - selecting the desired variables
+- renaming the bullet and land variables
+- creating study and set variables
+- re-coding the bullet and land names
+
+```{r}
+# Clean the Hamby 224 set 1 data
+hamby224_set1_cleaned <- hamby224_set1 %>%
+  select(-bullet_score, -land1, -land2, -aligned, -striae, -features) %>%
+  rename(bullet1 = bulletA,
+         bullet2 = bulletB, 
+         land1 = landA,
+         land2 = landB) %>%
[…]

### 2020-09-11 code/file-organization.R

@@ -1,0 +1,73 @@
+## Code for organizing files associated with the paper
+## Last Run: September 11, 2020
+
+# Load packages
+library(zip)
+
+# Compressing files for GitHub ------------------------------------------
+
+# Save the static figure that is used in the paper as a zip file
+zip("figure-static/figure-08-1.png.zip", "figure-static/figure-08-1.png")
+
+# Save the bullet training and testing datasets a zip files
+zip("data/data-bullet-train.csv.zip", "data/data-bullet-train.csv")
+zip("data/data-bullet-test.csv.zip", "data/data-bullet-test.csv")
+
+# Save the dataset with two example matching signatures as a zip file
+zip("data/data-example-signatures.csv.zip", "data/data-example-signatures.csv")
+
+# Preparing files for submission ----------------------------------------
+
+# Create a submission folder file path
+submission_folder <- "submission"
+
+## DATA AND CODE
+
+# Extract the R code from the file paper.Rnw to be used for submission
+knitr::purl("paper.Rnw", output = "code/paper.R")
+
+# Create a temporary directory for storing code and data files for submission
+code_data_folder = "code-and-data"
+dir.create(code_data_folder) 
+
+# Create a vector with code and data files to be included for submission 
+code_data_files <-
+  c(
+    "code/paper.R",
+    "data/bullet-test.csv",
+    "data/bullet-train.csv",
+    "data/example-signatures.csv"
+  )
+
+# Copy the submission files to the temporary folder
+file.copy(code_data_files, "code-and-data")
+
+# Compress the folder with data and code for submission and store it 
+# in the submission folder
+zip(paste0(submission_folder, "/code-and-data.zip"), "code-and-data")
+
+# Remove the temporary folder with code and data for submission
+unlink(code_data_folder, recursive = TRUE)
+
+## FIGURES 
+
+# Identify the folders with files for submission
+folder_eps_figures <- "figure"
+folder_static_figures <- "figure-static"
+
+# Find the EPS figure files for submission
+list_of_generated_figures <- list.files(folder_eps_figures, ".eps$", full.names = T)
+list_of_static_figures <- list.files(folder_static_figures, ".eps$", full.names = T)
+
+# Copy files to the submission folder
+file.copy(list_of_generated_figures, submission_folder)
+file.copy(list_of_static_figures, submission_folder)
+
+## LATEX FILES
+
+# Copy files to the submission folder
[…]

### 2020-09-11 code/paper.R

@@ -1,0 +1,1408 @@
+## ----setup, echo = FALSE, include = FALSE--------------------
+
+# Specify global options
+knitr::opts_chunk$set(
+  warning = FALSE,
+  message = FALSE,
+  echo = FALSE,
+  fig.keep = 'high',
+  fig.align = 'center',
+  dev = c("cairo_pdf", "cairo_ps"),
+  dev.args = list(fallback_resolution = 800),
+  dpi = 1200
+)
+
+# Load packages
+library(Cairo)
+library(caret)
+library(cowplot)
+library(dplyr)
+library(forcats)
+library(ggforce)
+library(ggplot2)
+library(ggpcp) #remotes::install_github("yaweige/ggpcp")
+library(glmnet)
+library(gower)
+library(graphics)
+library(gretchenalbrecht) #remotes::install_github("dicook/gretchenalbrecht")
+library(latex2exp)
+library(lime) #remotes::install_github("goodekat/lime")
+library(limeaid) #remotes::install_github("goodekat/limeaid")
+library(magick)
+library(purrr)
+library(randomForest)
+library(stringr)
+library(tidyr)
+
+# Specify the (base) font size (fs) and font (ff) for all plots
+fs = 7
+ff = "Helvetica"
+
+
+## ----concept-data--------------------------------------------
+
+# Simulate example data
+set.seed(20190624)
+lime_data <-
+  data.frame(
+    feature1 = sort(runif(250, 0, 1)),
+    feature2 = sample(x = 1:250, size = 250, replace = FALSE)) %>%
+  mutate(
+    feature1_stnd = (feature1 - mean(feature1)) / sd(feature1),
+    feature2_stnd = (feature2 - mean(feature2)) / sd(feature2),
+    prediction = if_else(feature1 >= 0 & feature1 < 0.1,
+                         (0.3 * feature1) + rnorm(n(), 0, 0.01),
+                 if_else(feature1 >= 0.1 & feature1 < 0.3,
+                         rbeta(n(), 1, 0.5),
+                 if_else(feature1 >= 0.3 & feature1 < 0.5,
+                         sin(pi* feature1) + rnorm(n(), 0, 0.5),
+                 if_else(feature1 >= 0.5 & feature1 < 0.8,
+                         -(sin(pi* feature1) + rnorm(n(), 0, 0.1)) + 1,
+                 if_else(feature1 >= 0.8 & feature1 < 0.9,
[…]

### 2020-09-11 README.Rmd
fixed a typo
updated to unzip figure

--- 2020-09-09 README.Rmd
@@
 
+- Remove NAs from test data
+- Update readme after file changes (and practice making new submission folder, maybe create a script for copying the files)
+- Finish filling in questions in ASA submission document
+- Write cover letter
 - Figure out discrepancies with old and new versions of the training data
@@
 ```{r echo = FALSE}
-knitr::include_graphics("figure-readme.png")
+unzip("figure-static/figure-readme.png.zip")
+knitr::include_graphics("figure-static/figure-readme.png")
 ```
@@
 
-**Folders**
+The contents of the folders and main directory are described below:
 
-- `old-version` contains the files associated with an old version of the paper that is much longer the the submitted version.
-- `submission` contains all of the files submitted to the ASA data science journal.
-Note that the paper is specified slightly different in this folder in order to meet the requirements of the ASA data science journal.
-These are as follows:
-  - The figure path in the .Rnw saves the generated figures in the main folder (instead of a figures folder).
+**`code`**
+
+Contains the R code associated with the manuscript that is not directly included in `paper.Rnw` (such as some external data cleaning and file organization):
+
+- `data-preparation.R` contains R code for preparing the bullet training data (based on Hamby 173 and 252), bullet testing data (based on Hamby 224 sets 1 and 11), and example matching signatures (based on data provided by Heike).
+- `file-organization.R` contains R code for organizing the files to be added to the GitHub repository and preparing and moving files to the submission folder.
+- `paper.R` contains the R code extracted from `paper.Rnw` using code in `file-organization.R`.
+
+**`data`**
+
+Contains the data used to generate the manuscript:
+
+- `bullet-test.csv.zip` and `bullet-test.csv.zip` contain the data used for the bullet examples in the paper.
+Additional information about these files is included below under the heading "Additional Information on Bullet Data".
+- `example-signatures.csv.zip` contains signature data from two matching bullet lands that is used to generate a figure in the manuscript.
+
+**`figure-static`**
+
+Contains the static figure associated with the project:
+
+- `figure-08-1.png.zip` is the one figure in the manuscript that is not generated using R code.
+- `figure-readme.png` is a figure used in the readme.
+
+**`old-version`**
+
+Contains the files associated with an old version of the paper that is much longer the the submitted version
+
+**`submission`**
+
+Contains the files submitted to the ASA data science journal. These files are moved to this folder using code in the file `code/file-organization.R`.
 
@@
 
-- `code-file-organization.R` contains R code for organizing the files to be added to the GitHub repository and generating a file with code for submission.
-- `code-paper.R` contains the R code extracted from `paper.Rnw` using code in `code-file-organization.R`.
-- `code-trim-sig-data.R` contains R code for preparing the data in the file `data-example-signatures.csv.zip` based on data provided by Heike (that are not included in this directory).
-- `data-bullet-test.csv.zip` and `data-bullet-test.csv.zip` contain the data used for the bullet examples in the paper.
-Additional information about these files is included below under the heading "Additional Information on Bullet Data".
-- `data-example-signatures.csv.zip` contains signature data from two matching bullet lands that is used to generate a figure in the manuscript.
-- `figure-08-1.png.zip` is the one figure in the manuscript that is not generated using R code.
-- `figure-readme.png` is a figure used in the readme.
 - `.gitignore` contains objects to be ignored by git.
@@
 3. Knit paper (via the paper.Rnw file).
-et
+
 ## Additional Information on Bullet Data

### 2020-09-11 README.Rmd
returned to the png
working on updating and moving sumbission to do list to an R script

@@
 ```{r echo = FALSE}
-unzip("figure-static/figure-readme.png.zip")
 knitr::include_graphics("figure-static/figure-readme.png")
@@
 - `data-preparation.R` contains R code for preparing the bullet training data (based on Hamby 173 and 252), bullet testing data (based on Hamby 224 sets 1 and 11), and example matching signatures (based on data provided by Heike).
-- `file-organization.R` contains R code for organizing the files to be added to the GitHub repository and preparing and moving files to the submission folder.
+- `figure-compression.R` contains R code for compressing the static figure used in the manuscript
 - `paper.R` contains the R code extracted from `paper.Rnw` using code in `file-organization.R`.
+- `submission-steps.R` contains the to do list and R code for preparing the files for submission to the ASA Data Science Journal.
 

### 2020-09-11 code/data-preparation.R

@@ -1,6 +1,13 @@
 
 library(dplyr)
 
+# Save the bullet training and testing datasets a zip files
+zip("data/data-bullet-train.csv.zip", "data/data-bullet-train.csv")
+zip("data/data-bullet-test.csv.zip", "data/data-bullet-test.csv")
+
+# Save the dataset with two example matching signatures as a zip file
+zip("data/data-example-signatures.csv.zip", "data/data-example-signatures.csv")
+
 # The code in this script trims the data provided by Heike of two matching bullet signatures
 
 # Import the data
@@ -36,7 +43,7 @@ bullet_train <-
   rename("samesource" = "same_source") %>%
   select(case, land_id1, land_id2, everything())
 
-write.csv(bullet_train, "data/bullet-train.csv.zip")
+write.csv(bullet_train, "data/bullet-train.csv")
 
 
 # Load in the Hamby 224 datasets

### 2020-09-11 code/figure-compression.R

@@ -1,0 +1,8 @@
+## This R script contains code for compressing the static figure in the manuscript
+## Last run: September 11, 2020
+
+# Load packages
+library(zip)
+
+# Save the bullet image used in the paper as a zip file
+zip("figure-static/figure-08-1.png.zip", "figure-static/figure-08-1.png")

### 2020-09-11 code/submission-steps.R

@@ -1,20 +1,8 @@
-## Code for organizing files associated with the paper
+## Steps to follow for ASA Data Science Journal submission
 ## Last Run: September 11, 2020
 
 # Load packages
 library(zip)
-
-# Compressing files for GitHub ------------------------------------------
-
-# Save the static figure that is used in the paper as a zip file
-zip("figure-static/figure-08-1.png.zip", "figure-static/figure-08-1.png")
-
-# Save the bullet training and testing datasets a zip files
-zip("data/data-bullet-train.csv.zip", "data/data-bullet-train.csv")
-zip("data/data-bullet-test.csv.zip", "data/data-bullet-test.csv")
-
-# Save the dataset with two example matching signatures as a zip file
-zip("data/data-example-signatures.csv.zip", "data/data-example-signatures.csv")
 
 # Preparing files for submission ----------------------------------------
 

### 2020-09-11 README.Rmd
decided not to keep paper.R file in main directory (only in submission) so no confusion with code used in paper (only in Rnw)

@@
 - `figure-compression.R` contains R code for compressing the static figure used in the manuscript
-- `paper.R` contains the R code extracted from `paper.Rnw` using code in `file-organization.R`.
 - `submission-steps.R` contains the to do list and R code for preparing the files for submission to the ASA Data Science Journal.

### 2020-09-11 code/paper.R

@@ -1,1408 +1,0 @@
-## ----setup, echo = FALSE, include = FALSE--------------------
-
-# Specify global options
-knitr::opts_chunk$set(
-  warning = FALSE,
-  message = FALSE,
-  echo = FALSE,
-  fig.keep = 'high',
-  fig.align = 'center',
-  dev = c("cairo_pdf", "cairo_ps"),
-  dev.args = list(fallback_resolution = 800),
-  dpi = 1200
-)
-
-# Load packages
-library(Cairo)
-library(caret)
-library(cowplot)
-library(dplyr)
-library(forcats)
-library(ggforce)
-library(ggplot2)
-library(ggpcp) #remotes::install_github("yaweige/ggpcp")
-library(glmnet)
-library(gower)
-library(graphics)
-library(gretchenalbrecht) #remotes::install_github("dicook/gretchenalbrecht")
-library(latex2exp)
-library(lime) #remotes::install_github("goodekat/lime")
-library(limeaid) #remotes::install_github("goodekat/limeaid")
-library(magick)
-library(purrr)
-library(randomForest)
-library(stringr)
-library(tidyr)
-
-# Specify the (base) font size (fs) and font (ff) for all plots
-fs = 7
-ff = "Helvetica"
-
-
-## ----concept-data--------------------------------------------
-
-# Simulate example data
-set.seed(20190624)
-lime_data <-
-  data.frame(
-    feature1 = sort(runif(250, 0, 1)),
-    feature2 = sample(x = 1:250, size = 250, replace = FALSE)) %>%
-  mutate(
-    feature1_stnd = (feature1 - mean(feature1)) / sd(feature1),
-    feature2_stnd = (feature2 - mean(feature2)) / sd(feature2),
-    prediction = if_else(feature1 >= 0 & feature1 < 0.1,
-                         (0.3 * feature1) + rnorm(n(), 0, 0.01),
-                 if_else(feature1 >= 0.1 & feature1 < 0.3,
-                         rbeta(n(), 1, 0.5),
-                 if_else(feature1 >= 0.3 & feature1 < 0.5,
-                         sin(pi* feature1) + rnorm(n(), 0, 0.5),
-                 if_else(feature1 >= 0.5 & feature1 < 0.8,
-                         -(sin(pi* feature1) + rnorm(n(), 0, 0.1)) + 1,
-                 if_else(feature1 >= 0.8 & feature1 < 0.9,
[…]

### 2020-09-11 code/submission-steps.R

@@ -11,17 +11,16 @@ submission_folder <- "submission"
 
 ## DATA AND CODE
 
-# Extract the R code from the file paper.Rnw to be used for submission
-knitr::purl("paper.Rnw", output = "code/paper.R")
-
 # Create a temporary directory for storing code and data files for submission
 code_data_folder = "code-and-data"
 dir.create(code_data_folder) 
 
+# Extract the R code from the file paper.Rnw to be used for submission
+knitr::purl("paper.Rnw", output = paste0(code_data_folder, "/paper.R"))
+
 # Create a vector with code and data files to be included for submission 
-code_data_files <-
+data_files <-
   c(
-    "code/paper.R",
     "data/bullet-test.csv",
     "data/bullet-train.csv",
     "data/example-signatures.csv"

### 2020-09-11 README.Rmd
updated based on changes made to repository

@@
 - Remove NAs from test data
-- Update readme after file changes (and practice making new submission folder, maybe create a script for copying the files)
+- Write cover letter
 - Finish filling in questions in ASA submission document
-- Write cover letter
 - Figure out discrepancies with old and new versions of the training data
@@
 - instructions for knitting the paper,
-- descriptions of the bullet data used in the paper, 
-- information on the font sizes used for the figures in the manuscript, and
-- the steps taken to create the `submission` folder.
+- descriptions of the bullet data used in the paper, and
+- information on the font sizes used for the figures in the paper.
 
@@
 
-Contains the R code associated with the manuscript that is not directly included in `paper.Rnw` (such as some external data cleaning and file organization):
+Contains the R code associated with the paper that is not directly included in `paper.Rnw` (such as some external data cleaning and file organization):
 
-- `data-preparation.R` contains R code for preparing the bullet training data (based on Hamby 173 and 252), bullet testing data (based on Hamby 224 sets 1 and 11), and example matching signatures (based on data provided by Heike).
-- `figure-compression.R` contains R code for compressing the static figure used in the manuscript
+- `data-preparation.R` contains R code for preparing the raw bullet data (bullet training data, bullet testing data, and example matching signatures) to be used in the paper
+- `figure-compression.R` contains R code for compressing the static figure used in the paper
 - `submission-steps.R` contains the to do list and R code for preparing the files for submission to the ASA Data Science Journal.
@@
 
-Contains the data used to generate the manuscript:
+Contains the data used to generate the paper:
 
@@
 Additional information about these files is included below under the heading "Additional Information on Bullet Data".
-- `example-signatures.csv.zip` contains signature data from two matching bullet lands that is used to generate a figure in the manuscript.
+- `example-signatures.csv.zip` contains signature data from two matching bullet lands that is used to generate a figure in the paper.
+- `raw` contains the raw versions of the data files that the above datasets are derived from.
 
@@
 
-Contains the static figure associated with the project:
+Contains the static figures associated with the project:
 
-- `figure-08-1.png.zip` is the one figure in the manuscript that is not generated using R code.
+- `figure-08-1.png.zip` is the one figure in the paper that is not generated using R code.
 - `figure-readme.png` is a figure used in the readme.
@@
 
-Contains the files submitted to the ASA data science journal. These files are moved to this folder using code in the file `code/file-organization.R`.
+Contains the files submitted to the ASA Data Science Journal.
+These files are moved to this folder using code in the file `code/submission-steps.R`.
+The only figures not included on GitHub are the EPS figures that are submitted due to size constraints.
 
-**Files**
+**Main Directory**
 
 - `.gitignore` contains objects to be ignored by git.
-- `paper.Rnw`, `paper.pdf`, and `paper.tex` are the manuscript. Note that `paper.pdf` and `paper.tex` are generated by `paper.Rnw`.
-- `README.Rmd` and `README.md` are the readme files that generated this output. :)
-- `references.bib` contains the bibtex information for the 
-- `WileyNJG-AMS.bst` and `WileyNJG-v2.cls` contain the latex formatting specifications for the ASA data science journal.
+- `paper.Rnw`, `paper.pdf`, and `paper.tex` are the paper. Note that `paper.pdf` and `paper.tex` are generated by `paper.Rnw`.
+- `README.Rmd` and `README.md` are the readme files that generated this output.
+- `readme.txt` contains descriptions of the data files that are included with the submission
+- `references.bib` contains the bibtex information for the references in the paper
+- `WileyNJG-AMS.bst` and `WileyNJG-v2.cls` contain the latex formatting specifications for the ASA Data Science Journal.
 
@@
 2.
-Install R packages goodekat/lime and goodekat/limeaid from GitHub using the remotes R package.
-(Note that goodekat/lime is a forked versions of thomasp85/lime with minor changes to extract objects for the analysis in the manuscript.)
+Install R packages [goodekat/lime](https://github.com/goodekat/lime) and [goodekat/limeaid](https://github.com/goodekat/limeaid) from GitHub using the remotes R package.
+(Note that goodekat/lime is a forked versions of [thomasp85/lime](https://github.com/thomasp85/lime) with minor changes to extract objects for the analysis in the paper.)
 
@@
 
-The data used in the manuscript for the bullet comparison examples is described below.
+The data used in the paper for the bullet comparison examples is described below.
 
@@
 The text sizes are either set to 7 pt or 5.5 pt as indicated by the table below.
-Note that the text in the manuscript is 9 pt and a similar approach was used to ensure that line sizes are larger than 0.5 pt.
+Note that the text in the paper is 9 pt and a similar approach was used to ensure that line sizes are larger than 0.5 pt.
 
@@
 | Legend labels | 5.5 pt |
-
-## Steps Followed to Create the Submission Folder
-
-Follow these steps to make sure all guidelines are met for submission.
-
-1. Knit the file `paper.Rnw` (to make sure everything is up to date).
-2. Run the code in the file `code-file-organization.R` for producing an R script with all of the code from the manuscript (paper.Rnw).
-3. Move the following files to the `submission` folder:
-    - `code-paper.R`
-    - `data-bullet-test.csv`
-    - `data-bullet-train.csv`
-    - `data-example-signatures.csv`
-    - `figure/figure-XX-1.eps` (for XX = 01-07, 09, 11-13, B1, B2, and C3)
-    - `figure-08-1.eps`
-    - `figure-10-1.eps`
-    - `paper.tex`
-    - `readme.txt`
-    - `references.bib`
-    - `WileyNJD-AMS.bst`
-    - `WileyNJD-v1.csl`
-4. Change the name of `paper.tex` to `paper-submission.tex`.
-5. Delete `figure/` from the figure file paths in `paper-submission.tex`. For example, change \includegraphics[width=6.5in]{figure/figure-01-1} to \includegraphics[width=6.5in]{figure-01-1}.
-6. Compile the file `paper-submission.tex` (using LaTex, then bibTex, then LaTeX twice more) to make sure it compiles correctly. 
-7. Besides for `paper-submission.pdf`, delete all other files generated when `paper-sumbission.tex` was compiled. This includes other `paper-submission` files and pdf versions of the figures.
-8. Convert the following files in the submission folder to a zip file, call it `code-and-data.zip`, and then delete the unzipped versions of the files:
-    - `code-paper.R`
-    - `data-bullet-test.csv`
-    - `data-bullet-train.csv`
-    - `data-example-signatures.csv`
-    - `readme.txt`
-9. Upload all remaining files to ASA data science journal submission page (except for `paper-submission.Rnw`) which should be:
-    - `code-and-data.zip`
-    - `figure-01-1.eps` through `figure-C3-1.eps`
-    - `paper-sumbission.pdf`
-    - `paper-sumbission.tex`
-    - `references.bib`
-    - `WileyNJD-AMS.bst`
-    - `WileyNJD-v2.cls`

### 2020-09-11 paper.Rnw
changed name of variable based on change in data

@@
 signatures %>%
-  ggplot(aes(x = x/1000, y = sig)) + 
+  ggplot(aes(x = x/1000, y = y)) + 
   geom_line() +

### 2020-09-11 code/data-preparation.R
added all code related to preparing the raw data to be used in the paper

@@ -1,127 +1,183 @@
+# Code for preparing the raw bullet data (from Heike) to be used in the paper
+# Last run: September 11, 2020
 
+# Load packages
 library(dplyr)
+library(stringr)
 
-# Save the bullet training and testing datasets a zip files
-zip("data/data-bullet-train.csv.zip", "data/data-bullet-train.csv")
-zip("data/data-bullet-test.csv.zip", "data/data-bullet-test.csv")
+# -----------------------------------------------------------------------------
+# Bullet Training Data
+# -----------------------------------------------------------------------------
 
-# Save the dataset with two example matching signatures as a zip file
-zip("data/data-example-signatures.csv.zip", "data/data-example-signatures.csv")
-
-# The code in this script trims the data provided by Heike of two matching bullet signatures
-
-# Import the data
-signatures <- readRDS("data/signatures.rds")
-
-# Create a land variable based on the source variable and select only variables 
-# necessary for the manuscript
-signatures_trimmed <- signatures %>% 
-  mutate(land = c("Signature 1", "Signature 2")[as.factor(source)]) %>%
-  select(land, x, sig)
-
-# Export the trimmed data as a csv file into the manuscript directory
-write.csv(signatures_trimmed, "../diagnostics-paper/data-example-signatures.csv", row.names = FALSE)
-
+# Load the raw version of the Hamby 172 and 252 bullet comparison data, 
+# remove any lands with tank rash, select only variables of use for the paper,
+# add a case variable, and rename same_source as samesource'
 bullet_train <- 
   read.csv("data/raw/hamby-comparisons.csv") %>%
   filter(!(
-  land_id1 %in% c(
-    "Hamby173-Br6-B2-L1",
-    "Hamby173-Br9-B2-L4",
-    "Hamby173-BrUnk-BB-L2",
-    "Hamby173-BrUnk-BQ-L4"
-  ) |
-    land_id2 %in% c(
+    land_id1 %in% c(
       "Hamby173-Br6-B2-L1",
       "Hamby173-Br9-B2-L4",
       "Hamby173-BrUnk-BB-L2",
       "Hamby173-BrUnk-BQ-L4"
-    )
-)) %>%
+    ) |
+      land_id2 %in% c(
+        "Hamby173-Br6-B2-L1",
+        "Hamby173-Br9-B2-L4",
+        "Hamby173-BrUnk-BB-L2",
+        "Hamby173-BrUnk-BQ-L4"
+      )
+  )) %>%
[…]

### 2020-09-11 code/submission-steps.R
added a file with the steps to create the submission folder and included code for copying the files

@@ -4,39 +4,47 @@
 # Load packages
 library(zip)
 
-# Preparing files for submission ----------------------------------------
+## Follow these steps to make sure all guidelines are met for submission:
+
+# ----------------------------------------------------------------------------
+# Step 1
+# ----------------------------------------------------------------------------
+
+# Knit the file paper.Rnw (to make sure everything is up to date).
+
+# ----------------------------------------------------------------------------
+# Step 2
+# ----------------------------------------------------------------------------
+
+# Run the following code to move all files necessary to the submission folder.
 
 # Create a submission folder file path
 submission_folder <- "submission"
 
-## DATA AND CODE
+# DATA AND CODE
 
 # Create a temporary directory for storing code and data files for submission
 code_data_folder = "code-and-data"
 dir.create(code_data_folder) 
 
-# Extract the R code from the file paper.Rnw to be used for submission
+# Extract the R code from the files paper.Rnw to be used for submission
 knitr::purl("paper.Rnw", output = paste0(code_data_folder, "/paper.R"))
 
 # Create a vector with code and data files to be included for submission 
-data_files <-
-  c(
-    "data/bullet-test.csv",
-    "data/bullet-train.csv",
-    "data/example-signatures.csv"
-  )
+data_files <- c("readme.txt", "data/bullet-test.csv", "data/bullet-train.csv", 
+                "data/example-signatures.csv")
 
 # Copy the submission files to the temporary folder
-file.copy(code_data_files, "code-and-data")
+file.copy(data_files, "code-and-data")
 
-# Compress the folder with data and code for submission and store it 
-# in the submission folder
+# Compress the folder with data and code for submission and store it in the 
+# submission folder
 zip(paste0(submission_folder, "/code-and-data.zip"), "code-and-data")
 
 # Remove the temporary folder with code and data for submission
 unlink(code_data_folder, recursive = TRUE)
 
-## FIGURES 
+# FIGURES 
 
 # Identify the folders with files for submission
 folder_eps_figures <- "figure"
@@ -50,7 +58,7 @@ list_of_static_figures <- list.files(folder_static_figures, ".eps$", full.names 
 file.copy(list_of_generated_figures, submission_folder)
 file.copy(list_of_static_figures, submission_folder)
 
-## LATEX FILES
+# LATEX FILES
 
 # Copy files to the submission folder
 file.copy("paper.tex", submission_folder)
@@ -58,3 +66,39 @@ file.copy("paper.pdf", submission_folder)
[…]

### 2020-09-11 paper.Rnw
fixed typo in code

@@
 
-# Load the bullet matching training data and make some adjustments:
-#   1. filter out observations known to have tank rash
-#   2. exclude features not used to train the rtrees random forest 
-#   3. add a case variable
-#   4. change the name of the same_source variable to match the test data
-#   5. reorder the variables
-bullet_train <- readr::read_csv("data/bullet-train.csv.zip") %>%
-
-# Load the bullet test data
+# Load the bullet matching training and testing data
+bullet_train <- readr::read_csv("data/bullet-train.csv.zip")
 bullet_test <- readr::read_csv("data/bullet-test.csv.zip")

### 2020-09-11 code/data-preparation.R
updated code after I realized that I needed to remove some rows

@@ -133,6 +133,9 @@ hamby224_set11_cleaned <-
 # bullet, and land (remove those variables afterwards)
 hamby224_test <-
   bind_rows(hamby224_set1_cleaned, hamby224_set11_cleaned) %>%
+  filter(!(bullet1 == "BUnk" & bullet2 == "B1"),
+         !(bullet1 == "BUnk" & bullet2 == "B2"),
+         !(bullet1 == "B2" & bullet2 == "B1")) %>%
   mutate(
     case = factor(1:length(study)),
     land_id1 = paste(study, set, bullet1, land1, sep = "-"),
@@ -181,3 +184,4 @@ write.csv(
 # Also, save the original and trimmed data as a zip files (for GitHub repo)
 zip("data/raw/signatures.rds.zip", "data/raw/signatures.rds")
 zip("data/example-signatures.csv.zip", "data/example-signatures.csv")
+

### 2020-09-11 README.Rmd
removed NA from test data

@@
 
-- Remove NAs from test data
 - Write cover letter

### 2020-09-11 code/data-preparation.R
reordered vars in test data

@@ -142,7 +142,7 @@ hamby224_test <-
     land_id2 = paste(study, set, bullet2, land2, sep = "-")
   ) %>%
   select(-study,-set,-bullet1,-land1,-bullet2,-land2) %>%
-  select(case, land_id1, land_id2, everything())
+  select(case, land_id1, land_id2, all_of(rf_features), samesource, rfscore)
 
 # ave the file to the folder where the LIME diagnostics paper is stored
 write.csv(

### 2020-09-11 code/data-preparation.R
another small change to data organization

@@ -34,7 +34,11 @@ bullet_train <-
   select(case, land_id1, land_id2, everything())
 
 # Save the prepared data as a csv file
-write.csv(bullet_train, "data/bullet-train.csv")
+write.csv(
+  x = bullet_train, 
+  file = "data/bullet-train.csv", 
+  row.names = FALSE
+)
 
 # Also, save the original and prepared data as a zip files (for GitHub repo)
 zip("data/raw/hamby-comparisons.csv.zip", "data/raw/hamby-comparisons.csv")

### 2020-09-11 code/data-preparation.Rmd
converted code files to R markdown documents and added additional information about the raw data and cleaning process

---
title: "Bullet Data Preparation for LIME Diagnostics Paper"
author: "Katherine Goode"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: 
  html_document: 
    toc: TRUE
    toc_float: TRUE
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
```

This document contains code for preparing the raw bullet data sets (training, testing, and example matching signatures) to be used the paper "Visual Diagnostics of a Model Explainer -- Tools for the Assessment of LIME Explanations".

Load R packages:

```{r}
library(cowplot)
library(dplyr)
library(ggplot2)
library(stringr)
```

Obtain features used when fitting the rtrees random forest:

```{r}
rf_features <- rownames(bulletxtrctr::rtrees$importance)
```

# Bullet Training Data

Load the raw version of the Hamby 172 and 252 bullet comparison data:

```{r}
bullet_train_raw = read.csv("../data/raw/hamby-comparisons.csv")
```

Remove any lands with tank rash, select only variables of use for the paper, add a case variable, and rename `same_source` as `samesource`:

```{r}
bullet_train <- 
  bullet_train_raw %>%
  filter(!(
    land_id1 %in% c(
      "Hamby173-Br6-B2-L1",
      "Hamby173-Br9-B2-L4",
      "Hamby173-BrUnk-BB-L2",
      "Hamby173-BrUnk-BQ-L4"
    ) |
      land_id2 %in% c(
        "Hamby173-Br6-B2-L1",
        "Hamby173-Br9-B2-L4",
        "Hamby173-BrUnk-BB-L2",
        "Hamby173-BrUnk-BQ-L4"
      )
  )) %>%
  select(-lag, -abs_lag, -overlap, -signature_length) %>%
  mutate(case = factor(1:n())) %>%
  rename("samesource" = "same_source") %>%
  select(case, land_id1, land_id2, everything())
```

Save the prepared data as a csv file:

```{r}
write.csv(
  x = bullet_train, 
  file = "../data/bullet-train.csv", 
  row.names = FALSE
)
```

Also, save the original and prepared data as a zip files (for uploading to the GitHub repository):

```{r}
zip(
  zipfile = "../data/raw/hamby-comparisons.csv.zip", 
  files = "../data/raw/hamby-comparisons.csv"
)
zip(
  zipfile = "../data/bullet-train.csv.zip", 
  files = "../data/bullet-train.csv"
)
```

# Bullet Testing Data

Load in the raw Hamby 224 datasets (sets 1 and 11):

```{r}
hamby224_set1 <- readRDS("../data/raw/h224-set1-features.rds")
hamby224_set11 <- readRDS("../data/raw/h224-set11-features.rds")
```

The bullet and land names from each of the sets are included below. This indicates that each set contains `r length(unique(hamby224_set1$bulletA))` bullets with `r length(unique(hamby224_set1$landA))` lands each.

| Set | Bullets | Lands | 
| --- | -------------- | -------------- | 
| 1 | `r unique(hamby224_set1$bulletA)` | `r unique(hamby224_set1$landA)` |
| 11 | `r unique(hamby224_set11$bulletA)` | `r unique(hamby224_set11$landA)` |

The dimensions of the datasets are:

| Set | Number of Rows | Number of Columns | 
| --- | -------------- | -------------- | 
| 1 | `r dim(hamby224_set1)[1]` | `r dim(hamby224_set1)[2]` |
| 11 | `r dim(hamby224_set11)[1]` | `r dim(hamby224_set11)[2]` |

The number of rows in each of these datasets indicates that there are some lands missing since a complete set with 3 bullets and 6 lands would contains 3 bullets x 3 bullets x 6 lands x 6 lands  = `r 6 * 6 * 3 * 3` comparisons. The figures below show that set 1 is missing land 4 from bullet Q, and set 11 is missing land2 from bullet 1 and land 4 from bullet I.

```{r fig.width = 10, fig.height = 4.5}
plot_grid(
  hamby224_set1 %>%
    count(bulletA, bulletB, landA, landB) %>%
    ggplot(aes(
      x = landA, y = landB, fill = n
    )) +
    geom_tile() +
    facet_grid(bulletB ~ bulletA) +
    scale_fill_distiller(palette = "GnBu", direction = 1) +
    theme_minimal() +
    theme(aspect.ratio = 1),
  hamby224_set11 %>%
    count(bulletA, bulletB, landA, landB) %>%
    ggplot(aes(
      x = landA, y = landB, fill = n
    )) +
    geom_tile() +
    facet_grid(bulletB ~ bulletA) +
    scale_fill_distiller(palette = "GnBu", direction = 1) +
    theme_minimal() +
    theme(aspect.ratio = 1, 
          axis.text.x = element_text(angle = 45, hjust = 1)),
  align = "hv"
)
```
Preparing the data from sets 1 and 11 for analysis:

```{r}
hamby224_set1_cleaned <-
  hamby224_set1 %>%
  # Remove unneeded variables
  select(-bullet_score,-land1,-land2,-aligned,-striae,-features) %>%
  # Rename bullet and land variables
  rename(
    bullet1 = bulletA,
    bullet2 = bulletB,
    land1 = landA,
    land2 = landB
  ) %>%
  # Create study and set variables and change levels of bullet and land
  # variables to match those in the training data
  mutate(
    study = factor("Hamby224"),
    set = factor("Set1"),
    bullet1 = recode(factor(bullet1), "1" = "B1", "2" = "B2", "Q" = "BUnk"),
    bullet2 = recode(factor(bullet2), "1" = "B1", "2" = "B2", "Q" = "BUnk"),
    land1 = paste0("L", land1),
    land2 = paste0("L", land2)
  ) %>%
  # Order the variables as desired
  select(study, set, bullet1, land1, bullet2, land2, all_of(rf_features), rfscore, samesource)

hamby224_set11_cleaned <- 
  hamby224_set11 %>%
  # Remove unneeded variables
  select(-bullet_score,-land1,-land2,-aligned,-striae,-features) %>%
  # Rename bullet and land variables
  rename(
    bullet1 = bulletA,
    bullet2 = bulletB,
    land1 = landA,
    land2 = landB
  ) %>%
  # Create study and set variables and change levels of bullet and land
  # variables to match those in the training data
  mutate(
    study = factor("Hamby224"),
    set = factor("Set11"),
    bullet1 = recode(factor(bullet1), "Bullet 1" = "B1", "Bullet 2" = "B2", "Bullet I" = "BUnk"),
    bullet2 = recode(factor(bullet2), "Bullet 1" = "B1", "Bullet 2" = "B2", "Bullet I" = "BUnk"),
    land1 = str_remove(land1, "and "),
    land2 = str_remove(land2, "and ")
  ) %>%
  # Order the variables as desired
  select(study, set, bullet1, land1, bullet2, land2, all_of(rf_features), rfscore, samesource)
```

Plots show that the number of observations is still the same after cleaning:

```{r fig.width = 10, fig.height = 4.5}
plot_grid(
  hamby224_set1_cleaned %>%
    count(bullet1, bullet2, land1, land2) %>%
    ggplot(aes(
      x = land1, y = land2, fill = n
    )) +
    geom_tile() +
    facet_grid(bullet2 ~ bullet1) +
    scale_fill_distiller(palette = "GnBu", direction = 1) +
    theme_minimal() +
    theme(aspect.ratio = 1),
  hamby224_set11_cleaned %>%
    count(bullet1, bullet2, land1, land2) %>%
    ggplot(aes(
      x = land1, y = land2, fill = n
    )) +
    geom_tile() +
    facet_grid(bullet2 ~ bullet1) +
    scale_fill_distiller(palette = "GnBu", direction = 1) +
    theme_minimal() +
    theme(aspect.ratio = 1),
  align = "hv"
)
```

Join the two cleaned Hamby 224 sets into one testing set, remove duplicate comparisons, create a case variable, and create land ids based on the study, set, bullet, and land (remove those variables afterwards):

```{r}
hamby224_test_extra_vars <-
  # Join the two data sets
  bind_rows(hamby224_set1_cleaned, hamby224_set11_cleaned) %>%
  # Remove duplicate comparisons
  filter(!(bullet1 == "BUnk" & bullet2 == "B1"),
         !(bullet1 == "BUnk" & bullet2 == "B2"),
         !(bullet1 == "B2" & bullet2 == "B1")) %>%
  # Create a case and land_id variables
  mutate(
    case = factor(1:length(study)),
    land_id1 = paste(study, set, bullet1, land1, sep = "-"),
    land_id2 = paste(study, set, bullet2, land2, sep = "-")
  ) # Leave the extract variables for plotting

# Select and order variables to keep for analysis
hamby224_test <- hamby224_test_extra_vars %>%
  select(case, land_id1, land_id2, all_of(rf_features), samesource, rfscore)
```

Remaining comparisons included in the test data after the duplicate comparisons are removed:

```{r fig.width = 10, fig.height = 4.5}
plot_grid(
  hamby224_test_extra_vars %>%
    filter(set == "Set1") %>%
    count(bullet1, land1, bullet2, land2) %>%
    ggplot(aes(
      x = land1, y = land2, fill = n
    )) +
    geom_tile() +
    facet_grid(bullet2 ~ bullet1) +
    scale_fill_distiller(palette = "GnBu", direction = 1) +
    theme_minimal() +
    theme(aspect.ratio = 1),
  hamby224_test_extra_vars %>%
    filter(set == "Set11") %>%
    count(bullet1, land1, bullet2, land2) %>%
    ggplot(aes(
      x = land1, y = land2, fill = n
    )) +
    geom_tile() +
    facet_grid(bullet2 ~ bullet1) +
    scale_fill_distiller(palette = "GnBu", direction = 1) +
    theme_minimal() +
    theme(aspect.ratio = 1),
  align = "hv"
)
```

Save the test data as a csv file:

```{r}
write.csv(
  x = hamby224_test, 
  file = "../data/bullet-test.csv", 
  row.names = FALSE
)
```

Also, save the original and prepared data as a zip files (for uploading to the GitHub repository):

```{r}
zip(
  zipfile = "../data/raw/h224-set1-features.rds.zip", 
  files = "../data/raw/h224-set1-features.rds"
)
zip(
  zipfile = "../data/raw/h224-set11-features.rds.zip", 
  files = "../data/raw/h224-set11-features.rds"
)
zip(
  zipfile = "../data/bullet-test.csv.zip", 
  files = "../data/bullet-test.csv"
)
```

# Example Matching Signatures

The following code trims the data provided by Heike of two matching bullet-land signatures

Import the data:

```{r}
signatures <- readRDS("../data/raw/signatures.rds")
```

Structure of the data:

```{r}
signatures %>% str()
```

Create a land variable based on the source variable, select only variables necessary for the manuscript, and rename sig as y:

```{r}
signatures_trimmed <-
  signatures %>%
  mutate(land = c("Signature 1", "Signature 2")[as.factor(source)]) %>%
  select(land, x, sig) %>%
  rename(y = sig)
```

Export the trimmed data as a csv file:

```{r}
write.csv(
  x = signatures_trimmed,
  file = "../data/example-signatures.csv",
  row.names = FALSE
)
```

Also, save the original and prepared data as a zip files (for uploading to the GitHub repository):

```{r}
zip(
  zipfile = "../data/raw/signatures.rds.zip", 
  files = "../data/raw/signatures.rds"
)
zip(
  zipfile = "../data/example-signatures.csv.zip", 
  files = "../data/example-signatures.csv"
)
```

### 2020-09-11 code/figure-compression.Rmd
converted code files to R markdown documents and added additional information about the raw data and cleaning process

---
title: "Figure Compression"
author: "Katherine Goode"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
```

This document contains code for compressing the static figure in the manuscript.

```{r}
# Load packages
library(zip)

# Save the bullet image used in the paper as a zip file
zip(
  zipfile = "../figure-static/figure-08-1.png.zip",
  files =  "../figure-static/figure-08-1.png"
)
```

### 2020-09-11 code/submission-steps.Rmd
converted code files to R markdown documents and added additional information about the raw data and cleaning process

---
title: "Sumbission Steps"
author: "Katherine Goode"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
```

This document contains the steps to follow to make sure all guidelines are met for submission to the ASA Data Science Journal.

1. Knit the file `paper.Rnw` (to make sure everything is up to date).

2. Run the following code to move all files necessary to the submission folder.:

    ```{r}
    # Load package
    library(zip)

    # Create a submission folder file path:
    submission_folder <- "../submission"

    # If the submission folder does not exist, create one
    if (!dir.exists(submission_folder)) dir.create(submission_folder)

    # DATA AND CODE

    # Create a temporary directory for storing code and data files for submission
    code_data_folder = "code-and-data"
    dir.create(code_data_folder)

    # Extract the R code from the files paper.Rnw to be used for submission
    knitr::purl("../paper.Rnw", output = paste0(code_data_folder, "/paper.R"))

    # Create a vector with code and data files to be included for submission 
    data_files <-
      c(
        "../readme.txt",
        "../data/bullet-test.csv",
        "../data/bullet-train.csv",
        "../data/example-signatures.csv"
      )

    # Copy the submission files to the temporary folder
    file.copy(data_files, code_data_folder)

    # Compress the folder with data and code for submission and store it in the 
    # submission folder
    zip(paste0(submission_folder, "/code-and-data.zip"), code_data_folder)

    # Remove the temporary folder with code and data for submission
    unlink(code_data_folder, recursive = TRUE)

    # FIGURES

    # Identify the folders with files for submission
    folder_eps_figures <- "../figure"
    folder_static_figures <- "../figure-static"

    # Find the EPS figure files for submission
    list_of_generated_figures <- list.files(folder_eps_figures, ".eps$", full.names = T)
    list_of_static_figures <- list.files(folder_static_figures, ".eps$", full.names = T)

    # Copy files to the submission folder
    file.copy(list_of_generated_figures, submission_folder)
    file.copy(list_of_static_figures, submission_folder)

    # LATEX FILES

    # Copy files to the submission folder
    file.copy("../paper.tex", submission_folder)
    file.copy("../paper.pdf", submission_folder)
    file.copy("../references.bib", submission_folder)
    file.copy("../WileyNJD-AMS.bst", submission_folder)
    file.copy("../WileyNJD-v2.cls", submission_folder)
    ```

3. Manually delete `figure/` and `figure-static/` from the figure file paths in `paper.tex`. For example, change `\includegraphics[width=6.5in]{figure/figure-01-1}` to `\includegraphics[width=6.5in]{figure-01-1}`.

4. Compile the file `paper.tex` (using LaTex, then bibTex, then LaTeX twice more) to make sure it compiles correctly (especially references).

5. Besides for `paper.pdf`, delete all other files generated when `paper.tex` was compiled. This includes other paper files and pdf versions of the figures.

6. Upload all remaining files to ASA Data Science Journal submission page which should be:

  - `code-and-data.zip`
  - `figure-01-1.eps` through `figure-C3-1.eps`
  - `paper.pdf`
  - `paper.tex`
  - `references.bib`
  - `WileyNJD-AMS.bst`
  - `WileyNJD-v2.cls`

### 2020-09-11 code/data-preparation.R

@@ -1,191 +1,0 @@
-# Code for preparing the raw bullet data (from Heike) to be used in the paper
-# Last run: September 11, 2020
-
-# Load packages
-library(dplyr)
-library(stringr)
-
-# -----------------------------------------------------------------------------
-# Bullet Training Data
-# -----------------------------------------------------------------------------
-
-# Load the raw version of the Hamby 172 and 252 bullet comparison data, 
-# remove any lands with tank rash, select only variables of use for the paper,
-# add a case variable, and rename same_source as samesource'
-bullet_train <- 
-  read.csv("data/raw/hamby-comparisons.csv") %>%
-  filter(!(
-    land_id1 %in% c(
-      "Hamby173-Br6-B2-L1",
-      "Hamby173-Br9-B2-L4",
-      "Hamby173-BrUnk-BB-L2",
-      "Hamby173-BrUnk-BQ-L4"
-    ) |
-      land_id2 %in% c(
-        "Hamby173-Br6-B2-L1",
-        "Hamby173-Br9-B2-L4",
-        "Hamby173-BrUnk-BB-L2",
-        "Hamby173-BrUnk-BQ-L4"
-      )
-  )) %>%
-  select(-lag, -abs_lag, -overlap, -signature_length) %>%
-  mutate(case = factor(1:n())) %>%
-  rename("samesource" = "same_source") %>%
-  select(case, land_id1, land_id2, everything())
-
-# Save the prepared data as a csv file
-write.csv(
-  x = bullet_train, 
-  file = "data/bullet-train.csv", 
-  row.names = FALSE
-)
-
-# Also, save the original and prepared data as a zip files (for GitHub repo)
-zip("data/raw/hamby-comparisons.csv.zip", "data/raw/hamby-comparisons.csv")
-zip("data/bullet-train.csv.zip", "data/bullet-train.csv")
-
-# -----------------------------------------------------------------------------
-# Bullet Testing Data
-# -----------------------------------------------------------------------------
-
-# Load in the Hamby 224 datasets
-hamby224_set1 <- readRDS("data/raw/h224-set1-features.rds")
-hamby224_set11 <- readRDS("data/raw/h224-set11-features.rds")
-
-# Obtain features used when fitting the rtrees random forest
-rf_features <- rownames(bulletxtrctr::rtrees$importance)
-
[…]

### 2020-09-11 code/figure-compression.R

@@ -1,8 +1,0 @@
-## This R script contains code for compressing the static figure in the manuscript
-## Last run: September 11, 2020
-
-# Load packages
-library(zip)
-
-# Save the bullet image used in the paper as a zip file
-zip("figure-static/figure-08-1.png.zip", "figure-static/figure-08-1.png")

### 2020-09-11 code/submission-steps.R

@@ -1,104 +1,0 @@
-## Steps to follow for ASA Data Science Journal submission
-## Last Run: September 11, 2020
-
-# Load packages
-library(zip)
-
-## Follow these steps to make sure all guidelines are met for submission:
-
-# ----------------------------------------------------------------------------
-# Step 1
-# ----------------------------------------------------------------------------
-
-# Knit the file paper.Rnw (to make sure everything is up to date).
-
-# ----------------------------------------------------------------------------
-# Step 2
-# ----------------------------------------------------------------------------
-
-# Run the following code to move all files necessary to the submission folder.
-
-# Create a submission folder file path
-submission_folder <- "submission"
-
-# DATA AND CODE
-
-# Create a temporary directory for storing code and data files for submission
-code_data_folder = "code-and-data"
-dir.create(code_data_folder) 
-
-# Extract the R code from the files paper.Rnw to be used for submission
-knitr::purl("paper.Rnw", output = paste0(code_data_folder, "/paper.R"))
-
-# Create a vector with code and data files to be included for submission 
-data_files <- c("readme.txt", "data/bullet-test.csv", "data/bullet-train.csv", 
-                "data/example-signatures.csv")
-
-# Copy the submission files to the temporary folder
-file.copy(data_files, "code-and-data")
-
-# Compress the folder with data and code for submission and store it in the 
-# submission folder
-zip(paste0(submission_folder, "/code-and-data.zip"), "code-and-data")
-
-# Remove the temporary folder with code and data for submission
-unlink(code_data_folder, recursive = TRUE)
-
-# FIGURES 
-
-# Identify the folders with files for submission
-folder_eps_figures <- "figure"
-folder_static_figures <- "figure-static"
-
-# Find the EPS figure files for submission
-list_of_generated_figures <- list.files(folder_eps_figures, ".eps$", full.names = T)
-list_of_static_figures <- list.files(folder_static_figures, ".eps$", full.names = T)
-
-# Copy files to the submission folder
-file.copy(list_of_generated_figures, submission_folder)
-file.copy(list_of_static_figures, submission_folder)
-
-# LATEX FILES
-
-# Copy files to the submission folder
-file.copy("paper.tex", submission_folder)
-file.copy("paper.pdf", submission_folder)
-file.copy("references.bib", submission_folder)
-file.copy("WileyNJD-AMS.bst", submission_folder)
-file.copy("WileyNJD-v2.cls", submission_folder)
-
-# ----------------------------------------------------------------------------
-# Step 3
[…]

### 2020-09-11 README.Rmd
updated code file names

@@
 
-- `data-preparation.R` contains R code for preparing the raw bullet data (bullet training data, bullet testing data, and example matching signatures) to be used in the paper
-- `figure-compression.R` contains R code for compressing the static figure used in the paper
-- `submission-steps.R` contains the to do list and R code for preparing the files for submission to the ASA Data Science Journal.
+- `data-preparation.Rmd` contains R code for preparing the raw bullet data (bullet training data, bullet testing data, and example matching signatures) to be used in the paper
+- `figure-compression.Rmd` contains R code for compressing the static figure used in the paper
+- `submission-steps.Rmd` contains the to do list and R code for preparing the files for submission to the ASA Data Science Journal.
 

### 2020-09-12 code/submission-steps.Rmd
updated the submission steps with more code to help automate the process

@@
 ```{r setup, include = FALSE}
-knitr::opts_chunk$set(echo = TRUE, message = FALSE)
+knitr::opts_chunk$set(echo = TRUE, message = FALSE, eval = FALSE)
 ```
@@
 
-1. Knit the file `paper.Rnw` (to make sure everything is up to date).
+**NOTE** The knitr option of `eval = FALSE` has been set for this document, so all code must be run manually from withing the Rmd file. This is done to be safe about not deleting or replacing files.
 
-2. Run the following code to move all files necessary to the submission folder.:
+1. Delete all files generated by `paper.Rnw` and current existing submission folder using the code below.
+
+    ```{r}
+    # Individual files to delete
+    file.remove("../data/bullet-explain.rds")
+    file.remove("../data/bullet-lime.rds")
+    file.remove("../data/sine-lime-explain.rds")
+    file.remove("../figure-static/figure-10-1.eps")
+    file.remove("../figure-static/figure-10-1.png")
+
+    # Folders to delete
+    unlink("../figure", recursive = TRUE)
+    unlink("../submission", recursive = TRUE)
+    ```
+
+2. Knit the file `paper.Rnw`.
+
+3. Run the following code to move all files necessary to the submission folder.
 
@@
     # Find the EPS figure files for submission
-    list_of_generated_figures <- list.files(folder_eps_figures, ".eps$", full.names = T)
-    list_of_static_figures <- list.files(folder_static_figures, ".eps$", full.names = T)
+    list_of_generated_figures <-
+      list.files(folder_eps_figures, ".eps$", full.names = T)
+    list_of_static_figures <-
+      list.files(folder_static_figures, ".eps$", full.names = T)
 
@@
 
-3.
+4.
 Manually delete `figure/` and `figure-static/` from the figure file paths in `paper.tex`.
@@
 
-4. Compile the file `paper.tex` (using LaTex, then bibTex, then LaTeX twice more) to make sure it compiles correctly (especially references).
+5. Compile the file `paper.tex` (using LaTex, then bibTex, then LaTeX twice more) to make sure it compiles correctly (especially references).
 
-5. Besides for `paper.pdf`, delete all other files generated when `paper.tex` was compiled. This includes other paper files and pdf versions of the figures.
+6. Besides for `paper.pdf`, delete all other files generated when `paper.tex` was compiled. This includes other paper files and pdf versions of the figures.
 
-6. Upload all remaining files to ASA Data Science Journal submission page which should be:
+    ```{r}
+    # Remove the paper files that may have been generated during compilation
+    file.remove("../submission/paper.aux")
+    file.remove("../submission/paper.bbl")
+    file.remove("../submission/paper.blg")
+    file.remove("../submission/paper.log")
+    file.remove("../submission/paper.synctex.gz")
+    file.remove("../submission/paper.pag")
+
+    # Remove the pdf versions of the figures generated during compilation
+    file.remove(list.files(
+      path = "../submission/",
+      pattern = "converted-to",
+      full.names = TRUE
+    ))
+    ```
+
+7. Upload all remaining files in the submission folder to the ASA Data Science Journal submission page which should be:
 

### 2020-09-12 paper.Rnw
reknit the paper after updating test data

@@
 \cname{\author{Goode K.}, \author{H. Hofmann}, }
-\cyear{2019},
+\cyear{2020},
 \ctitle{Visual Diagnostics of a Model Explainer -- Tools for the Assessment of LIME Explanations},
@@
 
+# File names for parallel coordinate plot
+pcp_file_name_png = "figure-static/figure-10-1.png"
+pcp_file_name_eps = "figure-static/figure-10-1.eps"
+
 # Create the parallel coordinate plot (if needed)
-if (!file.exists("figure-static/figure-10-1.png")) {
+if (!file.exists(pcp_file_name_png) | !file.exists(pcp_file_name_eps)) {
 
@@
     plot = bullet_pcp,
-    filename = "figure-10-1.png",
+    filename = pcp_file_name_png,
     width = 7.5,
@@
   # Load the figure and then save as an EPS file
-  bullet_pcp <- image_read("figure-static/figure-10-1.png")
-  image_write(bullet_pcp, path = "figure-static/figure-10-1.eps", format = "eps")
+  bullet_pcp <- image_read(pcp_file_name_png)
+  image_write(bullet_pcp, path = pcp_file_name_eps, format = "eps")
 
@@
 # Load and print the plot
-knitr::include_graphics("figure-static/figure-10-1.eps")
+knitr::include_graphics(pcp_file_name_eps)
 
@@
 
-<<figure-12, out.width = '6.5in', warning = FALSE, fig.width = 10, fig.height = 4.25>>=
+<<figure-12, out.width = '6.5in', warning = FALSE, fig.width = 10, fig.height = 4>>=
 

### 2020-09-12 README.Rmd
updated descriptions of code files

--- 2020-09-11 README.Rmd
@@
 
-- `data-preparation.R` contains R code for preparing the raw bullet data (bullet training data, bullet testing data, and example matching signatures) to be used in the paper
-- `figure-compression.R` contains R code for compressing the static figure used in the paper
-- `submission-steps.R` contains the to do list and R code for preparing the files for submission to the ASA Data Science Journal.
+- `data-preparation.Rmd` contains R code for preparing the raw bullet data (bullet training data, bullet testing data, and example matching signatures) to be used in the paper and saves zip versions of the data sets to be uploaded to GitHub
+- `figure-compression.Rmd` contains R code for compressing the static figure used in the paper to be uploaded to GitHub
+- `submission-steps.Rmd` contains the to do list and R code for preparing the files for submission to the ASA Data Science Journal.
 

### 2020-09-12 code/data-preparation.Rmd
updated work relating to trying to determine the issue with the number of observations in the training data

@@
 library(stringr)
+library(tidyr)
 ```
@@
 
+Create a new version of the data with the land IDs separated into separate variables for an analysis of the number of observations in this data:
+
+```{r}
+bullet_train_raw_expanded <-
+  bullet_train_raw %>%
+  separate(land_id1,
+           sep = "-",
+           into = c("study1", "barrel1", "bullet1", "land1")) %>%
+  separate(land_id2,
+           sep = "-",
+           into = c("study2", "barrel2", "bullet2", "land2"))
+```
+
+The number of comparisons within the two studies are included below:
+
+```{r}
+table(
+  bullet_train_raw_expanded$study1,
+  bullet_train_raw_expanded$study2
+)
+```
+
+The dimension of the data once the observations with tank rash (`flag != FALSE`) are removed:
+
+```{r}
+bullet_train_raw %>% filter(flag == FALSE) %>% dim()
+```
+
+The number of observations in the random forest `rtrees` (note that they do not match the number of rows in the above dataset):
+
+```{r}
+length(bulletxtrctr::rtrees$predicted)
+```
+
 Remove any lands with tank rash, select only variables of use for the paper, add a case variable, and rename `same_source` as `samesource`:
@@
   bullet_train_raw %>%
-  filter(!(
-    land_id1 %in% c(
-      "Hamby173-Br6-B2-L1",
-      "Hamby173-Br9-B2-L4",
-      "Hamby173-BrUnk-BB-L2",
-      "Hamby173-BrUnk-BQ-L4"
-    ) |
-      land_id2 %in% c(
-        "Hamby173-Br6-B2-L1",
-        "Hamby173-Br9-B2-L4",
-        "Hamby173-BrUnk-BB-L2",
-        "Hamby173-BrUnk-BQ-L4"
-      )
-  )) %>%
+  filter(flag == FALSE) %>%
   select(-lag, -abs_lag, -overlap, -signature_length) %>%

### 2020-09-12 paper.Rnw
fixed issue with change in test data numbering (now rerunning everything again)

@@
 # Specify two cases of interest
-bullet_poi_match <- unique(bullet_explain_noperms$case)[c(325)]
-bullet_poi_nonmatch <- unique(bullet_explain_noperms$case)[c(20)]
+bullet_poi_match <- 
+  bullet_test %>% 
+  filter(land_id1 == "Hamby224-Set11-B1-L5", 
+         land_id2 == "Hamby224-Set11-B2-L2") %>% 
+  pull(case)
+bullet_poi_nonmatch <- bullet_test %>% 
+  filter(land_id1 == "Hamby224-Set1-B2-L5", 
+         land_id2 == "Hamby224-Set1-BUnk-L3") %>% 
+  pull(case)
 
@@
                        bullet_poi_match,
-                       bullet_poi_nonmatch))
+                       bullet_poi_nonmatch) %>% as.character())
 

### 2020-09-14 README.Rmd
added a clarification
changes to fix font size issue in Figure 11 and cut off text in Figure 12

@@
 - `example-signatures.csv.zip` contains signature data from two matching bullet lands that is used to generate a figure in the paper.
-- `raw` contains the raw versions of the data files that the above datasets are derived from.
+- `raw` contains the raw versions of the data files (from Heike and CSAFE) that the above datasets are derived from.
 
@@
 The font sizes in the figures are calculated based on how the figures are scaled due to the specification of both fig.width and out.width in the Rnw file to ensure that they are consistent across figures.
-The text sizes are either set to 7 pt or 5.5 pt as indicated by the table below.
-Note that the text in the paper is 9 pt and a similar approach was used to ensure that line sizes are larger than 0.5 pt.
+The text sizes are either set to 7 pt or 5.5 pt (Helvetica) as indicated by the table below.
+Note that the text in the paper is 9 pt (Times) and a similar approach was used to ensure that line sizes are larger than 0.5 pt.
 
@@
 | Legend labels | 5.5 pt |
+
+Note: The only figure that does not follow these values is Figure 11 where the facet labels were set to font size 5 (Helvetica) in order for them to fit appropriately.

### 2020-09-14 paper.Rnw
changes to fix font size issue in Figure 11 and cut off text in Figure 12

@@
     strip.background = element_rect(color = "white", fill = "white"),
-    strip.text.y.right = element_text(angle = 0),
+    strip.text.y.right = element_text(angle = 0, size = f11_fs*0.7),
+    strip.text.x = element_text(size = f11_fs*0.7),
     legend.position = "bottom",

### 2020-09-14 cover-letter/cover-letter.Rmd
added cover letter

---
title: "Cover Letter for Submission to Statistical Analysis and Data Mining"
author: "Katherine"
output: pagedown::html_letter
knit: pagedown::chrome_print
---

<style>
body{
  font-size: 9.1pt;
}
</style>

![ISU logo](isu-logo.png){.logo}

::: from
Katherine Goode, PhD Candidate  
Iowa State University  
Department of Statistics  
Ames, IA 50011  
kgoode@iastate.edu
:::

Dr. Jia Li  
Editor-In-Chief  
Statistical Analysis and Data Mining

::: date
September 18, 2020
:::

Dear Dr. Jia Li and other editors of Statistical Analysis and Data Mining,

We submit for review an article entitled "Visual Diagnostics of a Model Explainer -- Tools for the Assessment of LIME Explanations" by Katherine Goode and Dr. Heike Hofmann. In this paper, we present visual diagnostic tools for the explainable machine learning method LIME (local interpretable model agnostic explanations) developed by Marco Tulio Ribeiro, Sameer Singh, and Carlos Guestrin (2016). We confirm that this work is original, has not been previously published, and is not under consideration for publication elsewhere.

We believe this manuscript is appropriate for publication by Statistical Analysis and Data Mining, because explainable machine learning is an important aspect for gaining trust in machine learning models, and our paper addresses the need to assess explanations from the popular method LIME. LIME is intended to gain insight into black-box models by using a simple linear model to approximate the complex model in a local region of interest. We argue that without an assessment of the approximation, LIME becomes a black-box method that requires blind trust from the user. The visual diagnostics we propose allow for the assessment of LIME explanations and highlight common issues with LIME. Our paper encourages users of LIME to be cautious of the explanations produced without diagnosing the fit of the linear model.

We have no conflicts of interest to disclose.

Thank you for your consideration. We look forward to your response.

Sincerely,

![ISU logo](signature.png){width=25%}

Katherine Goode, PhD Candidate  
Iowa State University
Department of Statistics

### 2020-09-14 README.Rmd
updated readme with cover letter folder

@@
 
-- Write cover letter
+- Figure out discrepancies with old and new versions of the training data
 - Finish filling in questions in ASA submission document
-- Figure out discrepancies with old and new versions of the training data
 - Rerun the lime explanations with the finalized training data
@@
 - `submission-steps.Rmd` contains the to do list and R code for preparing the files for submission to the ASA Data Science Journal.
+
+**`cover-letter`**
+
+Contains the files associated with the cover letter submitted to the ASA Data Science journal.
 

### 2020-09-14 README.Rmd
updatd to do list and descriptions of data

@@
 
+- Paper
   - Figure out discrepancies with old and new versions of the training data
-- Finish filling in questions in ASA submission document
   - Rerun the lime explanations with the finalized training data
+  - Update all files in the submission folder
+- Submission
+  - Add Heike's ORCID ID
+  - Not required but "Authors are requested to suggest at least one recommended reviewer"
+  - Edit cover letter and upload
+  - Enter the name of the Editor you are submitting to.
   - Edit dataset descriptions in README and add to the readme.txt document for submission
-- Update all files in the submission folder
   - Upload the files for submission and submit
@@
 
+```{r echo = FALSE}
+bullet_train = readr::read_csv("data/bullet-train.csv.zip")
+bullet_test = readr::read_csv("data/bullet-test.csv.zip")
+signatures = readr::read_csv("data/example-signatures.csv.zip")
+```
+
 The data used in the paper for the bullet comparison examples is described below.
 
-`data-bullet-train`: Contains comparison features from the Hamby 173 and 252 sets.
+`bullet-train`: A dataset with `r dim(bullet_train)[1]` rows and `r dim(bullet_train)[2]` columns that contains comparison features from the Hamby 173 and 252 sets (XXX reference XXX).
+XXX Additional information about the number of comparisons.XXX See XXX for additional information on the data.
+The variables in the data are as follows:
 
-`data-bullet-test`: Contains comparison features from the Hamby 224 Clone sets.
-As with all Hamby sets, Hamby set 224, is a collection of 35 bullets, organized as 20 known bullets and 15 questioned bullets.
-The known bullets are fired in pairs of two through one of ten consecutively manufactures P-85 barrels.
-Clone set 224 is arranged as a test set of fifteen tests, one for each questioned bullet.
+- `r names(bullet_train)[1]` = ID number associated with the bullet-land signature comparison
+- `r names(bullet_train)[2]` = ID associated with the first bullet-land in the comparison. The format is 'study-barrel number-bullet number-land number'.
+- `r names(bullet_train)[3]` = ID associated with the second bullet-land in the comparison. Again, the format is 'study-barrel number-bullet number-land number'.
+- `r names(bullet_train)[4]`, `r names(bullet_train)[5]`, `r names(bullet_train)[6]`, `r names(bullet_train)[7]`, `r names(bullet_train)[8]`, `r names(bullet_train)[9]`, `r names(bullet_train)[10]`, `r names(bullet_train)[11]`, and `r names(bullet_train)[12]` = comparison features of the two bullet-land signatures.
+See XXX for definitions of these features.
+- `r names(bullet_train)[13]` = indicator variable specifying whether the two bullet-lands are a match
+- `r names(bullet_train)[14]` = indictor variable specifying whether one of the bullets in the comparison has tank rash
+
+`bullet-test`: A dataset with `r dim(bullet_test)[1]` rows and `r dim(bullet_test)[2]` columns that contains comparison features from sets 1 and 11 of the Hamby 224 Clone sets (XXX reference XXX).
 Each test set is arranged as a combination of three bullets: two known bullets and a questioned bullet.
-The test asks for a decision on whether the questioned bullet comes from the same source as the two known bullets or from a different source.
-This situation is similar to what a firearms and toolmarks examiner might encounter in case work.
+Each bullet has 6 lands.
+The data contains comparisons of bullet-lands within a set.
+With three bullets with six lands per set, there are a total of (2 sets) x (3!
+bullet comparisons) x (6^2 land comparisons) = `r 2 * (3 + 2 + 1) * 6^2` comparisons.
+However, there are only `r dim(bullet_test)[1]` comparisons in the `bullet-test` data.
+This is due to the fact that some of the lands are missing from the data (probably due to tank rank): land 4 from the unknown bullet in set 1, land 2 from bullet 1 in set 11, and land 4 from the unknown bullet in set 11.
+The first `r dim(bullet_test)[2] - 1` variables in the data are the same as those in the training data (see the variable definitions associated with `bullet-train`).
+The ``r dim(bullet_test)[2]`th variable is:
 
-`data-example-signatures`: Contains the signature data from two bullet-lands that are a match. The variables in the data are as follows:
+- `r names(bullet_test)[14]` = the random forest score associated with the comparison in support of a match
 
-  - land = Indicates where the observation corresponds to 'Signature 1' or 'Signature 2'
-  - x = The x position of the signature
-  - sig = The y position of the signature
+`example-signatures`: Contains the signature data from two bullet-land signatures that are a match. The variables in the data are as follows:
+
+- `r names(signatures)[1]` = Indicates where the observation corresponds to 'Signature 1' or 'Signature 2'
+- `r names(signatures)[2]` = The x position of the signature
+- `r names(signatures)[3]` = The y position of the signature
 

### 2020-09-14 README.Rmd
removed the flag variable from the training data and add the random forest score to match the test data (now the 14 variables in each data is the same)

@@
 `bullet-train`: A dataset with `r dim(bullet_train)[1]` rows and `r dim(bullet_train)[2]` columns that contains comparison features from the Hamby 173 and 252 sets (XXX reference XXX).
-XXX Additional information about the number of comparisons.XXX See XXX for additional information on the data.
+This dataset is created using the data available XXX, which contains XXX (add more info about the comparisons).
+The only changes made to the data from XXX were to remove any lands with tank rash, select only variables of use for the paper, add a case variable, rename `same_source` as `samesource`, and attach the random forest scores associated with the comparisons.
 The variables in the data are as follows:
@@
 - `r names(bullet_train)[13]` = indicator variable specifying whether the two bullet-lands are a match
-- `r names(bullet_train)[14]` = indictor variable specifying whether one of the bullets in the comparison has tank rash
+- `r names(bullet_train)[14]` = the random forest score associated with the comparison in support of a match
 
@@
 This is due to the fact that some of the lands are missing from the data (probably due to tank rank): land 4 from the unknown bullet in set 1, land 2 from bullet 1 in set 11, and land 4 from the unknown bullet in set 11.
-The first `r dim(bullet_test)[2] - 1` variables in the data are the same as those in the training data (see the variable definitions associated with `bullet-train`).
-The ``r dim(bullet_test)[2]`th variable is:
-
-- `r names(bullet_test)[14]` = the random forest score associated with the comparison in support of a match
+The `r dim(bullet_test)[2]` variables in the data are the same as those in the training data (see the variable definitions associated with `bullet-train`).
 

### 2020-09-14 code/data-preparation.Rmd
removed the flag variable from the training data and add the random forest score to match the test data (now the 14 variables in each data is the same)

@@
 library(ggplot2)
+library(randomForest)
 library(stringr)
@@
   filter(flag == FALSE) %>%
-  select(-lag, -abs_lag, -overlap, -signature_length) %>%
+  select(-lag, -abs_lag, -overlap, -signature_length, -flag) %>%
   mutate(case = factor(1:n())) %>%
@@
   select(case, land_id1, land_id2, everything())
+```
+
+Add a variable to the training data with the random forest probability in support of a match using the random forest model `rtrees` from `bulletxtrctr`:
+
+```{r}
+bullet_features <- rownames(bulletxtrctr::rtrees$importance)
+bullet_train$rfscore <- 
+  bulletxtrctr::rtrees %>%
+  predict(bullet_train %>% select(all_of(bullet_features)), type = "prob") %>%
+  data.frame() %>%
+  pull(TRUE.)
 ```

### 2020-09-14 code/data-preparation.Rmd
small changes

@@
 ```{r setup, include = FALSE}
-knitr::opts_chunk$set(echo = TRUE, message = FALSE)
+knitr::opts_chunk$set(echo = TRUE, message = FALSE, fig.align = "center")
 ```
@@
 This document contains code for preparing the raw bullet data sets (training, testing, and example matching signatures) to be used the paper "Visual Diagnostics of a Model Explainer -- Tools for the Assessment of LIME Explanations".
+
+**NOTE** The code chunks where the prepared data versions are shared have `eval = FALSE`. These code chunks must be run manually. This is done to help avoid any accidental changes of the data.
 
@@
 library(dplyr)
+library(forcats)
 library(ggplot2)
@@
 
-Create a new version of the data with the land IDs separated into separate variables for an analysis of the number of observations in this data:
+Create a new version of the data with the land IDs separated into separate variables for an analysis of the number of observations in this data and reorder the barrels:
 
@@
            sep = "-",
-           into = c("study2", "barrel2", "bullet2", "land2"))
+           into = c("study2", "barrel2", "bullet2", "land2")) %>%
+  mutate(barrel1 = fct_relevel(barrel1, paste0("Br", 1:10), "BrUnk"),
+         barrel2 = fct_relevel(barrel2, paste0("Br", 1:10), "BrUnk"))
 ```
@@
 ```
+
+## Compare Dimensions to rtrees
 
@@
 ```
+
+**XXX Need to determine why the number of dimensions do not match. XXX**
+
+## Preparing Data
 
@@
 
-```{r}
+```{r eval = FALSE}
 write.csv(
@@
 
-```{r}
+```{r eval = FALSE}
 zip(

### 2020-09-14 paper.Rnw
updated paper after changing data
added the link for installing bullextrctr for future reference

@@
 # Load packages
+library(bulletxtrctr) #remotes::install_github("heike/bulletxtrctr")
 library(Cairo)
@@
 
-# Add a variable to the training data with the random forest probability
-# in support of a match
-bullet_train$rfscore <- 
-  bulletxtrctr::rtrees %>%
-  predict(bullet_train %>% select(all_of(bullet_features)), type = "prob") %>%
-  data.frame() %>%
-  pull(TRUE.)
-
 # Order the features based on feature importance

### 2020-09-14 README.Rmd
more small changes

@@
 
-`bullet-train`: A dataset with `r dim(bullet_train)[1]` rows and `r dim(bullet_train)[2]` columns that contains comparison features from the Hamby 173 and 252 sets (XXX reference XXX).
-This dataset is created using the data available XXX, which contains XXX (add more info about the comparisons).
+**`bullet-train`**
+
+A dataset with `r dim(bullet_train)[1]` rows and `r dim(bullet_train)[2]` columns that contains comparison features from the Hamby 173 and 252 sets (XXX reference XXX).
+This dataset is created using the data available at XXX, which contains XXX (add more info about the comparisons).
 The only changes made to the data from XXX were to remove any lands with tank rash, select only variables of use for the paper, add a case variable, rename `same_source` as `samesource`, and attach the random forest scores associated with the comparisons.
@@
 
-`bullet-test`: A dataset with `r dim(bullet_test)[1]` rows and `r dim(bullet_test)[2]` columns that contains comparison features from sets 1 and 11 of the Hamby 224 Clone sets (XXX reference XXX).
+**`bullet-test`**
+
+A dataset with `r dim(bullet_test)[1]` rows and `r dim(bullet_test)[2]` columns that contains comparison features from sets 1 and 11 of the Hamby 224 Clone sets (XXX reference XXX).
 Each test set is arranged as a combination of three bullets: two known bullets and a questioned bullet.
@@
 
-`example-signatures`: Contains the signature data from two bullet-land signatures that are a match. The variables in the data are as follows:
+**`example-signatures`**
+
+Contains the signature data from two bullet-land signatures that are a match. The variables in the data are as follows:
 

### 2020-09-15 README.Rmd
fixed an issue with the data descriptions

@@
 - `r names(bullet_train)[1]` = ID number associated with the bullet-land signature comparison
-- `r names(bullet_train)[2]` = ID associated with the first bullet-land in the comparison. The format is 'study-barrel number-bullet number-land number'.
-- `r names(bullet_train)[3]` = ID associated with the second bullet-land in the comparison. Again, the format is 'study-barrel number-bullet number-land number'.
+- `r names(bullet_train)[2]` = ID associated with the first bullet-land in the comparison. The format is 'study - barrel number - bullet number - land number'
+- `r names(bullet_train)[3]` = ID associated with the second bullet-land in the comparison. Again, the format is 'study - barrel number - bullet number - land number'
 - `r names(bullet_train)[4]`, `r names(bullet_train)[5]`, `r names(bullet_train)[6]`, `r names(bullet_train)[7]`, `r names(bullet_train)[8]`, `r names(bullet_train)[9]`, `r names(bullet_train)[10]`, `r names(bullet_train)[11]`, and `r names(bullet_train)[12]` = comparison features of the two bullet-land signatures.
-See XXX for definitions of these features.
+See XXX for definitions of these features
 - `r names(bullet_train)[13]` = indicator variable specifying whether the two bullet-lands are a match
@@
 This is due to the fact that some of the lands are missing from the data (probably due to tank rank): land 4 from the unknown bullet in set 1, land 2 from bullet 1 in set 11, and land 4 from the unknown bullet in set 11.
-The `r dim(bullet_test)[2]` variables in the data are the same as those in the training data (see the variable definitions associated with `bullet-train`).
+The variables in the data are as follows:
+
+- `r names(bullet_test)[1]` = ID number associated with the bullet-land signature comparison
+- `r names(bullet_test)[2]` = ID associated with the first bullet-land in the comparison with a format of 'study - set number - bullet number - land number'
+- `r names(bullet_test)[3]` = ID associated with the second bullet-land in the comparison with a format of 'study - set number - bullet number - land number'
+- `r names(bullet_test)[4]`, `r names(bullet_test)[5]`, `r names(bullet_test)[6]`, `r names(bullet_test)[7]`, `r names(bullet_test)[8]`, `r names(bullet_test)[9]`, `r names(bullet_test)[10]`, `r names(bullet_test)[11]`, and `r names(bullet_test)[12]` = comparison features of the two bullet-land signatures.
+See XXX for definitions of these features.
+- `r names(bullet_test)[13]` = indicator variable specifying whether the two bullet-lands are a match
+- `r names(bullet_test)[14]` = the random forest score associated with the comparison in support of a match
 

### 2020-09-15 code/submission-steps.Rmd
updated the submission data to be in zip file format

@@
         "../readme.txt",
-        "../data/bullet-test.csv",
-        "../data/bullet-train.csv",
-        "../data/example-signatures.csv"
+        "../data/bullet-test.csv.zip",
+        "../data/bullet-train.csv.zip",
+        "../data/example-signatures.csv.zip"
       )

### 2020-09-16 README.Rmd
updated to do list

@@
 - Paper
-  - Figure out discrepancies with old and new versions of the training data
-  - Rerun the lime explanations with the finalized training data
+  - Adjust order of match and non-match in feature heat map
+  - Train a random forest model on prepared training data (make sure to set a seed!) 
+  - Make predictions on test data
+  - Rerun all code in paper (check for changes in results)
+  - Update text in paper to describe the random forest model process
   - Update all files in the submission folder
 - Submission
-  - Add Heike's ORCID ID
+  - Take photos of lime R package defaults with a data and save in figure-static for future reference and security
+  - Determine the number of land comparisons in training data (in code file) and add to readme
   - Not required but "Authors are requested to suggest at least one recommended reviewer"
+    - Matthias: does research related to visual explanations
+    - Simon: exploratory data modeling
+    - Pedersen: author of R lime package
   - Edit cover letter and upload
-  - Enter the name of the Editor you are submitting to.
   - Edit dataset descriptions in README and add to the readme.txt document for submission
   - Upload the files for submission and submit
-- Look into using renev
 

### 2020-09-16 cover-letter/cover-letter.Rmd
small updates to cover letter

@@
 Heike Hofmann.
-In this paper, we present visual diagnostic tools for the explainable machine learning method LIME (local interpretable model agnostic explanations) developed by Marco Tulio Ribeiro, Sameer Singh, and Carlos Guestrin (2016).
+In this manuscript, we present visual diagnostic tools for the explainable machine learning method LIME (local interpretable model agnostic explanations) developed by Marco Tulio Ribeiro, Sameer Singh, and Carlos Guestrin (2016).
 We confirm that this work is original, has not been previously published, and is not under consideration for publication elsewhere.
 
-We believe this manuscript is appropriate for publication by Statistical Analysis and Data Mining, because explainable machine learning is an important aspect for gaining trust in machine learning models, and our paper addresses the need to assess explanations from the popular method LIME.
+We believe this manuscript is appropriate for publication by Statistical Analysis and Data Mining, because explainable machine learning is an important aspect for gaining trust in machine learning models, and our manuscript addresses the need to assess explanations from the popular method LIME.
 LIME is intended to gain insight into black-box models by using a simple linear model to approximate the complex model in a local region of interest.
@@
 The visual diagnostics we propose allow for the assessment of LIME explanations and highlight common issues with LIME.
-Our paper encourages users of LIME to be cautious of the explanations produced without diagnosing the fit of the linear model.
+Our manuscript encourages users of LIME to be cautious of the explanations produced without diagnosing the fit of the LIME linear model.
 

### 2020-09-16 README.Rmd
updated data files in preparation for training the random forest model

--- 2020-09-15 README.Rmd
@@
 
-- Paper
-  - Figure out discrepancies with old and new versions of the training data
-  - Rerun the lime explanations with the finalized training data
+- Manuscript
+  - Adjust order of match and non-match in feature heat map
+  - Train a random forest model on prepared training data (make sure to set a seed!) 
+  - Make predictions on test data
+  - Rerun all code in manuscript (check for changes in results)
+  - Update text in manuscript to describe the random forest model process
   - Update all files in the submission folder
 - Submission
-  - Add Heike's ORCID ID
-  - Not required but "Authors are requested to suggest at least one recommended reviewer"
-  - Edit cover letter and upload
-  - Enter the name of the Editor you are submitting to.
   - Edit dataset descriptions in README and add to the readme.txt document for submission
   - Upload the files for submission and submit
-- Look into using renev
 
-# LIME Diagnostics Paper
+# LIME Diagnostics Manuscript
 
@@
 
-This repository contains the files associated with the paper "Visual Diagnostics of a Model Explainer -- Tools for the Assessment of LIME Explanations" by Katherine Goode and Heike Hofmann.
+This repository contains the files associated with the manuscript "Visual Diagnostics of a Model Explainer -- Tools for the Assessment of LIME Explanations" by Katherine Goode and Heike Hofmann.
 The rest of this readme contains:
@@
 - information about the files in the repository,
-- instructions for knitting the paper,
-- descriptions of the bullet data used in the paper, and
-- information on the font sizes used for the figures in the paper.
+- instructions for knitting the manuscript,
+- descriptions of the bullet data used in the manuscript, and
+- information on the font sizes used for the figures in the manuscript.
 
@@
 
-Contains the R code associated with the paper that is not directly included in `paper.Rnw` (such as some external data cleaning and file organization):
+Contains the R code associated with the manuscript that is not directly included in `paper.Rnw` (such as some external data cleaning and file organization):
 
-- `data-preparation.Rmd` contains R code for preparing the raw bullet data (bullet training data, bullet testing data, and example matching signatures) to be used in the paper and saves zip versions of the data sets to be uploaded to GitHub
-- `figure-compression.Rmd` contains R code for compressing the static figure used in the paper to be uploaded to GitHub
+- `data-preparation.Rmd` contains R code for preparing the raw bullet data (bullet training data, bullet testing data, and example matching signatures) to be used in the manuscript and saves zip versions of the data sets to be uploaded to GitHub
+- `figure-compression.Rmd` contains R code for compressing the static figure used in the manuscript to be uploaded to GitHub
 - `submission-steps.Rmd` contains the to do list and R code for preparing the files for submission to the ASA Data Science Journal.
@@
 
-Contains the data used to generate the paper:
+Contains the data used to generate the manuscript:
 
-- `bullet-test.csv.zip` and `bullet-test.csv.zip` contain the data used for the bullet examples in the paper.
+- `bullet-test.csv.zip` and `bullet-test.csv.zip` contain the data used for the bullet examples in the manuscript.
 Additional information about these files is included below under the heading "Additional Information on Bullet Data".
-- `example-signatures.csv.zip` contains signature data from two matching bullet lands that is used to generate a figure in the paper.
+- `example-signatures.csv.zip` contains signature data from two matching bullet lands that is used to generate a figure in the manuscript.
 - `raw` contains the raw versions of the data files (from Heike and CSAFE) that the above datasets are derived from.
@@
 
-- `figure-08-1.png.zip` is the one figure in the paper that is not generated using R code.
+- `figure-08-1.png.zip` is the one figure in the manuscript that is not generated using R code.
 - `figure-readme.png` is a figure used in the readme.
@@
 
-Contains the files associated with an old version of the paper that is much longer the the submitted version
+Contains the files associated with an old version of the manuscript that is much longer the the submitted version
 
@@
 - `.gitignore` contains objects to be ignored by git.
-- `paper.Rnw`, `paper.pdf`, and `paper.tex` are the paper. Note that `paper.pdf` and `paper.tex` are generated by `paper.Rnw`.
+- `paper.Rnw`, `paper.pdf`, and `paper.tex` are the manuscript. Note that `paper.pdf` and `paper.tex` are generated by `paper.Rnw`.
 - `README.Rmd` and `README.md` are the readme files that generated this output.
 - `readme.txt` contains descriptions of the data files that are included with the submission
-- `references.bib` contains the bibtex information for the references in the paper
+- `references.bib` contains the bibtex information for the references in the manuscript
 - `WileyNJG-AMS.bst` and `WileyNJG-v2.cls` contain the latex formatting specifications for the ASA Data Science Journal.
 
-## Instructions for Knitting Paper
+## Instructions for Knitting Manuscript
 
-When the paper is knit, various files will be generated (such as `data-bullet-explain.rds` and `figure-10-1.png`).
-The first time the paper is knit, it will take a while (approximately 45 minutes on Katherine's computer).
-Once these files have been generated during the first knit, the paper will take much less time to knit (approximately 1 minute on Katherine's computer).
+When the manuscript is knit, various files will be generated (such as `data-bullet-explain.rds` and `figure-10-1.png`).
+The first time the manuscript is knit, it will take a while (approximately 45 minutes on Katherine's computer).
+Once these files have been generated during the first knit, the manuscript will take much less time to knit (approximately 1 minute on Katherine's computer).
 
-Follow these instructions to knit the paper:
+Follow these instructions to knit the manuscript:
 
@@
 Install R packages [goodekat/lime](https://github.com/goodekat/lime) and [goodekat/limeaid](https://github.com/goodekat/limeaid) from GitHub using the remotes R package.
-(Note that goodekat/lime is a forked versions of [thomasp85/lime](https://github.com/thomasp85/lime) with minor changes to extract objects for the analysis in the paper.)
+(Note that goodekat/lime is a forked versions of [thomasp85/lime](https://github.com/thomasp85/lime) with minor changes to extract objects for the analysis in the manuscript.)
 
@@
 
-3. Knit paper (via the paper.Rnw file).
+3. Knit manuscript (via the `paper.Rnw` file).
 
@@
 
-The data used in the paper for the bullet comparison examples is described below.
+The data used in the manuscript for the bullet comparison examples is described below.
 
@@
 A dataset with `r dim(bullet_train)[1]` rows and `r dim(bullet_train)[2]` columns that contains comparison features from the Hamby 173 and 252 sets (XXX reference XXX).
+It contains comparisons from `r length(unique(bullet_train$land_id1))` bullet-land signatures with some lands missing due to tank rash or other reasons.
 This dataset is created using the data available at XXX, which contains XXX (add more info about the comparisons).
-The only changes made to the data from XXX were to remove any lands with tank rash, select only variables of use for the paper, add a case variable, rename `same_source` as `samesource`, and attach the random forest scores associated with the comparisons.
+The only changes made to the data from XXX were to remove any lands with tank rash, select only variables of use for the manuscript, add a case variable, rename `same_source` as `samesource`, and attach the random forest scores associated with the comparisons.
 The variables in the data are as follows:
@@
 - `r names(bullet_train)[13]` = indicator variable specifying whether the two bullet-lands are a match
-- `r names(bullet_train)[14]` = the random forest score associated with the comparison in support of a match
 
@@
 - `r names(bullet_test)[13]` = indicator variable specifying whether the two bullet-lands are a match
-- `r names(bullet_test)[14]` = the random forest score associated with the comparison in support of a match
 
@@
 The text sizes are either set to 7 pt or 5.5 pt (Helvetica) as indicated by the table below.
-Note that the text in the paper is 9 pt (Times) and a similar approach was used to ensure that line sizes are larger than 0.5 pt.
+Note that the text in the manuscript is 9 pt (Times) and a similar approach was used to ensure that line sizes are larger than 0.5 pt.
 

### 2020-09-16 code/data-preparation.Rmd
added a missed r package
updated data files in preparation for training the random forest model

@@
 library(tidyr)
+library(zip)
 ```
@@
 
-Create a new version of the data with the land IDs separated into separate variables for an analysis of the number of observations in this data and reorder the barrels:
+Determine the number of total study-barrel-bullet-lands in the data:
 
 ```{r}
-bullet_train_raw_expanded <-
-  bullet_train_raw %>%
-  separate(land_id1,
-           sep = "-",
-           into = c("study1", "barrel1", "bullet1", "land1")) %>%
-  separate(land_id2,
-           sep = "-",
-           into = c("study2", "barrel2", "bullet2", "land2")) %>%
-  mutate(barrel1 = fct_relevel(barrel1, paste0("Br", 1:10), "BrUnk"),
-         barrel2 = fct_relevel(barrel2, paste0("Br", 1:10), "BrUnk"))
+length(unique(bullet_train_raw %>% pull(land_id1)))
 ```
 
-The number of comparisons within the two studies are included below:
+Determine the number of total study-barrel-bullet-lands in the data when observations with tank rash are excluded:
 
 ```{r}
-table(
-  bullet_train_raw_expanded$study1,
-  bullet_train_raw_expanded$study2
-)
+length(unique(bullet_train_raw %>% filter(flag == FALSE) %>% pull(land_id1)))
+```
+
+There is only one less land id when the cases with tank rash are excluded.
+The code below shows that this case is `Hamby252-Br9-B2-L4` since there are no rows in the filtered data without `Hamby252-Br9-B2-L4` as one of the land ids:
+
+```{r}
+length(unique(
+  bullet_train_raw %>% filter(flag == TRUE) %>% filter(
+    land_id1 != "Hamby252-Br9-B2-L4",
+    land_id2 != "Hamby252-Br9-B2-L4"
+  ) %>% pull(land_id1)
+))
 ```
@@
 
-**XXX Need to determine why the number of dimensions do not match. XXX**
+The discrepancy in the number of observations has led us to decide to train a new random forest model using the data provided by Heike where `flag == FALSE` (observations known to not have tank rash).
+The code for the random forest can be found in the document `paper.Rnw`.
 
@@
   select(case, land_id1, land_id2, everything())
-```
-
-Add a variable to the training data with the random forest probability in support of a match using the random forest model `rtrees` from `bulletxtrctr`:
-
-```{r}
-bullet_features <- rownames(bulletxtrctr::rtrees$importance)
-bullet_train$rfscore <- 
-  bulletxtrctr::rtrees %>%
-  predict(bullet_train %>% select(all_of(bullet_features)), type = "prob") %>%
-  data.frame() %>%
-  pull(TRUE.)
 ```
@@
   # Remove unneeded variables
-  select(-bullet_score,-land1,-land2,-aligned,-striae,-features) %>%
+  select(-bullet_score,-land1,-land2,-aligned,-striae,-features,-rfscore) %>%
   # Rename bullet and land variables
@@
   # Order the variables as desired
-  select(study, set, bullet1, land1, bullet2, land2, all_of(rf_features), rfscore, samesource)
+  select(study, set, bullet1, land1, bullet2, land2, all_of(rf_features), samesource)
 
@@
   # Order the variables as desired
-  select(study, set, bullet1, land1, bullet2, land2, all_of(rf_features), rfscore, samesource)
+  select(study, set, bullet1, land1, bullet2, land2, all_of(rf_features), samesource)
 ```
@@
 hamby224_test <- hamby224_test_extra_vars %>%
-  select(case, land_id1, land_id2, all_of(rf_features), samesource, rfscore)
+  select(case, land_id1, land_id2, all_of(rf_features), samesource)
 ```

### 2020-09-16 code/data-preparation.Rmd
moved the compression of all raw data and static figure to the same document and resaved all data

@@
 ```{r eval = FALSE}
-zip(
-  zipfile = "../data/raw/hamby-comparisons.csv.zip", 
-  files = "../data/raw/hamby-comparisons.csv"
-)
 zip(
@@
 zip(
-  zipfile = "../data/raw/h224-set1-features.rds.zip", 
-  files = "../data/raw/h224-set1-features.rds"
-)
-zip(
-  zipfile = "../data/raw/h224-set11-features.rds.zip", 
-  files = "../data/raw/h224-set11-features.rds"
-)
-zip(
   zipfile = "../data/bullet-test.csv.zip", 
@@
 zip(
-  zipfile = "../data/raw/signatures.rds.zip", 
-  files = "../data/raw/signatures.rds"
-)
-zip(
   zipfile = "../data/example-signatures.csv.zip", 

### 2020-09-16 code/raw-file-compression.Rmd
moved the compression of all raw data and static figure to the same document and resaved all data

---
title: "Compression of Raw Files"
author: "Katherine Goode"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, eval = FALSE)
```

This document contains code for compressing the raw files (data and figure) associated with the manuscript.

```{r}
# Load packages
library(zip)
```

Save the bullet image used in the paper as a zip file:

```{r}
zip(
  zipfile = "../figure-static/figure-08-1.png.zip",
  files =  "../figure-static/figure-08-1.png"
)
```

Save the raw bullet training data files as zip files:

```{r}
zip(
  zipfile = "../data/raw/hamby-comparisons.csv.zip", 
  files = "../data/raw/hamby-comparisons.csv"
)
```

Save the raw bullet testing data files as zip files:

```{r}
zip(
  zipfile = "../data/raw/h224-set1-features.rds.zip", 
  files = "../data/raw/h224-set1-features.rds"
)
zip(
  zipfile = "../data/raw/h224-set11-features.rds.zip", 
  files = "../data/raw/h224-set11-features.rds"
)
```

Save the raw data with an example of matching signatures as a zip file:

```{r}
zip(
  zipfile = "../data/raw/signatures.rds.zip", 
  files = "../data/raw/signatures.rds"
)
```

### 2020-09-16 code/data-preparation.Rmd
changed code to work with the zip files of the data

@@
 library(randomForest)
+library(readr)
 library(stringr)
@@
 
-Load the raw version of the Hamby 172 and 252 bullet comparison data:
+Load the raw version of the Hamby 172 and 252 bullet comparison data (provided by Heike and CSAFE):
 
 ```{r}
-bullet_train_raw = read.csv("../data/raw/hamby-comparisons.csv")
+bullet_train_raw = read_csv("../data/raw/hamby-comparisons.csv.zip")
 ```
@@
 
-Load in the raw Hamby 224 datasets (sets 1 and 11):
+Load in the raw Hamby 224 datasets (sets 1 and 11; provided by Heike and CSAFE):
 
 ```{r}
+if (!file.exists("../data/raw/h224-set1-features.rds")) unzip("../data/raw/h224-set1-features.rds.zip")
+if (!file.exists("../data/raw/h224-set11-features.rds")) unzip("../data/raw/h224-set11-features.rds.zip")
+
 hamby224_set1 <- readRDS("../data/raw/h224-set1-features.rds")
@@
 
-The following code trims the data provided by Heike of two matching bullet-land signatures
+The following code trims the data provided by Heike of two matching bullet-land signatures.
 
-Import the data:
+Import the data (provided by Heike and CSAFE):
 
 ```{r}
+if (!file.exists("../data/raw/signatures.rds")) unzip("../data/raw/signatures.rds.zip")
 signatures <- readRDS("../data/raw/signatures.rds")

### 2020-09-16 code/03-submission-steps.Rmd
small changes

--- 2020-09-15 code/submission-steps.Rmd
@@
 
-**NOTE** The knitr option of `eval = FALSE` has been set for this document, so all code must be run manually from withing the Rmd file. This is done to be safe about not deleting or replacing files.
+**NOTE** The knitr option of `eval = FALSE` has been set for this document, so all code must be run manually from within the Rmd file. This is done to be safe about not deleting or replacing files.
 
-1. Delete all files generated by `paper.Rnw` and current existing submission folder using the code below.
+0. Run the code if desired to update the saved state of the project R package versions. Use with caution!
+
+    ```{r}
+    # Save the r package versions
+    renv::snapshot()
+    ```
+
+1. Delete all data files created from the raw versions, files generated by `paper.Rnw`, and current existing submission folder using the code below.
 
@@
     file.remove("../data/bullet-lime.rds")
+    file.remove("../data/bullet-rf.rds")
+    file.remove("../data/bullet-test.csv")
+    file.remove("../data/bullet-test.csv.zip")
+    file.remove("../data/bullet-train.csv")
+    file.remove("../data/bullet-train.csv.zip")
+    file.remove("../data/example-signatures.csv")
+    file.remove("../data/example-signatures.csv.zip")
     file.remove("../data/sine-lime-explain.rds")
+    file.remove("../figure-static/figure-08-1.eps")
+    file.remove("../figure-static/figure-08-1.png.zip")
     file.remove("../figure-static/figure-10-1.eps")
@@
 
-2. Knit the file `paper.Rnw`.
+2. Manually run the code in `code/01-raw-file-compression.Rmd` to compress the raw versions of the data files and static figure. Also, knit the file to make sure the html version is up to date.
 
-3. Run the following code to move all files necessary to the submission folder.
+3.
+Manually run the code in `code/02-data-preparation.Rmd` to create the versions of the data to be used in the manuscript and submitted with the manuscript.
+Also, knit the file to make sure the html version is up to date.
+
+4. Knit the file `paper.Rnw`.
+
+5. Run the following code to move all files necessary to the submission folder.
 
@@
 
-4.
+6.
 Manually delete `figure/` and `figure-static/` from the figure file paths in `paper.tex`.
@@
 
-5. Compile the file `paper.tex` (using LaTex, then bibTex, then LaTeX twice more) to make sure it compiles correctly (especially references).
+7. Compile the file `paper.tex` (using LaTex, then bibTex, then LaTeX twice more) to make sure it compiles correctly (especially references).
 
-6. Besides for `paper.pdf`, delete all other files generated when `paper.tex` was compiled. This includes other paper files and pdf versions of the figures.
+8. Besides for `paper.pdf`, delete all other files generated when `paper.tex` was compiled. This includes other paper files and pdf versions of the figures.
 
@@
 
-7. Upload all remaining files in the submission folder to the ASA Data Science Journal submission page which should be:
+9. Upload all remaining files in the submission folder to the ASA Data Science Journal submission page which should be:
 

### 2020-09-16 paper.Rnw
reran paper with my random forest model

@@
 bullet_test <- readr::read_csv("data/bullet-test.csv.zip")
+@
+
+<<bullet-random-forest>>=
 
@@
 bullet_features <- rownames(bulletxtrctr::rtrees$importance)
+
+# Create a path where the random forest will be saved
+bullet_rf_file = "data/bullet-rf.rds"
+if (file.exists(bullet_rf_file)) {
+  # Load the random forest
+  bullet_rf = readRDS(bullet_rf_file)
+} else {
+  # Fit the random forest to mimic rtrees
+  set.seed(20160104)
+  bullet_rf <-
+    randomForest(
+      y = factor(bullet_train$samesource),
+      x = bullet_train %>% select(all_of(bullet_features)),
+      ntree = bulletxtrctr::rtrees$ntree,
+      mtry = bulletxtrctr::rtrees$mtry
+    )
+  #Save the random forest
+  saveRDS(bullet_rf, bullet_rf_file)
+}
 
@@
   data.frame(
-    feature = rownames(bulletxtrctr::rtrees$importance),
-    MeanDecreaseGini = bulletxtrctr::rtrees$importance
+    feature = rownames(bullet_rf$importance),
+    MeanDecreaseGini = bullet_rf$importance
   ) %>%
@@
   mutate(feature = factor(feature, levels = bullet_features_ordered$feature))
+
+# Add a variables to training and testing data with random forest predictions
+bullet_train$rfscore = predict(bullet_rf, type = "prob")[,2]
+bullet_test$rfscore = predict(bullet_rf, bullet_test %>% select(bullet_features), type = "prob")[,2]
+
 @
@@
     na.omit() %>%
+    arrange(rfscore) %>%
     ggplot(aes(color = rfscore)) +
@@
       na.omit(),
-    model = bulletxtrctr::rtrees,
+    model = bullet_rf,
     label = as.character(TRUE),
@@
     select(all_of(bullet_features)),
-  model = bulletxtrctr::rtrees,
+  model = bullet_rf,
   label = as.character(TRUE),
@@
       "Non-Match" = "FALSE"
+    )) %>%
+    mutate(samesource = fct_relevel(
+      samesource, 
+      "Non-Match",
+      "Match"
     )) %>%

### 2020-09-16 paper.tex
reorganized again and wrote code for moving the files to the submission folder
reknit the paper after updating test data
reran paper with my random forest model

@@
 \end{figure*}
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
+\begin{verbatim}
+## [16:31:27] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:27] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:27] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:27] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:27] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:27] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:27] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:27] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:27] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:27] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:27] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:27] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:27] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:27] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:27] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:27] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:28] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:28] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:28] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:28] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:28] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:28] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:28] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:28] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:28] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:28] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:28] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:28] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:28] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:28] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:28] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:28] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:29] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:29] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:29] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:29] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:29] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:29] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:29] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:29] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:29] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:29] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:29] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:29] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:29] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:29] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:29] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:30] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:30] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:30] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:30] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:30] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:30] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:30] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:30] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:30] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:30] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:30] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:30] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:30] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:30] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:30] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:30] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:31] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:31] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:31] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:31] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:31] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:31] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:31] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:31] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:31] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:31] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:31] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:31] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:31] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:31] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:31] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:32] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:32] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:32] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:32] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:32] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:32] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:32] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:32] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:32] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:32] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:32] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:32] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:32] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:32] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:32] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:33] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:33] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:33] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:33] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:33] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:33] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:33] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:46] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:46] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:47] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:47] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:47] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:47] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:47] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:47] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:47] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:47] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:47] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:47] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:47] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:47] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:47] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:48] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:48] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:48] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:48] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:48] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:48] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:48] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:48] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:48] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:48] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:48] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:48] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:48] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:48] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:48] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:48] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:48] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:48] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:49] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:49] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:49] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:49] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:49] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:49] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:49] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:49] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:49] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:49] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:49] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:49] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:49] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:49] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:49] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:49] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:49] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:50] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:50] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:50] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:50] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:50] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:50] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:50] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:50] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:50] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:50] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:50] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:50] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:50] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:50] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:50] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:50] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:50] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:51] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:51] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:51] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:51] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:51] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:51] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:51] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:51] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:51] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:51] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:51] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:51] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:51] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:51] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:51] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:51] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:51] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:52] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:52] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:52] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:52] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:52] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:52] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:52] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:52] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:52] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:52] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:52] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:52] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:52] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:53] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:53] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:31:53] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:08] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:08] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:08] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:08] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:08] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:08] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:08] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:08] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:08] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:08] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:08] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:08] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:08] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:08] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:08] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:08] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:08] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:08] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:09] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:09] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:09] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:09] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:09] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:09] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:09] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:09] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:09] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:09] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:09] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:09] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:09] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:09] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:09] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:09] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:09] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:10] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:10] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:10] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:10] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:10] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:10] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:10] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:10] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:10] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:10] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:10] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:10] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:10] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:11] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:11] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:11] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:11] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:11] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:11] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:11] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:11] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:11] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:11] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:11] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:11] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:11] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:11] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:11] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:11] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:25] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:25] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:25] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:25] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:25] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:25] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:25] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:25] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:25] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:25] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:25] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:26] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:26] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:26] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:26] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:26] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:26] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:26] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:26] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:27] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:27] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:27] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:27] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:27] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:27] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:27] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:27] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:27] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:27] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:27] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:27] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:27] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:28] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:28] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:28] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:28] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:28] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:28] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:28] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:28] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:28] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:28] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:28] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:28] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:28] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:28] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:28] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:29] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:29] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:29] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:29] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:29] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:29] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:29] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:29] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:29] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:29] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:29] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:29] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:29] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:30] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:30] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:30] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:30] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:30] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:30] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:30] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:30] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:30] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:30] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:31] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:31] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:31] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:31] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:31] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:31] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:31] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:31] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:31] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:31] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:31] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:31] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:31] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:31] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:31] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:32] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:32] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:32] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:32] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:32] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:32] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:32] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:32] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:32] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:32] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:45] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:46] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:46] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:46] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:46] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:46] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:46] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:46] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:46] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:46] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:46] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:46] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:46] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:46] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:46] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:46] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:47] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:47] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:47] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:47] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:47] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:47] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:47] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:47] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:47] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:47] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:47] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:47] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:47] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:47] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:47] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:47] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:47] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:48] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:48] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:48] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:48] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:48] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:48] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:48] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:48] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:48] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:48] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:48] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:48] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:48] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:48] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:48] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:48] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:48] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:49] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:49] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:49] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:49] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:49] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:49] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:49] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:49] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:49] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:49] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:49] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:49] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:49] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:49] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:49] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:49] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:49] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:49] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:50] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:50] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:50] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:50] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:50] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:50] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:50] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:50] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:50] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:50] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:50] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:50] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:50] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:50] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:50] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:50] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:50] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:50] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:51] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:51] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:51] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:51] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:51] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:51] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:51] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:51] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:51] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:51] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:51] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:51] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:51] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:32:51] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:04] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:04] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:04] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:08] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:08] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:08] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:08] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:08] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:08] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:08] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:08] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:08] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:08] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:08] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:08] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:08] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:08] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:08] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:08] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:08] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:08] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:08] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:09] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:09] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:09] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:09] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:09] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:09] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:09] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:09] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:09] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:09] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:09] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:09] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:09] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:09] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:09] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:09] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:09] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:09] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:10] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:10] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:10] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:10] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:10] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [16:33:10] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+\end{verbatim}
+\end{kframe}
+\end{knitrout}
 
@@
 
-{\centering \includegraphics[width=2.25in]{figure-08-1}
+{\centering \includegraphics[width=2.25in]{figure-static/figure-08-1}
 
@@
 
-{\centering \includegraphics[width=6.5in]{figure-10-1}
+{\centering \includegraphics[width=6.5in]{figure-static/figure-10-1}
 
@@
 
-We apply the trained random forest model from \citet{hare:2016} to another set of bullets from the Hamby study with 432 rows of land comparisons.
+We apply the trained random forest model from \citet{hare:2016} to another set of bullets from the Hamby study with 364 rows of land comparisons.
 We first consider a global visualization of the relationship between the random forest predictions and the model features with a parallel coordinate plot of the training data (top facet) and testing data (bottom facets) predictions (\autoref{fig:figure-10}).
@@
 \begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-
-{\centering \includegraphics[width=6.25in]{figure/figure-13-1}
-
-}
-
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
+
+{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in `[[<-.data.frame`(`*tmp*`, i, value = c("{}grey50"{}, "{}darkorange"{}: replacement has 2 rows, data has 1}}\end{kframe}
 \end{knitrout}

### 2020-09-16 paper.Rnw
simplified code

@@
     )) %>%
-    mutate(samesource = fct_relevel(
-      samesource, 
-      "Non-Match",
-      "Match"
-    )) %>%
-    pull(samesource) %>%
-    na.omit(), 
+    pull(samesource), 
   order_method = "PCA"

### 2020-09-16 paper.tex
simplified code

--- 2020-09-09 paper.tex
@@
 \begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
 
-{\centering \includegraphics[width=6.25in]{figure/figure-13-1}
-
-}
-
+{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in `[[<-.data.frame`(`*tmp*`, i, value = c("{}grey50"{}, "{}darkorange"{}: replacement has 2 rows, data has 1}}\end{kframe}
 \end{knitrout}

### 2020-09-16 README.Rmd
updated to do list

@@
 - Manuscript
-  - Adjust order of match and non-match in feature heat map
-  - Train a random forest model on prepared training data (make sure to set a seed!) 
-  - Make predictions on test data
-  - Rerun all code in manuscript (check for changes in results)
-  - Update text in manuscript to describe the random forest model process
-  - Update all files in the submission folder
+  - Determine what to do about random forest in paper
 - Submission
   - Edit dataset descriptions in README and add to the readme.txt document for submission
+  - Update all files in the submission folder
   - Upload the files for submission and submit
@@
 When the manuscript is knit, various files will be generated (such as `data-bullet-explain.rds` and `figure-10-1.png`).
-The first time the manuscript is knit, it will take a while (approximately 45 minutes on Katherine's computer).
-Once these files have been generated during the first knit, the manuscript will take much less time to knit (approximately 1 minute on Katherine's computer).
+The first time the manuscript is knit, it will take a while (possibly up to several hours).
+Once these files have been generated during the first knit, the manuscript will take much less time to knit (approximately a few minutes).
 

### 2020-09-16 paper.Rnw
fixed Figure 13 issue

@@
   ) +
-  bullet_eoi_plot_theme
+  bullet_eoi_plot_theme +
+  guides(linetype = guide_legend(override.aes = list(color = c("darkorange"))))
 eoiM_3eb <-

### 2020-09-18 code/02-data-preparation.Rmd
pushing code to save for now (was just about to go on a run - need to improve upon later)

--- 2020-09-16 code/data-preparation.Rmd
@@
 
-The discrepancy in the number of observations has led us to decide to train a new random forest model using the data provided by Heike where `flag == FALSE` (observations known to not have tank rash).
-The code for the random forest can be found in the document `paper.Rnw`.
+Current state of the code used to get to the right number of observations (need to clean up and document better and use in paper):
+
+```{r}
+read_csv("../data/raw/hamby-comparisons.csv.zip") %>%
+  separate(land_id1, into = c("study1", "barrel1", "bullet1", "land1")) %>%
+  separate(land_id2, into = c("study2", "barrel2", "bullet2", "land2")) %>%
+  mutate(barrel1 = str_remove(barrel1, "Br"),
+         bullet1 = str_remove(bullet1, "B"),
+         land1 = str_remove(land1, "L"),
+         barrel2 = str_remove(barrel2, "Br"),
+         bullet2 = str_remove(bullet2, "B"),
+         land2 = str_remove(land2, "L")) %>%
+  mutate(bbl1 = factor(barrel1):factor(bullet1):factor(land1),
+         bbl2 = factor(barrel2):factor(bullet2):factor(land2)) %>%
+  filter(!(bbl1 %in% c("6:2:1", "9:2:4", "Unk:B:2", "Unk:Q:4") | 
+           bbl2 %in% c("6:2:1", "9:2:4", "Unk:B:2", "Unk:Q:4"))) %>%
+  dim()
+```
 

### 2020-09-18 README.Rmd
updated readme

@@
 
-- Manuscript
-  - Determine what to do about random forest in paper
-- Submission
 - Edit dataset descriptions in README and add to the readme.txt document for submission
-  - Update all files in the submission folder
+- Go through all steps in the sumbission steps (one more time)
 - Upload the files for submission and submit
@@
 - `example-signatures.csv.zip` contains signature data from two matching bullet lands that is used to generate a figure in the manuscript.
-- `raw` contains the raw versions of the data files (from Heike and CSAFE) that the above datasets are derived from.
+- `raw` contains the raw versions of the data files (from Heike and CSAFE) that the above datasets are derived from. *Do not alter these files in any way.*
 
@@
 
-The data used in the manuscript for the bullet comparison examples is described below.
+The data used in the manuscript for the bullet comparison examples is described below. Note that this text is also included in the file readme.txt that is submitted with the manuscript.
 
@@
 It contains comparisons from `r length(unique(bullet_train$land_id1))` bullet-land signatures with some lands missing due to tank rash or other reasons.
-This dataset is created using the data available at XXX, which contains XXX (add more info about the comparisons).
+This dataset is created using the data available at XXX, which contains XXX.
 The only changes made to the data from XXX were to remove any lands with tank rash, select only variables of use for the manuscript, add a case variable, rename `same_source` as `samesource`, and attach the random forest scores associated with the comparisons.
@@
 
-- `r names(bullet_train)[1]` = ID number associated with the bullet-land signature comparison
-- `r names(bullet_train)[2]` = ID associated with the first bullet-land in the comparison. The format is 'study - barrel number - bullet number - land number'
-- `r names(bullet_train)[3]` = ID associated with the second bullet-land in the comparison. Again, the format is 'study - barrel number - bullet number - land number'
-- `r names(bullet_train)[4]`, `r names(bullet_train)[5]`, `r names(bullet_train)[6]`, `r names(bullet_train)[7]`, `r names(bullet_train)[8]`, `r names(bullet_train)[9]`, `r names(bullet_train)[10]`, `r names(bullet_train)[11]`, and `r names(bullet_train)[12]` = comparison features of the two bullet-land signatures.
-See XXX for definitions of these features
-- `r names(bullet_train)[13]` = indicator variable specifying whether the two bullet-lands are a match
+- `r names(bullet_train)[1]` = ID number associated with the bullet-land signature comparison.
+- `r names(bullet_train)[2]` = ID associated with the first bullet-land in the comparison. The format is 'study - barrel number - bullet number - land number'.
+- `r names(bullet_train)[3]` = ID associated with the second bullet-land in the comparison. Again, the format is 'study - barrel number - bullet number - land number'.
+- `r names(bullet_train)[4]` = the comparison feature of two signatures of cross correlation.
+- `r names(bullet_train)[5]` = the comparison feature of two signatures of rough correlation.
+- `r names(bullet_train)[6]` = the comparison feature of two signatures of distance.
+- `r names(bullet_train)[7]` = the comparison feature of two signatures of standard deviation of distance.
+- `r names(bullet_train)[8]` = the comparison feature of two signatures of matches.
+- `r names(bullet_train)[9]` = the comparison feature of two signatures of mismatches.
+- `r names(bullet_train)[10]` = the comparison feature of two signatures of consecutively matched striae.
+- `r names(bullet_train)[11]` = the comparison feature of two signatures of non-consecutively matched striae.
+- `r names(bullet_train)[12]` = the comparison feature of two signatures of sum of peaks.
+- `r names(bullet_train)[13]` = indicator variable specifying whether the two bullet-lands are a match.
+- `r names(bullet_train)[14]` = the random forest score associated with the comparison in support of a match.
+
+For further details about the signatures comparison features, see XXX.
 
@@
 
-- `r names(bullet_test)[1]` = ID number associated with the bullet-land signature comparison
-- `r names(bullet_test)[2]` = ID associated with the first bullet-land in the comparison with a format of 'study - set number - bullet number - land number'
-- `r names(bullet_test)[3]` = ID associated with the second bullet-land in the comparison with a format of 'study - set number - bullet number - land number'
-- `r names(bullet_test)[4]`, `r names(bullet_test)[5]`, `r names(bullet_test)[6]`, `r names(bullet_test)[7]`, `r names(bullet_test)[8]`, `r names(bullet_test)[9]`, `r names(bullet_test)[10]`, `r names(bullet_test)[11]`, and `r names(bullet_test)[12]` = comparison features of the two bullet-land signatures.
-See XXX for definitions of these features.
-- `r names(bullet_test)[13]` = indicator variable specifying whether the two bullet-lands are a match
+- `r names(bullet_test)[1]` = ID number associated with the bullet-land signature comparison.
+- `r names(bullet_test)[2]` = ID associated with the first bullet-land in the comparison with a format of 'study - set number - bullet number - land number'.
+- `r names(bullet_test)[3]` = ID associated with the second bullet-land in the comparison with a format of 'study - set number - bullet number - land number'.
+- `r names(bullet_test)[4]` = the comparison feature of two signatures of cross correlation.
+- `r names(bullet_test)[5]` = the comparison feature of two signatures of rough correlation.
+- `r names(bullet_test)[6]` = the comparison feature of two signatures of distance.
+- `r names(bullet_test)[7]` = the comparison feature of two signatures of standard deviation of distance.
+- `r names(bullet_test)[8]` = the comparison feature of two signatures of matches.
+- `r names(bullet_test)[9]` = the comparison feature of two signatures of mismatches.
+- `r names(bullet_test)[10]` = the comparison feature of two signatures of consecutively matched striae.
+- `r names(bullet_test)[11]` = the comparison feature of two signatures of non-consecutively matched striae.
+- `r names(bullet_test)[12]` = the comparison feature of two signatures of sum of peaks.
+- `r names(bullet_test)[13]` = indicator variable specifying whether the two bullet-lands are a match.
+- `r names(bullet_test)[14]` = the random forest score associated with the comparison in support of a match.
+
+For further details about the signatures comparison features, see XXX.
 

### 2020-09-18 code/02-data-preparation.Rmd
updated code and data after figuring out issue with bullet training data

--- 2020-09-16 code/data-preparation.Rmd
@@
 
-The number of observations in the random forest `rtrees` (note that they do not match the number of rows in the above dataset):
+The number of observations in the random forest `rtrees`:
 
@@
 
-The discrepancy in the number of observations has led us to decide to train a new random forest model using the data provided by Heike where `flag == FALSE` (observations known to not have tank rash).
-The code for the random forest can be found in the document `paper.Rnw`.
+The number of rows in the training data with the flagged observations excluded does not match the number of observations used to train `rtrees`.
+In the Hare, Hofmann, and Carriquiry (2017), they describe removing four land impressions that were flagged for quality assessment:
+
+- Barrel 6 Bullet 2-1
+- Barrel 9 Bullet 2-4
+- Unknown Bullet B-2
+- Unknown Bullet Q-4
+
+It is unclear which study these lands correspond to. The code below removes all comparisons that include these barrel, bullet, and land combinations:
+
+```{r}
+bullet_train_filtered <- 
+  bullet_train_raw %>%
+  mutate(bbl1 = str_remove(land_id1, pattern = "Hamby252-|Hamby173-"),
+         bbl2 = str_remove(land_id2, pattern = "Hamby252-|Hamby173-")) %>%
+  filter(!(bbl1 %in% c("Br6-B2-L1", "Br9-B2-L4", "BrUnk-BB-L2", "BrUnk-BQ-L4") | 
+           bbl2 %in% c("Br6-B2-L1", "Br9-B2-L4", "BrUnk-BB-L2", "BrUnk-BQ-L4"))) %>%
+  select(-bbl1, -bbl2) 
+```
+
+The dimensions now agree with the number of observations in `rtrees`:
+
+```{r}
+dim(bullet_train_filtered)
+length(bulletxtrctr::rtrees$predicted) == dim(bullet_train_filtered)[1]
+```
 
@@
 
-Remove any lands with tank rash, select only variables of use for the paper, add a case variable, and rename `same_source` as `samesource`:
+Using the data with the flagged lands removed, select only variables of use for the paper, add a case variable, and rename `same_source` as `samesource`:
 
@@
 bullet_train <- 
-  bullet_train_raw %>%
-  filter(flag == FALSE) %>%
+  bullet_train_filtered %>%
   select(-lag, -abs_lag, -overlap, -signature_length, -flag) %>%
@@
   # Remove unneeded variables
-  select(-bullet_score,-land1,-land2,-aligned,-striae,-features,-rfscore) %>%
+  select(-bullet_score,-land1,-land2,-aligned,-striae,-features) %>%
   # Rename bullet and land variables
@@
   # Order the variables as desired
-  select(study, set, bullet1, land1, bullet2, land2, all_of(rf_features), samesource)
+  select(study, set, bullet1, land1, bullet2, land2, all_of(rf_features), samesource, rfscore)
 
@@
   # Order the variables as desired
-  select(study, set, bullet1, land1, bullet2, land2, all_of(rf_features), samesource)
+  select(study, set, bullet1, land1, bullet2, land2, all_of(rf_features), samesource, rfscore)
 ```
@@
 ```{r}
-hamby224_test_extra_vars <-
+bullet_test_extra_vars <-
   # Join the two data sets
@@
     land_id2 = paste(study, set, bullet2, land2, sep = "-")
-  ) # Leave the extract variables for plotting
+  ) # Leave the extra variables for plotting
 
 # Select and order variables to keep for analysis
-hamby224_test <- hamby224_test_extra_vars %>%
-  select(case, land_id1, land_id2, all_of(rf_features), samesource)
+bullet_test <- bullet_test_extra_vars %>%
+  select(case, land_id1, land_id2, all_of(rf_features), samesource, rfscore)
 ```
@@
 plot_grid(
-  hamby224_test_extra_vars %>%
+  bullet_test_extra_vars %>%
     filter(set == "Set1") %>%
@@
     theme(aspect.ratio = 1),
-  hamby224_test_extra_vars %>%
+  bullet_test_extra_vars %>%
     filter(set == "Set11") %>%
@@
 write.csv(
-  x = hamby224_test, 
+  x = bullet_test, 
   file = "../data/bullet-test.csv", 

### 2020-09-18 code/03-submission-steps.Rmd
updated code and data after figuring out issue with bullet training data

@@
     file.remove("../data/bullet-lime.rds")
-    file.remove("../data/bullet-rf.rds")
     file.remove("../data/bullet-test.csv")
@@
     file.remove("../data/sine-lime-explain.rds")
+    file.remove("../data/raw/h224-set1-features.rds.zip")
+    file.remove("../data/raw/h224-set11-features.rds.zip")
+    file.remove("../data/raw/hamby-comparisons.csv.zip")
+    file.remove("../data/raw/signatures.rds.zip")
     file.remove("../figure-static/figure-08-1.eps")

### 2020-09-18 paper.Rnw
reran paper

--- 2020-09-16 paper.Rnw
@@
 
+# Load the bullet matching training and testing data
+bullet_train <- readr::read_csv("data/bullet-train.csv.zip")
+bullet_test <- readr::read_csv("data/bullet-test.csv.zip")
+
 # Extract the features
 bullet_features <- rownames(bulletxtrctr::rtrees$importance)
-
-# Create a path where the random forest will be saved
-bullet_rf_file = "data/bullet-rf.rds"
-if (file.exists(bullet_rf_file)) {
-  # Load the random forest
-  bullet_rf = readRDS(bullet_rf_file)
-} else {
-  # Fit the random forest to mimic rtrees
-  set.seed(20160104)
-  bullet_rf <-
-    randomForest(
-      y = factor(bullet_train$samesource),
-      x = bullet_train %>% select(all_of(bullet_features)),
-      ntree = bulletxtrctr::rtrees$ntree,
-      mtry = bulletxtrctr::rtrees$mtry
-    )
-  #Save the random forest
-  saveRDS(bullet_rf, bullet_rf_file)
-}
 
@@
   data.frame(
-    feature = rownames(bullet_rf$importance),
-    MeanDecreaseGini = bullet_rf$importance
+    feature = rownames(bulletxtrctr::rtrees$importance),
+    MeanDecreaseGini = bulletxtrctr::rtrees$importance
   ) %>%
@@
   mutate(feature = factor(feature, levels = bullet_features_ordered$feature))
-
-# Add a variables to training and testing data with random forest predictions
-bullet_train$rfscore = predict(bullet_rf, type = "prob")[,2]
-bullet_test$rfscore = predict(bullet_rf, bullet_test %>% select(bullet_features), type = "prob")[,2]
 
@@
     na.omit() %>%
-    arrange(rfscore) %>%
     ggplot(aes(color = rfscore)) +
@@
   bullet_lime_explain_noperms <- apply_lime(
-    train = bullet_train %>% select(all_of(bullet_features)),
+    train = bullet_train %>% 
+      arrange(rfscore) %>% 
+      select(all_of(bullet_features)),
     test = bullet_test %>%
@@
       na.omit(),
-    model = bullet_rf,
+    model = bulletxtrctr::rtrees,
     label = as.character(TRUE),
@@
     select(all_of(bullet_features)),
-  model = bullet_rf,
+  model = bulletxtrctr::rtrees,
   label = as.character(TRUE),
@@
     )) %>%
-    pull(samesource), 
+    pull(samesource) %>%
+    na.omit(),
   order_method = "PCA"

### 2020-09-18 paper.tex
fixed Figure 13 issue
reran paper

@@
 
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
+\begin{verbatim}
+## [10:40:51] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:51] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:51] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:51] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:52] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:52] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:52] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:52] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:52] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:52] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:52] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:52] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:52] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:52] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:52] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:52] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:52] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:53] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:53] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:53] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:53] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:53] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:53] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:53] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:53] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:53] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:53] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:53] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:53] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:53] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:53] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:53] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:54] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:54] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:54] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:54] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:54] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:54] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:54] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:54] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:54] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:54] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:54] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:54] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:54] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:54] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:54] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:55] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:55] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:55] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:55] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:55] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:55] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:55] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:55] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:55] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:55] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:55] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:55] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:55] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:55] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:55] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:56] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:56] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:56] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:56] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:56] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:56] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:56] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:56] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:56] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:56] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:56] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:56] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:56] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:56] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:57] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:57] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:57] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:57] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:57] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:57] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:57] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:57] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:57] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:57] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:57] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:57] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:57] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:57] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:57] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:58] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:58] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:58] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:58] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:58] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:58] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:58] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:58] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:40:58] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:12] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:12] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:12] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:12] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:12] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:12] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:12] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:12] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:12] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:12] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:12] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:12] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:12] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:13] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:13] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:13] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:13] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:13] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:13] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:13] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:13] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:13] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:13] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:13] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:13] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:13] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:13] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:13] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:13] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:14] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:14] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:14] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:14] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:14] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:14] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:14] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:14] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:14] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:14] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:14] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:14] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:14] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:14] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:14] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:14] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:15] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:15] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:15] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:15] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:15] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:15] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:15] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:15] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:15] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:15] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:15] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:15] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:15] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:15] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:15] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:15] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:16] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:16] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:16] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:16] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:16] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:16] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:16] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:16] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:16] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:16] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:16] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:16] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:16] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:16] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:16] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:16] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:17] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:17] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:17] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:17] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:17] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:17] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:17] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:17] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:17] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:17] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:17] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:17] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:17] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:17] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:18] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:18] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:18] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:18] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:18] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:18] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:18] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:18] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:18] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:31] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:31] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:31] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:31] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:31] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:31] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:31] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:31] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:32] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:32] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:32] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:32] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:32] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:32] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:32] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:32] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:32] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:32] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:32] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:32] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:32] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:32] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:32] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:32] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:32] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:32] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:33] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:33] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:33] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:33] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:33] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:33] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:33] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:33] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:33] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:33] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:33] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:33] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:33] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:33] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:33] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:33] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:34] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:34] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:34] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:34] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:34] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:34] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:34] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:34] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:34] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:34] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:34] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:34] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:34] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:34] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:34] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:34] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:34] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:35] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:35] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:35] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:35] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:35] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:35] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:35] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:35] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:35] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:35] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:35] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:35] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:35] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:35] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:35] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:35] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:36] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:36] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:36] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:36] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:36] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:36] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:36] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:36] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:36] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:36] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:36] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:36] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:36] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:36] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:37] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:37] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:37] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:37] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:37] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:37] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:37] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:37] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:37] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:37] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:37] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:50] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:50] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:50] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:50] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:50] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:50] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:50] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:50] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:50] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:51] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:51] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:51] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:51] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:51] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:51] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:51] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:51] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:51] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:51] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:51] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:51] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:51] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:51] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:51] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:51] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:51] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:52] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:52] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:52] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:52] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:52] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:52] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:52] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:52] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:52] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:52] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:52] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:52] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:52] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:52] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:52] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:52] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:53] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:53] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:53] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:53] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:53] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:53] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:53] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:53] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:53] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:53] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:53] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:53] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:53] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:53] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:53] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:53] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:54] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:54] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:54] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:54] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:54] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:54] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:54] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:54] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:54] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:54] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:54] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:54] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:54] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:54] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:54] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:54] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:55] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:55] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:55] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:55] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:55] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:55] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:55] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:55] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:55] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:55] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:55] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:55] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:55] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:56] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:56] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:56] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:56] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:56] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:56] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:56] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:56] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:56] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:56] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:56] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:56] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:41:56] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:09] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:09] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:09] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:09] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:09] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:10] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:10] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:10] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:10] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:10] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:10] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:10] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:10] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:10] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:10] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:10] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:10] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:10] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:10] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:10] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:10] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:10] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:11] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:11] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:11] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:11] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:11] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:11] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:11] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:11] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:11] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:11] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:11] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:11] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:11] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:11] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:11] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:11] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:12] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:12] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:12] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:12] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:12] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:12] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:12] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:12] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:12] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:12] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:12] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:12] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:12] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:12] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:12] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:12] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:12] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:13] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:13] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:13] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:13] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:13] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:13] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:13] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:13] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:13] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:13] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:13] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:13] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:13] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:13] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:13] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:13] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:14] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:14] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:14] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:14] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:14] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:14] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:14] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:14] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:14] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:14] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:14] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:14] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:14] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:14] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:14] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:14] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:14] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:15] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:15] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:15] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:15] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:15] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:15] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:15] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:15] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:15] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:15] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:15] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:15] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:28] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:28] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:28] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:28] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:29] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:29] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:29] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:29] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:29] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:29] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:29] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:29] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:29] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:29] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:29] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:29] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:29] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:29] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:29] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:29] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:29] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:29] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:30] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:30] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:30] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:30] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:30] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:30] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:30] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:30] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:30] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:30] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:30] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:30] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:30] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:30] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:30] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:30] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:31] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:31] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:31] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:31] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:31] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:31] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:31] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:31] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:31] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:31] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:31] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:31] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:31] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:31] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:31] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:31] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:31] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:32] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:32] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:32] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:32] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:32] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:32] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:32] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:32] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:32] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:32] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:32] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:32] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:32] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:32] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:32] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:32] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:32] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:33] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:33] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:33] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:33] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:33] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:33] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:33] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:33] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:33] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:33] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:33] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:33] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:33] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:33] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:33] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:33] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:34] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:34] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:34] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:34] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:34] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:34] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:34] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:34] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:34] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:34] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:34] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [10:42:34] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+\end{verbatim}
+\end{kframe}
+\end{knitrout}
+
 In this section, we introduce three visual diagnostic plots for the assessment of LIME.
@@
 \begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
-
-{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in `[[<-.data.frame`(`*tmp*`, i, value = c("{}grey50"{}, "{}darkorange"{}: replacement has 2 rows, data has 1}}\end{kframe}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+
+{\centering \includegraphics[width=6.25in]{figure/figure-13-1}
+
+}
+
 \end{knitrout}

### 2020-09-18 paper.Rnw
one small change to code in paper (removed unnecessary line) and reran everything

@@
     train = bullet_train %>%
-      arrange(rfscore) %>% 
       select(all_of(bullet_features)),

### 2020-09-18 paper.tex
one small change to code in paper (removed unnecessary line) and reran everything

--- 2020-09-16 paper.tex
@@
 
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
+\begin{verbatim}
+## [11:58:03] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:03] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:03] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:03] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:03] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:03] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:03] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:03] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:03] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:03] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:04] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:04] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:04] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:04] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:04] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:04] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:04] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:04] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:04] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:04] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:04] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:04] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:04] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:04] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:04] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:04] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:04] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:08] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:08] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:08] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:08] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:08] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:08] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:08] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:08] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:08] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:08] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:08] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:08] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:08] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:08] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:08] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:08] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:09] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:09] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:09] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:09] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:09] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:09] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:09] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:09] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:09] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:09] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:09] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:23] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:23] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:23] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:23] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:25] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:25] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:25] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:25] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:25] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:25] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:25] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:25] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:25] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:25] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:25] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:25] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:25] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:25] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:25] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:25] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:25] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:25] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:26] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:26] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:26] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:26] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:26] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:26] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:26] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:26] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:26] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:26] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:26] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:26] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:26] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:26] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:26] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:26] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:26] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:26] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:27] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:27] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:27] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:27] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:27] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:27] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:27] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:27] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:27] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:27] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:27] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:27] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:27] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:27] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:27] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:27] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:27] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:27] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:28] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:28] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:28] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:28] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:28] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:28] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:28] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:28] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:28] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:28] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:28] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:28] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:28] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:28] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:28] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:29] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:29] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:29] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:29] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:29] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:29] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:29] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:29] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:29] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:42] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:42] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:43] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:43] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:43] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:43] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:43] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:43] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:43] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:43] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:43] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:43] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:43] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:43] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:43] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:43] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:43] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:43] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:43] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:43] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:44] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:44] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:44] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:44] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:44] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:44] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:44] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:44] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:44] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:44] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:44] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:44] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:44] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:44] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:44] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:44] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:44] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:44] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:44] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:45] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:45] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:45] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:45] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:45] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:45] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:45] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:45] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:45] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:45] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:45] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:45] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:45] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:45] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:45] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:45] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:45] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:45] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:46] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:46] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:46] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:46] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:46] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:46] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:46] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:46] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:46] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:46] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:46] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:46] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:46] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:46] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:46] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:46] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:46] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:46] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:47] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:47] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:47] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:47] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:47] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:47] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:47] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:47] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:47] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:47] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:47] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:47] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:47] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:47] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:48] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:48] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:48] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:48] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:48] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:48] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:48] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:48] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:48] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:48] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:48] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:01] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:01] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:01] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:01] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:01] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:01] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:01] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:02] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:02] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:02] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:02] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:02] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:02] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:02] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:02] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:02] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:02] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:02] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:02] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:02] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:02] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:02] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:02] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:02] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:02] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:03] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:03] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:03] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:03] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:03] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:03] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:03] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:03] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:03] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:03] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:03] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:03] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:03] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:03] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:03] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:03] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:03] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:04] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:04] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:04] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:04] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:04] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:04] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:04] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:04] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:04] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:04] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:04] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:04] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:04] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:04] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:04] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:04] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:04] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:04] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:19] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:19] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:19] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:19] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:19] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:19] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:19] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:19] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:19] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:19] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:19] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:20] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:20] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:20] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:20] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:20] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:20] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:20] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:20] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:20] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:20] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:20] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:20] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:20] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:20] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:20] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:20] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:20] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:20] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:21] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:21] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:21] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:21] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:21] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:21] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:21] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:21] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:21] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:21] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:21] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:21] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:21] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:21] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:21] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:21] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:21] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:22] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:22] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:22] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:22] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:22] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:22] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:22] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:22] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:22] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:22] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:22] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:22] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:22] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:22] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:22] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:22] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:22] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:23] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:23] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:23] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:23] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:23] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:23] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:23] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:23] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:23] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:23] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:23] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:23] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:23] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:23] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:23] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:23] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:23] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:23] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:25] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:38] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:38] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:38] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:38] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:38] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:38] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:38] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:38] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:38] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:38] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:38] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:39] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:39] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:39] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:39] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:39] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:39] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:39] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:39] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:39] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:39] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:39] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:39] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:39] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:39] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:39] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:39] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:39] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:39] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:40] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:40] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:40] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:40] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:40] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:40] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:40] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:40] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:40] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:40] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:40] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:40] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:40] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:40] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:40] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:40] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:40] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:40] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:41] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:41] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:41] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:41] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:41] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:41] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:41] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:41] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:41] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:41] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:41] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:41] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:41] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:41] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:41] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:41] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:41] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:42] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:42] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:42] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:42] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:42] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:42] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:42] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:42] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:42] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:42] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:42] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:42] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:42] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:42] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:42] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:42] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:42] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:43] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:43] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:43] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:43] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:43] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:43] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:43] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:43] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:43] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:43] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:43] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:43] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:43] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:43] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:43] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:43] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:43] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:43] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:44] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+\end{verbatim}
+\end{kframe}
+\end{knitrout}
+
 In this section, we introduce three visual diagnostic plots for the assessment of LIME.

### 2020-09-18 submission/paper.tex
reorganized again and wrote code for moving the files to the submission folder
added updated versions of the submission files
one small change to code in paper (removed unnecessary line) and reran everything

--- 2020-09-09 paper.tex
@@
 \end{figure*}
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
+\begin{verbatim}
+## [11:58:03] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:03] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:03] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:03] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:03] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:03] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:03] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:03] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:03] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:03] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:04] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:04] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:04] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:04] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:04] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:04] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:04] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:04] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:04] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:04] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:04] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:04] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:04] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:04] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:04] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:04] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:04] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:08] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:08] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:08] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:08] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:08] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:08] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:08] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:08] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:08] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:08] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:08] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:08] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:08] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:08] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:08] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:08] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:09] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:09] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:09] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:09] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:09] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:09] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:09] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:09] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:09] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:09] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:09] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:23] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:23] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:23] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:23] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:25] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:25] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:25] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:25] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:25] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:25] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:25] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:25] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:25] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:25] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:25] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:25] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:25] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:25] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:25] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:25] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:25] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:25] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:26] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:26] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:26] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:26] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:26] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:26] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:26] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:26] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:26] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:26] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:26] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:26] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:26] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:26] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:26] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:26] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:26] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:26] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:27] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:27] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:27] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:27] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:27] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:27] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:27] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:27] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:27] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:27] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:27] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:27] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:27] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:27] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:27] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:27] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:27] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:27] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:28] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:28] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:28] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:28] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:28] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:28] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:28] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:28] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:28] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:28] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:28] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:28] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:28] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:28] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:28] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:29] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:29] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:29] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:29] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:29] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:29] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:29] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:29] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:29] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:42] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:42] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:43] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:43] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:43] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:43] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:43] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:43] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:43] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:43] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:43] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:43] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:43] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:43] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:43] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:43] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:43] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:43] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:43] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:43] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:44] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:44] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:44] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:44] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:44] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:44] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:44] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:44] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:44] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:44] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:44] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:44] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:44] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:44] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:44] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:44] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:44] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:44] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:44] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:45] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:45] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:45] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:45] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:45] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:45] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:45] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:45] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:45] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:45] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:45] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:45] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:45] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:45] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:45] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:45] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:45] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:45] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:46] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:46] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:46] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:46] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:46] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:46] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:46] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:46] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:46] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:46] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:46] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:46] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:46] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:46] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:46] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:46] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:46] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:46] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:47] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:47] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:47] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:47] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:47] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:47] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:47] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:47] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:47] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:47] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:47] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:47] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:47] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:47] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:48] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:48] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:48] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:48] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:48] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:48] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:48] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:48] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:48] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:48] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:58:48] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:01] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:01] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:01] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:01] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:01] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:01] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:01] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:02] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:02] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:02] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:02] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:02] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:02] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:02] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:02] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:02] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:02] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:02] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:02] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:02] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:02] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:02] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:02] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:02] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:02] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:03] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:03] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:03] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:03] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:03] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:03] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:03] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:03] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:03] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:03] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:03] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:03] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:03] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:03] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:03] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:03] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:03] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:04] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:04] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:04] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:04] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:04] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:04] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:04] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:04] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:04] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:04] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:04] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:04] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:04] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:04] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:04] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:04] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:04] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:04] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:19] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:19] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:19] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:19] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:19] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:19] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:19] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:19] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:19] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:19] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:19] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:20] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:20] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:20] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:20] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:20] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:20] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:20] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:20] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:20] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:20] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:20] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:20] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:20] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:20] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:20] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:20] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:20] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:20] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:21] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:21] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:21] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:21] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:21] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:21] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:21] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:21] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:21] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:21] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:21] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:21] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:21] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:21] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:21] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:21] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:21] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:22] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:22] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:22] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:22] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:22] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:22] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:22] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:22] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:22] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:22] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:22] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:22] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:22] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:22] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:22] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:22] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:22] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:23] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:23] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:23] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:23] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:23] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:23] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:23] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:23] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:23] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:23] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:23] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:23] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:23] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:23] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:23] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:23] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:23] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:23] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:25] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:38] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:38] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:38] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:38] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:38] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:38] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:38] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:38] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:38] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:38] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:38] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:39] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:39] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:39] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:39] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:39] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:39] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:39] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:39] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:39] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:39] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:39] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:39] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:39] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:39] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:39] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:39] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:39] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:39] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:40] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:40] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:40] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:40] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:40] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:40] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:40] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:40] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:40] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:40] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:40] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:40] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:40] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:40] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:40] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:40] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:40] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:40] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:41] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:41] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:41] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:41] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:41] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:41] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:41] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:41] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:41] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:41] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:41] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:41] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:41] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:41] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:41] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:41] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:41] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:42] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:42] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:42] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:42] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:42] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:42] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:42] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:42] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:42] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:42] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:42] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:42] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:42] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:42] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:42] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:42] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:42] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:43] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:43] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:43] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:43] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:43] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:43] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:43] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:43] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:43] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:43] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:43] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:43] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:43] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:43] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:43] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:43] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:43] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:43] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [11:59:44] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+\end{verbatim}
+\end{kframe}
+\end{knitrout}
 

### 2020-09-18 README.Rmd
updated to do list

@@
 - Edit dataset descriptions in README and add to the readme.txt document for submission
-- Go through all steps in the sumbission steps (one more time)
 - Upload the files for submission and submit

### 2020-09-20 code/02-data-preparation.Rmd
added figure comparing rtrees predictions to our predictions

@@
 length(bulletxtrctr::rtrees$predicted) == dim(bullet_train_filtered)[1]
+```
+
+Extracting the predictions on the training data from `rtrees` and using `rtrees` to make predictions on the filtered data:
+
+```{r}
+rtrees_pred = predict(bulletxtrctr::rtrees, type = "prob")[,2]
+new_pred = predict(bulletxtrctr::rtrees, bullet_train_filtered %>% select(rownames(bulletxtrctr::rtrees$importance)), type = "prob")[,2]
+```
+
+Plot comparing the two predictions:
+
+```{r}
+data.frame(rtrees_pred = sort(rtrees_pred), new_pred = sort(new_pred)) %>%
+  ggplot(aes(rtrees_pred, new_pred)) + 
+  geom_point()
 ```

### 2020-09-21 code/02-data-preparation.Rmd
updated figure

@@
 new_pred = predict(bulletxtrctr::rtrees, bullet_train_filtered %>% select(rownames(bulletxtrctr::rtrees$importance)), type = "prob")[,2]
+new_pred_full = predict(bulletxtrctr::rtrees, bullet_train_raw %>% select(rownames(bulletxtrctr::rtrees$importance)), type = "prob")[,2]
 ```
@@
   geom_point()
+```
+
+Plot showing distributions of predictions from `rtrees` and new predictions made on full training data:
+
+```{r}
+data.frame(data = c(rep("rtrees", length(rtrees_pred)), rep("new predictions on full data", length(new_pred_full))), pred = c(rtrees_pred, new_pred_full)) %>%
+  ggplot(aes(x = pred, fill = data)) + 
+  geom_density(alpha = 0.75)
+```
+
+```{r}
+data.frame(rtrees_pred = sort(rtrees_pred), new_pred = sort(new_pred))
 ```

### 2020-09-21 code/02-data-preparation.Rmd
fixed typo

@@
 new_pred = predict(bulletxtrctr::rtrees, bullet_train_filtered %>% select(rownames(bulletxtrctr::rtrees$importance)), type = "prob")[,2]
-new_pred_full = predict(bulletxtrctr::rtrees, bullet_train_raw %>% select(rownames(bulletxtrctr::rtrees$importance)), type = "prob")[,2]
+new_pred_full = predict(bulletxtrctr::rtrees, bullet_train_raw %>% select(rownames(bulletxtrctr::rtrees$importance)[]), type = "prob")[,2]
 ```
@@
   geom_density(alpha = 0.75)
-```
-
-```{r}
-data.frame(rtrees_pred = sort(rtrees_pred), new_pred = sort(new_pred))
 ```

### 2020-09-21 code/02-data-preparation.Rmd
removed some extra spaces

@@
 ```
+
 Preparing the data from sets 1 and 11 for analysis:

### 2020-09-23 code/02-data-preparation.Rmd
trying a new filtering method

@@
 
+The dimensions of the raw data:
+
+```{r}
+bullet_train_raw %>% dim()
+```
+
 The dimension of the data once the observations with tank rash (`flag != FALSE`) are removed:
@@
 
+The code below removes observations based on Eric Hare's code (available [here](ttps://github.com/erichare/imaging-paper/blob/master/code/full_run.R)), which he thinks may be the code used to train `rtrees`:
+
+```{r}
+bullet_train_eric_filter <- 
+  bullet_train_raw %>%
+  separate(col = "land_id1", into = c("study1", "barrel1", "bullet1", "land1")) %>%
+  separate(col = "land_id2", into = c("study2", "barrel2", "bullet2", "land2")) %>%
+  filter(study1 != "Hamby173" | bullet1 != "BE") %>%
+  filter(study2 != "Hamby173" | bullet2 != "BE")
+
+# Eric's code for reference:
+# filter(study.y != "Hamby44" | barrel.y != "E") %>%
+# filter(study.x != "Hamby44" | barrel.x != "E") %>%
+```
+
+Here, the dimensions to not agree with the number of observations in `rtrees`:
+
+```{r}
+dim(bullet_train_eric_filter)
+length(bulletxtrctr::rtrees$predicted) == dim(bullet_train_eric_filter)[1]
+```
+
 Extracting the predictions on the training data from `rtrees` and using `rtrees` to make predictions on the filtered data:
@@
 rtrees_pred = predict(bulletxtrctr::rtrees, type = "prob")[,2]
-new_pred = predict(bulletxtrctr::rtrees, bullet_train_filtered %>% select(rownames(bulletxtrctr::rtrees$importance)), type = "prob")[,2]
-new_pred_full = predict(bulletxtrctr::rtrees, bullet_train_raw %>% select(rownames(bulletxtrctr::rtrees$importance)[]), type = "prob")[,2]
+
+new_pred = predict(bulletxtrctr::rtrees, 
+                   bullet_train_filtered %>% 
+                     select(rownames(bulletxtrctr::rtrees$importance)), type = "prob")[,2]
+
+new_pred_full = predict(bulletxtrctr::rtrees, 
+                        bullet_train_raw %>%
+                          select(rownames(bulletxtrctr::rtrees$importance)), type = "prob")[,2]
 ```
@@
 ```{r}
-data.frame(data = c(rep("rtrees", length(rtrees_pred)), rep("new predictions on full data", length(new_pred_full))), pred = c(rtrees_pred, new_pred_full)) %>%
+bulletxtrctr::rtrees$call
+```
+
+```{r}
+data.frame(data = c(rep("rtrees", length(rtrees_pred)), 
+                    rep("new predictions on full data", length(new_pred_full))), pred = c(rtrees_pred, new_pred_full)) %>%
   ggplot(aes(x = pred, fill = data)) + 
   geom_density(alpha = 0.75)
+```
+
+Comparison to the data Eric Hare said was used to fit `rtrees` which has half the number of observations as the number of rtrees predictions:
+
+```{r}
+eric <- read.csv("https://raw.githubusercontent.com/erichare/imaging-paper/master/data/data-25-25/bullet-stats.csv")
+dim(eric)
 ```

### 2020-09-23 code/02-data-preparation.Rmd
added comments about not comparing the random forest predictions

@@
 
-Plot comparing the two predictions:
+Plot comparing the two predictions (we discovered that the `predict` function from random forest returns different results when applied to only the model (out-of-bag predictions) and the training data (regular predictions), so this is not a good way to test for agreement between training data and models):
 
@@
 
-Plot showing distributions of predictions from `rtrees` and new predictions made on full training data:
-
-```{r}
-bulletxtrctr::rtrees$call
-```
+Plot showing distributions of predictions from `rtrees` and new predictions made on full training data (same comment here as above about not being able to use this to determine if we have the correct training data for the model):
 

### 2020-09-23 code/02-data-preparation.Rmd
fixed hyperlink

@@
 
-The code below removes observations based on Eric Hare's code (available [here](ttps://github.com/erichare/imaging-paper/blob/master/code/full_run.R)), which he thinks may be the code used to train `rtrees`:
+The code below removes observations based on Eric Hare's code (available [here](https://github.com/erichare/imaging-paper/blob/master/code/full_run.R)), which he thinks may be the code used to train `rtrees`:
 

### 2020-09-25 code/02-data-preparation.Rmd
removed an extra space
trying to compare the data

@@
 
+## Comparing Training Datasets
+
+Load the newest training data provided by Heike to determine if the same data:
+
+```{r}
+ccfs_withlands_raw = read.csv("../data/raw/CCFs_withlands.csv")
+```
+
+Adjust the raw data to match the structure of `bullet_train_raw`:
+
+```{r}
+ccfs_withlands_raw_expanded <- 
+  ccfs_withlands_raw %>%
+  rename("study1" = "study.x", "barrel1" = "barrel.x", "bullet1" = "bullet.x", "land1" = "land.x",
+         "study2" = "study.y", "barrel2" = "barrel.y", "bullet2" = "bullet.y", "land2" = "land.y") %>%
+  select(
+    study1, barrel1, bullet1, land1, 
+    study2, barrel2, bullet2, land2,
+    all_of(rf_features), 
+    match
+  ) %>%
+  mutate(across(c(study1, barrel1, bullet1, land1, study2, barrel2, bullet2, land2), factor))
+```
+
+```{r}
+bullet_train_raw_expanded <- 
+  bullet_train_raw %>%
+  separate(land_id1, c("study1", "barrel1", "bullet1", "land1")) %>%
+  separate(land_id2, c("study2", "barrel2", "bullet2", "land2")) %>%
+  mutate(across(where(is.character), factor)) %>%
+  mutate(barrel1 = fct_relevel(barrel1, paste0("Br", 1:10)),
+         barrel2 = fct_relevel(barrel2, paste0("Br", 1:10)))
+```
+
+Shows that `Hamby44` needs to be changed to `Hamby173` in `ccfs_withlands`:
+
+```{r fig.width = 10, fig.height = 4, echo = FALSE}
+plot_grid(
+  bullet_train_raw_expanded %>% count(study1, study2) %>%
+    ggplot(aes(
+      x = study1, y = study2, fill = n
+    )) +
+    geom_tile() +
+    theme(aspect.ratio = 1) + 
+    labs(title = "Hamby comparisons data"),
+  ccfs_withlands_raw_expanded %>% count(study1, study2) %>%
+    ggplot(aes(
+      x = study1, y = study2, fill = n
+    )) +
+    geom_tile() +
+    theme(aspect.ratio = 1) +
+    labs(title = "CCFs with lands data")
+)
+```
+
+Shows that lettered barrels need to be changed to `BrUnk` and `Br` added to other barrels in `ccfs_withlands`:
+
+```{r fig.width = 10, fig.height = 4, echo = FALSE}
+plot_grid(
+  bullet_train_raw_expanded %>% count(barrel1, barrel2) %>%
+    ggplot(aes(
+      x = barrel1, y = barrel2, fill = n
+    )) +
+    geom_tile() +
+    theme(aspect.ratio = 1) + 
+    labs(title = "Hamby comparisons data"),
+  ccfs_withlands_raw_expanded %>% count(barrel1, barrel2) %>%
+    ggplot(aes(
+      x = barrel1, y = barrel2, fill = n
+    )) +
+    geom_tile() +
+    theme(aspect.ratio = 1) +
+    labs(title = "CCFs with lands data")
+)
+```
+
+Shows that barrel letters from in `ccfs_withlands` need to be made the bullet and `B` added to all bullets:
+
+```{r fig.width = 10, fig.height = 4, echo = FALSE}
+plot_grid(
+  bullet_train_raw_expanded %>% count(bullet1, bullet2) %>%
+    ggplot(aes(
+      x = bullet1, y = bullet2, fill = n
+    )) +
+    geom_tile() +
+    theme(aspect.ratio = 1) + 
+    labs(title = "Hamby comparisons data"),
+  ccfs_withlands_raw_expanded %>% count(bullet1, bullet2) %>%
+    ggplot(aes(
+      x = bullet1, y = bullet2, fill = n
+    )) +
+    geom_tile() +
+    theme(aspect.ratio = 1) +
+    labs(title = "CCFs with lands data")
+)
+```
+
+Shows that `L` needs to be added to lands in `ccfs_withlands`:
+
+```{r fig.width = 10, fig.height = 4, echo = FALSE}
+plot_grid(
+  bullet_train_raw_expanded %>% count(land1, land2) %>%
+    ggplot(aes(
+      x = land1, y = land2, fill = n
+    )) +
+    geom_tile() +
+    theme(aspect.ratio = 1) + 
+    labs(title = "Hamby comparisons data"),
+  ccfs_withlands_raw_expanded %>% count(land1, land2) %>%
+    ggplot(aes(
+      x = land1, y = land2, fill = n
+    )) +
+    geom_tile() +
+    theme(aspect.ratio = 1) +
+    labs(title = "CCFs with lands data")
+)
+```
+
+```{r}
+# Determine the letters in barrels
+letters <- 
+  ccfs_withlands_raw_expanded %>%
+  filter(!(barrel1 %in% 1:10)) %>% 
+  pull(barrel1) %>%
+  unique()
+
+letters2 <- 
+  ccfs_withlands_raw_expanded %>%
+  filter(!(barrel2 %in% 1:10)) %>% 
+  pull(barrel2) %>%
+  unique()
+sum(letters != letters2) > 0
+
+ccfs_withlands_expanded <- ccfs_withlands_raw_expanded %>%
+  mutate(
+    study1 = fct_recode(study1, "Hamby173" = "Hamby44"),
+    study2 = fct_recode(study2, "Hamby173" = "Hamby44"),
+    bullet1 = ifelse(barrel1 %in% letters, as.character(barrel1), as.character(bullet1)),
+    barrel1 = ifelse(barrel1 %in% letters, "Unk", barrel1),
+    bullet2 = ifelse(barrel2 %in% letters, as.character(barrel2), as.character(bullet2)),
+    barrel2 = ifelse(barrel2 %in% letters, "Unk", barrel2)
+    ) %>%
+  mutate(
+    study1 = fct_relevel(study1, "Hamby173", "Hamby252"),
+    study2 = fct_relevel(study2, "Hamby173", "Hamby252"),
+    barrel1 = paste0("Br", barrel1),
+    bullet1 = paste0("B", bullet1),
+    land1 = paste0("L", land1),
+    barrel2 = paste0("Br", barrel2),
+    bullet2 = paste0("B", bullet2),
+    land2 = paste0("L", land2)
+  ) %>% 
+  mutate(across(where(is.character), factor)) %>%
+  mutate(barrel1 = fct_relevel(barrel1, paste0("Br", 1:10)),
+         barrel2 = fct_relevel(barrel2, paste0("Br", 1:10)))
+```
+
+The labels agree now but note that :
+
+```{r fig.width = 10, fig.height = 4, echo = FALSE}
+plot_grid(
+  bullet_train_raw_expanded %>% count(study1, study2) %>%
+    ggplot(aes(
+      x = study1, y = study2, fill = n
+    )) +
+    geom_tile() +
+    theme(aspect.ratio = 1) + 
+    labs(title = "Hamby comparisons data"),
+  ccfs_withlands_expanded %>% count(study1, study2) %>%
+    ggplot(aes(
+      x = study1, y = study2, fill = n
+    )) +
+    geom_tile() +
+    theme(aspect.ratio = 1) +
+    labs(title = "CCFs with lands data")
+)
+```
+
+The labels agree now but we are starting to see some differences in the two datasets:
+
+```{r fig.width = 10, fig.height = 4, echo = FALSE}
+plot_grid(
+  bullet_train_raw_expanded %>% count(barrel1, barrel2) %>%
+    ggplot(aes(
+      x = barrel1, y = barrel2, fill = n
+    )) +
+    geom_tile() +
+    theme(aspect.ratio = 1) + 
+    labs(title = "Hamby comparisons data"),
+  ccfs_withlands_expanded %>% count(barrel1, barrel2) %>%
+    ggplot(aes(
+      x = barrel1, y = barrel2, fill = n
+    )) +
+    geom_tile() +
+    theme(aspect.ratio = 1) +
+    labs(title = "CCFs with lands data")
+)
+```
+
+The labels agree now but again, there are apparent differences between datasets:
+
+```{r fig.width = 10, fig.height = 4, echo = FALSE}
+plot_grid(
+  bullet_train_raw_expanded %>% count(bullet1, bullet2) %>%
+    ggplot(aes(
+      x = bullet1, y = bullet2, fill = n
+    )) +
+    geom_tile() +
+    theme(aspect.ratio = 1) + 
+    labs(title = "Hamby comparisons data"),
+  ccfs_withlands_expanded %>% count(bullet1, bullet2) %>%
+    ggplot(aes(
+      x = bullet1, y = bullet2, fill = n
+    )) +
+    geom_tile() +
+    theme(aspect.ratio = 1) +
+    labs(title = "CCFs with lands data")
+)
+```
+
+The labels agree now:
+
+```{r fig.width = 10, fig.height = 4, echo = FALSE}
+plot_grid(
+  bullet_train_raw_expanded %>% count(land1, land2) %>%
+    ggplot(aes(
+      x = land1, y = land2, fill = n
+    )) +
+    geom_tile() +
+    theme(aspect.ratio = 1) + 
+    labs(title = "Hamby comparisons data"),
+  ccfs_withlands_expanded %>% count(land1, land2) %>%
+    ggplot(aes(
+      x = land1, y = land2, fill = n
+    )) +
+    geom_tile() +
+    theme(aspect.ratio = 1) +
+    labs(title = "CCFs with lands data")
+)
+```
+
+```{r}
+ccfs_withlands <- 
+  ccfs_withlands_expanded %>%
+  mutate(
+    land_id1 = paste(study1, barrel1, bullet1, land1, sep = "-"),
+    land_id2 = paste(study2, barrel2, bullet2, land2, sep = "-")
+  ) %>%
+  select(land_id1, land_id2, all_of(rf_features), match)
+```
+
+```{r fig.width = 12, fig.height = 6, echo = FALSE}
+plot_grid(
+  bullet_train_raw_expanded %>% 
+    mutate(across(where(is.character), factor)) %>%
+    filter(study1 == "Hamby173", study2 == "Hamby173") %>%
+    filter(bullet1 %in% c("B1","B2"), bullet2 %in% c("B1", "B2")) %>% 
+    count(study1, barrel1, bullet1, land1, study2, barrel2, bullet2, land2) %>%
+    ggplot(aes(
+      x = barrel1:land1, y = barrel2:land2, fill = n
+    )) +
+    geom_tile() +
+    facet_grid(study2 + bullet2 ~ study1 + bullet1) +
+    theme(aspect.ratio = 1,
+          axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)) + 
+    labs(title = "Hamby comparisons data"),
+  ccfs_withlands_expanded %>% 
+    filter(study1 == "Hamby173", study2 == "Hamby173") %>%
+    filter(bullet1 %in% c("B1","B2"), bullet2 %in% c("B1", "B2")) %>% 
+    count(study1, barrel1, bullet1, land1, study2, barrel2, bullet2, land2) %>%
+    ggplot(aes(
+      x = barrel1:land1, y = barrel2:land2, fill = n
+    )) +
+    geom_tile() +
+    facet_grid(study2 + bullet2 ~ study1 + bullet1) +
+    theme(aspect.ratio = 1, 
+          axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)) + 
+    labs(title = "CCFs with lands data")
+)
+```
+
+```{r}
+bullet_train_raw_switch <-
+  bullet_train_raw_expanded %>%
+  mutate(across(where(is.factor), as.character)) %>%
+  mutate(temp_barrel = ifelse(barrel1 == "Br10", barrel1, "NA")) %>%
+  mutate(barrel1 = ifelse(temp_barrel == "Br10", barrel2, barrel1)) %>%
+  mutate(barrel2 = ifelse(temp_barrel == "Br10", temp_barrel, barrel2)) %>%
+  select(-temp_barrel) %>%
+  mutate(across(where(is.character), factor)) %>%
+  mutate(barrel1 = fct_relevel(barrel1, paste0("Br", 1:10)),
+         barrel2 = fct_relevel(barrel2, paste0("Br", 1:10)))
+```
+
+```{r fig.width = 15, fig.height = 30, echo = FALSE}
+plot_grid(
+  bullet_train_raw_switch %>% 
+    filter(study1 == "Hamby173", study2 == "Hamby173") %>%
+    filter(bullet1 %in% c("B1","B2"), bullet2 %in% c("B1", "B2")) %>% 
+    count(study1, barrel1, bullet1, study2, barrel2, bullet2) %>%
+    ggplot(aes(
+      x = barrel1, y = barrel2, fill = n
+    )) +
+    geom_tile() +
+    facet_grid(study2 + bullet2 ~ study1 + bullet1) +
+    theme(aspect.ratio = 1,
+          axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)) + 
+    labs(title = "Hamby comparisons data"),
+  ccfs_withlands_expanded %>% 
+    filter(study1 == "Hamby173", study2 == "Hamby173") %>%
+    filter(bullet1 %in% c("B1","B2"), bullet2 %in% c("B1", "B2")) %>% 
+    count(study1, barrel1, bullet1, study2, barrel2, bullet2) %>%
+    ggplot(aes(
+      x = barrel1, y = barrel2, fill = n
+    )) +
+    geom_tile() +
+    facet_grid(study2 + bullet2 ~ study1 + bullet1) +
+    theme(aspect.ratio = 1, 
+          axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)) + 
+    labs(title = "CCFs with lands data"), 
+bullet_train_raw_switch %>% 
+    filter(study1 == "Hamby173", study2 == "Hamby252") %>%
+    filter(bullet1 %in% c("B1","B2"), bullet2 %in% c("B1", "B2")) %>% 
+    count(study1, barrel1, bullet1, study2, barrel2, bullet2) %>%
+    ggplot(aes(
+      x = barrel1, y = barrel2, fill = n
+    )) +
+    geom_tile() +
+    facet_grid(study2 + bullet2 ~ study1 + bullet1) +
+    theme(aspect.ratio = 1,
+          axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)) + 
+    labs(title = "Hamby comparisons data"),
+  ccfs_withlands_expanded %>% 
+    filter(study1 == "Hamby173", study2 == "Hamby252") %>%
+    filter(bullet1 %in% c("B1","B2"), bullet2 %in% c("B1", "B2")) %>% 
+    count(study1, barrel1, bullet1, study2, barrel2, bullet2) %>%
+    ggplot(aes(
+      x = barrel1, y = barrel2, fill = n
+    )) +
+    geom_tile() +
+    facet_grid(study2 + bullet2 ~ study1 + bullet1) +
+    theme(aspect.ratio = 1, 
+          axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)) + 
+    labs(title = "CCFs with lands data"),
+bullet_train_raw_switch %>% 
+    filter(study1 == "Hamby252", study2 == "Hamby173") %>%
+    filter(bullet1 %in% c("B1","B2"), bullet2 %in% c("B1", "B2")) %>% 
+    count(study1, barrel1, bullet1, study2, barrel2, bullet2) %>%
+    ggplot(aes(
+      x = barrel1, y = barrel2, fill = n
+    )) +
+    geom_tile() +
+    facet_grid(study2 + bullet2 ~ study1 + bullet1) +
+    theme(aspect.ratio = 1,
+          axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)) + 
+    labs(title = "Hamby comparisons data"),
+  ccfs_withlands_expanded %>% 
+    filter(study1 == "Hamby252", study2 == "Hamby173") %>%
+    filter(bullet1 %in% c("B1","B2"), bullet2 %in% c("B1", "B2")) %>% 
+    count(study1, barrel1, bullet1, study2, barrel2, bullet2) %>%
+    ggplot(aes(
+      x = barrel1, y = barrel2, fill = n
+    )) +
+    geom_tile() +
+    facet_grid(study2 + bullet2 ~ study1 + bullet1) +
+    theme(aspect.ratio = 1, 
+          axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)) + 
+    labs(title = "CCFs with lands data"),
+  bullet_train_raw_switch %>% 
+    filter(study1 == "Hamby252", study2 == "Hamby252") %>%
+    filter(bullet1 %in% c("B1","B2"), bullet2 %in% c("B1", "B2")) %>% 
+    count(study1, barrel1, bullet1, study2, barrel2, bullet2) %>%
+    ggplot(aes(
+      x = barrel1, y = barrel2, fill = n
+    )) +
+    geom_tile() +
+    facet_grid(study2 + bullet2 ~ study1 + bullet1) +
+    theme(aspect.ratio = 1,
+          axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)) + 
+    labs(title = "Hamby comparisons data"),
+  ccfs_withlands_expanded %>% 
+    filter(study1 == "Hamby252", study2 == "Hamby252") %>%
+    filter(bullet1 %in% c("B1","B2"), bullet2 %in% c("B1", "B2")) %>% 
+    count(study1, barrel1, bullet1, study2, barrel2, bullet2) %>%
+    ggplot(aes(
+      x = barrel1, y = barrel2, fill = n
+    )) +
+    geom_tile() +
+    facet_grid(study2 + bullet2 ~ study1 + bullet1) +
+    theme(aspect.ratio = 1, 
+          axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)) + 
+    labs(title = "CCFs with lands data"), 
+  ncol = 2
+)
+```
+
+```{r}
+bullet_train_cleaned <-
+  bullet_train_raw_switch %>%
+  mutate(
+    land_id1 = paste(study1, barrel1, bullet1, land1, sep = "-"),
+    land_id2 = paste(study2, barrel2, bullet2, land2, sep = "-")
+  ) %>%
+  select(land_id1, land_id2, rf_features)
+
+ccfs_withlands_cleaned <- ccfs_withlands_expanded %>%
+  mutate(
+    land_id1 = paste(study1, barrel1, bullet1, land1, sep = "-"),
+    land_id2 = paste(study2, barrel2, bullet2, land2, sep = "-")
+  ) %>%
+  select(land_id1, land_id2, rf_features)
+```
+
+```{r}
+land_ids_old = bullet_train_cleaned %>% select(land_id1, land_id2)
+land_ids_new = ccfs_withlands_cleaned %>% select(land_id1, land_id2)
+dim(land_ids_old)
+dim(land_ids_new)
+```
+
+```{r}
+extra_leas_in_old <- 
+  anti_join(x = land_ids_old, y = land_ids_new, by = c("land_id1", "land_id2")) %>%
+  separate(land_id1, c("study1", "barrel1", "bullet1", "land1")) %>%
+  separate(land_id2, c("study2", "barrel2", "bullet2", "land2"))
+dim(extra_leas_in_old)
+```
+
+```{r fig.height = 6, echo = FALSE}
+extra_leas_in_old %>%
+  count(study1, barrel1, study2, barrel2) %>%
+  ggplot(aes(x = barrel1, y = barrel2, fill = n)) +
+  geom_tile() +
+  facet_grid(study2 ~ study1, scales = "free") + 
+  theme(aspect.ratio = 1)
+```
+
+```{r}
+extra_leas_in_new <- 
+  anti_join(x = land_ids_new, y = land_ids_old, by = c("land_id1", "land_id2")) %>%
+  separate(land_id1, c("study1", "barrel1", "bullet1", "land1")) %>%
+  separate(land_id2, c("study2", "barrel2", "bullet2", "land2"))
+dim(extra_leas_in_new)
+```
+
+```{r fig.height = 6, echo = FALSE}
+extra_leas_in_new %>%
+  count(study1, barrel1, study2, barrel2) %>%
+  ggplot(aes(x = barrel1, y = barrel2, fill = n)) +
+  geom_tile() +
+  facet_grid(study2 ~ study1, scales = "free") + 
+  theme(aspect.ratio = 1)
+```
+
+```{r}
+extra_leas_in_new <- 
+  anti_join(x = land_ids_new, y = land_ids_old, by = c("land_id1", "land_id2")) %>%
+  separate(land_id1, c("study1", "barrel1", "bullet1", "land1")) %>%
+  separate(land_id2, c("study2", "barrel2", "bullet2", "land2"))
+dim(extra_leas_in_new)
+```
+
 ## Compare Dimensions to rtrees
@@
 length(bulletxtrctr::rtrees$predicted) == dim(bullet_train_eric_filter)[1]
+```
+
+```{r}
+bullet_train_eric_filter_v2 <-
+  bullet_train_raw %>%
+  mutate(bbl1 = str_remove(land_id1, pattern = "Hamby252-|Hamby173-"),
+         bbl2 = str_remove(land_id2, pattern = "Hamby252-|Hamby173-")) %>%
+  filter(!(bbl1 %in% c("Br6-B2-L1", "Br9-B2-L4", "BrUnk-BB-L2", "BrUnk-BQ-L4") | 
+           bbl2 %in% c("Br6-B2-L1", "Br9-B2-L4", "BrUnk-BB-L2", "BrUnk-BQ-L4"))) %>%
+  select(-bbl1, -bbl2) %>%
+  separate(col = "land_id1",
+           into = c("study1", "barrel1", "bullet1", "land1")) %>%
+  separate(col = "land_id2",
+           into = c("study2", "barrel2", "bullet2", "land2")) %>%
+  filter(study1 != "Hamby173" | bullet1 != "BE") %>%
+  filter(study2 != "Hamby173" | bullet2 != "BE")
+
+dim(bullet_train_eric_filter_v2)
+length(bulletxtrctr::rtrees$predicted) == dim(bullet_train_eric_filter_v2)[1]
 ```

### 2020-09-25 code/02-data-preparation.Rmd
updated code to check for lands in one data but not the other (see section "Bullet Training Data", sub-section "Comparing Training Datasets", sub-sub-section "Land ID Differences" for the results)

--- 2020-09-23 code/02-data-preparation.Rmd
@@
 
+## Comparing Training Datasets
+
+We are trying to determine which of two datasets were used to train `rtrees` in `bulletxtrctr`.
+
 Load the raw version of the Hamby 172 and 252 bullet comparison data (provided by Heike and CSAFE):
@@
 
-Determine the number of total study-barrel-bullet-lands in the data:
+Load the newest training data provided by Heike (on 9/24/2020 from CSAFE data base):
 
 ```{r}
-length(unique(bullet_train_raw %>% pull(land_id1)))
+ccfs_withlands_raw = read.csv("../data/raw/CCFs_withlands.csv")
 ```
 
-Determine the number of total study-barrel-bullet-lands in the data when observations with tank rash are excluded:
+### Initial Comparisons
+
+Data dimensions:
 
 ```{r}
-length(unique(bullet_train_raw %>% filter(flag == FALSE) %>% pull(land_id1)))
+dim(bullet_train_raw)
+dim(ccfs_withlands_raw)
 ```
 
-There is only one less land id when the cases with tank rash are excluded.
-The code below shows that this case is `Hamby252-Br9-B2-L4` since there are no rows in the filtered data without `Hamby252-Br9-B2-L4` as one of the land ids:
+Comparing the distributions of the two datasets:
 
 ```{r}
-length(unique(
-  bullet_train_raw %>% filter(flag == TRUE) %>% filter(
-    land_id1 != "Hamby252-Br9-B2-L4",
-    land_id2 != "Hamby252-Br9-B2-L4"
-  ) %>% pull(land_id1)
+summary(bullet_train_raw %>% filter(flag == FALSE) %>% select(rf_features))
+summary(ccfs_withlands_raw %>% select(rf_features))
+```
+
+### Clean CCFs with lands
+
+Rename some of the variables to match the structure of `bullet_train_raw`, select only variables of interest, and convert LEA labels to factors (for plotting purposes):
+
+```{r}
+ccfs_withlands_raw_expanded <- 
+  ccfs_withlands_raw %>%
+  rename("study1" = "study.x", "barrel1" = "barrel.x", "bullet1" = "bullet.x", "land1" = "land.x",
+         "study2" = "study.y", "barrel2" = "barrel.y", "bullet2" = "bullet.y", "land2" = "land.y") %>%
+  select(
+    study1, barrel1, bullet1, land1, 
+    study2, barrel2, bullet2, land2,
+    all_of(rf_features), 
+    match
+  ) %>%
+  mutate(across(c(study1, barrel1, bullet1, land1, study2, barrel2, bullet2, land2), factor))
+```
+
+Create a version of the `bullet_train_raw` data with the land IDs expanded to multiple columns for plotting:
+
+```{r}
+bullet_train_raw_expanded <- 
+  bullet_train_raw %>%
+  separate(land_id1, c("study1", "barrel1", "bullet1", "land1")) %>%
+  separate(land_id2, c("study2", "barrel2", "bullet2", "land2")) %>%
+  mutate(across(where(is.character), factor)) %>%
+  mutate(barrel1 = fct_relevel(barrel1, paste0("Br", 1:10)),
+         barrel2 = fct_relevel(barrel2, paste0("Br", 1:10)))
+```
+
+Shows that `Hamby44` needs to be changed to `Hamby173` in `ccfs_withlands`:
+
+```{r fig.width = 12, fig.height = 5, echo = FALSE}
+plot_grid(
+  bullet_train_raw_expanded %>% count(study1, study2) %>%
+    ggplot(aes(
+      x = study1, y = study2, fill = n
+    )) +
+    geom_tile() +
+    theme(aspect.ratio = 1) + 
+    labs(title = "Hamby comparisons data"),
+  ccfs_withlands_raw_expanded %>% count(study1, study2) %>%
+    ggplot(aes(
+      x = study1, y = study2, fill = n
+    )) +
+    geom_tile() +
+    theme(aspect.ratio = 1) +
+    labs(title = "CCFs with lands data")
+)
+```
+
+Shows that lettered barrels need to be changed to `BrUnk` and `Br` added to other barrels in `ccfs_withlands`:
+
+```{r fig.width = 12, fig.height = 5, echo = FALSE}
+plot_grid(
+  bullet_train_raw_expanded %>% count(barrel1, barrel2) %>%
+    ggplot(aes(
+      x = barrel1, y = barrel2, fill = n
+    )) +
+    geom_tile() +
+    theme(aspect.ratio = 1) + 
+    labs(title = "Hamby comparisons data"),
+  ccfs_withlands_raw_expanded %>% count(barrel1, barrel2) %>%
+    ggplot(aes(
+      x = barrel1, y = barrel2, fill = n
+    )) +
+    geom_tile() +
+    theme(aspect.ratio = 1) +
+    labs(title = "CCFs with lands data")
+)
+```
+
+Shows that barrel letters from in `ccfs_withlands` need to be made the bullet and `B` added to all bullets:
+
+```{r fig.width = 12, fig.height = 5, echo = FALSE}
+plot_grid(
+  bullet_train_raw_expanded %>% count(bullet1, bullet2) %>%
+    ggplot(aes(
+      x = bullet1, y = bullet2, fill = n
+    )) +
+    geom_tile() +
+    theme(aspect.ratio = 1) + 
+    labs(title = "Hamby comparisons data"),
+  ccfs_withlands_raw_expanded %>% count(bullet1, bullet2) %>%
+    ggplot(aes(
+      x = bullet1, y = bullet2, fill = n
+    )) +
+    geom_tile() +
+    theme(aspect.ratio = 1) +
+    labs(title = "CCFs with lands data")
+)
+```
+
+Shows that `L` needs to be added to lands in `ccfs_withlands`:
+
+```{r fig.width = 12, fig.height = 5, echo = FALSE}
+plot_grid(
+  bullet_train_raw_expanded %>% count(land1, land2) %>%
+    ggplot(aes(
+      x = land1, y = land2, fill = n
+    )) +
+    geom_tile() +
+    theme(aspect.ratio = 1) + 
+    labs(title = "Hamby comparisons data"),
+  ccfs_withlands_raw_expanded %>% count(land1, land2) %>%
+    ggplot(aes(
+      x = land1, y = land2, fill = n
+    )) +
+    geom_tile() +
+    theme(aspect.ratio = 1) +
+    labs(title = "CCFs with lands data")
+)
+```
+
+Determine the letters in barrels:
+
+```{r}
+all_barrel_labels <-
+  unique(c(
+    as.character(ccfs_withlands_raw_expanded$barrel1),
+    as.character(ccfs_withlands_raw_expanded$barrel2)
   ))
+letters <- all_barrel_labels[!(all_barrel_labels %in% 1:10)]
+letters
+```
+
+Clean `ccfs_withlands` so the labels match `bullet_train_raw`:
+
+```{r}
+ccfs_withlands_clean_expanded <- ccfs_withlands_raw_expanded %>%
+  mutate(
+    study1 = fct_recode(study1, "Hamby173" = "Hamby44"),
+    study2 = fct_recode(study2, "Hamby173" = "Hamby44"),
+    bullet1 = ifelse(barrel1 %in% letters, as.character(barrel1), as.character(bullet1)),
+    barrel1 = ifelse(barrel1 %in% letters, "Unk", barrel1),
+    bullet2 = ifelse(barrel2 %in% letters, as.character(barrel2), as.character(bullet2)),
+    barrel2 = ifelse(barrel2 %in% letters, "Unk", barrel2)
+    ) %>%
+  mutate(
+    study1 = fct_relevel(study1, "Hamby173", "Hamby252"),
+    study2 = fct_relevel(study2, "Hamby173", "Hamby252"),
+    barrel1 = paste0("Br", barrel1),
+    bullet1 = paste0("B", bullet1),
+    land1 = paste0("L", land1),
+    barrel2 = paste0("Br", barrel2),
+    bullet2 = paste0("B", bullet2),
+    land2 = paste0("L", land2)
+  ) %>% 
+  mutate(across(where(is.character), factor)) %>%
+  mutate(barrel1 = fct_relevel(barrel1, paste0("Br", 1:10)),
+         barrel2 = fct_relevel(barrel2, paste0("Br", 1:10)))
+```
+
+The labels agree now but we are starting to see some differences in the two datasets:
+
+```{r fig.width = 12, fig.height = 5, echo = FALSE}
+plot_grid(
+  bullet_train_raw_expanded %>% count(study1, study2) %>%
+    ggplot(aes(
+      x = study1, y = study2, fill = n
+    )) +
+    geom_tile() +
+    theme(aspect.ratio = 1) + 
+    labs(title = "Hamby comparisons data"),
+  ccfs_withlands_clean_expanded %>% count(study1, study2) %>%
+    ggplot(aes(
+      x = study1, y = study2, fill = n
+    )) +
+    geom_tile() +
+    theme(aspect.ratio = 1) +
+    labs(title = "CCFs with lands data")
+)
+```
+
+The labels agree now but still can see the differences in the two datasets:
+
+```{r fig.width = 12, fig.height = 5, echo = FALSE}
+plot_grid(
+  bullet_train_raw_expanded %>% count(barrel1, barrel2) %>%
+    ggplot(aes(
+      x = barrel1, y = barrel2, fill = n
+    )) +
+    geom_tile() +
+    theme(aspect.ratio = 1) + 
+    labs(title = "Hamby comparisons data"),
+  ccfs_withlands_clean_expanded %>% count(barrel1, barrel2) %>%
+    ggplot(aes(
+      x = barrel1, y = barrel2, fill = n
+    )) +
+    geom_tile() +
+    theme(aspect.ratio = 1) +
+    labs(title = "CCFs with lands data")
+)
+```
+
+The labels agree now but again, there are apparent differences between datasets:
+
+```{r fig.width = 12, fig.height = 5, echo = FALSE}
+plot_grid(
+  bullet_train_raw_expanded %>% 
+    count(bullet1, bullet2) %>%
+    ggplot(aes(
+      x = bullet1, y = bullet2, fill = n
+    )) +
+    geom_tile() +
+    theme(aspect.ratio = 1) + 
+    labs(title = "Hamby comparisons data"),
+  ccfs_withlands_clean_expanded %>% 
+    count(bullet1, bullet2) %>%
+    ggplot(aes(
+      x = bullet1, y = bullet2, fill = n
+    )) +
+    geom_tile() +
+    theme(aspect.ratio = 1) +
+    labs(title = "CCFs with lands data")
+)
+```
+
+The labels agree now:
+
+```{r fig.width = 12, fig.height = 5, echo = FALSE}
+plot_grid(
+  bullet_train_raw_expanded %>% 
+    count(land1, land2) %>%
+    ggplot(aes(
+      x = land1, y = land2, fill = n
+    )) +
+    geom_tile() +
+    theme(aspect.ratio = 1) + 
+    labs(title = "Hamby comparisons data"),
+  ccfs_withlands_clean_expanded %>% 
+    count(land1, land2) %>%
+    ggplot(aes(
+      x = land1, y = land2, fill = n
+    )) +
+    geom_tile() +
+    theme(aspect.ratio = 1) +
+    labs(title = "CCFs with lands data")
+)
+```
+
+Compress the land labels for `ccfs_withlands`:
+
+```{r}
+ccfs_withlands_clean <- 
+  ccfs_withlands_clean_expanded %>%
+  mutate(
+    land_id1 = paste(study1, barrel1, bullet1, land1, sep = "-"),
+    land_id2 = paste(study2, barrel2, bullet2, land2, sep = "-")
+  ) %>%
+  select(land_id1, land_id2, all_of(rf_features), match)
+```
+
+### Land ID Differences
+
+Extract the unique land IDs from the two datasets:
+
+```{r}
+ccfs_withlands_ids = unique(c(ccfs_withlands_clean$land_id1, ccfs_withlands_clean$land_id2))
+bullet_train_ids = unique(c(bullet_train_raw$land_id1, bullet_train_raw$land_id1))
+```
+
+Identify the land ID in `CCFs_withlands` but not in `hamby-comparisons`:
+
+```{r}
+ccfs_withlands_ids[!(ccfs_withlands_ids %in% bullet_train_ids)]
+```
+
+Identify the land ID in `hamby-comparisons` but not in `CCFs_withlands`:
+
+```{r}
+bullet_train_ids[!(bullet_train_ids %in% ccfs_withlands_ids)]
 ```
@@
 
+```{r}
+bullet_train_eric_filter_v2 <-
+  bullet_train_raw %>%
+  mutate(bbl1 = str_remove(land_id1, pattern = "Hamby252-|Hamby173-"),
+         bbl2 = str_remove(land_id2, pattern = "Hamby252-|Hamby173-")) %>%
+  filter(!(bbl1 %in% c("Br6-B2-L1", "Br9-B2-L4", "BrUnk-BB-L2", "BrUnk-BQ-L4") | 
+           bbl2 %in% c("Br6-B2-L1", "Br9-B2-L4", "BrUnk-BB-L2", "BrUnk-BQ-L4"))) %>%
+  select(-bbl1, -bbl2) %>%
+  separate(col = "land_id1",
+           into = c("study1", "barrel1", "bullet1", "land1")) %>%
+  separate(col = "land_id2",
+           into = c("study2", "barrel2", "bullet2", "land2")) %>%
+  filter(study1 != "Hamby173" | bullet1 != "BE") %>%
+  filter(study2 != "Hamby173" | bullet2 != "BE")
+
+dim(bullet_train_eric_filter_v2)
+length(bulletxtrctr::rtrees$predicted) == dim(bullet_train_eric_filter_v2)[1]
+```
+
 Extracting the predictions on the training data from `rtrees` and using `rtrees` to make predictions on the filtered data:
@@
 ## Preparing Data
+
+Determine the number of total study-barrel-bullet-lands in the data:
+
+```{r}
+length(unique(bullet_train_raw %>% pull(land_id1)))
+```
+
+Determine the number of total study-barrel-bullet-lands in the data when observations with tank rash are excluded:
+
+```{r}
+length(unique(bullet_train_raw %>% filter(flag == FALSE) %>% pull(land_id1)))
+```
+
+There is only one less land id when the cases with tank rash are excluded.
+The code below shows that this case is `Hamby252-Br9-B2-L4` since there are no rows in the filtered data without `Hamby252-Br9-B2-L4` as one of the land ids:
+
+```{r}
+length(unique(
+  bullet_train_raw %>% filter(flag == TRUE) %>% filter(
+    land_id1 != "Hamby252-Br9-B2-L4",
+    land_id2 != "Hamby252-Br9-B2-L4"
+  ) %>% pull(land_id1)
+))
+```
 

### 2020-09-25 LEAscans/bullete.Rmd
scans in md

---
output: rmarkdown::github_document
always_allow_html: yes
---

## The bullet that doesn't fit

Bullet E  of Hamby set 173 is given by NIST () as being fired from Barrel 1,   but visual inspection does not show a match to any other bullets fired from barrel 1 (known or questioned from either set).

Land 1

![Hamby173-BrE-B1-L1.png](Bullet E/Hamby173-BrE-B1-L1.png)

Land 2

![Hamby173-BrE-B1-L2.png](Bullet E/Hamby173-BrE-B1-L2.png)

Land 3

![Hamby173-BrE-B1-L3.png](Bullet E/Hamby173-BrE-B1-L3.png)

Land 4

![Hamby173-BrE-B1-L4.png](Bullet E/Hamby173-BrE-B1-L4.png)

Land 5

![Hamby173-BrE-B1-L5.png](Bullet E/Hamby173-BrE-B1-L5.png)

Land 6

![Hamby173-BrE-B1-L6.png](Bullet E/Hamby173-BrE-B1-L6.png)

### 2020-09-25 LEAscans/tankrash.Rmd
scans in md

---
output: rmarkdown::github_document
always_allow_html: yes
---

## Land engraved areas exhibiting damage

### Extreme pitting

Pitting is caused by left-over gun powder exploding in the barrel. This causes holes in the surface of the bullet. Usually these holes are small. The example below is an extreme form of pitting.

Hamby173-Br4-B2-L1

![Hamby173-Br4-B2-L1.png](Hamby173-Br4-B2-L1.png)

### Tank rash

Tank rash is damage to the bullet after it exits the barrel during the firing. 
This kind of damage is often caused by a bulled scraping along the side of the tank used during the bullet collection, hence the name. 
Because the damage happens after the firing, the marks are unrelated to the barrel and should not be used for any comparisons. 
The scans below are excluded from the training data because they are unsuitable for a comparison of striation marks.

Hamby252-Br6-B2-L1

![Hamby252-Br6-B2-L1.png](Hamby252-Br6-B2-L1.png)

Hamby252-Br9-B1-L2

![Hamby252-Br9-B1-L2.png](Hamby252-Br9-B1-L2.png)

Hamby252-BrUkn-BB-L2

![Hamby252-BrUkn-BB-L2.png](Hamby252-BrUkn-BB-L2.png)

Hamby252-BrUkn-BQ-L4

![Hamby252-BrUkn-BQ-L4.png](Hamby252-BrUkn-BQ-L4.png)

Hamby252-BrUkn-BU-L4

![Hamby252-BrUkn-BU-L4.png](Hamby252-BrUkn-BU-L4.png)

### 2020-09-26 README.Rmd
trying to compare the data
updated to do list

@@
 
+- Move all code and results from our work identifying the data to my LIME-research-journals repo for future reference (including LIME explanations from different training datasets/models)
+- Update 02-data-preparation.Rmd to only include the preparation of the CCFs_withlands data to be used in the paper
+- Update code/figures in paper to train a random forest using CCFs_withlands data (and a set seed) and apply LIME predictions
+- Rewrite Section 4 as needed
+- Prepare for submission
 - Edit dataset descriptions in README and add to the readme.txt document for submission
@@
 - `example-signatures.csv.zip` contains signature data from two matching bullet lands that is used to generate a figure in the manuscript.
-- `raw` contains the raw versions of the data files (from Heike and CSAFE) that the above datasets are derived from. *Do not alter these files in any way.*
+- `raw` contains the raw versions of the data files (from Heike and CSAFE) that the above datasets are derived from. *Do not alter the data in these files.*
 

### 2020-09-26 README.Rmd
explanation of comparison features

--- 2020-09-18 README.Rmd
@@
 
-A dataset with `r dim(bullet_train)[1]` rows and `r dim(bullet_train)[2]` columns that contains comparison features from the Hamby 173 and 252 sets (XXX reference XXX).
-It contains comparisons from `r length(unique(bullet_train$land_id1))` bullet-land signatures with some lands missing due to tank rash or other reasons.
-This dataset is created using the data available at XXX, which contains XXX.
-The only changes made to the data from XXX were to remove any lands with tank rash, select only variables of use for the manuscript, add a case variable, rename `same_source` as `samesource`, and attach the random forest scores associated with the comparisons.
+A dataset with `r dim(bullet_train)[1]` rows and `r dim(bullet_train)[2]` columns that contains comparison features based on high resolution microscopy scans of fired bullets from Hamby sets 173 and 252 [@hamby].
+This dataset is created from the x3p scans of bullet land engraved areas available from the [NIST Ballistics Toolmark Research Database](https://tsapps.nist.gov/NRBTD/).
+It contains comparisons from `r length(unique(c(bullet_train$land_id1, bullet_train$land_id2)))` bullet-land signatures.
+12 of the overall 420 lands (6 lands per bullets, 35 bullets in each set) are excluded from the comparison.
+Six of these lands show so-called "tank rash" - damage to the bullets after it exited the barrel (see [tank rash scans](LEAscans/tankrash.md)).
+Another bullet (Bullet E from Hamby 173) is excluded because it could not be matched visually to the barrel it was supposedly from (see [scans from bullet E](LEAscans/bullete.md)).
+The <b>bullet_train</b> data is based on a set of features extracted from the x3p scans as described in @hare:2016.
+The raw file of comparison features is found [here](data/raw/hamby-comparisons.csv.zip).
+The only changes made to the data were XXX I think the following statement needs to be adjusted XXX to select only variables of use for the manuscript, add a case variable, rename `same_source` as `samesource`, and attach the random forest scores associated with the comparisons.
 The variables in the data are as follows:
 
-- `r names(bullet_train)[1]` = ID number associated with the bullet-land signature comparison.
-- `r names(bullet_train)[2]` = ID associated with the first bullet-land in the comparison. The format is 'study - barrel number - bullet number - land number'.
-- `r names(bullet_train)[3]` = ID associated with the second bullet-land in the comparison. Again, the format is 'study - barrel number - bullet number - land number'.
-- `r names(bullet_train)[4]` = the comparison feature of two signatures of cross correlation.
-- `r names(bullet_train)[5]` = the comparison feature of two signatures of rough correlation.
-- `r names(bullet_train)[6]` = the comparison feature of two signatures of distance.
-- `r names(bullet_train)[7]` = the comparison feature of two signatures of standard deviation of distance.
-- `r names(bullet_train)[8]` = the comparison feature of two signatures of matches.
-- `r names(bullet_train)[9]` = the comparison feature of two signatures of mismatches.
-- `r names(bullet_train)[10]` = the comparison feature of two signatures of consecutively matched striae.
-- `r names(bullet_train)[11]` = the comparison feature of two signatures of non-consecutively matched striae.
-- `r names(bullet_train)[12]` = the comparison feature of two signatures of sum of peaks.
-- `r names(bullet_train)[13]` = indicator variable specifying whether the two bullet-lands are a match.
-- `r names(bullet_train)[14]` = the random forest score associated with the comparison in support of a match.
+#### Variables used as key variables:
+- `r names(bullet_train)[1]`: ID number associated with the bullet-land signature comparison.
+- `r names(bullet_train)[2]`, `r names(bullet_train)[3]`: IDs describing the two land engraved areas in the comparison. The format is 'study - barrel number - bullet number - land number'.
 
-For further details about the signatures comparison features, see XXX.
+#### Comparison features
+- `r names(bullet_train)[4]`: maximized cross-correlation between two LEA signatures.
+- `r names(bullet_train)[5]`: correlation after detrending aligned signatures.
+- `r names(bullet_train)[6]`: Euclidean distance (in millimeters) between two aligned signatures.
+- `r names(bullet_train)[7]`: standard deviation of the previous measure along the signature.
+- `r names(bullet_train)[8]`, `r names(bullet_train)[9]`: number of matching/non-matching peaks and valleys in the aligned signatures.
+- `r names(bullet_train)[10]`: consecutively matching striae is a measure introduced by @biasotti describing the longest run of matching peaks between two aligned signatures.
+- `r names(bullet_train)[11]`: the number of consecutively non-matching peaks.
+- `r names(bullet_train)[12]`: the depth of peaks measured as the sum of matching peaks between two aligned signatures (in microns).
+- `r names(bullet_train)[13]`: ground truth whether a pair is from the same source (`TRUE`) or from different sources (`FALSE`).
+- `r names(bullet_train)[14]`: the random forest score associated with the comparison in support of a match.
+
+<!--For further details about the signatures comparison features, see XXX.-->
 
@@
 
-A dataset with `r dim(bullet_test)[1]` rows and `r dim(bullet_test)[2]` columns that contains comparison features from sets 1 and 11 of the Hamby 224 Clone sets (XXX reference XXX).
+A dataset with `r dim(bullet_test)[1]` rows and `r dim(bullet_test)[2]` columns that contains comparison features from test sets 1 and 11 of the Hamby 224 Clone sets.
 Each test set is arranged as a combination of three bullets: two known bullets and a questioned bullet.
-Each bullet has 6 lands.
+Similar to the training set, each bullet has 6 lands.
 The data contains comparisons of bullet-lands within a set.
@@
 However, there are only `r dim(bullet_test)[1]` comparisons in the `bullet-test` data.
-This is due to the fact that some of the lands are missing from the data (probably due to tank rank): land 4 from the unknown bullet in set 1, land 2 from bullet 1 in set 11, and land 4 from the unknown bullet in set 11.
-The variables in the data are as follows:
+This is due to the fact that some of the lands are missing from the data (due to tank rash): land 4 from the unknown bullet in set 1, land 2 from bullet 1 in set 11, and land 4 from the unknown bullet in set 11.
+The variables in the test data are the same as the training data described above.
 
-- `r names(bullet_test)[1]` = ID number associated with the bullet-land signature comparison.
-- `r names(bullet_test)[2]` = ID associated with the first bullet-land in the comparison with a format of 'study - set number - bullet number - land number'.
-- `r names(bullet_test)[3]` = ID associated with the second bullet-land in the comparison with a format of 'study - set number - bullet number - land number'.
-- `r names(bullet_test)[4]` = the comparison feature of two signatures of cross correlation.
-- `r names(bullet_test)[5]` = the comparison feature of two signatures of rough correlation.
-- `r names(bullet_test)[6]` = the comparison feature of two signatures of distance.
-- `r names(bullet_test)[7]` = the comparison feature of two signatures of standard deviation of distance.
-- `r names(bullet_test)[8]` = the comparison feature of two signatures of matches.
-- `r names(bullet_test)[9]` = the comparison feature of two signatures of mismatches.
-- `r names(bullet_test)[10]` = the comparison feature of two signatures of consecutively matched striae.
-- `r names(bullet_test)[11]` = the comparison feature of two signatures of non-consecutively matched striae.
-- `r names(bullet_test)[12]` = the comparison feature of two signatures of sum of peaks.
-- `r names(bullet_test)[13]` = indicator variable specifying whether the two bullet-lands are a match.
-- `r names(bullet_test)[14]` = the random forest score associated with the comparison in support of a match.
-
-For further details about the signatures comparison features, see XXX.
+<!-- For further details about the signatures comparison features, see XXX.-->
 
@@
 
-Contains the signature data from two bullet-land signatures that are a match. The variables in the data are as follows:
+Contains the signature data from aligned signatures of two bullet-lands from the same source. The variables in the data are as follows:
 
-- `r names(signatures)[1]` = Indicates where the observation corresponds to 'Signature 1' or 'Signature 2'
-- `r names(signatures)[2]` = The x position of the signature
-- `r names(signatures)[3]` = The y position of the signature
+- `r names(signatures)[1]`: Indicator variable whether the observation corresponds to 'Signature 1' or 'Signature 2'
+- `r names(signatures)[2]`: the (relative) x position of the signature (in microns)
+- `r names(signatures)[3]`: the (relative) y position of the signature height (in microns)
 

### 2020-09-28 code/02-data-preparation.Rmd
moving code to LIME-research-journals

--- 2020-09-23 code/02-data-preparation.Rmd
@@
 ```
+
+Load the newest training data provided by Heike (on 9/24/2020 from CSAFE data base):
+
+```{r}
+ccfs_withlands_raw = read.csv("../data/raw/CCFs_withlands.csv")
+```
+
+## Preparing Data
 
@@
 ```
-
-## Compare Dimensions to rtrees
-
-The dimensions of the raw data:
-
-```{r}
-bullet_train_raw %>% dim()
-```
-
-The dimension of the data once the observations with tank rash (`flag != FALSE`) are removed:
-
-```{r}
-bullet_train_raw %>% filter(flag == FALSE) %>% dim()
-```
-
-The number of observations in the random forest `rtrees`:
-
-```{r}
-length(bulletxtrctr::rtrees$predicted)
-```
-
-The number of rows in the training data with the flagged observations excluded does not match the number of observations used to train `rtrees`.
-In the Hare, Hofmann, and Carriquiry (2017), they describe removing four land impressions that were flagged for quality assessment:
-
-- Barrel 6 Bullet 2-1
-- Barrel 9 Bullet 2-4
-- Unknown Bullet B-2
-- Unknown Bullet Q-4
-
-It is unclear which study these lands correspond to. The code below removes all comparisons that include these barrel, bullet, and land combinations:
-
-```{r}
-bullet_train_filtered <- 
-  bullet_train_raw %>%
-  mutate(bbl1 = str_remove(land_id1, pattern = "Hamby252-|Hamby173-"),
-         bbl2 = str_remove(land_id2, pattern = "Hamby252-|Hamby173-")) %>%
-  filter(!(bbl1 %in% c("Br6-B2-L1", "Br9-B2-L4", "BrUnk-BB-L2", "BrUnk-BQ-L4") | 
-           bbl2 %in% c("Br6-B2-L1", "Br9-B2-L4", "BrUnk-BB-L2", "BrUnk-BQ-L4"))) %>%
-  select(-bbl1, -bbl2) 
-```
-
-The dimensions now agree with the number of observations in `rtrees`:
-
-```{r}
-dim(bullet_train_filtered)
-length(bulletxtrctr::rtrees$predicted) == dim(bullet_train_filtered)[1]
-```
-
-The code below removes observations based on Eric Hare's code (available [here](https://github.com/erichare/imaging-paper/blob/master/code/full_run.R)), which he thinks may be the code used to train `rtrees`:
-
-```{r}
-bullet_train_eric_filter <- 
-  bullet_train_raw %>%
-  separate(col = "land_id1", into = c("study1", "barrel1", "bullet1", "land1")) %>%
-  separate(col = "land_id2", into = c("study2", "barrel2", "bullet2", "land2")) %>%
-  filter(study1 != "Hamby173" | bullet1 != "BE") %>%
-  filter(study2 != "Hamby173" | bullet2 != "BE")
-
-# Eric's code for reference:
-# filter(study.y != "Hamby44" | barrel.y != "E") %>%
-# filter(study.x != "Hamby44" | barrel.x != "E") %>%
-```
-
-Here, the dimensions to not agree with the number of observations in `rtrees`:
-
-```{r}
-dim(bullet_train_eric_filter)
-length(bulletxtrctr::rtrees$predicted) == dim(bullet_train_eric_filter)[1]
-```
-
-Extracting the predictions on the training data from `rtrees` and using `rtrees` to make predictions on the filtered data:
-
-```{r}
-rtrees_pred = predict(bulletxtrctr::rtrees, type = "prob")[,2]
-
-new_pred = predict(bulletxtrctr::rtrees, 
-                   bullet_train_filtered %>% 
-                     select(rownames(bulletxtrctr::rtrees$importance)), type = "prob")[,2]
-
-new_pred_full = predict(bulletxtrctr::rtrees, 
-                        bullet_train_raw %>%
-                          select(rownames(bulletxtrctr::rtrees$importance)), type = "prob")[,2]
-```
-
-Plot comparing the two predictions (we discovered that the `predict` function from random forest returns different results when applied to only the model (out-of-bag predictions) and the training data (regular predictions), so this is not a good way to test for agreement between training data and models):
-
-```{r}
-data.frame(rtrees_pred = sort(rtrees_pred), new_pred = sort(new_pred)) %>%
-  ggplot(aes(rtrees_pred, new_pred)) + 
-  geom_point()
-```
-
-Plot showing distributions of predictions from `rtrees` and new predictions made on full training data (same comment here as above about not being able to use this to determine if we have the correct training data for the model):
-
-```{r}
-data.frame(data = c(rep("rtrees", length(rtrees_pred)), 
-                    rep("new predictions on full data", length(new_pred_full))), pred = c(rtrees_pred, new_pred_full)) %>%
-  ggplot(aes(x = pred, fill = data)) + 
-  geom_density(alpha = 0.75)
-```
-
-Comparison to the data Eric Hare said was used to fit `rtrees` which has half the number of observations as the number of rtrees predictions:
-
-```{r}
-eric <- read.csv("https://raw.githubusercontent.com/erichare/imaging-paper/master/data/data-25-25/bullet-stats.csv")
-dim(eric)
-```
-
-## Preparing Data
 

### 2020-09-28 code/01-raw-file-compression.Rmd
small changes
worked on updating to using new training data

--- 2020-09-16 code/raw-file-compression.Rmd
@@
 This document contains code for compressing the raw files (data and figure) associated with the manuscript.
+
+**NOTE** All code chunks in this document have `eval = FALSE` and must be run manually from within the Rmd file. This is done to avoid an accidental change of files.
 
@@
 zip(
-  zipfile = "../data/raw/hamby-comparisons.csv.zip", 
-  files = "../data/raw/hamby-comparisons.csv"
+  zipfile = "../data/raw/CCFs_withlands.csv.zip", 
+  files = "../../data/raw/CCFs_withlands.csv"
 )
@@
   zipfile = "../data/raw/h224-set1-features.rds.zip", 
-  files = "../data/raw/h224-set1-features.rds"
+  files = "../../data/raw/h224-set1-features.rds"
 )
@@
   zipfile = "../data/raw/h224-set11-features.rds.zip", 
-  files = "../data/raw/h224-set11-features.rds"
+  files = "../../data/raw/h224-set11-features.rds"
 )
@@
   zipfile = "../data/raw/signatures.rds.zip", 
-  files = "../data/raw/signatures.rds"
+  files = "../../data/raw/signatures.rds"
 )

### 2020-09-28 code/02-data-preparation.Rmd
worked on updating to using new training data

@@
 ```{r}
-rf_features <- rownames(bulletxtrctr::rtrees$importance)
+rtrees_features <- rownames(bulletxtrctr::rtrees$importance)
 ```
@@
 
-## Comparing Training Datasets
-
-We are trying to determine which of two datasets were used to train `rtrees` in `bulletxtrctr`.
-
-Load the raw version of the Hamby 172 and 252 bullet comparison data (provided by Heike and CSAFE):
+Load the training data provided by Heike (from CSAFE data base; see this [R script](https://github.com/erichare/imaging-paper/blob/master/code/full_run.R) for the code used to access the data):
 
 ```{r}
-bullet_train_raw = read_csv("../data/raw/hamby-comparisons.csv.zip")
-```
-
-Load the newest training data provided by Heike (on 9/24/2020 from CSAFE data base):
-
-```{r}
-ccfs_withlands_raw = read.csv("../data/raw/CCFs_withlands.csv")
+unzip(zipfile = "../data/raw/CCFs_withlands.csv.zip", exdir = "../data/raw")
+bullet_train_raw = read.csv("../data/raw/CCFs_withlands.csv")
 ```
@@
 
+```{r}
+bullet_train_select <- 
+  bullet_train_raw %>%
+  rename(
+    "study1" = "study.x",
+    "barrel1" = "barrel.x",
+    "bullet1" = "bullet.x",
+    "land1" = "land.x",
+    "study2" = "study.y",
+    "barrel2" = "barrel.y",
+    "bullet2" = "bullet.y",
+    "land2" = "land.y",
+    "same_source"= "match"
+  ) %>%
+  select(
+    study1,
+    barrel1,
+    bullet1,
+    land1,
+    study2,
+    barrel2,
+    bullet2,
+    land2,
+    all_of(rtrees_features),
+    same_source
+  ) %>%
+  mutate(across(c(barrel1, bullet1, land1, barrel2, bullet2, land2), as.character))
+```
+
+```{r}
+bullet_train_labelled <- 
+  bullet_train_select %>%
+  mutate(
+    study1 = ifelse(study1 == "Hamby44", "Hamby173", study1),
+    study2 = ifelse(study2 == "Hamby44", "Hamby173", study2),
+    bullet1 = ifelse(barrel1 %in% letters, as.character(barrel1), as.character(bullet1)),
+    barrel1 = ifelse(barrel1 %in% letters, "Unk", barrel1),
+    bullet2 = ifelse(barrel2 %in% letters, as.character(barrel2), as.character(bullet2)),
+    barrel2 = ifelse(barrel2 %in% letters, "Unk", barrel2)
+    ) %>%
+  mutate(
+    barrel1 = paste0("Br", barrel1),
+    bullet1 = paste0("B", bullet1),
+    land1 = paste0("L", land1),
+    barrel2 = paste0("Br", barrel2),
+    bullet2 = paste0("B", bullet2),
+    land2 = paste0("L", land2)
+  )
+```
+
+```{r}
+bullet_train <-
+  bullet_train_labelled %>%
+  mutate(
+    land_id1 = paste(study1, barrel1, bullet1, land1, sep = "-"),
+    land_id2 = paste(study2, barrel2, bullet2, land2, sep = "-")
+  ) %>%
+  select(land_id1, land_id2, all_of(rtrees_features), same_source)
+```
+
 Determine the number of total study-barrel-bullet-lands in the data:
@@
 ```{r}
-length(unique(bullet_train_raw %>% pull(land_id1)))
-```
-
-Determine the number of total study-barrel-bullet-lands in the data when observations with tank rash are excluded:
-
-```{r}
-length(unique(bullet_train_raw %>% filter(flag == FALSE) %>% pull(land_id1)))
-```
-
-There is only one less land id when the cases with tank rash are excluded.
-The code below shows that this case is `Hamby252-Br9-B2-L4` since there are no rows in the filtered data without `Hamby252-Br9-B2-L4` as one of the land ids:
-
-```{r}
-length(unique(
-  bullet_train_raw %>% filter(flag == TRUE) %>% filter(
-    land_id1 != "Hamby252-Br9-B2-L4",
-    land_id2 != "Hamby252-Br9-B2-L4"
-  ) %>% pull(land_id1)
-))
-```
-
-Using the data with the flagged lands removed, select only variables of use for the paper, add a case variable, and rename `same_source` as `samesource`:
-
-```{r}
-bullet_train <- 
-  bullet_train_filtered %>%
-  select(-lag, -abs_lag, -overlap, -signature_length, -flag) %>%
-  mutate(case = factor(1:n())) %>%
-  rename("samesource" = "same_source") %>%
-  select(case, land_id1, land_id2, everything())
-```
-
-Add a variable to the training data with the random forest probability in support of a match using the random forest model `rtrees` from `bulletxtrctr`:
-
-```{r}
-bullet_features <- rownames(bulletxtrctr::rtrees$importance)
-bullet_train$rfscore <- 
-  bulletxtrctr::rtrees %>%
-  predict(bullet_train %>% select(all_of(bullet_features)), type = "prob") %>%
-  data.frame() %>%
-  pull(TRUE.)
+length(unique(c(bullet_train$land_id1, bullet_train$land_id2)))
 ```
@@
 ```{r}
-if (!file.exists("../data/raw/h224-set1-features.rds")) unzip("../data/raw/h224-set1-features.rds.zip")
-if (!file.exists("../data/raw/h224-set11-features.rds")) unzip("../data/raw/h224-set11-features.rds.zip")
+if (!file.exists("../data/raw/h224-set1-features.rds")) unzip("../data/raw/h224-set1-features.rds.zip", exdir = "../data/raw")
+if (!file.exists("../data/raw/h224-set11-features.rds")) unzip("../data/raw/h224-set11-features.rds.zip", exdir = "../data/raw")
 
@@
   # Order the variables as desired
-  select(study, set, bullet1, land1, bullet2, land2, all_of(rf_features), samesource, rfscore)
+  select(study, set, bullet1, land1, bullet2, land2, all_of(rtrees_features), samesource)
 
@@
   # Order the variables as desired
-  select(study, set, bullet1, land1, bullet2, land2, all_of(rf_features), samesource, rfscore)
+  select(study, set, bullet1, land1, bullet2, land2, all_of(rtrees_features), samesource)
 ```
@@
 bullet_test <- bullet_test_extra_vars %>%
-  select(case, land_id1, land_id2, all_of(rf_features), samesource, rfscore)
+  select(case, land_id1, land_id2, all_of(rtrees_features), samesource)
 ```
@@
 ```{r}
-if (!file.exists("../data/raw/signatures.rds")) unzip("../data/raw/signatures.rds.zip")
+if (!file.exists("../data/raw/signatures.rds")) unzip("../data/raw/signatures.rds.zip", exdir = "../data/raw")
 signatures <- readRDS("../data/raw/signatures.rds")

### 2020-09-28 code/02-data-preparation.Rmd
some more work done to update prepartion of new training data (still workign on this)

@@
 
-## Preparing Data
+The raw data contains `r dim(bullet_train_raw)[1]` observations (comparisons of signatures) and `r dim(bullet_train_raw)[2]` variables.
+The table below lists the levels of study, barrel, bullet, and land contained within the raw data.
+One of the study labels is `Hamby44`.
+CSAFE has determined that these bullets are actually from study `Hamby173`.
+Additionally, note that the barrel labels contains letters.
+These barrels are "unknown" barrels, and the new labeling convention used by CSAFE is to use the label for barrel of `BrUnk` and label the bullet using the letter (such as `BA`).
+
+| Descriptor | Levels | 
+| --- | -------------- |
+| Study | `r unique(c(bullet_train_raw$study.x, bullet_train_raw$study.y))` |
+| Barrel | `r unique(c(bullet_train_raw$barrel.x, bullet_train_raw$barrel.y))` |
+| Bullet | `r unique(c(bullet_train_raw$bullet.x, bullet_train_raw$bullet.y))` |
+| Land | `r unique(c(bullet_train_raw$land.x, bullet_train_raw$land.y))` |
+
+The code below cleans and prepares the data for use in the paper. The steps taken are as follows:
+
+1. Rename the label variables using numbers instead of letters (e.g. `study.x` and `study.y` become `study1` and `study2`, respectively). 
+2.
+Select only the variables of interest for the study: signature ID labels (`study1`, `barrel1`, `bullet1`, `land1`, `study2`, `barrel2`, `bullet2`, and `land2`), features used to train the `rtrees` random forest model (`ccf`, `rough_cor`, `D`, `sd_D`, `matches`, `mismatches`, `cms`, `non_cms`, and `sum_peaks`), and the variable identifying whether the two signatures are fired from the same gun (`same_source`).
+3. Convert all categorical variables to characters.
+4. Change the study labels to the correct studies and the barrel and bullet variable labels to the new CSAFE labeling conventions. 
+5. Add letters to the barrel, bullet, and land labels to conform to the CSAFE labeling conventions.
 
 ```{r}
-bullet_train_select <- 
+bullet_train <- 
   bullet_train_raw %>%
   rename(
-    "study1" = "study.x",
-    "barrel1" = "barrel.x",
-    "bullet1" = "bullet.x",
-    "land1" = "land.x",
-    "study2" = "study.y",
-    "barrel2" = "barrel.y",
-    "bullet2" = "bullet.y",
-    "land2" = "land.y",
+    "study1" = "study.x", "barrel1" = "barrel.x", "bullet1" = "bullet.x", "land1" = "land.x",
+    "study2" = "study.y", "barrel2" = "barrel.y", "bullet2" = "bullet.y", "land2" = "land.y",
     "same_source"= "match"
@@
   select(
-    study1,
-    barrel1,
-    bullet1,
-    land1,
-    study2,
-    barrel2,
-    bullet2,
-    land2,
-    all_of(rtrees_features),
-    same_source
+    study1, barrel1, bullet1, land1,
+    study2, barrel2, bullet2, land2,
+    all_of(rtrees_features), same_source
   ) %>%
-  mutate(across(c(barrel1, bullet1, land1, barrel2, bullet2, land2), as.character))
-```
-
-```{r}
-bullet_train_labelled <- 
-  bullet_train_select %>%
+  mutate(across(c(barrel1, bullet1, land1, barrel2, bullet2, land2), as.character)) %>%
   mutate(
@@
     bullet1 = ifelse(barrel1 %in% letters, as.character(barrel1), as.character(bullet1)),
+    bullet2 = ifelse(barrel2 %in% letters, as.character(barrel2), as.character(bullet2)),
     barrel1 = ifelse(barrel1 %in% letters, "Unk", barrel1),
-    bullet2 = ifelse(barrel2 %in% letters, as.character(barrel2), as.character(bullet2)),
     barrel2 = ifelse(barrel2 %in% letters, "Unk", barrel2)
@@
     barrel1 = paste0("Br", barrel1),
+    barrel2 = paste0("Br", barrel2),
     bullet1 = paste0("B", bullet1),
+    bullet2 = paste0("B", bullet2),
     land1 = paste0("L", land1),
-    barrel2 = paste0("Br", barrel2),
-    bullet2 = paste0("B", bullet2),
     land2 = paste0("L", land2)
@@
 
-```{r}
-bullet_train <-
-  bullet_train_labelled %>%
-  mutate(
-    land_id1 = paste(study1, barrel1, bullet1, land1, sep = "-"),
-    land_id2 = paste(study2, barrel2, bullet2, land2, sep = "-")
-  ) %>%
-  select(land_id1, land_id2, all_of(rtrees_features), same_source)
-```
+| Descriptor | Levels | 
+| --- | -------------- |
+| Study | `r unique(c(bullet_train$study1, bullet_train$study2))` |
+| Barrel | `r unique(c(bullet_train$barrel1, bullet_train$barrel2))` |
+| Bullet | `r unique(c(bullet_train$bullet1, bullet_train$bullet2))` |
+| Land | `r unique(c(bullet_train$land1, bullet_train$land2))` |
 
@@
 ```{r}
-if (!file.exists("../data/raw/h224-set1-features.rds")) unzip("../data/raw/h224-set1-features.rds.zip", exdir = "../data/raw")
-if (!file.exists("../data/raw/h224-set11-features.rds")) unzip("../data/raw/h224-set11-features.rds.zip", exdir = "../data/raw")
-
+if (!file.exists("../data/raw/h224-set1-features.rds")) {
+  unzip("../data/raw/h224-set1-features.rds.zip", exdir = "../data/raw")
+}
+if (!file.exists("../data/raw/h224-set11-features.rds")) {
+  unzip("../data/raw/h224-set11-features.rds.zip", exdir = "../data/raw")
+}
 hamby224_set1 <- readRDS("../data/raw/h224-set1-features.rds")
@@
 The bullet and land names from each of the sets are included below.
-This indicates that each set contains `r length(unique(hamby224_set1$bulletA))` bullets with `r length(unique(hamby224_set1$landA))` lands each.
+This indicates that each set contains `r length(unique(c(hamby224_set1$bulletA, hamby224_set1$bulletB)))` bullets with `r length(unique(c(hamby224_set1$landA, hamby224_set1$landB)))` lands each.
 
@@
 | --- | -------------- | -------------- | 
-| 1 | `r unique(hamby224_set1$bulletA)` | `r unique(hamby224_set1$landA)` |
-| 11 | `r unique(hamby224_set11$bulletA)` | `r unique(hamby224_set11$landA)` |
+| 1 | `r unique(c(hamby224_set1$bulletA, hamby224_set1$bulletB))` | `r unique(c(hamby224_set1$landA, hamby224_set1$landB))` |
+| 11 | `r unique(c(hamby224_set11$bulletA, hamby224_set11$bulletB))` | `r unique(c(hamby224_set11$landA, hamby224_set11$landB))` |
 

### 2020-09-28 code/02-data-preparation.Rmd
some more work on updating training data for paper (but still working)

@@
 ```{r}
-unzip(zipfile = "../data/raw/CCFs_withlands.csv.zip", exdir = "../data/raw")
+if (!file.exists("../data/raw/CCFs_withlands.csv")) {
+  unzip("../data/raw/CCFs_withlands.csv.zip", exdir = "../data/raw")
+}
 bullet_train_raw = read.csv("../data/raw/CCFs_withlands.csv")
@@
 5. Add letters to the barrel, bullet, and land labels to conform to the CSAFE labeling conventions.
+6. Create land ID variables that combine study, barrel, bullet, and land labels. 
+7. Add a case variable (just numbering comparisons 1 through `r dim(bullet_train_raw)[1]` based on current order in the data). 
+8. Reorder the variables.
 
 ```{r}
+# Identify the letters used to label barrels 
+all_barrel_labels <- unique(c(bullet_train_raw$barrel.x, bullet_train_raw$barrel.y))
+letters <- all_barrel_labels[!(all_barrel_labels %in% 1:10)]
+
 bullet_train <- 
   bullet_train_raw %>%
+  # 1. Rename variables
   rename(
@@
   ) %>%
+  # 2. Select variables of interest
   select(
@@
   ) %>%
+  # 3. Convert categorical variables to characters
   mutate(across(c(barrel1, bullet1, land1, barrel2, bullet2, land2), as.character)) %>%
+  # 4. Adjust study, barrel, and bullet labels
   mutate(
@@
     study2 = ifelse(study2 == "Hamby44", "Hamby173", study2),
-    bullet1 = ifelse(barrel1 %in% letters, as.character(barrel1), as.character(bullet1)),
-    bullet2 = ifelse(barrel2 %in% letters, as.character(barrel2), as.character(bullet2)),
+    bullet1 = ifelse(barrel1 %in% letters, barrel1, bullet1),
+    bullet2 = ifelse(barrel2 %in% letters, barrel2, bullet2),
     barrel1 = ifelse(barrel1 %in% letters, "Unk", barrel1),
@@
     ) %>%
+  # 5. Add abbreviations infront of barrel, bullet, and land labels
   mutate(
@@
     land2 = paste0("L", land2)
-  )
+  ) %>%
+  # 6. Create land ID variables
+  mutate(
+    land_id1 = paste(study1, barrel1, bullet1, land1, sep = "-"),
+    land_id2 = paste(study2, barrel2, bullet2, land2, sep = "-")
+  ) %>%
+  # 7. Add a case variable
+  mutate(case = as.character(1:n())) %>%
+  # 8. Reorder the variables
+  select(land_id1, land_id2, 
+         study1, barrel1, bullet1, study2, land1, barrel2, bullet2, land2,
+         all_of(rtrees_features), same_source)
 ```
 
-| Descriptor | Levels | 
+Check to make sure the number of rows in the data is still the same:
+
+```{r}
+dim(bullet_train)
+```
+
+The updated signature identification labels are included below:
+
+| Descriptor | Labels | 
 | --- | -------------- |

### 2020-09-28 code/02-data-preparation.Rmd
finished updating preparation code based on CCFs_withlands training data

@@
 
-1. Rename the label variables using numbers instead of letters (e.g. `study.x` and `study.y` become `study1` and `study2`, respectively). 
+1. Rename the label variables using numbers instead of letters (e.g. `study.x` and `study.y` become `study1` and `study2`, respectively), and rename `match` as `samesource`. 
 2.
-Select only the variables of interest for the study: signature ID labels (`study1`, `barrel1`, `bullet1`, `land1`, `study2`, `barrel2`, `bullet2`, and `land2`), features used to train the `rtrees` random forest model (`ccf`, `rough_cor`, `D`, `sd_D`, `matches`, `mismatches`, `cms`, `non_cms`, and `sum_peaks`), and the variable identifying whether the two signatures are fired from the same gun (`same_source`).
+Select only the variables of interest for the study: signature ID labels (`study1`, `barrel1`, `bullet1`, `land1`, `study2`, `barrel2`, `bullet2`, and `land2`), features used to train the `rtrees` random forest model (`ccf`, `rough_cor`, `D`, `sd_D`, `matches`, `mismatches`, `cms`, `non_cms`, and `sum_peaks`), and the variable identifying whether the two signatures are fired from the same gun (`samesource`).
 3. Convert all categorical variables to characters.
@@
 7. Add a case variable (just numbering comparisons 1 through `r dim(bullet_train_raw)[1]` based on current order in the data). 
-8. Reorder the variables.
+8.
+Select final variables for data to use in paper: number assinged to signature (`case`), land IDs (`land_ID1`, `land_ID2`), features used to train the `rtrees` random forest model (`ccf`, `rough_cor`, `D`, `sd_D`, `matches`, `mismatches`, `cms`, `non_cms`, and `sum_peaks`), and the variable identifying whether the two signatures are fired from the same gun (`samesource`).
 
@@
     "study2" = "study.y", "barrel2" = "barrel.y", "bullet2" = "bullet.y", "land2" = "land.y",
-    "same_source"= "match"
+    "samesource"= "match"
   ) %>%
@@
     study2, barrel2, bullet2, land2,
-    all_of(rtrees_features), same_source
+    all_of(rtrees_features), samesource
   ) %>%
@@
     ) %>%
-  # 5. Add abbreviations infront of barrel, bullet, and land labels
+  # 5. Add abbreviations in front of barrel, bullet, and land labels
   mutate(
@@
   mutate(case = as.character(1:n())) %>%
-  # 8. Reorder the variables
-  select(land_id1, land_id2, 
-         study1, barrel1, bullet1, study2, land1, barrel2, bullet2, land2,
-         all_of(rtrees_features), same_source)
+  # 8. Select final variables
+  select(case, land_id1, land_id2, all_of(rtrees_features), samesource)
 ```
@@
 
-The updated signature identification labels are included below:
+The land IDs in the cleaned bullet training data are separated in the code below, so that the updated signature identification labels can be included in the table below:
+
+```{r}
+bullet_train_expanded <- 
+  bullet_train %>% 
+  separate(col = land_id1, into = c("study1", "barrel1", "bullet1", "land1")) %>%
+  separate(col = land_id2, into = c("study2", "barrel2", "bullet2", "land2"))
+```
 
@@
 | --- | -------------- |
-| Study | `r unique(c(bullet_train$study1, bullet_train$study2))` |
-| Barrel | `r unique(c(bullet_train$barrel1, bullet_train$barrel2))` |
-| Bullet | `r unique(c(bullet_train$bullet1, bullet_train$bullet2))` |
-| Land | `r unique(c(bullet_train$land1, bullet_train$land2))` |
+| Study | `r unique(c(bullet_train_expanded$study1, bullet_train_expanded$study2))` |
+| Barrel | `r unique(c(bullet_train_expanded$barrel1, bullet_train_expanded$barrel2))` |
+| Bullet | `r unique(c(bullet_train_expanded$bullet1, bullet_train_expanded$bullet2))` |
+| Land | `r unique(c(bullet_train_expanded$land1, bullet_train_expanded$land2))` |
 

### 2020-09-28 paper.Rnw
fixed small typo in code
updated lime results with new bullet training data (using seed of 20200923 to "commemorate" the day when CCFs_withlands was found :)) and started work on updating paper based on results

--- 2020-09-16 paper.Rnw
@@
 <<bullet-data>>=
-
 # Load the bullet matching training and testing data
@@
 
-<<bullet-random-forest>>=
-
-# Extract the features
+<<bullet-rf>>=
+
+# Extract the features from the original random forest model (rtrees)
 bullet_features <- rownames(bulletxtrctr::rtrees$importance)
-
-# Create a path where the random forest will be saved
-bullet_rf_file = "data/bullet-rf.rds"
-if (file.exists(bullet_rf_file)) {
-  # Load the random forest
-  bullet_rf = readRDS(bullet_rf_file)
-} else {
-  # Fit the random forest to mimic rtrees
-  set.seed(20160104)
+bullet_rf_ntrees <- bulletxtrctr::rtrees$ntree
+bullet_rf_mtry <- bulletxtrctr::rtrees$mtry
+
+# Train a new random forest that mimics the rtrees models 
+# (or load if already trained)
+bullet_rf_file = "./data/bullet-rf.rds"
+if (!file.exists(bullet_rf_file)) {
+  set.seed(20200923) # the day that the updated data was found :)
   bullet_rf <-
@@
       y = factor(bullet_train$samesource),
-      x = bullet_train %>% select(all_of(bullet_features)),
-      ntree = bulletxtrctr::rtrees$ntree,
-      mtry = bulletxtrctr::rtrees$mtry
-    )
-  #Save the random forest
-  saveRDS(bullet_rf, bullet_rf_file)
+      x = bullet_train %>% select(bullet_features),
+      ntree = bullet_rf_ntrees,
+      mtry = bullet_rf_mtry
+    )  
+  saveRDS(object = bullet_rf, file = bullet_rf_file)
+} else {
+  bullet_rf = readRDS(file = bullet_rf_file)
 }
 
+# Add variables to both training and testing data with the random forest probability
+# that the signatures are a match from the model bullet_rf
+bullet_train$rfscore = predict(bullet_rf, bullet_train %>% select(bullet_features), type = "prob")[,2]
+bullet_test$rfscore = predict(bullet_rf, bullet_test %>% select(bullet_features), type = "prob")[,2]
+@
+
+<<bullet-feature-importance>>=
 # Order the features based on feature importance
@@
 # Create an ordered version of the data
-bullet_features_ordered <- bullet_features_ordered %>%
+bullet_features_ordered <-
+  bullet_features_ordered %>%
   mutate(feature = factor(feature, levels = bullet_features_ordered$feature))
-
-# Add a variables to training and testing data with random forest predictions
-bullet_train$rfscore = predict(bullet_rf, type = "prob")[,2]
-bullet_test$rfscore = predict(bullet_rf, bullet_test %>% select(bullet_features), type = "prob")[,2]
 
@@
 Nine features quantifying the similarity of signatures, such as the cross-correlation function, the distance between signatures, and the number of matching striae, are extracted and used to train a random forest (available in the \emph{bulletxtrctr} R package) to determine the probability of a comparison resulting from the same source (matching signatures) or from different sources (non-matching signatures).
-See the supporting information for additional information on the data.
-The model was trained on a set of scans of bullets from the James Hamby Consecutively Rifled Ruger Barrel Study \citep{hamby:2009}, which includes over 80,000 land-to-land comparisons.
+See the supporting information for \kge{definitions of the features \sout{additional information on the data}}.
+The model was trained on a set of scans of bullets from the James Hamby Consecutively Rifled Ruger Barrel Study \citep{hamby:2009}, which included \kge{10,384 land-to-land comparisons \citet{hare:2016}}.
 
@@
 if (!file.exists("figure-static/figure-08-1.eps")) {
-  unzip("figure-static/figure-08-1.png.zip")
+  unzip(zipfile = "figure-static/figure-08-1.png.zip", exdir = "figure-static")
   bullets <- image_read("figure-static/figure-08-1.png")
@@
     ) %>%
-    na.omit() %>%
     arrange(rfscore) %>%
@@
 
-We apply the trained random forest model from \citet{hare:2016} to another set of bullets from the Hamby study with \Sexpr{dim(bullet_test)[1]} rows of land comparisons.
+\kge{We train a new random forest model using \Sexpr{format(dim(bullet_train)[1], big.mark = ",")} land-to-land comparisons from bullets in the James Hamby Consecutively Rifled Ruger Barrel Study \citep{hamby:2009} using the same nine comparison features used by \citet{hare:2016} to predict whether the two lands are a match.} We apply the trained random forest model to another set of bullets from the Hamby study with \Sexpr{dim(bullet_test)[1]} rows of land comparisons.
+\kge{See the supporting information for further descriptions of the data.}
+
 We first consider a global visualization of the relationship between the random forest predictions and the model features with a parallel coordinate plot of the training data (top facet) and testing data (bottom facets) predictions (\autoref{fig:figure-10}).
-The majority of same source observations with random forest probabilities close to 1 have a clear pattern of corresponding feature values.
+\kgc{May want to change the next sentence a bit now:} The majority of same source observations with random forest probabilities close to 1 have a clear pattern of corresponding feature values.
 The known same source observations where the random forest is wrong (does not return probabilities close to 1) have feature values that reflect those of observations where same source is known to be false.
@@
 
-  # Apply lime with various input options to the hamby data
+  # Apply lime with various input options to the Hamby data
   bullet_lime_explain_noperms <- apply_lime(
-    train = bullet_train %>% select(all_of(bullet_features)),
+    train = bullet_train %>%
+      select(all_of(bullet_features)),
     test = bullet_test %>%
-      select(all_of(bullet_features)) %>%
-      na.omit(),
+      select(all_of(bullet_features)),
     model = bullet_rf,
@@
 
-First, the density simulation methods produce the same explanations for almost all cases and LIME tuning parameter values suggesting the LIME explanations are global and not local.
+\kgc{Will need to edit this paragraph:} First, the density simulation methods produce the same explanations for almost all cases and LIME tuning parameter values suggesting the LIME explanations are global and not local.
 Second, within a bin based simulation method, the features selected by LIME for an observation often vary by the number of bins but do not appear to vary by the Gower power.
@@
 @
-\caption{Assessment metric plot for the applications of LIME on the bullet comparison data test set.
+\caption{\kgc{Need to edit this:} Assessment metric plot for the applications of LIME on the bullet comparison data test set.
 The density simulation methods perform well for all metrics.
@@
 To try to identify a set of LIME tuning parameter values with the most trustworthy set of explanations, an assessment metric plot is considered (\autoref{fig:figure-12}).
-All density simulation methods performed well based on the three metrics.
+\kgc{Need to edit the rest of this paragraph:} All density simulation methods performed well based on the three metrics.
 This is an interesting result, since \autoref{fig:figure-11} shows that the density methods results in global explanations.
@@
 
-First, focus on the explanation for case NM with 3 quantile bins.
+\kgc{Need to edit this pargraph:} First, focus on the explanation for case NM with 3 quantile bins.
 The explanation plot from \emph{lime} shows that an observed CCF value greater than 0.320 supports a random forest prediction in favor of a match, and the scatter plots show that many of the simulated values with CCF greater then 0.320 have random forest predictions greater than 0.5.
@@
 
-The other explanation scatterplots can be interpreted in a similar manner.
+\kgc{Maybe edit this pargraph:} The other explanation scatterplots can be interpreted in a similar manner.
 Overall, the plots identify that the 3 quantile bin explanations are not faithful to the random forest model predictions.
@@
   ) +
-  bullet_eoi_plot_theme
+  bullet_eoi_plot_theme + 
+  guides(linetype = guide_legend(override.aes = list(color = c("darkorange"))))
 eoiNM_3eb <-
@@
 
-Even with an explainer model that is interpreted correctly, the interpretation is worthless if the explainer model is not \textbf{faithful} to the complex model.
+\kgc{Need to make some edits in this paragraph:} Even with an explainer model that is interpreted correctly, the interpretation is worthless if the explainer model is not \textbf{faithful} to the complex model.
 This claim can be assessed using the diagnostic plots suggested in this paper.
@@
 
-The final claim, \textbf{localness}, is addressed by the feature heatmap and metric comparison plots.
+\kgc{Probably need to make some edits here:} The final claim, \textbf{localness}, is addressed by the feature heatmap and metric comparison plots.
 As stated, the feature heatmap reveals that the density simulation methods in the examples of this paper results in global explanations where the same features are repeatedly chosen across all (or almost all) observations in the set of explanations.

### 2020-09-28 paper.tex
fixed small typo in code
updated lime results with new bullet training data (using seed of 20200923 to "commemorate" the day when CCFs_withlands was found :)) and started work on updating paper based on results

--- 2020-09-16 paper.tex
@@
 
-We apply the trained random forest model from \citet{hare:2016} to another set of bullets from the Hamby study with 364 rows of land comparisons.
+\kge{We train a new random forest model using 83,028 land-to-land comparisons from bullets in the James Hamby Consecutively Rifled Ruger Barrel Study \citep{hamby:2009} using the same nine comparison features used by \citet{hare:2016} to predict whether the two lands are a match.} We apply the trained random forest model to another set of bullets from the Hamby study with 364 rows of land comparisons.
+\kge{See the supporting information for further descriptions of the data.}
+
 We first consider a global visualization of the relationship between the random forest predictions and the model features with a parallel coordinate plot of the training data (top facet) and testing data (bottom facets) predictions (\autoref{fig:figure-10}).
-The majority of same source observations with random forest probabilities close to 1 have a clear pattern of corresponding feature values.
+\kgc{May want to change the next sentence a bit now:} The majority of same source observations with random forest probabilities close to 1 have a clear pattern of corresponding feature values.
 The known same source observations where the random forest is wrong (does not return probabilities close to 1) have feature values that reflect those of observations where same source is known to be false.
@@
 \end{knitrout}
-\caption{Assessment metric plot for the applications of LIME on the bullet comparison data test set.
+\caption{\kgc{Need to edit this:} Assessment metric plot for the applications of LIME on the bullet comparison data test set.
 The density simulation methods perform well for all metrics.
@@
 \begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
 
-{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in `[[<-.data.frame`(`*tmp*`, i, value = c("{}grey50"{}, "{}darkorange"{}: replacement has 2 rows, data has 1}}\end{kframe}
+{\centering \includegraphics[width=6.25in]{figure/figure-13-1}
+
+}
+
 \end{knitrout}

### 2020-09-28 README.Rmd
remove line break
added to Heike's description of the data and some other updates to files in the repo

--- 2020-09-26 README.Rmd
@@
 always_allow_html: yes
+bibliography: references.bib
 ---
@@
 
+- Move all code and results from our work identifying the data to my LIME-research-journals repo for future reference (including LIME explanations from different training datasets/models)
+- Rewrite Sections 4 and 5 as needed
+- Prepare for submission
 - Edit dataset descriptions in README and add to the readme.txt document for submission
@@
 
-- `data-preparation.Rmd` contains R code for preparing the raw bullet data (bullet training data, bullet testing data, and example matching signatures) to be used in the manuscript and saves zip versions of the data sets to be uploaded to GitHub
-- `figure-compression.Rmd` contains R code for compressing the static figure used in the manuscript to be uploaded to GitHub
-- `submission-steps.Rmd` contains the to do list and R code for preparing the files for submission to the ASA Data Science Journal.
+- `01-raw-file-compression.Rmd/.html` contains R code for compressing the static figure used in the manuscript and accessing and compressing the raw bullet data to be uploaded to GitHub
+- `02-data-preparation.Rmd/.html` contains R code for preparing the raw bullet data (bullet training data, bullet testing data, and example matching signatures) to be used in the manuscript and saves zip versions of the prepared data sets to be uploaded to GitHub
+- `03-submission-steps.Rmd/.html` contains the to do list and R code for preparing the files for submission to the ASA Data Science Journal
 
@@
 - `bullet-test.csv.zip` and `bullet-test.csv.zip` contain the data used for the bullet examples in the manuscript.
-Additional information about these files is included below under the heading "Additional Information on Bullet Data".
+See ""Additional Information on Bullet Data" below for more information about the data.
 - `example-signatures.csv.zip` contains signature data from two matching bullet lands that is used to generate a figure in the manuscript.
-- `raw` contains the raw versions of the data files (from Heike and CSAFE) that the above datasets are derived from. *Do not alter the data in these files.*
+- `raw` contains the raw versions of the data files (from Heike and CSAFE) that the above datasets are derived from. *Do not alter the data in these files.*:
+  - `CCFs_withlands.csv.zip`: raw version of the bullet training data
+  - `h224-set1-features.rds.zip` and `h224-set11-features.rds.zip`: raw versions of the bullet testing data
+  - `signatures.rds.zip`: raw version of the example matching signatures data
+- `readme.txt` contains descriptions of the data files provided with the submission of the paper.
 
@@
 - `figure-08-1.png.zip` is the one figure in the manuscript that is not generated using R code.
-- `figure-readme.png` is a figure used in the readme.
+- `figure-readme.png` is a figure used in this readme.
 
@@
 
-Contains the files associated with an old version of the manuscript that is much longer the the submitted version
+Contains the files associated with an old version of the manuscript that is much longer than the submitted version.
 
@@
 These files are moved to this folder using code in the file `code/submission-steps.R`.
-The only figures not included on GitHub are the EPS figures that are submitted due to size constraints.
+The only submission files not included on GitHub are the EPS figures due to size constraints.
 
@@
 - `README.Rmd` and `README.md` are the readme files that generated this output.
-- `readme.txt` contains descriptions of the data files that are included with the submission
-- `references.bib` contains the bibtex information for the references in the manuscript
+- `references.bib` contains the bibtex information for the references in the manuscript.
 - `WileyNJG-AMS.bst` and `WileyNJG-v2.cls` contain the latex formatting specifications for the ASA Data Science Journal.
@@
 
-The data used in the manuscript for the bullet comparison examples is described below. Note that this text is also included in the file readme.txt that is submitted with the manuscript.
+The data used in the manuscript for the bullet comparison examples is described below. Note that this text is also included in the file `data/readme.txt` that is submitted with the manuscript.
 
-**`bullet-train`**
+### `bullet-train.csv`
 
-A dataset with `r dim(bullet_train)[1]` rows and `r dim(bullet_train)[2]` columns that contains comparison features based on high resolution microscopy scans of fired bullets from Hamby sets 173 and 252 [@hamby].
+The [<b>bullet_train</b>](data/bullet_train.csv) data has `r format(dim(bullet_train)[1], big.mark = ",")` rows and `r dim(bullet_train)[2]` columns that contain comparison features described in @hare:2016 based on high resolution microscopy scans of fired bullets from Hamby sets 173 and 252 [@hamby:2009].
 This dataset is created from the x3p scans of bullet land engraved areas available from the [NIST Ballistics Toolmark Research Database](https://tsapps.nist.gov/NRBTD/).
@@
 Another bullet (Bullet E from Hamby 173) is excluded because it could not be matched visually to the barrel it was supposedly from (see [scans from bullet E](LEAscans/bullete.md)).
-The <b>bullet_train</b> data is based on a set of features extracted from the x3p scans as described in @hare:2016.
-The raw file of comparison features is found [here](data/raw/hamby-comparisons.csv.zip).
-The only changes made to the data were XXX I think the following statement needs to be adjusted XXX to select only variables of use for the manuscript, add a case variable, rename `same_source` as `samesource`, and attach the random forest scores associated with the comparisons.
-The variables in the data are as follows:
+
+[<b>bullet_train</b>](data/bullet_train.csv) is generated from the raw file of comparison features, which is found [here](data/raw/CCFs_withlands.csv.zip).
+The steps taken to create **bullet_train** from the raw data are found [here](code/02-data-preparation.Rmd).
+These steps involve renaming some variables, selecting the variables of interest for the manuscript, and adjusting the land IDs associated with the signatures.
+
+The variables in the data are described below. Further descriptions of the comparison features are found in @hare:2016.
 
 #### Variables used as key variables:
+
 - `r names(bullet_train)[1]`: ID number associated with the bullet-land signature comparison.
-- `r names(bullet_train)[2]`, `r names(bullet_train)[3]`: IDs describing the two land engraved areas in the comparison. The format is 'study - barrel number - bullet number - land number'.
+- `r names(bullet_train)[2]`, `r names(bullet_train)[3]`: IDs describing the two land engraved areas in the comparison. The format is `study-barrelnumber-bulletnumber-landnumber`.
 
-#### Comparison features
-- `r names(bullet_train)[4]`: maximized cross-correlation between two LEA signatures.
-- `r names(bullet_train)[5]`: correlation after detrending aligned signatures.
+#### Comparison features:
+
+- `r names(bullet_train)[4]`: Maximized cross-correlation between two LEA signatures.
+- `r names(bullet_train)[5]`: Correlation after detrending aligned signatures.
 - `r names(bullet_train)[6]`: Euclidean distance (in millimeters) between two aligned signatures.
-- `r names(bullet_train)[7]`: standard deviation of the previous measure along the signature.
-- `r names(bullet_train)[8]`, `r names(bullet_train)[9]`: number of matching/non-matching peaks and valleys in the aligned signatures.
-- `r names(bullet_train)[10]`: consecutively matching striae is a measure introduced by @biasotti describing the longest run of matching peaks between two aligned signatures.
-- `r names(bullet_train)[11]`: the number of consecutively non-matching peaks.
-- `r names(bullet_train)[12]`: the depth of peaks measured as the sum of matching peaks between two aligned signatures (in microns).
-- `r names(bullet_train)[13]`: ground truth whether a pair is from the same source (`TRUE`) or from different sources (`FALSE`).
-- `r names(bullet_train)[14]`: the random forest score associated with the comparison in support of a match.
+- `r names(bullet_train)[7]`: Standard deviation of the previous measure along the signature.
+- `r names(bullet_train)[8]`, `r names(bullet_train)[9]`: Number of matching/non-matching peaks and valleys in the aligned signatures.
+- `r names(bullet_train)[10]`: Consecutively matching striae is a measure introduced by @biasotti:1959 describing the longest run of matching peaks between two aligned signatures.
+- `r names(bullet_train)[11]`: The number of consecutively non-matching peaks.
+- `r names(bullet_train)[12]`: The depth of peaks measured as the sum of matching peaks between two aligned signatures (in microns).
+- `r names(bullet_train)[13]`: Ground truth whether a pair is from the same source (`TRUE`) or from different sources (`FALSE`).
 
-<!--For further details about the signatures comparison features, see XXX.-->
+### `bullet-test.csv`
 
-**`bullet-test`**
-
-A dataset with `r dim(bullet_test)[1]` rows and `r dim(bullet_test)[2]` columns that contains comparison features from test sets 1 and 11 of the Hamby 224 Clone sets.
+[**bullet-test.csv**](data/bullet_test.csv.zip) has `r dim(bullet_test)[1]` rows and `r dim(bullet_test)[2]` columns that contains comparison features from test sets 1 and 11 of the Hamby 224 Clone Test Sets.
 Each test set is arranged as a combination of three bullets: two known bullets and a questioned bullet.
@@
 This is due to the fact that some of the lands are missing from the data (due to tank rash): land 4 from the unknown bullet in set 1, land 2 from bullet 1 in set 11, and land 4 from the unknown bullet in set 11.
+[**bullet-test.csv**](data/bullet_test.csv.zip) is generated from the raw versions of the data found [here](data/raw/h224-set1-features.rds.zip) and [here](data/raw/h224-set11-features.rds.zip).
 The variables in the test data are the same as the training data described above.
 
-<!-- For further details about the signatures comparison features, see XXX.-->
+### `example-signatures.csv`
 
-**`example-signatures`**
-
-Contains the signature data from aligned signatures of two bullet-lands from the same source. The variables in the data are as follows:
+[**example-signatures.csv**](data/example-signatures.csv.zip) contains the signature data from aligned signatures of two bullet-lands from the same source. The variables in the data are as follows:
 

### 2020-09-28 README.Rmd
fixed some link typos

@@
 
-The [<b>bullet_train</b>](data/bullet_train.csv) data has `r format(dim(bullet_train)[1], big.mark = ",")` rows and `r dim(bullet_train)[2]` columns that contain comparison features described in @hare:2016 based on high resolution microscopy scans of fired bullets from Hamby sets 173 and 252 [@hamby:2009].
+The [<b>bullet_train</b>](data/bullet_train.csv.zip) data has `r format(dim(bullet_train)[1], big.mark = ",")` rows and `r dim(bullet_train)[2]` columns that contain comparison features described in @hare:2016 based on high resolution microscopy scans of fired bullets from Hamby sets 173 and 252 [@hamby:2009].
 This dataset is created from the x3p scans of bullet land engraved areas available from the [NIST Ballistics Toolmark Research Database](https://tsapps.nist.gov/NRBTD/).
@@
 
-[<b>bullet_train</b>](data/bullet_train.csv) is generated from the raw file of comparison features, which is found [here](data/raw/CCFs_withlands.csv.zip).
+**bullet_train** is generated from the raw file of comparison features, which is found [here](data/raw/CCFs_withlands.csv.zip).
 The steps taken to create **bullet_train** from the raw data are found [here](code/02-data-preparation.Rmd).
@@
 
-[**bullet-test.csv**](data/bullet_test.csv.zip) has `r dim(bullet_test)[1]` rows and `r dim(bullet_test)[2]` columns that contains comparison features from test sets 1 and 11 of the Hamby 224 Clone Test Sets.
+[**bullet-test.csv**](data/bullet-test.csv.zip) has `r dim(bullet_test)[1]` rows and `r dim(bullet_test)[2]` columns that contains comparison features from test sets 1 and 11 of the Hamby 224 Clone Test Sets.
 Each test set is arranged as a combination of three bullets: two known bullets and a questioned bullet.
@@
 This is due to the fact that some of the lands are missing from the data (due to tank rash): land 4 from the unknown bullet in set 1, land 2 from bullet 1 in set 11, and land 4 from the unknown bullet in set 11.
-[**bullet-test.csv**](data/bullet_test.csv.zip) is generated from the raw versions of the data found [here](data/raw/h224-set1-features.rds.zip) and [here](data/raw/h224-set11-features.rds.zip).
+**bullet-test.csv** is generated from the raw versions of the data found [here](data/raw/h224-set1-features.rds.zip) and [here](data/raw/h224-set11-features.rds.zip).
 The variables in the test data are the same as the training data described above.
@@
 
-- `r names(signatures)[1]`: Indicator variable whether the observation corresponds to 'Signature 1' or 'Signature 2'
-- `r names(signatures)[2]`: the (relative) x position of the signature (in microns)
-- `r names(signatures)[3]`: the (relative) y position of the signature height (in microns)
+- `r names(signatures)[1]`: Indicator variable whether the observation corresponds to "Signature 1" or "Signature 2".
+- `r names(signatures)[2]`: The (relative) x position of the signature (in microns).
+- `r names(signatures)[3]`: The (relative) y position of the signature height (in microns).
 

### 2020-09-28 paper.Rnw
knit paper after updating label for hare paper from hare:2016 to hare:2017

@@
 
-In response, \citet{hare:2016} proposed an automated machine learning method for bullet matching to complement a visual inspection by firearm examiners.
-Based on high-resolution topological scans of land engraved areas, \citet{hare:2016} obtain signatures of striations from two bullet lands (\autoref{fig:figure-09}).
+In response, \citet{hare:2017} proposed an automated machine learning method for bullet matching to complement a visual inspection by firearm examiners.
+Based on high-resolution topological scans of land engraved areas, \citet{hare:2017} obtain signatures of striations from two bullet lands (\autoref{fig:figure-09}).
 Nine features quantifying the similarity of signatures, such as the cross-correlation function, the distance between signatures, and the number of matching striae, are extracted and used to train a random forest (available in the \emph{bulletxtrctr} R package) to determine the probability of a comparison resulting from the same source (matching signatures) or from different sources (non-matching signatures).
 See the supporting information for \kge{definitions of the features \sout{additional information on the data}}.
-The model was trained on a set of scans of bullets from the James Hamby Consecutively Rifled Ruger Barrel Study \citep{hamby:2009}, which included \kge{10,384 land-to-land comparisons \citet{hare:2016}}.
+The model was trained on a set of scans of bullets from the James Hamby Consecutively Rifled Ruger Barrel Study \citep{hamby:2009}, which included \kge{10,384 land-to-land comparisons \citet{hare:2017}}.
 
@@
 The bullet signatures correspond to the same land and therefore have very similar patterns.
-The \citet{hare:2016} random forest is fit using various features that measure the similarity between two such signatures.}
+The \citet{hare:2017} random forest is fit using various features that measure the similarity between two such signatures.}
 \label{fig:figure-09}
@@
 @
-\caption{Parallel coordinate plots of the \citet{hare:2016} random forest predictions from the training (top facet) and testing (bottom facet) data.
+\caption{Parallel coordinate plots of the \citet{hare:2017} random forest predictions from the training (top facet) and testing (bottom facet) data.
 The observations are separated by known matching (right column) and non-matching (left column) signatures.
@@
 
-\kge{We train a new random forest model using \Sexpr{format(dim(bullet_train)[1], big.mark = ",")} land-to-land comparisons from bullets in the James Hamby Consecutively Rifled Ruger Barrel Study \citep{hamby:2009} using the same nine comparison features used by \citet{hare:2016} to predict whether the two lands are a match.} We apply the trained random forest model to another set of bullets from the Hamby study with \Sexpr{dim(bullet_test)[1]} rows of land comparisons.
+\kge{We train a new random forest model using \Sexpr{format(dim(bullet_train)[1], big.mark = ",")} land-to-land comparisons from bullets in the James Hamby Consecutively Rifled Ruger Barrel Study \citep{hamby:2009} using the same nine comparison features used by \citet{hare:2017} to predict whether the two lands are a match.} We apply the trained random forest model to another set of bullets from the Hamby study with \Sexpr{dim(bullet_test)[1]} rows of land comparisons.
 \kge{See the supporting information for further descriptions of the data.}

### 2020-09-28 paper.tex
knit paper after updating label for hare paper from hare:2016 to hare:2017

@@
 \end{knitrout}
-\caption{Parallel coordinate plots of the \citet{hare:2016} random forest predictions from the training (top facet) and testing (bottom facet) data.
+\caption{Parallel coordinate plots of the \citet{hare:2017} random forest predictions from the training (top facet) and testing (bottom facet) data.
 The observations are separated by known matching (right column) and non-matching (left column) signatures.
@@
 
-\kge{We train a new random forest model using 83,028 land-to-land comparisons from bullets in the James Hamby Consecutively Rifled Ruger Barrel Study \citep{hamby:2009} using the same nine comparison features used by \citet{hare:2016} to predict whether the two lands are a match.} We apply the trained random forest model to another set of bullets from the Hamby study with 364 rows of land comparisons.
+\kge{We train a new random forest model using 83,028 land-to-land comparisons from bullets in the James Hamby Consecutively Rifled Ruger Barrel Study \citep{hamby:2009} using the same nine comparison features used by \citet{hare:2017} to predict whether the two lands are a match.} We apply the trained random forest model to another set of bullets from the Hamby study with 364 rows of land comparisons.
 \kge{See the supporting information for further descriptions of the data.}

### 2020-09-28 README.Rmd
added description of LEAscans folder

@@
 
+**`LEAscans`**
+
+Contains information on the land engraved areas (LEAs) excluded from the Hamby bullets used to create the training data.
+
 **`old-version`**
@@
 
-The [<b>bullet_train</b>](data/bullet_train.csv.zip) data has `r format(dim(bullet_train)[1], big.mark = ",")` rows and `r dim(bullet_train)[2]` columns that contain comparison features described in @hare:2016 based on high resolution microscopy scans of fired bullets from Hamby sets 173 and 252 [@hamby:2009].
+The [<b>bullet_train</b>](data/bullet_train.csv.zip) data has `r format(dim(bullet_train)[1], big.mark = ",")` rows and `r dim(bullet_train)[2]` columns that contain comparison features described in @hare:2017 based on high resolution microscopy scans of fired bullets from Hamby sets 173 and 252 [@hamby:2009].
 This dataset is created from the x3p scans of bullet land engraved areas available from the [NIST Ballistics Toolmark Research Database](https://tsapps.nist.gov/NRBTD/).
@@
 
-The variables in the data are described below. Further descriptions of the comparison features are found in @hare:2016.
+The variables in the data are described below. Further descriptions of the comparison features are found in @hare:2017.
 

### 2020-09-28 README.Rmd
fixed one more link typo

@@
 
-The [<b>bullet_train</b>](data/bullet_train.csv.zip) data has `r format(dim(bullet_train)[1], big.mark = ",")` rows and `r dim(bullet_train)[2]` columns that contain comparison features described in @hare:2017 based on high resolution microscopy scans of fired bullets from Hamby sets 173 and 252 [@hamby:2009].
+The [<b>bullet_train</b>](data/bullet-train.csv.zip) data has `r format(dim(bullet_train)[1], big.mark = ",")` rows and `r dim(bullet_train)[2]` columns that contain comparison features described in @hare:2017 based on high resolution microscopy scans of fired bullets from Hamby sets 173 and 252 [@hamby:2009].
 This dataset is created from the x3p scans of bullet land engraved areas available from the [NIST Ballistics Toolmark Research Database](https://tsapps.nist.gov/NRBTD/).

### 2020-09-28 README.Rmd
changed description

@@
 This is due to the fact that some of the lands are missing from the data (due to tank rash): land 4 from the unknown bullet in set 1, land 2 from bullet 1 in set 11, and land 4 from the unknown bullet in set 11.
-**bullet-test.csv** is generated from the raw versions of the data found [here](data/raw/h224-set1-features.rds.zip) and [here](data/raw/h224-set11-features.rds.zip).
+**bullet-test.csv** is generated from the raw versions of the data for [set 1](data/raw/h224-set1-features.rds.zip) and [set 11](data/raw/h224-set11-features.rds.zip).
 The variables in the test data are the same as the training data described above.

### 2020-09-28 README.Rmd
fixed another typo

@@
 
-The [<b>bullet_train</b>](data/bullet-train.csv.zip) data has `r format(dim(bullet_train)[1], big.mark = ",")` rows and `r dim(bullet_train)[2]` columns that contain comparison features described in @hare:2017 based on high resolution microscopy scans of fired bullets from Hamby sets 173 and 252 [@hamby:2009].
+The [<b>bullet-train.csv</b>](data/bullet-train.csv.zip) data has `r format(dim(bullet_train)[1], big.mark = ",")` rows and `r dim(bullet_train)[2]` columns that contain comparison features described in @hare:2017 based on high resolution microscopy scans of fired bullets from Hamby sets 173 and 252 [@hamby:2009].
 This dataset is created from the x3p scans of bullet land engraved areas available from the [NIST Ballistics Toolmark Research Database](https://tsapps.nist.gov/NRBTD/).
@@
 
-**bullet_train** is generated from the raw file of comparison features, which is found [here](data/raw/CCFs_withlands.csv.zip).
-The steps taken to create **bullet_train** from the raw data are found [here](code/02-data-preparation.Rmd).
+**bullet-train** is generated from the raw file of comparison features, which is found [here](data/raw/CCFs_withlands.csv.zip).
+The steps taken to create **bullet-train** from the raw data are found [here](code/02-data-preparation.Rmd).
 These steps involve renaming some variables, selecting the variables of interest for the manuscript, and adjusting the land IDs associated with the signatures.

### 2020-09-28 README.Rmd
small changes

@@
 
-The [<b>bullet-train.csv</b>](data/bullet-train.csv.zip) data has `r format(dim(bullet_train)[1], big.mark = ",")` rows and `r dim(bullet_train)[2]` columns that contain comparison features described in @hare:2017 based on high resolution microscopy scans of fired bullets from Hamby sets 173 and 252 [@hamby:2009].
+The [<b>bullet-train</b>](data/bullet-train.csv.zip) data has `r format(dim(bullet_train)[1], big.mark = ",")` rows and `r dim(bullet_train)[2]` columns that contain comparison features described in @hare:2017 based on high resolution microscopy scans of fired bullets from Hamby sets 173 and 252 [@hamby:2009].
 This dataset is created from the x3p scans of bullet land engraved areas available from the [NIST Ballistics Toolmark Research Database](https://tsapps.nist.gov/NRBTD/).
@@
 
-[**bullet-test.csv**](data/bullet-test.csv.zip) has `r dim(bullet_test)[1]` rows and `r dim(bullet_test)[2]` columns that contains comparison features from test sets 1 and 11 of the Hamby 224 Clone Test Sets.
+[**bullet-test**](data/bullet-test.csv.zip) has `r dim(bullet_test)[1]` rows and `r dim(bullet_test)[2]` columns that contains comparison features from test sets 1 and 11 of the Hamby 224 Clone Test Sets.
 Each test set is arranged as a combination of three bullets: two known bullets and a questioned bullet.
@@
 This is due to the fact that some of the lands are missing from the data (due to tank rash): land 4 from the unknown bullet in set 1, land 2 from bullet 1 in set 11, and land 4 from the unknown bullet in set 11.
-**bullet-test.csv** is generated from the raw versions of the data for [set 1](data/raw/h224-set1-features.rds.zip) and [set 11](data/raw/h224-set11-features.rds.zip).
+**bullet-test** is generated from the raw versions of the data for [set 1](data/raw/h224-set1-features.rds.zip) and [set 11](data/raw/h224-set11-features.rds.zip).
 The variables in the test data are the same as the training data described above.
@@
 
-[**example-signatures.csv**](data/example-signatures.csv.zip) contains the signature data from aligned signatures of two bullet-lands from the same source. The variables in the data are as follows:
+[**example-signatures**](data/example-signatures.csv.zip) contains the signature data from aligned signatures of two bullet-lands from the same source. The variables in the data are as follows:
 

### 2020-09-28 README.Rmd
removed item from to do list

@@
 - Prepare for submission
-- Edit dataset descriptions in README and add to the readme.txt document for submission
 - Upload the files for submission and submit

### 2020-09-28 README.Rmd
added more file links

@@
 
-- Move all code and results from our work identifying the data to my LIME-research-journals repo for future reference (including LIME explanations from different training datasets/models)
+- Finish documenting the identification of the training data for rtrees in research journals (including LIME explanations from different training datasets/models)
 - Rewrite Sections 4 and 5 as needed
@@
 
-**`code`**
+[**`code`**](code)
 
@@
 
-- `01-raw-file-compression.Rmd/.html` contains R code for compressing the static figure used in the manuscript and accessing and compressing the raw bullet data to be uploaded to GitHub
-- `02-data-preparation.Rmd/.html` contains R code for preparing the raw bullet data (bullet training data, bullet testing data, and example matching signatures) to be used in the manuscript and saves zip versions of the prepared data sets to be uploaded to GitHub
-- `03-submission-steps.Rmd/.html` contains the to do list and R code for preparing the files for submission to the ASA Data Science Journal
+- [`01-raw-file-compression.Rmd`](code/01-raw-file-compression.Rmd)/`.html` contains R code for compressing the static figure used in the manuscript and accessing and compressing the raw bullet data to be uploaded to GitHub
+- [`02-data-preparation.Rmd`](code/02-data-preparation.Rmd)`/.html` contains R code for preparing the raw bullet data (bullet training data, bullet testing data, and example matching signatures) to be used in the manuscript and saves zip versions of the prepared data sets to be uploaded to GitHub
+- [`03-submission-steps.Rmd`](code/03-submission-steps.Rmd)`/.html` contains the to do list and R code for preparing the files for submission to the ASA Data Science Journal
 
-**`cover-letter`**
+[**`cover-letter`**](cover-letter)
 
@@
 
-**`data`**
+[**`data`**](data/)
 
@@
 
-- `bullet-test.csv.zip` and `bullet-test.csv.zip` contain the data used for the bullet examples in the manuscript.
+- [`bullet-train.csv.zip`](data/bullet-train.csv.zip) and [`bullet-test.csv.zip`](data/bullet-test.csv.zip) contain the data used for the bullet examples in the manuscript.
 See ""Additional Information on Bullet Data" below for more information about the data.
-- `example-signatures.csv.zip` contains signature data from two matching bullet lands that is used to generate a figure in the manuscript.
-- `raw` contains the raw versions of the data files (from Heike and CSAFE) that the above datasets are derived from. *Do not alter the data in these files.*:
-  - `CCFs_withlands.csv.zip`: raw version of the bullet training data
-  - `h224-set1-features.rds.zip` and `h224-set11-features.rds.zip`: raw versions of the bullet testing data
-  - `signatures.rds.zip`: raw version of the example matching signatures data
-- `readme.txt` contains descriptions of the data files provided with the submission of the paper.
+- [`example-signatures.csv.zip`](data/example-signatures.csv.zip) contains signature data from two matching bullet lands that is used to generate a figure in the manuscript.
+- [`raw`](data/raw) contains the raw versions of the data files (from Heike and CSAFE) that the above datasets are derived from. *Do not alter the data in these files.*:
+  - [`CCFs_withlands.csv.zip`](data/raw/CCFs_withlands.csv.zip): raw version of the bullet training data
+  - [`h224-set1-features.rds.zip`](data/raw/h224-set1-features.rds.zip) and [`h224-set11-features.rds.zip`](data/raw/h224-set11-features.rds.zip): raw versions of the bullet testing data
+  - [`signatures.rds.zip`](data/raw/signatures.rds.zip): raw version of the example matching signatures data
+- [`readme.txt`](data/readme.txt) contains descriptions of the data files (and code files) provided with the submission of the paper.
 
-**`figure-static`**
+[**`figure-static`**](figure-static/)
 
@@
 
-- `figure-08-1.png.zip` is the one figure in the manuscript that is not generated using R code.
-- `figure-readme.png` is a figure used in this readme.
+- [`figure-08-1.png.zip`](figure-static/figure-08-1.png.zip) is the one figure in the manuscript that is not generated using R code.
+- [`figure-readme.png`](figure-static/figure-readme.png) is a figure used in this readme.
 
-**`LEAscans`**
+[**`LEAscans`**](LEAscans/)
 
@@
 
-**`old-version`**
+[**`old-version`**](old-version/)
 
@@
 
-**`submission`**
+[**`submission`**](submission)
 
@@
 
-- `.gitignore` contains objects to be ignored by git.
-- `paper.Rnw`, `paper.pdf`, and `paper.tex` are the manuscript. Note that `paper.pdf` and `paper.tex` are generated by `paper.Rnw`.
-- `README.Rmd` and `README.md` are the readme files that generated this output.
-- `references.bib` contains the bibtex information for the references in the manuscript.
-- `WileyNJG-AMS.bst` and `WileyNJG-v2.cls` contain the latex formatting specifications for the ASA Data Science Journal.
+- [`.gitignore`](.gitignore) contains objects to be ignored by git.
+- [`paper.Rnw`](paper.Rnw), [`paper.pdf`](paper.pdf), and [`paper.tex`](paper.tex) are the manuscript. Note that `paper.pdf` and `paper.tex` are generated by `paper.Rnw`.
+- [`README.Rmd`](README.Rmd) and [`README.md`](README.md) are the readme files that generated this output.
+- [`references.bib`](references.bib) contains the bibtex information for the references in the manuscript.
+- [`WileyNJG-AMS.bst`](WileyNJD-AMS.bst) and [`WileyNJG-v2.cls`](WileyNJD-v2.cls) contain the latex formatting specifications for the ASA Data Science Journal.
 

### 2020-09-28 README.Rmd
added extra links

@@
 
-- [`01-raw-file-compression.Rmd`](code/01-raw-file-compression.Rmd)/`.html` contains R code for compressing the static figure used in the manuscript and accessing and compressing the raw bullet data to be uploaded to GitHub
-- [`02-data-preparation.Rmd`](code/02-data-preparation.Rmd)`/.html` contains R code for preparing the raw bullet data (bullet training data, bullet testing data, and example matching signatures) to be used in the manuscript and saves zip versions of the prepared data sets to be uploaded to GitHub
-- [`03-submission-steps.Rmd`](code/03-submission-steps.Rmd)`/.html` contains the to do list and R code for preparing the files for submission to the ASA Data Science Journal
+- [`01-raw-file-compression.Rmd`](code/01-raw-file-compression.Rmd)/[`.html`](code/01-raw-file-compression.html) contains R code for compressing the static figure used in the manuscript and accessing and compressing the raw bullet data to be uploaded to GitHub
+- [`02-data-preparation.Rmd`](code/02-data-preparation.Rmd)/[`.html`](code/02-data-preparation.html) contains R code for preparing the raw bullet data (bullet training data, bullet testing data, and example matching signatures) to be used in the manuscript and saves zip versions of the prepared data sets to be uploaded to GitHub
+- [`03-submission-steps.Rmd`](code/03-submission-steps.Rmd)/[`.html`](code/03-submission-steps.html) contains the to do list and R code for preparing the files for submission to the ASA Data Science Journal
 

### 2020-09-28 README.Rmd
added even more links (I love them!)

@@
 - [`example-signatures.csv.zip`](data/example-signatures.csv.zip) contains signature data from two matching bullet lands that is used to generate a figure in the manuscript.
-- [`raw`](data/raw) contains the raw versions of the data files (from Heike and CSAFE) that the above datasets are derived from. *Do not alter the data in these files.*:
+- [`raw`](data/raw) contains the raw versions of the data files (from Heike and CSAFE) that the above datasets are derived from. *Do not alter the data in these files*:
   - [`CCFs_withlands.csv.zip`](data/raw/CCFs_withlands.csv.zip): raw version of the bullet training data
@@
 Contains the files submitted to the ASA Data Science Journal.
-These files are moved to this folder using code in the file `code/submission-steps.R`.
+These files are moved to this folder using code in the file [`code/03-submission-steps.R`](code/03-submission-steps.Rmd).
 The only submission files not included on GitHub are the EPS figures due to size constraints.
@@
 
-3. Knit manuscript (via the `paper.Rnw` file).
+3. Knit manuscript (via the [`paper.Rnw`](paper.Rnw) file).
 
@@
 
-The data used in the manuscript for the bullet comparison examples is described below. Note that this text is also included in the file `data/readme.txt` that is submitted with the manuscript.
+The data used in the manuscript for the bullet comparison examples is described below.
+Note that this text is also included in the file [`data/readme.txt`](data/readme.txt) that is submitted with the manuscript.
 
@@
 Note: The only figure that does not follow these values is Figure 11 where the facet labels were set to font size 5 (Helvetica) in order for them to fit appropriately.
+
+## References

### 2020-09-28 README.Rmd
formatting changes

--- 2020-09-28 README.Rmd
@@
 
-[**`code`**](code)
+[**code**](code)
 
-Contains the R code associated with the manuscript that is not directly included in `paper.Rnw` (such as some external data cleaning and file organization):
+Contains the R code associated with the manuscript that is not directly included in [paper.Rnw](paper.Rnw) (such as some external data cleaning and file organization):
 
-- [`01-raw-file-compression.Rmd`](code/01-raw-file-compression.Rmd)/`.html` contains R code for compressing the static figure used in the manuscript and accessing and compressing the raw bullet data to be uploaded to GitHub
-- [`02-data-preparation.Rmd`](code/02-data-preparation.Rmd)`/.html` contains R code for preparing the raw bullet data (bullet training data, bullet testing data, and example matching signatures) to be used in the manuscript and saves zip versions of the prepared data sets to be uploaded to GitHub
-- [`03-submission-steps.Rmd`](code/03-submission-steps.Rmd)`/.html` contains the to do list and R code for preparing the files for submission to the ASA Data Science Journal
+- [01-raw-file-compression.Rmd](code/01-raw-file-compression.Rmd)/[.html](code/01-raw-file-compression.html) contains R code for compressing the static figure used in the manuscript and accessing and compressing the raw bullet data to be uploaded to GitHub
+- [02-data-preparation.Rmd](code/02-data-preparation.Rmd)/[.html](code/02-data-preparation.html) contains R code for preparing the raw bullet data (bullet training data, bullet testing data, and example matching signatures) to be used in the manuscript and saves zip versions of the prepared data sets to be uploaded to GitHub
+- [03-submission-steps.Rmd](code/03-submission-steps.Rmd)/[.html](code/03-submission-steps.html) contains the to do list and R code for preparing the files for submission to the ASA Data Science Journal
 
-[**`cover-letter`**](cover-letter)
+[**cover-letter**](cover-letter)
 
@@
 
-[**`data`**](data/)
+[**data**](data/)
 
@@
 
-- [`bullet-train.csv.zip`](data/bullet-train.csv.zip) and [`bullet-test.csv.zip`](data/bullet-test.csv.zip) contain the data used for the bullet examples in the manuscript.
+- [bullet-train.csv.zip](data/bullet-train.csv.zip) and [bullet-test.csv.zip](data/bullet-test.csv.zip) contain the data used for the bullet examples in the manuscript.
 See ""Additional Information on Bullet Data" below for more information about the data.
-- [`example-signatures.csv.zip`](data/example-signatures.csv.zip) contains signature data from two matching bullet lands that is used to generate a figure in the manuscript.
-- [`raw`](data/raw) contains the raw versions of the data files (from Heike and CSAFE) that the above datasets are derived from. *Do not alter the data in these files.*:
-  - [`CCFs_withlands.csv.zip`](data/raw/CCFs_withlands.csv.zip): raw version of the bullet training data
-  - [`h224-set1-features.rds.zip`](data/raw/h224-set1-features.rds.zip) and [`h224-set11-features.rds.zip`](data/raw/h224-set11-features.rds.zip): raw versions of the bullet testing data
-  - [`signatures.rds.zip`](data/raw/signatures.rds.zip): raw version of the example matching signatures data
-- [`readme.txt`](data/readme.txt) contains descriptions of the data files (and code files) provided with the submission of the paper.
+- [example-signatures.csv.zip](data/example-signatures.csv.zip) contains signature data from two matching bullet lands that is used to generate a figure in the manuscript.
+- [raw](data/raw) contains the raw versions of the data files (from Heike and CSAFE) that the above datasets are derived from. *Do not alter the data in these files*:
+  - [CCFs_withlands.csv.zip](data/raw/CCFs_withlands.csv.zip): raw version of the bullet training data
+  - [h224-set1-features.rds.zip](data/raw/h224-set1-features.rds.zip) and [h224-set11-features.rds.zip](data/raw/h224-set11-features.rds.zip): raw versions of the bullet testing data
+  - [signatures.rds.zip](data/raw/signatures.rds.zip): raw version of the example matching signatures data
+- [readme.txt](data/readme.txt) contains descriptions of the data files (and code files) provided with the submission of the paper.
 
-[**`figure-static`**](figure-static/)
+[**figure-static**](figure-static/)
 
@@
 
-- [`figure-08-1.png.zip`](figure-static/figure-08-1.png.zip) is the one figure in the manuscript that is not generated using R code.
-- [`figure-readme.png`](figure-static/figure-readme.png) is a figure used in this readme.
+- [figure-08-1.png.zip](figure-static/figure-08-1.png.zip) is the one figure in the manuscript that is not generated using R code.
+- [figure-readme.png](figure-static/figure-readme.png) is a figure used in this readme.
 
-[**`LEAscans`**](LEAscans/)
+[**LEAscans**](LEAscans/)
 
@@
 
-[**`old-version`**](old-version/)
+[**old-version**](old-version/)
 
@@
 
-[**`submission`**](submission)
+[**submission**](submission)
 
 Contains the files submitted to the ASA Data Science Journal.
-These files are moved to this folder using code in the file `code/submission-steps.R`.
+These files are moved to this folder using code in the file [code/03-submission-steps.R](code/03-submission-steps.Rmd).
 The only submission files not included on GitHub are the EPS figures due to size constraints.
@@
 
-- [`.gitignore`](.gitignore) contains objects to be ignored by git.
-- [`paper.Rnw`](paper.Rnw), [`paper.pdf`](paper.pdf), and [`paper.tex`](paper.tex) are the manuscript. Note that `paper.pdf` and `paper.tex` are generated by `paper.Rnw`.
-- [`README.Rmd`](README.Rmd) and [`README.md`](README.md) are the readme files that generated this output.
-- [`references.bib`](references.bib) contains the bibtex information for the references in the manuscript.
-- [`WileyNJG-AMS.bst`](WileyNJD-AMS.bst) and [`WileyNJG-v2.cls`](WileyNJD-v2.cls) contain the latex formatting specifications for the ASA Data Science Journal.
+- [.gitignore](.gitignore) contains objects to be ignored by git.
+- [paper.Rnw](paper.Rnw), [paper.pdf](paper.pdf), and [paper.tex](paper.tex) are the manuscript. Note that paper.pdf and paper.tex are generated by paper.Rnw.
+- [README.Rmd](README.Rmd) and [README.md](README.md) are the readme files that generated this output.
+- [references.bib](references.bib) contains the bibtex information for the references in the manuscript.
+- [WileyNJG-AMS.bst](WileyNJD-AMS.bst) and [WileyNJG-v2.cls](WileyNJD-v2.cls) contain the latex formatting specifications for the ASA Data Science Journal.
 
@@
 
-When the manuscript is knit, various files will be generated (such as `data-bullet-explain.rds` and `figure-10-1.png`).
+When the manuscript is knit, various files will be generated (such as data-bullet-explain.rds and figure-10-1.png).
 The first time the manuscript is knit, it will take a while (possibly up to several hours).
@@
 
-3. Knit manuscript (via the `paper.Rnw` file).
+3. Knit manuscript (via the [paper.Rnw](paper.Rnw) file).
 
@@
 
-The data used in the manuscript for the bullet comparison examples is described below. Note that this text is also included in the file `data/readme.txt` that is submitted with the manuscript.
+The data used in the manuscript for the bullet comparison examples is described below.
+Note that this text is also included in the file [data/readme.txt](data/readme.txt) that is submitted with the manuscript.
 
-### `bullet-train.csv`
+### bullet-train.csv
 
@@
 
-**bullet-train** is generated from the raw file of comparison features, which is found [here](data/raw/CCFs_withlands.csv.zip).
-The steps taken to create **bullet-train** from the raw data are found [here](code/02-data-preparation.Rmd).
+bullet-train is generated from the raw file of comparison features, which is found [here](data/raw/CCFs_withlands.csv.zip).
+The steps taken to create bullet-train from the raw data are found [here](code/02-data-preparation.Rmd).
 These steps involve renaming some variables, selecting the variables of interest for the manuscript, and adjusting the land IDs associated with the signatures.
@@
 
-- `r names(bullet_train)[1]`: ID number associated with the bullet-land signature comparison.
-- `r names(bullet_train)[2]`, `r names(bullet_train)[3]`: IDs describing the two land engraved areas in the comparison. The format is `study-barrelnumber-bulletnumber-landnumber`.
+- **`r names(bullet_train)[1]`**: ID number associated with the bullet-land signature comparison.
+- **`r names(bullet_train)[2]`**, **`r names(bullet_train)[3]`**: IDs describing the two land engraved areas in the comparison. The format is "study-barrelnumber-bulletnumber-landnumber".
 
@@
 
-- `r names(bullet_train)[4]`: Maximized cross-correlation between two LEA signatures.
-- `r names(bullet_train)[5]`: Correlation after detrending aligned signatures.
-- `r names(bullet_train)[6]`: Euclidean distance (in millimeters) between two aligned signatures.
-- `r names(bullet_train)[7]`: Standard deviation of the previous measure along the signature.
-- `r names(bullet_train)[8]`, `r names(bullet_train)[9]`: Number of matching/non-matching peaks and valleys in the aligned signatures.
-- `r names(bullet_train)[10]`: Consecutively matching striae is a measure introduced by @biasotti:1959 describing the longest run of matching peaks between two aligned signatures.
-- `r names(bullet_train)[11]`: The number of consecutively non-matching peaks.
-- `r names(bullet_train)[12]`: The depth of peaks measured as the sum of matching peaks between two aligned signatures (in microns).
-- `r names(bullet_train)[13]`: Ground truth whether a pair is from the same source (`TRUE`) or from different sources (`FALSE`).
+- **`r names(bullet_train)[4]`**: Maximized cross-correlation between two LEA signatures.
+- **`r names(bullet_train)[5]`**: Correlation after detrending aligned signatures.
+- **`r names(bullet_train)[6]`**: Euclidean distance (in millimeters) between two aligned signatures.
+- **`r names(bullet_train)[7]`**: Standard deviation of the previous measure along the signature.
+- **`r names(bullet_train)[8]`**, **`r names(bullet_train)[9]`**: Number of matching/non-matching peaks and valleys in the aligned signatures.
+- **`r names(bullet_train)[10]`**: Consecutively matching striae is a measure introduced by @biasotti:1959 describing the longest run of matching peaks between two aligned signatures.
+- **`r names(bullet_train)[11]`**: The number of consecutively non-matching peaks.
+- **`r names(bullet_train)[12]`**: The depth of peaks measured as the sum of matching peaks between two aligned signatures (in microns).
+- **`r names(bullet_train)[13]`**: Ground truth whether a pair is from the same source ("TRUE") or from different sources ("FALSE").
 
-### `bullet-test.csv`
+### bullet-test.csv
 
@@
 bullet comparisons) x (6^2 land comparisons) = `r 2 * (3 + 2 + 1) * 6^2` comparisons.
-However, there are only `r dim(bullet_test)[1]` comparisons in the `bullet-test` data.
+However, there are only `r dim(bullet_test)[1]` comparisons in the bullet-test data.
 This is due to the fact that some of the lands are missing from the data (due to tank rash): land 4 from the unknown bullet in set 1, land 2 from bullet 1 in set 11, and land 4 from the unknown bullet in set 11.
-**bullet-test** is generated from the raw versions of the data for [set 1](data/raw/h224-set1-features.rds.zip) and [set 11](data/raw/h224-set11-features.rds.zip).
+bullet-test is generated from the raw versions of the data for [set 1](data/raw/h224-set1-features.rds.zip) and [set 11](data/raw/h224-set11-features.rds.zip).
 The variables in the test data are the same as the training data described above.
 
-### `example-signatures.csv`
+### example-signatures.csv
 
@@
 
-- `r names(signatures)[1]`: Indicator variable whether the observation corresponds to "Signature 1" or "Signature 2".
-- `r names(signatures)[2]`: The (relative) x position of the signature (in microns).
-- `r names(signatures)[3]`: The (relative) y position of the signature height (in microns).
+- **`r names(signatures)[1]`**: Indicator variable whether the observation corresponds to "Signature 1" or "Signature 2".
+- **`r names(signatures)[2]`**: The (relative) x position of the signature (in microns).
+- **`r names(signatures)[3]`**: The (relative) y position of the signature height (in microns).
 

### 2020-09-29 code/03-submission-steps.Rmd
changed file paths

--- 2020-09-16 code/03-submission-steps.Rmd
@@
     file.remove("../data/sine-lime-explain.rds")
+    file.remove("../data/raw/h224-set1-features.rds")
+    file.remove("../data/raw/h224-set11-features.rds")
+    file.remove("../data/raw/CCFs_withlands.csv")
+    file.remove("../data/raw/signatures.rds")
     file.remove("../figure-static/figure-08-1.eps")

### 2020-09-30 README.Rmd
Cleaned up land ID description
updated to do list

@@
 
-- Finish documenting the identification of the training data for rtrees in research journals (including LIME explanations from different training datasets/models)
 - Rewrite Sections 4 and 5 as needed
@@
 - **`r names(bullet_train)[1]`**: ID number associated with the bullet-land signature comparison.
-- **`r names(bullet_train)[2]`**, **`r names(bullet_train)[3]`**: IDs describing the two land engraved areas in the comparison. The format is "study-barrelnumber-bulletnumber-landnumber".
+- **`r names(bullet_train)[2]`**, **`r names(bullet_train)[3]`**: IDs describing the two land engraved areas in the comparison. The format is "study-barrel-bullet-land".
 

### 2020-09-30 paper.Rnw
small change to appendix plot to match bullet colors (orange, grey)

@@
   plot_explain_scatter(
-    bullet_explain_perms[16:18,] %>% mutate(case = "NM"),
+    bullet_explain_perms[16:18, ] %>% mutate(case = "NM"),
     alpha = 0.75,
@@
     line_size = fb2_ls
+  ) +
+  scale_fill_gradient2(
+    low = "grey50",
+    high = "darkorange",
+    midpoint = 0.5,
+    limits = c(0, 1)
   ) +

### 2020-09-30 paper.Rnw
updated text to match results in bullet example

@@
 Based on high-resolution topological scans of land engraved areas, \citet{hare:2017} obtain signatures of striations from two bullet lands (\autoref{fig:figure-09}).
-Nine features quantifying the similarity of signatures, such as the cross-correlation function, the distance between signatures, and the number of matching striae, are extracted and used to train a random forest (available in the \emph{bulletxtrctr} R package) to determine the probability of a comparison resulting from the same source (matching signatures) or from different sources (non-matching signatures).
-See the supporting information for \kge{definitions of the features \sout{additional information on the data}}.
-The model was trained on a set of scans of bullets from the James Hamby Consecutively Rifled Ruger Barrel Study \citep{hamby:2009}, which included \kge{10,384 land-to-land comparisons \citet{hare:2017}}.
+Nine features quantifying the similarity of signatures, such as the cross-correlation function, the distance between signatures, and the number of matching striae, are extracted and used to train a random forest \kge{\sout{(available in the \emph{bulletxtrctr} R package)}} to determine the probability of a comparison resulting from the same source (matching signatures) or from different sources (non-matching signatures).
+The model \kge{in \citet{hare:2017}} was trained on a set of scans of bullets from the James Hamby Consecutively Rifled Ruger Barrel Study \citep{hamby:2009}, which included \kge{10,384 land-to-land comparisons \citet{hare:2017}}.
+\kgc{Moved this sentence to the end of the paragraph:} See the supporting information for additional information on the \kge{signature similarity features\sout{data}}.
 
@@
 
-We first consider a global visualization of the relationship between the random forest predictions and the model features with a parallel coordinate plot of the training data (top facet) and testing data (bottom facets) predictions (\autoref{fig:figure-10}).
-\kgc{May want to change the next sentence a bit now:} The majority of same source observations with random forest probabilities close to 1 have a clear pattern of corresponding feature values.
-The known same source observations where the random forest is wrong (does not return probabilities close to 1) have feature values that reflect those of observations where same source is known to be false.
+We first consider a global visualization of the relationship between the random forest predictions and the model features with a parallel coordinate plot of the training data (top facet) and testing data (bottom facets) \kge{\sout{predictions}} (\autoref{fig:figure-10}).
+\kge{\sout{The majority of same source observations with random forest probabilities close to 1 have a clear pattern of corresponding feature values.
+The known same source observations where the random forest is wrong (does not return probabilities close to 1) have feature values that reflect those of observations where same source is known to be false.}} \kge{The training data observations show a clear difference in feature values based on whether the corresponding random forest probability is close to 1 or 0.
+For example, observations with a random forest probability close to 1 tend to have high values of rough correlation, cross correlation function, and matches and low values of mismatches, distance, and non-consecutivley matching striae.
+The observations in the test data that are classified incorrectly by the random forest tend to have feature values similar to observations in the training data with similar random forest scores.
+For example, the observations in the test set known to be a match but have a random forest score below 0.5 have relatively low values of rough correlation, cross correlation function, and matches and relatively large values of mismatches, distance, and non-consecutivley matching striae compared to observations with a random forest probability close to 1.}
 
@@
   ),
-  nbins = 3,
+  nbins = 4,
   feature_select = "auto",
@@
   filter(case %in% c(bullet_poi_match, bullet_poi_nonmatch),
-         nbins %in% c(3, NA),
+         nbins %in% c(4, NA),
          gower_pow == 0.5) %>%
@@
     bullet_explain_perms %>%
-      mutate(
-        implementation = fct_recode(
-          implementation,
-          "2" = "1",
-          "7" = "2",
+      mutate(implementation = fct_recode(implementation,
+          "3" = "1",
+          "8" = "2",
           "31" = "3",
@@
       select(
-        -perms_raw,
-        -perms_numerified,-perms_pred_simple,
-        -perms_pred_complex,-weights
+        -perms_raw,-perms_numerified,
+        -perms_pred_simple,-perms_pred_complex,
+        -weights
       )
@@
 
-\kgc{Will need to edit this paragraph:} First, the density simulation methods produce the same explanations for almost all cases and LIME tuning parameter values suggesting the LIME explanations are global and not local.
-Second, within a bin based simulation method, the features selected by LIME for an observation often vary by the number of bins but do not appear to vary by the Gower power.
-With the equal bins, there are vertical stripes that suggest a dependence of the LIME explanations on the number of bins.
+First, \kge{2 quantile bin \sout{the density}} simulation method \kge{applications} produce the same explanations for almost all cases and LIME tuning parameter values suggesting the LIME explanations are global and not local.
+Second, within a \kge{simulation method \sout{bin based simulation method}}, the features selected by LIME for an observation \kge{\sout{often vary by the number of bins but}} do not appear to vary by the Gower power.
+\kge{However, the LIME explanation for an observation often varies across simuluation methods.} With the equal bins, there are vertical stripes that suggest a dependence of the LIME explanations on the number of bins.
 The vertical stripes are not as apparent with the quantile bins.
@@
 @
-\caption{\kgc{Need to edit this:} Assessment metric plot for the applications of LIME on the bullet comparison data test set.
-The density simulation methods perform well for all metrics.
-The bin based metrics often do not agree in terms of performance across metrics.}
+\caption{Assessment metric plot for the applications of LIME on the bullet comparison data test set.
+\kge{\sout{The density simulation methods perform well for all metrics.
+The bin based metrics often do not agree in terms of performance across metrics.} There are discrepancies in performance across metrics for a set of tuning parameter values, but based on the overall performance of all three metrics, 4 equal bins with a Gower power of 0.5 appears to perform the best.}}
 \label{fig:figure-12}
@@
 To try to identify a set of LIME tuning parameter values with the most trustworthy set of explanations, an assessment metric plot is considered (\autoref{fig:figure-12}).
-\kgc{Need to edit the rest of this paragraph:} All density simulation methods performed well based on the three metrics.
-This is an interesting result, since \autoref{fig:figure-11} shows that the density methods results in global explanations.
+\kge{\sout{All density simulation methods performed well based on the three metrics.
+This is an interesting result, since Figure \ref{fig:figure-11} shows that the density methods results in global explanations.
 The metric values for the bin based methods do not agree across metrics.
 For example, 2 and 3 quantile bins performed well according to the average $R^2$ but poorly according to MSEE.
-As a result, with the bin based methods, it is difficult to know which method to recommend.
-The applications using a power of 0.5 perform the best or as well as the other powers across all simulation methods suggesting that the power that leads to a more global explanation is preferred by LIME.
-Perhaps we can say that the kernel density method or 3 equal bins  are the best performing methods, but unfortunately, \autoref{fig:figure-12} leaves us without a clear indication of which set of explanations to use to explain the random forest.
+As a result, with the bin based methods, it is difficult to know which method to recommend.}} \kge{The performance of a set of tuning parameter values often do not agree across metrics.
+For example, both density methods perform well according to average fidelity but poorly according to MSEE, and all quantile bin methods perform well accroding to average $R^2$ but poorly based on average fidelity and MSEE.
+However, there is consistency in results across different Gower powers.} The applications using a power of 0.5 perform the best or as well as the other powers across all simulation methods suggesting that the power that leads to a more global explanation is preferred by LIME.
+\kge{\sout{Perhaps we can say that the kernel density method or 3 equal bins are the best performing methods, but unfortunately, Figure \ref{fig:figure-12} leaves us without a clear indication of which set of explanations to use to explain the random forest.}} \kge{It is not obvious which set of of tuning parameters are best, but perhaps, we can say that based on all three metrics, the 4 equal bins with a Gower power of 0.5 performs bettter than the other tuning parameter values considered.}
 
@@
 Figure~\ref{fig:figure-13} includes the visual representation plots of explanations (from \emph{lime}) and explanation scatterplots for cases M and NM.
-Plots for 3 equal bins and 3 quantile bins are included to depict tuning parameter values with good (3 equal bins) and mediocre (3 quantile bins) performance based on the assessment metric plot.
+Plots for 4 equal bins and 4 quantile bins are included to depict tuning parameter values with good (4 equal bins) and mediocre (4 quantile bins) performance based on the assessment metric plot.
 Plots for the kernel density simulation method are included in Appendix~\ref{exp-scatter_plus} (Figure \ref{fig:figure-B2}).
 
-\kgc{Need to edit this pargraph:} First, focus on the explanation for case NM with 3 quantile bins.
-The explanation plot from \emph{lime} shows that an observed CCF value greater than 0.320 supports a random forest prediction in favor of a match, and the scatter plots show that many of the simulated values with CCF greater then 0.320 have random forest predictions greater than 0.5.
-Additionally, the LIME explanation indicates that a value of matches less than or equal to 1.66 contradicts a prediction in favor of a match, and the scatter plots show that almost all simulated values with a value of matches less than or equal to 1.66 have random forest predictions close to 0.
+First, focus on the explanation for case NM with 4 quantile bins.
+\kge{The explanation plot from \emph{lime} shows that observed values with rough correlation (rough\_cor) greater than 0.05 and mismatches value less than or equal to 7.17 support a random forest prediction in favor of a match, and the scatter plots show that many of the simulated values with rough correlation greater then 0.05 and mismatches less than 7.17 have random forest predictions greater than 0.5.
+Additionally, the LIME explanation indicates that a value of cross correlation function (ccf) greater than 0.28 and less than or equal to 0.35 supports a non-match, and the scatter plots shows that the simulated values within this region have mostly random forest predictions less than 0.5.
+However, the random forest assigns a probability of 0.19 to case NM, which is not explained by the LIME explanation.
+Instead, consider that a better explanation based on the scatterplots would be that the random forest assigned a prediction probably close to 0 since the observation has a rough correlation less than 0.5, mismatches greater than 4, and cross correlation function 0.6.} \kge{\sout{Additionally, the LIME explanation indicates that a value of matches less than or equal to 1.66 contradicts a prediction in favor of a match, and the scatter plots show that almost all simulated values with a value of matches less than or equal to 1.66 have random forest predictions close to 0.
 While the LIME explanation makes sense based on the observations made from the explanation scatter plot, the plot also indicates that LIME falls short of providing a good explanation of the random forest prediction for case NM.
 Based on the scatter plot of CCF versus matches, a better explanation would be that because case NM has a value of CCF less than 0.8 and a value of matches less than 7, the random forest provides a prediction supporting a non-match.
-The relationship between CCF and rough correlation does not provide much evidence to support the random forest prediction one way or the other, but there is a pentagon shaped region at the bottom of the scatter plot of matches versus rough correlation with mostly predictions close to 0 that case NM falls in and supports the random forest prediction of a non-match.
-
-\kgc{Maybe edit this pargraph:} The other explanation scatterplots can be interpreted in a similar manner.
-Overall, the plots identify that the 3 quantile bin explanations are not faithful to the random forest model predictions.
-The 3 equal bin explanations are more faithful to the random forest, but the regions captured by the bins still do not align with the regions with similar probabilities produced by the random forest.
+The relationship between CCF and rough correlation does not provide much evidence to support the random forest prediction one way or the other, but there is a pentagon shaped region at the bottom of the scatter plot of matches versus rough correlation with mostly predictions close to 0 that case NM falls in and supports the random forest prediction of a non-match.}}
+
+The other explanation scatterplots can be interpreted in a similar manner.
+Overall, the plots identify that the \kge{\sout{3} 4} quantile bin explanations are not faithful to the random forest model predictions.
+The \kge{4 \sout{3}} equal bin explanations are more faithful to the random forest, but the regions captured by the bins do not align \kge{as well as they could} with the regions \kge{containing \sout{with}} similar probabilities produced by the random forest.
 
@@
 @
-\caption{Plots of LIME explanations (first and third rows) and explanation scatterplots (second and fourth rows) for  cases M and NM in the bullet test data for two tuning parameter values: 3 quantile bins (first column) and 3 equal bins (second column).
+\caption{Plots of LIME explanations (first and third rows) and explanation scatterplots (second and fourth rows) for  cases M and NM in the bullet test data for two tuning parameter values: \kge{4 \sout{3}} quantile bins (first column) and \kge{4 \sout{3}} equal bins (second column).
 The plots provide insights into the LIME explanations and allow for the assessment of the explanation quality.}
@@
 Supplementing \citet{pedersen:2020}'s compact visualization of the explanation with an explanation scatterplot that shows a more detailed visualization of the explainer model (such as Figures~\ref{fig:figure-04} and \ref{fig:figure-13}) promotes a more complete understanding of the explanation.
-
-\kgc{Need to make some edits in this paragraph:} Even with an explainer model that is interpreted correctly, the interpretation is worthless if the explainer model is not \textbf{faithful} to the complex model.
+Even with an explainer model that is interpreted correctly, the interpretation is worthless if the explainer model is not \textbf{faithful} to the complex model.
 This claim can be assessed using the diagnostic plots suggested in this paper.
@@
 The examples of faithfulness metric comparisons in this paper (Figures \ref{fig:figure-07} and \ref{fig:figure-12}) both produced conflicting results.
-The density based simulation methods result in the best or close to the best performance even though the feature heatmaps (Figures \ref{fig:figure-06} and \ref{fig:figure-11}) show that the density simulation methods produce global explanations with minimal variation in features selected by LIME.
-For the bin based simulation methods, the two metrics often do not agree or contradict one another, which makes it difficult to decide on a recommendation of a set of tuning parameter values that produce the explanations with the most faithful explainer model.
+\kge{\sout{The density based simulation methods result in the best or close to the best performance even though the feature heatmaps (Figures \ref{fig:figure-06} and \ref{fig:figure-11}) show that the density simulation methods produce global explanations with minimal variation in features selected by LIME.
+For the bin based simulation methods, the two metrics often do not agree or contradict one another, which} This} makes it difficult to decide on a recommendation of a set of tuning parameter values that produce the explanations with the most faithful explainer model.
 
@@
 
-\kgc{Probably need to make some edits here:} The final claim, \textbf{localness}, is addressed by the feature heatmap and metric comparison plots.
-As stated, the feature heatmap reveals that the density simulation methods in the examples of this paper results in global explanations where the same features are repeatedly chosen across all (or almost all) observations in the set of explanations.
-This finding agrees with that of \citep{laugel:2018} who found LIME produced global explanations with the normal approximation simulation method.
+The final claim, \textbf{localness}, is addressed by the feature heatmap and metric comparison plots.
+As stated, the feature heatmap reveals that the density simulation methods in the \kge{\data \ example \sout{examples of this paper}} results in global explanations where the same features are repeatedly chosen across all (or almost all) observations in the set of explanations.
+This finding agrees with that of \citet{laugel:2018} who found LIME produced global explanations with the normal approximation simulation method.
 For the bin based simulation methods in the bullet data example, the feature heatmap showed that the features chosen for the explanations varied between the two classification categories (match versus non-match).

### 2020-09-30 paper.tex
updated text to match results in bullet example

@@
 \end{knitrout}
-\caption{\kgc{Need to edit this:} Assessment metric plot for the applications of LIME on the bullet comparison data test set.
-The density simulation methods perform well for all metrics.
-The bin based metrics often do not agree in terms of performance across metrics.}
+\caption{Assessment metric plot for the applications of LIME on the bullet comparison data test set.
+\kge{\sout{The density simulation methods perform well for all metrics.
+The bin based metrics often do not agree in terms of performance across metrics.} There are discrepancies in performance across metrics for a set of tuning parameter values, but based on the overall performance of all three metrics, 4 equal bins with a Gower power of 0.5 appears to perform the best.}}
 \label{fig:figure-12}
@@
 Figure~\ref{fig:figure-13} includes the visual representation plots of explanations (from \emph{lime}) and explanation scatterplots for cases M and NM.
-Plots for 3 equal bins and 3 quantile bins are included to depict tuning parameter values with good (3 equal bins) and mediocre (3 quantile bins) performance based on the assessment metric plot.
+Plots for 4 equal bins and 4 quantile bins are included to depict tuning parameter values with good (4 equal bins) and mediocre (4 quantile bins) performance based on the assessment metric plot.
 Plots for the kernel density simulation method are included in Appendix~\ref{exp-scatter_plus} (Figure \ref{fig:figure-B2}).
 
-\kgc{Need to edit this pargraph:} First, focus on the explanation for case NM with 3 quantile bins.
-The explanation plot from \emph{lime} shows that an observed CCF value greater than 0.320 supports a random forest prediction in favor of a match, and the scatter plots show that many of the simulated values with CCF greater then 0.320 have random forest predictions greater than 0.5.
-Additionally, the LIME explanation indicates that a value of matches less than or equal to 1.66 contradicts a prediction in favor of a match, and the scatter plots show that almost all simulated values with a value of matches less than or equal to 1.66 have random forest predictions close to 0.
+First, focus on the explanation for case NM with 4 quantile bins.
+\kge{The explanation plot from \emph{lime} shows that observed values with rough correlation (rough\_cor) greater than 0.05 and mismatches value less than or equal to 7.17 support a random forest prediction in favor of a match, and the scatter plots show that many of the simulated values with rough correlation greater then 0.05 and mismatches less than 7.17 have random forest predictions greater than 0.5.
+Additionally, the LIME explanation indicates that a value of cross correlation function (ccf) greater than 0.28 and less than or equal to 0.35 supports a non-match, and the scatter plots shows that the simulated values within this region have mostly random forest predictions less than 0.5.
+However, the random forest assigns a probability of 0.19 to case NM, which is not explained by the LIME explanation.
+Instead, consider that a better explanation based on the scatterplots would be that the random forest assigned a prediction probably close to 0 since the observation has a rough correlation less than 0.5, mismatches greater than 4, and cross correlation function 0.6.} \kge{\sout{Additionally, the LIME explanation indicates that a value of matches less than or equal to 1.66 contradicts a prediction in favor of a match, and the scatter plots show that almost all simulated values with a value of matches less than or equal to 1.66 have random forest predictions close to 0.
 While the LIME explanation makes sense based on the observations made from the explanation scatter plot, the plot also indicates that LIME falls short of providing a good explanation of the random forest prediction for case NM.
 Based on the scatter plot of CCF versus matches, a better explanation would be that because case NM has a value of CCF less than 0.8 and a value of matches less than 7, the random forest provides a prediction supporting a non-match.
-The relationship between CCF and rough correlation does not provide much evidence to support the random forest prediction one way or the other, but there is a pentagon shaped region at the bottom of the scatter plot of matches versus rough correlation with mostly predictions close to 0 that case NM falls in and supports the random forest prediction of a non-match.
+The relationship between CCF and rough correlation does not provide much evidence to support the random forest prediction one way or the other, but there is a pentagon shaped region at the bottom of the scatter plot of matches versus rough correlation with mostly predictions close to 0 that case NM falls in and supports the random forest prediction of a non-match.}}
 
-\kgc{Maybe edit this pargraph:} The other explanation scatterplots can be interpreted in a similar manner.
-Overall, the plots identify that the 3 quantile bin explanations are not faithful to the random forest model predictions.
-The 3 equal bin explanations are more faithful to the random forest, but the regions captured by the bins still do not align with the regions with similar probabilities produced by the random forest.
+The other explanation scatterplots can be interpreted in a similar manner.
+Overall, the plots identify that the \kge{\sout{3} 4} quantile bin explanations are not faithful to the random forest model predictions.
+The \kge{4 \sout{3}} equal bin explanations are more faithful to the random forest, but the regions captured by the bins do not align \kge{as well as they could} with the regions \kge{containing \sout{with}} similar probabilities produced by the random forest.
 
@@
 \end{knitrout}
-\caption{Plots of LIME explanations (first and third rows) and explanation scatterplots (second and fourth rows) for  cases M and NM in the bullet test data for two tuning parameter values: 3 quantile bins (first column) and 3 equal bins (second column).
+\caption{Plots of LIME explanations (first and third rows) and explanation scatterplots (second and fourth rows) for  cases M and NM in the bullet test data for two tuning parameter values: \kge{4 \sout{3}} quantile bins (first column) and \kge{4 \sout{3}} equal bins (second column).
 The plots provide insights into the LIME explanations and allow for the assessment of the explanation quality.}

### 2020-10-01 code/03-submission-steps.Rmd
small updates

--- 2020-09-16 code/03-submission-steps.Rmd
@@
 author: "Katherine Goode"
-date: "`r format(Sys.time(), '%B %d, %Y')`"
-output: html_document
+date: "<br>`r format(Sys.time(), '%B %d, %Y')`"
+output: rmarkdown::github_document
 ---
@@
     file.remove("../data/sine-lime-explain.rds")
+    file.remove("../data/raw/h224-set1-features.rds")
+    file.remove("../data/raw/h224-set1-features.rds.zip")
+    file.remove("../data/raw/h224-set11-features.rds")
+    file.remove("../data/raw/h224-set11-features.rds.zip")
+    file.remove("../data/raw/CCFs_withlands.csv")
+    file.remove("../data/raw/CCFs_withlands.csv.zip")
+    file.remove("../data/raw/signatures.rds")
+    file.remove("../data/raw/signatures.rds.zip")
     file.remove("../figure-static/figure-08-1.eps")
@@
 
-2. Manually run the code in `code/01-raw-file-compression.Rmd` to compress the raw versions of the data files and static figure. Also, knit the file to make sure the html version is up to date.
+2.
+Manually run the code in `code/01-raw-file-compression.Rmd` to add compressed versions of the raw data files and to compress the static figure for the manuscript.
+Also, knit the file to make sure the md version is up to date.
 
@@
 Manually run the code in `code/02-data-preparation.Rmd` to create the versions of the data to be used in the manuscript and submitted with the manuscript.
-Also, knit the file to make sure the html version is up to date.
+Also, knit the file to make sure the md version is up to date.
 
@@
       c(
-        "../readme.txt",
+        "../data/readme.txt",
         "../data/bullet-test.csv.zip",
@@
 
-7. Compile the file `paper.tex` (using LaTex, then bibTex, then LaTeX twice more) to make sure it compiles correctly (especially references).
+7. Compile the file `paper.tex` to make sure it compiles correctly (especially references). (If using texShop, make sure to compile using LaTex, then bibTex, then LaTeX twice more.)
 
@@
   - `WileyNJD-v2.cls`
+
+10. Knit this document to make sure the md version is up to date.

### 2020-10-01 submission/paper.tex
just checking that submission code still works

--- 2020-09-09 paper.tex
@@
 \end{figure*}
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
+\begin{verbatim}
+## [18:11:47] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:47] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:47] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:47] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:47] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:47] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:47] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:47] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:47] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:48] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:48] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:48] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:48] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:48] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:48] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:48] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:48] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:48] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:48] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:48] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:48] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:48] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:48] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:48] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:48] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:48] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:49] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:49] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:49] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:49] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:49] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:49] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:49] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:49] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:49] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:49] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:49] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:49] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:49] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:49] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:49] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:49] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:49] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:49] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:50] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:50] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:50] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:50] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:50] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:50] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:50] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:50] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:50] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:50] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:50] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:50] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:50] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:50] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:50] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:50] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:50] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:51] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:51] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:51] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:51] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:51] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:51] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:51] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:51] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:51] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:51] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:51] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:51] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:51] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:51] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:51] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:51] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:51] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:52] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:52] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:52] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:52] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:52] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:52] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:52] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:52] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:52] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:52] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:52] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:52] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:52] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:53] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:53] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:53] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:53] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:53] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:53] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:53] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:53] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:11:53] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:08] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:08] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:08] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:08] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:08] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:08] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:08] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:08] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:08] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:08] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:08] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:08] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:08] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:08] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:08] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:08] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:08] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:08] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:08] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:09] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:09] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:09] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:09] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:09] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:09] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:09] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:09] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:09] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:09] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:09] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:09] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:09] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:09] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:09] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:09] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:09] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:09] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:10] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:10] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:10] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:10] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:10] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:10] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:10] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:10] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:10] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:10] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:10] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:10] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:10] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:10] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:10] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:10] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:10] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:10] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:11] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:11] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:11] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:11] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:11] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:11] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:11] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:11] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:25] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:25] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:25] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:25] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:25] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:25] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:25] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:25] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:25] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:25] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:25] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:25] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:25] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:25] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:25] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:25] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:25] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:25] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:26] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:26] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:26] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:26] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:26] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:26] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:26] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:26] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:26] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:26] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:26] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:26] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:26] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:26] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:26] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:26] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:26] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:26] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:27] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:27] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:27] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:27] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:27] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:27] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:27] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:27] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:27] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:27] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:27] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:27] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:27] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:27] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:27] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:27] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:27] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:27] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:27] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:28] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:28] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:28] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:28] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:28] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:28] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:28] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:28] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:28] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:28] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:28] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:28] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:28] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:28] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:28] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:28] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:28] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:29] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:29] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:29] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:29] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:29] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:29] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:29] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:29] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:29] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:29] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:29] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:29] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:29] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:29] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:29] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:29] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:42] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:42] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:42] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:42] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:42] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:42] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:42] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:42] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:42] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:42] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:43] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:43] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:43] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:43] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:43] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:43] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:43] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:43] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:43] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:43] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:43] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:43] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:43] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:43] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:43] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:43] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:43] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:43] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:44] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:44] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:44] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:44] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:44] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:44] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:44] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:44] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:44] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:44] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:44] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:44] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:44] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:44] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:44] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:44] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:44] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:44] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:44] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:45] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:45] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:45] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:45] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:45] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:45] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:45] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:45] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:45] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:45] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:45] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:45] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:45] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:45] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:45] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:45] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:45] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:45] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:46] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:46] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:46] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:46] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:46] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:46] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:46] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:46] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:46] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:46] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:46] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:46] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:46] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:46] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:46] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:46] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:46] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:47] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:47] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:47] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:47] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:47] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:47] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:47] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:47] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:47] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:47] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:47] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:47] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:47] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:47] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:47] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:47] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:47] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:12:47] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:01] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:01] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:01] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:01] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:01] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:01] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:01] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:01] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:01] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:01] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:01] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:01] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:02] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:02] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:02] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:02] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:02] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:02] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:02] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:02] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:02] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:02] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:02] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:02] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:02] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:02] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:02] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:02] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:02] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:03] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:03] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:03] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:03] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:03] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:03] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:03] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:03] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:03] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:03] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:03] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:03] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:03] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:03] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:03] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:03] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:03] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:03] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:04] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:04] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:04] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:04] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:04] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:04] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:04] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:04] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:04] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:04] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:04] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:04] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:04] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:04] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:04] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:05] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:06] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:07] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:20] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:20] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:20] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:20] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:20] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:20] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:20] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:20] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:21] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:21] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:21] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:21] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:21] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:21] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:21] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:21] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:21] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:21] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:21] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:21] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:21] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:21] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:21] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:21] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:21] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:21] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:22] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:22] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:22] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:22] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:22] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:22] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:22] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:22] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:22] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:22] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:22] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:22] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:22] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:22] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:22] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:22] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:22] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:22] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:23] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:23] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:23] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:23] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:23] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:23] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:23] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:23] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:23] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:23] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:23] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:23] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:23] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:23] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:23] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:23] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:23] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:23] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:24] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:25] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:25] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:25] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:25] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:25] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:25] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:25] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:25] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:25] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:25] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:25] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:25] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:25] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:25] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:25] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:25] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:25] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:25] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:25] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+## 
+## 
+## [18:13:26] WARNING: amalgamation/../src/learner.cc:516: 
+## Parameters: { silent } might not be used.
+## 
+##   This may not be accurate due to some parameters are only used in language bindings but
+##   passed down to XGBoost core.  Or some parameters are not used but slip through this
+##   verification. Please open an issue if you find above cases.
+\end{verbatim}
+\end{kframe}
+\end{knitrout}
 
@@
 
-In response, \citet{hare:2016} proposed an automated machine learning method for bullet matching to complement a visual inspection by firearm examiners.
-Based on high-resolution topological scans of land engraved areas, \citet{hare:2016} obtain signatures of striations from two bullet lands (\autoref{fig:figure-09}).
-Nine features quantifying the similarity of signatures, such as the cross-correlation function, the distance between signatures, and the number of matching striae, are extracted and used to train a random forest (available in the \emph{bulletxtrctr} R package) to determine the probability of a comparison resulting from the same source (matching signatures) or from different sources (non-matching signatures).
-See the supporting information for additional information on the data.
-The model was trained on a set of scans of bullets from the James Hamby Consecutively Rifled Ruger Barrel Study \citep{hamby:2009}, which includes over 80,000 land-to-land comparisons.
+In response, \citet{hare:2017} proposed an automated machine learning method for bullet matching to complement a visual inspection by firearm examiners.
+Based on high-resolution topological scans of land engraved areas, \citet{hare:2017} obtain signatures of striations from two bullet lands (\autoref{fig:figure-09}).
+Nine features quantifying the similarity of signatures, such as the cross-correlation function, the distance between signatures, and the number of matching striae, are extracted and used to train a random forest \kge{\sout{(available in the \emph{bulletxtrctr} R package)}} to determine the probability of a comparison resulting from the same source (matching signatures) or from different sources (non-matching signatures).
+The model \kge{in \citet{hare:2017}} was trained on a set of scans of bullets from the James Hamby Consecutively Rifled Ruger Barrel Study \citep{hamby:2009}, which included \kge{10,384 land-to-land comparisons \citet{hare:2017}}.
+\kgc{Moved this sentence to the end of the paragraph:} See the supporting information for additional information on the \kge{signature similarity features\sout{data}}.
 
@@
 
-We apply the trained random forest model from \citet{hare:2016} to another set of bullets from the Hamby study with 432 rows of land comparisons.
-We first consider a global visualization of the relationship between the random forest predictions and the model features with a parallel coordinate plot of the training data (top facet) and testing data (bottom facets) predictions (\autoref{fig:figure-10}).
-The majority of same source observations with random forest probabilities close to 1 have a clear pattern of corresponding feature values.
-The known same source observations where the random forest is wrong (does not return probabilities close to 1) have feature values that reflect those of observations where same source is known to be false.
+\kge{We train a new random forest model using 83,028 land-to-land comparisons from bullets in the James Hamby Consecutively Rifled Ruger Barrel Study \citep{hamby:2009} using the same nine comparison features used by \citet{hare:2017} to predict whether the two lands are a match.} We apply the trained random forest model to another set of bullets from the Hamby study with 364 rows of land comparisons.
+\kge{See the supporting information for further descriptions of the data.}
+
+We first consider a global visualization of the relationship between the random forest predictions and the model features with a parallel coordinate plot of the training data (top facet) and testing data (bottom facets) \kge{\sout{predictions}} (\autoref{fig:figure-10}).
+\kge{\sout{The majority of same source observations with random forest probabilities close to 1 have a clear pattern of corresponding feature values.
+The known same source observations where the random forest is wrong (does not return probabilities close to 1) have feature values that reflect those of observations where same source is known to be false.}} \kge{The training data observations show a clear difference in feature values based on whether the corresponding random forest probability is close to 1 or 0.
+For example, observations with a random forest probability close to 1 tend to have high values of rough correlation, cross correlation function, and matches and low values of mismatches, distance, and non-consecutivley matching striae.
+The observations in the test data that are classified incorrectly by the random forest tend to have feature values similar to observations in the training data with similar random forest scores.
+For example, the observations in the test set known to be a match but have a random forest score below 0.5 have relatively low values of rough correlation, cross correlation function, and matches and relatively large values of mismatches, distance, and non-consecutivley matching striae compared to observations with a random forest probability close to 1.}
 
@@
 
-First, the density simulation methods produce the same explanations for almost all cases and LIME tuning parameter values suggesting the LIME explanations are global and not local.
-Second, within a bin based simulation method, the features selected by LIME for an observation often vary by the number of bins but do not appear to vary by the Gower power.
-With the equal bins, there are vertical stripes that suggest a dependence of the LIME explanations on the number of bins.
+First, \kge{2 quantile bin \sout{the density}} simulation method \kge{applications} produce the same explanations for almost all cases and LIME tuning parameter values suggesting the LIME explanations are global and not local.
+Second, within a \kge{simulation method \sout{bin based simulation method}}, the features selected by LIME for an observation \kge{\sout{often vary by the number of bins but}} do not appear to vary by the Gower power.
+\kge{However, the LIME explanation for an observation often varies across simuluation methods.} With the equal bins, there are vertical stripes that suggest a dependence of the LIME explanations on the number of bins.
 The vertical stripes are not as apparent with the quantile bins.
@@
 \caption{Assessment metric plot for the applications of LIME on the bullet comparison data test set.
-The density simulation methods perform well for all metrics.
-The bin based metrics often do not agree in terms of performance across metrics.}
+\kge{\sout{The density simulation methods perform well for all metrics.
+The bin based metrics often do not agree in terms of performance across metrics.} There are discrepancies in performance across metrics for a set of tuning parameter values, but based on the overall performance of all three metrics, 4 equal bins with a Gower power of 0.5 appears to perform the best.}}
 \label{fig:figure-12}
@@
 To try to identify a set of LIME tuning parameter values with the most trustworthy set of explanations, an assessment metric plot is considered (\autoref{fig:figure-12}).
-All density simulation methods performed well based on the three metrics.
-This is an interesting result, since \autoref{fig:figure-11} shows that the density methods results in global explanations.
+\kge{\sout{All density simulation methods performed well based on the three metrics.
+This is an interesting result, since Figure \ref{fig:figure-11} shows that the density methods results in global explanations.
 The metric values for the bin based methods do not agree across metrics.
 For example, 2 and 3 quantile bins performed well according to the average $R^2$ but poorly according to MSEE.
-As a result, with the bin based methods, it is difficult to know which method to recommend.
-The applications using a power of 0.5 perform the best or as well as the other powers across all simulation methods suggesting that the power that leads to a more global explanation is preferred by LIME.
-Perhaps we can say that the kernel density method or 3 equal bins  are the best performing methods, but unfortunately, \autoref{fig:figure-12} leaves us without a clear indication of which set of explanations to use to explain the random forest.
+As a result, with the bin based methods, it is difficult to know which method to recommend.}} \kge{The performance of a set of tuning parameter values often do not agree across metrics.
+For example, both density methods perform well according to average fidelity but poorly according to MSEE, and all quantile bin methods perform well accroding to average $R^2$ but poorly based on average fidelity and MSEE.
+However, there is consistency in results across different Gower powers.} The applications using a power of 0.5 perform the best or as well as the other powers across all simulation methods suggesting that the power that leads to a more global explanation is preferred by LIME.
+\kge{\sout{Perhaps we can say that the kernel density method or 3 equal bins are the best performing methods, but unfortunately, Figure \ref{fig:figure-12} leaves us without a clear indication of which set of explanations to use to explain the random forest.}} \kge{It is not obvious which set of of tuning parameters are best, but perhaps, we can say that based on all three metrics, the 4 equal bins with a Gower power of 0.5 performs bettter than the other tuning parameter values considered.}
 
@@
 Figure~\ref{fig:figure-13} includes the visual representation plots of explanations (from \emph{lime}) and explanation scatterplots for cases M and NM.
-Plots for 3 equal bins and 3 quantile bins are included to depict tuning parameter values with good (3 equal bins) and mediocre (3 quantile bins) performance based on the assessment metric plot.
+Plots for 4 equal bins and 4 quantile bins are included to depict tuning parameter values with good (4 equal bins) and mediocre (4 quantile bins) performance based on the assessment metric plot.
 Plots for the kernel density simulation method are included in Appendix~\ref{exp-scatter_plus} (Figure \ref{fig:figure-B2}).
 
-First, focus on the explanation for case NM with 3 quantile bins.
-The explanation plot from \emph{lime} shows that an observed CCF value greater than 0.320 supports a random forest prediction in favor of a match, and the scatter plots show that many of the simulated values with CCF greater then 0.320 have random forest predictions greater than 0.5.
-Additionally, the LIME explanation indicates that a value of matches less than or equal to 1.66 contradicts a prediction in favor of a match, and the scatter plots show that almost all simulated values with a value of matches less than or equal to 1.66 have random forest predictions close to 0.
+First, focus on the explanation for case NM with 4 quantile bins.
+\kge{The explanation plot from \emph{lime} shows that observed values with rough correlation (rough\_cor) greater than 0.05 and mismatches value less than or equal to 7.17 support a random forest prediction in favor of a match, and the scatter plots show that many of the simulated values with rough correlation greater then 0.05 and mismatches less than 7.17 have random forest predictions greater than 0.5.
+Additionally, the LIME explanation indicates that a value of cross correlation function (ccf) greater than 0.28 and less than or equal to 0.35 supports a non-match, and the scatter plots shows that the simulated values within this region have mostly random forest predictions less than 0.5.
+However, the random forest assigns a probability of 0.19 to case NM, which is not explained by the LIME explanation.
+Instead, consider that a better explanation based on the scatterplots would be that the random forest assigned a prediction probably close to 0 since the observation has a rough correlation less than 0.5, mismatches greater than 4, and cross correlation function 0.6.} \kge{\sout{Additionally, the LIME explanation indicates that a value of matches less than or equal to 1.66 contradicts a prediction in favor of a match, and the scatter plots show that almost all simulated values with a value of matches less than or equal to 1.66 have random forest predictions close to 0.
 While the LIME explanation makes sense based on the observations made from the explanation scatter plot, the plot also indicates that LIME falls short of providing a good explanation of the random forest prediction for case NM.
 Based on the scatter plot of CCF versus matches, a better explanation would be that because case NM has a value of CCF less than 0.8 and a value of matches less than 7, the random forest provides a prediction supporting a non-match.
-The relationship between CCF and rough correlation does not provide much evidence to support the random forest prediction one way or the other, but there is a pentagon shaped region at the bottom of the scatter plot of matches versus rough correlation with mostly predictions close to 0 that case NM falls in and supports the random forest prediction of a non-match.
+The relationship between CCF and rough correlation does not provide much evidence to support the random forest prediction one way or the other, but there is a pentagon shaped region at the bottom of the scatter plot of matches versus rough correlation with mostly predictions close to 0 that case NM falls in and supports the random forest prediction of a non-match.}}
 
 The other explanation scatterplots can be interpreted in a similar manner.
-Overall, the plots identify that the 3 quantile bin explanations are not faithful to the random forest model predictions.
-The 3 equal bin explanations are more faithful to the random forest, but the regions captured by the bins still do not align with the regions with similar probabilities produced by the random forest.
+Overall, the plots identify that the \kge{\sout{3} 4} quantile bin explanations are not faithful to the random forest model predictions.
+The \kge{4 \sout{3}} equal bin explanations are more faithful to the random forest, but the regions captured by the bins do not align \kge{as well as they could} with the regions \kge{containing \sout{with}} similar probabilities produced by the random forest.
 
@@
 Supplementing \citet{pedersen:2020}'s compact visualization of the explanation with an explanation scatterplot that shows a more detailed visualization of the explainer model (such as Figures~\ref{fig:figure-04} and \ref{fig:figure-13}) promotes a more complete understanding of the explanation.
-
 Even with an explainer model that is interpreted correctly, the interpretation is worthless if the explainer model is not \textbf{faithful} to the complex model.
@@
 The final claim, \textbf{localness}, is addressed by the feature heatmap and metric comparison plots.
-As stated, the feature heatmap reveals that the density simulation methods in the examples of this paper results in global explanations where the same features are repeatedly chosen across all (or almost all) observations in the set of explanations.
-This finding agrees with that of \citep{laugel:2018} who found LIME produced global explanations with the normal approximation simulation method.
+As stated, the feature heatmap reveals that the density simulation methods in the \kge{\data \ example \sout{examples of this paper}} results in global explanations where the same features are repeatedly chosen across all (or almost all) observations in the set of explanations.
+This finding agrees with that of \citet{laugel:2018} who found LIME produced global explanations with the normal approximation simulation method.
 For the bin based simulation methods in the bullet data example, the feature heatmap showed that the features chosen for the explanations varied between the two classification categories (match versus non-match).

### 2020-10-03 paper.Rnw
couple of small edits

@@
 We use 6 bins as the maximum, because the complexity of the explanations increases with the number of bins.
-Note that 4 quantile bins are the default method in \emph{lime}.
+Note that 4-quantile-bins are the default method in \emph{lime}.
 The sixth application of LIME uses a kernel density simulation method (samples are drawn from kernel density approximations of the feature distributions).
@@
 The plot is created using the \emph{lime} R package and provides a visual representation of a LIME explanation for the prediction of interest indicated in \autoref{fig:figure-03}.
-In particular, the explanation is obtained using 4 quantile bins to simulate the data.
+In particular, the explanation is obtained using 4-quantile-bins to simulate the data.
 In this scenario, LIME converts continuous predictor variables to indicator variables identifying whether the variable value falls in the same quantile bin as the prediction of interest or not.
@@
 The format of an explanation scatterplot depends on the LIME simulation method.
-We introduce the explanation scatterplot here under the \emph{lime} R package default method of four quantile bins.
+We introduce the explanation scatterplot here under the \emph{lime} R package default method of 4-quantile-bins.
 
@@
 First, consider the claim of localness.
-The weights decay relatively slowly  outside of the intersection of the two quantile bins suggesting that the LIME explanation is highly influenced by points outside of the bins containing the prediction of interest.
+The weights decay relatively slowly  outside of the intersection of the 2-quantil-bin suggesting that the LIME explanation is highly influenced by points outside of the bins containing the prediction of interest.
 However, it is  difficult to say if the claim of localness has been violated, because a definition of a local region is not specified.
@@
 
-Now, consider the claim of faithfulness: It can be said that the majority of the points in the $x_2$ quantile support a prediction of blue, which is captured by the bar supporting a prediction of blue in the LIME explanation, and a similar statement can be made about the $x_1$ quantile bin.
+Now, consider the claim of faithfulness: It can be said that the majority of the points in the $x_2$ quantile support a prediction of blue, which is captured by the bar supporting a prediction of blue in the LIME explanation, and a similar statement can be made about the $x_1$-quantile-bin.
 These statements validate the explanation produced by LIME.
@@
 For the quantile bins, the original features prior to the indicator variable transformation are included since it is obvious that different features would be selected when the sizes of the bins change.
-This figure shows that for kernel density and 2 quantile bins, LIME selects $x_1$ as the most important feature and $x_2$ as the second most important feature across all cases in the test set.
+This figure shows that for kernel density and 2-quantile-bins, LIME selects $x_1$ as the most important feature and $x_2$ as the second most important feature across all cases in the test set.
 These explanations are not local.
-There is variability in the features selected by LIME for 3 to 6 quantile bins suggesting more local explanations.
+There is variability in the features selected by LIME for 3- to 6-quantile-bins suggesting more local explanations.
 There are signs of vertical striping, which suggests a dependence on tuning parameters.
-Note that the explanations from 3 and 5 quantile bins include the selection of the random noise variable ($x_3$) as an important variable in many predictions, which should not be the case.
-The pattern seen in the explanations for 3 to 6 quantile bins may suggest local explanations, but the dependence on tuning parameters makes it unclear which set of explanations to use.
+Note that the explanations from 3- and 5-quantile-bins include the selection of the random noise variable ($x_3$) as an important variable in many predictions, which should not be the case.
+The pattern seen in the explanations for 3- to 6-quantile-bins may suggest local explanations, but the dependence on tuning parameters makes it unclear which set of explanations to use.
 
@@
 All three metrics suggest that the kernel density method performed well, but the metrics disagree for the quantile bins methods.
-Average $R^2$ and average fidelity rank the performance of the number of quantile bins the same (2 quantile bins perform the best and 6 quantile bins perform the worst).
+Average $R^2$ and average fidelity rank the performance of the number of quantile bins the same (2-quantile-bins perform the best and 6-quantile-bins perform the worst).
 In fact, these two metrics appear to have a mirrored  relationship in this example.
-MSEE provides almost the exact opposite results with  6 quantile bins performing the best and 2 quantile bins performing the worst.
+MSEE provides almost the exact opposite results with  6-quantile-bins performing the best and 2-quantile-bins performing the worst.
 Average fidelity and MSEE are similar metrics, so it is not surprising that they would agree in this example.
@@
 Based on high-resolution topological scans of land engraved areas, \citet{hare:2017} obtain signatures of striations from two bullet lands (\autoref{fig:figure-09}).
-Nine features quantifying the similarity of signatures, such as the cross-correlation function, the distance between signatures, and the number of matching striae, are extracted and used to train a random forest \kge{\sout{(available in the \emph{bulletxtrctr} R package)}} to determine the probability of a comparison resulting from the same source (matching signatures) or from different sources (non-matching signatures).
-The model \kge{in \citet{hare:2017}} was trained on a set of scans of bullets from the James Hamby Consecutively Rifled Ruger Barrel Study \citep{hamby:2009}, which included \kge{10,384 land-to-land comparisons \citet{hare:2017}}.
-\kgc{Moved this sentence to the end of the paragraph:} See the supporting information for additional information on the \kge{signature similarity features\sout{data}}.
+Nine features quantifying the similarity of signatures, such as the cross-correlation function, the distance between signatures, and the number of matching striae, are extracted and used to train a random forest to determine the probability of a comparison resulting from the same source (matching signatures) or from different sources (non-matching signatures).
+The model in \citet{hare:2017} was trained on a set of scans of bullets from the James Hamby Consecutively Rifled Ruger Barrel Study \citep{hamby:2009}, which included 10,384 land-to-land comparisons \citet{hare:2017}.
+See the supporting information for additional information on the signature similarity features.
 
@@
 
-\kge{We train a new random forest model using \Sexpr{format(dim(bullet_train)[1], big.mark = ",")} land-to-land comparisons from bullets in the James Hamby Consecutively Rifled Ruger Barrel Study \citep{hamby:2009} using the same nine comparison features used by \citet{hare:2017} to predict whether the two lands are a match.} We apply the trained random forest model to another set of bullets from the Hamby study with \Sexpr{dim(bullet_test)[1]} rows of land comparisons.
-\kge{See the supporting information for further descriptions of the data.}
-
-We first consider a global visualization of the relationship between the random forest predictions and the model features with a parallel coordinate plot of the training data (top facet) and testing data (bottom facets) \kge{\sout{predictions}} (\autoref{fig:figure-10}).
-\kge{\sout{The majority of same source observations with random forest probabilities close to 1 have a clear pattern of corresponding feature values.
-The known same source observations where the random forest is wrong (does not return probabilities close to 1) have feature values that reflect those of observations where same source is known to be false.}} \kge{The training data observations show a clear difference in feature values based on whether the corresponding random forest probability is close to 1 or 0.
-For example, observations with a random forest probability close to 1 tend to have high values of rough correlation, cross correlation function, and matches and low values of mismatches, distance, and non-consecutivley matching striae.
-The observations in the test data that are classified incorrectly by the random forest tend to have feature values similar to observations in the training data with similar random forest scores.
-For example, the observations in the test set known to be a match but have a random forest score below 0.5 have relatively low values of rough correlation, cross correlation function, and matches and relatively large values of mismatches, distance, and non-consecutivley matching striae compared to observations with a random forest probability close to 1.}
-
-LIME is applied to all test set observations using different tuning parameter values: 12 sampling methods (2-6 equally spaced bins, 2-6 quantile bins, kernel density estimation, and normal approximation) and 3 Gower exponents (0.5, 1, and 10).
+\hh{XXX minor change to emphasize that this is not a completly new model, just an expanded training set - otherwise you open yourself up to criticism of not using a validated model.
+The bulletxtrctr model was used in an external validation in \citet{validation}.
+}
+\hh{Here, we train a } random forest model using the same nine comparison features as \citet{hare:2017} to predict whether  \hh{two lands come from the same source} (i.e.\ are a match) in an expanded set of \Sexpr{format(dim(bullet_train)[1], big.mark = ",")} land-to-land comparisons from \hh{two sets of} bullets in the James Hamby Consecutively Rifled Ruger Barrel Study \citep{hamby:2009}.
+We apply the trained random forest model to 6 bullets from \hh{another set of} the Hamby study with \Sexpr{dim(bullet_test)[1]} rows of land comparisons.
+See the supporting information for further descriptions of the data.
+
+We first consider a global visualization of the relationship between the random forest predictions and the model features with a parallel coordinate plot of the training data (top facet) and testing data (bottom facets)  (\autoref{fig:figure-10}).
+In the training data we observe a clear difference in feature values based on whether the corresponding random forest scores are close to 1 or 0.
+High values of rough correlation, cross correlation function, and number of matches are indicative of random forest scores close to 1; similarly, low values of mismatches, distance, and non-consecutively matching striae are also associated with random forest scores close to 1.
+Observations in the test data that are classified incorrectly by the random forest tend to have feature values similar to observations in the training data with similar random forest scores.
+For example, the observations in the test set known to be a match but have a random forest score below 0.5 have relatively low values of rough correlation, cross correlation function, and matches and relatively large values of mismatches, distance, and non-consecutivley matching striae compared to observations with a random forest probability close to 1.
+
+LIME is applied to all test set observations using different tuning parameter values: 12 sampling methods (2 to 6 equally spaced bins, 2 to 6 quantile-bins, kernel density estimation, and normal approximation) and 3 Gower exponents (0.5, 1, and 10).
 Thus, a total of $12\times 3=36$ different applications of LIME are performed.
@@
 
-First, \kge{2 quantile bin \sout{the density}} simulation method \kge{applications} produce the same explanations for almost all cases and LIME tuning parameter values suggesting the LIME explanations are global and not local.
-Second, within a \kge{simulation method \sout{bin based simulation method}}, the features selected by LIME for an observation \kge{\sout{often vary by the number of bins but}} do not appear to vary by the Gower power.
-\kge{However, the LIME explanation for an observation often varies across simuluation methods.} With the equal bins, there are vertical stripes that suggest a dependence of the LIME explanations on the number of bins.
+First, applications of 2-quantile-bin simulations produce the same explanations for almost all cases and LIME tuning parameter values.
+This suggests that the LIME explanations are global and not local.
+Second, within a simulation method, the features selected by LIME for an observation do not appear to vary by the Gower power.
+However, the LIME explanation for an observation often varies across simuluation methods.
+With the-equal-bins, there are vertical stripes that suggest a dependence of the LIME explanations on the number of bins.
 The vertical stripes are not as apparent with the quantile bins.
 Lastly, there are clear differences between the LIME explanations produced by the bin based simulation methods for the matches and non-matches.
-This suggests that the features the random forest uses to classify a match or non-match are different.
+This suggests that different features are of importance in the random forest, depending on whether the observation corresponds to match or non-match.
 
@@
 \caption{Assessment metric plot for the applications of LIME on the bullet comparison data test set.
-\kge{\sout{The density simulation methods perform well for all metrics.
-The bin based metrics often do not agree in terms of performance across metrics.} There are discrepancies in performance across metrics for a set of tuning parameter values, but based on the overall performance of all three metrics, 4 equal bins with a Gower power of 0.5 appears to perform the best.}}
+There are discrepancies in performance across metrics for a set of tuning parameter values, but based on the overall performance of all three metrics, 4-equal-bins with a Gower power of 0.5 appears to perform the best.}
 \label{fig:figure-12}
@@
 To try to identify a set of LIME tuning parameter values with the most trustworthy set of explanations, an assessment metric plot is considered (\autoref{fig:figure-12}).
-\kge{\sout{All density simulation methods performed well based on the three metrics.
-This is an interesting result, since Figure \ref{fig:figure-11} shows that the density methods results in global explanations.
-The metric values for the bin based methods do not agree across metrics.
-For example, 2 and 3 quantile bins performed well according to the average $R^2$ but poorly according to MSEE.
-As a result, with the bin based methods, it is difficult to know which method to recommend.}} \kge{The performance of a set of tuning parameter values often do not agree across metrics.
-For example, both density methods perform well according to average fidelity but poorly according to MSEE, and all quantile bin methods perform well accroding to average $R^2$ but poorly based on average fidelity and MSEE.
-However, there is consistency in results across different Gower powers.} The applications using a power of 0.5 perform the best or as well as the other powers across all simulation methods suggesting that the power that leads to a more global explanation is preferred by LIME.
-\kge{\sout{Perhaps we can say that the kernel density method or 3 equal bins are the best performing methods, but unfortunately, Figure \ref{fig:figure-12} leaves us without a clear indication of which set of explanations to use to explain the random forest.}} \kge{It is not obvious which set of of tuning parameters are best, but perhaps, we can say that based on all three metrics, the 4 equal bins with a Gower power of 0.5 performs bettter than the other tuning parameter values considered.}
+The performance of a set of tuning parameter values often do not agree across metrics.
+For example, both density methods perform well according to average fidelity but poorly according to MSEE.
+All quantile bin methods perform well according to average $R^2$ but poorly based on average fidelity and MSEE.
+However, there is consistency in results across different Gower powers.
+The applications using a power of 0.5 perform the best or as well as the other powers across all simulation methods suggesting that the power that leads to a more global explanation is preferred by LIME.
+It is not apparent which set of tuning parameters is the best.
+Considering all three metrics, we might conclude that the 4-equal-bins with a Gower power of 0.5 performs better than the other tuning parameter values considered.
 
@@
 Figure~\ref{fig:figure-13} includes the visual representation plots of explanations (from \emph{lime}) and explanation scatterplots for cases M and NM.
-Plots for 4 equal bins and 4 quantile bins are included to depict tuning parameter values with good (4 equal bins) and mediocre (4 quantile bins) performance based on the assessment metric plot.
+Plots for 4-equal-bins and 4-quantile-bins are included to depict tuning parameter values with good (4-equal-bins) and mediocre (4-quantile-bins) performance based on the assessment metric plot.
 Plots for the kernel density simulation method are included in Appendix~\ref{exp-scatter_plus} (Figure \ref{fig:figure-B2}).
 
-First, focus on the explanation for case NM with 4 quantile bins.
-\kge{The explanation plot from \emph{lime} shows that observed values with rough correlation (rough\_cor) greater than 0.05 and mismatches value less than or equal to 7.17 support a random forest prediction in favor of a match, and the scatter plots show that many of the simulated values with rough correlation greater then 0.05 and mismatches less than 7.17 have random forest predictions greater than 0.5.
+First, focus on the explanation for case NM with 4-quantile-bins.
+The explanation plot from \emph{lime} shows that observed values with rough correlation (rough\_cor) greater than 0.05 and mismatches value less than or equal to 7.17 support a random forest prediction in favor of a match, and the scatter plots show that many of the simulated values with rough correlation greater than 0.05 and mismatches less than 7.17 have random forest predictions greater than 0.5.
 Additionally, the LIME explanation indicates that a value of cross correlation function (ccf) greater than 0.28 and less than or equal to 0.35 supports a non-match, and the scatter plots shows that the simulated values within this region have mostly random forest predictions less than 0.5.
 However, the random forest assigns a probability of 0.19 to case NM, which is not explained by the LIME explanation.
-Instead, consider that a better explanation based on the scatterplots would be that the random forest assigned a prediction probably close to 0 since the observation has a rough correlation less than 0.5, mismatches greater than 4, and cross correlation function 0.6.} \kge{\sout{Additionally, the LIME explanation indicates that a value of matches less than or equal to 1.66 contradicts a prediction in favor of a match, and the scatter plots show that almost all simulated values with a value of matches less than or equal to 1.66 have random forest predictions close to 0.
-While the LIME explanation makes sense based on the observations made from the explanation scatter plot, the plot also indicates that LIME falls short of providing a good explanation of the random forest prediction for case NM.
-Based on the scatter plot of CCF versus matches, a better explanation would be that because case NM has a value of CCF less than 0.8 and a value of matches less than 7, the random forest provides a prediction supporting a non-match.
-The relationship between CCF and rough correlation does not provide much evidence to support the random forest prediction one way or the other, but there is a pentagon shaped region at the bottom of the scatter plot of matches versus rough correlation with mostly predictions close to 0 that case NM falls in and supports the random forest prediction of a non-match.}}
+Instead, consider that a better explanation based on the scatterplots would be that the random forest assigned a prediction probably close to 0 since the observation has a rough correlation less than 0.5, mismatches greater than 4, and cross correlation function 0.6.
 
 The other explanation scatterplots can be interpreted in a similar manner.
-Overall, the plots identify that the \kge{\sout{3} 4} quantile bin explanations are not faithful to the random forest model predictions.
-The \kge{4 \sout{3}} equal bin explanations are more faithful to the random forest, but the regions captured by the bins do not align \kge{as well as they could} with the regions \kge{containing \sout{with}} similar probabilities produced by the random forest.
+Overall, the plots identify that the 4-quantile-bin explanations are not faithful to the random forest model predictions.
+The 4-equal-bin explanations are more faithful to the random forest, but the regions captured by the bins do not align well with the regions containing  similar probabilities produced by the random forest.
 
@@
 @
-\caption{Plots of LIME explanations (first and third rows) and explanation scatterplots (second and fourth rows) for  cases M and NM in the bullet test data for two tuning parameter values: \kge{4 \sout{3}} quantile bins (first column) and \kge{4 \sout{3}} equal bins (second column).
+\caption{Plots of LIME explanations (first and third rows) and explanation scatterplots (second and fourth rows) for  cases M and NM in the bullet test data for two tuning parameter values: 4-quantile-bins (first column) and 4-equal-bins (second column).
 The plots provide insights into the LIME explanations and allow for the assessment of the explanation quality.}
@@
 The examples of faithfulness metric comparisons in this paper (Figures \ref{fig:figure-07} and \ref{fig:figure-12}) both produced conflicting results.
-\kge{\sout{The density based simulation methods result in the best or close to the best performance even though the feature heatmaps (Figures \ref{fig:figure-06} and \ref{fig:figure-11}) show that the density simulation methods produce global explanations with minimal variation in features selected by LIME.
-For the bin based simulation methods, the two metrics often do not agree or contradict one another, which} This} makes it difficult to decide on a recommendation of a set of tuning parameter values that produce the explanations with the most faithful explainer model.
+This makes it difficult to decide on a recommendation of a set of tuning parameter values that produce the explanations with the most faithful explainer model.
 
@@
 The final claim, \textbf{localness}, is addressed by the feature heatmap and metric comparison plots.
-As stated, the feature heatmap reveals that the density simulation methods in the \kge{\data \ example \sout{examples of this paper}} results in global explanations where the same features are repeatedly chosen across all (or almost all) observations in the set of explanations.
+As stated, the feature heatmap reveals that the density simulation methods in the \data \ example  results in global explanations where the same features are repeatedly chosen across all (or almost all) observations in the set of explanations.
 This finding agrees with that of \citet{laugel:2018} who found LIME produced global explanations with the normal approximation simulation method.
@@
 
-Section \ref{exp-scatter} introduces explanation scatterplots under the default simulation method in the \emph{lime} R package: four quantile bins.
+Section \ref{exp-scatter} introduces explanation scatterplots under the default simulation method in the \emph{lime} R package: 4-quantile-bins.
 The structure of an explanation scatterplot remains the same if any bin based simulation method is used, i.e., any number of quantile or equally spaced bins.

### 2020-10-03 paper.tex
reknit paper for practice submission
couple of small edits

--- 2020-09-28 paper.tex
@@
 Based on high-resolution topological scans of land engraved areas, \citet{hare:2017} obtain signatures of striations from two bullet lands (\autoref{fig:figure-09}).
-Nine features quantifying the similarity of signatures, such as the cross-correlation function, the distance between signatures, and the number of matching striae, are extracted and used to train a random forest (available in the \emph{bulletxtrctr} R package) to determine the probability of a comparison resulting from the same source (matching signatures) or from different sources (non-matching signatures).
-See the supporting information for \kge{definitions of the features \sout{additional information on the data}}.
-The model was trained on a set of scans of bullets from the James Hamby Consecutively Rifled Ruger Barrel Study \citep{hamby:2009}, which included \kge{10,384 land-to-land comparisons \citet{hare:2017}}.
+Nine features quantifying the similarity of signatures, such as the cross-correlation function, the distance between signatures, and the number of matching striae, are extracted and used to train a random forest to determine the probability of a comparison resulting from the same source (matching signatures) or from different sources (non-matching signatures).
+The model in \citet{hare:2017} was trained on a set of scans of bullets from the James Hamby Consecutively Rifled Ruger Barrel Study \citep{hamby:2009}, which included 10,384 land-to-land comparisons \citet{hare:2017}.
+See the supporting information for additional information on the signature similarity features.
 
@@
 
-\kge{We train a new random forest model using 83,028 land-to-land comparisons from bullets in the James Hamby Consecutively Rifled Ruger Barrel Study \citep{hamby:2009} using the same nine comparison features used by \citet{hare:2017} to predict whether the two lands are a match.} We apply the trained random forest model to another set of bullets from the Hamby study with 364 rows of land comparisons.
-\kge{See the supporting information for further descriptions of the data.}
+\hh{XXX minor change to emphasize that this is not a completly new model, just an expanded training set - otherwise you open yourself up to criticism of not using a validated model.
+The bulletxtrctr model was used in an external validation in \citet{validation}.
+}
+\hh{Here, we train a } random forest model using the same nine comparison features as \citet{hare:2017} to predict whether  \hh{two lands come from the same source} (i.e.\ are a match) in an expanded set of 83,028 land-to-land comparisons from \hh{two sets of} bullets in the James Hamby Consecutively Rifled Ruger Barrel Study \citep{hamby:2009}.
+We apply the trained random forest model to 6 bullets from \hh{another set of} the Hamby study with 364 rows of land comparisons.
+See the supporting information for further descriptions of the data.
 
-We first consider a global visualization of the relationship between the random forest predictions and the model features with a parallel coordinate plot of the training data (top facet) and testing data (bottom facets) predictions (\autoref{fig:figure-10}).
-\kgc{May want to change the next sentence a bit now:} The majority of same source observations with random forest probabilities close to 1 have a clear pattern of corresponding feature values.
-The known same source observations where the random forest is wrong (does not return probabilities close to 1) have feature values that reflect those of observations where same source is known to be false.
+We first consider a global visualization of the relationship between the random forest predictions and the model features with a parallel coordinate plot of the training data (top facet) and testing data (bottom facets)  (\autoref{fig:figure-10}).
+In the training data we observe a clear difference in feature values based on whether the corresponding random forest scores are close to 1 or 0.
+High values of rough correlation, cross correlation function, and number of matches are indicative of random forest scores close to 1; similarly, low values of mismatches, distance, and non-consecutively matching striae are also associated with random forest scores close to 1.
+Observations in the test data that are classified incorrectly by the random forest tend to have feature values similar to observations in the training data with similar random forest scores.
+For example, the observations in the test set known to be a match but have a random forest score below 0.5 have relatively low values of rough correlation, cross correlation function, and matches and relatively large values of mismatches, distance, and non-consecutivley matching striae compared to observations with a random forest probability close to 1.
 
-LIME is applied to all test set observations using different tuning parameter values: 12 sampling methods (2-6 equally spaced bins, 2-6 quantile bins, kernel density estimation, and normal approximation) and 3 Gower exponents (0.5, 1, and 10).
+LIME is applied to all test set observations using different tuning parameter values: 12 sampling methods (2 to 6 equally spaced bins, 2 to 6 quantile-bins, kernel density estimation, and normal approximation) and 3 Gower exponents (0.5, 1, and 10).
 Thus, a total of $12\times 3=36$ different applications of LIME are performed.
@@
 
-\kgc{Will need to edit this paragraph:} First, the density simulation methods produce the same explanations for almost all cases and LIME tuning parameter values suggesting the LIME explanations are global and not local.
-Second, within a bin based simulation method, the features selected by LIME for an observation often vary by the number of bins but do not appear to vary by the Gower power.
-With the equal bins, there are vertical stripes that suggest a dependence of the LIME explanations on the number of bins.
+First, applications of 2-quantile-bin simulations produce the same explanations for almost all cases and LIME tuning parameter values.
+This suggests that the LIME explanations are global and not local.
+Second, within a simulation method, the features selected by LIME for an observation do not appear to vary by the Gower power.
+However, the LIME explanation for an observation often varies across simuluation methods.
+With the-equal-bins, there are vertical stripes that suggest a dependence of the LIME explanations on the number of bins.
 The vertical stripes are not as apparent with the quantile bins.
 Lastly, there are clear differences between the LIME explanations produced by the bin based simulation methods for the matches and non-matches.
-This suggests that the features the random forest uses to classify a match or non-match are different.
+This suggests that different features are of importance in the random forest, depending on whether the observation corresponds to match or non-match.
 
@@
 \end{knitrout}
-\caption{\kgc{Need to edit this:} Assessment metric plot for the applications of LIME on the bullet comparison data test set.
-The density simulation methods perform well for all metrics.
-The bin based metrics often do not agree in terms of performance across metrics.}
+\caption{Assessment metric plot for the applications of LIME on the bullet comparison data test set.
+There are discrepancies in performance across metrics for a set of tuning parameter values, but based on the overall performance of all three metrics, 4-equal-bins with a Gower power of 0.5 appears to perform the best.}
 \label{fig:figure-12}
@@
 To try to identify a set of LIME tuning parameter values with the most trustworthy set of explanations, an assessment metric plot is considered (\autoref{fig:figure-12}).
-\kgc{Need to edit the rest of this paragraph:} All density simulation methods performed well based on the three metrics.
-This is an interesting result, since \autoref{fig:figure-11} shows that the density methods results in global explanations.
-The metric values for the bin based methods do not agree across metrics.
-For example, 2 and 3 quantile bins performed well according to the average $R^2$ but poorly according to MSEE.
-As a result, with the bin based methods, it is difficult to know which method to recommend.
+The performance of a set of tuning parameter values often do not agree across metrics.
+For example, both density methods perform well according to average fidelity but poorly according to MSEE.
+All quantile bin methods perform well according to average $R^2$ but poorly based on average fidelity and MSEE.
+However, there is consistency in results across different Gower powers.
 The applications using a power of 0.5 perform the best or as well as the other powers across all simulation methods suggesting that the power that leads to a more global explanation is preferred by LIME.
-Perhaps we can say that the kernel density method or 3 equal bins  are the best performing methods, but unfortunately, \autoref{fig:figure-12} leaves us without a clear indication of which set of explanations to use to explain the random forest.
+It is not apparent which set of tuning parameters is the best.
+Considering all three metrics, we might conclude that the 4-equal-bins with a Gower power of 0.5 performs better than the other tuning parameter values considered.
 
@@
 Figure~\ref{fig:figure-13} includes the visual representation plots of explanations (from \emph{lime}) and explanation scatterplots for cases M and NM.
-Plots for 3 equal bins and 3 quantile bins are included to depict tuning parameter values with good (3 equal bins) and mediocre (3 quantile bins) performance based on the assessment metric plot.
+Plots for 4-equal-bins and 4-quantile-bins are included to depict tuning parameter values with good (4-equal-bins) and mediocre (4-quantile-bins) performance based on the assessment metric plot.
 Plots for the kernel density simulation method are included in Appendix~\ref{exp-scatter_plus} (Figure \ref{fig:figure-B2}).
 
-\kgc{Need to edit this pargraph:} First, focus on the explanation for case NM with 3 quantile bins.
-The explanation plot from \emph{lime} shows that an observed CCF value greater than 0.320 supports a random forest prediction in favor of a match, and the scatter plots show that many of the simulated values with CCF greater then 0.320 have random forest predictions greater than 0.5.
-Additionally, the LIME explanation indicates that a value of matches less than or equal to 1.66 contradicts a prediction in favor of a match, and the scatter plots show that almost all simulated values with a value of matches less than or equal to 1.66 have random forest predictions close to 0.
-While the LIME explanation makes sense based on the observations made from the explanation scatter plot, the plot also indicates that LIME falls short of providing a good explanation of the random forest prediction for case NM.
-Based on the scatter plot of CCF versus matches, a better explanation would be that because case NM has a value of CCF less than 0.8 and a value of matches less than 7, the random forest provides a prediction supporting a non-match.
-The relationship between CCF and rough correlation does not provide much evidence to support the random forest prediction one way or the other, but there is a pentagon shaped region at the bottom of the scatter plot of matches versus rough correlation with mostly predictions close to 0 that case NM falls in and supports the random forest prediction of a non-match.
+First, focus on the explanation for case NM with 4-quantile-bins.
+The explanation plot from \emph{lime} shows that observed values with rough correlation (rough\_cor) greater than 0.05 and mismatches value less than or equal to 7.17 support a random forest prediction in favor of a match, and the scatter plots show that many of the simulated values with rough correlation greater than 0.05 and mismatches less than 7.17 have random forest predictions greater than 0.5.
+Additionally, the LIME explanation indicates that a value of cross correlation function (ccf) greater than 0.28 and less than or equal to 0.35 supports a non-match, and the scatter plots shows that the simulated values within this region have mostly random forest predictions less than 0.5.
+However, the random forest assigns a probability of 0.19 to case NM, which is not explained by the LIME explanation.
+Instead, consider that a better explanation based on the scatterplots would be that the random forest assigned a prediction probably close to 0 since the observation has a rough correlation less than 0.5, mismatches greater than 4, and cross correlation function 0.6.
 
-\kgc{Maybe edit this pargraph:} The other explanation scatterplots can be interpreted in a similar manner.
-Overall, the plots identify that the 3 quantile bin explanations are not faithful to the random forest model predictions.
-The 3 equal bin explanations are more faithful to the random forest, but the regions captured by the bins still do not align with the regions with similar probabilities produced by the random forest.
+The other explanation scatterplots can be interpreted in a similar manner.
+Overall, the plots identify that the 4-quantile-bin explanations are not faithful to the random forest model predictions.
+The 4-equal-bin explanations are more faithful to the random forest, but the regions captured by the bins do not align well with the regions containing  similar probabilities produced by the random forest.
 
@@
 \end{knitrout}
-\caption{Plots of LIME explanations (first and third rows) and explanation scatterplots (second and fourth rows) for  cases M and NM in the bullet test data for two tuning parameter values: 3 quantile bins (first column) and 3 equal bins (second column).
+\caption{Plots of LIME explanations (first and third rows) and explanation scatterplots (second and fourth rows) for  cases M and NM in the bullet test data for two tuning parameter values: 4-quantile-bins (first column) and 4-equal-bins (second column).
 The plots provide insights into the LIME explanations and allow for the assessment of the explanation quality.}
@@
 The examples of faithfulness metric comparisons in this paper (Figures \ref{fig:figure-07} and \ref{fig:figure-12}) both produced conflicting results.
-The density based simulation methods result in the best or close to the best performance even though the feature heatmaps (Figures \ref{fig:figure-06} and \ref{fig:figure-11}) show that the density simulation methods produce global explanations with minimal variation in features selected by LIME.
-For the bin based simulation methods, the two metrics often do not agree or contradict one another, which makes it difficult to decide on a recommendation of a set of tuning parameter values that produce the explanations with the most faithful explainer model.
+This makes it difficult to decide on a recommendation of a set of tuning parameter values that produce the explanations with the most faithful explainer model.
 
@@
 
-\kgc{Probably need to make some edits here:} The final claim, \textbf{localness}, is addressed by the feature heatmap and metric comparison plots.
-As stated, the feature heatmap reveals that the density simulation methods in the examples of this paper results in global explanations where the same features are repeatedly chosen across all (or almost all) observations in the set of explanations.
-This finding agrees with that of \citep{laugel:2018} who found LIME produced global explanations with the normal approximation simulation method.
+The final claim, \textbf{localness}, is addressed by the feature heatmap and metric comparison plots.
+As stated, the feature heatmap reveals that the density simulation methods in the \data \ example  results in global explanations where the same features are repeatedly chosen across all (or almost all) observations in the set of explanations.
+This finding agrees with that of \citet{laugel:2018} who found LIME produced global explanations with the normal approximation simulation method.
 For the bin based simulation methods in the bullet data example, the feature heatmap showed that the features chosen for the explanations varied between the two classification categories (match versus non-match).

### 2020-10-03 paper.Rnw
couple of typos

@@
 
+\hh{XXX mention overall goodness of fit or oob error rates?}
 We first consider a global visualization of the relationship between the random forest predictions and the model features with a parallel coordinate plot of the training data (top facet) and testing data (bottom facets)  (\autoref{fig:figure-10}).
@@
 Observations in the test data that are classified incorrectly by the random forest tend to have feature values similar to observations in the training data with similar random forest scores.
-For example, the observations in the test set known to be a match but have a random forest score below 0.5 have relatively low values of rough correlation, cross correlation function, and matches and relatively large values of mismatches, distance, and non-consecutivley matching striae compared to observations with a random forest probability close to 1.
+For example, the observations in the test set known to be a match but have a random forest score below 0.5 have relatively low values of rough correlation, cross correlation function, and matches and relatively large values of mismatches, distance, and non-consecutively matching striae compared to observations with a random forest probability close to 1.
 
@@
 Second, within a simulation method, the features selected by LIME for an observation do not appear to vary by the Gower power.
-However, the LIME explanation for an observation often varies across simuluation methods.
+However, the LIME explanation for an observation often varies across simulation methods.
 With the-equal-bins, there are vertical stripes that suggest a dependence of the LIME explanations on the number of bins.
@@
 The code used to produce the manuscript and the data from examples in Section \ref{application} are available in the following GitHub Repository: \href{https://github.com/goodekat/LIME-diagnostics-paper}{https://github.com/goodekat/LIME-diagnostics-paper}.
-Additional information about the bullet matching data are available at XXX.
+\hh{\sout{ Additional information about the bullet matching data are available at XXX.}}
 

### 2020-10-06 code/03-submission-steps.Rmd
changed readme to uppercase in data folder

@@
       c(
-        "../data/readme.txt",
+        "../data/README.txt",
         "../data/bullet-test.csv.zip",

### 2020-10-06 paper.Rnw
results were reproducible! so I updated the text and am working on more changes to text now

@@
 \articletype{Research Article}
-\received{XX XX 2020}
+\received{XX XX XXXX}
 \revised{XX XX XXXX}
@@
 First, consider the claim of localness.
-The weights decay relatively slowly  outside of the intersection of the 2-quantil-bin suggesting that the LIME explanation is highly influenced by points outside of the bins containing the prediction of interest.
+The weights decay relatively slowly outside of the intersection of the 2-quantile-bin suggesting that the LIME explanation is highly influenced by points outside of the bins containing the prediction of interest.
 However, it is difficult to say if the claim of localness has been violated, because a definition of a local region is not specified.
@@
       y = factor(bullet_train$samesource),
-      x = bullet_train %>% select(bullet_features),
+      x = bullet_train %>% select(all_of(bullet_features)),
       ntree = bullet_rf_ntrees,
@@
 
-\hh{XXX minor change to emphasize that this is not a completly new model, just an expanded training set - otherwise you open yourself up to criticism of not using a validated model.
-The bulletxtrctr model was used in an external validation in \citet{validation}.
-}
-\hh{Here, we train a } random forest model using the same nine comparison features as \citet{hare:2017} to predict whether  \hh{two lands come from the same source} (i.e.\ are a match) in an expanded set of \Sexpr{format(dim(bullet_train)[1], big.mark = ",")} land-to-land comparisons from \hh{two sets of} bullets in the James Hamby Consecutively Rifled Ruger Barrel Study \citep{hamby:2009}.
-We apply the trained random forest model to 6 bullets from \hh{another set of} the Hamby study with \Sexpr{dim(bullet_test)[1]} rows of land comparisons.
+%XXX minor change to emphasize that this is not a completely new model, just an expanded training set - otherwise you open yourself up to criticism of not using a validated model.
+The bulletxtrctr model was used in an external validation in \citet{vanderplas:2020b}.
+
+\kgc{Your comment about not training a whole new model made lost of sense. Are my changes okay?}
+
+\kge{A random forest model fit to an expanded dataset of \Sexpr{format(dim(bullet_train)[1], big.mark = ",")} land-to-land comparisons from two sets of bullets in the James Hamby Consecutively Rifled Ruger Barrel Study \citep{hamby:2009} was validated in \citet{vanderplas:2020b}.
+Here, we train a random forest model to mimic the one validated in model \citet{vanderplas:2020b} using the same data, model structure, and features (the nine similarity measures developed in \citet{hare:2017})}.
+%Here, we train a random forest model using the same \kge{data, features (the nine similarity measures developed in \citet{hare:2017}), and model structure as a random forest validated in \citet{vanderplas:2020b}} \kge{\sout{nine comparison features as \citet{hare:2017}}} to predict whether two lands come from the same source (i.e.\ are a match) in an expanded set of \Sexpr{format(dim(bullet_train)[1], big.mark = ",")} land-to-land comparisons from two sets of bullets in the James Hamby Consecutively Rifled Ruger Barrel Study \citep{hamby:2009}.
+We apply the trained random forest model to 6 bullets from another set of the Hamby study with \Sexpr{dim(bullet_test)[1]} rows of land comparisons.
 See the supporting information for further descriptions of the data.
 
-\hh{XXX mention overall goodness of fit or oob error rates?}
-We first consider a global visualization of the relationship between the random forest predictions and the model features with a parallel coordinate plot of the training data (top facet) and testing data (bottom facets)  (\autoref{fig:figure-10}).
+\hh{XXX mention overall goodness of fit or oob error rates?} We first consider a global visualization of the relationship between the random forest predictions and the model features with a parallel coordinate plot of the training data (top facet) and testing data (bottom facets)  (\autoref{fig:figure-10}).
 In the training data we observe a clear difference in feature values based on whether the corresponding random forest scores are close to 1 or 0.
@@
 
-First, focus on the explanation for case NM with 4-quantile-bins.
-The explanation plot from \emph{lime} shows that observed values with rough correlation (rough\_cor) greater than 0.05 and mismatches value less than or equal to 7.17 support a random forest prediction in favor of a match, and the scatter plots show that many of the simulated values with rough correlation greater than 0.05 and mismatches less than 7.17 have random forest predictions greater than 0.5.
+\kge{We \sout{First,}} focus on the explanation for case NM with 4-quantile-bins.
+The explanation plot from \emph{lime} shows that \kge{the} observed values \kge{of NM of \sout{with}} \kge{mismatches less than or equal to 7.17, rough correlation (rough\_cor) greater than 0.05, and D less than or equal to 0.002 support a random forest prediction in favor of a match.
+The scatter plots show that many of the simulated values in the rectangular regions with mismatches less than 7.17, rough correlation greater than 0.05, and distance less than or equal to 0.002 have random forest predictions greater than 0.5.} %rough correlation (rough\_cor) greater than 0.05 and mismatches value less than or equal to 7.17 support a random forest prediction in favor of a match, and the scatter plots show that many of the simulated values with rough correlation greater than 0.05 and mismatches less than 7.17 have random forest predictions greater than 0.5.
 Additionally, the LIME explanation indicates that a value of cross correlation function (ccf) greater than 0.28 and less than or equal to 0.35 supports a non-match, and the scatter plots shows that the simulated values within this region have mostly random forest predictions less than 0.5.
-However, the random forest assigns a probability of 0.19 to case NM, which is not explained by the LIME explanation.
-Instead, consider that a better explanation based on the scatterplots would be that the random forest assigned a prediction probably close to 0 since the observation has a rough correlation less than 0.5, mismatches greater than 4, and cross correlation function 0.6.
+However, the random forest assigns a probability of 0.21 to case NM, which is not explained by the LIME explanation \kge{that provides all explanations in support of a match}.
+Instead, consider that a better explanation based on the scatterplots would be that the random forest assigned a prediction probably \kge{below 0.5 \sout{close to 0}} since \kge{NM has observed values of mismatches less than 5, rough correlation greater than 0.25, and distance greater than 0.001.}%the observation has a rough correlation less than 0.5, mismatches greater than 4, and cross correlation function 0.6.
 
 The other explanation scatterplots can be interpreted in a similar manner.
-Overall, the plots identify that the 4-quantile-bin explanations are not faithful to the random forest model predictions.
-The 4-equal-bin explanations are more faithful to the random forest, but the regions captured by the bins do not align well with the regions containing  similar probabilities produced by the random forest.
+\kge{\sout{Overall, t} T}he \kge{three plots depict situations where the explanations are faithful} %plots identify that the 4-quantile-bin explanations are not faithful to the random forest model predictions.
+The 4-equal-bin explanations are more faithful
+to the random forest, but the regions captured by the \kge{intersections of the} bins do not align well with the regions containing similar probabilities produced by the random forest.
 
@@
 The code used to produce the manuscript and the data from examples in Section \ref{application} are available in the following GitHub Repository: \href{https://github.com/goodekat/LIME-diagnostics-paper}{https://github.com/goodekat/LIME-diagnostics-paper}.
-\hh{\sout{ Additional information about the bullet matching data are available at XXX.}}
 
@@
 @
-\caption{Explanation scatterplots for LIME explanations using kernel density simulation for the cases M and NM of the bullet comparison.}
+\caption{Explanation scatterplots for LIME explanations using kernel density simulation for the cases M and NM of the bullet comparison test data.}
 \label{fig:figure-B2}

### 2020-10-07 paper.Rnw
edits to text in paper

@@
 bullet_test$rfscore = predict(bullet_rf, bullet_test %>% select(bullet_features), type = "prob")[,2]
+
+# Compute OOB model metrics
+bullet_rf_oob_acc = round(sum(predict(bullet_rf) == bullet_train$samesource) / length(bullet_train$samesource), 2)
+bullet_rf_oob_fp = round(bullet_rf$confusion[,3][2], 2)
+bullet_rf_oob_fn = round(bullet_rf$confusion[,3][1], 4)
+
+# Obtain model predictions and confusion matrix from test data
+bullet_test_pred = predict(bullet_rf, bullet_test %>% select(bullet_features))
+bullet_test_confus = table(bullet_test_pred, bullet_test$samesource)
+
+# Compute test data model metrics
+bullet_rf_test_acc = round(sum(bullet_test_pred == bullet_test$samesource) / length(bullet_test$samesource), 2)
+bullet_rf_test_fp = round(bullet_test_confus[2,1] / (bullet_test_confus[2,1] + bullet_test_confus[2,2]), 2)
+bullet_rf_test_fn = round(bullet_test_confus[1,2] / (bullet_test_confus[1,1] + bullet_test_confus[1,2]), 4)
 @
@@
 
-\kgc{Your comment about not training a whole new model made lost of sense. Are my changes okay?}
-
-\kge{A random forest model fit to an expanded dataset of \Sexpr{format(dim(bullet_train)[1], big.mark = ",")} land-to-land comparisons from two sets of bullets in the James Hamby Consecutively Rifled Ruger Barrel Study \citep{hamby:2009} was validated in \citet{vanderplas:2020b}.
-Here, we train a random forest model to mimic the one validated in model \citet{vanderplas:2020b} using the same data, model structure, and features (the nine similarity measures developed in \citet{hare:2017})}.
+\kgc{Your comment about being clear that we are not training a whole new model made lots of sense.
+I made a few more changes.
+Do they look okay?} \kge{A random forest model fit to an expanded dataset of \Sexpr{format(dim(bullet_train)[1], big.mark = ",")} land-to-land comparisons from two sets of bullets in the James Hamby Consecutively Rifled Ruger Barrel Study \citep{hamby:2009} was validated in \citet{vanderplas:2020b}.
+Here, we train a random forest model to mimic the model validated in \citet{vanderplas:2020b} using the same data, model structure, and features (the nine similarity measures developed in \citet{hare:2017})}.
 %Here, we train a random forest model using the same \kge{data, features (the nine similarity measures developed in \citet{hare:2017}), and model structure as a random forest validated in \citet{vanderplas:2020b}} \kge{\sout{nine comparison features as \citet{hare:2017}}} to predict whether two lands come from the same source (i.e.\ are a match) in an expanded set of \Sexpr{format(dim(bullet_train)[1], big.mark = ",")} land-to-land comparisons from two sets of bullets in the James Hamby Consecutively Rifled Ruger Barrel Study \citep{hamby:2009}.
@@
 See the supporting information for further descriptions of the data.
-
-\hh{XXX mention overall goodness of fit or oob error rates?} We first consider a global visualization of the relationship between the random forest predictions and the model features with a parallel coordinate plot of the training data (top facet) and testing data (bottom facets)  (\autoref{fig:figure-10}).
+\kge{The newly trained random forest has an out-of-bag accuracy of \Sexpr{bullet_rf_oob_acc} and out-of-bag false positive and false negative rates of \Sexpr{bullet_rf_oob_fp} and \Sexpr{bullet_rf_oob_fn}, respectively.
+On the test data, the random forest has an accuracy of \Sexpr{bullet_rf_test_acc} and false positive and false negative rates of \Sexpr{bullet_rf_test_fp} and \Sexpr{bullet_rf_test_fn}, respectively.}
+
+We first consider a global visualization of the relationship between the random forest predictions and the model features with a parallel coordinate plot of the training data (top facet) and testing data (bottom facets)  (\autoref{fig:figure-10}).
 In the training data we observe a clear difference in feature values based on whether the corresponding random forest scores are close to 1 or 0.

### 2020-10-07 paper.tex
results were reproducible! so I updated the text and am working on more changes to text now
edits to text in paper

@@
 
-\hh{XXX minor change to emphasize that this is not a completly new model, just an expanded training set - otherwise you open yourself up to criticism of not using a validated model.
-The bulletxtrctr model was used in an external validation in \citet{validation}.
-}
-\hh{Here, we train a } random forest model using the same nine comparison features as \citet{hare:2017} to predict whether  \hh{two lands come from the same source} (i.e.\ are a match) in an expanded set of 83,028 land-to-land comparisons from \hh{two sets of} bullets in the James Hamby Consecutively Rifled Ruger Barrel Study \citep{hamby:2009}.
-We apply the trained random forest model to 6 bullets from \hh{another set of} the Hamby study with 364 rows of land comparisons.
+%XXX minor change to emphasize that this is not a completely new model, just an expanded training set - otherwise you open yourself up to criticism of not using a validated model.
+The bulletxtrctr model was used in an external validation in \citet{vanderplas:2020b}.
+
+\kgc{Your comment about being clear that we are not training a whole new model made lots of sense.
+I made a few more changes.
+Do they look okay?} \kge{A random forest model fit to an expanded dataset of 83,028 land-to-land comparisons from two sets of bullets in the James Hamby Consecutively Rifled Ruger Barrel Study \citep{hamby:2009} was validated in \citet{vanderplas:2020b}.
+Here, we train a random forest model to mimic the model validated in \citet{vanderplas:2020b} using the same data, model structure, and features (the nine similarity measures developed in \citet{hare:2017})}.
+%Here, we train a random forest model using the same \kge{data, features (the nine similarity measures developed in \citet{hare:2017}), and model structure as a random forest validated in \citet{vanderplas:2020b}} \kge{\sout{nine comparison features as \citet{hare:2017}}} to predict whether two lands come from the same source (i.e.\ are a match) in an expanded set of 83,028 land-to-land comparisons from two sets of bullets in the James Hamby Consecutively Rifled Ruger Barrel Study \citep{hamby:2009}.
+We apply the trained random forest model to 6 bullets from another set of the Hamby study with 364 rows of land comparisons.
 See the supporting information for further descriptions of the data.
+\kge{The newly trained random forest has an out-of-bag accuracy of 1 and out-of-bag false positive and false negative rates of 0.3 and \ensuremath{2\times 10^{-4}}, respectively.
+On the test data, the random forest has an accuracy of 0.85 and false positive and false negative rates of 0.55 and 0.011, respectively.}
 
-\hh{XXX mention overall goodness of fit or oob error rates?}
 We first consider a global visualization of the relationship between the random forest predictions and the model features with a parallel coordinate plot of the training data (top facet) and testing data (bottom facets)  (\autoref{fig:figure-10}).
@@
 \end{knitrout}
-\caption{Explanation scatterplots for LIME explanations using kernel density simulation for the cases M and NM of the bullet comparison.}
+\caption{Explanation scatterplots for LIME explanations using kernel density simulation for the cases M and NM of the bullet comparison test data.}
 \label{fig:figure-B2}

### 2020-10-07 submission/paper.tex
updating submission folder with current versions (but will need to be updated again)

--- 2020-09-09 paper.tex
@@
 First, consider the claim of localness.
-The weights decay relatively slowly  outside of the intersection of the two quantile bins suggesting that the LIME explanation is highly influenced by points outside of the bins containing the prediction of interest.
+The weights decay relatively slowly outside of the intersection of the 2-quantile-bin suggesting that the LIME explanation is highly influenced by points outside of the bins containing the prediction of interest.
 However, it is difficult to say if the claim of localness has been violated, because a definition of a local region is not specified.
@@
 
-In response, \citet{hare:2016} proposed an automated machine learning method for bullet matching to complement a visual inspection by firearm examiners.
-Based on high-resolution topological scans of land engraved areas, \citet{hare:2016} obtain signatures of striations from two bullet lands (\autoref{fig:figure-09}).
-Nine features quantifying the similarity of signatures, such as the cross-correlation function, the distance between signatures, and the number of matching striae, are extracted and used to train a random forest (available in the \emph{bulletxtrctr} R package) to determine the probability of a comparison resulting from the same source (matching signatures) or from different sources (non-matching signatures).
-See the supporting information for additional information on the data.
-The model was trained on a set of scans of bullets from the James Hamby Consecutively Rifled Ruger Barrel Study \citep{hamby:2009}, which includes over 80,000 land-to-land comparisons.
+In response, \citet{hare:2017} proposed an automated machine learning method for bullet matching to complement a visual inspection by firearm examiners.
+Based on high-resolution topological scans of land engraved areas, \citet{hare:2017} obtain signatures of striations from two bullet lands (\autoref{fig:figure-09}).
+Nine features quantifying the similarity of signatures, such as the cross-correlation function, the distance between signatures, and the number of matching striae, are extracted and used to train a random forest to determine the probability of a comparison resulting from the same source (matching signatures) or from different sources (non-matching signatures).
+The model in \citet{hare:2017} was trained on a set of scans of bullets from the James Hamby Consecutively Rifled Ruger Barrel Study \citep{hamby:2009}, which included 10,384 land-to-land comparisons \citet{hare:2017}.
+See the supporting information for additional information on the signature similarity features.
 
@@
 
-We apply the trained random forest model from \citet{hare:2016} to another set of bullets from the Hamby study with 432 rows of land comparisons.
-We first consider a global visualization of the relationship between the random forest predictions and the model features with a parallel coordinate plot of the training data (top facet) and testing data (bottom facets) predictions (\autoref{fig:figure-10}).
-The majority of same source observations with random forest probabilities close to 1 have a clear pattern of corresponding feature values.
-The known same source observations where the random forest is wrong (does not return probabilities close to 1) have feature values that reflect those of observations where same source is known to be false.
+%XXX minor change to emphasize that this is not a completely new model, just an expanded training set - otherwise you open yourself up to criticism of not using a validated model.
+The bulletxtrctr model was used in an external validation in \citet{vanderplas:2020b}.
 
-LIME is applied to all test set observations using different tuning parameter values: 12 sampling methods (2-6 equally spaced bins, 2-6 quantile bins, kernel density estimation, and normal approximation) and 3 Gower exponents (0.5, 1, and 10).
+\kgc{Your comment about being clear that we are not training a whole new model made lots of sense.
+I made a few more changes.
+Do they look okay?} \kge{A random forest model fit to an expanded dataset of 83,028 land-to-land comparisons from two sets of bullets in the James Hamby Consecutively Rifled Ruger Barrel Study \citep{hamby:2009} was validated in \citet{vanderplas:2020b}.
+Here, we train a random forest model to mimic the model validated in \citet{vanderplas:2020b} using the same data, model structure, and features (the nine similarity measures developed in \citet{hare:2017})}.
+%Here, we train a random forest model using the same \kge{data, features (the nine similarity measures developed in \citet{hare:2017}), and model structure as a random forest validated in \citet{vanderplas:2020b}} \kge{\sout{nine comparison features as \citet{hare:2017}}} to predict whether two lands come from the same source (i.e.\ are a match) in an expanded set of 83,028 land-to-land comparisons from two sets of bullets in the James Hamby Consecutively Rifled Ruger Barrel Study \citep{hamby:2009}.
+We apply the trained random forest model to 6 bullets from another set of the Hamby study with 364 rows of land comparisons.
+See the supporting information for further descriptions of the data.
+\kge{The newly trained random forest has an out-of-bag accuracy of 1 and out-of-bag false positive and false negative rates of 0.3 and \ensuremath{2\times 10^{-4}}, respectively.
+On the test data, the random forest has an accuracy of 0.85 and false positive and false negative rates of 0.55 and 0.011, respectively.}
+
+We first consider a global visualization of the relationship between the random forest predictions and the model features with a parallel coordinate plot of the training data (top facet) and testing data (bottom facets)  (\autoref{fig:figure-10}).
+In the training data we observe a clear difference in feature values based on whether the corresponding random forest scores are close to 1 or 0.
+High values of rough correlation, cross correlation function, and number of matches are indicative of random forest scores close to 1; similarly, low values of mismatches, distance, and non-consecutively matching striae are also associated with random forest scores close to 1.
+Observations in the test data that are classified incorrectly by the random forest tend to have feature values similar to observations in the training data with similar random forest scores.
+For example, the observations in the test set known to be a match but have a random forest score below 0.5 have relatively low values of rough correlation, cross correlation function, and matches and relatively large values of mismatches, distance, and non-consecutively matching striae compared to observations with a random forest probability close to 1.
+
+LIME is applied to all test set observations using different tuning parameter values: 12 sampling methods (2 to 6 equally spaced bins, 2 to 6 quantile-bins, kernel density estimation, and normal approximation) and 3 Gower exponents (0.5, 1, and 10).
 Thus, a total of $12\times 3=36$ different applications of LIME are performed.
@@
 
-First, the density simulation methods produce the same explanations for almost all cases and LIME tuning parameter values suggesting the LIME explanations are global and not local.
-Second, within a bin based simulation method, the features selected by LIME for an observation often vary by the number of bins but do not appear to vary by the Gower power.
-With the equal bins, there are vertical stripes that suggest a dependence of the LIME explanations on the number of bins.
+First, applications of 2-quantile-bin simulations produce the same explanations for almost all cases and LIME tuning parameter values.
+This suggests that the LIME explanations are global and not local.
+Second, within a simulation method, the features selected by LIME for an observation do not appear to vary by the Gower power.
+However, the LIME explanation for an observation often varies across simulation methods.
+With the-equal-bins, there are vertical stripes that suggest a dependence of the LIME explanations on the number of bins.
 The vertical stripes are not as apparent with the quantile bins.
 Lastly, there are clear differences between the LIME explanations produced by the bin based simulation methods for the matches and non-matches.
-This suggests that the features the random forest uses to classify a match or non-match are different.
+This suggests that different features are of importance in the random forest, depending on whether the observation corresponds to match or non-match.
 
@@
 \caption{Assessment metric plot for the applications of LIME on the bullet comparison data test set.
-The density simulation methods perform well for all metrics.
-The bin based metrics often do not agree in terms of performance across metrics.}
+There are discrepancies in performance across metrics for a set of tuning parameter values, but based on the overall performance of all three metrics, 4-equal-bins with a Gower power of 0.5 appears to perform the best.}
 \label{fig:figure-12}
@@
 To try to identify a set of LIME tuning parameter values with the most trustworthy set of explanations, an assessment metric plot is considered (\autoref{fig:figure-12}).
-All density simulation methods performed well based on the three metrics.
-This is an interesting result, since \autoref{fig:figure-11} shows that the density methods results in global explanations.
-The metric values for the bin based methods do not agree across metrics.
-For example, 2 and 3 quantile bins performed well according to the average $R^2$ but poorly according to MSEE.
-As a result, with the bin based methods, it is difficult to know which method to recommend.
+The performance of a set of tuning parameter values often do not agree across metrics.
+For example, both density methods perform well according to average fidelity but poorly according to MSEE.
+All quantile bin methods perform well according to average $R^2$ but poorly based on average fidelity and MSEE.
+However, there is consistency in results across different Gower powers.
 The applications using a power of 0.5 perform the best or as well as the other powers across all simulation methods suggesting that the power that leads to a more global explanation is preferred by LIME.
-Perhaps we can say that the kernel density method or 3 equal bins  are the best performing methods, but unfortunately, \autoref{fig:figure-12} leaves us without a clear indication of which set of explanations to use to explain the random forest.
+It is not apparent which set of tuning parameters is the best.
+Considering all three metrics, we might conclude that the 4-equal-bins with a Gower power of 0.5 performs better than the other tuning parameter values considered.
 
@@
 Figure~\ref{fig:figure-13} includes the visual representation plots of explanations (from \emph{lime}) and explanation scatterplots for cases M and NM.
-Plots for 3 equal bins and 3 quantile bins are included to depict tuning parameter values with good (3 equal bins) and mediocre (3 quantile bins) performance based on the assessment metric plot.
+Plots for 4-equal-bins and 4-quantile-bins are included to depict tuning parameter values with good (4-equal-bins) and mediocre (4-quantile-bins) performance based on the assessment metric plot.
 Plots for the kernel density simulation method are included in Appendix~\ref{exp-scatter_plus} (Figure \ref{fig:figure-B2}).
 
-First, focus on the explanation for case NM with 3 quantile bins.
-The explanation plot from \emph{lime} shows that an observed CCF value greater than 0.320 supports a random forest prediction in favor of a match, and the scatter plots show that many of the simulated values with CCF greater then 0.320 have random forest predictions greater than 0.5.
-Additionally, the LIME explanation indicates that a value of matches less than or equal to 1.66 contradicts a prediction in favor of a match, and the scatter plots show that almost all simulated values with a value of matches less than or equal to 1.66 have random forest predictions close to 0.
-While the LIME explanation makes sense based on the observations made from the explanation scatter plot, the plot also indicates that LIME falls short of providing a good explanation of the random forest prediction for case NM.
-Based on the scatter plot of CCF versus matches, a better explanation would be that because case NM has a value of CCF less than 0.8 and a value of matches less than 7, the random forest provides a prediction supporting a non-match.
-The relationship between CCF and rough correlation does not provide much evidence to support the random forest prediction one way or the other, but there is a pentagon shaped region at the bottom of the scatter plot of matches versus rough correlation with mostly predictions close to 0 that case NM falls in and supports the random forest prediction of a non-match.
+\kge{We \sout{First,}} focus on the explanation for case NM with 4-quantile-bins.
+The explanation plot from \emph{lime} shows that \kge{the} observed values \kge{of NM of \sout{with}} \kge{mismatches less than or equal to 7.17, rough correlation (rough\_cor) greater than 0.05, and D less than or equal to 0.002 support a random forest prediction in favor of a match.
+The scatter plots show that many of the simulated values in the rectangular regions with mismatches less than 7.17, rough correlation greater than 0.05, and distance less than or equal to 0.002 have random forest predictions greater than 0.5.} %rough correlation (rough\_cor) greater than 0.05 and mismatches value less than or equal to 7.17 support a random forest prediction in favor of a match, and the scatter plots show that many of the simulated values with rough correlation greater than 0.05 and mismatches less than 7.17 have random forest predictions greater than 0.5.
+Additionally, the LIME explanation indicates that a value of cross correlation function (ccf) greater than 0.28 and less than or equal to 0.35 supports a non-match, and the scatter plots shows that the simulated values within this region have mostly random forest predictions less than 0.5.
+However, the random forest assigns a probability of 0.21 to case NM, which is not explained by the LIME explanation \kge{that provides all explanations in support of a match}.
+Instead, consider that a better explanation based on the scatterplots would be that the random forest assigned a prediction probably \kge{below 0.5 \sout{close to 0}} since \kge{NM has observed values of mismatches less than 5, rough correlation greater than 0.25, and distance greater than 0.001.}%the observation has a rough correlation less than 0.5, mismatches greater than 4, and cross correlation function 0.6.
 
 The other explanation scatterplots can be interpreted in a similar manner.
-Overall, the plots identify that the 3 quantile bin explanations are not faithful to the random forest model predictions.
-The 3 equal bin explanations are more faithful to the random forest, but the regions captured by the bins still do not align with the regions with similar probabilities produced by the random forest.
+\kge{\sout{Overall, t} T}he \kge{three plots depict situations where the explanations are faithful} %plots identify that the 4-quantile-bin explanations are not faithful to the random forest model predictions.
+The 4-equal-bin explanations are more faithful
+to the random forest, but the regions captured by the \kge{intersections of the} bins do not align well with the regions containing similar probabilities produced by the random forest.
 
@@
 The final claim, \textbf{localness}, is addressed by the feature heatmap and metric comparison plots.
-As stated, the feature heatmap reveals that the density simulation methods in the examples of this paper results in global explanations where the same features are repeatedly chosen across all (or almost all) observations in the set of explanations.
-This finding agrees with that of \citep{laugel:2018} who found LIME produced global explanations with the normal approximation simulation method.
+As stated, the feature heatmap reveals that the density simulation methods in the \data \ example  results in global explanations where the same features are repeatedly chosen across all (or almost all) observations in the set of explanations.
+This finding agrees with that of \citet{laugel:2018} who found LIME produced global explanations with the normal approximation simulation method.
 For the bin based simulation methods in the bullet data example, the feature heatmap showed that the features chosen for the explanations varied between the two classification categories (match versus non-match).
@@
 The code used to produce the manuscript and the data from examples in Section \ref{application} are available in the following GitHub Repository: \href{https://github.com/goodekat/LIME-diagnostics-paper}{https://github.com/goodekat/LIME-diagnostics-paper}.
-Additional information about the bullet matching data are available at XXX.
 

### 2020-10-07 README.Rmd
updated to do list
changed wording from knit to compile

@@
 
-- Rewrite Sections 4 and 5 as needed
-- Prepare for submission
+- Final clean up and proof read of sections 4 and 5
+- Prepare for submission (make sure to update date on cover letter)
 - Upload the files for submission and submit
@@
 
-## Instructions for Knitting Manuscript
+## Instructions for Compiling Manuscript
 
-When the manuscript is knit, various files will be generated (such as data-bullet-explain.rds and figure-10-1.png).
-The first time the manuscript is knit, it will take a while (possibly up to several hours).
-Once these files have been generated during the first knit, the manuscript will take much less time to knit (approximately a few minutes).
+When the manuscript is compiled, various files will be generated (such as data-bullet-explain.rds and figure-10-1.png).
+The first time the manuscript is compiled, it will take a while (possibly up to several hours).
+Once these files have been generated, the manuscript will take much less time to compile (approximately a few minutes).
 
-Follow these instructions to knit the manuscript:
+Follow these instructions to compile the manuscript:
 
@@
 
-3. Knit manuscript (via the [paper.Rnw](paper.Rnw) file).
+3. Compile manuscript (via the [paper.Rnw](paper.Rnw) file).
 

### 2020-10-07 README.Rmd
added an idea

@@
 
+- Add a sentence in the section on explanation scatterplots about removing the blindfold
 - Final clean up and proof read of sections 4 and 5

### 2020-10-07 README.Rmd
updated to do list

--- 2020-10-07 README.Rmd
@@
 
-- Final clean up and proof read of sections 4 and 5
+- Final proof read of sections 4 and 5
 - Prepare for submission (make sure to update date on cover letter)
 - Upload the files for submission and submit
+- Save a "snapshot" of the repo in the CyBox folder
 

### 2020-10-07 paper.Rnw
updates to paper after meeting (just need to proof read sections 4 and 5 one more time)

@@
 
-The explanation scatterplot is built by plotting the LIME simulated data for the top two features identified by the explanation in a scatterplot and coloring these points by the  predictions from the complex model.
+The explanation scatterplot applies the concept of plotting the model in the data space discussed in \citet{wickham:2015}.
+The plot is built by plotting the LIME simulated data for the top two features identified by the explanation in a scatterplot and coloring these points by the predictions from the complex model.
 The point size represents the weight assigned by LIME.
@@
 
-%XXX minor change to emphasize that this is not a completely new model, just an expanded training set - otherwise you open yourself up to criticism of not using a validated model.
-The bulletxtrctr model was used in an external validation in \citet{vanderplas:2020b}.
-
-\kgc{Your comment about being clear that we are not training a whole new model made lots of sense.
-I made a few more changes.
-Do they look okay?} \kge{A random forest model fit to an expanded dataset of \Sexpr{format(dim(bullet_train)[1], big.mark = ",")} land-to-land comparisons from two sets of bullets in the James Hamby Consecutively Rifled Ruger Barrel Study \citep{hamby:2009} was validated in \citet{vanderplas:2020b}.
-Here, we train a random forest model to mimic the model validated in \citet{vanderplas:2020b} using the same data, model structure, and features (the nine similarity measures developed in \citet{hare:2017})}.
-%Here, we train a random forest model using the same \kge{data, features (the nine similarity measures developed in \citet{hare:2017}), and model structure as a random forest validated in \citet{vanderplas:2020b}} \kge{\sout{nine comparison features as \citet{hare:2017}}} to predict whether two lands come from the same source (i.e.\ are a match) in an expanded set of \Sexpr{format(dim(bullet_train)[1], big.mark = ",")} land-to-land comparisons from two sets of bullets in the James Hamby Consecutively Rifled Ruger Barrel Study \citep{hamby:2009}.
+A random forest model fit to an expanded dataset of \Sexpr{format(dim(bullet_train)[1], big.mark = ",")} land-to-land comparisons from two sets of bullets in the James Hamby Consecutively Rifled Ruger Barrel Study \citep{hamby:2009} was validated in \citet{vanderplas:2020}.
+Here, we train a random forest model to mimic the model validated in \citet{vanderplas:2020} using the same data, model structure, and features (the nine similarity measures developed in \citet{hare:2017}).
 We apply the trained random forest model to 6 bullets from another set of the Hamby study with \Sexpr{dim(bullet_test)[1]} rows of land comparisons.
 See the supporting information for further descriptions of the data.
-\kge{The newly trained random forest has an out-of-bag accuracy of \Sexpr{bullet_rf_oob_acc} and out-of-bag false positive and false negative rates of \Sexpr{bullet_rf_oob_fp} and \Sexpr{bullet_rf_oob_fn}, respectively.
-On the test data, the random forest has an accuracy of \Sexpr{bullet_rf_test_acc} and false positive and false negative rates of \Sexpr{bullet_rf_test_fp} and \Sexpr{bullet_rf_test_fn}, respectively.}
-
-We first consider a global visualization of the relationship between the random forest predictions and the model features with a parallel coordinate plot of the training data (top facet) and testing data (bottom facets)  (\autoref{fig:figure-10}).
+
+The newly trained random forest has an out-of-bag accuracy of \Sexpr{bullet_rf_oob_acc} and out-of-bag false positive and false negative rates of \Sexpr{bullet_rf_oob_fp} and \Sexpr{bullet_rf_oob_fn}, respectively.
+On the test data, the random forest performance decreases with an accuracy of \Sexpr{bullet_rf_test_acc} and false positive and false negative rates of \Sexpr{bullet_rf_test_fp} and \Sexpr{bullet_rf_test_fn}, respectively.
+This is an example where explanations of the model predictions could provide insight to the cause of the decrease in model performance on the test data.
+
+We consider a global visualization of the relationship between the random forest predictions and the model features with a parallel coordinate plot of the training data (top facet) and testing data (bottom facets)  (\autoref{fig:figure-10}).
 In the training data we observe a clear difference in feature values based on whether the corresponding random forest scores are close to 1 or 0.
@@
 
-\kge{We \sout{First,}} focus on the explanation for case NM with 4-quantile-bins.
-The explanation plot from \emph{lime} shows that \kge{the} observed values \kge{of NM of \sout{with}} \kge{mismatches less than or equal to 7.17, rough correlation (rough\_cor) greater than 0.05, and D less than or equal to 0.002 support a random forest prediction in favor of a match.
-The scatter plots show that many of the simulated values in the rectangular regions with mismatches less than 7.17, rough correlation greater than 0.05, and distance less than or equal to 0.002 have random forest predictions greater than 0.5.} %rough correlation (rough\_cor) greater than 0.05 and mismatches value less than or equal to 7.17 support a random forest prediction in favor of a match, and the scatter plots show that many of the simulated values with rough correlation greater than 0.05 and mismatches less than 7.17 have random forest predictions greater than 0.5.
-Additionally, the LIME explanation indicates that a value of cross correlation function (ccf) greater than 0.28 and less than or equal to 0.35 supports a non-match, and the scatter plots shows that the simulated values within this region have mostly random forest predictions less than 0.5.
-However, the random forest assigns a probability of 0.21 to case NM, which is not explained by the LIME explanation \kge{that provides all explanations in support of a match}.
-Instead, consider that a better explanation based on the scatterplots would be that the random forest assigned a prediction probably \kge{below 0.5 \sout{close to 0}} since \kge{NM has observed values of mismatches less than 5, rough correlation greater than 0.25, and distance greater than 0.001.}%the observation has a rough correlation less than 0.5, mismatches greater than 4, and cross correlation function 0.6.
+We focus on the explanation for case NM with 4-quantile-bins.
+The explanation plot from \emph{lime} shows that the observed values of NM of mismatches less than or equal to 7.17, rough correlation (rough\_cor) greater than 0.05, and D less than or equal to 0.002 support a random forest prediction in favor of a match.
+The scatter plots show that many of the simulated values in the rectangular regions with mismatches less than 7.17, rough correlation greater than 0.05, and distance less than or equal to 0.002 have random forest predictions greater than 0.5.
+However, the random forest assigns a probability of 0.21 to case NM, which is not explained by the LIME explanation that provides all explanations in support of a match.
+Instead, consider that a better explanation based on the scatterplots would be that the random forest assigned a prediction probably below 0.5 since NM has observed values of mismatches less than 5, rough correlation greater than 0.25, and distance greater than 0.001.
 
 The other explanation scatterplots can be interpreted in a similar manner.
-\kge{\sout{Overall, t} T}he \kge{three plots depict situations where the explanations are faithful} %plots identify that the 4-quantile-bin explanations are not faithful to the random forest model predictions.
-The 4-equal-bin explanations are more faithful
-to the random forest, but the regions captured by the \kge{intersections of the} bins do not align well with the regions containing similar probabilities produced by the random forest.
+The three plots depict situations where the explanations are faithful to the random forest, but the regions captured by the intersections of the bins do not align well with the regions containing similar probabilities produced by the random forest.
 
@@
 Supplementing \citet{pedersen:2020}'s compact visualization of the explanation with an explanation scatterplot that shows a more detailed visualization of the explainer model (such as Figures~\ref{fig:figure-04} and \ref{fig:figure-13}) promotes a more complete understanding of the explanation.
+
 Even with an explainer model that is interpreted correctly, the interpretation is worthless if the explainer model is not \textbf{faithful} to the complex model.

### 2020-10-07 paper.tex
updates to paper after meeting (just need to proof read sections 4 and 5 one more time)

--- 2020-10-03 paper.tex
@@
 
-\hh{XXX minor change to emphasize that this is not a completly new model, just an expanded training set - otherwise you open yourself up to criticism of not using a validated model.
-The bulletxtrctr model was used in an external validation in \citet{validation}.
-}
-\hh{Here, we train a } random forest model using the same nine comparison features as \citet{hare:2017} to predict whether  \hh{two lands come from the same source} (i.e.\ are a match) in an expanded set of 83,028 land-to-land comparisons from \hh{two sets of} bullets in the James Hamby Consecutively Rifled Ruger Barrel Study \citep{hamby:2009}.
-We apply the trained random forest model to 6 bullets from \hh{another set of} the Hamby study with 364 rows of land comparisons.
+A random forest model fit to an expanded dataset of 83,028 land-to-land comparisons from two sets of bullets in the James Hamby Consecutively Rifled Ruger Barrel Study \citep{hamby:2009} was validated in \citet{vanderplas:2020}.
+Here, we train a random forest model to mimic the model validated in \citet{vanderplas:2020} using the same data, model structure, and features (the nine similarity measures developed in \citet{hare:2017}).
+We apply the trained random forest model to 6 bullets from another set of the Hamby study with 364 rows of land comparisons.
 See the supporting information for further descriptions of the data.
 
-\hh{XXX mention overall goodness of fit or oob error rates?}
-We first consider a global visualization of the relationship between the random forest predictions and the model features with a parallel coordinate plot of the training data (top facet) and testing data (bottom facets)  (\autoref{fig:figure-10}).
+The newly trained random forest has an out-of-bag accuracy of 1 and out-of-bag false positive and false negative rates of 0.3 and \ensuremath{2\times 10^{-4}}, respectively.
+On the test data, the random forest performance decreases with an accuracy of 0.85 and false positive and false negative rates of 0.55 and 0.011, respectively.
+This is an example where explanations of the model predictions could provide insight to the cause of the decrease in model performance on the test data.
+
+We consider a global visualization of the relationship between the random forest predictions and the model features with a parallel coordinate plot of the training data (top facet) and testing data (bottom facets)  (\autoref{fig:figure-10}).
 In the training data we observe a clear difference in feature values based on whether the corresponding random forest scores are close to 1 or 0.
@@
 
-First, focus on the explanation for case NM with 4-quantile-bins.
-The explanation plot from \emph{lime} shows that observed values with rough correlation (rough\_cor) greater than 0.05 and mismatches value less than or equal to 7.17 support a random forest prediction in favor of a match, and the scatter plots show that many of the simulated values with rough correlation greater than 0.05 and mismatches less than 7.17 have random forest predictions greater than 0.5.
-Additionally, the LIME explanation indicates that a value of cross correlation function (ccf) greater than 0.28 and less than or equal to 0.35 supports a non-match, and the scatter plots shows that the simulated values within this region have mostly random forest predictions less than 0.5.
-However, the random forest assigns a probability of 0.19 to case NM, which is not explained by the LIME explanation.
-Instead, consider that a better explanation based on the scatterplots would be that the random forest assigned a prediction probably close to 0 since the observation has a rough correlation less than 0.5, mismatches greater than 4, and cross correlation function 0.6.
+We focus on the explanation for case NM with 4-quantile-bins.
+The explanation plot from \emph{lime} shows that the observed values of NM of mismatches less than or equal to 7.17, rough correlation (rough\_cor) greater than 0.05, and D less than or equal to 0.002 support a random forest prediction in favor of a match.
+The scatter plots show that many of the simulated values in the rectangular regions with mismatches less than 7.17, rough correlation greater than 0.05, and distance less than or equal to 0.002 have random forest predictions greater than 0.5.
+However, the random forest assigns a probability of 0.21 to case NM, which is not explained by the LIME explanation that provides all explanations in support of a match.
+Instead, consider that a better explanation based on the scatterplots would be that the random forest assigned a prediction probably below 0.5 since NM has observed values of mismatches less than 5, rough correlation greater than 0.25, and distance greater than 0.001.
 
 The other explanation scatterplots can be interpreted in a similar manner.
-Overall, the plots identify that the 4-quantile-bin explanations are not faithful to the random forest model predictions.
-The 4-equal-bin explanations are more faithful to the random forest, but the regions captured by the bins do not align well with the regions containing  similar probabilities produced by the random forest.
+The three plots depict situations where the explanations are faithful to the random forest, but the regions captured by the intersections of the bins do not align well with the regions containing similar probabilities produced by the random forest.
 

### 2020-10-07 paper.Rnw
edits during final proof read

@@
 
-Now, consider the claim of faithfulness: It can be said that the majority of the points in the $x_2$ quantile support a prediction of blue, which is captured by the bar supporting a prediction of blue in the LIME explanation, and a similar statement can be made about the $x_1$-quantile-bin.
+Now, consider the claim of faithfulness: It can be said that the majority of the points in the $x_2$ quantile support a prediction of blue, which is captured by the bar supporting a prediction of blue in the LIME explanation, and a similar statement can be made about the $x_1$ quantile-bin.
 These statements validate the explanation produced by LIME.
@@
 Thus, a total of $12\times 3=36$ different applications of LIME are performed.
-We specify that each LIME explanation return 3 features and feature selection is performed by selecting the features with the highest weights in a ridge regression model (default option).
+We specify that each LIME explanation return 3 features, and feature selection is performed using the default option in LIME, which selects the features with the highest weights in a ridge regression model.
 
@@
 However, the LIME explanation for an observation often varies across simulation methods.
-With the-equal-bins, there are vertical stripes that suggest a dependence of the LIME explanations on the number of bins.
+With the equal-bins, there are vertical stripes that suggest a dependence of the LIME explanations on the number of bins.
 The vertical stripes are not as apparent with the quantile bins.
@@
 The explanation plot from \emph{lime} shows that the observed values of NM of mismatches less than or equal to 7.17, rough correlation (rough\_cor) greater than 0.05, and D less than or equal to 0.002 support a random forest prediction in favor of a match.
-The scatter plots show that many of the simulated values in the rectangular regions with mismatches less than 7.17, rough correlation greater than 0.05, and distance less than or equal to 0.002 have random forest predictions greater than 0.5.
+The scatter plots show that many of the simulated values in the rectangular regions with mismatches less than 7.17, rough correlation greater than 0.05, and distance less than or equal to 0.002 have random forest predictions greater than 0.5, which agrees with the LIME explanation.
 However, the random forest assigns a probability of 0.21 to case NM, which is not explained by the LIME explanation that provides all explanations in support of a match.
@@
 For example, the visualization of a LIME explanation available from the \emph{lime} R package \citep{pedersen:2020} (shown in Figures \ref{fig:figure-04} and \ref{fig:figure-13}) is a major simplification of the explainer model, which could lead to under-interpreted or misinterpreted LIME explanation.
-Supplementing \citet{pedersen:2020}'s compact visualization of the explanation with an explanation scatterplot that shows a more detailed visualization of the explainer model (such as Figures~\ref{fig:figure-04} and \ref{fig:figure-13}) promotes a more complete understanding of the explanation.
+Supplementing \citet{pedersen:2020}'s compact visualization of the explanation with an explanation scatterplot that shows a more detailed visualization of the explainer model promotes a more complete understanding of the explanation (such as Figures~\ref{fig:figure-04} and \ref{fig:figure-13}).
 
@@
 In addition to assessing faithfulness by visually comparing the complex and explainer model, we propose a visual comparison of two faithfulness metrics (MSEE and average fidelity).
-The examples of faithfulness metric comparisons in this paper (Figures \ref{fig:figure-07} and \ref{fig:figure-12}) both produced conflicting results.
+The examples of faithfulness metric comparisons in this paper both produced conflicting results (Figures \ref{fig:figure-07} and \ref{fig:figure-12}).
 This makes it difficult to decide on a recommendation of a set of tuning parameter values that produce the explanations with the most faithful explainer model.
@@
 Most of the average $R^2$ values in the examples from this paper are below 0.5 suggesting a poor linear fit of the explainer models.
-The poor linear fit of the explainer model is also seen with the residual plot (\autoref{fig:figure-C3}).
+A poor linear fit of the explainer model is also seen with the residual plot (\autoref{fig:figure-C3}).
 
@@
 This finding agrees with that of \citet{laugel:2018} who found LIME produced global explanations with the normal approximation simulation method.
-For the bin based simulation methods in the bullet data example, the feature heatmap showed that the features chosen for the explanations varied between the two classification categories (match versus non-match).
+For the bin based simulation methods in the bullet data example, the feature heatmap shows that the features chosen for the explanations vary between the two classification categories (match versus non-match).
 This is an interesting finding that suggests that different features can play a role in the predictions of observations in different response categories.
@@
 The largest limitation to the diagnostic visualizations is the dimensionality of the data shown, both in the number of dimensions or features as well as the number of observations.
-Fortunately, in the situation of LIME, both of these aspects are rather well controlled: LIME relies heavily on simulations to generate data scenarios that are close to the data observed but exhibits variability.
+Fortunately, in the situation of LIME, both of these aspects are rather well controlled: LIME relies heavily on simulations to generate data scenarios that are close to the data observed but exhibit variability.
 Effects from overplotting should be relatively mild, because output from simulations is shown, which is expected to be (relatively) continuous such that overplotting only occurs for points with (relatively) similar values.

### 2020-10-07 README.Rmd
updated to do list

--- 2020-10-07 README.Rmd
@@
 
-- Final clean up and proof read of sections 4 and 5
 - Prepare for submission (make sure to update date on cover letter)
 - Upload the files for submission and submit
+- Save a "snapshot" of the repo in the CyBox folder
 

### 2020-10-07 submission/paper.tex
updates to submission folder with final version

@@
 \begin{figure*}[!thp]
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-
-{\centering \includegraphics[width=6.5in]{figure-01-1}
-
-}
-
-\end{knitrout}
+\centering 
+\includegraphics[width=6.5in]{figure-01-1}
 \caption{A conceptual depiction of a faithful LIME explainer model in the immediate neighborhood of a prediction of interest.
@@
 
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-
-{\centering \includegraphics[width=6.5in]{figure-02-1}
-
-}
-
-\end{knitrout}
+\centering 
+\includegraphics[width=6.5in]{figure-02-1} 
 \caption{A conceptual depiction of an unfaithful local explainer model in the immediate neighborhood of a prediction of interest.
@@
 
-%XXX minor change to emphasize that this is not a completely new model, just an expanded training set - otherwise you open yourself up to criticism of not using a validated model.
-The bulletxtrctr model was used in an external validation in \citet{vanderplas:2020b}.
-
-\kgc{Your comment about being clear that we are not training a whole new model made lots of sense.
-I made a few more changes.
-Do they look okay?} \kge{A random forest model fit to an expanded dataset of 83,028 land-to-land comparisons from two sets of bullets in the James Hamby Consecutively Rifled Ruger Barrel Study \citep{hamby:2009} was validated in \citet{vanderplas:2020b}.
-Here, we train a random forest model to mimic the model validated in \citet{vanderplas:2020b} using the same data, model structure, and features (the nine similarity measures developed in \citet{hare:2017})}.
-%Here, we train a random forest model using the same \kge{data, features (the nine similarity measures developed in \citet{hare:2017}), and model structure as a random forest validated in \citet{vanderplas:2020b}} \kge{\sout{nine comparison features as \citet{hare:2017}}} to predict whether two lands come from the same source (i.e.\ are a match) in an expanded set of 83,028 land-to-land comparisons from two sets of bullets in the James Hamby Consecutively Rifled Ruger Barrel Study \citep{hamby:2009}.
+A random forest model fit to an expanded dataset of 83,028 land-to-land comparisons from two sets of bullets in the James Hamby Consecutively Rifled Ruger Barrel Study \citep{hamby:2009} was validated in \citet{vanderplas:2020}.
+Here, we train a random forest model to mimic the model validated in \citet{vanderplas:2020} using the same data, model structure, and features (the nine similarity measures developed in \citet{hare:2017}).
 We apply the trained random forest model to 6 bullets from another set of the Hamby study with 364 rows of land comparisons.
 See the supporting information for further descriptions of the data.
-\kge{The newly trained random forest has an out-of-bag accuracy of 1 and out-of-bag false positive and false negative rates of 0.3 and \ensuremath{2\times 10^{-4}}, respectively.
-On the test data, the random forest has an accuracy of 0.85 and false positive and false negative rates of 0.55 and 0.011, respectively.}
 
-We first consider a global visualization of the relationship between the random forest predictions and the model features with a parallel coordinate plot of the training data (top facet) and testing data (bottom facets)  (\autoref{fig:figure-10}).
+The newly trained random forest has an out-of-bag accuracy of 1 and out-of-bag false positive and false negative rates of 0.3 and \ensuremath{2\times 10^{-4}}, respectively.
+On the test data, the random forest performance decreases with an accuracy of 0.85 and false positive and false negative rates of 0.55 and 0.011, respectively.
+This is an example where explanations of the model predictions could provide insight to the cause of the decrease in model performance on the test data.
+
+We consider a global visualization of the relationship between the random forest predictions and the model features with a parallel coordinate plot of the training data (top facet) and testing data (bottom facets)  (\autoref{fig:figure-10}).
 In the training data we observe a clear difference in feature values based on whether the corresponding random forest scores are close to 1 or 0.
@@
 
-\kge{We \sout{First,}} focus on the explanation for case NM with 4-quantile-bins.
-The explanation plot from \emph{lime} shows that \kge{the} observed values \kge{of NM of \sout{with}} \kge{mismatches less than or equal to 7.17, rough correlation (rough\_cor) greater than 0.05, and D less than or equal to 0.002 support a random forest prediction in favor of a match.
-The scatter plots show that many of the simulated values in the rectangular regions with mismatches less than 7.17, rough correlation greater than 0.05, and distance less than or equal to 0.002 have random forest predictions greater than 0.5.} %rough correlation (rough\_cor) greater than 0.05 and mismatches value less than or equal to 7.17 support a random forest prediction in favor of a match, and the scatter plots show that many of the simulated values with rough correlation greater than 0.05 and mismatches less than 7.17 have random forest predictions greater than 0.5.
-Additionally, the LIME explanation indicates that a value of cross correlation function (ccf) greater than 0.28 and less than or equal to 0.35 supports a non-match, and the scatter plots shows that the simulated values within this region have mostly random forest predictions less than 0.5.
-However, the random forest assigns a probability of 0.21 to case NM, which is not explained by the LIME explanation \kge{that provides all explanations in support of a match}.
-Instead, consider that a better explanation based on the scatterplots would be that the random forest assigned a prediction probably \kge{below 0.5 \sout{close to 0}} since \kge{NM has observed values of mismatches less than 5, rough correlation greater than 0.25, and distance greater than 0.001.}%the observation has a rough correlation less than 0.5, mismatches greater than 4, and cross correlation function 0.6.
+We focus on the explanation for case NM with 4-quantile-bins.
+The explanation plot from \emph{lime} shows that the observed values of NM of mismatches less than or equal to 7.17, rough correlation (rough\_cor) greater than 0.05, and D less than or equal to 0.002 support a random forest prediction in favor of a match.
+The scatter plots show that many of the simulated values in the rectangular regions with mismatches less than 7.17, rough correlation greater than 0.05, and distance less than or equal to 0.002 have random forest predictions greater than 0.5, which agrees with the LIME explanation.
+However, the random forest assigns a probability of 0.21 to case NM, which is not explained by the LIME explanation that provides all explanations in support of a match.
+Instead, consider that a better explanation based on the scatterplots would be that the random forest assigned a prediction probably below 0.5 since NM has observed values of mismatches less than 5, rough correlation greater than 0.25, and distance greater than 0.001.
 
 The other explanation scatterplots can be interpreted in a similar manner.
-\kge{\sout{Overall, t} T}he \kge{three plots depict situations where the explanations are faithful} %plots identify that the 4-quantile-bin explanations are not faithful to the random forest model predictions.
-The 4-equal-bin explanations are more faithful
-to the random forest, but the regions captured by the \kge{intersections of the} bins do not align well with the regions containing similar probabilities produced by the random forest.
+The three plots depict situations where the explanations are faithful to the random forest, but the regions captured by the intersections of the bins do not align well with the regions containing similar probabilities produced by the random forest.
 
@@
 For example, the visualization of a LIME explanation available from the \emph{lime} R package \citep{pedersen:2020} (shown in Figures \ref{fig:figure-04} and \ref{fig:figure-13}) is a major simplification of the explainer model, which could lead to under-interpreted or misinterpreted LIME explanation.
-Supplementing \citet{pedersen:2020}'s compact visualization of the explanation with an explanation scatterplot that shows a more detailed visualization of the explainer model (such as Figures~\ref{fig:figure-04} and \ref{fig:figure-13}) promotes a more complete understanding of the explanation.
+Supplementing \citet{pedersen:2020}'s compact visualization of the explanation with an explanation scatterplot that shows a more detailed visualization of the explainer model promotes a more complete understanding of the explanation (such as Figures~\ref{fig:figure-04} and \ref{fig:figure-13}).
+
 Even with an explainer model that is interpreted correctly, the interpretation is worthless if the explainer model is not \textbf{faithful} to the complex model.

### 2020-10-07 code/03-submission-steps.Rmd
changed name of code file for submission (from paper.r to code.r)
switched to submitting the non-compressed versions of the data

@@
     # Extract the R code from the files paper.Rnw to be used for submission
-    knitr::purl("../paper.Rnw", output = paste0(code_data_folder, "/paper.R"))
+    knitr::purl("../paper.Rnw", output = paste0(code_data_folder, "/code.R"))
 
@@
         "../data/README.txt",
-        "../data/bullet-test.csv.zip",
-        "../data/bullet-train.csv.zip",
-        "../data/example-signatures.csv.zip"
+        "../data/bullet-test.csv",
+        "../data/bullet-train.csv",
+        "../data/example-signatures.csv"
       )

### 2020-10-07 submission/paper.tex
switched to submitting the non-compressed versions of the data

@@
 \begin{figure*}[!thp]
-\centering 
-\includegraphics[width=6.5in]{figure-01-1}
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+
+{\centering \includegraphics[width=6.5in]{figure-01-1}
+
+}
+
+\end{knitrout}
 \caption{A conceptual depiction of a faithful LIME explainer model in the immediate neighborhood of a prediction of interest.
@@
 
-\centering 
-\includegraphics[width=6.5in]{figure-02-1} 
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+
+{\centering \includegraphics[width=6.5in]{figure-02-1}
+
+}
+
+\end{knitrout}
 \caption{A conceptual depiction of an unfaithful local explainer model in the immediate neighborhood of a prediction of interest.
@@
 
-\begin{figure*}[!thp]
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-
-{\centering \includegraphics[width=6.5in]{figure-10-1}
-
-}
-
-\end{knitrout}
-\caption{Parallel coordinate plots of the \citet{hare:2017} random forest predictions from the training (top facet) and testing (bottom facet) data.
+% \begin{figure*}[!thp]
+% \begin{knitrout}
+% \definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+% {\centering \includegraphics[width=6.5in]{figure-10-1} 
+% }
+% \end{knitrout}
+% \caption{Parallel coordinate plots of the \citet{hare:2017} random forest predictions from the training (top facet) and testing (bottom facet) data.
 The observations are separated by known matching (right column) and non-matching (left column) signatures.
@@
 There are clear relationships between the feature values and the random forest probabilities.}
-\label{fig:figure-10}
-\end{figure*}
+% \label{fig:figure-10}
+% \end{figure*}
 

### 2020-10-07 paper.Rnw
one more update - all should be ready now!

@@
 # that the signatures are a match from the model bullet_rf
-bullet_train$rfscore = predict(bullet_rf, bullet_train %>% select(bullet_features), type = "prob")[,2]
-bullet_test$rfscore = predict(bullet_rf, bullet_test %>% select(bullet_features), type = "prob")[,2]
+bullet_train$rfscore = predict(bullet_rf, bullet_train %>% select(all_of(bullet_features)), type = "prob")[,2]
+bullet_test$rfscore = predict(bullet_rf, bullet_test %>% select(all_of(bullet_features)), type = "prob")[,2]
 
@@
 # Obtain model predictions and confusion matrix from test data
-bullet_test_pred = predict(bullet_rf, bullet_test %>% select(bullet_features))
+bullet_test_pred = predict(bullet_rf, bullet_test %>% select(all_of(bullet_features)))
 bullet_test_confus = table(bullet_test_pred, bullet_test$samesource)
@@
     units = "in",
-    dpi = 1200
+    dpi = 400
   )

### 2020-12-04 README.Rmd
removed to do list
fixed some file paths

@@
 ```
-
-## To Do
-
-- Prepare for submission (make sure to update date on cover letter)
-- Upload the files for submission and submit
-- Save a "snapshot" of the repo in the CyBox folder
 
@@
 
-- [01-raw-file-compression.Rmd](code/01-raw-file-compression.Rmd)/[.html](code/01-raw-file-compression.html) contains R code for compressing the static figure used in the manuscript and accessing and compressing the raw bullet data to be uploaded to GitHub
-- [02-data-preparation.Rmd](code/02-data-preparation.Rmd)/[.html](code/02-data-preparation.html) contains R code for preparing the raw bullet data (bullet training data, bullet testing data, and example matching signatures) to be used in the manuscript and saves zip versions of the prepared data sets to be uploaded to GitHub
-- [03-submission-steps.Rmd](code/03-submission-steps.Rmd)/[.html](code/03-submission-steps.html) contains the to do list and R code for preparing the files for submission to the ASA Data Science Journal
+- [01-raw-file-compression.Rmd](code/01-raw-file-compression.Rmd)/[.md](code/01-raw-file-compression.md) contains R code for compressing the static figure used in the manuscript and accessing and compressing the raw bullet data to be uploaded to GitHub
+- [02-data-preparation.Rmd](code/02-data-preparation.Rmd)/[.md](code/02-data-preparation.md) contains R code for preparing the raw bullet data (bullet training data, bullet testing data, and example matching signatures) to be used in the manuscript and saves zip versions of the prepared data sets to be uploaded to GitHub
+- [03-submission-steps.Rmd](code/03-submission-steps.Rmd)/[.md](code/03-submission-steps.md) contains the to do list and R code for preparing the files for submission to the ASA Data Science Journal
 

### 2020-12-04 README.Rmd
reformatted a bit

@@
 
-- [01-raw-file-compression.Rmd](code/01-raw-file-compression.Rmd)/[.md](code/01-raw-file-compression.md) contains R code for compressing the static figure used in the manuscript and accessing and compressing the raw bullet data to be uploaded to GitHub
-- [02-data-preparation.Rmd](code/02-data-preparation.Rmd)/[.md](code/02-data-preparation.md) contains R code for preparing the raw bullet data (bullet training data, bullet testing data, and example matching signatures) to be used in the manuscript and saves zip versions of the prepared data sets to be uploaded to GitHub
-- [03-submission-steps.Rmd](code/03-submission-steps.Rmd)/[.md](code/03-submission-steps.md) contains the to do list and R code for preparing the files for submission to the ASA Data Science Journal
+- [01-raw-file-compression](code/01-raw-file-compression.md) contains R code for compressing the static figure used in the manuscript and accessing and compressing the raw bullet data to be uploaded to GitHub
+- [02-data-preparation](code/02-data-preparation.md) contains R code for preparing the raw bullet data (bullet training data, bullet testing data, and example matching signatures) to be used in the manuscript and saves zip versions of the prepared data sets to be uploaded to GitHub
+- [03-submission-steps](code/03-submission-steps.md) contains the to do list and R code for preparing the files for submission to the ASA Data Science Journal
 

### 2020-12-05 paper.Rnw
starting to tighten the paper

@@
 \newcommand{\data}{sine data}
+\renewcommand{\sout}[1]{\unskip}
 
@@
 % Paper header (title and authors)
-\title{Visual Diagnostics of a Model Explainer -- Tools for the Assessment of LIME Explanations}
+\title{Visual Diagnostics of a\kge{n} \sout{Model} Explainer \kge{Model} -- Tools for the Assessment of LIME Explanations}
 \author[1]{Katherine Goode*}
@@
 % Abstract and keywords
-\abstract[Abstract]{The importance of providing explanations for predictions made by black-box models has led to the development of model explainer methods such as LIME (local interpretable model-agnostic explanations).
+\abstract[Abstract]{The importance of providing explanations for predictions made by black-box models has led to the development of \kge{explainer} model \sout{explainer} methods such as LIME (local interpretable model-agnostic explanations).
 LIME uses a surrogate model to explain the relationship between predictor variables and predictions from a black-box model in a local region around a prediction of interest.
@@
 \cyear{2020},
-\ctitle{Visual Diagnostics of a Model Explainer -- Tools for the Assessment of LIME Explanations},
+\ctitle{Visual Diagnostics of a\kge{n} \sout{Model} Explainer \kge{Model} -- Tools for the Assessment of LIME Explanations},
 \cjournal{Stat Anal Data Min: The ASA Data Sci Journal},
@@
 In the field of statistics, there are two main uses for models: inference and prediction.
-Machine learning models are often used for the latter purpose.
-These models have proven to perform well in a wide range of prediction problems, but the accuracy of many machine learning models comes at the cost of interpretability due to their algorithmic complexity (hence the phrase "black-box models").
+Machine learning models \sout{are often used for the latter purpose.
+These models} have proven to perform well \kge{for problems with the latter objective} \sout{in a wide range of prediction problems}, but the accuracy of many machine learning models comes at the cost of interpretability due to their algorithmic complexity (hence the phrase "black-box models").
 Model interpretability allows for the understanding and assessment of how a model produces predictions.
-The lack of the ability to understand and assess a model makes it difficult to trust the model, especially in areas with high stakes decisions such as medical and forensics sciences.
+The lack of the ability to understand and assess a model makes it difficult to trust the model, especially in areas with high stakes decisions such as \kge{the} medical and forensics sciences.
 The increased use of machine learning models in applications and the introduction of the General Data Protection Regulation (GDPR) in 2018 \citep{goodman:2016} has resulted in a dramatic increase in explainable machine learning research, which focuses on developing ways to explain output from machine learning algorithms.
@@
 \citep{fisher:2018} and \citep{strumbelj:2014}).
-In this paper, we focus on one specific model-agnostic method: LIME \citep{ribeiro:2016}.
-
-LIME (local interpretable model-agnostic explanations) is a method that uses a surrogate model to relate predictor variables to black-box model predictions (i.e.
-a model explainer) \citep{ribeiro:2016}.
-We distinguish between the terms of model explainer and explainer model: by \emph{model explainer} we denote the method for explaining a complex model using a surrogate model, while the \emph{explainer model}, or simply the \emph{explainer}, is the surrogate model.
-
-While some model explainers focus on understanding a model at the global level, LIME claims to provide explanations for individual predictions (local).
+In this paper, we focus on \kge{the} \sout{one specific} model-agnostic method\sout{:} \kge{of} LIME \citep{ribeiro:2016}.
+
+LIME (local interpretable model-agnostic explanations) \sout{is a method that} uses a surrogate model, to relate predictor variables to black-box model predictions \sout{(i.e.
+a model explainer)} \citep{ribeiro:2016}.
+\sout{We distinguish between the terms of model explainer and explainer model: by \emph{model explainer} we denote the method for explaining a complex model using a surrogate model, while the \emph{explainer model}, or simply the \emph{explainer}, is the surrogate model.} While some \kge{explainer} model\kge{s} \sout{explainers} focus on understanding a model at the global level, LIME claims to provide explanations for individual predictions (local).
 Additionally, LIME is designed to work with any model (model-agnostic) and to produce easily understandable results (explanations) \citep{ribeiro:2016}.
-Conceptually, LIME fits a simple (interpretable) model, the explainer model,  meant to capture the behavior of the (complex) black-box model in a local region around a prediction of interest.
-The  simple model then provides interpretable estimates for variables that most influenced the prediction made by the complex model.
+Conceptually, LIME fits a simple (interpretable) model, the explainer model, \kge{to approximate} \sout{meant to capture the behavior of} the \sout{(}complex\sout{) black-box} model in a local region around a prediction of interest.
+The simple model \kge{ma be interpreted to identify the} \sout{then provides interpretable estimates for} variables that most influenced the \kge{complex model} prediction\sout{made by the complex model}.
+
+\kge{While t}\sout{T}he concept of LIME is relatively simple\sout{: use an interpretable model to approximate a complex model in a local region.
+However}, a practical implementation of LIME is not straightforward, and research is being done to improve the procedure \citep{laugel:2018}.
+The current implementations of LIME \citep{ribeiro:2020} \citep{pedersen:2020} offer various tuning parameters (see Section \ref{background}) that affect the explainer model and ultimately, the explanation.
+Since the explainer model is an approximation of the complex model and not a direct interpretation, the explanations produced by an explainer model are subject to the quality of the approximation.
+Thus, in order to achieve accurate explanations, the tuning parameter values selected need to be assessed.
+
+\kge{To demonstrate the effect of tuning parameters on LIME, we consider two different explainer models applied to the same prediction.
+Suppose a black-box model is trained using two features: Feature 1 and Feature 2.
+Figure \ref{fig:figure-01} shows the black-box model predictions versus standardized versions of Feature 1 (left) and Feature 2 (right).
+The diamond shaped point in the plots indicates the location of the prediction of interest to explain.
+A weight ridge regression with the black-box predictions as the response variable and standardized versions the features as predictor variables will be used as the explainer model in both scenarios, but the weights will vary.
+Note that the standardized features allow for direct comparisons of the model coefficients.}
 
@@
 
+\kge{Figure \ref{fig:figure-01} depicts the first scenario where the weights are computed as the inverse proximity of the point to the prediction of interest computed using the Gower distance metric \citep{gower:1971} raised to the power of \Sexpr{good_gower_power} to emphasize a very local region.
+The point size represents the weight, and the black lines depict the ridge regression model given the observed prediction of interest value from the opposite feature.
+For Feature 1 (left), the explainer model captures the relationship in an immediate neighborhood around the prediction of interest with a slope of \Sexpr{coefs_data %>% filter(case == "good", feature == "Feature 1") %>% pull(slope) %>% round(3)}, and for Feature 2 (right), the ridge regression has a small slope of \Sexpr{coefs_data %>% filter(case == "good", feature == "Feature 2") %>% pull(slope) %>% round(3)} that accurately reflects the absence of any global or local relationship between the black-box predictions and Feature 2.
+The magnitude of the slope associated with Feature 1 is larger than the slope of Feature 2, which suggests that Feature 1 plays a more important role in the prediction made by the black-box model for the prediction of interest.
+This explanation agrees with a visual assessment of the relationships between the predictions and predictor variables.}
+
 \begin{figure*}[!thp]
@@
       size = distance_value,
-      alpha = distance_value,
       color = distance
-    )
+    ), alpha = 0.6
   ) +
@@
   ) +
-  scale_alpha(range = c(0.3, 1)) +
   scale_color_manual(values = c(NA, "grey30"), guide = "none") +
@@
 \caption{A conceptual depiction of a faithful LIME explainer model in the immediate neighborhood of a prediction of interest.
-The predictions from a hypothetical black-box model are plotted against the standardized values of the two hypothetical predictor variables.
+\kge{The explainer model in this scenario is a ridge regression weighted by the inverse Gower distance to the prediction of interest raised to the power of \Sexpr{good_gower_power}.} \sout{The predictions from a hypothetical black-box model are plotted against the standardized values of the two hypothetical predictor variables.
 The diamond shaped points represent the location of a prediction of interest.
@@
 The black lines represent a weighted ridge regression model used as an explainer model that reasonably captures the relationship between the black-box predictions and the features in a local region around the prediction of interest.
-That is, the explainer is faithful to the complex model and produces a reasonable explanation that Feature 1 plays a more important role in the prediction of interest than Feature 2 since the magnitude of the slope associated with Feature 1 is larger.}
+That is, the explainer is faithful to the complex model and produces a reasonable explanation that Feature 1 plays a more important role in the prediction of interest than Feature 2 since the magnitude of the slope associated with Feature 1 is larger.}}
 \label{fig:figure-01}
-
-\vspace*{\floatsep}
-
+\end{figure*}
+
+\sout{\autoref{fig:figure-01} provides a visualization of this conceptual understanding of LIME.
+The two plots show the predictions from a hypothetical black-box model plotted against the two hypothetical model predictor variables.
+The diamond shaped points represent the location of the prediction of interest.
+A Gower distance metric \citep{gower:1971} is used to define locality such that the size of the points represent the inverse of the Gower distance raised to some value and indicate the proximity to the prediction of interest.
+In the example of \autoref{fig:figure-01}, an exponent of \Sexpr{good_gower_power} is used to emphasize a very local region around the prediction of interest.
+A ridge regression model weighted by the proximity values is used as the explainer model with the black-box predictions as the response variable and standardized versions of two features in the data as predictor variables.
+Standardized features allow direct comparisons of the model coefficients.
+The explainer model is depicted by the black lines in the figure.}
+
+\sout{The plot on the left of \autoref{fig:figure-01} shows the relationship between the black-box predictions and Feature 1.
+Here, the explainer model is plotted with Feature 2 fixed at the observed value of the prediction of interest.
+The explainer model captures the relationship in an immediate neighborhood around the prediction of interest with a slope of \Sexpr{coefs_data %>% filter(case == "good", feature == "Feature 1") %>% pull(slope) %>% round(3)}.
+The plot on the right shows no global or local relationships between the black-box predictions and Feature 2.
+Here, the explainer model is plotted with Feature 1 set as the observed value of the prediction of interest, and it has an appropriately small slope of \Sexpr{coefs_data %>% filter(case == "good", feature == "Feature 2") %>% pull(slope) %>% round(3)}.
+The magnitude of the slope associated with Feature 1 is larger than the slope of Feature 2, which suggests that Feature 1 plays a more important role in the prediction made by the black-box model for the prediction of interest.
+This explanation agrees with a visual assessment of the relationships between the predictions and predictor variables.}
+
+\sout{The concept of LIME is relatively simple: use an interpretable model to approximate a complex model in a local region.
+However, a practical implementation of LIME is not straightforward, and research is being done to improve the procedure \citep{laugel:2018}.
+The current implementations of LIME \citep{ribeiro:2020} \citep{pedersen:2020} offer various tuning parameters (see Section \ref{background}) that affect the explainer model and ultimately, the explanation.
+Since the explainer model is an approximation of the complex model and not a direct interpretation, the explanations produced by an explainer model are subject to the quality of the approximation.
+Thus, in order to achieve accurate explanations, the tuning parameter values selected need to be assessed.}
+
+\kge{Figure \ref{fig:figure-02} depicts the second explainer model scenario.
+Again, the weights are computed using the Gower distance metric, but in this situation, the distances are raise to a power of \Sexpr{bad_gower_power} (the default exponent in the \emph{lime} R package).} \sout{We consider an example where the choice of exponent for the weights is crucial to the quality of the explanation.
+The plots in Figure \ref{fig:figure-02} show the same data as \autoref{fig:figure-01}, but the Gower distance metric exponent is decreased to \Sexpr{bad_gower_power} (the default exponent in the \emph{lime} R package).} This causes the observations that are further away from the prediction of interest to be given larger weights than before.
+In \autoref{fig:figure-01}, the explainer model captures the relationship between the black-box predictions in an immediate neighborhood of the prediction of interest.
+This cannot be said of the explainer model in \autoref{fig:figure-02}.
+In addition, the magnitude of the slope associated with Feature 2  (\Sexpr{coefs_data %>% filter(case == "bad", feature == "Feature 2") %>% pull(slope) %>% round(3) %>% abs()}) is larger than that of Feature 1 (\Sexpr{coefs_data %>% filter(case == "bad", feature == "Feature 1") %>% pull(slope) %>% round(3) %>% abs()}).
+Thus, this explainer model actually provides a misleading explanation that Feature 2 plays a more important role in the prediction of interest.
+
+\begin{figure*}[!thp]
 <<figure-02, out.width = '6.5in', fig.width = 7.95, fig.height = 3.75, warning = FALSE>>=
@@
       size = distance_value,
-      alpha = distance_value,
       color = distance
-    )
+    ), 
+    alpha = 0.6
   ) +
@@
   ) +
-  scale_alpha(range = c(0.3, 1)) +
   scale_color_manual(values = c("grey30", NA), guide = "none") +
@@
 \caption{A conceptual depiction of an unfaithful local explainer model in the immediate neighborhood of a prediction of interest.
-A ridge regression model is fit to the same hypothetical black-box model predictions and predictor variables as in \autoref{fig:figure-01}, but the weights are computed using a Gower exponent of 1.
-The explainer model is unfaithful to the complex model in any immediate neighborhood of the prediction of interest.}
+A\kge{gain, a weighted} ridge regression \kge{is used as the explainer model} \sout{is fit to the same hypothetical black-box model predictions and predictor variables as in \autoref{fig:figure-01}}, but the \kge{Gower distance is raised to a power} \sout{weights are computed using a Gower exponent} of 1.
+\sout{The explainer model is unfaithful to the complex model in any immediate neighborhood of the prediction of interest.}}
 \label{fig:figure-02}
@@
 
-\autoref{fig:figure-01} provides a visualization of this conceptual understanding of LIME.
-The two plots show the predictions from a hypothetical black-box model plotted against the two hypothetical model predictor variables.
-The diamond shaped points represent the location of the prediction of interest.
-A Gower distance metric \citep{gower:1971} is used to define locality such that the size of the points represent the inverse of the Gower distance raised to some value and indicate the proximity to the prediction of interest.
-In the example of \autoref{fig:figure-01}, an exponent of \Sexpr{good_gower_power} is used to emphasize a very local region around the prediction of interest.
-A ridge regression model weighted by the proximity values is used as the explainer model with the black-box predictions as the response variable and standardized versions of two features in the data as predictor variables.
-Standardized features allow direct comparisons of the model coefficients.
-The explainer model is depicted by the black lines in the figure.
-
-The plot on the left of \autoref{fig:figure-01} shows the relationship between the black-box predictions and Feature 1.
-Here, the explainer model is plotted with Feature 2 fixed at the observed value of the prediction of interest.
-The explainer model captures the relationship in an  immediate neighborhood around the prediction of interest with a slope of \Sexpr{coefs_data %>% filter(case == "good", feature == "Feature 1") %>% pull(slope) %>% round(3)}.
-The plot on the right shows no global or local relationships between the black-box predictions and Feature 2.
-Here, the explainer model is plotted with Feature 1 set as the observed value of the prediction of interest, and it has an appropriately small slope of \Sexpr{coefs_data %>% filter(case == "good", feature == "Feature 2") %>% pull(slope) %>% round(3)}.
-The magnitude of the slope associated with Feature 1 is larger than the slope of Feature 2, which suggests that Feature 1 plays a more important role in the prediction made by the black-box model for the prediction of interest.
-This explanation agrees with a visual assessment of the relationships between the predictions and predictor variables.
-
-The concept of LIME is relatively simple: use an interpretable model to approximate a complex model in a local region.
-However, a practical implementation of LIME is not straightforward, and research is being done to improve the procedure \citep{laugel:2018}.
-The current implementations of LIME \citep{ribeiro:2020} \citep{pedersen:2020} offer various tuning parameters (see Section \ref{background}) that affect the explainer model and ultimately, the explanation.
-Since the explainer model is an approximation of the complex model and not a direct interpretation, the explanations produced by an explainer model are subject to the quality of the approximation.
-Thus, in order to achieve accurate explanations, the tuning parameter values selected need to be assessed.
-
-We consider an example where the choice of exponent for the weights is crucial to the quality of the explanation.
-The plots in Figure \ref{fig:figure-02} show the same data as \autoref{fig:figure-01}, but the Gower distance metric exponent is decreased to \Sexpr{bad_gower_power} (the default exponent in the \emph{lime} R package).
-This causes the observations that are further away from the prediction of interest to be given larger weights than before.
-In \autoref{fig:figure-01}, the explainer model captures the relationship between the black-box predictions in an immediate neighborhood of the prediction of interest.
-This cannot be said of the explainer model in \autoref{fig:figure-02}.
-In addition, the magnitude of the slope associated with Feature 2  (\Sexpr{coefs_data %>% filter(case == "bad", feature == "Feature 2") %>% pull(slope) %>% round(3) %>% abs()}) is larger than that of Feature 1 (\Sexpr{coefs_data %>% filter(case == "bad", feature == "Feature 1") %>% pull(slope) %>% round(3) %>% abs()}).
-Thus, this explainer model actually provides a misleading explanation that Feature 2 plays a more important role in the prediction of interest.
-
-Several sources in the literature discuss the performance of LIME.
-One of the biggest difficulties with LIME is determining how to specify a local region \citep{laugel:2018} \citep{molnar:2019}.
+\kge{This example demonstrates the effect of the selection of weights on the LIME explanations, but other concerns with LIME have been raised in the literature.} \sout{Several sources in the literature discuss the performance of LIME.} One of the biggest difficulties with LIME is determining how to specify a local region \citep{laugel:2018} \citep{molnar:2019}.
 This is due to an unclear definition of a "local region" and how to apply LIME to achieve an appropriate local region as demonstrated by \autoref{fig:figure-02}.
-\citet{alvarezmelis:2018} raise a concern pertaining to the robustness of explanations from LIME and other model explainers: they find that even small changes in predictor variables can lead to very different LIME explanations.
+\citet{alvarezmelis:2018} raise a concern pertaining to the robustness of explanations from LIME and other \kge{explainer} model\kge{s} \sout{explainers}: they find that even small changes in predictor variables can lead to very different LIME explanations.
 Additionally, \citet{ribeiro:2016} acknowledge that if a linear model is used as the explainer, LIME relies on a linear approximation of the explainer model to the complex model and state "if the underlying model is highly non-linear even in the locality of the prediction, there may not be a faithful explanation".
 
-As a result of the various ways LIME can fail, it is important to assess LIME explanations.
+\kge{In this paper, we stress the importance of assessing LIME by introducing several diagnostic plots that highlight key issues with LIME.} \sout{As a result of the various ways LIME can fail, it is important to assess LIME explanations.
 We suggest the use of visual diagnostics for assessment.
-In this paper, we lay out the set of claims about LIME made by \citet{ribeiro:2016} and propose three visualizations for the assessment of these claims: (1) \emph{explanation scatterplot}, (2) \emph{feature heatmap}, (3) \emph{assessment metric plot}.
+In this paper,} \kge{To do this,} we lay out the set of claims about LIME made by \citet{ribeiro:2016} and propose three visualizations for the assessment of these claims: (1) \emph{explanation scatterplots}, (2) \emph{feature heatmaps}, (3) \emph{assessment metric plots}.
 While LIME is implemented for image, tabular, and text data, we only focus on tabular data.
 For additional simplicity, we only discuss classification prediction models with a dichotomous response variable and continuous predictor variables.
-However, the proposed diagnostics may be extended to a wider range of situations.
+However, the proposed diagnostics may be extended to \kge{other} \sout{a wider range of} situations.
 

### 2020-12-05 paper.tex
starting to tighten the paper

@@
 \citep{fisher:2018} and \citep{strumbelj:2014}).
-In this paper, we focus on one specific model-agnostic method: LIME \citep{ribeiro:2016}.
+In this paper, we focus on \kge{the} \sout{one specific} model-agnostic method\sout{:} \kge{of} LIME \citep{ribeiro:2016}.
 
-LIME (local interpretable model-agnostic explanations) is a method that uses a surrogate model to relate predictor variables to black-box model predictions (i.e.
-a model explainer) \citep{ribeiro:2016}.
-We distinguish between the terms of model explainer and explainer model: by \emph{model explainer} we denote the method for explaining a complex model using a surrogate model, while the \emph{explainer model}, or simply the \emph{explainer}, is the surrogate model.
+LIME (local interpretable model-agnostic explanations) \sout{is a method that} uses a surrogate model, to relate predictor variables to black-box model predictions \sout{(i.e.
+a model explainer)} \citep{ribeiro:2016}.
+\sout{We distinguish between the terms of model explainer and explainer model: by \emph{model explainer} we denote the method for explaining a complex model using a surrogate model, while the \emph{explainer model}, or simply the \emph{explainer}, is the surrogate model.} While some \kge{explainer} model\kge{s} \sout{explainers} focus on understanding a model at the global level, LIME claims to provide explanations for individual predictions (local).
+Additionally, LIME is designed to work with any model (model-agnostic) and to produce easily understandable results (explanations) \citep{ribeiro:2016}.
+Conceptually, LIME fits a simple (interpretable) model, the explainer model, \kge{to approximate} \sout{meant to capture the behavior of} the \sout{(}complex\sout{) black-box} model in a local region around a prediction of interest.
+The simple model \kge{ma be interpreted to identify the} \sout{then provides interpretable estimates for} variables that most influenced the \kge{complex model} prediction\sout{made by the complex model}.
 
-While some model explainers focus on understanding a model at the global level, LIME claims to provide explanations for individual predictions (local).
-Additionally, LIME is designed to work with any model (model-agnostic) and to produce easily understandable results (explanations) \citep{ribeiro:2016}.
-Conceptually, LIME fits a simple (interpretable) model, the explainer model,  meant to capture the behavior of the (complex) black-box model in a local region around a prediction of interest.
-The  simple model then provides interpretable estimates for variables that most influenced the prediction made by the complex model.
+\kge{While t}\sout{T}he concept of LIME is relatively simple\sout{: use an interpretable model to approximate a complex model in a local region.
+However}, a practical implementation of LIME is not straightforward, and research is being done to improve the procedure \citep{laugel:2018}.
+The current implementations of LIME \citep{ribeiro:2020} \citep{pedersen:2020} offer various tuning parameters (see Section \ref{background}) that affect the explainer model and ultimately, the explanation.
+Since the explainer model is an approximation of the complex model and not a direct interpretation, the explanations produced by an explainer model are subject to the quality of the approximation.
+Thus, in order to achieve accurate explanations, the tuning parameter values selected need to be assessed.
+
+\kge{To demonstrate the effect of tuning parameters on LIME, we consider two different explainer models applied to the same prediction.
+Suppose a black-box model is trained using two features: Feature 1 and Feature 2.
+Figure \ref{fig:figure-01} shows the black-box model predictions versus standardized versions of Feature 1 (left) and Feature 2 (right).
+The diamond shaped point in the plots indicates the location of the prediction of interest to explain.
+A weight ridge regression with the black-box predictions as the response variable and standardized versions the features as predictor variables will be used as the explainer model in both scenarios, but the weights will vary.
+Note that the standardized features allow for direct comparisons of the model coefficients.}
+
+\kge{Figure \ref{fig:figure-01} depicts the first scenario where the weights are computed as the inverse proximity of the point to the prediction of interest computed using the Gower distance metric \citep{gower:1971} raised to the power of 50 to emphasize a very local region.
+The point size represents the weight, and the black lines depict the ridge regression model given the observed prediction of interest value from the opposite feature.
+For Feature 1 (left), the explainer model captures the relationship in an immediate neighborhood around the prediction of interest with a slope of 0.068, and for Feature 2 (right), the ridge regression has a small slope of -0.001 that accurately reflects the absence of any global or local relationship between the black-box predictions and Feature 2.
+The magnitude of the slope associated with Feature 1 is larger than the slope of Feature 2, which suggests that Feature 1 plays a more important role in the prediction made by the black-box model for the prediction of interest.
+This explanation agrees with a visual assessment of the relationships between the predictions and predictor variables.}
 
@@
 \caption{A conceptual depiction of a faithful LIME explainer model in the immediate neighborhood of a prediction of interest.
-The predictions from a hypothetical black-box model are plotted against the standardized values of the two hypothetical predictor variables.
+\kge{The explainer model in this scenario is a ridge regression weighted by the inverse Gower distance to the prediction of interest raised to the power of 50.} \sout{The predictions from a hypothetical black-box model are plotted against the standardized values of the two hypothetical predictor variables.
 The diamond shaped points represent the location of a prediction of interest.
@@
 The black lines represent a weighted ridge regression model used as an explainer model that reasonably captures the relationship between the black-box predictions and the features in a local region around the prediction of interest.
-That is, the explainer is faithful to the complex model and produces a reasonable explanation that Feature 1 plays a more important role in the prediction of interest than Feature 2 since the magnitude of the slope associated with Feature 1 is larger.}
+That is, the explainer is faithful to the complex model and produces a reasonable explanation that Feature 1 plays a more important role in the prediction of interest than Feature 2 since the magnitude of the slope associated with Feature 1 is larger.}}
 \label{fig:figure-01}
+\end{figure*}
 
-\vspace*{\floatsep}
+\sout{\autoref{fig:figure-01} provides a visualization of this conceptual understanding of LIME.
+The two plots show the predictions from a hypothetical black-box model plotted against the two hypothetical model predictor variables.
+The diamond shaped points represent the location of the prediction of interest.
+A Gower distance metric \citep{gower:1971} is used to define locality such that the size of the points represent the inverse of the Gower distance raised to some value and indicate the proximity to the prediction of interest.
+In the example of \autoref{fig:figure-01}, an exponent of 50 is used to emphasize a very local region around the prediction of interest.
+A ridge regression model weighted by the proximity values is used as the explainer model with the black-box predictions as the response variable and standardized versions of two features in the data as predictor variables.
+Standardized features allow direct comparisons of the model coefficients.
+The explainer model is depicted by the black lines in the figure.}
 
+\sout{The plot on the left of \autoref{fig:figure-01} shows the relationship between the black-box predictions and Feature 1.
+Here, the explainer model is plotted with Feature 2 fixed at the observed value of the prediction of interest.
+The explainer model captures the relationship in an immediate neighborhood around the prediction of interest with a slope of 0.068.
+The plot on the right shows no global or local relationships between the black-box predictions and Feature 2.
+Here, the explainer model is plotted with Feature 1 set as the observed value of the prediction of interest, and it has an appropriately small slope of -0.001.
+The magnitude of the slope associated with Feature 1 is larger than the slope of Feature 2, which suggests that Feature 1 plays a more important role in the prediction made by the black-box model for the prediction of interest.
+This explanation agrees with a visual assessment of the relationships between the predictions and predictor variables.}
+
+\sout{The concept of LIME is relatively simple: use an interpretable model to approximate a complex model in a local region.
+However, a practical implementation of LIME is not straightforward, and research is being done to improve the procedure \citep{laugel:2018}.
+The current implementations of LIME \citep{ribeiro:2020} \citep{pedersen:2020} offer various tuning parameters (see Section \ref{background}) that affect the explainer model and ultimately, the explanation.
+Since the explainer model is an approximation of the complex model and not a direct interpretation, the explanations produced by an explainer model are subject to the quality of the approximation.
+Thus, in order to achieve accurate explanations, the tuning parameter values selected need to be assessed.}
+
+\kge{Figure \ref{fig:figure-02} depicts the second explainer model scenario.
+Again, the weights are computed using the Gower distance metric, but in this situation, the distances are raise to a power of 1 (the default exponent in the \emph{lime} R package).} \sout{We consider an example where the choice of exponent for the weights is crucial to the quality of the explanation.
+The plots in Figure \ref{fig:figure-02} show the same data as \autoref{fig:figure-01}, but the Gower distance metric exponent is decreased to 1 (the default exponent in the \emph{lime} R package).} This causes the observations that are further away from the prediction of interest to be given larger weights than before.
+In \autoref{fig:figure-01}, the explainer model captures the relationship between the black-box predictions in an immediate neighborhood of the prediction of interest.
+This cannot be said of the explainer model in \autoref{fig:figure-02}.
+In addition, the magnitude of the slope associated with Feature 2  (0.011) is larger than that of Feature 1 (0.005).
+Thus, this explainer model actually provides a misleading explanation that Feature 2 plays a more important role in the prediction of interest.
+
+\begin{figure*}[!thp]
 \begin{knitrout}
@@
 
-\autoref{fig:figure-01} provides a visualization of this conceptual understanding of LIME.
-The two plots show the predictions from a hypothetical black-box model plotted against the two hypothetical model predictor variables.
-The diamond shaped points represent the location of the prediction of interest.
-A Gower distance metric \citep{gower:1971} is used to define locality such that the size of the points represent the inverse of the Gower distance raised to some value and indicate the proximity to the prediction of interest.
-In the example of \autoref{fig:figure-01}, an exponent of 50 is used to emphasize a very local region around the prediction of interest.
-A ridge regression model weighted by the proximity values is used as the explainer model with the black-box predictions as the response variable and standardized versions of two features in the data as predictor variables.
-Standardized features allow direct comparisons of the model coefficients.
-The explainer model is depicted by the black lines in the figure.
-
-The plot on the left of \autoref{fig:figure-01} shows the relationship between the black-box predictions and Feature 1.
-Here, the explainer model is plotted with Feature 2 fixed at the observed value of the prediction of interest.
-The explainer model captures the relationship in an  immediate neighborhood around the prediction of interest with a slope of 0.068.
-The plot on the right shows no global or local relationships between the black-box predictions and Feature 2.
-Here, the explainer model is plotted with Feature 1 set as the observed value of the prediction of interest, and it has an appropriately small slope of -0.001.
-The magnitude of the slope associated with Feature 1 is larger than the slope of Feature 2, which suggests that Feature 1 plays a more important role in the prediction made by the black-box model for the prediction of interest.
-This explanation agrees with a visual assessment of the relationships between the predictions and predictor variables.
-
-The concept of LIME is relatively simple: use an interpretable model to approximate a complex model in a local region.
-However, a practical implementation of LIME is not straightforward, and research is being done to improve the procedure \citep{laugel:2018}.
-The current implementations of LIME \citep{ribeiro:2020} \citep{pedersen:2020} offer various tuning parameters (see Section \ref{background}) that affect the explainer model and ultimately, the explanation.
-Since the explainer model is an approximation of the complex model and not a direct interpretation, the explanations produced by an explainer model are subject to the quality of the approximation.
-Thus, in order to achieve accurate explanations, the tuning parameter values selected need to be assessed.
-
-We consider an example where the choice of exponent for the weights is crucial to the quality of the explanation.
-The plots in Figure \ref{fig:figure-02} show the same data as \autoref{fig:figure-01}, but the Gower distance metric exponent is decreased to 1 (the default exponent in the \emph{lime} R package).
-This causes the observations that are further away from the prediction of interest to be given larger weights than before.
-In \autoref{fig:figure-01}, the explainer model captures the relationship between the black-box predictions in an immediate neighborhood of the prediction of interest.
-This cannot be said of the explainer model in \autoref{fig:figure-02}.
-In addition, the magnitude of the slope associated with Feature 2  (0.011) is larger than that of Feature 1 (0.005).
-Thus, this explainer model actually provides a misleading explanation that Feature 2 plays a more important role in the prediction of interest.
-
-Several sources in the literature discuss the performance of LIME.
-One of the biggest difficulties with LIME is determining how to specify a local region \citep{laugel:2018} \citep{molnar:2019}.
+\kge{This example demonstrates the effect of the selection of weights on the LIME explanations, but other concerns with LIME have been raised in the literature.} \sout{Several sources in the literature discuss the performance of LIME.} One of the biggest difficulties with LIME is determining how to specify a local region \citep{laugel:2018} \citep{molnar:2019}.
 This is due to an unclear definition of a "local region" and how to apply LIME to achieve an appropriate local region as demonstrated by \autoref{fig:figure-02}.
-\citet{alvarezmelis:2018} raise a concern pertaining to the robustness of explanations from LIME and other model explainers: they find that even small changes in predictor variables can lead to very different LIME explanations.
+\citet{alvarezmelis:2018} raise a concern pertaining to the robustness of explanations from LIME and other \kge{explainer} model\kge{s} \sout{explainers}: they find that even small changes in predictor variables can lead to very different LIME explanations.
 Additionally, \citet{ribeiro:2016} acknowledge that if a linear model is used as the explainer, LIME relies on a linear approximation of the explainer model to the complex model and state "if the underlying model is highly non-linear even in the locality of the prediction, there may not be a faithful explanation".
 
-As a result of the various ways LIME can fail, it is important to assess LIME explanations.
+\kge{In this paper, we stress the importance of assessing LIME by introducing several diagnostic plots that highlight key issues with LIME.} \sout{As a result of the various ways LIME can fail, it is important to assess LIME explanations.
 We suggest the use of visual diagnostics for assessment.
-In this paper, we lay out the set of claims about LIME made by \citet{ribeiro:2016} and propose three visualizations for the assessment of these claims: (1) \emph{explanation scatterplot}, (2) \emph{feature heatmap}, (3) \emph{assessment metric plot}.
+In this paper,} \kge{To do this,} we lay out the set of claims about LIME made by \citet{ribeiro:2016} and propose three visualizations for the assessment of these claims: (1) \emph{explanation scatterplots}, (2) \emph{feature heatmaps}, (3) \emph{assessment metric plots}.
 While LIME is implemented for image, tabular, and text data, we only focus on tabular data.
 For additional simplicity, we only discuss classification prediction models with a dichotomous response variable and continuous predictor variables.
-However, the proposed diagnostics may be extended to a wider range of situations.
+However, the proposed diagnostics may be extended to \kge{other} \sout{a wider range of} situations.
 

### 2020-12-08 paper.Rnw
worked on trimming section 1 even more

@@
 \usepackage{natbib}
-\usepackage{subcaption}
 \usepackage{xcolor}
@@
 
-In the field of statistics, there are two main uses for models: inference and prediction.
-Machine learning models \sout{are often used for the latter purpose.
-These models} have proven to perform well \kge{for problems with the latter objective} \sout{in a wide range of prediction problems}, but the accuracy of many machine learning models comes at the cost of interpretability due to their algorithmic complexity (hence the phrase "black-box models").
-Model interpretability allows for the understanding and assessment of how a model produces predictions.
-The lack of the ability to understand and assess a model makes it difficult to trust the model, especially in areas with high stakes decisions such as \kge{the} medical and forensics sciences.
-The increased use of machine learning models in applications and the introduction of the General Data Protection Regulation (GDPR) in 2018 \citep{goodman:2016} has resulted in a dramatic increase in explainable machine learning research, which focuses on developing ways to explain output from machine learning algorithms.
-
-Throughout this paper, we distinguish between interpretability and explanability of models.
-We define {\it interpretability} as the ability to directly use model parameters to understand the relationships in the data captured by the model: e.g., a linear model coefficient associated with a predictor variable indicates the amount the response variable changes based on a change in the predictor variable.
-In contrast, define {\it explanability} as the ability to use the model in an indirect manner to understand the relationships in the data captured by the model: e.g., partial dependence plots depict the marginal relationship between model predictions and predictor variables \citep{friedman:2001}.
-
-Numerous methods have been proposed to provide explanations for black-box model predictions \citep{gilpin:2018, guidotti:2018, ming:2017, molnar:2019}.
-Some are specific to one type of model (e.g.
-\citep{simonyan:2013} and \citep{urbanek:2008}), and others are model-agnostic (e.g.
-\citep{fisher:2018} and \citep{strumbelj:2014}).
-In this paper, we focus on \kge{the} \sout{one specific} model-agnostic method\sout{:} \kge{of} LIME \citep{ribeiro:2016}.
-
-LIME (local interpretable model-agnostic explanations) \sout{is a method that} uses a surrogate model, to relate predictor variables to black-box model predictions \sout{(i.e.
-a model explainer)} \citep{ribeiro:2016}.
-\sout{We distinguish between the terms of model explainer and explainer model: by \emph{model explainer} we denote the method for explaining a complex model using a surrogate model, while the \emph{explainer model}, or simply the \emph{explainer}, is the surrogate model.} While some \kge{explainer} model\kge{s} \sout{explainers} focus on understanding a model at the global level, LIME claims to provide explanations for individual predictions (local).
-Additionally, LIME is designed to work with any model (model-agnostic) and to produce easily understandable results (explanations) \citep{ribeiro:2016}.
-Conceptually, LIME fits a simple (interpretable) model, the explainer model, \kge{to approximate} \sout{meant to capture the behavior of} the \sout{(}complex\sout{) black-box} model in a local region around a prediction of interest.
-The simple model \kge{ma be interpreted to identify the} \sout{then provides interpretable estimates for} variables that most influenced the \kge{complex model} prediction\sout{made by the complex model}.
-
-\kge{While t}\sout{T}he concept of LIME is relatively simple\sout{: use an interpretable model to approximate a complex model in a local region.
-However}, a practical implementation of LIME is not straightforward, and research is being done to improve the procedure \citep{laugel:2018}.
-The current implementations of LIME \citep{ribeiro:2020} \citep{pedersen:2020} offer various tuning parameters (see Section \ref{background}) that affect the explainer model and ultimately, the explanation.
-Since the explainer model is an approximation of the complex model and not a direct interpretation, the explanations produced by an explainer model are subject to the quality of the approximation.
-Thus, in order to achieve accurate explanations, the tuning parameter values selected need to be assessed.
-
-\kge{To demonstrate the effect of tuning parameters on LIME, we consider two different explainer models applied to the same prediction.
-Suppose a black-box model is trained using two features: Feature 1 and Feature 2.
-Figure \ref{fig:figure-01} shows the black-box model predictions versus standardized versions of Feature 1 (left) and Feature 2 (right).
-The diamond shaped point in the plots indicates the location of the prediction of interest to explain.
-A weight ridge regression with the black-box predictions as the response variable and standardized versions the features as predictor variables will be used as the explainer model in both scenarios, but the weights will vary.
-Note that the standardized features allow for direct comparisons of the model coefficients.}
-
-<<concept-data>>=
+<<concept-data, eval = FALSE>>=
+
+# # Simulate example data
+# set.seed(20190624)
+# lime_data <-
+#   data.frame(
+#     feature1 = sort(runif(250, 0, 1)),
+#     feature2 = sample(x = 1:250, size = 250, replace = FALSE)) %>%
+#   mutate(
+#     feature1_stnd = (feature1 - mean(feature1)) / sd(feature1),
+#     feature2_stnd = (feature2 - mean(feature2)) / sd(feature2),
+#     prediction = if_else(feature1 >= 0 & feature1 < 0.1,
+#                          (0.3 * feature1) + rnorm(n(), 0, 0.01),
+#                  if_else(feature1 >= 0.1 & feature1 < 0.3,
+#                          rbeta(n(), 1, 0.5),
+#                  if_else(feature1 >= 0.3 & feature1 < 0.5,
+#                          sin(pi* feature1) + rnorm(n(), 0, 0.5),
+#                  if_else(feature1 >= 0.5 & feature1 < 0.8,
+#                          -(sin(pi* feature1) + rnorm(n(), 0, 0.1)) + 1,
+#                  if_else(feature1 >= 0.8 & feature1 < 0.9,
+#                          0.5 + runif(n(), -0.5, 0.5),
+#                          0.5 + rnorm(n(), 0, 0.3))))))) %>%
+#   bind_rows(
+#     data.frame(feature1 = rep(1, 30) + rnorm(5, 0, 0.05),
+#            feature2 = rep(245, 30) + rnorm(5, 0, 1),
+#            prediction = rep(0, 30) + rnorm(5, 0, 0.05)) %>%
+#   mutate(feature1_stnd = (feature1 - mean(feature1)) / sd(feature1),
+#          feature2_stnd = (feature2 - mean(feature2)) / sd(feature2)))
+# 
+# # Specify a prediction of interest
+# prediction_of_interest <-
+#   data.frame(feature1 = 0.07, feature2 = 200) %>%
+#   mutate(feature1_stnd = (feature1 - mean(lime_data$feature1)) /
+#            sd(lime_data$feature1),
+#          feature2_stnd = (feature2 - mean(lime_data$feature2)) /
+#            sd(lime_data$feature2),
+#          prediction = 0.05,
+#          color = factor("Prediction \nof Interest"))
+# 
+# # Specify the gower exponents
+# good_gower_power <- 50
+# bad_gower_power <- 1
+# 
+# # Compute the good distances between the prediction of interest
+# # and all other observations
+# lime_data$distance_good <-
+#   (1 - gower_dist(x = prediction_of_interest %>%
+#                     select(feature1_stnd, feature2_stnd),
+#                   y = lime_data %>%
+#                     select(feature1_stnd,
+#                            feature2_stnd)))^good_gower_power
+# 
+# # Compute the bad distances between the prediction of interest
+# # and all other observations
+# lime_data$distance_bad <-
+#   (1 - gower_dist(x = prediction_of_interest %>%
+#                     select(feature1_stnd, feature2_stnd),
+#                   y = lime_data %>%
+#                     select(feature1_stnd,
+#                            feature2_stnd)))^bad_gower_power
+# 
+# # Prepare the data for plotting
+# lime_data_gathered <- lime_data %>%
+#   gather(feature, feature_stnd_value,
+#          feature1_stnd:feature2_stnd) %>%
+#   gather(distance, distance_value, distance_good:distance_bad) %>%
+#   mutate(distance = fct_recode(distance,
+#                                "good" = "distance_good",
+#                                "bad" = "distance_bad"),
+#          feature = fct_recode(feature,
+#                               "Feature 1" = "feature1_stnd",
+#                               "Feature 2" = "feature2_stnd"))
+# 
+# # Prepare the prediction of interest data for plotting
+# prediction_of_interest_gathered <- prediction_of_interest %>%
+#   select(-feature1, -feature2) %>%
+#   gather(feature, feature_value, feature1_stnd, feature2_stnd) %>%
+#   mutate(feature = fct_recode(feature,
+#                               "Feature 1" = "feature1_stnd",
+#                               "Feature 2" = "feature2_stnd"))
+
+@
+
+<<concept-explainers, eval = FALSE>>=
+
+# # Fit the good interpretable explainer model
+# explainer_good <-
+#   glmnet(x = lime_data %>% select(feature1_stnd, feature2_stnd)
+#          %>% as.matrix(),
+#          y = lime_data$prediction,
+#          alpha = 0,
+#          lambda = 1,
+#          weights = lime_data$distance_good)
+# 
+# # Fit the bad interpretable explainer model
+# explainer_bad <-
+#   glmnet(x = lime_data %>% select(feature1_stnd, feature2_stnd)
+#          %>% as.matrix(),
+#          y = lime_data$prediction,
+#          alpha = 0,
+#          lambda = 1,
+#          weights = lime_data$distance_bad)
+# 
+# # Join the coefficients from the explainer model into a dataframe
+# coefs_data <- data.frame(case = c("good", "bad"),
+#                          b0 = c(coef(explainer_good)[1],
+#                                 coef(explainer_bad)[1]),
+#                          b1 = c(coef(explainer_good)[2],
+#                                 coef(explainer_bad)[2]),
+#                          b2 = c(coef(explainer_good)[3],
+#                                 coef(explainer_bad)[3])) %>%
+#   mutate(feature1 = b0 + b2*prediction_of_interest$feature2_stnd,
+#          feature2 = b0 + b1*prediction_of_interest$feature1_stnd) %>%
+#   gather(key = feature, value = int, feature1:feature2) %>%
+#   mutate(slope = c(coef(explainer_good)[2],
+#                    coef(explainer_good)[3],
+#                    coef(explainer_bad)[2],
+#                    coef(explainer_bad)[3]),
+#          feature = fct_recode(feature,
+#                               "Feature 1" = "feature1",
+#                               "Feature 2" = "feature2"))
+
+@
+
+<<concept-data-explainer>>=
+
+# Specify the gower exponents
+good_gower_power <- 0.00000000000000005
+bad_gower_power <- 1
+
+# Specify a prediction of interest
+poi <-
+  data.frame(
+    poi = "Prediction \nof Interest",
+    feature = 0.1,
+    prediction = 0.05
+  )
 
@@
 set.seed(20190624)
-lime_data <-
-  data.frame(
-    feature1 = sort(runif(250, 0, 1)),
-    feature2 = sample(x = 1:250, size = 250, replace = FALSE)) %>%
-  mutate(
-    feature1_stnd = (feature1 - mean(feature1)) / sd(feature1),
-    feature2_stnd = (feature2 - mean(feature2)) / sd(feature2),
-    prediction = if_else(feature1 >= 0 & feature1 < 0.1,
-                         (0.3 * feature1) + rnorm(n(), 0, 0.01),
-                 if_else(feature1 >= 0.1 & feature1 < 0.3,
-                         rbeta(n(), 1, 0.5),
-                 if_else(feature1 >= 0.3 & feature1 < 0.5,
-                         sin(pi* feature1) + rnorm(n(), 0, 0.5),
-                 if_else(feature1 >= 0.5 & feature1 < 0.8,
-                         -(sin(pi* feature1) + rnorm(n(), 0, 0.1)) + 1,
-                 if_else(feature1 >= 0.8 & feature1 < 0.9,
-                         0.5 + runif(n(), -0.5, 0.5),
-                         0.5 + rnorm(n(), 0, 0.3))))))) %>%
-  bind_rows(
-    data.frame(feature1 = rep(1, 30) + rnorm(5, 0, 0.05),
-           feature2 = rep(245, 30) + rnorm(5, 0, 1),
-           prediction = rep(0, 30) + rnorm(5, 0, 0.05)) %>%
-  mutate(feature1_stnd = (feature1 - mean(feature1)) / sd(feature1),
-         feature2_stnd = (feature2 - mean(feature2)) / sd(feature2)))
-
-# Specify a prediction of interest
-prediction_of_interest <-
-  data.frame(feature1 = 0.07, feature2 = 200) %>%
-  mutate(feature1_stnd = (feature1 - mean(lime_data$feature1)) /
-           sd(lime_data$feature1),
-         feature2_stnd = (feature2 - mean(lime_data$feature2)) /
-           sd(lime_data$feature2),
-         prediction = 0.05,
-         color = factor("Prediction \nof Interest"))
-
-# Specify the gower exponents
-good_gower_power <- 50
-bad_gower_power <- 1
+concept_data <-
+  data.frame(poi = "Training Data", 
+             feature = sort(c(runif(100, 0, 1), runif(250, 0, 7)))) %>%
+  mutate(prediction = sin(feature) + rnorm(350, 0, 0.25)) %>%
+  bind_rows(poi)
 
@@
 # and all other observations
-lime_data$distance_good <-
-  (1 - gower_dist(x = prediction_of_interest %>%
-                    select(feature1_stnd, feature2_stnd),
-                  y = lime_data %>%
-                    select(feature1_stnd,
-                           feature2_stnd)))^good_gower_power
+concept_data$weights_good <-
+  1 - (gower_dist(
+    x = poi %>% select(feature),
+    y = concept_data %>% select(feature)
+  )) ^ good_gower_power
 
@@
 # and all other observations
-lime_data$distance_bad <-
-  (1 - gower_dist(x = prediction_of_interest %>%
-                    select(feature1_stnd, feature2_stnd),
-                  y = lime_data %>%
-                    select(feature1_stnd,
-                           feature2_stnd)))^bad_gower_power
-
-# Prepare the data for plotting
-lime_data_gathered <- lime_data %>%
-  gather(feature, feature_stnd_value,
-         feature1_stnd:feature2_stnd) %>%
-  gather(distance, distance_value, distance_good:distance_bad) %>%
-  mutate(distance = fct_recode(distance,
-                               "good" = "distance_good",
-                               "bad" = "distance_bad"),
-         feature = fct_recode(feature,
-                              "Feature 1" = "feature1_stnd",
-                              "Feature 2" = "feature2_stnd"))
-
-# Prepare the prediction of interest data for plotting
-prediction_of_interest_gathered <- prediction_of_interest %>%
-  select(-feature1, -feature2) %>%
-  gather(feature, feature_value, feature1_stnd, feature2_stnd) %>%
-  mutate(feature = fct_recode(feature,
-                              "Feature 1" = "feature1_stnd",
-                              "Feature 2" = "feature2_stnd"))
-
-@
-
-<<concept-explainers>>=
-
-# Fit the good interpretable explainer model
+concept_data$weights_bad <-
+  1 - (gower_dist(
+    x = poi %>% select(feature),
+    y = concept_data %>% select(feature)
+  )) ^ bad_gower_power
+
+# Fit the good and bad interpretable explainer models
 explainer_good <-
-  glmnet(x = lime_data %>% select(feature1_stnd, feature2_stnd)
-         %>% as.matrix(),
-         y = lime_data$prediction,
-         alpha = 0,
-         lambda = 1,
-         weights = lime_data$distance_good)
-
-# Fit the bad interpretable explainer model
+  lm(prediction ~ feature, data = concept_data, weights = weights_good)
 explainer_bad <-
-  glmnet(x = lime_data %>% select(feature1_stnd, feature2_stnd)
-         %>% as.matrix(),
-         y = lime_data$prediction,
-         alpha = 0,
-         lambda = 1,
-         weights = lime_data$distance_bad)
+  lm(prediction ~ feature, data = concept_data, weights = weights_bad)
+
+# Create labels for the gower powers
+good_power_label <-
+  paste0("Faithful Local Explainer \n(exponent used to compute weights: ",
+         good_gower_power,
+         ")")
+bad_power_label <-
+  paste0("Unfaithful Local Explainer \n(exponent used to compute weights: ",
+         bad_gower_power,
+         ")")
 
 # Join the coefficients from the explainer model into a dataframe
-coefs_data <- data.frame(case = c("good", "bad"),
+coefs_data <-
+  data.frame(
+    case = c(good_power_label, bad_power_label),
     b0 = c(coef(explainer_good)[1],
@@
            coef(explainer_bad)[2]),
-                         b2 = c(coef(explainer_good)[3],
-                                coef(explainer_bad)[3])) %>%
-  mutate(feature1 = b0 + b2*prediction_of_interest$feature2_stnd,
-         feature2 = b0 + b1*prediction_of_interest$feature1_stnd) %>%
-  gather(key = feature, value = int, feature1:feature2) %>%
-  mutate(slope = c(coef(explainer_good)[2],
-                   coef(explainer_good)[3],
-                   coef(explainer_bad)[2],
-                   coef(explainer_bad)[3]),
-         feature = fct_recode(feature,
-                              "Feature 1" = "feature1",
-                              "Feature 2" = "feature2"))
-
-@
-
-\kge{Figure \ref{fig:figure-01} depicts the first scenario where the weights are computed as the inverse proximity of the point to the prediction of interest computed using the Gower distance metric \citep{gower:1971} raised to the power of \Sexpr{good_gower_power} to emphasize a very local region.
-The point size represents the weight, and the black lines depict the ridge regression model given the observed prediction of interest value from the opposite feature.
-For Feature 1 (left), the explainer model captures the relationship in an immediate neighborhood around the prediction of interest with a slope of \Sexpr{coefs_data %>% filter(case == "good", feature == "Feature 1") %>% pull(slope) %>% round(3)}, and for Feature 2 (right), the ridge regression has a small slope of \Sexpr{coefs_data %>% filter(case == "good", feature == "Feature 2") %>% pull(slope) %>% round(3)} that accurately reflects the absence of any global or local relationship between the black-box predictions and Feature 2.
-The magnitude of the slope associated with Feature 1 is larger than the slope of Feature 2, which suggests that Feature 1 plays a more important role in the prediction made by the black-box model for the prediction of interest.
-This explanation agrees with a visual assessment of the relationships between the predictions and predictor variables.}
+    feature = 6,
+    prediction = 1.6
+  ) %>%
+  mutate(text = paste0("Slope: ", round(b1, 3)))
+
+# Prepare data for plotting
+concept_data_long <-
+  concept_data %>%
+  pivot_longer(names_to = "case",
+               values_to = "weight",
+               cols = weights_good:weights_bad) %>%
+  mutate(case = ifelse(case == "weights_good", good_power_label, bad_power_label))
+@
 
 \begin{figure*}[!thp]
-<<figure-01, out.width = '6.5in', fig.width = 7.95, fig.height = 3.75, warning = FALSE>>=
+<<figure-01, out.width = '6.5in', fig.width = 7.95, fig.height = 3, warning = FALSE>>=
 
@@
 ggplot() +
-  facet_grid(. ~ feature, switch = "x") +
+  facet_grid(. ~ case) +
   geom_point(
-    data = lime_data_gathered,
+    data = concept_data_long,
     mapping = aes(
-      x = feature_stnd_value,
+      x = feature,
       y = prediction,
-      size = distance_value,
-      color = distance
-    ), alpha = 0.6
+      fill = poi,
+      color = poi,
+      shape = poi,
+      alpha = poi,
+      size = weight
+    )
   ) +
   geom_abline(
-    data = coefs_data %>% filter(case == "good"),
-    mapping = aes(intercept = int, slope = slope),
+    data = coefs_data,
+    mapping = aes(intercept = b0, slope = b1),
     size = 1
   ) +
-  scale_color_manual(values = c(NA, "grey30"), guide = "none") +
-  geom_point(
-    data = prediction_of_interest_gathered,
-    mapping = aes(x = feature_value,
+  scale_fill_manual(values = c("#FAAA72", "grey30")) +
+  scale_color_manual(values = c("grey30", "grey30")) +
+  scale_alpha_manual(values = c(0.75, 0.6)) +
+  scale_shape_manual(values = c(23, 21)) +
+  geom_text(
+    data = coefs_data,
+    mapping = aes(x = feature,
                   y = prediction,
-                  fill = color),
-    color = "black",
-    size = 5,
-    shape = 23,
-    alpha = 0.75
-  ) +
-  scale_fill_manual(values = "#FAAA72") +
-  geom_text(
-    data = data.frame(
-      feature_stnd_value = 1.2,
-      prediction = 1.6,
-      feature = c("Feature 1", "Feature 2"),
-      slope = c(
-        paste(
-          "Slope:",
-          coefs_data %>%
-            filter(case == "good",
-                   feature == "Feature 1") %>%
-            pull(slope) %>%
-            round(3)
-        ),
-        paste(
-          "Slope:",
-          coefs_data %>%
-            filter(case == "good",
-                   feature == "Feature 2") %>%
-            pull(slope) %>%
-            round(3)
-        )
-      )
-    ),
-    mapping = aes(x = feature_stnd_value,
-                  y = prediction,
-                  label = slope),
+                  label = text),
     family = ff,
@@
   ) +
-  labs(
-    x = "",
+  labs(x = "Black-Box Model Feature",
        y = "Black-Box Prediction",
-    title = "Conceptual Depiction of a Faithful Local Explainer Model",
-    subtitle = paste("Gower Distance Metric Exponent:", good_gower_power),
+       size = "Weight", 
        fill = "", 
-    alpha = "Weight",
-    size = "Weight"
-  ) +
+       color = "",
+       alpha = "",
+       shape = "") +
   theme_linedraw(base_family = ff, base_size = f1_fs) +
@@
   guides(
-    fill = guide_legend(order = 1),
-    size = guide_legend(order = 2),
-    alpha = guide_legend(order = 2)
-  )
-
-@
-\caption{A conceptual depiction of a faithful LIME explainer model in the immediate neighborhood of a prediction of interest.
-\kge{The explainer model in this scenario is a ridge regression weighted by the inverse Gower distance to the prediction of interest raised to the power of \Sexpr{good_gower_power}.} \sout{The predictions from a hypothetical black-box model are plotted against the standardized values of the two hypothetical predictor variables.
+    fill = guide_legend(order = 1, override.aes = list(size = 5)),
+    color = guide_legend(order = 1),
+    shape = guide_legend(order = 1),
+    alpha = guide_legend(order = 1),
+    size = guide_legend(
+      order = 2,
+      override.aes = list(color = "grey30", alpha = 0.6)
+    )
+  )
+
+# # Plot of good explainer model
+# ggplot() +
+#   facet_grid(. ~ feature, switch = "x") +
+#   geom_point(
+#     data = lime_data_gathered %>% mutate(
+#       feature = fct_recode(
+#         feature,
+#         "Feature 1 (standardized)" = "Feature 1",
+#         "Feature 2 (standardized)" = "Feature 2"
+#       )
+#     ),
+#     mapping = aes(
+#       x = feature_stnd_value,
+#       y = prediction,
+#       size = distance_value,
+#       color = distance
+#     ),
+#     alpha = 0.6
+#   ) +
+#   geom_abline(
+#     data = coefs_data %>%
+#       filter(case == "good") %>%
+#       mutate(
+#         feature = fct_recode(
+#           feature,
+#           "Feature 1 (standardized)" = "Feature 1",
+#           "Feature 2 (standardized)" = "Feature 2"
+#           )
+#         ),
+#     mapping = aes(intercept = int, slope = slope),
+#     size = 1
+#   ) +
+#   scale_color_manual(values = c(NA, "grey30"), guide = "none") +
+#   geom_point(
+#     data = prediction_of_interest_gathered %>% mutate(
+#       feature = fct_recode(
+#         feature,
+#         "Feature 1 (standardized)" = "Feature 1",
+#         "Feature 2 (standardized)" = "Feature 2"
+#       )
+#     ),
+#     mapping = aes(x = feature_value,
+#                   y = prediction,
+#                   fill = color),
+#     color = "black",
+#     size = 5,
+#     shape = 23,
+#     alpha = 0.75
+#   ) +
+#   scale_fill_manual(values = "#FAAA72") +
+#   geom_text(
+#     data = data.frame(
+#       feature_stnd_value = 1.2,
+#       prediction = 1.6,
+#       feature = c("Feature 1 (standardized)", "Feature 2 (standardized)"),
+#       slope = c(
+#         paste(
+#           "Slope:",
+#           coefs_data %>%
+#             filter(case == "good",
+#                    feature == "Feature 1") %>%
+#             pull(slope) %>%
+#             round(3)
+#         ),
+#         paste(
+#           "Slope:",
+#           coefs_data %>%
+#             filter(case == "good",
+#                    feature == "Feature 2") %>%
+#             pull(slope) %>%
+#             round(3)
+#         )
+#       )
+#     ),
+#     mapping = aes(x = feature_stnd_value,
+#                   y = prediction,
+#                   label = slope),
+#     family = ff,
+#     size = f1_fs / 2.85
+#   ) +
+#   labs(
+#     x = "",
+#     y = "Black-Box Prediction",
+#     title = "Conceptual Depiction of a Faithful Local Explainer Model",
+#     subtitle = paste("Gower Distance Metric Exponent:", good_gower_power),
+#     fill = "",
+#     alpha = "Weight",
+#     size = "Weight"
+#   ) +
+#   theme_linedraw(base_family = ff, base_size = f1_fs) +
+#   theme(
+#     panel.grid.major = element_blank(),
+#     panel.grid.minor = element_blank(),
+#     axis.text.x = element_blank(),
+#     axis.ticks.x = element_blank(),
+#     axis.text.y = element_blank(),
+#     axis.ticks.y = element_blank(),
+#     strip.placement = "outside",
+#     strip.background = element_rect(color = "white", fill = "white"),
+#     strip.text.x = element_text(size = f1_fs, color = "black"),
+#     plot.title = element_text(size = f1_fs)
+#   ) +
+#   guides(
+#     fill = guide_legend(order = 1),
+#     size = guide_legend(order = 2),
+#     alpha = guide_legend(order = 2)
+#   )
+
+@
+\caption{\kge{Hypothetical scenarios depicting the effect of different weights on LIME (Left) An example of an explainer model with appropriate weights to provide a faithful approximation of the complex model.
+(Right) An example of an explainer model for the same prediction but with different weights that results in an explanation unfaithful to the complex model.} \sout{A conceptual depiction of a faithful LIME explainer model in the immediate neighborhood of a prediction of interest \kge{for a hypothetical black-box model trained using two features: Feature 1 (left) and Feature 2 (right).
+The explainer model is a ridge regression weighted by the inverse Gower distance to the prediction of interest raised to the power of \Sexpr{good_gower_power}.}} \sout{The predictions from a hypothetical black-box model are plotted against the standardized values of the two hypothetical predictor variables.
 The diamond shaped points represent the location of a prediction of interest.
@@
 
-\sout{\autoref{fig:figure-01} provides a visualization of this conceptual understanding of LIME.
+In the field of statistics, there are two main uses for models: inference and prediction.
+Machine learning models \sout{are often used for the latter purpose.
+These models} have proven to perform well \kge{in problems with the latter objective} \sout{in a wide range of prediction problems}, but the accuracy of many machine learning models comes at the cost of interpretability due to their algorithmic complexity (hence the phrase "black-box models").
+Model interpretability allows for the understanding and assessment of how a model produces predictions.
+The lack of the ability to understand and assess a model makes it difficult to trust the model, especially in areas with high stakes decisions such as \kge{the} medical and forensics sciences.
+The increased use of machine learning models in applications and the introduction of the General Data Protection Regulation (GDPR) in 2018 \citep{goodman:2016} has resulted in a dramatic increase in explainable machine learning research, which focuses on developing ways to explain output from machine learning algorithms.
+
+Throughout this paper, we distinguish between interpretability and explanability of models.
+We define {\it interpretability} as the ability to directly use model parameters to understand the relationships in the data captured by the model: e.g., a linear model coefficient associated with a predictor variable indicates the amount the response variable changes based on a change in the predictor variable.
+In contrast, define {\it explanability} as the ability to use the model in an indirect manner to understand the relationships in the data captured by the model: e.g., partial dependence plots depict the marginal relationship between model predictions and predictor variables \citep{friedman:2001}.
+
+Numerous methods have been proposed to provide explanations for black-box model predictions \citep{gilpin:2018, guidotti:2018, ming:2017, molnar:2019}.
+Some are specific to one type of model (e.g.
+\citep{simonyan:2013} and \citep{urbanek:2008}), and others are model-agnostic (e.g.
+\citep{fisher:2018} and \citep{strumbelj:2014}).
+In this paper, we focus on \kge{the} \sout{one specific} model-agnostic method\sout{:} \kge{of} LIME \citep{ribeiro:2016}.
+
+LIME (local interpretable model-agnostic explanations) \sout{is a method that} uses a surrogate model to relate predictor variables to black-box model predictions \sout{(i.e.
+a model explainer)} \citep{ribeiro:2016}.
+\sout{We distinguish between the terms of model explainer and explainer model: by \emph{model explainer} we denote the method for explaining a complex model using a surrogate model, while the \emph{explainer model}, or simply the \emph{explainer}, is the surrogate model.} While some \kge{explainer} model\kge{s} \sout{explainers} focus on understanding a model at the global level, LIME claims to provide explanations for individual predictions (local).
+Additionally, LIME is designed to work with any model (model-agnostic) and to produce easily understandable results (explanations) \citep{ribeiro:2016}.
+Conceptually, LIME fits a simple (interpretable) model, the explainer model, \kge{to approximate} \sout{meant to capture the behavior of} the \sout{(}complex\sout{) black-box} model in a local region around a prediction of interest.
+The simple model \kge{is interpreted to identify the} \sout{then provides interpretable estimates for} variables that most influence\sout{d} the \kge{complex model} prediction\sout{made by the complex model}.
+
+\kge{While t}\sout{T}he concept of LIME is relatively simple\sout{: use an interpretable model to approximate a complex model in a local region.
+However}, a practical implementation of LIME is not straightforward, and research is being done to improve the procedure \citep{laugel:2018}.
+The current implementations of LIME \citep{pedersen:2020} \citep{ribeiro:2020} offer various tuning parameters (see Section \ref{background}) that affect the explainer model and ultimately, the explanation.
+Since the explainer model is an approximation of the complex model and not a direct interpretation, the explanations produced by an explainer model are subject to the quality of the approximation.
+Thus, in order to achieve \kge{reasonable} \sout{accurate} explanations, the tuning parameter values selected \kge{shoud} \sout{need to} be assessed.
+
+\kge{To demonstrate the effect of a tuning parameter on LIME, we consider two different explainer models applied to the same prediction.
+Figure \ref{fig:figure-01} depicts two plots of the predictions from a hypothetical black-box model versus the feature used to train the model.
+The location of a prediction of interest is indicated by the diamonds.
+Globally, there is a clear non-linear relationship between the predictions and the feature, but the relationship could be approximated by a linear model in a local region around the prediction of interest.
+In both scenarios, a linear regression weighted by the proximity from an observation to the prediction of interest is used as the explainer model, but the proximities are computed differently as depicted by the varying sizes of the observations in the two plots.}
+
+\kge{On the left, the distance between an observation and the prediction of interest is computed using the Gower distance metric \citep{gower:1971} and then raised to the power of \Sexpr{good_gower_power} to emphasize a very local region.
+The distances are subtracted from 1 to obtain a proximity.
+For the scenario on the right, the computation is the same except the distances are raised to a power of \Sexpr{bad_gower_power} (the default exponent in the \emph{lime} R package \citep{pedersen:2020}).
+This causes the observations that are further away from the prediction of interest to be given larger weights than the scenario on the left.}
+
+In \kge{the left scenario}\sout{\autoref{fig:figure-01}}, the explainer model \kge{is faithful to the complex model since it} captures the \kge{linear} relationship between the black-box predictions in an immediate neighborhood of the prediction of interest.
+\kge{The slope of \Sexpr{coefs_data %>% filter(case == good_power_label) %>% pull(b1) %>% round(3)} explains that the black-box predictions increase as the feature increases in the local region around the prediction of interest}.
+\kge{The explainer model on the right does not capture the linear trend near the prediction of interest, but instead, the explainer captures a more global trend.
+Without an assessment of this explainer model, the slope of \Sexpr{coefs_data %>% filter(case == bad_power_label) %>% pull(b1) %>% round(3)} would incorrectly explain that the predictions decrease as the feature increases near the prediction of interest.} %\sout{This cannot be said of the explainer model in \autoref{fig:figure-02}.
+In addition, the magnitude of the slope associated with Feature 2  (\Sexpr{coefs_data %>% filter(case == "bad", feature == "Feature 2") %>% pull(b1) %>% round(3) %>% abs()}) is larger than that of Feature 1 (\Sexpr{coefs_data %>% filter(case == "bad", feature == "Feature 1") %>% pull(b1) %>% round(3) %>% abs()}).
+Thus, this explainer model actually provides a misleading explanation that Feature 2 plays a more important role in the prediction of interest.}
+
+%\kge{To demonstrate the effect of tuning parameters on LIME,we consider two different explainer models applied to the same prediction.
+Suppose a hypothetical black-box model is trained using one feature.
+Both plots in Figure1show the black-box model predictions versus the feature used to train the model.The diamond shaped point in the plots indicates the location of the prediction of interest to explain.
+A weight ridge regression with the black-box predictions as the response variable and standardized versions the features as predictor variables will be used as the explainer model in both scenarios, but the weights will vary.
+Note that the standardized features allow for direct comparisons of the model coefficients.}
+
+%\kge{Figure \ref{fig:figure-01} depicts the first scenario where the weights are computed as the inverse proximity of the point to the prediction of interest computed using the Gower distance metric \citep{gower:1971} raised to the power of \Sexpr{good_gower_power} to emphasize a very local region.
+The point size represents the weight, and the black lines depict the ridge regression model given the observed prediction of interest value from the opposite feature.
+For Feature 1 (left), the explainer model captures the relationship in an immediate neighborhood around the prediction of interest with a slope of \Sexpr{coefs_data %>% filter(case == "good", feature == "Feature 1") %>% pull(slope) %>% round(3)}, and for Feature 2 (right), the ridge regression has a small slope of \Sexpr{coefs_data %>% filter(case == "good", feature == "Feature 2") %>% pull(slope) %>% round(3)} that accurately reflects the absence of any global or local relationship between the black-box predictions and Feature 2.
+The magnitude of the slope associated with Feature 1 is larger than the slope of Feature 2, which suggests that Feature 1 plays a more important role in the prediction made by the black-box model for the prediction of interest.
+This explanation agrees with a visual assessment of the relationships between the predictions and predictor variables.}
+
+%\sout{\autoref{fig:figure-01} provides a visualization of this conceptual understanding of LIME.
 The two plots show the predictions from a hypothetical black-box model plotted against the two hypothetical model predictor variables.
@@
 
-\sout{The plot on the left of \autoref{fig:figure-01} shows the relationship between the black-box predictions and Feature 1.
+%\sout{The plot on the left of \autoref{fig:figure-01} shows the relationship between the black-box predictions and Feature 1.
 Here, the explainer model is plotted with Feature 2 fixed at the observed value of the prediction of interest.
@@
 
-\sout{The concept of LIME is relatively simple: use an interpretable model to approximate a complex model in a local region.
+%\sout{The concept of LIME is relatively simple: use an interpretable model to approximate a complex model in a local region.
 However, a practical implementation of LIME is not straightforward, and research is being done to improve the procedure \citep{laugel:2018}.
@@
 
-\kge{Figure \ref{fig:figure-02} depicts the second explainer model scenario.
+%\kge{Figure \ref{fig:figure-02} depicts the second explainer model scenario.
 Again, the weights are computed using the Gower distance metric, but in this situation, the distances are raise to a power of \Sexpr{bad_gower_power} (the default exponent in the \emph{lime} R package).} \sout{We consider an example where the choice of exponent for the weights is crucial to the quality of the explanation.
@@
 
-\begin{figure*}[!thp]
-<<figure-02, out.width = '6.5in', fig.width = 7.95, fig.height = 3.75, warning = FALSE>>=
-
-# Specify the figure size (for determining font size)
-f2_ow = 6.5
-f2_fw = 7.95
-f2_fs = fs * (f2_fw / f2_ow)
-
-# Plot of good explainer model
-ggplot() +
-  facet_grid(. ~ feature, switch = "x") +
-  geom_point(
-    data = lime_data_gathered,
-    mapping = aes(
-      x = feature_stnd_value,
-      y = prediction,
-      size = distance_value,
-      color = distance
-    ), 
-    alpha = 0.6
-  ) +
-  geom_abline(
-    data = coefs_data %>% filter(case == "bad"),
-    mapping = aes(intercept = int, slope = slope),
-    size = 1
-  ) +
-  scale_color_manual(values = c("grey30", NA), guide = "none") +
-  geom_point(
-    data = prediction_of_interest_gathered,
-    mapping = aes(x = feature_value,
-                  y = prediction,
-                  fill = color),
-    color = "black",
-    size = 5,
-    shape = 23,
-    alpha = 0.75
-  ) +
-  scale_fill_manual(values = "#FAAA72") +
-  geom_text(
-    data = data.frame(
-      feature_stnd_value = 1.2,
-      prediction = 1.6,
-      feature = c("Feature 1", "Feature 2"),
-      slope = c(
-        paste(
-          "Slope:",
-          coefs_data %>%
-            filter(case == "bad",
-                   feature == "Feature 1") %>%
-            pull(slope) %>%
-            round(3)
-        ),
-        paste(
-          "Slope:",
-          coefs_data %>%
-            filter(case == "bad",
-                   feature == "Feature 2") %>%
-            pull(slope) %>%
-            round(3)
-        )
-      )
-    ),
-    mapping = aes(x = feature_stnd_value,
-                  y = prediction,
-                  label = slope),
-    family = ff,
-    size = f2_fs / 3
-  ) +
-  labs(
-    x = "",
-    y = "Black-Box Prediction",
-    title = "Conceptual Depiction of an Unfaithful Local Explainer Model",
-    subtitle = paste("Gower Distance Metric Exponent:", bad_gower_power),
-    fill = "",
-    alpha = "Weight",
-    size = "Weight"
-  ) +
-  theme_linedraw(base_family = ff, base_size = f2_fs) +
-  theme(
-    panel.grid.major = element_blank(),
-    panel.grid.minor = element_blank(),
-    axis.text.x = element_blank(),
-    axis.ticks.x = element_blank(),
-    axis.text.y = element_blank(),
-    axis.ticks.y = element_blank(),
-    strip.placement = "outside",
-    strip.background = element_rect(color = "white", fill = "white"),
-    strip.text.x = element_text(size = f2_fs, color = "black"),
-    plot.title = element_text(size = f2_fs)
-  ) +
-  guides(
-    fill = guide_legend(order = 1),
-    size = guide_legend(order = 2),
-    alpha = guide_legend(order = 2)
-  )
-
-@
-\caption{A conceptual depiction of an unfaithful local explainer model in the immediate neighborhood of a prediction of interest.
+% \begin{figure*}[!thp]
+% <<figure-02, out.width = '6.25in', fig.width = 7.95, fig.height = 3.25, warning = FALSE, eval = FALSE>>=
+% 
+% # Specify the figure size (for determining font size)
+% f2_ow = 6.25
+% f2_fw = 7.95
+% f2_fs = fs * (f2_fw / f2_ow)
+% 
+% # Plot of good explainer model
+% ggplot() +
+%   facet_grid(. ~ feature, switch = "x") +
+%   geom_point(
+%     data = lime_data_gathered %>% 
+%       mutate(
+%         feature = fct_recode(
+%           feature,
+%           "Feature 1 (standardized)" = "Feature 1",
+%           "Feature 2 (standardized)" = "Feature 2"
+%           )
+%         ),
+%     mapping = aes(
+%       x = feature_stnd_value,
+%       y = prediction,
+%       size = distance_value,
+%       color = distance
+%     ), 
+%     alpha = 0.6
+%   ) +
+%   geom_abline(
+%     data = coefs_data %>% 
+%       filter(case == "bad") %>% 
+%       mutate(
+%         feature = fct_recode(
+%           feature,
+%           "Feature 1 (standardized)" = "Feature 1",
+%           "Feature 2 (standardized)" = "Feature 2"
+%           )
+%         ),
+%     mapping = aes(intercept = int, slope = slope),
+%     size = 1
+%   ) +
+%   scale_color_manual(values = c("grey30", NA), guide = "none") +
+%   geom_point(
+%     data = prediction_of_interest_gathered %>% 
+%       mutate(
+%         feature = fct_recode(
+%           feature,
+%           "Feature 1 (standardized)" = "Feature 1",
+%           "Feature 2 (standardized)" = "Feature 2"
+%           )
+%         ),
+%     mapping = aes(x = feature_value,
+%                   y = prediction,
+%                   fill = color),
+%     color = "black",
+%     size = 5,
+%     shape = 23,
+%     alpha = 0.75
+%   ) +
+%   scale_fill_manual(values = "#FAAA72") +
+%   geom_text(
+%     data = data.frame(
+%       feature_stnd_value = 1.2,
+%       prediction = 1.6,
+%       feature = c("Feature 1 (standardized)", "Feature 2 (standardized)"),
+%       slope = c(
+%         paste(
+%           "Slope:",
+%           coefs_data %>%
+%             filter(case == "bad",
+%                    feature == "Feature 1") %>%
+%             pull(slope) %>%
+%             round(3)
+%         ),
+%         paste(
+%           "Slope:",
+%           coefs_data %>%
+%             filter(case == "bad",
+%                    feature == "Feature 2") %>%
+%             pull(slope) %>%
+%             round(3)
+%         )
+%       )
+%     ),
+%     mapping = aes(x = feature_stnd_value,
+%                   y = prediction,
+%                   label = slope),
+%     family = ff,
+%     size = f2_fs / 3
+%   ) +
+%   labs(
+%     x = "",
+%     y = "Black-Box Prediction",
+%     title = "Conceptual Depiction of an Unfaithful Local Explainer Model",
+%     subtitle = paste("Gower Distance Metric Exponent:", bad_gower_power),
+%     fill = "",
+%     alpha = "Weight",
+%     size = "Weight"
+%   ) +
+%   theme_linedraw(base_family = ff, base_size = f2_fs) +
+%   theme(
+%     panel.grid.major = element_blank(),
+%     panel.grid.minor = element_blank(),
+%     axis.text.x = element_blank(),
+%     axis.ticks.x = element_blank(),
+%     axis.text.y = element_blank(),
+%     axis.ticks.y = element_blank(),
+%     strip.placement = "outside",
+%     strip.background = element_rect(color = "white", fill = "white"),
+%     strip.text.x = element_text(size = f2_fs, color = "black"),
+%     plot.title = element_text(size = f2_fs)
+%   ) +
+%   guides(
+%     fill = guide_legend(order = 1),
+%     size = guide_legend(order = 2),
+%     alpha = guide_legend(order = 2)
+%   )
+% 
+% @
+% \caption{A conceptual depiction of an unfaithful local explainer model in the immediate neighborhood of a prediction of interest.
 A\kge{gain, a weighted} ridge regression \kge{is used as the explainer model} \sout{is fit to the same hypothetical black-box model predictions and predictor variables as in \autoref{fig:figure-01}}, but the \kge{Gower distance is raised to a power} \sout{weights are computed using a Gower exponent} of 1.
 \sout{The explainer model is unfaithful to the complex model in any immediate neighborhood of the prediction of interest.}}
-\label{fig:figure-02}
-\end{figure*}
-
-\kge{This example demonstrates the effect of the selection of weights on the LIME explanations, but other concerns with LIME have been raised in the literature.} \sout{Several sources in the literature discuss the performance of LIME.} One of the biggest difficulties with LIME is determining how to specify a local region \citep{laugel:2018} \citep{molnar:2019}.
-This is due to an unclear definition of a "local region" and how to apply LIME to achieve an appropriate local region as demonstrated by \autoref{fig:figure-02}.
-\citet{alvarezmelis:2018} raise a concern pertaining to the robustness of explanations from LIME and other \kge{explainer} model\kge{s} \sout{explainers}: they find that even small changes in predictor variables can lead to very different LIME explanations.
-Additionally, \citet{ribeiro:2016} acknowledge that if a linear model is used as the explainer, LIME relies on a linear approximation of the explainer model to the complex model and state "if the underlying model is highly non-linear even in the locality of the prediction, there may not be a faithful explanation".
-
-\kge{In this paper, we stress the importance of assessing LIME by introducing several diagnostic plots that highlight key issues with LIME.} \sout{As a result of the various ways LIME can fail, it is important to assess LIME explanations.
+% \label{fig:figure-02}
+% \end{figure*}
+
+\kge{\autoref{fig:figure-01} demonstrates a simple example in which the explanation quality varies drastically when different weights are used.
+Similar concerns with LIME have been raised in the literature.} \sout{Several sources in the literature discuss the performance of LIME.} \kge{\citet{laugel:2018} and \citet{molnar:2019} discuss the difficulty specifying a local region with LIME due to both} \sout{One of the biggest difficulties with LIME is determining how to specify a local region \citep{laugel:2018} \citep{molnar:2019}.
+This is due to} an unclear definition of \kge{what is} a "local region" and how to apply LIME to achieve an appropriate local region\sout{ as demonstrated by \autoref{fig:figure-02}}.
+\kge{A different concern about LIME is raised by} \citet{alvarezmelis:2018} \sout{raise a concern} pertaining to the robustness of explanations from LIME and other \kge{explainer} model\kge{s} \sout{explainers}: they find that even small changes in predictor variables can lead to very different LIME explanations.
+\kge{Even the original authors of LIME,} \sout{Additionally,} \citet{ribeiro:2016}\kge{,} acknowledge that if a linear model is used as the explainer, LIME relies on a linear approximation of the explainer model to the complex model and state "if the underlying model is highly non-linear even in the locality of the prediction, there may not be a faithful explanation".
+
+\kge{In this paper, we stress the importance of assessing LIME by introducing several diagnostic plots for LIME and using the plots to highlight key issues with LIME.} \sout{As a result of the various ways LIME can fail, it is important to assess LIME explanations.
 We suggest the use of visual diagnostics for assessment.
@@
 
-All runs of LIME in this paper are executed in a forked version\footnote{https://github.com/goodekat/lime} of the R package \emph{lime} (version \Sexpr{packageVersion("lime")}) by \citet{pedersen:2020}.
+All runs of LIME in this paper are executed in a forked version (https://github.com/goodekat/lime) of the R package \emph{lime} (version \Sexpr{packageVersion("lime")}) by \citet{pedersen:2020}.
 The forked version is functionally indistinguishable from \citeauthor{pedersen:2020}'s implementation but allows us to export internal values relevant for an assessment of the explainer.

### 2020-12-08 paper.tex
worked on trimming section 1 even more

@@
 
+\begin{figure*}[!thp]
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+
+{\centering \includegraphics[width=6.5in]{figure/figure-01-1}
+
+}
+
+\end{knitrout}
+\caption{\kge{Hypothetical scenarios depicting the effect of different weights on LIME (Left) An example of an explainer model with appropriate weights to provide a faithful approximation of the complex model.
+(Right) An example of an explainer model for the same prediction but with different weights that results in an explanation unfaithful to the complex model.} \sout{A conceptual depiction of a faithful LIME explainer model in the immediate neighborhood of a prediction of interest \kge{for a hypothetical black-box model trained using two features: Feature 1 (left) and Feature 2 (right).
+The explainer model is a ridge regression weighted by the inverse Gower distance to the prediction of interest raised to the power of \ensuremath{5\times 10^{-17}}.}} \sout{The predictions from a hypothetical black-box model are plotted against the standardized values of the two hypothetical predictor variables.
+The diamond shaped points represent the location of a prediction of interest.
+The size and opacity of the circular points indicate the weight assigned based on the distance to the prediction of interest computed using the inverse of the Gower distance metric raised to the power of \ensuremath{5\times 10^{-17}}.
+The black lines represent a weighted ridge regression model used as an explainer model that reasonably captures the relationship between the black-box predictions and the features in a local region around the prediction of interest.
+That is, the explainer is faithful to the complex model and produces a reasonable explanation that Feature 1 plays a more important role in the prediction of interest than Feature 2 since the magnitude of the slope associated with Feature 1 is larger.}}
+\label{fig:figure-01}
+\end{figure*}
+
 In the field of statistics, there are two main uses for models: inference and prediction.
 Machine learning models \sout{are often used for the latter purpose.
-These models} have proven to perform well \kge{for problems with the latter objective} \sout{in a wide range of prediction problems}, but the accuracy of many machine learning models comes at the cost of interpretability due to their algorithmic complexity (hence the phrase "black-box models").
+These models} have proven to perform well \kge{in problems with the latter objective} \sout{in a wide range of prediction problems}, but the accuracy of many machine learning models comes at the cost of interpretability due to their algorithmic complexity (hence the phrase "black-box models").
 Model interpretability allows for the understanding and assessment of how a model produces predictions.
@@
 
-LIME (local interpretable model-agnostic explanations) \sout{is a method that} uses a surrogate model, to relate predictor variables to black-box model predictions \sout{(i.e.
+LIME (local interpretable model-agnostic explanations) \sout{is a method that} uses a surrogate model to relate predictor variables to black-box model predictions \sout{(i.e.
 a model explainer)} \citep{ribeiro:2016}.
@@
 Conceptually, LIME fits a simple (interpretable) model, the explainer model, \kge{to approximate} \sout{meant to capture the behavior of} the \sout{(}complex\sout{) black-box} model in a local region around a prediction of interest.
-The simple model \kge{ma be interpreted to identify the} \sout{then provides interpretable estimates for} variables that most influenced the \kge{complex model} prediction\sout{made by the complex model}.
+The simple model \kge{is interpreted to identify the} \sout{then provides interpretable estimates for} variables that most influence\sout{d} the \kge{complex model} prediction\sout{made by the complex model}.
 
@@
 However}, a practical implementation of LIME is not straightforward, and research is being done to improve the procedure \citep{laugel:2018}.
-The current implementations of LIME \citep{ribeiro:2020} \citep{pedersen:2020} offer various tuning parameters (see Section \ref{background}) that affect the explainer model and ultimately, the explanation.
+The current implementations of LIME \citep{pedersen:2020} \citep{ribeiro:2020} offer various tuning parameters (see Section \ref{background}) that affect the explainer model and ultimately, the explanation.
 Since the explainer model is an approximation of the complex model and not a direct interpretation, the explanations produced by an explainer model are subject to the quality of the approximation.
-Thus, in order to achieve accurate explanations, the tuning parameter values selected need to be assessed.
-
-\kge{To demonstrate the effect of tuning parameters on LIME, we consider two different explainer models applied to the same prediction.
-Suppose a black-box model is trained using two features: Feature 1 and Feature 2.
-Figure \ref{fig:figure-01} shows the black-box model predictions versus standardized versions of Feature 1 (left) and Feature 2 (right).
-The diamond shaped point in the plots indicates the location of the prediction of interest to explain.
+Thus, in order to achieve \kge{reasonable} \sout{accurate} explanations, the tuning parameter values selected \kge{shoud} \sout{need to} be assessed.
+
+\kge{To demonstrate the effect of a tuning parameter on LIME, we consider two different explainer models applied to the same prediction.
+Figure \ref{fig:figure-01} depicts two plots of the predictions from a hypothetical black-box model versus the feature used to train the model.
+The location of a prediction of interest is indicated by the diamonds.
+Globally, there is a clear non-linear relationship between the predictions and the feature, but the relationship could be approximated by a linear model in a local region around the prediction of interest.
+In both scenarios, a linear regression weighted by the proximity from an observation to the prediction of interest is used as the explainer model, but the proximities are computed differently as depicted by the varying sizes of the observations in the two plots.}
+
+\kge{On the left, the distance between an observation and the prediction of interest is computed using the Gower distance metric \citep{gower:1971} and then raised to the power of \ensuremath{5\times 10^{-17}} to emphasize a very local region.
+The distances are subtracted from 1 to obtain a proximity.
+For the scenario on the right, the computation is the same except the distances are raised to a power of 1 (the default exponent in the \emph{lime} R package \citep{pedersen:2020}).
+This causes the observations that are further away from the prediction of interest to be given larger weights than the scenario on the left.}
+
+In \kge{the left scenario}\sout{\autoref{fig:figure-01}}, the explainer model \kge{is faithful to the complex model since it} captures the \kge{linear} relationship between the black-box predictions in an immediate neighborhood of the prediction of interest.
+\kge{The slope of 0.634 explains that the black-box predictions increase as the feature increases in the local region around the prediction of interest}.
+\kge{The explainer model on the right does not capture the linear trend near the prediction of interest, but instead, the explainer captures a more global trend.
+Without an assessment of this explainer model, the slope of -0.181 would incorrectly explain that the predictions decrease as the feature increases near the prediction of interest.} %\sout{This cannot be said of the explainer model in \autoref{fig:figure-02}.
+In addition, the magnitude of the slope associated with Feature 2  () is larger than that of Feature 1 ().
+Thus, this explainer model actually provides a misleading explanation that Feature 2 plays a more important role in the prediction of interest.}
+
+%\kge{To demonstrate the effect of tuning parameters on LIME,we consider two different explainer models applied to the same prediction.
+Suppose a hypothetical black-box model is trained using one feature.
+Both plots in Figure1show the black-box model predictions versus the feature used to train the model.The diamond shaped point in the plots indicates the location of the prediction of interest to explain.
 A weight ridge regression with the black-box predictions as the response variable and standardized versions the features as predictor variables will be used as the explainer model in both scenarios, but the weights will vary.
@@
 
-\kge{Figure \ref{fig:figure-01} depicts the first scenario where the weights are computed as the inverse proximity of the point to the prediction of interest computed using the Gower distance metric \citep{gower:1971} raised to the power of 50 to emphasize a very local region.
+%\kge{Figure \ref{fig:figure-01} depicts the first scenario where the weights are computed as the inverse proximity of the point to the prediction of interest computed using the Gower distance metric \citep{gower:1971} raised to the power of good_gower_power to emphasize a very local region.
 The point size represents the weight, and the black lines depict the ridge regression model given the observed prediction of interest value from the opposite feature.
-For Feature 1 (left), the explainer model captures the relationship in an immediate neighborhood around the prediction of interest with a slope of 0.068, and for Feature 2 (right), the ridge regression has a small slope of -0.001 that accurately reflects the absence of any global or local relationship between the black-box predictions and Feature 2.
+For Feature 1 (left), the explainer model captures the relationship in an immediate neighborhood around the prediction of interest with a slope of coefs_data %>% filter(case == "good", feature == "Feature 1") %>% pull(slope) %>% round(3), and for Feature 2 (right), the ridge regression has a small slope of coefs_data %>% filter(case == "good", feature == "Feature 2") %>% pull(slope) %>% round(3) that accurately reflects the absence of any global or local relationship between the black-box predictions and Feature 2.
 The magnitude of the slope associated with Feature 1 is larger than the slope of Feature 2, which suggests that Feature 1 plays a more important role in the prediction made by the black-box model for the prediction of interest.
@@
 
-\begin{figure*}[!thp]
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-
-{\centering \includegraphics[width=6.5in]{figure/figure-01-1}
-
-}
-
-\end{knitrout}
-\caption{A conceptual depiction of a faithful LIME explainer model in the immediate neighborhood of a prediction of interest.
-\kge{The explainer model in this scenario is a ridge regression weighted by the inverse Gower distance to the prediction of interest raised to the power of 50.} \sout{The predictions from a hypothetical black-box model are plotted against the standardized values of the two hypothetical predictor variables.
-The diamond shaped points represent the location of a prediction of interest.
-The size and opacity of the circular points indicate the weight assigned based on the distance to the prediction of interest computed using the inverse of the Gower distance metric raised to the power of 50.
-The black lines represent a weighted ridge regression model used as an explainer model that reasonably captures the relationship between the black-box predictions and the features in a local region around the prediction of interest.
-That is, the explainer is faithful to the complex model and produces a reasonable explanation that Feature 1 plays a more important role in the prediction of interest than Feature 2 since the magnitude of the slope associated with Feature 1 is larger.}}
-\label{fig:figure-01}
-\end{figure*}
-
-\sout{\autoref{fig:figure-01} provides a visualization of this conceptual understanding of LIME.
+%\sout{\autoref{fig:figure-01} provides a visualization of this conceptual understanding of LIME.
 The two plots show the predictions from a hypothetical black-box model plotted against the two hypothetical model predictor variables.
@@
 A Gower distance metric \citep{gower:1971} is used to define locality such that the size of the points represent the inverse of the Gower distance raised to some value and indicate the proximity to the prediction of interest.
-In the example of \autoref{fig:figure-01}, an exponent of 50 is used to emphasize a very local region around the prediction of interest.
+In the example of \autoref{fig:figure-01}, an exponent of good_gower_power is used to emphasize a very local region around the prediction of interest.
 A ridge regression model weighted by the proximity values is used as the explainer model with the black-box predictions as the response variable and standardized versions of two features in the data as predictor variables.
@@
 
-\sout{The plot on the left of \autoref{fig:figure-01} shows the relationship between the black-box predictions and Feature 1.
+%\sout{The plot on the left of \autoref{fig:figure-01} shows the relationship between the black-box predictions and Feature 1.
 Here, the explainer model is plotted with Feature 2 fixed at the observed value of the prediction of interest.
-The explainer model captures the relationship in an immediate neighborhood around the prediction of interest with a slope of 0.068.
+The explainer model captures the relationship in an immediate neighborhood around the prediction of interest with a slope of coefs_data %>% filter(case == "good", feature == "Feature 1") %>% pull(slope) %>% round(3).
 The plot on the right shows no global or local relationships between the black-box predictions and Feature 2.
-Here, the explainer model is plotted with Feature 1 set as the observed value of the prediction of interest, and it has an appropriately small slope of -0.001.
+Here, the explainer model is plotted with Feature 1 set as the observed value of the prediction of interest, and it has an appropriately small slope of coefs_data %>% filter(case == "good", feature == "Feature 2") %>% pull(slope) %>% round(3).
 The magnitude of the slope associated with Feature 1 is larger than the slope of Feature 2, which suggests that Feature 1 plays a more important role in the prediction made by the black-box model for the prediction of interest.
@@
 
-\kge{Figure \ref{fig:figure-02} depicts the second explainer model scenario.
-Again, the weights are computed using the Gower distance metric, but in this situation, the distances are raise to a power of 1 (the default exponent in the \emph{lime} R package).} \sout{We consider an example where the choice of exponent for the weights is crucial to the quality of the explanation.
-The plots in Figure \ref{fig:figure-02} show the same data as \autoref{fig:figure-01}, but the Gower distance metric exponent is decreased to 1 (the default exponent in the \emph{lime} R package).} This causes the observations that are further away from the prediction of interest to be given larger weights than before.
+%\kge{Figure \ref{fig:figure-02} depicts the second explainer model scenario.
+Again, the weights are computed using the Gower distance metric, but in this situation, the distances are raise to a power of bad_gower_power (the default exponent in the \emph{lime} R package).} \sout{We consider an example where the choice of exponent for the weights is crucial to the quality of the explanation.
+The plots in Figure \ref{fig:figure-02} show the same data as \autoref{fig:figure-01}, but the Gower distance metric exponent is decreased to bad_gower_power (the default exponent in the \emph{lime} R package).} This causes the observations that are further away from the prediction of interest to be given larger weights than before.
 In \autoref{fig:figure-01}, the explainer model captures the relationship between the black-box predictions in an immediate neighborhood of the prediction of interest.
 This cannot be said of the explainer model in \autoref{fig:figure-02}.
-In addition, the magnitude of the slope associated with Feature 2  (0.011) is larger than that of Feature 1 (0.005).
+In addition, the magnitude of the slope associated with Feature 2  (coefs_data %>% filter(case == "bad", feature == "Feature 2") %>% pull(slope) %>% round(3) %>% abs()) is larger than that of Feature 1 (coefs_data %>% filter(case == "bad", feature == "Feature 1") %>% pull(slope) %>% round(3) %>% abs()).
 Thus, this explainer model actually provides a misleading explanation that Feature 2 plays a more important role in the prediction of interest.
 
-\begin{figure*}[!thp]
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-
-{\centering \includegraphics[width=6.5in]{figure/figure-02-1}
-
-}
-
-\end{knitrout}
-\caption{A conceptual depiction of an unfaithful local explainer model in the immediate neighborhood of a prediction of interest.
+% \begin{figure*}[!thp]
+% <<figure-02, out.width = '6.25in', fig.width = 7.95, fig.height = 3.25, warning = FALSE, eval = FALSE>>=
+% 
+% # Specify the figure size (for determining font size)
+% f2_ow = 6.25
+% f2_fw = 7.95
+% f2_fs = fs * (f2_fw / f2_ow)
+% 
+% # Plot of good explainer model
+% ggplot() +
+%   facet_grid(. ~ feature, switch = "x") +
+%   geom_point(
+%     data = lime_data_gathered %>% 
+%       mutate(
+%         feature = fct_recode(
+%           feature,
+%           "Feature 1 (standardized)" = "Feature 1",
+%           "Feature 2 (standardized)" = "Feature 2"
+%           )
+%         ),
+%     mapping = aes(
+%       x = feature_stnd_value,
+%       y = prediction,
+%       size = distance_value,
+%       color = distance
+%     ), 
+%     alpha = 0.6
+%   ) +
+%   geom_abline(
+%     data = coefs_data %>% 
+%       filter(case == "bad") %>% 
+%       mutate(
+%         feature = fct_recode(
+%           feature,
+%           "Feature 1 (standardized)" = "Feature 1",
+%           "Feature 2 (standardized)" = "Feature 2"
+%           )
+%         ),
+%     mapping = aes(intercept = int, slope = slope),
+%     size = 1
+%   ) +
+%   scale_color_manual(values = c("grey30", NA), guide = "none") +
+%   geom_point(
+%     data = prediction_of_interest_gathered %>% 
+%       mutate(
+%         feature = fct_recode(
+%           feature,
+%           "Feature 1 (standardized)" = "Feature 1",
+%           "Feature 2 (standardized)" = "Feature 2"
+%           )
+%         ),
+%     mapping = aes(x = feature_value,
+%                   y = prediction,
+%                   fill = color),
+%     color = "black",
+%     size = 5,
+%     shape = 23,
+%     alpha = 0.75
+%   ) +
+%   scale_fill_manual(values = "#FAAA72") +
+%   geom_text(
+%     data = data.frame(
+%       feature_stnd_value = 1.2,
+%       prediction = 1.6,
+%       feature = c("Feature 1 (standardized)", "Feature 2 (standardized)"),
+%       slope = c(
+%         paste(
+%           "Slope:",
+%           coefs_data %>%
+%             filter(case == "bad",
+%                    feature == "Feature 1") %>%
+%             pull(slope) %>%
+%             round(3)
+%         ),
+%         paste(
+%           "Slope:",
+%           coefs_data %>%
+%             filter(case == "bad",
+%                    feature == "Feature 2") %>%
+%             pull(slope) %>%
+%             round(3)
+%         )
+%       )
+%     ),
+%     mapping = aes(x = feature_stnd_value,
+%                   y = prediction,
+%                   label = slope),
+%     family = ff,
+%     size = f2_fs / 3
+%   ) +
+%   labs(
+%     x = "",
+%     y = "Black-Box Prediction",
+%     title = "Conceptual Depiction of an Unfaithful Local Explainer Model",
+%     subtitle = paste("Gower Distance Metric Exponent:", bad_gower_power),
+%     fill = "",
+%     alpha = "Weight",
+%     size = "Weight"
+%   ) +
+%   theme_linedraw(base_family = ff, base_size = f2_fs) +
+%   theme(
+%     panel.grid.major = element_blank(),
+%     panel.grid.minor = element_blank(),
+%     axis.text.x = element_blank(),
+%     axis.ticks.x = element_blank(),
+%     axis.text.y = element_blank(),
+%     axis.ticks.y = element_blank(),
+%     strip.placement = "outside",
+%     strip.background = element_rect(color = "white", fill = "white"),
+%     strip.text.x = element_text(size = f2_fs, color = "black"),
+%     plot.title = element_text(size = f2_fs)
+%   ) +
+%   guides(
+%     fill = guide_legend(order = 1),
+%     size = guide_legend(order = 2),
+%     alpha = guide_legend(order = 2)
+%   )
+% 
+% @
+% \caption{A conceptual depiction of an unfaithful local explainer model in the immediate neighborhood of a prediction of interest.
 A\kge{gain, a weighted} ridge regression \kge{is used as the explainer model} \sout{is fit to the same hypothetical black-box model predictions and predictor variables as in \autoref{fig:figure-01}}, but the \kge{Gower distance is raised to a power} \sout{weights are computed using a Gower exponent} of 1.
 \sout{The explainer model is unfaithful to the complex model in any immediate neighborhood of the prediction of interest.}}
-\label{fig:figure-02}
-\end{figure*}
-
-\kge{This example demonstrates the effect of the selection of weights on the LIME explanations, but other concerns with LIME have been raised in the literature.} \sout{Several sources in the literature discuss the performance of LIME.} One of the biggest difficulties with LIME is determining how to specify a local region \citep{laugel:2018} \citep{molnar:2019}.
-This is due to an unclear definition of a "local region" and how to apply LIME to achieve an appropriate local region as demonstrated by \autoref{fig:figure-02}.
-\citet{alvarezmelis:2018} raise a concern pertaining to the robustness of explanations from LIME and other \kge{explainer} model\kge{s} \sout{explainers}: they find that even small changes in predictor variables can lead to very different LIME explanations.
-Additionally, \citet{ribeiro:2016} acknowledge that if a linear model is used as the explainer, LIME relies on a linear approximation of the explainer model to the complex model and state "if the underlying model is highly non-linear even in the locality of the prediction, there may not be a faithful explanation".
-
-\kge{In this paper, we stress the importance of assessing LIME by introducing several diagnostic plots that highlight key issues with LIME.} \sout{As a result of the various ways LIME can fail, it is important to assess LIME explanations.
+% \label{fig:figure-02}
+% \end{figure*}
+
+\kge{\autoref{fig:figure-01} demonstrates a simple example in which the explanation quality varies drastically when different weights are used.
+Similar concerns with LIME have been raised in the literature.} \sout{Several sources in the literature discuss the performance of LIME.} \kge{\citet{laugel:2018} and \citet{molnar:2019} discuss the difficulty specifying a local region with LIME due to both} \sout{One of the biggest difficulties with LIME is determining how to specify a local region \citep{laugel:2018} \citep{molnar:2019}.
+This is due to} an unclear definition of \kge{what is} a "local region" and how to apply LIME to achieve an appropriate local region\sout{ as demonstrated by \autoref{fig:figure-02}}.
+\kge{A different concern about LIME is raised by} \citet{alvarezmelis:2018} \sout{raise a concern} pertaining to the robustness of explanations from LIME and other \kge{explainer} model\kge{s} \sout{explainers}: they find that even small changes in predictor variables can lead to very different LIME explanations.
+\kge{Even the original authors of LIME,} \sout{Additionally,} \citet{ribeiro:2016}\kge{,} acknowledge that if a linear model is used as the explainer, LIME relies on a linear approximation of the explainer model to the complex model and state "if the underlying model is highly non-linear even in the locality of the prediction, there may not be a faithful explanation".
+
+\kge{In this paper, we stress the importance of assessing LIME by introducing several diagnostic plots for LIME and using the plots to highlight key issues with LIME.} \sout{As a result of the various ways LIME can fail, it is important to assess LIME explanations.
 We suggest the use of visual diagnostics for assessment.
@@
 
-All runs of LIME in this paper are executed in a forked version\footnote{https://github.com/goodekat/lime} of the R package \emph{lime} (version 0.5.1) by \citet{pedersen:2020}.
+All runs of LIME in this paper are executed in a forked version (https://github.com/goodekat/lime) of the R package \emph{lime} (version 0.5.1) by \citet{pedersen:2020}.
 The forked version is functionally indistinguishable from \citeauthor{pedersen:2020}'s implementation but allows us to export internal values relevant for an assessment of the explainer.

### 2020-12-08 paper.Rnw
renumbered figures to match sec 1

@@
 The distances are subtracted from 1 to obtain a proximity.
-For the scenario on the right, the computation is the same except the distances are raised to a power of \Sexpr{bad_gower_power} (the default exponent in the \emph{lime} R package \citep{pedersen:2020}).
-This causes the observations that are further away from the prediction of interest to be given larger weights than the scenario on the left.}
-
-In \kge{the left scenario}\sout{\autoref{fig:figure-01}}, the explainer model \kge{is faithful to the complex model since it} captures the \kge{linear} relationship between the black-box predictions in an immediate neighborhood of the prediction of interest.
-\kge{The slope of \Sexpr{coefs_data %>% filter(case == good_power_label) %>% pull(b1) %>% round(3)} explains that the black-box predictions increase as the feature increases in the local region around the prediction of interest}.
-\kge{The explainer model on the right does not capture the linear trend near the prediction of interest, but instead, the explainer captures a more global trend.
+Here, the explainer model is faithful to the complex model since it captures the linear relationship between the black-box predictions in an immediate neighborhood of the prediction of interest.
+The slope of \Sexpr{coefs_data %>% filter(case == good_power_label) %>% pull(b1) %>% round(3)} explains that the black-box predictions increase as the feature increases in the local region around the prediction of interest.}
+
+\kge{For the scenario on the right, the computation of the proximities is the same except the distances are raised to a power of \Sexpr{bad_gower_power} (the default exponent in the \emph{lime} R package \citep{pedersen:2020}).
+This causes the observations that are further away from the prediction of interest to be given larger weights than the scenario on the left.
+Here, the explainer model does not capture the linear trend near the prediction of interest, but instead, the explainer captures a more global trend.
 Without an assessment of this explainer model, the slope of \Sexpr{coefs_data %>% filter(case == bad_power_label) %>% pull(b1) %>% round(3)} would incorrectly explain that the predictions decrease as the feature increases near the prediction of interest.} %\sout{This cannot be said of the explainer model in \autoref{fig:figure-02}.
@@
 
-\section{Visual Diagnostics for LIME} \label{diagnostics}
-
 <<sine-data, echo = FALSE, include = FALSE>>=
@@
 \centering
-<<figure-03, out.width = '6.5in', fig.width = 8, fig.height = 3.1>>=
+<<figure-02, out.width = '6.5in', fig.width = 8, fig.height = 3.1>>=
 
@@
 The prediction of interest to explain is indicated by a diamond.}
-\label{fig:figure-03}
+\label{fig:figure-02}
 \end{figure*}
+
+\section{Visual Diagnostics for LIME} \label{diagnostics}
 
@@
 
-\autoref{fig:figure-03} shows scatterplots of $x_2$ versus $x_1$ from the training data (left) and the testing data (right).
+\autoref{fig:figure-02} shows scatterplots of $x_2$ versus $x_1$ from the training data (left) and the testing data (right).
 Both plots include the true classification boundary of the rotated sine function plotted as the solid black line.
@@
 The random forest  misclassifies \Sexpr{dim(sine_data_test %>% filter(y != rfpred))[1]} points, which are all located near  the classification boundary.
-These are identified by open circles in \autoref{fig:figure-03}.
+These are identified by open circles in \autoref{fig:figure-02}.
 
@@
 
-For the presentation of the explanation scatterplot, we focus on the misclassified point with $(x_1, x_2, x_3)$ coordinates of (\Sexpr{round(sine_poi$x1, 2)}, \Sexpr{round(sine_poi$x2, 2)}, \Sexpr{round(sine_poi$x3, 2)}) indicated by a diamond in \autoref{fig:figure-03}.
+For the presentation of the explanation scatterplot, we focus on the misclassified point with $(x_1, x_2, x_3)$ coordinates of (\Sexpr{round(sine_poi$x1, 2)}, \Sexpr{round(sine_poi$x2, 2)}, \Sexpr{round(sine_poi$x3, 2)}) indicated by a diamond in \autoref{fig:figure-02}.
 Misclassified points are often of interest to explain since they may provide information about ways to improve the model.
@@
 \begin{figure*}[!thp]
-<<figure-04, out.width = '6.5in', fig.width = 12, fig.height = 5, warning = FALSE>>=
+<<figure-03, out.width = '6.5in', fig.width = 12, fig.height = 5, warning = FALSE>>=
 
@@
 @
-\caption{(left) Visualization from the \emph{lime} R package of a LIME explanation for the \data \ prediction of interest identified in \autoref{fig:figure-03}.
+\caption{(left) Visualization from the \emph{lime} R package of a LIME explanation for the \data \ prediction of interest identified in \autoref{fig:figure-02}.
 (right) \emph{Explanation Scatterplot}.
@@
 This figure shows that the quantile bins are not flexible enough to capture the relationship between the random forest predictions and the $x_1$ and $x_2$ values.}
-\label{fig:figure-04}
+\label{fig:figure-03}
 \end{figure*}
@@
 
-Before introducing the visual diagnostics, let us consider a commonly used visualization of a LIME explanation that is shown in Figure \ref{fig:figure-04} (left).
-The plot is created using the \emph{lime} R package and provides a visual representation of a LIME explanation for the prediction of interest indicated in \autoref{fig:figure-03}.
+Before introducing the visual diagnostics, let us consider a commonly used visualization of a LIME explanation that is shown in Figure \ref{fig:figure-03} (left).
+The plot is created using the \emph{lime} R package and provides a visual representation of a LIME explanation for the prediction of interest indicated in \autoref{fig:figure-02}.
 In particular, the explanation is obtained using 4-quantile-bins to simulate the data.
@@
 
-The explanation for the prediction of interest depicted in Figure \ref{fig:figure-04} is interpreted as follows.
+The explanation for the prediction of interest depicted in Figure \ref{fig:figure-03} is interpreted as follows.
 A random forest classification of blue is supported by the prediction of interest having a value of $x_2$ that is greater than \Sexpr{str_split(sine_poi_lime_default$feature_desc[[1]], pattern = " ")[[1]][1]}, but the prediction of interest having a value of $x_1$ that is greater than \Sexpr{str_split(sine_poi_lime_default$feature_desc[[2]], pattern = " ")[[1]][1]} and less than or equal to \Sexpr{str_split(sine_poi_lime_default$feature_desc[[2]], pattern = " ")[[1]][5]} provides support against a classification of blue.
@@
 
-Based on the plot on the left of \autoref{fig:figure-04} alone, it is not possible to make an informed assessment of the explanation.
+Based on the plot on the left of \autoref{fig:figure-03} alone, it is not possible to make an informed assessment of the explanation.
 For a further assessment of the explainer model, we turn to an \emph{explanation scatterplot}: a visual diagnostic for assessing the LIME claims of locality and fidelity for an individual explanation by juxtaposing the complex and explainer models in one plot.
@@
 
-An explanation scatterplot corresponding to the LIME explanation depicted on the left in \autoref{fig:figure-04} is shown on the right hand side of \autoref{fig:figure-04}.
+An explanation scatterplot corresponding to the LIME explanation depicted on the left in \autoref{fig:figure-03} is shown on the right hand side of \autoref{fig:figure-03}.
 By juxtaposing the random forest predictions and the explainer model boundaries, we are able to assess the faithfulness and localness of the explainer model.
@@
 It is difficult to assess linearity from this explanation scatterplot, but a residual plot of the explainer model could be used to check the linearity claim.
-See Appendix~\ref{residual-plot} for the residual plot associated with the explanation considered in Figure \ref{fig:figure-04}, which shows a violation of the linearity claim.
+See Appendix~\ref{residual-plot} for the residual plot associated with the explanation considered in Figure \ref{fig:figure-03}, which shows a violation of the linearity claim.
 
@@
 \begin{figure}[!thp]
-<<figure-05, out.width = '3.125in', fig.width = 6, fig.height = 3>>=
+<<figure-04, out.width = '3.125in', fig.width = 6, fig.height = 3>>=
 
@@
 Situation 1 is the ideal, because the explanations vary across cases but do not dependent on specific tuning parameter values.}
-\label{fig:figure-05}
+\label{fig:figure-04}
 
@@
 
-<<figure-06, out.width = '3.125in', fig.width = 4, fig.height = 4.5>>=
+<<figure-05, out.width = '3.125in', fig.width = 4, fig.height = 4.5>>=
 
@@
 The vertical striping indicates that the LIME explanations are not consistent across tuning parameter values.}
-\label{fig:figure-06}
+\label{fig:figure-05}
 \end{figure}
@@
 
-Two hypothetical examples of feature heatmaps are included in \autoref{fig:figure-05}.
+Two hypothetical examples of feature heatmaps are included in \autoref{fig:figure-04}.
 The plots are created with the assumption that LIME is applied to select the top feature out of $p=4$  features for $n=10$ cases with $t=5$ sets of tuning parameter values.
@@
 
-\autoref{fig:figure-06} shows a feature heatmap for the LIME applications to the 100 observations in the \data \ test set.
+\autoref{fig:figure-05} shows a feature heatmap for the LIME applications to the 100 observations in the \data \ test set.
 The most important and second most important features selected by lime are shown in in the top and bottom facets, respectively.
@@
 \begin{figure}[!thp]
-<<figure-07, out.width = '3.25in', fig.width = 4.5, fig.height = 3.75, warning = FALSE>>=
+<<figure-06, out.width = '3.25in', fig.width = 4.5, fig.height = 3.75, warning = FALSE>>=
 
@@
 The kernel density simulation methods performs well across all three metrics.}
-\label{fig:figure-07}
+\label{fig:figure-06}
 \end{figure}
@@
 
-\autoref{fig:figure-07} shows an example assessment metric plot.
+\autoref{fig:figure-06} shows an example assessment metric plot.
 The three metrics are computed for each of the LIME applications to the \data \ test set.
@@
 
-Recall that \autoref{fig:figure-06} indicated that the kernel density method selected the same feature across all cases in the test set for both the first and second features.
+Recall that \autoref{fig:figure-05} indicated that the kernel density method selected the same feature across all cases in the test set for both the first and second features.
 It appears that a global trend may be the best explanation for this example, which may be reasonable considering that we know that both $x_1$ and $x_2$ are the two features that should be the features used by the random forest to distinguish between response categories.
@@
 
-In current practice, forensic firearm examiners evaluate whether two bullets are from the same source (fired from the same gun) or from different sources based on microscopic comparison of the striation patterns engraved on bullets during the firing process (see \autoref{fig:figure-08}).
+In current practice, forensic firearm examiners evaluate whether two bullets are from the same source (fired from the same gun) or from different sources based on microscopic comparison of the striation patterns engraved on bullets during the firing process (see \autoref{fig:figure-07}).
 The process is based on a visual and therefore subjective assessment of the evidence.
@@
 In response, \citet{hare:2017} proposed an automated machine learning method for bullet matching to complement a visual inspection by firearm examiners.
-Based on high-resolution topological scans of land engraved areas, \citet{hare:2017} obtain signatures of striations from two bullet lands (\autoref{fig:figure-09}).
+Based on high-resolution topological scans of land engraved areas, \citet{hare:2017} obtain signatures of striations from two bullet lands (\autoref{fig:figure-08}).
 Nine features quantifying the similarity of signatures, such as the cross-correlation function, the distance between signatures, and the number of matching striae, are extracted and used to train a random forest to determine the probability of a comparison resulting from the same source (matching signatures) or from different sources (non-matching signatures).
@@
 \centering
-<<figure-08, out.width = '2.25in', fig.width = 6, fig.height = 3, warning = FALSE>>=
+<<figure-07, out.width = '2.25in', fig.width = 6, fig.height = 3, warning = FALSE>>=
 
 # Convert the bullet figure to eps (if needed)
-if (!file.exists("figure-static/figure-08-1.eps")) {
-  unzip(zipfile = "figure-static/figure-08-1.png.zip", exdir = "figure-static")
-  bullets <- image_read("figure-static/figure-08-1.png")
-  image_write(bullets, path = "figure-static/figure-08-1.eps", format = "eps")
+if (!file.exists("figure-static/figure-07-1.eps")) {
+  unzip(zipfile = "figure-static/figure-07-1.png.zip", exdir = "figure-static")
+  bullets <- image_read("figure-static/figure-07-1.png")
+  image_write(bullets, path = "figure-static/figure-07-1.eps", format = "eps")
 }
@@
 # Load and print the plot
-knitr::include_graphics("figure-static/figure-08-1.eps")
+knitr::include_graphics("figure-static/figure-07-1.eps")
 
@@
 (Bottom) Close up of a land engraved area showing striations (vertical lines).}
-\label{fig:figure-08}
+\label{fig:figure-07}
 
@@
 
-<<figure-09, out.width = '3.125in', fig.width = 6, fig.height = 3.5, warning = FALSE>>=
+<<figure-08, out.width = '3.125in', fig.width = 6, fig.height = 3.5, warning = FALSE>>=
 
@@
 The \citet{hare:2017} random forest is fit using various features that measure the similarity between two such signatures.}
-\label{fig:figure-09}
+\label{fig:figure-08}
 \end{figure}
@@
 \begin{figure*}[!thp]
-<<figure-10, out.width = '6.5in', warning = FALSE>>=
+<<figure-09, out.width = '6.5in', warning = FALSE>>=
 
 # File names for parallel coordinate plot
-pcp_file_name_png = "figure-static/figure-10-1.png"
-pcp_file_name_eps = "figure-static/figure-10-1.eps"
+pcp_file_name_png = "figure-static/figure-09-1.png"
+pcp_file_name_eps = "figure-static/figure-09-1.eps"
 
@@
 There are clear relationships between the feature values and the random forest probabilities.}
-\label{fig:figure-10}
+\label{fig:figure-09}
 \end{figure*}
@@
 
-We consider a global visualization of the relationship between the random forest predictions and the model features with a parallel coordinate plot of the training data (top facet) and testing data (bottom facets)  (\autoref{fig:figure-10}).
+We consider a global visualization of the relationship between the random forest predictions and the model features with a parallel coordinate plot of the training data (top facet) and testing data (bottom facets)  (\autoref{fig:figure-09}).
 In the training data we observe a clear difference in feature values based on whether the corresponding random forest scores are close to 1 or 0.
@@
 
-To get an overview of the LIME explanations from the 36 applications, we consider a feature heatmap (\autoref{fig:figure-11}).
+To get an overview of the LIME explanations from the 36 applications, we consider a feature heatmap (\autoref{fig:figure-10}).
 In addition to facets for simulation method and LIME feature importance, this plot includes a vertical facet for Gower power and a horizontal facet for whether the observation is a known match or non-match.
@@
 \begin{figure*}[!thp]
-<<figure-11, out.width = '6.5in', fig.width = 18, fig.height = 14>>=
+<<figure-10, out.width = '6.5in', fig.width = 18, fig.height = 14>>=
 
@@
 The vertical stripes of features selected indicate a dependence between the LIME explanations and tuning parameter values.}
-\label{fig:figure-11}
+\label{fig:figure-10}
 
@@
 
-<<figure-12, out.width = '6.5in', warning = FALSE, fig.width = 10, fig.height = 4.25>>=
+<<figure-11, out.width = '6.5in', warning = FALSE, fig.width = 10, fig.height = 4.25>>=
 
@@
 There are discrepancies in performance across metrics for a set of tuning parameter values, but based on the overall performance of all three metrics, 4-equal-bins with a Gower power of 0.5 appears to perform the best.}
-\label{fig:figure-12}
+\label{fig:figure-11}
 \end{figure*}
 
-To try to identify a set of LIME tuning parameter values with the most trustworthy set of explanations, an assessment metric plot is considered (\autoref{fig:figure-12}).
+To try to identify a set of LIME tuning parameter values with the most trustworthy set of explanations, an assessment metric plot is considered (\autoref{fig:figure-11}).
 The performance of a set of tuning parameter values often do not agree across metrics.
@@
 To provide a more detailed view of explanations obtained using different tuning parameter values, we take a closer look at explanations for two observations of interest, which will be referred to as case M (a known match) and case NM (a known non-match), using explanation scatterplots.
-Figure~\ref{fig:figure-13} includes the visual representation plots of explanations (from \emph{lime}) and explanation scatterplots for cases M and NM.
+Figure~\ref{fig:figure-12} includes the visual representation plots of explanations (from \emph{lime}) and explanation scatterplots for cases M and NM.
 Plots for 4-equal-bins and 4-quantile-bins are included to depict tuning parameter values with good (4-equal-bins) and mediocre (4-quantile-bins) performance based on the assessment metric plot.
@@
 \begin{figure*}[!thp]
-<<figure-13, out.width = '6.25in', fig.width = 13, fig.height = 17.5, message = FALSE>>=
+<<figure-12, out.width = '6.25in', fig.width = 13, fig.height = 17.5, message = FALSE>>=
 
@@
 The plots provide insights into the LIME explanations and allow for the assessment of the explanation quality.}
-\label{fig:figure-13}
+\label{fig:figure-12}
 \end{figure*}
@@
 Without applying LIME with multiple tuning parameter values to the bullet test data or viewing diagnostic plots of the LIME explanations, it may be very possible to formulate reasons why the LIME explanations make sense.
-However, the sequence of plots in this section (Figures \ref{fig:figure-11}, \ref{fig:figure-12}, and \ref{fig:figure-13}) suggest that we should be cautious to trust any of these LIME explanations.
+However, the sequence of plots in this section (Figures \ref{fig:figure-10}, \ref{fig:figure-11}, and \ref{fig:figure-12}) suggest that we should be cautious to trust any of these LIME explanations.
 It appears that either LIME needs to be further tuned to provide trustworthy and good explanations, or a different approach may provide better insight.
@@
 Even though an explanation will be interpretable as long as the complexity of the explainer model is appropriately chosen, a lack of understanding of the process used to create the explanation could lead to an incorrect interpretation of the explanation.
-For example, the visualization of a LIME explanation available from the \emph{lime} R package \citep{pedersen:2020} (shown in Figures \ref{fig:figure-04} and \ref{fig:figure-13}) is a major simplification of the explainer model, which could lead to under-interpreted or misinterpreted LIME explanation.
-Supplementing \citet{pedersen:2020}'s compact visualization of the explanation with an explanation scatterplot that shows a more detailed visualization of the explainer model promotes a more complete understanding of the explanation (such as Figures~\ref{fig:figure-04} and \ref{fig:figure-13}).
+For example, the visualization of a LIME explanation available from the \emph{lime} R package \citep{pedersen:2020} (shown in Figures \ref{fig:figure-03} and \ref{fig:figure-12}) is a major simplification of the explainer model, which could lead to under-interpreted or misinterpreted LIME explanation.
+Supplementing \citet{pedersen:2020}'s compact visualization of the explanation with an explanation scatterplot that shows a more detailed visualization of the explainer model promotes a more complete understanding of the explanation (such as Figures~\ref{fig:figure-03} and \ref{fig:figure-12}).
 
@@
 The explanation scatterplots allow for a comparison of the explainer model to the complex model.
-The examples in this paper show cases where the explainer model bins do not accurately capture the regions with similar random forest probabilities that contain the prediction of interest and oversimplify the model (Figures \ref{fig:figure-04} and \ref{fig:figure-13}).
+The examples in this paper show cases where the explainer model bins do not accurately capture the regions with similar random forest probabilities that contain the prediction of interest and oversimplify the model (Figures \ref{fig:figure-03} and \ref{fig:figure-12}).
 Using fewer bins would clearly not help improve the faithfulness of the explainer model in these examples, and while an increase in the number of bins would lead to a finer resolution of the random forest classification boundaries, interpretability of the explainer model would quickly be lost.
@@
 In addition to assessing faithfulness by visually comparing the complex and explainer model, we propose a visual comparison of two faithfulness metrics (MSEE and average fidelity).
-The examples of faithfulness metric comparisons in this paper both produced conflicting results (Figures \ref{fig:figure-07} and \ref{fig:figure-12}).
+The examples of faithfulness metric comparisons in this paper both produced conflicting results (Figures \ref{fig:figure-06} and \ref{fig:figure-11}).
 This makes it difficult to decide on a recommendation of a set of tuning parameter values that produce the explanations with the most faithful explainer model.

### 2020-12-08 paper.tex
renumbered figures to match sec 1

@@
 The distances are subtracted from 1 to obtain a proximity.
-For the scenario on the right, the computation is the same except the distances are raised to a power of 1 (the default exponent in the \emph{lime} R package \citep{pedersen:2020}).
-This causes the observations that are further away from the prediction of interest to be given larger weights than the scenario on the left.}
-
-In \kge{the left scenario}\sout{\autoref{fig:figure-01}}, the explainer model \kge{is faithful to the complex model since it} captures the \kge{linear} relationship between the black-box predictions in an immediate neighborhood of the prediction of interest.
-\kge{The slope of 0.634 explains that the black-box predictions increase as the feature increases in the local region around the prediction of interest}.
-\kge{The explainer model on the right does not capture the linear trend near the prediction of interest, but instead, the explainer captures a more global trend.
+Here, the explainer model is faithful to the complex model since it captures the linear relationship between the black-box predictions in an immediate neighborhood of the prediction of interest.
+The slope of 0.634 explains that the black-box predictions increase as the feature increases in the local region around the prediction of interest.}
+
+\kge{For the scenario on the right, the computation of the proximities is the same except the distances are raised to a power of 1 (the default exponent in the \emph{lime} R package \citep{pedersen:2020}).
+This causes the observations that are further away from the prediction of interest to be given larger weights than the scenario on the left.
+Here, the explainer model does not capture the linear trend near the prediction of interest, but instead, the explainer captures a more global trend.
 Without an assessment of this explainer model, the slope of -0.181 would incorrectly explain that the predictions decrease as the feature increases near the prediction of interest.} %\sout{This cannot be said of the explainer model in \autoref{fig:figure-02}.
@@
 
-\section{Visual Diagnostics for LIME} \label{diagnostics}
-
 \begin{figure*}[!thp]
@@
 
-{\centering \includegraphics[width=6.5in]{figure/figure-03-1}
+{\centering \includegraphics[width=6.5in]{figure/figure-02-1}
 
@@
 The random forest  misclassifies 18 points, which are all located near  the classification boundary.
-These are identified by open circles in \autoref{fig:figure-03}.
+These are identified by open circles in \autoref{fig:figure-02}.
 
@@
 
-For the presentation of the explanation scatterplot, we focus on the misclassified point with $(x_1, x_2, x_3)$ coordinates of (1.23, 8.47, -0.99) indicated by a diamond in \autoref{fig:figure-03}.
+For the presentation of the explanation scatterplot, we focus on the misclassified point with $(x_1, x_2, x_3)$ coordinates of (1.23, 8.47, -0.99) indicated by a diamond in \autoref{fig:figure-02}.
 Misclassified points are often of interest to explain since they may provide information about ways to improve the model.
@@
 
-{\centering \includegraphics[width=6.5in]{figure/figure-04-1}
-
-}
-
-\end{knitrout}
-\caption{(left) Visualization from the \emph{lime} R package of a LIME explanation for the \data \ prediction of interest identified in \autoref{fig:figure-03}.
+{\centering \includegraphics[width=6.5in]{figure/figure-03-1}
+
+}
+
+\end{knitrout}
+\caption{(left) Visualization from the \emph{lime} R package of a LIME explanation for the \data \ prediction of interest identified in \autoref{fig:figure-02}.
 (right) \emph{Explanation Scatterplot}.
@@
 
-The explanation for the prediction of interest depicted in Figure \ref{fig:figure-04} is interpreted as follows.
+The explanation for the prediction of interest depicted in Figure \ref{fig:figure-03} is interpreted as follows.
 A random forest classification of blue is supported by the prediction of interest having a value of $x_2$ that is greater than 4.834, but the prediction of interest having a value of $x_1$ that is greater than -0.302 and less than or equal to 4.844 provides support against a classification of blue.
@@
 
-{\centering \includegraphics[width=3.125in]{figure/figure-05-1}
+{\centering \includegraphics[width=3.125in]{figure/figure-04-1}
 
@@
 
-{\centering \includegraphics[width=3.125in]{figure/figure-06-1}
+{\centering \includegraphics[width=3.125in]{figure/figure-05-1}
 
@@
 
-{\centering \includegraphics[width=3.25in]{figure/figure-07-1}
+{\centering \includegraphics[width=3.25in]{figure/figure-06-1}
 
@@
 
-{\centering \includegraphics[width=2.25in]{figure-static/figure-08-1}
+{\centering \includegraphics[width=2.25in]{figure-static/figure-07-1}
 
@@
 
-{\centering \includegraphics[width=3.125in]{figure/figure-09-1}
+{\centering \includegraphics[width=3.125in]{figure/figure-08-1}
 
@@
 
-{\centering \includegraphics[width=6.5in]{figure-static/figure-10-1}
+{\centering \includegraphics[width=6.5in]{figure-static/figure-09-1}
 
@@
 
-{\centering \includegraphics[width=6.5in]{figure/figure-11-1}
+{\centering \includegraphics[width=6.5in]{figure/figure-10-1}
 
@@
 
-{\centering \includegraphics[width=6.5in]{figure/figure-12-1}
+{\centering \includegraphics[width=6.5in]{figure/figure-11-1}
 
@@
 
-{\centering \includegraphics[width=6.25in]{figure/figure-13-1}
+{\centering \includegraphics[width=6.25in]{figure/figure-12-1}
 

### 2020-12-14 paper.Rnw
worked on more trimming

@@
 \begin{figure*}[!thp]
-<<figure-01, out.width = '6.5in', fig.width = 7.95, fig.height = 3, warning = FALSE>>=
+<<figure-01, out.width = '6.5in', fig.width = 7.95, fig.height = 2.75, warning = FALSE>>=
 
@@
 Here, the explainer model is faithful to the complex model since it captures the linear relationship between the black-box predictions in an immediate neighborhood of the prediction of interest.
-The slope of \Sexpr{coefs_data %>% filter(case == good_power_label) %>% pull(b1) %>% round(3)} explains that the black-box predictions increase as the feature increases in the local region around the prediction of interest.}
+The slope \sout{of \Sexpr{coefs_data %>% filter(case == good_power_label) %>% pull(b1) %>% round(3)}} explains that the black-box predictions increase as the feature increases in the local region around the prediction of interest.}
 
@@
 Here, the explainer model does not capture the linear trend near the prediction of interest, but instead, the explainer captures a more global trend.
-Without an assessment of this explainer model, the slope of \Sexpr{coefs_data %>% filter(case == bad_power_label) %>% pull(b1) %>% round(3)} would incorrectly explain that the predictions decrease as the feature increases near the prediction of interest.} %\sout{This cannot be said of the explainer model in \autoref{fig:figure-02}.
+Without an assessment of this explainer model, the slope \sout{of \Sexpr{coefs_data %>% filter(case == bad_power_label) %>% pull(b1) %>% round(3)}} would incorrectly explain that the predictions decrease as the feature increases near the prediction of interest.} %\sout{This cannot be said of the explainer model in \autoref{fig:figure-02}.
 In addition, the magnitude of the slope associated with Feature 2  (\Sexpr{coefs_data %>% filter(case == "bad", feature == "Feature 2") %>% pull(b1) %>% round(3) %>% abs()}) is larger than that of Feature 1 (\Sexpr{coefs_data %>% filter(case == "bad", feature == "Feature 1") %>% pull(b1) %>% round(3) %>% abs()}).
@@
 
-\kge{In this paper, we stress the importance of assessing LIME by introducing several diagnostic plots for LIME and using the plots to highlight key issues with LIME.} \sout{As a result of the various ways LIME can fail, it is important to assess LIME explanations.
+\sout{As a result of the various ways LIME can fail, it is important to assess LIME explanations.
 We suggest the use of visual diagnostics for assessment.
-In this paper,} \kge{To do this,} we lay out the set of claims about LIME made by \citet{ribeiro:2016} and propose three visualizations for the assessment of these claims: (1) \emph{explanation scatterplots}, (2) \emph{feature heatmaps}, (3) \emph{assessment metric plots}.
+In this paper,} \kge{Without an assessment of the LIME explainer model, the user is putting trust in another black-box procedure to explain the complex black-box model.
+In this paper, we stress the importance of assessing the LIME explainer model.} \kge{To do this, w}e lay out the set of claims about LIME made by \citet{ribeiro:2016}, and \kge{we provide a toolkit of visual diagnostics} \sout{propose three visualizations} for the assessment of these claims: (1) \emph{explanation scatterplots}, (2) \emph{feature heatmaps}, (3) \emph{assessment metric plots}.
+\kge{With the help of these visual diagnostics, we demonstrate examples where LIME does not meet the claims and produces poor or less than optimal explanations.}
+
 While LIME is implemented for image, tabular, and text data, we only focus on tabular data.
@@
 
-\citet{ribeiro:2016} provide an implementation of LIME in a Python package \cite{ribeiro:2020}.
-An adaption of the Python package in R has been implemented and made available by Thomas Lin-Pedersen \citep{pedersen:2020}.
-The discussion of parameter choices and implementation details of LIME in this paper are based on the R package.
+\kgc{I ended up moving some of the paragraphs in this section around and adding a little bit of additional text. I think this organization flows more smoothly. What do you think?}
 
@@
 
-During the application of LIME, the user is asked to select various tuning parameter options: the number of features to return in the explanation, the simulation method, the feature selection method, and how the weights are computed.
-An overview of the options available for the tuning parameters is included in Appendix~\ref{lime-details}.
+\citet{ribeiro:2016} provide an implementation of LIME in a Python package \cite{ribeiro:2020}.
+An adaption of the Python package in R has been implemented and made available by Thomas Lin-Pedersen \citep{pedersen:2020}.
+\kge{In both implementations, a ridge regression model is used as the explainer model, and} \sout{During the application of LIME, t} the user is asked to select various tuning parameter options: the number of features to return in the explanation, the simulation method, the feature selection method, and how the weights are computed.
+The discussion of parameter choices and implementation details of LIME in this paper are based on the R package.
+\kge{See Appendix~\ref{lime-details} for}
+an overview of the options available for the tuning parameters\sout{ is included in Appendix~\ref{lime-details}}.
 
@@
 \end{itemize}
-
-The assumption of interpretability only depends on the complexity of the model used as explainer model.
-If the model is too complex to provide meaningful explanations (e.g.
-there are too many variables in the model), it is clear that the assumption of interpretability is violated.
-The other three assumptions are not as easy to assess, and for those, we suggest the use of diagnostic plots.
 
@@
 @
-\caption{Plots of $x_2$ versus $x_1$ from the training (left) and testing (right) sets of the \data \ introduced in Section \ref{diagnostics}.
-The true classification boundary is shown as the solid black line in both plots.
-The color of the training data  represents the value of the observed response variable ($y$).
-The color of the testing data  represents the random forest probability that an observation belongs to the category of blue.
-The \Sexpr{dim(sine_data_test %>% filter(y != rfpred))[1]} cases that are misclassified by the random forest are identified by black circles.
-The prediction of interest to explain is indicated by a diamond.}
+\caption{Plots of $x_2$ versus $x_1$ from the \kge{\data \ } training (left) and testing (right) sets\sout{ of the \data \ } introduced in Section \ref{diagnostics} \sout{.
+T} \kge{with t}he true classification boundary \sout{is} shown as a solid black line\sout{ in both plots}.
+\sout{The color of the training data represents the value of the observed response variable ($y$).
+The color of the testing data represents the random forest probability that an observation belongs to the category of blue.} \kge{In the testing set, the open black circles identify cases misclassified by the random forest, and the diamond indicates a prediction of interest.} \sout{The \Sexpr{dim(sine_data_test %>% filter(y != rfpred))[1]} cases that are misclassified by the random forest are identified by black circles.} \sout{The prediction of interest \kge{in the test data} \sout{to explain} is indicated by a diamond.}}
 \label{fig:figure-02}
 \end{figure*}
+
+The assumption of interpretability only depends on the complexity of the model used as explainer model.
+If the model is too complex to provide meaningful explanations (e.g.
+there are too many variables in the model), it is clear that the assumption of interpretability is violated.
+The other three assumptions are not as easy to assess, and for those, we suggest the use of diagnostic plots.
 
@@
 
-In this section, we introduce three visual diagnostic plots for the assessment of LIME.
+In this section, we introduce three visual diagnostic plots \sout{for the assessment of LIME.
 The plots focus on different levels of application of LIME (e.g.
-on explanation versus a set of explanations) to assess the LIME claims from different perspectives:
+on explanation versus a set of explanations) to} \kge{that} assess the LIME claims from different perspectives:
 
@@
 To demonstrate the visual diagnostics, we generate an example dataset that will be referred to as the \data.
-The \data \ contains \Sexpr{dim(sine_data)[1]} observations with three features and one response variable.
-The features, $x_1$, $x_2$, and $x_3$, are randomly sampled from Unif(\Sexpr{min}, \Sexpr{max}), Unif(\Sexpr{min}, \Sexpr{max}), and $\mbox{N}(0,1)$ distributions, respectively.
-A binary response variable $y$ is  created using a rotated sine curve.
-In particular, let $x'_1=x_1\cos(\theta)-x_2\sin(\theta)$ and $x'_2=x_1\sin(\theta)+x_2\cos(\theta)$ where $\theta=-0.9$.
-Then $y$ is defined as
+The \data \ contains \Sexpr{dim(sine_data)[1]} observations with \sout{three features and one response variable.
+The} features\sout{,} \kge{of} $x_1$, $x_2$, and $x_3$\sout{,} \kge{that} are randomly sampled from Unif(\Sexpr{min}, \Sexpr{max}), Unif(\Sexpr{min}, \Sexpr{max}), and $\mbox{N}(0,1)$ distributions, respectively.
+A binary response variable $y$ is created using a \sout{rotated} sine curve \sout{.
+In particular, let} \kge{such that}
 \begin{eqnarray}\label{eq:data}
@@
   \mbox{blue} & \mbox{ if } x'_2 > \sin\left(x'_1\right) \\
-  \mbox{red} & \mbox{ if } x'_2 \le \sin\left(x'_1\right) \ . %\nolabel
+  \mbox{red} & \mbox{ if } x'_2 \le \sin\left(x'_1\right) \ .
   \end{cases}
 \end{eqnarray}
+where $x'_1=x_1\cos(\theta)-x_2\sin(\theta)$\kge{,} \sout{and} $x'_2=x_1\sin(\theta)+x_2\cos(\theta)$\kge{, and} \sout{where} $\theta=-0.9$. \sout{Then $y$ is defined as
+\begin{eqnarray}\label{eq:data}
+  y=\begin{cases}
+  \mbox{blue} & \mbox{ if } x'_2 > \sin\left(x'_1\right) \\
+  \mbox{red} & \mbox{ if } x'_2 \le \sin\left(x'_1\right) \ .
+  \end{cases}
+\end{eqnarray}}
 Note that due to the creation of $y$ in this manner, $y$ is dependent on $x_1$ and $x_2$ and independent of $x_3$.
-The dataset is divided into training and testing sets of \Sexpr{dim(sine_data_train)[1]} and \Sexpr{dim(sine_data_test)[1]} observations, respectively.
-A random forest  is fit using the R package \emph{randomForest} (version \Sexpr{packageVersion("randomForest")}) \citep{liaw:2002} with the default settings.
-The model is applied to the test set to obtain predictions.
+The dataset is \kge{randomly} divided into training and testing sets of \Sexpr{dim(sine_data_train)[1]} and \Sexpr{dim(sine_data_test)[1]} observations, respectively.
+A random forest is fit using the R package \emph{randomForest} (version \Sexpr{packageVersion("randomForest")}) \citep{liaw:2002} with the default settings\sout{.
+The model} \kge{and} is applied to the test set to obtain predictions.
 
 \autoref{fig:figure-02} shows scatterplots of $x_2$ versus $x_1$ from the training data (left) and the testing data (right).
-Both plots include the true classification boundary of the rotated sine function plotted as the solid black line.
+Both plots include the true classification boundary \sout{of the rotated sine function plotted} as the solid black line.
 The training data are colored by the observed response variable ($y$), and the testing data are colored by random forest prediction probabilities.
-The random forest  misclassifies \Sexpr{dim(sine_data_test %>% filter(y != rfpred))[1]} points, which are all located near  the classification boundary.
-These are identified by open circles in \autoref{fig:figure-02}.
-
-From these scatterplots, we also see that the global relationship between response $y$ and features $x_1$ and $x_2$ is linear: the probability for label blue increases with the difference between features $x_2$ and $x_1$.
+The random forest  misclassifies \Sexpr{dim(sine_data_test %>% filter(y != rfpred))[1]} points, which are all located near the classification boundary \sout{.
+These are} \kge{and} identified by open circles\sout{ in \autoref{fig:figure-02}}.
+
+From these scatterplots, we \sout{also} see that the global relationship between response $y$ and features $x_1$ and $x_2$ is linear: the probability for label blue increases with the difference between features $x_2$ and $x_1$.
 Locally, the relationship between $y$ and features $x_2$ and $x_1$ varies a lot more around the line of identity.
-Here, the relationship is determined by the sine waves.
-However, the sine is a good-natured function that can be approximated well linearly in local regions.
-
-We apply LIME using six sets of tuning parameter values to all observations in the \data \ test set to observe variability across tuning parameter values.
-A quantile bin based simulation method (samples are simulated uniformly from a specified number of quantile bins) is used for five of the LIME applications with the number of bins varying from 2 to 6 by application.
+Here, the relationship is determined by the sine wave.
+However, the sine is a good-natured function that can be approximated well linearly in local regions \kge{as shown in Figure \ref{fig:figure-01}}.
+
+We apply LIME using six sets of tuning parameter values to all observations in the \data \ test set to observe \kge{explanation} variability\sout{ across tuning parameter values}.
+\kge{Five of the LIME applications use a} \sout{A} quantile bin based simulation method (samples are simulated uniformly from a \kge{feature using a} specified number of quantile bins) \sout{is used for five of the LIME applications} with the number of bins varying from 2 to 6 by application.
 We use 6 bins as the maximum, because the complexity of the explanations increases with the number of bins.
-Note that 4-quantile-bins are the default method in \emph{lime}.
+Note that 4-quantile-bins \kge{is} \sout{are} the default method in \emph{lime}.
 The sixth application of LIME uses a kernel density simulation method (samples are drawn from kernel density approximations of the feature distributions).
@@
 Misclassified points are often of interest to explain since they may provide information about ways to improve the model.
-For the introduction of the other two  plots, we consider the LIME explanations for  all observations in the \data \ test data.
+For the introduction of the other two  plots, we consider the LIME explanations for  all observations in the \data \ test set.
 
@@
 
-Before introducing the visual diagnostics, let us consider a commonly used visualization of a LIME explanation that is shown in Figure \ref{fig:figure-03} (left).
-The plot is created using the \emph{lime} R package and provides a visual representation of a LIME explanation for the prediction of interest indicated in \autoref{fig:figure-02}.
-In particular, the explanation is obtained using 4-quantile-bins to simulate the data.
-In this scenario, LIME converts continuous predictor variables to indicator variables identifying whether the variable value falls in the same quantile bin as the prediction of interest or not.
+Before introducing the visual diagnostics, let us consider a commonly used visualization of a LIME explanation\sout{ that is shown in Figure \ref{fig:figure-03} (left)}.
+\kge{Figure \ref{fig:figure-03} (left) shows the explanation for the prediction of interested indicated in \autoref{fig:figure-02} obtained using 4-quantile-bins.} \sout{The plot is created using the \emph{lime} R package and provides a visual representation of a LIME explanation for the prediction of interest indicated in \autoref{fig:figure-02}.
+In particular, the explanation is obtained using 4-quantile-bins to simulate the data.} In this scenario, LIME converts continuous predictor variables to indicator variables identifying whether the variable value falls in the same quantile bin as the prediction of interest or not.
 The indicator variables are used as the explainer model features.

### 2020-12-14 paper.tex
worked on more trimming

@@
 Here, the explainer model is faithful to the complex model since it captures the linear relationship between the black-box predictions in an immediate neighborhood of the prediction of interest.
-The slope of 0.634 explains that the black-box predictions increase as the feature increases in the local region around the prediction of interest.}
+The slope \sout{of 0.634} explains that the black-box predictions increase as the feature increases in the local region around the prediction of interest.}
 
@@
 Here, the explainer model does not capture the linear trend near the prediction of interest, but instead, the explainer captures a more global trend.
-Without an assessment of this explainer model, the slope of -0.181 would incorrectly explain that the predictions decrease as the feature increases near the prediction of interest.} %\sout{This cannot be said of the explainer model in \autoref{fig:figure-02}.
+Without an assessment of this explainer model, the slope \sout{of -0.181} would incorrectly explain that the predictions decrease as the feature increases near the prediction of interest.} %\sout{This cannot be said of the explainer model in \autoref{fig:figure-02}.
 In addition, the magnitude of the slope associated with Feature 2  () is larger than that of Feature 1 ().
@@
 
+\begin{figure*}[!thp]
+\centering
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+
+{\centering \includegraphics[width=6.5in]{figure/figure-02-1}
+
+}
+
+\end{knitrout}
+\caption{Plots of $x_2$ versus $x_1$ from the \kge{\data \ } training (left) and testing (right) sets\sout{ of the \data \ } introduced in Section \ref{diagnostics} \sout{.
+T} \kge{with t}he true classification boundary \sout{is} shown as a solid black line\sout{ in both plots}.
+\sout{The color of the training data represents the value of the observed response variable ($y$).
+The color of the testing data represents the random forest probability that an observation belongs to the category of blue.} \kge{In the testing set, the open black circles identify cases misclassified by the random forest, and the diamond indicates a prediction of interest.} \sout{The 18 cases that are misclassified by the random forest are identified by black circles.} \sout{The prediction of interest \kge{in the test data} \sout{to explain} is indicated by a diamond.}}
+\label{fig:figure-02}
+\end{figure*}
+
 The assumption of interpretability only depends on the complexity of the model used as explainer model.
@@
 
-\begin{figure*}[!thp]
-\centering
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-
-{\centering \includegraphics[width=6.5in]{figure/figure-02-1}
-
-}
-
-\end{knitrout}
-\caption{Plots of $x_2$ versus $x_1$ from the training (left) and testing (right) sets of the \data \ introduced in Section \ref{diagnostics}.
-The true classification boundary is shown as the solid black line in both plots.
-The color of the training data  represents the value of the observed response variable ($y$).
-The color of the testing data  represents the random forest probability that an observation belongs to the category of blue.
-The 18 cases that are misclassified by the random forest are identified by black circles.
-The prediction of interest to explain is indicated by a diamond.}
-\label{fig:figure-02}
-\end{figure*}
-
 \section{Visual Diagnostics for LIME} \label{diagnostics}
 
-In this section, we introduce three visual diagnostic plots for the assessment of LIME.
+In this section, we introduce three visual diagnostic plots \sout{for the assessment of LIME.
 The plots focus on different levels of application of LIME (e.g.
-on explanation versus a set of explanations) to assess the LIME claims from different perspectives:
+on explanation versus a set of explanations) to} \kge{that} assess the LIME claims from different perspectives:
 
@@
 To demonstrate the visual diagnostics, we generate an example dataset that will be referred to as the \data.
-The \data \ contains 600 observations with three features and one response variable.
-The features, $x_1$, $x_2$, and $x_3$, are randomly sampled from Unif(-10, 10), Unif(-10, 10), and $\mbox{N}(0,1)$ distributions, respectively.
-A binary response variable $y$ is  created using a rotated sine curve.
-In particular, let $x'_1=x_1\cos(\theta)-x_2\sin(\theta)$ and $x'_2=x_1\sin(\theta)+x_2\cos(\theta)$ where $\theta=-0.9$.
-Then $y$ is defined as
+The \data \ contains 600 observations with \sout{three features and one response variable.
+The} features\sout{,} \kge{of} $x_1$, $x_2$, and $x_3$\sout{,} \kge{that} are randomly sampled from Unif(-10, 10), Unif(-10, 10), and $\mbox{N}(0,1)$ distributions, respectively.
+A binary response variable $y$ is created using a \sout{rotated} sine curve \sout{.
+In particular, let} \kge{such that}
 \begin{eqnarray}\label{eq:data}
@@
   \mbox{blue} & \mbox{ if } x'_2 > \sin\left(x'_1\right) \\
-  \mbox{red} & \mbox{ if } x'_2 \le \sin\left(x'_1\right) \ . %\nolabel
+  \mbox{red} & \mbox{ if } x'_2 \le \sin\left(x'_1\right) \ .
   \end{cases}
 \end{eqnarray}
+where $x'_1=x_1\cos(\theta)-x_2\sin(\theta)$\kge{,} \sout{and} $x'_2=x_1\sin(\theta)+x_2\cos(\theta)$\kge{, and} \sout{where} $\theta=-0.9$. \sout{Then $y$ is defined as
+\begin{eqnarray}\label{eq:data}
+  y=\begin{cases}
+  \mbox{blue} & \mbox{ if } x'_2 > \sin\left(x'_1\right) \\
+  \mbox{red} & \mbox{ if } x'_2 \le \sin\left(x'_1\right) \ .
+  \end{cases}
+\end{eqnarray}}
 Note that due to the creation of $y$ in this manner, $y$ is dependent on $x_1$ and $x_2$ and independent of $x_3$.
-The dataset is divided into training and testing sets of 500 and 100 observations, respectively.
-A random forest  is fit using the R package \emph{randomForest} (version 4.6.14) \citep{liaw:2002} with the default settings.
-The model is applied to the test set to obtain predictions.
+The dataset is \kge{randomly} divided into training and testing sets of 500 and 100 observations, respectively.
+A random forest is fit using the R package \emph{randomForest} (version 4.6.14) \citep{liaw:2002} with the default settings\sout{.
+The model} \kge{and} is applied to the test set to obtain predictions.
 
 \autoref{fig:figure-02} shows scatterplots of $x_2$ versus $x_1$ from the training data (left) and the testing data (right).
-Both plots include the true classification boundary of the rotated sine function plotted as the solid black line.
+Both plots include the true classification boundary \sout{of the rotated sine function plotted} as the solid black line.
 The training data are colored by the observed response variable ($y$), and the testing data are colored by random forest prediction probabilities.
-The random forest  misclassifies 18 points, which are all located near  the classification boundary.
-These are identified by open circles in \autoref{fig:figure-02}.
-
-From these scatterplots, we also see that the global relationship between response $y$ and features $x_1$ and $x_2$ is linear: the probability for label blue increases with the difference between features $x_2$ and $x_1$.
+The random forest  misclassifies 18 points, which are all located near the classification boundary \sout{.
+These are} \kge{and} identified by open circles\sout{ in \autoref{fig:figure-02}}.
+
+From these scatterplots, we \sout{also} see that the global relationship between response $y$ and features $x_1$ and $x_2$ is linear: the probability for label blue increases with the difference between features $x_2$ and $x_1$.
 Locally, the relationship between $y$ and features $x_2$ and $x_1$ varies a lot more around the line of identity.
-Here, the relationship is determined by the sine waves.
-However, the sine is a good-natured function that can be approximated well linearly in local regions.
-
-We apply LIME using six sets of tuning parameter values to all observations in the \data \ test set to observe variability across tuning parameter values.
-A quantile bin based simulation method (samples are simulated uniformly from a specified number of quantile bins) is used for five of the LIME applications with the number of bins varying from 2 to 6 by application.
+Here, the relationship is determined by the sine wave.
+However, the sine is a good-natured function that can be approximated well linearly in local regions \kge{as shown in Figure \ref{fig:figure-01}}.
+
+We apply LIME using six sets of tuning parameter values to all observations in the \data \ test set to observe \kge{explanation} variability\sout{ across tuning parameter values}.
+\kge{Five of the LIME applications use a} \sout{A} quantile bin based simulation method (samples are simulated uniformly from a \kge{feature using a} specified number of quantile bins) \sout{is used for five of the LIME applications} with the number of bins varying from 2 to 6 by application.
 We use 6 bins as the maximum, because the complexity of the explanations increases with the number of bins.
-Note that 4-quantile-bins are the default method in \emph{lime}.
+Note that 4-quantile-bins \kge{is} \sout{are} the default method in \emph{lime}.
 The sixth application of LIME uses a kernel density simulation method (samples are drawn from kernel density approximations of the feature distributions).
@@
 
-The explanation for the prediction of interest depicted in Figure \ref{fig:figure-03} is interpreted as follows.
+\kgc{I've come to the conclusion that I like the numbers included here with the interpretation, but I tried to get rid of numbers else where.} The explanation for the prediction of interest depicted in Figure \ref{fig:figure-03} is interpreted as follows.
 A random forest classification of blue is supported by the prediction of interest having a value of $x_2$ that is greater than 4.834, but the prediction of interest having a value of $x_1$ that is greater than -0.302 and less than or equal to 4.844 provides support against a classification of blue.

### 2020-12-15 paper.Rnw
more trimming

@@
 In this paper, we stress the importance of assessing the LIME explainer model.} \kge{To do this, w}e lay out the set of claims about LIME made by \citet{ribeiro:2016}, and \kge{we provide a toolkit of visual diagnostics} \sout{propose three visualizations} for the assessment of these claims: (1) \emph{explanation scatterplots}, (2) \emph{feature heatmaps}, (3) \emph{assessment metric plots}.
-\kge{With the help of these visual diagnostics, we demonstrate examples where LIME does not meet the claims and produces poor or less than optimal explanations.}
+\kge{Using these visual diagnostics, we demonstrate problematic examples of LIME explanations where the claims about LIME are not met and the explanations are highly dependent on tuning parameter values without a clear way to identify a set of tuning parameter values that produce the "best" explanations.}
 
@@
 # Specify the figure size (for determining font size)
-f3_ow = 6.5
-f3_fw = 8
-f3_fs = fs * (f3_fw / f3_ow)
-f3_ls = 0.5 * (f3_fw / f3_ow)
+f2_ow = 6.5
+f2_fw = 8
+f2_fs = fs * (f2_fw / f2_ow)
+f2_ls = 0.5 * (f2_fw / f2_ow)
 
@@
             color = "black", 
-            size = f3_ls) +
+            size = f2_ls) +
   scale_colour_manual(values = c(sinecolor_blue, sinecolor_red)) +
-  theme_bw(base_family = ff, base_size = f3_fs) +
+  theme_bw(base_family = ff, base_size = f2_fs) +
   theme(aspect.ratio = 1, 
-        plot.title = element_text(size = f3_fs)) +
+        plot.title = element_text(size = f2_fs)) +
   labs(x = TeX("$x_1$"),
@@
             color = "black", 
-            size = f3_ls) +
+            size = f2_ls) +
   scale_color_gradient2(low = sinecolor_red,
@@
   scale_shape_manual(values = 23) +
-  theme_bw(base_family = ff, base_size = f3_fs) +
+  theme_bw(base_family = ff, base_size = f2_fs) +
   theme(aspect.ratio = 1,
-        plot.title = element_text(size = f3_fs)) +
+        plot.title = element_text(size = f2_fs)) +
   labs(x = TeX("$x_1$"),
@@
 
-<<sine-lime-default>>=
+<<sine-lime-default, warning = FALSE>>=
 
@@
 
-@
+# Obtain the simulated data associated with the poi
+sine_poi_perms <- sine_poi_lime_default %>%
+  slice(1) %>%
+  select(perms_raw, perms_pred_complex, perms_numerified, weights) %>%
+  mutate(perms_numerified =
+           map(perms_numerified,
+               .f = function(x) rename(x,
+                                       "x1num" = "x1",
+                                       "x2num" = "x2",
+                                       "x3num" = "x3"))) %>%
+  unnest(cols = c(perms_raw, perms_pred_complex, perms_numerified, weights)) %>%
+  select(-red) %>%
+  rename(rfpred = blue) %>%
+  mutate(case = factor(1:n())) %>%
+  select(case, everything())
+
+@
+
+<<sine-poi-explainer, warning = FALSE>>=
+
+# Determine the lime explanation cutoffs
+sine_poi_bounds <- sine_poi_lime_default %>%
+  select(case, feature, feature_value, feature_desc) %>%
+  separate(feature_desc, c("other", "upper"), sep = " <= ") %>%
+  separate(other, c("lower", "feature2"), sep = " < ") %>%
+  mutate(upper = ifelse(is.na(upper), "Inf", upper)) %>%
+  select(-feature2) %>%
+  mutate_at(.vars = c("lower", "upper"), .funs = as.numeric)
+
+# Extract the coefficients from the explainer
+sine_b0 <- sine_poi_lime_default$model_intercept[1]
+sine_b1 <- sine_poi_lime_default$feature_weight[2]
+sine_b2 <- sine_poi_lime_default$feature_weight[1]
+
+# Extract the bounds of the bins
+x1_lower <- sine_poi_bounds %>% filter(feature == "x1") %>% pull(lower)
+x1_upper <- sine_poi_bounds %>% filter(feature == "x1") %>% pull(upper)
+x2_lower <- sine_poi_bounds %>% filter(feature == "x2") %>% pull(lower)
+x2_upper <- sine_poi_bounds %>% filter(feature == "x2") %>% pull(upper)
+
+# Function for computing the predicted value via the explainer model
+sine_explainer <- function(z1, z2) sine_b0 + sine_b1 * z1 + sine_b2 * z2
+
+@
+
+\begin{figure*}[!thp]
+<<figure-03, out.width = '6.5in', fig.width = 12, fig.height = 5, warning = FALSE>>=
+
+# Specify the figure size (for determining font size)
+f3_ow = 6.5
+f3_fw = 12
+f3_fs = fs * (f3_fw / f3_ow)
+f3_ls = 0.5 * (f3_fw / f3_ow)
+
+# Create the lime R package explanation visualization for the sine data
+sine_poi_exp <- 
+  sine_poi_lime_default %>% 
+  plot_features() + 
+  theme(text = element_text(family = ff, size = f3_fs),
+        strip.text = element_text(size = f3_fs, face = "plain"))
+
+# Create the explanation scatterplot for the lime explanation for the sine data
+exp_scatter <-
+  plot_explain_scatter(
+    sine_poi_lime_default,
+    alpha = 0.4,
+    line_size = f3_ls
+  ) +
+  facet_grid(switch = "both") +
+  labs(
+    x = TeX("x_1"),
+    y = TeX("x_2"),
+    size = "Weight",
+    shape = "",
+    fill = "Random \nForest \nProbability \nfor 'blue'",
+    color = "Random \nForest \nProbability \nfor 'blue'",
+    linetype = "",
+    title = "Explanation Scatterplot"
+  ) +
+  theme_bw(base_family = ff, base_size = f3_fs) +
+  guides(shape = guide_legend(order = 1),
+         size = guide_legend(
+           nrow = 2,
+           byrow = T,
+           override.aes = list(alpha = 1)
+         )) +
+  theme(aspect.ratio = 1,
+        plot.title = element_text(size = f3_fs))
+
+# Join the plots
+plot_grid(sine_poi_exp, exp_scatter)
+
+# Save the figure to use in the GitHub repo readme
+# ggsave(
+#   filename = "figure-readme.png",
+#   plot = plot_grid(sine_poi_exp, exp_scatter),
+#   width = 12,
+#   height = 5
+# )
+
+@
+\caption{(left) Visualization from the \emph{lime} R package of a LIME explanation for the \data \ prediction of interest identified in \autoref{fig:figure-02}.
+(right) \emph{Explanation Scatterplot}.
+\sout{The points represent the simulated data colored by the random forest probabilities and sized by the assigned LIME weights.
+The prediction of interest is shown as the diamond shaped point.
+The explainer model indicator variables associated with $x_1$ and $x_2$ (quantile bins containing the prediction of interest) are depicted by the solid lines.
+The line colors represent the explainer model coefficient signs and indicate whether the feature supports a prediction of `blue' (blue lines) or supports a prediction of `red' (red lines).} \kge{An explanation scatterplot associated with the explanation for the prediction of interest depicted on the left.} \sout{This figure shows that t}\kge{T}he \kge{4} quantile bins are not flexible enough to capture the relationship between the random forest predictions and the $x_1$ and $x_2$ values.}
+\label{fig:figure-03}
+\end{figure*}
 
@@
 The \data \ contains \Sexpr{dim(sine_data)[1]} observations with \sout{three features and one response variable.
-The} features\sout{,} \kge{of} $x_1$, $x_2$, and $x_3$\sout{,} \kge{that} are randomly sampled from Unif(\Sexpr{min}, \Sexpr{max}), Unif(\Sexpr{min}, \Sexpr{max}), and $\mbox{N}(0,1)$ distributions, respectively.
+The} features\sout{,} \kge{of} $x_1$\sout{,} \kge{and} $x_2$ \kge{independently sampled from Unif(\Sexpr{min}, \Sexpr{max}) distributions}\sout{,} and $x_3$\sout{,} \sout{\kge{that} are randomly sampled from Unif(\Sexpr{min}, \Sexpr{max}), Unif(\Sexpr{min}, \Sexpr{max}), and} \kge{sampled from a} $\mbox{N}(0,1)$ distribution\sout{s, respectively}.
 A binary response variable $y$ is created using a \sout{rotated} sine curve \sout{.
@@
 The dataset is \kge{randomly} divided into training and testing sets of \Sexpr{dim(sine_data_train)[1]} and \Sexpr{dim(sine_data_test)[1]} observations, respectively.
-A random forest is fit using the R package \emph{randomForest} (version \Sexpr{packageVersion("randomForest")}) \citep{liaw:2002} with the default settings\sout{.
+A random forest is fit \kge{to the training set} using the R package \emph{randomForest} (version \Sexpr{packageVersion("randomForest")}) \citep{liaw:2002} with the default settings\sout{.
 The model} \kge{and} is applied to the test set to obtain predictions.
@@
 The default methods for feature selection (forward selection) and the computation of the weights (Gower distance raised to an exponent of 1) are used for all applications.
-(See Appendix~\ref{lime-details} for descriptions of the tuning parameters.)
-
-For the presentation of the explanation scatterplot, we focus on the misclassified point with $(x_1, x_2, x_3)$ coordinates of (\Sexpr{round(sine_poi$x1, 2)}, \Sexpr{round(sine_poi$x2, 2)}, \Sexpr{round(sine_poi$x3, 2)}) indicated by a diamond in \autoref{fig:figure-02}.
+See Appendix~\ref{lime-details} for \kge{more detailed} descriptions of the tuning parameters.
+
+For the presentation of the explanation scatterplot, we focus on the misclassified point \sout{with $(x_1, x_2, x_3)$ coordinates of (\Sexpr{round(sine_poi$x1, 2)}, \Sexpr{round(sine_poi$x2, 2)}, \Sexpr{round(sine_poi$x3, 2)})} indicated by a diamond in \autoref{fig:figure-02}.
 Misclassified points are often of interest to explain since they may provide information about ways to improve the model.
@@
 
-<<warning = FALSE>>=
-
-# Obtain the simulated data associated with the poi
-sine_poi_perms <- sine_poi_lime_default %>%
-  slice(1) %>%
-  select(perms_raw, perms_pred_complex, perms_numerified, weights) %>%
-  mutate(perms_numerified =
-           map(perms_numerified,
-               .f = function(x) rename(x,
-                                       "x1num" = "x1",
-                                       "x2num" = "x2",
-                                       "x3num" = "x3"))) %>%
-  unnest(cols = c(perms_raw, perms_pred_complex, perms_numerified, weights)) %>%
-  select(-red) %>%
-  rename(rfpred = blue) %>%
-  mutate(case = factor(1:n())) %>%
-  select(case, everything())
-
-# Determine the bin cuts for the default lime application
-sine_lime_default_bin_cuts <- sine_lime_default %>%
-  select(feature, feature_desc) %>%
-  unique() %>%
-  separate(feature_desc, c("other", "bin_cut"), sep = " <= ") %>%
-  select(-other) %>%
-  na.omit() %>%
-  mutate(bin_cut = as.numeric(bin_cut)) %>%
-  arrange(feature) %>%
-  mutate(case = rep(1:3, 2)) %>%
-  spread(feature, bin_cut)
-
-@
-
-<<sine-poi-explainer, warning = FALSE>>=
-
-# Determine the lime explanation cutoffs
-sine_poi_bounds <- sine_poi_lime_default %>%
-  select(case, feature, feature_value, feature_desc) %>%
-  separate(feature_desc, c("other", "upper"), sep = " <= ") %>%
-  separate(other, c("lower", "feature2"), sep = " < ") %>%
-  mutate(upper = ifelse(is.na(upper), "Inf", upper)) %>%
-  select(-feature2) %>%
-  mutate_at(.vars = c("lower", "upper"), .funs = as.numeric)
-
-# Extract the coefficients from the explainer
-sine_b0 <- sine_poi_lime_default$model_intercept[1]
-sine_b1 <- sine_poi_lime_default$feature_weight[2]
-sine_b2 <- sine_poi_lime_default$feature_weight[1]
-
-# Extract the bounds of the bins
-x1_lower <- sine_poi_bounds %>% filter(feature == "x1") %>% pull(lower)
-x1_upper <- sine_poi_bounds %>% filter(feature == "x1") %>% pull(upper)
-x2_lower <- sine_poi_bounds %>% filter(feature == "x2") %>% pull(lower)
-x2_upper <- sine_poi_bounds %>% filter(feature == "x2") %>% pull(upper)
-
-# Function for computing the predicted value via the explainer model
-sine_explainer <- function(z1, z2) sine_b0 + sine_b1 * z1 + sine_b2 * z2
-
-@
-
-\begin{figure*}[!thp]
-<<figure-03, out.width = '6.5in', fig.width = 12, fig.height = 5, warning = FALSE>>=
-
-# Specify the figure size (for determining font size)
-f4_ow = 6.5
-f4_fw = 12
-f4_fs = fs * (f4_fw / f4_ow)
-f4_ls = 0.5 * (f4_fw / f4_ow)
-
-# Create the lime R package explanation visualization for the sine data
-sine_poi_exp <- 
-  sine_poi_lime_default %>% 
-  plot_features() + 
-  theme(text = element_text(family = ff, size = f4_fs),
-        strip.text = element_text(size = f4_fs, face = "plain"))
-
-# Create the explanation scatterplot for the lime explanation for the sine data
-exp_scatter <-
-  plot_explain_scatter(
-    sine_poi_lime_default,
-    alpha = 0.4,
-    line_size = f4_ls
-  ) +
-  facet_grid(switch = "both") +
-  labs(
-    x = TeX("x_1"),
-    y = TeX("x_2"),
-    size = "Weight",
-    shape = "",
-    fill = "Random \nForest \nProbability \nfor 'blue'",
-    color = "Random \nForest \nProbability \nfor 'blue'",
-    linetype = "",
-    title = "Explanation Scatterplot"
-  ) +
-  theme_bw(base_family = ff, base_size = f4_fs) +
-  guides(shape = guide_legend(order = 1),
-         size = guide_legend(
-           nrow = 2,
-           byrow = T,
-           override.aes = list(alpha = 1)
-         )) +
-  theme(aspect.ratio = 1,
-        plot.title = element_text(size = f4_fs))
-
-# Join the plots
-plot_grid(sine_poi_exp, exp_scatter)
-
-# Save the figure to use in the GitHub repo readme
-# ggsave(
-#   filename = "figure-readme.png",
-#   plot = plot_grid(sine_poi_exp, exp_scatter),
-#   width = 12,
-#   height = 5
-# )
-
-@
-\caption{(left) Visualization from the \emph{lime} R package of a LIME explanation for the \data \ prediction of interest identified in \autoref{fig:figure-02}.
-(right) \emph{Explanation Scatterplot}.
-The points represent the simulated data colored by the random forest probabilities and sized by the assigned LIME weights.
-The prediction of interest is shown as the diamond shaped point.
-The explainer model indicator variables associated with $x_1$ and $x_2$ (quantile bins containing the prediction of interest) are depicted by the solid lines.
-The line colors represent the explainer model coefficient signs and indicate whether the feature supports a prediction of `blue' (blue lines) or supports a prediction of `red' (red lines).
-This figure shows that the quantile bins are not flexible enough to capture the relationship between the random forest predictions and the $x_1$ and $x_2$ values.}
-\label{fig:figure-03}
-\end{figure*}
-
 \paragraph{A Visual Representation of a LIME Explanation}
@@
 Before introducing the visual diagnostics, let us consider a commonly used visualization of a LIME explanation\sout{ that is shown in Figure \ref{fig:figure-03} (left)}.
-\kge{Figure \ref{fig:figure-03} (left) shows the explanation for the prediction of interested indicated in \autoref{fig:figure-02} obtained using 4-quantile-bins.} \sout{The plot is created using the \emph{lime} R package and provides a visual representation of a LIME explanation for the prediction of interest indicated in \autoref{fig:figure-02}.
-In particular, the explanation is obtained using 4-quantile-bins to simulate the data.} In this scenario, LIME converts continuous predictor variables to indicator variables identifying whether the variable value falls in the same quantile bin as the prediction of interest or not.
-The indicator variables are used as the explainer model features.
-
-The plot reports \Sexpr{round(sine_poi_lime_default$label_prob[1], 2)} as  the random forest  probability  that the observation of interest belongs to category blue (denoted as the ``label" in the plot).
+\kge{Figure \ref{fig:figure-03} (left) depicts the explanation for the prediction of interest indicated in \autoref{fig:figure-02} obtained using 4-quantile-bins.
+In the text at the top, the "Probability" is the random forest probability of \Sexpr{round(sine_poi_lime_default$label_prob[1], 2)} that the observation of interest belongs to the "Label" category of blue.
+The "Explanation Fit" is the deviance ratio of \Sexpr{round(sine_poi_lime_default$model_r2[1], 2)} associated with the ridge regression explainer model (often interpreted as an $R^2$), which suggests that the explainer model is not a good linear fit.}
+
+\kge{Since 4-quantile-bins are used to simulate data, LIME converts continuous predictor variables to indicator variables identifying whether the variable value falls in the same quantile bin as the prediction of interest or not.
+The indicator variables are used as the features in the ridge regression explainer model.
+The features included in the visualization are the ones selected by feature selection, the lengths of the bars represent the coefficients from the ridge regression associated with the indicator variables, and the color of a bar denotes the sign of the coefficient.
+This explainer model explains that the random forest prediction that the observation of interest belongs to the category of blue is mostly supported by the prediction of interest having a value of $x_2$ that is greater than \Sexpr{str_split(sine_poi_lime_default$feature_desc[[1]], pattern = " ")[[1]][1]} but somewhat contradicted by the prediction of interest having a value of $x_1$ that is greater than \Sexpr{str_split(sine_poi_lime_default$feature_desc[[2]], pattern = " ")[[1]][1]} and less than or equal to \Sexpr{str_split(sine_poi_lime_default$feature_desc[[2]], pattern = " ")[[1]][5]}.} \kgc{I decided to leave the values here, because this is how I would interpret this explanation, but I cut out a lot of text from this subsection in other ways.}
+
+\sout{Before introducing the visual diagnostics, let us consider a commonly used visualization of a LIME explanation\sout{ that is shown in Figure \ref{fig:figure-03} (left)}.
+\kge{Figure \ref{fig:figure-03} (left) shows the explanation for the prediction of interest indicated in \autoref{fig:figure-02} obtained using 4-quantile-bins.} \sout{The plot is created using the \emph{lime} R package and provides a visual representation of a LIME explanation for the prediction of interest indicated in \autoref{fig:figure-02}.
+In particular, the explanation is obtained using 4-quantile-bins to simulate the data.} \kge{When quantile bins are used to simulate data}\sout{ In this scenario}, LIME converts continuous predictor variables to indicator variables identifying whether the variable value falls in the same quantile bin as the prediction of interest or not.
+The\kge{n the} indicator variables are used as the explainer model features.}
+
+\sout{The plot reports \Sexpr{round(sine_poi_lime_default$label_prob[1], 2)} as the random forest  probability that the observation of interest belongs to category blue (denoted as the ``label" in the plot).
 The lengths of the bars represent the coefficients from a ridge regression model (the explainer model) fit using the R package \emph{glmnet} \citep{simon:2011} associated with the indicator variables chosen via feature selection.
@@
 In this case, it is \Sexpr{round(sine_poi_lime_default$model_r2[1], 2)} suggesting that the explainer model is not a good linear fit.
-However, it is commonly accepted that $R^2$ has limitations for assessing the quality of fit of a model \citep{sapra:2014} and  should not be used as the only metric in a model assessment.
-
-The explanation for the prediction of interest depicted in Figure \ref{fig:figure-03} is interpreted as follows.
+However, it is commonly accepted that $R^2$ has limitations for assessing the quality of fit of a model \citep{sapra:2014} and  should not be used as the only metric in a model assessment.}
+
+\sout{The explanation for the prediction of interest depicted in Figure \ref{fig:figure-03} is interpreted as follows.
 A random forest classification of blue is supported by the prediction of interest having a value of $x_2$ that is greater than \Sexpr{str_split(sine_poi_lime_default$feature_desc[[1]], pattern = " ")[[1]][1]}, but the prediction of interest having a value of $x_1$ that is greater than \Sexpr{str_split(sine_poi_lime_default$feature_desc[[2]], pattern = " ")[[1]][1]} and less than or equal to \Sexpr{str_split(sine_poi_lime_default$feature_desc[[2]], pattern = " ")[[1]][5]} provides support against a classification of blue.
@@
 Additionally, consider that since the support for blue by $x_2$ outweighs the support for red by $x_1$, the explainer model overall favors a label of blue for the prediction of interest, which agrees with the random forest probability of \Sexpr{sine_poi_lime_default$label_prob[1]} for blue.
-Note that both models classify the observation incorrectly.
+Note that both models classify the observation incorrectly.}
 
@@
 
-Based on the plot on the left of \autoref{fig:figure-03} alone, it is not possible to make an informed assessment of the explanation.
+\kge{As a first check to determine whether the explanation depicted in \autoref{fig:figure-03} (left) is trustworthy, we note that since the support for blue by $x_2$ outweighs the support for red by $x_1$, the explainer model overall favors a label of blue for the prediction of interest agreeing with the random forest probability.
+In fact, both random forest and explainer model classify the observation incorrectly.
+However, based on the information in \autoref{fig:figure-03} (left) alone, it is not possible to make an informed assessment of the explanation.} \sout{Based on the plot on the left of \autoref{fig:figure-03} alone, it is not possible to make an informed assessment of the explanation.}
+
 For a further assessment of the explainer model, we turn to an \emph{explanation scatterplot}: a visual diagnostic for assessing the LIME claims of locality and fidelity for an individual explanation by juxtaposing the complex and explainer models in one plot.
@@
 We introduce the explanation scatterplot here under the \emph{lime} R package default method of 4-quantile-bins.
+\kge{Appendix \ref{exp-scatter_plus} addresses the explanation scatterplot formats in other LIME simulation scenarios.}
 
@@
 The point size represents the weight assigned by LIME.
-In order to show the LIME results for the observation of interest, lines are drawn on top of the points.
-These lines  represent the boundaries of the indicator variables used to fit the explainer model.
+In order to show the LIME results for the observation of interest, lines are drawn on top of the points\sout{.
+These lines}  represent\kge{ing} the boundaries of the indicator variables used to fit the explainer model.
 The line color  denotes whether LIME indicates that a feature supports or contradicts a class prediction.
-Appendix \ref{exp-scatter_plus} addresses the explanation scatterplot formats in other LIME simulation scenarios.
+\sout{Appendix \ref{exp-scatter_plus} addresses the explanation scatterplot formats in other LIME simulation scenarios.}
 
@@
 These statements validate the explanation produced by LIME.
-However, the explanation scatterplot plot shows that the random forest performs well at capturing the sine curve classification boundary by creating various sized rectangles consisting of predictions with similar probabilities, which the LIME explanation does not pick up on.
+However, the explanation scatterplot plot shows that the random forest performs well at capturing the sine curve classification boundary by creating various sized rectangles consisting of predictions with similar probabilities, which the LIME explanation does not pick up on \kge{since the bins are created without information about the random forest predictions}.
 Thus, LIME does provide an explanation for the prediction, but it is a very poor explanation in terms of faithfulness to the random forest prediction regions.
@@
 
+Explanations produced by LIME are likely to be affected by the choice of tuning parameter values.
+A hypothetical example of this is shown by Figures \ref{fig:figure-01} and \ref{fig:figure-02} where the method used to weight the observations influenced the explanation.
+As of the time of writing this manuscript, we have encountered no recommendations for how to specify the parameter values besides for the default settings in \emph{lime}.
+In order to compare the explanations produced by LIME using different tuning parameter values and provide another perspective for assessing localness, we visualize an overview of the explanations with the \emph{feature heatmap} diagnostic plot.
+
+The feature heatmap uses colors to identify the features selected by LIME across multiple predictions (referred to as cases here) and tuning parameter values organized by the feature importance assigned by LIME.
+That is, for LIME applied with $t$ sets of tuning parameter values to $n$ cases to select the $f$ top features, create $f$ heatmaps (one for each of the positions of importance determined by the magnitude of the explainer model coefficients) with the cases on the $y$-axis, the tuning parameter values on the $x$-axis, and the cells colored by the feature chosen for the corresponding case and tuning parameter value.
+Additional tuning parameters may also be included in the plot via facets.
+
+\kge{When interpreting feature heatmaps, horizontal lines of the same color represent the ideal situation where the explanations are consistent and do not depend on the tuning parameter values but do depend on the location of the observation in the feature space.
+Vertical lines of color represent explanations that are dependent on the tuning parameter values and may not be local since the same feature is chosen regardless of the location of the observation in the feature space.
+See Appendix \ref{feat-heat-ex} for hypothetical examples depicting feature heatmaps with the extreme cases of horizontal and vertical lines.}
+
+\begin{figure}[!tp]
+<<figure-04, out.width = '3.125in', fig.width = 4, fig.height = 4.5>>=
+
+# Specify the figure size (for determining font size)
+f4_ow = 3.125
+f4_fw = 4
+f4_fs = fs * (f4_fw / f4_ow)
+
+# Create the example feature heatmap with the sine data
+plot_feature_heatmap(sine_lime_explain$explain,
+                     order_method = "PCA") +
+  theme_bw(base_family = ff, base_size = f4_fs) +
+  theme(
+    legend.position = "bottom",
+    axis.text.y = element_blank(),
+    axis.ticks.y = element_blank(),
+    strip.background = element_rect(color = "white", fill = "white")
+  ) +
+  labs(y = "Case")
+
+@
+\caption{\emph{Feature Heatmap}.
+An example feature heatmap of the explanations from the applications of LIME with different tuning parameter values to the \data \ test set.
+\sout{The cases from the test set are plotted on the y-axis, and the tuning parameter values (simulation methods here) are included on the x-axis.
+The colors of the tiles indicate the feature selected by LIME for the corresponding case and tuning parameter value.
+The plot is faceted by the first and second most important features selected by LIME (top and bottom facets, respectively).
+The vertical facets separate the kernel density method from the quantile bin methods.} The vertical striping indicates that the LIME explanations are not consistent across tuning parameter values.}
+\label{fig:figure-04}
+\end{figure}
+
+\sout{Two hypothetical examples of feature heatmaps are included in \autoref{fig:figure-04}.
+The plots are created with the assumption that LIME is applied to select the top feature out of $p=4$  features for $n=10$ cases with $t=5$ sets of tuning parameter values.
+Situation 1 is an example where the features selected are consistent across tuning parameter values within a case but vary across cases within a tuning parameter value.
+This is the ideal situation, because the LIME explanations do not depend on the tuning parameters but do depend on the location of the observation in the feature space.
+Situation 2 is an example where the selected features vary across tuning parameter values within a case but are consistent across cases within a tuning parameter value.
+This situation indicates that the features selected by LIME are dependent on the tuning parameters, and the explanations may not be  local, because the same feature is chosen regardless of the case.
+In practice, it is expected that the plot will exhibit a combination of these two situations.}
+
+\autoref{fig:figure-04} shows a feature heatmap for the LIME applications to the 100 observations in the \data \ test set.
+The most important and second most important features selected by lime are shown in in the top and bottom facets, respectively.
+For the quantile bins, the original features prior to \kge{being converted to indicator variables} \sout{the indicator variable transformation} are included since it is obvious that different features would be selected when the sizes of the bins change.
+This figure shows that for kernel density and 2-quantile-bins, LIME \kge{produces global explanations since} \sout{selects} $x_1$ \kge{is selected} as the most important feature and $x_2$ \kge{is selected} as the second most important feature across all cases in the test set.
+\sout{These explanations are not local.} There is variability in the features selected by LIME for 3- to 6-quantile-bins suggesting more local explanations.
+There are signs of vertical striping, which suggests a dependence on tuning parameters.
+Note that the explanations from 3- and 5-quantile-bins include the selection of the random noise variable ($x_3$) as an important variable in many predictions, which \kge{would not be expected to be important to a random forest}\sout{should not be the case}.
+\kge{It is unclear whether the random forest is using a variable that would not be expected to be important or LIME is incorrectly identifying the important variable when 3- and 5- quantile bins are used.} \sout{The pattern seen in the explanations for 3- to 6-quantile-bins may suggest local explanations, but the dependence on tuning parameters makes it unclear which set of explanations to use.}
+
+\subsection{Assessment Metric Plot} \label{assess-metric}
+
+The feature heatmap for the \data \ in the previous section shows an example of inconsistent LIME explanations across tuning parameter values.
+In this situation, the user must determine which set of explanations to trust.
+One way to do this is to compute assessment metrics for each set of explanations to identify the optimal tuning parameter values.
+We discuss three metrics for this purpose and present a visual comparison in an \emph{assessment metric plot}.
+
+Each metric presented below is computed on LIME explanations for a set of predictions obtained using the same tuning parameter values.
+Here we provide a high level description of the metrics.
+Notation and formulas for these metrics are included in Appendix \ref{metric-details}.
+
+\begin{itemize}
+\item \emph{Average $R^2$}: Assess the model fit and linearity claim by computing the average of the explainer model $R^2$ values (deviance ratios from the R package \emph{glmnet}).
+
+\item \emph{Average Fidelity}: Measures the faithfulness of the explainer model to the complex model by comparing their predictions.
+Computed as the average of the explainer model fidelity metrics: a metric presented in \citet{ribeiro:2016} (the weighted distance between explainer and complex model predictions for all observations in the LIME simulated data associated with an individual prediction of interest).
+
+\item \emph{Mean Squared Explanation Error (MSEE)}: Also measures the faithfulness of the explainer model to the complex model by comparing their predictions, but only the prediction of interest is used to compute an average squared deviation between explainer and complex model predictions.
+\end{itemize}
+
+\begin{figure}[!tp]
+<<figure-05, out.width = '3.25in', fig.width = 4.5, fig.height = 3.75, warning = FALSE>>=
+
+# Specify the figure size (for determining font size)
+f5_ow = 3.25
+f5_fw = 4.5
+f5_fs = fs * (f5_fw / f5_ow)
+
+# Create the metric plot
+plot_metrics(sine_lime_explain$explain, rank_legend = "discrete") +
+  theme_bw(base_family = ff, base_size = f5_fs) +
+  theme(
+    strip.background = element_rect(color = "white", fill = "white"),
+    strip.placement = "outside",
+    strip.text.y = element_text(size = f5_fs)
+  )
+
+@
+\caption{\emph{Assessment metric plot}.
+The assessment metrics computed on the applications of LIME to the \data \ test set are included in this example assessment metric plot.
+\sout{Each horizontal facet corresponds to one of three metrics: average $R^2$, average fidelity, or MSEE.
+The LIME tuning parameter values (simulation methods in this example) are plotted on the x-axis, and the metric values are shown on the y-axis.
+The points are colored by rank (within a metric) indicating best to worst (dark to light).} The kernel density simulation methods performs well across all three metrics.}
+\label{fig:figure-05}
+\end{figure}
+
+\autoref{fig:figure-05} shows an example assessment metric plot.
+The three metrics are computed for each of the LIME applications to the \data \ test set.
+The simulation methods are listed on the x-axis.
+The plot is faceted by metric, and the metric values are plotted on the y-axis.
+The colors of the points represent the rank of the simulation methods performance based on a particular metric (darker indicates a better metric value and lighter indicates a worse metric value).
+Higher average $R^2$ values are better, and lower average fidelity and MSEE values are better.
+This example only includes one tuning parameter: the simulation method.
+If more than one tuning parameter is considered, the assessment metric plot is extended by adding additional facets or levels to the x-axis.
+
+All three metrics suggest that the kernel density method performed well, but the metrics disagree for the quantile bins methods.
+Average $R^2$ and average fidelity rank the performance of the number of quantile bins the same (2-quantile-bins perform the best and 6-quantile-bins perform the worst).
+In fact, these two metrics appear to have a mirrored  relationship in this example.
+MSEE provides almost the exact opposite results with  6-quantile-bins performing the best and 2-quantile-bins performing the worst.
+Average fidelity and MSEE are similar metrics, so it is \sout{not} surprising that they would \kge{not} agree in this example\kge{, but it may be becuase} \sout{.
+Another factor might be that} MSEE only takes the prediction of interest into account and not the full simulated dataset.
+The contradiction between metrics makes it difficult to identify which simulation method to trust.
+\kgc{I missed this reading through the manuscript before submission, but at some point the text above was changed to say that the "Average fidelity and MSEE are similar metrics, so it is not surprising that they would agree in this example." It should be as I have it now since they don't agree.}
+
+Recall that \autoref{fig:figure-04} indicated that the kernel density method selected the same feature across all cases in the test set for both the first and second features.
+It appears that a global trend may be the best explanation for this example, which may be reasonable considering that we \kge{would expect that} \sout{know that} both $x_1$ and $x_2$ \kge{would be} \sout{are} the two features that should \sout{be the features} used by the random forest to distinguish between response categories.
+\kge{However, futher exploration of individual explanations using explanation scatterplots may help to identify the tuning parameter values considered here that produce the most trustworthy explanations.}
+
+\section{Application to Bullet Matching Data} \label{application}
+
+In this section, we provide a discussion of the application of the visual diagnostics for LIME explanations to a practical data problem investigating the similarity of marks on fired bullets.
+
+\subsection{Bullet Matching Data}
+
+<<bullet-data>>=
+# Load the bullet matching training and testing data
+bullet_train <- readr::read_csv("data/bullet-train.csv.zip")
+bullet_test <- readr::read_csv("data/bullet-test.csv.zip")
+@
+
+<<bullet-rf>>=
+
+# Extract the features from the original random forest model (rtrees)
+bullet_features <- rownames(bulletxtrctr::rtrees$importance)
+bullet_rf_ntrees <- bulletxtrctr::rtrees$ntree
+bullet_rf_mtry <- bulletxtrctr::rtrees$mtry
+
+# Train a new random forest that mimics the rtrees models 
+# (or load if already trained)
+bullet_rf_file = "./data/bullet-rf.rds"
+if (!file.exists(bullet_rf_file)) {
+  set.seed(20200923) # the day that the updated data was found :)
+  bullet_rf <-
+    randomForest(
+      y = factor(bullet_train$samesource),
+      x = bullet_train %>% select(all_of(bullet_features)),
+      ntree = bullet_rf_ntrees,
+      mtry = bullet_rf_mtry
+    )  
+  saveRDS(object = bullet_rf, file = bullet_rf_file)
+} else {
+  bullet_rf = readRDS(file = bullet_rf_file)
+}
+
+# Add variables to both training and testing data with the random forest probability
+# that the signatures are a match from the model bullet_rf
+bullet_train$rfscore = predict(bullet_rf, bullet_train %>% select(all_of(bullet_features)), type = "prob")[,2]
+bullet_test$rfscore = predict(bullet_rf, bullet_test %>% select(all_of(bullet_features)), type = "prob")[,2]
+
+# Compute OOB model metrics
+bullet_rf_oob_acc = round(sum(predict(bullet_rf) == bullet_train$samesource) / length(bullet_train$samesource), 2)
+bullet_rf_oob_fp = round(bullet_rf$confusion[,3][2], 2)
+bullet_rf_oob_fn = round(bullet_rf$confusion[,3][1], 4)
+
+# Obtain model predictions and confusion matrix from test data
+bullet_test_pred = predict(bullet_rf, bullet_test %>% select(all_of(bullet_features)))
+bullet_test_confus = table(bullet_test_pred, bullet_test$samesource)
+
+# Compute test data model metrics
+bullet_rf_test_acc = round(sum(bullet_test_pred == bullet_test$samesource) / length(bullet_test$samesource), 2)
+bullet_rf_test_fp = round(bullet_test_confus[2,1] / (bullet_test_confus[2,1] + bullet_test_confus[2,2]), 2)
+bullet_rf_test_fn = round(bullet_test_confus[1,2] / (bullet_test_confus[1,1] + bullet_test_confus[1,2]), 4)
+@
+
+<<bullet-feature-importance>>=
+# Order the features based on feature importance
+bullet_features_ordered <-
+  data.frame(
+    feature = rownames(bullet_rf$importance),
+    MeanDecreaseGini = bullet_rf$importance
+  ) %>%
+  arrange(desc(MeanDecreaseGini)) %>%
+  mutate(
+    feature = fct_recode(feature,
+      "Cross Correlation\nFunction" = "ccf",
+      "Consecutively\nMatching Striae" = "cms",
+      "Matches" = "matches",
+      "Mismatches" = "mismatches",
+      "Non-Consecutively\nMatching Striae" = "non_cms",
+      "Rough\nCorrelation" = "rough_cor",
+      "Distance Standard\nDeviation" = "sd_D",
+      "Distance" = "D",
+      "Sum of Peaks" = "sum_peaks"
+    )
+  )
+
+# Create an ordered version of the data
+bullet_features_ordered <-
+  bullet_features_ordered %>%
+  mutate(feature = factor(feature, levels = bullet_features_ordered$feature))
+
+@
+
+In current practice, forensic firearm examiners evaluate whether two bullets are from the same source (fired from the same gun) or from different sources based on microscopic comparison of the striation patterns engraved on bullets during the firing process (see \autoref{fig:figure-06}).
+The process is based on a visual and therefore subjective assessment of the evidence.
+The lack of objective evaluation and the associated absence of established error rates has first been criticized by the National Research Council \cite{nrc:2009} and later by the President's Council of Advisors on Science and Technology \cite{pcast:2016}.
+
+In response, \citet{hare:2017} proposed an automated machine learning method for bullet matching to complement a visual inspection by firearm examiners.
+Based on high-resolution topological scans of land engraved areas, \citet{hare:2017} obtain signatures of striations from two bullet lands (\autoref{fig:figure-07}).
+Nine features quantifying the similarity of signatures, such as the cross-correlation function, the distance between signatures, and the number of matching striae, are extracted and used to train a random forest to determine the probability of a comparison resulting from the same source (matching signatures) or from different sources (non-matching signatures).
+The model in \citet{hare:2017} was trained on a set of scans of bullets from the James Hamby Consecutively Rifled Ruger Barrel Study \citep{hamby:2009}, which included 10,384 land-to-land comparisons \citet{hare:2017}.
+See the supporting information for additional information on the signature similarity features.
+
+\begin{figure}[!t]
+\centering
+<<figure-06, out.width = '2.25in', fig.width = 6, fig.height = 3, warning = FALSE>>=
+
+# Convert the bullet figure to eps (if needed)
+if (!file.exists("figure-static/figure-06-1.eps")) {
+  unzip(zipfile = "figure-static/figure-06-1.png.zip", exdir = "figure-static")
+  bullets <- image_read("figure-static/figure-06-1.png")
+  image_write(bullets, path = "figure-static/figure-06-1.eps", format = "eps")
+}
+
+# Load and print the plot
+knitr::include_graphics("figure-static/figure-06-1.eps")
+
+@
+\caption{(Top left) Traditionally rifled gun barrel.
+The grooves and lands alternate to give bullets a spin during the firing process, which create markings (striations) on a bullet when fired.
+(Top right) Image of a fired bullet.
+The vertical stripes along the lower half of the bullet show groove and land engraved areas.
+The land engraved areas contain the microscopic striations created when the bullet passed through the barrel of the gun.
+(Bottom) Close up of a land engraved area showing striations (vertical lines).}
+\label{fig:figure-06}
+
+\vspace*{\floatsep}
+
+<<figure-07, out.width = '3.125in', fig.width = 6, fig.height = 3.5, warning = FALSE>>=
+
+# Specify the figure size (for determining font size)
+f7_ow = 3.125
+f7_fw = 6
+f7_fs = fs * (f7_fw / f7_ow)
+
+# Load the signatures data
+signatures <- readr::read_csv("data/example-signatures.csv.zip")
+
+# Create plot of the signatures
+signatures %>%
+  ggplot(aes(x = x/1000, y = y)) + 
+  geom_line() +
+  facet_grid(land ~ .) +
+  ylim(c(-4,6)) +
+  theme_bw(base_family = ff, base_size = f7_fs) +
+  theme(strip.background = element_blank()) +
+  ylab("Surface Measurement (in microns)") +
+  xlab("Relative Location (in millimeters)")
+
+@
+\caption{Example bullet signatures.
+The bullet signatures correspond to the same land and therefore have very similar patterns.
+The \citet{hare:2017} random forest is fit using various features that measure the similarity between two such signatures.}
+\label{fig:figure-07}
+\end{figure}
+
+\subsection{Application of LIME to Bullet Matching Data}
+
+\begin{figure*}[!thp]
+<<figure-08, out.width = '6.5in', warning = FALSE>>=
+
+# File names for parallel coordinate plot
+pcp_file_name_png = "figure-static/figure-08-1.png"
+pcp_file_name_eps = "figure-static/figure-08-1.eps"
+
+# Create the parallel coordinate plot (if needed)
+if (!file.exists(pcp_file_name_png) | !file.exists(pcp_file_name_eps)) {
+
+  # Specify the figure size (for determining font size)
+  f8_ow = 6.5
+  f8_fw = 7.5
+  f8_fs = 7 * (f8_fw / f8_ow)
+  f8_ls = 0.5 * (f8_fw / f8_ow)
+
+  # Create the plot
+  bullet_pcp <-
+    bullet_train %>%
+    select(all_of(bullet_features), samesource, rfscore) %>%
+    bind_rows(bullet_test %>%
+                select(all_of(bullet_features), samesource, rfscore),
+              .id = "set") %>%
+    mutate(
+      set = fct_recode(set,
+                       "Training Set" = "1",
+                       "Testing Set" = "2"),
+      samesource = fct_recode(
+        factor(samesource),
+        "Match" = "TRUE",
+        "Non-Match" = "FALSE"
+      )
+    ) %>%
+    rename(
+      "Cross Correlation\nFunction" = "ccf",
+      "Consecutively\nMatching Striae" = "cms",
+      "Matches" = "matches",
+      "Mismatches" = "mismatches",
+      "Non-Consecutively\nMatching Striae" = "non_cms",
+      "Rough\nCorrelation" = "rough_cor",
+      "Distance Standard\nDeviation" = "sd_D",
+      "Distance" = "D",
+      "Sum of Peaks" = "sum_peaks"
+    ) %>%
+    arrange(rfscore) %>%
+    ggplot(aes(color = rfscore)) +
+    geom_pcp(
+      mapping = aes(vars = vars(bullet_features_ordered$feature)),
+      alpha = 0.2,
+      size = f8_ls
+    ) +
+    facet_grid(set ~ samesource) +
+    scale_color_gradient2(low = "grey50",
+                          high = "darkorange",
+                          midpoint = 0.5) +
+    theme_bw(base_family = ff, base_size = f8_fs) +
+    theme(
+      axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
+      strip.placement = "outside",
+      strip.background = element_rect(color = "white",
+                                      fill = "white")
+    ) +
+    labs(x = "Features Ordered by Random Forest Variable Importance \n(highest to lowest from left to right)",
+         y = "Scaled Feature Values",
+         color = "Random \nForest \nProbability")
+
+  # Save the plot
+  ggplot2::ggsave(
+    plot = bullet_pcp,
+    filename = pcp_file_name_png,
+    width = 7.5,
+    height = 3.5,
+    units = "in",
+    dpi = 400
+  )
+
+  # Load the figure and then save as an EPS file
+  bullet_pcp <- image_read(pcp_file_name_png)
+  image_write(bullet_pcp, path = pcp_file_name_eps, format = "eps")
+
+}
+
+# Load and print the plot
+knitr::include_graphics(pcp_file_name_eps)
+
+@
+\caption{Parallel coordinate plots of the \citet{hare:2017} random forest predictions from the training (top facet) and testing (bottom facet) data.
+The observations are separated by known matching (right column) and non-matching (left column) signatures.
+The y-axis shows the standardized feature values, and the x-axis shows the features used to fit the random forest (ordered by random forest impurity based feature importance).
+Each line corresponds to an observation, and the line color represents the associated random forest probability.
+There are clear relationships between the feature values and the random forest probabilities.}
+\label{fig:figure-08}
+\end{figure*}
+
+Since firearm identification is commonly used as evidence for convictions in court cases, it is important to be able to understand and assess a model used to quantify the probability that a bullet is fired from a gun.
+LIME explanations would provide a local explanation for an individual prediction, but just as it is important to assess the model for this high-stakes application, it is also important to assess the LIME explanations.
+We will demonstrate an assessment of LIME explanations using the visual diagnostics introduced in this paper.
+
+A random forest model fit to an expanded dataset of \Sexpr{format(dim(bullet_train)[1], big.mark = ",")} land-to-land comparisons from two sets of bullets in the James Hamby Consecutively Rifled Ruger Barrel Study \citep{hamby:2009} was validated in \citet{vanderplas:2020}.
+Here, we train a random forest model to mimic the model validated in \citet{vanderplas:2020} using the same data, model structure, and features (the nine similarity measures developed in \citet{hare:2017}).
+We apply the trained random forest model to 6 bullets from another set of the Hamby study with \Sexpr{dim(bullet_test)[1]} rows of land comparisons.
+See the supporting information for further descriptions of the data.
+
+The newly trained random forest has an out-of-bag accuracy of \Sexpr{bullet_rf_oob_acc} and out-of-bag false positive and false negative rates of \Sexpr{bullet_rf_oob_fp} and \Sexpr{bullet_rf_oob_fn}, respectively.
+On the test data, the random forest performance decreases with an accuracy of \Sexpr{bullet_rf_test_acc} and false positive and false negative rates of \Sexpr{bullet_rf_test_fp} and \Sexpr{bullet_rf_test_fn}, respectively.
+This is an example where explanations of the model predictions could provide insight to the cause of the decrease in model performance on the test data.
+
+We consider a global visualization of the relationship between the random forest predictions and the model features with a parallel coordinate plot of the training data (top facet) and testing data (bottom facets)  (\autoref{fig:figure-08}).
+In the training data we observe a clear difference in feature values based on whether the corresponding random forest scores are close to 1 or 0.
+High values of rough correlation, cross correlation function, and number of matches are indicative of random forest scores close to 1; similarly, low values of mismatches, distance, and non-consecutively matching striae are also associated with random forest scores close to 1.
+Observations in the test data that are classified incorrectly by the random forest tend to have feature values similar to observations in the training data with similar random forest scores.
+For example, the observations in the test set known to be a match but have a random forest score below 0.5 have relatively low values of rough correlation, cross correlation function, and matches and relatively large values of mismatches, distance, and non-consecutively matching striae compared to observations with a random forest probability close to 1.
+
+LIME is applied to all test set observations using different tuning parameter values: 12 sampling methods (2 to 6 equally spaced bins, 2 to 6 quantile-bins, kernel density estimation, and normal approximation) and 3 Gower exponents (0.5, 1, and 10).
+Thus, a total of $12\times 3=36$ different applications of LIME are performed.
+We specify that each LIME explanation return 3 features, and feature selection is performed using the default option in LIME, which selects the features with the highest weights in a ridge regression model.
+
+<<bullet-lime>>=
+
+# Apply LIME to all but two cases without returning the permutations
+if (!file.exists("data/bullet-lime.rds") | !file.exists("data/bullet-explain.rds")){
+
+  # Apply lime with various input options to the Hamby data
+  bullet_lime_explain_noperms <- apply_lime(
+    train = bullet_train %>%
+      select(all_of(bullet_features)),
+    test = bullet_test %>%
+      select(all_of(bullet_features)),
+    model = bullet_rf,
+    label = as.character(TRUE),
+    n_features = 3,
+    sim_method = c('quantile_bins', 'equal_bins',
+                   'kernel_density', 'normal_approx'),
+    nbins = 2:6,
+    feature_select = "auto",
+    dist_fun = "gower",
+    kernel_width = NULL,
+    gower_pow = c(0.5, 1, 10),
+    return_perms = FALSE,
+    all_fs = FALSE,
+    seed = 20190914)
+
+  # Separate the lime and explain parts of the results
+  bullet_lime_noperms <- bullet_lime_explain_noperms$lime
+  bullet_explain_noperms <- bullet_lime_explain_noperms$explain
+
+  # Save the output objects
+  saveRDS(object = bullet_lime_noperms, file = "data/bullet-lime.rds")
+  saveRDS(object = bullet_explain_noperms, file = "data/bullet-explain.rds")
+
+} else {
+
+  # Load the files
+  bullet_explain_noperms <- readRDS("data/bullet-explain.rds")
+
+}
+
+@
+
+<<bullet-lime-perms>>=
+
+# Specify two cases of interest
+bullet_poi_match <- 
+  bullet_test %>% 
+  filter(land_id1 == "Hamby224-Set11-B1-L5", 
+         land_id2 == "Hamby224-Set11-B2-L2") %>% 
+  pull(case)
+bullet_poi_nonmatch <- bullet_test %>% 
+  filter(land_id1 == "Hamby224-Set1-B2-L5", 
+         land_id2 == "Hamby224-Set1-BUnk-L3") %>% 
+  pull(case)
+
+# Apply LIME to two cases with the permutations returned
+bullet_lime_explain_perms <- apply_lime(
+  train = bullet_train %>% select(all_of(bullet_features)),
+  test = bullet_test %>%
+    filter(case %in% bullet_poi_match) %>%
+    bind_rows(bullet_test %>%
+                filter(case %in% bullet_poi_nonmatch)) %>%
+    select(all_of(bullet_features)),
+  model = bullet_rf,
+  label = as.character(TRUE),
+  n_features = 3,
+  sim_method = c(
+    'quantile_bins',
+    'equal_bins',
+    'kernel_density',
+    'normal_approx'
+  ),
+  nbins = 4,
+  feature_select = "auto",
+  dist_fun = "gower",
+  kernel_width = NULL,
+  gower_pow = 0.5,
+  return_perms = TRUE,
+  all_fs = FALSE,
+  seed = 20190914
+)
+
+# Separate the lime and explain parts of the results
+bullet_lime_perms <- bullet_lime_explain_perms$lime
+bullet_explain_perms <- bullet_lime_explain_perms$explain %>%
+  mutate(case = ifelse(case == 1,
+                       bullet_poi_match,
+                       bullet_poi_nonmatch) %>% as.character())
+
+@
+
+<<bullet-lime-combined>>=
+
+# Determine the application and case number of the poi
+# in the no_perms data
+poi_cases_no_perms <- bullet_explain_noperms %>%
+  filter(case %in% c(bullet_poi_match, bullet_poi_nonmatch),
+         nbins %in% c(4, NA),
+         gower_pow == 0.5) %>%
+  select(case, implementation) %>%
+  unique()
+
+# Join the no perms data (with poi removed) with the
+# perms data (perms removed)
+bullet_explain <- bullet_explain_noperms %>%
+  anti_join(poi_cases_no_perms,
+            by = c("implementation", "case")) %>%
+  bind_rows(
+    bullet_explain_perms %>%
+      mutate(implementation = fct_recode(implementation,
+          "3" = "1",
+          "8" = "2",
+          "31" = "3",
+          "32" = "4"
+        )
+      ) %>%
+      select(
+        -perms_raw,-perms_numerified,
+        -perms_pred_simple,-perms_pred_complex,
+        -weights
+      )
+  )
+
+@
+
+\subsection{LIME Assessment Visualizations} \label{bullet-assess-ex}
+
+To get an overview of the LIME explanations from the 36 applications, we consider a feature heatmap (\autoref{fig:figure-09}).
+In addition to facets for simulation method and LIME feature importance, this plot includes a vertical facet for Gower power and a horizontal facet for whether the observation is a known match or non-match.
+This plot highlights several key features of the LIME explanations from the bullet matching dataset.
+
+First, applications of 2-quantile-bin simulations produce the same explanations for almost all cases and LIME tuning parameter values.
+This suggests that the LIME explanations are global and not local.
+Second, within a simulation method, the features selected by LIME for an observation do not appear to vary by the Gower power.
+However, the LIME explanation for an observation often varies across simulation methods.
+With the equal-bins, there are vertical stripes that suggest a dependence of the LIME explanations on the number of bins.
+The vertical stripes are not as apparent with the quantile bins.
+Lastly, there are clear differences between the LIME explanations produced by the bin based simulation methods for the matches and non-matches.
+This suggests that different features are of importance in the random forest, depending on whether the observation corresponds to match or non-match.
+
+\begin{figure*}[!thp]
+<<figure-09, out.width = '6.5in', fig.width = 18, fig.height = 14>>=
+
+# Specify the figure size (for determining font size)
+f9_ow = 6.5
+f9_fw = 18
+f9_fs = fs * (f9_fw / f9_ow)
+
+# Create a feature heatmap
+plot_feature_heatmap(
+  bullet_explain %>%
+    mutate(
+      label = as.factor(label),
+      feature = fct_recode(
+        feature,
+        "Rough Correlation" = "rough_cor",
+        "Consecutively Matching Striae" = "cms",
+        "Distance" = "D",
+        "Matches" = "matches",
+        "Mismatches" = "mismatches",
+        "Non-Consecutively Matching Striae" = "non_cms",
+        "Cross Correlation Function" = "ccf",
+        "Sum of Peaks" = "sum_peaks",
+        "Distance Standard Deviation" = "sd_D"
+      )
+    ),
+  facet_var = bullet_test %>%
+    mutate(samesource = fct_recode(
+      factor(samesource),
+      "Match" = "TRUE",
+      "Non-Match" = "FALSE"
+    )) %>%
+    pull(samesource),
+  order_method = "PCA"
+) +
+  scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) +
+  scale_color_gretchenalbrecht(palette = "last_rays",
+                               discrete = TRUE,
+                               reverse = TRUE) +
+  theme_bw(base_family = ff, base_size = f9_fs) +
+  theme(
+    axis.text.y = element_blank(),
+    axis.ticks.y = element_blank(),
+    strip.background = element_rect(color = "white", fill = "white"),
+    strip.text.y.right = element_text(angle = 0, size = f9_fs*0.7),
+    strip.text.x = element_text(size = f9_fs*0.7),
+    legend.position = "bottom",
+    axis.text.x = element_text(angle = 45, hjust = 1)
+  ) +
+  guides(fill = guide_legend(nrow = 3)) +
+  labs(y = "Case", color = "Complex Model Feature", fill = "Complex Model Feature")
+
+@
+\caption{Feature heatmap of 36 LIME applications to the bullet comparison data test set.
+In addition to faceting the results by simulation method and LIME feature selection order, facets for the Gower power and whether the observation is a match or non-match are included.
+The vertical stripes of features selected indicate a dependence between the LIME explanations and tuning parameter values.}
+\label{fig:figure-09}
+
+\vspace*{\floatsep}
+
+<<figure-10, out.width = '6.5in', warning = FALSE, fig.width = 10, fig.height = 4.25>>=
+
+# Specify the figure size (for determining font size)
+f10_ow = 6.5
+f10_fw = 10
+f10_fs = fs * (f10_fw / f10_ow)
+f10_ls = 0.5 * (f10_fw / f10_ow)
+
+# Create a metric comparison plot
+plot_metrics(
+  bullet_explain %>%
+    mutate(label = as.factor(label)),
+  add_lines = TRUE,
+  line_alpha = 0.75,
+  line_size = f10_ls
+) +
+  theme_bw(base_family = ff, base_size = f10_fs) +
+  theme(
+    strip.background = element_rect(color = "white", fill = "white"),
+    strip.placement = "outside",
+    strip.text.y = element_text(size = f10_fs)
+  )
+
+@
+\caption{Assessment metric plot for the applications of LIME on the bullet comparison data test set.
+There are discrepancies in performance across metrics for a set of tuning parameter values, but based on the overall performance of all three metrics, 4-equal-bins with a Gower power of 0.5 appears to perform the best.}
+\label{fig:figure-10}
+\end{figure*}
+
+To try to identify a set of LIME tuning parameter values with the most trustworthy set of explanations, an assessment metric plot is considered (\autoref{fig:figure-10}).
+The performance of a set of tuning parameter values often do not agree across metrics.
+For example, both density methods perform well according to average fidelity but poorly according to MSEE.
+All quantile bin methods perform well according to average $R^2$ but poorly based on average fidelity and MSEE.
+However, there is consistency in results across different Gower powers.
+The applications using a power of 0.5 perform the best or as well as the other powers across all simulation methods suggesting that the power that leads to a more global explanation is preferred by LIME.
+It is not apparent which set of tuning parameters is the best.
+Considering all three metrics, we might conclude that the 4-equal-bins with a Gower power of 0.5 performs better than the other tuning parameter values considered.
+
+To provide a more detailed view of explanations obtained using different tuning parameter values, we take a closer look at explanations for two observations of interest, which will be referred to as case M (a known match) and case NM (a known non-match), using explanation scatterplots.
+Figure~\ref{fig:figure-11} includes the visual representation plots of explanations (from \emph{lime}) and explanation scatterplots for cases M and NM.
+Plots for 4-equal-bins and 4-quantile-bins are included to depict tuning parameter values with good (4-equal-bins) and mediocre (4-quantile-bins) performance based on the assessment metric plot.
+Plots for the kernel density simulation method are included in Appendix~\ref{exp-scatter_plus} (Figure \ref{fig:figure-B2}).
+
+We focus on the explanation for case NM with 4-quantile-bins.
+The explanation plot from \emph{lime} shows that the observed values of NM of mismatches less than or equal to 7.17, rough correlation (rough\_cor) greater than 0.05, and D less than or equal to 0.002 support a random forest prediction in favor of a match.
+The scatter plots show that many of the simulated values in the rectangular regions with mismatches less than 7.17, rough correlation greater than 0.05, and distance less than or equal to 0.002 have random forest predictions greater than 0.5, which agrees with the LIME explanation.
+However, the random forest assigns a probability of 0.21 to case NM, which is not explained by the LIME explanation that provides all explanations in support of a match.
+Instead, consider that a better explanation based on the scatterplots would be that the random forest assigned a prediction probably below 0.5 since NM has observed values of mismatches less than 5, rough correlation greater than 0.25, and distance greater than 0.001.
+
+The other explanation scatterplots can be interpreted in a similar manner.
+The three plots depict situations where the explanations are faithful to the random forest, but the regions captured by the intersections of the bins do not align well with the regions containing similar probabilities produced by the random forest.
+
+\begin{figure*}[!thp]
+<<figure-11, out.width = '6.25in', fig.width = 13, fig.height = 8.75, message = FALSE>>=
+
+# Specify the figure size (for determining font size)
+f11_ow = 6.25
+f11_fw = 13
+f11_fs = fs * (f11_fw / f11_ow)
+f11_ls = 0.5 * (f11_fw / f11_ow)
+
+# Adjust names of the cases
+bullet_explain_perms_clean <- bullet_explain_perms %>%
+  mutate(case = ifelse(case == bullet_poi_nonmatch, "NM", "M"))
+
+# Create a theme for the lime explanation visualizations
+bullet_explain_plot_theme <-
+  list(
+    scale_fill_manual(values = c("darkorange", "grey50")),
+    theme(
+      text = element_text(family = ff, size = f11_fs),
+      strip.text.x = element_text(face = "plain", size = f11_fs)
+    )
+  )
+
+# Create the lime explanation visualizations
+pfNM_3qb <- plot_features(bullet_explain_perms_clean[4:6,]) + bullet_explain_plot_theme
+pfNM_3eb <- plot_features(bullet_explain_perms_clean[10:12,]) + bullet_explain_plot_theme
+
+# Create theme for explanation scatterplots
+bullet_eoi_plot_theme <-
+  list(
+    scale_color_gradient2(
+      low = "grey50",
+      high = "darkorange",
+      midpoint = 0.5,
+      limits = c(0, 1)
+    ),
+    scale_fill_gradient2(
+      low = "grey50",
+      high = "darkorange",
+      midpoint = 0.5,
+      limits = c(0, 1)
+    ),
+    theme_bw(base_family = ff, base_size = f11_fs),
+    theme(
+      aspect.ratio = 1,
+      plot.title = element_text(size = f11_fs),
+      strip.text.x = element_text(size = f11_fs),
+      strip.text.y = element_text(size = f11_fs),
+      strip.placement = "outside",
+      strip.background = element_rect(color = "white", fill = "white")
+    ),
+    guides(size = guide_legend(nrow = 2, byrow = T), 
+           linetype = guide_legend(override.aes = list(color = c("grey50", "darkorange"))))
+  )
+
+# Create the explanation scatterplots
+eoiNM_3qb <-
+  plot_explain_scatter(
+    bullet_explain_perms_clean[4:6, ],
+    alpha = 0.9,
+    weights = TRUE,
+    line_size = f11_ls
+  ) +
+  bullet_eoi_plot_theme + 
+  guides(linetype = guide_legend(override.aes = list(color = c("darkorange"))))
+eoiNM_3eb <-
+  plot_explain_scatter(
+    bullet_explain_perms_clean[10:12,],
+    alpha = 0.9,
+    weights = TRUE,
+    line_size = f11_ls
+  ) +
+  bullet_eoi_plot_theme
+
+# Join the plots
+plot_grid(
+  pfNM_3qb,
+  pfNM_3eb,
+  eoiNM_3qb,
+  eoiNM_3eb,
+  nrow = 2,
+  rel_heights = c(0.2, 0.3)
+)
+
+@
+\caption{Plots of LIME explanations (first row) and explanation scatterplots (second row) for case NM in the bullet test data for two tuning parameter values: 4-quantile-bins (first column) and 4-equal-bins (second column).
+The plots provide insights into the LIME explanations and allow for the assessment of the explanation quality.}
+\label{fig:figure-11}
+\end{figure*}
+
+Without applying LIME with multiple tuning parameter values to the bullet test data or viewing diagnostic plots of the LIME explanations, it may be very possible to formulate reasons why the LIME explanations make sense.
+However, the sequence of plots in this section (Figures \ref{fig:figure-09}, \ref{fig:figure-10}, and \ref{fig:figure-11}) suggest that we should be cautious to trust any of these LIME explanations.
+It appears that either LIME needs to be further tuned to provide trustworthy and good explanations, or a different approach may provide better insight.
+
+\section{Discussion} \label{discussion}
+
+This paper highlights that while an explainer model is meant to provide clarity, it actually adds another layer of complexity to predictive models by requiring yet another model that needs to be assessed.
+Without an assessment of the explainer model, LIME is a black-box procedure of its own requiring blind trust in the explainer model.
+We suggest the use of visual diagnostics to counteract the black-box nature of LIME and provide three diagnostic plots.
+
+The visualizations are intended to provide insight on how LIME works, assess the ability of the explainer model to capture the complex predictive model, and compare LIME explanations produced by different tuning parameter values.
+While the visualizations accomplish these tasks, they also expose examples of the failings of LIME.
+To address the discovered failings of LIME, we reconsider each of the claims about the performance of LIME made by \citet{ribeiro:2016} in light of the insights gained from the diagnostic visualizations.
+
+As previously discussed, the \textbf{interpretability} of the LIME explanations is controllable  by the complexity of the explainer model.
+For example, the number of bins selected for simulation can control the interpretability of the explanations.
+If too many bins are selected, the bin range that is reported in the LIME explanation will be too small to be meaningful in the context of the feature.
+An appropriate choice of the number of bins will keep the bin range meaningful.
+Thus, the claim of interpretability does not need to be assessed using the visualizations.
+However, diagnostic visualizations do present a different perspective on the meaning of interpretability.
+
+Even though an explanation will be interpretable as long as the complexity of the explainer model is appropriately chosen, a lack of understanding of the process used to create the explanation could lead to an incorrect interpretation of the explanation.
+For example, the visualization of a LIME explanation available from the \emph{lime} R package \citep{pedersen:2020} (shown in Figures \ref{fig:figure-03} and \ref{fig:figure-11}) is a major simplification of the explainer model, which could lead to under-interpreted or misinterpreted LIME explanation.
+Supplementing \citet{pedersen:2020}'s compact visualization of the explanation with an explanation scatterplot that shows a more detailed visualization of the explainer model promotes a more complete understanding of the explanation (such as Figures~\ref{fig:figure-03} and \ref{fig:figure-11}).
+
+Even with an explainer model that is interpreted correctly, the interpretation is worthless if the explainer model is not \textbf{faithful} to the complex model.
+This claim can be assessed using the diagnostic plots suggested in this paper.
+Many of the visualizations in this paper highlight problems with the faithfulness of the explainer models.
+The explanation scatterplots allow for a comparison of the explainer model to the complex model.
+The examples in this paper show cases where the explainer model bins do not accurately capture the regions with similar random forest probabilities that contain the prediction of interest and oversimplify the model (Figures \ref{fig:figure-03} and \ref{fig:figure-11}).
+Using fewer bins would clearly not help improve the faithfulness of the explainer model in these examples, and while an increase in the number of bins would lead to a finer resolution of the random forest classification boundaries, interpretability of the explainer model would quickly be lost.
+Perhaps this could be improved by allowing the bin creation to account for the relationships between the features and response variable or a different number of bins for each feature.
+
+In addition to assessing faithfulness by visually comparing the complex and explainer model, we propose a visual comparison of two faithfulness metrics (MSEE and average fidelity).
+The examples of faithfulness metric comparisons in this paper both produced conflicting results (Figures \ref{fig:figure-05} and \ref{fig:figure-10}).
+This makes it difficult to decide on a recommendation of a set of tuning parameter values that produce the explanations with the most faithful explainer model.
+
+The metric comparison plot also includes a comparison of average $R^2$ values, which is a metric that can be used to assess the claim of \textbf{linearity}.
+Most of the average $R^2$ values in the examples from this paper are below 0.5 suggesting a poor linear fit of the explainer models.
+A poor linear fit of the explainer model is also seen with the residual plot (\autoref{fig:figure-C3}).
+
+The final claim, \textbf{localness}, is addressed by the feature heatmap and metric comparison plots.
+As stated, the feature heatmap reveals that the density simulation methods in the \data \ example  results in global explanations where the same features are repeatedly chosen across all (or almost all) observations in the set of explanations.
+This finding agrees with that of \citet{laugel:2018} who found LIME produced global explanations with the normal approximation simulation method.
+For the bin based simulation methods in the bullet data example, the feature heatmap shows that the features chosen for the explanations vary between the two classification categories (match versus non-match).
+This is an interesting finding that suggests that different features can play a role in the predictions of observations in different response categories.
+Furthermore, while the metric comparison plot in the bullet example does not provide agreement between metrics on a best bin based method, all metrics agree that a Gower power of 0.5 for computing the model weights associated with distance of a simulated data point from the prediction of interest is the best.
+This suggests that a less local explanation provides a better explanation of the performance of the random forest.
+
+Some of the visualizations in the paper generalize easily to any application of LIME such as the feature heatmap and metric plot.
+Other plots such as the visualizations of the LIME procedure would require extensions such as the use of scatterplot matrices to compare explanations with more than two features.
+The addition of interactivity to the diagnostic plots would provide additional enhancement of the assessment process.
+For example, a diagnostic plot that provides a summary of multiple LIME explanations, such as the feature heatmap, could be displayed and clicked on to reveal more detailed figures associated with individual predictions of interest, such as an explanation scatterplot.
+
+The largest limitation to the diagnostic visualizations is the dimensionality of the data shown, both in the number of dimensions or features as well as the number of observations.
+Fortunately, in the situation of LIME, both of these aspects are rather well controlled: LIME relies heavily on simulations to generate data scenarios that are close to the data observed but exhibit variability.
+Effects from overplotting should be relatively mild, because output from simulations is shown, which is expected to be (relatively) continuous such that overplotting only occurs for points with (relatively) similar values.
+In that respect, the diagnostics shown for the \data \ and the bullet example are representative of what is expected.
+But in cases where overplotting does become problematic, the user could either simply reduce the size of the simulations or use some well-studied binning techniques in the visualizations, as discussed for example in \citet{carr:1987} or \citet{unwin:2006}.
+
+While it would be ideal if LIME could be used as a method to provide easily understandable explanations for black-box models as \citet{ribeiro:2016} claim, that dream is not yet a reality.
+The examples using diagnostic plots to assess LIME in this paper show frequent issues with LIME.
+We hope that our plots provide motivation to assess LIME explanations, to not blindly use the default settings (even if it is not clear how to tune the parameters), and to encourage work on improving LIME, so that it can be a lime and not a lemon.
+
+\section*{Acknowledgments}
+
+HH was partially funded by the Center for Statistics and Applications in Forensic Evidence (CSAFE) through Cooperative Agreement 70NANB20H019 between NIST and Iowa State University, which includes activities carried out at Carnegie Mellon University, Duke University, University of California Irvine, University of Virginia, West Virginia University, University of Pennsylvania, Swarthmore College and University of Nebraska, Lincoln.
+
+\subsection*{Author contributions}
+
+{\bf Katherine Goode, Heike Hofmann}: Conceptualization, Methodology, Investigation, Visualizations, Writing - Reviewing and Editing. {\bf Katherine Goode}: Writing - Initial Draft, Software.
+
+\subsection*{Financial disclosure}
+
+None reported.
+
+\subsection*{Conflict of interest}
+
+The authors declare no potential conflict of interests.
+
+\section*{Supporting information}
+
+The code used to produce the manuscript and the data from examples in Section \ref{application} are available in the following GitHub Repository: \href{https://github.com/goodekat/LIME-diagnostics-paper}{https://github.com/goodekat/LIME-diagnostics-paper}.
+
+\bibliography{references}
+
+\newpage
+
+\appendix
+
+\section{LIME Tuning Parameter Options} \label{lime-details}
+
+The following tuning parameters for the LIME algorithm are available in the \emph{lime} R package \citep{pedersen:2020}.
+
+\begin{itemize}
+
+\item Data simulation methods:
+
+\begin{itemize}
+\item Equally spaced bins: observations are uniformly sampled from equally spaced bins (number of bins may be specified)
+\item Quantile bins: observations are uniformly sampled from quantile bins (number of bins may be specified)
+\item Normal density approximation: observations are sampled from a normal distribution with mean and standard deviation computed from the corresponding feature
+\item Kernel density approximation: observations are sampled from an kernel density approximation of the corresponding feature
+\end{itemize}
+
+\item Number of observations to simulate
+
+\item Distance metric for determining proximity to the prediction of interest: Gower distance (where the power may be specified) or exponential kernel (where the kernel width may be specified)
+
+\item Number of features to return in an explanation
+
+\item Feature selection method for determining the features to return in an explanation: forward selection applied to a ridge regression, features with the largest magnitude coefficients in ridge regression, LASSO, classification/regression tree splits
+
+\end{itemize}
+
+\section{Explanation Scatterplots Under Other Simulation Scenarios} \label{exp-scatter_plus}
+
+\begin{figure*}[!thp]
+<<figure-B1, out.width = '6.5in', fig.width = 12, fig.height = 5, fig.align = "center">>=
+
+# Specify the figure size (for determining font size and line size)
+fb1_ow = 6.5
+fb1_fw = 12
+fb1_fs = fs * (fb1_fw / fb1_ow)
+fb1_ls = 0.5 * (fb1_fw / fb1_ow)
+
+# Create the explanation scatterplot
+plot_explain_scatter(
+  sine_lime_explain$explain %>%
+    filter(sim_method == "kernel_density", case == sine_poi %>% pull(case)),
+  alpha = 0.75,
+  title.opt = FALSE, 
+  line_size = fb1_ls 
+) +
+  theme_bw(base_family = ff, base_size = fb1_fs) +
+  theme(
+    strip.background = element_rect(fill = "white", color = "white"),
+    strip.placement = "outside",
+    strip.text.x = element_text(size = fb1_fs)
+  )
+
+@
+\caption{Explanation scatterplots for the \data \ prediction of interest with the kernel density simulation method.}
+\label{fig:figure-B1}
+\end{figure*}
+
+\begin{figure*}[!thp]
+<<figure-B2, out.width = '6.5in', fig.width = 12, fig.height = 10, fig.align = "center">>=
+
+# Specify the figure size (for determining font size and line size)
+fb2_ow = 6.5
+fb2_fw = 12
+fb2_fs = fs * (fb2_fw / fb2_ow)
+fb2_ls = 0.5 * (fb2_fw / fb2_ow)
+
+# Create the explanation scatterplot: case M, kernel density
+bullet_es_M <-
+  plot_explain_scatter(
+    bullet_explain_perms[16:18, ] %>% mutate(case = "NM"),
+    alpha = 0.75,
+    title.opt = TRUE,
+    line_size = fb2_ls
+  ) +
+  scale_fill_gradient2(
+    low = "grey50",
+    high = "darkorange",
+    midpoint = 0.5,
+    limits = c(0, 1)
+  ) +
+  theme_bw(base_family = ff, base_size = fb2_fs) +
+  theme(
+    aspect.ratio = 1,
+    strip.background = element_rect(fill = "white", color = "white"),
+    strip.placement = "outside",
+    strip.text.x = element_text(size = fb2_fs),
+    plot.title = element_text(size = fb2_fs)
+  )
+
+# Create the explanation scatterplot: case NM, kernel density
+bullet_es_NM <-
+  plot_explain_scatter(
+    bullet_explain_perms[13:15, ] %>% mutate(case = "M"),
+    alpha = 0.75,
+    title.opt = TRUE, 
+    line_size = fb2_ls
+  ) +
+  scale_fill_gradient2(
+    low = "grey50",
+    high = "darkorange",
+    midpoint = 0.5,
+    limits = c(0, 1)
+  ) +
+  theme_bw(base_family = ff, base_size = fb2_fs) +
+  theme(
+    aspect.ratio = 1,
+    strip.background = element_rect(fill = "white", color = "white"),
+    strip.placement = "outside",
+    strip.text.x = element_text(size = fb2_fs), 
+    plot.title = element_text(size = fb2_fs)
+  )
+
+# Join the plots
+plot_grid(bullet_es_NM, bullet_es_M, nrow = 2)
+
+@
+\caption{Explanation scatterplots for LIME explanations using kernel density simulation for the cases M and NM of the bullet comparison test data.}
+\label{fig:figure-B2}
+\end{figure*}
+
+Section \ref{exp-scatter} introduces explanation scatterplots under the default simulation method in the \emph{lime} R package: 4-quantile-bins.
+The structure of an explanation scatterplot remains the same if any bin based simulation method is used, i.e., any number of quantile or equally spaced bins.
+However, if the kernel density or normal approximation simulation methods are used, the format of the explanation scatterplot changes.
+In the density based simulation method scenarios, LIME uses the standardized versions of the predictor variables to fit the explainer model.
+Thus, the explainer model needs to be represented differently in the explanation scatterplot.
+
+When the kernel density or normal approximation simulation methods are applied, the explanation scatterplot depicts the complex model by plotting the complex model predictions versus a feature selected in LIME the explanation from the simulated data.
+The explainer model is included as a line on the figure where all features excluding the one plotted on the x-axis are set to the observed values of the prediction of interest.
+An explanation scatterplot is created for each feature included in the LIME explanation.
+As with the bin based simulation method, the size of the points represent the weight assigned by LIME.
+
+Figure \ref{fig:figure-B1} provides example explanation scatterplots for each feature in the default LIME explanation obtained using the kernel density simulation method for the \data \ prediction of interest.
+Figure \ref{fig:figure-B2} includes explanation scatterplots for the explanations generated using kernel density simulation for the bullet example cases M and NM discussed in Section \ref{bullet-assess-ex}.
+
+\section{Explainer Model Residual Plot} \label{residual-plot}
+
+In order to assess the claim of linearity for the \data \ prediction of interest discussed in Section \ref{exp-scatter}, we use one of the most basic diagnostics in a statistician's tool box and draw a residual plot for the explainer model.
+This is shown in Figure \ref{fig:figure-C3} with the explainer model residuals on the y-axis and explainer model predictions on the x-axis.
+The points along the x-axis have been jittered to ease the effect of the over-plotted points in the visualization.
+There is a clear increasing trend in the residuals as the explainer model predictions increase.
+This is a clear violation of the linearity assumption with the ridge regression model.
+
 \begin{figure}[!thp]
-<<figure-04, out.width = '3.125in', fig.width = 6, fig.height = 3>>=
+<<figure-C3, out.width = '3.125in', fig.width = 5, fig.height = 4, warning = FALSE>>=
+
+# Specify the figure size (for determining font size and line size)
+fc3_ow = 3.125
+fc3_fw = 5
+fc3_fs = fs * (fc3_fw / fc3_ow)
+fc3_ls = 0.5 * (fc3_fw / fc3_ow)
+
+# Calculate the residuals from the explainer model
+y <- sine_poi_perms$rfpred
+sine_poi_explainer <-
+  function(x1, x2)
+    sine_b0 + (sine_b1 * x1) + (sine_b2 * x2)
+sine_poi_perms <- sine_poi_perms %>%
+  mutate(exppred = sine_poi_explainer(x1num, x2num)) %>%
+  mutate(resid = exppred - rfpred)
+
+# Create the residual plot
+ggplot(sine_poi_perms, aes(x = exppred, y = resid)) +
+  geom_hline(yintercept = 0, size = fc3_ls) +
+  geom_jitter(alpha = 0.5, width = 0.02) +
+  theme_bw(base_family = ff, base_size = fc3_fs) +
+  theme(plot.title = element_text(size = fc3_fs)) +
+  labs(x = "Explainer Model Predictions",
+       y = "Explainer Model Residuals",
+       title = "Explainer Model Residual Plot")
+
+@
+\caption{Residual plot of the explainer model associated with \data \ prediction of interest from Section \ref{exp-scatter}.
+The residuals are plotted against the predicted values.
+The points are jittered in the x-direction to alleviate the over-plotting of points.
+There is an upward trend in the residuals as the explainer model predictions increase, which suggests a violation of the linearity assumption.}
+\label{fig:figure-C3}
+\end{figure}
+
+\section{Extreme Feature Heatmap Scenarios} \label{feat-heat-ex}
+
+Two hypothetical examples of feature heatmaps are included in \autoref{fig:figure-D4}.
+The plots are created with the assumption that LIME is applied to select the top feature out of $p=4$  features for $n=10$ cases with $t=5$ sets of tuning parameter values.
+Situation 1 is an example where the features selected are consistent across tuning parameter values within a case but vary across cases within a tuning parameter value.
+This is the ideal situation, because the LIME explanations do not depend on the tuning parameters but do depend on the location of the observation in the feature space.
+Situation 2 is an example where the selected features vary across tuning parameter values within a case but are consistent across cases within a tuning parameter value.
+This situation indicates that the features selected by LIME are dependent on the tuning parameters, and the explanations may not be  local, because the same feature is chosen regardless of the case.
+In practice, it is expected that the plot will exhibit a combination of these two situations.
+
+\begin{figure}[!thp]
+<<figure-D4, out.width = '3.125in', fig.width = 6, fig.height = 3>>=
 
 # Specify the figure size (for determining font size)
-f5_ow = 3.125
-f5_fw = 6
-f5_fs = fs * (f5_fw / f5_ow)
+fd4_ow = 3.125
+fd4_fw = 6
+fd4_fs = fs * (fd4_fw / fd4_ow)
 
@@
   ) +
-  theme_bw(base_family = ff, base_size = f5_fs) +
+  theme_bw(base_family = ff, base_size = fd4_fs) +
   scale_fill_grey() +
@@
   theme(legend.position = "none", 
-        plot.title = element_text(size = f5_fs))
+        plot.title = element_text(size = fd4_fs))
 
@@
   ) +
-  theme_bw(base_family = ff, base_size = f5_fs) +
-  theme(plot.title = element_text(size = f5_fs)) +
+  theme_bw(base_family = ff, base_size = fd4_fs) +
+  theme(plot.title = element_text(size = fd4_fs)) +
   scale_fill_grey() +
@@
 Situation 1 is the ideal, because the explanations vary across cases but do not dependent on specific tuning parameter values.}
-\label{fig:figure-04}
-
-\vspace*{\floatsep}
-
-<<figure-05, out.width = '3.125in', fig.width = 4, fig.height = 4.5>>=
+\label{fig:figure-D4}
+\end{figure}
+
+\section{Details on Assessment Metrics} \label{metric-details}
+
+Suppose $f$ is a complex model, and let $\textbf{X}$ be a matrix of observed data with $K$ features and $E$ observations where $x_e$ is an observed feature vector for observation $e$.
+Let $f(x_e)$ be the complex model prediction for observation $e$.
+It is of interest to explain the predictions made by $f$ applied to $X$ using LIME.
+
+For $x_e$ and a set of tuning parameter values $t$, let $\textbf{X}_{e,t}'$ be the LIME simulated dataset with $K$ features and $S$ rows such that $x'_{e,t,s}$ is the feature vector for simulated data point $s$ corresponding to explanation $e$ and tuning parameter values $t$.
+Let $\textbf{Z}'_{e,t}$ be the matrix of simulated data transformed to bin indicator variables (for bin based simulation methods) or standardization (for density based simulation methods) with $K$ features and $S$ observations such that $z'_{e,t,s}$ is the interpretability transformed feature vector for explanation $e$, tuning parameter values $t$, and simulated data point $s$.
+Note that $z_{e,t}$ will represent the  transformed version of $x_e$.
+
+Next, let $\omega_t$ represent a proximity distance metric corresponding to tuning parameter values $t$.
+Then $\omega_t\left(x_e, x'_{e,t,s}\right)$ is the weight assigned to $x'_{e,t,s}$, which is the proximity between $x_e$ and $x'_{e,t,s}$.
+Allow $g_{e,t}$ to be the explainer model for an explanation $e$ and tuning parameter values $t$.
+Thus, $g_{e,t}\left(z'_{e,s,t}\right)$ is the explainer model prediction for the interpretability transformed simulated data point $s$.
+
+For a set of $E$ explanations and a set of tuning parameter values $t$, we define the assessment metrics as follows:\\
+\\
+\emph{Average $R^2$} is denoted as $R^2_{\mbox{ave}}$ and computed as
+
+  $$R^2_{\mbox{ave}} = \frac{1}{E}\sum_{e=1}^E R_{e,t}^2$$
+
+\noindent where $R_{e,t}^2$ is the $R^2$ value for $g_{e,t}$.\\
+\\
+\emph{Average fidelity} is denoted by $\mathcal{L}_{\mbox{ave}}$ and computed as
+
+\begin{eqnarray*} \mathcal{L}_{\mbox{ave}} & = & \frac{1}{E}\sum_{e=1}^E\mathcal{L}(f, \ g_{e,t}, \ \pi_{t}) \\ & = & \frac{1}{E}\sum_{e=1}^E\sum_{s=1}^{S}\omega_{t}\left(x_e, x'_{e,t,s}\right)\left(f\left(x'_{e,t,s}\right)-g_{e,t}\left(z_{e,t,s}'\right)\right)^2.
+\end{eqnarray*}
+
+\noindent where $\mathcal{L}$ is the fidelity metric originally defined in \citet{ribeiro:2016}.\\
+\\
+\emph{Mean squared explanation error} is denoted by MSEE and computed as
+
+$$MSEE=\frac{1}{E}\sum_{e=1}^E\left(f\left(x_e\right)-g_{e,t}\left(z_{e,t}\right)\right)^2.$$
+
+\section{Matching Bullets Explanation Scatterplots} \label{match-bullets}
+
+\begin{figure*}[!thp]
+<<figure-e5, out.width = '6.25in', fig.width = 13, fig.height = 8.75, message = FALSE>>=
 
 # Specify the figure size (for determining font size)
-f6_ow = 3.125
-f6_fw = 4
-f6_fs = fs * (f6_fw / f6_ow)
-
-# Create the example feature heatmap with the sine data
-plot_feature_heatmap(sine_lime_explain$explain,
-                     order_method = "PCA") +
-  theme_bw(base_family = ff, base_size = f6_fs) +
-  theme(
-    legend.position = "bottom",
-    axis.text.y = element_blank(),
-    axis.ticks.y = element_blank(),
-    strip.background = element_rect(color = "white", fill = "white")
-  ) +
-  labs(y = "Case")
-
-@
-\caption{\emph{Feature Heatmap}.
-An example feature heatmap of the explanations from the applications of LIME with different tuning parameter values to the \data \ test set.
-The cases from the test set are plotted on the y-axis, and the tuning parameter values (simulation methods here) are included on the x-axis.
-The colors of the tiles indicate the feature selected by LIME for the corresponding case and tuning parameter value.
-The plot is faceted by the first and second most important features selected by LIME (top and bottom facets, respectively).
-The vertical facets separate the  kernel density method from the quantile bin methods.
-The vertical striping indicates that the LIME explanations are not consistent across tuning parameter values.}
-\label{fig:figure-05}
-\end{figure}
-
-Explanations produced by LIME are likely to be affected by the choice of tuning parameter values.
-A hypothetical example of this is shown by Figures \ref{fig:figure-01} and \ref{fig:figure-02} where the method used to weight the observations influenced the explanation.
-As of the time of writing this manuscript, we have encountered no recommendations for how to specify the parameter values besides for the default settings in \emph{lime}.
-In order to compare the explanations produced by LIME using different tuning parameter values and provide another perspective for assessing localness, we visualize an overview of the explanations with the \emph{feature heatmap} diagnostic plot.
-
-The feature heatmap uses colors to identify the features selected by LIME across multiple predictions (referred to as cases here) and tuning parameter values organized by the  feature importance assigned by LIME.
-That is, for LIME applied with $t$ sets of tuning parameter values to $n$ cases to select the $f$ top features, create $f$ heatmaps (one for each of the positions of importance determined by the magnitude of the explainer model coefficients) with the cases on the $y$-axis, the tuning parameter values on the $x$-axis, and the cells colored by the feature chosen for the corresponding case and tuning parameter value.
-Additional tuning parameters may also be included in the plot via facets.
-
-Two hypothetical examples of feature heatmaps are included in \autoref{fig:figure-04}.
-The plots are created with the assumption that LIME is applied to select the top feature out of $p=4$  features for $n=10$ cases with $t=5$ sets of tuning parameter values.
-Situation 1 is  an example where the features selected are consistent across tuning parameter values within a case but vary across cases within a tuning parameter value.
-This is the ideal situation, because the LIME explanations do not depend on the tuning parameters but do depend on the location of the observation in the feature space.
-Situation 2 is an example where the selected features vary across tuning parameter values within a case but are consistent across cases within a tuning parameter value.
-This situation indicates that the features selected by LIME are dependent on the tuning parameters, and the explanations may not be  local, because the same feature is chosen regardless of the case.
-In practice, it is expected that the plot will exhibit a combination of these two situations.
-
-\autoref{fig:figure-05} shows a feature heatmap for the LIME applications to the 100 observations in the \data \ test set.
-The most important and second most important features selected by lime are shown in in the top and bottom facets, respectively.
-For the quantile bins, the original features prior to the indicator variable transformation are included since it is obvious that different features would be selected when the sizes of the bins change.
-This figure shows that for kernel density and 2-quantile-bins, LIME selects $x_1$ as the most important feature and $x_2$ as the second most important feature across all cases in the test set.
-These explanations are not local.
-There is variability in the features selected by LIME for 3- to 6-quantile-bins suggesting more local explanations.
-There are signs of vertical striping, which suggests a dependence on tuning parameters.
-Note that the explanations from 3- and 5-quantile-bins include the selection of the random noise variable ($x_3$) as an important variable in many predictions, which should not be the case.
-The pattern seen in the explanations for 3- to 6-quantile-bins may suggest local explanations, but the dependence on tuning parameters makes it unclear which set of explanations to use.
-
-\subsection{Assessment Metric Plot} \label{assess-metric}
-
-\begin{figure}[!thp]
-<<figure-06, out.width = '3.25in', fig.width = 4.5, fig.height = 3.75, warning = FALSE>>=
-
-# Specify the figure size (for determining font size)
-f7_ow = 3.25
-f7_fw = 4.5
-f7_fs = fs * (f7_fw / f7_ow)
-
-# Create the metric plot
-plot_metrics(sine_lime_explain$explain, rank_legend = "discrete") +
-  theme_bw(base_family = ff, base_size = f7_fs) +
-  theme(
-    strip.background = element_rect(color = "white", fill = "white"),
-    strip.placement = "outside",
-    strip.text.y = element_text(size = f7_fs)
-  )
-
-@
-\caption{\emph{Assessment metric plot}.
-The assessment metrics computed on the applications of LIME to the \data \ test set are included in this example assessment metric plot.
-Each horizontal facet corresponds to one of three metrics: average $R^2$, average fidelity, or MSEE.
-The LIME tuning parameter values (simulation methods in this example) are plotted on the x-axis, and the metric values are shown on the y-axis.
-The points are colored by rank (within a metric) indicating best to worst (dark to light).
-The kernel density simulation methods performs well across all three metrics.}
-\label{fig:figure-06}
-\end{figure}
-
-The feature heatmap for the \data \ in the previous section shows an example of inconsistent LIME explanations across tuning parameter values.
-In this situation, the user must determine which set of explanations to trust.
-One way to do this is to compute assessment metrics for each set of explanations to identify the optimal tuning parameter values.
-We discuss three metrics for this purpose and present a visual comparison in an \emph{assessment metric plot}.
-
-Each metric presented below is computed on  LIME explanations for a set of predictions obtained using the same tuning parameter values.
-Here we provide a high level description of the metrics.
-Notation and formulas for these metrics are included in Appendix \ref{metric-details}.
-
-\begin{itemize}
-\item \emph{Average $R^2$}: Assess the model fit and linearity claim by computing the average of the explainer model $R^2$ values (deviance ratios from the R package \emph{glmnet}).
-
-\item \emph{Average Fidelity}: Measures the faithfulness of the explainer model to the complex model by comparing their predictions.
-Computed as the average of the explainer model fidelity metrics: a metric presented in \citet{ribeiro:2016} (the weighted distance between explainer and complex model predictions for all observations in the LIME simulated data associated with an individual prediction of interest).
-
-\item \emph{Mean Squared Explanation Error (MSEE)}: Also measures the faithfulness of the explainer model to the complex model by comparing their predictions, but only the prediction of interest is used to compute an average squared deviation between explainer and complex model predictions.
-\end{itemize}
-
-\autoref{fig:figure-06} shows an example assessment metric plot.
-The three metrics are computed for each of the LIME applications to the \data \ test set.
-The simulation methods are listed on the x-axis.
-The plot is faceted by metric, and the metric values are plotted on the y-axis.
-The colors of the points represent the rank of the simulation methods performance based on a particular metric (darker indicates a better metric value and lighter indicates a worse metric value).
-Higher average $R^2$ values are better, and lower average fidelity and MSEE values are better.
-This example only includes one tuning parameter: the simulation method.
-If more than one tuning parameter is considered, the assessment metric plot is extended by adding additional facets or levels to the x-axis.
-
-All three metrics suggest that the kernel density method performed well, but the metrics disagree for the quantile bins methods.
-Average $R^2$ and average fidelity rank the performance of the number of quantile bins the same (2-quantile-bins perform the best and 6-quantile-bins perform the worst).
-In fact, these two metrics appear to have a mirrored  relationship in this example.
-MSEE provides almost the exact opposite results with  6-quantile-bins performing the best and 2-quantile-bins performing the worst.
-Average fidelity and MSEE are similar metrics, so it is not surprising that they would agree in this example.
-Another factor might be that MSEE only takes the prediction of interest  into account and not the full simulated dataset.
-The contradiction between metrics makes it difficult to identify which simulation method to trust.
-
-Recall that \autoref{fig:figure-05} indicated that the kernel density method selected the same feature across all cases in the test set for both the first and second features.
-It appears that a global trend may be the best explanation for this example, which may be reasonable considering that we know that both $x_1$ and $x_2$ are the two features that should be the features used by the random forest to distinguish between response categories.
-
-\section{Application to Bullet Matching Data} \label{application}
-
-In this section, we provide a discussion of the application of the visual diagnostics for LIME explanations to a practical data problem investigating the similarity of marks on fired bullets.
-
-\subsection{Bullet Matching Data}
-
-<<bullet-data>>=
-# Load the bullet matching training and testing data
-bullet_train <- readr::read_csv("data/bullet-train.csv.zip")
-bullet_test <- readr::read_csv("data/bullet-test.csv.zip")
-@
-
-<<bullet-rf>>=
-
-# Extract the features from the original random forest model (rtrees)
-bullet_features <- rownames(bulletxtrctr::rtrees$importance)
-bullet_rf_ntrees <- bulletxtrctr::rtrees$ntree
-bullet_rf_mtry <- bulletxtrctr::rtrees$mtry
-
-# Train a new random forest that mimics the rtrees models 
-# (or load if already trained)
-bullet_rf_file = "./data/bullet-rf.rds"
-if (!file.exists(bullet_rf_file)) {
-  set.seed(20200923) # the day that the updated data was found :)
-  bullet_rf <-
-    randomForest(
-      y = factor(bullet_train$samesource),
-      x = bullet_train %>% select(all_of(bullet_features)),
-      ntree = bullet_rf_ntrees,
-      mtry = bullet_rf_mtry
-    )  
-  saveRDS(object = bullet_rf, file = bullet_rf_file)
-} else {
-  bullet_rf = readRDS(file = bullet_rf_file)
-}
-
-# Add variables to both training and testing data with the random forest probability
-# that the signatures are a match from the model bullet_rf
-bullet_train$rfscore = predict(bullet_rf, bullet_train %>% select(all_of(bullet_features)), type = "prob")[,2]
-bullet_test$rfscore = predict(bullet_rf, bullet_test %>% select(all_of(bullet_features)), type = "prob")[,2]
-
-# Compute OOB model metrics
-bullet_rf_oob_acc = round(sum(predict(bullet_rf) == bullet_train$samesource) / length(bullet_train$samesource), 2)
-bullet_rf_oob_fp = round(bullet_rf$confusion[,3][2], 2)
-bullet_rf_oob_fn = round(bullet_rf$confusion[,3][1], 4)
-
-# Obtain model predictions and confusion matrix from test data
-bullet_test_pred = predict(bullet_rf, bullet_test %>% select(all_of(bullet_features)))
-bullet_test_confus = table(bullet_test_pred, bullet_test$samesource)
-
-# Compute test data model metrics
-bullet_rf_test_acc = round(sum(bullet_test_pred == bullet_test$samesource) / length(bullet_test$samesource), 2)
-bullet_rf_test_fp = round(bullet_test_confus[2,1] / (bullet_test_confus[2,1] + bullet_test_confus[2,2]), 2)
-bullet_rf_test_fn = round(bullet_test_confus[1,2] / (bullet_test_confus[1,1] + bullet_test_confus[1,2]), 4)
-@
-
-<<bullet-feature-importance>>=
-# Order the features based on feature importance
-bullet_features_ordered <-
-  data.frame(
-    feature = rownames(bullet_rf$importance),
-    MeanDecreaseGini = bullet_rf$importance
-  ) %>%
-  arrange(desc(MeanDecreaseGini)) %>%
-  mutate(
-    feature = fct_recode(feature,
-      "Cross Correlation\nFunction" = "ccf",
-      "Consecutively\nMatching Striae" = "cms",
-      "Matches" = "matches",
-      "Mismatches" = "mismatches",
-      "Non-Consecutively\nMatching Striae" = "non_cms",
-      "Rough\nCorrelation" = "rough_cor",
-      "Distance Standard\nDeviation" = "sd_D",
-      "Distance" = "D",
-      "Sum of Peaks" = "sum_peaks"
-    )
-  )
-
-# Create an ordered version of the data
-bullet_features_ordered <-
-  bullet_features_ordered %>%
-  mutate(feature = factor(feature, levels = bullet_features_ordered$feature))
-
-@
-
-In current practice, forensic firearm examiners evaluate whether two bullets are from the same source (fired from the same gun) or from different sources based on microscopic comparison of the striation patterns engraved on bullets during the firing process (see \autoref{fig:figure-07}).
-The process is based on a visual and therefore subjective assessment of the evidence.
-The lack of objective evaluation and the associated absence of established error rates has first been criticized by the National Research Council \cite{nrc:2009} and later by the President's Council of Advisors on Science and Technology \cite{pcast:2016}.
-
-In response, \citet{hare:2017} proposed an automated machine learning method for bullet matching to complement a visual inspection by firearm examiners.
-Based on high-resolution topological scans of land engraved areas, \citet{hare:2017} obtain signatures of striations from two bullet lands (\autoref{fig:figure-08}).
-Nine features quantifying the similarity of signatures, such as the cross-correlation function, the distance between signatures, and the number of matching striae, are extracted and used to train a random forest to determine the probability of a comparison resulting from the same source (matching signatures) or from different sources (non-matching signatures).
-The model in \citet{hare:2017} was trained on a set of scans of bullets from the James Hamby Consecutively Rifled Ruger Barrel Study \citep{hamby:2009}, which included 10,384 land-to-land comparisons \citet{hare:2017}.
-See the supporting information for additional information on the signature similarity features.
-
-\begin{figure}[!t]
-\centering
-<<figure-07, out.width = '2.25in', fig.width = 6, fig.height = 3, warning = FALSE>>=
-
-# Convert the bullet figure to eps (if needed)
-if (!file.exists("figure-static/figure-07-1.eps")) {
-  unzip(zipfile = "figure-static/figure-07-1.png.zip", exdir = "figure-static")
-  bullets <- image_read("figure-static/figure-07-1.png")
-  image_write(bullets, path = "figure-static/figure-07-1.eps", format = "eps")
-}
-
-# Load and print the plot
-knitr::include_graphics("figure-static/figure-07-1.eps")
-
-@
-\caption{(Top left) Traditionally rifled gun barrel.
-The grooves and lands alternate to give bullets a spin during the firing process, which create markings (striations) on a bullet when fired.
-(Top right) Image of a fired bullet.
-The vertical stripes along the lower half of the bullet show groove and land engraved areas.
-The land engraved areas contain the microscopic striations created when the bullet passed through the barrel of the gun.
-(Bottom) Close up of a land engraved area showing striations (vertical lines).}
-\label{fig:figure-07}
-
-\vspace*{\floatsep}
-
-<<figure-08, out.width = '3.125in', fig.width = 6, fig.height = 3.5, warning = FALSE>>=
-
-# Specify the figure size (for determining font size)
-f9_ow = 3.125
-f9_fw = 6
-f9_fs = fs * (f9_fw / f9_ow)
-
-# Load the signatures data
-signatures <- readr::read_csv("data/example-signatures.csv.zip")
-
-# Create plot of the signatures
-signatures %>%
-  ggplot(aes(x = x/1000, y = y)) + 
-  geom_line() +
-  facet_grid(land ~ .) +
-  ylim(c(-4,6)) +
-  theme_bw(base_family = ff, base_size = f9_fs) +
-  theme(strip.background = element_blank()) +
-  ylab("Surface Measurement (in microns)") +
-  xlab("Relative Location (in millimeters)")
-
-@
-\caption{Example bullet signatures.
-The bullet signatures correspond to the same land and therefore have very similar patterns.
-The \citet{hare:2017} random forest is fit using various features that measure the similarity between two such signatures.}
-\label{fig:figure-08}
-\end{figure}
-
-\subsection{Application of LIME to Bullet Matching Data}
-
-\begin{figure*}[!thp]
-<<figure-09, out.width = '6.5in', warning = FALSE>>=
-
-# File names for parallel coordinate plot
-pcp_file_name_png = "figure-static/figure-09-1.png"
-pcp_file_name_eps = "figure-static/figure-09-1.eps"
-
-# Create the parallel coordinate plot (if needed)
-if (!file.exists(pcp_file_name_png) | !file.exists(pcp_file_name_eps)) {
-
-  # Specify the figure size (for determining font size)
-  f10_ow = 6.5
-  f10_fw = 7.5
-  f10_fs = 7 * (f10_fw / f10_ow)
-  f10_ls = 0.5 * (f10_fw / f10_ow)
-
-  # Create the plot
-  bullet_pcp <-
-    bullet_train %>%
-    select(all_of(bullet_features), samesource, rfscore) %>%
-    bind_rows(bullet_test %>%
-                select(all_of(bullet_features), samesource, rfscore),
-              .id = "set") %>%
-    mutate(
-      set = fct_recode(set,
-                       "Training Set" = "1",
-                       "Testing Set" = "2"),
-      samesource = fct_recode(
-        factor(samesource),
-        "Match" = "TRUE",
-        "Non-Match" = "FALSE"
-      )
-    ) %>%
-    rename(
-      "Cross Correlation\nFunction" = "ccf",
-      "Consecutively\nMatching Striae" = "cms",
-      "Matches" = "matches",
-      "Mismatches" = "mismatches",
-      "Non-Consecutively\nMatching Striae" = "non_cms",
-      "Rough\nCorrelation" = "rough_cor",
-      "Distance Standard\nDeviation" = "sd_D",
-      "Distance" = "D",
-      "Sum of Peaks" = "sum_peaks"
-    ) %>%
-    arrange(rfscore) %>%
-    ggplot(aes(color = rfscore)) +
-    geom_pcp(
-      mapping = aes(vars = vars(bullet_features_ordered$feature)),
-      alpha = 0.2,
-      size = f10_ls
-    ) +
-    facet_grid(set ~ samesource) +
-    scale_color_gradient2(low = "grey50",
-                          high = "darkorange",
-                          midpoint = 0.5) +
-    theme_bw(base_family = ff, base_size = f10_fs) +
-    theme(
-      axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
-      strip.placement = "outside",
-      strip.background = element_rect(color = "white",
-                                      fill = "white")
-    ) +
-    labs(x = "Features Ordered by Random Forest Variable Importance \n(highest to lowest from left to right)",
-         y = "Scaled Feature Values",
-         color = "Random \nForest \nProbability")
-
-  # Save the plot
-  ggplot2::ggsave(
-    plot = bullet_pcp,
-    filename = pcp_file_name_png,
-    width = 7.5,
-    height = 3.5,
-    units = "in",
-    dpi = 400
-  )
-
-  # Load the figure and then save as an EPS file
-  bullet_pcp <- image_read(pcp_file_name_png)
-  image_write(bullet_pcp, path = pcp_file_name_eps, format = "eps")
-
-}
-
-# Load and print the plot
-knitr::include_graphics(pcp_file_name_eps)
-
-@
-\caption{Parallel coordinate plots of the \citet{hare:2017} random forest predictions from the training (top facet) and testing (bottom facet) data.
-The observations are separated by known matching (right column) and non-matching (left column) signatures.
-The y-axis shows the standardized feature values, and the x-axis shows the features used to fit the random forest (ordered by random forest impurity based feature importance).
-Each line corresponds to an observation, and the line color represents the associated random forest probability.
-There are clear relationships between the feature values and the random forest probabilities.}
-\label{fig:figure-09}
-\end{figure*}
-
-Since firearm identification is commonly used as evidence for convictions in court cases, it is important to be able to understand and assess a model used to quantify the probability that a bullet is fired from a gun.
-LIME explanations would provide a local explanation for an individual prediction, but just as it is important to assess the model for this high-stakes application, it is also important to assess the LIME explanations.
-We will demonstrate an assessment of LIME explanations using the visual diagnostics introduced in this paper.
-
-A random forest model fit to an expanded dataset of \Sexpr{format(dim(bullet_train)[1], big.mark = ",")} land-to-land comparisons from two sets of bullets in the James Hamby Consecutively Rifled Ruger Barrel Study \citep{hamby:2009} was validated in \citet{vanderplas:2020}.
-Here, we train a random forest model to mimic the model validated in \citet{vanderplas:2020} using the same data, model structure, and features (the nine similarity measures developed in \citet{hare:2017}).
-We apply the trained random forest model to 6 bullets from another set of the Hamby study with \Sexpr{dim(bullet_test)[1]} rows of land comparisons.
-See the supporting information for further descriptions of the data.
-
-The newly trained random forest has an out-of-bag accuracy of \Sexpr{bullet_rf_oob_acc} and out-of-bag false positive and false negative rates of \Sexpr{bullet_rf_oob_fp} and \Sexpr{bullet_rf_oob_fn}, respectively.
-On the test data, the random forest performance decreases with an accuracy of \Sexpr{bullet_rf_test_acc} and false positive and false negative rates of \Sexpr{bullet_rf_test_fp} and \Sexpr{bullet_rf_test_fn}, respectively.
-This is an example where explanations of the model predictions could provide insight to the cause of the decrease in model performance on the test data.
-
-We consider a global visualization of the relationship between the random forest predictions and the model features with a parallel coordinate plot of the training data (top facet) and testing data (bottom facets)  (\autoref{fig:figure-09}).
-In the training data we observe a clear difference in feature values based on whether the corresponding random forest scores are close to 1 or 0.
-High values of rough correlation, cross correlation function, and number of matches are indicative of random forest scores close to 1; similarly, low values of mismatches, distance, and non-consecutively matching striae are also associated with random forest scores close to 1.
-Observations in the test data that are classified incorrectly by the random forest tend to have feature values similar to observations in the training data with similar random forest scores.
-For example, the observations in the test set known to be a match but have a random forest score below 0.5 have relatively low values of rough correlation, cross correlation function, and matches and relatively large values of mismatches, distance, and non-consecutively matching striae compared to observations with a random forest probability close to 1.
-
-LIME is applied to all test set observations using different tuning parameter values: 12 sampling methods (2 to 6 equally spaced bins, 2 to 6 quantile-bins, kernel density estimation, and normal approximation) and 3 Gower exponents (0.5, 1, and 10).
-Thus, a total of $12\times 3=36$ different applications of LIME are performed.
-We specify that each LIME explanation return 3 features, and feature selection is performed using the default option in LIME, which selects the features with the highest weights in a ridge regression model.
-
-<<bullet-lime>>=
-
-# Apply LIME to all but two cases without returning the permutations
-if (!file.exists("data/bullet-lime.rds") | !file.exists("data/bullet-explain.rds")){
-
-  # Apply lime with various input options to the Hamby data
-  bullet_lime_explain_noperms <- apply_lime(
-    train = bullet_train %>%
-      select(all_of(bullet_features)),
-    test = bullet_test %>%
-      select(all_of(bullet_features)),
-    model = bullet_rf,
-    label = as.character(TRUE),
-    n_features = 3,
-    sim_method = c('quantile_bins', 'equal_bins',
-                   'kernel_density', 'normal_approx'),
-    nbins = 2:6,
-    feature_select = "auto",
-    dist_fun = "gower",
-    kernel_width = NULL,
-    gower_pow = c(0.5, 1, 10),
-    return_perms = FALSE,
-    all_fs = FALSE,
-    seed = 20190914)
-
-  # Separate the lime and explain parts of the results
-  bullet_lime_noperms <- bullet_lime_explain_noperms$lime
-  bullet_explain_noperms <- bullet_lime_explain_noperms$explain
-
-  # Save the output objects
-  saveRDS(object = bullet_lime_noperms, file = "data/bullet-lime.rds")
-  saveRDS(object = bullet_explain_noperms, file = "data/bullet-explain.rds")
-
-} else {
-
-  # Load the files
-  bullet_explain_noperms <- readRDS("data/bullet-explain.rds")
-
-}
-
-@
-
-<<bullet-lime-perms>>=
-
-# Specify two cases of interest
-bullet_poi_match <- 
-  bullet_test %>% 
-  filter(land_id1 == "Hamby224-Set11-B1-L5", 
-         land_id2 == "Hamby224-Set11-B2-L2") %>% 
-  pull(case)
-bullet_poi_nonmatch <- bullet_test %>% 
-  filter(land_id1 == "Hamby224-Set1-B2-L5", 
-         land_id2 == "Hamby224-Set1-BUnk-L3") %>% 
-  pull(case)
-
-# Apply LIME to two cases with the permutations returned
-bullet_lime_explain_perms <- apply_lime(
-  train = bullet_train %>% select(all_of(bullet_features)),
-  test = bullet_test %>%
-    filter(case %in% bullet_poi_match) %>%
-    bind_rows(bullet_test %>%
-                filter(case %in% bullet_poi_nonmatch)) %>%
-    select(all_of(bullet_features)),
-  model = bullet_rf,
-  label = as.character(TRUE),
-  n_features = 3,
-  sim_method = c(
-    'quantile_bins',
-    'equal_bins',
-    'kernel_density',
-    'normal_approx'
-  ),
-  nbins = 4,
-  feature_select = "auto",
-  dist_fun = "gower",
-  kernel_width = NULL,
-  gower_pow = 0.5,
-  return_perms = TRUE,
-  all_fs = FALSE,
-  seed = 20190914
-)
-
-# Separate the lime and explain parts of the results
-bullet_lime_perms <- bullet_lime_explain_perms$lime
-bullet_explain_perms <- bullet_lime_explain_perms$explain %>%
-  mutate(case = ifelse(case == 1,
-                       bullet_poi_match,
-                       bullet_poi_nonmatch) %>% as.character())
-
-@
-
-<<bullet-lime-combined>>=
-
-# Determine the application and case number of the poi
-# in the no_perms data
-poi_cases_no_perms <- bullet_explain_noperms %>%
-  filter(case %in% c(bullet_poi_match, bullet_poi_nonmatch),
-         nbins %in% c(4, NA),
-         gower_pow == 0.5) %>%
-  select(case, implementation) %>%
-  unique()
-
-# Join the no perms data (with poi removed) with the
-# perms data (perms removed)
-bullet_explain <- bullet_explain_noperms %>%
-  anti_join(poi_cases_no_perms,
-            by = c("implementation", "case")) %>%
-  bind_rows(
-    bullet_explain_perms %>%
-      mutate(implementation = fct_recode(implementation,
-          "3" = "1",
-          "8" = "2",
-          "31" = "3",
-          "32" = "4"
-        )
-      ) %>%
-      select(
-        -perms_raw,-perms_numerified,
-        -perms_pred_simple,-perms_pred_complex,
-        -weights
-      )
-  )
-
-@
-
-\subsection{LIME Assessment Visualizations} \label{bullet-assess-ex}
-
-To get an overview of the LIME explanations from the 36 applications, we consider a feature heatmap (\autoref{fig:figure-10}).
-In addition to facets for simulation method and LIME feature importance, this plot includes a vertical facet for Gower power and a horizontal facet for whether the observation is a known match or non-match.
-This plot highlights several key features of the LIME explanations from the bullet matching dataset.
-
-First, applications of 2-quantile-bin simulations produce the same explanations for almost all cases and LIME tuning parameter values.
-This suggests that the LIME explanations are global and not local.
-Second, within a simulation method, the features selected by LIME for an observation do not appear to vary by the Gower power.
-However, the LIME explanation for an observation often varies across simulation methods.
-With the equal-bins, there are vertical stripes that suggest a dependence of the LIME explanations on the number of bins.
-The vertical stripes are not as apparent with the quantile bins.
-Lastly, there are clear differences between the LIME explanations produced by the bin based simulation methods for the matches and non-matches.
-This suggests that different features are of importance in the random forest, depending on whether the observation corresponds to match or non-match.
-
-\begin{figure*}[!thp]
-<<figure-10, out.width = '6.5in', fig.width = 18, fig.height = 14>>=
-
-# Specify the figure size (for determining font size)
-f11_ow = 6.5
-f11_fw = 18
-f11_fs = fs * (f11_fw / f11_ow)
-
-# Create a feature heatmap
-plot_feature_heatmap(
-  bullet_explain %>%
-    mutate(
-      label = as.factor(label),
-      feature = fct_recode(
-        feature,
-        "Rough Correlation" = "rough_cor",
-        "Consecutively Matching Striae" = "cms",
-        "Distance" = "D",
-        "Matches" = "matches",
-        "Mismatches" = "mismatches",
-        "Non-Consecutively Matching Striae" = "non_cms",
-        "Cross Correlation Function" = "ccf",
-        "Sum of Peaks" = "sum_peaks",
-        "Distance Standard Deviation" = "sd_D"
-      )
-    ),
-  facet_var = bullet_test %>%
-    mutate(samesource = fct_recode(
-      factor(samesource),
-      "Match" = "TRUE",
-      "Non-Match" = "FALSE"
-    )) %>%
-    pull(samesource),
-  order_method = "PCA"
-) +
-  scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) +
-  scale_color_gretchenalbrecht(palette = "last_rays",
-                               discrete = TRUE,
-                               reverse = TRUE) +
-  theme_bw(base_family = ff, base_size = f11_fs) +
-  theme(
-    axis.text.y = element_blank(),
-    axis.ticks.y = element_blank(),
-    strip.background = element_rect(color = "white", fill = "white"),
-    strip.text.y.right = element_text(angle = 0, size = f11_fs*0.7),
-    strip.text.x = element_text(size = f11_fs*0.7),
-    legend.position = "bottom",
-    axis.text.x = element_text(angle = 45, hjust = 1)
-  ) +
-  guides(fill = guide_legend(nrow = 3)) +
-  labs(y = "Case", color = "Complex Model Feature", fill = "Complex Model Feature")
-
-@
-\caption{Feature heatmap of 36 LIME applications to the bullet comparison data test set.
-In addition to faceting the results by simulation method and LIME feature selection order, facets for the Gower power and whether the observation is a match or non-match are included.
-The vertical stripes of features selected indicate a dependence between the LIME explanations and tuning parameter values.}
-\label{fig:figure-10}
-
-\vspace*{\floatsep}
-
-<<figure-11, out.width = '6.5in', warning = FALSE, fig.width = 10, fig.height = 4.25>>=
-
-# Specify the figure size (for determining font size)
-f12_ow = 6.5
-f12_fw = 10
-f12_fs = fs * (f12_fw / f12_ow)
-f12_ls = 0.5 * (f12_fw / f12_ow)
-
-# Create a metric comparison plot
-plot_metrics(
-  bullet_explain %>%
-    mutate(label = as.factor(label)),
-  add_lines = TRUE,
-  line_alpha = 0.75,
-  line_size = f12_ls
-) +
-  theme_bw(base_family = ff, base_size = f12_fs) +
-  theme(
-    strip.background = element_rect(color = "white", fill = "white"),
-    strip.placement = "outside",
-    strip.text.y = element_text(size = f12_fs)
-  )
-
-@
-\caption{Assessment metric plot for the applications of LIME on the bullet comparison data test set.
-There are discrepancies in performance across metrics for a set of tuning parameter values, but based on the overall performance of all three metrics, 4-equal-bins with a Gower power of 0.5 appears to perform the best.}
-\label{fig:figure-11}
-\end{figure*}
-
-To try to identify a set of LIME tuning parameter values with the most trustworthy set of explanations, an assessment metric plot is considered (\autoref{fig:figure-11}).
-The performance of a set of tuning parameter values often do not agree across metrics.
-For example, both density methods perform well according to average fidelity but poorly according to MSEE.
-All quantile bin methods perform well according to average $R^2$ but poorly based on average fidelity and MSEE.
-However, there is consistency in results across different Gower powers.
-The applications using a power of 0.5 perform the best or as well as the other powers across all simulation methods suggesting that the power that leads to a more global explanation is preferred by LIME.
-It is not apparent which set of tuning parameters is the best.
-Considering all three metrics, we might conclude that the 4-equal-bins with a Gower power of 0.5 performs better than the other tuning parameter values considered.
-
-To provide a more detailed view of explanations obtained using different tuning parameter values, we take a closer look at explanations for two observations of interest, which will be referred to as case M (a known match) and case NM (a known non-match), using explanation scatterplots.
-Figure~\ref{fig:figure-12} includes the visual representation plots of explanations (from \emph{lime}) and explanation scatterplots for cases M and NM.
-Plots for 4-equal-bins and 4-quantile-bins are included to depict tuning parameter values with good (4-equal-bins) and mediocre (4-quantile-bins) performance based on the assessment metric plot.
-Plots for the kernel density simulation method are included in Appendix~\ref{exp-scatter_plus} (Figure \ref{fig:figure-B2}).
-
-We focus on the explanation for case NM with 4-quantile-bins.
-The explanation plot from \emph{lime} shows that the observed values of NM of mismatches less than or equal to 7.17, rough correlation (rough\_cor) greater than 0.05, and D less than or equal to 0.002 support a random forest prediction in favor of a match.
-The scatter plots show that many of the simulated values in the rectangular regions with mismatches less than 7.17, rough correlation greater than 0.05, and distance less than or equal to 0.002 have random forest predictions greater than 0.5, which agrees with the LIME explanation.
-However, the random forest assigns a probability of 0.21 to case NM, which is not explained by the LIME explanation that provides all explanations in support of a match.
-Instead, consider that a better explanation based on the scatterplots would be that the random forest assigned a prediction probably below 0.5 since NM has observed values of mismatches less than 5, rough correlation greater than 0.25, and distance greater than 0.001.
-
-The other explanation scatterplots can be interpreted in a similar manner.
-The three plots depict situations where the explanations are faithful to the random forest, but the regions captured by the intersections of the bins do not align well with the regions containing similar probabilities produced by the random forest.
-
-\begin{figure*}[!thp]
-<<figure-12, out.width = '6.25in', fig.width = 13, fig.height = 17.5, message = FALSE>>=
-
-# Specify the figure size (for determining font size)
-f13_ow = 6.25
-f13_fw = 13
-f13_fs = fs * (f13_fw / f13_ow)
-f13_ls = 0.5 * (f13_fw / f13_ow)
-
-# Adjust names of the cases
-bullet_explain_perms_clean <- bullet_explain_perms %>%
-  mutate(case = ifelse(case == bullet_poi_nonmatch, "NM", "M"))
-
-# Create a theme for the lime explanation visualizations
-bullet_explain_plot_theme <-
-  list(
-    scale_fill_manual(values = c("darkorange", "grey50")),
-    theme(
-      text = element_text(family = ff, size = f13_fs),
-      strip.text.x = element_text(face = "plain", size = f13_fs)
-    )
-  )
+fe5_ow = 6.25
+fe5_fw = 13
+fe5_fs = fs * (fe5_fw / fe5_ow)
+fe5_ls = 0.5 * (fe5_fw / fe5_ow)
 
@@
 pfM_3qb <- plot_features(bullet_explain_perms_clean[1:3,]) + bullet_explain_plot_theme
-pfNM_3qb <- plot_features(bullet_explain_perms_clean[4:6,]) + bullet_explain_plot_theme
 pfM_3eb <- plot_features(bullet_explain_perms_clean[7:9,]) + bullet_explain_plot_theme
-pfNM_3eb <- plot_features(bullet_explain_perms_clean[10:12,]) + bullet_explain_plot_theme
-
-# Create theme for explanation scatterplots
-bullet_eoi_plot_theme <-
-  list(
-    scale_color_gradient2(
-      low = "grey50",
-      high = "darkorange",
-      midpoint = 0.5,
-      limits = c(0, 1)
-    ),
-    scale_fill_gradient2(
-      low = "grey50",
-      high = "darkorange",
-      midpoint = 0.5,
-      limits = c(0, 1)
-    ),
-    theme_bw(base_family = ff, base_size = f13_fs),
-    theme(
-      aspect.ratio = 1,
-      plot.title = element_text(size = f13_fs),
-      strip.text.x = element_text(size = f13_fs),
-      strip.text.y = element_text(size = f13_fs),
-      strip.placement = "outside",
-      strip.background = element_rect(color = "white", fill = "white")
-    ),
-    guides(size = guide_legend(nrow = 2, byrow = T), 
-           linetype = guide_legend(override.aes = list(color = c("grey50", "darkorange"))))
-  )
 
@@
     weights = TRUE,
-    line_size = f13_ls
-  ) +
-  bullet_eoi_plot_theme +
-  guides(linetype = guide_legend(override.aes = list(color = c("darkorange"))))
-eoiNM_3qb <-
-  plot_explain_scatter(
-    bullet_explain_perms_clean[4:6, ],
-    alpha = 0.9,
-    weights = TRUE,
-    line_size = f13_ls
+    line_size = fe5_ls
   ) +
@@
     weights = TRUE,
-    line_size = f13_ls
+    line_size = fe5_ls
   ) +
@@
   guides(linetype = guide_legend(override.aes = list(color = c("darkorange"))))
-eoiNM_3eb <-
-  plot_explain_scatter(
-    bullet_explain_perms_clean[10:12,],
-    alpha = 0.9,
-    weights = TRUE,
-    line_size = f13_ls
-  ) +
-  bullet_eoi_plot_theme
 
@@
 plot_grid(
-  pfNM_3qb,
-  pfNM_3eb,
-  eoiNM_3qb,
-  eoiNM_3eb,
   pfM_3qb,
@@
   eoiM_3eb,
-  nrow = 4,
-  rel_heights = c(0.2, 0.3, 0.2, 0.3)
-)
-
-@
-\caption{Plots of LIME explanations (first and third rows) and explanation scatterplots (second and fourth rows) for  cases M and NM in the bullet test data for two tuning parameter values: 4-quantile-bins (first column) and 4-equal-bins (second column).
+  nrow = 2,
+  rel_heights = c(0.2, 0.3)
+)
+
+@
+\caption{Plots of LIME explanations (first row) and explanation scatterplots (second row) for case M in the bullet test data for two tuning parameter values: 4-quantile-bins (first column) and 4-equal-bins (second column).
 The plots provide insights into the LIME explanations and allow for the assessment of the explanation quality.}
-\label{fig:figure-12}
+\label{fig:figure-e5}
 \end{figure*}
 
-Without applying LIME with multiple tuning parameter values to the bullet test data or viewing diagnostic plots of the LIME explanations, it may be very possible to formulate reasons why the LIME explanations make sense.
-However, the sequence of plots in this section (Figures \ref{fig:figure-10}, \ref{fig:figure-11}, and \ref{fig:figure-12}) suggest that we should be cautious to trust any of these LIME explanations.
-It appears that either LIME needs to be further tuned to provide trustworthy and good explanations, or a different approach may provide better insight.
-
-\section{Discussion} \label{discussion}
-
-This paper highlights that while an explainer model is meant to provide clarity, it actually adds another layer of complexity to predictive models by requiring yet another model that needs to be assessed.
-Without an assessment of the explainer model, LIME is a black-box procedure of its own requiring blind trust in the explainer model.
-We suggest the use of visual diagnostics to counteract the black-box nature of LIME and provide three diagnostic plots.
-
-The visualizations are intended to provide insight on how LIME works, assess the ability of the explainer model to capture the complex predictive model, and compare LIME explanations produced by different tuning parameter values.
-While the visualizations accomplish these tasks, they also expose examples of the failings of LIME.
-To address the discovered failings of LIME, we reconsider each of the claims about the performance of LIME made by \citet{ribeiro:2016} in light of the insights gained from the diagnostic visualizations.
-
-As previously discussed, the \textbf{interpretability} of the LIME explanations is controllable  by the complexity of the explainer model.
-For example, the number of bins selected for simulation can control the interpretability of the explanations.
-If too many bins are selected, the bin range that is reported in the LIME explanation will be too small to be meaningful in the context of the feature.
-An appropriate choice of the number of bins will keep the bin range meaningful.
-Thus, the claim of interpretability does not need to be assessed using the visualizations.
-However, diagnostic visualizations do present a different perspective on the meaning of interpretability.
-
-Even though an explanation will be interpretable as long as the complexity of the explainer model is appropriately chosen, a lack of understanding of the process used to create the explanation could lead to an incorrect interpretation of the explanation.
-For example, the visualization of a LIME explanation available from the \emph{lime} R package \citep{pedersen:2020} (shown in Figures \ref{fig:figure-03} and \ref{fig:figure-12}) is a major simplification of the explainer model, which could lead to under-interpreted or misinterpreted LIME explanation.
-Supplementing \citet{pedersen:2020}'s compact visualization of the explanation with an explanation scatterplot that shows a more detailed visualization of the explainer model promotes a more complete understanding of the explanation (such as Figures~\ref{fig:figure-03} and \ref{fig:figure-12}).
-
-Even with an explainer model that is interpreted correctly, the interpretation is worthless if the explainer model is not \textbf{faithful} to the complex model.
-This claim can be assessed using the diagnostic plots suggested in this paper.
-Many of the visualizations in this paper highlight problems with the faithfulness of the explainer models.
-The explanation scatterplots allow for a comparison of the explainer model to the complex model.
-The examples in this paper show cases where the explainer model bins do not accurately capture the regions with similar random forest probabilities that contain the prediction of interest and oversimplify the model (Figures \ref{fig:figure-03} and \ref{fig:figure-12}).
-Using fewer bins would clearly not help improve the faithfulness of the explainer model in these examples, and while an increase in the number of bins would lead to a finer resolution of the random forest classification boundaries, interpretability of the explainer model would quickly be lost.
-Perhaps this could be improved by allowing the bin creation to account for the relationships between the features and response variable or a different number of bins for each feature.
-
-In addition to assessing faithfulness by visually comparing the complex and explainer model, we propose a visual comparison of two faithfulness metrics (MSEE and average fidelity).
-The examples of faithfulness metric comparisons in this paper both produced conflicting results (Figures \ref{fig:figure-06} and \ref{fig:figure-11}).
-This makes it difficult to decide on a recommendation of a set of tuning parameter values that produce the explanations with the most faithful explainer model.
-
-The metric comparison plot also includes a comparison of average $R^2$ values, which is a metric that can be used to assess the claim of \textbf{linearity}.
-Most of the average $R^2$ values in the examples from this paper are below 0.5 suggesting a poor linear fit of the explainer models.
-A poor linear fit of the explainer model is also seen with the residual plot (\autoref{fig:figure-C3}).
-
-The final claim, \textbf{localness}, is addressed by the feature heatmap and metric comparison plots.
-As stated, the feature heatmap reveals that the density simulation methods in the \data \ example  results in global explanations where the same features are repeatedly chosen across all (or almost all) observations in the set of explanations.
-This finding agrees with that of \citet{laugel:2018} who found LIME produced global explanations with the normal approximation simulation method.
-For the bin based simulation methods in the bullet data example, the feature heatmap shows that the features chosen for the explanations vary between the two classification categories (match versus non-match).
-This is an interesting finding that suggests that different features can play a role in the predictions of observations in different response categories.
-Furthermore, while the metric comparison plot in the bullet example does not provide agreement between metrics on a best bin based method, all metrics agree that a Gower power of 0.5 for computing the model weights associated with distance of a simulated data point from the prediction of interest is the best.
-This suggests that a less local explanation provides a better explanation of the performance of the random forest.
-
-Some of the visualizations in the paper generalize easily to any application of LIME such as the feature heatmap and metric plot.
-Other plots such as the visualizations of the LIME procedure would require extensions such as the use of scatterplot matrices to compare explanations with more than two features.
-The addition of interactivity to the diagnostic plots would provide additional enhancement of the assessment process.
-For example, a diagnostic plot that provides a summary of multiple LIME explanations, such as the feature heatmap, could be displayed and clicked on to reveal more detailed figures associated with individual predictions of interest, such as an explanation scatterplot.
-
-The largest limitation to the diagnostic visualizations is the dimensionality of the data shown, both in the number of dimensions or features as well as the number of observations.
-Fortunately, in the situation of LIME, both of these aspects are rather well controlled: LIME relies heavily on simulations to generate data scenarios that are close to the data observed but exhibit variability.
-Effects from overplotting should be relatively mild, because output from simulations is shown, which is expected to be (relatively) continuous such that overplotting only occurs for points with (relatively) similar values.
-In that respect, the diagnostics shown for the \data \ and the bullet example are representative of what is expected.
-But in cases where overplotting does become problematic, the user could either simply reduce the size of the simulations or use some well-studied binning techniques in the visualizations, as discussed for example in \citet{carr:1987} or \citet{unwin:2006}.
-
-While it would be ideal if LIME could be used as a method to provide easily understandable explanations for black-box models as \citet{ribeiro:2016} claim, that dream is not yet a reality.
-The examples using diagnostic plots to assess LIME in this paper show frequent issues with LIME.
-We hope that our plots provide motivation to assess LIME explanations, to not blindly use the default settings (even if it is not clear how to tune the parameters), and to encourage work on improving LIME, so that it can be a lime and not a lemon.
-
-\section*{Acknowledgments}
-
-HH was partially funded by the Center for Statistics and Applications in Forensic Evidence (CSAFE) through Cooperative Agreement 70NANB20H019 between NIST and Iowa State University, which includes activities carried out at Carnegie Mellon University, Duke University, University of California Irvine, University of Virginia, West Virginia University, University of Pennsylvania, Swarthmore College and University of Nebraska, Lincoln.
-
-\subsection*{Author contributions}
-
-{\bf Katherine Goode, Heike Hofmann}: Conceptualization, Methodology, Investigation, Visualizations, Writing - Reviewing and Editing. {\bf Katherine Goode}: Writing - Initial Draft, Software.
-
-\subsection*{Financial disclosure}
-
-None reported.
-
-\subsection*{Conflict of interest}
-
-The authors declare no potential conflict of interests.
-
-\section*{Supporting information}
-
-The code used to produce the manuscript and the data from examples in Section \ref{application} are available in the following GitHub Repository: \href{https://github.com/goodekat/LIME-diagnostics-paper}{https://github.com/goodekat/LIME-diagnostics-paper}.
-
-\bibliography{references}
-
-\newpage
-
-\appendix
-
-\section{LIME Tuning Parameter Options} \label{lime-details}
-
-The following tuning parameters for the LIME algorithm are available in the \emph{lime} R package \citep{pedersen:2020}.
-
-\begin{itemize}
-
-\item Data simulation methods:
-
-\begin{itemize}
-\item Equally spaced bins: observations are uniformly sampled from equally spaced bins (number of bins may be specified)
-\item Quantile bins: observations are uniformly sampled from quantile bins (number of bins may be specified)
-\item Normal density approximation: observations are sampled from a normal distribution with mean and standard deviation computed from the corresponding feature
-\item Kernel density approximation: observations are sampled from an kernel density approximation of the corresponding feature
-\end{itemize}
-
-\item Number of observations to simulate
-
-\item Distance metric for determining proximity to the prediction of interest: Gower distance (where the power may be specified) or exponential kernel (where the kernel width may be specified)
-
-\item Number of features to return in an explanation
-
-\item Feature selection method for determining the features to return in an explanation: forward selection applied to a ridge regression, features with the largest magnitude coefficients in ridge regression, LASSO, classification/regression tree splits
-
-\end{itemize}
-
-\section{Explanation Scatterplots Under Other Simulation Scenarios} \label{exp-scatter_plus}
-
-Section \ref{exp-scatter} introduces explanation scatterplots under the default simulation method in the \emph{lime} R package: 4-quantile-bins.
-The structure of an explanation scatterplot remains the same if any bin based simulation method is used, i.e., any number of quantile or equally spaced bins.
-However, if the kernel density or normal approximation simulation methods are used, the format of the explanation scatterplot changes.
-In the density based simulation method scenarios, LIME uses the standardized versions of the predictor variables to fit the explainer model.
-Thus, the explainer model needs to be represented differently in the explanation scatterplot.
-
-When the kernel density or normal approximation simulation methods are applied, the explanation scatterplot depicts the complex model by plotting the complex model predictions versus a feature selected in LIME the explanation from the simulated data.
-The explainer model is included as a line on the figure where all features excluding the one plotted on the x-axis are set to the observed values of the prediction of interest.
-An explanation scatterplot is created for each feature included in the LIME explanation.
-As with the bin based simulation method, the size of the points represent the weight assigned by LIME.
-
-Figure \ref{fig:figure-B1} provides example explanation scatterplots for each feature in the default LIME explanation obtained using the kernel density simulation method for the \data \ prediction of interest.
-Figure \ref{fig:figure-B2} includes explanation scatterplots for the explanations generated using kernel density simulation for the bullet example cases M and NM discussed in Section \ref{bullet-assess-ex}.
-
-\begin{figure*}[!thp]
-<<figure-B1, out.width = '6.5in', fig.width = 12, fig.height = 5, fig.align = "center">>=
-
-# Specify the figure size (for determining font size and line size)
-fb1_ow = 6.5
-fb1_fw = 12
-fb1_fs = fs * (fb1_fw / fb1_ow)
-fb1_ls = 0.5 * (fb1_fw / fb1_ow)
-
-# Create the explanation scatterplot
-plot_explain_scatter(
-  sine_lime_explain$explain %>%
-    filter(sim_method == "kernel_density", case == sine_poi %>% pull(case)),
-  alpha = 0.75,
-  title.opt = FALSE, 
-  line_size = fb1_ls 
-) +
-  theme_bw(base_family = ff, base_size = fb1_fs) +
-  theme(
-    strip.background = element_rect(fill = "white", color = "white"),
-    strip.placement = "outside",
-    strip.text.x = element_text(size = fb1_fs)
-  )
-
-@
-\caption{Explanation scatterplots for the \data \ prediction of interest with the kernel density simulation method.}
-\label{fig:figure-B1}
-\end{figure*}
-
-\begin{figure*}[!thp]
-<<figure-B2, out.width = '6.5in', fig.width = 12, fig.height = 10, fig.align = "center">>=
-
-# Specify the figure size (for determining font size and line size)
-fb2_ow = 6.5
-fb2_fw = 12
-fb2_fs = fs * (fb2_fw / fb2_ow)
-fb2_ls = 0.5 * (fb2_fw / fb2_ow)
-
-# Create the explanation scatterplot: case M, kernel density
-bullet_es_M <-
-  plot_explain_scatter(
-    bullet_explain_perms[16:18, ] %>% mutate(case = "NM"),
-    alpha = 0.75,
-    title.opt = TRUE,
-    line_size = fb2_ls
-  ) +
-  scale_fill_gradient2(
-    low = "grey50",
-    high = "darkorange",
-    midpoint = 0.5,
-    limits = c(0, 1)
-  ) +
-  theme_bw(base_family = ff, base_size = fb2_fs) +
-  theme(
-    aspect.ratio = 1,
-    strip.background = element_rect(fill = "white", color = "white"),
-    strip.placement = "outside",
-    strip.text.x = element_text(size = fb2_fs),
-    plot.title = element_text(size = fb2_fs)
-  )
-
-# Create the explanation scatterplot: case NM, kernel density
-bullet_es_NM <-
-  plot_explain_scatter(
-    bullet_explain_perms[13:15, ] %>% mutate(case = "M"),
-    alpha = 0.75,
-    title.opt = TRUE, 
-    line_size = fb2_ls
-  ) +
-  scale_fill_gradient2(
-    low = "grey50",
-    high = "darkorange",
-    midpoint = 0.5,
-    limits = c(0, 1)
-  ) +
-  theme_bw(base_family = ff, base_size = fb2_fs) +
-  theme(
-    aspect.ratio = 1,
-    strip.background = element_rect(fill = "white", color = "white"),
-    strip.placement = "outside",
-    strip.text.x = element_text(size = fb2_fs), 
-    plot.title = element_text(size = fb2_fs)
-  )
-
-# Join the plots
-plot_grid(bullet_es_NM, bullet_es_M, nrow = 2)
-
-@
-\caption{Explanation scatterplots for LIME explanations using kernel density simulation for the cases M and NM of the bullet comparison test data.}
-\label{fig:figure-B2}
-\end{figure*}
-
-\section{Explainer Model Residual Plot} \label{residual-plot}
-
-In order to assess the claim of linearity for the \data \ prediction of interest discussed in Section \ref{exp-scatter}, we use one of the most basic diagnostics in a statistician's tool box and draw a residual plot for the explainer model.
-This is shown in Figure \ref{fig:figure-C3} with the explainer model residuals on the y-axis and explainer model predictions on the x-axis.
-The points along the x-axis have been jittered to ease the effect of the over-plotted points in the visualization.
-There is a clear increasing trend in the residuals as the explainer model predictions increase.
-This is a clear violation of the linearity assumption with the ridge regression model.
-
-\begin{figure}[!thp]
-<<figure-C3, out.width = '3.125in', fig.width = 5, fig.height = 4, warning = FALSE>>=
-
-# Specify the figure size (for determining font size and line size)
-fc3_ow = 3.125
-fc3_fw = 5
-fc3_fs = fs * (fc3_fw / fc3_ow)
-fc3_ls = 0.5 * (fc3_fw / fc3_ow)
-
-# Calculate the residuals from the explainer model
-y <- sine_poi_perms$rfpred
-sine_poi_explainer <-
-  function(x1, x2)
-    sine_b0 + (sine_b1 * x1) + (sine_b2 * x2)
-sine_poi_perms <- sine_poi_perms %>%
-  mutate(exppred = sine_poi_explainer(x1num, x2num)) %>%
-  mutate(resid = exppred - rfpred)
-
-# Create the residual plot
-ggplot(sine_poi_perms, aes(x = exppred, y = resid)) +
-  geom_hline(yintercept = 0, size = fc3_ls) +
-  geom_jitter(alpha = 0.5, width = 0.02) +
-  theme_bw(base_family = ff, base_size = fc3_fs) +
-  theme(plot.title = element_text(size = fc3_fs)) +
-  labs(x = "Explainer Model Predictions",
-       y = "Explainer Model Residuals",
-       title = "Explainer Model Residual Plot")
-
-@
-\caption{Residual plot of the explainer model associated with \data \ prediction of interest from Section \ref{exp-scatter}.
-The residuals are plotted against the predicted values.
-The points are jittered in the x-direction to alleviate the over-plotting of points.
-There is an upward trend in the residuals as the explainer model predictions increase, which suggests a violation of the linearity assumption.}
-\label{fig:figure-C3}
-\end{figure}
-
-\section{Details on Assessment Metrics} \label{metric-details}
-
-Suppose $f$ is a complex model, and let $\textbf{X}$ be a matrix of observed data with $K$ features and $E$ observations where $x_e$ is an observed feature vector for observation $e$.
-Let $f(x_e)$ be the complex model prediction for observation $e$.
-It is of interest to explain the predictions made by $f$ applied to $X$ using LIME.
-
-For $x_e$ and a set of tuning parameter values $t$, let $\textbf{X}_{e,t}'$ be the LIME simulated dataset with $K$ features and $S$ rows such that $x'_{e,t,s}$ is the feature vector for simulated data point $s$ corresponding to explanation $e$ and tuning parameter values $t$.
-Let $\textbf{Z}'_{e,t}$ be the matrix of simulated data transformed to bin indicator variables (for bin based simulation methods) or standardization (for density based simulation methods) with $K$ features and $S$ observations such that $z'_{e,t,s}$ is the interpretability transformed feature vector for explanation $e$, tuning parameter values $t$, and simulated data point $s$.
-Note that $z_{e,t}$ will represent the  transformed version of $x_e$.
-
-Next, let $\omega_t$ represent a proximity distance metric corresponding to tuning parameter values $t$.
-Then $\omega_t\left(x_e, x'_{e,t,s}\right)$ is the weight assigned to $x'_{e,t,s}$, which is the proximity between $x_e$ and $x'_{e,t,s}$.
-Allow $g_{e,t}$ to be the explainer model for an explanation $e$ and tuning parameter values $t$.
-Thus, $g_{e,t}\left(z'_{e,s,t}\right)$ is the explainer model prediction for the interpretability transformed simulated data point $s$.
-
-For a set of $E$ explanations and a set of tuning parameter values $t$, we define the assessment metrics as follows:\\
-\\
-\emph{Average $R^2$} is denoted as $R^2_{\mbox{ave}}$ and computed as
-
-  $$R^2_{\mbox{ave}} = \frac{1}{E}\sum_{e=1}^E R_{e,t}^2$$
-
-\noindent where $R_{e,t}^2$ is the $R^2$ value for $g_{e,t}$.\\
-\\
-\emph{Average fidelity} is denoted by $\mathcal{L}_{\mbox{ave}}$ and computed as
-
-\begin{eqnarray*} \mathcal{L}_{\mbox{ave}} & = & \frac{1}{E}\sum_{e=1}^E\mathcal{L}(f, \ g_{e,t}, \ \pi_{t}) \\ & = & \frac{1}{E}\sum_{e=1}^E\sum_{s=1}^{S}\omega_{t}\left(x_e, x'_{e,t,s}\right)\left(f\left(x'_{e,t,s}\right)-g_{e,t}\left(z_{e,t,s}'\right)\right)^2.
-\end{eqnarray*}
-
-\noindent where $\mathcal{L}$ is the fidelity metric originally defined in \citet{ribeiro:2016}.\\
-\\
-\emph{Mean squared explanation error} is denoted by MSEE and computed as
-
-$$MSEE=\frac{1}{E}\sum_{e=1}^E\left(f\left(x_e\right)-g_{e,t}\left(z_{e,t}\right)\right)^2.$$
-
 \end{document}

### 2020-12-15 paper.tex
more trimming

@@
 
+\begin{figure*}[!thp]
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+
+{\centering \includegraphics[width=6.5in]{figure/figure-03-1}
+
+}
+
+\end{knitrout}
+\caption{(left) Visualization from the \emph{lime} R package of a LIME explanation for the \data \ prediction of interest identified in \autoref{fig:figure-02}.
+(right) \emph{Explanation Scatterplot}.
+\sout{The points represent the simulated data colored by the random forest probabilities and sized by the assigned LIME weights.
+The prediction of interest is shown as the diamond shaped point.
+The explainer model indicator variables associated with $x_1$ and $x_2$ (quantile bins containing the prediction of interest) are depicted by the solid lines.
+The line colors represent the explainer model coefficient signs and indicate whether the feature supports a prediction of `blue' (blue lines) or supports a prediction of `red' (red lines).} \kge{An explanation scatterplot associated with the explanation for the prediction of interest depicted on the left.} \sout{This figure shows that t}\kge{T}he \kge{4} quantile bins are not flexible enough to capture the relationship between the random forest predictions and the $x_1$ and $x_2$ values.}
+\label{fig:figure-03}
+\end{figure*}
+
 In this section, we introduce three visual diagnostic plots \sout{for the assessment of LIME.
@@
 The \data \ contains 600 observations with \sout{three features and one response variable.
-The} features\sout{,} \kge{of} $x_1$, $x_2$, and $x_3$\sout{,} \kge{that} are randomly sampled from Unif(-10, 10), Unif(-10, 10), and $\mbox{N}(0,1)$ distributions, respectively.
+The} features\sout{,} \kge{of} $x_1$\sout{,} \kge{and} $x_2$ \kge{independently sampled from Unif(-10, 10) distributions}\sout{,} and $x_3$\sout{,} \sout{\kge{that} are randomly sampled from Unif(-10, 10), Unif(-10, 10), and} \kge{sampled from a} $\mbox{N}(0,1)$ distribution\sout{s, respectively}.
 A binary response variable $y$ is created using a \sout{rotated} sine curve \sout{.
@@
 The dataset is \kge{randomly} divided into training and testing sets of 500 and 100 observations, respectively.
-A random forest is fit using the R package \emph{randomForest} (version 4.6.14) \citep{liaw:2002} with the default settings\sout{.
+A random forest is fit \kge{to the training set} using the R package \emph{randomForest} (version 4.6.14) \citep{liaw:2002} with the default settings\sout{.
 The model} \kge{and} is applied to the test set to obtain predictions.
@@
 The default methods for feature selection (forward selection) and the computation of the weights (Gower distance raised to an exponent of 1) are used for all applications.
-(See Appendix~\ref{lime-details} for descriptions of the tuning parameters.)
-
-For the presentation of the explanation scatterplot, we focus on the misclassified point with $(x_1, x_2, x_3)$ coordinates of (1.23, 8.47, -0.99) indicated by a diamond in \autoref{fig:figure-02}.
+See Appendix~\ref{lime-details} for \kge{more detailed} descriptions of the tuning parameters.
+
+For the presentation of the explanation scatterplot, we focus on the misclassified point \sout{with $(x_1, x_2, x_3)$ coordinates of (1.23, 8.47, -0.99)} indicated by a diamond in \autoref{fig:figure-02}.
 Misclassified points are often of interest to explain since they may provide information about ways to improve the model.
@@
 
-\begin{figure*}[!thp]
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-
-{\centering \includegraphics[width=6.5in]{figure/figure-03-1}
-
-}
-
-\end{knitrout}
-\caption{(left) Visualization from the \emph{lime} R package of a LIME explanation for the \data \ prediction of interest identified in \autoref{fig:figure-02}.
-(right) \emph{Explanation Scatterplot}.
-The points represent the simulated data colored by the random forest probabilities and sized by the assigned LIME weights.
-The prediction of interest is shown as the diamond shaped point.
-The explainer model indicator variables associated with $x_1$ and $x_2$ (quantile bins containing the prediction of interest) are depicted by the solid lines.
-The line colors represent the explainer model coefficient signs and indicate whether the feature supports a prediction of `blue' (blue lines) or supports a prediction of `red' (red lines).
-This figure shows that the quantile bins are not flexible enough to capture the relationship between the random forest predictions and the $x_1$ and $x_2$ values.}
-\label{fig:figure-03}
-\end{figure*}
-
 \paragraph{A Visual Representation of a LIME Explanation}
@@
 Before introducing the visual diagnostics, let us consider a commonly used visualization of a LIME explanation\sout{ that is shown in Figure \ref{fig:figure-03} (left)}.
-\kge{Figure \ref{fig:figure-03} (left) shows the explanation for the prediction of interested indicated in \autoref{fig:figure-02} obtained using 4-quantile-bins.} \sout{The plot is created using the \emph{lime} R package and provides a visual representation of a LIME explanation for the prediction of interest indicated in \autoref{fig:figure-02}.
-In particular, the explanation is obtained using 4-quantile-bins to simulate the data.} In this scenario, LIME converts continuous predictor variables to indicator variables identifying whether the variable value falls in the same quantile bin as the prediction of interest or not.
-The indicator variables are used as the explainer model features.
-
-The plot reports 0.74 as  the random forest  probability  that the observation of interest belongs to category blue (denoted as the ``label" in the plot).
+\kge{Figure \ref{fig:figure-03} (left) depicts the explanation for the prediction of interest indicated in \autoref{fig:figure-02} obtained using 4-quantile-bins.
+In the text at the top, the "Probability" is the random forest probability of 0.74 that the observation of interest belongs to the "Label" category of blue.
+The "Explanation Fit" is the deviance ratio of 0.21 associated with the ridge regression explainer model (often interpreted as an $R^2$), which suggests that the explainer model is not a good linear fit.}
+
+\kge{Since 4-quantile-bins are used to simulate data, LIME converts continuous predictor variables to indicator variables identifying whether the variable value falls in the same quantile bin as the prediction of interest or not.
+The indicator variables are used as the features in the ridge regression explainer model.
+The features included in the visualization are the ones selected by feature selection, the lengths of the bars represent the coefficients from the ridge regression associated with the indicator variables, and the color of a bar denotes the sign of the coefficient.
+This explainer model explains that the random forest prediction that the observation of interest belongs to the category of blue is mostly supported by the prediction of interest having a value of $x_2$ that is greater than 4.834 but somewhat contradicted by the prediction of interest having a value of $x_1$ that is greater than -0.302 and less than or equal to 4.844.} \kgc{I decided to leave the values here, because this is how I would interpret this explanation, but I cut out a lot of text from this subsection in other ways.}
+
+\sout{Before introducing the visual diagnostics, let us consider a commonly used visualization of a LIME explanation\sout{ that is shown in Figure \ref{fig:figure-03} (left)}.
+\kge{Figure \ref{fig:figure-03} (left) shows the explanation for the prediction of interest indicated in \autoref{fig:figure-02} obtained using 4-quantile-bins.} \sout{The plot is created using the \emph{lime} R package and provides a visual representation of a LIME explanation for the prediction of interest indicated in \autoref{fig:figure-02}.
+In particular, the explanation is obtained using 4-quantile-bins to simulate the data.} \kge{When quantile bins are used to simulate data}\sout{ In this scenario}, LIME converts continuous predictor variables to indicator variables identifying whether the variable value falls in the same quantile bin as the prediction of interest or not.
+The\kge{n the} indicator variables are used as the explainer model features.}
+
+\sout{The plot reports 0.74 as the random forest  probability that the observation of interest belongs to category blue (denoted as the ``label" in the plot).
 The lengths of the bars represent the coefficients from a ridge regression model (the explainer model) fit using the R package \emph{glmnet} \citep{simon:2011} associated with the indicator variables chosen via feature selection.
@@
 In this case, it is 0.21 suggesting that the explainer model is not a good linear fit.
-However, it is commonly accepted that $R^2$ has limitations for assessing the quality of fit of a model \citep{sapra:2014} and  should not be used as the only metric in a model assessment.
-
-\kgc{I've come to the conclusion that I like the numbers included here with the interpretation, but I tried to get rid of numbers else where.} The explanation for the prediction of interest depicted in Figure \ref{fig:figure-03} is interpreted as follows.
+However, it is commonly accepted that $R^2$ has limitations for assessing the quality of fit of a model \citep{sapra:2014} and  should not be used as the only metric in a model assessment.}
+
+\sout{The explanation for the prediction of interest depicted in Figure \ref{fig:figure-03} is interpreted as follows.
 A random forest classification of blue is supported by the prediction of interest having a value of $x_2$ that is greater than 4.834, but the prediction of interest having a value of $x_1$ that is greater than -0.302 and less than or equal to 4.844 provides support against a classification of blue.
@@
 Additionally, consider that since the support for blue by $x_2$ outweighs the support for red by $x_1$, the explainer model overall favors a label of blue for the prediction of interest, which agrees with the random forest probability of 0.744 for blue.
-Note that both models classify the observation incorrectly.
+Note that both models classify the observation incorrectly.}
 
@@
 
-\begin{figure}[!thp]
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-
-{\centering \includegraphics[width=3.125in]{figure/figure-04-1}
-
-}
-
-\end{knitrout}
-\caption{Hypothetical examples of feature heatmaps in two possible situations.
-The heatmaps show the top feature chosen for 10 cases across 5 different sets of tuning parameter values.
-The color of the cell indicates the feature chosen by LIME.
-Situation 1 is the ideal, because the explanations vary across cases but do not dependent on specific tuning parameter values.}
-\label{fig:figure-04}
-
-\vspace*{\floatsep}
-
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-
-{\centering \includegraphics[width=3.125in]{figure/figure-05-1}
-
-}
-
-\end{knitrout}
-\caption{\emph{Feature Heatmap}.
-An example feature heatmap of the explanations from the applications of LIME with different tuning parameter values to the \data \ test set.
-The cases from the test set are plotted on the y-axis, and the tuning parameter values (simulation methods here) are included on the x-axis.
-The colors of the tiles indicate the feature selected by LIME for the corresponding case and tuning parameter value.
-The plot is faceted by the first and second most important features selected by LIME (top and bottom facets, respectively).
-The vertical facets separate the  kernel density method from the quantile bin methods.
-The vertical striping indicates that the LIME explanations are not consistent across tuning parameter values.}
-\label{fig:figure-05}
-\end{figure}
-
 Explanations produced by LIME are likely to be affected by the choice of tuning parameter values.
@@
 
-Two hypothetical examples of feature heatmaps are included in \autoref{fig:figure-04}.
+\kge{When interpreting feature heatmaps, horizontal lines of the same color represent the ideal situation where the explanations are consistent and do not depend on the tuning parameter values but do depend on the location of the observation in the feature space.
+Vertical lines of color represent explanations that are dependent on the tuning parameter values and may not be local since the same feature is chosen regardless of the location of the observation in the feature space.
+See Appendix \ref{feat-heat-ex} for hypothetical examples depicting feature heatmaps with the extreme cases of horizontal and vertical lines.}
+
+\begin{figure}[!tp]
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+
+{\centering \includegraphics[width=3.125in]{figure/figure-04-1}
+
+}
+
+\end{knitrout}
+\caption{\emph{Feature Heatmap}.
+An example feature heatmap of the explanations from the applications of LIME with different tuning parameter values to the \data \ test set.
+\sout{The cases from the test set are plotted on the y-axis, and the tuning parameter values (simulation methods here) are included on the x-axis.
+The colors of the tiles indicate the feature selected by LIME for the corresponding case and tuning parameter value.
+The plot is faceted by the first and second most important features selected by LIME (top and bottom facets, respectively).
+The vertical facets separate the kernel density method from the quantile bin methods.} The vertical striping indicates that the LIME explanations are not consistent across tuning parameter values.}
+\label{fig:figure-04}
+\end{figure}
+
+\sout{Two hypothetical examples of feature heatmaps are included in \autoref{fig:figure-04}.
 The plots are created with the assumption that LIME is applied to select the top feature out of $p=4$  features for $n=10$ cases with $t=5$ sets of tuning parameter values.
@@
 This situation indicates that the features selected by LIME are dependent on the tuning parameters, and the explanations may not be  local, because the same feature is chosen regardless of the case.
-In practice, it is expected that the plot will exhibit a combination of these two situations.
-
-\autoref{fig:figure-05} shows a feature heatmap for the LIME applications to the 100 observations in the \data \ test set.
+In practice, it is expected that the plot will exhibit a combination of these two situations.}
+
+\autoref{fig:figure-04} shows a feature heatmap for the LIME applications to the 100 observations in the \data \ test set.
 The most important and second most important features selected by lime are shown in in the top and bottom facets, respectively.
-For the quantile bins, the original features prior to the indicator variable transformation are included since it is obvious that different features would be selected when the sizes of the bins change.
-This figure shows that for kernel density and 2-quantile-bins, LIME selects $x_1$ as the most important feature and $x_2$ as the second most important feature across all cases in the test set.
-These explanations are not local.
-There is variability in the features selected by LIME for 3- to 6-quantile-bins suggesting more local explanations.
+For the quantile bins, the original features prior to \kge{being converted to indicator variables} \sout{the indicator variable transformation} are included since it is obvious that different features would be selected when the sizes of the bins change.
+This figure shows that for kernel density and 2-quantile-bins, LIME \kge{produces global explanations since} \sout{selects} $x_1$ \kge{is selected} as the most important feature and $x_2$ \kge{is selected} as the second most important feature across all cases in the test set.
+\sout{These explanations are not local.} There is variability in the features selected by LIME for 3- to 6-quantile-bins suggesting more local explanations.
 There are signs of vertical striping, which suggests a dependence on tuning parameters.
-Note that the explanations from 3- and 5-quantile-bins include the selection of the random noise variable ($x_3$) as an important variable in many predictions, which should not be the case.
-The pattern seen in the explanations for 3- to 6-quantile-bins may suggest local explanations, but the dependence on tuning parameters makes it unclear which set of explanations to use.
+Note that the explanations from 3- and 5-quantile-bins include the selection of the random noise variable ($x_3$) as an important variable in many predictions, which \kge{would not be expected to be important to a random forest}\sout{should not be the case}.
+\kge{It is unclear whether the random forest is using a variable that would not be expected to be important or LIME is incorrectly identifying the important variable when 3- and 5- quantile bins are used.} \sout{The pattern seen in the explanations for 3- to 6-quantile-bins may suggest local explanations, but the dependence on tuning parameters makes it unclear which set of explanations to use.}
 
 \subsection{Assessment Metric Plot} \label{assess-metric}
-
-\begin{figure}[!thp]
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-
-{\centering \includegraphics[width=3.25in]{figure/figure-06-1}
-
-}
-
-\end{knitrout}
-\caption{\emph{Assessment metric plot}.
-The assessment metrics computed on the applications of LIME to the \data \ test set are included in this example assessment metric plot.
-Each horizontal facet corresponds to one of three metrics: average $R^2$, average fidelity, or MSEE.
-The LIME tuning parameter values (simulation methods in this example) are plotted on the x-axis, and the metric values are shown on the y-axis.
-The points are colored by rank (within a metric) indicating best to worst (dark to light).
-The kernel density simulation methods performs well across all three metrics.}
-\label{fig:figure-06}
-\end{figure}
 
@@
 
-\autoref{fig:figure-06} shows an example assessment metric plot.
+\begin{figure}[!tp]
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+
+{\centering \includegraphics[width=3.25in]{figure/figure-05-1}
+
+}
+
+\end{knitrout}
+\caption{\emph{Assessment metric plot}.
+The assessment metrics computed on the applications of LIME to the \data \ test set are included in this example assessment metric plot.
+\sout{Each horizontal facet corresponds to one of three metrics: average $R^2$, average fidelity, or MSEE.
+The LIME tuning parameter values (simulation methods in this example) are plotted on the x-axis, and the metric values are shown on the y-axis.
+The points are colored by rank (within a metric) indicating best to worst (dark to light).} The kernel density simulation methods performs well across all three metrics.}
+\label{fig:figure-05}
+\end{figure}
+
+\autoref{fig:figure-05} shows an example assessment metric plot.
 The three metrics are computed for each of the LIME applications to the \data \ test set.
@@
 MSEE provides almost the exact opposite results with  6-quantile-bins performing the best and 2-quantile-bins performing the worst.
-Average fidelity and MSEE are similar metrics, so it is not surprising that they would agree in this example.
-Another factor might be that MSEE only takes the prediction of interest  into account and not the full simulated dataset.
+Average fidelity and MSEE are similar metrics, so it is \sout{not} surprising that they would \kge{not} agree in this example\kge{, but it may be becuase} \sout{.
+Another factor might be that} MSEE only takes the prediction of interest into account and not the full simulated dataset.
 The contradiction between metrics makes it difficult to identify which simulation method to trust.
-
-Recall that \autoref{fig:figure-05} indicated that the kernel density method selected the same feature across all cases in the test set for both the first and second features.
-It appears that a global trend may be the best explanation for this example, which may be reasonable considering that we know that both $x_1$ and $x_2$ are the two features that should be the features used by the random forest to distinguish between response categories.
+\kgc{I missed this reading through the manuscript before submission, but at some point the text above was changed to say that the "Average fidelity and MSEE are similar metrics, so it is not surprising that they would agree in this example." It should be as I have it now since they don't agree.}
+
+Recall that \autoref{fig:figure-04} indicated that the kernel density method selected the same feature across all cases in the test set for both the first and second features.
+It appears that a global trend may be the best explanation for this example, which may be reasonable considering that we \kge{would expect that} \sout{know that} both $x_1$ and $x_2$ \kge{would be} \sout{are} the two features that should \sout{be the features} used by the random forest to distinguish between response categories.
+\kge{However, futher exploration of individual explanations using explanation scatterplots may help to identify the tuning parameter values considered here that produce the most trustworthy explanations.}
 
@@
 
-In current practice, forensic firearm examiners evaluate whether two bullets are from the same source (fired from the same gun) or from different sources based on microscopic comparison of the striation patterns engraved on bullets during the firing process (see \autoref{fig:figure-07}).
+In current practice, forensic firearm examiners evaluate whether two bullets are from the same source (fired from the same gun) or from different sources based on microscopic comparison of the striation patterns engraved on bullets during the firing process (see \autoref{fig:figure-06}).
 The process is based on a visual and therefore subjective assessment of the evidence.
@@
 In response, \citet{hare:2017} proposed an automated machine learning method for bullet matching to complement a visual inspection by firearm examiners.
-Based on high-resolution topological scans of land engraved areas, \citet{hare:2017} obtain signatures of striations from two bullet lands (\autoref{fig:figure-08}).
+Based on high-resolution topological scans of land engraved areas, \citet{hare:2017} obtain signatures of striations from two bullet lands (\autoref{fig:figure-07}).
 Nine features quantifying the similarity of signatures, such as the cross-correlation function, the distance between signatures, and the number of matching striae, are extracted and used to train a random forest to determine the probability of a comparison resulting from the same source (matching signatures) or from different sources (non-matching signatures).
@@
 
-{\centering \includegraphics[width=2.25in]{figure-static/figure-07-1}
+{\centering \includegraphics[width=2.25in]{figure-static/figure-06-1}
 
@@
 (Bottom) Close up of a land engraved area showing striations (vertical lines).}
-\label{fig:figure-07}
+\label{fig:figure-06}
 
@@
 
-{\centering \includegraphics[width=3.125in]{figure/figure-08-1}
+{\centering \includegraphics[width=3.125in]{figure/figure-07-1}
 
@@
 The \citet{hare:2017} random forest is fit using various features that measure the similarity between two such signatures.}
-\label{fig:figure-08}
+\label{fig:figure-07}
 \end{figure}
@@
 
-{\centering \includegraphics[width=6.5in]{figure-static/figure-09-1}
+{\centering \includegraphics[width=6.5in]{figure-static/figure-08-1}
 
@@
 There are clear relationships between the feature values and the random forest probabilities.}
-\label{fig:figure-09}
+\label{fig:figure-08}
 \end{figure*}
@@
 
-We consider a global visualization of the relationship between the random forest predictions and the model features with a parallel coordinate plot of the training data (top facet) and testing data (bottom facets)  (\autoref{fig:figure-09}).
+We consider a global visualization of the relationship between the random forest predictions and the model features with a parallel coordinate plot of the training data (top facet) and testing data (bottom facets)  (\autoref{fig:figure-08}).
 In the training data we observe a clear difference in feature values based on whether the corresponding random forest scores are close to 1 or 0.
@@
 
-To get an overview of the LIME explanations from the 36 applications, we consider a feature heatmap (\autoref{fig:figure-10}).
+To get an overview of the LIME explanations from the 36 applications, we consider a feature heatmap (\autoref{fig:figure-09}).
 In addition to facets for simulation method and LIME feature importance, this plot includes a vertical facet for Gower power and a horizontal facet for whether the observation is a known match or non-match.
@@
 
-{\centering \includegraphics[width=6.5in]{figure/figure-10-1}
+{\centering \includegraphics[width=6.5in]{figure/figure-09-1}
 
@@
 The vertical stripes of features selected indicate a dependence between the LIME explanations and tuning parameter values.}
-\label{fig:figure-10}
+\label{fig:figure-09}
 
@@
 There are discrepancies in performance across metrics for a set of tuning parameter values, but based on the overall performance of all three metrics, 4-equal-bins with a Gower power of 0.5 appears to perform the best.}
-\label{fig:figure-11}
+\label{fig:figure-10}
 \end{figure*}
 
-To try to identify a set of LIME tuning parameter values with the most trustworthy set of explanations, an assessment metric plot is considered (\autoref{fig:figure-11}).
+To try to identify a set of LIME tuning parameter values with the most trustworthy set of explanations, an assessment metric plot is considered (\autoref{fig:figure-10}).
 The performance of a set of tuning parameter values often do not agree across metrics.
@@
 To provide a more detailed view of explanations obtained using different tuning parameter values, we take a closer look at explanations for two observations of interest, which will be referred to as case M (a known match) and case NM (a known non-match), using explanation scatterplots.
-Figure~\ref{fig:figure-12} includes the visual representation plots of explanations (from \emph{lime}) and explanation scatterplots for cases M and NM.
+Figure~\ref{fig:figure-11} includes the visual representation plots of explanations (from \emph{lime}) and explanation scatterplots for cases M and NM.
 Plots for 4-equal-bins and 4-quantile-bins are included to depict tuning parameter values with good (4-equal-bins) and mediocre (4-quantile-bins) performance based on the assessment metric plot.
@@
 
-{\centering \includegraphics[width=6.25in]{figure/figure-12-1}
-
-}
-
-\end{knitrout}
-\caption{Plots of LIME explanations (first and third rows) and explanation scatterplots (second and fourth rows) for  cases M and NM in the bullet test data for two tuning parameter values: 4-quantile-bins (first column) and 4-equal-bins (second column).
+{\centering \includegraphics[width=6.25in]{figure/figure-11-1}
+
+}
+
+\end{knitrout}
+\caption{Plots of LIME explanations (first row) and explanation scatterplots (second row) for case NM in the bullet test data for two tuning parameter values: 4-quantile-bins (first column) and 4-equal-bins (second column).
 The plots provide insights into the LIME explanations and allow for the assessment of the explanation quality.}
-\label{fig:figure-12}
+\label{fig:figure-11}
 \end{figure*}
@@
 Without applying LIME with multiple tuning parameter values to the bullet test data or viewing diagnostic plots of the LIME explanations, it may be very possible to formulate reasons why the LIME explanations make sense.
-However, the sequence of plots in this section (Figures \ref{fig:figure-10}, \ref{fig:figure-11}, and \ref{fig:figure-12}) suggest that we should be cautious to trust any of these LIME explanations.
+However, the sequence of plots in this section (Figures \ref{fig:figure-09}, \ref{fig:figure-10}, and \ref{fig:figure-11}) suggest that we should be cautious to trust any of these LIME explanations.
 It appears that either LIME needs to be further tuned to provide trustworthy and good explanations, or a different approach may provide better insight.
@@
 Even though an explanation will be interpretable as long as the complexity of the explainer model is appropriately chosen, a lack of understanding of the process used to create the explanation could lead to an incorrect interpretation of the explanation.
-For example, the visualization of a LIME explanation available from the \emph{lime} R package \citep{pedersen:2020} (shown in Figures \ref{fig:figure-03} and \ref{fig:figure-12}) is a major simplification of the explainer model, which could lead to under-interpreted or misinterpreted LIME explanation.
-Supplementing \citet{pedersen:2020}'s compact visualization of the explanation with an explanation scatterplot that shows a more detailed visualization of the explainer model promotes a more complete understanding of the explanation (such as Figures~\ref{fig:figure-03} and \ref{fig:figure-12}).
+For example, the visualization of a LIME explanation available from the \emph{lime} R package \citep{pedersen:2020} (shown in Figures \ref{fig:figure-03} and \ref{fig:figure-11}) is a major simplification of the explainer model, which could lead to under-interpreted or misinterpreted LIME explanation.
+Supplementing \citet{pedersen:2020}'s compact visualization of the explanation with an explanation scatterplot that shows a more detailed visualization of the explainer model promotes a more complete understanding of the explanation (such as Figures~\ref{fig:figure-03} and \ref{fig:figure-11}).
 
@@
 The explanation scatterplots allow for a comparison of the explainer model to the complex model.
-The examples in this paper show cases where the explainer model bins do not accurately capture the regions with similar random forest probabilities that contain the prediction of interest and oversimplify the model (Figures \ref{fig:figure-03} and \ref{fig:figure-12}).
+The examples in this paper show cases where the explainer model bins do not accurately capture the regions with similar random forest probabilities that contain the prediction of interest and oversimplify the model (Figures \ref{fig:figure-03} and \ref{fig:figure-11}).
 Using fewer bins would clearly not help improve the faithfulness of the explainer model in these examples, and while an increase in the number of bins would lead to a finer resolution of the random forest classification boundaries, interpretability of the explainer model would quickly be lost.
@@
 In addition to assessing faithfulness by visually comparing the complex and explainer model, we propose a visual comparison of two faithfulness metrics (MSEE and average fidelity).
-The examples of faithfulness metric comparisons in this paper both produced conflicting results (Figures \ref{fig:figure-06} and \ref{fig:figure-11}).
+The examples of faithfulness metric comparisons in this paper both produced conflicting results (Figures \ref{fig:figure-05} and \ref{fig:figure-10}).
 This makes it difficult to decide on a recommendation of a set of tuning parameter values that produce the explanations with the most faithful explainer model.
@@
 
+\begin{figure*}[!thp]
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+
+{\centering \includegraphics[width=6.5in]{figure/figure-B1-1}
+
+}
+
+\end{knitrout}
+\caption{Explanation scatterplots for the \data \ prediction of interest with the kernel density simulation method.}
+\label{fig:figure-B1}
+\end{figure*}
+
+\begin{figure*}[!thp]
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+
+{\centering \includegraphics[width=6.5in]{figure/figure-B2-1}
+
+}
+
+\end{knitrout}
+\caption{Explanation scatterplots for LIME explanations using kernel density simulation for the cases M and NM of the bullet comparison test data.}
+\label{fig:figure-B2}
+\end{figure*}
+
 Section \ref{exp-scatter} introduces explanation scatterplots under the default simulation method in the \emph{lime} R package: 4-quantile-bins.
@@
 Figure \ref{fig:figure-B2} includes explanation scatterplots for the explanations generated using kernel density simulation for the bullet example cases M and NM discussed in Section \ref{bullet-assess-ex}.
-
-\begin{figure*}[!thp]
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-
-{\centering \includegraphics[width=6.5in]{figure/figure-B1-1}
-
-}
-
-\end{knitrout}
-\caption{Explanation scatterplots for the \data \ prediction of interest with the kernel density simulation method.}
-\label{fig:figure-B1}
-\end{figure*}
-
-\begin{figure*}[!thp]
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-
-{\centering \includegraphics[width=6.5in]{figure/figure-B2-1}
-
-}
-
-\end{knitrout}
-\caption{Explanation scatterplots for LIME explanations using kernel density simulation for the cases M and NM of the bullet comparison test data.}
-\label{fig:figure-B2}
-\end{figure*}
 
@@
 
+\section{Extreme Feature Heatmap Scenarios} \label{feat-heat-ex}
+
+Two hypothetical examples of feature heatmaps are included in \autoref{fig:figure-D4}.
+The plots are created with the assumption that LIME is applied to select the top feature out of $p=4$  features for $n=10$ cases with $t=5$ sets of tuning parameter values.
+Situation 1 is an example where the features selected are consistent across tuning parameter values within a case but vary across cases within a tuning parameter value.
+This is the ideal situation, because the LIME explanations do not depend on the tuning parameters but do depend on the location of the observation in the feature space.
+Situation 2 is an example where the selected features vary across tuning parameter values within a case but are consistent across cases within a tuning parameter value.
+This situation indicates that the features selected by LIME are dependent on the tuning parameters, and the explanations may not be  local, because the same feature is chosen regardless of the case.
+In practice, it is expected that the plot will exhibit a combination of these two situations.
+
+\begin{figure}[!thp]
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+
+{\centering \includegraphics[width=3.125in]{figure/figure-D4-1}
+
+}
+
+\end{knitrout}
+\caption{Hypothetical examples of feature heatmaps in two possible situations.
+The heatmaps show the top feature chosen for 10 cases across 5 different sets of tuning parameter values.
+The color of the cell indicates the feature chosen by LIME.
+Situation 1 is the ideal, because the explanations vary across cases but do not dependent on specific tuning parameter values.}
+\label{fig:figure-D4}
+\end{figure}
+
 \section{Details on Assessment Metrics} \label{metric-details}
@@
 
+\section{Matching Bullets Explanation Scatterplots} \label{match-bullets}
+
+\begin{figure*}[!thp]
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+
+{\centering \includegraphics[width=6.25in]{figure/figure-e5-1}
+
+}
+
+\end{knitrout}
+\caption{Plots of LIME explanations (first row) and explanation scatterplots (second row) for case M in the bullet test data for two tuning parameter values: 4-quantile-bins (first column) and 4-equal-bins (second column).
+The plots provide insights into the LIME explanations and allow for the assessment of the explanation quality.}
+\label{fig:figure-e5}
+\end{figure*}
+
 \end{document}

### 2020-12-17 paper.Rnw
more trimming (almost done with the first round!)

@@
 @
-\caption{\kge{Hypothetical scenarios depicting the effect of different weights on LIME (Left) An example of an explainer model with appropriate weights to provide a faithful approximation of the complex model.
+\caption{\kge{Hypothetical scenarios depicting the effect of different weights on LIME.
+(Left) An example of an explainer model with appropriate weights to provide a faithful approximation of the complex model.
 (Right) An example of an explainer model for the same prediction but with different weights that results in an explanation unfaithful to the complex model.} \sout{A conceptual depiction of a faithful LIME explainer model in the immediate neighborhood of a prediction of interest \kge{for a hypothetical black-box model trained using two features: Feature 1 (left) and Feature 2 (right).
@@
 The forked version is functionally indistinguishable from \citeauthor{pedersen:2020}'s implementation but allows us to export internal values relevant for an assessment of the explainer.
-The diagnostic plots included in this paper are created using the R package \emph{limeaid} \citep{goode:2020}.
+The \kge{code for the} diagnostic plots included in this paper \kge{is stored in} \sout{are created using} the R package \emph{limeaid} \citep{goode:2020}.
 
@@
 The explainer model indicator variables associated with $x_1$ and $x_2$ (quantile bins containing the prediction of interest) are depicted by the solid lines.
-The line colors represent the explainer model coefficient signs and indicate whether the feature supports a prediction of `blue' (blue lines) or supports a prediction of `red' (red lines).} \kge{An explanation scatterplot associated with the explanation for the prediction of interest depicted on the left.} \sout{This figure shows that t}\kge{T}he \kge{4} quantile bins are not flexible enough to capture the relationship between the random forest predictions and the $x_1$ and $x_2$ values.}
+The line colors represent the explainer model coefficient signs and indicate whether the feature supports a prediction of `blue' (blue lines) or supports a prediction of `red' (red lines).} \kge{An explanation scatterplot associated with the explanation \sout{for the prediction of interest depicted} on the left.} \sout{This figure shows that t}\kge{T}he \kge{4} quantile bins \kge{over simplify} \sout{are not flexible enough to capture}
+the relationship between the random forest predictions and the $x_1$ and $x_2$ values \kge{near the prediction of interest}.}
 \label{fig:figure-03}
@@
 We use 6 bins as the maximum, because the complexity of the explanations increases with the number of bins.
-Note that 4-quantile-bins \kge{is} \sout{are} the default method in \emph{lime}.
+Note that 4-quantile-bins \kge{is} \sout{are} the default method in the \emph{lime} R package.
 The sixth application of LIME uses a kernel density simulation method (samples are drawn from kernel density approximations of the feature distributions).
@@
 A hypothetical example of this is shown by Figures \ref{fig:figure-01} and \ref{fig:figure-02} where the method used to weight the observations influenced the explanation.
-As of the time of writing this manuscript, we have encountered no recommendations for how to specify the parameter values besides for the default settings in \emph{lime}.
+As of the time of writing this manuscript, we have encountered no recommendations for how to specify the parameter values besides for the default settings in the \emph{lime} R package.
 In order to compare the explanations produced by LIME using different tuning parameter values and provide another perspective for assessing localness, we visualize an overview of the explanations with the \emph{feature heatmap} diagnostic plot.
@@
 \begin{figure}[!tp]
-<<figure-04, out.width = '3.125in', fig.width = 4, fig.height = 4.5>>=
+<<figure-04, out.width = '3.125in', fig.width = 4.5, fig.height = 4.5>>=
 
@@
 f4_ow = 3.125
-f4_fw = 4
+f4_fw = 4.5
 f4_fs = fs * (f4_fw / f4_ow)
@@
 \autoref{fig:figure-04} shows a feature heatmap for the LIME applications to the 100 observations in the \data \ test set.
-The most important and second most important features selected by lime are shown in in the top and bottom facets, respectively.
+The most important and second most important features selected by LIME are shown in in the top and bottom facets, respectively.
 For the quantile bins, the original features prior to \kge{being converted to indicator variables} \sout{the indicator variable transformation} are included since it is obvious that different features would be selected when the sizes of the bins change.
@@
 \caption{\emph{Assessment metric plot}.
-The assessment metrics computed on the applications of LIME to the \data \ test set are included in this example assessment metric plot.
+\kge{This example assessment metric plot contains metrics} \sout{The assessment metrics} computed on the applications of LIME to the \data \ test set\sout{are included in this example assessment metric plot}.
 \sout{Each horizontal facet corresponds to one of three metrics: average $R^2$, average fidelity, or MSEE.
@@
 MSEE provides almost the exact opposite results with 6-quantile-bins performing the best and 2-quantile-bins performing the worst.
-Average fidelity and MSEE are similar metrics, so it is \sout{not} surprising that they would \kge{not} agree in this example\kge{, but it may be becuase} \sout{.
-Another factor might be that} MSEE only takes the prediction of interest into account and not the full simulated dataset.
-The contradiction between metrics makes it difficult to identify which simulation method to trust.
-\kgc{I missed this reading through the manuscript before submission, but at some point the text above was changed to say that the "Average fidelity and MSEE are similar metrics, so it is not surprising that they would agree in this example." It should be as I have it now since they don't agree.}
-
-Recall that \autoref{fig:figure-04} indicated that the kernel density method selected the same feature across all cases in the test set for both the first and second features.
-It appears that a global trend may be the best explanation for this example, which may be reasonable considering that we \kge{would expect that} \sout{know that} both $x_1$ and $x_2$ \kge{would be} \sout{are} the two features that should \sout{be the features} used by the random forest to distinguish between response categories.
-\kge{However, futher exploration of individual explanations using explanation scatterplots may help to identify the tuning parameter values considered here that produce the most trustworthy explanations.}
+Average fidelity and MSEE are similar metrics, \kge{but} \sout{so it is \sout{not} surprising that they \sout{would} \kge{do not} agree in this example.
+\kge{The discrepancy may be because} \sout{Another factor might be that}} MSEE only takes the prediction of interest into account and not the full simulated dataset \kge{as average fidelity does.} \kge{This suggests that 6-quantile-bins produce an explainer model more faithful for the prediction of interest while 2-quantile-bins produce an explainer model more faithful over all simulated data observations}.
+\sout{The contradiction between metrics makes it difficult to identify which simulation method to trust.}
+
+Recall\kge{,} \sout{that} \autoref{fig:figure-04} \kge{shows} \sout{indicates that} the kernel density method \kge{returns the same explanations} \sout{selected the same feature} across all cases in the test set\sout{ for both the first and second features.
+It appears that} \kge{suggesting} a global trend may be the best explanation for this example\kge{.}\sout{, which} \kge{This} may be reasonable considering that we \kge{would expect} \sout{know that both} $x_1$ and $x_2$ \kge{to be} \sout{are} the two features \sout{that should be the features} used by the random forest to distinguish between response categories.
+\kge{However, futher exploration of individual explanations using explanation scatterplots may help to identify the tuning parameter values that produce the most trustworthy explanations.}
 
@@
 
-In this section, we provide a discussion of the application of the visual diagnostics for LIME explanations to a practical data problem investigating the similarity of marks on fired bullets.
+In this section, we \sout{provide a discussion of the application of} \kge{apply} the visual diagnostics for LIME explanations to a practical data problem investigating the similarity of marks on fired bullets.
 
@@
 Nine features quantifying the similarity of signatures, such as the cross-correlation function, the distance between signatures, and the number of matching striae, are extracted and used to train a random forest to determine the probability of a comparison resulting from the same source (matching signatures) or from different sources (non-matching signatures).
-The model in \citet{hare:2017} was trained on a set of scans of bullets from the James Hamby Consecutively Rifled Ruger Barrel Study \citep{hamby:2009}, which included 10,384 land-to-land comparisons \citet{hare:2017}.
+The model in \citet{hare:2017} was trained on a set of scans of bullets from the James Hamby Consecutively Rifled Ruger Barrel Study \citep{hamby:2009}, which included 10,384 land-to-land comparisons \citep{hare:2017}.
 See the supporting information for additional information on the signature similarity features.
@@
 
-<<figure-07, out.width = '3.125in', fig.width = 6, fig.height = 3.5, warning = FALSE>>=
+<<figure-07, out.width = '3.125in', fig.width = 6, fig.height = 3.25, warning = FALSE>>=
 
@@
   theme(strip.background = element_blank()) +
-  ylab("Surface Measurement (in microns)") +
+  ylab("Surface Measurement \n(in microns)") +
   xlab("Relative Location (in millimeters)")
@@
 \caption{Example bullet signatures.
-The bullet signatures correspond to the same land and therefore have very similar patterns.
-The \citet{hare:2017} random forest is fit using various features that measure the similarity between two such signatures.}
+The \sout{bullet} signatures \kge{are from} \sout{correspond to} the same land and therefore have very similar patterns.
+\sout{The \citet{hare:2017} random forest is fit using various features that measure the similarity between two such signatures.}}
 \label{fig:figure-07}
@@
 @
-\caption{Parallel coordinate plots of the \citet{hare:2017} random forest predictions from the training (top facet) and testing (bottom facet) data.
-The observations are separated by known matching (right column) and non-matching (left column) signatures.
-The y-axis shows the standardized feature values, and the x-axis shows the features used to fit the random forest (ordered by random forest impurity based feature importance).
-Each line corresponds to an observation, and the line color represents the associated random forest probability.
+\caption{Parallel coordinate plots of the \kge{bullet matching} \sout{\citet{hare:2017}} random forest predictions\sout{from the training (top \kge{row}\sout{facet}) and testing (bottom \kge{row}\sout{facet}) data}.
+\sout{The observations are separated by known matching (right column) and non-matching (left column) signatures.
+The y-axis shows the standardized feature values, and the x-axis shows the features used to fit the random forest (ordered by random forest impurity based feature importance).} Each line corresponds to an observation, and the line color represents the associated random forest probability.
 There are clear relationships between the feature values and the random forest probabilities.}
@@
 
-We consider a global visualization of the relationship between the random forest predictions and the model features with a parallel coordinate plot of the training data (top facet) and testing data (bottom facets)  (\autoref{fig:figure-08}).
+\kge{In \autoref{fig:figure-08}, } \sout{W}\kge{w}e consider a global visualization of the relationship between the random forest predictions and the model features with a parallel coordinate plot of the training data (top \kge{row}\sout{facet}) and testing data (bottom \kge{row}\sout{facets})\sout{ (\autoref{fig:figure-08})}.
 In the training data we observe a clear difference in feature values based on whether the corresponding random forest scores are close to 1 or 0.
@@
 Observations in the test data that are classified incorrectly by the random forest tend to have feature values similar to observations in the training data with similar random forest scores.
-For example, the observations in the test set known to be a match but have a random forest score below 0.5 have relatively low values of rough correlation, cross correlation function, and matches and relatively large values of mismatches, distance, and non-consecutively matching striae compared to observations with a random forest probability close to 1.
+\sout{For example, the observations in the test set known to be a match but have a random forest score below 0.5 have relatively low values of rough correlation, cross correlation function, and matches and relatively large values of mismatches, distance, and non-consecutively matching striae compared to observations with a random forest probability close to 1.}
 
@@
 
-First, applications of 2-quantile-bin simulations produce the same explanations for almost all cases and LIME tuning parameter values.
-This suggests that the LIME explanations are global and not local.
+First, applications of 2-quantile-bins\kge{, 2-equal-bins, and somewhat for the density based} simulations produce the same explanations for almost all cases and LIME tuning parameter values\kge{,}\sout{.
+This suggests that the LIME} \kge{suggesting these} explanations are global and not local.
 Second, within a simulation method, the features selected by LIME for an observation do not appear to vary by the Gower power.
-However, the LIME explanation for an observation often varies across simulation methods.
-With the equal-bins, there are vertical stripes that suggest a dependence of the LIME explanations on the number of bins.
+However, the LIME explanation\kge{s} for an observation often var\kge{y}\sout{ies} across simulation methods.
+With the equal bins, there are vertical stripes that suggest a dependence of the LIME explanations on the number of bins.
 The vertical stripes are not as apparent with the quantile bins.
@@
 \caption{Feature heatmap of 36 LIME applications to the bullet comparison data test set.
-In addition to faceting the results by simulation method and LIME feature selection order, facets for the Gower power and whether the observation is a match or non-match are included.
-The vertical stripes of features selected indicate a dependence between the LIME explanations and tuning parameter values.}
+\sout{In addition to faceting the results by simulation method and LIME feature selection order, facets for the Gower power and whether the observation is a match or non-match are included.} The vertical stripes of features selected indicate a dependence between the LIME explanations and tuning parameter values.}
 \label{fig:figure-09}
@@
 \caption{Assessment metric plot for the applications of LIME on the bullet comparison data test set.
-There are discrepancies in performance across metrics for a set of tuning parameter values, but based on the overall performance of all three metrics, 4-equal-bins with a Gower power of 0.5 appears to perform the best.}
+There are discrepancies in \kge{metric} performance\kge{s}\sout{ across metrics for a set of tuning parameter values}, but \sout{based on the} overall\sout{ performance of all \sout{three} metrics}, 4-equal-bins with a Gower power of 0.5 appear\sout{s} to perform the best.}
 \label{fig:figure-10}
@@
 However, there is consistency in results across different Gower powers.
-The applications using a power of 0.5 perform the best or as well as the other powers across all simulation methods suggesting that the power that leads to a more global explanation is preferred by LIME.
-It is not apparent which set of tuning parameters is the best.
-Considering all three metrics, we might conclude that the 4-equal-bins with a Gower power of 0.5 performs better than the other tuning parameter values considered.
-
-To provide a more detailed view of explanations obtained using different tuning parameter values, we take a closer look at explanations for two observations of interest, which will be referred to as case M (a known match) and case NM (a known non-match), using explanation scatterplots.
-Figure~\ref{fig:figure-11} includes the visual representation plots of explanations (from \emph{lime}) and explanation scatterplots for cases M and NM.
+The applications using a power of 0.5 perform the best or as well as the other powers across all simulation methods suggesting that the power that leads to a more \kge{local} \sout{global} explanation is preferred\sout{ by LIME}.
+It is not \kge{obvious} \sout{apparent} which set of tuning parameters is the best\kge{, but}\sout{.
+C}\kge{c}onsidering all three metrics, we might conclude that the 4-equal-bins with a Gower power of 0.5 performs better than the other tuning parameter values considered.
+
+To provide a more detailed view of explanations obtained using different tuning parameter values, we \kge{consider explanation scatterplots for one prediction of interest} \sout{take a closer look at explanations for two observations of interest, which will be} referred to as case NM (a known non-match)\sout{ and case NM (a known non-match), using explanation scatterplots.} \kge{shown in} Figure~\ref{fig:figure-11} \sout{includes} \kge{along with} the visual \sout{representation plots of} explanation\sout{s} \kge{plots} \sout{(}from \kge{the} \emph{lime} \kge{R package}\sout{)\ and explanation scatterplots for cases M and NM}.
 Plots for 4-equal-bins and 4-quantile-bins are included to depict tuning parameter values with good (4-equal-bins) and mediocre (4-quantile-bins) performance based on the assessment metric plot.
-Plots for the kernel density simulation method are included in Appendix~\ref{exp-scatter_plus} (Figure \ref{fig:figure-B2}).
-
-We focus on the explanation for case NM with 4-quantile-bins.
-The explanation plot from \emph{lime} shows that the observed values of NM of mismatches less than or equal to 7.17, rough correlation (rough\_cor) greater than 0.05, and D less than or equal to 0.002 support a random forest prediction in favor of a match.
+\kge{Also, recall that 4-quantile-bins are the default option in the \emph{lime} R package.} \sout{Plots} \kge{Explanation scatterplots for a known match, referred to as case M, and} for the kernel density simulation method \kge{applied to both M and NM} are included in Appendix~\ref{bullets-plus}\sout{ (Figure \ref{fig:figure-F5})}.
+
+\kge{When 4-quantile-bins are applied to case NM, LIME explains that the feature of mismatches, rough correlation, and distance are important and support a prediction of the class true (Figure~\ref{fig:figure-11} top left).
+However, this explanation contradicts that random forest prediction probability that correctly provides evidence that the observation is a non-match.
+The explanation scatterplot (Figure~\ref{fig:figure-11} bottom left) clarifies the reason for the highly unfaithful explanation.
+Case NM falls on boundaries of regions for these three features where the random forest predictions transition from below 0.5 to above 0.5.
+However, the regions created when applying LIME from the 4-quantile-bins where case NM falls contain mostly observations with random forest predictions above 0.5.
+leading to the unfaithful explanation.}
+
+\kge{Figure~\ref{fig:figure-11} (top right) shows the LIME explanation for case NM when 4-equal-bins are used.
+Here, the features identified as important are distance and mismatches, which support a match and matches, which supports a non-match.
+This explanation is more faithful having at least one feature supporting a non-match and has a better linear fit, but the most important feature identified by LIME still supports a match, contradicting the random forest.
+The explanation scatterplot (Figure~\ref{fig:figure-11} bottom right) again shows the features supporting a match arise from NM falling on the boundary of random forest prediction regions that are not well captured by the LIME bins.}
+
+\kge{Without an assessment of the LIME explanations, the default method would produce poor explanations such as the one shown in Figure~\ref{fig:figure-11} (left column).
+Our assessment here led to better explanations when the four equal bins are used.
+However, the explanation quality is still lacking from the one prediction considered.
+Additional investigations using explanations scatterplots would help to determine whether to trust this set of explanations, continue tuning the LIME parameters, or use another approach to provide better insight.}
+
+\sout{We focus on the explanation for case NM with 4-quantile-bins.
+The explanation plot from the \emph{lime} R package shows that the observed values of NM of mismatches less than or equal to 7.17, rough correlation (rough\_cor) greater than 0.05, and D less than or equal to 0.002 support a random forest prediction in favor of a match.
 The scatter plots show that many of the simulated values in the rectangular regions with mismatches less than 7.17, rough correlation greater than 0.05, and distance less than or equal to 0.002 have random forest predictions greater than 0.5, which agrees with the LIME explanation.
 However, the random forest assigns a probability of 0.21 to case NM, which is not explained by the LIME explanation that provides all explanations in support of a match.
-Instead, consider that a better explanation based on the scatterplots would be that the random forest assigned a prediction probably below 0.5 since NM has observed values of mismatches less than 5, rough correlation greater than 0.25, and distance greater than 0.001.
-
-The other explanation scatterplots can be interpreted in a similar manner.
-The three plots depict situations where the explanations are faithful to the random forest, but the regions captured by the intersections of the bins do not align well with the regions containing similar probabilities produced by the random forest.
+Instead, consider that a better explanation based on the scatterplots would be that the random forest assigned a prediction probably below 0.5 since NM has observed values of mismatches less than 5, rough correlation greater than 0.25, and distance greater than 0.001.}
+
+\sout{The other explanation scatterplots can be interpreted in a similar manner.
+The three plots depict situations where the explanations are faithful to the random forest, but the regions captured by the intersections of the bins do not align well with the regions containing similar probabilities produced by the random forest.}
 
@@
 
-Without applying LIME with multiple tuning parameter values to the bullet test data or viewing diagnostic plots of the LIME explanations, it may be very possible to formulate reasons why the LIME explanations make sense.
+\sout{Without applying LIME with multiple tuning parameter values to the bullet test data or viewing diagnostic plots of the LIME explanations, it may be very possible to formulate reasons why the LIME explanations make sense.
 However, the sequence of plots in this section (Figures \ref{fig:figure-09}, \ref{fig:figure-10}, and \ref{fig:figure-11}) suggest that we should be cautious to trust any of these LIME explanations.
-It appears that either LIME needs to be further tuned to provide trustworthy and good explanations, or a different approach may provide better insight.
+It appears that either LIME needs to be further tuned to provide trustworthy and good explanations, or a different approach may provide better insight.}
 
@@
 Even with an explainer model that is interpreted correctly, the interpretation is worthless if the explainer model is not \textbf{faithful} to the complex model.
-This claim can be assessed using the diagnostic plots suggested in this paper.
-Many of the visualizations in this paper highlight problems with the faithfulness of the explainer models.
+\sout{This claim can be assessed using the diagnostic plots suggested in this paper.} Many of the visualizations in this paper highlight problems with the faithfulness of the explainer models.
 The explanation scatterplots allow for a comparison of the explainer model to the complex model.
-The examples in this paper show cases where the explainer model bins do not accurately capture the regions with similar random forest probabilities that contain the prediction of interest and oversimplify the model (Figures \ref{fig:figure-03} and \ref{fig:figure-11}).
+The examples in this paper show cases where the explainer model oversimplifies the model and bins do not accurately capture the regions with similar random forest probabilities that contain the prediction of interest (Figures \ref{fig:figure-03} and \ref{fig:figure-11}).
 Using fewer bins would clearly not help improve the faithfulness of the explainer model in these examples, and while an increase in the number of bins would lead to a finer resolution of the random forest classification boundaries, interpretability of the explainer model would quickly be lost.
@@
 
-In addition to assessing faithfulness by visually comparing the complex and explainer model, we propose a visual comparison of two faithfulness metrics (MSEE and average fidelity).
+\kgc{Rethink what I want to say here.} In addition to assessing faithfulness by visually comparing the complex and explainer model, we propose a visual comparison of two faithfulness metrics (MSEE and average fidelity).
 The examples of faithfulness metric comparisons in this paper both produced conflicting results (Figures \ref{fig:figure-05} and \ref{fig:figure-10}).
@@
 Most of the average $R^2$ values in the examples from this paper are below 0.5 suggesting a poor linear fit of the explainer models.
-A poor linear fit of the explainer model is also seen with the residual plot (\autoref{fig:figure-C3}).
-
-The final claim, \textbf{localness}, is addressed by the feature heatmap and metric comparison plots.
+A poor linear fit of the explainer model is also seen with the residual plot (\autoref{fig:figure-C2}).
+
+\kgc{Need to focus more on how LIME fails with localness.} The final claim, \textbf{localness}, is addressed by the feature heatmap and metric comparison plots.
 As stated, the feature heatmap reveals that the density simulation methods in the \data \ example  results in global explanations where the same features are repeatedly chosen across all (or almost all) observations in the set of explanations.
 This finding agrees with that of \citet{laugel:2018} who found LIME produced global explanations with the normal approximation simulation method.
-For the bin based simulation methods in the bullet data example, the feature heatmap shows that the features chosen for the explanations vary between the two classification categories (match versus non-match).
-This is an interesting finding that suggests that different features can play a role in the predictions of observations in different response categories.
-Furthermore, while the metric comparison plot in the bullet example does not provide agreement between metrics on a best bin based method, all metrics agree that a Gower power of 0.5 for computing the model weights associated with distance of a simulated data point from the prediction of interest is the best.
-This suggests that a less local explanation provides a better explanation of the performance of the random forest.
-
-Some of the visualizations in the paper generalize easily to any application of LIME such as the feature heatmap and metric plot.
-Other plots such as the visualizations of the LIME procedure would require extensions such as the use of scatterplot matrices to compare explanations with more than two features.
-The addition of interactivity to the diagnostic plots would provide additional enhancement of the assessment process.
+\sout{For the bin based simulation methods in the bullet data example, the feature heatmap shows that the features chosen for the explanations vary between the two classification categories (match versus non-match).
+This is an interesting finding that suggests that different features can play a role in the predictions of observations in different response categories.} Furthermore, while the metric comparison plot in the bullet example does not provide agreement between metrics on a best bin based method, all metrics agree that a Gower power of 0.5 for computing the model weights associated with distance of a simulated data point from the prediction of interest is the best.
+This suggests that a \sout{less} \kge{more} local explanation provides a better explanation of the performance of the random forest.
+
+\sout{Some of the visualizations in the paper generalize easily to any application of LIME such as the feature heatmap and metric plot.
+Other plots such as the visualizations of the LIME procedure would require extensions such as the use of scatterplot matrices to compare explanations with more than two features.} \kgc{Add a sentence transitioning to say something about these plots being a starting point that could be expanded on and examples of how.} The addition of interactivity to the diagnostic plots would \sout{provide additional} enhance\sout{ment of} the assessment process.
 For example, a diagnostic plot that provides a summary of multiple LIME explanations, such as the feature heatmap, could be displayed and clicked on to reveal more detailed figures associated with individual predictions of interest, such as an explanation scatterplot.
@@
 While it would be ideal if LIME could be used as a method to provide easily understandable explanations for black-box models as \citet{ribeiro:2016} claim, that dream is not yet a reality.
-The examples using diagnostic plots to assess LIME in this paper show frequent issues with LIME.
-We hope that our plots provide motivation to assess LIME explanations, to not blindly use the default settings (even if it is not clear how to tune the parameters), and to encourage work on improving LIME, so that it can be a lime and not a lemon.
+The examples using diagnostic plots to assess LIME in this paper show frequent \kge{instances when the claims about LIME are not met} \sout{issues with LIME}.
+We hope that our plots provide motivation to assess LIME explanations, to not blindly use the default settings (even if it is not clear how to tune the parameters), and to encourage work \sout{on} improving LIME, so that it can be a lime and not a lemon.
 
@@
 
-\begin{figure*}[!thp]
-<<figure-B2, out.width = '6.5in', fig.width = 12, fig.height = 10, fig.align = "center">>=
-
-# Specify the figure size (for determining font size and line size)
-fb2_ow = 6.5
-fb2_fw = 12
-fb2_fs = fs * (fb2_fw / fb2_ow)
-fb2_ls = 0.5 * (fb2_fw / fb2_ow)
-
-# Create the explanation scatterplot: case M, kernel density
-bullet_es_M <-
-  plot_explain_scatter(
-    bullet_explain_perms[16:18, ] %>% mutate(case = "NM"),
-    alpha = 0.75,
-    title.opt = TRUE,
-    line_size = fb2_ls
-  ) +
-  scale_fill_gradient2(
-    low = "grey50",
-    high = "darkorange",
-    midpoint = 0.5,
-    limits = c(0, 1)
-  ) +
-  theme_bw(base_family = ff, base_size = fb2_fs) +
-  theme(
-    aspect.ratio = 1,
-    strip.background = element_rect(fill = "white", color = "white"),
-    strip.placement = "outside",
-    strip.text.x = element_text(size = fb2_fs),
-    plot.title = element_text(size = fb2_fs)
-  )
-
-# Create the explanation scatterplot: case NM, kernel density
-bullet_es_NM <-
-  plot_explain_scatter(
-    bullet_explain_perms[13:15, ] %>% mutate(case = "M"),
-    alpha = 0.75,
-    title.opt = TRUE, 
-    line_size = fb2_ls
-  ) +
-  scale_fill_gradient2(
-    low = "grey50",
-    high = "darkorange",
-    midpoint = 0.5,
-    limits = c(0, 1)
-  ) +
-  theme_bw(base_family = ff, base_size = fb2_fs) +
-  theme(
-    aspect.ratio = 1,
-    strip.background = element_rect(fill = "white", color = "white"),
-    strip.placement = "outside",
-    strip.text.x = element_text(size = fb2_fs), 
-    plot.title = element_text(size = fb2_fs)
-  )
-
-# Join the plots
-plot_grid(bullet_es_NM, bullet_es_M, nrow = 2)
-
-@
-\caption{Explanation scatterplots for LIME explanations using kernel density simulation for the cases M and NM of the bullet comparison test data.}
-\label{fig:figure-B2}
-\end{figure*}
-
 Section \ref{exp-scatter} introduces explanation scatterplots under the default simulation method in the \emph{lime} R package: 4-quantile-bins.
@@
 Figure \ref{fig:figure-B1} provides example explanation scatterplots for each feature in the default LIME explanation obtained using the kernel density simulation method for the \data \ prediction of interest.
-Figure \ref{fig:figure-B2} includes explanation scatterplots for the explanations generated using kernel density simulation for the bullet example cases M and NM discussed in Section \ref{bullet-assess-ex}.
+\sout{Figure \ref{fig:figure-F5} includes explanation scatterplots for the explanations generated using kernel density simulation for the bullet example cases M and NM discussed in Section \ref{bullet-assess-ex}.}
 
@@
 In order to assess the claim of linearity for the \data \ prediction of interest discussed in Section \ref{exp-scatter}, we use one of the most basic diagnostics in a statistician's tool box and draw a residual plot for the explainer model.
-This is shown in Figure \ref{fig:figure-C3} with the explainer model residuals on the y-axis and explainer model predictions on the x-axis.
+This is shown in Figure \ref{fig:figure-C2} with the explainer model residuals on the y-axis and explainer model predictions on the x-axis.
 The points along the x-axis have been jittered to ease the effect of the over-plotted points in the visualization.
@@
 \begin{figure}[!thp]
-<<figure-C3, out.width = '3.125in', fig.width = 5, fig.height = 4, warning = FALSE>>=
+<<figure-C2, out.width = '3.125in', fig.width = 5, fig.height = 4, warning = FALSE>>=
 
 # Specify the figure size (for determining font size and line size)
-fc3_ow = 3.125
-fc3_fw = 5
-fc3_fs = fs * (fc3_fw / fc3_ow)
-fc3_ls = 0.5 * (fc3_fw / fc3_ow)
+fc2_ow = 3.125
+fc2_fw = 5
+fc2_fs = fs * (fc2_fw / fc2_ow)
+fc2_ls = 0.5 * (fc2_fw / fc2_ow)
 
@@
 ggplot(sine_poi_perms, aes(x = exppred, y = resid)) +
-  geom_hline(yintercept = 0, size = fc3_ls) +
+  geom_hline(yintercept = 0, size = fc2_ls) +
   geom_jitter(alpha = 0.5, width = 0.02) +
-  theme_bw(base_family = ff, base_size = fc3_fs) +
-  theme(plot.title = element_text(size = fc3_fs)) +
+  theme_bw(base_family = ff, base_size = fc2_fs) +
+  theme(plot.title = element_text(size = fc2_fs)) +
   labs(x = "Explainer Model Predictions",
@@
 There is an upward trend in the residuals as the explainer model predictions increase, which suggests a violation of the linearity assumption.}
-\label{fig:figure-C3}
+\label{fig:figure-C2}
 \end{figure}
@@
 
-Two hypothetical examples of feature heatmaps are included in \autoref{fig:figure-D4}.
+Two hypothetical examples of feature heatmaps are included in \autoref{fig:figure-D3}.
 The plots are created with the assumption that LIME is applied to select the top feature out of $p=4$  features for $n=10$ cases with $t=5$ sets of tuning parameter values.
@@
 \begin{figure}[!thp]
-<<figure-D4, out.width = '3.125in', fig.width = 6, fig.height = 3>>=
+<<figure-D3, out.width = '3.125in', fig.width = 6, fig.height = 3>>=
 
 # Specify the figure size (for determining font size)
-fd4_ow = 3.125
-fd4_fw = 6
-fd4_fs = fs * (fd4_fw / fd4_ow)
+fd3_ow = 3.125
+fd3_fw = 6
+fd3_fs = fs * (fd3_fw / fd3_ow)
 
@@
   ) +
-  theme_bw(base_family = ff, base_size = fd4_fs) +
+  theme_bw(base_family = ff, base_size = fd3_fs) +
   scale_fill_grey() +
@@
   theme(legend.position = "none", 
-        plot.title = element_text(size = fd4_fs))
+        plot.title = element_text(size = fd3_fs))
 
@@
   ) +
-  theme_bw(base_family = ff, base_size = fd4_fs) +
-  theme(plot.title = element_text(size = fd4_fs)) +
+  theme_bw(base_family = ff, base_size = fd3_fs) +
+  theme(plot.title = element_text(size = fd3_fs)) +
   scale_fill_grey() +
@@
 Situation 1 is the ideal, because the explanations vary across cases but do not dependent on specific tuning parameter values.}
-\label{fig:figure-D4}
+\label{fig:figure-D3}
 \end{figure}
@@
 
-\section{Matching Bullets Explanation Scatterplots} \label{match-bullets}
+\section{Additional Bullet Matching Explanation Scatterplots} \label{bullets-plus}
+
+\kge{Figure \ref{fig:figure-F5} includes explanation scatterplots for the explanations generated using kernel density simulation for the bullet example cases M and NM discussed in Section \ref{bullet-assess-ex}.}
+
+\kge{The other explanation scatterplots can be interpreted in a similar manner.
+The three plots depict situations where the explanations are faithful to the random forest, but the regions captured by the intersections of the bins do not align well with the regions containing similar probabilities produced by the random forest.}
 
 \begin{figure*}[!thp]
-<<figure-e5, out.width = '6.25in', fig.width = 13, fig.height = 8.75, message = FALSE>>=
+<<figure-F4, out.width = '6.25in', fig.width = 13, fig.height = 8.75, message = FALSE>>=
 
 # Specify the figure size (for determining font size)
-fe5_ow = 6.25
-fe5_fw = 13
-fe5_fs = fs * (fe5_fw / fe5_ow)
-fe5_ls = 0.5 * (fe5_fw / fe5_ow)
+ff4_ow = 6.25
+ff4_fw = 13
+ff4_fs = fs * (ff4_fw / ff4_ow)
+ff4_ls = 0.5 * (ff4_fw / ff4_ow)
 
@@
     weights = TRUE,
-    line_size = fe5_ls
+    line_size = ff4_ls
   ) +
@@
 The plots provide insights into the LIME explanations and allow for the assessment of the explanation quality.}
-\label{fig:figure-e5}
+\label{fig:figure-F4}
 \end{figure*}
 
+\begin{figure*}[!thp]
+<<figure-F5, out.width = '6.5in', fig.width = 12, fig.height = 10, fig.align = "center">>=
+
+# Specify the figure size (for determining font size and line size)
+ff5_ow = 6.5
+ff5_fw = 12
+ff5_fs = fs * (ff5_fw / ff5_ow)
+ff5_ls = 0.5 * (ff5_fw / ff5_ow)
+
+# Create the explanation scatterplot: case M, kernel density
+bullet_es_M <-
+  plot_explain_scatter(
+    bullet_explain_perms[16:18, ] %>% mutate(case = "NM"),
+    alpha = 0.75,
+    title.opt = TRUE,
+    line_size = ff5_ls
+  ) +
+  scale_fill_gradient2(
+    low = "grey50",
+    high = "darkorange",
+    midpoint = 0.5,
+    limits = c(0, 1)
+  ) +
+  theme_bw(base_family = ff, base_size = ff5_fs) +
+  theme(
+    aspect.ratio = 1,
+    strip.background = element_rect(fill = "white", color = "white"),
+    strip.placement = "outside",
+    strip.text.x = element_text(size = ff5_fs),
+    plot.title = element_text(size = ff5_fs)
+  )
+
+# Create the explanation scatterplot: case NM, kernel density
+bullet_es_NM <-
+  plot_explain_scatter(
+    bullet_explain_perms[13:15, ] %>% mutate(case = "M"),
+    alpha = 0.75,
+    title.opt = TRUE, 
+    line_size = ff5_ls
+  ) +
+  scale_fill_gradient2(
+    low = "grey50",
+    high = "darkorange",
+    midpoint = 0.5,
+    limits = c(0, 1)
+  ) +
+  theme_bw(base_family = ff, base_size = ff5_fs) +
+  theme(
+    aspect.ratio = 1,
+    strip.background = element_rect(fill = "white", color = "white"),
+    strip.placement = "outside",
+    strip.text.x = element_text(size = ff5_fs), 
+    plot.title = element_text(size = ff5_fs)
+  )
+
+# Join the plots
+plot_grid(bullet_es_NM, bullet_es_M, nrow = 2)
+
+@
+\caption{Explanation scatterplots for LIME explanations using kernel density simulation for the cases M and NM of the bullet comparison test data.}
+\label{fig:figure-F5}
+\end{figure*}
+
 \end{document}

### 2020-12-17 paper.tex
more trimming (almost done with the first round!)

@@
 \end{knitrout}
-\caption{\kge{Hypothetical scenarios depicting the effect of different weights on LIME (Left) An example of an explainer model with appropriate weights to provide a faithful approximation of the complex model.
+\caption{\kge{Hypothetical scenarios depicting the effect of different weights on LIME.
+(Left) An example of an explainer model with appropriate weights to provide a faithful approximation of the complex model.
 (Right) An example of an explainer model for the same prediction but with different weights that results in an explanation unfaithful to the complex model.} \sout{A conceptual depiction of a faithful LIME explainer model in the immediate neighborhood of a prediction of interest \kge{for a hypothetical black-box model trained using two features: Feature 1 (left) and Feature 2 (right).
@@
 \end{knitrout}
-\caption{Parallel coordinate plots of the \citet{hare:2017} random forest predictions from the training (top facet) and testing (bottom facet) data.
-The observations are separated by known matching (right column) and non-matching (left column) signatures.
-The y-axis shows the standardized feature values, and the x-axis shows the features used to fit the random forest (ordered by random forest impurity based feature importance).
-Each line corresponds to an observation, and the line color represents the associated random forest probability.
+\caption{Parallel coordinate plots of the \kge{bullet matching} \sout{\citet{hare:2017}} random forest predictions\sout{from the training (top \kge{row}\sout{facet}) and testing (bottom \kge{row}\sout{facet}) data}.
+\sout{The observations are separated by known matching (right column) and non-matching (left column) signatures.
+The y-axis shows the standardized feature values, and the x-axis shows the features used to fit the random forest (ordered by random forest impurity based feature importance).} Each line corresponds to an observation, and the line color represents the associated random forest probability.
 There are clear relationships between the feature values and the random forest probabilities.}
@@
 
-\begin{figure*}[!thp]
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-
-{\centering \includegraphics[width=6.5in]{figure/figure-B2-1}
-
-}
-
-\end{knitrout}
-\caption{Explanation scatterplots for LIME explanations using kernel density simulation for the cases M and NM of the bullet comparison test data.}
-\label{fig:figure-B2}
-\end{figure*}
-
 Section \ref{exp-scatter} introduces explanation scatterplots under the default simulation method in the \emph{lime} R package: 4-quantile-bins.
@@
 
-{\centering \includegraphics[width=3.125in]{figure/figure-C3-1}
+{\centering \includegraphics[width=3.125in]{figure/figure-C2-1}
 
@@
 
-{\centering \includegraphics[width=3.125in]{figure/figure-D4-1}
+{\centering \includegraphics[width=3.125in]{figure/figure-D3-1}
 
@@
 
-\section{Matching Bullets Explanation Scatterplots} \label{match-bullets}
+\section{Additional Bullet Matching Explanation Scatterplots} \label{bullets-plus}
+
+\kge{Figure \ref{fig:figure-F5} includes explanation scatterplots for the explanations generated using kernel density simulation for the bullet example cases M and NM discussed in Section \ref{bullet-assess-ex}.}
+
+\kge{The other explanation scatterplots can be interpreted in a similar manner.
+The three plots depict situations where the explanations are faithful to the random forest, but the regions captured by the intersections of the bins do not align well with the regions containing similar probabilities produced by the random forest.}
 
@@
 
-{\centering \includegraphics[width=6.25in]{figure/figure-e5-1}
+{\centering \includegraphics[width=6.25in]{figure/figure-F4-1}
 
@@
 The plots provide insights into the LIME explanations and allow for the assessment of the explanation quality.}
-\label{fig:figure-e5}
+\label{fig:figure-F4}
 \end{figure*}
 
+\begin{figure*}[!thp]
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+
+{\centering \includegraphics[width=6.5in]{figure/figure-F5-1}
+
+}
+
+\end{knitrout}
+\caption{Explanation scatterplots for LIME explanations using kernel density simulation for the cases M and NM of the bullet comparison test data.}
+\label{fig:figure-F5}
+\end{figure*}
+
 \end{document}

### 2020-12-17 paper.Rnw
finished first round of revisions

@@
 Since the explainer model is an approximation of the complex model and not a direct interpretation, the explanations produced by an explainer model are subject to the quality of the approximation.
-Thus, in order to achieve \kge{reasonable} \sout{accurate} explanations, the tuning parameter values selected \kge{shoud} \sout{need to} be assessed.
+\sout{Thus, i }\kge{I}n order to achieve \kge{reasonable} \sout{accurate} explanations, the tuning parameter values selected \kge{shoud} \sout{need to} be assessed.
 
@@
 \kge{\autoref{fig:figure-01} demonstrates a simple example in which the explanation quality varies drastically when different weights are used.
-Similar concerns with LIME have been raised in the literature.} \sout{Several sources in the literature discuss the performance of LIME.} \kge{\citet{laugel:2018} and \citet{molnar:2019} discuss the difficulty specifying a local region with LIME due to both} \sout{One of the biggest difficulties with LIME is determining how to specify a local region \citep{laugel:2018} \citep{molnar:2019}.
+Other concerns with LIME have been raised in the literature.} \sout{Several sources in the literature discuss the performance of LIME.} \kge{\citet{laugel:2018} and \citet{molnar:2019} discuss the difficulty specifying a local region with LIME due to both} \sout{One of the biggest difficulties with LIME is determining how to specify a local region \citep{laugel:2018} \citep{molnar:2019}.
 This is due to} an unclear definition of \kge{what is} a "local region" and how to apply LIME to achieve an appropriate local region\sout{ as demonstrated by \autoref{fig:figure-02}}.
-\kge{A different concern about LIME is raised by} \citet{alvarezmelis:2018} \sout{raise a concern} pertaining to the robustness of explanations from LIME and other \kge{explainer} model\kge{s} \sout{explainers}: they find that even small changes in predictor variables can lead to very different LIME explanations.
+\kge{\citet{laugel:2018} also present examples of LIME explanations that are clearly global and not local.} \kge{A different concern about LIME is raised by} \citet{alvarezmelis:2018} \sout{raise a concern} pertaining to the robustness of explanations from LIME and other \kge{explainer} model\kge{s} \sout{explainers}: they find that even small changes in predictor variables can lead to very different LIME explanations.
 \kge{Even the original authors of LIME,} \sout{Additionally,} \citet{ribeiro:2016}\kge{,} acknowledge that if a linear model is used as the explainer, LIME relies on a linear approximation of the explainer model to the complex model and state "if the underlying model is highly non-linear even in the locality of the prediction, there may not be a faithful explanation".
@@
 While LIME is implemented for image, tabular, and text data, we only focus on tabular data.
-For additional simplicity, we only discuss classification prediction models with a dichotomous response variable and continuous predictor variables.
+For additional simplicity, we only discuss classification prediction models with a dichotomous response \sout{variable} and continuous predictor\sout{ variable}s.
 However, the proposed diagnostics may be extended to \kge{other} \sout{a wider range of} situations.
@@
 The forked version is functionally indistinguishable from \citeauthor{pedersen:2020}'s implementation but allows us to export internal values relevant for an assessment of the explainer.
-The \kge{code for the} diagnostic plots included in this paper \kge{is stored in} \sout{are created using} the R package \emph{limeaid} \citep{goode:2020}.
+The \kge{code for the} diagnostic plots \sout{included in this paper} \kge{is stored in} \sout{are created using} the R package \emph{limeaid} \citep{goode:2020}.
 
@@
 
-\kgc{I ended up moving some of the paragraphs in this section around and adding a little bit of additional text. I think this organization flows more smoothly. What do you think?}
-
-The general form of the LIME algorithm can be divided into three steps \citep[see also][]{laugel:2018}:
+\kgc{I moved the paragraphs in this section around} The general form of the LIME algorithm can be divided into three steps \citep[see also][]{laugel:2018}:
 
@@
 The features included in the visualization are the ones selected by feature selection, the lengths of the bars represent the coefficients from the ridge regression associated with the indicator variables, and the color of a bar denotes the sign of the coefficient.
-This explainer model explains that the random forest prediction that the observation of interest belongs to the category of blue is mostly supported by the prediction of interest having a value of $x_2$ that is greater than \Sexpr{str_split(sine_poi_lime_default$feature_desc[[1]], pattern = " ")[[1]][1]} but somewhat contradicted by the prediction of interest having a value of $x_1$ that is greater than \Sexpr{str_split(sine_poi_lime_default$feature_desc[[2]], pattern = " ")[[1]][1]} and less than or equal to \Sexpr{str_split(sine_poi_lime_default$feature_desc[[2]], pattern = " ")[[1]][5]}.} \kgc{I decided to leave the values here, because this is how I would interpret this explanation, but I cut out a lot of text from this subsection in other ways.}
+This explainer model explains that the random forest prediction that the observation of interest belongs to the category of blue is mostly supported by the prediction of interest having a value of $x_2$ that is greater than \Sexpr{str_split(sine_poi_lime_default$feature_desc[[1]], pattern = " ")[[1]][1]} but somewhat contradicted by the prediction of interest having a value of $x_1$ that is greater than \Sexpr{str_split(sine_poi_lime_default$feature_desc[[2]], pattern = " ")[[1]][1]} and less than or equal to \Sexpr{str_split(sine_poi_lime_default$feature_desc[[2]], pattern = " ")[[1]][5]}.} \kgc{I decided to leave the values here.
+I actually prefer it this way myself, but I cut out a lot of text from this subsection in other ways.}
 
@@
 \begin{figure*}[!thp]
-<<figure-11, out.width = '6.25in', fig.width = 13, fig.height = 8.75, message = FALSE>>=
+<<figure-11, out.width = '6.25in', fig.width = 13, fig.height = 8.5, message = FALSE>>=
 
@@
   nrow = 2,
-  rel_heights = c(0.2, 0.3)
+  rel_heights = c(0.4, 0.6)
 )
@@
 \caption{Plots of LIME explanations (first row) and explanation scatterplots (second row) for case NM in the bullet test data for two tuning parameter values: 4-quantile-bins (first column) and 4-equal-bins (second column).
-The plots provide insights into the LIME explanations and allow for the assessment of the explanation quality.}
+\sout{The plots provide insights into the LIME explanations and allow for the assessment of the explanation quality.}}
 \label{fig:figure-11}
@@
 This paper highlights that while an explainer model is meant to provide clarity, it actually adds another layer of complexity to predictive models by requiring yet another model that needs to be assessed.
-Without an assessment of the explainer model, LIME is a black-box procedure of its own requiring blind trust in the explainer model.
-We suggest the use of visual diagnostics to counteract the black-box nature of LIME and provide three diagnostic plots.
-
-The visualizations are intended to provide insight on how LIME works, assess the ability of the explainer model to capture the complex predictive model, and compare LIME explanations produced by different tuning parameter values.
+Without an assessment of the explainer model, LIME is a black-box procedure \sout{of its own} requiring blind trust in the explainer model.
+We suggest the use of visual diagnostics to counteract the black-box nature of LIME\sout{ and provide three diagnostic plots}.
+\kge{We provide three diagnostic plots} \sout{The \kge{plots} \sout{visualizations} are} intended to \kge{assess whether LIME explanations meet the claims made by \citet{ribeiro:2016}.
+The examples in this paper bring to light many scenarios in which the claims are not met or are difficult to assess.
+We reconsider each of the claims and how the visual diagnostics identify their failings.} \sout{provide insight on how LIME works, assess the ability of the explainer model to capture the complex predictive model, and compare LIME explanations produced by different tuning parameter values.
 While the visualizations accomplish these tasks, they also expose examples of the failings of LIME.
-To address the discovered failings of LIME, we reconsider each of the claims about the performance of LIME made by \citet{ribeiro:2016} in light of the insights gained from the diagnostic visualizations.
+To address the discovered failings of LIME, we reconsider each of the claims about the performance of LIME made by \citet{ribeiro:2016} in light of the insights gained from the diagnostic visualizations.}
 
@@
 
-Even though an explanation will be interpretable as long as the complexity of the explainer model is appropriately chosen, a lack of understanding of the process used to create the explanation could lead to an incorrect interpretation of the explanation.
-For example, the visualization of a LIME explanation available from the \emph{lime} R package \citep{pedersen:2020} (shown in Figures \ref{fig:figure-03} and \ref{fig:figure-11}) is a major simplification of the explainer model, which could lead to under-interpreted or misinterpreted LIME explanation.
-Supplementing \citet{pedersen:2020}'s compact visualization of the explanation with an explanation scatterplot that shows a more detailed visualization of the explainer model promotes a more complete understanding of the explanation (such as Figures~\ref{fig:figure-03} and \ref{fig:figure-11}).
+Even though an explanation will be interpretable \kge{if} \sout{as long as} the complexity of the explainer model is appropriately chosen, a lack of understanding of the \kge{explainer model} \sout{process used to create the explanation} could lead to an incorrect interpretation of the explanation.
+For example, the visualization of a LIME explanation \sout{available} from the \emph{lime} R package \citep{pedersen:2020} (\sout{shown in }Figure\sout{s} \ref{fig:figure-03} \kge{left; } \sout{and} \kge{Figure} \ref{fig:figure-11} \kge{top}) is a \sout{major} simplification of the explainer model, which could lead to \sout{under-interpreted or} misinterpreted LIME explanation\kge{s}.
+Supplementing \citet{pedersen:2020}'s compact visualization of the explanation with an explanation scatterplot that shows a more detailed visualization of the explainer model promotes a more complete understanding of the explanation (\sout{such as }Figures~\ref{fig:figure-03} \kge{right; } \sout{and} \ref{fig:figure-11} \kge{bottom}).
 
 Even with an explainer model that is interpreted correctly, the interpretation is worthless if the explainer model is not \textbf{faithful} to the complex model.
-\sout{This claim can be assessed using the diagnostic plots suggested in this paper.} Many of the visualizations in this paper highlight problems with the faithfulness of the explainer models.
-The explanation scatterplots allow for a comparison of the explainer model to the complex model.
+\sout{This claim can be assessed using the diagnostic plots suggested in this paper.
+Many of the visualizations in this paper highlight problems with the faithfulness of the explainer models.
+The e} \kge{E}xplanation scatterplots allow for a comparison of the explainer model to the complex model.
 The examples in this paper show cases where the explainer model oversimplifies the model and bins do not accurately capture the regions with similar random forest probabilities that contain the prediction of interest (Figures \ref{fig:figure-03} and \ref{fig:figure-11}).
@@
 
-\kgc{Rethink what I want to say here.} In addition to assessing faithfulness by visually comparing the complex and explainer model, we propose a visual comparison of two faithfulness metrics (MSEE and average fidelity).
-The examples of faithfulness metric comparisons in this paper both produced conflicting results (Figures \ref{fig:figure-05} and \ref{fig:figure-10}).
-This makes it difficult to decide on a recommendation of a set of tuning parameter values that produce the explanations with the most faithful explainer model.
+\sout{In addition to assessing faithfulness by visually comparing the complex and explainer model, w}\kge{W}e \kge{also} propose a\kge{n assessment metric plot for the} visual comparison of two faithfulness metrics: MSEE and average fidelity.
+\kge{Both metrics measure faithfulness, but MSEE only accounts for the prediction of interest while average fidelity accounts for all observations in the simulated data.
+As a result, the measures may disagree (Figures \ref{fig:figure-05} and \ref{fig:figure-10}), and the user is left to determine which is preferable.} \sout{The examples of faithfulness metric comparisons in this paper both produced conflicting results (Figures \ref{fig:figure-05} and \ref{fig:figure-10}).
+This makes it difficult to decide on a recommendation of a set of tuning parameter values that produce the explanations with the most faithful explainer model.}
 
@@
 Most of the average $R^2$ values in the examples from this paper are below 0.5 suggesting a poor linear fit of the explainer models.
-A poor linear fit of the explainer model is also seen with the residual plot (\autoref{fig:figure-C2}).
-
-\kgc{Need to focus more on how LIME fails with localness.} The final claim, \textbf{localness}, is addressed by the feature heatmap and metric comparison plots.
-As stated, the feature heatmap reveals that the density simulation methods in the \data \ example  results in global explanations where the same features are repeatedly chosen across all (or almost all) observations in the set of explanations.
+A poor linear fit of the explainer model is also seen with the residual plot \kge{shown in} \sout{(}\autoref{fig:figure-C2}\sout{)}.
+
+The final claim, \textbf{localness}, is addressed by \sout{the} feature heatmap\kge{s} and \kge{explanation scatterplots}\sout{ metric comparison plots}.
+\kge{The vertical stripes seen in the feature heatmaps (Figures \ref{fig:figure-04} and \ref{fig:figure-09}) suggest global explanations produced by LIME since the same explanation is returned for almost all observations regardless of feature values.
+The explanation scatterplots visualize the locality of the explanation using point size to indicate weight.
+However, the lack of definition of a local region makes it difficult to assess whether the weights capture an appropriately local region.} \sout{As stated, the feature heatmap reveals that the density simulation methods in the \data \ example results in global explanations where the same features are repeatedly chosen across all (or almost all) observations in the set of explanations.
 This finding agrees with that of \citet{laugel:2018} who found LIME produced global explanations with the normal approximation simulation method.
-\sout{For the bin based simulation methods in the bullet data example, the feature heatmap shows that the features chosen for the explanations vary between the two classification categories (match versus non-match).
-This is an interesting finding that suggests that different features can play a role in the predictions of observations in different response categories.} Furthermore, while the metric comparison plot in the bullet example does not provide agreement between metrics on a best bin based method, all metrics agree that a Gower power of 0.5 for computing the model weights associated with distance of a simulated data point from the prediction of interest is the best.
-This suggests that a \sout{less} \kge{more} local explanation provides a better explanation of the performance of the random forest.
+For the bin based simulation methods in the bullet data example, the feature heatmap shows that the features chosen for the explanations vary between the two classification categories (match versus non-match).
+This is an interesting finding that suggests that different features can play a role in the predictions of observations in different response categories.
+Furthermore, while the metric comparison plot in the bullet example does not provide agreement between metrics on a best bin based method, all metrics agree that a Gower power of 0.5 for computing the model weights associated with distance of a simulated data point from the prediction of interest is the best.
+This suggests that a \sout{less} \kge{more} local explanation provides a better explanation of the performance of the random forest.}
 
 \sout{Some of the visualizations in the paper generalize easily to any application of LIME such as the feature heatmap and metric plot.
-Other plots such as the visualizations of the LIME procedure would require extensions such as the use of scatterplot matrices to compare explanations with more than two features.} \kgc{Add a sentence transitioning to say something about these plots being a starting point that could be expanded on and examples of how.} The addition of interactivity to the diagnostic plots would \sout{provide additional} enhance\sout{ment of} the assessment process.
+Other plots such as the visualizations of the LIME procedure would require extensions such as the use of scatterplot matrices to compare explanations with more than two features.}
+
+\kge{These diagnostic visualizations are a starting point that already highlight seemingly common issues with the LIME claims.
+Additions, such as visualizations of the step-by-step process of the creation of LIME explanations and} \sout{The addition of} interactivity\kge{,} \sout{to the diagnostic plots would provide additional} enhance\sout{ment of} the assessment process.
 For example, a diagnostic plot that provides a summary of multiple LIME explanations, such as the feature heatmap, could be displayed and clicked on to reveal more detailed figures associated with individual predictions of interest, such as an explanation scatterplot.
@@
 
-\section{Explanation Scatterplots Under Other Simulation Scenarios} \label{exp-scatter_plus}
+\kge{The \emph{lime} R package uses a ridge regression fit using the \emph{glmnet} R package \citep{simon:2011} as the explainer model.
+Note that the ridge regression penalty parameter (referred to as $\lambda$ in \emph{glmnet}) is usually treated as a tuning parameter, but the \emph{lime} R package always sets $\lambda$ to 2 divided by the number of observations in the simulated dataset.}
 
@@
 
+\section{Explanation Scatterplots Under \sout{Other} \kge{Density} Simulation Scenarios} \label{exp-scatter_plus}
+
 Section \ref{exp-scatter} introduces explanation scatterplots under the default simulation method in the \emph{lime} R package: 4-quantile-bins.
@@
 
-Figure \ref{fig:figure-B1} provides example explanation scatterplots for each feature in the default LIME explanation obtained using the kernel density simulation method for the \data \ prediction of interest.
-\sout{Figure \ref{fig:figure-F5} includes explanation scatterplots for the explanations generated using kernel density simulation for the bullet example cases M and NM discussed in Section \ref{bullet-assess-ex}.}
+Figure \ref{fig:figure-B1} provides example explanation scatterplots \kge{for the \data \ prediction of interest when the kernel density simulation method is used.
+The plots show the relationships between the random forest prediction and the selected features of $x_1$ and $x_2$ on the left and right, respectively.} \sout{for each feature in the default LIME explanation obtained using the kernel density simulation method for the \data \ prediction of interest.} \sout{Figure \ref{fig:figure-F5} includes explanation scatterplots for the explanations generated using kernel density simulation for the bullet example cases M and NM discussed in Section \ref{bullet-assess-ex}.}
 
 \section{Explainer Model Residual Plot} \label{residual-plot}
-
-In order to assess the claim of linearity for the \data \ prediction of interest discussed in Section \ref{exp-scatter}, we use one of the most basic diagnostics in a statistician's tool box and draw a residual plot for the explainer model.
-This is shown in Figure \ref{fig:figure-C2} with the explainer model residuals on the y-axis and explainer model predictions on the x-axis.
-The points along the x-axis have been jittered to ease the effect of the over-plotted points in the visualization.
-There is a clear increasing trend in the residuals as the explainer model predictions increase.
-This is a clear violation of the linearity assumption with the ridge regression model.
-
-\begin{figure}[!thp]
+\begin{figure}[!b]
 <<figure-C2, out.width = '3.125in', fig.width = 5, fig.height = 4, warning = FALSE>>=
@@
 @
-\caption{Residual plot of the explainer model associated with \data \ prediction of interest from Section \ref{exp-scatter}.
+\caption{Residual plot of the explainer model associated with \data \ prediction of interest from Section \ref{exp-scatter}\sout{.
 The residuals are plotted against the predicted values.
 The points are jittered in the x-direction to alleviate the over-plotting of points.
-There is an upward trend in the residuals as the explainer model predictions increase, which suggests a violation of the linearity assumption.}
+There is\kge{a clear increase} \sout{an upward trend} in the residuals as the explainer model predictions increase}, which suggests a violation of the linearity assumption.}
 \label{fig:figure-C2}
 \end{figure}
+
+In order to assess the claim of linearity for the \data \ prediction of interest discussed in Section \ref{exp-scatter}, we use one of the most basic diagnostics in a statistician's tool box and draw a residual plot for the explainer model.
+This is shown in Figure \ref{fig:figure-C2} with the explainer model residuals on the y-axis and explainer model predictions on the x-axis.
+The points along the x-axis have been jittered to ease the effect of the over-plotted points\sout{ in the visualization}.
+There is a clear increasing trend in the residuals as the explainer model predictions increase\kge{,}\sout{.
+This is a clear} \kge{which indicates a} violation of the \kge{ridge regression} linearity assumption\sout{ with the ridge regression model}.
 
@@
 
-\begin{figure}[!thp]
+\begin{figure}[!t]
 <<figure-D3, out.width = '3.125in', fig.width = 6, fig.height = 3>>=
@@
 \caption{Hypothetical examples of feature heatmaps in two possible situations.
-The heatmaps show the top feature chosen for 10 cases across 5 different sets of tuning parameter values.
-The color of the cell indicates the feature chosen by LIME.
-Situation 1 is the ideal, because the explanations vary across cases but do not dependent on specific tuning parameter values.}
+\sout{The heatmaps show the top feature chosen for 10 cases across 5 different sets of tuning parameter values.
+The color of the cell indicates the feature chosen by LIME.} Situation 1 is the ideal, because the explanations vary across cases but do not dependent on specific tuning parameter values.
+\kge{Situation 2 suggets global explanations and extreme explanation dependence on the tuning parameter values.}}
 \label{fig:figure-D3}
@@
 
-\kge{Figure \ref{fig:figure-F5} includes explanation scatterplots for the explanations generated using kernel density simulation for the bullet example cases M and NM discussed in Section \ref{bullet-assess-ex}.}
-
-\kge{The other explanation scatterplots can be interpreted in a similar manner.
-The three plots depict situations where the explanations are faithful to the random forest, but the regions captured by the intersections of the bins do not align well with the regions containing similar probabilities produced by the random forest.}
-
-\begin{figure*}[!thp]
-<<figure-F4, out.width = '6.25in', fig.width = 13, fig.height = 8.75, message = FALSE>>=
+\kge{Figure \ref{fig:figure-F4} includes visual representations of LIME explanation from the \emph{lime} R package and explanation scatterplots for a known match observation in the the bullet example referred to as cases M for two different data simulation methods: 4-quantile-bins (left column) and 4-equal-bins (right column).
+Both explanations appear to be more faithful to the random forest than those associated with case NM in Section \ref{bullet-assess-ex}, but the intersections of the bins could be better aligned with the regions containing similar probabilities produced by the random forest.
+Figure \ref{fig:figure-F5} includes explanation scatterplots for bullet example cases M and NM when the kernel density simulation method is used.}
+
+\begin{figure*}[!t]
+<<figure-F4, out.width = '6.25in', fig.width = 13, fig.height = 8.5, message = FALSE>>=
 
@@
 @
-\caption{Plots of LIME explanations (first row) and explanation scatterplots (second row) for case M in the bullet test data for two tuning parameter values: 4-quantile-bins (first column) and 4-equal-bins (second column).
-The plots provide insights into the LIME explanations and allow for the assessment of the explanation quality.}
+\caption{Plots of LIME explanations (first row) and explanation scatterplots (second row) for case M in the bullet test data for two tuning parameter values: 4-quantile-bins (first column) and 4-equal-bins (second column).\sout{ The plots provide insights into the LIME explanations and allow for the assessment of the explanation quality.}}
 \label{fig:figure-F4}
@@
 # Join the plots
-plot_grid(bullet_es_NM, bullet_es_M, nrow = 2)
+plot_grid(bullet_es_M, bullet_es_NM, nrow = 2)
 

### 2020-12-17 paper.tex
finished first round of revisions

@@
 The features included in the visualization are the ones selected by feature selection, the lengths of the bars represent the coefficients from the ridge regression associated with the indicator variables, and the color of a bar denotes the sign of the coefficient.
-This explainer model explains that the random forest prediction that the observation of interest belongs to the category of blue is mostly supported by the prediction of interest having a value of $x_2$ that is greater than 4.834 but somewhat contradicted by the prediction of interest having a value of $x_1$ that is greater than -0.302 and less than or equal to 4.844.} \kgc{I decided to leave the values here, because this is how I would interpret this explanation, but I cut out a lot of text from this subsection in other ways.}
+This explainer model explains that the random forest prediction that the observation of interest belongs to the category of blue is mostly supported by the prediction of interest having a value of $x_2$ that is greater than 4.834 but somewhat contradicted by the prediction of interest having a value of $x_1$ that is greater than -0.302 and less than or equal to 4.844.} \kgc{I decided to leave the values here.
+I actually prefer it this way myself, but I cut out a lot of text from this subsection in other ways.}
 
@@
 \end{figure*}
+
+\section{Explanation Scatterplots Under \sout{Other} \kge{Density} Simulation Scenarios} \label{exp-scatter_plus}
 
@@
 
-Figure \ref{fig:figure-B1} provides example explanation scatterplots for each feature in the default LIME explanation obtained using the kernel density simulation method for the \data \ prediction of interest.
-\sout{Figure \ref{fig:figure-F5} includes explanation scatterplots for the explanations generated using kernel density simulation for the bullet example cases M and NM discussed in Section \ref{bullet-assess-ex}.}
+Figure \ref{fig:figure-B1} provides example explanation scatterplots \kge{for the \data \ prediction of interest when the kernel density simulation method is used.
+The plots show the relationships between the random forest prediction and the selected features of $x_1$ and $x_2$ on the left and right, respectively.} \sout{for each feature in the default LIME explanation obtained using the kernel density simulation method for the \data \ prediction of interest.} \sout{Figure \ref{fig:figure-F5} includes explanation scatterplots for the explanations generated using kernel density simulation for the bullet example cases M and NM discussed in Section \ref{bullet-assess-ex}.}
 
 \section{Explainer Model Residual Plot} \label{residual-plot}
+\begin{figure}[!b]
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+
+{\centering \includegraphics[width=3.125in]{figure/figure-C2-1}
+
+}
+
+\end{knitrout}
+\caption{Residual plot of the explainer model associated with \data \ prediction of interest from Section \ref{exp-scatter}\sout{.
+The residuals are plotted against the predicted values.
+The points are jittered in the x-direction to alleviate the over-plotting of points.
+There is\kge{a clear increase} \sout{an upward trend} in the residuals as the explainer model predictions increase}, which suggests a violation of the linearity assumption.}
+\label{fig:figure-C2}
+\end{figure}
 
@@
 This is shown in Figure \ref{fig:figure-C2} with the explainer model residuals on the y-axis and explainer model predictions on the x-axis.
-The points along the x-axis have been jittered to ease the effect of the over-plotted points in the visualization.
-There is a clear increasing trend in the residuals as the explainer model predictions increase.
-This is a clear violation of the linearity assumption with the ridge regression model.
-
-\begin{figure}[!thp]
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-
-{\centering \includegraphics[width=3.125in]{figure/figure-C2-1}
-
-}
-
-\end{knitrout}
-\caption{Residual plot of the explainer model associated with \data \ prediction of interest from Section \ref{exp-scatter}.
-The residuals are plotted against the predicted values.
-The points are jittered in the x-direction to alleviate the over-plotting of points.
-There is an upward trend in the residuals as the explainer model predictions increase, which suggests a violation of the linearity assumption.}
-\label{fig:figure-C2}
-\end{figure}
+The points along the x-axis have been jittered to ease the effect of the over-plotted points\sout{ in the visualization}.
+There is a clear increasing trend in the residuals as the explainer model predictions increase\kge{,}\sout{.
+This is a clear} \kge{which indicates a} violation of the \kge{ridge regression} linearity assumption\sout{ with the ridge regression model}.
 
@@
 
-\begin{figure}[!thp]
+\begin{figure}[!t]
 \begin{knitrout}
@@
 
-\kge{Figure \ref{fig:figure-F5} includes explanation scatterplots for the explanations generated using kernel density simulation for the bullet example cases M and NM discussed in Section \ref{bullet-assess-ex}.}
-
-\kge{The other explanation scatterplots can be interpreted in a similar manner.
-The three plots depict situations where the explanations are faithful to the random forest, but the regions captured by the intersections of the bins do not align well with the regions containing similar probabilities produced by the random forest.}
-
-\begin{figure*}[!thp]
+\kge{Figure \ref{fig:figure-F4} includes visual representations of LIME explanation from the \emph{lime} R package and explanation scatterplots for a known match observation in the the bullet example referred to as cases M for two different data simulation methods: 4-quantile-bins (left column) and 4-equal-bins (right column).
+Both explanations appear to be more faithful to the random forest than those associated with case NM in Section \ref{bullet-assess-ex}, but the intersections of the bins could be better aligned with the regions containing similar probabilities produced by the random forest.
+Figure \ref{fig:figure-F5} includes explanation scatterplots for bullet example cases M and NM when the kernel density simulation method is used.}
+
+\begin{figure*}[!t]
 \begin{knitrout}
@@
 \end{knitrout}
-\caption{Plots of LIME explanations (first row) and explanation scatterplots (second row) for case M in the bullet test data for two tuning parameter values: 4-quantile-bins (first column) and 4-equal-bins (second column).
-The plots provide insights into the LIME explanations and allow for the assessment of the explanation quality.}
+\caption{Plots of LIME explanations (first row) and explanation scatterplots (second row) for case M in the bullet test data for two tuning parameter values: 4-quantile-bins (first column) and 4-equal-bins (second column).\sout{ The plots provide insights into the LIME explanations and allow for the assessment of the explanation quality.}}
 \label{fig:figure-F4}

### 2020-12-30 paper.Rnw
removing extraneous text

@@
 \begin{document}
+\SweaveOpts{concordance=TRUE}
 
 % Paper header (title and authors)
-\title{Visual Diagnostics of a\kge{n} \sout{Model} Explainer \kge{Model} -- Tools for the Assessment of LIME Explanations}
+\title{Visual Diagnostics of a\kge{n}  Explainer \kge{Model} -- Tools for the Assessment of LIME Explanations}
 \author[1]{Katherine Goode*}
@@
 % Abstract and keywords
-\abstract[Abstract]{The importance of providing explanations for predictions made by black-box models has led to the development of \kge{explainer} model \sout{explainer} methods such as LIME (local interpretable model-agnostic explanations).
+\abstract[Abstract]{The importance of providing explanations for predictions made by black-box models has led to the development of \kge{explainer} model  methods such as LIME (local interpretable model-agnostic explanations).
 LIME uses a surrogate model to explain the relationship between predictor variables and predictions from a black-box model in a local region around a prediction of interest.
@@
 \cyear{2020},
-\ctitle{Visual Diagnostics of a\kge{n} \sout{Model} Explainer \kge{Model} -- Tools for the Assessment of LIME Explanations},
+\ctitle{Visual Diagnostics of a\kge{n}  Explainer \kge{Model} -- Tools for the Assessment of LIME Explanations},
 \cjournal{Stat Anal Data Min: The ASA Data Sci Journal},
@@
 (Left) An example of an explainer model with appropriate weights to provide a faithful approximation of the complex model.
-(Right) An example of an explainer model for the same prediction but with different weights that results in an explanation unfaithful to the complex model.} \sout{A conceptual depiction of a faithful LIME explainer model in the immediate neighborhood of a prediction of interest \kge{for a hypothetical black-box model trained using two features: Feature 1 (left) and Feature 2 (right).
-The explainer model is a ridge regression weighted by the inverse Gower distance to the prediction of interest raised to the power of \Sexpr{good_gower_power}.}} \sout{The predictions from a hypothetical black-box model are plotted against the standardized values of the two hypothetical predictor variables.
-The diamond shaped points represent the location of a prediction of interest.
-The size and opacity of the circular points indicate the weight assigned based on the distance to the prediction of interest computed using the inverse of the Gower distance metric raised to the power of \Sexpr{good_gower_power}.
-The black lines represent a weighted ridge regression model used as an explainer model that reasonably captures the relationship between the black-box predictions and the features in a local region around the prediction of interest.
-That is, the explainer is faithful to the complex model and produces a reasonable explanation that Feature 1 plays a more important role in the prediction of interest than Feature 2 since the magnitude of the slope associated with Feature 1 is larger.}}
+(Right) An example of an explainer model for the same prediction but with different weights that results in an explanation unfaithful to the complex model.}  }
 \label{fig:figure-01}
@@
 In the field of statistics, there are two main uses for models: inference and prediction.
-Machine learning models \sout{are often used for the latter purpose.
-These models} have proven to perform well \kge{in problems with the latter objective} \sout{in a wide range of prediction problems}, but the accuracy of many machine learning models comes at the cost of interpretability due to their algorithmic complexity (hence the phrase "black-box models").
+Machine learning models  have proven to perform well \kge{in problems with the latter objective} , but the accuracy of many machine learning models comes at the cost of interpretability due to their algorithmic complexity (hence the phrase "black-box models").
 Model interpretability allows for the understanding and assessment of how a model produces predictions.
@@
 \citep{fisher:2018} and \citep{strumbelj:2014}).
-In this paper, we focus on \kge{the} \sout{one specific} model-agnostic method\sout{:} \kge{of} LIME \citep{ribeiro:2016}.
-
-LIME (local interpretable model-agnostic explanations) \sout{is a method that} uses a surrogate model to relate predictor variables to black-box model predictions \sout{(i.e.
-a model explainer)} \citep{ribeiro:2016}.
-\sout{We distinguish between the terms of model explainer and explainer model: by \emph{model explainer} we denote the method for explaining a complex model using a surrogate model, while the \emph{explainer model}, or simply the \emph{explainer}, is the surrogate model.} While some \kge{explainer} model\kge{s} \sout{explainers} focus on understanding a model at the global level, LIME claims to provide explanations for individual predictions (local).
+In this paper, we focus on \kge{the}  model-agnostic method \kge{of} LIME \citep{ribeiro:2016}.
+
+LIME (local interpretable model-agnostic explanations)  uses a surrogate model to relate predictor variables to black-box model predictions  \citep{ribeiro:2016}.
+While some \kge{explainer} model\kge{s}  focus on understanding a model at the global level, LIME claims to provide explanations for individual predictions (local).
 Additionally, LIME is designed to work with any model (model-agnostic) and to produce easily understandable results (explanations) \citep{ribeiro:2016}.
-Conceptually, LIME fits a simple (interpretable) model, the explainer model, \kge{to approximate} \sout{meant to capture the behavior of} the \sout{(}complex\sout{) black-box} model in a local region around a prediction of interest.
-The simple model \kge{is interpreted to identify the} \sout{then provides interpretable estimates for} variables that most influence\sout{d} the \kge{complex model} prediction\sout{made by the complex model}.
-
-\kge{While t}\sout{T}he concept of LIME is relatively simple\sout{: use an interpretable model to approximate a complex model in a local region.
-However}, a practical implementation of LIME is not straightforward, and research is being done to improve the procedure \citep{laugel:2018}.
+Conceptually, LIME fits a simple (interpretable) model, the explainer model, \kge{to approximate}  the complex model in a local region around a prediction of interest.
+The simple model \kge{is interpreted to identify the}  variables that most influence the \kge{complex model} prediction.
+
+\kge{While t}he concept of LIME is relatively simple, a practical implementation of LIME is not straightforward, and research is being done to improve the procedure \citep{laugel:2018}.
 The current implementations of LIME \citep{pedersen:2020} \citep{ribeiro:2020} offer various tuning parameters (see Section \ref{background}) that affect the explainer model and ultimately, the explanation.
 Since the explainer model is an approximation of the complex model and not a direct interpretation, the explanations produced by an explainer model are subject to the quality of the approximation.
-\sout{Thus, i }\kge{I}n order to achieve \kge{reasonable} \sout{accurate} explanations, the tuning parameter values selected \kge{shoud} \sout{need to} be assessed.
+\kge{I}n order to achieve \kge{reasonable}  explanations, the tuning parameter values selected \kge{shoud}  be assessed.
 
@@
 Here, the explainer model is faithful to the complex model since it captures the linear relationship between the black-box predictions in an immediate neighborhood of the prediction of interest.
-The slope \sout{of \Sexpr{coefs_data %>% filter(case == good_power_label) %>% pull(b1) %>% round(3)}} explains that the black-box predictions increase as the feature increases in the local region around the prediction of interest.}
+The slope  explains that the black-box predictions increase as the feature increases in the local region around the prediction of interest.}
 
@@
 Here, the explainer model does not capture the linear trend near the prediction of interest, but instead, the explainer captures a more global trend.
-Without an assessment of this explainer model, the slope \sout{of \Sexpr{coefs_data %>% filter(case == bad_power_label) %>% pull(b1) %>% round(3)}} would incorrectly explain that the predictions decrease as the feature increases near the prediction of interest.} %\sout{This cannot be said of the explainer model in \autoref{fig:figure-02}.
+Without an assessment of this explainer model, the slope  would incorrectly explain that the predictions decrease as the feature increases near the prediction of interest.} %\sout{This cannot be said of the explainer model in \autoref{fig:figure-02}.
 In addition, the magnitude of the slope associated with Feature 2  (\Sexpr{coefs_data %>% filter(case == "bad", feature == "Feature 2") %>% pull(b1) %>% round(3) %>% abs()}) is larger than that of Feature 1 (\Sexpr{coefs_data %>% filter(case == "bad", feature == "Feature 1") %>% pull(b1) %>% round(3) %>% abs()}).
@@
 \kge{\autoref{fig:figure-01} demonstrates a simple example in which the explanation quality varies drastically when different weights are used.
-Other concerns with LIME have been raised in the literature.} \sout{Several sources in the literature discuss the performance of LIME.} \kge{\citet{laugel:2018} and \citet{molnar:2019} discuss the difficulty specifying a local region with LIME due to both} \sout{One of the biggest difficulties with LIME is determining how to specify a local region \citep{laugel:2018} \citep{molnar:2019}.
-This is due to} an unclear definition of \kge{what is} a "local region" and how to apply LIME to achieve an appropriate local region\sout{ as demonstrated by \autoref{fig:figure-02}}.
-\kge{\citet{laugel:2018} also present examples of LIME explanations that are clearly global and not local.} \kge{A different concern about LIME is raised by} \citet{alvarezmelis:2018} \sout{raise a concern} pertaining to the robustness of explanations from LIME and other \kge{explainer} model\kge{s} \sout{explainers}: they find that even small changes in predictor variables can lead to very different LIME explanations.
-\kge{Even the original authors of LIME,} \sout{Additionally,} \citet{ribeiro:2016}\kge{,} acknowledge that if a linear model is used as the explainer, LIME relies on a linear approximation of the explainer model to the complex model and state "if the underlying model is highly non-linear even in the locality of the prediction, there may not be a faithful explanation".
-
-\sout{As a result of the various ways LIME can fail, it is important to assess LIME explanations.
-We suggest the use of visual diagnostics for assessment.
-In this paper,} \kge{Without an assessment of the LIME explainer model, the user is putting trust in another black-box procedure to explain the complex black-box model.
-In this paper, we stress the importance of assessing the LIME explainer model.} \kge{To do this, w}e lay out the set of claims about LIME made by \citet{ribeiro:2016}, and \kge{we provide a toolkit of visual diagnostics} \sout{propose three visualizations} for the assessment of these claims: (1) \emph{explanation scatterplots}, (2) \emph{feature heatmaps}, (3) \emph{assessment metric plots}.
+Other concerns with LIME have been raised in the literature.}  \kge{\citet{laugel:2018} and \citet{molnar:2019} discuss the difficulty specifying a local region with LIME due to both}  an unclear definition of \kge{what is} a "local region" and how to apply LIME to achieve an appropriate local region.
+\kge{\citet{laugel:2018} also present examples of LIME explanations that are clearly global and not local.} \kge{A different concern about LIME is raised by} \citet{alvarezmelis:2018}  pertaining to the robustness of explanations from LIME and other \kge{explainer} model\kge{s} : they find that even small changes in predictor variables can lead to very different LIME explanations.
+\kge{Even the original authors of LIME,}  \citet{ribeiro:2016}\kge{,} acknowledge that if a linear model is used as the explainer, LIME relies on a linear approximation of the explainer model to the complex model and state "if the underlying model is highly non-linear even in the locality of the prediction, there may not be a faithful explanation".
+
+ \kge{Without an assessment of the LIME explainer model, the user is putting trust in another black-box procedure to explain the complex black-box model.
+In this paper, we stress the importance of assessing the LIME explainer model.} \kge{To do this, w}e lay out the set of claims about LIME made by \citet{ribeiro:2016}, and \kge{we provide a toolkit of visual diagnostics}  for the assessment of these claims: (1) \emph{explanation scatterplots}, (2) \emph{feature heatmaps}, (3) \emph{assessment metric plots}.
 \kge{Using these visual diagnostics, we demonstrate problematic examples of LIME explanations where the claims about LIME are not met and the explanations are highly dependent on tuning parameter values without a clear way to identify a set of tuning parameter values that produce the "best" explanations.}
@@
 While LIME is implemented for image, tabular, and text data, we only focus on tabular data.
-For additional simplicity, we only discuss classification prediction models with a dichotomous response \sout{variable} and continuous predictor\sout{ variable}s.
-However, the proposed diagnostics may be extended to \kge{other} \sout{a wider range of} situations.
+For additional simplicity, we only discuss classification prediction models with a dichotomous response  and continuous predictors.
+However, the proposed diagnostics may be extended to \kge{other}  situations.
 
@@
 The forked version is functionally indistinguishable from \citeauthor{pedersen:2020}'s implementation but allows us to export internal values relevant for an assessment of the explainer.
-The \kge{code for the} diagnostic plots \sout{included in this paper} \kge{is stored in} \sout{are created using} the R package \emph{limeaid} \citep{goode:2020}.
+The \kge{code for the} diagnostic plots  \kge{is stored in}  the R package \emph{limeaid} \citep{goode:2020}.
 
@@
 An adaption of the Python package in R has been implemented and made available by Thomas Lin-Pedersen \citep{pedersen:2020}.
-\kge{In both implementations, a ridge regression model is used as the explainer model, and} \sout{During the application of LIME, t} the user is asked to select various tuning parameter options: the number of features to return in the explanation, the simulation method, the feature selection method, and how the weights are computed.
+\kge{In both implementations, a ridge regression model is used as the explainer model, and}  the user is asked to select various tuning parameter options: the number of features to return in the explanation, the simulation method, the feature selection method, and how the weights are computed.
 The discussion of parameter choices and implementation details of LIME in this paper are based on the R package.
 \kge{See Appendix~\ref{lime-details} for}
-an overview of the options available for the tuning parameters\sout{ is included in Appendix~\ref{lime-details}}.
+an overview of the options available for the tuning parameters.
 
@@
 @
-\caption{Plots of $x_2$ versus $x_1$ from the \kge{\data \ } training (left) and testing (right) sets\sout{ of the \data \ } introduced in Section \ref{diagnostics} \sout{.
-T} \kge{with t}he true classification boundary \sout{is} shown as a solid black line\sout{ in both plots}.
-\sout{The color of the training data represents the value of the observed response variable ($y$).
-The color of the testing data represents the random forest probability that an observation belongs to the category of blue.} \kge{In the testing set, the open black circles identify cases misclassified by the random forest, and the diamond indicates a prediction of interest.} \sout{The \Sexpr{dim(sine_data_test %>% filter(y != rfpred))[1]} cases that are misclassified by the random forest are identified by black circles.} \sout{The prediction of interest \kge{in the test data} \sout{to explain} is indicated by a diamond.}}
+\caption{Plots of $x_2$ versus $x_1$ from the \kge{\data \ } training (left) and testing (right) sets introduced in Section \ref{diagnostics}  \kge{with t}he true classification boundary  shown as a solid black line.
+\kge{In the testing set, the open black circles identify cases misclassified by the random forest, and the diamond indicates a prediction of interest.} }
 \label{fig:figure-02}
@@
 (right) \emph{Explanation Scatterplot}.
-\sout{The points represent the simulated data colored by the random forest probabilities and sized by the assigned LIME weights.
-The prediction of interest is shown as the diamond shaped point.
-The explainer model indicator variables associated with $x_1$ and $x_2$ (quantile bins containing the prediction of interest) are depicted by the solid lines.
-The line colors represent the explainer model coefficient signs and indicate whether the feature supports a prediction of `blue' (blue lines) or supports a prediction of `red' (red lines).} \kge{An explanation scatterplot associated with the explanation \sout{for the prediction of interest depicted} on the left.} \sout{This figure shows that t}\kge{T}he \kge{4} quantile bins \kge{over simplify} \sout{are not flexible enough to capture}
+\kge{An explanation scatterplot associated with the explanation  on the left.} \kge{T}he \kge{4} quantile bins \kge{over simplify}
 the relationship between the random forest predictions and the $x_1$ and $x_2$ values \kge{near the prediction of interest}.}
@@
 
-In this section, we introduce three visual diagnostic plots \sout{for the assessment of LIME.
-The plots focus on different levels of application of LIME (e.g.
-on explanation versus a set of explanations) to} \kge{that} assess the LIME claims from different perspectives:
+In this section, we introduce three visual diagnostic plots  \kge{that} assess the LIME claims from different perspectives:
 
@@
 To demonstrate the visual diagnostics, we generate an example dataset that will be referred to as the \data.
-The \data \ contains \Sexpr{dim(sine_data)[1]} observations with \sout{three features and one response variable.
-The} features\sout{,} \kge{of} $x_1$\sout{,} \kge{and} $x_2$ \kge{independently sampled from Unif(\Sexpr{min}, \Sexpr{max}) distributions}\sout{,} and $x_3$\sout{,} \sout{\kge{that} are randomly sampled from Unif(\Sexpr{min}, \Sexpr{max}), Unif(\Sexpr{min}, \Sexpr{max}), and} \kge{sampled from a} $\mbox{N}(0,1)$ distribution\sout{s, respectively}.
-A binary response variable $y$ is created using a \sout{rotated} sine curve \sout{.
-In particular, let} \kge{such that}
+The \data \ contains \Sexpr{dim(sine_data)[1]} observations with  features \kge{of} $x_1$ \kge{and} $x_2$ \kge{independently sampled from Unif(\Sexpr{min}, \Sexpr{max}) distributions} and $x_3$  \kge{sampled from a} $\mbox{N}(0,1)$ distribution.
+A binary response variable $y$ is created using a  sine curve  \kge{such that}
 \begin{eqnarray}\label{eq:data}
@@
 \end{eqnarray}
-where $x'_1=x_1\cos(\theta)-x_2\sin(\theta)$\kge{,} \sout{and} $x'_2=x_1\sin(\theta)+x_2\cos(\theta)$\kge{, and} \sout{where} $\theta=-0.9$. \sout{Then $y$ is defined as
+where $x'_1=x_1\cos(\theta)-x_2\sin(\theta)$\kge{,}  $x'_2=x_1\sin(\theta)+x_2\cos(\theta)$\kge{, and}  $\theta=-0.9$. \sout{Then $y$ is defined as
 \begin{eqnarray}\label{eq:data}
@@
 The dataset is \kge{randomly} divided into training and testing sets of \Sexpr{dim(sine_data_train)[1]} and \Sexpr{dim(sine_data_test)[1]} observations, respectively.
-A random forest is fit \kge{to the training set} using the R package \emph{randomForest} (version \Sexpr{packageVersion("randomForest")}) \citep{liaw:2002} with the default settings\sout{.
-The model} \kge{and} is applied to the test set to obtain predictions.
+A random forest is fit \kge{to the training set} using the R package \emph{randomForest} (version \Sexpr{packageVersion("randomForest")}) \citep{liaw:2002} with the default settings \kge{and} is applied to the test set to obtain predictions.
 
 \autoref{fig:figure-02} shows scatterplots of $x_2$ versus $x_1$ from the training data (left) and the testing data (right).
-Both plots include the true classification boundary \sout{of the rotated sine function plotted} as the solid black line.
+Both plots include the true classification boundary  as the solid black line.
 The training data are colored by the observed response variable ($y$), and the testing data are colored by random forest prediction probabilities.
-The random forest  misclassifies \Sexpr{dim(sine_data_test %>% filter(y != rfpred))[1]} points, which are all located near the classification boundary \sout{.
-These are} \kge{and} identified by open circles\sout{ in \autoref{fig:figure-02}}.
-
-From these scatterplots, we \sout{also} see that the global relationship between response $y$ and features $x_1$ and $x_2$ is linear: the probability for label blue increases with the difference between features $x_2$ and $x_1$.
+The random forest  misclassifies \Sexpr{dim(sine_data_test %>% filter(y != rfpred))[1]} points, which are all located near the classification boundary  \kge{and} identified by open circles.
+
+From these scatterplots, we  see that the global relationship between response $y$ and features $x_1$ and $x_2$ is linear: the probability for label blue increases with the difference between features $x_2$ and $x_1$.
 Locally, the relationship between $y$ and features $x_2$ and $x_1$ varies a lot more around the line of identity.
@@
 
-We apply LIME using six sets of tuning parameter values to all observations in the \data \ test set to observe \kge{explanation} variability\sout{ across tuning parameter values}.
-\kge{Five of the LIME applications use a} \sout{A} quantile bin based simulation method (samples are simulated uniformly from a \kge{feature using a} specified number of quantile bins) \sout{is used for five of the LIME applications} with the number of bins varying from 2 to 6 by application.
+We apply LIME using six sets of tuning parameter values to all observations in the \data \ test set to observe \kge{explanation} variability.
+\kge{Five of the LIME applications use a}  quantile bin based simulation method (samples are simulated uniformly from a \kge{feature using a} specified number of quantile bins)  with the number of bins varying from 2 to 6 by application.
 We use 6 bins as the maximum, because the complexity of the explanations increases with the number of bins.
-Note that 4-quantile-bins \kge{is} \sout{are} the default method in the \emph{lime} R package.
+Note that 4-quantile-bins \kge{is}  the default method in the \emph{lime} R package.
 The sixth application of LIME uses a kernel density simulation method (samples are drawn from kernel density approximations of the feature distributions).
@@
 
-For the presentation of the explanation scatterplot, we focus on the misclassified point \sout{with $(x_1, x_2, x_3)$ coordinates of (\Sexpr{round(sine_poi$x1, 2)}, \Sexpr{round(sine_poi$x2, 2)}, \Sexpr{round(sine_poi$x3, 2)})} indicated by a diamond in \autoref{fig:figure-02}.
+For the presentation of the explanation scatterplot, we focus on the misclassified point  indicated by a diamond in \autoref{fig:figure-02}.
 Misclassified points are often of interest to explain since they may provide information about ways to improve the model.
@@
 
-Before introducing the visual diagnostics, let us consider a commonly used visualization of a LIME explanation\sout{ that is shown in Figure \ref{fig:figure-03} (left)}.
+Before introducing the visual diagnostics, let us consider a commonly used visualization of a LIME explanation.
 \kge{Figure \ref{fig:figure-03} (left) depicts the explanation for the prediction of interest indicated in \autoref{fig:figure-02} obtained using 4-quantile-bins.
@@
 
-\sout{Before introducing the visual diagnostics, let us consider a commonly used visualization of a LIME explanation\sout{ that is shown in Figure \ref{fig:figure-03} (left)}.
-\kge{Figure \ref{fig:figure-03} (left) shows the explanation for the prediction of interest indicated in \autoref{fig:figure-02} obtained using 4-quantile-bins.} \sout{The plot is created using the \emph{lime} R package and provides a visual representation of a LIME explanation for the prediction of interest indicated in \autoref{fig:figure-02}.
-In particular, the explanation is obtained using 4-quantile-bins to simulate the data.} \kge{When quantile bins are used to simulate data}\sout{ In this scenario}, LIME converts continuous predictor variables to indicator variables identifying whether the variable value falls in the same quantile bin as the prediction of interest or not.
-The\kge{n the} indicator variables are used as the explainer model features.}
-
-\sout{The plot reports \Sexpr{round(sine_poi_lime_default$label_prob[1], 2)} as the random forest  probability that the observation of interest belongs to category blue (denoted as the ``label" in the plot).
-The lengths of the bars represent the coefficients from a ridge regression model (the explainer model) fit using the R package \emph{glmnet} \citep{simon:2011} associated with the indicator variables chosen via feature selection.
-The color of a bar denotes the sign of the coefficient and whether the feature "supports" or "contradicts" a random forest classification of `blue'.
-The "explanation fit" is the deviance ratio from  \emph{glmnet}.
-In other words, this is the $R^2$ value associated with the explainer model.
-In this case, it is \Sexpr{round(sine_poi_lime_default$model_r2[1], 2)} suggesting that the explainer model is not a good linear fit.
-However, it is commonly accepted that $R^2$ has limitations for assessing the quality of fit of a model \citep{sapra:2014} and  should not be used as the only metric in a model assessment.}
-
-\sout{The explanation for the prediction of interest depicted in Figure \ref{fig:figure-03} is interpreted as follows.
-A random forest classification of blue is supported by the prediction of interest having a value of $x_2$ that is greater than \Sexpr{str_split(sine_poi_lime_default$feature_desc[[1]], pattern = " ")[[1]][1]}, but the prediction of interest having a value of $x_1$ that is greater than \Sexpr{str_split(sine_poi_lime_default$feature_desc[[2]], pattern = " ")[[1]][1]} and less than or equal to \Sexpr{str_split(sine_poi_lime_default$feature_desc[[2]], pattern = " ")[[1]][5]} provides support against a classification of blue.
-Since the weight associated with $x_2$ has a larger magnitude than the weight associated with $x_1$, LIME explains that $x_2$ plays a more important role in the random forest prediction.
-Additionally, consider that since the support for blue by $x_2$ outweighs the support for red by $x_1$, the explainer model overall favors a label of blue for the prediction of interest, which agrees with the random forest probability of \Sexpr{sine_poi_lime_default$label_prob[1]} for blue.
-Note that both models classify the observation incorrectly.}
-
 \subsection{Explanation Scatterplots} \label{exp-scatter}
@@
 In fact, both random forest and explainer model classify the observation incorrectly.
-However, based on the information in \autoref{fig:figure-03} (left) alone, it is not possible to make an informed assessment of the explanation.} \sout{Based on the plot on the left of \autoref{fig:figure-03} alone, it is not possible to make an informed assessment of the explanation.}
+However, based on the information in \autoref{fig:figure-03} (left) alone, it is not possible to make an informed assessment of the explanation.}
 
@@
 The point size represents the weight assigned by LIME.
-In order to show the LIME results for the observation of interest, lines are drawn on top of the points\sout{.
-These lines}  represent\kge{ing} the boundaries of the indicator variables used to fit the explainer model.
+In order to show the LIME results for the observation of interest, lines are drawn on top of the points  represent\kge{ing} the boundaries of the indicator variables used to fit the explainer model.
 The line color  denotes whether LIME indicates that a feature supports or contradicts a class prediction.
-\sout{Appendix \ref{exp-scatter_plus} addresses the explanation scatterplot formats in other LIME simulation scenarios.}
 
@@
 An example feature heatmap of the explanations from the applications of LIME with different tuning parameter values to the \data \ test set.
-\sout{The cases from the test set are plotted on the y-axis, and the tuning parameter values (simulation methods here) are included on the x-axis.
-The colors of the tiles indicate the feature selected by LIME for the corresponding case and tuning parameter value.
-The plot is faceted by the first and second most important features selected by LIME (top and bottom facets, respectively).
-The vertical facets separate the kernel density method from the quantile bin methods.} The vertical striping indicates that the LIME explanations are not consistent across tuning parameter values.}
+The vertical striping indicates that the LIME explanations are not consistent across tuning parameter values.}
 \label{fig:figure-04}
@@
 
-\sout{Two hypothetical examples of feature heatmaps are included in \autoref{fig:figure-04}.
-The plots are created with the assumption that LIME is applied to select the top feature out of $p=4$  features for $n=10$ cases with $t=5$ sets of tuning parameter values.
-Situation 1 is an example where the features selected are consistent across tuning parameter values within a case but vary across cases within a tuning parameter value.
-This is the ideal situation, because the LIME explanations do not depend on the tuning parameters but do depend on the location of the observation in the feature space.
-Situation 2 is an example where the selected features vary across tuning parameter values within a case but are consistent across cases within a tuning parameter value.
-This situation indicates that the features selected by LIME are dependent on the tuning parameters, and the explanations may not be  local, because the same feature is chosen regardless of the case.
-In practice, it is expected that the plot will exhibit a combination of these two situations.}
-
 \autoref{fig:figure-04} shows a feature heatmap for the LIME applications to the 100 observations in the \data \ test set.
 The most important and second most important features selected by LIME are shown in in the top and bottom facets, respectively.
-For the quantile bins, the original features prior to \kge{being converted to indicator variables} \sout{the indicator variable transformation} are included since it is obvious that different features would be selected when the sizes of the bins change.
-This figure shows that for kernel density and 2-quantile-bins, LIME \kge{produces global explanations since} \sout{selects} $x_1$ \kge{is selected} as the most important feature and $x_2$ \kge{is selected} as the second most important feature across all cases in the test set.
-\sout{These explanations are not local.} There is variability in the features selected by LIME for 3- to 6-quantile-bins suggesting more local explanations.
+For the quantile bins, the original features prior to \kge{being converted to indicator variables}  are included since it is obvious that different features would be selected when the sizes of the bins change.
+This figure shows that for kernel density and 2-quantile-bins, LIME \kge{produces global explanations since}  $x_1$ \kge{is selected} as the most important feature and $x_2$ \kge{is selected} as the second most important feature across all cases in the test set.
+There is variability in the features selected by LIME for 3- to 6-quantile-bins suggesting more local explanations.
 There are signs of vertical striping, which suggests a dependence on tuning parameters.
-Note that the explanations from 3- and 5-quantile-bins include the selection of the random noise variable ($x_3$) as an important variable in many predictions, which \kge{would not be expected to be important to a random forest}\sout{should not be the case}.
-\kge{It is unclear whether the random forest is using a variable that would not be expected to be important or LIME is incorrectly identifying the important variable when 3- and 5- quantile bins are used.} \sout{The pattern seen in the explanations for 3- to 6-quantile-bins may suggest local explanations, but the dependence on tuning parameters makes it unclear which set of explanations to use.}
+Note that the explanations from 3- and 5-quantile-bins include the selection of the random noise variable ($x_3$) as an important variable in many predictions, which \kge{would not be expected to be important to a random forest}.
+\kge{It is unclear whether the random forest is using a variable that would not be expected to be important or LIME is incorrectly identifying the important variable when 3- and 5- quantile bins are used.}
 
@@
 \caption{\emph{Assessment metric plot}.
-\kge{This example assessment metric plot contains metrics} \sout{The assessment metrics} computed on the applications of LIME to the \data \ test set\sout{are included in this example assessment metric plot}.
-\sout{Each horizontal facet corresponds to one of three metrics: average $R^2$, average fidelity, or MSEE.
-The LIME tuning parameter values (simulation methods in this example) are plotted on the x-axis, and the metric values are shown on the y-axis.
-The points are colored by rank (within a metric) indicating best to worst (dark to light).} The kernel density simulation methods performs well across all three metrics.}
+\kge{This example assessment metric plot contains metrics}  computed on the applications of LIME to the \data \ test set.
+The kernel density simulation methods performs well across all three metrics.}
 \label{fig:figure-05}
@@
 MSEE provides almost the exact opposite results with 6-quantile-bins performing the best and 2-quantile-bins performing the worst.
-Average fidelity and MSEE are similar metrics, \kge{but} \sout{so it is \sout{not} surprising that they \sout{would} \kge{do not} agree in this example.
-\kge{The discrepancy may be because} \sout{Another factor might be that}} MSEE only takes the prediction of interest into account and not the full simulated dataset \kge{as average fidelity does.} \kge{This suggests that 6-quantile-bins produce an explainer model more faithful for the prediction of interest while 2-quantile-bins produce an explainer model more faithful over all simulated data observations}.
-\sout{The contradiction between metrics makes it difficult to identify which simulation method to trust.}
-
-Recall\kge{,} \sout{that} \autoref{fig:figure-04} \kge{shows} \sout{indicates that} the kernel density method \kge{returns the same explanations} \sout{selected the same feature} across all cases in the test set\sout{ for both the first and second features.
-It appears that} \kge{suggesting} a global trend may be the best explanation for this example\kge{.}\sout{, which} \kge{This} may be reasonable considering that we \kge{would expect} \sout{know that both} $x_1$ and $x_2$ \kge{to be} \sout{are} the two features \sout{that should be the features} used by the random forest to distinguish between response categories.
+Average fidelity and MSEE are similar metrics, \kge{but}  MSEE only takes the prediction of interest into account and not the full simulated dataset \kge{as average fidelity does.} \kge{This suggests that 6-quantile-bins produce an explainer model more faithful for the prediction of interest while 2-quantile-bins produce an explainer model more faithful over all simulated data observations}.
+
+Recall\kge{,}  \autoref{fig:figure-04} \kge{shows}  the kernel density method \kge{returns the same explanations}  across all cases in the test set \kge{suggesting} a global trend may be the best explanation for this example\kge{.} \kge{This} may be reasonable considering that we \kge{would expect}  $x_1$ and $x_2$ \kge{to be}  the two features  used by the random forest to distinguish between response categories.
 \kge{However, futher exploration of individual explanations using explanation scatterplots may help to identify the tuning parameter values that produce the most trustworthy explanations.}
@@
 
-In this section, we \sout{provide a discussion of the application of} \kge{apply} the visual diagnostics for LIME explanations to a practical data problem investigating the similarity of marks on fired bullets.
+In this section, we  \kge{apply} the visual diagnostics for LIME explanations to a practical data problem investigating the similarity of marks on fired bullets.
 
@@
 @
-\caption{Example bullet signatures.
-The \sout{bullet} signatures \kge{are from} \sout{correspond to} the same land and therefore have very similar patterns.
-\sout{The \citet{hare:2017} random forest is fit using various features that measure the similarity between two such signatures.}}
+\caption{Example bullet signatures. The  signatures \kge{are from}  the same land and therefore have very similar patterns. }
 \label{fig:figure-07}
@@
 @
-\caption{Parallel coordinate plots of the \kge{bullet matching} \sout{\citet{hare:2017}} random forest predictions\sout{from the training (top \kge{row}\sout{facet}) and testing (bottom \kge{row}\sout{facet}) data}.
-\sout{The observations are separated by known matching (right column) and non-matching (left column) signatures.
-The y-axis shows the standardized feature values, and the x-axis shows the features used to fit the random forest (ordered by random forest impurity based feature importance).} Each line corresponds to an observation, and the line color represents the associated random forest probability.
+\caption{Parallel coordinate plots of the \kge{bullet matching}  random forest predictions.
+Each line corresponds to an observation, and the line color represents the associated random forest probability.
 There are clear relationships between the feature values and the random forest probabilities.}
@@
 
-\kge{In \autoref{fig:figure-08}, } \sout{W}\kge{w}e consider a global visualization of the relationship between the random forest predictions and the model features with a parallel coordinate plot of the training data (top \kge{row}\sout{facet}) and testing data (bottom \kge{row}\sout{facets})\sout{ (\autoref{fig:figure-08})}.
+\kge{In \autoref{fig:figure-08}, } \kge{w}e consider a global visualization of the relationship between the random forest predictions and the model features with a parallel coordinate plot of the training data (top \kge{row}) and testing data (bottom \kge{row}).
 In the training data we observe a clear difference in feature values based on whether the corresponding random forest scores are close to 1 or 0.
@@
 Observations in the test data that are classified incorrectly by the random forest tend to have feature values similar to observations in the training data with similar random forest scores.
-\sout{For example, the observations in the test set known to be a match but have a random forest score below 0.5 have relatively low values of rough correlation, cross correlation function, and matches and relatively large values of mismatches, distance, and non-consecutively matching striae compared to observations with a random forest probability close to 1.}
 
@@
 
-First, applications of 2-quantile-bins\kge{, 2-equal-bins, and somewhat for the density based} simulations produce the same explanations for almost all cases and LIME tuning parameter values\kge{,}\sout{.
-This suggests that the LIME} \kge{suggesting these} explanations are global and not local.
+First, applications of 2-quantile-bins\kge{, 2-equal-bins, and somewhat for the density based} simulations produce the same explanations for almost all cases and LIME tuning parameter values\kge{,} \kge{suggesting these} explanations are global and not local.
 Second, within a simulation method, the features selected by LIME for an observation do not appear to vary by the Gower power.
-However, the LIME explanation\kge{s} for an observation often var\kge{y}\sout{ies} across simulation methods.
+However, the LIME explanation\kge{s} for an observation often var\kge{y} across simulation methods.
 With the equal bins, there are vertical stripes that suggest a dependence of the LIME explanations on the number of bins.
@@
 \caption{Feature heatmap of 36 LIME applications to the bullet comparison data test set.
-\sout{In addition to faceting the results by simulation method and LIME feature selection order, facets for the Gower power and whether the observation is a match or non-match are included.} The vertical stripes of features selected indicate a dependence between the LIME explanations and tuning parameter values.}
+The vertical stripes of features selected indicate a dependence between the LIME explanations and tuning parameter values.}
 \label{fig:figure-09}
@@
 \caption{Assessment metric plot for the applications of LIME on the bullet comparison data test set.
-There are discrepancies in \kge{metric} performance\kge{s}\sout{ across metrics for a set of tuning parameter values}, but \sout{based on the} overall\sout{ performance of all \sout{three} metrics}, 4-equal-bins with a Gower power of 0.5 appear\sout{s} to perform the best.}
+There are discrepancies in \kge{metric} performance\kge{s}, but  overall, 4-equal-bins with a Gower power of 0.5 appear to perform the best.}
 \label{fig:figure-10}
@@
 However, there is consistency in results across different Gower powers.
-The applications using a power of 0.5 perform the best or as well as the other powers across all simulation methods suggesting that the power that leads to a more \kge{local} \sout{global} explanation is preferred\sout{ by LIME}.
-It is not \kge{obvious} \sout{apparent} which set of tuning parameters is the best\kge{, but}\sout{.
-C}\kge{c}onsidering all three metrics, we might conclude that the 4-equal-bins with a Gower power of 0.5 performs better than the other tuning parameter values considered.
-
-To provide a more detailed view of explanations obtained using different tuning parameter values, we \kge{consider explanation scatterplots for one prediction of interest} \sout{take a closer look at explanations for two observations of interest, which will be} referred to as case NM (a known non-match)\sout{ and case NM (a known non-match), using explanation scatterplots.} \kge{shown in} Figure~\ref{fig:figure-11} \sout{includes} \kge{along with} the visual \sout{representation plots of} explanation\sout{s} \kge{plots} \sout{(}from \kge{the} \emph{lime} \kge{R package}\sout{)\ and explanation scatterplots for cases M and NM}.
+The applications using a power of 0.5 perform the best or as well as the other powers across all simulation methods suggesting that the power that leads to a more \kge{local}  explanation is preferred.
+It is not \kge{obvious}  which set of tuning parameters is the best\kge{, but}\kge{c}onsidering all three metrics, we might conclude that the 4-equal-bins with a Gower power of 0.5 performs better than the other tuning parameter values considered.
+
+To provide a more detailed view of explanations obtained using different tuning parameter values, we \kge{consider explanation scatterplots for one prediction of interest}  referred to as case NM (a known non-match) \kge{shown in} Figure~\ref{fig:figure-11}  \kge{along with} the visual  explanation \kge{plots} from \kge{the} \emph{lime} \kge{R package}.
 Plots for 4-equal-bins and 4-quantile-bins are included to depict tuning parameter values with good (4-equal-bins) and mediocre (4-quantile-bins) performance based on the assessment metric plot.
-\kge{Also, recall that 4-quantile-bins are the default option in the \emph{lime} R package.} \sout{Plots} \kge{Explanation scatterplots for a known match, referred to as case M, and} for the kernel density simulation method \kge{applied to both M and NM} are included in Appendix~\ref{bullets-plus}\sout{ (Figure \ref{fig:figure-F5})}.
+\kge{Also, recall that 4-quantile-bins are the default option in the \emph{lime} R package.}  \kge{Explanation scatterplots for a known match, referred to as case M, and} for the kernel density simulation method \kge{applied to both M and NM} are included in Appendix~\ref{bullets-plus}.
 
@@
 Additional investigations using explanations scatterplots would help to determine whether to trust this set of explanations, continue tuning the LIME parameters, or use another approach to provide better insight.}
-
-\sout{We focus on the explanation for case NM with 4-quantile-bins.
-The explanation plot from the \emph{lime} R package shows that the observed values of NM of mismatches less than or equal to 7.17, rough correlation (rough\_cor) greater than 0.05, and D less than or equal to 0.002 support a random forest prediction in favor of a match.
-The scatter plots show that many of the simulated values in the rectangular regions with mismatches less than 7.17, rough correlation greater than 0.05, and distance less than or equal to 0.002 have random forest predictions greater than 0.5, which agrees with the LIME explanation.
-However, the random forest assigns a probability of 0.21 to case NM, which is not explained by the LIME explanation that provides all explanations in support of a match.
-Instead, consider that a better explanation based on the scatterplots would be that the random forest assigned a prediction probably below 0.5 since NM has observed values of mismatches less than 5, rough correlation greater than 0.25, and distance greater than 0.001.}
-
-\sout{The other explanation scatterplots can be interpreted in a similar manner.
-The three plots depict situations where the explanations are faithful to the random forest, but the regions captured by the intersections of the bins do not align well with the regions containing similar probabilities produced by the random forest.}
 
@@
 \caption{Plots of LIME explanations (first row) and explanation scatterplots (second row) for case NM in the bullet test data for two tuning parameter values: 4-quantile-bins (first column) and 4-equal-bins (second column).
-\sout{The plots provide insights into the LIME explanations and allow for the assessment of the explanation quality.}}
+}
 \label{fig:figure-11}
@@
 
-\sout{Without applying LIME with multiple tuning parameter values to the bullet test data or viewing diagnostic plots of the LIME explanations, it may be very possible to formulate reasons why the LIME explanations make sense.
-However, the sequence of plots in this section (Figures \ref{fig:figure-09}, \ref{fig:figure-10}, and \ref{fig:figure-11}) suggest that we should be cautious to trust any of these LIME explanations.
-It appears that either LIME needs to be further tuned to provide trustworthy and good explanations, or a different approach may provide better insight.}
-
 \section{Discussion} \label{discussion}
@@
 This paper highlights that while an explainer model is meant to provide clarity, it actually adds another layer of complexity to predictive models by requiring yet another model that needs to be assessed.
-Without an assessment of the explainer model, LIME is a black-box procedure \sout{of its own} requiring blind trust in the explainer model.
-We suggest the use of visual diagnostics to counteract the black-box nature of LIME\sout{ and provide three diagnostic plots}.
-\kge{We provide three diagnostic plots} \sout{The \kge{plots} \sout{visualizations} are} intended to \kge{assess whether LIME explanations meet the claims made by \citet{ribeiro:2016}.
+Without an assessment of the explainer model, LIME is a black-box procedure  requiring blind trust in the explainer model.
+We suggest the use of visual diagnostics to counteract the black-box nature of LIME.
+\kge{We provide three diagnostic plots}  intended to \kge{assess whether LIME explanations meet the claims made by \citet{ribeiro:2016}.
 The examples in this paper bring to light many scenarios in which the claims are not met or are difficult to assess.
-We reconsider each of the claims and how the visual diagnostics identify their failings.} \sout{provide insight on how LIME works, assess the ability of the explainer model to capture the complex predictive model, and compare LIME explanations produced by different tuning parameter values.
-While the visualizations accomplish these tasks, they also expose examples of the failings of LIME.
-To address the discovered failings of LIME, we reconsider each of the claims about the performance of LIME made by \citet{ribeiro:2016} in light of the insights gained from the diagnostic visualizations.}
+We reconsider each of the claims and how the visual diagnostics identify their failings.}
 
@@
 
-Even though an explanation will be interpretable \kge{if} \sout{as long as} the complexity of the explainer model is appropriately chosen, a lack of understanding of the \kge{explainer model} \sout{process used to create the explanation} could lead to an incorrect interpretation of the explanation.
-For example, the visualization of a LIME explanation \sout{available} from the \emph{lime} R package \citep{pedersen:2020} (\sout{shown in }Figure\sout{s} \ref{fig:figure-03} \kge{left; } \sout{and} \kge{Figure} \ref{fig:figure-11} \kge{top}) is a \sout{major} simplification of the explainer model, which could lead to \sout{under-interpreted or} misinterpreted LIME explanation\kge{s}.
-Supplementing \citet{pedersen:2020}'s compact visualization of the explanation with an explanation scatterplot that shows a more detailed visualization of the explainer model promotes a more complete understanding of the explanation (\sout{such as }Figures~\ref{fig:figure-03} \kge{right; } \sout{and} \ref{fig:figure-11} \kge{bottom}).
+Even though an explanation will be interpretable \kge{if}  the complexity of the explainer model is appropriately chosen, a lack of understanding of the \kge{explainer model}  could lead to an incorrect interpretation of the explanation.
+For example, the visualization of a LIME explanation  from the \emph{lime} R package \citep{pedersen:2020} (Figure \ref{fig:figure-03} \kge{left; }  \kge{Figure} \ref{fig:figure-11} \kge{top}) is a  simplification of the explainer model, which could lead to  misinterpreted LIME explanation\kge{s}.
+Supplementing \citet{pedersen:2020}'s compact visualization of the explanation with an explanation scatterplot that shows a more detailed visualization of the explainer model promotes a more complete understanding of the explanation (Figures~\ref{fig:figure-03} \kge{right; }  \ref{fig:figure-11} \kge{bottom}).
 
 Even with an explainer model that is interpreted correctly, the interpretation is worthless if the explainer model is not \textbf{faithful} to the complex model.
-\sout{This claim can be assessed using the diagnostic plots suggested in this paper.
-Many of the visualizations in this paper highlight problems with the faithfulness of the explainer models.
-The e} \kge{E}xplanation scatterplots allow for a comparison of the explainer model to the complex model.
+\kge{E}xplanation scatterplots allow for a comparison of the explainer model to the complex model.
 The examples in this paper show cases where the explainer model oversimplifies the model and bins do not accurately capture the regions with similar random forest probabilities that contain the prediction of interest (Figures \ref{fig:figure-03} and \ref{fig:figure-11}).
@@
 
-\sout{In addition to assessing faithfulness by visually comparing the complex and explainer model, w}\kge{W}e \kge{also} propose a\kge{n assessment metric plot for the} visual comparison of two faithfulness metrics: MSEE and average fidelity.
+\kge{W}e \kge{also} propose a\kge{n assessment metric plot for the} visual comparison of two faithfulness metrics: MSEE and average fidelity.
 \kge{Both metrics measure faithfulness, but MSEE only accounts for the prediction of interest while average fidelity accounts for all observations in the simulated data.
-As a result, the measures may disagree (Figures \ref{fig:figure-05} and \ref{fig:figure-10}), and the user is left to determine which is preferable.} \sout{The examples of faithfulness metric comparisons in this paper both produced conflicting results (Figures \ref{fig:figure-05} and \ref{fig:figure-10}).
-This makes it difficult to decide on a recommendation of a set of tuning parameter values that produce the explanations with the most faithful explainer model.}
+As a result, the measures may disagree (Figures \ref{fig:figure-05} and \ref{fig:figure-10}), and the user is left to determine which is preferable.}
 
@@
 Most of the average $R^2$ values in the examples from this paper are below 0.5 suggesting a poor linear fit of the explainer models.
-A poor linear fit of the explainer model is also seen with the residual plot \kge{shown in} \sout{(}\autoref{fig:figure-C2}\sout{)}.
-
-The final claim, \textbf{localness}, is addressed by \sout{the} feature heatmap\kge{s} and \kge{explanation scatterplots}\sout{ metric comparison plots}.
+A poor linear fit of the explainer model is also seen with the residual plot \kge{shown in} \autoref{fig:figure-C2}.
+
+The final claim, \textbf{localness}, is addressed by  feature heatmap\kge{s} and \kge{explanation scatterplots}.
 \kge{The vertical stripes seen in the feature heatmaps (Figures \ref{fig:figure-04} and \ref{fig:figure-09}) suggest global explanations produced by LIME since the same explanation is returned for almost all observations regardless of feature values.
 The explanation scatterplots visualize the locality of the explanation using point size to indicate weight.
-However, the lack of definition of a local region makes it difficult to assess whether the weights capture an appropriately local region.} \sout{As stated, the feature heatmap reveals that the density simulation methods in the \data \ example results in global explanations where the same features are repeatedly chosen across all (or almost all) observations in the set of explanations.
-This finding agrees with that of \citet{laugel:2018} who found LIME produced global explanations with the normal approximation simulation method.
-For the bin based simulation methods in the bullet data example, the feature heatmap shows that the features chosen for the explanations vary between the two classification categories (match versus non-match).
-This is an interesting finding that suggests that different features can play a role in the predictions of observations in different response categories.
-Furthermore, while the metric comparison plot in the bullet example does not provide agreement between metrics on a best bin based method, all metrics agree that a Gower power of 0.5 for computing the model weights associated with distance of a simulated data point from the prediction of interest is the best.
-This suggests that a \sout{less} \kge{more} local explanation provides a better explanation of the performance of the random forest.}
-
-\sout{Some of the visualizations in the paper generalize easily to any application of LIME such as the feature heatmap and metric plot.
-Other plots such as the visualizations of the LIME procedure would require extensions such as the use of scatterplot matrices to compare explanations with more than two features.}
+However, the lack of definition of a local region makes it difficult to assess whether the weights capture an appropriately local region.}
 
 \kge{These diagnostic visualizations are a starting point that already highlight seemingly common issues with the LIME claims.
-Additions, such as visualizations of the step-by-step process of the creation of LIME explanations and} \sout{The addition of} interactivity\kge{,} \sout{to the diagnostic plots would provide additional} enhance\sout{ment of} the assessment process.
+Additions, such as visualizations of the step-by-step process of the creation of LIME explanations and}  interactivity\kge{,}  enhance the assessment process.
 For example, a diagnostic plot that provides a summary of multiple LIME explanations, such as the feature heatmap, could be displayed and clicked on to reveal more detailed figures associated with individual predictions of interest, such as an explanation scatterplot.
@@
 While it would be ideal if LIME could be used as a method to provide easily understandable explanations for black-box models as \citet{ribeiro:2016} claim, that dream is not yet a reality.
-The examples using diagnostic plots to assess LIME in this paper show frequent \kge{instances when the claims about LIME are not met} \sout{issues with LIME}.
-We hope that our plots provide motivation to assess LIME explanations, to not blindly use the default settings (even if it is not clear how to tune the parameters), and to encourage work \sout{on} improving LIME, so that it can be a lime and not a lemon.
+The examples using diagnostic plots to assess LIME in this paper show frequent \kge{instances when the claims about LIME are not met} .
+We hope that our plots provide motivation to assess LIME explanations, to not blindly use the default settings (even if it is not clear how to tune the parameters), and to encourage work  improving LIME, so that it can be a lime and not a lemon.
 
@@
 
-\section{Explanation Scatterplots Under \sout{Other} \kge{Density} Simulation Scenarios} \label{exp-scatter_plus}
+\section{Explanation Scatterplots Under  \kge{Density} Simulation Scenarios} \label{exp-scatter_plus}
 
@@
 Figure \ref{fig:figure-B1} provides example explanation scatterplots \kge{for the \data \ prediction of interest when the kernel density simulation method is used.
-The plots show the relationships between the random forest prediction and the selected features of $x_1$ and $x_2$ on the left and right, respectively.} \sout{for each feature in the default LIME explanation obtained using the kernel density simulation method for the \data \ prediction of interest.} \sout{Figure \ref{fig:figure-F5} includes explanation scatterplots for the explanations generated using kernel density simulation for the bullet example cases M and NM discussed in Section \ref{bullet-assess-ex}.}
+The plots show the relationships between the random forest prediction and the selected features of $x_1$ and $x_2$ on the left and right, respectively.}
 
@@
 @
-\caption{Residual plot of the explainer model associated with \data \ prediction of interest from Section \ref{exp-scatter}\sout{.
-The residuals are plotted against the predicted values.
-The points are jittered in the x-direction to alleviate the over-plotting of points.
-There is\kge{a clear increase} \sout{an upward trend} in the residuals as the explainer model predictions increase}, which suggests a violation of the linearity assumption.}
+\caption{Residual plot of the explainer model associated with \data \ prediction of interest from Section \ref{exp-scatter}, which suggests a violation of the linearity assumption.}
 \label{fig:figure-C2}
@@
 This is shown in Figure \ref{fig:figure-C2} with the explainer model residuals on the y-axis and explainer model predictions on the x-axis.
-The points along the x-axis have been jittered to ease the effect of the over-plotted points\sout{ in the visualization}.
-There is a clear increasing trend in the residuals as the explainer model predictions increase\kge{,}\sout{.
-This is a clear} \kge{which indicates a} violation of the \kge{ridge regression} linearity assumption\sout{ with the ridge regression model}.
+The points along the x-axis have been jittered to ease the effect of the over-plotted points.
+There is a clear increasing trend in the residuals as the explainer model predictions increase\kge{,} \kge{which indicates a} violation of the \kge{ridge regression} linearity assumption.
 
@@
 \caption{Hypothetical examples of feature heatmaps in two possible situations.
-\sout{The heatmaps show the top feature chosen for 10 cases across 5 different sets of tuning parameter values.
-The color of the cell indicates the feature chosen by LIME.} Situation 1 is the ideal, because the explanations vary across cases but do not dependent on specific tuning parameter values.
+Situation 1 is the ideal, because the explanations vary across cases but do not dependent on specific tuning parameter values.
 \kge{Situation 2 suggets global explanations and extreme explanation dependence on the tuning parameter values.}}
@@
 @
-\caption{Plots of LIME explanations (first row) and explanation scatterplots (second row) for case M in the bullet test data for two tuning parameter values: 4-quantile-bins (first column) and 4-equal-bins (second column).\sout{ The plots provide insights into the LIME explanations and allow for the assessment of the explanation quality.}}
+\caption{Plots of LIME explanations (first row) and explanation scatterplots (second row) for case M in the bullet test data for two tuning parameter values: 4-quantile-bins (first column) and 4-equal-bins (second column).}
 \label{fig:figure-F4}

### 2020-12-30 paper.tex
removing extraneous text

--- 2020-12-15 paper.tex
@@
-\documentclass[AMS,STIX2COL]{WileyNJD-v2}\usepackage[]{graphicx}\usepackage[]{color}
-% maxwidth is the original width if it is less than linewidth
-% otherwise use linewidth (to make sure the graphics do not exceed the margin)
-\makeatletter
-\def\maxwidth{ %
-  \ifdim\Gin@nat@width>\linewidth
-    \linewidth
-  \else
-    \Gin@nat@width
-  \fi
-}
-\makeatother
-
-\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
-\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
-\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
-\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
-\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
-\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
-\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
-\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
-\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
-\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%
-\let\hlipl\hlkwb
-
-\usepackage{framed}
-\makeatletter
-\newenvironment{kframe}{%
- \def\at@end@of@kframe{}%
- \ifinner\ifhmode%
-  \def\at@end@of@kframe{\end{minipage}}%
-  \begin{minipage}{\columnwidth}%
- \fi\fi%
- \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
- \colorbox{shadecolor}{##1}\hskip-\fboxsep
-     % There is no \\@totalrightmargin, so:
-     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
- \MakeFramed {\advance\hsize-\width
-   \@totalleftmargin\z@ \linewidth\hsize
-   \@setminipage}}%
- {\par\unskip\endMakeFramed%
- \at@end@of@kframe}
-\makeatother
-
-\definecolor{shadecolor}{rgb}{.97, .97, .97}
-\definecolor{messagecolor}{rgb}{0, 0, 0}
-\definecolor{warningcolor}{rgb}{1, 0, 1}
-\definecolor{errorcolor}{rgb}{1, 0, 0}
-\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX
-
-\usepackage{alltt}
+\documentclass[AMS,STIX2COL]{WileyNJD-v2}
 
@@
 \raggedbottom
-\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
+
+\usepackage{Sweave}
 \begin{document}
+\input{paper-concordance}
 
 % Paper header (title and authors)
-\title{Visual Diagnostics of a\kge{n} \sout{Model} Explainer \kge{Model} -- Tools for the Assessment of LIME Explanations}
+\title{Visual Diagnostics of a\kge{n}  Explainer \kge{Model} -- Tools for the Assessment of LIME Explanations}
 \author[1]{Katherine Goode*}
@@
 
-\begin{figure*}[!thp]
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\begin{Schunk}
+\begin{Sinput}
+> 
+> # # Simulate example data
+> # set.seed(20190624)
+> # lime_data <-
+> #   data.frame(
+> #     feature1 = sort(runif(250, 0, 1)),
+> #     feature2 = sample(x = 1:250, size = 250, replace = FALSE)) %>%
+> #   mutate(
+> #     feature1_stnd = (feature1 - mean(feature1)) / sd(feature1),
+> #     feature2_stnd = (feature2 - mean(feature2)) / sd(feature2),
+> #     prediction = if_else(feature1 >= 0 & feature1 < 0.1,
+> #                          (0.3 * feature1) + rnorm(n(), 0, 0.01),
+> #                  if_else(feature1 >= 0.1 & feature1 < 0.3,
+> #                          rbeta(n(), 1, 0.5),
+> #                  if_else(feature1 >= 0.3 & feature1 < 0.5,
+> #                          sin(pi* feature1) + rnorm(n(), 0, 0.5),
+> #                  if_else(feature1 >= 0.5 & feature1 < 0.8,
+> #                          -(sin(pi* feature1) + rnorm(n(), 0, 0.1)) + 1,
+> #                  if_else(feature1 >= 0.8 & feature1 < 0.9,
+> #                          0.5 + runif(n(), -0.5, 0.5),
+> #                          0.5 + rnorm(n(), 0, 0.3))))))) %>%
+> #   bind_rows(
+> #     data.frame(feature1 = rep(1, 30) + rnorm(5, 0, 0.05),
+> #            feature2 = rep(245, 30) + rnorm(5, 0, 1),
+> #            prediction = rep(0, 30) + rnorm(5, 0, 0.05)) %>%
+> #   mutate(feature1_stnd = (feature1 - mean(feature1)) / sd(feature1),
+> #          feature2_stnd = (feature2 - mean(feature2)) / sd(feature2)))
+> # 
+> # # Specify a prediction of interest
+> # prediction_of_interest <-
+> #   data.frame(feature1 = 0.07, feature2 = 200) %>%
+> #   mutate(feature1_stnd = (feature1 - mean(lime_data$feature1)) /
+> #            sd(lime_data$feature1),
+> #          feature2_stnd = (feature2 - mean(lime_data$feature2)) /
+> #            sd(lime_data$feature2),
+> #          prediction = 0.05,
+> #          color = factor("Prediction \nof Interest"))
+> # 
+> # # Specify the gower exponents
+> # good_gower_power <- 50
+> # bad_gower_power <- 1
+> # 
+> # # Compute the good distances between the prediction of interest
+> # # and all other observations
+> # lime_data$distance_good <-
+> #   (1 - gower_dist(x = prediction_of_interest %>%
+> #                     select(feature1_stnd, feature2_stnd),
+> #                   y = lime_data %>%
+> #                     select(feature1_stnd,
+> #                            feature2_stnd)))^good_gower_power
+> # 
+> # # Compute the bad distances between the prediction of interest
+> # # and all other observations
+> # lime_data$distance_bad <-
+> #   (1 - gower_dist(x = prediction_of_interest %>%
+> #                     select(feature1_stnd, feature2_stnd),
+> #                   y = lime_data %>%
+> #                     select(feature1_stnd,
+> #                            feature2_stnd)))^bad_gower_power
+> # 
+> # # Prepare the data for plotting
+> # lime_data_gathered <- lime_data %>%
+> #   gather(feature, feature_stnd_value,
+> #          feature1_stnd:feature2_stnd) %>%
+> #   gather(distance, distance_value, distance_good:distance_bad) %>%
+> #   mutate(distance = fct_recode(distance,
+> #                                "good" = "distance_good",
+> #                                "bad" = "distance_bad"),
+> #          feature = fct_recode(feature,
+> #                               "Feature 1" = "feature1_stnd",
+> #                               "Feature 2" = "feature2_stnd"))
+> # 
+> # # Prepare the prediction of interest data for plotting
+> # prediction_of_interest_gathered <- prediction_of_interest %>%
+> #   select(-feature1, -feature2) %>%
+> #   gather(feature, feature_value, feature1_stnd, feature2_stnd) %>%
+> #   mutate(feature = fct_recode(feature,
+> #                               "Feature 1" = "feature1_stnd",
+> #                               "Feature 2" = "feature2_stnd"))
+> 
+\end{Sinput}
+\end{Schunk}
 
-{\centering \includegraphics[width=6.5in]{figure/figure-01-1}
+\begin{Schunk}
+\begin{Sinput}
+> 
+> # # Fit the good interpretable explainer model
+> # explainer_good <-
+> #   glmnet(x = lime_data %>% select(feature1_stnd, feature2_stnd)
+> #          %>% as.matrix(),
+> #          y = lime_data$prediction,
+> #          alpha = 0,
+> #          lambda = 1,
+> #          weights = lime_data$distance_good)
+> # 
+> # # Fit the bad interpretable explainer model
+> # explainer_bad <-
+> #   glmnet(x = lime_data %>% select(feature1_stnd, feature2_stnd)
+> #          %>% as.matrix(),
+> #          y = lime_data$prediction,
+> #          alpha = 0,
+> #          lambda = 1,
+> #          weights = lime_data$distance_bad)
+> # 
+> # # Join the coefficients from the explainer model into a dataframe
+> # coefs_data <- data.frame(case = c("good", "bad"),
+> #                          b0 = c(coef(explainer_good)[1],
+> #                                 coef(explainer_bad)[1]),
+> #                          b1 = c(coef(explainer_good)[2],
+> #                                 coef(explainer_bad)[2]),
+> #                          b2 = c(coef(explainer_good)[3],
+> #                                 coef(explainer_bad)[3])) %>%
+> #   mutate(feature1 = b0 + b2*prediction_of_interest$feature2_stnd,
+> #          feature2 = b0 + b1*prediction_of_interest$feature1_stnd) %>%
+> #   gather(key = feature, value = int, feature1:feature2) %>%
+> #   mutate(slope = c(coef(explainer_good)[2],
+> #                    coef(explainer_good)[3],
+> #                    coef(explainer_bad)[2],
+> #                    coef(explainer_bad)[3]),
+> #          feature = fct_recode(feature,
+> #                               "Feature 1" = "feature1",
+> #                               "Feature 2" = "feature2"))
+> 
+\end{Sinput}
+\end{Schunk}
 
-}
-
-\end{knitrout}
-\caption{\kge{Hypothetical scenarios depicting the effect of different weights on LIME (Left) An example of an explainer model with appropriate weights to provide a faithful approximation of the complex model.
-(Right) An example of an explainer model for the same prediction but with different weights that results in an explanation unfaithful to the complex model.} \sout{A conceptual depiction of a faithful LIME explainer model in the immediate neighborhood of a prediction of interest \kge{for a hypothetical black-box model trained using two features: Feature 1 (left) and Feature 2 (right).
-The explainer model is a ridge regression weighted by the inverse Gower distance to the prediction of interest raised to the power of \ensuremath{5\times 10^{-17}}.}} \sout{The predictions from a hypothetical black-box model are plotted against the standardized values of the two hypothetical predictor variables.
-The diamond shaped points represent the location of a prediction of interest.
-The size and opacity of the circular points indicate the weight assigned based on the distance to the prediction of interest computed using the inverse of the Gower distance metric raised to the power of \ensuremath{5\times 10^{-17}}.
-The black lines represent a weighted ridge regression model used as an explainer model that reasonably captures the relationship between the black-box predictions and the features in a local region around the prediction of interest.
-That is, the explainer is faithful to the complex model and produces a reasonable explanation that Feature 1 plays a more important role in the prediction of interest than Feature 2 since the magnitude of the slope associated with Feature 1 is larger.}}
-\label{fig:figure-01}
-\end{figure*}
-
-In the field of statistics, there are two main uses for models: inference and prediction.
-Machine learning models \sout{are often used for the latter purpose.
-These models} have proven to perform well \kge{in problems with the latter objective} \sout{in a wide range of prediction problems}, but the accuracy of many machine learning models comes at the cost of interpretability due to their algorithmic complexity (hence the phrase "black-box models").
-Model interpretability allows for the understanding and assessment of how a model produces predictions.
-The lack of the ability to understand and assess a model makes it difficult to trust the model, especially in areas with high stakes decisions such as \kge{the} medical and forensics sciences.
-The increased use of machine learning models in applications and the introduction of the General Data Protection Regulation (GDPR) in 2018 \citep{goodman:2016} has resulted in a dramatic increase in explainable machine learning research, which focuses on developing ways to explain output from machine learning algorithms.
-
-Throughout this paper, we distinguish between interpretability and explanability of models.
-We define {\it interpretability} as the ability to directly use model parameters to understand the relationships in the data captured by the model: e.g., a linear model coefficient associated with a predictor variable indicates the amount the response variable changes based on a change in the predictor variable.
-In contrast, define {\it explanability} as the ability to use the model in an indirect manner to understand the relationships in the data captured by the model: e.g., partial dependence plots depict the marginal relationship between model predictions and predictor variables \citep{friedman:2001}.
-
-Numerous methods have been proposed to provide explanations for black-box model predictions \citep{gilpin:2018, guidotti:2018, ming:2017, molnar:2019}.
-Some are specific to one type of model (e.g.
-\citep{simonyan:2013} and \citep{urbanek:2008}), and others are model-agnostic (e.g.
-\citep{fisher:2018} and \citep{strumbelj:2014}).
-In this paper, we focus on \kge{the} \sout{one specific} model-agnostic method\sout{:} \kge{of} LIME \citep{ribeiro:2016}.
-
-LIME (local interpretable model-agnostic explanations) \sout{is a method that} uses a surrogate model to relate predictor variables to black-box model predictions \sout{(i.e.
-a model explainer)} \citep{ribeiro:2016}.
-\sout{We distinguish between the terms of model explainer and explainer model: by \emph{model explainer} we denote the method for explaining a complex model using a surrogate model, while the \emph{explainer model}, or simply the \emph{explainer}, is the surrogate model.} While some \kge{explainer} model\kge{s} \sout{explainers} focus on understanding a model at the global level, LIME claims to provide explanations for individual predictions (local).
-Additionally, LIME is designed to work with any model (model-agnostic) and to produce easily understandable results (explanations) \citep{ribeiro:2016}.
-Conceptually, LIME fits a simple (interpretable) model, the explainer model, \kge{to approximate} \sout{meant to capture the behavior of} the \sout{(}complex\sout{) black-box} model in a local region around a prediction of interest.
-The simple model \kge{is interpreted to identify the} \sout{then provides interpretable estimates for} variables that most influence\sout{d} the \kge{complex model} prediction\sout{made by the complex model}.
-
-\kge{While t}\sout{T}he concept of LIME is relatively simple\sout{: use an interpretable model to approximate a complex model in a local region.
-However}, a practical implementation of LIME is not straightforward, and research is being done to improve the procedure \citep{laugel:2018}.
-The current implementations of LIME \citep{pedersen:2020} \citep{ribeiro:2020} offer various tuning parameters (see Section \ref{background}) that affect the explainer model and ultimately, the explanation.
-Since the explainer model is an approximation of the complex model and not a direct interpretation, the explanations produced by an explainer model are subject to the quality of the approximation.
-Thus, in order to achieve \kge{reasonable} \sout{accurate} explanations, the tuning parameter values selected \kge{shoud} \sout{need to} be assessed.
-
-\kge{To demonstrate the effect of a tuning parameter on LIME, we consider two different explainer models applied to the same prediction.
-Figure \ref{fig:figure-01} depicts two plots of the predictions from a hypothetical black-box model versus the feature used to train the model.
-The location of a prediction of interest is indicated by the diamonds.
-Globally, there is a clear non-linear relationship between the predictions and the feature, but the relationship could be approximated by a linear model in a local region around the prediction of interest.
-In both scenarios, a linear regression weighted by the proximity from an observation to the prediction of interest is used as the explainer model, but the proximities are computed differently as depicted by the varying sizes of the observations in the two plots.}
-
-\kge{On the left, the distance between an observation and the prediction of interest is computed using the Gower distance metric \citep{gower:1971} and then raised to the power of \ensuremath{5\times 10^{-17}} to emphasize a very local region.
-The distances are subtracted from 1 to obtain a proximity.
-Here, the explainer model is faithful to the complex model since it captures the linear relationship between the black-box predictions in an immediate neighborhood of the prediction of interest.
-The slope \sout{of 0.634} explains that the black-box predictions increase as the feature increases in the local region around the prediction of interest.}
-
-\kge{For the scenario on the right, the computation of the proximities is the same except the distances are raised to a power of 1 (the default exponent in the \emph{lime} R package \citep{pedersen:2020}).
-This causes the observations that are further away from the prediction of interest to be given larger weights than the scenario on the left.
-Here, the explainer model does not capture the linear trend near the prediction of interest, but instead, the explainer captures a more global trend.
-Without an assessment of this explainer model, the slope \sout{of -0.181} would incorrectly explain that the predictions decrease as the feature increases near the prediction of interest.} %\sout{This cannot be said of the explainer model in \autoref{fig:figure-02}.
-In addition, the magnitude of the slope associated with Feature 2  () is larger than that of Feature 1 ().
-Thus, this explainer model actually provides a misleading explanation that Feature 2 plays a more important role in the prediction of interest.}
-
-%\kge{To demonstrate the effect of tuning parameters on LIME,we consider two different explainer models applied to the same prediction.
-Suppose a hypothetical black-box model is trained using one feature.
-Both plots in Figure1show the black-box model predictions versus the feature used to train the model.The diamond shaped point in the plots indicates the location of the prediction of interest to explain.
-A weight ridge regression with the black-box predictions as the response variable and standardized versions the features as predictor variables will be used as the explainer model in both scenarios, but the weights will vary.
-Note that the standardized features allow for direct comparisons of the model coefficients.}
-
-%\kge{Figure \ref{fig:figure-01} depicts the first scenario where the weights are computed as the inverse proximity of the point to the prediction of interest computed using the Gower distance metric \citep{gower:1971} raised to the power of good_gower_power to emphasize a very local region.
-The point size represents the weight, and the black lines depict the ridge regression model given the observed prediction of interest value from the opposite feature.
-For Feature 1 (left), the explainer model captures the relationship in an immediate neighborhood around the prediction of interest with a slope of coefs_data %>% filter(case == "good", feature == "Feature 1") %>% pull(slope) %>% round(3), and for Feature 2 (right), the ridge regression has a small slope of coefs_data %>% filter(case == "good", feature == "Feature 2") %>% pull(slope) %>% round(3) that accurately reflects the absence of any global or local relationship between the black-box predictions and Feature 2.
-The magnitude of the slope associated with Feature 1 is larger than the slope of Feature 2, which suggests that Feature 1 plays a more important role in the prediction made by the black-box model for the prediction of interest.
-This explanation agrees with a visual assessment of the relationships between the predictions and predictor variables.}
-
-%\sout{\autoref{fig:figure-01} provides a visualization of this conceptual understanding of LIME.
-The two plots show the predictions from a hypothetical black-box model plotted against the two hypothetical model predictor variables.
-The diamond shaped points represent the location of the prediction of interest.
-A Gower distance metric \citep{gower:1971} is used to define locality such that the size of the points represent the inverse of the Gower distance raised to some value and indicate the proximity to the prediction of interest.
-In the example of \autoref{fig:figure-01}, an exponent of good_gower_power is used to emphasize a very local region around the prediction of interest.
-A ridge regression model weighted by the proximity values is used as the explainer model with the black-box predictions as the response variable and standardized versions of two features in the data as predictor variables.
-Standardized features allow direct comparisons of the model coefficients.
-The explainer model is depicted by the black lines in the figure.}
-
-%\sout{The plot on the left of \autoref{fig:figure-01} shows the relationship between the black-box predictions and Feature 1.
-Here, the explainer model is plotted with Feature 2 fixed at the observed value of the prediction of interest.
-The explainer model captures the relationship in an immediate neighborhood around the prediction of interest with a slope of coefs_data %>% filter(case == "good", feature == "Feature 1") %>% pull(slope) %>% round(3).
-The plot on the right shows no global or local relationships between the black-box predictions and Feature 2.
-Here, the explainer model is plotted with Feature 1 set as the observed value of the prediction of interest, and it has an appropriately small slope of coefs_data %>% filter(case == "good", feature == "Feature 2") %>% pull(slope) %>% round(3).
-The magnitude of the slope associated with Feature 1 is larger than the slope of Feature 2, which suggests that Feature 1 plays a more important role in the prediction made by the black-box model for the prediction of interest.
-This explanation agrees with a visual assessment of the relationships between the predictions and predictor variables.}
-
-%\sout{The concept of LIME is relatively simple: use an interpretable model to approximate a complex model in a local region.
-However, a practical implementation of LIME is not straightforward, and research is being done to improve the procedure \citep{laugel:2018}.
-The current implementations of LIME \citep{ribeiro:2020} \citep{pedersen:2020} offer various tuning parameters (see Section \ref{background}) that affect the explainer model and ultimately, the explanation.
-Since the explainer model is an approximation of the complex model and not a direct interpretation, the explanations produced by an explainer model are subject to the quality of the approximation.
-Thus, in order to achieve accurate explanations, the tuning parameter values selected need to be assessed.}
-
-%\kge{Figure \ref{fig:figure-02} depicts the second explainer model scenario.
-Again, the weights are computed using the Gower distance metric, but in this situation, the distances are raise to a power of bad_gower_power (the default exponent in the \emph{lime} R package).} \sout{We consider an example where the choice of exponent for the weights is crucial to the quality of the explanation.
-The plots in Figure \ref{fig:figure-02} show the same data as \autoref{fig:figure-01}, but the Gower distance metric exponent is decreased to bad_gower_power (the default exponent in the \emph{lime} R package).} This causes the observations that are further away from the prediction of interest to be given larger weights than before.
-In \autoref{fig:figure-01}, the explainer model captures the relationship between the black-box predictions in an immediate neighborhood of the prediction of interest.
-This cannot be said of the explainer model in \autoref{fig:figure-02}.
-In addition, the magnitude of the slope associated with Feature 2  (coefs_data %>% filter(case == "bad", feature == "Feature 2") %>% pull(slope) %>% round(3) %>% abs()) is larger than that of Feature 1 (coefs_data %>% filter(case == "bad", feature == "Feature 1") %>% pull(slope) %>% round(3) %>% abs()).
-Thus, this explainer model actually provides a misleading explanation that Feature 2 plays a more important role in the prediction of interest.
-
-% \begin{figure*}[!thp]
-% <<figure-02, out.width = '6.25in', fig.width = 7.95, fig.height = 3.25, warning = FALSE, eval = FALSE>>=
-% 
-% # Specify the figure size (for determining font size)
-% f2_ow = 6.25
-% f2_fw = 7.95
-% f2_fs = fs * (f2_fw / f2_ow)
-% 
-% # Plot of good explainer model
-% ggplot() +
-%   facet_grid(. ~ feature, switch = "x") +
-%   geom_point(
-%     data = lime_data_gathered %>% 
-%       mutate(
-%         feature = fct_recode(
-%           feature,
-%           "Feature 1 (standardized)" = "Feature 1",
-%           "Feature 2 (standardized)" = "Feature 2"
-%           )
-%         ),
-%     mapping = aes(
-%       x = feature_stnd_value,
-%       y = prediction,
-%       size = distance_value,
-%       color = distance
-%     ), 
-%     alpha = 0.6
-%   ) +
-%   geom_abline(
-%     data = coefs_data %>% 
-%       filter(case == "bad") %>% 
-%       mutate(
-%         feature = fct_recode(
-%           feature,
-%           "Feature 1 (standardized)" = "Feature 1",
-%           "Feature 2 (standardized)" = "Feature 2"
-%           )
-%         ),
-%     mapping = aes(intercept = int, slope = slope),
-%     size = 1
-%   ) +
-%   scale_color_manual(values = c("grey30", NA), guide = "none") +
-%   geom_point(
-%     data = prediction_of_interest_gathered %>% 
-%       mutate(
-%         feature = fct_recode(
-%           feature,
-%           "Feature 1 (standardized)" = "Feature 1",
-%           "Feature 2 (standardized)" = "Feature 2"
-%           )
-%         ),
-%     mapping = aes(x = feature_value,
-%                   y = prediction,
-%                   fill = color),
-%     color = "black",
-%     size = 5,
-%     shape = 23,
-%     alpha = 0.75
-%   ) +
-%   scale_fill_manual(values = "#FAAA72") +
-%   geom_text(
-%     data = data.frame(
-%       feature_stnd_value = 1.2,
-%       prediction = 1.6,
-%       feature = c("Feature 1 (standardized)", "Feature 2 (standardized)"),
-%       slope = c(
-%         paste(
-%           "Slope:",
-%           coefs_data %>%
-%             filter(case == "bad",
-%                    feature == "Feature 1") %>%
-%             pull(slope) %>%
-%             round(3)
-%         ),
-%         paste(
-%           "Slope:",
-%           coefs_data %>%
-%             filter(case == "bad",
-%                    feature == "Feature 2") %>%
-%             pull(slope) %>%
-%             round(3)
-%         )
-%       )
-%     ),
-%     mapping = aes(x = feature_stnd_value,
-%                   y = prediction,
-%                   label = slope),
-%     family = ff,
-%     size = f2_fs / 3
-%   ) +
-%   labs(
-%     x = "",
-%     y = "Black-Box Prediction",
-%     title = "Conceptual Depiction of an Unfaithful Local Explainer Model",
-%     subtitle = paste("Gower Distance Metric Exponent:", bad_gower_power),
-%     fill = "",
-%     alpha = "Weight",
-%     size = "Weight"
-%   ) +
-%   theme_linedraw(base_family = ff, base_size = f2_fs) +
-%   theme(
-%     panel.grid.major = element_blank(),
-%     panel.grid.minor = element_blank(),
-%     axis.text.x = element_blank(),
-%     axis.ticks.x = element_blank(),
-%     axis.text.y = element_blank(),
-%     axis.ticks.y = element_blank(),
-%     strip.placement = "outside",
-%     strip.background = element_rect(color = "white", fill = "white"),
-%     strip.text.x = element_text(size = f2_fs, color = "black"),
-%     plot.title = element_text(size = f2_fs)
-%   ) +
-%   guides(
-%     fill = guide_legend(order = 1),
-%     size = guide_legend(order = 2),
-%     alpha = guide_legend(order = 2)
-%   )
-% 
-% @
-% \caption{A conceptual depiction of an unfaithful local explainer model in the immediate neighborhood of a prediction of interest.
-A\kge{gain, a weighted} ridge regression \kge{is used as the explainer model} \sout{is fit to the same hypothetical black-box model predictions and predictor variables as in \autoref{fig:figure-01}}, but the \kge{Gower distance is raised to a power} \sout{weights are computed using a Gower exponent} of 1.
-\sout{The explainer model is unfaithful to the complex model in any immediate neighborhood of the prediction of interest.}}
-% \label{fig:figure-02}
-% \end{figure*}
-
-\kge{\autoref{fig:figure-01} demonstrates a simple example in which the explanation quality varies drastically when different weights are used.
-Similar concerns with LIME have been raised in the literature.} \sout{Several sources in the literature discuss the performance of LIME.} \kge{\citet{laugel:2018} and \citet{molnar:2019} discuss the difficulty specifying a local region with LIME due to both} \sout{One of the biggest difficulties with LIME is determining how to specify a local region \citep{laugel:2018} \citep{molnar:2019}.
-This is due to} an unclear definition of \kge{what is} a "local region" and how to apply LIME to achieve an appropriate local region\sout{ as demonstrated by \autoref{fig:figure-02}}.
-\kge{A different concern about LIME is raised by} \citet{alvarezmelis:2018} \sout{raise a concern} pertaining to the robustness of explanations from LIME and other \kge{explainer} model\kge{s} \sout{explainers}: they find that even small changes in predictor variables can lead to very different LIME explanations.
-\kge{Even the original authors of LIME,} \sout{Additionally,} \citet{ribeiro:2016}\kge{,} acknowledge that if a linear model is used as the explainer, LIME relies on a linear approximation of the explainer model to the complex model and state "if the underlying model is highly non-linear even in the locality of the prediction, there may not be a faithful explanation".
-
-\sout{As a result of the various ways LIME can fail, it is important to assess LIME explanations.
-We suggest the use of visual diagnostics for assessment.
-In this paper,} \kge{Without an assessment of the LIME explainer model, the user is putting trust in another black-box procedure to explain the complex black-box model.
-In this paper, we stress the importance of assessing the LIME explainer model.} \kge{To do this, w}e lay out the set of claims about LIME made by \citet{ribeiro:2016}, and \kge{we provide a toolkit of visual diagnostics} \sout{propose three visualizations} for the assessment of these claims: (1) \emph{explanation scatterplots}, (2) \emph{feature heatmaps}, (3) \emph{assessment metric plots}.
-\kge{Using these visual diagnostics, we demonstrate problematic examples of LIME explanations where the claims about LIME are not met and the explanations are highly dependent on tuning parameter values without a clear way to identify a set of tuning parameter values that produce the "best" explanations.}
-
-While LIME is implemented for image, tabular, and text data, we only focus on tabular data.
-For additional simplicity, we only discuss classification prediction models with a dichotomous response variable and continuous predictor variables.
-However, the proposed diagnostics may be extended to \kge{other} \sout{a wider range of} situations.
-
-The remainder of the paper is structured as follows.
-Section \ref{background} provides background and claims made by \citet{ribeiro:2016} about LIME.
-We introduce the suggested diagnostic plots in Section \ref{diagnostics}.
-Then in Section \ref{application}, we demonstrate the use of the diagnostics to assess LIME explanations for a random forest  fit to a forensics bullet matching dataset.
-Section \ref{discussion} concludes with a discussion on extensions and limitations of the diagnostic plots and concerns about LIME in regards to the claims made by \citet{ribeiro:2016} brought about by the visualization examples in this paper that agree with \citet{alvarezmelis:2018}, \citet{laugel:2018}, and \citet{molnar:2019}.
-
-All runs of LIME in this paper are executed in a forked version (https://github.com/goodekat/lime) of the R package \emph{lime} (version 0.5.1) by \citet{pedersen:2020}.
-The forked version is functionally indistinguishable from \citeauthor{pedersen:2020}'s implementation but allows us to export internal values relevant for an assessment of the explainer.
-The diagnostic plots included in this paper are created using the R package \emph{limeaid} \citep{goode:2020}.
-
-\section{Background on LIME} \label{background}
-
-\kgc{I ended up moving some of the paragraphs in this section around and adding a little bit of additional text. I think this organization flows more smoothly. What do you think?}
-
-The general form of the LIME algorithm can be divided into three steps \citep[see also][]{laugel:2018}:
-
-\begin{enumerate}
-
-\item \emph{Data Simulation and Interpretable Transformation}: Simulate a dataset from the original data used to fit the black-box model.
-Apply a transformation to the simulated data and the prediction of interest that will allow for interpretable explanations.
-
-\item \emph{Explainer Model Fitting}: Apply the black-box model to the simulated data to obtain predictions.
-Compute the distance between each of the simulated data points and the prediction of interest.
-Perform feature selection.
-Fit an interpretable model with the black-box predictions from the simulated data as the response, the selected features from the transformed simulated data as the predictors, and the distances as weights.
-This model is the explainer model.
-
-\item \emph{Explainer Model Interpretation}: Interpret the explainer model to determine which features played the most important role in the prediction of interest.
-
-\end{enumerate}
-
-\citet{ribeiro:2016} provide an implementation of LIME in a Python package \cite{ribeiro:2020}.
-An adaption of the Python package in R has been implemented and made available by Thomas Lin-Pedersen \citep{pedersen:2020}.
-\kge{In both implementations, a ridge regression model is used as the explainer model, and} \sout{During the application of LIME, t} the user is asked to select various tuning parameter options: the number of features to return in the explanation, the simulation method, the feature selection method, and how the weights are computed.
-The discussion of parameter choices and implementation details of LIME in this paper are based on the R package.
-\kge{See Appendix~\ref{lime-details} for}
-an overview of the options available for the tuning parameters\sout{ is included in Appendix~\ref{lime-details}}.
-
-In the original paper, \citet{ribeiro:2016} make the following set of claims regarding the performance of LIME:
-
-\begin{itemize}
-\item \emph{Interpretability}: The explainer model can be easily interpreted to provide meaningful explanations.
-\item \emph{Faithfulness}: The explainer model sufficiently captures the relationship between the complex model predictions and the features in the local region around a prediction of interest to produce explanations that are faithful to the complex model.
-\item \emph{Linearity}: By using a ridge regression model as the explainer model, it is assumed that there is a linear relationship between complex model predictions and the features in the local region around a prediction of interest.
-\item \emph{Localness}: The explanations produced by LIME are local in regards to a prediction of interest.
-\end{itemize}
+\begin{Schunk}
+\begin{Sinput}
+> # Specify the gower exponents
+> good_gower_power <- 0.00000000000000005
+> bad_gower_power <- 1
+> # Specify a prediction of interest
+> poi <-
++   data.frame(
++     poi = "Prediction \nof Interest",
++     feature = 0.1,
++     prediction = 0.05
++   )
+> # Simulate example data
+> set.seed(20190624)
+> concept_data <-
++   data.frame(poi = "Training Data", 
++              feature = sort(c(runif(100, 0, 1), runif(250, 0, 7)))) %>%
++   mutate(prediction = sin(feature) + rnorm(350, 0, 0.25)) %>%
++   bind_rows(poi)
+> # Compute the good distances between the prediction of interest
+> # and all other observations
+> concept_data$weights_good <-
++   1 - (gower_dist(
++     x = poi %>% select(feature),
++     y = concept_data %>% select(feature)
++   )) ^ good_gower_power
+> # Compute the bad distances between the prediction of interest
+> # and all other observations
+> concept_data$weights_bad <-
++   1 - (gower_dist(
++     x = poi %>% select(feature),
++     y = concept_data %>% select(feature)
++   )) ^ bad_gower_power
+> # Fit the good and bad interpretable explainer models
+> explainer_good <-
++   lm(prediction ~ feature, data = concept_data, weights = weights_good)
+> explainer_bad <-
++   lm(prediction ~ feature, data = concept_data, weights = weights_bad)
+> # Create labels for the gower powers
+> good_power_label <-
++   paste0("Faithful Local Explainer \n(exponent used to compute weights: ",
++          good_gower_power,
++          ")")
+> bad_power_label <-
++   paste0("Unfaithful Local Explainer \n(exponent used to compute weights: ",
++          bad_gower_power,
++          ")")
+> # Join the coefficients from the explainer model into a dataframe
+> coefs_data <-
++   data.frame(
++     case = c(good_power_label, bad_power_label),
++     b0 = c(coef(explainer_good)[1],
++            coef(explainer_bad)[1]),
++     b1 = c(coef(explainer_good)[2],
++            coef(explainer_bad)[2]),
++     feature = 6,
++     prediction = 1.6
++   ) %>%
++   mutate(text = paste0("Slope: ", round(b1, 3)))
+> # Prepare data for plotting
+> concept_data_long <-
++   concept_data %>%
++   pivot_longer(names_to = "case",
++                values_to = "weight",
++                cols = weights_good:weights_bad) %>%
++   mutate(case = ifelse(case == "weights_good", good_power_label, bad_power_label))
+\end{Sinput}
+\end{Schunk}
 
 \begin{figure*}[!thp]
-\centering
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-
-{\centering \includegraphics[width=6.5in]{figure/figure-02-1}
-
-}
-
-\end{knitrout}
-\caption{Plots of $x_2$ versus $x_1$ from the \kge{\data \ } training (left) and testing (right) sets\sout{ of the \data \ } introduced in Section \ref{diagnostics} \sout{.
-T} \kge{with t}he true classification boundary \sout{is} shown as a solid black line\sout{ in both plots}.
-\sout{The color of the training data represents the value of the observed response variable ($y$).
-The color of the testing data represents the random forest probability that an observation belongs to the category of blue.} \kge{In the testing set, the open black circles identify cases misclassified by the random forest, and the diamond indicates a prediction of interest.} \sout{The 18 cases that are misclassified by the random forest are identified by black circles.} \sout{The prediction of interest \kge{in the test data} \sout{to explain} is indicated by a diamond.}}
-\label{fig:figure-02}
-\end{figure*}
-
-The assumption of interpretability only depends on the complexity of the model used as explainer model.
-If the model is too complex to provide meaningful explanations (e.g.
-there are too many variables in the model), it is clear that the assumption of interpretability is violated.
-The other three assumptions are not as easy to assess, and for those, we suggest the use of diagnostic plots.
-
-\section{Visual Diagnostics for LIME} \label{diagnostics}
-
-\begin{figure*}[!thp]
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-
-{\centering \includegraphics[width=6.5in]{figure/figure-03-1}
-
-}
-
-\end{knitrout}
-\caption{(left) Visualization from the \emph{lime} R package of a LIME explanation for the \data \ prediction of interest identified in \autoref{fig:figure-02}.
-(right) \emph{Explanation Scatterplot}.
-\sout{The points represent the simulated data colored by the random forest probabilities and sized by the assigned LIME weights.
-The prediction of interest is shown as the diamond shaped point.
-The explainer model indicator variables associated with $x_1$ and $x_2$ (quantile bins containing the prediction of interest) are depicted by the solid lines.
-The line colors represent the explainer model coefficient signs and indicate whether the feature supports a prediction of `blue' (blue lines) or supports a prediction of `red' (red lines).} \kge{An explanation scatterplot associated with the explanation for the prediction of interest depicted on the left.} \sout{This figure shows that t}\kge{T}he \kge{4} quantile bins are not flexible enough to capture the relationship between the random forest predictions and the $x_1$ and $x_2$ values.}
-\label{fig:figure-03}
-\end{figure*}
-
-In this section, we introduce three visual diagnostic plots \sout{for the assessment of LIME.
-The plots focus on different levels of application of LIME (e.g.
-on explanation versus a set of explanations) to} \kge{that} assess the LIME claims from different perspectives:
-
-\begin{enumerate}
-\item \emph{Explanation Scatterplot} (Section \ref{exp-scatter}): Comparison of the explainer and complex models for an individual prediction of interest.
-\item \emph{Feature Heatmap} (Section \ref{feat-heat}): Comparison of features selected by LIME across applications of LIME with different tuning parameter values.
-\item \emph{Assessment Metric Plot} (Section \ref{assess-metric}): Comparison of performance metrics for LIME across applications of LIME with different tuning parameter values. 
-\end{enumerate}
-
-\paragraph{The \data}
-
-To demonstrate the visual diagnostics, we generate an example dataset that will be referred to as the \data.
-The \data \ contains 600 observations with \sout{three features and one response variable.
-The} features\sout{,} \kge{of} $x_1$\sout{,} \kge{and} $x_2$ \kge{independently sampled from Unif(-10, 10) distributions}\sout{,} and $x_3$\sout{,} \sout{\kge{that} are randomly sampled from Unif(-10, 10), Unif(-10, 10), and} \kge{sampled from a} $\mbox{N}(0,1)$ distribution\sout{s, respectively}.
-A binary response variable $y$ is created using a \sout{rotated} sine curve \sout{.
-In particular, let} \kge{such that}
-\begin{eqnarray}\label{eq:data}
-  y=\begin{cases}
-  \mbox{blue} & \mbox{ if } x'_2 > \sin\left(x'_1\right) \\
-  \mbox{red} & \mbox{ if } x'_2 \le \sin\left(x'_1\right) \ .
-  \end{cases}
-\end{eqnarray}
-where $x'_1=x_1\cos(\theta)-x_2\sin(\theta)$\kge{,} \sout{and} $x'_2=x_1\sin(\theta)+x_2\cos(\theta)$\kge{, and} \sout{where} $\theta=-0.9$. \sout{Then $y$ is defined as
-\begin{eqnarray}\label{eq:data}
-  y=\begin{cases}
-  \mbox{blue} & \mbox{ if } x'_2 > \sin\left(x'_1\right) \\
-  \mbox{red} & \mbox{ if } x'_2 \le \sin\left(x'_1\right) \ .
-  \end{cases}
-\end{eqnarray}}
-Note that due to the creation of $y$ in this manner, $y$ is dependent on $x_1$ and $x_2$ and independent of $x_3$.
-The dataset is \kge{randomly} divided into training and testing sets of 500 and 100 observations, respectively.
-A random forest is fit \kge{to the training set} using the R package \emph{randomForest} (version 4.6.14) \citep{liaw:2002} with the default settings\sout{.
-The model} \kge{and} is applied to the test set to obtain predictions.
-
-\autoref{fig:figure-02} shows scatterplots of $x_2$ versus $x_1$ from the training data (left) and the testing data (right).
-Both plots include the true classification boundary \sout{of the rotated sine function plotted} as the solid black line.
-The training data are colored by the observed response variable ($y$), and the testing data are colored by random forest prediction probabilities.
-The random forest  misclassifies 18 points, which are all located near the classification boundary \sout{.
-These are} \kge{and} identified by open circles\sout{ in \autoref{fig:figure-02}}.
-
-From these scatterplots, we \sout{also} see that the global relationship between response $y$ and features $x_1$ and $x_2$ is linear: the probability for label blue increases with the difference between features $x_2$ and $x_1$.
-Locally, the relationship between $y$ and features $x_2$ and $x_1$ varies a lot more around the line of identity.
-Here, the relationship is determined by the sine wave.
-However, the sine is a good-natured function that can be approximated well linearly in local regions \kge{as shown in Figure \ref{fig:figure-01}}.
-
-We apply LIME using six sets of tuning parameter values to all observations in the \data \ test set to observe \kge{explanation} variability\sout{ across tuning parameter values}.
-\kge{Five of the LIME applications use a} \sout{A} quantile bin based simulation method (samples are simulated uniformly from a \kge{feature using a} specified number of quantile bins) \sout{is used for five of the LIME applications} with the number of bins varying from 2 to 6 by application.
-We use 6 bins as the maximum, because the complexity of the explanations increases with the number of bins.
-Note that 4-quantile-bins \kge{is} \sout{are} the default method in \emph{lime}.
-The sixth application of LIME uses a kernel density simulation method (samples are drawn from kernel density approximations of the feature distributions).
-The default methods for feature selection (forward selection) and the computation of the weights (Gower distance raised to an exponent of 1) are used for all applications.
-See Appendix~\ref{lime-details} for \kge{more detailed} descriptions of the tuning parameters.
-
-For the presentation of the explanation scatterplot, we focus on the misclassified point \sout{with $(x_1, x_2, x_3)$ coordinates of (1.23, 8.47, -0.99)} indicated by a diamond in \autoref{fig:figure-02}.
-Misclassified points are often of interest to explain since they may provide information about ways to improve the model.
-For the introduction of the other two  plots, we consider the LIME explanations for  all observations in the \data \ test set.
-
-\paragraph{A Visual Representation of a LIME Explanation}
-
-Before introducing the visual diagnostics, let us consider a commonly used visualization of a LIME explanation\sout{ that is shown in Figure \ref{fig:figure-03} (left)}.
-\kge{Figure \ref{fig:figure-03} (left) depicts the explanation for the prediction of interest indicated in \autoref{fig:figure-02} obtained using 4-quantile-bins.
-In the text at the top, the "Probability" is the random forest probability of 0.74 that the observation of interest belongs to the "Label" category of blue.
-The "Explanation Fit" is the deviance ratio of 0.21 associated with the ridge regression explainer model (often interpreted as an $R^2$), which suggests that the explainer model is not a good linear fit.}
-
-\kge{Since 4-quantile-bins are used to simulate data, LIME converts continuous predictor variables to indicator variables identifying whether the variable value falls in the same quantile bin as the prediction of interest or not.
-The indicator variables are used as the features in the ridge regression explainer model.
-The features included in the visualization are the ones selected by feature selection, the lengths of the bars represent the coefficients from the ridge regression associated with the indicator variables, and the color of a bar denotes the sign of the coefficient.
-This explainer model explains that the random forest prediction that the observation of interest belongs to the category of blue is mostly supported by the prediction of interest having a value of $x_2$ that is greater than 4.834 but somewhat contradicted by the prediction of interest having a value of $x_1$ that is greater than -0.302 and less than or equal to 4.844.} \kgc{I decided to leave the values here, because this is how I would interpret this explanation, but I cut out a lot of text from this subsection in other ways.}
-
-\sout{Before introducing the visual diagnostics, let us consider a commonly used visualization of a LIME explanation\sout{ that is shown in Figure \ref{fig:figure-03} (left)}.
-\kge{Figure \ref{fig:figure-03} (left) shows the explanation for the prediction of interest indicated in \autoref{fig:figure-02} obtained using 4-quantile-bins.} \sout{The plot is created using the \emph{lime} R package and provides a visual representation of a LIME explanation for the prediction of interest indicated in \autoref{fig:figure-02}.
-In particular, the explanation is obtained using 4-quantile-bins to simulate the data.} \kge{When quantile bins are used to simulate data}\sout{ In this scenario}, LIME converts continuous predictor variables to indicator variables identifying whether the variable value falls in the same quantile bin as the prediction of interest or not.
-The\kge{n the} indicator variables are used as the explainer model features.}
-
-\sout{The plot reports 0.74 as the random forest  probability that the observation of interest belongs to category blue (denoted as the ``label" in the plot).
-The lengths of the bars represent the coefficients from a ridge regression model (the explainer model) fit using the R package \emph{glmnet} \citep{simon:2011} associated with the indicator variables chosen via feature selection.
-The color of a bar denotes the sign of the coefficient and whether the feature "supports" or "contradicts" a random forest classification of `blue'.
-The "explanation fit" is the deviance ratio from  \emph{glmnet}.
-In other words, this is the $R^2$ value associated with the explainer model.
-In this case, it is 0.21 suggesting that the explainer model is not a good linear fit.
-However, it is commonly accepted that $R^2$ has limitations for assessing the quality of fit of a model \citep{sapra:2014} and  should not be used as the only metric in a model assessment.}
-
-\sout{The explanation for the prediction of interest depicted in Figure \ref{fig:figure-03} is interpreted as follows.
-A random forest classification of blue is supported by the prediction of interest having a value of $x_2$ that is greater than 4.834, but the prediction of interest having a value of $x_1$ that is greater than -0.302 and less than or equal to 4.844 provides support against a classification of blue.
-Since the weight associated with $x_2$ has a larger magnitude than the weight associated with $x_1$, LIME explains that $x_2$ plays a more important role in the random forest prediction.
-Additionally, consider that since the support for blue by $x_2$ outweighs the support for red by $x_1$, the explainer model overall favors a label of blue for the prediction of interest, which agrees with the random forest probability of 0.744 for blue.
-Note that both models classify the observation incorrectly.}
-
-\subsection{Explanation Scatterplots} \label{exp-scatter}
-
-\kge{As a first check to determine whether the explanation depicted in \autoref{fig:figure-03} (left) is trustworthy, we note that since the support for blue by $x_2$ outweighs the support for red by $x_1$, the explainer model overall favors a label of blue for the prediction of interest agreeing with the random forest probability.
-In fact, both random forest and explainer model classify the observation incorrectly.
-However, based on the information in \autoref{fig:figure-03} (left) alone, it is not possible to make an informed assessment of the explanation.} \sout{Based on the plot on the left of \autoref{fig:figure-03} alone, it is not possible to make an informed assessment of the explanation.}
-
-For a further assessment of the explainer model, we turn to an \emph{explanation scatterplot}: a visual diagnostic for assessing the LIME claims of locality and fidelity for an individual explanation by juxtaposing the complex and explainer models in one plot.
-The format of an explanation scatterplot depends on the LIME simulation method.
-We introduce the explanation scatterplot here under the \emph{lime} R package default method of 4-quantile-bins.
-\kge{Appendix \ref{exp-scatter_plus} addresses the explanation scatterplot formats in other LIME simulation scenarios.}
-
-The explanation scatterplot applies the concept of plotting the model in the data space discussed in \citet{wickham:2015}.
-The plot is built by plotting the LIME simulated data for the top two features identified by the explanation in a scatterplot and coloring these points by the predictions from the complex model.
-The point size represents the weight assigned by LIME.
-In order to show the LIME results for the observation of interest, lines are drawn on top of the points\sout{.
-These lines}  represent\kge{ing} the boundaries of the indicator variables used to fit the explainer model.
-The line color  denotes whether LIME indicates that a feature supports or contradicts a class prediction.
-\sout{Appendix \ref{exp-scatter_plus} addresses the explanation scatterplot formats in other LIME simulation scenarios.}
-
-An explanation scatterplot corresponding to the LIME explanation depicted on the left in \autoref{fig:figure-03} is shown on the right hand side of \autoref{fig:figure-03}.
-By juxtaposing the random forest predictions and the explainer model boundaries, we are able to assess the faithfulness and localness of the explainer model.
-
-First, consider the claim of localness.
-The weights decay relatively slowly outside of the intersection of the 2-quantile-bin suggesting that the LIME explanation is highly influenced by points outside of the bins containing the prediction of interest.
-However, it is difficult to say if the claim of localness has been violated, because a definition of a local region is not specified.
-Depending on what region a viewer considers to be local, an argument could be made in favor of or against a violation of localness.
-The explanation scatterplot raises awareness of the unclear definition of a local region with LIME.
-Nevertheless, it is possible to say that the weights assigned to the simulated data do not capture  the local region identified by the intersection of the quantile bins.
-
-Now, consider the claim of faithfulness: It can be said that the majority of the points in the $x_2$ quantile support a prediction of blue, which is captured by the bar supporting a prediction of blue in the LIME explanation, and a similar statement can be made about the $x_1$ quantile-bin.
-These statements validate the explanation produced by LIME.
-However, the explanation scatterplot plot shows that the random forest performs well at capturing the sine curve classification boundary by creating various sized rectangles consisting of predictions with similar probabilities, which the LIME explanation does not pick up on \kge{since the bins are created without information about the random forest predictions}.
-Thus, LIME does provide an explanation for the prediction, but it is a very poor explanation in terms of faithfulness to the random forest prediction regions.
-
-It is difficult to assess linearity from this explanation scatterplot, but a residual plot of the explainer model could be used to check the linearity claim.
-See Appendix~\ref{residual-plot} for the residual plot associated with the explanation considered in Figure \ref{fig:figure-03}, which shows a violation of the linearity claim.
-
-This example explanation only includes two features.
-In situations where more than two features are included in a LIME explanation, the explanation scatterplots can be extended to a generalized pairs plot \citep{emerson:2013} that includes all pairwise combinations of features.
-Generalized pairs plots (and scatterplot matrices in general) have diminishing value when the number of features increase \citep{jensen:2011} \citep{sweller:2011}.
-Machine learning models are commonly fit using a large number of features, and therefore, a generalized pairs plot of explanation scatterplots for all features would be ineffective.
-However, when applying LIME, the user selects the number of features to return in the explanation.
-In the \emph{lime} R package, \citet{pedersen:2020} encourage users to select less than 10 features.
-As long as a small number of features are returned in the LIME explanation,  it is feasible to use a generalized pairs plot of explanation scatterplots.
-An example is shown in Section~\ref{bullet-assess-ex}.
-
-\subsection{Feature Heatmap} \label{feat-heat}
-
-Explanations produced by LIME are likely to be affected by the choice of tuning parameter values.
-A hypothetical example of this is shown by Figures \ref{fig:figure-01} and \ref{fig:figure-02} where the method used to weight the observations influenced the explanation.
-As of the time of writing this manuscript, we have encountered no recommendations for how to specify the parameter values besides for the default settings in \emph{lime}.
-In order to compare the explanations produced by LIME using different tuning parameter values and provide another perspective for assessing localness, we visualize an overview of the explanations with the \emph{feature heatmap} diagnostic plot.
-
-The feature heatmap uses colors to identify the features selected by LIME across multiple predictions (referred to as cases here) and tuning parameter values organized by the feature importance assigned by LIME.
-That is, for LIME applied with $t$ sets of tuning parameter values to $n$ cases to select the $f$ top features, create $f$ heatmaps (one for each of the positions of importance determined by the magnitude of the explainer model coefficients) with the cases on the $y$-axis, the tuning parameter values on the $x$-axis, and the cells colored by the feature chosen for the corresponding case and tuning parameter value.
-Additional tuning parameters may also be included in the plot via facets.
-
-\kge{When interpreting feature heatmaps, horizontal lines of the same color represent the ideal situation where the explanations are consistent and do not depend on the tuning parameter values but do depend on the location of the observation in the feature space.
-Vertical lines of color represent explanations that are dependent on the tuning parameter values and may not be local since the same feature is chosen regardless of the location of the observation in the feature space.
-See Appendix \ref{feat-heat-ex} for hypothetical examples depicting feature heatmaps with the extreme cases of horizontal and vertical lines.}
-
-\begin{figure}[!tp]
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-
-{\centering \includegraphics[width=3.125in]{figure/figure-04-1}
-
-}
-
-\end{knitrout}
-\caption{\emph{Feature Heatmap}.
-An example feature heatmap of the explanations from the applications of LIME with different tuning parameter values to the \data \ test set.
-\sout{The cases from the test set are plotted on the y-axis, and the tuning parameter values (simulation methods here) are included on the x-axis.
-The colors of the tiles indicate the feature selected by LIME for the corresponding case and tuning parameter value.
-The plot is faceted by the first and second most important features selected by LIME (top and bottom facets, respectively).
-The vertical facets separate the kernel density method from the quantile bin methods.} The vertical striping indicates that the LIME explanations are not consistent across tuning parameter values.}
-\label{fig:figure-04}
-\end{figure}
-
-\sout{Two hypothetical examples of feature heatmaps are included in \autoref{fig:figure-04}.
-The plots are created with the assumption that LIME is applied to select the top feature out of $p=4$  features for $n=10$ cases with $t=5$ sets of tuning parameter values.
-Situation 1 is an example where the features selected are consistent across tuning parameter values within a case but vary across cases within a tuning parameter value.
-This is the ideal situation, because the LIME explanations do not depend on the tuning parameters but do depend on the location of the observation in the feature space.
-Situation 2 is an example where the selected features vary across tuning parameter values within a case but are consistent across cases within a tuning parameter value.
-This situation indicates that the features selected by LIME are dependent on the tuning parameters, and the explanations may not be  local, because the same feature is chosen regardless of the case.
-In practice, it is expected that the plot will exhibit a combination of these two situations.}
-
-\autoref{fig:figure-04} shows a feature heatmap for the LIME applications to the 100 observations in the \data \ test set.
-The most important and second most important features selected by lime are shown in in the top and bottom facets, respectively.
-For the quantile bins, the original features prior to \kge{being converted to indicator variables} \sout{the indicator variable transformation} are included since it is obvious that different features would be selected when the sizes of the bins change.
-This figure shows that for kernel density and 2-quantile-bins, LIME \kge{produces global explanations since} \sout{selects} $x_1$ \kge{is selected} as the most important feature and $x_2$ \kge{is selected} as the second most important feature across all cases in the test set.
-\sout{These explanations are not local.} There is variability in the features selected by LIME for 3- to 6-quantile-bins suggesting more local explanations.
-There are signs of vertical striping, which suggests a dependence on tuning parameters.
-Note that the explanations from 3- and 5-quantile-bins include the selection of the random noise variable ($x_3$) as an important variable in many predictions, which \kge{would not be expected to be important to a random forest}\sout{should not be the case}.
-\kge{It is unclear whether the random forest is using a variable that would not be expected to be important or LIME is incorrectly identifying the important variable when 3- and 5- quantile bins are used.} \sout{The pattern seen in the explanations for 3- to 6-quantile-bins may suggest local explanations, but the dependence on tuning parameters makes it unclear which set of explanations to use.}
-
-\subsection{Assessment Metric Plot} \label{assess-metric}
-
-The feature heatmap for the \data \ in the previous section shows an example of inconsistent LIME explanations across tuning parameter values.
-In this situation, the user must determine which set of explanations to trust.
-One way to do this is to compute assessment metrics for each set of explanations to identify the optimal tuning parameter values.
-We discuss three metrics for this purpose and present a visual comparison in an \emph{assessment metric plot}.
-
-Each metric presented below is computed on LIME explanations for a set of predictions obtained using the same tuning parameter values.
-Here we provide a high level description of the metrics.
-Notation and formulas for these metrics are included in Appendix \ref{metric-details}.
-
-\begin{itemize}
-\item \emph{Average $R^2$}: Assess the model fit and linearity claim by computing the average of the explainer model $R^2$ values (deviance ratios from the R package \emph{glmnet}).
-
-\item \emph{Average Fidelity}: Measures the faithfulness of the explainer model to the complex model by comparing their predictions.
-Computed as the average of the explainer model fidelity metrics: a metric presented in \citet{ribeiro:2016} (the weighted distance between explainer and complex model predictions for all observations in the LIME simulated data associated with an individual prediction of interest).
-
-\item \emph{Mean Squared Explanation Error (MSEE)}: Also measures the faithfulness of the explainer model to the complex model by comparing their predictions, but only the prediction of interest is used to compute an average squared deviation between explainer and complex model predictions.
-\end{itemize}
-
-\begin{figure}[!tp]
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-
-{\centering \includegraphics[width=3.25in]{figure/figure-05-1}
-
-}
-
-\end{knitrout}
-\caption{\emph{Assessment metric plot}.
-The assessment metrics computed on the applications of LIME to the \data \ test set are included in this example assessment metric plot.
-\sout{Each horizontal facet corresponds to one of three metrics: average $R^2$, average fidelity, or MSEE.
-The LIME tuning parameter values (simulation methods in this example) are plotted on the x-axis, and the metric values are shown on the y-axis.
-The points are colored by rank (within a metric) indicating best to worst (dark to light).} The kernel density simulation methods performs well across all three metrics.}
-\label{fig:figure-05}
-\end{figure}
-
-\autoref{fig:figure-05} shows an example assessment metric plot.
-The three metrics are computed for each of the LIME applications to the \data \ test set.
-The simulation methods are listed on the x-axis.
-The plot is faceted by metric, and the metric values are plotted on the y-axis.
-The colors of the points represent the rank of the simulation methods performance based on a particular metric (darker indicates a better metric value and lighter indicates a worse metric value).
-Higher average $R^2$ values are better, and lower average fidelity and MSEE values are better.
-This example only includes one tuning parameter: the simulation method.
-If more than one tuning parameter is considered, the assessment metric plot is extended by adding additional facets or levels to the x-axis.
-
-All three metrics suggest that the kernel density method performed well, but the metrics disagree for the quantile bins methods.
-Average $R^2$ and average fidelity rank the performance of the number of quantile bins the same (2-quantile-bins perform the best and 6-quantile-bins perform the worst).
-In fact, these two metrics appear to have a mirrored  relationship in this example.
-MSEE provides almost the exact opposite results with  6-quantile-bins performing the best and 2-quantile-bins performing the worst.
-Average fidelity and MSEE are similar metrics, so it is \sout{not} surprising that they would \kge{not} agree in this example\kge{, but it may be becuase} \sout{.
-Another factor might be that} MSEE only takes the prediction of interest into account and not the full simulated dataset.
-The contradiction between metrics makes it difficult to identify which simulation method to trust.
-\kgc{I missed this reading through the manuscript before submission, but at some point the text above was changed to say that the "Average fidelity and MSEE are similar metrics, so it is not surprising that they would agree in this example." It should be as I have it now since they don't agree.}
-
-Recall that \autoref{fig:figure-04} indicated that the kernel density method selected the same feature across all cases in the test set for both the first and second features.
-It appears that a global trend may be the best explanation for this example, which may be reasonable considering that we \kge{would expect that} \sout{know that} both $x_1$ and $x_2$ \kge{would be} \sout{are} the two features that should \sout{be the features} used by the random forest to distinguish between response categories.
-\kge{However, futher exploration of individual explanations using explanation scatterplots may help to identify the tuning parameter values considered here that produce the most trustworthy explanations.}
-
-\section{Application to Bullet Matching Data} \label{application}
-
-In this section, we provide a discussion of the application of the visual diagnostics for LIME explanations to a practical data problem investigating the similarity of marks on fired bullets.
-
-\subsection{Bullet Matching Data}
-
-In current practice, forensic firearm examiners evaluate whether two bullets are from the same source (fired from the same gun) or from different sources based on microscopic comparison of the striation patterns engraved on bullets during the firing process (see \autoref{fig:figure-06}).
-The process is based on a visual and therefore subjective assessment of the evidence.
-The lack of objective evaluation and the associated absence of established error rates has first been criticized by the National Research Council \cite{nrc:2009} and later by the President's Council of Advisors on Science and Technology \cite{pcast:2016}.
-
-In response, \citet{hare:2017} proposed an automated machine learning method for bullet matching to complement a visual inspection by firearm examiners.
-Based on high-resolution topological scans of land engraved areas, \citet{hare:2017} obtain signatures of striations from two bullet lands (\autoref{fig:figure-07}).
-Nine features quantifying the similarity of signatures, such as the cross-correlation function, the distance between signatures, and the number of matching striae, are extracted and used to train a random forest to determine the probability of a comparison resulting from the same source (matching signatures) or from different sources (non-matching signatures).
-The model in \citet{hare:2017} was trained on a set of scans of bullets from the James Hamby Consecutively Rifled Ruger Barrel Study \citep{hamby:2009}, which included 10,384 land-to-land comparisons \citet{hare:2017}.
-See the supporting information for additional information on the signature similarity features.
-
-\begin{figure}[!t]
-\centering
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-
-{\centering \includegraphics[width=2.25in]{figure-static/figure-06-1}
-
-}
-
-\end{knitrout}
-\caption{(Top left) Traditionally rifled gun barrel.
-The grooves and lands alternate to give bullets a spin during the firing process, which create markings (striations) on a bullet when fired.
-(Top right) Image of a fired bullet.
-The vertical stripes along the lower half of the bullet show groove and land engraved areas.
-The land engraved areas contain the microscopic striations created when the bullet passed through the barrel of the gun.
-(Bottom) Close up of a land engraved area showing striations (vertical lines).}
-\label{fig:figure-06}
-
-\vspace*{\floatsep}
-
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-
-{\centering \includegraphics[width=3.125in]{figure/figure-07-1}
-
-}
-
-\end{knitrout}
-\caption{Example bullet signatures.
-The bullet signatures correspond to the same land and therefore have very similar patterns.
-The \citet{hare:2017} random forest is fit using various features that measure the similarity between two such signatures.}
-\label{fig:figure-07}
-\end{figure}
-
-\subsection{Application of LIME to Bullet Matching Data}
-
-\begin{figure*}[!thp]
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-
-{\centering \includegraphics[width=6.5in]{figure-static/figure-08-1}
-
-}
-
-\end{knitrout}
-\caption{Parallel coordinate plots of the \citet{hare:2017} random forest predictions from the training (top facet) and testing (bottom facet) data.
-The observations are separated by known matching (right column) and non-matching (left column) signatures.
-The y-axis shows the standardized feature values, and the x-axis shows the features used to fit the random forest (ordered by random forest impurity based feature importance).
-Each line corresponds to an observation, and the line color represents the associated random forest probability.
-There are clear relationships between the feature values and the random forest probabilities.}
-\label{fig:figure-08}
-\end{figure*}
-
-Since firearm identification is commonly used as evidence for convictions in court cases, it is important to be able to understand and assess a model used to quantify the probability that a bullet is fired from a gun.
-LIME explanations would provide a local explanation for an individual prediction, but just as it is important to assess the model for this high-stakes application, it is also important to assess the LIME explanations.
-We will demonstrate an assessment of LIME explanations using the visual diagnostics introduced in this paper.
-
-A random forest model fit to an expanded dataset of 83,028 land-to-land comparisons from two sets of bullets in the James Hamby Consecutively Rifled Ruger Barrel Study \citep{hamby:2009} was validated in \citet{vanderplas:2020}.
-Here, we train a random forest model to mimic the model validated in \citet{vanderplas:2020} using the same data, model structure, and features (the nine similarity measures developed in \citet{hare:2017}).
-We apply the trained random forest model to 6 bullets from another set of the Hamby study with 364 rows of land comparisons.
-See the supporting information for further descriptions of the data.
-
-The newly trained random forest has an out-of-bag accuracy of 1 and out-of-bag false positive and false negative rates of 0.3 and \ensuremath{2\times 10^{-4}}, respectively.
-On the test data, the random forest performance decreases with an accuracy of 0.85 and false positive and false negative rates of 0.55 and 0.011, respectively.
-This is an example where explanations of the model predictions could provide insight to the cause of the decrease in model performance on the test data.
-
-We consider a global visualization of the relationship between the random forest predictions and the model features with a parallel coordinate plot of the training data (top facet) and testing data (bottom facets)  (\autoref{fig:figure-08}).
-In the training data we observe a clear difference in feature values based on whether the corresponding random forest scores are close to 1 or 0.
-High values of rough correlation, cross correlation function, and number of matches are indicative of random forest scores close to 1; similarly, low values of mismatches, distance, and non-consecutively matching striae are also associated with random forest scores close to 1.
-Observations in the test data that are classified incorrectly by the random forest tend to have feature values similar to observations in the training data with similar random forest scores.
-For example, the observations in the test set known to be a match but have a random forest score below 0.5 have relatively low values of rough correlation, cross correlation function, and matches and relatively large values of mismatches, distance, and non-consecutively matching striae compared to observations with a random forest probability close to 1.
-
-LIME is applied to all test set observations using different tuning parameter values: 12 sampling methods (2 to 6 equally spaced bins, 2 to 6 quantile-bins, kernel density estimation, and normal approximation) and 3 Gower exponents (0.5, 1, and 10).
-Thus, a total of $12\times 3=36$ different applications of LIME are performed.
-We specify that each LIME explanation return 3 features, and feature selection is performed using the default option in LIME, which selects the features with the highest weights in a ridge regression model.
-
-\subsection{LIME Assessment Visualizations} \label{bullet-assess-ex}
-
-To get an overview of the LIME explanations from the 36 applications, we consider a feature heatmap (\autoref{fig:figure-09}).
-In addition to facets for simulation method and LIME feature importance, this plot includes a vertical facet for Gower power and a horizontal facet for whether the observation is a known match or non-match.
-This plot highlights several key features of the LIME explanations from the bullet matching dataset.
-
-First, applications of 2-quantile-bin simulations produce the same explanations for almost all cases and LIME tuning parameter values.
-This suggests that the LIME explanations are global and not local.
-Second, within a simulation method, the features selected by LIME for an observation do not appear to vary by the Gower power.
-However, the LIME explanation for an observation often varies across simulation methods.
-With the equal-bins, there are vertical stripes that suggest a dependence of the LIME explanations on the number of bins.
-The vertical stripes are not as apparent with the quantile bins.
-Lastly, there are clear differences between the LIME explanations produced by the bin based simulation methods for the matches and non-matches.
-This suggests that different features are of importance in the random forest, depending on whether the observation corresponds to match or non-match.
-
-\begin{figure*}[!thp]
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-
-{\centering \includegraphics[width=6.5in]{figure/figure-09-1}
-
-}
-
-\end{knitrout}
-\caption{Feature heatmap of 36 LIME applications to the bullet comparison data test set.
-In addition to faceting the results by simulation method and LIME feature selection order, facets for the Gower power and whether the observation is a match or non-match are included.
-The vertical stripes of features selected indicate a dependence between the LIME explanations and tuning parameter values.}
-\label{fig:figure-09}
-
-\vspace*{\floatsep}
-
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-
-{\centering \includegraphics[width=6.5in]{figure/figure-10-1}
-
-}
-
-\end{knitrout}
-\caption{Assessment metric plot for the applications of LIME on the bullet comparison data test set.
-There are discrepancies in performance across metrics for a set of tuning parameter values, but based on the overall performance of all three metrics, 4-equal-bins with a Gower power of 0.5 appears to perform the best.}
-\label{fig:figure-10}
-\end{figure*}
-
-To try to identify a set of LIME tuning parameter values with the most trustworthy set of explanations, an assessment metric plot is considered (\autoref{fig:figure-10}).
-The performance of a set of tuning parameter values often do not agree across metrics.
-For example, both density methods perform well according to average fidelity but poorly according to MSEE.
-All quantile bin methods perform well according to average $R^2$ but poorly based on average fidelity and MSEE.
-However, there is consistency in results across different Gower powers.
-The applications using a power of 0.5 perform the best or as well as the other powers across all simulation methods suggesting that the power that leads to a more global explanation is preferred by LIME.
-It is not apparent which set of tuning parameters is the best.
-Considering all three metrics, we might conclude that the 4-equal-bins with a Gower power of 0.5 performs better than the other tuning parameter values considered.
-
-To provide a more detailed view of explanations obtained using different tuning parameter values, we take a closer look at explanations for two observations of interest, which will be referred to as case M (a known match) and case NM (a known non-match), using explanation scatterplots.
-Figure~\ref{fig:figure-11} includes the visual representation plots of explanations (from \emph{lime}) and explanation scatterplots for cases M and NM.
-Plots for 4-equal-bins and 4-quantile-bins are included to depict tuning parameter values with good (4-equal-bins) and mediocre (4-quantile-bins) performance based on the assessment metric plot.
-Plots for the kernel density simulation method are included in Appendix~\ref{exp-scatter_plus} (Figure \ref{fig:figure-B2}).
-
-We focus on the explanation for case NM with 4-quantile-bins.
-The explanation plot from \emph{lime} shows that the observed values of NM of mismatches less than or equal to 7.17, rough correlation (rough\_cor) greater than 0.05, and D less than or equal to 0.002 support a random forest prediction in favor of a match.
-The scatter plots show that many of the simulated values in the rectangular regions with mismatches less than 7.17, rough correlation greater than 0.05, and distance less than or equal to 0.002 have random forest predictions greater than 0.5, which agrees with the LIME explanation.
-However, the random forest assigns a probability of 0.21 to case NM, which is not explained by the LIME explanation that provides all explanations in support of a match.
-Instead, consider that a better explanation based on the scatterplots would be that the random forest assigned a prediction probably below 0.5 since NM has observed values of mismatches less than 5, rough correlation greater than 0.25, and distance greater than 0.001.
-
-The other explanation scatterplots can be interpreted in a similar manner.
-The three plots depict situations where the explanations are faithful to the random forest, but the regions captured by the intersections of the bins do not align well with the regions containing similar probabilities produced by the random forest.
-
-\begin{figure*}[!thp]
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-
-{\centering \includegraphics[width=6.25in]{figure/figure-11-1}
-
-}
-
-\end{knitrout}
-\caption{Plots of LIME explanations (first row) and explanation scatterplots (second row) for case NM in the bullet test data for two tuning parameter values: 4-quantile-bins (first column) and 4-equal-bins (second column).
-The plots provide insights into the LIME explanations and allow for the assessment of the explanation quality.}
-\label{fig:figure-11}
-\end{figure*}
-
-Without applying LIME with multiple tuning parameter values to the bullet test data or viewing diagnostic plots of the LIME explanations, it may be very possible to formulate reasons why the LIME explanations make sense.
-However, the sequence of plots in this section (Figures \ref{fig:figure-09}, \ref{fig:figure-10}, and \ref{fig:figure-11}) suggest that we should be cautious to trust any of these LIME explanations.
-It appears that either LIME needs to be further tuned to provide trustworthy and good explanations, or a different approach may provide better insight.
-
-\section{Discussion} \label{discussion}
-
-This paper highlights that while an explainer model is meant to provide clarity, it actually adds another layer of complexity to predictive models by requiring yet another model that needs to be assessed.
-Without an assessment of the explainer model, LIME is a black-box procedure of its own requiring blind trust in the explainer model.
-We suggest the use of visual diagnostics to counteract the black-box nature of LIME and provide three diagnostic plots.
-
-The visualizations are intended to provide insight on how LIME works, assess the ability of the explainer model to capture the complex predictive model, and compare LIME explanations produced by different tuning parameter values.
-While the visualizations accomplish these tasks, they also expose examples of the failings of LIME.
-To address the discovered failings of LIME, we reconsider each of the claims about the performance of LIME made by \citet{ribeiro:2016} in light of the insights gained from the diagnostic visualizations.
-
-As previously discussed, the \textbf{interpretability} of the LIME explanations is controllable  by the complexity of the explainer model.
-For example, the number of bins selected for simulation can control the interpretability of the explanations.
-If too many bins are selected, the bin range that is reported in the LIME explanation will be too small to be meaningful in the context of the feature.
-An appropriate choice of the number of bins will keep the bin range meaningful.
-Thus, the claim of interpretability does not need to be assessed using the visualizations.
-However, diagnostic visualizations do present a different perspective on the meaning of interpretability.
-
-Even though an explanation will be interpretable as long as the complexity of the explainer model is appropriately chosen, a lack of understanding of the process used to create the explanation could lead to an incorrect interpretation of the explanation.
-For example, the visualization of a LIME explanation available from the \emph{lime} R package \citep{pedersen:2020} (shown in Figures \ref{fig:figure-03} and \ref{fig:figure-11}) is a major simplification of the explainer model, which could lead to under-interpreted or misinterpreted LIME explanation.
-Supplementing \citet{pedersen:2020}'s compact visualization of the explanation with an explanation scatterplot that shows a more detailed visualization of the explainer model promotes a more complete understanding of the explanation (such as Figures~\ref{fig:figure-03} and \ref{fig:figure-11}).
-
-Even with an explainer model that is interpreted correctly, the interpretation is worthless if the explainer model is not \textbf{faithful} to the complex model.
-This claim can be assessed using the diagnostic plots suggested in this paper.
-Many of the visualizations in this paper highlight problems with the faithfulness of the explainer models.
-The explanation scatterplots allow for a comparison of the explainer model to the complex model.
-The examples in this paper show cases where the explainer model bins do not accurately capture the regions with similar random forest probabilities that contain the prediction of interest and oversimplify the model (Figures \ref{fig:figure-03} and \ref{fig:figure-11}).
-Using fewer bins would clearly not help improve the faithfulness of the explainer model in these examples, and while an increase in the number of bins would lead to a finer resolution of the random forest classification boundaries, interpretability of the explainer model would quickly be lost.
-Perhaps this could be improved by allowing the bin creation to account for the relationships between the features and response variable or a different number of bins for each feature.
-
-In addition to assessing faithfulness by visually comparing the complex and explainer model, we propose a visual comparison of two faithfulness metrics (MSEE and average fidelity).
-The examples of faithfulness metric comparisons in this paper both produced conflicting results (Figures \ref{fig:figure-05} and \ref{fig:figure-10}).
-This makes it difficult to decide on a recommendation of a set of tuning parameter values that produce the explanations with the most faithful explainer model.
-
-The metric comparison plot also includes a comparison of average $R^2$ values, which is a metric that can be used to assess the claim of \textbf{linearity}.
-Most of the average $R^2$ values in the examples from this paper are below 0.5 suggesting a poor linear fit of the explainer models.
-A poor linear fit of the explainer model is also seen with the residual plot (\autoref{fig:figure-C3}).
-
-The final claim, \textbf{localness}, is addressed by the feature heatmap and metric comparison plots.
-As stated, the feature heatmap reveals that the density simulation methods in the \data \ example  results in global explanations where the same features are repeatedly chosen across all (or almost all) observations in the set of explanations.
-This finding agrees with that of \citet{laugel:2018} who found LIME produced global explanations with the normal approximation simulation method.
-For the bin based simulation methods in the bullet data example, the feature heatmap shows that the features chosen for the explanations vary between the two classification categories (match versus non-match).
-This is an interesting finding that suggests that different features can play a role in the predictions of observations in different response categories.
-Furthermore, while the metric comparison plot in the bullet example does not provide agreement between metrics on a best bin based method, all metrics agree that a Gower power of 0.5 for computing the model weights associated with distance of a simulated data point from the prediction of interest is the best.
-This suggests that a less local explanation provides a better explanation of the performance of the random forest.
-
-Some of the visualizations in the paper generalize easily to any application of LIME such as the feature heatmap and metric plot.
-Other plots such as the visualizations of the LIME procedure would require extensions such as the use of scatterplot matrices to compare explanations with more than two features.
-The addition of interactivity to the diagnostic plots would provide additional enhancement of the assessment process.
-For example, a diagnostic plot that provides a summary of multiple LIME explanations, such as the feature heatmap, could be displayed and clicked on to reveal more detailed figures associated with individual predictions of interest, such as an explanation scatterplot.
-
-The largest limitation to the diagnostic visualizations is the dimensionality of the data shown, both in the number of dimensions or features as well as the number of observations.
-Fortunately, in the situation of LIME, both of these aspects are rather well controlled: LIME relies heavily on simulations to generate data scenarios that are close to the data observed but exhibit variability.
-Effects from overplotting should be relatively mild, because output from simulations is shown, which is expected to be (relatively) continuous such that overplotting only occurs for points with (relatively) similar values.
-In that respect, the diagnostics shown for the \data \ and the bullet example are representative of what is expected.
-But in cases where overplotting does become problematic, the user could either simply reduce the size of the simulations or use some well-studied binning techniques in the visualizations, as discussed for example in \citet{carr:1987} or \citet{unwin:2006}.
-
-While it would be ideal if LIME could be used as a method to provide easily understandable explanations for black-box models as \citet{ribeiro:2016} claim, that dream is not yet a reality.
-The examples using diagnostic plots to assess LIME in this paper show frequent issues with LIME.
-We hope that our plots provide motivation to assess LIME explanations, to not blindly use the default settings (even if it is not clear how to tune the parameters), and to encourage work on improving LIME, so that it can be a lime and not a lemon.
-
-\section*{Acknowledgments}
-
-HH was partially funded by the Center for Statistics and Applications in Forensic Evidence (CSAFE) through Cooperative Agreement 70NANB20H019 between NIST and Iowa State University, which includes activities carried out at Carnegie Mellon University, Duke University, University of California Irvine, University of Virginia, West Virginia University, University of Pennsylvania, Swarthmore College and University of Nebraska, Lincoln.
-
-\subsection*{Author contributions}
-
-{\bf Katherine Goode, Heike Hofmann}: Conceptualization, Methodology, Investigation, Visualizations, Writing - Reviewing and Editing. {\bf Katherine Goode}: Writing - Initial Draft, Software.
-
-\subsection*{Financial disclosure}
-
-None reported.
-
-\subsection*{Conflict of interest}
-
-The authors declare no potential conflict of interests.
-
-\section*{Supporting information}
-
-The code used to produce the manuscript and the data from examples in Section \ref{application} are available in the following GitHub Repository: \href{https://github.com/goodekat/LIME-diagnostics-paper}{https://github.com/goodekat/LIME-diagnostics-paper}.
-
-\bibliography{references}
-
-\newpage
-
-\appendix
-
-\section{LIME Tuning Parameter Options} \label{lime-details}
-
-The following tuning parameters for the LIME algorithm are available in the \emph{lime} R package \citep{pedersen:2020}.
-
-\begin{itemize}
-
-\item Data simulation methods:
-
-\begin{itemize}
-\item Equally spaced bins: observations are uniformly sampled from equally spaced bins (number of bins may be specified)
-\item Quantile bins: observations are uniformly sampled from quantile bins (number of bins may be specified)
-\item Normal density approximation: observations are sampled from a normal distribution with mean and standard deviation computed from the corresponding feature
-\item Kernel density approximation: observations are sampled from an kernel density approximation of the corresponding feature
-\end{itemize}
-
-\item Number of observations to simulate
-
-\item Distance metric for determining proximity to the prediction of interest: Gower distance (where the power may be specified) or exponential kernel (where the kernel width may be specified)
-
-\item Number of features to return in an explanation
-
-\item Feature selection method for determining the features to return in an explanation: forward selection applied to a ridge regression, features with the largest magnitude coefficients in ridge regression, LASSO, classification/regression tree splits
-
-\end{itemize}
-
-\section{Explanation Scatterplots Under Other Simulation Scenarios} \label{exp-scatter_plus}
-
-\begin{figure*}[!thp]
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-
-{\centering \includegraphics[width=6.5in]{figure/figure-B1-1}
-
-}
-
-\end{knitrout}
-\caption{Explanation scatterplots for the \data \ prediction of interest with the kernel density simulation method.}
-\label{fig:figure-B1}
-\end{figure*}
-
-\begin{figure*}[!thp]
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-
-{\centering \includegraphics[width=6.5in]{figure/figure-B2-1}
-
-}
-
-\end{knitrout}
-\caption{Explanation scatterplots for LIME explanations using kernel density simulation for the cases M and NM of the bullet comparison test data.}
-\label{fig:figure-B2}
-\end{figure*}
-
-Section \ref{exp-scatter} introduces explanation scatterplots under the default simulation method in the \emph{lime} R package: 4-quantile-bins.
-The structure of an explanation scatterplot remains the same if any bin based simulation method is used, i.e., any number of quantile or equally spaced bins.
-However, if the kernel density or normal approximation simulation methods are used, the format of the explanation scatterplot changes.
-In the density based simulation method scenarios, LIME uses the standardized versions of the predictor variables to fit the explainer model.
-Thus, the explainer model needs to be represented differently in the explanation scatterplot.
-
-When the kernel density or normal approximation simulation methods are applied, the explanation scatterplot depicts the complex model by plotting the complex model predictions versus a feature selected in LIME the explanation from the simulated data.
-The explainer model is included as a line on the figure where all features excluding the one plotted on the x-axis are set to the observed values of the prediction of interest.
-An explanation scatterplot is created for each feature included in the LIME explanation.
-As with the bin based simulation method, the size of the points represent the weight assigned by LIME.
-
-Figure \ref{fig:figure-B1} provides example explanation scatterplots for each feature in the default LIME explanation obtained using the kernel density simulation method for the \data \ prediction of interest.
-Figure \ref{fig:figure-B2} includes explanation scatterplots for the explanations generated using kernel density simulation for the bullet example cases M and NM discussed in Section \ref{bullet-assess-ex}.
-
-\section{Explainer Model Residual Plot} \label{residual-plot}
-
-In order to assess the claim of linearity for the \data \ prediction of interest discussed in Section \ref{exp-scatter}, we use one of the most basic diagnostics in a statistician's tool box and draw a residual plot for the explainer model.
-This is shown in Figure \ref{fig:figure-C3} with the explainer model residuals on the y-axis and explainer model predictions on the x-axis.
-The points along the x-axis have been jittered to ease the effect of the over-plotted points in the visualization.
-There is a clear increasing trend in the residuals as the explainer model predictions increase.
-This is a clear violation of the linearity assumption with the ridge regression model.
-
-\begin{figure}[!thp]
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-
-{\centering \includegraphics[width=3.125in]{figure/figure-C3-1}
-
-}
-
-\end{knitrout}
-\caption{Residual plot of the explainer model associated with \data \ prediction of interest from Section \ref{exp-scatter}.
-The residuals are plotted against the predicted values.
-The points are jittered in the x-direction to alleviate the over-plotting of points.
-There is an upward trend in the residuals as the explainer model predictions increase, which suggests a violation of the linearity assumption.}
-\label{fig:figure-C3}
-\end{figure}
-
-\section{Extreme Feature Heatmap Scenarios} \label{feat-heat-ex}
-
-Two hypothetical examples of feature heatmaps are included in \autoref{fig:figure-D4}.
-The plots are created with the assumption that LIME is applied to select the top feature out of $p=4$  features for $n=10$ cases with $t=5$ sets of tuning parameter values.
-Situation 1 is an example where the features selected are consistent across tuning parameter values within a case but vary across cases within a tuning parameter value.
-This is the ideal situation, because the LIME explanations do not depend on the tuning parameters but do depend on the location of the observation in the feature space.
-Situation 2 is an example where the selected features vary across tuning parameter values within a case but are consistent across cases within a tuning parameter value.
-This situation indicates that the features selected by LIME are dependent on the tuning parameters, and the explanations may not be  local, because the same feature is chosen regardless of the case.
-In practice, it is expected that the plot will exhibit a combination of these two situations.
-
-\begin{figure}[!thp]
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-
-{\centering \includegraphics[width=3.125in]{figure/figure-D4-1}
-
-}
-
-\end{knitrout}
-\caption{Hypothetical examples of feature heatmaps in two possible situations.
-The heatmaps show the top feature chosen for 10 cases across 5 different sets of tuning parameter values.
-The color of the cell indicates the feature chosen by LIME.
-Situation 1 is the ideal, because the explanations vary across cases but do not dependent on specific tuning parameter values.}
-\label{fig:figure-D4}
-\end{figure}
-
-\section{Details on Assessment Metrics} \label{metric-details}
-
-Suppose $f$ is a complex model, and let $\textbf{X}$ be a matrix of observed data with $K$ features and $E$ observations where $x_e$ is an observed feature vector for observation $e$.
-Let $f(x_e)$ be the complex model prediction for observation $e$.
-It is of interest to explain the predictions made by $f$ applied to $X$ using LIME.
-
-For $x_e$ and a set of tuning parameter values $t$, let $\textbf{X}_{e,t}'$ be the LIME simulated dataset with $K$ features and $S$ rows such that $x'_{e,t,s}$ is the feature vector for simulated data point $s$ corresponding to explanation $e$ and tuning parameter values $t$.
-Let $\textbf{Z}'_{e,t}$ be the matrix of simulated data transformed to bin indicator variables (for bin based simulation methods) or standardization (for density based simulation methods) with $K$ features and $S$ observations such that $z'_{e,t,s}$ is the interpretability transformed feature vector for explanation $e$, tuning parameter values $t$, and simulated data point $s$.
-Note that $z_{e,t}$ will represent the  transformed version of $x_e$.
-
-Next, let $\omega_t$ represent a proximity distance metric corresponding to tuning parameter values $t$.
-Then $\omega_t\left(x_e, x'_{e,t,s}\right)$ is the weight assigned to $x'_{e,t,s}$, which is the proximity between $x_e$ and $x'_{e,t,s}$.
-Allow $g_{e,t}$ to be the explainer model for an explanation $e$ and tuning parameter values $t$.
-Thus, $g_{e,t}\left(z'_{e,s,t}\right)$ is the explainer model prediction for the interpretability transformed simulated data point $s$.
-
-For a set of $E$ explanations and a set of tuning parameter values $t$, we define the assessment metrics as follows:\\
-\\
-\emph{Average $R^2$} is denoted as $R^2_{\mbox{ave}}$ and computed as
-
-  $$R^2_{\mbox{ave}} = \frac{1}{E}\sum_{e=1}^E R_{e,t}^2$$
-
-\noindent where $R_{e,t}^2$ is the $R^2$ value for $g_{e,t}$.\\
-\\
-\emph{Average fidelity} is denoted by $\mathcal{L}_{\mbox{ave}}$ and computed as
-
-\begin{eqnarray*} \mathcal{L}_{\mbox{ave}} & = & \frac{1}{E}\sum_{e=1}^E\mathcal{L}(f, \ g_{e,t}, \ \pi_{t}) \\ & = & \frac{1}{E}\sum_{e=1}^E\sum_{s=1}^{S}\omega_{t}\left(x_e, x'_{e,t,s}\right)\left(f\left(x'_{e,t,s}\right)-g_{e,t}\left(z_{e,t,s}'\right)\right)^2.
-\end{eqnarray*}
-
-\noindent where $\mathcal{L}$ is the fidelity metric originally defined in \citet{ribeiro:2016}.\\
-\\
-\emph{Mean squared explanation error} is denoted by MSEE and computed as
-
-$$MSEE=\frac{1}{E}\sum_{e=1}^E\left(f\left(x_e\right)-g_{e,t}\left(z_{e,t}\right)\right)^2.$$
-
-\section{Matching Bullets Explanation Scatterplots} \label{match-bullets}
-
-\begin{figure*}[!thp]
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-
-{\centering \includegraphics[width=6.25in]{figure/figure-e5-1}
-
-}
-
-\end{knitrout}
-\caption{Plots of LIME explanations (first row) and explanation scatterplots (second row) for case M in the bullet test data for two tuning parameter values: 4-quantile-bins (first column) and 4-equal-bins (second column).
-The plots provide insights into the LIME explanations and allow for the assessment of the explanation quality.}
-\label{fig:figure-e5}
-\end{figure*}
-
-\end{document}
+\begin{Schunk}
+\begin{Sinput}
+> # Specify the figure size (for determining font size)
+> f1_ow = 6.5
+> f1_fw = 7.95
+> f1_fs = fs * (f1_fw / f1_ow)
+> # Plot of good explainer model
+> ggplot() +
++   facet_grid(. ~ case) +
++   geom_point(
++     data = concept_data_long,
++     mapping = aes(
++       x = feature,
++       y = prediction,
++       fill = poi,
++       color = poi,
++       shape = poi,
++       alpha = poi,
++       size = weight
++     )
++   ) +
++   geom_abline(
++     data = coefs_data,
++     mapping = aes(intercept = b0, slope = b1),
++     size = 1
++   ) +
++   scale_fill_manual(values = c("#FAAA72", "grey30")) +
++   scale_color_manual(values = c("grey30", "grey30")) +
++   scale_alpha_manual(values = c(0.75, 0.6)) +
++   scale_shape_manual(values = c(23, 21)) +
++   geom_text(
++     data = coefs_data,
++     mapping = aes(x = feature,
++                   y = prediction,
++                   label = text),
++     family = ff,
++     size = f1_fs / 2.85
++   ) +
++   labs(x = "Black-Box Model Feature",
++        y = "Black-Box Prediction",
++        size = "Weight", 
++        fill = "", 
++        color = "",
++        alpha = "",
++        shape = "") +
++   theme_linedraw(base_family = ff, base_size = f1_fs) +
++   theme(
++     panel.grid.major = element_blank(),
++     panel.grid.minor = element_blank(),
++     axis.text.x = element_blank(),
++     axis.ticks.x = element_blank(),
++     axis.text.y = element_blank(),
++     axis.ticks.y = element_blank(),
++     strip.placement = "outside",
++     strip.background = element_rect(color = "white", fill = "white"),
++     strip.text.x = element_text(size = f1_fs, color = "black"),
++     plot.title = element_text(size = f1_fs)
++   ) +
++   guides(
++     fill = guide_legend(order = 1, override.aes = list(size = 5)),
++     color = guide_legend(order = 1),
++     shape = guide_legend(order = 1),
++     alpha = guide_legend(order = 1),
++     size = guide_legend(
++       order = 2,
++       override.aes = list(color = "grey30", alpha = 0.6)
++     )
++   )
+> 
+> # # Plot of good explainer model
+> # ggplot() +
+> #   facet_grid(. ~ feature, switch = "x") +
+> #   geom_point(
+> #     data = lime_data_gathered %>% mutate(
+> #       feature = fct_recode(
+> #         feature,
+> #         "Feature 1 (standardized)" = "Feature 1",
+> #         "Feature 2 (standardized)" = "Feature 2"
+> #       )
+> #     ),
+> #     mapping = aes(
+> #       x = feature_stnd_value,
+> #       y = prediction,
+> #       size = distance_value,
+> #       color = distance
+> #     ),
+> #     alpha = 0.6
+> #   ) +
+> #   geom_abline(
+> #     data = coefs_data %>%
+> #       filter(case == "good") %>%
+> #       mutate(
+> #         feature = fct_recode(
+> #           feature,
+> #           "Feature 1 (standardized)" = "Feature 1",
+> #           "Feature 2 (standardized)" = "Feature 2"
+> #           )
+> #         ),
+> #     mapping = aes(intercept = int, slope = slope),
+> #     size = 1
+> #   ) +
+> #   scale_color_manual(values = c(NA, "grey30"), guide = "none") +
+> #   geom_point(
+> #     data = prediction_of_interest_gathered %>% mutate(
+> #       feature = fct_recode(
+> #         feature,
+> #         "Feature 1 (standardized)" = "Feature 1",
+> #         "Feature 2 (standardized)" = "Feature 2"
+> #       )
+> #     ),
+> #     mapping = aes(x = feature_value,
+> #                   y = prediction,
+> #                   fill = color),
+> #     color = "black",
+> #     size = 5,
+> #     shape = 23,
+> #     alpha = 0.75
+> #   ) +
+> #   scale_fill_manual(values = "#FAAA72") +
+> #   geom_text(
+> #     data = data.frame(
+> #       feature_stnd_value = 1.2,
+> #       prediction = 1.6,
+> #       feature = c("Feature 1 (standardized)", "Feature 2 (standardized)"),
+> #       slope = c(
+> #         paste(
+> #           "Slope:",
+> #           coefs_data %>%
+> #             filter(case == "good",
+> #                    feature == "Feature 1") %>%
+> #             pull(slope) %>%
+> #             round(3)
+> #         ),
+> #         paste(
+> #           "Slope:",
+> #           coefs_data %>%
+> #             filter(case == "good",
+> #                    feature == "Feature 2") %>%
+> #             pull(slope) %>%
+> #             round(3)
+> #         )
+> #       )
+> #     ),
+> #     mapping = aes(x = feature_stnd_value,
+> #                   y = prediction,
+> #                   label = slope),
+> #     family = ff,
+> #     size = f1_fs / 2.85
+> #   ) +
+> #   labs(
+> #     x = "",
+> #     y = "Black-Box Prediction",
+> #     title = "Conceptual Depiction of a Faithful Local Explainer Model",
+> #     subtitle = paste("Gower Distance Metric Exponent:", good_gower_power),
+> #     fill = "",
+> #     alpha = "Weight",
+> #     size = "Weight"
+> #   ) +
+> #   theme_linedraw(base_family = ff, base_size = f1_fs) +
+> #   theme(
+> #     panel.grid.major = element_blank(),
+> #     panel.grid.minor = element_blank(),
+> #     axis.text.x = element_blank(),
+> #     axis.ticks.x = element_blank(),
+> #     axis.text.y = element_blank(),
+> #     axis.ticks.y = element_blank(),
+> #     strip.placement = "outside",
+> #     strip.background = element_rect(color = "white", fill = "white"),
+> #     strip.text.x = element_text(size = f1_fs, color = "black"),
+> #     plot.title = element_text(size = f1_fs)
+> #   ) +
+> #   guides(
+> #     fill = guide_legend(order = 1),
+> #     size = guide_legend(order = 2),
+> #     alpha = guide_legend(order = 2)
+> #   )
+> 
+\end{Sinput}
+\end{Schunk}

### 2020-12-30 paper.Rnw
more color out

@@
 % Paper header (title and authors)
-\title{Visual Diagnostics of a\kge{n}  Explainer \kge{Model} -- Tools for the Assessment of LIME Explanations}
+\title{Visual Diagnostics of an  Explainer Model -- Tools for the Assessment of LIME Explanations}
 \author[1]{Katherine Goode*}
@@
 % Abstract and keywords
-\abstract[Abstract]{The importance of providing explanations for predictions made by black-box models has led to the development of \kge{explainer} model  methods such as LIME (local interpretable model-agnostic explanations).
+\abstract[Abstract]{The importance of providing explanations for predictions made by black-box models has led to the development of explainer model  methods such as LIME (local interpretable model-agnostic explanations).
 LIME uses a surrogate model to explain the relationship between predictor variables and predictions from a black-box model in a local region around a prediction of interest.
@@
 \cyear{2020},
-\ctitle{Visual Diagnostics of a\kge{n}  Explainer \kge{Model} -- Tools for the Assessment of LIME Explanations},
+\ctitle{Visual Diagnostics of an  Explainer Model -- Tools for the Assessment of LIME Explanations},
 \cjournal{Stat Anal Data Min: The ASA Data Sci Journal},
@@
 @
-\caption{\kge{Hypothetical scenarios depicting the effect of different weights on LIME.
+\caption{Hypothetical scenarios depicting the effect of different weights on LIME.
 (Left) An example of an explainer model with appropriate weights to provide a faithful approximation of the complex model.
-(Right) An example of an explainer model for the same prediction but with different weights that results in an explanation unfaithful to the complex model.}  }
+(Right) An example of an explainer model for the same prediction but with different weights that results in an explanation unfaithful to the complex model.
+}
 \label{fig:figure-01}
@@
 In the field of statistics, there are two main uses for models: inference and prediction.
-Machine learning models  have proven to perform well \kge{in problems with the latter objective} , but the accuracy of many machine learning models comes at the cost of interpretability due to their algorithmic complexity (hence the phrase "black-box models").
+Machine learning models  have proven to perform well in problems with the latter objective , but the accuracy of many machine learning models comes at the cost of interpretability due to their algorithmic complexity (hence the phrase "black-box models").
 Model interpretability allows for the understanding and assessment of how a model produces predictions.
-The lack of the ability to understand and assess a model makes it difficult to trust the model, especially in areas with high stakes decisions such as \kge{the} medical and forensics sciences.
+The lack of the ability to understand and assess a model makes it difficult to trust the model, especially in areas with high stakes decisions such as the medical and forensics sciences.
 The increased use of machine learning models in applications and the introduction of the General Data Protection Regulation (GDPR) in 2018 \citep{goodman:2016} has resulted in a dramatic increase in explainable machine learning research, which focuses on developing ways to explain output from machine learning algorithms.
@@
 \citep{fisher:2018} and \citep{strumbelj:2014}).
-In this paper, we focus on \kge{the}  model-agnostic method \kge{of} LIME \citep{ribeiro:2016}.
+In this paper, we focus on the  model-agnostic method of LIME \citep{ribeiro:2016}.
 
 LIME (local interpretable model-agnostic explanations)  uses a surrogate model to relate predictor variables to black-box model predictions  \citep{ribeiro:2016}.
-While some \kge{explainer} model\kge{s}  focus on understanding a model at the global level, LIME claims to provide explanations for individual predictions (local).
+While some explainer models  focus on understanding a model at the global level, LIME claims to provide explanations for individual predictions (local).
 Additionally, LIME is designed to work with any model (model-agnostic) and to produce easily understandable results (explanations) \citep{ribeiro:2016}.
-Conceptually, LIME fits a simple (interpretable) model, the explainer model, \kge{to approximate}  the complex model in a local region around a prediction of interest.
-The simple model \kge{is interpreted to identify the}  variables that most influence the \kge{complex model} prediction.
-
-\kge{While t}he concept of LIME is relatively simple, a practical implementation of LIME is not straightforward, and research is being done to improve the procedure \citep{laugel:2018}.
+Conceptually, LIME fits a simple (interpretable) model, the explainer model, to approximate  the complex model in a local region around a prediction of interest.
+The simple model is interpreted to identify the  variables that most influence the complex model prediction.
+
+While the concept of LIME is relatively simple, a practical implementation of LIME is not straightforward, and research is being done to improve the procedure \citep{laugel:2018}.
 The current implementations of LIME \citep{pedersen:2020} \citep{ribeiro:2020} offer various tuning parameters (see Section \ref{background}) that affect the explainer model and ultimately, the explanation.
 Since the explainer model is an approximation of the complex model and not a direct interpretation, the explanations produced by an explainer model are subject to the quality of the approximation.
-\kge{I}n order to achieve \kge{reasonable}  explanations, the tuning parameter values selected \kge{shoud}  be assessed.
-
-\kge{To demonstrate the effect of a tuning parameter on LIME, we consider two different explainer models applied to the same prediction.
+In order to achieve reasonable  explanations, the tuning parameter values selected shoud  be assessed.
+
+To demonstrate the effect of a tuning parameter on LIME, we consider two different explainer models applied to the same prediction.
 Figure \ref{fig:figure-01} depicts two plots of the predictions from a hypothetical black-box model versus the feature used to train the model.
@@
 Globally, there is a clear non-linear relationship between the predictions and the feature, but the relationship could be approximated by a linear model in a local region around the prediction of interest.
-In both scenarios, a linear regression weighted by the proximity from an observation to the prediction of interest is used as the explainer model, but the proximities are computed differently as depicted by the varying sizes of the observations in the two plots.}
-
-\kge{On the left, the distance between an observation and the prediction of interest is computed using the Gower distance metric \citep{gower:1971} and then raised to the power of \Sexpr{good_gower_power} to emphasize a very local region.
+In both scenarios, a linear regression weighted by the proximity from an observation to the prediction of interest is used as the explainer model, but the proximities are computed differently as depicted by the varying sizes of the observations in the two plots.
+
+On the left, the distance between an observation and the prediction of interest is computed using the Gower distance metric \citep{gower:1971} and then raised to the power of \Sexpr{good_gower_power} to emphasize a very local region.
 The distances are subtracted from 1 to obtain a proximity.
 Here, the explainer model is faithful to the complex model since it captures the linear relationship between the black-box predictions in an immediate neighborhood of the prediction of interest.
-The slope  explains that the black-box predictions increase as the feature increases in the local region around the prediction of interest.}
-
-\kge{For the scenario on the right, the computation of the proximities is the same except the distances are raised to a power of \Sexpr{bad_gower_power} (the default exponent in the \emph{lime} R package \citep{pedersen:2020}).
+The slope  explains that the black-box predictions increase as the feature increases in the local region around the prediction of interest.
+
+For the scenario on the right, the computation of the proximities is the same except the distances are raised to a power of \Sexpr{bad_gower_power} (the default exponent in the \emph{lime} R package \citep{pedersen:2020}).
 This causes the observations that are further away from the prediction of interest to be given larger weights than the scenario on the left.
 Here, the explainer model does not capture the linear trend near the prediction of interest, but instead, the explainer captures a more global trend.
-Without an assessment of this explainer model, the slope  would incorrectly explain that the predictions decrease as the feature increases near the prediction of interest.} %\sout{This cannot be said of the explainer model in \autoref{fig:figure-02}.
+Without an assessment of this explainer model, the slope incorrectly suggests that the predictions decrease as the feature increases near the prediction of interest.
+%\sout{This cannot be said of the explainer model in \autoref{fig:figure-02}.
 In addition, the magnitude of the slope associated with Feature 2  (\Sexpr{coefs_data %>% filter(case == "bad", feature == "Feature 2") %>% pull(b1) %>% round(3) %>% abs()}) is larger than that of Feature 1 (\Sexpr{coefs_data %>% filter(case == "bad", feature == "Feature 1") %>% pull(b1) %>% round(3) %>% abs()}).
@@
 
-\kge{\autoref{fig:figure-01} demonstrates a simple example in which the explanation quality varies drastically when different weights are used.
-Other concerns with LIME have been raised in the literature.}  \kge{\citet{laugel:2018} and \citet{molnar:2019} discuss the difficulty specifying a local region with LIME due to both}  an unclear definition of \kge{what is} a "local region" and how to apply LIME to achieve an appropriate local region.
-\kge{\citet{laugel:2018} also present examples of LIME explanations that are clearly global and not local.} \kge{A different concern about LIME is raised by} \citet{alvarezmelis:2018}  pertaining to the robustness of explanations from LIME and other \kge{explainer} model\kge{s} : they find that even small changes in predictor variables can lead to very different LIME explanations.
-\kge{Even the original authors of LIME,}  \citet{ribeiro:2016}\kge{,} acknowledge that if a linear model is used as the explainer, LIME relies on a linear approximation of the explainer model to the complex model and state "if the underlying model is highly non-linear even in the locality of the prediction, there may not be a faithful explanation".
-
- \kge{Without an assessment of the LIME explainer model, the user is putting trust in another black-box procedure to explain the complex black-box model.
-In this paper, we stress the importance of assessing the LIME explainer model.} \kge{To do this, w}e lay out the set of claims about LIME made by \citet{ribeiro:2016}, and \kge{we provide a toolkit of visual diagnostics}  for the assessment of these claims: (1) \emph{explanation scatterplots}, (2) \emph{feature heatmaps}, (3) \emph{assessment metric plots}.
-\kge{Using these visual diagnostics, we demonstrate problematic examples of LIME explanations where the claims about LIME are not met and the explanations are highly dependent on tuning parameter values without a clear way to identify a set of tuning parameter values that produce the "best" explanations.}
+\autoref{fig:figure-01} demonstrates a simple example in which the explanation quality varies drastically when different weights are used.
+Other concerns with LIME have been raised in the literature: \citet{laugel:2018} and \citet{molnar:2019} discuss the difficulty specifying a local region with LIME due to both  an unclear definition of what is a "local region" and how to apply LIME to achieve an appropriate local region.
+\citet{laugel:2018} also present examples of LIME explanations that are clearly global and not local.
+A different concern about LIME is raised by \citet{alvarezmelis:2018}  pertaining to the robustness of explanations from LIME and other explainer models : they find that even small changes in predictor variables can lead to very different LIME explanations.
+Even the original authors of LIME,  \citet{ribeiro:2016}, acknowledge that if a linear model is used as the explainer, LIME relies on a linear approximation of the explainer model to the complex model and state "if the underlying model is highly non-linear even in the locality of the prediction, there may not be a faithful explanation".
+
+ Without an assessment of the LIME explainer model, the user is putting trust in another black-box procedure to explain the complex black-box model.
+In this paper, we stress the importance of assessing the LIME explainer model.
+To do this, we lay out the set of claims about LIME made by \citet{ribeiro:2016}, and we provide a toolkit of visual diagnostics  for the assessment of these claims: (1) \emph{explanation scatterplots}, (2) \emph{feature heatmaps}, (3) \emph{assessment metric plots}.
+Using these visual diagnostics, we demonstrate problematic examples of LIME explanations where the claims about LIME are not met and the explanations are highly dependent on tuning parameter values without a clear way to identify a set of tuning parameter values that produce the "best" explanations.
 
@@
 For additional simplicity, we only discuss classification prediction models with a dichotomous response  and continuous predictors.
-However, the proposed diagnostics may be extended to \kge{other}  situations.
+However, the proposed diagnostics may be extended to other  situations.
 
@@
 The forked version is functionally indistinguishable from \citeauthor{pedersen:2020}'s implementation but allows us to export internal values relevant for an assessment of the explainer.
-The \kge{code for the} diagnostic plots  \kge{is stored in}  the R package \emph{limeaid} \citep{goode:2020}.
+The code for the diagnostic plots  is stored in  the R package \emph{limeaid} \citep{goode:2020}.
 
@@
 An adaption of the Python package in R has been implemented and made available by Thomas Lin-Pedersen \citep{pedersen:2020}.
-\kge{In both implementations, a ridge regression model is used as the explainer model, and}  the user is asked to select various tuning parameter options: the number of features to return in the explanation, the simulation method, the feature selection method, and how the weights are computed.
+In both implementations, a ridge regression model is used as the explainer model, and  the user is asked to select various tuning parameter options: the number of features to return in the explanation, the simulation method, the feature selection method, and how the weights are computed.
 The discussion of parameter choices and implementation details of LIME in this paper are based on the R package.
-\kge{See Appendix~\ref{lime-details} for}
+See Appendix~\ref{lime-details} for
 an overview of the options available for the tuning parameters.
@@
 @
-\caption{Plots of $x_2$ versus $x_1$ from the \kge{\data \ } training (left) and testing (right) sets introduced in Section \ref{diagnostics}  \kge{with t}he true classification boundary  shown as a solid black line.
-\kge{In the testing set, the open black circles identify cases misclassified by the random forest, and the diamond indicates a prediction of interest.} }
+\caption{Plots of $x_2$ versus $x_1$ from the \data \  training (left) and testing (right) sets introduced in Section \ref{diagnostics}  with the true classification boundary  shown as a solid black line.
+In the testing set, the open black circles identify cases misclassified by the random forest, and the diamond indicates a prediction of interest.
+}
 \label{fig:figure-02}
@@
 (right) \emph{Explanation Scatterplot}.
-\kge{An explanation scatterplot associated with the explanation  on the left.} \kge{T}he \kge{4} quantile bins \kge{over simplify}
-the relationship between the random forest predictions and the $x_1$ and $x_2$ values \kge{near the prediction of interest}.}
+An explanation scatterplot associated with the explanation  on the left.
+The four quantile bins over-simplify
+the relationship between the random forest predictions and the $x_1$ and $x_2$ values near the prediction of interest.}
 \label{fig:figure-03}
@@
 
-In this section, we introduce three visual diagnostic plots  \kge{that} assess the LIME claims from different perspectives:
+In this section, we introduce three visual diagnostic plots  that assess the LIME claims from different perspectives:
 
@@
 To demonstrate the visual diagnostics, we generate an example dataset that will be referred to as the \data.
-The \data \ contains \Sexpr{dim(sine_data)[1]} observations with  features \kge{of} $x_1$ \kge{and} $x_2$ \kge{independently sampled from Unif(\Sexpr{min}, \Sexpr{max}) distributions} and $x_3$  \kge{sampled from a} $\mbox{N}(0,1)$ distribution.
-A binary response variable $y$ is created using a  sine curve  \kge{such that}
+The \data \ contains \Sexpr{dim(sine_data)[1]} observations with  features of $x_1$ and $x_2$ independently sampled from Unif(\Sexpr{min}, \Sexpr{max}) distributions and $x_3$  sampled from a $\mbox{N}(0,1)$ distribution.
+A binary response variable $y$ is created using a  sine curve  such that
 \begin{eqnarray}\label{eq:data}
@@
 \end{eqnarray}
-where $x'_1=x_1\cos(\theta)-x_2\sin(\theta)$\kge{,}  $x'_2=x_1\sin(\theta)+x_2\cos(\theta)$\kge{, and}  $\theta=-0.9$. \sout{Then $y$ is defined as
+where $x'_1=x_1\cos(\theta)-x_2\sin(\theta)$,  $x'_2=x_1\sin(\theta)+x_2\cos(\theta)$, and  $\theta=-0.9$. \sout{Then $y$ is defined as
 \begin{eqnarray}\label{eq:data}
@@
 Note that due to the creation of $y$ in this manner, $y$ is dependent on $x_1$ and $x_2$ and independent of $x_3$.
-The dataset is \kge{randomly} divided into training and testing sets of \Sexpr{dim(sine_data_train)[1]} and \Sexpr{dim(sine_data_test)[1]} observations, respectively.
-A random forest is fit \kge{to the training set} using the R package \emph{randomForest} (version \Sexpr{packageVersion("randomForest")}) \citep{liaw:2002} with the default settings \kge{and} is applied to the test set to obtain predictions.
+The dataset is randomly divided into training and testing sets of \Sexpr{dim(sine_data_train)[1]} and \Sexpr{dim(sine_data_test)[1]} observations, respectively.
+A random forest is fit to the training set using the R package \emph{randomForest} (version \Sexpr{packageVersion("randomForest")}) \citep{liaw:2002} with the default settings and is applied to the test set to obtain predictions.
 
@@
 The training data are colored by the observed response variable ($y$), and the testing data are colored by random forest prediction probabilities.
-The random forest  misclassifies \Sexpr{dim(sine_data_test %>% filter(y != rfpred))[1]} points, which are all located near the classification boundary  \kge{and} identified by open circles.
+The random forest  misclassifies \Sexpr{dim(sine_data_test %>% filter(y != rfpred))[1]} points, which are all located near the classification boundary  and identified by open circles.
 
@@
 Here, the relationship is determined by the sine wave.
-However, the sine is a good-natured function that can be approximated well linearly in local regions \kge{as shown in Figure \ref{fig:figure-01}}.
-
-We apply LIME using six sets of tuning parameter values to all observations in the \data \ test set to observe \kge{explanation} variability.
-\kge{Five of the LIME applications use a}  quantile bin based simulation method (samples are simulated uniformly from a \kge{feature using a} specified number of quantile bins)  with the number of bins varying from 2 to 6 by application.
+However, the sine is a good-natured function that can be approximated well linearly in local regions as shown in Figure \ref{fig:figure-01}.
+
+We apply LIME using six sets of tuning parameter values to all observations in the \data \ test set to observe explanation variability.
+Five of the LIME applications use a  quantile bin based simulation method (samples are simulated uniformly from a feature using a specified number of quantile bins)  with the number of bins varying from 2 to 6 by application.
 We use 6 bins as the maximum, because the complexity of the explanations increases with the number of bins.
-Note that 4-quantile-bins \kge{is}  the default method in the \emph{lime} R package.
+Note that 4-quantile-bins is  the default method in the \emph{lime} R package.
 The sixth application of LIME uses a kernel density simulation method (samples are drawn from kernel density approximations of the feature distributions).
 The default methods for feature selection (forward selection) and the computation of the weights (Gower distance raised to an exponent of 1) are used for all applications.
-See Appendix~\ref{lime-details} for \kge{more detailed} descriptions of the tuning parameters.
+See Appendix~\ref{lime-details} for more detailed descriptions of the tuning parameters.
 
@@
 Before introducing the visual diagnostics, let us consider a commonly used visualization of a LIME explanation.
-\kge{Figure \ref{fig:figure-03} (left) depicts the explanation for the prediction of interest indicated in \autoref{fig:figure-02} obtained using 4-quantile-bins.
+Figure \ref{fig:figure-03} (left) depicts the explanation for the prediction of interest indicated in \autoref{fig:figure-02} obtained using 4-quantile-bins.
 In the text at the top, the "Probability" is the random forest probability of \Sexpr{round(sine_poi_lime_default$label_prob[1], 2)} that the observation of interest belongs to the "Label" category of blue.
-The "Explanation Fit" is the deviance ratio of \Sexpr{round(sine_poi_lime_default$model_r2[1], 2)} associated with the ridge regression explainer model (often interpreted as an $R^2$), which suggests that the explainer model is not a good linear fit.}
-
-\kge{Since 4-quantile-bins are used to simulate data, LIME converts continuous predictor variables to indicator variables identifying whether the variable value falls in the same quantile bin as the prediction of interest or not.
+The "Explanation Fit" is the deviance ratio of \Sexpr{round(sine_poi_lime_default$model_r2[1], 2)} associated with the ridge regression explainer model (often interpreted as an $R^2$), which suggests that the explainer model is not a good linear fit.
+
+Since 4-quantile-bins are used to simulate data, LIME converts continuous predictor variables to indicator variables identifying whether the variable value falls in the same quantile bin as the prediction of interest or not.
 The indicator variables are used as the features in the ridge regression explainer model.
-The features included in the visualization are the ones selected by feature selection, the lengths of the bars represent the coefficients from the ridge regression associated with the indicator variables, and the color of a bar denotes the sign of the coefficient.
-This explainer model explains that the random forest prediction that the observation of interest belongs to the category of blue is mostly supported by the prediction of interest having a value of $x_2$ that is greater than \Sexpr{str_split(sine_poi_lime_default$feature_desc[[1]], pattern = " ")[[1]][1]} but somewhat contradicted by the prediction of interest having a value of $x_1$ that is greater than \Sexpr{str_split(sine_poi_lime_default$feature_desc[[2]], pattern = " ")[[1]][1]} and less than or equal to \Sexpr{str_split(sine_poi_lime_default$feature_desc[[2]], pattern = " ")[[1]][5]}.} \kgc{I decided to leave the values here.
-I actually prefer it this way myself, but I cut out a lot of text from this subsection in other ways.}
+The features included in the visualization are the ones selected by feature selection, the lengths of the bars represent the coefficients from the ridge regression associated with the indicator variables, while the color of a bar denotes the sign of the coefficient.
+This explainer model suggests that a random forest prediction of `blue' for this observation is mostly supported by the prediction of interest having a value of $x_2$ that is greater than \Sexpr{str_split(sine_poi_lime_default$feature_desc[[1]], pattern = " ")[[1]][1]} but somewhat contradicted by the prediction of interest having a value of $x_1$ that is greater than \Sexpr{str_split(sine_poi_lime_default$feature_desc[[2]], pattern = " ")[[1]][1]} and less than or equal to \Sexpr{str_split(sine_poi_lime_default$feature_desc[[2]], pattern = " ")[[1]][5]}.
+\kgc{I decided to leave the values here.
+I actually prefer it this way myself, but I cut out a lot of text from this subsection in other ways.}\hh{XXX }
 

### 2020-12-31 paper.Rnw
color removed

@@
 \begin{document}
-\SweaveOpts{concordance=TRUE}
 
@@
 <<setup, echo = FALSE, include = FALSE>>=
-
 # Specify global options
@@
 While the concept of LIME is relatively simple, a practical implementation of LIME is not straightforward, and research is being done to improve the procedure \citep{laugel:2018}.
-The current implementations of LIME \citep{pedersen:2020} \citep{ribeiro:2020} offer various tuning parameters (see Section \ref{background}) that affect the explainer model and ultimately, the explanation.
+The current implementations of LIME \citep{pedersen:2020, ribeiro:2020} offer various tuning parameters (see Section \ref{background}) that affect the explainer model and ultimately, the explanation.
 Since the explainer model is an approximation of the complex model and not a direct interpretation, the explanations produced by an explainer model are subject to the quality of the approximation.
@@
 To demonstrate the effect of a tuning parameter on LIME, we consider two different explainer models applied to the same prediction.
-Figure \ref{fig:figure-01} depicts two plots of the predictions from a hypothetical black-box model versus the feature used to train the model.
+\autoref{fig:figure-01} depicts two plots of the predictions from a hypothetical black-box model versus the feature used to train the model.
 The location of a prediction of interest is indicated by the diamonds.
@@
 
-%\kge{Figure \ref{fig:figure-01} depicts the first scenario where the weights are computed as the inverse proximity of the point to the prediction of interest computed using the Gower distance metric \citep{gower:1971} raised to the power of \Sexpr{good_gower_power} to emphasize a very local region.
-The point size represents the weight, and the black lines depict the ridge regression model given the observed prediction of interest value from the opposite feature.
-For Feature 1 (left), the explainer model captures the relationship in an immediate neighborhood around the prediction of interest with a slope of \Sexpr{coefs_data %>% filter(case == "good", feature == "Feature 1") %>% pull(slope) %>% round(3)}, and for Feature 2 (right), the ridge regression has a small slope of \Sexpr{coefs_data %>% filter(case == "good", feature == "Feature 2") %>% pull(slope) %>% round(3)} that accurately reflects the absence of any global or local relationship between the black-box predictions and Feature 2.
-The magnitude of the slope associated with Feature 1 is larger than the slope of Feature 2, which suggests that Feature 1 plays a more important role in the prediction made by the black-box model for the prediction of interest.
-This explanation agrees with a visual assessment of the relationships between the predictions and predictor variables.}
-
-%\sout{\autoref{fig:figure-01} provides a visualization of this conceptual understanding of LIME.
-The two plots show the predictions from a hypothetical black-box model plotted against the two hypothetical model predictor variables.
-The diamond shaped points represent the location of the prediction of interest.
-A Gower distance metric \citep{gower:1971} is used to define locality such that the size of the points represent the inverse of the Gower distance raised to some value and indicate the proximity to the prediction of interest.
-In the example of \autoref{fig:figure-01}, an exponent of \Sexpr{good_gower_power} is used to emphasize a very local region around the prediction of interest.
-A ridge regression model weighted by the proximity values is used as the explainer model with the black-box predictions as the response variable and standardized versions of two features in the data as predictor variables.
-Standardized features allow direct comparisons of the model coefficients.
-The explainer model is depicted by the black lines in the figure.}
-
-%\sout{The plot on the left of \autoref{fig:figure-01} shows the relationship between the black-box predictions and Feature 1.
-Here, the explainer model is plotted with Feature 2 fixed at the observed value of the prediction of interest.
-The explainer model captures the relationship in an immediate neighborhood around the prediction of interest with a slope of \Sexpr{coefs_data %>% filter(case == "good", feature == "Feature 1") %>% pull(slope) %>% round(3)}.
-The plot on the right shows no global or local relationships between the black-box predictions and Feature 2.
-Here, the explainer model is plotted with Feature 1 set as the observed value of the prediction of interest, and it has an appropriately small slope of \Sexpr{coefs_data %>% filter(case == "good", feature == "Feature 2") %>% pull(slope) %>% round(3)}.
-The magnitude of the slope associated with Feature 1 is larger than the slope of Feature 2, which suggests that Feature 1 plays a more important role in the prediction made by the black-box model for the prediction of interest.
-This explanation agrees with a visual assessment of the relationships between the predictions and predictor variables.}
-
-%\sout{The concept of LIME is relatively simple: use an interpretable model to approximate a complex model in a local region.
-However, a practical implementation of LIME is not straightforward, and research is being done to improve the procedure \citep{laugel:2018}.
-The current implementations of LIME \citep{ribeiro:2020} \citep{pedersen:2020} offer various tuning parameters (see Section \ref{background}) that affect the explainer model and ultimately, the explanation.
-Since the explainer model is an approximation of the complex model and not a direct interpretation, the explanations produced by an explainer model are subject to the quality of the approximation.
-Thus, in order to achieve accurate explanations, the tuning parameter values selected need to be assessed.}
-
-%\kge{Figure \ref{fig:figure-02} depicts the second explainer model scenario.
-Again, the weights are computed using the Gower distance metric, but in this situation, the distances are raise to a power of \Sexpr{bad_gower_power} (the default exponent in the \emph{lime} R package).} \sout{We consider an example where the choice of exponent for the weights is crucial to the quality of the explanation.
-The plots in Figure \ref{fig:figure-02} show the same data as \autoref{fig:figure-01}, but the Gower distance metric exponent is decreased to \Sexpr{bad_gower_power} (the default exponent in the \emph{lime} R package).} This causes the observations that are further away from the prediction of interest to be given larger weights than before.
-In \autoref{fig:figure-01}, the explainer model captures the relationship between the black-box predictions in an immediate neighborhood of the prediction of interest.
-This cannot be said of the explainer model in \autoref{fig:figure-02}.
-In addition, the magnitude of the slope associated with Feature 2  (\Sexpr{coefs_data %>% filter(case == "bad", feature == "Feature 2") %>% pull(slope) %>% round(3) %>% abs()}) is larger than that of Feature 1 (\Sexpr{coefs_data %>% filter(case == "bad", feature == "Feature 1") %>% pull(slope) %>% round(3) %>% abs()}).
-Thus, this explainer model actually provides a misleading explanation that Feature 2 plays a more important role in the prediction of interest.
-
-% \begin{figure*}[!thp]
-% <<figure-02, out.width = '6.25in', fig.width = 7.95, fig.height = 3.25, warning = FALSE, eval = FALSE>>=
-% 
-% # Specify the figure size (for determining font size)
-% f2_ow = 6.25
-% f2_fw = 7.95
-% f2_fs = fs * (f2_fw / f2_ow)
-% 
-% # Plot of good explainer model
-% ggplot() +
-%   facet_grid(. ~ feature, switch = "x") +
-%   geom_point(
-%     data = lime_data_gathered %>% 
-%       mutate(
-%         feature = fct_recode(
-%           feature,
-%           "Feature 1 (standardized)" = "Feature 1",
-%           "Feature 2 (standardized)" = "Feature 2"
-%           )
-%         ),
-%     mapping = aes(
-%       x = feature_stnd_value,
-%       y = prediction,
-%       size = distance_value,
-%       color = distance
-%     ), 
-%     alpha = 0.6
-%   ) +
-%   geom_abline(
-%     data = coefs_data %>% 
-%       filter(case == "bad") %>% 
-%       mutate(
-%         feature = fct_recode(
-%           feature,
-%           "Feature 1 (standardized)" = "Feature 1",
-%           "Feature 2 (standardized)" = "Feature 2"
-%           )
-%         ),
-%     mapping = aes(intercept = int, slope = slope),
-%     size = 1
-%   ) +
-%   scale_color_manual(values = c("grey30", NA), guide = "none") +
-%   geom_point(
-%     data = prediction_of_interest_gathered %>% 
-%       mutate(
-%         feature = fct_recode(
-%           feature,
-%           "Feature 1 (standardized)" = "Feature 1",
-%           "Feature 2 (standardized)" = "Feature 2"
-%           )
-%         ),
-%     mapping = aes(x = feature_value,
-%                   y = prediction,
-%                   fill = color),
-%     color = "black",
-%     size = 5,
-%     shape = 23,
-%     alpha = 0.75
-%   ) +
-%   scale_fill_manual(values = "#FAAA72") +
-%   geom_text(
-%     data = data.frame(
-%       feature_stnd_value = 1.2,
-%       prediction = 1.6,
-%       feature = c("Feature 1 (standardized)", "Feature 2 (standardized)"),
-%       slope = c(
-%         paste(
-%           "Slope:",
-%           coefs_data %>%
-%             filter(case == "bad",
-%                    feature == "Feature 1") %>%
-%             pull(slope) %>%
-%             round(3)
-%         ),
-%         paste(
-%           "Slope:",
-%           coefs_data %>%
-%             filter(case == "bad",
-%                    feature == "Feature 2") %>%
-%             pull(slope) %>%
-%             round(3)
-%         )
-%       )
-%     ),
-%     mapping = aes(x = feature_stnd_value,
-%                   y = prediction,
-%                   label = slope),
-%     family = ff,
-%     size = f2_fs / 3
-%   ) +
-%   labs(
-%     x = "",
-%     y = "Black-Box Prediction",
-%     title = "Conceptual Depiction of an Unfaithful Local Explainer Model",
-%     subtitle = paste("Gower Distance Metric Exponent:", bad_gower_power),
-%     fill = "",
-%     alpha = "Weight",
-%     size = "Weight"
-%   ) +
-%   theme_linedraw(base_family = ff, base_size = f2_fs) +
-%   theme(
-%     panel.grid.major = element_blank(),
-%     panel.grid.minor = element_blank(),
-%     axis.text.x = element_blank(),
-%     axis.ticks.x = element_blank(),
-%     axis.text.y = element_blank(),
-%     axis.ticks.y = element_blank(),
-%     strip.placement = "outside",
-%     strip.background = element_rect(color = "white", fill = "white"),
-%     strip.text.x = element_text(size = f2_fs, color = "black"),
-%     plot.title = element_text(size = f2_fs)
-%   ) +
-%   guides(
-%     fill = guide_legend(order = 1),
-%     size = guide_legend(order = 2),
-%     alpha = guide_legend(order = 2)
-%   )
-% 
-% @
-% \caption{A conceptual depiction of an unfaithful local explainer model in the immediate neighborhood of a prediction of interest.
-A\kge{gain, a weighted} ridge regression \kge{is used as the explainer model} \sout{is fit to the same hypothetical black-box model predictions and predictor variables as in \autoref{fig:figure-01}}, but the \kge{Gower distance is raised to a power} \sout{weights are computed using a Gower exponent} of 1.
-\sout{The explainer model is unfaithful to the complex model in any immediate neighborhood of the prediction of interest.}}
-% \label{fig:figure-02}
-% \end{figure*}
-
 \autoref{fig:figure-01} demonstrates a simple example in which the explanation quality varies drastically when different weights are used.
@@
 The remainder of the paper is structured as follows.
-Section \ref{background} provides background and claims made by \citet{ribeiro:2016} about LIME.
+Section ~\ref{background} provides background and claims made by \citet{ribeiro:2016} about LIME.
 We introduce the suggested diagnostic plots in Section \ref{diagnostics}.
-Then in Section \ref{application}, we demonstrate the use of the diagnostics to assess LIME explanations for a random forest  fit to a forensics bullet matching dataset.
-Section \ref{discussion} concludes with a discussion on extensions and limitations of the diagnostic plots and concerns about LIME in regards to the claims made by \citet{ribeiro:2016} brought about by the visualization examples in this paper that agree with \citet{alvarezmelis:2018}, \citet{laugel:2018}, and \citet{molnar:2019}.
+Then in Section~\ref{application}, we demonstrate the use of the diagnostics to assess LIME explanations for a random forest  fit to a forensics bullet matching dataset.
+Section~\ref{discussion} concludes with a discussion on extensions and limitations of the diagnostic plots and concerns about LIME in regards to the claims made by~\citet{ribeiro:2016} brought about by the visualization examples in this paper that agree with \citet{alvarezmelis:2018, laugel:2018}, and \citet{molnar:2019}.
 
@@
 
-\kgc{I moved the paragraphs in this section around} The general form of the LIME algorithm can be divided into three steps \citep[see also][]{laugel:2018}:
+The general form of the LIME algorithm can be divided into three steps \citep[see also][]{laugel:2018}:
 
@@
 Here, the relationship is determined by the sine wave.
-However, the sine is a good-natured function that can be approximated well linearly in local regions as shown in Figure \ref{fig:figure-01}.
+However, the sine is a good-natured function that can be approximated well linearly in local regions as shown in \autoref{fig:figure-01}.
 
@@
 Before introducing the visual diagnostics, let us consider a commonly used visualization of a LIME explanation.
-Figure \ref{fig:figure-03} (left) depicts the explanation for the prediction of interest indicated in \autoref{fig:figure-02} obtained using 4-quantile-bins.
+\autoref{fig:figure-03} (left) depicts the explanation for the prediction of interest indicated in \autoref{fig:figure-02} obtained using 4-quantile-bins.
 In the text at the top, the "Probability" is the random forest probability of \Sexpr{round(sine_poi_lime_default$label_prob[1], 2)} that the observation of interest belongs to the "Label" category of blue.
@@
 
-\kge{As a first check to determine whether the explanation depicted in \autoref{fig:figure-03} (left) is trustworthy, we note that since the support for blue by $x_2$ outweighs the support for red by $x_1$, the explainer model overall favors a label of blue for the prediction of interest agreeing with the random forest probability.
+As a first check to determine whether the explanation depicted in \autoref{fig:figure-03} (left) is trustworthy, we note that since the support for blue by $x_2$ outweighs the support for red by $x_1$, the explainer model overall favors a label of blue for the prediction of interest agreeing with the random forest probability.
 In fact, both random forest and explainer model classify the observation incorrectly.
-However, based on the information in \autoref{fig:figure-03} (left) alone, it is not possible to make an informed assessment of the explanation.}
+However, based on the information in \autoref{fig:figure-03} (left) alone, it is not possible to make an informed assessment of the explanation.
 
@@
 We introduce the explanation scatterplot here under the \emph{lime} R package default method of 4-quantile-bins.
-\kge{Appendix \ref{exp-scatter_plus} addresses the explanation scatterplot formats in other LIME simulation scenarios.}
+Appendix \ref{exp-scatter_plus} addresses the explanation scatterplot formats in other LIME simulation scenarios.
 
@@
 The point size represents the weight assigned by LIME.
-In order to show the LIME results for the observation of interest, lines are drawn on top of the points  represent\kge{ing} the boundaries of the indicator variables used to fit the explainer model.
+In order to show the LIME results for the observation of interest, lines are drawn on top of the points  representing the boundaries of the indicator variables used to fit the explainer model.
 The line color  denotes whether LIME indicates that a feature supports or contradicts a class prediction.
@@
 These statements validate the explanation produced by LIME.
-However, the explanation scatterplot plot shows that the random forest performs well at capturing the sine curve classification boundary by creating various sized rectangles consisting of predictions with similar probabilities, which the LIME explanation does not pick up on \kge{since the bins are created without information about the random forest predictions}.
+However, the explanation scatterplot plot shows that the random forest performs well at capturing the sine curve classification boundary by creating various sized rectangles consisting of predictions with similar probabilities, which the LIME explanation does not pick up on since the bins are created without information about the random forest predictions.
 Thus, LIME does provide an explanation for the prediction, but it is a very poor explanation in terms of faithfulness to the random forest prediction regions.
@@
 It is difficult to assess linearity from this explanation scatterplot, but a residual plot of the explainer model could be used to check the linearity claim.
-See Appendix~\ref{residual-plot} for the residual plot associated with the explanation considered in Figure \ref{fig:figure-03}, which shows a violation of the linearity claim.
+See Appendix~\ref{residual-plot} for the residual plot associated with the explanation considered in \autoref{fig:figure-03}, which shows a violation of the linearity claim.
 
@@
 
-\kge{When interpreting feature heatmaps, horizontal lines of the same color represent the ideal situation where the explanations are consistent and do not depend on the tuning parameter values but do depend on the location of the observation in the feature space.
+When interpreting feature heatmaps, horizontal lines of the same color represent the ideal situation where the explanations are consistent and do not depend on the tuning parameter values but do depend on the location of the observation in the feature space.
 Vertical lines of color represent explanations that are dependent on the tuning parameter values and may not be local since the same feature is chosen regardless of the location of the observation in the feature space.
-See Appendix \ref{feat-heat-ex} for hypothetical examples depicting feature heatmaps with the extreme cases of horizontal and vertical lines.}
+See Appendix \ref{feat-heat-ex} for hypothetical examples depicting feature heatmaps with the extreme cases of horizontal and vertical lines.
 
@@
 The most important and second most important features selected by LIME are shown in in the top and bottom facets, respectively.
-For the quantile bins, the original features prior to \kge{being converted to indicator variables}  are included since it is obvious that different features would be selected when the sizes of the bins change.
-This figure shows that for kernel density and 2-quantile-bins, LIME \kge{produces global explanations since}  $x_1$ \kge{is selected} as the most important feature and $x_2$ \kge{is selected} as the second most important feature across all cases in the test set.
+For the quantile bins, the original features prior to being converted to indicator variables  are included since it is obvious that different features would be selected when the sizes of the bins change.
+This figure shows that for kernel density and 2-quantile-bins, LIME produces global explanations since  $x_1$ is selected as the most important feature and $x_2$ is selected as the second most important feature across all cases in the test set.
 There is variability in the features selected by LIME for 3- to 6-quantile-bins suggesting more local explanations.
 There are signs of vertical striping, which suggests a dependence on tuning parameters.
-Note that the explanations from 3- and 5-quantile-bins include the selection of the random noise variable ($x_3$) as an important variable in many predictions, which \kge{would not be expected to be important to a random forest}.
-\kge{It is unclear whether the random forest is using a variable that would not be expected to be important or LIME is incorrectly identifying the important variable when 3- and 5- quantile bins are used.}
+Note that the explanations from 3- and 5-quantile-bins include the selection of the random noise variable ($x_3$) as an important variable in many predictions, which would not be expected to be important to a random forest.
+It is unclear whether the random forest is using a variable that would not be expected to be important or LIME is incorrectly identifying the important variable when 3- and 5- quantile bins are used.
 
@@
 \caption{\emph{Assessment metric plot}.
-\kge{This example assessment metric plot contains metrics}  computed on the applications of LIME to the \data \ test set.
+This example assessment metric plot contains metrics  computed on the applications of LIME to the \data \ test set.
 The kernel density simulation methods performs well across all three metrics.}
@@
 MSEE provides almost the exact opposite results with 6-quantile-bins performing the best and 2-quantile-bins performing the worst.
-Average fidelity and MSEE are similar metrics, \kge{but}  MSEE only takes the prediction of interest into account and not the full simulated dataset \kge{as average fidelity does.} \kge{This suggests that 6-quantile-bins produce an explainer model more faithful for the prediction of interest while 2-quantile-bins produce an explainer model more faithful over all simulated data observations}.
-
-Recall\kge{,}  \autoref{fig:figure-04} \kge{shows}  the kernel density method \kge{returns the same explanations}  across all cases in the test set \kge{suggesting} a global trend may be the best explanation for this example\kge{.} \kge{This} may be reasonable considering that we \kge{would expect}  $x_1$ and $x_2$ \kge{to be}  the two features  used by the random forest to distinguish between response categories.
-\kge{However, futher exploration of individual explanations using explanation scatterplots may help to identify the tuning parameter values that produce the most trustworthy explanations.}
+Average fidelity and MSEE are similar metrics, but  MSEE only takes the prediction of interest into account and not the full simulated dataset as average fidelity does.
+This suggests that 6-quantile-bins produce an explainer model more faithful for the prediction of interest while 2-quantile-bins produce an explainer model more faithful over all simulated data observations.
+
+Recall,  \autoref{fig:figure-04} shows  the kernel density method returns the same explanations  across all cases in the test set suggesting a global trend may be the best explanation for this example.
+This may be reasonable considering that we would expect  $x_1$ and $x_2$ to be  the two features  used by the random forest to distinguish between response categories.
+However, futher exploration of individual explanations using explanation scatterplots may help to identify the tuning parameter values that produce the most trustworthy explanations.
 
@@
 
-In this section, we  \kge{apply} the visual diagnostics for LIME explanations to a practical data problem investigating the similarity of marks on fired bullets.
+In this section, we  apply the visual diagnostics for LIME explanations to a practical data problem investigating the similarity of marks on fired bullets.
 
@@
 @
-\caption{Example bullet signatures. The  signatures \kge{are from}  the same land and therefore have very similar patterns. }
+\caption{Example bullet signatures. The  signatures are from  the same land and therefore have very similar patterns. }
 \label{fig:figure-07}
@@
 @
-\caption{Parallel coordinate plots of the \kge{bullet matching}  random forest predictions.
+\caption{Parallel coordinate plots of the bullet matching  random forest predictions.
 Each line corresponds to an observation, and the line color represents the associated random forest probability.
@@
 
-\kge{In \autoref{fig:figure-08}, } \kge{w}e consider a global visualization of the relationship between the random forest predictions and the model features with a parallel coordinate plot of the training data (top \kge{row}) and testing data (bottom \kge{row}).
+In \autoref{fig:figure-08},  we consider a global visualization of the relationship between the random forest predictions and the model features with a parallel coordinate plot of the training data (top row) and testing data (bottom row).
 In the training data we observe a clear difference in feature values based on whether the corresponding random forest scores are close to 1 or 0.
@@
 
-First, applications of 2-quantile-bins\kge{, 2-equal-bins, and somewhat for the density based} simulations produce the same explanations for almost all cases and LIME tuning parameter values\kge{,} \kge{suggesting these} explanations are global and not local.
+First, applications of 2-quantile-bins, 2-equal-bins, and somewhat for the density based simulations produce the same explanations for almost all cases and LIME tuning parameter values, suggesting these explanations are global and not local.
 Second, within a simulation method, the features selected by LIME for an observation do not appear to vary by the Gower power.
-However, the LIME explanation\kge{s} for an observation often var\kge{y} across simulation methods.
+However, the LIME explanations for an observation often vary across simulation methods.
 With the equal bins, there are vertical stripes that suggest a dependence of the LIME explanations on the number of bins.
@@
 \caption{Assessment metric plot for the applications of LIME on the bullet comparison data test set.
-There are discrepancies in \kge{metric} performance\kge{s}, but  overall, 4-equal-bins with a Gower power of 0.5 appear to perform the best.}
+There are discrepancies in metric performances, but  overall, 4-equal-bins with a Gower power of 0.5 appear to perform the best.}
 \label{fig:figure-10}
@@
 However, there is consistency in results across different Gower powers.
-The applications using a power of 0.5 perform the best or as well as the other powers across all simulation methods suggesting that the power that leads to a more \kge{local}  explanation is preferred.
-It is not \kge{obvious}  which set of tuning parameters is the best\kge{, but}\kge{c}onsidering all three metrics, we might conclude that the 4-equal-bins with a Gower power of 0.5 performs better than the other tuning parameter values considered.
-
-To provide a more detailed view of explanations obtained using different tuning parameter values, we \kge{consider explanation scatterplots for one prediction of interest}  referred to as case NM (a known non-match) \kge{shown in} Figure~\ref{fig:figure-11}  \kge{along with} the visual  explanation \kge{plots} from \kge{the} \emph{lime} \kge{R package}.
+The applications using a power of 0.5 perform the best or as well as the other powers across all simulation methods suggesting that the power that leads to a more local  explanation is preferred.
+It is not obvious  which set of tuning parameters is the best, but considering all three metrics, we might conclude that the 4-equal-bins with a Gower power of 0.5 performs better than the other tuning parameter values considered.
+
+To provide a more detailed view of explanations obtained using different tuning parameter values, we consider explanation scatterplots for one prediction of interest  referred to as case NM (a known non-match) shown in Figure~\ref{fig:figure-11}  along with the visual  explanation plots from the \emph{lime} R package.
 Plots for 4-equal-bins and 4-quantile-bins are included to depict tuning parameter values with good (4-equal-bins) and mediocre (4-quantile-bins) performance based on the assessment metric plot.
-\kge{Also, recall that 4-quantile-bins are the default option in the \emph{lime} R package.}  \kge{Explanation scatterplots for a known match, referred to as case M, and} for the kernel density simulation method \kge{applied to both M and NM} are included in Appendix~\ref{bullets-plus}.
-
-\kge{When 4-quantile-bins are applied to case NM, LIME explains that the feature of mismatches, rough correlation, and distance are important and support a prediction of the class true (Figure~\ref{fig:figure-11} top left).
-However, this explanation contradicts that random forest prediction probability that correctly provides evidence that the observation is a non-match.
+%\kge{Also, recall that 4-quantile-bins are the default option in the \emph{lime} R package.}
+Explanation scatterplots for a known match, referred to as case M, and for the kernel density simulation method applied to both M and NM are included in Appendix~\ref{bullets-plus}.
+
+When 4-quantile-bins are applied to case NM, LIME explains that the values of mismatches, rough correlation, and distance are important and support a prediction of the class true (Figure~\ref{fig:figure-11} top left).
+However, this explanation contradicts the random forest prediction which correctly assigns the observation  a non-match.
 The explanation scatterplot (Figure~\ref{fig:figure-11} bottom left) clarifies the reason for the highly unfaithful explanation.
-Case NM falls on boundaries of regions for these three features where the random forest predictions transition from below 0.5 to above 0.5.
-However, the regions created when applying LIME from the 4-quantile-bins where case NM falls contain mostly observations with random forest predictions above 0.5.
-leading to the unfaithful explanation.}
-
-\kge{Figure~\ref{fig:figure-11} (top right) shows the LIME explanation for case NM when 4-equal-bins are used.
+Case NM falls on the boundary of regions for each of these three features where the random forest predictions transition from below 0.5 to above 0.5.
+However, the regions used when applying LIME from the 4-quantile-bins where case NM falls contain mostly observations with random forest predictions above 0.5, leading to the unfaithful explanation.
+
+Figure~\ref{fig:figure-11} (top right) shows the LIME explanation for case NM when 4-equal-bins are used.
 Here, the features identified as important are distance and mismatches, which support a match and matches, which supports a non-match.
 This explanation is more faithful having at least one feature supporting a non-match and has a better linear fit, but the most important feature identified by LIME still supports a match, contradicting the random forest.
-The explanation scatterplot (Figure~\ref{fig:figure-11} bottom right) again shows the features supporting a match arise from NM falling on the boundary of random forest prediction regions that are not well captured by the LIME bins.}
-
-\kge{Without an assessment of the LIME explanations, the default method would produce poor explanations such as the one shown in Figure~\ref{fig:figure-11} (left column).
+The explanation scatterplot (Figure~\ref{fig:figure-11} bottom right) again shows the features supporting a match arise from NM falling on the boundary of random forest prediction regions that are not well captured by the LIME bins.
+
+Without an assessment of the LIME explanations, the default method would produce poor explanations such as the one shown in Figure~\ref{fig:figure-11} (left column).
 Our assessment here led to better explanations when the four equal bins are used.
 However, the explanation quality is still lacking from the one prediction considered.
-Additional investigations using explanations scatterplots would help to determine whether to trust this set of explanations, continue tuning the LIME parameters, or use another approach to provide better insight.}
+Additional investigations using explanations scatterplots would help to determine whether to trust this set of explanations, continue tuning the LIME parameters, or use another approach to provide better insight.
 
@@
 We suggest the use of visual diagnostics to counteract the black-box nature of LIME.
-\kge{We provide three diagnostic plots}  intended to \kge{assess whether LIME explanations meet the claims made by \citet{ribeiro:2016}.
+We provide three diagnostic plots  intended to assess whether LIME explanations meet the claims made by \citet{ribeiro:2016}.
 The examples in this paper bring to light many scenarios in which the claims are not met or are difficult to assess.
-We reconsider each of the claims and how the visual diagnostics identify their failings.}
+We reconsider each of the claims and how the visual diagnostics identify their failings.
 
@@
 
-Even though an explanation will be interpretable \kge{if}  the complexity of the explainer model is appropriately chosen, a lack of understanding of the \kge{explainer model}  could lead to an incorrect interpretation of the explanation.
-For example, the visualization of a LIME explanation  from the \emph{lime} R package \citep{pedersen:2020} (Figure \ref{fig:figure-03} \kge{left; }  \kge{Figure} \ref{fig:figure-11} \kge{top}) is a  simplification of the explainer model, which could lead to  misinterpreted LIME explanation\kge{s}.
-Supplementing \citet{pedersen:2020}'s compact visualization of the explanation with an explanation scatterplot that shows a more detailed visualization of the explainer model promotes a more complete understanding of the explanation (Figures~\ref{fig:figure-03} \kge{right; }  \ref{fig:figure-11} \kge{bottom}).
+Even though an explanation will be interpretable if  the complexity of the explainer model is appropriately chosen, a lack of understanding of the explainer model  could lead to an incorrect interpretation of the explanation.
+For example, the visualization of a LIME explanation  from the \emph{lime} R package \citep{pedersen:2020} (\autoref{fig:figure-03} left;   \autoref{fig:figure-11} top) is a  simplification of the explainer model, which could lead to  misinterpreted LIME explanations.
+Supplementing \citet{pedersen:2020}'s compact visualization of the explanation with an explanation scatterplot that shows a more detailed visualization of the explainer model promotes a more complete understanding of the explanation (Figures~\ref{fig:figure-03} right;   \ref{fig:figure-11} bottom).
 
 Even with an explainer model that is interpreted correctly, the interpretation is worthless if the explainer model is not \textbf{faithful} to the complex model.
-\kge{E}xplanation scatterplots allow for a comparison of the explainer model to the complex model.
+Explanation scatterplots allow for a comparison of the explainer model to the complex model.
 The examples in this paper show cases where the explainer model oversimplifies the model and bins do not accurately capture the regions with similar random forest probabilities that contain the prediction of interest (Figures \ref{fig:figure-03} and \ref{fig:figure-11}).
@@
 
-\kge{W}e \kge{also} propose a\kge{n assessment metric plot for the} visual comparison of two faithfulness metrics: MSEE and average fidelity.
-\kge{Both metrics measure faithfulness, but MSEE only accounts for the prediction of interest while average fidelity accounts for all observations in the simulated data.
-As a result, the measures may disagree (Figures \ref{fig:figure-05} and \ref{fig:figure-10}), and the user is left to determine which is preferable.}
+We also propose an assessment metric plot for the visual comparison of two faithfulness metrics: MSEE and average fidelity.
+Both metrics measure faithfulness, but MSEE only accounts for the prediction of interest while average fidelity accounts for all observations in the simulated data.
+As a result, the measures may disagree (Figures \ref{fig:figure-05} and \ref{fig:figure-10}), and the user is left to determine which is preferable.
 
@@
 Most of the average $R^2$ values in the examples from this paper are below 0.5 suggesting a poor linear fit of the explainer models.
-A poor linear fit of the explainer model is also seen with the residual plot \kge{shown in} \autoref{fig:figure-C2}.
-
-The final claim, \textbf{localness}, is addressed by  feature heatmap\kge{s} and \kge{explanation scatterplots}.
-\kge{The vertical stripes seen in the feature heatmaps (Figures \ref{fig:figure-04} and \ref{fig:figure-09}) suggest global explanations produced by LIME since the same explanation is returned for almost all observations regardless of feature values.
+A poor linear fit of the explainer model is also seen with the residual plot shown in \autoref{fig:figure-C2}.
+
+The final claim, \textbf{localness}, is addressed by  feature heatmaps and explanation scatterplots.
+The vertical stripes seen in the feature heatmaps (Figures \ref{fig:figure-04} and \ref{fig:figure-09}) suggest global explanations produced by LIME since the same explanation is returned for almost all observations regardless of feature values.
 The explanation scatterplots visualize the locality of the explanation using point size to indicate weight.
-However, the lack of definition of a local region makes it difficult to assess whether the weights capture an appropriately local region.}
-
-\kge{These diagnostic visualizations are a starting point that already highlight seemingly common issues with the LIME claims.
-Additions, such as visualizations of the step-by-step process of the creation of LIME explanations and}  interactivity\kge{,}  enhance the assessment process.
+However, the lack of definition of a local region makes it difficult to assess whether the weights capture an appropriately local region.
+
+These diagnostic visualizations are a starting point that already highlight seemingly common issues with the LIME claims.
+Additions, such as visualizations of the step-by-step process of the creation of LIME explanations and  interactivity,  enhance the assessment process.
 For example, a diagnostic plot that provides a summary of multiple LIME explanations, such as the feature heatmap, could be displayed and clicked on to reveal more detailed figures associated with individual predictions of interest, such as an explanation scatterplot.
@@
 While it would be ideal if LIME could be used as a method to provide easily understandable explanations for black-box models as \citet{ribeiro:2016} claim, that dream is not yet a reality.
-The examples using diagnostic plots to assess LIME in this paper show frequent \kge{instances when the claims about LIME are not met} .
+The examples using diagnostic plots to assess LIME in this paper show frequent instances when the claims about LIME are not met .
 We hope that our plots provide motivation to assess LIME explanations, to not blindly use the default settings (even if it is not clear how to tune the parameters), and to encourage work  improving LIME, so that it can be a lime and not a lemon.
@@
 
-\kge{The \emph{lime} R package uses a ridge regression fit using the \emph{glmnet} R package \citep{simon:2011} as the explainer model.
-Note that the ridge regression penalty parameter (referred to as $\lambda$ in \emph{glmnet}) is usually treated as a tuning parameter, but the \emph{lime} R package always sets $\lambda$ to 2 divided by the number of observations in the simulated dataset.}
+The \emph{lime} R package uses a ridge regression fit using the \emph{glmnet} R package \citep{simon:2011} as the explainer model.
+Note that the ridge regression penalty parameter (referred to as $\lambda$ in \emph{glmnet}) is usually treated as a tuning parameter, but the \emph{lime} R package always sets $\lambda$ to 2 divided by the number of observations in the simulated dataset.
 
@@
 
-\section{Explanation Scatterplots Under  \kge{Density} Simulation Scenarios} \label{exp-scatter_plus}
+\section{Explanation Scatterplots Under  Density Simulation Scenarios} \label{exp-scatter_plus}
 
@@
 
-Figure \ref{fig:figure-B1} provides example explanation scatterplots \kge{for the \data \ prediction of interest when the kernel density simulation method is used.
-The plots show the relationships between the random forest prediction and the selected features of $x_1$ and $x_2$ on the left and right, respectively.}
+\autoref{fig:figure-B1} provides example explanation scatterplots for the \data \ prediction of interest when the kernel density simulation method is used.
+The plots show the relationships between the random forest prediction and the selected features of $x_1$ and $x_2$ on the left and right, respectively.
 
@@
 In order to assess the claim of linearity for the \data \ prediction of interest discussed in Section \ref{exp-scatter}, we use one of the most basic diagnostics in a statistician's tool box and draw a residual plot for the explainer model.
-This is shown in Figure \ref{fig:figure-C2} with the explainer model residuals on the y-axis and explainer model predictions on the x-axis.
+This is shown in \autoref{fig:figure-C2} with the explainer model residuals on the y-axis and explainer model predictions on the x-axis.
 The points along the x-axis have been jittered to ease the effect of the over-plotted points.
-There is a clear increasing trend in the residuals as the explainer model predictions increase\kge{,} \kge{which indicates a} violation of the \kge{ridge regression} linearity assumption.
+There is a clear increasing trend in the residuals as the explainer model predictions increase, which indicates a violation of the ridge regression linearity assumption.
 
@@
 Situation 1 is the ideal, because the explanations vary across cases but do not dependent on specific tuning parameter values.
-\kge{Situation 2 suggets global explanations and extreme explanation dependence on the tuning parameter values.}}
+Situation 2 suggests global explanations and extreme explanation dependence on the tuning parameter values.}
 \label{fig:figure-D3}
@@
 
-\kge{Figure \ref{fig:figure-F4} includes visual representations of LIME explanation from the \emph{lime} R package and explanation scatterplots for a known match observation in the the bullet example referred to as cases M for two different data simulation methods: 4-quantile-bins (left column) and 4-equal-bins (right column).
+\autoref{fig:figure-F4} includes visual representations of LIME explanation from the \emph{lime} R package and explanation scatterplots for a known match observation in the the bullet example referred to as cases M for two different data simulation methods: 4-quantile-bins (left column) and 4-equal-bins (right column).
 Both explanations appear to be more faithful to the random forest than those associated with case NM in Section \ref{bullet-assess-ex}, but the intersections of the bins could be better aligned with the regions containing similar probabilities produced by the random forest.
-Figure \ref{fig:figure-F5} includes explanation scatterplots for bullet example cases M and NM when the kernel density simulation method is used.}
+\autoref{fig:figure-F5} includes explanation scatterplots for bullet example cases M and NM when the kernel density simulation method is used.
 

### 2020-12-31 paper.tex
color removed

--- 2020-12-17 paper.tex
@@
 % Paper header (title and authors)
-\title{Visual Diagnostics of a\kge{n} \sout{Model} Explainer \kge{Model} -- Tools for the Assessment of LIME Explanations}
+\title{Visual Diagnostics of an  Explainer Model -- Tools for the Assessment of LIME Explanations}
 \author[1]{Katherine Goode*}
@@
 % Abstract and keywords
-\abstract[Abstract]{The importance of providing explanations for predictions made by black-box models has led to the development of \kge{explainer} model \sout{explainer} methods such as LIME (local interpretable model-agnostic explanations).
+\abstract[Abstract]{The importance of providing explanations for predictions made by black-box models has led to the development of explainer model  methods such as LIME (local interpretable model-agnostic explanations).
 LIME uses a surrogate model to explain the relationship between predictor variables and predictions from a black-box model in a local region around a prediction of interest.
@@
 \cyear{2020},
-\ctitle{Visual Diagnostics of a\kge{n} \sout{Model} Explainer \kge{Model} -- Tools for the Assessment of LIME Explanations},
+\ctitle{Visual Diagnostics of an  Explainer Model -- Tools for the Assessment of LIME Explanations},
 \cjournal{Stat Anal Data Min: The ASA Data Sci Journal},
@@
 \end{knitrout}
-\caption{\kge{Hypothetical scenarios depicting the effect of different weights on LIME.
+\caption{Hypothetical scenarios depicting the effect of different weights on LIME.
 (Left) An example of an explainer model with appropriate weights to provide a faithful approximation of the complex model.
-(Right) An example of an explainer model for the same prediction but with different weights that results in an explanation unfaithful to the complex model.} \sout{A conceptual depiction of a faithful LIME explainer model in the immediate neighborhood of a prediction of interest \kge{for a hypothetical black-box model trained using two features: Feature 1 (left) and Feature 2 (right).
-The explainer model is a ridge regression weighted by the inverse Gower distance to the prediction of interest raised to the power of \ensuremath{5\times 10^{-17}}.}} \sout{The predictions from a hypothetical black-box model are plotted against the standardized values of the two hypothetical predictor variables.
-The diamond shaped points represent the location of a prediction of interest.
-The size and opacity of the circular points indicate the weight assigned based on the distance to the prediction of interest computed using the inverse of the Gower distance metric raised to the power of \ensuremath{5\times 10^{-17}}.
-The black lines represent a weighted ridge regression model used as an explainer model that reasonably captures the relationship between the black-box predictions and the features in a local region around the prediction of interest.
-That is, the explainer is faithful to the complex model and produces a reasonable explanation that Feature 1 plays a more important role in the prediction of interest than Feature 2 since the magnitude of the slope associated with Feature 1 is larger.}}
+(Right) An example of an explainer model for the same prediction but with different weights that results in an explanation unfaithful to the complex model.
+}
 \label{fig:figure-01}
@@
 In the field of statistics, there are two main uses for models: inference and prediction.
-Machine learning models \sout{are often used for the latter purpose.
-These models} have proven to perform well \kge{in problems with the latter objective} \sout{in a wide range of prediction problems}, but the accuracy of many machine learning models comes at the cost of interpretability due to their algorithmic complexity (hence the phrase "black-box models").
+Machine learning models  have proven to perform well in problems with the latter objective , but the accuracy of many machine learning models comes at the cost of interpretability due to their algorithmic complexity (hence the phrase "black-box models").
 Model interpretability allows for the understanding and assessment of how a model produces predictions.
-The lack of the ability to understand and assess a model makes it difficult to trust the model, especially in areas with high stakes decisions such as \kge{the} medical and forensics sciences.
+The lack of the ability to understand and assess a model makes it difficult to trust the model, especially in areas with high stakes decisions such as the medical and forensics sciences.
 The increased use of machine learning models in applications and the introduction of the General Data Protection Regulation (GDPR) in 2018 \citep{goodman:2016} has resulted in a dramatic increase in explainable machine learning research, which focuses on developing ways to explain output from machine learning algorithms.
@@
 \citep{fisher:2018} and \citep{strumbelj:2014}).
-In this paper, we focus on \kge{the} \sout{one specific} model-agnostic method\sout{:} \kge{of} LIME \citep{ribeiro:2016}.
-
-LIME (local interpretable model-agnostic explanations) \sout{is a method that} uses a surrogate model to relate predictor variables to black-box model predictions \sout{(i.e.
-a model explainer)} \citep{ribeiro:2016}.
-\sout{We distinguish between the terms of model explainer and explainer model: by \emph{model explainer} we denote the method for explaining a complex model using a surrogate model, while the \emph{explainer model}, or simply the \emph{explainer}, is the surrogate model.} While some \kge{explainer} model\kge{s} \sout{explainers} focus on understanding a model at the global level, LIME claims to provide explanations for individual predictions (local).
+In this paper, we focus on the  model-agnostic method of LIME \citep{ribeiro:2016}.
+
+LIME (local interpretable model-agnostic explanations)  uses a surrogate model to relate predictor variables to black-box model predictions  \citep{ribeiro:2016}.
+While some explainer models  focus on understanding a model at the global level, LIME claims to provide explanations for individual predictions (local).
 Additionally, LIME is designed to work with any model (model-agnostic) and to produce easily understandable results (explanations) \citep{ribeiro:2016}.
-Conceptually, LIME fits a simple (interpretable) model, the explainer model, \kge{to approximate} \sout{meant to capture the behavior of} the \sout{(}complex\sout{) black-box} model in a local region around a prediction of interest.
-The simple model \kge{is interpreted to identify the} \sout{then provides interpretable estimates for} variables that most influence\sout{d} the \kge{complex model} prediction\sout{made by the complex model}.
-
-\kge{While t}\sout{T}he concept of LIME is relatively simple\sout{: use an interpretable model to approximate a complex model in a local region.
-However}, a practical implementation of LIME is not straightforward, and research is being done to improve the procedure \citep{laugel:2018}.
-The current implementations of LIME \citep{pedersen:2020} \citep{ribeiro:2020} offer various tuning parameters (see Section \ref{background}) that affect the explainer model and ultimately, the explanation.
+Conceptually, LIME fits a simple (interpretable) model, the explainer model, to approximate  the complex model in a local region around a prediction of interest.
+The simple model is interpreted to identify the  variables that most influence the complex model prediction.
+
+While the concept of LIME is relatively simple, a practical implementation of LIME is not straightforward, and research is being done to improve the procedure \citep{laugel:2018}.
+The current implementations of LIME \citep{pedersen:2020, ribeiro:2020} offer various tuning parameters (see Section \ref{background}) that affect the explainer model and ultimately, the explanation.
 Since the explainer model is an approximation of the complex model and not a direct interpretation, the explanations produced by an explainer model are subject to the quality of the approximation.
-\sout{Thus, i }\kge{I}n order to achieve \kge{reasonable} \sout{accurate} explanations, the tuning parameter values selected \kge{shoud} \sout{need to} be assessed.
-
-\kge{To demonstrate the effect of a tuning parameter on LIME, we consider two different explainer models applied to the same prediction.
-Figure \ref{fig:figure-01} depicts two plots of the predictions from a hypothetical black-box model versus the feature used to train the model.
+In order to achieve reasonable  explanations, the tuning parameter values selected shoud  be assessed.
+
+To demonstrate the effect of a tuning parameter on LIME, we consider two different explainer models applied to the same prediction.
+\autoref{fig:figure-01} depicts two plots of the predictions from a hypothetical black-box model versus the feature used to train the model.
 The location of a prediction of interest is indicated by the diamonds.
 Globally, there is a clear non-linear relationship between the predictions and the feature, but the relationship could be approximated by a linear model in a local region around the prediction of interest.
-In both scenarios, a linear regression weighted by the proximity from an observation to the prediction of interest is used as the explainer model, but the proximities are computed differently as depicted by the varying sizes of the observations in the two plots.}
-
-\kge{On the left, the distance between an observation and the prediction of interest is computed using the Gower distance metric \citep{gower:1971} and then raised to the power of \ensuremath{5\times 10^{-17}} to emphasize a very local region.
+In both scenarios, a linear regression weighted by the proximity from an observation to the prediction of interest is used as the explainer model, but the proximities are computed differently as depicted by the varying sizes of the observations in the two plots.
+
+On the left, the distance between an observation and the prediction of interest is computed using the Gower distance metric \citep{gower:1971} and then raised to the power of \ensuremath{5\times 10^{-17}} to emphasize a very local region.
 The distances are subtracted from 1 to obtain a proximity.
 Here, the explainer model is faithful to the complex model since it captures the linear relationship between the black-box predictions in an immediate neighborhood of the prediction of interest.
-The slope \sout{of 0.634} explains that the black-box predictions increase as the feature increases in the local region around the prediction of interest.}
-
-\kge{For the scenario on the right, the computation of the proximities is the same except the distances are raised to a power of 1 (the default exponent in the \emph{lime} R package \citep{pedersen:2020}).
+The slope  explains that the black-box predictions increase as the feature increases in the local region around the prediction of interest.
+
+For the scenario on the right, the computation of the proximities is the same except the distances are raised to a power of 1 (the default exponent in the \emph{lime} R package \citep{pedersen:2020}).
 This causes the observations that are further away from the prediction of interest to be given larger weights than the scenario on the left.
 Here, the explainer model does not capture the linear trend near the prediction of interest, but instead, the explainer captures a more global trend.
-Without an assessment of this explainer model, the slope \sout{of -0.181} would incorrectly explain that the predictions decrease as the feature increases near the prediction of interest.} %\sout{This cannot be said of the explainer model in \autoref{fig:figure-02}.
+Without an assessment of this explainer model, the slope incorrectly suggests that the predictions decrease as the feature increases near the prediction of interest.
+%\sout{This cannot be said of the explainer model in \autoref{fig:figure-02}.
 In addition, the magnitude of the slope associated with Feature 2  () is larger than that of Feature 1 ().
@@
 
-%\kge{Figure \ref{fig:figure-01} depicts the first scenario where the weights are computed as the inverse proximity of the point to the prediction of interest computed using the Gower distance metric \citep{gower:1971} raised to the power of good_gower_power to emphasize a very local region.
-The point size represents the weight, and the black lines depict the ridge regression model given the observed prediction of interest value from the opposite feature.
-For Feature 1 (left), the explainer model captures the relationship in an immediate neighborhood around the prediction of interest with a slope of coefs_data %>% filter(case == "good", feature == "Feature 1") %>% pull(slope) %>% round(3), and for Feature 2 (right), the ridge regression has a small slope of coefs_data %>% filter(case == "good", feature == "Feature 2") %>% pull(slope) %>% round(3) that accurately reflects the absence of any global or local relationship between the black-box predictions and Feature 2.
-The magnitude of the slope associated with Feature 1 is larger than the slope of Feature 2, which suggests that Feature 1 plays a more important role in the prediction made by the black-box model for the prediction of interest.
-This explanation agrees with a visual assessment of the relationships between the predictions and predictor variables.}
-
-%\sout{\autoref{fig:figure-01} provides a visualization of this conceptual understanding of LIME.
-The two plots show the predictions from a hypothetical black-box model plotted against the two hypothetical model predictor variables.
-The diamond shaped points represent the location of the prediction of interest.
-A Gower distance metric \citep{gower:1971} is used to define locality such that the size of the points represent the inverse of the Gower distance raised to some value and indicate the proximity to the prediction of interest.
-In the example of \autoref{fig:figure-01}, an exponent of good_gower_power is used to emphasize a very local region around the prediction of interest.
-A ridge regression model weighted by the proximity values is used as the explainer model with the black-box predictions as the response variable and standardized versions of two features in the data as predictor variables.
-Standardized features allow direct comparisons of the model coefficients.
-The explainer model is depicted by the black lines in the figure.}
-
-%\sout{The plot on the left of \autoref{fig:figure-01} shows the relationship between the black-box predictions and Feature 1.
-Here, the explainer model is plotted with Feature 2 fixed at the observed value of the prediction of interest.
-The explainer model captures the relationship in an immediate neighborhood around the prediction of interest with a slope of coefs_data %>% filter(case == "good", feature == "Feature 1") %>% pull(slope) %>% round(3).
-The plot on the right shows no global or local relationships between the black-box predictions and Feature 2.
-Here, the explainer model is plotted with Feature 1 set as the observed value of the prediction of interest, and it has an appropriately small slope of coefs_data %>% filter(case == "good", feature == "Feature 2") %>% pull(slope) %>% round(3).
-The magnitude of the slope associated with Feature 1 is larger than the slope of Feature 2, which suggests that Feature 1 plays a more important role in the prediction made by the black-box model for the prediction of interest.
-This explanation agrees with a visual assessment of the relationships between the predictions and predictor variables.}
-
-%\sout{The concept of LIME is relatively simple: use an interpretable model to approximate a complex model in a local region.
-However, a practical implementation of LIME is not straightforward, and research is being done to improve the procedure \citep{laugel:2018}.
-The current implementations of LIME \citep{ribeiro:2020} \citep{pedersen:2020} offer various tuning parameters (see Section \ref{background}) that affect the explainer model and ultimately, the explanation.
-Since the explainer model is an approximation of the complex model and not a direct interpretation, the explanations produced by an explainer model are subject to the quality of the approximation.
-Thus, in order to achieve accurate explanations, the tuning parameter values selected need to be assessed.}
-
-%\kge{Figure \ref{fig:figure-02} depicts the second explainer model scenario.
-Again, the weights are computed using the Gower distance metric, but in this situation, the distances are raise to a power of bad_gower_power (the default exponent in the \emph{lime} R package).} \sout{We consider an example where the choice of exponent for the weights is crucial to the quality of the explanation.
-The plots in Figure \ref{fig:figure-02} show the same data as \autoref{fig:figure-01}, but the Gower distance metric exponent is decreased to bad_gower_power (the default exponent in the \emph{lime} R package).} This causes the observations that are further away from the prediction of interest to be given larger weights than before.
-In \autoref{fig:figure-01}, the explainer model captures the relationship between the black-box predictions in an immediate neighborhood of the prediction of interest.
-This cannot be said of the explainer model in \autoref{fig:figure-02}.
-In addition, the magnitude of the slope associated with Feature 2  (coefs_data %>% filter(case == "bad", feature == "Feature 2") %>% pull(slope) %>% round(3) %>% abs()) is larger than that of Feature 1 (coefs_data %>% filter(case == "bad", feature == "Feature 1") %>% pull(slope) %>% round(3) %>% abs()).
-Thus, this explainer model actually provides a misleading explanation that Feature 2 plays a more important role in the prediction of interest.
-
-% \begin{figure*}[!thp]
-% <<figure-02, out.width = '6.25in', fig.width = 7.95, fig.height = 3.25, warning = FALSE, eval = FALSE>>=
-% 
-% # Specify the figure size (for determining font size)
-% f2_ow = 6.25
-% f2_fw = 7.95
-% f2_fs = fs * (f2_fw / f2_ow)
-% 
-% # Plot of good explainer model
-% ggplot() +
-%   facet_grid(. ~ feature, switch = "x") +
-%   geom_point(
-%     data = lime_data_gathered %>% 
-%       mutate(
-%         feature = fct_recode(
-%           feature,
-%           "Feature 1 (standardized)" = "Feature 1",
-%           "Feature 2 (standardized)" = "Feature 2"
-%           )
-%         ),
-%     mapping = aes(
-%       x = feature_stnd_value,
-%       y = prediction,
-%       size = distance_value,
-%       color = distance
-%     ), 
-%     alpha = 0.6
-%   ) +
-%   geom_abline(
-%     data = coefs_data %>% 
-%       filter(case == "bad") %>% 
-%       mutate(
-%         feature = fct_recode(
-%           feature,
-%           "Feature 1 (standardized)" = "Feature 1",
-%           "Feature 2 (standardized)" = "Feature 2"
-%           )
-%         ),
-%     mapping = aes(intercept = int, slope = slope),
-%     size = 1
-%   ) +
-%   scale_color_manual(values = c("grey30", NA), guide = "none") +
-%   geom_point(
-%     data = prediction_of_interest_gathered %>% 
-%       mutate(
-%         feature = fct_recode(
-%           feature,
-%           "Feature 1 (standardized)" = "Feature 1",
-%           "Feature 2 (standardized)" = "Feature 2"
-%           )
-%         ),
-%     mapping = aes(x = feature_value,
-%                   y = prediction,
-%                   fill = color),
-%     color = "black",
-%     size = 5,
-%     shape = 23,
-%     alpha = 0.75
-%   ) +
-%   scale_fill_manual(values = "#FAAA72") +
-%   geom_text(
-%     data = data.frame(
-%       feature_stnd_value = 1.2,
-%       prediction = 1.6,
-%       feature = c("Feature 1 (standardized)", "Feature 2 (standardized)"),
-%       slope = c(
-%         paste(
-%           "Slope:",
-%           coefs_data %>%
-%             filter(case == "bad",
-%                    feature == "Feature 1") %>%
-%             pull(slope) %>%
-%             round(3)
-%         ),
-%         paste(
-%           "Slope:",
-%           coefs_data %>%
-%             filter(case == "bad",
-%                    feature == "Feature 2") %>%
-%             pull(slope) %>%
-%             round(3)
-%         )
-%       )
-%     ),
-%     mapping = aes(x = feature_stnd_value,
-%                   y = prediction,
-%                   label = slope),
-%     family = ff,
-%     size = f2_fs / 3
-%   ) +
-%   labs(
-%     x = "",
-%     y = "Black-Box Prediction",
-%     title = "Conceptual Depiction of an Unfaithful Local Explainer Model",
-%     subtitle = paste("Gower Distance Metric Exponent:", bad_gower_power),
-%     fill = "",
-%     alpha = "Weight",
-%     size = "Weight"
-%   ) +
-%   theme_linedraw(base_family = ff, base_size = f2_fs) +
-%   theme(
-%     panel.grid.major = element_blank(),
-%     panel.grid.minor = element_blank(),
-%     axis.text.x = element_blank(),
-%     axis.ticks.x = element_blank(),
-%     axis.text.y = element_blank(),
-%     axis.ticks.y = element_blank(),
-%     strip.placement = "outside",
-%     strip.background = element_rect(color = "white", fill = "white"),
-%     strip.text.x = element_text(size = f2_fs, color = "black"),
-%     plot.title = element_text(size = f2_fs)
-%   ) +
-%   guides(
-%     fill = guide_legend(order = 1),
-%     size = guide_legend(order = 2),
-%     alpha = guide_legend(order = 2)
-%   )
-% 
-% @
-% \caption{A conceptual depiction of an unfaithful local explainer model in the immediate neighborhood of a prediction of interest.
-A\kge{gain, a weighted} ridge regression \kge{is used as the explainer model} \sout{is fit to the same hypothetical black-box model predictions and predictor variables as in \autoref{fig:figure-01}}, but the \kge{Gower distance is raised to a power} \sout{weights are computed using a Gower exponent} of 1.
-\sout{The explainer model is unfaithful to the complex model in any immediate neighborhood of the prediction of interest.}}
-% \label{fig:figure-02}
-% \end{figure*}
-
-\kge{\autoref{fig:figure-01} demonstrates a simple example in which the explanation quality varies drastically when different weights are used.
-Other concerns with LIME have been raised in the literature.} \sout{Several sources in the literature discuss the performance of LIME.} \kge{\citet{laugel:2018} and \citet{molnar:2019} discuss the difficulty specifying a local region with LIME due to both} \sout{One of the biggest difficulties with LIME is determining how to specify a local region \citep{laugel:2018} \citep{molnar:2019}.
-This is due to} an unclear definition of \kge{what is} a "local region" and how to apply LIME to achieve an appropriate local region\sout{ as demonstrated by \autoref{fig:figure-02}}.
-\kge{\citet{laugel:2018} also present examples of LIME explanations that are clearly global and not local.} \kge{A different concern about LIME is raised by} \citet{alvarezmelis:2018} \sout{raise a concern} pertaining to the robustness of explanations from LIME and other \kge{explainer} model\kge{s} \sout{explainers}: they find that even small changes in predictor variables can lead to very different LIME explanations.
-\kge{Even the original authors of LIME,} \sout{Additionally,} \citet{ribeiro:2016}\kge{,} acknowledge that if a linear model is used as the explainer, LIME relies on a linear approximation of the explainer model to the complex model and state "if the underlying model is highly non-linear even in the locality of the prediction, there may not be a faithful explanation".
-
-\sout{As a result of the various ways LIME can fail, it is important to assess LIME explanations.
-We suggest the use of visual diagnostics for assessment.
-In this paper,} \kge{Without an assessment of the LIME explainer model, the user is putting trust in another black-box procedure to explain the complex black-box model.
-In this paper, we stress the importance of assessing the LIME explainer model.} \kge{To do this, w}e lay out the set of claims about LIME made by \citet{ribeiro:2016}, and \kge{we provide a toolkit of visual diagnostics} \sout{propose three visualizations} for the assessment of these claims: (1) \emph{explanation scatterplots}, (2) \emph{feature heatmaps}, (3) \emph{assessment metric plots}.
-\kge{Using these visual diagnostics, we demonstrate problematic examples of LIME explanations where the claims about LIME are not met and the explanations are highly dependent on tuning parameter values without a clear way to identify a set of tuning parameter values that produce the "best" explanations.}
+\autoref{fig:figure-01} demonstrates a simple example in which the explanation quality varies drastically when different weights are used.
+Other concerns with LIME have been raised in the literature: \citet{laugel:2018} and \citet{molnar:2019} discuss the difficulty specifying a local region with LIME due to both  an unclear definition of what is a "local region" and how to apply LIME to achieve an appropriate local region.
+\citet{laugel:2018} also present examples of LIME explanations that are clearly global and not local.
+A different concern about LIME is raised by \citet{alvarezmelis:2018}  pertaining to the robustness of explanations from LIME and other explainer models : they find that even small changes in predictor variables can lead to very different LIME explanations.
+Even the original authors of LIME,  \citet{ribeiro:2016}, acknowledge that if a linear model is used as the explainer, LIME relies on a linear approximation of the explainer model to the complex model and state "if the underlying model is highly non-linear even in the locality of the prediction, there may not be a faithful explanation".
+
+ Without an assessment of the LIME explainer model, the user is putting trust in another black-box procedure to explain the complex black-box model.
+In this paper, we stress the importance of assessing the LIME explainer model.
+To do this, we lay out the set of claims about LIME made by \citet{ribeiro:2016}, and we provide a toolkit of visual diagnostics  for the assessment of these claims: (1) \emph{explanation scatterplots}, (2) \emph{feature heatmaps}, (3) \emph{assessment metric plots}.
+Using these visual diagnostics, we demonstrate problematic examples of LIME explanations where the claims about LIME are not met and the explanations are highly dependent on tuning parameter values without a clear way to identify a set of tuning parameter values that produce the "best" explanations.
 
 While LIME is implemented for image, tabular, and text data, we only focus on tabular data.
-For additional simplicity, we only discuss classification prediction models with a dichotomous response \sout{variable} and continuous predictor\sout{ variable}s.
-However, the proposed diagnostics may be extended to \kge{other} \sout{a wider range of} situations.
+For additional simplicity, we only discuss classification prediction models with a dichotomous response  and continuous predictors.
+However, the proposed diagnostics may be extended to other  situations.
 
 The remainder of the paper is structured as follows.
-Section \ref{background} provides background and claims made by \citet{ribeiro:2016} about LIME.
+Section ~\ref{background} provides background and claims made by \citet{ribeiro:2016} about LIME.
 We introduce the suggested diagnostic plots in Section \ref{diagnostics}.
-Then in Section \ref{application}, we demonstrate the use of the diagnostics to assess LIME explanations for a random forest  fit to a forensics bullet matching dataset.
-Section \ref{discussion} concludes with a discussion on extensions and limitations of the diagnostic plots and concerns about LIME in regards to the claims made by \citet{ribeiro:2016} brought about by the visualization examples in this paper that agree with \citet{alvarezmelis:2018}, \citet{laugel:2018}, and \citet{molnar:2019}.
+Then in Section~\ref{application}, we demonstrate the use of the diagnostics to assess LIME explanations for a random forest  fit to a forensics bullet matching dataset.
+Section~\ref{discussion} concludes with a discussion on extensions and limitations of the diagnostic plots and concerns about LIME in regards to the claims made by~\citet{ribeiro:2016} brought about by the visualization examples in this paper that agree with \citet{alvarezmelis:2018, laugel:2018}, and \citet{molnar:2019}.
 
@@
 The forked version is functionally indistinguishable from \citeauthor{pedersen:2020}'s implementation but allows us to export internal values relevant for an assessment of the explainer.
-The \kge{code for the} diagnostic plots \sout{included in this paper} \kge{is stored in} \sout{are created using} the R package \emph{limeaid} \citep{goode:2020}.
+The code for the diagnostic plots  is stored in  the R package \emph{limeaid} \citep{goode:2020}.
 
@@
 An adaption of the Python package in R has been implemented and made available by Thomas Lin-Pedersen \citep{pedersen:2020}.
-\kge{In both implementations, a ridge regression model is used as the explainer model, and} \sout{During the application of LIME, t} the user is asked to select various tuning parameter options: the number of features to return in the explanation, the simulation method, the feature selection method, and how the weights are computed.
+In both implementations, a ridge regression model is used as the explainer model, and  the user is asked to select various tuning parameter options: the number of features to return in the explanation, the simulation method, the feature selection method, and how the weights are computed.
 The discussion of parameter choices and implementation details of LIME in this paper are based on the R package.
-\kge{See Appendix~\ref{lime-details} for}
-an overview of the options available for the tuning parameters\sout{ is included in Appendix~\ref{lime-details}}.
+See Appendix~\ref{lime-details} for
+an overview of the options available for the tuning parameters.
 
@@
 \end{knitrout}
-\caption{Plots of $x_2$ versus $x_1$ from the \kge{\data \ } training (left) and testing (right) sets\sout{ of the \data \ } introduced in Section \ref{diagnostics} \sout{.
-T} \kge{with t}he true classification boundary \sout{is} shown as a solid black line\sout{ in both plots}.
-\sout{The color of the training data represents the value of the observed response variable ($y$).
-The color of the testing data represents the random forest probability that an observation belongs to the category of blue.} \kge{In the testing set, the open black circles identify cases misclassified by the random forest, and the diamond indicates a prediction of interest.} \sout{The 18 cases that are misclassified by the random forest are identified by black circles.} \sout{The prediction of interest \kge{in the test data} \sout{to explain} is indicated by a diamond.}}
+\caption{Plots of $x_2$ versus $x_1$ from the \data \  training (left) and testing (right) sets introduced in Section \ref{diagnostics}  with the true classification boundary  shown as a solid black line.
+In the testing set, the open black circles identify cases misclassified by the random forest, and the diamond indicates a prediction of interest.
+}
 \label{fig:figure-02}
@@
 (right) \emph{Explanation Scatterplot}.
-\sout{The points represent the simulated data colored by the random forest probabilities and sized by the assigned LIME weights.
-The prediction of interest is shown as the diamond shaped point.
-The explainer model indicator variables associated with $x_1$ and $x_2$ (quantile bins containing the prediction of interest) are depicted by the solid lines.
-The line colors represent the explainer model coefficient signs and indicate whether the feature supports a prediction of `blue' (blue lines) or supports a prediction of `red' (red lines).} \kge{An explanation scatterplot associated with the explanation \sout{for the prediction of interest depicted} on the left.} \sout{This figure shows that t}\kge{T}he \kge{4} quantile bins \kge{over simplify} \sout{are not flexible enough to capture}
-the relationship between the random forest predictions and the $x_1$ and $x_2$ values \kge{near the prediction of interest}.}
+An explanation scatterplot associated with the explanation  on the left.
+The four quantile bins over-simplify
+the relationship between the random forest predictions and the $x_1$ and $x_2$ values near the prediction of interest.}
 \label{fig:figure-03}
@@
 
-In this section, we introduce three visual diagnostic plots \sout{for the assessment of LIME.
-The plots focus on different levels of application of LIME (e.g.
-on explanation versus a set of explanations) to} \kge{that} assess the LIME claims from different perspectives:
+In this section, we introduce three visual diagnostic plots  that assess the LIME claims from different perspectives:
 
@@
 To demonstrate the visual diagnostics, we generate an example dataset that will be referred to as the \data.
-The \data \ contains 600 observations with \sout{three features and one response variable.
-The} features\sout{,} \kge{of} $x_1$\sout{,} \kge{and} $x_2$ \kge{independently sampled from Unif(-10, 10) distributions}\sout{,} and $x_3$\sout{,} \sout{\kge{that} are randomly sampled from Unif(-10, 10), Unif(-10, 10), and} \kge{sampled from a} $\mbox{N}(0,1)$ distribution\sout{s, respectively}.
-A binary response variable $y$ is created using a \sout{rotated} sine curve \sout{.
-In particular, let} \kge{such that}
+The \data \ contains 600 observations with  features of $x_1$ and $x_2$ independently sampled from Unif(-10, 10) distributions and $x_3$  sampled from a $\mbox{N}(0,1)$ distribution.
+A binary response variable $y$ is created using a  sine curve  such that
 \begin{eqnarray}\label{eq:data}
@@
 \end{eqnarray}
-where $x'_1=x_1\cos(\theta)-x_2\sin(\theta)$\kge{,} \sout{and} $x'_2=x_1\sin(\theta)+x_2\cos(\theta)$\kge{, and} \sout{where} $\theta=-0.9$. \sout{Then $y$ is defined as
+where $x'_1=x_1\cos(\theta)-x_2\sin(\theta)$,  $x'_2=x_1\sin(\theta)+x_2\cos(\theta)$, and  $\theta=-0.9$. \sout{Then $y$ is defined as
 \begin{eqnarray}\label{eq:data}
@@
 Note that due to the creation of $y$ in this manner, $y$ is dependent on $x_1$ and $x_2$ and independent of $x_3$.
-The dataset is \kge{randomly} divided into training and testing sets of 500 and 100 observations, respectively.
-A random forest is fit \kge{to the training set} using the R package \emph{randomForest} (version 4.6.14) \citep{liaw:2002} with the default settings\sout{.
-The model} \kge{and} is applied to the test set to obtain predictions.
+The dataset is randomly divided into training and testing sets of 500 and 100 observations, respectively.
+A random forest is fit to the training set using the R package \emph{randomForest} (version 4.6.14) \citep{liaw:2002} with the default settings and is applied to the test set to obtain predictions.
 
 \autoref{fig:figure-02} shows scatterplots of $x_2$ versus $x_1$ from the training data (left) and the testing data (right).
-Both plots include the true classification boundary \sout{of the rotated sine function plotted} as the solid black line.
+Both plots include the true classification boundary  as the solid black line.
 The training data are colored by the observed response variable ($y$), and the testing data are colored by random forest prediction probabilities.
-The random forest  misclassifies 18 points, which are all located near the classification boundary \sout{.
-These are} \kge{and} identified by open circles\sout{ in \autoref{fig:figure-02}}.
-
-From these scatterplots, we \sout{also} see that the global relationship between response $y$ and features $x_1$ and $x_2$ is linear: the probability for label blue increases with the difference between features $x_2$ and $x_1$.
+The random forest  misclassifies 18 points, which are all located near the classification boundary  and identified by open circles.
+
+From these scatterplots, we  see that the global relationship between response $y$ and features $x_1$ and $x_2$ is linear: the probability for label blue increases with the difference between features $x_2$ and $x_1$.
 Locally, the relationship between $y$ and features $x_2$ and $x_1$ varies a lot more around the line of identity.
 Here, the relationship is determined by the sine wave.
-However, the sine is a good-natured function that can be approximated well linearly in local regions \kge{as shown in Figure \ref{fig:figure-01}}.
-
-We apply LIME using six sets of tuning parameter values to all observations in the \data \ test set to observe \kge{explanation} variability\sout{ across tuning parameter values}.
-\kge{Five of the LIME applications use a} \sout{A} quantile bin based simulation method (samples are simulated uniformly from a \kge{feature using a} specified number of quantile bins) \sout{is used for five of the LIME applications} with the number of bins varying from 2 to 6 by application.
+However, the sine is a good-natured function that can be approximated well linearly in local regions as shown in \autoref{fig:figure-01}.
+
+We apply LIME using six sets of tuning parameter values to all observations in the \data \ test set to observe explanation variability.
+Five of the LIME applications use a  quantile bin based simulation method (samples are simulated uniformly from a feature using a specified number of quantile bins)  with the number of bins varying from 2 to 6 by application.
 We use 6 bins as the maximum, because the complexity of the explanations increases with the number of bins.
-Note that 4-quantile-bins \kge{is} \sout{are} the default method in the \emph{lime} R package.
+Note that 4-quantile-bins is  the default method in the \emph{lime} R package.
 The sixth application of LIME uses a kernel density simulation method (samples are drawn from kernel density approximations of the feature distributions).
 The default methods for feature selection (forward selection) and the computation of the weights (Gower distance raised to an exponent of 1) are used for all applications.
-See Appendix~\ref{lime-details} for \kge{more detailed} descriptions of the tuning parameters.
-
-For the presentation of the explanation scatterplot, we focus on the misclassified point \sout{with $(x_1, x_2, x_3)$ coordinates of (1.23, 8.47, -0.99)} indicated by a diamond in \autoref{fig:figure-02}.
+See Appendix~\ref{lime-details} for more detailed descriptions of the tuning parameters.
+
+For the presentation of the explanation scatterplot, we focus on the misclassified point  indicated by a diamond in \autoref{fig:figure-02}.
 Misclassified points are often of interest to explain since they may provide information about ways to improve the model.
@@
 
-Before introducing the visual diagnostics, let us consider a commonly used visualization of a LIME explanation\sout{ that is shown in Figure \ref{fig:figure-03} (left)}.
-\kge{Figure \ref{fig:figure-03} (left) depicts the explanation for the prediction of interest indicated in \autoref{fig:figure-02} obtained using 4-quantile-bins.
+Before introducing the visual diagnostics, let us consider a commonly used visualization of a LIME explanation.
+\autoref{fig:figure-03} (left) depicts the explanation for the prediction of interest indicated in \autoref{fig:figure-02} obtained using 4-quantile-bins.
 In the text at the top, the "Probability" is the random forest probability of 0.74 that the observation of interest belongs to the "Label" category of blue.
-The "Explanation Fit" is the deviance ratio of 0.21 associated with the ridge regression explainer model (often interpreted as an $R^2$), which suggests that the explainer model is not a good linear fit.}
-
-\kge{Since 4-quantile-bins are used to simulate data, LIME converts continuous predictor variables to indicator variables identifying whether the variable value falls in the same quantile bin as the prediction of interest or not.
+The "Explanation Fit" is the deviance ratio of 0.21 associated with the ridge regression explainer model (often interpreted as an $R^2$), which suggests that the explainer model is not a good linear fit.
+
+Since 4-quantile-bins are used to simulate data, LIME converts continuous predictor variables to indicator variables identifying whether the variable value falls in the same quantile bin as the prediction of interest or not.
 The indicator variables are used as the features in the ridge regression explainer model.
-The features included in the visualization are the ones selected by feature selection, the lengths of the bars represent the coefficients from the ridge regression associated with the indicator variables, and the color of a bar denotes the sign of the coefficient.
-This explainer model explains that the random forest prediction that the observation of interest belongs to the category of blue is mostly supported by the prediction of interest having a value of $x_2$ that is greater than 4.834 but somewhat contradicted by the prediction of interest having a value of $x_1$ that is greater than -0.302 and less than or equal to 4.844.} \kgc{I decided to leave the values here.
-I actually prefer it this way myself, but I cut out a lot of text from this subsection in other ways.}
-
-\sout{Before introducing the visual diagnostics, let us consider a commonly used visualization of a LIME explanation\sout{ that is shown in Figure \ref{fig:figure-03} (left)}.
-\kge{Figure \ref{fig:figure-03} (left) shows the explanation for the prediction of interest indicated in \autoref{fig:figure-02} obtained using 4-quantile-bins.} \sout{The plot is created using the \emph{lime} R package and provides a visual representation of a LIME explanation for the prediction of interest indicated in \autoref{fig:figure-02}.
-In particular, the explanation is obtained using 4-quantile-bins to simulate the data.} \kge{When quantile bins are used to simulate data}\sout{ In this scenario}, LIME converts continuous predictor variables to indicator variables identifying whether the variable value falls in the same quantile bin as the prediction of interest or not.
-The\kge{n the} indicator variables are used as the explainer model features.}
-
-\sout{The plot reports 0.74 as the random forest  probability that the observation of interest belongs to category blue (denoted as the ``label" in the plot).
-The lengths of the bars represent the coefficients from a ridge regression model (the explainer model) fit using the R package \emph{glmnet} \citep{simon:2011} associated with the indicator variables chosen via feature selection.
-The color of a bar denotes the sign of the coefficient and whether the feature "supports" or "contradicts" a random forest classification of `blue'.
-The "explanation fit" is the deviance ratio from  \emph{glmnet}.
-In other words, this is the $R^2$ value associated with the explainer model.
-In this case, it is 0.21 suggesting that the explainer model is not a good linear fit.
-However, it is commonly accepted that $R^2$ has limitations for assessing the quality of fit of a model \citep{sapra:2014} and  should not be used as the only metric in a model assessment.}
-
-\sout{The explanation for the prediction of interest depicted in Figure \ref{fig:figure-03} is interpreted as follows.
-A random forest classification of blue is supported by the prediction of interest having a value of $x_2$ that is greater than 4.834, but the prediction of interest having a value of $x_1$ that is greater than -0.302 and less than or equal to 4.844 provides support against a classification of blue.
-Since the weight associated with $x_2$ has a larger magnitude than the weight associated with $x_1$, LIME explains that $x_2$ plays a more important role in the random forest prediction.
-Additionally, consider that since the support for blue by $x_2$ outweighs the support for red by $x_1$, the explainer model overall favors a label of blue for the prediction of interest, which agrees with the random forest probability of 0.744 for blue.
-Note that both models classify the observation incorrectly.}
+The features included in the visualization are the ones selected by feature selection, the lengths of the bars represent the coefficients from the ridge regression associated with the indicator variables, while the color of a bar denotes the sign of the coefficient.
+This explainer model suggests that a random forest prediction of `blue' for this observation is mostly supported by the prediction of interest having a value of $x_2$ that is greater than 4.834 but somewhat contradicted by the prediction of interest having a value of $x_1$ that is greater than -0.302 and less than or equal to 4.844.
+\kgc{I decided to leave the values here.
+I actually prefer it this way myself, but I cut out a lot of text from this subsection in other ways.}\hh{XXX }
 
@@
 
-\kge{As a first check to determine whether the explanation depicted in \autoref{fig:figure-03} (left) is trustworthy, we note that since the support for blue by $x_2$ outweighs the support for red by $x_1$, the explainer model overall favors a label of blue for the prediction of interest agreeing with the random forest probability.
+As a first check to determine whether the explanation depicted in \autoref{fig:figure-03} (left) is trustworthy, we note that since the support for blue by $x_2$ outweighs the support for red by $x_1$, the explainer model overall favors a label of blue for the prediction of interest agreeing with the random forest probability.
 In fact, both random forest and explainer model classify the observation incorrectly.
-However, based on the information in \autoref{fig:figure-03} (left) alone, it is not possible to make an informed assessment of the explanation.} \sout{Based on the plot on the left of \autoref{fig:figure-03} alone, it is not possible to make an informed assessment of the explanation.}
+However, based on the information in \autoref{fig:figure-03} (left) alone, it is not possible to make an informed assessment of the explanation.
 
@@
 The point size represents the weight assigned by LIME.
-In order to show the LIME results for the observation of interest, lines are drawn on top of the points\sout{.
-These lines}  represent\kge{ing} the boundaries of the indicator variables used to fit the explainer model.
+In order to show the LIME results for the observation of interest, lines are drawn on top of the points  representing the boundaries of the indicator variables used to fit the explainer model.
 The line color  denotes whether LIME indicates that a feature supports or contradicts a class prediction.
-\sout{Appendix \ref{exp-scatter_plus} addresses the explanation scatterplot formats in other LIME simulation scenarios.}
 
@@
 
-\sout{Two hypothetical examples of feature heatmaps are included in \autoref{fig:figure-04}.
-The plots are created with the assumption that LIME is applied to select the top feature out of $p=4$  features for $n=10$ cases with $t=5$ sets of tuning parameter values.
-Situation 1 is an example where the features selected are consistent across tuning parameter values within a case but vary across cases within a tuning parameter value.
-This is the ideal situation, because the LIME explanations do not depend on the tuning parameters but do depend on the location of the observation in the feature space.
-Situation 2 is an example where the selected features vary across tuning parameter values within a case but are consistent across cases within a tuning parameter value.
-This situation indicates that the features selected by LIME are dependent on the tuning parameters, and the explanations may not be  local, because the same feature is chosen regardless of the case.
-In practice, it is expected that the plot will exhibit a combination of these two situations.}
-
 \autoref{fig:figure-04} shows a feature heatmap for the LIME applications to the 100 observations in the \data \ test set.
 The most important and second most important features selected by LIME are shown in in the top and bottom facets, respectively.
-For the quantile bins, the original features prior to \kge{being converted to indicator variables} \sout{the indicator variable transformation} are included since it is obvious that different features would be selected when the sizes of the bins change.
-This figure shows that for kernel density and 2-quantile-bins, LIME \kge{produces global explanations since} \sout{selects} $x_1$ \kge{is selected} as the most important feature and $x_2$ \kge{is selected} as the second most important feature across all cases in the test set.
-\sout{These explanations are not local.} There is variability in the features selected by LIME for 3- to 6-quantile-bins suggesting more local explanations.
+For the quantile bins, the original features prior to being converted to indicator variables  are included since it is obvious that different features would be selected when the sizes of the bins change.
+This figure shows that for kernel density and 2-quantile-bins, LIME produces global explanations since  $x_1$ is selected as the most important feature and $x_2$ is selected as the second most important feature across all cases in the test set.
+There is variability in the features selected by LIME for 3- to 6-quantile-bins suggesting more local explanations.
 There are signs of vertical striping, which suggests a dependence on tuning parameters.
-Note that the explanations from 3- and 5-quantile-bins include the selection of the random noise variable ($x_3$) as an important variable in many predictions, which \kge{would not be expected to be important to a random forest}\sout{should not be the case}.
-\kge{It is unclear whether the random forest is using a variable that would not be expected to be important or LIME is incorrectly identifying the important variable when 3- and 5- quantile bins are used.} \sout{The pattern seen in the explanations for 3- to 6-quantile-bins may suggest local explanations, but the dependence on tuning parameters makes it unclear which set of explanations to use.}
+Note that the explanations from 3- and 5-quantile-bins include the selection of the random noise variable ($x_3$) as an important variable in many predictions, which would not be expected to be important to a random forest.
+It is unclear whether the random forest is using a variable that would not be expected to be important or LIME is incorrectly identifying the important variable when 3- and 5- quantile bins are used.
 
@@
 \caption{\emph{Assessment metric plot}.
-\kge{This example assessment metric plot contains metrics} \sout{The assessment metrics} computed on the applications of LIME to the \data \ test set\sout{are included in this example assessment metric plot}.
-\sout{Each horizontal facet corresponds to one of three metrics: average $R^2$, average fidelity, or MSEE.
-The LIME tuning parameter values (simulation methods in this example) are plotted on the x-axis, and the metric values are shown on the y-axis.
-The points are colored by rank (within a metric) indicating best to worst (dark to light).} The kernel density simulation methods performs well across all three metrics.}
+This example assessment metric plot contains metrics  computed on the applications of LIME to the \data \ test set.
+The kernel density simulation methods performs well across all three metrics.}
 \label{fig:figure-05}
@@
 MSEE provides almost the exact opposite results with 6-quantile-bins performing the best and 2-quantile-bins performing the worst.
-Average fidelity and MSEE are similar metrics, \kge{but} \sout{so it is \sout{not} surprising that they \sout{would} \kge{do not} agree in this example.
-\kge{The discrepancy may be because} \sout{Another factor might be that}} MSEE only takes the prediction of interest into account and not the full simulated dataset \kge{as average fidelity does.} \kge{This suggests that 6-quantile-bins produce an explainer model more faithful for the prediction of interest while 2-quantile-bins produce an explainer model more faithful over all simulated data observations}.
-\sout{The contradiction between metrics makes it difficult to identify which simulation method to trust.}
-
-Recall\kge{,} \sout{that} \autoref{fig:figure-04} \kge{shows} \sout{indicates that} the kernel density method \kge{returns the same explanations} \sout{selected the same feature} across all cases in the test set\sout{ for both the first and second features.
-It appears that} \kge{suggesting} a global trend may be the best explanation for this example\kge{.}\sout{, which} \kge{This} may be reasonable considering that we \kge{would expect} \sout{know that both} $x_1$ and $x_2$ \kge{to be} \sout{are} the two features \sout{that should be the features} used by the random forest to distinguish between response categories.
-\kge{However, futher exploration of individual explanations using explanation scatterplots may help to identify the tuning parameter values that produce the most trustworthy explanations.}
+Average fidelity and MSEE are similar metrics, but  MSEE only takes the prediction of interest into account and not the full simulated dataset as average fidelity does.
+This suggests that 6-quantile-bins produce an explainer model more faithful for the prediction of interest while 2-quantile-bins produce an explainer model more faithful over all simulated data observations.
+
+Recall,  \autoref{fig:figure-04} shows  the kernel density method returns the same explanations  across all cases in the test set suggesting a global trend may be the best explanation for this example.
+This may be reasonable considering that we would expect  $x_1$ and $x_2$ to be  the two features  used by the random forest to distinguish between response categories.
+However, futher exploration of individual explanations using explanation scatterplots may help to identify the tuning parameter values that produce the most trustworthy explanations.
 
@@
 
-In this section, we \sout{provide a discussion of the application of} \kge{apply} the visual diagnostics for LIME explanations to a practical data problem investigating the similarity of marks on fired bullets.
+In this section, we  apply the visual diagnostics for LIME explanations to a practical data problem investigating the similarity of marks on fired bullets.
 
@@
 \end{knitrout}
-\caption{Example bullet signatures.
-The \sout{bullet} signatures \kge{are from} \sout{correspond to} the same land and therefore have very similar patterns.
-\sout{The \citet{hare:2017} random forest is fit using various features that measure the similarity between two such signatures.}}
+\caption{Example bullet signatures. The  signatures are from  the same land and therefore have very similar patterns. }
 \label{fig:figure-07}
@@
 \end{knitrout}
-\caption{Parallel coordinate plots of the \kge{bullet matching} \sout{\citet{hare:2017}} random forest predictions\sout{from the training (top \kge{row}\sout{facet}) and testing (bottom \kge{row}\sout{facet}) data}.
-\sout{The observations are separated by known matching (right column) and non-matching (left column) signatures.
-The y-axis shows the standardized feature values, and the x-axis shows the features used to fit the random forest (ordered by random forest impurity based feature importance).} Each line corresponds to an observation, and the line color represents the associated random forest probability.
+\caption{Parallel coordinate plots of the bullet matching  random forest predictions.
+Each line corresponds to an observation, and the line color represents the associated random forest probability.
 There are clear relationships between the feature values and the random forest probabilities.}
@@
 
-\kge{In \autoref{fig:figure-08}, } \sout{W}\kge{w}e consider a global visualization of the relationship between the random forest predictions and the model features with a parallel coordinate plot of the training data (top \kge{row}\sout{facet}) and testing data (bottom \kge{row}\sout{facets})\sout{ (\autoref{fig:figure-08})}.
+In \autoref{fig:figure-08},  we consider a global visualization of the relationship between the random forest predictions and the model features with a parallel coordinate plot of the training data (top row) and testing data (bottom row).
 In the training data we observe a clear difference in feature values based on whether the corresponding random forest scores are close to 1 or 0.
@@
 
-First, applications of 2-quantile-bins\kge{, 2-equal-bins, and somewhat for the density based} simulations produce the same explanations for almost all cases and LIME tuning parameter values\kge{,}\sout{.
-This suggests that the LIME} \kge{suggesting these} explanations are global and not local.
+First, applications of 2-quantile-bins, 2-equal-bins, and somewhat for the density based simulations produce the same explanations for almost all cases and LIME tuning parameter values, suggesting these explanations are global and not local.
 Second, within a simulation method, the features selected by LIME for an observation do not appear to vary by the Gower power.
-However, the LIME explanation\kge{s} for an observation often var\kge{y}\sout{ies} across simulation methods.
+However, the LIME explanations for an observation often vary across simulation methods.
 With the equal bins, there are vertical stripes that suggest a dependence of the LIME explanations on the number of bins.
@@
 \caption{Assessment metric plot for the applications of LIME on the bullet comparison data test set.
-There are discrepancies in \kge{metric} performance\kge{s}\sout{ across metrics for a set of tuning parameter values}, but \sout{based on the} overall\sout{ performance of all \sout{three} metrics}, 4-equal-bins with a Gower power of 0.5 appear\sout{s} to perform the best.}
+There are discrepancies in metric performances, but  overall, 4-equal-bins with a Gower power of 0.5 appear to perform the best.}
 \label{fig:figure-10}
@@
 However, there is consistency in results across different Gower powers.
-The applications using a power of 0.5 perform the best or as well as the other powers across all simulation methods suggesting that the power that leads to a more \kge{local} \sout{global} explanation is preferred\sout{ by LIME}.
-It is not \kge{obvious} \sout{apparent} which set of tuning parameters is the best\kge{, but}\sout{.
-C}\kge{c}onsidering all three metrics, we might conclude that the 4-equal-bins with a Gower power of 0.5 performs better than the other tuning parameter values considered.
-
-To provide a more detailed view of explanations obtained using different tuning parameter values, we \kge{consider explanation scatterplots for one prediction of interest} \sout{take a closer look at explanations for two observations of interest, which will be} referred to as case NM (a known non-match)\sout{ and case NM (a known non-match), using explanation scatterplots.} \kge{shown in} Figure~\ref{fig:figure-11} \sout{includes} \kge{along with} the visual \sout{representation plots of} explanation\sout{s} \kge{plots} \sout{(}from \kge{the} \emph{lime} \kge{R package}\sout{)\ and explanation scatterplots for cases M and NM}.
+The applications using a power of 0.5 perform the best or as well as the other powers across all simulation methods suggesting that the power that leads to a more local  explanation is preferred.
+It is not obvious  which set of tuning parameters is the best, but considering all three metrics, we might conclude that the 4-equal-bins with a Gower power of 0.5 performs better than the other tuning parameter values considered.
+
+To provide a more detailed view of explanations obtained using different tuning parameter values, we consider explanation scatterplots for one prediction of interest  referred to as case NM (a known non-match) shown in Figure~\ref{fig:figure-11}  along with the visual  explanation plots from the \emph{lime} R package.
 Plots for 4-equal-bins and 4-quantile-bins are included to depict tuning parameter values with good (4-equal-bins) and mediocre (4-quantile-bins) performance based on the assessment metric plot.
-\kge{Also, recall that 4-quantile-bins are the default option in the \emph{lime} R package.} \sout{Plots} \kge{Explanation scatterplots for a known match, referred to as case M, and} for the kernel density simulation method \kge{applied to both M and NM} are included in Appendix~\ref{bullets-plus}\sout{ (Figure \ref{fig:figure-F5})}.
-
-\kge{When 4-quantile-bins are applied to case NM, LIME explains that the feature of mismatches, rough correlation, and distance are important and support a prediction of the class true (Figure~\ref{fig:figure-11} top left).
-However, this explanation contradicts that random forest prediction probability that correctly provides evidence that the observation is a non-match.
+%\kge{Also, recall that 4-quantile-bins are the default option in the \emph{lime} R package.}
+Explanation scatterplots for a known match, referred to as case M, and for the kernel density simulation method applied to both M and NM are included in Appendix~\ref{bullets-plus}.
+
+When 4-quantile-bins are applied to case NM, LIME explains that the values of mismatches, rough correlation, and distance are important and support a prediction of the class true (Figure~\ref{fig:figure-11} top left).
+However, this explanation contradicts the random forest prediction which correctly assigns the observation  a non-match.
 The explanation scatterplot (Figure~\ref{fig:figure-11} bottom left) clarifies the reason for the highly unfaithful explanation.
-Case NM falls on boundaries of regions for these three features where the random forest predictions transition from below 0.5 to above 0.5.
-However, the regions created when applying LIME from the 4-quantile-bins where case NM falls contain mostly observations with random forest predictions above 0.5.
-leading to the unfaithful explanation.}
-
-\kge{Figure~\ref{fig:figure-11} (top right) shows the LIME explanation for case NM when 4-equal-bins are used.
+Case NM falls on the boundary of regions for each of these three features where the random forest predictions transition from below 0.5 to above 0.5.
+However, the regions used when applying LIME from the 4-quantile-bins where case NM falls contain mostly observations with random forest predictions above 0.5, leading to the unfaithful explanation.
+
+Figure~\ref{fig:figure-11} (top right) shows the LIME explanation for case NM when 4-equal-bins are used.
 Here, the features identified as important are distance and mismatches, which support a match and matches, which supports a non-match.
 This explanation is more faithful having at least one feature supporting a non-match and has a better linear fit, but the most important feature identified by LIME still supports a match, contradicting the random forest.
-The explanation scatterplot (Figure~\ref{fig:figure-11} bottom right) again shows the features supporting a match arise from NM falling on the boundary of random forest prediction regions that are not well captured by the LIME bins.}
-
-\kge{Without an assessment of the LIME explanations, the default method would produce poor explanations such as the one shown in Figure~\ref{fig:figure-11} (left column).
+The explanation scatterplot (Figure~\ref{fig:figure-11} bottom right) again shows the features supporting a match arise from NM falling on the boundary of random forest prediction regions that are not well captured by the LIME bins.
+
+Without an assessment of the LIME explanations, the default method would produce poor explanations such as the one shown in Figure~\ref{fig:figure-11} (left column).
 Our assessment here led to better explanations when the four equal bins are used.
 However, the explanation quality is still lacking from the one prediction considered.
-Additional investigations using explanations scatterplots would help to determine whether to trust this set of explanations, continue tuning the LIME parameters, or use another approach to provide better insight.}
-
-\sout{We focus on the explanation for case NM with 4-quantile-bins.
-The explanation plot from the \emph{lime} R package shows that the observed values of NM of mismatches less than or equal to 7.17, rough correlation (rough\_cor) greater than 0.05, and D less than or equal to 0.002 support a random forest prediction in favor of a match.
-The scatter plots show that many of the simulated values in the rectangular regions with mismatches less than 7.17, rough correlation greater than 0.05, and distance less than or equal to 0.002 have random forest predictions greater than 0.5, which agrees with the LIME explanation.
-However, the random forest assigns a probability of 0.21 to case NM, which is not explained by the LIME explanation that provides all explanations in support of a match.
-Instead, consider that a better explanation based on the scatterplots would be that the random forest assigned a prediction probably below 0.5 since NM has observed values of mismatches less than 5, rough correlation greater than 0.25, and distance greater than 0.001.}
-
-\sout{The other explanation scatterplots can be interpreted in a similar manner.
-The three plots depict situations where the explanations are faithful to the random forest, but the regions captured by the intersections of the bins do not align well with the regions containing similar probabilities produced by the random forest.}
+Additional investigations using explanations scatterplots would help to determine whether to trust this set of explanations, continue tuning the LIME parameters, or use another approach to provide better insight.
 
@@
 This paper highlights that while an explainer model is meant to provide clarity, it actually adds another layer of complexity to predictive models by requiring yet another model that needs to be assessed.
-Without an assessment of the explainer model, LIME is a black-box procedure \sout{of its own} requiring blind trust in the explainer model.
-We suggest the use of visual diagnostics to counteract the black-box nature of LIME\sout{ and provide three diagnostic plots}.
-\kge{We provide three diagnostic plots} \sout{The \kge{plots} \sout{visualizations} are} intended to \kge{assess whether LIME explanations meet the claims made by \citet{ribeiro:2016}.
+Without an assessment of the explainer model, LIME is a black-box procedure  requiring blind trust in the explainer model.
+We suggest the use of visual diagnostics to counteract the black-box nature of LIME.
+We provide three diagnostic plots  intended to assess whether LIME explanations meet the claims made by \citet{ribeiro:2016}.
 The examples in this paper bring to light many scenarios in which the claims are not met or are difficult to assess.
-We reconsider each of the claims and how the visual diagnostics identify their failings.} \sout{provide insight on how LIME works, assess the ability of the explainer model to capture the complex predictive model, and compare LIME explanations produced by different tuning parameter values.
-While the visualizations accomplish these tasks, they also expose examples of the failings of LIME.
-To address the discovered failings of LIME, we reconsider each of the claims about the performance of LIME made by \citet{ribeiro:2016} in light of the insights gained from the diagnostic visualizations.}
+We reconsider each of the claims and how the visual diagnostics identify their failings.
 
@@
 
-Even though an explanation will be interpretable \kge{if} \sout{as long as} the complexity of the explainer model is appropriately chosen, a lack of understanding of the \kge{explainer model} \sout{process used to create the explanation} could lead to an incorrect interpretation of the explanation.
-For example, the visualization of a LIME explanation \sout{available} from the \emph{lime} R package \citep{pedersen:2020} (\sout{shown in }Figure\sout{s} \ref{fig:figure-03} \kge{left; } \sout{and} \kge{Figure} \ref{fig:figure-11} \kge{top}) is a \sout{major} simplification of the explainer model, which could lead to \sout{under-interpreted or} misinterpreted LIME explanation\kge{s}.
-Supplementing \citet{pedersen:2020}'s compact visualization of the explanation with an explanation scatterplot that shows a more detailed visualization of the explainer model promotes a more complete understanding of the explanation (\sout{such as }Figures~\ref{fig:figure-03} \kge{right; } \sout{and} \ref{fig:figure-11} \kge{bottom}).
+Even though an explanation will be interpretable if  the complexity of the explainer model is appropriately chosen, a lack of understanding of the explainer model  could lead to an incorrect interpretation of the explanation.
+For example, the visualization of a LIME explanation  from the \emph{lime} R package \citep{pedersen:2020} (\autoref{fig:figure-03} left;   \autoref{fig:figure-11} top) is a  simplification of the explainer model, which could lead to  misinterpreted LIME explanations.
+Supplementing \citet{pedersen:2020}'s compact visualization of the explanation with an explanation scatterplot that shows a more detailed visualization of the explainer model promotes a more complete understanding of the explanation (Figures~\ref{fig:figure-03} right;   \ref{fig:figure-11} bottom).
 
 Even with an explainer model that is interpreted correctly, the interpretation is worthless if the explainer model is not \textbf{faithful} to the complex model.
-\sout{This claim can be assessed using the diagnostic plots suggested in this paper.
-Many of the visualizations in this paper highlight problems with the faithfulness of the explainer models.
-The e} \kge{E}xplanation scatterplots allow for a comparison of the explainer model to the complex model.
+Explanation scatterplots allow for a comparison of the explainer model to the complex model.
 The examples in this paper show cases where the explainer model oversimplifies the model and bins do not accurately capture the regions with similar random forest probabilities that contain the prediction of interest (Figures \ref{fig:figure-03} and \ref{fig:figure-11}).
@@
 
-\sout{In addition to assessing faithfulness by visually comparing the complex and explainer model, w}\kge{W}e \kge{also} propose a\kge{n assessment metric plot for the} visual comparison of two faithfulness metrics: MSEE and average fidelity.
-\kge{Both metrics measure faithfulness, but MSEE only accounts for the prediction of interest while average fidelity accounts for all observations in the simulated data.
-As a result, the measures may disagree (Figures \ref{fig:figure-05} and \ref{fig:figure-10}), and the user is left to determine which is preferable.} \sout{The examples of faithfulness metric comparisons in this paper both produced conflicting results (Figures \ref{fig:figure-05} and \ref{fig:figure-10}).
-This makes it difficult to decide on a recommendation of a set of tuning parameter values that produce the explanations with the most faithful explainer model.}
+We also propose an assessment metric plot for the visual comparison of two faithfulness metrics: MSEE and average fidelity.
+Both metrics measure faithfulness, but MSEE only accounts for the prediction of interest while average fidelity accounts for all observations in the simulated data.
+As a result, the measures may disagree (Figures \ref{fig:figure-05} and \ref{fig:figure-10}), and the user is left to determine which is preferable.
 
@@
 Most of the average $R^2$ values in the examples from this paper are below 0.5 suggesting a poor linear fit of the explainer models.
-A poor linear fit of the explainer model is also seen with the residual plot \kge{shown in} \sout{(}\autoref{fig:figure-C2}\sout{)}.
-
-The final claim, \textbf{localness}, is addressed by \sout{the} feature heatmap\kge{s} and \kge{explanation scatterplots}\sout{ metric comparison plots}.
-\kge{The vertical stripes seen in the feature heatmaps (Figures \ref{fig:figure-04} and \ref{fig:figure-09}) suggest global explanations produced by LIME since the same explanation is returned for almost all observations regardless of feature values.
+A poor linear fit of the explainer model is also seen with the residual plot shown in \autoref{fig:figure-C2}.
+
+The final claim, \textbf{localness}, is addressed by  feature heatmaps and explanation scatterplots.
+The vertical stripes seen in the feature heatmaps (Figures \ref{fig:figure-04} and \ref{fig:figure-09}) suggest global explanations produced by LIME since the same explanation is returned for almost all observations regardless of feature values.
 The explanation scatterplots visualize the locality of the explanation using point size to indicate weight.
-However, the lack of definition of a local region makes it difficult to assess whether the weights capture an appropriately local region.} \sout{As stated, the feature heatmap reveals that the density simulation methods in the \data \ example results in global explanations where the same features are repeatedly chosen across all (or almost all) observations in the set of explanations.
-This finding agrees with that of \citet{laugel:2018} who found LIME produced global explanations with the normal approximation simulation method.
-For the bin based simulation methods in the bullet data example, the feature heatmap shows that the features chosen for the explanations vary between the two classification categories (match versus non-match).
-This is an interesting finding that suggests that different features can play a role in the predictions of observations in different response categories.
-Furthermore, while the metric comparison plot in the bullet example does not provide agreement between metrics on a best bin based method, all metrics agree that a Gower power of 0.5 for computing the model weights associated with distance of a simulated data point from the prediction of interest is the best.
-This suggests that a \sout{less} \kge{more} local explanation provides a better explanation of the performance of the random forest.}
-
-\sout{Some of the visualizations in the paper generalize easily to any application of LIME such as the feature heatmap and metric plot.
-Other plots such as the visualizations of the LIME procedure would require extensions such as the use of scatterplot matrices to compare explanations with more than two features.}
-
-\kge{These diagnostic visualizations are a starting point that already highlight seemingly common issues with the LIME claims.
-Additions, such as visualizations of the step-by-step process of the creation of LIME explanations and} \sout{The addition of} interactivity\kge{,} \sout{to the diagnostic plots would provide additional} enhance\sout{ment of} the assessment process.
+However, the lack of definition of a local region makes it difficult to assess whether the weights capture an appropriately local region.
+
+These diagnostic visualizations are a starting point that already highlight seemingly common issues with the LIME claims.
+Additions, such as visualizations of the step-by-step process of the creation of LIME explanations and  interactivity,  enhance the assessment process.
 For example, a diagnostic plot that provides a summary of multiple LIME explanations, such as the feature heatmap, could be displayed and clicked on to reveal more detailed figures associated with individual predictions of interest, such as an explanation scatterplot.
@@
 While it would be ideal if LIME could be used as a method to provide easily understandable explanations for black-box models as \citet{ribeiro:2016} claim, that dream is not yet a reality.
-The examples using diagnostic plots to assess LIME in this paper show frequent \kge{instances when the claims about LIME are not met} \sout{issues with LIME}.
-We hope that our plots provide motivation to assess LIME explanations, to not blindly use the default settings (even if it is not clear how to tune the parameters), and to encourage work \sout{on} improving LIME, so that it can be a lime and not a lemon.
+The examples using diagnostic plots to assess LIME in this paper show frequent instances when the claims about LIME are not met .
+We hope that our plots provide motivation to assess LIME explanations, to not blindly use the default settings (even if it is not clear how to tune the parameters), and to encourage work  improving LIME, so that it can be a lime and not a lemon.
 
@@
 
-\section{Explanation Scatterplots Under \sout{Other} \kge{Density} Simulation Scenarios} \label{exp-scatter_plus}
+\section{Explanation Scatterplots Under  Density Simulation Scenarios} \label{exp-scatter_plus}
 
@@
 
-Figure \ref{fig:figure-B1} provides example explanation scatterplots \kge{for the \data \ prediction of interest when the kernel density simulation method is used.
-The plots show the relationships between the random forest prediction and the selected features of $x_1$ and $x_2$ on the left and right, respectively.} \sout{for each feature in the default LIME explanation obtained using the kernel density simulation method for the \data \ prediction of interest.} \sout{Figure \ref{fig:figure-F5} includes explanation scatterplots for the explanations generated using kernel density simulation for the bullet example cases M and NM discussed in Section \ref{bullet-assess-ex}.}
+\autoref{fig:figure-B1} provides example explanation scatterplots for the \data \ prediction of interest when the kernel density simulation method is used.
+The plots show the relationships between the random forest prediction and the selected features of $x_1$ and $x_2$ on the left and right, respectively.
 
@@
 \end{knitrout}
-\caption{Residual plot of the explainer model associated with \data \ prediction of interest from Section \ref{exp-scatter}\sout{.
-The residuals are plotted against the predicted values.
-The points are jittered in the x-direction to alleviate the over-plotting of points.
-There is\kge{a clear increase} \sout{an upward trend} in the residuals as the explainer model predictions increase}, which suggests a violation of the linearity assumption.}
+\caption{Residual plot of the explainer model associated with \data \ prediction of interest from Section \ref{exp-scatter}, which suggests a violation of the linearity assumption.}
 \label{fig:figure-C2}
@@
 In order to assess the claim of linearity for the \data \ prediction of interest discussed in Section \ref{exp-scatter}, we use one of the most basic diagnostics in a statistician's tool box and draw a residual plot for the explainer model.
-This is shown in Figure \ref{fig:figure-C2} with the explainer model residuals on the y-axis and explainer model predictions on the x-axis.
-The points along the x-axis have been jittered to ease the effect of the over-plotted points\sout{ in the visualization}.
-There is a clear increasing trend in the residuals as the explainer model predictions increase\kge{,}\sout{.
-This is a clear} \kge{which indicates a} violation of the \kge{ridge regression} linearity assumption\sout{ with the ridge regression model}.
+This is shown in \autoref{fig:figure-C2} with the explainer model residuals on the y-axis and explainer model predictions on the x-axis.
+The points along the x-axis have been jittered to ease the effect of the over-plotted points.
+There is a clear increasing trend in the residuals as the explainer model predictions increase, which indicates a violation of the ridge regression linearity assumption.
 
@@
 \caption{Hypothetical examples of feature heatmaps in two possible situations.
-\sout{The heatmaps show the top feature chosen for 10 cases across 5 different sets of tuning parameter values.
-The color of the cell indicates the feature chosen by LIME.} Situation 1 is the ideal, because the explanations vary across cases but do not dependent on specific tuning parameter values.
-\kge{Situation 2 suggets global explanations and extreme explanation dependence on the tuning parameter values.}}
+Situation 1 is the ideal, because the explanations vary across cases but do not dependent on specific tuning parameter values.
+Situation 2 suggests global explanations and extreme explanation dependence on the tuning parameter values.}
 \label{fig:figure-D3}
@@
 \end{knitrout}
-\caption{Plots of LIME explanations (first row) and explanation scatterplots (second row) for case M in the bullet test data for two tuning parameter values: 4-quantile-bins (first column) and 4-equal-bins (second column).\sout{ The plots provide insights into the LIME explanations and allow for the assessment of the explanation quality.}}
+\caption{Plots of LIME explanations (first row) and explanation scatterplots (second row) for case M in the bullet test data for two tuning parameter values: 4-quantile-bins (first column) and 4-equal-bins (second column).}
 \label{fig:figure-F4}

### 2020-12-31 paper.Rnw
typos

@@
 Since the explainer model is an approximation of the complex model and not a direct interpretation, the explanations produced by an explainer model are subject to the quality of the approximation.
-In order to achieve reasonable  explanations, the tuning parameter values selected shoud  be assessed.
+In order to achieve reasonable  explanations, the tuning parameter values selected should  be assessed.
 
@@
 This may be reasonable considering that we would expect  $x_1$ and $x_2$ to be  the two features  used by the random forest to distinguish between response categories.
-However, futher exploration of individual explanations using explanation scatterplots may help to identify the tuning parameter values that produce the most trustworthy explanations.
+However, further exploration of individual explanations using explanation scatterplots may help to identify the tuning parameter values that produce the most trustworthy explanations.
 

### 2020-12-31 paper.Rnw
small edits

@@
 In the field of statistics, there are two main uses for models: inference and prediction.
-Machine learning models  have proven to perform well in problems with the latter objective , but the accuracy of many machine learning models comes at the cost of interpretability due to their algorithmic complexity (hence the phrase "black-box models").
+Machine learning models  have proven to perform well in problems with the latter objective, but the accuracy of many machine learning models comes at the cost of interpretability due to their algorithmic complexity (hence the phrase "black-box models").
 Model interpretability allows for the understanding and assessment of how a model produces predictions.
-The lack of the ability to understand and assess a model makes it difficult to trust the model, especially in areas with high stakes decisions such as the medical and forensics sciences.
+The lack of the ability to understand and assess a model makes trusting it difficult, especially in areas with high stakes decisions such as the medical and forensics sciences.
 The increased use of machine learning models in applications and the introduction of the General Data Protection Regulation (GDPR) in 2018 \citep{goodman:2016} has resulted in a dramatic increase in explainable machine learning research, which focuses on developing ways to explain output from machine learning algorithms.
@@
 We define {\it interpretability} as the ability to directly use model parameters to understand the relationships in the data captured by the model: e.g., a linear model coefficient associated with a predictor variable indicates the amount the response variable changes based on a change in the predictor variable.
-In contrast, define {\it explanability} as the ability to use the model in an indirect manner to understand the relationships in the data captured by the model: e.g., partial dependence plots depict the marginal relationship between model predictions and predictor variables \citep{friedman:2001}.
+In contrast, we define {\it explanability} as the ability to use the model in an indirect manner to understand the relationships in the data captured by the model: e.g., partial dependence plots depict the marginal relationship between model predictions and predictor variables \citep{friedman:2001}.
 
@@
 Some are specific to one type of model (e.g.
-\citep{simonyan:2013} and \citep{urbanek:2008}), and others are model-agnostic (e.g.
-\citep{fisher:2018} and \citep{strumbelj:2014}).
+\citep{simonyan:2013, urbanek:2008}), others are model-agnostic (e.g.
+\citep{fisher:2018, strumbelj:2014}).
 In this paper, we focus on the  model-agnostic method of LIME \citep{ribeiro:2016}.
@@
 While some explainer models  focus on understanding a model at the global level, LIME claims to provide explanations for individual predictions (local).
-Additionally, LIME is designed to work with any model (model-agnostic) and to produce easily understandable results (explanations) \citep{ribeiro:2016}.
+Beyond that, LIME is designed to work with any model (model-agnostic) and to produce easily understandable results (explanations) \citep{ribeiro:2016}.
 Conceptually, LIME fits a simple (interpretable) model, the explainer model, to approximate  the complex model in a local region around a prediction of interest.
@@
 
-On the left, the distance between an observation and the prediction of interest is computed using the Gower distance metric \citep{gower:1971} and then raised to the power of \Sexpr{good_gower_power} to emphasize a very local region.
+On the left, the distance between an observation and the prediction of interest is calculated using the Gower distance metric \citep{gower:1971}  raised to the power of \Sexpr{good_gower_power} to emphasize a very local region.
 The distances are subtracted from 1 to obtain a proximity.
-Here, the explainer model is faithful to the complex model since it captures the linear relationship between the black-box predictions in an immediate neighborhood of the prediction of interest.
-The slope  explains that the black-box predictions increase as the feature increases in the local region around the prediction of interest.
-
-For the scenario on the right, the computation of the proximities is the same except the distances are raised to a power of \Sexpr{bad_gower_power} (the default exponent in the \emph{lime} R package \citep{pedersen:2020}).
-This causes the observations that are further away from the prediction of interest to be given larger weights than the scenario on the left.
-Here, the explainer model does not capture the linear trend near the prediction of interest, but instead, the explainer captures a more global trend.
-Without an assessment of this explainer model, the slope incorrectly suggests that the predictions decrease as the feature increases near the prediction of interest.
+Here, the explainer model is faithful to the complex model since it captures the linear relationship between the black-box predictions in an immediate neighborhood of the prediction of interest: with an increase in the feature the black-box predictions increase in a local region around the prediction of interest.
+
+For the scenario on the right, the computation of the proximities is the same except that distances are raised to a power of \Sexpr{bad_gower_power} (the default exponent in the \emph{lime} R package \citep{pedersen:2020}).
+This difference gives larger weights to observations that are further away from the prediction of interest than the scenario on the left.
+Instead of capturing a local trend, the slope in the explainer model describes a more global trend.
+Here, the explainer model incorrectly suggests, that a decrease in prediction values as the feature increases near the prediction of interest.
 %\sout{This cannot be said of the explainer model in \autoref{fig:figure-02}.

### 2021-01-03 paper.Rnw
started moving material to a supplement

--- 2020-12-31 paper.Rnw
@@
 \section{Introduction}
-
-<<concept-data, eval = FALSE>>=
-
-# # Simulate example data
-# set.seed(20190624)
-# lime_data <-
-#   data.frame(
-#     feature1 = sort(runif(250, 0, 1)),
-#     feature2 = sample(x = 1:250, size = 250, replace = FALSE)) %>%
-#   mutate(
-#     feature1_stnd = (feature1 - mean(feature1)) / sd(feature1),
-#     feature2_stnd = (feature2 - mean(feature2)) / sd(feature2),
-#     prediction = if_else(feature1 >= 0 & feature1 < 0.1,
-#                          (0.3 * feature1) + rnorm(n(), 0, 0.01),
-#                  if_else(feature1 >= 0.1 & feature1 < 0.3,
-#                          rbeta(n(), 1, 0.5),
-#                  if_else(feature1 >= 0.3 & feature1 < 0.5,
-#                          sin(pi* feature1) + rnorm(n(), 0, 0.5),
-#                  if_else(feature1 >= 0.5 & feature1 < 0.8,
-#                          -(sin(pi* feature1) + rnorm(n(), 0, 0.1)) + 1,
-#                  if_else(feature1 >= 0.8 & feature1 < 0.9,
-#                          0.5 + runif(n(), -0.5, 0.5),
-#                          0.5 + rnorm(n(), 0, 0.3))))))) %>%
-#   bind_rows(
-#     data.frame(feature1 = rep(1, 30) + rnorm(5, 0, 0.05),
-#            feature2 = rep(245, 30) + rnorm(5, 0, 1),
-#            prediction = rep(0, 30) + rnorm(5, 0, 0.05)) %>%
-#   mutate(feature1_stnd = (feature1 - mean(feature1)) / sd(feature1),
-#          feature2_stnd = (feature2 - mean(feature2)) / sd(feature2)))
-# 
-# # Specify a prediction of interest
-# prediction_of_interest <-
-#   data.frame(feature1 = 0.07, feature2 = 200) %>%
-#   mutate(feature1_stnd = (feature1 - mean(lime_data$feature1)) /
-#            sd(lime_data$feature1),
-#          feature2_stnd = (feature2 - mean(lime_data$feature2)) /
-#            sd(lime_data$feature2),
-#          prediction = 0.05,
-#          color = factor("Prediction \nof Interest"))
-# 
-# # Specify the gower exponents
-# good_gower_power <- 50
-# bad_gower_power <- 1
-# 
-# # Compute the good distances between the prediction of interest
-# # and all other observations
-# lime_data$distance_good <-
-#   (1 - gower_dist(x = prediction_of_interest %>%
-#                     select(feature1_stnd, feature2_stnd),
-#                   y = lime_data %>%
-#                     select(feature1_stnd,
-#                            feature2_stnd)))^good_gower_power
-# 
-# # Compute the bad distances between the prediction of interest
-# # and all other observations
-# lime_data$distance_bad <-
-#   (1 - gower_dist(x = prediction_of_interest %>%
-#                     select(feature1_stnd, feature2_stnd),
-#                   y = lime_data %>%
-#                     select(feature1_stnd,
-#                            feature2_stnd)))^bad_gower_power
-# 
-# # Prepare the data for plotting
-# lime_data_gathered <- lime_data %>%
-#   gather(feature, feature_stnd_value,
-#          feature1_stnd:feature2_stnd) %>%
-#   gather(distance, distance_value, distance_good:distance_bad) %>%
-#   mutate(distance = fct_recode(distance,
-#                                "good" = "distance_good",
-#                                "bad" = "distance_bad"),
-#          feature = fct_recode(feature,
-#                               "Feature 1" = "feature1_stnd",
-#                               "Feature 2" = "feature2_stnd"))
-# 
-# # Prepare the prediction of interest data for plotting
-# prediction_of_interest_gathered <- prediction_of_interest %>%
-#   select(-feature1, -feature2) %>%
-#   gather(feature, feature_value, feature1_stnd, feature2_stnd) %>%
-#   mutate(feature = fct_recode(feature,
-#                               "Feature 1" = "feature1_stnd",
-#                               "Feature 2" = "feature2_stnd"))
-
-@
-
-<<concept-explainers, eval = FALSE>>=
-
-# # Fit the good interpretable explainer model
-# explainer_good <-
-#   glmnet(x = lime_data %>% select(feature1_stnd, feature2_stnd)
-#          %>% as.matrix(),
-#          y = lime_data$prediction,
-#          alpha = 0,
-#          lambda = 1,
-#          weights = lime_data$distance_good)
-# 
-# # Fit the bad interpretable explainer model
-# explainer_bad <-
-#   glmnet(x = lime_data %>% select(feature1_stnd, feature2_stnd)
-#          %>% as.matrix(),
-#          y = lime_data$prediction,
-#          alpha = 0,
-#          lambda = 1,
-#          weights = lime_data$distance_bad)
-# 
-# # Join the coefficients from the explainer model into a dataframe
-# coefs_data <- data.frame(case = c("good", "bad"),
-#                          b0 = c(coef(explainer_good)[1],
-#                                 coef(explainer_bad)[1]),
-#                          b1 = c(coef(explainer_good)[2],
-#                                 coef(explainer_bad)[2]),
-#                          b2 = c(coef(explainer_good)[3],
-#                                 coef(explainer_bad)[3])) %>%
-#   mutate(feature1 = b0 + b2*prediction_of_interest$feature2_stnd,
-#          feature2 = b0 + b1*prediction_of_interest$feature1_stnd) %>%
-#   gather(key = feature, value = int, feature1:feature2) %>%
-#   mutate(slope = c(coef(explainer_good)[2],
-#                    coef(explainer_good)[3],
-#                    coef(explainer_bad)[2],
-#                    coef(explainer_bad)[3]),
-#          feature = fct_recode(feature,
-#                               "Feature 1" = "feature1",
-#                               "Feature 2" = "feature2"))
-
-@
 
@@
 
-# # Plot of good explainer model
-# ggplot() +
-#   facet_grid(. ~ feature, switch = "x") +
-#   geom_point(
-#     data = lime_data_gathered %>% mutate(
-#       feature = fct_recode(
-#         feature,
-#         "Feature 1 (standardized)" = "Feature 1",
-#         "Feature 2 (standardized)" = "Feature 2"
-#       )
-#     ),
-#     mapping = aes(
-#       x = feature_stnd_value,
-#       y = prediction,
-#       size = distance_value,
-#       color = distance
-#     ),
-#     alpha = 0.6
-#   ) +
-#   geom_abline(
-#     data = coefs_data %>%
-#       filter(case == "good") %>%
-#       mutate(
-#         feature = fct_recode(
-#           feature,
-#           "Feature 1 (standardized)" = "Feature 1",
-#           "Feature 2 (standardized)" = "Feature 2"
-#           )
-#         ),
-#     mapping = aes(intercept = int, slope = slope),
-#     size = 1
-#   ) +
-#   scale_color_manual(values = c(NA, "grey30"), guide = "none") +
-#   geom_point(
-#     data = prediction_of_interest_gathered %>% mutate(
-#       feature = fct_recode(
-#         feature,
-#         "Feature 1 (standardized)" = "Feature 1",
-#         "Feature 2 (standardized)" = "Feature 2"
-#       )
-#     ),
-#     mapping = aes(x = feature_value,
-#                   y = prediction,
-#                   fill = color),
-#     color = "black",
-#     size = 5,
-#     shape = 23,
-#     alpha = 0.75
-#   ) +
-#   scale_fill_manual(values = "#FAAA72") +
-#   geom_text(
-#     data = data.frame(
-#       feature_stnd_value = 1.2,
-#       prediction = 1.6,
-#       feature = c("Feature 1 (standardized)", "Feature 2 (standardized)"),
-#       slope = c(
-#         paste(
-#           "Slope:",
-#           coefs_data %>%
-#             filter(case == "good",
-#                    feature == "Feature 1") %>%
-#             pull(slope) %>%
-#             round(3)
-#         ),
-#         paste(
-#           "Slope:",
-#           coefs_data %>%
-#             filter(case == "good",
-#                    feature == "Feature 2") %>%
-#             pull(slope) %>%
-#             round(3)
-#         )
-#       )
-#     ),
-#     mapping = aes(x = feature_stnd_value,
-#                   y = prediction,
-#                   label = slope),
-#     family = ff,
-#     size = f1_fs / 2.85
-#   ) +
-#   labs(
-#     x = "",
-#     y = "Black-Box Prediction",
-#     title = "Conceptual Depiction of a Faithful Local Explainer Model",
-#     subtitle = paste("Gower Distance Metric Exponent:", good_gower_power),
-#     fill = "",
-#     alpha = "Weight",
-#     size = "Weight"
-#   ) +
-#   theme_linedraw(base_family = ff, base_size = f1_fs) +
-#   theme(
-#     panel.grid.major = element_blank(),
-#     panel.grid.minor = element_blank(),
-#     axis.text.x = element_blank(),
-#     axis.ticks.x = element_blank(),
-#     axis.text.y = element_blank(),
-#     axis.ticks.y = element_blank(),
-#     strip.placement = "outside",
-#     strip.background = element_rect(color = "white", fill = "white"),
-#     strip.text.x = element_text(size = f1_fs, color = "black"),
-#     plot.title = element_text(size = f1_fs)
-#   ) +
-#   guides(
-#     fill = guide_legend(order = 1),
-#     size = guide_legend(order = 2),
-#     alpha = guide_legend(order = 2)
-#   )
-
 @
@@
 Without an assessment of this explainer model, the slope incorrectly suggests that the predictions decrease as the feature increases near the prediction of interest.
-%\sout{This cannot be said of the explainer model in \autoref{fig:figure-02}.
-In addition, the magnitude of the slope associated with Feature 2  (\Sexpr{coefs_data %>% filter(case == "bad", feature == "Feature 2") %>% pull(b1) %>% round(3) %>% abs()}) is larger than that of Feature 1 (\Sexpr{coefs_data %>% filter(case == "bad", feature == "Feature 1") %>% pull(b1) %>% round(3) %>% abs()}).
-Thus, this explainer model actually provides a misleading explanation that Feature 2 plays a more important role in the prediction of interest.}
-
-%\kge{To demonstrate the effect of tuning parameters on LIME,we consider two different explainer models applied to the same prediction.
-Suppose a hypothetical black-box model is trained using one feature.
-Both plots in Figure1show the black-box model predictions versus the feature used to train the model.The diamond shaped point in the plots indicates the location of the prediction of interest to explain.
-A weight ridge regression with the black-box predictions as the response variable and standardized versions the features as predictor variables will be used as the explainer model in both scenarios, but the weights will vary.
-Note that the standardized features allow for direct comparisons of the model coefficients.}
 
@@
 As previously discussed, the \textbf{interpretability} of the LIME explanations is controllable by the complexity of the explainer model.
-For example, the number of bins selected for simulation can control the interpretability of the explanations.
+For example, the number of bins selected for simulation controls the interpretability of the explanations.
 If too many bins are selected, the bin range that is reported in the LIME explanation will be too small to be meaningful in the context of the feature.
@@
 While it would be ideal if LIME could be used as a method to provide easily understandable explanations for black-box models as \citet{ribeiro:2016} claim, that dream is not yet a reality.
-The examples using diagnostic plots to assess LIME in this paper show frequent instances when the claims about LIME are not met .
-We hope that our plots provide motivation to assess LIME explanations, to not blindly use the default settings (even if it is not clear how to tune the parameters), and to encourage work  improving LIME, so that it can be a lime and not a lemon.
+The examples using diagnostic plots to assess LIME in this paper show frequent instances when the claims about LIME are not met.
+We hope that our plots provide motivation to assess LIME explanations, to not blindly use the default settings (even if how to tune the parameters is not clear), and to encourage work improving LIME, so that it can be a lime and not a lemon.
 
@@
 
-\section{Extreme Feature Heatmap Scenarios} \label{feat-heat-ex}
-
-Two hypothetical examples of feature heatmaps are included in \autoref{fig:figure-D3}.
-The plots are created with the assumption that LIME is applied to select the top feature out of $p=4$  features for $n=10$ cases with $t=5$ sets of tuning parameter values.
-Situation 1 is an example where the features selected are consistent across tuning parameter values within a case but vary across cases within a tuning parameter value.
-This is the ideal situation, because the LIME explanations do not depend on the tuning parameters but do depend on the location of the observation in the feature space.
-Situation 2 is an example where the selected features vary across tuning parameter values within a case but are consistent across cases within a tuning parameter value.
-This situation indicates that the features selected by LIME are dependent on the tuning parameters, and the explanations may not be  local, because the same feature is chosen regardless of the case.
-In practice, it is expected that the plot will exhibit a combination of these two situations.
-
-\begin{figure}[!t]
-<<figure-D3, out.width = '3.125in', fig.width = 6, fig.height = 3>>=
-
-# Specify the figure size (for determining font size)
-fd3_ow = 3.125
-fd3_fw = 6
-fd3_fs = fs * (fd3_fw / fd3_ow)
-
-# Specify the number of cases and LIME input options
-ncases = 10
-ninputs = 5
-
-# Create a good case of chosen feature example data
-set.seed(20191008)
-heatmap_data_good <-
-  tibble(
-    case = factor(rep(1:ncases, each = ninputs),
-                  levels = ncases:1),
-    input = factor(rep(1:ninputs, ncases)),
-    feature = factor(c(
-      rep(1, 5),
-      rep(2, 5),
-      rep(3, 5),
-      rep(1, 5),
-      rep(1, 5),
-      rep(4, 5),
-      rep(1, 5),
-      rep(3, 5),
-      rep(1, 5),
-      rep(4, 5)
-    ))
-  ) %>%
-  mutate(input = forcats::fct_recode(
-    input,
-    "A" = "1",
-    "B" = "2",
-    "C" = "3",
-    "D" = "4",
-    "E" = "5"
-  ))
-
-# Create the conceptual good heatmap
-heatmap_plot_good <- ggplot(data = heatmap_data_good,
-                            mapping = aes(
-                              x = input,
-                              y = case,
-                              fill = feature,
-                              color = feature
-                            )) +
-  geom_tile() +
-  labs(
-    x = "Tuning Parameter Value",
-    y = "Case",
-    fill = "Feature",
-    color = "Feature",
-    title = "Situation 1",
-    subtitle = "Consistent Explanations"
-  ) +
-  theme_bw(base_family = ff, base_size = fd3_fs) +
-  scale_fill_grey() +
-  scale_color_grey() +
-  theme(legend.position = "none", 
-        plot.title = element_text(size = fd3_fs))
-
-# Create a bad case of chosen feature example data
-set.seed(20190627)
-heatmap_data_bad <- tibble(
-  case = factor(rep(1:ncases, ninputs),
-                levels = ncases:1),
-  input = factor(rep(1:ninputs, each = ncases)),
-  feature = factor(rep(c(1, 2, 4, 3, 2), each = 10))
-) %>%
-  mutate(input = forcats::fct_recode(
-    input,
-    "A" = "1",
-    "B" = "2",
-    "C" = "3",
-    "D" = "4",
-    "E" = "5"
-  ))
-
-# Create the conceptual bad heat map
-heatmap_plot_bad <- ggplot(data = heatmap_data_bad,
-                           mapping = aes(
-                             x = input,
-                             y = case,
-                             fill = feature,
-                             color = feature
-                           )) +
-  geom_tile() +
-  labs(
-    x = "Tuning Parameter Value",
-    y = "Case",
-    fill = "Feature",
-    color = "Feature",
-    title = "Situation 2",
-    subtitle = "Inconsistent Explanations"
-  ) +
-  theme_bw(base_family = ff, base_size = fd3_fs) +
-  theme(plot.title = element_text(size = fd3_fs)) +
-  scale_fill_grey() +
-  scale_color_grey()
-
-heatmap_leg <- get_legend(heatmap_plot_bad)
-heatmap_plot_bad <-
-  heatmap_plot_bad + theme(legend.position = 'none')
-
-# Join the plots
-plot_grid(
-  heatmap_plot_good,
-  heatmap_plot_bad,
-  heatmap_leg,
-  nrow = 1,
-  rel_widths = c(0.43, 0.43, 0.14)
-)
-
-@
-\caption{Hypothetical examples of feature heatmaps in two possible situations.
-Situation 1 is the ideal, because the explanations vary across cases but do not dependent on specific tuning parameter values.
-Situation 2 suggests global explanations and extreme explanation dependence on the tuning parameter values.}
-\label{fig:figure-D3}
-\end{figure}
-
 \section{Details on Assessment Metrics} \label{metric-details}
@@
 
-\section{Additional Bullet Matching Explanation Scatterplots} \label{bullets-plus}
-
-\autoref{fig:figure-F4} includes visual representations of LIME explanation from the \emph{lime} R package and explanation scatterplots for a known match observation in the the bullet example referred to as cases M for two different data simulation methods: 4-quantile-bins (left column) and 4-equal-bins (right column).
-Both explanations appear to be more faithful to the random forest than those associated with case NM in Section \ref{bullet-assess-ex}, but the intersections of the bins could be better aligned with the regions containing similar probabilities produced by the random forest.
-\autoref{fig:figure-F5} includes explanation scatterplots for bullet example cases M and NM when the kernel density simulation method is used.
-
-\begin{figure*}[!t]
-<<figure-F4, out.width = '6.25in', fig.width = 13, fig.height = 8.5, message = FALSE>>=
-
-# Specify the figure size (for determining font size)
-ff4_ow = 6.25
-ff4_fw = 13
-ff4_fs = fs * (ff4_fw / ff4_ow)
-ff4_ls = 0.5 * (ff4_fw / ff4_ow)
-
-# Create the lime explanation visualizations
-pfM_3qb <- plot_features(bullet_explain_perms_clean[1:3,]) + bullet_explain_plot_theme
-pfM_3eb <- plot_features(bullet_explain_perms_clean[7:9,]) + bullet_explain_plot_theme
-
-# Create the explanation scatterplots
-eoiM_3qb <-
-  plot_explain_scatter(
-    bullet_explain_perms_clean[1:3, ],
-    alpha = 0.9,
-    weights = TRUE,
-    line_size = ff4_ls
-  ) +
-  bullet_eoi_plot_theme +
-  guides(linetype = guide_legend(override.aes = list(color = c("darkorange"))))
-eoiM_3eb <-
-  plot_explain_scatter(
-    bullet_explain_perms_clean[7:9, ],
-    alpha = 0.9,
-    weights = TRUE,
-    line_size = ff4_ls
-  ) +
-  bullet_eoi_plot_theme + 
-  guides(linetype = guide_legend(override.aes = list(color = c("darkorange"))))
-
-# Join the plots
-plot_grid(
-  pfM_3qb,
-  pfM_3eb,
-  eoiM_3qb,
-  eoiM_3eb,
-  nrow = 2,
-  rel_heights = c(0.2, 0.3)
-)
-
-@
-\caption{Plots of LIME explanations (first row) and explanation scatterplots (second row) for case M in the bullet test data for two tuning parameter values: 4-quantile-bins (first column) and 4-equal-bins (second column).}
-\label{fig:figure-F4}
-\end{figure*}
-
-\begin{figure*}[!thp]
-<<figure-F5, out.width = '6.5in', fig.width = 12, fig.height = 10, fig.align = "center">>=
-
-# Specify the figure size (for determining font size and line size)
-ff5_ow = 6.5
-ff5_fw = 12
-ff5_fs = fs * (ff5_fw / ff5_ow)
-ff5_ls = 0.5 * (ff5_fw / ff5_ow)
-
-# Create the explanation scatterplot: case M, kernel density
-bullet_es_M <-
-  plot_explain_scatter(
-    bullet_explain_perms[16:18, ] %>% mutate(case = "NM"),
-    alpha = 0.75,
-    title.opt = TRUE,
-    line_size = ff5_ls
-  ) +
-  scale_fill_gradient2(
-    low = "grey50",
-    high = "darkorange",
-    midpoint = 0.5,
-    limits = c(0, 1)
-  ) +
-  theme_bw(base_family = ff, base_size = ff5_fs) +
-  theme(
-    aspect.ratio = 1,
-    strip.background = element_rect(fill = "white", color = "white"),
-    strip.placement = "outside",
-    strip.text.x = element_text(size = ff5_fs),
-    plot.title = element_text(size = ff5_fs)
-  )
-
-# Create the explanation scatterplot: case NM, kernel density
-bullet_es_NM <-
-  plot_explain_scatter(
-    bullet_explain_perms[13:15, ] %>% mutate(case = "M"),
-    alpha = 0.75,
-    title.opt = TRUE, 
-    line_size = ff5_ls
-  ) +
-  scale_fill_gradient2(
-    low = "grey50",
-    high = "darkorange",
-    midpoint = 0.5,
-    limits = c(0, 1)
-  ) +
-  theme_bw(base_family = ff, base_size = ff5_fs) +
-  theme(
-    aspect.ratio = 1,
-    strip.background = element_rect(fill = "white", color = "white"),
-    strip.placement = "outside",
-    strip.text.x = element_text(size = ff5_fs), 
-    plot.title = element_text(size = ff5_fs)
-  )
-
-# Join the plots
-plot_grid(bullet_es_M, bullet_es_NM, nrow = 2)
-
-@
-\caption{Explanation scatterplots for LIME explanations using kernel density simulation for the cases M and NM of the bullet comparison test data.}
-\label{fig:figure-F5}
-\end{figure*}
-
 \end{document}

### 2021-01-03 paper.tex
started moving material to a supplement

@@
 Without an assessment of this explainer model, the slope incorrectly suggests that the predictions decrease as the feature increases near the prediction of interest.
-%\sout{This cannot be said of the explainer model in \autoref{fig:figure-02}.
-In addition, the magnitude of the slope associated with Feature 2  () is larger than that of Feature 1 ().
-Thus, this explainer model actually provides a misleading explanation that Feature 2 plays a more important role in the prediction of interest.}
-
-%\kge{To demonstrate the effect of tuning parameters on LIME,we consider two different explainer models applied to the same prediction.
-Suppose a hypothetical black-box model is trained using one feature.
-Both plots in Figure1show the black-box model predictions versus the feature used to train the model.The diamond shaped point in the plots indicates the location of the prediction of interest to explain.
-A weight ridge regression with the black-box predictions as the response variable and standardized versions the features as predictor variables will be used as the explainer model in both scenarios, but the weights will vary.
-Note that the standardized features allow for direct comparisons of the model coefficients.}
 
@@
 
-\section{Extreme Feature Heatmap Scenarios} \label{feat-heat-ex}
-
-Two hypothetical examples of feature heatmaps are included in \autoref{fig:figure-D3}.
-The plots are created with the assumption that LIME is applied to select the top feature out of $p=4$  features for $n=10$ cases with $t=5$ sets of tuning parameter values.
-Situation 1 is an example where the features selected are consistent across tuning parameter values within a case but vary across cases within a tuning parameter value.
-This is the ideal situation, because the LIME explanations do not depend on the tuning parameters but do depend on the location of the observation in the feature space.
-Situation 2 is an example where the selected features vary across tuning parameter values within a case but are consistent across cases within a tuning parameter value.
-This situation indicates that the features selected by LIME are dependent on the tuning parameters, and the explanations may not be  local, because the same feature is chosen regardless of the case.
-In practice, it is expected that the plot will exhibit a combination of these two situations.
-
-\begin{figure}[!t]
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-
-{\centering \includegraphics[width=3.125in]{figure/figure-D3-1}
-
-}
-
-\end{knitrout}
-\caption{Hypothetical examples of feature heatmaps in two possible situations.
-Situation 1 is the ideal, because the explanations vary across cases but do not dependent on specific tuning parameter values.
-Situation 2 suggests global explanations and extreme explanation dependence on the tuning parameter values.}
-\label{fig:figure-D3}
-\end{figure}
-
 \section{Details on Assessment Metrics} \label{metric-details}
@@
 
-\section{Additional Bullet Matching Explanation Scatterplots} \label{bullets-plus}
-
-\autoref{fig:figure-F4} includes visual representations of LIME explanation from the \emph{lime} R package and explanation scatterplots for a known match observation in the the bullet example referred to as cases M for two different data simulation methods: 4-quantile-bins (left column) and 4-equal-bins (right column).
-Both explanations appear to be more faithful to the random forest than those associated with case NM in Section \ref{bullet-assess-ex}, but the intersections of the bins could be better aligned with the regions containing similar probabilities produced by the random forest.
-\autoref{fig:figure-F5} includes explanation scatterplots for bullet example cases M and NM when the kernel density simulation method is used.
-
-\begin{figure*}[!t]
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-
-{\centering \includegraphics[width=6.25in]{figure/figure-F4-1}
-
-}
-
-\end{knitrout}
-\caption{Plots of LIME explanations (first row) and explanation scatterplots (second row) for case M in the bullet test data for two tuning parameter values: 4-quantile-bins (first column) and 4-equal-bins (second column).}
-\label{fig:figure-F4}
-\end{figure*}
-
-\begin{figure*}[!thp]
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-
-{\centering \includegraphics[width=6.5in]{figure/figure-F5-1}
-
-}
-
-\end{knitrout}
-\caption{Explanation scatterplots for LIME explanations using kernel density simulation for the cases M and NM of the bullet comparison test data.}
-\label{fig:figure-F5}
-\end{figure*}
-
 \end{document}

### 2021-01-03 supplement/supplemental.Rnw
started moving material to a supplement

\documentclass{article}

\title{Supplemental Material for the manuscript titled "Visual Diagnostics of an Explainer Model -- Tools for the Assessment of LIME Explanations"}

\begin{document}

\maketitle

<<setup, echo = FALSE, include = FALSE>>=
# Specify global options
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  fig.keep = 'high',
  fig.align = 'center',
  dev = c("cairo_pdf", "cairo_ps"),
  dev.args = list(fallback_resolution = 800),
  dpi = 1200
)

# Load packages
library(Cairo)
library(cowplot)
library(dplyr)
library(forcats)
library(ggplot2)
library(gretchenalbrecht) #remotes::install_github("dicook/gretchenalbrecht")
library(tidyr)

# Specify the (base) font size (fs) and font (ff) for all plots
fs = 7
ff = "Helvetica"
@

\section{Extreme Feature Heatmap Scenarios} \label{feat-heat-ex}

Two hypothetical examples of feature heatmaps are included in Figure \ref{fig:figure-s1}. The plots are created with the assumption that LIME is applied to select the top feature out of $p=4$  features for $n=10$ cases with $t=5$ sets of tuning parameter values. Situation 1 is an example where the features selected are consistent across tuning parameter values within a case but vary across cases within a tuning parameter value. This is the ideal situation, because the LIME explanations do not depend on the tuning parameters but do depend on the location of the observation in the feature space. Situation 2 is an example where the selected features vary across tuning parameter values within a case but are consistent across cases within a tuning parameter value. This situation indicates that the features selected by LIME are dependent on the tuning parameters, and the explanations may not be  local, because the same feature is chosen regardless of the case. In practice, it is expected that the plot will exhibit a combination of these two situations.

\begin{figure}
<<figure-s1, out.width = '3.125in', fig.width = 6, fig.height = 3>>=

# Specify the figure size (for determining font size)
fs1_ow = 3.125
fs1_fw = 6
fs1_fs = fs * (fs1_fw / fs1_ow)

# Specify the number of cases and LIME input options
ncases = 10
ninputs = 5

# Create a good case of chosen feature example data
set.seed(20191008)
heatmap_data_good <-
  tibble(
    case = factor(rep(1:ncases, each = ninputs),
                  levels = ncases:1),
    input = factor(rep(1:ninputs, ncases)),
    feature = factor(c(
      rep(1, 5),
      rep(2, 5),
      rep(3, 5),
      rep(1, 5),
      rep(1, 5),
      rep(4, 5),
      rep(1, 5),
      rep(3, 5),
      rep(1, 5),
      rep(4, 5)
    ))
  ) %>%
  mutate(input = forcats::fct_recode(
    input,
    "A" = "1",
    "B" = "2",
    "C" = "3",
    "D" = "4",
    "E" = "5"
  ))

# Create the conceptual good heatmap
heatmap_plot_good <- ggplot(data = heatmap_data_good,
                            mapping = aes(
                              x = input,
                              y = case,
                              fill = feature,
                              color = feature
                            )) +
  geom_tile() +
  labs(
    x = "Tuning Parameter Value",
    y = "Case",
    fill = "Feature",
    color = "Feature",
    title = "Situation 1",
    subtitle = "Consistent Explanations"
  ) +
  theme_bw(base_family = ff, base_size = fs1_fs) +
  scale_fill_grey() +
  scale_color_grey() +
  theme(legend.position = "none", 
        plot.title = element_text(size = fs1_fs))

# Create a bad case of chosen feature example data
set.seed(20190627)
heatmap_data_bad <- tibble(
  case = factor(rep(1:ncases, ninputs),
                levels = ncases:1),
  input = factor(rep(1:ninputs, each = ncases)),
  feature = factor(rep(c(1, 2, 4, 3, 2), each = 10))
) %>%
  mutate(input = forcats::fct_recode(
    input,
    "A" = "1",
    "B" = "2",
    "C" = "3",
    "D" = "4",
    "E" = "5"
  ))

# Create the conceptual bad heat map
heatmap_plot_bad <- ggplot(data = heatmap_data_bad,
                           mapping = aes(
                             x = input,
                             y = case,
                             fill = feature,
                             color = feature
                           )) +
  geom_tile() +
  labs(
    x = "Tuning Parameter Value",
    y = "Case",
    fill = "Feature",
    color = "Feature",
    title = "Situation 2",
    subtitle = "Inconsistent Explanations"
  ) +
  theme_bw(base_family = ff, base_size = fs1_fs) +
  theme(plot.title = element_text(size = fs1_fs)) +
  scale_fill_grey() +
  scale_color_grey()

heatmap_leg <- get_legend(heatmap_plot_bad)
heatmap_plot_bad <-
  heatmap_plot_bad + theme(legend.position = 'none')

# Join the plots
plot_grid(
  heatmap_plot_good,
  heatmap_plot_bad,
  heatmap_leg,
  nrow = 1,
  rel_widths = c(0.43, 0.43, 0.14)
)

@
\caption{Hypothetical examples of feature heatmaps in two possible situations.  Situation 1 is the ideal, because the explanations vary across cases but do not dependent on specific tuning parameter values. Situation 2 suggests global explanations and extreme explanation dependence on the tuning parameter values.}
\label{fig:figure-s1}
\end{figure}

\section{Additional Bullet Matching Explanation Scatterplots} \label{bullets-plus}

Figure \ref{fig:figure-s2} includes visual representations of LIME explanation from the \emph{lime} R package and explanation scatterplots for a known match observation in the the bullet example referred to as cases M for two different data simulation methods: 4-quantile-bins (left column) and 4-equal-bins (right column). Both explanations appear to be more faithful to the random forest than those associated with case NM in Section \ref{bullet-assess-ex}, but the intersections of the bins could be better aligned with the regions containing similar probabilities produced by the random forest. Figure \ref{fig:figure-s3} includes explanation scatterplots for bullet example cases M and NM when the kernel density simulation method is used.

\begin{figure*}[!t]
<<figure-s2, out.width = '6.25in', fig.width = 13, fig.height = 8.5, message = FALSE, echo = FALSE, eval = FALSE>>=

# Specify the figure size (for determining font size)
fs2_ow = 6.25
fs2_fw = 13
fs2_fs = fs * (fs2_fw / fs2_ow)
fs2_ls = 0.5 * (fs2_fw / fs2_ow)

# Create the lime explanation visualizations
pfM_3qb <- plot_features(bullet_explain_perms_clean[1:3,]) + bullet_explain_plot_theme
pfM_3eb <- plot_features(bullet_explain_perms_clean[7:9,]) + bullet_explain_plot_theme

# Create the explanation scatterplots
eoiM_3qb <-
  plot_explain_scatter(
    bullet_explain_perms_clean[1:3, ],
    alpha = 0.9,
    weights = TRUE,
    line_size = fs2_ls
  ) +
  bullet_eoi_plot_theme +
  guides(linetype = guide_legend(override.aes = list(color = c("darkorange"))))
eoiM_3eb <-
  plot_explain_scatter(
    bullet_explain_perms_clean[7:9, ],
    alpha = 0.9,
    weights = TRUE,
    line_size = fs2_ls
  ) +
  bullet_eoi_plot_theme + 
  guides(linetype = guide_legend(override.aes = list(color = c("darkorange"))))

# Join the plots
plot_grid(
  pfM_3qb,
  pfM_3eb,
  eoiM_3qb,
  eoiM_3eb,
  nrow = 2,
  rel_heights = c(0.2, 0.3)
)

@
\caption{Plots of LIME explanations (first row) and explanation scatterplots (second row) for case M in the bullet test data for two tuning parameter values: 4-quantile-bins (first column) and 4-equal-bins (second column).}
\label{fig:figure-s2}
\end{figure*}

\begin{figure*}[!thp]
<<figure-s3, out.width = '6.5in', fig.width = 12, fig.height = 10, fig.align = "center", echo = FALSE, eval = FALSE>>=

# Specify the figure size (for determining font size and line size)
fs3_ow = 6.5
fs3_fw = 12
fs3_fs = fs * (fs3_fw / fs3_ow)
fs3_ls = 0.5 * (fs3_fw / fs3_ow)

# Create the explanation scatterplot: case M, kernel density
bullet_es_M <-
  plot_explain_scatter(
    bullet_explain_perms[16:18, ] %>% mutate(case = "NM"),
    alpha = 0.75,
    title.opt = TRUE,
    line_size = fs3_ls
  ) +
  scale_fill_gradient2(
    low = "grey50",
    high = "darkorange",
    midpoint = 0.5,
    limits = c(0, 1)
  ) +
  theme_bw(base_family = ff, base_size = fs3_fs) +
  theme(
    aspect.ratio = 1,
    strip.background = element_rect(fill = "white", color = "white"),
    strip.placement = "outside",
    strip.text.x = element_text(size = fs3_fs),
    plot.title = element_text(size = fs3_fs)
  )

# Create the explanation scatterplot: case NM, kernel density
bullet_es_NM <-
  plot_explain_scatter(
    bullet_explain_perms[13:15, ] %>% mutate(case = "M"),
    alpha = 0.75,
    title.opt = TRUE, 
    line_size = fs3_ls
  ) +
  scale_fill_gradient2(
    low = "grey50",
    high = "darkorange",
    midpoint = 0.5,
    limits = c(0, 1)
  ) +
  theme_bw(base_family = ff, base_size = fs3_fs) +
  theme(
    aspect.ratio = 1,
    strip.background = element_rect(fill = "white", color = "white"),
    strip.placement = "outside",
    strip.text.x = element_text(size = fs3_fs), 
    plot.title = element_text(size = fs3_fs)
  )

# Join the plots
plot_grid(bullet_es_M, bullet_es_NM, nrow = 2)

@
\caption{Explanation scatterplots for LIME explanations using kernel density simulation for the cases M and NM of the bullet comparison test data.}
\label{fig:figure-s3}
\end{figure*}

\end{document}

### 2021-01-03 supplement/supplemental.tex
started moving material to a supplement

--- 2020-10-07 submission/paper.tex
@@
-\documentclass[AMS,STIX2COL]{WileyNJD-v2}\usepackage[]{graphicx}\usepackage[]{color}
+\documentclass{article}\usepackage[]{graphicx}\usepackage[]{color}
 % maxwidth is the original width if it is less than linewidth
@@
 
-% Packages
-\usepackage{amsmath}
-\usepackage{amsfonts}
-\usepackage{natbib}
-\usepackage{subcaption}
-\usepackage{xcolor}
-
-% Commands
-\definecolor{orange}{rgb}{0.94, 0.59, 0.19}
-\definecolor{purple}{rgb}{0.5, 0.0, 0.5}
-\definecolor{teal}{rgb}{0, 0.502, 0.502}
-\newcommand{\hh}[1]{\textcolor{orange}{#1}}
-\newcommand{\kgc}[1]{\textcolor{purple}{#1}}
-\newcommand{\kge}[1]{\textcolor{teal}{#1}}
-\newcommand{\data}{sine data}
-
-% Set up for ASA data science journal
-\articletype{Research Article}
-\received{XX XX XXXX}
-\revised{XX XX XXXX}
-\accepted{XX XX XXXX}
-\raggedbottom
+\title{Supplemental Material for the manuscript titled "Visual Diagnostics of an Explainer Model -- Tools for the Assessment of LIME Explanations"}
 \IfFileExists{upquote.sty}{\usepackage{upquote}}{}
@@
 
-% Paper header (title and authors)
-\title{Visual Diagnostics of a Model Explainer -- Tools for the Assessment of LIME Explanations}
-\author[1]{Katherine Goode*}
-\author[1,2]{Heike Hofmann}
-\authormark{Goode and Hofmann}
-\address[1]{\orgdiv{Department of Statistics}, \orgname{Iowa State University}, \orgaddress{\state{Iowa}, \country{United States}}}
-\address[2]{\orgdiv{Center for Statistics and Applications in Forensic Evidence (CSAFE)}, \orgname{Iowa State University}, \orgaddress{\state{Iowa}, \country{United States}}}
-\corres{*Katherine Goode, Department of Statistics, Iowa State University, Ames, IA. \email{kgoode@iastate.edu}}
-
-% Abstract and keywords
-\abstract[Abstract]{The importance of providing explanations for predictions made by black-box models has led to the development of model explainer methods such as LIME (local interpretable model-agnostic explanations).
-LIME uses a surrogate model to explain the relationship between predictor variables and predictions from a black-box model in a local region around a prediction of interest.
-However, the quality of the resulting explanations relies on how well the explainer model captures the black-box model in a specified local region.
-Here we introduce three visual diagnostics to assess the quality of LIME explanations: (1) explanation scatterplots, (2) assessment metric plots, and (3) feature heatmaps.
-We apply the visual diagnostics to a forensics bullet matching dataset to show examples where LIME explanations depend on the tuning parameter values and the explainer model oversimplifies the black-box model.
-Our examples raise concerns about claims made of LIME that are similar to other criticisms in the literature.}
-\keywords{explainable machine learning, black-box models, interpretability, statistical graphics, data science}
-
-% Citation information
-\jnlcitation{
-\cname{\author{Goode K.}, \author{H. Hofmann}, }
-\cyear{2020},
-\ctitle{Visual Diagnostics of a Model Explainer -- Tools for the Assessment of LIME Explanations},
-\cjournal{Stat Anal Data Min: The ASA Data Sci Journal},
-\cvol{volume, number and page}.}
-
 \maketitle
 
-\section{Introduction}
+\section{Extreme Feature Heatmap Scenarios} \label{feat-heat-ex}
 
-In the field of statistics, there are two main uses for models: inference and prediction.
-Machine learning models are often used for the latter purpose.
-These models have proven to perform well in a wide range of prediction problems, but the accuracy of many machine learning models comes at the cost of interpretability due to their algorithmic complexity (hence the phrase "black-box models").
-Model interpretability allows for the understanding and assessment of how a model produces predictions.
-The lack of the ability to understand and assess a model makes it difficult to trust the model, especially in areas with high stakes decisions such as medical and forensics sciences.
-The increased use of machine learning models in applications and the introduction of the General Data Protection Regulation (GDPR) in 2018 \citep{goodman:2016} has resulted in a dramatic increase in explainable machine learning research, which focuses on developing ways to explain output from machine learning algorithms.
-
-Throughout this paper, we distinguish between interpretability and explanability of models.
-We define {\it interpretability} as the ability to directly use model parameters to understand the relationships in the data captured by the model: e.g., a linear model coefficient associated with a predictor variable indicates the amount the response variable changes based on a change in the predictor variable.
-In contrast, define {\it explanability} as the ability to use the model in an indirect manner to understand the relationships in the data captured by the model: e.g., partial dependence plots depict the marginal relationship between model predictions and predictor variables \citep{friedman:2001}.
-
-Numerous methods have been proposed to provide explanations for black-box model predictions \citep{gilpin:2018, guidotti:2018, ming:2017, molnar:2019}.
-Some are specific to one type of model (e.g.
-\citep{simonyan:2013} and \citep{urbanek:2008}), and others are model-agnostic (e.g.
-\citep{fisher:2018} and \citep{strumbelj:2014}).
-In this paper, we focus on one specific model-agnostic method: LIME \citep{ribeiro:2016}.
-
-LIME (local interpretable model-agnostic explanations) is a method that uses a surrogate model to relate predictor variables to black-box model predictions (i.e.
-a model explainer) \citep{ribeiro:2016}.
-We distinguish between the terms of model explainer and explainer model: by \emph{model explainer} we denote the method for explaining a complex model using a surrogate model, while the \emph{explainer model}, or simply the \emph{explainer}, is the surrogate model.
-
-While some model explainers focus on understanding a model at the global level, LIME claims to provide explanations for individual predictions (local).
-Additionally, LIME is designed to work with any model (model-agnostic) and to produce easily understandable results (explanations) \citep{ribeiro:2016}.
-Conceptually, LIME fits a simple (interpretable) model, the explainer model,  meant to capture the behavior of the (complex) black-box model in a local region around a prediction of interest.
-The  simple model then provides interpretable estimates for variables that most influenced the prediction made by the complex model.
-
-\begin{figure*}[!thp]
-\centering 
-\includegraphics[width=6.5in]{figure-01-1}
-\caption{A conceptual depiction of a faithful LIME explainer model in the immediate neighborhood of a prediction of interest.
-The predictions from a hypothetical black-box model are plotted against the standardized values of the two hypothetical predictor variables.
-The diamond shaped points represent the location of a prediction of interest.
-The size and opacity of the circular points indicate the weight assigned based on the distance to the prediction of interest computed using the inverse of the Gower distance metric raised to the power of 50.
-The black lines represent  a weighted ridge regression model used as an explainer model that reasonably captures the relationship between the black-box predictions and the features in a local region around the prediction of interest.
-That is, the explainer is faithful to the complex model and produces a reasonable explanation that Feature 1 plays a more important role in the prediction of interest than Feature 2 since the magnitude of the slope associated with Feature 1 is larger.}
-\label{fig:figure-01}
-
-\vspace*{\floatsep}
-
-\centering 
-\includegraphics[width=6.5in]{figure-02-1} 
-\caption{A conceptual depiction of an unfaithful local explainer model in the immediate neighborhood of a prediction of interest.
-A ridge regression model is fit to the same hypothetical black-box model predictions and predictor variables as in \autoref{fig:figure-01}, but the weights are computed using a Gower exponent of 1.
-The explainer model is unfaithful to the complex model in any immediate neighborhood of the prediction of interest.}
-\label{fig:figure-02}
-\end{figure*}
-
-\autoref{fig:figure-01} provides a visualization of this conceptual understanding of LIME.
-The two plots show the predictions from a hypothetical black-box model plotted against the two hypothetical model predictor variables.
-The diamond shaped points represent the location of the prediction of interest.
-A Gower distance metric \citep{gower:1971} is used to define locality such that the size of the points represent the inverse of the Gower distance raised to some value and indicate the proximity to the prediction of interest.
-In the example of \autoref{fig:figure-01}, an exponent of 50 is used to emphasize a very local region around the prediction of interest.
-A ridge regression model weighted by the proximity values is used as the explainer model with the black-box predictions as the response variable and standardized versions of two features in the data as predictor variables.
-Standardized features allow direct comparisons of the model coefficients.
-The explainer model is depicted by the black lines in the figure.
-
-The plot on the left of \autoref{fig:figure-01} shows the relationship between the black-box predictions and Feature 1.
-Here, the explainer model is plotted with Feature 2 fixed at the observed value of the prediction of interest.
-The explainer model captures the relationship in an  immediate neighborhood around the prediction of interest with a slope of 0.068.
-The plot on the right shows no global or local relationships between the black-box predictions and Feature 2.
-Here, the explainer model is plotted with Feature 1 set as the observed value of the prediction of interest, and it has an appropriately small slope of -0.001.
-The magnitude of the slope associated with Feature 1 is larger than the slope of Feature 2, which suggests that Feature 1 plays a more important role in the prediction made by the black-box model for the prediction of interest.
-This explanation agrees with a visual assessment of the relationships between the predictions and predictor variables.
-
-The concept of LIME is relatively simple: use an interpretable model to approximate a complex model in a local region.
-However, a practical implementation of LIME is not straightforward, and research is being done to improve the procedure \citep{laugel:2018}.
-The current implementations of LIME \citep{ribeiro:2020} \citep{pedersen:2020} offer various tuning parameters (see Section \ref{background}) that affect the explainer model and ultimately, the explanation.
-Since the explainer model is an approximation of the complex model and not a direct interpretation, the explanations produced by an explainer model are subject to the quality of the approximation.
-Thus, in order to achieve accurate explanations, the tuning parameter values selected need to be assessed.
-
-We consider an example where the choice of exponent for the weights is crucial to the quality of the explanation.
-The plots in Figure \ref{fig:figure-02} show the same data as \autoref{fig:figure-01}, but the Gower distance metric exponent is decreased to 1 (the default exponent in the \emph{lime} R package).
-This causes the observations that are further away from the prediction of interest to be given larger weights than before.
-In \autoref{fig:figure-01}, the explainer model captures the relationship between the black-box predictions in an immediate neighborhood of the prediction of interest.
-This cannot be said of the explainer model in \autoref{fig:figure-02}.
-In addition, the magnitude of the slope associated with Feature 2  (0.011) is larger than that of Feature 1 (0.005).
-Thus, this explainer model actually provides a misleading explanation that Feature 2 plays a more important role in the prediction of interest.
-
-Several sources in the literature discuss the performance of LIME.
-One of the biggest difficulties with LIME is determining how to specify a local region \citep{laugel:2018} \citep{molnar:2019}.
-This is due to an unclear definition of a "local region" and how to apply LIME to achieve an appropriate local region as demonstrated by \autoref{fig:figure-02}.
-\citet{alvarezmelis:2018} raise a concern pertaining to the robustness of explanations from LIME and other model explainers: they find that even small changes in predictor variables can lead to very different LIME explanations.
-Additionally, \citet{ribeiro:2016} acknowledge that if a linear model is used as the explainer, LIME relies on a linear approximation of the explainer model to the complex model and state "if the underlying model is highly non-linear even in the locality of the prediction, there may not be a faithful explanation".
-
-As a result of the various ways LIME can fail, it is important to assess LIME explanations.
-We suggest the use of visual diagnostics for assessment.
-In this paper, we lay out the set of claims about LIME made by \citet{ribeiro:2016} and propose three visualizations for the assessment of these claims: (1) \emph{explanation scatterplot}, (2) \emph{feature heatmap}, (3) \emph{assessment metric plot}.
-While LIME is implemented for image, tabular, and text data, we only focus on tabular data.
-For additional simplicity, we only discuss classification prediction models with a dichotomous response variable and continuous predictor variables.
-However, the proposed diagnostics may be extended to a wider range of situations.
-
-The remainder of the paper is structured as follows.
-Section \ref{background} provides background and claims made by \citet{ribeiro:2016} about LIME.
-We introduce the suggested diagnostic plots in Section \ref{diagnostics}.
-Then in Section \ref{application}, we demonstrate the use of the diagnostics to assess LIME explanations for a random forest  fit to a forensics bullet matching dataset.
-Section \ref{discussion} concludes with a discussion on extensions and limitations of the diagnostic plots and concerns about LIME in regards to the claims made by \citet{ribeiro:2016} brought about by the visualization examples in this paper that agree with \citet{alvarezmelis:2018}, \citet{laugel:2018}, and \citet{molnar:2019}.
-
-All runs of LIME in this paper are executed in a forked version\footnote{https://github.com/goodekat/lime} of the R package \emph{lime} (version 0.5.1) by \citet{pedersen:2020}.
-The forked version is functionally indistinguishable from \citeauthor{pedersen:2020}'s implementation but allows us to export internal values relevant for an assessment of the explainer.
-The diagnostic plots included in this paper are created using the R package \emph{limeaid} \citep{goode:2020}.
-
-\section{Background on LIME} \label{background}
-
-\citet{ribeiro:2016} provide an implementation of LIME in a Python package \cite{ribeiro:2020}.
-An adaption of the Python package in R has been implemented and made available by Thomas Lin-Pedersen \citep{pedersen:2020}.
-The discussion of parameter choices and implementation details of LIME in this paper are based on the R package.
-
-The general form of the LIME algorithm can be divided into three steps \citep[see also][]{laugel:2018}:
-
-\begin{enumerate}
-
-\item \emph{Data Simulation and Interpretable Transformation}: Simulate a dataset from the original data used to fit the black-box model.
-Apply a transformation to the simulated data and the prediction of interest that will allow for interpretable explanations.
-
-\item \emph{Explainer Model Fitting}: Apply the black-box model to the simulated data to obtain predictions.
-Compute the distance between each of the simulated data points and the prediction of interest.
-Perform feature selection.
-Fit an interpretable model with the black-box predictions from the simulated data as the response, the selected features from the transformed simulated data as the predictors, and the distances as weights.
-This model is the explainer model.
-
-\item \emph{Explainer Model Interpretation}: Interpret the explainer model to determine which features played the most important role in the prediction of interest.
-
-\end{enumerate}
-
-During the application of LIME, the user is asked to select various tuning parameter options: the number of features to return in the explanation, the simulation method, the feature selection method, and how the weights are computed.
-An overview of the options available for the tuning parameters is included in Appendix~\ref{lime-details}.
-
-In the original paper, \citet{ribeiro:2016} make the following set of claims regarding the performance of LIME:
-
-\begin{itemize}
-\item \emph{Interpretability}: The explainer model can be easily interpreted to provide meaningful explanations.
-\item \emph{Faithfulness}: The explainer model sufficiently captures the relationship between the complex model predictions and the features in the local region around a prediction of interest to produce explanations that are faithful to the complex model.
-\item \emph{Linearity}: By using a ridge regression model as the explainer model, it is assumed that there is a linear relationship between complex model predictions and the features in the local region around a prediction of interest.
-\item \emph{Localness}: The explanations produced by LIME are local in regards to a prediction of interest.
-\end{itemize}
-
-The assumption of interpretability only depends on the complexity of the model used as explainer model.
-If the model is too complex to provide meaningful explanations (e.g.
-there are too many variables in the model), it is clear that the assumption of interpretability is violated.
-The other three assumptions are not as easy to assess, and for those, we suggest the use of diagnostic plots.
-
-\section{Visual Diagnostics for LIME} \label{diagnostics}
-
-\begin{figure*}[!thp]
-\centering
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-
-{\centering \includegraphics[width=6.5in]{figure-03-1}
-
-}
-
-\end{knitrout}
-\caption{Plots of $x_2$ versus $x_1$ from the training (left) and testing (right) sets of the \data \ introduced in Section \ref{diagnostics}.
-The true classification boundary is shown as the solid black line in both plots.
-The color of the training data  represents the value of the observed response variable ($y$).
-The color of the testing data  represents the random forest probability that an observation belongs to the category of blue.
-The 18 cases that are misclassified by the random forest are identified by black circles.
-The prediction of interest to explain is indicated by a diamond.}
-\label{fig:figure-03}
-\end{figure*}
-
-In this section, we introduce three visual diagnostic plots for the assessment of LIME.
-The plots focus on different levels of application of LIME (e.g.
-on explanation versus a set of explanations) to assess the LIME claims from different perspectives:
-
-\begin{enumerate}
-\item \emph{Explanation Scatterplot} (Section \ref{exp-scatter}): Comparison of the explainer and complex models for an individual prediction of interest.
-\item \emph{Feature Heatmap} (Section \ref{feat-heat}): Comparison of features selected by LIME across applications of LIME with different tuning parameter values.
-\item \emph{Assessment Metric Plot} (Section \ref{assess-metric}): Comparison of performance metrics for LIME across applications of LIME with different tuning parameter values. 
-\end{enumerate}
-
-\paragraph{The \data}
-
-To demonstrate the visual diagnostics, we generate an example dataset that will be referred to as the \data.
-The \data \ contains 600 observations with three features and one response variable.
-The features, $x_1$, $x_2$, and $x_3$, are randomly sampled from Unif(-10, 10), Unif(-10, 10), and $\mbox{N}(0,1)$ distributions, respectively.
-A binary response variable $y$ is  created using a rotated sine curve.
-In particular, let $x'_1=x_1\cos(\theta)-x_2\sin(\theta)$ and $x'_2=x_1\sin(\theta)+x_2\cos(\theta)$ where $\theta=-0.9$.
-Then $y$ is defined as
-\begin{eqnarray}\label{eq:data}
-  y=\begin{cases}
-  \mbox{blue} & \mbox{ if } x'_2 > \sin\left(x'_1\right) \\
-  \mbox{red} & \mbox{ if } x'_2 \le \sin\left(x'_1\right) \ . %\nolabel
-  \end{cases}
-\end{eqnarray}
-Note that due to the creation of $y$ in this manner, $y$ is dependent on $x_1$ and $x_2$ and independent of $x_3$.
-The dataset is divided into training and testing sets of 500 and 100 observations, respectively.
-A random forest  is fit using the R package \emph{randomForest} (version 4.6.14) \citep{liaw:2002} with the default settings.
-The model is applied to the test set to obtain predictions.
-
-\autoref{fig:figure-03} shows scatterplots of $x_2$ versus $x_1$ from the training data (left) and the testing data (right).
-Both plots include the true classification boundary of the rotated sine function plotted as the solid black line.
-The training data are colored by the observed response variable ($y$), and the testing data are colored by random forest  prediction probabilities.
-The random forest  misclassifies 18 points, which are all located near  the classification boundary.
-These are identified by open circles in \autoref{fig:figure-03}.
-
-From these scatterplots, we also see that the global relationship between response $y$ and features $x_1$ and $x_2$ is linear: the probability for label blue increases with the difference between features $x_2$ and $x_1$.
-Locally, the relationship between $y$ and features $x_2$ and $x_1$ varies a lot more around the line of identity.
-Here, the relationship is determined by the sine waves.
-However, the sine is a good-natured function that can be approximated well linearly in local regions.
-
-We apply LIME using six sets of tuning parameter values to all observations in the \data \ test set to observe variability across tuning parameter values.
-A quantile bin based simulation method (samples are simulated uniformly from a specified number of quantile bins) is used for five of the LIME applications with the number of bins varying from 2 to 6 by application.
-We use 6 bins as the maximum, because the complexity of the explanations increases with the number of bins.
-Note that 4-quantile-bins are the default method in \emph{lime}.
-The sixth application of LIME uses a kernel density simulation method (samples are drawn from kernel density approximations of the feature distributions).
-The default methods for feature selection (forward selection) and the computation of the weights (Gower distance raised to an exponent of 1) are used for all applications.
-(See Appendix~\ref{lime-details} for descriptions of the tuning parameters.)
-
-For the presentation of the explanation scatterplot, we focus on the misclassified point with $(x_1, x_2, x_3)$ coordinates of (1.23, 8.47, -0.99) indicated by a diamond in \autoref{fig:figure-03}.
-Misclassified points are often of interest to explain since they may provide information about ways to improve the model.
-For the introduction of the other two  plots, we consider the LIME explanations for  all observations in the \data \ test data.
-
-\begin{figure*}[!thp]
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-
-{\centering \includegraphics[width=6.5in]{figure-04-1}
-
-}
-
-\end{knitrout}
-\caption{(left) Visualization from the \emph{lime} R package of a LIME explanation for the \data \ prediction of interest identified in \autoref{fig:figure-03}.
-(right) \emph{Explanation Scatterplot}.
-The points represent the simulated data colored by the random forest probabilities and sized by the assigned LIME weights.
-The prediction of interest is shown as the diamond shaped point.
-The explainer model indicator variables associated with $x_1$ and $x_2$ (quantile bins containing the prediction of interest) are depicted by the solid lines.
-The line colors represent the explainer model coefficient signs and indicate whether the feature supports a prediction of `blue' (blue lines) or supports a prediction of `red' (red lines).
-This figure shows that the quantile bins are not flexible enough to capture the relationship between the random forest predictions and the $x_1$ and $x_2$ values.}
-\label{fig:figure-04}
-\end{figure*}
-
-\paragraph{A Visual Representation of a LIME Explanation}
-
-Before introducing the visual diagnostics, let us consider a commonly used visualization of a LIME explanation that is shown in Figure \ref{fig:figure-04} (left).
-The plot is created using the \emph{lime} R package and provides a visual representation of a LIME explanation for the prediction of interest indicated in \autoref{fig:figure-03}.
-In particular, the explanation is obtained using 4-quantile-bins to simulate the data.
-In this scenario, LIME converts continuous predictor variables to indicator variables identifying whether the variable value falls in the same quantile bin as the prediction of interest or not.
-The indicator variables are used as the explainer model features.
-
-The plot reports 0.74 as  the random forest  probability  that the observation of interest belongs to category blue (denoted as the ``label" in the plot).
-The lengths of the bars represent the  coefficients from a ridge regression model (the explainer model) fit using the R package \emph{glmnet} \citep{simon:2011} associated with the indicator variables chosen via feature selection.
-The color of a  bar denotes the sign of the coefficient and whether the feature "supports" or "contradicts" a random forest classification of `blue'.
-The "explanation fit" is the deviance ratio from  \emph{glmnet}.
-In other words, this is the $R^2$ value associated with the explainer model.
-In this case, it is 0.21 suggesting that the explainer model is not a good linear fit.
-However, it is commonly accepted that $R^2$ has limitations for assessing the quality of fit of a model \citep{sapra:2014} and  should not be used as the only metric in a model assessment.
-
-The explanation for the prediction of interest depicted in Figure \ref{fig:figure-04} is interpreted as follows.
-A random forest classification of blue is supported by the prediction of interest having a value of $x_2$ that is greater than 4.834, but the prediction of interest having a value of $x_1$ that is greater than -0.302 and less than or equal to 4.844 provides support against a classification of blue.
-Since the weight associated with $x_2$ has a larger magnitude than the weight associated with $x_1$, LIME explains that $x_2$ plays a more important role in the random forest prediction.
-Additionally, consider that since the support for blue by $x_2$ outweighs the support for red by $x_1$, the explainer model overall favors a label of blue for the prediction of interest, which agrees with the random forest probability of 0.744 for blue.
-Note that both models classify the observation incorrectly.
-
-\subsection{Explanation Scatterplots} \label{exp-scatter}
-
-Based on the plot on the left of \autoref{fig:figure-04} alone, it is not possible to make an informed assessment of the explanation.
-For a further assessment of the explainer model, we turn to an \emph{explanation scatterplot}: a visual diagnostic for assessing the LIME claims of locality and fidelity for an individual explanation by juxtaposing the complex and explainer models in one plot.
-The format of an explanation scatterplot depends on the LIME simulation method.
-We introduce the explanation scatterplot here under the \emph{lime} R package default method of 4-quantile-bins.
-
-The explanation scatterplot applies the concept of plotting the model in the data space discussed in \citet{wickham:2015}.
-The plot is built by plotting the LIME simulated data for the top two features identified by the explanation in a scatterplot and coloring these points by the predictions from the complex model.
-The point size represents the weight assigned by LIME.
-In order to show the LIME results for the observation of interest, lines are drawn on top of the points.
-These lines  represent the boundaries of the indicator variables used to fit the explainer model.
-The line color  denotes whether LIME indicates that a feature supports or contradicts a class prediction.
-Appendix \ref{exp-scatter_plus} addresses the explanation scatterplot formats in other LIME simulation scenarios.
-
-An explanation scatterplot corresponding to the LIME explanation depicted on the left in \autoref{fig:figure-04} is shown on the right hand side of \autoref{fig:figure-04}.
-By juxtaposing the random forest predictions and the explainer model boundaries, we are able to assess the faithfulness and localness of the explainer model.
-
-First, consider the claim of localness.
-The weights decay relatively slowly outside of the intersection of the 2-quantile-bin suggesting that the LIME explanation is highly influenced by points outside of the bins containing the prediction of interest.
-However, it is difficult to say if the claim of localness has been violated, because a definition of a local region is not specified.
-Depending on what region a viewer considers to be local, an argument could be made in favor of or against a violation of localness.
-The explanation scatterplot raises awareness of the unclear definition of a local region with LIME.
-Nevertheless, it is possible to say that the weights assigned to the simulated data do not capture  the local region identified by the intersection of the quantile bins.
-
-Now, consider the claim of faithfulness: It can be said that the majority of the points in the $x_2$ quantile support a prediction of blue, which is captured by the bar supporting a prediction of blue in the LIME explanation, and a similar statement can be made about the $x_1$ quantile-bin.
-These statements validate the explanation produced by LIME.
-However, the explanation scatterplot plot shows that the random forest performs well at capturing the sine curve classification boundary by creating various sized rectangles consisting of predictions with similar probabilities, which the LIME explanation does not pick up on.
-Thus, LIME does provide an explanation for the prediction, but it is a very poor explanation in terms of faithfulness to the random forest prediction regions.
-
-It is difficult to assess linearity from this explanation scatterplot, but a residual plot of the explainer model could be used to check the linearity claim.
-See Appendix~\ref{residual-plot} for the residual plot associated with the explanation considered in Figure \ref{fig:figure-04}, which shows a violation of the linearity claim.
-
-This example explanation only includes two features.
-In situations where more than two features are included in a LIME explanation, the explanation scatterplots can be extended to a generalized pairs plot \citep{emerson:2013} that includes all pairwise combinations of features.
-Generalized pairs plots (and scatterplot matrices in general) have diminishing value when the number of features increase \citep{jensen:2011} \citep{sweller:2011}.
-Machine learning models are commonly fit using a large number of features, and therefore, a generalized pairs plot of explanation scatterplots for all features would be ineffective.
-However, when applying LIME, the user selects the number of features to return in the explanation.
-In the \emph{lime} R package, \citet{pedersen:2020} encourage users to select less than 10 features.
-As long as a small number of features are returned in the LIME explanation,  it is feasible to use a generalized pairs plot of explanation scatterplots.
-An example is shown in Section~\ref{bullet-assess-ex}.
-
-\subsection{Feature Heatmap} \label{feat-heat}
-
-\begin{figure}[!thp]
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-
-{\centering \includegraphics[width=3.125in]{figure-05-1}
-
-}
-
-\end{knitrout}
-\caption{Hypothetical examples of feature heatmaps in two possible situations.
-The heatmaps show the top feature chosen for 10 cases across 5 different sets of tuning parameter values.
-The color of the cell indicates the feature chosen by LIME.
-Situation 1 is the ideal, because the explanations vary across cases but do not dependent on specific tuning parameter values.}
-\label{fig:figure-05}
-
-\vspace*{\floatsep}
-
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-
-{\centering \includegraphics[width=3.125in]{figure-06-1}
-
-}
-
-\end{knitrout}
-\caption{\emph{Feature Heatmap}.
-An example feature heatmap of the explanations from the applications of LIME with different tuning parameter values to the \data \ test set.
-The cases from the test set are plotted on the y-axis, and the tuning parameter values (simulation methods here) are included on the x-axis.
-The colors of the tiles indicate the feature selected by LIME for the corresponding case and tuning parameter value.
-The plot is faceted by the first and second most important features selected by LIME (top and bottom facets, respectively).
-The vertical facets separate the  kernel density method from the quantile bin methods.
-The vertical striping indicates that the LIME explanations are not consistent across tuning parameter values.}
-\label{fig:figure-06}
-\end{figure}
-
-Explanations produced by LIME are likely to be affected by the choice of tuning parameter values.
-A hypothetical example of this is shown by Figures \ref{fig:figure-01} and \ref{fig:figure-02} where the method used to weight the observations influenced the explanation.
-As of the time of writing this manuscript, we have encountered no recommendations for how to specify the parameter values besides for the default settings in \emph{lime}.
-In order to compare the explanations produced by LIME using different tuning parameter values and provide another perspective for assessing localness, we visualize an overview of the explanations with the \emph{feature heatmap} diagnostic plot.
-
-The feature heatmap uses colors to identify the features selected by LIME across multiple predictions (referred to as cases here) and tuning parameter values organized by the  feature importance assigned by LIME.
-That is, for LIME applied with $t$ sets of tuning parameter values to $n$ cases to select the $f$ top features, create $f$ heatmaps (one for each of the positions of importance determined by the magnitude of the explainer model coefficients) with the cases on the $y$-axis, the tuning parameter values on the $x$-axis, and the cells colored by the feature chosen for the corresponding case and tuning parameter value.
-Additional tuning parameters may also be included in the plot via facets.
-
-Two hypothetical examples of feature heatmaps are included in \autoref{fig:figure-05}.
+Two hypothetical examples of feature heatmaps are included in Figure \ref{fig:figure-s1}.
 The plots are created with the assumption that LIME is applied to select the top feature out of $p=4$  features for $n=10$ cases with $t=5$ sets of tuning parameter values.
@@
 
-\autoref{fig:figure-06} shows a feature heatmap for the LIME applications to the 100 observations in the \data \ test set.
-The most important and second most important features selected by lime are shown in in the top and bottom facets, respectively.
-For the quantile bins, the original features prior to the indicator variable transformation are included since it is obvious that different features would be selected when the sizes of the bins change.
-This figure shows that for kernel density and 2-quantile-bins, LIME selects $x_1$ as the most important feature and $x_2$ as the second most important feature across all cases in the test set.
-These explanations are not local.
-There is variability in the features selected by LIME for 3- to 6-quantile-bins suggesting more local explanations.
-There are signs of vertical striping, which suggests a dependence on tuning parameters.
-Note that the explanations from 3- and 5-quantile-bins include the selection of the random noise variable ($x_3$) as an important variable in many predictions, which should not be the case.
-The pattern seen in the explanations for 3- to 6-quantile-bins may suggest local explanations, but the dependence on tuning parameters makes it unclear which set of explanations to use.
-
-\subsection{Assessment Metric Plot} \label{assess-metric}
-
-\begin{figure}[!thp]
+\begin{figure}
 \begin{knitrout}
@@
 
-{\centering \includegraphics[width=3.25in]{figure-07-1}
+{\centering \includegraphics[width=3.125in]{figure/figure-s1-1}
 
@@
 \end{knitrout}
-\caption{\emph{Assessment metric plot}.
-The assessment metrics computed on the applications of LIME to the \data \ test set are included in this example assessment metric plot.
-Each horizontal facet corresponds to one of three metrics: average $R^2$, average fidelity, or MSEE.
-The LIME tuning parameter values (simulation methods in this example) are plotted on the x-axis, and the metric values are shown on the y-axis.
-The points are colored by rank (within a metric) indicating best to worst (dark to light).
-The kernel density simulation methods performs well across all three metrics.}
-\label{fig:figure-07}
+\caption{Hypothetical examples of feature heatmaps in two possible situations.
+Situation 1 is the ideal, because the explanations vary across cases but do not dependent on specific tuning parameter values.
+Situation 2 suggests global explanations and extreme explanation dependence on the tuning parameter values.}
+\label{fig:figure-s1}
 \end{figure}
 
-The feature heatmap for the \data \ in the previous section shows an example of inconsistent LIME explanations across tuning parameter values.
-In this situation, the user must determine which set of explanations to trust.
-One way to do this is to compute assessment metrics for each set of explanations to identify the optimal tuning parameter values.
-We discuss three metrics for this purpose and present a visual comparison in an \emph{assessment metric plot}.
+\section{Additional Bullet Matching Explanation Scatterplots} \label{bullets-plus}
 
-Each metric presented below is computed on  LIME explanations for a set of predictions obtained using the same tuning parameter values.
-Here we provide a high level description of the metrics.
-Notation and formulas for these metrics are included in Appendix \ref{metric-details}.
+Figure \ref{fig:figure-s2} includes visual representations of LIME explanation from the \emph{lime} R package and explanation scatterplots for a known match observation in the the bullet example referred to as cases M for two different data simulation methods: 4-quantile-bins (left column) and 4-equal-bins (right column).
+Both explanations appear to be more faithful to the random forest than those associated with case NM in Section \ref{bullet-assess-ex}, but the intersections of the bins could be better aligned with the regions containing similar probabilities produced by the random forest.
+Figure \ref{fig:figure-s3} includes explanation scatterplots for bullet example cases M and NM when the kernel density simulation method is used.
 
-\begin{itemize}
-\item \emph{Average $R^2$}: Assess the model fit and linearity claim by computing the average of the explainer model $R^2$ values (deviance ratios from the R package \emph{glmnet}).
+\begin{figure*}[!t]
 
-\item \emph{Average Fidelity}: Measures the faithfulness of the explainer model to the complex model by comparing their predictions.
-Computed as the average of the explainer model fidelity metrics: a metric presented in \citet{ribeiro:2016} (the weighted distance between explainer and complex model predictions for all observations in the LIME simulated data associated with an individual prediction of interest).
-
-\item \emph{Mean Squared Explanation Error (MSEE)}: Also measures the faithfulness of the explainer model to the complex model by comparing their predictions, but only the prediction of interest is used to compute an average squared deviation between explainer and complex model predictions.
-\end{itemize}
-
-\autoref{fig:figure-07} shows an example assessment metric plot.
-The three metrics are computed for each of the LIME applications to the \data \ test set.
-The simulation methods are listed on the x-axis.
-The plot is faceted by metric, and the metric values are plotted on the y-axis.
-The colors of the points represent the rank of the simulation methods performance based on a particular metric (darker indicates a better metric value and lighter indicates a worse metric value).
-Higher average $R^2$ values are better, and lower average fidelity and MSEE values are better.
-This example only includes one tuning parameter: the simulation method.
-If more than one tuning parameter is considered, the assessment metric plot is extended by adding additional facets or levels to the x-axis.
-
-All three metrics suggest that the kernel density method performed well, but the metrics disagree for the quantile bins methods.
-Average $R^2$ and average fidelity rank the performance of the number of quantile bins the same (2-quantile-bins perform the best and 6-quantile-bins perform the worst).
-In fact, these two metrics appear to have a mirrored  relationship in this example.
-MSEE provides almost the exact opposite results with  6-quantile-bins performing the best and 2-quantile-bins performing the worst.
-Average fidelity and MSEE are similar metrics, so it is not surprising that they would agree in this example.
-Another factor might be that MSEE only takes the prediction of interest  into account and not the full simulated dataset.
-The contradiction between metrics makes it difficult to identify which simulation method to trust.
-
-Recall that \autoref{fig:figure-06} indicated that the kernel density method selected the same feature across all cases in the test set for both the first and second features.
-It appears that a global trend may be the best explanation for this example, which may be reasonable considering that we know that both $x_1$ and $x_2$ are the two features that should be the features used by the random forest to distinguish between response categories.
-
-\section{Application to Bullet Matching Data} \label{application}
-
-In this section, we provide a discussion of the application of the visual diagnostics for LIME explanations to a practical data problem investigating the similarity of marks on fired bullets.
-
-\subsection{Bullet Matching Data}
-
-In current practice, forensic firearm examiners evaluate whether two bullets are from the same source (fired from the same gun) or from different sources based on microscopic comparison of the striation patterns engraved on bullets during the firing process (see \autoref{fig:figure-08}).
-The process is based on a visual and therefore subjective assessment of the evidence.
-The lack of objective evaluation and the associated absence of established error rates has first been criticized by the National Research Council \cite{nrc:2009} and later by the President's Council of Advisors on Science and Technology \cite{pcast:2016}.
-
-In response, \citet{hare:2017} proposed an automated machine learning method for bullet matching to complement a visual inspection by firearm examiners.
-Based on high-resolution topological scans of land engraved areas, \citet{hare:2017} obtain signatures of striations from two bullet lands (\autoref{fig:figure-09}).
-Nine features quantifying the similarity of signatures, such as the cross-correlation function, the distance between signatures, and the number of matching striae, are extracted and used to train a random forest to determine the probability of a comparison resulting from the same source (matching signatures) or from different sources (non-matching signatures).
-The model in \citet{hare:2017} was trained on a set of scans of bullets from the James Hamby Consecutively Rifled Ruger Barrel Study \citep{hamby:2009}, which included 10,384 land-to-land comparisons \citet{hare:2017}.
-See the supporting information for additional information on the signature similarity features.
-
-\begin{figure}[!t]
-\centering
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-
-{\centering \includegraphics[width=2.25in]{figure-08-1}
-
-}
-
-\end{knitrout}
-\caption{(Top left) Traditionally rifled gun barrel.
-The grooves and lands alternate to give bullets a spin during the firing process, which create markings (striations) on a bullet when fired.
-(Top right) Image of a fired bullet.
-The vertical stripes along the lower half of the bullet show groove and land engraved areas.
-The land engraved areas contain the microscopic striations created when the bullet passed through the barrel of the gun.
-(Bottom) Close up of a land engraved area showing striations (vertical lines).}
-\label{fig:figure-08}
-
-\vspace*{\floatsep}
-
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-
-{\centering \includegraphics[width=3.125in]{figure-09-1}
-
-}
-
-\end{knitrout}
-\caption{Example bullet signatures.
-The bullet signatures correspond to the same land and therefore have very similar patterns.
-The \citet{hare:2017} random forest is fit using various features that measure the similarity between two such signatures.}
-\label{fig:figure-09}
-\end{figure}
-
-\subsection{Application of LIME to Bullet Matching Data}
-
-\begin{figure*}[!thp]
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-
-{\centering \includegraphics[width=6.5in]{figure-10-1}
-
-}
-
-\end{knitrout}
-\caption{Parallel coordinate plots of the \citet{hare:2017} random forest predictions from the training (top facet) and testing (bottom facet) data.
-The observations are separated by known matching (right column) and non-matching (left column) signatures.
-The y-axis shows the standardized feature values, and the x-axis shows the features used to fit the random forest (ordered by random forest impurity based feature importance).
-Each line corresponds to an observation, and the line color represents the associated random forest probability.
-There are clear relationships between the feature values and the random forest probabilities.}
-\label{fig:figure-10}
-\end{figure*}
-
-Since firearm identification is commonly used as evidence for convictions in court cases, it is important to be able to understand and assess a model used to quantify the probability that a bullet is fired from a gun.
-LIME explanations would provide a local explanation for an individual prediction, but just as it is important to assess the model for this high-stakes application, it is also important to assess the LIME explanations.
-We will demonstrate an assessment of LIME explanations using the visual diagnostics introduced in this paper.
-
-A random forest model fit to an expanded dataset of 83,028 land-to-land comparisons from two sets of bullets in the James Hamby Consecutively Rifled Ruger Barrel Study \citep{hamby:2009} was validated in \citet{vanderplas:2020}.
-Here, we train a random forest model to mimic the model validated in \citet{vanderplas:2020} using the same data, model structure, and features (the nine similarity measures developed in \citet{hare:2017}).
-We apply the trained random forest model to 6 bullets from another set of the Hamby study with 364 rows of land comparisons.
-See the supporting information for further descriptions of the data.
-
-The newly trained random forest has an out-of-bag accuracy of 1 and out-of-bag false positive and false negative rates of 0.3 and \ensuremath{2\times 10^{-4}}, respectively.
-On the test data, the random forest performance decreases with an accuracy of 0.85 and false positive and false negative rates of 0.55 and 0.011, respectively.
-This is an example where explanations of the model predictions could provide insight to the cause of the decrease in model performance on the test data.
-
-We consider a global visualization of the relationship between the random forest predictions and the model features with a parallel coordinate plot of the training data (top facet) and testing data (bottom facets)  (\autoref{fig:figure-10}).
-In the training data we observe a clear difference in feature values based on whether the corresponding random forest scores are close to 1 or 0.
-High values of rough correlation, cross correlation function, and number of matches are indicative of random forest scores close to 1; similarly, low values of mismatches, distance, and non-consecutively matching striae are also associated with random forest scores close to 1.
-Observations in the test data that are classified incorrectly by the random forest tend to have feature values similar to observations in the training data with similar random forest scores.
-For example, the observations in the test set known to be a match but have a random forest score below 0.5 have relatively low values of rough correlation, cross correlation function, and matches and relatively large values of mismatches, distance, and non-consecutively matching striae compared to observations with a random forest probability close to 1.
-
-LIME is applied to all test set observations using different tuning parameter values: 12 sampling methods (2 to 6 equally spaced bins, 2 to 6 quantile-bins, kernel density estimation, and normal approximation) and 3 Gower exponents (0.5, 1, and 10).
-Thus, a total of $12\times 3=36$ different applications of LIME are performed.
-We specify that each LIME explanation return 3 features, and feature selection is performed using the default option in LIME, which selects the features with the highest weights in a ridge regression model.
-
-\subsection{LIME Assessment Visualizations} \label{bullet-assess-ex}
-
-To get an overview of the LIME explanations from the 36 applications, we consider a feature heatmap (\autoref{fig:figure-11}).
-In addition to facets for simulation method and LIME feature importance, this plot includes a vertical facet for Gower power and a horizontal facet for whether the observation is a known match or non-match.
-This plot highlights several key features of the LIME explanations from the bullet matching dataset.
-
-First, applications of 2-quantile-bin simulations produce the same explanations for almost all cases and LIME tuning parameter values.
-This suggests that the LIME explanations are global and not local.
-Second, within a simulation method, the features selected by LIME for an observation do not appear to vary by the Gower power.
-However, the LIME explanation for an observation often varies across simulation methods.
-With the equal-bins, there are vertical stripes that suggest a dependence of the LIME explanations on the number of bins.
-The vertical stripes are not as apparent with the quantile bins.
-Lastly, there are clear differences between the LIME explanations produced by the bin based simulation methods for the matches and non-matches.
-This suggests that different features are of importance in the random forest, depending on whether the observation corresponds to match or non-match.
-
-\begin{figure*}[!thp]
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-
-{\centering \includegraphics[width=6.5in]{figure-11-1}
-
-}
-
-\end{knitrout}
-\caption{Feature heatmap of 36 LIME applications to the bullet comparison data test set.
-In addition to faceting the results by simulation method and LIME feature selection order, facets for the Gower power and whether the observation is a match or non-match are included.
-The vertical stripes of features selected indicate a dependence between the LIME explanations and tuning parameter values.}
-\label{fig:figure-11}
-
-\vspace*{\floatsep}
-
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-
-{\centering \includegraphics[width=6.5in]{figure-12-1}
-
-}
-
-\end{knitrout}
-\caption{Assessment metric plot for the applications of LIME on the bullet comparison data test set.
-There are discrepancies in performance across metrics for a set of tuning parameter values, but based on the overall performance of all three metrics, 4-equal-bins with a Gower power of 0.5 appears to perform the best.}
-\label{fig:figure-12}
-\end{figure*}
-
-To try to identify a set of LIME tuning parameter values with the most trustworthy set of explanations, an assessment metric plot is considered (\autoref{fig:figure-12}).
-The performance of a set of tuning parameter values often do not agree across metrics.
-For example, both density methods perform well according to average fidelity but poorly according to MSEE.
-All quantile bin methods perform well according to average $R^2$ but poorly based on average fidelity and MSEE.
-However, there is consistency in results across different Gower powers.
-The applications using a power of 0.5 perform the best or as well as the other powers across all simulation methods suggesting that the power that leads to a more global explanation is preferred by LIME.
-It is not apparent which set of tuning parameters is the best.
-Considering all three metrics, we might conclude that the 4-equal-bins with a Gower power of 0.5 performs better than the other tuning parameter values considered.
-
-To provide a more detailed view of explanations obtained using different tuning parameter values, we take a closer look at explanations for two observations of interest, which will be referred to as case M (a known match) and case NM (a known non-match), using explanation scatterplots.
-Figure~\ref{fig:figure-13} includes the visual representation plots of explanations (from \emph{lime}) and explanation scatterplots for cases M and NM.
-Plots for 4-equal-bins and 4-quantile-bins are included to depict tuning parameter values with good (4-equal-bins) and mediocre (4-quantile-bins) performance based on the assessment metric plot.
-Plots for the kernel density simulation method are included in Appendix~\ref{exp-scatter_plus} (Figure \ref{fig:figure-B2}).
-
-We focus on the explanation for case NM with 4-quantile-bins.
-The explanation plot from \emph{lime} shows that the observed values of NM of mismatches less than or equal to 7.17, rough correlation (rough\_cor) greater than 0.05, and D less than or equal to 0.002 support a random forest prediction in favor of a match.
-The scatter plots show that many of the simulated values in the rectangular regions with mismatches less than 7.17, rough correlation greater than 0.05, and distance less than or equal to 0.002 have random forest predictions greater than 0.5, which agrees with the LIME explanation.
-However, the random forest assigns a probability of 0.21 to case NM, which is not explained by the LIME explanation that provides all explanations in support of a match.
-Instead, consider that a better explanation based on the scatterplots would be that the random forest assigned a prediction probably below 0.5 since NM has observed values of mismatches less than 5, rough correlation greater than 0.25, and distance greater than 0.001.
-
-The other explanation scatterplots can be interpreted in a similar manner.
-The three plots depict situations where the explanations are faithful to the random forest, but the regions captured by the intersections of the bins do not align well with the regions containing similar probabilities produced by the random forest.
-
-\begin{figure*}[!thp]
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-
-{\centering \includegraphics[width=6.25in]{figure-13-1}
-
-}
-
-\end{knitrout}
-\caption{Plots of LIME explanations (first and third rows) and explanation scatterplots (second and fourth rows) for  cases M and NM in the bullet test data for two tuning parameter values: 4-quantile-bins (first column) and 4-equal-bins (second column).
-The plots provide insights into the LIME explanations and allow for the assessment of the explanation quality.}
-\label{fig:figure-13}
-\end{figure*}
-
-Without applying LIME with multiple tuning parameter values to the bullet test data or viewing diagnostic plots of the LIME explanations, it may be very possible to formulate reasons why the LIME explanations make sense.
-However, the sequence of plots in this section (Figures \ref{fig:figure-11}, \ref{fig:figure-12}, and \ref{fig:figure-13}) suggest that we should be cautious to trust any of these LIME explanations.
-It appears that either LIME needs to be further tuned to provide trustworthy and good explanations, or a different approach may provide better insight.
-
-\section{Discussion} \label{discussion}
-
-This paper highlights that while an explainer model is meant to provide clarity, it actually adds another layer of complexity to predictive models by requiring yet another model that needs to be assessed.
-Without an assessment of the explainer model, LIME is a black-box procedure of its own requiring blind trust in the explainer model.
-We suggest the use of visual diagnostics to counteract the black-box nature of LIME and provide three diagnostic plots.
-
-The visualizations are intended to provide insight on how LIME works, assess the ability of the explainer model to capture the complex predictive model, and compare LIME explanations produced by different tuning parameter values.
-While the visualizations accomplish these tasks, they also expose examples of the failings of LIME.
-To address the discovered failings of LIME, we reconsider each of the claims about the performance of LIME made by \citet{ribeiro:2016} in light of the insights gained from the diagnostic visualizations.
-
-As previously discussed, the \textbf{interpretability} of the LIME explanations is controllable  by the complexity of the explainer model.
-For example, the number of bins selected for simulation can control the interpretability of the explanations.
-If too many bins are selected, the bin range that is reported in the LIME explanation will be too small to be meaningful in the context of the feature.
-An appropriate choice of the number of bins will keep the bin range meaningful.
-Thus, the claim of interpretability does not need to be assessed using the visualizations.
-However, diagnostic visualizations do present a different perspective on the meaning of interpretability.
-
-Even though an explanation will be interpretable as long as the complexity of the explainer model is appropriately chosen, a lack of understanding of the process used to create the explanation could lead to an incorrect interpretation of the explanation.
-For example, the visualization of a LIME explanation available from the \emph{lime} R package \citep{pedersen:2020} (shown in Figures \ref{fig:figure-04} and \ref{fig:figure-13}) is a major simplification of the explainer model, which could lead to under-interpreted or misinterpreted LIME explanation.
-Supplementing \citet{pedersen:2020}'s compact visualization of the explanation with an explanation scatterplot that shows a more detailed visualization of the explainer model promotes a more complete understanding of the explanation (such as Figures~\ref{fig:figure-04} and \ref{fig:figure-13}).
-
-Even with an explainer model that is interpreted correctly, the interpretation is worthless if the explainer model is not \textbf{faithful} to the complex model.
-This claim can be assessed using the diagnostic plots suggested in this paper.
-Many of the visualizations in this paper highlight problems with the faithfulness of the explainer models.
-The explanation scatterplots allow for a comparison of the explainer model to the complex model.
-The examples in this paper show cases where the explainer model bins do not accurately capture the regions with similar random forest probabilities that contain the prediction of interest and oversimplify the model (Figures \ref{fig:figure-04} and \ref{fig:figure-13}).
-Using fewer bins would clearly not help improve the faithfulness of the explainer model in these examples, and while an increase in the number of bins would lead to a finer resolution of the random forest classification boundaries, interpretability of the explainer model would quickly be lost.
-Perhaps this could be improved by allowing the bin creation to account for the relationships between the features and response variable or a different number of bins for each feature.
-
-In addition to assessing faithfulness by visually comparing the complex and explainer model, we propose a visual comparison of two faithfulness metrics (MSEE and average fidelity).
-The examples of faithfulness metric comparisons in this paper both produced conflicting results (Figures \ref{fig:figure-07} and \ref{fig:figure-12}).
-This makes it difficult to decide on a recommendation of a set of tuning parameter values that produce the explanations with the most faithful explainer model.
-
-The metric comparison plot also includes a comparison of average $R^2$ values, which is a metric that can be used to assess the claim of \textbf{linearity}.
-Most of the average $R^2$ values in the examples from this paper are below 0.5 suggesting a poor linear fit of the explainer models.
-A poor linear fit of the explainer model is also seen with the residual plot (\autoref{fig:figure-C3}).
-
-The final claim, \textbf{localness}, is addressed by the feature heatmap and metric comparison plots.
-As stated, the feature heatmap reveals that the density simulation methods in the \data \ example  results in global explanations where the same features are repeatedly chosen across all (or almost all) observations in the set of explanations.
-This finding agrees with that of \citet{laugel:2018} who found LIME produced global explanations with the normal approximation simulation method.
-For the bin based simulation methods in the bullet data example, the feature heatmap shows that the features chosen for the explanations vary between the two classification categories (match versus non-match).
-This is an interesting finding that suggests that different features can play a role in the predictions of observations in different response categories.
-Furthermore, while the metric comparison plot in the bullet example does not provide agreement between metrics on a best bin based method, all metrics agree that a Gower power of 0.5 for computing the model weights associated with distance of a simulated data point from the prediction of interest is the best.
-This suggests that a less local explanation provides a better explanation of the performance of the random forest.
-
-Some of the visualizations in the paper generalize easily to any application of LIME such as the feature heatmap and metric plot.
-Other plots such as the visualizations of the LIME procedure would require extensions such as the use of scatterplot matrices to compare explanations with more than two features.
-The addition of interactivity to the diagnostic plots would provide additional enhancement of the assessment process.
-For example, a diagnostic plot that provides a summary of multiple LIME explanations, such as the feature heatmap, could be displayed and clicked on to reveal more detailed figures associated with individual predictions of interest, such as an explanation scatterplot.
-
-The largest limitation to the diagnostic visualizations is the dimensionality of the data shown, both in the number of dimensions or features as well as the number of observations.
-Fortunately, in the situation of LIME, both of these aspects are rather well controlled: LIME relies heavily on simulations to generate data scenarios that are close to the data observed but exhibit variability.
-Effects from overplotting should be relatively mild, because output from simulations is shown, which is expected to be (relatively) continuous such that overplotting only occurs for points with (relatively) similar values.
-In that respect, the diagnostics shown for the \data \ and the bullet example are representative of what is expected.
-But in cases where overplotting does become problematic, the user could either simply reduce the size of the simulations or use some well-studied binning techniques in the visualizations, as discussed for example in \citet{carr:1987} or \citet{unwin:2006}.
-
-While it would be ideal if LIME could be used as a method to provide easily understandable explanations for black-box models as \citet{ribeiro:2016} claim, that dream is not yet a reality.
-The examples using diagnostic plots to assess LIME in this paper show frequent issues with LIME.
-We hope that our plots provide motivation to assess LIME explanations, to not blindly use the default settings (even if it is not clear how to tune the parameters), and to encourage work on improving LIME, so that it can be a lime and not a lemon.
-
-\section*{Acknowledgments}
-
-HH was partially funded by the Center for Statistics and Applications in Forensic Evidence (CSAFE) through Cooperative Agreement 70NANB20H019 between NIST and Iowa State University, which includes activities carried out at Carnegie Mellon University, Duke University, University of California Irvine, University of Virginia, West Virginia University, University of Pennsylvania, Swarthmore College and University of Nebraska, Lincoln.
-
-\subsection*{Author contributions}
-
-{\bf Katherine Goode, Heike Hofmann}: Conceptualization, Methodology, Investigation, Visualizations, Writing - Reviewing and Editing. {\bf Katherine Goode}: Writing - Initial Draft, Software.
-
-\subsection*{Financial disclosure}
-
-None reported.
-
-\subsection*{Conflict of interest}
-
-The authors declare no potential conflict of interests.
-
-\section*{Supporting information}
-
-The code used to produce the manuscript and the data from examples in Section \ref{application} are available in the following GitHub Repository: \href{https://github.com/goodekat/LIME-diagnostics-paper}{https://github.com/goodekat/LIME-diagnostics-paper}.
-
-\bibliography{references}
-
-\newpage
-
-\appendix
-
-\section{LIME Tuning Parameter Options} \label{lime-details}
-
-The following tuning parameters for the LIME algorithm are available in the \emph{lime} R package \citep{pedersen:2020}.
-
-\begin{itemize}
-
-\item Data simulation methods:
-
-\begin{itemize}
-\item Equally spaced bins: observations are uniformly sampled from equally spaced bins (number of bins may be specified)
-\item Quantile bins: observations are uniformly sampled from quantile bins (number of bins may be specified)
-\item Normal density approximation: observations are sampled from a normal distribution with mean and standard deviation computed from the corresponding feature
-\item Kernel density approximation: observations are sampled from an kernel density approximation of the corresponding feature
-\end{itemize}
-
-\item Number of observations to simulate
-
-\item Distance metric for determining proximity to the prediction of interest: Gower distance (where the power may be specified) or exponential kernel (where the kernel width may be specified)
-
-\item Number of features to return in an explanation
-
-\item Feature selection method for determining the features to return in an explanation: forward selection applied to a ridge regression, features with the largest magnitude coefficients in ridge regression, LASSO, classification/regression tree splits
-
-\end{itemize}
-
-\section{Explanation Scatterplots Under Other Simulation Scenarios} \label{exp-scatter_plus}
-
-Section \ref{exp-scatter} introduces explanation scatterplots under the default simulation method in the \emph{lime} R package: 4-quantile-bins.
-The structure of an explanation scatterplot remains the same if any bin based simulation method is used, i.e., any number of quantile or equally spaced bins.
-However, if the kernel density or normal approximation simulation methods are used, the format of the explanation scatterplot changes.
-In the density based simulation method scenarios, LIME uses the standardized versions of the predictor variables to fit the explainer model.
-Thus, the explainer model needs to be represented differently in the explanation scatterplot.
-
-When the kernel density or normal approximation simulation methods are applied, the explanation scatterplot depicts the complex model by plotting the complex model predictions versus a feature selected in LIME the explanation from the simulated data.
-The explainer model is included as a line on the figure where all features excluding the one plotted on the x-axis are set to the observed values of the prediction of interest.
-An explanation scatterplot is created for each feature included in the LIME explanation.
-As with the bin based simulation method, the size of the points represent the weight assigned by LIME.
-
-Figure \ref{fig:figure-B1} provides example explanation scatterplots for each feature in the default LIME explanation obtained using the kernel density simulation method for the \data \ prediction of interest.
-Figure \ref{fig:figure-B2} includes explanation scatterplots for the explanations generated using kernel density simulation for the bullet example cases M and NM discussed in Section \ref{bullet-assess-ex}.
-
-\begin{figure*}[!thp]
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-
-{\centering \includegraphics[width=6.5in]{figure-B1-1}
-
-}
-
-\end{knitrout}
-\caption{Explanation scatterplots for the \data \ prediction of interest with the kernel density simulation method.}
-\label{fig:figure-B1}
+\caption{Plots of LIME explanations (first row) and explanation scatterplots (second row) for case M in the bullet test data for two tuning parameter values: 4-quantile-bins (first column) and 4-equal-bins (second column).}
+\label{fig:figure-s2}
 \end{figure*}
@@
 \begin{figure*}[!thp]
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
 
-{\centering \includegraphics[width=6.5in]{figure-B2-1}
-
-}
-
-\end{knitrout}
 \caption{Explanation scatterplots for LIME explanations using kernel density simulation for the cases M and NM of the bullet comparison test data.}
-\label{fig:figure-B2}
+\label{fig:figure-s3}
 \end{figure*}
 
-\section{Explainer Model Residual Plot} \label{residual-plot}
-
-In order to assess the claim of linearity for the \data \ prediction of interest discussed in Section \ref{exp-scatter}, we use one of the most basic diagnostics in a statistician's tool box and draw a residual plot for the explainer model.
-This is shown in Figure \ref{fig:figure-C3} with the explainer model residuals on the y-axis and explainer model predictions on the x-axis.
-The points along the x-axis have been jittered to ease the effect of the over-plotted points in the visualization.
-There is a clear increasing trend in the residuals as the explainer model predictions increase.
-This is a clear violation of the linearity assumption with the ridge regression model.
-
-\begin{figure}[!thp]
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-
-{\centering \includegraphics[width=3.125in]{figure-C3-1}
-
-}
-
-\end{knitrout}
-\caption{Residual plot of the explainer model associated with \data \ prediction of interest from Section \ref{exp-scatter}.
-The residuals are plotted against the predicted values.
-The points are jittered in the x-direction to alleviate the over-plotting of points.
-There is an upward trend in the residuals as the explainer model predictions increase, which suggests a violation of the linearity assumption.}
-\label{fig:figure-C3}
-\end{figure}
-
-\section{Details on Assessment Metrics} \label{metric-details}
-
-Suppose $f$ is a complex model, and let $\textbf{X}$ be a matrix of observed data with $K$ features and $E$ observations where $x_e$ is an observed feature vector for observation $e$.
-Let $f(x_e)$ be the complex model prediction for observation $e$.
-It is of interest to explain the predictions made by $f$ applied to $X$ using LIME.
-
-For $x_e$ and a set of tuning parameter values $t$, let $\textbf{X}_{e,t}'$ be the LIME simulated dataset with $K$ features and $S$ rows such that $x'_{e,t,s}$ is the feature vector for simulated data point $s$ corresponding to explanation $e$ and tuning parameter values $t$.
-Let $\textbf{Z}'_{e,t}$ be the matrix of simulated data transformed to bin indicator variables (for bin based simulation methods) or standardization (for density based simulation methods) with $K$ features and $S$ observations such that $z'_{e,t,s}$ is the interpretability transformed feature vector for explanation $e$, tuning parameter values $t$, and simulated data point $s$.
-Note that $z_{e,t}$ will represent the  transformed version of $x_e$.
-
-Next, let $\omega_t$ represent a proximity distance metric corresponding to tuning parameter values $t$.
-Then $\omega_t\left(x_e, x'_{e,t,s}\right)$ is the weight assigned to $x'_{e,t,s}$, which is the proximity between $x_e$ and $x'_{e,t,s}$.
-Allow $g_{e,t}$ to be the explainer model for an explanation $e$ and tuning parameter values $t$.
-Thus, $g_{e,t}\left(z'_{e,s,t}\right)$ is the explainer model prediction for the interpretability transformed simulated data point $s$.
-
-For a set of $E$ explanations and a set of tuning parameter values $t$, we define the assessment metrics as follows:\\
-\\
-\emph{Average $R^2$} is denoted as $R^2_{\mbox{ave}}$ and computed as
-
-  $$R^2_{\mbox{ave}} = \frac{1}{E}\sum_{e=1}^E R_{e,t}^2$$
-
-\noindent where $R_{e,t}^2$ is the $R^2$ value for $g_{e,t}$.\\
-\\
-\emph{Average fidelity} is denoted by $\mathcal{L}_{\mbox{ave}}$ and computed as
-
-\begin{eqnarray*} \mathcal{L}_{\mbox{ave}} & = & \frac{1}{E}\sum_{e=1}^E\mathcal{L}(f, \ g_{e,t}, \ \pi_{t}) \\ & = & \frac{1}{E}\sum_{e=1}^E\sum_{s=1}^{S}\omega_{t}\left(x_e, x'_{e,t,s}\right)\left(f\left(x'_{e,t,s}\right)-g_{e,t}\left(z_{e,t,s}'\right)\right)^2.
-\end{eqnarray*}
-
-\noindent where $\mathcal{L}$ is the fidelity metric originally defined in \citet{ribeiro:2016}.\\
-\\
-\emph{Mean squared explanation error} is denoted by MSEE and computed as
-
-$$MSEE=\frac{1}{E}\sum_{e=1}^E\left(f\left(x_e\right)-g_{e,t}\left(z_{e,t}\right)\right)^2.$$
-
 \end{document}

### 2021-01-04 supplemental/supplemental.Rnw
finished creating supplemental material document

\documentclass[9pt]{article}

\usepackage[margin=1in]{geometry}

\title{Supplemental Material Corresponding to ``Visual Diagnostics of an Explainer Model -- Tools for the Assessment of LIME Explanations"}
\date{}

\begin{document}

\maketitle

<<setup, echo = FALSE, include = FALSE>>=
# Specify global options
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  fig.keep = 'high',
  fig.align = 'center',
  dev = c("cairo_pdf", "cairo_ps"),
  dev.args = list(fallback_resolution = 800),
  dpi = 1200
)

# Load packages
library(Cairo)
library(cowplot)
library(dplyr)
library(forcats)
library(ggplot2)
library(gretchenalbrecht) #remotes::install_github("dicook/gretchenalbrecht")
library(lime) #remotes::install_github("goodekat/lime")
library(limeaid) #remotes::install_github("goodekat/limeaid")
library(tidyr)

# Specify the (base) font size (fs) and font (ff) for all plots
fs = 7
ff = "Helvetica"
@

\section{Extreme Feature Heatmap Scenarios} \label{feat-heat-ex}

Two hypothetical examples of feature heatmaps are included in Figure \ref{fig:figure-s1}. The plots are created with the assumption that LIME is applied to select the top feature out of $p=4$  features for $n=10$ cases with $t=5$ sets of tuning parameter values. Situation 1 (left) is an example where the features selected are consistent across tuning parameter values within a case but vary across cases within a tuning parameter value. This is the ideal situation, because the LIME explanations do not depend on the tuning parameters but do depend on the location of the observation in the feature space. Situation 2 (right) is an example where the selected features vary across tuning parameter values within a case but are consistent across cases within a tuning parameter value. This situation indicates that the features selected by LIME are dependent on the tuning parameters, and the explanations may not be  local, because the same feature is chosen regardless of the case. In practice, it is expected that the plot will exhibit a combination of these two situations.

\vspace{0.5cm}

\renewcommand{\thefigure}{S1}
\begin{figure}[!h]
<<figure-s1, out.width = '4.5in', fig.width = 8, fig.height = 3.5>>=

# Specify the figure size (for determining font size)
fs1_ow = 4.5
fs1_fw = 8
fs1_fs = fs * (fs1_fw / fs1_ow)

# Specify the number of cases and LIME input options
ncases = 10
ninputs = 5

# Create a good case of chosen feature example data
set.seed(20191008)
heatmap_data_good <-
  tibble(
    case = factor(rep(1:ncases, each = ninputs),
                  levels = ncases:1),
    input = factor(rep(1:ninputs, ncases)),
    feature = factor(c(
      rep(1, 5),
      rep(2, 5),
      rep(3, 5),
      rep(1, 5),
      rep(1, 5),
      rep(4, 5),
      rep(1, 5),
      rep(3, 5),
      rep(1, 5),
      rep(4, 5)
    ))
  ) %>%
  mutate(input = fct_recode(
    input,
    "A" = "1",
    "B" = "2",
    "C" = "3",
    "D" = "4",
    "E" = "5"
  ))

# Create the conceptual good heatmap
heatmap_plot_good <- ggplot(data = heatmap_data_good,
                            mapping = aes(
                              x = input,
                              y = case,
                              fill = feature,
                              color = feature
                            )) +
  geom_tile() +
  labs(
    x = "Tuning Parameter Value",
    y = "Case",
    fill = "Feature",
    color = "Feature",
    title = "Situation 1",
    subtitle = "Consistent Explanations"
  ) +
  theme_bw(base_family = ff, base_size = fs1_fs) +
  scale_fill_grey() +
  scale_color_grey() +
  theme(legend.position = "none", 
        plot.title = element_text(size = fs1_fs))

# Create a bad case of chosen feature example data
set.seed(20190627)
heatmap_data_bad <- tibble(
  case = factor(rep(1:ncases, ninputs),
                levels = ncases:1),
  input = factor(rep(1:ninputs, each = ncases)),
  feature = factor(rep(c(1, 2, 4, 3, 2), each = 10))
) %>%
  mutate(input = fct_recode(
    input,
    "A" = "1",
    "B" = "2",
    "C" = "3",
    "D" = "4",
    "E" = "5"
  ))

# Create the conceptual bad heat map
heatmap_plot_bad <- ggplot(data = heatmap_data_bad,
                           mapping = aes(
                             x = input,
                             y = case,
                             fill = feature,
                             color = feature
                           )) +
  geom_tile() +
  labs(
    x = "Tuning Parameter Value",
    y = "Case",
    fill = "Feature",
    color = "Feature",
    title = "Situation 2",
    subtitle = "Inconsistent Explanations"
  ) +
  theme_bw(base_family = ff, base_size = fs1_fs) +
  theme(plot.title = element_text(size = fs1_fs)) +
  scale_fill_grey() +
  scale_color_grey()

heatmap_leg <- get_legend(heatmap_plot_bad)
heatmap_plot_bad <-
  heatmap_plot_bad + theme(legend.position = 'none')

# Join the plots
plot_grid(
  heatmap_plot_good,
  heatmap_plot_bad,
  heatmap_leg,
  nrow = 1,
  rel_widths = c(0.43, 0.43, 0.14)
)

@
\caption{Hypothetical examples of feature heatmaps in two possible situations. (Left) Situation 1 is the ideal, because the explanations vary across cases but do not depend on tuning parameter values. (Right) Situation 2 suggests global explanations and extreme explanation dependence on tuning parameter values.}
\label{fig:figure-s1}
\end{figure}

\section{Additional Bullet Matching Explanation Scatterplots} \label{bullets-plus}

Figures \ref{fig:figure-s2} and \ref{fig:figure-s3} include visual representations of LIME explanations from the \emph{lime} R package (left) and explanation scatterplots (right) for a known match observation in the the bullet example referred to as case M. The explanations in Figures \ref{fig:figure-s2} and \ref{fig:figure-s3} are obtained using 4-quantile-bins and Figure 4-equal-bins, respectively. The explanations appear to be faithful to the random forest than those associated with case NM in Section 4 of ``Visual Diagnostics of an Explainer Model -- Tools for the Assessment of LIME Explanations". However, the intersections of the bins are still not well aligned with the regions containing similar probabilities produced by the random forest. Figure \ref{fig:figure-s4} includes explanation scatterplots using the kernel density simulation method for both cases M and NM from the bullet example.

\vspace{0.5cm}

<<>>=
# Load the cleaned explanations
bullet_explain_perms_clean <- readRDS("../data/bullet-explain-perms-clean.rds")
@

\renewcommand{\thefigure}{S2}
\begin{figure*}[!h]
<<figure-s2, out.width = '6.5in', fig.width = 14, fig.height = 7>>=

# Specify the figure size (for determining font size)
fs2_ow = 6.5
fs2_fw = 14
fs2_fs = fs * (fs2_fw / fs2_ow)
fs2_ls = 0.5 * (fs2_fw / fs2_ow)

# Create a theme for the lime explanation visualizations
bullet_explain_plot_theme <-
  list(
    scale_fill_manual(values = c("darkorange", "grey50")),
    theme(
      text = element_text(family = ff, size = fs2_fs),
      strip.text.x = element_text(face = "plain", size = fs2_fs),
      aspect.ratio = 1
    )
  )

# Create theme for explanation scatterplots
bullet_eoi_plot_theme <-
  list(
    scale_color_gradient2(
      low = "grey50",
      high = "darkorange",
      midpoint = 0.5,
      limits = c(0, 1)
    ),
    scale_fill_gradient2(
      low = "grey50",
      high = "darkorange",
      midpoint = 0.5,
      limits = c(0, 1)
    ),
    theme_bw(base_family = ff, base_size = fs2_fs),
    theme(
      aspect.ratio = 1,
      plot.title = element_text(size = fs2_fs),
      strip.text.x = element_text(size = fs2_fs),
      strip.text.y = element_text(size = fs2_fs),
      strip.placement = "outside",
      strip.background = element_rect(color = "white", fill = "white")
    ),
    guides(size = guide_legend(nrow = 2, byrow = T), 
           linetype = guide_legend(override.aes = list(color = c("grey50", "darkorange"))))
  )

# Create the lime explanation visualizations
pfM_3qb <- plot_features(bullet_explain_perms_clean[1:3,]) + bullet_explain_plot_theme

# Create the explanation scatterplots
eoiM_3qb <-
  plot_explain_scatter(
    bullet_explain_perms_clean[1:3, ],
    alpha = 0.9,
    weights = TRUE,
    line_size = fs2_ls
  ) +
  bullet_eoi_plot_theme +
  guides(linetype = guide_legend(override.aes = list(color = c("darkorange"))))

# Join the plots
plot_grid(
  pfM_3qb,
  eoiM_3qb,
  nrow = 1,
  rel_widths = c(0.35, 0.65)
)

@
\caption{Explanation plot from \emph{lime} R package (left) and explanation scatterplot (right) for case M in the bullet test data for 4-quantile-bins.}
\label{fig:figure-s2}
\end{figure*}

\renewcommand{\thefigure}{S3}
\begin{figure*}[!h]
<<figure-s3, out.width = '6.5in', fig.width = 14, fig.height = 7>>=

# Specify the figure size (for determining font size)
fs3_ow = 6.5
fs3_fw = 14
fs3_fs = fs * (fs3_fw / fs3_ow)
fs3_ls = 0.5 * (fs3_fw / fs3_ow)

# Create the lime explanation visualizations
pfM_3eb <- plot_features(bullet_explain_perms_clean[7:9,]) + bullet_explain_plot_theme

# Create the explanation scatterplots
eoiM_3eb <-
  plot_explain_scatter(
    bullet_explain_perms_clean[7:9, ],
    alpha = 0.9,
    weights = TRUE,
    line_size = fs3_ls
  ) +
  bullet_eoi_plot_theme + 
  guides(linetype = guide_legend(override.aes = list(color = c("darkorange"))))

# Join the plots
plot_grid(
  pfM_3eb,
  eoiM_3eb,
  nrow = 1,
  rel_widths = c(0.35, 0.65)
)

@
\caption{Explanation plot from \emph{lime} R package (left) and explanation scatterplot (right) for case M in the bullet test data for 4-equal-bins.}
\label{fig:figure-s3}
\end{figure*}

\renewcommand{\thefigure}{S4}
\begin{figure*}[!h]
<<figure-s4, out.width = '6.5in', fig.width = 12, fig.height = 10>>=

# Specify the figure size (for determining font size and line size)
fs4_ow = 6.5
fs4_fw = 12
fs4_fs = fs * (fs4_fw / fs4_ow)
fs4_ls = 0.5 * (fs4_fw / fs4_ow)

# Create the explanation scatterplot: case M, kernel density
bullet_es_M <-
  plot_explain_scatter(
    bullet_explain_perms_clean %>% filter(case == "M", sim_method == "kernel_density"),
    alpha = 0.75,
    title.opt = TRUE,
    line_size = fs4_ls
  ) +
  scale_fill_gradient2(
    low = "grey50",
    high = "darkorange",
    midpoint = 0.5,
    limits = c(0, 1)
  ) +
  theme_bw(base_family = ff, base_size = fs4_fs) +
  theme(
    aspect.ratio = 1,
    strip.background = element_rect(fill = "white", color = "white"),
    strip.placement = "outside",
    strip.text.x = element_text(size = fs4_fs),
    plot.title = element_text(size = fs4_fs)
  )

# Create the explanation scatterplot: case NM, kernel density
bullet_es_NM <-
  plot_explain_scatter(
    bullet_explain_perms_clean %>% filter(case == "NM", sim_method == "kernel_density"),
    alpha = 0.75,
    title.opt = TRUE, 
    line_size = fs4_ls
  ) +
  scale_fill_gradient2(
    low = "grey50",
    high = "darkorange",
    midpoint = 0.5,
    limits = c(0, 1)
  ) +
  theme_bw(base_family = ff, base_size = fs4_fs) +
  theme(
    aspect.ratio = 1,
    strip.background = element_rect(fill = "white", color = "white"),
    strip.placement = "outside",
    strip.text.x = element_text(size = fs4_fs), 
    plot.title = element_text(size = fs4_fs)
  )

# Join the plots
plot_grid(bullet_es_M, bullet_es_NM, nrow = 2)

@
\caption{Explanation scatterplots for LIME explanations using kernel density simulation for the cases M (top) and NM (bottom) of the bullet comparison test data.}
\label{fig:figure-s4}
\end{figure*}

\end{document}

### 2021-01-04 supplemental/supplemental.tex
finished creating supplemental material document

--- 2021-01-04 supplemental/supplemental.Rnw
@@
-\documentclass[9pt]{article}
+\documentclass[9pt]{article}\usepackage[]{graphicx}\usepackage[]{color}
+% maxwidth is the original width if it is less than linewidth
+% otherwise use linewidth (to make sure the graphics do not exceed the margin)
+\makeatletter
+\def\maxwidth{ %
+  \ifdim\Gin@nat@width>\linewidth
+    \linewidth
+  \else
+    \Gin@nat@width
+  \fi
+}
+\makeatother
+
+\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
+\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
+\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
+\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
+\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
+\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
+\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
+\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
+\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
+\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%
+\let\hlipl\hlkwb
+
+\usepackage{framed}
+\makeatletter
+\newenvironment{kframe}{%
+ \def\at@end@of@kframe{}%
+ \ifinner\ifhmode%
+  \def\at@end@of@kframe{\end{minipage}}%
+  \begin{minipage}{\columnwidth}%
+ \fi\fi%
+ \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
+ \colorbox{shadecolor}{##1}\hskip-\fboxsep
+     % There is no \\@totalrightmargin, so:
+     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
+ \MakeFramed {\advance\hsize-\width
+   \@totalleftmargin\z@ \linewidth\hsize
+   \@setminipage}}%
+ {\par\unskip\endMakeFramed%
+ \at@end@of@kframe}
+\makeatother
+
+\definecolor{shadecolor}{rgb}{.97, .97, .97}
+\definecolor{messagecolor}{rgb}{0, 0, 0}
+\definecolor{warningcolor}{rgb}{1, 0, 1}
+\definecolor{errorcolor}{rgb}{1, 0, 0}
+\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX
+
+\usepackage{alltt}
 
@@
 \date{}
-
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
 \begin{document}
@@
 \maketitle
-
-<<setup, echo = FALSE, include = FALSE>>=
-# Specify global options
-knitr::opts_chunk$set(
-  warning = FALSE,
-  message = FALSE,
-  echo = FALSE,
-  fig.keep = 'high',
-  fig.align = 'center',
-  dev = c("cairo_pdf", "cairo_ps"),
-  dev.args = list(fallback_resolution = 800),
-  dpi = 1200
-)
-
-# Load packages
-library(Cairo)
-library(cowplot)
-library(dplyr)
-library(forcats)
-library(ggplot2)
-library(gretchenalbrecht) #remotes::install_github("dicook/gretchenalbrecht")
-library(lime) #remotes::install_github("goodekat/lime")
-library(limeaid) #remotes::install_github("goodekat/limeaid")
-library(tidyr)
-
-# Specify the (base) font size (fs) and font (ff) for all plots
-fs = 7
-ff = "Helvetica"
-@
 
@@
 \begin{figure}[!h]
-<<figure-s1, out.width = '4.5in', fig.width = 8, fig.height = 3.5>>=
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
 
-# Specify the figure size (for determining font size)
-fs1_ow = 4.5
-fs1_fw = 8
-fs1_fs = fs * (fs1_fw / fs1_ow)
+{\centering \includegraphics[width=4.5in]{figure/figure-s1-1}
 
-# Specify the number of cases and LIME input options
-ncases = 10
-ninputs = 5
+}
 
-# Create a good case of chosen feature example data
-set.seed(20191008)
-heatmap_data_good <-
-  tibble(
-    case = factor(rep(1:ncases, each = ninputs),
-                  levels = ncases:1),
-    input = factor(rep(1:ninputs, ncases)),
-    feature = factor(c(
-      rep(1, 5),
-      rep(2, 5),
-      rep(3, 5),
-      rep(1, 5),
-      rep(1, 5),
-      rep(4, 5),
-      rep(1, 5),
-      rep(3, 5),
-      rep(1, 5),
-      rep(4, 5)
-    ))
-  ) %>%
-  mutate(input = fct_recode(
-    input,
-    "A" = "1",
-    "B" = "2",
-    "C" = "3",
-    "D" = "4",
-    "E" = "5"
-  ))
-
-# Create the conceptual good heatmap
-heatmap_plot_good <- ggplot(data = heatmap_data_good,
-                            mapping = aes(
-                              x = input,
-                              y = case,
-                              fill = feature,
-                              color = feature
-                            )) +
-  geom_tile() +
-  labs(
-    x = "Tuning Parameter Value",
-    y = "Case",
-    fill = "Feature",
-    color = "Feature",
-    title = "Situation 1",
-    subtitle = "Consistent Explanations"
-  ) +
-  theme_bw(base_family = ff, base_size = fs1_fs) +
-  scale_fill_grey() +
-  scale_color_grey() +
-  theme(legend.position = "none", 
-        plot.title = element_text(size = fs1_fs))
-
-# Create a bad case of chosen feature example data
-set.seed(20190627)
-heatmap_data_bad <- tibble(
-  case = factor(rep(1:ncases, ninputs),
-                levels = ncases:1),
-  input = factor(rep(1:ninputs, each = ncases)),
-  feature = factor(rep(c(1, 2, 4, 3, 2), each = 10))
-) %>%
-  mutate(input = fct_recode(
-    input,
-    "A" = "1",
-    "B" = "2",
-    "C" = "3",
-    "D" = "4",
-    "E" = "5"
-  ))
-
-# Create the conceptual bad heat map
-heatmap_plot_bad <- ggplot(data = heatmap_data_bad,
-                           mapping = aes(
-                             x = input,
-                             y = case,
-                             fill = feature,
-                             color = feature
-                           )) +
-  geom_tile() +
-  labs(
-    x = "Tuning Parameter Value",
-    y = "Case",
-    fill = "Feature",
-    color = "Feature",
-    title = "Situation 2",
-    subtitle = "Inconsistent Explanations"
-  ) +
-  theme_bw(base_family = ff, base_size = fs1_fs) +
-  theme(plot.title = element_text(size = fs1_fs)) +
-  scale_fill_grey() +
-  scale_color_grey()
-
-heatmap_leg <- get_legend(heatmap_plot_bad)
-heatmap_plot_bad <-
-  heatmap_plot_bad + theme(legend.position = 'none')
-
-# Join the plots
-plot_grid(
-  heatmap_plot_good,
-  heatmap_plot_bad,
-  heatmap_leg,
-  nrow = 1,
-  rel_widths = c(0.43, 0.43, 0.14)
-)
-
-@
+\end{knitrout}
 \caption{Hypothetical examples of feature heatmaps in two possible situations.
@@
 
-<<>>=
-# Load the cleaned explanations
-bullet_explain_perms_clean <- readRDS("../data/bullet-explain-perms-clean.rds")
-@
-
 \renewcommand{\thefigure}{S2}
 \begin{figure*}[!h]
-<<figure-s2, out.width = '6.5in', fig.width = 14, fig.height = 7>>=
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
 
-# Specify the figure size (for determining font size)
-fs2_ow = 6.5
-fs2_fw = 14
-fs2_fs = fs * (fs2_fw / fs2_ow)
-fs2_ls = 0.5 * (fs2_fw / fs2_ow)
+{\centering \includegraphics[width=6.5in]{figure/figure-s2-1}
 
-# Create a theme for the lime explanation visualizations
-bullet_explain_plot_theme <-
-  list(
-    scale_fill_manual(values = c("darkorange", "grey50")),
-    theme(
-      text = element_text(family = ff, size = fs2_fs),
-      strip.text.x = element_text(face = "plain", size = fs2_fs),
-      aspect.ratio = 1
-    )
-  )
+}
 
-# Create theme for explanation scatterplots
-bullet_eoi_plot_theme <-
-  list(
-    scale_color_gradient2(
-      low = "grey50",
-      high = "darkorange",
-      midpoint = 0.5,
-      limits = c(0, 1)
-    ),
-    scale_fill_gradient2(
-      low = "grey50",
-      high = "darkorange",
-      midpoint = 0.5,
-      limits = c(0, 1)
-    ),
-    theme_bw(base_family = ff, base_size = fs2_fs),
-    theme(
-      aspect.ratio = 1,
-      plot.title = element_text(size = fs2_fs),
-      strip.text.x = element_text(size = fs2_fs),
-      strip.text.y = element_text(size = fs2_fs),
-      strip.placement = "outside",
-      strip.background = element_rect(color = "white", fill = "white")
-    ),
-    guides(size = guide_legend(nrow = 2, byrow = T), 
-           linetype = guide_legend(override.aes = list(color = c("grey50", "darkorange"))))
-  )
-
-# Create the lime explanation visualizations
-pfM_3qb <- plot_features(bullet_explain_perms_clean[1:3,]) + bullet_explain_plot_theme
-
-# Create the explanation scatterplots
-eoiM_3qb <-
-  plot_explain_scatter(
-    bullet_explain_perms_clean[1:3, ],
-    alpha = 0.9,
-    weights = TRUE,
-    line_size = fs2_ls
-  ) +
-  bullet_eoi_plot_theme +
-  guides(linetype = guide_legend(override.aes = list(color = c("darkorange"))))
-
-# Join the plots
-plot_grid(
-  pfM_3qb,
-  eoiM_3qb,
-  nrow = 1,
-  rel_widths = c(0.35, 0.65)
-)
-
-@
+\end{knitrout}
 \caption{Explanation plot from \emph{lime} R package (left) and explanation scatterplot (right) for case M in the bullet test data for 4-quantile-bins.}
@@
 \begin{figure*}[!h]
-<<figure-s3, out.width = '6.5in', fig.width = 14, fig.height = 7>>=
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
 
-# Specify the figure size (for determining font size)
-fs3_ow = 6.5
-fs3_fw = 14
-fs3_fs = fs * (fs3_fw / fs3_ow)
-fs3_ls = 0.5 * (fs3_fw / fs3_ow)
+{\centering \includegraphics[width=6.5in]{figure/figure-s3-1}
 
-# Create the lime explanation visualizations
-pfM_3eb <- plot_features(bullet_explain_perms_clean[7:9,]) + bullet_explain_plot_theme
+}
 
-# Create the explanation scatterplots
-eoiM_3eb <-
-  plot_explain_scatter(
-    bullet_explain_perms_clean[7:9, ],
-    alpha = 0.9,
-    weights = TRUE,
-    line_size = fs3_ls
-  ) +
-  bullet_eoi_plot_theme + 
-  guides(linetype = guide_legend(override.aes = list(color = c("darkorange"))))
-
-# Join the plots
-plot_grid(
-  pfM_3eb,
-  eoiM_3eb,
-  nrow = 1,
-  rel_widths = c(0.35, 0.65)
-)
-
-@
+\end{knitrout}
 \caption{Explanation plot from \emph{lime} R package (left) and explanation scatterplot (right) for case M in the bullet test data for 4-equal-bins.}
@@
 \begin{figure*}[!h]
-<<figure-s4, out.width = '6.5in', fig.width = 12, fig.height = 10>>=
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
 
-# Specify the figure size (for determining font size and line size)
-fs4_ow = 6.5
-fs4_fw = 12
-fs4_fs = fs * (fs4_fw / fs4_ow)
-fs4_ls = 0.5 * (fs4_fw / fs4_ow)
+{\centering \includegraphics[width=6.5in]{figure/figure-s4-1}
 
-# Create the explanation scatterplot: case M, kernel density
-bullet_es_M <-
-  plot_explain_scatter(
-    bullet_explain_perms_clean %>% filter(case == "M", sim_method == "kernel_density"),
-    alpha = 0.75,
-    title.opt = TRUE,
-    line_size = fs4_ls
-  ) +
-  scale_fill_gradient2(
-    low = "grey50",
-    high = "darkorange",
-    midpoint = 0.5,
-    limits = c(0, 1)
-  ) +
-  theme_bw(base_family = ff, base_size = fs4_fs) +
-  theme(
-    aspect.ratio = 1,
-    strip.background = element_rect(fill = "white", color = "white"),
-    strip.placement = "outside",
-    strip.text.x = element_text(size = fs4_fs),
-    plot.title = element_text(size = fs4_fs)
-  )
+}
 
-# Create the explanation scatterplot: case NM, kernel density
-bullet_es_NM <-
-  plot_explain_scatter(
-    bullet_explain_perms_clean %>% filter(case == "NM", sim_method == "kernel_density"),
-    alpha = 0.75,
-    title.opt = TRUE, 
-    line_size = fs4_ls
-  ) +
-  scale_fill_gradient2(
-    low = "grey50",
-    high = "darkorange",
-    midpoint = 0.5,
-    limits = c(0, 1)
-  ) +
-  theme_bw(base_family = ff, base_size = fs4_fs) +
-  theme(
-    aspect.ratio = 1,
-    strip.background = element_rect(fill = "white", color = "white"),
-    strip.placement = "outside",
-    strip.text.x = element_text(size = fs4_fs), 
-    plot.title = element_text(size = fs4_fs)
-  )
-
-# Join the plots
-plot_grid(bullet_es_M, bullet_es_NM, nrow = 2)
-
-@
+\end{knitrout}
 \caption{Explanation scatterplots for LIME explanations using kernel density simulation for the cases M (top) and NM (bottom) of the bullet comparison test data.}

### 2021-01-04 supporting-info/supporting-info.Rnw
small updates

--- 2021-01-04 supplemental/supplemental.Rnw
@@
 
-\title{Supplemental Material Corresponding to ``Visual Diagnostics of an Explainer Model -- Tools for the Assessment of LIME Explanations"}
+\title{Supporting Information Corresponding to ``Visual Diagnostics of an Explainer Model -- Tools for the Assessment of LIME Explanations"}
 \date{}
@@
 The explanations in Figures \ref{fig:figure-s2} and \ref{fig:figure-s3} are obtained using 4-quantile-bins and Figure 4-equal-bins, respectively.
-The explanations appear to be faithful to the random forest than those associated with case NM in Section 4 of ``Visual Diagnostics of an Explainer Model -- Tools for the Assessment of LIME Explanations".
+The explanations appear to be faithful to the random forest than those associated with the known non-match (case NM) in Section 4 of ``Visual Diagnostics of an Explainer Model -- Tools for the Assessment of LIME Explanations".
 However, the intersections of the bins are still not well aligned with the regions containing similar probabilities produced by the random forest.

### 2021-01-04 paper.Rnw
finished creating supplemental material document
updated text to account for supporting info document

@@
 \jnlcitation{
-\cname{\author{Goode K.}, \author{H. Hofmann}, }
+\cname{\author{Goode K.}, \author{H. Hofmann}},
 \cyear{2020},
@@
 (Left) An example of an explainer model with appropriate weights to provide a faithful approximation of the complex model.
-(Right) An example of an explainer model for the same prediction but with different weights that results in an explanation unfaithful to the complex model.
-}
+(Right) An example of an explainer model for the same prediction but with different weights that results in an explanation unfaithful to the complex model.}
 \label{fig:figure-01}
@@
 In the field of statistics, there are two main uses for models: inference and prediction.
-Machine learning models  have proven to perform well in problems with the latter objective , but the accuracy of many machine learning models comes at the cost of interpretability due to their algorithmic complexity (hence the phrase "black-box models").
+Machine learning models have proven to perform well in problems with the latter objective, but the accuracy of many machine learning models comes at the cost of interpretability due to their algorithmic complexity (hence the phrase "black-box models").
 Model interpretability allows for the understanding and assessment of how a model produces predictions.
@@
 Since the explainer model is an approximation of the complex model and not a direct interpretation, the explanations produced by an explainer model are subject to the quality of the approximation.
-In order to achieve reasonable  explanations, the tuning parameter values selected shoud  be assessed.
+In order to achieve reasonable explanations, the tuning parameter values selected should  be assessed.
 
@@
 \citet{laugel:2018} also present examples of LIME explanations that are clearly global and not local.
-A different concern about LIME is raised by \citet{alvarezmelis:2018}  pertaining to the robustness of explanations from LIME and other explainer models : they find that even small changes in predictor variables can lead to very different LIME explanations.
+A different concern about LIME is raised by \citet{alvarezmelis:2018} pertaining to the robustness of explanations from LIME and other explainer models: they find that even small changes in predictor variables can lead to very different LIME explanations.
 Even the original authors of LIME, \citet{ribeiro:2016}, acknowledge that if a linear model is used as the explainer, LIME relies on a linear approximation of the explainer model to the complex model and state "if the underlying model is highly non-linear even in the locality of the prediction, there may not be a faithful explanation".
@@
 The discussion of parameter choices and implementation details of LIME in this paper are based on the R package.
-See Appendix~\ref{lime-details} for
-an overview of the options available for the tuning parameters.
+See Appendix~\ref{lime-details} for an overview of the options available for the tuning parameters.
 
@@
 \caption{Plots of $x_2$ versus $x_1$ from the \data \ training (left) and testing (right) sets introduced in Section \ref{diagnostics} with the true classification boundary shown as a solid black line.
-In the testing set, the open black circles identify cases misclassified by the random forest, and the diamond indicates a prediction of interest.
-}
+In the testing set, the open black circles identify cases misclassified by the random forest, and the diamond indicates a prediction of interest.}
 \label{fig:figure-02}
@@
 An explanation scatterplot associated with the explanation on the left.
-The four quantile bins over-simplify
-the relationship between the random forest predictions and the $x_1$ and $x_2$ values near the prediction of interest.}
+The four quantile bins over-simplify the relationship between the random forest predictions and the $x_1$ and $x_2$ values near the prediction of interest.}
 \label{fig:figure-03}
@@
 \end{eqnarray}
-where $x'_1=x_1\cos(\theta)-x_2\sin(\theta)$,  $x'_2=x_1\sin(\theta)+x_2\cos(\theta)$, and  $\theta=-0.9$. \sout{Then $y$ is defined as
-\begin{eqnarray}\label{eq:data}
-  y=\begin{cases}
-  \mbox{blue} & \mbox{ if } x'_2 > \sin\left(x'_1\right) \\
-  \mbox{red} & \mbox{ if } x'_2 \le \sin\left(x'_1\right) \ .
-  \end{cases}
-\end{eqnarray}}
+where $x'_1=x_1\cos(\theta)-x_2\sin(\theta)$,  $x'_2=x_1\sin(\theta)+x_2\cos(\theta)$, and  $\theta=-0.9$.
 Note that due to the creation of $y$ in this manner, $y$ is dependent on $x_1$ and $x_2$ and independent of $x_3$.
@@
 Vertical lines of color represent explanations that are dependent on the tuning parameter values and may not be local since the same feature is chosen regardless of the location of the observation in the feature space.
-See Appendix \ref{feat-heat-ex} for hypothetical examples depicting feature heatmaps with the extreme cases of horizontal and vertical lines.
+See \kge{the supporting information (Figure S1)} \sout{Appendix \ref{feat-heat-ex}} for hypothetical examples depicting \kge{the extreme cases of} feature heatmaps\kge{.} \sout{with the extreme cases of horizontal and vertical lines.}
 
@@
 This may be reasonable considering that we would expect $x_1$ and $x_2$ to be  the two features used by the random forest to distinguish between response categories.
-However, futher exploration of individual explanations using explanation scatterplots may help to identify the tuning parameter values that produce the most trustworthy explanations.
+However, further exploration of individual explanations using explanation scatterplots may help to identify the tuning parameter values that produce the most trustworthy explanations.
 
@@
 @
-\caption{Example bullet signatures. The  signatures are from  the same land and therefore have very similar patterns. }
+\caption{Example bullet signatures. The signatures are from the same land and therefore have very similar patterns.}
 \label{fig:figure-07}
@@
 Plots for 4-equal-bins and 4-quantile-bins are included to depict tuning parameter values with good (4-equal-bins) and mediocre (4-quantile-bins) performance based on the assessment metric plot.
-%\kge{Also, recall that 4-quantile-bins are the default option in the \emph{lime} R package.}
-Explanation scatterplots for a known match, referred to as case M, and for the kernel density simulation method applied to both M and NM are included in Appendix~\ref{bullets-plus}.
+\kge{Additional examples of explanation scatterplots including explanations for a known match and explanation produced using the kernel density simulation method are included in the  the supporting information (Figures S2 to S4).} \sout{Explanation scatterplots for a known match, referred to as case M, and for the kernel density simulation method applied to both M and NM are included in Appendix~\ref{bullets-plus}.}
 
@@
 \begin{figure*}[!thp]
-<<figure-11, out.width = '6.25in', fig.width = 13, fig.height = 8.5, message = FALSE>>=
+<<figure-11, out.width = '6.25in', fig.width = 13, fig.height = 9, message = FALSE>>=
 
@@
   mutate(case = ifelse(case == bullet_poi_nonmatch, "NM", "M"))
+
+# Save the cleaned explanations to use with the supporting information
+if(!file.exists("data/bullet-explain-perms-clean.rds")) {
+ saveRDS(bullet_explain_perms_clean, "data/bullet-explain-perms-clean.rds") 
+}
 
@@
 @
-\caption{Plots of LIME explanations (first row) and explanation scatterplots (second row) for case NM in the bullet test data for two tuning parameter values: 4-quantile-bins (first column) and 4-equal-bins (second column).
-}
+\caption{Plots of LIME explanations (first row) and explanation scatterplots (second row) for case NM in the bullet test data for two tuning parameter values: 4-quantile-bins (first column) and 4-equal-bins (second column).}
 \label{fig:figure-11}
@@
 
-The code used to produce the manuscript and the data from examples in Section \ref{application} are available in the following GitHub Repository: \href{https://github.com/goodekat/LIME-diagnostics-paper}{https://github.com/goodekat/LIME-diagnostics-paper}.
+\kge{Additional example visual diagnostics may be found online in the Supporting Information section at the end of this manuscript.} The code used to produce the manuscript and the data from examples in Section \ref{application} are available in the following GitHub Repository: \href{https://github.com/goodekat/LIME-diagnostics-paper}{https://github.com/goodekat/LIME-diagnostics-paper}.
 

### 2021-01-04 paper.tex
updated text to account for supporting info document

@@
 \end{knitrout}
-\caption{Example bullet signatures. The  signatures are from  the same land and therefore have very similar patterns. }
+\caption{Example bullet signatures. The signatures are from the same land and therefore have very similar patterns.}
 \label{fig:figure-07}
@@
 \end{knitrout}
-\caption{Plots of LIME explanations (first row) and explanation scatterplots (second row) for case NM in the bullet test data for two tuning parameter values: 4-quantile-bins (first column) and 4-equal-bins (second column).
-}
+\caption{Plots of LIME explanations (first row) and explanation scatterplots (second row) for case NM in the bullet test data for two tuning parameter values: 4-quantile-bins (first column) and 4-equal-bins (second column).}
 \label{fig:figure-11}

### 2021-01-04 paper.Rnw
worked on more edits to the paper

@@
 Throughout this paper, we distinguish between interpretability and explanability of models.
-We define {\it interpretability} as the ability to directly use model parameters to understand the relationships in the data captured by the model: e.g., a linear model coefficient associated with a predictor variable indicates the amount the response variable changes based on a change in the predictor variable.
-In contrast, define {\it explanability} as the ability to use the model in an indirect manner to understand the relationships in the data captured by the model: e.g., partial dependence plots depict the marginal relationship between model predictions and predictor variables \citep{friedman:2001}.
+We define {\it interpretability} as the ability to directly use model parameters to understand the relationships in the data captured by the model: e.g., a linear model coefficient associated with a predictor variable indicates the amount the response variable changes based on a change in the predictor\sout{ variable}.
+In contrast, we define {\it explanability} as the ability to use the model in an indirect manner to understand the relationships in the data captured by the model: e.g., partial dependence plots depict the marginal relationship between model predictions and predictor variables \citep{friedman:2001}.
 
@@
 \autoref{fig:figure-01} depicts two plots of the predictions from a hypothetical black-box model versus the feature used to train the model.
-The location of a prediction of interest is indicated by the diamonds.
+The location of a prediction of interest is indicated by the diamond shaped points.
 Globally, there is a clear non-linear relationship between the predictions and the feature, but the relationship could be approximated by a linear model in a local region around the prediction of interest.
@@
 This causes the observations that are further away from the prediction of interest to be given larger weights than the scenario on the left.
-Here, the explainer model does not capture the linear trend near the prediction of interest, but instead, the explainer captures a more global trend.
+Here, the explainer model does not capture the linear trend near the prediction of interest, but instead, \sout{the explainer captures} a more global trend.
 Without an assessment of this explainer model, the slope incorrectly suggests that the predictions decrease as the feature increases near the prediction of interest.
@@
 \autoref{fig:figure-01} demonstrates a simple example in which the explanation quality varies drastically when different weights are used.
-Other concerns with LIME have been raised in the literature: \citet{laugel:2018} and \citet{molnar:2019} discuss the difficulty specifying a local region with LIME due to both an unclear definition of what is a "local region" and how to apply LIME to achieve an appropriate local region.
+Other concerns \sout{with} LIME have been raised in the literature: \citet{laugel:2018} and \citet{molnar:2019} discuss the difficulty specifying a local region with LIME due to both an unclear definition of \sout{what is} a "local region" and how to apply LIME to achieve an appropriate local region.
 \citet{laugel:2018} also present examples of LIME explanations that are clearly global and not local.
@@
 
-Without an assessment of the LIME explainer model, the user is putting trust in another black-box procedure to explain the complex black-box model.
+Without an assessment of the LIME explainer model, the user is putting trust in another black-box \kge{algorithm} \sout{procedure} to explain the complex black-box model.
 In this paper, we stress the importance of assessing the LIME explainer model.
@@
 \citet{ribeiro:2016} provide an implementation of LIME in a Python package \cite{ribeiro:2020}.
-An adaption of the Python package in R has been implemented and made available by Thomas Lin-Pedersen \citep{pedersen:2020}.
-In both implementations, a ridge regression model is used as the explainer model, and the user is asked to select various tuning parameter options: the number of features to return in the explanation, the simulation method, the feature selection method, and how the weights are computed.
-The discussion of parameter choices and implementation details of LIME in this paper are based on the R package.
-See Appendix~\ref{lime-details} for an overview of the options available for the tuning parameters.
+An adaption of the Python package in R has been implemented and made available by \citet{pedersen:2020}.
+In both implementations, a ridge regression model is used as the explainer model, and the user \sout{is asked to} select\kge{s} various tuning parameter options: the number of features to return in the explanation, the simulation method, the feature selection method, and how the weights are computed.
+\sout{The discussion of parameter choices and implementation details of LIME in this paper are based on the R package.} See Appendix~\ref{lime-details} for an overview of the options available for the tuning parameters \kge{based on the R package}.
 
@@
   rename(rfprob_blue = blue, rfprob_red = red)
+
+# Save the training and testing data
+if(!file.exists("data/sine-data-train.rds")) saveRDS(sine_data_train, "data/sine-data-train.rds")
+if(!file.exists("data/sine-data-test.rds")) saveRDS(sine_data_test, "data/sine-data-test.rds")
 
@@
 @
-\caption{(left) Visualization from the \emph{lime} R package of a LIME explanation for the \data \ prediction of interest identified in \autoref{fig:figure-02}.
-(right) \emph{Explanation Scatterplot}.
+\caption{(Left) Visualization from the \emph{lime} R package of a LIME explanation for the \data \ prediction of interest identified in \autoref{fig:figure-02}.
+(Right) \emph{Explanation Scatterplot}.
 An explanation scatterplot associated with the explanation on the left.
@@
 
-Since 4-quantile-bins are used to simulate data, LIME converts continuous predictor variables to indicator variables identifying whether the variable value falls in the same quantile bin as the prediction of interest or not.
+\sout{Since 4-quantile-bins} \kge{When quantile bins} are used to simulate data, LIME converts continuous predictor variables to indicator variables identifying whether the variable value falls in the same quantile bin as the prediction of interest or not.
 The indicator variables are used as the features in the ridge regression explainer model.
@@
 This explainer model suggests that a random forest prediction of `blue' for this observation is mostly supported by the prediction of interest having a value of $x_2$ that is greater than \Sexpr{str_split(sine_poi_lime_default$feature_desc[[1]], pattern = " ")[[1]][1]} but somewhat contradicted by the prediction of interest having a value of $x_1$ that is greater than \Sexpr{str_split(sine_poi_lime_default$feature_desc[[2]], pattern = " ")[[1]][1]} and less than or equal to \Sexpr{str_split(sine_poi_lime_default$feature_desc[[2]], pattern = " ")[[1]][5]}.
-\kgc{I decided to leave the values here.
+%\kgc{I decided to leave the values here.
 I actually prefer it this way myself, but I cut out a lot of text from this subsection in other ways.}\hh{XXX }
@@
 We introduce the explanation scatterplot here under the \emph{lime} R package default method of 4-quantile-bins.
-Appendix \ref{exp-scatter_plus} addresses the explanation scatterplot formats in other LIME simulation scenarios.
+\kge{See the supporting information for} \sout{Appendix \ref{exp-scatter_plus} addresses the} explanation scatterplot formats \kge{under} \sout{in} other LIME simulation scenarios.
 
 The explanation scatterplot applies the concept of plotting the model in the data space discussed in \citet{wickham:2015}.
-The plot is built by plotting the LIME simulated data for the top two features identified by the explanation in a scatterplot and coloring these points by the predictions from the complex model.
+The \kge{visualization} \sout{plot} is built by plotting the LIME simulated data for the top two features identified by the explanation in a scatterplot and coloring these points by the predictions from the complex model.
 The point size represents the weight assigned by LIME.
@@
 First, consider the claim of localness.
-The weights decay relatively slowly outside of the intersection of the 2-quantile-bin suggesting that the LIME explanation is highly influenced by points outside of the bins containing the prediction of interest.
+The weights decay relatively slowly outside of the intersection of the \kge{two quantile bins} \sout{2-quantile-bin} suggesting that the LIME explanation is highly influenced by points outside of the bins containing the prediction of interest.
 However, it is difficult to say if the claim of localness has been violated, because a definition of a local region is not specified.
 Depending on what region a viewer considers to be local, an argument could be made in favor of or against a violation of localness.
-The explanation scatterplot raises awareness of the unclear definition of a local region with LIME.
-Nevertheless, it is possible to say that the weights assigned to the simulated data do not capture  the local region identified by the intersection of the quantile bins.
-
-Now, consider the claim of faithfulness: It can be said that the majority of the points in the $x_2$ quantile support a prediction of blue, which is captured by the bar supporting a prediction of blue in the LIME explanation, and a similar statement can be made about the $x_1$ quantile-bin.
+\sout{The explanation scatterplot raises awareness of the unclear definition of a local region with LIME.
+Nevertheless, it is possible to say that the weights assigned to the simulated data do not capture the local region identified by the intersection of the quantile bins.}
+
+Now, consider the claim of faithfulness: It can be said that the majority of the points in the $x_2$ quantile \kge{bin} support a prediction of blue, which is captured by the bar supporting a prediction of blue in the LIME explanation, and a similar statement can be made about the $x_1$ quantile-bin.
 These statements validate the explanation produced by LIME.
@@
 
-This example explanation only includes two features.
+This example explanation \kge{scatterplot} only includes two features.
 In situations where more than two features are included in a LIME explanation, the explanation scatterplots can be extended to a generalized pairs plot \citep{emerson:2013} that includes all pairwise combinations of features.
@@
 Vertical lines of color represent explanations that are dependent on the tuning parameter values and may not be local since the same feature is chosen regardless of the location of the observation in the feature space.
-See \kge{the supporting information (Figure S1)} \sout{Appendix \ref{feat-heat-ex}} for hypothetical examples depicting \kge{the extreme cases of} feature heatmaps\kge{.} \sout{with the extreme cases of horizontal and vertical lines.}
+See \kge{the supporting information} \sout{Appendix \ref{feat-heat-ex}} for hypothetical examples depicting \kge{the extreme cases of} feature heatmaps\kge{.} \sout{with the extreme cases of horizontal and vertical lines.}
 
@@
 Plots for 4-equal-bins and 4-quantile-bins are included to depict tuning parameter values with good (4-equal-bins) and mediocre (4-quantile-bins) performance based on the assessment metric plot.
-\kge{Additional examples of explanation scatterplots including explanations for a known match and explanation produced using the kernel density simulation method are included in the  the supporting information (Figures S2 to S4).} \sout{Explanation scatterplots for a known match, referred to as case M, and for the kernel density simulation method applied to both M and NM are included in Appendix~\ref{bullets-plus}.}
+\kge{Additional examples of explanation scatterplots including explanations for a known match and explanation produced using the kernel density simulation method are included in the  the supporting information.} \sout{Explanation scatterplots for a known match, referred to as case M, and for the kernel density simulation method applied to both M and NM are included in Appendix~\ref{bullets-plus}.}
 
@@
 Most of the average $R^2$ values in the examples from this paper are below 0.5 suggesting a poor linear fit of the explainer models.
-A poor linear fit of the explainer model is also seen with the residual plot shown in \autoref{fig:figure-C2}.
+A poor linear fit of the explainer model is also seen with the residual plot shown in \autoref{fig:figure-B1}.
 
@@
 
-\begin{figure*}[!thp]
-<<figure-B1, out.width = '6.5in', fig.width = 12, fig.height = 5, fig.align = "center">>=
+\section{Explainer Model Residual Plot} \label{residual-plot}
+\begin{figure}[!h]
+<<figure-B1, out.width = '3.125in', fig.width = 5, fig.height = 4, warning = FALSE>>=
 
 # Specify the figure size (for determining font size and line size)
-fb1_ow = 6.5
-fb1_fw = 12
+fb1_ow = 3.125
+fb1_fw = 5
 fb1_fs = fs * (fb1_fw / fb1_ow)
 fb1_ls = 0.5 * (fb1_fw / fb1_ow)
-
-# Create the explanation scatterplot
-plot_explain_scatter(
-  sine_lime_explain$explain %>%
-    filter(sim_method == "kernel_density", case == sine_poi %>% pull(case)),
-  alpha = 0.75,
-  title.opt = FALSE, 
-  line_size = fb1_ls 
-) +
-  theme_bw(base_family = ff, base_size = fb1_fs) +
-  theme(
-    strip.background = element_rect(fill = "white", color = "white"),
-    strip.placement = "outside",
-    strip.text.x = element_text(size = fb1_fs)
-  )
-
-@
-\caption{Explanation scatterplots for the \data \ prediction of interest with the kernel density simulation method.}
-\label{fig:figure-B1}
-\end{figure*}
-
-\section{Explanation Scatterplots Under Density Simulation Scenarios} \label{exp-scatter_plus}
-
-Section \ref{exp-scatter} introduces explanation scatterplots under the default simulation method in the \emph{lime} R package: 4-quantile-bins.
-The structure of an explanation scatterplot remains the same if any bin based simulation method is used, i.e., any number of quantile or equally spaced bins.
-However, if the kernel density or normal approximation simulation methods are used, the format of the explanation scatterplot changes.
-In the density based simulation method scenarios, LIME uses the standardized versions of the predictor variables to fit the explainer model.
-Thus, the explainer model needs to be represented differently in the explanation scatterplot.
-
-When the kernel density or normal approximation simulation methods are applied, the explanation scatterplot depicts the complex model by plotting the complex model predictions versus a feature selected in LIME the explanation from the simulated data.
-The explainer model is included as a line on the figure where all features excluding the one plotted on the x-axis are set to the observed values of the prediction of interest.
-An explanation scatterplot is created for each feature included in the LIME explanation.
-As with the bin based simulation method, the size of the points represent the weight assigned by LIME.
-
-\autoref{fig:figure-B1} provides example explanation scatterplots for the \data \ prediction of interest when the kernel density simulation method is used.
-The plots show the relationships between the random forest prediction and the selected features of $x_1$ and $x_2$ on the left and right, respectively.
-
-\section{Explainer Model Residual Plot} \label{residual-plot}
-\begin{figure}[!b]
-<<figure-C2, out.width = '3.125in', fig.width = 5, fig.height = 4, warning = FALSE>>=
-
-# Specify the figure size (for determining font size and line size)
-fc2_ow = 3.125
-fc2_fw = 5
-fc2_fs = fs * (fc2_fw / fc2_ow)
-fc2_ls = 0.5 * (fc2_fw / fc2_ow)
 
@@
 ggplot(sine_poi_perms, aes(x = exppred, y = resid)) +
-  geom_hline(yintercept = 0, size = fc2_ls) +
+  geom_hline(yintercept = 0, size = fb1_ls) +
   geom_jitter(alpha = 0.5, width = 0.02) +
-  theme_bw(base_family = ff, base_size = fc2_fs) +
-  theme(plot.title = element_text(size = fc2_fs)) +
+  theme_bw(base_family = ff, base_size = fb1_fs) +
+  theme(plot.title = element_text(size = fb1_fs)) +
   labs(x = "Explainer Model Predictions",
@@
 \caption{Residual plot of the explainer model associated with \data \ prediction of interest from Section \ref{exp-scatter}, which suggests a violation of the linearity assumption.}
-\label{fig:figure-C2}
+\label{fig:figure-B1}
 \end{figure}
@@
 In order to assess the claim of linearity for the \data \ prediction of interest discussed in Section \ref{exp-scatter}, we use one of the most basic diagnostics in a statistician's tool box and draw a residual plot for the explainer model.
-This is shown in \autoref{fig:figure-C2} with the explainer model residuals on the y-axis and explainer model predictions on the x-axis.
+This is shown in \autoref{fig:figure-B1} with the explainer model residuals on the y-axis and explainer model predictions on the x-axis.
 The points along the x-axis have been jittered to ease the effect of the over-plotted points.

### 2021-01-04 paper.tex
worked on more edits to the paper

@@
 \end{knitrout}
-\caption{(left) Visualization from the \emph{lime} R package of a LIME explanation for the \data \ prediction of interest identified in \autoref{fig:figure-02}.
-(right) \emph{Explanation Scatterplot}.
+\caption{(Left) Visualization from the \emph{lime} R package of a LIME explanation for the \data \ prediction of interest identified in \autoref{fig:figure-02}.
+(Right) \emph{Explanation Scatterplot}.
 An explanation scatterplot associated with the explanation on the left.
@@
 This explainer model suggests that a random forest prediction of `blue' for this observation is mostly supported by the prediction of interest having a value of $x_2$ that is greater than 4.834 but somewhat contradicted by the prediction of interest having a value of $x_1$ that is greater than -0.302 and less than or equal to 4.844.
-\kgc{I decided to leave the values here.
+%\kgc{I decided to leave the values here.
 I actually prefer it this way myself, but I cut out a lot of text from this subsection in other ways.}\hh{XXX }
@@
 First, consider the claim of localness.
-The weights decay relatively slowly outside of the intersection of the 2-quantile-bin suggesting that the LIME explanation is highly influenced by points outside of the bins containing the prediction of interest.
+The weights decay relatively slowly outside of the intersection of the \kge{two quantile bins} \sout{2-quantile-bin} suggesting that the LIME explanation is highly influenced by points outside of the bins containing the prediction of interest.
 However, it is difficult to say if the claim of localness has been violated, because a definition of a local region is not specified.
 Depending on what region a viewer considers to be local, an argument could be made in favor of or against a violation of localness.
-The explanation scatterplot raises awareness of the unclear definition of a local region with LIME.
-Nevertheless, it is possible to say that the weights assigned to the simulated data do not capture  the local region identified by the intersection of the quantile bins.
+\sout{The explanation scatterplot raises awareness of the unclear definition of a local region with LIME.
+Nevertheless, it is possible to say that the weights assigned to the simulated data do not capture the local region identified by the intersection of the quantile bins.}
 
-Now, consider the claim of faithfulness: It can be said that the majority of the points in the $x_2$ quantile support a prediction of blue, which is captured by the bar supporting a prediction of blue in the LIME explanation, and a similar statement can be made about the $x_1$ quantile-bin.
+Now, consider the claim of faithfulness: It can be said that the majority of the points in the $x_2$ quantile \kge{bin} support a prediction of blue, which is captured by the bar supporting a prediction of blue in the LIME explanation, and a similar statement can be made about the $x_1$ quantile-bin.
 These statements validate the explanation produced by LIME.
@@
 
-\begin{figure*}[!thp]
+\section{Explainer Model Residual Plot} \label{residual-plot}
+\begin{figure}[!h]
 \begin{knitrout}
@@
 
-{\centering \includegraphics[width=6.5in]{figure/figure-B1-1}
-
-}
-
-\end{knitrout}
-\caption{Explanation scatterplots for the \data \ prediction of interest with the kernel density simulation method.}
-\label{fig:figure-B1}
-\end{figure*}
-
-\section{Explanation Scatterplots Under Density Simulation Scenarios} \label{exp-scatter_plus}
-
-Section \ref{exp-scatter} introduces explanation scatterplots under the default simulation method in the \emph{lime} R package: 4-quantile-bins.
-The structure of an explanation scatterplot remains the same if any bin based simulation method is used, i.e., any number of quantile or equally spaced bins.
-However, if the kernel density or normal approximation simulation methods are used, the format of the explanation scatterplot changes.
-In the density based simulation method scenarios, LIME uses the standardized versions of the predictor variables to fit the explainer model.
-Thus, the explainer model needs to be represented differently in the explanation scatterplot.
-
-When the kernel density or normal approximation simulation methods are applied, the explanation scatterplot depicts the complex model by plotting the complex model predictions versus a feature selected in LIME the explanation from the simulated data.
-The explainer model is included as a line on the figure where all features excluding the one plotted on the x-axis are set to the observed values of the prediction of interest.
-An explanation scatterplot is created for each feature included in the LIME explanation.
-As with the bin based simulation method, the size of the points represent the weight assigned by LIME.
-
-\autoref{fig:figure-B1} provides example explanation scatterplots for the \data \ prediction of interest when the kernel density simulation method is used.
-The plots show the relationships between the random forest prediction and the selected features of $x_1$ and $x_2$ on the left and right, respectively.
-
-\section{Explainer Model Residual Plot} \label{residual-plot}
-\begin{figure}[!b]
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-
-{\centering \includegraphics[width=3.125in]{figure/figure-C2-1}
+{\centering \includegraphics[width=3.125in]{figure/figure-B1-1}
 

### 2021-01-04 supporting-info/supporting-info.Rnw
worked on more edits to the paper

@@
 
+\newcommand{\data}{sine data}
+
 \title{Supporting Information Corresponding to ``Visual Diagnostics of an Explainer Model -- Tools for the Assessment of LIME Explanations"}
+
 \date{}
@@
 
-\section{Extreme Feature Heatmap Scenarios} \label{feat-heat-ex}
+\section{Explanation Scatterplots Under Density Simulation Scenarios}
 
-Two hypothetical examples of feature heatmaps are included in Figure \ref{fig:figure-s1}.
+The manuscript introduces explanation scatterplots under the default simulation method in the \emph{lime} R package: 4-quantile-bins.
+The structure of an explanation scatterplot remains the same if any bin based simulation method is used, i.e., any number of quantile or equally spaced bins.
+However, if the kernel density or normal approximation simulation methods are used, the format of the explanation scatterplot changes.
+In the density based simulation method scenarios, LIME uses the standardized versions of the predictor variables to fit the explainer model.
+Thus, the explainer model needs to be represented differently in the explanation scatterplot.
+
+When the kernel density or normal approximation simulation methods are applied, the explanation scatterplot depicts the complex model by plotting the complex model predictions versus a feature selected in LIME the explanation from the simulated data.
+The explainer model is included as a line on the figure where all features excluding the one plotted on the x-axis are set to the observed values of the prediction of interest.
+An explanation scatterplot is created for each feature included in the LIME explanation.
+As with the bin based simulation method, the size of the points represent the weight assigned by LIME.
+
+Figure \ref{fig:figure-s1} provides example explanation scatterplots for the \data \ prediction of interest when the kernel density simulation method is used.
+The plots show the relationships between the random forest prediction and the selected features of $x_1$ and $x_2$ on the left and right, respectively.
+
+\vspace{0.5cm}
+
+\renewcommand{\thefigure}{S1}
+\begin{figure*}[!thp]
+<<figure-s1, out.width = '6.5in', fig.width = 12, fig.height = 5, fig.align = "center">>=
+
+# Load the testing sine data
+sine_data_test <- readRDS("../data/sine-data-test.rds")
+
+# Load the sine data explanations
+sine_lime_explain <- readRDS("../data/sine-lime-explain.rds")
+
+# Extract the prediction of interest from the sine test data
+sine_poi <- sine_data_test %>% filter(y != rfpred, x1 > 0, x1 < 5, x2 > 5)
+
+# Specify the figure size (for determining font size and line size)
+fs1_ow = 6.5
+fs1_fw = 12
+fs1_fs = fs * (fs1_fw / fs1_ow)
+fs1_ls = 0.5 * (fs1_fw / fs1_ow)
+
+# Create the explanation scatterplot
+plot_explain_scatter(
+  sine_lime_explain$explain %>%
+    filter(sim_method == "kernel_density", case == sine_poi %>% pull(case)),
+  alpha = 0.75,
+  title.opt = FALSE, 
+  line_size = fs1_ls 
+) +
+  theme_bw(base_family = ff, base_size = fs1_fs) +
+  theme(
+    strip.background = element_rect(fill = "white", color = "white"),
+    strip.placement = "outside",
+    strip.text.x = element_text(size = fs1_fs)
+  )
+
+@
+\caption{Explanation scatterplots for the \data \ prediction of interest with the kernel density simulation method.}
+\label{fig:figure-s1}
+\end{figure*}
+
+\section{Extreme Feature Heatmap Scenarios}
+
+Two hypothetical examples of feature heatmaps are included in Figure \ref{fig:figure-s2}.
 The plots are created with the assumption that LIME is applied to select the top feature out of $p=4$  features for $n=10$ cases with $t=5$ sets of tuning parameter values.
@@
 
-\renewcommand{\thefigure}{S1}
+\renewcommand{\thefigure}{S2}
 \begin{figure}[!h]
-<<figure-s1, out.width = '4.5in', fig.width = 8, fig.height = 3.5>>=
+<<figure-s2, out.width = '4.5in', fig.width = 8, fig.height = 3.5>>=
 
 # Specify the figure size (for determining font size)
-fs1_ow = 4.5
-fs1_fw = 8
-fs1_fs = fs * (fs1_fw / fs1_ow)
+fs2_ow = 4.5
+fs2_fw = 8
+fs2_fs = fs * (fs2_fw / fs2_ow)
 
@@
   ) +
-  theme_bw(base_family = ff, base_size = fs1_fs) +
+  theme_bw(base_family = ff, base_size = fs2_fs) +
   scale_fill_grey() +
@@
   theme(legend.position = "none", 
-        plot.title = element_text(size = fs1_fs))
+        plot.title = element_text(size = fs2_fs))
 
@@
   ) +
-  theme_bw(base_family = ff, base_size = fs1_fs) +
-  theme(plot.title = element_text(size = fs1_fs)) +
+  theme_bw(base_family = ff, base_size = fs2_fs) +
+  theme(plot.title = element_text(size = fs2_fs)) +
   scale_fill_grey() +
@@
 (Right) Situation 2 suggests global explanations and extreme explanation dependence on tuning parameter values.}
-\label{fig:figure-s1}
+\label{fig:figure-s2}
 \end{figure}
 
-\section{Additional Bullet Matching Explanation Scatterplots} \label{bullets-plus}
+\section{Additional Bullet Matching Explanation Scatterplots}
 
-Figures \ref{fig:figure-s2} and \ref{fig:figure-s3} include visual representations of LIME explanations from the \emph{lime} R package (left) and explanation scatterplots (right) for a known match observation in the the bullet example referred to as case M.
-The explanations in Figures \ref{fig:figure-s2} and \ref{fig:figure-s3} are obtained using 4-quantile-bins and Figure 4-equal-bins, respectively.
-The explanations appear to be faithful to the random forest than those associated with the known non-match (case NM) in Section 4 of ``Visual Diagnostics of an Explainer Model -- Tools for the Assessment of LIME Explanations".
+Figures \ref{fig:figure-s3} and \ref{fig:figure-s4} include visual representations of LIME explanations from the \emph{lime} R package (left) and explanation scatterplots (right) for a known match observation in the the bullet example referred to as case M.
+The explanations in Figures \ref{fig:figure-s3} and \ref{fig:figure-s4} are obtained using 4-quantile-bins and Figure 4-equal-bins, respectively.
+The explanations appear to be faithful to the random forest than those associated with the known non-match (case NM) shown in the manuscript.
 However, the intersections of the bins are still not well aligned with the regions containing similar probabilities produced by the random forest.
-Figure \ref{fig:figure-s4} includes explanation scatterplots using the kernel density simulation method for both cases M and NM from the bullet example.
+Figure \ref{fig:figure-s5} includes explanation scatterplots using the kernel density simulation method for both cases M and NM from the bullet example.
 
@@
 
-\renewcommand{\thefigure}{S2}
+\renewcommand{\thefigure}{S3}
 \begin{figure*}[!h]
-<<figure-s2, out.width = '6.5in', fig.width = 14, fig.height = 7>>=
+<<figure-s3, out.width = '6.5in', fig.width = 14, fig.height = 7>>=
 
 # Specify the figure size (for determining font size)
-fs2_ow = 6.5
-fs2_fw = 14
-fs2_fs = fs * (fs2_fw / fs2_ow)
-fs2_ls = 0.5 * (fs2_fw / fs2_ow)
+fs3_ow = 6.5
+fs3_fw = 14
+fs3_fs = fs * (fs3_fw / fs3_ow)
+fs3_ls = 0.5 * (fs3_fw / fs3_ow)
 
@@
     theme(
-      text = element_text(family = ff, size = fs2_fs),
-      strip.text.x = element_text(face = "plain", size = fs2_fs),
+      text = element_text(family = ff, size = fs3_fs),
+      strip.text.x = element_text(face = "plain", size = fs3_fs),
       aspect.ratio = 1
@@
     ),
-    theme_bw(base_family = ff, base_size = fs2_fs),
+    theme_bw(base_family = ff, base_size = fs3_fs),
     theme(
       aspect.ratio = 1,
-      plot.title = element_text(size = fs2_fs),
-      strip.text.x = element_text(size = fs2_fs),
-      strip.text.y = element_text(size = fs2_fs),
+      plot.title = element_text(size = fs3_fs),
+      strip.text.x = element_text(size = fs3_fs),
+      strip.text.y = element_text(size = fs3_fs),
       strip.placement = "outside",
@@
     weights = TRUE,
-    line_size = fs2_ls
+    line_size = fs3_ls
   ) +
@@
 \caption{Explanation plot from \emph{lime} R package (left) and explanation scatterplot (right) for case M in the bullet test data for 4-quantile-bins.}
-\label{fig:figure-s2}
+\label{fig:figure-s3}
 \end{figure*}
 
-\renewcommand{\thefigure}{S3}
+\renewcommand{\thefigure}{S4}
 \begin{figure*}[!h]
-<<figure-s3, out.width = '6.5in', fig.width = 14, fig.height = 7>>=
+<<figure-s4, out.width = '6.5in', fig.width = 14, fig.height = 7>>=
 
 # Specify the figure size (for determining font size)
-fs3_ow = 6.5
-fs3_fw = 14
-fs3_fs = fs * (fs3_fw / fs3_ow)
-fs3_ls = 0.5 * (fs3_fw / fs3_ow)
+fs4_ow = 6.5
+fs4_fw = 14
+fs4_fs = fs * (fs4_fw / fs4_ow)
+fs4_ls = 0.5 * (fs4_fw / fs4_ow)
 
@@
     weights = TRUE,
-    line_size = fs3_ls
+    line_size = fs4_ls
   ) +
@@
 \caption{Explanation plot from \emph{lime} R package (left) and explanation scatterplot (right) for case M in the bullet test data for 4-equal-bins.}
-\label{fig:figure-s3}
+\label{fig:figure-s4}
 \end{figure*}
 
-\renewcommand{\thefigure}{S4}
+\renewcommand{\thefigure}{S5}
 \begin{figure*}[!h]
-<<figure-s4, out.width = '6.5in', fig.width = 12, fig.height = 10>>=
+<<figure-s5, out.width = '6.5in', fig.width = 12, fig.height = 10>>=
 
 # Specify the figure size (for determining font size and line size)
-fs4_ow = 6.5
-fs4_fw = 12
-fs4_fs = fs * (fs4_fw / fs4_ow)
-fs4_ls = 0.5 * (fs4_fw / fs4_ow)
+fs5_ow = 6.5
+fs5_fw = 12
+fs5_fs = fs * (fs5_fw / fs5_ow)
+fs5_ls = 0.5 * (fs5_fw / fs5_ow)
 
@@
     title.opt = TRUE,
-    line_size = fs4_ls
+    line_size = fs5_ls
   ) +
@@
   ) +
-  theme_bw(base_family = ff, base_size = fs4_fs) +
+  theme_bw(base_family = ff, base_size = fs5_fs) +
   theme(
@@
     strip.placement = "outside",
-    strip.text.x = element_text(size = fs4_fs),
-    plot.title = element_text(size = fs4_fs)
+    strip.text.x = element_text(size = fs5_fs),
+    plot.title = element_text(size = fs5_fs)
   )
@@
     title.opt = TRUE, 
-    line_size = fs4_ls
+    line_size = fs5_ls
   ) +
@@
     strip.placement = "outside",
-    strip.text.x = element_text(size = fs4_fs), 
-    plot.title = element_text(size = fs4_fs)
+    strip.text.x = element_text(size = fs5_fs), 
+    plot.title = element_text(size = fs5_fs)
   )
@@
 \caption{Explanation scatterplots for LIME explanations using kernel density simulation for the cases M (top) and NM (bottom) of the bullet comparison test data.}
-\label{fig:figure-s4}
+\label{fig:figure-s5}
 \end{figure*}

### 2021-01-04 supporting-info/supporting-info.tex
worked on more edits to the paper

@@
 
-\section{Extreme Feature Heatmap Scenarios} \label{feat-heat-ex}
+\section{Explanation Scatterplots Under Density Simulation Scenarios}
 
-Two hypothetical examples of feature heatmaps are included in Figure \ref{fig:figure-s1}.
+The manuscript introduces explanation scatterplots under the default simulation method in the \emph{lime} R package: 4-quantile-bins.
+The structure of an explanation scatterplot remains the same if any bin based simulation method is used, i.e., any number of quantile or equally spaced bins.
+However, if the kernel density or normal approximation simulation methods are used, the format of the explanation scatterplot changes.
+In the density based simulation method scenarios, LIME uses the standardized versions of the predictor variables to fit the explainer model.
+Thus, the explainer model needs to be represented differently in the explanation scatterplot.
+
+When the kernel density or normal approximation simulation methods are applied, the explanation scatterplot depicts the complex model by plotting the complex model predictions versus a feature selected in LIME the explanation from the simulated data.
+The explainer model is included as a line on the figure where all features excluding the one plotted on the x-axis are set to the observed values of the prediction of interest.
+An explanation scatterplot is created for each feature included in the LIME explanation.
+As with the bin based simulation method, the size of the points represent the weight assigned by LIME.
+
+Figure \ref{fig:figure-s1} provides example explanation scatterplots for the \data \ prediction of interest when the kernel density simulation method is used.
+The plots show the relationships between the random forest prediction and the selected features of $x_1$ and $x_2$ on the left and right, respectively.
+
+\vspace{0.5cm}
+
+\renewcommand{\thefigure}{S1}
+\begin{figure*}[!thp]
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+
+{\centering \includegraphics[width=6.5in]{figure/figure-s1-1}
+
+}
+
+\end{knitrout}
+\caption{Explanation scatterplots for the \data \ prediction of interest with the kernel density simulation method.}
+\label{fig:figure-s1}
+\end{figure*}
+
+\section{Extreme Feature Heatmap Scenarios}
+
+Two hypothetical examples of feature heatmaps are included in Figure \ref{fig:figure-s2}.
 The plots are created with the assumption that LIME is applied to select the top feature out of $p=4$  features for $n=10$ cases with $t=5$ sets of tuning parameter values.
@@
 
-\renewcommand{\thefigure}{S1}
+\renewcommand{\thefigure}{S2}
 \begin{figure}[!h]
@@
 
-{\centering \includegraphics[width=4.5in]{figure/figure-s1-1}
+{\centering \includegraphics[width=4.5in]{figure/figure-s2-1}
 
@@
 (Right) Situation 2 suggests global explanations and extreme explanation dependence on tuning parameter values.}
-\label{fig:figure-s1}
+\label{fig:figure-s2}
 \end{figure}
 
-\section{Additional Bullet Matching Explanation Scatterplots} \label{bullets-plus}
+\section{Additional Bullet Matching Explanation Scatterplots}
 
-Figures \ref{fig:figure-s2} and \ref{fig:figure-s3} include visual representations of LIME explanations from the \emph{lime} R package (left) and explanation scatterplots (right) for a known match observation in the the bullet example referred to as case M.
-The explanations in Figures \ref{fig:figure-s2} and \ref{fig:figure-s3} are obtained using 4-quantile-bins and Figure 4-equal-bins, respectively.
-The explanations appear to be faithful to the random forest than those associated with the known non-match (case NM) in Section 4 of ``Visual Diagnostics of an Explainer Model -- Tools for the Assessment of LIME Explanations".
+Figures \ref{fig:figure-s3} and \ref{fig:figure-s4} include visual representations of LIME explanations from the \emph{lime} R package (left) and explanation scatterplots (right) for a known match observation in the the bullet example referred to as case M.
+The explanations in Figures \ref{fig:figure-s3} and \ref{fig:figure-s4} are obtained using 4-quantile-bins and Figure 4-equal-bins, respectively.
+The explanations appear to be faithful to the random forest than those associated with the known non-match (case NM) shown in the manuscript.
 However, the intersections of the bins are still not well aligned with the regions containing similar probabilities produced by the random forest.
-Figure \ref{fig:figure-s4} includes explanation scatterplots using the kernel density simulation method for both cases M and NM from the bullet example.
+Figure \ref{fig:figure-s5} includes explanation scatterplots using the kernel density simulation method for both cases M and NM from the bullet example.
 
 \vspace{0.5cm}
-
-\renewcommand{\thefigure}{S2}
-\begin{figure*}[!h]
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-
-{\centering \includegraphics[width=6.5in]{figure/figure-s2-1}
-
-}
-
-\end{knitrout}
-\caption{Explanation plot from \emph{lime} R package (left) and explanation scatterplot (right) for case M in the bullet test data for 4-quantile-bins.}
-\label{fig:figure-s2}
-\end{figure*}
 
@@
 \end{knitrout}
-\caption{Explanation plot from \emph{lime} R package (left) and explanation scatterplot (right) for case M in the bullet test data for 4-equal-bins.}
+\caption{Explanation plot from \emph{lime} R package (left) and explanation scatterplot (right) for case M in the bullet test data for 4-quantile-bins.}
 \label{fig:figure-s3}
@@
 \end{knitrout}
-\caption{Explanation scatterplots for LIME explanations using kernel density simulation for the cases M (top) and NM (bottom) of the bullet comparison test data.}
+\caption{Explanation plot from \emph{lime} R package (left) and explanation scatterplot (right) for case M in the bullet test data for 4-equal-bins.}
 \label{fig:figure-s4}
@@
 
+\renewcommand{\thefigure}{S5}
+\begin{figure*}[!h]
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+
+{\centering \includegraphics[width=6.5in]{figure/figure-s5-1}
+
+}
+
+\end{knitrout}
+\caption{Explanation scatterplots for LIME explanations using kernel density simulation for the cases M (top) and NM (bottom) of the bullet comparison test data.}
+\label{fig:figure-s5}
+\end{figure*}
+
 \end{document}

### 2021-01-05 paper.Rnw
finished proof read (fixed typos and made small changes to text)

@@
 An explanation scatterplot associated with the explanation on the left.
-The four quantile bins over-simplify the relationship between the random forest predictions and the $x_1$ and $x_2$ values near the prediction of interest.}
+The 4-quantile-bins over-simplify the relationship between the random forest predictions and the $x_1$ and $x_2$ values near the prediction of interest.}
 \label{fig:figure-03}
@@
 Depending on what region a viewer considers to be local, an argument could be made in favor of or against a violation of localness.
-\sout{The explanation scatterplot raises awareness of the unclear definition of a local region with LIME.
-Nevertheless, it is possible to say that the weights assigned to the simulated data do not capture the local region identified by the intersection of the quantile bins.}
+The explanation scatterplot raises awareness of the unclear definition of a local region with LIME.
+\sout{Nevertheless, it is possible to say that the weights assigned to the simulated data do not capture the local region identified by the intersection of the quantile bins.}
 
@@
 Explanations produced by LIME are likely to be affected by the choice of tuning parameter values.
-A hypothetical example of this is shown by Figures \ref{fig:figure-01} and \ref{fig:figure-02} where the method used to weight the observations influenced the explanation.
+A hypothetical example of this is shown by Figure\sout{s} \ref{fig:figure-01} \sout{and \ref{fig:figure-02} }where the method used to weight the observations influenced the explanation.
 As of the time of writing this manuscript, we have encountered no recommendations for how to specify the parameter values besides for the default settings in the \emph{lime} R package.
@@
 Vertical lines of color represent explanations that are dependent on the tuning parameter values and may not be local since the same feature is chosen regardless of the location of the observation in the feature space.
-See \kge{the supporting information} \sout{Appendix \ref{feat-heat-ex}} for hypothetical examples depicting \kge{the extreme cases of} feature heatmaps\kge{.} \sout{with the extreme cases of horizontal and vertical lines.}
+See \kge{the supporting information} \sout{Appendix \ref{feat-heat-ex}} for hypothetical examples depicting \kge{the extreme cases of} feature heatmaps\kge{.} \sout{with the extreme cases of horizontal and vertical lines.} \kgc{Remove?}
 
@@
 \caption{\emph{Feature Heatmap}.
-An example feature heatmap of the explanations from the applications of LIME with different tuning parameter values to the \data \ test set.
+An example feature heatmap \sout{of the explanations} from the applications of LIME \sout{with different tuning parameter values} to the \data \ test set.
 The vertical striping indicates that the LIME explanations are not consistent across tuning parameter values.}
@@
 This figure shows that for kernel density and 2-quantile-bins, LIME produces global explanations since $x_1$ is selected as the most important feature and $x_2$ is selected as the second most important feature across all cases in the test set.
-There is variability in the features selected by LIME for 3- to 6-quantile-bins suggesting more local explanations.
+There is variability in the features selected by LIME for 3- to 6- quantile-bins suggesting more local explanations.
 There are signs of vertical striping, which suggests a dependence on tuning parameters.
-Note that the explanations from 3- and 5-quantile-bins include the selection of the random noise variable ($x_3$) as an important variable in many predictions, which would not be expected to be important to a random forest.
+Note that the explanations from 3- and 5-quantile-bins include the selection of the random noise variable ($x_3$) as an important variable in many predictions\sout{, which would not be expected to be important to a random forest}.
 It is unclear whether the random forest is using a variable that would not be expected to be important or LIME is incorrectly identifying the important variable when 3- and 5- quantile bins are used.
@@
 \begin{itemize}
-\item \emph{Average $R^2$}: Assess the model fit and linearity claim by computing the average of the explainer model $R^2$ values (deviance ratios from the R package \emph{glmnet}).
+\item \emph{Average $R^2$}: Assesses the model fit and linearity claim by computing the average of the explainer model $R^2$ values (deviance ratios from the R package \emph{glmnet}).
 
@@
 
-\begin{figure}[!tp]
+\begin{figure}[!bp]
 <<figure-05, out.width = '3.25in', fig.width = 4.5, fig.height = 3.75, warning = FALSE>>=
@@
 \caption{\emph{Assessment metric plot}.
-This example assessment metric plot contains metrics computed on the applications of LIME to the \data \ test set.
-The kernel density simulation methods performs well across all three metrics.}
+This example assessment metric plot \sout{contains metrics computed on} \kge{is from} the applications of LIME to the \data \ test set.
+The kernel density simulation method\sout{s} performs well across all three metrics.}
 \label{fig:figure-05}
@@
 The plot is faceted by metric, and the metric values are plotted on the y-axis.
-The colors of the points represent the rank of the simulation methods performance based on a particular metric (darker indicates a better metric value and lighter indicates a worse metric value).
+The \kge{point} color\sout{s of the points} represent the rank of the simulation methods performance based on a particular metric (darker indicates a better metric value and lighter indicates a worse metric value).
 Higher average $R^2$ values are better, and lower average fidelity and MSEE values are better.
 This example only includes one tuning parameter: the simulation method.
-If more than one tuning parameter is considered, the assessment metric plot is extended by adding additional facets or levels to the x-axis.
-
-All three metrics suggest that the kernel density method performed well, but the metrics disagree for the quantile bins methods.
+If more than one tuning parameter is considered, the assessment metric plot is extended by adding additional facets\kge{, point shapes,} or levels to the x-axis.
+
+All three metrics suggest that the kernel density method perform\sout{ed} well, but the metrics disagree for the quantile bin\sout{s} methods.
 Average $R^2$ and average fidelity rank the performance of the number of quantile bins the same (2-quantile-bins perform the best and 6-quantile-bins perform the worst).
@@
 Average fidelity and MSEE are similar metrics, but MSEE only takes the prediction of interest into account and not the full simulated dataset as average fidelity does.
-This suggests that 6-quantile-bins produce an explainer model more faithful for the prediction of interest while 2-quantile-bins produce an explainer model more faithful over all simulated data observations.
+This suggests that 6-quantile-bins produce an explainer model more faithful for the prediction of interest while 2-quantile-bins produce an explainer model more faithful over all simulated data observations \kge{(weighted by proximity to the prediction of interest)}.
 
@@
 
-LIME is applied to all test set observations using different tuning parameter values: 12 sampling methods (2 to 6 equally spaced bins, 2 to 6 quantile-bins, kernel density estimation, and normal approximation) and 3 Gower exponents (0.5, 1, and 10).
+LIME is applied to all test set observations using different tuning parameter values: 12 sampling methods (2- to 6- equally-spaced bins, 2- to 6- quantile-bins, kernel density estimation, and normal approximation) and 3 Gower exponents (0.5, 1, and 10).
 Thus, a total of $12\times 3=36$ different applications of LIME are performed.
@@
 Plots for 4-equal-bins and 4-quantile-bins are included to depict tuning parameter values with good (4-equal-bins) and mediocre (4-quantile-bins) performance based on the assessment metric plot.
-\kge{Additional examples of explanation scatterplots including explanations for a known match and explanation produced using the kernel density simulation method are included in the  the supporting information.} \sout{Explanation scatterplots for a known match, referred to as case M, and for the kernel density simulation method applied to both M and NM are included in Appendix~\ref{bullets-plus}.}
-
-When 4-quantile-bins are applied to case NM, LIME explains that the values of mismatches, rough correlation, and distance are important and support a prediction of the class true (Figure~\ref{fig:figure-11} top left).
+\kge{Additional examples of explanation scatterplots including explanations for a known match and explanations produced using the kernel density simulation method are included in the supporting information.} \sout{Explanation scatterplots for a known match, referred to as case M, and for the kernel density simulation method applied to both M and NM are included in Appendix~\ref{bullets-plus}.}
+
+\kge{Figure~\ref{fig:figure-11} (top left) shows that w}\sout{W}hen 4-quantile-bins are applied to case NM, LIME explains that the values of mismatches, rough correlation, and distance are important and support a prediction of the class true\sout{ (Figure~\ref{fig:figure-11} top left)}.
 However, this explanation contradicts the random forest prediction which correctly assigns the observation  a non-match.
@@
 
-Figure~\ref{fig:figure-11} (top right) shows the LIME explanation for case NM when 4-equal-bins are used.
-Here, the features identified as important are distance and mismatches, which support a match and matches, which supports a non-match.
+Figure~\ref{fig:figure-11} (top right) shows \sout{the LIME explanation for case NM} \kge{that} when 4-equal-bins are used\sout{.
+Here}, the features \kge{LIME} identifie\sout{d}\kge{s} as important are distance and mismatches, which support a match and matches, which supports a non-match.
 This explanation is more faithful having at least one feature supporting a non-match and has a better linear fit, but the most important feature identified by LIME still supports a match, contradicting the random forest.
@@
 For example, the visualization of a LIME explanation from the \emph{lime} R package \citep{pedersen:2020} (\autoref{fig:figure-03} left; \autoref{fig:figure-11} top) is a simplification of the explainer model, which could lead to misinterpreted LIME explanations.
-Supplementing \citet{pedersen:2020}'s compact visualization of the explanation with an explanation scatterplot that shows a more detailed visualization of the explainer model promotes a more complete understanding of the explanation (Figures~\ref{fig:figure-03} right; \ref{fig:figure-11} bottom).
+\kgc{Clarify?} Supplementing \citet{pedersen:2020}'s compact visualization of the explanation with an explanation scatterplot that shows a more detailed visualization of the explainer model promotes a more complete understanding of the explanation (\autoref{fig:figure-03} right; \autoref{fig:figure-11} bottom).
 
@@
 Explanation scatterplots allow for a comparison of the explainer model to the complex model.
-The examples in this paper show cases where the explainer model oversimplifies the model and bins do not accurately capture the regions with similar random forest probabilities that contain the prediction of interest (Figures \ref{fig:figure-03} and \ref{fig:figure-11}).
+The examples in this paper show cases where the explainer model oversimplifies the model and bins do not accurately capture the regions with similar random forest probabilities that contain the prediction of interest (\autoref{fig:figure-03} right; \autoref{fig:figure-11} bottom).
 Using fewer bins would clearly not help improve the faithfulness of the explainer model in these examples, and while an increase in the number of bins would lead to a finer resolution of the random forest classification boundaries, interpretability of the explainer model would quickly be lost.
@@
 These diagnostic visualizations are a starting point that already highlight seemingly common issues with the LIME claims.
-Additions, such as visualizations of the step-by-step process of the creation of LIME explanations and interactivity, enhance the assessment process.
-For example, a diagnostic plot that provides a summary of multiple LIME explanations, such as the feature heatmap, could be displayed and clicked on to reveal more detailed figures associated with individual predictions of interest, such as an explanation scatterplot.
+Additions, such as visualizations of the step-by-step process of the creation of LIME explanations and interactivity \kge{would}\sout{,} enhance the assessment process.
+For example, a diagnostic plot that provides a summary of multiple LIME explanations, such as the feature heatmap, could be \sout{displayed and} clicked on to reveal more detailed figures\kge{, such as an explanation scatterplot, for a prediction of interest.}\sout{ associated with individual prediction of interest, such as an explanation scatterplot.}
 
@@
 
-While it would be ideal if LIME could be used as a method to provide easily understandable explanations for black-box models as \citet{ribeiro:2016} claim, that dream is not yet a reality.
+While it would be ideal if LIME could be used as a method to provide easily understandable explanations for black-box models as \citet{ribeiro:2016} claim, \kge{there is still work to be done to achieve that} \sout{that dream is not yet a} reality.
 The examples using diagnostic plots to assess LIME in this paper show frequent instances when the claims about LIME are not met.
@@
 
-\kge{Additional example visual diagnostics may be found online in the Supporting Information section at the end of this manuscript.} The code used to produce the manuscript and the data from examples in Section \ref{application} are available in the following GitHub Repository: \href{https://github.com/goodekat/LIME-diagnostics-paper}{https://github.com/goodekat/LIME-diagnostics-paper}.
+\kge{Additional examples of the visual diagnostics and more info on the bullet matching data may be found in the Supporting Information section of the online version of the manuscript.} The code \sout{used to produce the manuscript} and \sout{the} data \sout{from examples in Section \ref{application}} \kge{associated with the manuscript} are available in the following GitHub Repository: \href{https://github.com/goodekat/LIME-diagnostics-paper}{https://github.com/goodekat/LIME-diagnostics-paper}.
 

### 2021-01-05 paper.tex
finished proof read (fixed typos and made small changes to text)

@@
 
-\begin{figure}[!tp]
+\begin{figure}[!bp]
 \begin{knitrout}
@@
 The plot is faceted by metric, and the metric values are plotted on the y-axis.
-The colors of the points represent the rank of the simulation methods performance based on a particular metric (darker indicates a better metric value and lighter indicates a worse metric value).
+The \kge{point} color\sout{s of the points} represent the rank of the simulation methods performance based on a particular metric (darker indicates a better metric value and lighter indicates a worse metric value).
 Higher average $R^2$ values are better, and lower average fidelity and MSEE values are better.
 This example only includes one tuning parameter: the simulation method.
-If more than one tuning parameter is considered, the assessment metric plot is extended by adding additional facets or levels to the x-axis.
+If more than one tuning parameter is considered, the assessment metric plot is extended by adding additional facets\kge{, point shapes,} or levels to the x-axis.
 
-All three metrics suggest that the kernel density method performed well, but the metrics disagree for the quantile bins methods.
+All three metrics suggest that the kernel density method perform\sout{ed} well, but the metrics disagree for the quantile bin\sout{s} methods.
 Average $R^2$ and average fidelity rank the performance of the number of quantile bins the same (2-quantile-bins perform the best and 6-quantile-bins perform the worst).
@@
 Plots for 4-equal-bins and 4-quantile-bins are included to depict tuning parameter values with good (4-equal-bins) and mediocre (4-quantile-bins) performance based on the assessment metric plot.
-\kge{Additional examples of explanation scatterplots including explanations for a known match and explanation produced using the kernel density simulation method are included in the  the supporting information.} \sout{Explanation scatterplots for a known match, referred to as case M, and for the kernel density simulation method applied to both M and NM are included in Appendix~\ref{bullets-plus}.}
+\kge{Additional examples of explanation scatterplots including explanations for a known match and explanations produced using the kernel density simulation method are included in the supporting information.} \sout{Explanation scatterplots for a known match, referred to as case M, and for the kernel density simulation method applied to both M and NM are included in Appendix~\ref{bullets-plus}.}
 
-When 4-quantile-bins are applied to case NM, LIME explains that the values of mismatches, rough correlation, and distance are important and support a prediction of the class true (Figure~\ref{fig:figure-11} top left).
+\kge{Figure~\ref{fig:figure-11} (top left) shows that w}\sout{W}hen 4-quantile-bins are applied to case NM, LIME explains that the values of mismatches, rough correlation, and distance are important and support a prediction of the class true\sout{ (Figure~\ref{fig:figure-11} top left)}.
 However, this explanation contradicts the random forest prediction which correctly assigns the observation  a non-match.

### 2021-01-05 support-info/support-info.Rnw
updated and proof read

--- 2021-01-04 supporting-info/supporting-info.Rnw
@@
-\documentclass[9pt]{article}
-
-\usepackage[margin=1in]{geometry}
-
+\documentclass{article}
+\usepackage{hyperref}
+\usepackage{natbib}
+\usepackage{placeins}
+\bibliographystyle{unsrtnat}
 \newcommand{\data}{sine data}
-
-\title{Supporting Information Corresponding to ``Visual Diagnostics of an Explainer Model -- Tools for the Assessment of LIME Explanations"}
-
+\title{Supporting Information for the Manuscript ``Visual Diagnostics of an Explainer Model -- Tools for the Assessment of LIME Explanations"}
 \date{}
@@
 \maketitle
+\tableofcontents
 
@@
 # Specify the (base) font size (fs) and font (ff) for all plots
-fs = 7
+fs = 6
 ff = "Helvetica"
@@
 
-When the kernel density or normal approximation simulation methods are applied, the explanation scatterplot depicts the complex model by plotting the complex model predictions versus a feature selected in LIME the explanation from the simulated data.
+When the kernel density or normal approximation simulation methods are applied, the explanation scatterplot depicts the complex model by plotting the complex model predictions versus a feature in LIME the explanation from the simulated data.
 The explainer model is included as a line on the figure where all features excluding the one plotted on the x-axis are set to the observed values of the prediction of interest.
@@
 \begin{figure*}[!thp]
-<<figure-s1, out.width = '6.5in', fig.width = 12, fig.height = 5, fig.align = "center">>=
+<<figure-s1, out.width = '4.5in', fig.width = 12, fig.height = 5.75, fig.align = "center">>=
 
@@
 # Specify the figure size (for determining font size and line size)
-fs1_ow = 6.5
+fs1_ow = 4.5
 fs1_fw = 12
@@
     strip.placement = "outside",
-    strip.text.x = element_text(size = fs1_fs)
+    strip.text.x = element_text(size = fs1_fs),
+    aspect.ratio = 1
   )
@@
 \begin{figure}[!h]
-<<figure-s2, out.width = '4.5in', fig.width = 8, fig.height = 3.5>>=
+<<figure-s2, out.width = '4in', fig.width = 8, fig.height = 3.5>>=
 
 # Specify the figure size (for determining font size)
-fs2_ow = 4.5
+fs2_ow = 4
 fs2_fw = 8
@@
   theme(legend.position = "none", 
-        plot.title = element_text(size = fs2_fs))
+        plot.title = element_text(size = fs2_fs),
+        aspect.ratio = 0.85)
 
@@
   theme_bw(base_family = ff, base_size = fs2_fs) +
-  theme(plot.title = element_text(size = fs2_fs)) +
+  theme(plot.title = element_text(size = fs2_fs), 
+        aspect.ratio = 0.85) +
   scale_fill_grey() +
@@
 
+\section{Additional Information on the Bullet Matching Data}
+
+\subsection{Training Data}
+
+The bullet matching training data has 83,028 rows and 13 columns that contain comparison features described in \citet{hare:2017} based on high resolution microscopy scans of fired bullets from Hamby sets 173 and 252 \citep{hamby:2009}.
+This dataset is created from the x3p scans of bullet land engraved areas available from the NIST Ballistics Toolmark Research Database\footnote{\url{https://tsapps.nist.gov/NRBTD/}}.
+It contains comparisons from 408 bullet-land signatures.
+12 of the overall 420 lands (6 lands per bullets, 35 bullets in each set) are excluded from the comparison.
+Six of these lands show so-called "tank rash" - damage to the bullets after it exited the barrel.\footnote{\url{https://github.com/goodekat/LIME-diagnostics-paper/blob/master/LEAscans/tankrash.md}} Another bullet (Bullet E from Hamby 173) is excluded because it could not be matched visually to the barrel it was supposedly from.\footnote{\url{https://github.com/goodekat/LIME-diagnostics-paper/blob/master/LEAscans/bullete.md}}
+
+The training data used in the manuscript it generated from a raw file of comparison features.\footnote{\url{https://github.com/goodekat/LIME-diagnostics-paper/blob/master/data/raw/CCFs\_withlands.zip}} The steps taken to create the bullet training data from the raw data involve renaming some variables, selecting the variables of interest for the manuscript, and adjusting the land IDs associated with the signatures.\footnote{\url{https://github.com/goodekat/LIME-diagnostics-paper/blob/master/code/02-data-preparation.Rmd}}
+
+\subsection{Testing Data}
+
+The bullet test data has 364 rows and 13 columns that contains comparison features from test sets 1 and 11 of the Hamby 224 Clone Test Sets.
+Each test set is arranged as a combination of three bullets: two known bullets and a questioned bullet.
+Similar to the training set, each bullet has 6 lands.
+The data contains comparisons of bullet-lands within a set.
+With three bullets with six lands per set, there are a total of (2 sets) $\times$ (3!
+bullet comparisons) $\times$ ($6^2$ land comparisons) = 432 comparisons.
+However, there are only 364 comparisons in the bullet-test data.
+This is due to the fact that some of the lands are missing from the data (due to tank rash): land 4 from the unknown bullet in set 1, land 2 from bullet 1 in set 11, and land 4 from the unknown bullet in set 11.
+The test data set using in the manuscript is generated from the raw versions of the data for set 1 and set 11.\footnote{\url{https://github.com/goodekat/LIME-diagnostics-paper/blob/master/data/raw/h224-set1-features.rds.zip} and \url{https://github.com/goodekat/LIME-diagnostics-paper/blob/master/data/raw/h224-set11-features.rds.zip}}
+
+\subsection{Variable Definitions}
+
+The variables included in the bullet training and testing data sets are defined below. Further descriptions of the comparison features are found in \citet{hare:2017}.\\
+
+\noindent Index variables:
+
+\begin{itemize}
+\item \textbf{case}: ID number associated with the bullet-land signature comparison.
+\item \textbf{land\_id1}, \textbf{land\_id2}: IDs describing the two land engraved areas in the comparison. The format is study-barrel-bullet-land.
+\end{itemize}
+
+\noindent Predictor (comparison) variables:
+
+\begin{itemize}
+\item \textbf{ccf}: Maximized cross-correlation between two LEA signatures.
+\item \textbf{rough\_cor}: Correlation after detrending aligned signatures.
+\item \textbf{D}: Euclidean distance (in millimeters) between two aligned signatures.
+\item \textbf{sd\_D}: Standard deviation of the previous measure along the signature.
+\item \textbf{matches}, \textbf{mismatches}: Number of matching/non-matching peaks and valleys in the aligned signatures.
+\item \textbf{cms}: Consecutively matching striae is a measure introduced by \citet{biasotti:1959} describing the longest run of matching peaks between two aligned signatures.
+\item \textbf{non\_cms}: The number of consecutively non-matching peaks.
+\item \textbf{sum\_peaks}: The depth of peaks measured as the sum of matching peaks between two aligned signatures (in microns).
+\end{itemize}
+
+\noindent Response variable:
+
+\begin{itemize}
+\item \textbf{samesource}: Ground truth whether a pair is from the same source (TRUE) or from different sources (FALSE).
+\end{itemize}
+
 \section{Additional Bullet Matching Explanation Scatterplots}
@@
 Figures \ref{fig:figure-s3} and \ref{fig:figure-s4} include visual representations of LIME explanations from the \emph{lime} R package (left) and explanation scatterplots (right) for a known match observation in the the bullet example referred to as case M.
-The explanations in Figures \ref{fig:figure-s3} and \ref{fig:figure-s4} are obtained using 4-quantile-bins and Figure 4-equal-bins, respectively.
-The explanations appear to be faithful to the random forest than those associated with the known non-match (case NM) shown in the manuscript.
+The explanations in Figures \ref{fig:figure-s3} and \ref{fig:figure-s4} are obtained using 4-quantile-bins and 4-equal-bins, respectively.
+The explanations appear to be more faithful to the random forest than those associated with the known non-match (case NM) shown in the manuscript.
 However, the intersections of the bins are still not well aligned with the regions containing similar probabilities produced by the random forest.
@@
 
-<<>>=
+<<bullet-perm-data>>=
 # Load the cleaned explanations
@@
 \begin{figure*}[!h]
-<<figure-s3, out.width = '6.5in', fig.width = 14, fig.height = 7>>=
+<<figure-s3, out.width = '4.5in', fig.width = 14, fig.height = 7>>=
 
 # Specify the figure size (for determining font size)
-fs3_ow = 6.5
+fs3_ow = 4.5
 fs3_fw = 14
@@
   nrow = 1,
-  rel_widths = c(0.35, 0.65)
+  rel_widths = c(0.4, 0.6)
 )
@@
 \begin{figure*}[!h]
-<<figure-s4, out.width = '6.5in', fig.width = 14, fig.height = 7>>=
+<<figure-s4, out.width = '4.5in', fig.width = 14, fig.height = 7>>=
 
 # Specify the figure size (for determining font size)
-fs4_ow = 6.5
+fs4_ow = 4.5
 fs4_fw = 14
@@
 \label{fig:figure-s4}
-\end{figure*}
+
+\vspace*{\floatsep}
 
 \renewcommand{\thefigure}{S5}
-\begin{figure*}[!h]
-<<figure-s5, out.width = '6.5in', fig.width = 12, fig.height = 10>>=
+<<figure-s5, out.width = '4.5in', fig.width = 12, fig.height = 10.5>>=
 
 # Specify the figure size (for determining font size and line size)
-fs5_ow = 6.5
+fs5_ow = 4.5
 fs5_fw = 12
@@
 @
-\caption{Explanation scatterplots for LIME explanations using kernel density simulation for the cases M (top) and NM (bottom) of the bullet comparison test data.}
+\caption{Explanation scatterplots for LIME explanations using kernel density simulation for cases M (top) and NM (bottom) of the bullet comparison test data.}
 \label{fig:figure-s5}
@@
 
+\FloatBarrier
+
+\bibliography{references}
+
 \end{document}

### 2021-01-05 support-info/support-info.tex
updated and proof read

--- 2021-01-05 support-info/support-info.Rnw
@@
-\documentclass{article}
+\documentclass{article}\usepackage[]{graphicx}\usepackage[]{color}
+% maxwidth is the original width if it is less than linewidth
+% otherwise use linewidth (to make sure the graphics do not exceed the margin)
+\makeatletter
+\def\maxwidth{ %
+  \ifdim\Gin@nat@width>\linewidth
+    \linewidth
+  \else
+    \Gin@nat@width
+  \fi
+}
+\makeatother
+
+\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
+\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
+\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
+\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
+\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
+\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
+\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
+\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
+\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
+\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%
+\let\hlipl\hlkwb
+
+\usepackage{framed}
+\makeatletter
+\newenvironment{kframe}{%
+ \def\at@end@of@kframe{}%
+ \ifinner\ifhmode%
+  \def\at@end@of@kframe{\end{minipage}}%
+  \begin{minipage}{\columnwidth}%
+ \fi\fi%
+ \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
+ \colorbox{shadecolor}{##1}\hskip-\fboxsep
+     % There is no \\@totalrightmargin, so:
+     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
+ \MakeFramed {\advance\hsize-\width
+   \@totalleftmargin\z@ \linewidth\hsize
+   \@setminipage}}%
+ {\par\unskip\endMakeFramed%
+ \at@end@of@kframe}
+\makeatother
+
+\definecolor{shadecolor}{rgb}{.97, .97, .97}
+\definecolor{messagecolor}{rgb}{0, 0, 0}
+\definecolor{warningcolor}{rgb}{1, 0, 1}
+\definecolor{errorcolor}{rgb}{1, 0, 0}
+\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX
+
+\usepackage{alltt}
 \usepackage{hyperref}
@@
 \tableofcontents
-
-<<setup, echo = FALSE, include = FALSE>>=
-# Specify global options
-knitr::opts_chunk$set(
-  warning = FALSE,
-  message = FALSE,
-  echo = FALSE,
-  fig.keep = 'high',
-  fig.align = 'center',
-  dev = c("cairo_pdf", "cairo_ps"),
-  dev.args = list(fallback_resolution = 800),
-  dpi = 1200
-)
-
-# Load packages
-library(Cairo)
-library(cowplot)
-library(dplyr)
-library(forcats)
-library(ggplot2)
-library(gretchenalbrecht) #remotes::install_github("dicook/gretchenalbrecht")
-library(lime) #remotes::install_github("goodekat/lime")
-library(limeaid) #remotes::install_github("goodekat/limeaid")
-library(tidyr)
-
-# Specify the (base) font size (fs) and font (ff) for all plots
-fs = 6
-ff = "Helvetica"
-@
 
@@
 \begin{figure*}[!thp]
-<<figure-s1, out.width = '4.5in', fig.width = 12, fig.height = 5.75, fig.align = "center">>=
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
 
-# Load the testing sine data
-sine_data_test <- readRDS("../data/sine-data-test.rds")
+{\centering \includegraphics[width=4.5in]{figure/figure-s1-1}
 
-# Load the sine data explanations
-sine_lime_explain <- readRDS("../data/sine-lime-explain.rds")
+}
 
-# Extract the prediction of interest from the sine test data
-sine_poi <- sine_data_test %>% filter(y != rfpred, x1 > 0, x1 < 5, x2 > 5)
-
-# Specify the figure size (for determining font size and line size)
-fs1_ow = 4.5
-fs1_fw = 12
-fs1_fs = fs * (fs1_fw / fs1_ow)
-fs1_ls = 0.5 * (fs1_fw / fs1_ow)
-
-# Create the explanation scatterplot
-plot_explain_scatter(
-  sine_lime_explain$explain %>%
-    filter(sim_method == "kernel_density", case == sine_poi %>% pull(case)),
-  alpha = 0.75,
-  title.opt = FALSE, 
-  line_size = fs1_ls 
-) +
-  theme_bw(base_family = ff, base_size = fs1_fs) +
-  theme(
-    strip.background = element_rect(fill = "white", color = "white"),
-    strip.placement = "outside",
-    strip.text.x = element_text(size = fs1_fs),
-    aspect.ratio = 1
-  )
-
-@
+\end{knitrout}
 \caption{Explanation scatterplots for the \data \ prediction of interest with the kernel density simulation method.}
@@
 \begin{figure}[!h]
-<<figure-s2, out.width = '4in', fig.width = 8, fig.height = 3.5>>=
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
 
-# Specify the figure size (for determining font size)
-fs2_ow = 4
-fs2_fw = 8
-fs2_fs = fs * (fs2_fw / fs2_ow)
+{\centering \includegraphics[width=4in]{figure/figure-s2-1}
 
-# Specify the number of cases and LIME input options
-ncases = 10
-ninputs = 5
+}
 
-# Create a good case of chosen feature example data
-set.seed(20191008)
-heatmap_data_good <-
-  tibble(
-    case = factor(rep(1:ncases, each = ninputs),
-                  levels = ncases:1),
-    input = factor(rep(1:ninputs, ncases)),
-    feature = factor(c(
-      rep(1, 5),
-      rep(2, 5),
-      rep(3, 5),
-      rep(1, 5),
-      rep(1, 5),
-      rep(4, 5),
-      rep(1, 5),
-      rep(3, 5),
-      rep(1, 5),
-      rep(4, 5)
-    ))
-  ) %>%
-  mutate(input = fct_recode(
-    input,
-    "A" = "1",
-    "B" = "2",
-    "C" = "3",
-    "D" = "4",
-    "E" = "5"
-  ))
-
-# Create the conceptual good heatmap
-heatmap_plot_good <- ggplot(data = heatmap_data_good,
-                            mapping = aes(
-                              x = input,
-                              y = case,
-                              fill = feature,
-                              color = feature
-                            )) +
-  geom_tile() +
-  labs(
-    x = "Tuning Parameter Value",
-    y = "Case",
-    fill = "Feature",
-    color = "Feature",
-    title = "Situation 1",
-    subtitle = "Consistent Explanations"
-  ) +
-  theme_bw(base_family = ff, base_size = fs2_fs) +
-  scale_fill_grey() +
-  scale_color_grey() +
-  theme(legend.position = "none", 
-        plot.title = element_text(size = fs2_fs),
-        aspect.ratio = 0.85)
-
-# Create a bad case of chosen feature example data
-set.seed(20190627)
-heatmap_data_bad <- tibble(
-  case = factor(rep(1:ncases, ninputs),
-                levels = ncases:1),
-  input = factor(rep(1:ninputs, each = ncases)),
-  feature = factor(rep(c(1, 2, 4, 3, 2), each = 10))
-) %>%
-  mutate(input = fct_recode(
-    input,
-    "A" = "1",
-    "B" = "2",
-    "C" = "3",
-    "D" = "4",
-    "E" = "5"
-  ))
-
-# Create the conceptual bad heat map
-heatmap_plot_bad <- ggplot(data = heatmap_data_bad,
-                           mapping = aes(
-                             x = input,
-                             y = case,
-                             fill = feature,
-                             color = feature
-                           )) +
-  geom_tile() +
-  labs(
-    x = "Tuning Parameter Value",
-    y = "Case",
-    fill = "Feature",
-    color = "Feature",
-    title = "Situation 2",
-    subtitle = "Inconsistent Explanations"
-  ) +
-  theme_bw(base_family = ff, base_size = fs2_fs) +
-  theme(plot.title = element_text(size = fs2_fs), 
-        aspect.ratio = 0.85) +
-  scale_fill_grey() +
-  scale_color_grey()
-
-heatmap_leg <- get_legend(heatmap_plot_bad)
-heatmap_plot_bad <-
-  heatmap_plot_bad + theme(legend.position = 'none')
-
-# Join the plots
-plot_grid(
-  heatmap_plot_good,
-  heatmap_plot_bad,
-  heatmap_leg,
-  nrow = 1,
-  rel_widths = c(0.43, 0.43, 0.14)
-)
-
-@
+\end{knitrout}
 \caption{Hypothetical examples of feature heatmaps in two possible situations.
@@
 
-<<bullet-perm-data>>=
-# Load the cleaned explanations
-bullet_explain_perms_clean <- readRDS("../data/bullet-explain-perms-clean.rds")
-@
-
 \renewcommand{\thefigure}{S3}
 \begin{figure*}[!h]
-<<figure-s3, out.width = '4.5in', fig.width = 14, fig.height = 7>>=
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
 
-# Specify the figure size (for determining font size)
-fs3_ow = 4.5
-fs3_fw = 14
-fs3_fs = fs * (fs3_fw / fs3_ow)
-fs3_ls = 0.5 * (fs3_fw / fs3_ow)
+{\centering \includegraphics[width=4.5in]{figure/figure-s3-1}
 
-# Create a theme for the lime explanation visualizations
-bullet_explain_plot_theme <-
-  list(
-    scale_fill_manual(values = c("darkorange", "grey50")),
-    theme(
-      text = element_text(family = ff, size = fs3_fs),
-      strip.text.x = element_text(face = "plain", size = fs3_fs),
-      aspect.ratio = 1
-    )
-  )
+}
 
-# Create theme for explanation scatterplots
-bullet_eoi_plot_theme <-
-  list(
-    scale_color_gradient2(
-      low = "grey50",
-      high = "darkorange",
-      midpoint = 0.5,
-      limits = c(0, 1)
-    ),
-    scale_fill_gradient2(
-      low = "grey50",
-      high = "darkorange",
-      midpoint = 0.5,
-      limits = c(0, 1)
-    ),
-    theme_bw(base_family = ff, base_size = fs3_fs),
-    theme(
-      aspect.ratio = 1,
-      plot.title = element_text(size = fs3_fs),
-      strip.text.x = element_text(size = fs3_fs),
-      strip.text.y = element_text(size = fs3_fs),
-      strip.placement = "outside",
-      strip.background = element_rect(color = "white", fill = "white")
-    ),
-    guides(size = guide_legend(nrow = 2, byrow = T), 
-           linetype = guide_legend(override.aes = list(color = c("grey50", "darkorange"))))
-  )
-
-# Create the lime explanation visualizations
-pfM_3qb <- plot_features(bullet_explain_perms_clean[1:3,]) + bullet_explain_plot_theme
-
-# Create the explanation scatterplots
-eoiM_3qb <-
-  plot_explain_scatter(
-    bullet_explain_perms_clean[1:3, ],
-    alpha = 0.9,
-    weights = TRUE,
-    line_size = fs3_ls
-  ) +
-  bullet_eoi_plot_theme +
-  guides(linetype = guide_legend(override.aes = list(color = c("darkorange"))))
-
-# Join the plots
-plot_grid(
-  pfM_3qb,
-  eoiM_3qb,
-  nrow = 1,
-  rel_widths = c(0.4, 0.6)
-)
-
-@
+\end{knitrout}
 \caption{Explanation plot from \emph{lime} R package (left) and explanation scatterplot (right) for case M in the bullet test data for 4-quantile-bins.}
@@
 \begin{figure*}[!h]
-<<figure-s4, out.width = '4.5in', fig.width = 14, fig.height = 7>>=
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
 
-# Specify the figure size (for determining font size)
-fs4_ow = 4.5
-fs4_fw = 14
-fs4_fs = fs * (fs4_fw / fs4_ow)
-fs4_ls = 0.5 * (fs4_fw / fs4_ow)
+{\centering \includegraphics[width=4.5in]{figure/figure-s4-1}
 
-# Create the lime explanation visualizations
-pfM_3eb <- plot_features(bullet_explain_perms_clean[7:9,]) + bullet_explain_plot_theme
+}
 
-# Create the explanation scatterplots
-eoiM_3eb <-
-  plot_explain_scatter(
-    bullet_explain_perms_clean[7:9, ],
-    alpha = 0.9,
-    weights = TRUE,
-    line_size = fs4_ls
-  ) +
-  bullet_eoi_plot_theme + 
-  guides(linetype = guide_legend(override.aes = list(color = c("darkorange"))))
-
-# Join the plots
-plot_grid(
-  pfM_3eb,
-  eoiM_3eb,
-  nrow = 1,
-  rel_widths = c(0.4, 0.6)
-)
-
-@
+\end{knitrout}
 \caption{Explanation plot from \emph{lime} R package (left) and explanation scatterplot (right) for case M in the bullet test data for 4-equal-bins.}
@@
 \renewcommand{\thefigure}{S5}
-<<figure-s5, out.width = '4.5in', fig.width = 12, fig.height = 10.5>>=
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
 
-# Specify the figure size (for determining font size and line size)
-fs5_ow = 4.5
-fs5_fw = 12
-fs5_fs = fs * (fs5_fw / fs5_ow)
-fs5_ls = 0.5 * (fs5_fw / fs5_ow)
+{\centering \includegraphics[width=4.5in]{figure/figure-s5-1}
 
-# Create the explanation scatterplot: case M, kernel density
-bullet_es_M <-
-  plot_explain_scatter(
-    bullet_explain_perms_clean %>% filter(case == "M", sim_method == "kernel_density"),
-    alpha = 0.75,
-    title.opt = TRUE,
-    line_size = fs5_ls
-  ) +
-  scale_fill_gradient2(
-    low = "grey50",
-    high = "darkorange",
-    midpoint = 0.5,
-    limits = c(0, 1)
-  ) +
-  theme_bw(base_family = ff, base_size = fs5_fs) +
-  theme(
-    aspect.ratio = 1,
-    strip.background = element_rect(fill = "white", color = "white"),
-    strip.placement = "outside",
-    strip.text.x = element_text(size = fs5_fs),
-    plot.title = element_text(size = fs5_fs)
-  )
+}
 
-# Create the explanation scatterplot: case NM, kernel density
-bullet_es_NM <-
-  plot_explain_scatter(
-    bullet_explain_perms_clean %>% filter(case == "NM", sim_method == "kernel_density"),
-    alpha = 0.75,
-    title.opt = TRUE, 
-    line_size = fs5_ls
-  ) +
-  scale_fill_gradient2(
-    low = "grey50",
-    high = "darkorange",
-    midpoint = 0.5,
-    limits = c(0, 1)
-  ) +
-  theme_bw(base_family = ff, base_size = fs5_fs) +
-  theme(
-    aspect.ratio = 1,
-    strip.background = element_rect(fill = "white", color = "white"),
-    strip.placement = "outside",
-    strip.text.x = element_text(size = fs5_fs), 
-    plot.title = element_text(size = fs5_fs)
-  )
-
-# Join the plots
-plot_grid(bullet_es_M, bullet_es_NM, nrow = 2)
-
-@
+\end{knitrout}
 \caption{Explanation scatterplots for LIME explanations using kernel density simulation for cases M (top) and NM (bottom) of the bullet comparison test data.}

### 2021-01-06 code/01-raw-file-compression.Rmd
updated the code files based on new version of paper

@@
 zip(
-  zipfile = "../figure-static/figure-08-1.png.zip",
-  files =  "../figure-static/figure-08-1.png"
+  zipfile = "../figure-static/figure-06-1.png.zip",
+  files =  "../figure-static/figure-06-1.png"
 )

### 2021-01-06 code/03-submission-steps.Rmd
updated the code files based on new version of paper

@@
     ```{r}
+    # Specify date of submission folder
+    submission_date = "2021-01-06"
+
+    # Create a submission folder file path:
+    submission_folder <- paste0("../submissions/", submission_date)
+
     # Individual files to delete
     file.remove("../data/bullet-explain.rds")
+    file.remove("../data/bullet-explain-perms-clean.rds")
     file.remove("../data/bullet-lime.rds")
@@
     file.remove("../data/example-signatures.csv.zip")
+    file.remove("../data/sine-data-test.rds")
+    file.remove("../data/sine-data-train.rds")
     file.remove("../data/sine-lime-explain.rds")
@@
     file.remove("../data/raw/signatures.rds.zip")
+    file.remove("../figure-static/figure-06-1.eps")
+    file.remove("../figure-static/figure-06-1.png.zip")
     file.remove("../figure-static/figure-08-1.eps")
-    file.remove("../figure-static/figure-08-1.png.zip")
-    file.remove("../figure-static/figure-10-1.eps")
-    file.remove("../figure-static/figure-10-1.png")
+    file.remove("../figure-static/figure-08-1.png")
 
@@
     unlink("../figure", recursive = TRUE)
-    unlink("../submission", recursive = TRUE)
+    unlink(submission_folder, recursive = TRUE)
+    unlink("../support-info/figure", recursive = TRUE)
     ```
@@
 
-5. Run the following code to move all files necessary to the submission folder.
+5. Knit the supporting information document `support-info/supporting-information.Rnw`.
+
+6. Run the following code to move all files necessary to the submission folder.
 
@@
     library(zip)
-
-    # Create a submission folder file path:
-    submission_folder <- "../submission"
 
@@
     file.copy("../WileyNJD-v2.cls", submission_folder)
+
+    # SUPPORTING INFORMATION
+
+    # Copy the supporting information pdf to the submission folder
+    file.copy("../support-info/supporting-information.pdf", submission_folder)
     ```
 
-6.
+7.
 Manually delete `figure/` and `figure-static/` from the figure file paths in `paper.tex`.
@@
 
-7. Compile the file `paper.tex` to make sure it compiles correctly (especially references). (If using texShop, make sure to compile using LaTex, then bibTex, then LaTeX twice more.)
+8. Compile the file `paper.tex` to make sure it compiles correctly (especially references). (If using texShop, make sure to compile using LaTex, then bibTex, then LaTeX twice more.)
 
-8. Besides for `paper.pdf`, delete all other files generated when `paper.tex` was compiled. This includes other paper files and pdf versions of the figures.
+9. Besides for `paper.pdf`, delete all other files generated when `paper.tex` was compiled. This includes other paper files and pdf versions of the figures.
 
@@
 
-9. Upload all remaining files in the submission folder to the ASA Data Science Journal submission page which should be:
+10. Upload all remaining files in the submission folder to the ASA Data Science Journal submission page which should be:
 
   - `code-and-data.zip`
-  - `figure-01-1.eps` through `figure-C3-1.eps`
+  - `figure-01-1.eps` through `figure-B1-1.eps`
   - `paper.pdf`
@@
   - `references.bib`
+  - `supporting-information.pdf`
   - `WileyNJD-AMS.bst`

### 2021-01-06 README.Rmd
working on updating the readme

@@
 
-- information about the files in the repository,
-- instructions for knitting the manuscript,
-- descriptions of the bullet data used in the manuscript, and
-- information on the font sizes used for the figures in the manuscript.
+- [information about the files in the repository](#description-of-items-in-repository),
+- [instructions for knitting the manuscript](#instructions-for-compiling-manuscript),
+- [descriptions of the bullet data used in the manuscript](#additional-information-on-bullet-data), and
+- [information on the font sizes used for the figures in the manuscript](#figure-font-size-information).
 
@@
 
-- [bullet-train.csv.zip](data/bullet-train.csv.zip) and [bullet-test.csv.zip](data/bullet-test.csv.zip) contain the data used for the bullet examples in the manuscript.
-See ""Additional Information on Bullet Data" below for more information about the data.
+- [bullet-rf.rds](data/bullet-rf.rds) contains the saved version of the random forest trained using the bullet matching training data.
+- [bullet-test.csv.zip](data/bullet-test.csv.zip) and [bullet-train.csv.zip](data/bullet-train.csv.zip) contain the data used for the bullet examples in the manuscript.
+See ["Additional Information on Bullet Data"](#additional-information-on-bullet-data) below for more information about the data.
 - [example-signatures.csv.zip](data/example-signatures.csv.zip) contains signature data from two matching bullet lands that is used to generate a figure in the manuscript.
@@
 - [readme.txt](data/readme.txt) contains descriptions of the data files (and code files) provided with the submission of the paper.
+- [sine-data-test.rds](data/sine-data-test.rds) and [sine-data-train.rds](data/sine-data-train.rds) contain saved version of the sine data testing and training sets generated by the code in the manuscript.
+- [sine-lime-explain.rds](data/sine-lime-explain.rds) contains the LIME explanations for the random forest predictions from the sine data test set.
 
@@
 
-- [figure-08-1.png.zip](figure-static/figure-08-1.png.zip) is the one figure in the manuscript that is not generated using R code.
+- [figure-06-1.png.zip](figure-static/figure-06-1.png.zip) is the one figure in the manuscript that is not generated using R code.
 - [figure-readme.png](figure-static/figure-readme.png) is a figure used in this readme.
@@
 
-[**submission**](submission)
+[**submission**](submission/)
 
-Contains the files submitted to the ASA Data Science Journal.
-These files are moved to this folder using code in the file [code/03-submission-steps.R](code/03-submission-steps.Rmd).
+Contains folders with the files submitted to the ASA Data Science Journal.
+The folders within are named by the date of submission.
+The files are moved here using code in the file [code/03-submission-steps.R](code/03-submission-steps.Rmd).
 The only submission files not included on GitHub are the EPS figures due to size constraints.
+
+[**support-info**](support-info/)
+
+Contains the files associated with the manuscript's supporting information document:
+
+- [figures](support-info/figures) contains the figures generated by the supporting information document.
+- [support-info-references.bib](support-info/support-info-references.bib) contains the bibtex information for the references in the supporting information document.
+- [supporting-information.pdf](support-info/supporting-information.pdf) and [supporting-information.Rnw](support-info/supporting-information.Rnw) are the supporting information document.
 
@@
 
+- [.gitattributes](.gitattributes) is needed for GitHub large file storage.
 - [.gitignore](.gitignore) contains objects to be ignored by git.

### 2021-01-06 README.Rmd
fixed typo

@@
   - [signatures.rds.zip](data/raw/signatures.rds.zip): raw version of the example matching signatures data
-- [readme.txt](data/readme.txt) contains descriptions of the data files (and code files) provided with the submission of the paper.
+- [README.txt](data/README.txt) contains descriptions of the data files (and code files) provided with the submission of the paper.
 - [sine-data-test.rds](data/sine-data-test.rds) and [sine-data-train.rds](data/sine-data-train.rds) contain saved version of the sine data testing and training sets generated by the code in the manuscript.

### 2021-01-06 README.Rmd
fixed another typo
finished going through a practice submission with the new paper

@@
 
-- [bullet-rf.rds](data/bullet-rf.rds) contains the saved version of the random forest trained using the bullet matching training data.
 - [bullet-test.csv.zip](data/bullet-test.csv.zip) and [bullet-train.csv.zip](data/bullet-train.csv.zip) contain the data used for the bullet examples in the manuscript.
@@
 - [README.txt](data/README.txt) contains descriptions of the data files (and code files) provided with the submission of the paper.
-- [sine-data-test.rds](data/sine-data-test.rds) and [sine-data-train.rds](data/sine-data-train.rds) contain saved version of the sine data testing and training sets generated by the code in the manuscript.
-- [sine-lime-explain.rds](data/sine-lime-explain.rds) contains the LIME explanations for the random forest predictions from the sine data test set.
 
@@
 
-[**submission**](submission/)
+[**submissions**](submissions/)
 

### 2021-01-06 paper.Rnw
finished going through a practice submission with the new paper

@@
 
-\kge{Additional examples of the visual diagnostics and more info on the bullet matching data may be found in the Supporting Information section of the online version of the manuscript.} The code \sout{used to produce the manuscript} and \sout{the} data \sout{from examples in Section \ref{application}} \kge{associated with the manuscript} are available in the following GitHub Repository: \href{https://github.com/goodekat/LIME-diagnostics-paper}{https://github.com/goodekat/LIME-diagnostics-paper}.
+\kge{Additional examples of the visual diagnostics and more info on the bullet matching data may be found in the Supporting Information section of the online version of the manuscript.} The code \sout{used to produce the manuscript} and \sout{the} data \sout{from examples in Section \ref{application}} \kge{associated with the manuscript} are \kge{also included in the online Supporting Information section and} \sout{available} in the following GitHub Repository: \href{https://github.com/goodekat/LIME-diagnostics-paper}{https://github.com/goodekat/LIME-diagnostics-paper}.
 

### 2021-01-06 paper.Rnw
small edit

--- 2021-01-04 paper.Rnw
@@
 \jnlcitation{
-\cname{\author{Goode K.}, \author{H. Hofmann}},
+\cname{\author{Goode K.}, \author{H. Hofmann}, }
 \cyear{2020},
@@
 \section{Introduction}
+
+<<concept-data, eval = FALSE>>=
+
+# # Simulate example data
+# set.seed(20190624)
+# lime_data <-
+#   data.frame(
+#     feature1 = sort(runif(250, 0, 1)),
+#     feature2 = sample(x = 1:250, size = 250, replace = FALSE)) %>%
+#   mutate(
+#     feature1_stnd = (feature1 - mean(feature1)) / sd(feature1),
+#     feature2_stnd = (feature2 - mean(feature2)) / sd(feature2),
+#     prediction = if_else(feature1 >= 0 & feature1 < 0.1,
+#                          (0.3 * feature1) + rnorm(n(), 0, 0.01),
+#                  if_else(feature1 >= 0.1 & feature1 < 0.3,
+#                          rbeta(n(), 1, 0.5),
+#                  if_else(feature1 >= 0.3 & feature1 < 0.5,
+#                          sin(pi* feature1) + rnorm(n(), 0, 0.5),
+#                  if_else(feature1 >= 0.5 & feature1 < 0.8,
+#                          -(sin(pi* feature1) + rnorm(n(), 0, 0.1)) + 1,
+#                  if_else(feature1 >= 0.8 & feature1 < 0.9,
+#                          0.5 + runif(n(), -0.5, 0.5),
+#                          0.5 + rnorm(n(), 0, 0.3))))))) %>%
+#   bind_rows(
+#     data.frame(feature1 = rep(1, 30) + rnorm(5, 0, 0.05),
+#            feature2 = rep(245, 30) + rnorm(5, 0, 1),
+#            prediction = rep(0, 30) + rnorm(5, 0, 0.05)) %>%
+#   mutate(feature1_stnd = (feature1 - mean(feature1)) / sd(feature1),
+#          feature2_stnd = (feature2 - mean(feature2)) / sd(feature2)))
+# 
+# # Specify a prediction of interest
+# prediction_of_interest <-
+#   data.frame(feature1 = 0.07, feature2 = 200) %>%
+#   mutate(feature1_stnd = (feature1 - mean(lime_data$feature1)) /
+#            sd(lime_data$feature1),
+#          feature2_stnd = (feature2 - mean(lime_data$feature2)) /
+#            sd(lime_data$feature2),
+#          prediction = 0.05,
+#          color = factor("Prediction \nof Interest"))
+# 
+# # Specify the gower exponents
+# good_gower_power <- 50
+# bad_gower_power <- 1
+# 
+# # Compute the good distances between the prediction of interest
+# # and all other observations
+# lime_data$distance_good <-
+#   (1 - gower_dist(x = prediction_of_interest %>%
+#                     select(feature1_stnd, feature2_stnd),
+#                   y = lime_data %>%
+#                     select(feature1_stnd,
+#                            feature2_stnd)))^good_gower_power
+# 
+# # Compute the bad distances between the prediction of interest
+# # and all other observations
+# lime_data$distance_bad <-
+#   (1 - gower_dist(x = prediction_of_interest %>%
+#                     select(feature1_stnd, feature2_stnd),
+#                   y = lime_data %>%
+#                     select(feature1_stnd,
+#                            feature2_stnd)))^bad_gower_power
+# 
+# # Prepare the data for plotting
+# lime_data_gathered <- lime_data %>%
+#   gather(feature, feature_stnd_value,
+#          feature1_stnd:feature2_stnd) %>%
+#   gather(distance, distance_value, distance_good:distance_bad) %>%
+#   mutate(distance = fct_recode(distance,
+#                                "good" = "distance_good",
+#                                "bad" = "distance_bad"),
+#          feature = fct_recode(feature,
+#                               "Feature 1" = "feature1_stnd",
+#                               "Feature 2" = "feature2_stnd"))
+# 
+# # Prepare the prediction of interest data for plotting
+# prediction_of_interest_gathered <- prediction_of_interest %>%
+#   select(-feature1, -feature2) %>%
+#   gather(feature, feature_value, feature1_stnd, feature2_stnd) %>%
+#   mutate(feature = fct_recode(feature,
+#                               "Feature 1" = "feature1_stnd",
+#                               "Feature 2" = "feature2_stnd"))
+
+@
+
+<<concept-explainers, eval = FALSE>>=
+
+# # Fit the good interpretable explainer model
+# explainer_good <-
+#   glmnet(x = lime_data %>% select(feature1_stnd, feature2_stnd)
+#          %>% as.matrix(),
+#          y = lime_data$prediction,
+#          alpha = 0,
+#          lambda = 1,
+#          weights = lime_data$distance_good)
+# 
+# # Fit the bad interpretable explainer model
+# explainer_bad <-
+#   glmnet(x = lime_data %>% select(feature1_stnd, feature2_stnd)
+#          %>% as.matrix(),
+#          y = lime_data$prediction,
+#          alpha = 0,
+#          lambda = 1,
+#          weights = lime_data$distance_bad)
+# 
+# # Join the coefficients from the explainer model into a dataframe
+# coefs_data <- data.frame(case = c("good", "bad"),
+#                          b0 = c(coef(explainer_good)[1],
+#                                 coef(explainer_bad)[1]),
+#                          b1 = c(coef(explainer_good)[2],
+#                                 coef(explainer_bad)[2]),
+#                          b2 = c(coef(explainer_good)[3],
+#                                 coef(explainer_bad)[3])) %>%
+#   mutate(feature1 = b0 + b2*prediction_of_interest$feature2_stnd,
+#          feature2 = b0 + b1*prediction_of_interest$feature1_stnd) %>%
+#   gather(key = feature, value = int, feature1:feature2) %>%
+#   mutate(slope = c(coef(explainer_good)[2],
+#                    coef(explainer_good)[3],
+#                    coef(explainer_bad)[2],
+#                    coef(explainer_bad)[3]),
+#          feature = fct_recode(feature,
+#                               "Feature 1" = "feature1",
+#                               "Feature 2" = "feature2"))
+
+@
 
@@
 
+# # Plot of good explainer model
+# ggplot() +
+#   facet_grid(. ~ feature, switch = "x") +
+#   geom_point(
+#     data = lime_data_gathered %>% mutate(
+#       feature = fct_recode(
+#         feature,
+#         "Feature 1 (standardized)" = "Feature 1",
+#         "Feature 2 (standardized)" = "Feature 2"
+#       )
+#     ),
+#     mapping = aes(
+#       x = feature_stnd_value,
+#       y = prediction,
+#       size = distance_value,
+#       color = distance
+#     ),
+#     alpha = 0.6
+#   ) +
+#   geom_abline(
+#     data = coefs_data %>%
+#       filter(case == "good") %>%
+#       mutate(
+#         feature = fct_recode(
+#           feature,
+#           "Feature 1 (standardized)" = "Feature 1",
+#           "Feature 2 (standardized)" = "Feature 2"
+#           )
+#         ),
+#     mapping = aes(intercept = int, slope = slope),
+#     size = 1
+#   ) +
+#   scale_color_manual(values = c(NA, "grey30"), guide = "none") +
+#   geom_point(
+#     data = prediction_of_interest_gathered %>% mutate(
+#       feature = fct_recode(
+#         feature,
+#         "Feature 1 (standardized)" = "Feature 1",
+#         "Feature 2 (standardized)" = "Feature 2"
+#       )
+#     ),
+#     mapping = aes(x = feature_value,
+#                   y = prediction,
+#                   fill = color),
+#     color = "black",
+#     size = 5,
+#     shape = 23,
+#     alpha = 0.75
+#   ) +
+#   scale_fill_manual(values = "#FAAA72") +
+#   geom_text(
+#     data = data.frame(
+#       feature_stnd_value = 1.2,
+#       prediction = 1.6,
+#       feature = c("Feature 1 (standardized)", "Feature 2 (standardized)"),
+#       slope = c(
+#         paste(
+#           "Slope:",
+#           coefs_data %>%
+#             filter(case == "good",
+#                    feature == "Feature 1") %>%
+#             pull(slope) %>%
+#             round(3)
+#         ),
+#         paste(
+#           "Slope:",
+#           coefs_data %>%
+#             filter(case == "good",
+#                    feature == "Feature 2") %>%
+#             pull(slope) %>%
+#             round(3)
+#         )
+#       )
+#     ),
+#     mapping = aes(x = feature_stnd_value,
+#                   y = prediction,
+#                   label = slope),
+#     family = ff,
+#     size = f1_fs / 2.85
+#   ) +
+#   labs(
+#     x = "",
+#     y = "Black-Box Prediction",
+#     title = "Conceptual Depiction of a Faithful Local Explainer Model",
+#     subtitle = paste("Gower Distance Metric Exponent:", good_gower_power),
+#     fill = "",
+#     alpha = "Weight",
+#     size = "Weight"
+#   ) +
+#   theme_linedraw(base_family = ff, base_size = f1_fs) +
+#   theme(
+#     panel.grid.major = element_blank(),
+#     panel.grid.minor = element_blank(),
+#     axis.text.x = element_blank(),
+#     axis.ticks.x = element_blank(),
+#     axis.text.y = element_blank(),
+#     axis.ticks.y = element_blank(),
+#     strip.placement = "outside",
+#     strip.background = element_rect(color = "white", fill = "white"),
+#     strip.text.x = element_text(size = f1_fs, color = "black"),
+#     plot.title = element_text(size = f1_fs)
+#   ) +
+#   guides(
+#     fill = guide_legend(order = 1),
+#     size = guide_legend(order = 2),
+#     alpha = guide_legend(order = 2)
+#   )
+
 @
@@
 (Left) An example of an explainer model with appropriate weights to provide a faithful approximation of the complex model.
-(Right) An example of an explainer model for the same prediction but with different weights that results in an explanation unfaithful to the complex model.}
+(Right) An example of an explainer model for the same prediction but with different weights that results in an explanation unfaithful to the complex model.
+}
 \label{fig:figure-01}
@@
 Model interpretability allows for the understanding and assessment of how a model produces predictions.
-The lack of the ability to understand and assess a model makes it difficult to trust the model, especially in areas with high stakes decisions such as the medical and forensics sciences.
+The lack of the ability to understand and assess a model makes trusting it difficult, especially in areas with high stakes decisions such as the medical and forensics sciences.
 The increased use of machine learning models in applications and the introduction of the General Data Protection Regulation (GDPR) in 2018 \citep{goodman:2016} has resulted in a dramatic increase in explainable machine learning research, which focuses on developing ways to explain output from machine learning algorithms.
@@
 Throughout this paper, we distinguish between interpretability and explanability of models.
-We define {\it interpretability} as the ability to directly use model parameters to understand the relationships in the data captured by the model: e.g., a linear model coefficient associated with a predictor variable indicates the amount the response variable changes based on a change in the predictor\sout{ variable}.
+We define {\it interpretability} as the ability to directly use model parameters to understand the relationships in the data captured by the model: e.g., a linear model coefficient associated with a predictor variable indicates the amount the response variable changes based on a change in the predictor variable.
 In contrast, we define {\it explanability} as the ability to use the model in an indirect manner to understand the relationships in the data captured by the model: e.g., partial dependence plots depict the marginal relationship between model predictions and predictor variables \citep{friedman:2001}.
@@
 \autoref{fig:figure-01} depicts two plots of the predictions from a hypothetical black-box model versus the feature used to train the model.
-The location of a prediction of interest is indicated by the diamond shaped points.
+The location of a prediction of interest is indicated by the diamonds.
 Globally, there is a clear non-linear relationship between the predictions and the feature, but the relationship could be approximated by a linear model in a local region around the prediction of interest.
@@
 
-On the left, the distance between an observation and the prediction of interest is computed using the Gower distance metric \citep{gower:1971} and then raised to the power of \Sexpr{good_gower_power} to emphasize a very local region.
+On the left, the distance between an observation and the prediction of interest is calculated using the Gower distance metric \citep{gower:1971}  raised to the power of \Sexpr{good_gower_power} to emphasize a very local region.
 The distances are subtracted from 1 to obtain a proximity.
-Here, the explainer model is faithful to the complex model since it captures the linear relationship between the black-box predictions in an immediate neighborhood of the prediction of interest.
-The slope explains that the black-box predictions increase as the feature increases in the local region around the prediction of interest.
-
-For the scenario on the right, the computation of the proximities is the same except the distances are raised to a power of \Sexpr{bad_gower_power} (the default exponent in the \emph{lime} R package \citep{pedersen:2020}).
-This causes the observations that are further away from the prediction of interest to be given larger weights than the scenario on the left.
-Here, the explainer model does not capture the linear trend near the prediction of interest, but instead, \sout{the explainer captures} a more global trend.
-Without an assessment of this explainer model, the slope incorrectly suggests that the predictions decrease as the feature increases near the prediction of interest.
+Here, the explainer model is faithful to the complex model since it captures the linear relationship between the black-box predictions in an immediate neighborhood of the prediction of interest: with an increase in the feature the black-box predictions increase in a local region around the prediction of interest.
+
+For the scenario on the right, the computation of the proximities is the same except that distances are raised to a power of \Sexpr{bad_gower_power} (the default exponent in the \emph{lime} R package \citep{pedersen:2020}).
+This difference gives larger weights to observations that are further away from the prediction of interest than the scenario on the left.
+Instead of capturing a local trend, the slope in the explainer model describes a more global trend.
+Here, the explainer model incorrectly suggests, that a decrease in prediction values as the feature increases near the prediction of interest.
+%\sout{This cannot be said of the explainer model in \autoref{fig:figure-02}.
+In addition, the magnitude of the slope associated with Feature 2  (\Sexpr{coefs_data %>% filter(case == "bad", feature == "Feature 2") %>% pull(b1) %>% round(3) %>% abs()}) is larger than that of Feature 1 (\Sexpr{coefs_data %>% filter(case == "bad", feature == "Feature 1") %>% pull(b1) %>% round(3) %>% abs()}).
+Thus, this explainer model actually provides a misleading explanation that Feature 2 plays a more important role in the prediction of interest.}
+
+%\kge{To demonstrate the effect of tuning parameters on LIME,we consider two different explainer models applied to the same prediction.
+Suppose a hypothetical black-box model is trained using one feature.
+Both plots in Figure1show the black-box model predictions versus the feature used to train the model.The diamond shaped point in the plots indicates the location of the prediction of interest to explain.
+A weight ridge regression with the black-box predictions as the response variable and standardized versions the features as predictor variables will be used as the explainer model in both scenarios, but the weights will vary.
+Note that the standardized features allow for direct comparisons of the model coefficients.}
 
 \autoref{fig:figure-01} demonstrates a simple example in which the explanation quality varies drastically when different weights are used.
-Other concerns \sout{with} LIME have been raised in the literature: \citet{laugel:2018} and \citet{molnar:2019} discuss the difficulty specifying a local region with LIME due to both an unclear definition of \sout{what is} a "local region" and how to apply LIME to achieve an appropriate local region.
+Other concerns with LIME have been raised in the literature: \citet{laugel:2018} and \citet{molnar:2019} discuss the difficulty specifying a local region with LIME due to both  an unclear definition of what a "local region" is and, secondly, how to achieve an appropriate local region in LIME.
 \citet{laugel:2018} also present examples of LIME explanations that are clearly global and not local.
@@
 
-Without an assessment of the LIME explainer model, the user is putting trust in another black-box \kge{algorithm} \sout{procedure} to explain the complex black-box model.
+ Without an assessment of the LIME explainer model, the user has to put trust in yet another black-box procedure to explain the complex black-box model.
 In this paper, we stress the importance of assessing the LIME explainer model.
-To do this, we lay out the set of claims about LIME made by \citet{ribeiro:2016}, and we provide a toolkit of visual diagnostics  for the assessment of these claims: (1) \emph{explanation scatterplots}, (2) \emph{feature heatmaps}, (3) \emph{assessment metric plots}.
+\hh{XXX This is where the paragraph has to go XXX} To do this, we lay out the set of claims about LIME made by \citet{ribeiro:2016}, and we provide a toolkit of visual diagnostics  for the assessment of these claims: (1) \emph{explanation scatterplots}, (2) \emph{feature heatmaps}, (3) \emph{assessment metric plots}.
 Using these visual diagnostics, we demonstrate problematic examples of LIME explanations where the claims about LIME are not met and the explanations are highly dependent on tuning parameter values without a clear way to identify a set of tuning parameter values that produce the "best" explanations.
@@
 \citet{ribeiro:2016} provide an implementation of LIME in a Python package \cite{ribeiro:2020}.
-An adaption of the Python package in R has been implemented and made available by \citet{pedersen:2020}.
-In both implementations, a ridge regression model is used as the explainer model, and the user \sout{is asked to} select\kge{s} various tuning parameter options: the number of features to return in the explanation, the simulation method, the feature selection method, and how the weights are computed.
-\sout{The discussion of parameter choices and implementation details of LIME in this paper are based on the R package.} See Appendix~\ref{lime-details} for an overview of the options available for the tuning parameters \kge{based on the R package}.
+An adaption of the Python package in R has been implemented and made available by Thomas Lin-Pedersen \citep{pedersen:2020}.
+In both implementations, a ridge regression model is used as the explainer model, and  the user is asked to select various tuning parameter options: the number of features to return in the explanation, the simulation method, the feature selection method, and how the weights are computed.
+The discussion of parameter choices and implementation details of LIME in this paper are based on the R package.
+See Appendix~\ref{lime-details} for
+an overview of the options available for the tuning parameters.
 
@@
   rename(rfprob_blue = blue, rfprob_red = red)
-
-# Save the training and testing data
-if(!file.exists("data/sine-data-train.rds")) saveRDS(sine_data_train, "data/sine-data-train.rds")
-if(!file.exists("data/sine-data-test.rds")) saveRDS(sine_data_test, "data/sine-data-test.rds")
 
@@
 \caption{Plots of $x_2$ versus $x_1$ from the \data \  training (left) and testing (right) sets introduced in Section \ref{diagnostics}  with the true classification boundary  shown as a solid black line.
-In the testing set, the open black circles identify cases misclassified by the random forest, and the diamond indicates a prediction of interest.}
+In the testing set, the open black circles identify cases misclassified by the random forest, and the diamond indicates a prediction of interest.
+}
 \label{fig:figure-02}
@@
 @
-\caption{(Left) Visualization from the \emph{lime} R package of a LIME explanation for the \data \ prediction of interest identified in \autoref{fig:figure-02}.
-(Right) \emph{Explanation Scatterplot}.
+\caption{(left) Visualization from the \emph{lime} R package of a LIME explanation for the \data \ prediction of interest identified in \autoref{fig:figure-02}.
+(right) \emph{Explanation Scatterplot}.
 An explanation scatterplot associated with the explanation  on the left.
-The four quantile bins over-simplify the relationship between the random forest predictions and the $x_1$ and $x_2$ values near the prediction of interest.}
+The four quantile bins over-simplify
+the relationship between the random forest predictions and the $x_1$ and $x_2$ values near the prediction of interest.}
 \label{fig:figure-03}
@@
 \end{eqnarray}
-where $x'_1=x_1\cos(\theta)-x_2\sin(\theta)$,  $x'_2=x_1\sin(\theta)+x_2\cos(\theta)$, and  $\theta=-0.9$.
+where $x'_1=x_1\cos(\theta)-x_2\sin(\theta)$,  $x'_2=x_1\sin(\theta)+x_2\cos(\theta)$, and  $\theta=-0.9$. \sout{Then $y$ is defined as
+\begin{eqnarray}\label{eq:data}
+  y=\begin{cases}
+  \mbox{blue} & \mbox{ if } x'_2 > \sin\left(x'_1\right) \\
+  \mbox{red} & \mbox{ if } x'_2 \le \sin\left(x'_1\right) \ .
+  \end{cases}
+\end{eqnarray}}
 Note that due to the creation of $y$ in this manner, $y$ is dependent on $x_1$ and $x_2$ and independent of $x_3$.
@@
 
-\sout{Since 4-quantile-bins} \kge{When quantile bins} are used to simulate data, LIME converts continuous predictor variables to indicator variables identifying whether the variable value falls in the same quantile bin as the prediction of interest or not.
+Since 4-quantile-bins are used to simulate data, LIME converts continuous predictor variables to indicator variables identifying whether the variable value falls in the same quantile bin as the prediction of interest or not.
 The indicator variables are used as the features in the ridge regression explainer model.
@@
 This explainer model suggests that a random forest prediction of `blue' for this observation is mostly supported by the prediction of interest having a value of $x_2$ that is greater than \Sexpr{str_split(sine_poi_lime_default$feature_desc[[1]], pattern = " ")[[1]][1]} but somewhat contradicted by the prediction of interest having a value of $x_1$ that is greater than \Sexpr{str_split(sine_poi_lime_default$feature_desc[[2]], pattern = " ")[[1]][1]} and less than or equal to \Sexpr{str_split(sine_poi_lime_default$feature_desc[[2]], pattern = " ")[[1]][5]}.
-%\kgc{I decided to leave the values here.
+\kgc{I decided to leave the values here.
 I actually prefer it this way myself, but I cut out a lot of text from this subsection in other ways.}\hh{XXX }
@@
 We introduce the explanation scatterplot here under the \emph{lime} R package default method of 4-quantile-bins.
-\kge{See the supporting information for} \sout{Appendix \ref{exp-scatter_plus} addresses the} explanation scatterplot formats \kge{under} \sout{in} other LIME simulation scenarios.
+Appendix \ref{exp-scatter_plus} addresses the explanation scatterplot formats in other LIME simulation scenarios.
 
 The explanation scatterplot applies the concept of plotting the model in the data space discussed in \citet{wickham:2015}.
-The \kge{visualization} \sout{plot} is built by plotting the LIME simulated data for the top two features identified by the explanation in a scatterplot and coloring these points by the predictions from the complex model.
+The plot is built by plotting the LIME simulated data for the top two features identified by the explanation in a scatterplot and coloring these points by the predictions from the complex model.
 The point size represents the weight assigned by LIME.
@@
 First, consider the claim of localness.
-The weights decay relatively slowly outside of the intersection of the \kge{two quantile bins} \sout{2-quantile-bin} suggesting that the LIME explanation is highly influenced by points outside of the bins containing the prediction of interest.
+The weights decay relatively slowly outside of the intersection of the 2-quantile-bin suggesting that the LIME explanation is highly influenced by points outside of the bins containing the prediction of interest.
 However, it is difficult to say if the claim of localness has been violated, because a definition of a local region is not specified.
 Depending on what region a viewer considers to be local, an argument could be made in favor of or against a violation of localness.
-\sout{The explanation scatterplot raises awareness of the unclear definition of a local region with LIME.
-Nevertheless, it is possible to say that the weights assigned to the simulated data do not capture the local region identified by the intersection of the quantile bins.}
-
-Now, consider the claim of faithfulness: It can be said that the majority of the points in the $x_2$ quantile \kge{bin} support a prediction of blue, which is captured by the bar supporting a prediction of blue in the LIME explanation, and a similar statement can be made about the $x_1$ quantile-bin.
+The explanation scatterplot raises awareness of the unclear definition of a local region with LIME.
+Nevertheless, it is possible to say that the weights assigned to the simulated data do not capture  the local region identified by the intersection of the quantile bins.
+
+Now, consider the claim of faithfulness: It can be said that the majority of the points in the $x_2$ quantile support a prediction of blue, which is captured by the bar supporting a prediction of blue in the LIME explanation, and a similar statement can be made about the $x_1$ quantile-bin.
 These statements validate the explanation produced by LIME.
@@
 
-This example explanation \kge{scatterplot} only includes two features.
+This example explanation only includes two features.
 In situations where more than two features are included in a LIME explanation, the explanation scatterplots can be extended to a generalized pairs plot \citep{emerson:2013} that includes all pairwise combinations of features.
@@
 Vertical lines of color represent explanations that are dependent on the tuning parameter values and may not be local since the same feature is chosen regardless of the location of the observation in the feature space.
-See \kge{the supporting information} \sout{Appendix \ref{feat-heat-ex}} for hypothetical examples depicting \kge{the extreme cases of} feature heatmaps\kge{.} \sout{with the extreme cases of horizontal and vertical lines.}
+See Appendix \ref{feat-heat-ex} for hypothetical examples depicting feature heatmaps with the extreme cases of horizontal and vertical lines.
 
@@
 @
-\caption{Example bullet signatures. The signatures are from the same land and therefore have very similar patterns.}
+\caption{Example bullet signatures. The  signatures are from  the same land and therefore have very similar patterns. }
 \label{fig:figure-07}
@@
 Plots for 4-equal-bins and 4-quantile-bins are included to depict tuning parameter values with good (4-equal-bins) and mediocre (4-quantile-bins) performance based on the assessment metric plot.
-\kge{Additional examples of explanation scatterplots including explanations for a known match and explanation produced using the kernel density simulation method are included in the  the supporting information.} \sout{Explanation scatterplots for a known match, referred to as case M, and for the kernel density simulation method applied to both M and NM are included in Appendix~\ref{bullets-plus}.}
+%\kge{Also, recall that 4-quantile-bins are the default option in the \emph{lime} R package.}
+Explanation scatterplots for a known match, referred to as case M, and for the kernel density simulation method applied to both M and NM are included in Appendix~\ref{bullets-plus}.
 
@@
 \begin{figure*}[!thp]
-<<figure-11, out.width = '6.25in', fig.width = 13, fig.height = 9, message = FALSE>>=
+<<figure-11, out.width = '6.25in', fig.width = 13, fig.height = 8.5, message = FALSE>>=
 
@@
   mutate(case = ifelse(case == bullet_poi_nonmatch, "NM", "M"))
-
-# Save the cleaned explanations to use with the supporting information
-if(!file.exists("data/bullet-explain-perms-clean.rds")) {
- saveRDS(bullet_explain_perms_clean, "data/bullet-explain-perms-clean.rds") 
-}
 
@@
 @
-\caption{Plots of LIME explanations (first row) and explanation scatterplots (second row) for case NM in the bullet test data for two tuning parameter values: 4-quantile-bins (first column) and 4-equal-bins (second column).}
+\caption{Plots of LIME explanations (first row) and explanation scatterplots (second row) for case NM in the bullet test data for two tuning parameter values: 4-quantile-bins (first column) and 4-equal-bins (second column).
+}
 \label{fig:figure-11}
@@
 As previously discussed, the \textbf{interpretability} of the LIME explanations is controllable  by the complexity of the explainer model.
-For example, the number of bins selected for simulation controls the interpretability of the explanations.
+For example, the number of bins selected for simulation can control the interpretability of the explanations.
 If too many bins are selected, the bin range that is reported in the LIME explanation will be too small to be meaningful in the context of the feature.
@@
 Most of the average $R^2$ values in the examples from this paper are below 0.5 suggesting a poor linear fit of the explainer models.
-A poor linear fit of the explainer model is also seen with the residual plot shown in \autoref{fig:figure-B1}.
+A poor linear fit of the explainer model is also seen with the residual plot shown in \autoref{fig:figure-C2}.
 
@@
 While it would be ideal if LIME could be used as a method to provide easily understandable explanations for black-box models as \citet{ribeiro:2016} claim, that dream is not yet a reality.
-The examples using diagnostic plots to assess LIME in this paper show frequent instances when the claims about LIME are not met.
-We hope that our plots provide motivation to assess LIME explanations, to not blindly use the default settings (even if how to tune the parameters is not clear), and to encourage work improving LIME, so that it can be a lime and not a lemon.
+The examples using diagnostic plots to assess LIME in this paper show frequent instances when the claims about LIME are not met .
+We hope that our plots provide motivation to assess LIME explanations, to not blindly use the default settings (even if it is not clear how to tune the parameters), and to encourage work  improving LIME, so that it can be a lime and not a lemon.
 
@@
 
-\kge{Additional example visual diagnostics may be found online in the Supporting Information section at the end of this manuscript.} The code used to produce the manuscript and the data from examples in Section \ref{application} are available in the following GitHub Repository: \href{https://github.com/goodekat/LIME-diagnostics-paper}{https://github.com/goodekat/LIME-diagnostics-paper}.
+The code used to produce the manuscript and the data from examples in Section \ref{application} are available in the following GitHub Repository: \href{https://github.com/goodekat/LIME-diagnostics-paper}{https://github.com/goodekat/LIME-diagnostics-paper}.
 
@@
 
-\section{Explainer Model Residual Plot} \label{residual-plot}
-\begin{figure}[!h]
-<<figure-B1, out.width = '3.125in', fig.width = 5, fig.height = 4, warning = FALSE>>=
+\begin{figure*}[!thp]
+<<figure-B1, out.width = '6.5in', fig.width = 12, fig.height = 5, fig.align = "center">>=
 
 # Specify the figure size (for determining font size and line size)
-fb1_ow = 3.125
-fb1_fw = 5
+fb1_ow = 6.5
+fb1_fw = 12
 fb1_fs = fs * (fb1_fw / fb1_ow)
 fb1_ls = 0.5 * (fb1_fw / fb1_ow)
+
+# Create the explanation scatterplot
+plot_explain_scatter(
+  sine_lime_explain$explain %>%
+    filter(sim_method == "kernel_density", case == sine_poi %>% pull(case)),
+  alpha = 0.75,
+  title.opt = FALSE, 
+  line_size = fb1_ls 
+) +
+  theme_bw(base_family = ff, base_size = fb1_fs) +
+  theme(
+    strip.background = element_rect(fill = "white", color = "white"),
+    strip.placement = "outside",
+    strip.text.x = element_text(size = fb1_fs)
+  )
+
+@
+\caption{Explanation scatterplots for the \data \ prediction of interest with the kernel density simulation method.}
+\label{fig:figure-B1}
+\end{figure*}
+
+\section{Explanation Scatterplots Under  Density Simulation Scenarios} \label{exp-scatter_plus}
+
+Section \ref{exp-scatter} introduces explanation scatterplots under the default simulation method in the \emph{lime} R package: 4-quantile-bins.
+The structure of an explanation scatterplot remains the same if any bin based simulation method is used, i.e., any number of quantile or equally spaced bins.
+However, if the kernel density or normal approximation simulation methods are used, the format of the explanation scatterplot changes.
+In the density based simulation method scenarios, LIME uses the standardized versions of the predictor variables to fit the explainer model.
+Thus, the explainer model needs to be represented differently in the explanation scatterplot.
+
+When the kernel density or normal approximation simulation methods are applied, the explanation scatterplot depicts the complex model by plotting the complex model predictions versus a feature selected in LIME the explanation from the simulated data.
+The explainer model is included as a line on the figure where all features excluding the one plotted on the x-axis are set to the observed values of the prediction of interest.
+An explanation scatterplot is created for each feature included in the LIME explanation.
+As with the bin based simulation method, the size of the points represent the weight assigned by LIME.
+
+\autoref{fig:figure-B1} provides example explanation scatterplots for the \data \ prediction of interest when the kernel density simulation method is used.
+The plots show the relationships between the random forest prediction and the selected features of $x_1$ and $x_2$ on the left and right, respectively.
+
+\section{Explainer Model Residual Plot} \label{residual-plot}
+\begin{figure}[!b]
+<<figure-C2, out.width = '3.125in', fig.width = 5, fig.height = 4, warning = FALSE>>=
+
+# Specify the figure size (for determining font size and line size)
+fc2_ow = 3.125
+fc2_fw = 5
+fc2_fs = fs * (fc2_fw / fc2_ow)
+fc2_ls = 0.5 * (fc2_fw / fc2_ow)
 
@@
 ggplot(sine_poi_perms, aes(x = exppred, y = resid)) +
-  geom_hline(yintercept = 0, size = fb1_ls) +
+  geom_hline(yintercept = 0, size = fc2_ls) +
   geom_jitter(alpha = 0.5, width = 0.02) +
-  theme_bw(base_family = ff, base_size = fb1_fs) +
-  theme(plot.title = element_text(size = fb1_fs)) +
+  theme_bw(base_family = ff, base_size = fc2_fs) +
+  theme(plot.title = element_text(size = fc2_fs)) +
   labs(x = "Explainer Model Predictions",
@@
 \caption{Residual plot of the explainer model associated with \data \ prediction of interest from Section \ref{exp-scatter}, which suggests a violation of the linearity assumption.}
-\label{fig:figure-B1}
+\label{fig:figure-C2}
 \end{figure}
@@
 In order to assess the claim of linearity for the \data \ prediction of interest discussed in Section \ref{exp-scatter}, we use one of the most basic diagnostics in a statistician's tool box and draw a residual plot for the explainer model.
-This is shown in \autoref{fig:figure-B1} with the explainer model residuals on the y-axis and explainer model predictions on the x-axis.
+This is shown in \autoref{fig:figure-C2} with the explainer model residuals on the y-axis and explainer model predictions on the x-axis.
 The points along the x-axis have been jittered to ease the effect of the over-plotted points.
 There is a clear increasing trend in the residuals as the explainer model predictions increase, which indicates a violation of the ridge regression linearity assumption.
+
+\section{Extreme Feature Heatmap Scenarios} \label{feat-heat-ex}
+
+Two hypothetical examples of feature heatmaps are included in \autoref{fig:figure-D3}.
+The plots are created with the assumption that LIME is applied to select the top feature out of $p=4$  features for $n=10$ cases with $t=5$ sets of tuning parameter values.
+Situation 1 is an example where the features selected are consistent across tuning parameter values within a case but vary across cases within a tuning parameter value.
+This is the ideal situation, because the LIME explanations do not depend on the tuning parameters but do depend on the location of the observation in the feature space.
+Situation 2 is an example where the selected features vary across tuning parameter values within a case but are consistent across cases within a tuning parameter value.
+This situation indicates that the features selected by LIME are dependent on the tuning parameters, and the explanations may not be  local, because the same feature is chosen regardless of the case.
+In practice, it is expected that the plot will exhibit a combination of these two situations.
+
+\begin{figure}[!t]
+<<figure-D3, out.width = '3.125in', fig.width = 6, fig.height = 3>>=
+
+# Specify the figure size (for determining font size)
+fd3_ow = 3.125
+fd3_fw = 6
+fd3_fs = fs * (fd3_fw / fd3_ow)
+
+# Specify the number of cases and LIME input options
+ncases = 10
+ninputs = 5
+
+# Create a good case of chosen feature example data
+set.seed(20191008)
+heatmap_data_good <-
+  tibble(
+    case = factor(rep(1:ncases, each = ninputs),
+                  levels = ncases:1),
+    input = factor(rep(1:ninputs, ncases)),
+    feature = factor(c(
+      rep(1, 5),
+      rep(2, 5),
+      rep(3, 5),
+      rep(1, 5),
+      rep(1, 5),
+      rep(4, 5),
+      rep(1, 5),
+      rep(3, 5),
+      rep(1, 5),
+      rep(4, 5)
+    ))
+  ) %>%
+  mutate(input = forcats::fct_recode(
+    input,
+    "A" = "1",
+    "B" = "2",
+    "C" = "3",
+    "D" = "4",
+    "E" = "5"
+  ))
+
+# Create the conceptual good heatmap
+heatmap_plot_good <- ggplot(data = heatmap_data_good,
+                            mapping = aes(
+                              x = input,
+                              y = case,
+                              fill = feature,
+                              color = feature
+                            )) +
+  geom_tile() +
+  labs(
+    x = "Tuning Parameter Value",
+    y = "Case",
+    fill = "Feature",
+    color = "Feature",
+    title = "Situation 1",
+    subtitle = "Consistent Explanations"
+  ) +
+  theme_bw(base_family = ff, base_size = fd3_fs) +
+  scale_fill_grey() +
+  scale_color_grey() +
+  theme(legend.position = "none", 
+        plot.title = element_text(size = fd3_fs))
+
+# Create a bad case of chosen feature example data
+set.seed(20190627)
+heatmap_data_bad <- tibble(
+  case = factor(rep(1:ncases, ninputs),
+                levels = ncases:1),
+  input = factor(rep(1:ninputs, each = ncases)),
+  feature = factor(rep(c(1, 2, 4, 3, 2), each = 10))
+) %>%
+  mutate(input = forcats::fct_recode(
+    input,
+    "A" = "1",
+    "B" = "2",
+    "C" = "3",
+    "D" = "4",
+    "E" = "5"
+  ))
+
+# Create the conceptual bad heat map
+heatmap_plot_bad <- ggplot(data = heatmap_data_bad,
+                           mapping = aes(
+                             x = input,
+                             y = case,
+                             fill = feature,
+                             color = feature
+                           )) +
+  geom_tile() +
+  labs(
+    x = "Tuning Parameter Value",
+    y = "Case",
+    fill = "Feature",
+    color = "Feature",
+    title = "Situation 2",
+    subtitle = "Inconsistent Explanations"
+  ) +
+  theme_bw(base_family = ff, base_size = fd3_fs) +
+  theme(plot.title = element_text(size = fd3_fs)) +
+  scale_fill_grey() +
+  scale_color_grey()
+
+heatmap_leg <- get_legend(heatmap_plot_bad)
+heatmap_plot_bad <-
+  heatmap_plot_bad + theme(legend.position = 'none')
+
+# Join the plots
+plot_grid(
+  heatmap_plot_good,
+  heatmap_plot_bad,
+  heatmap_leg,
+  nrow = 1,
+  rel_widths = c(0.43, 0.43, 0.14)
+)
+
+@
+\caption{Hypothetical examples of feature heatmaps in two possible situations.
+Situation 1 is the ideal, because the explanations vary across cases but do not dependent on specific tuning parameter values.
+Situation 2 suggests global explanations and extreme explanation dependence on the tuning parameter values.}
+\label{fig:figure-D3}
+\end{figure}
 
@@
 
+\section{Additional Bullet Matching Explanation Scatterplots} \label{bullets-plus}
+
+\autoref{fig:figure-F4} includes visual representations of LIME explanation from the \emph{lime} R package and explanation scatterplots for a known match observation in the the bullet example referred to as cases M for two different data simulation methods: 4-quantile-bins (left column) and 4-equal-bins (right column).
+Both explanations appear to be more faithful to the random forest than those associated with case NM in Section \ref{bullet-assess-ex}, but the intersections of the bins could be better aligned with the regions containing similar probabilities produced by the random forest.
+\autoref{fig:figure-F5} includes explanation scatterplots for bullet example cases M and NM when the kernel density simulation method is used.
+
+\begin{figure*}[!t]
+<<figure-F4, out.width = '6.25in', fig.width = 13, fig.height = 8.5, message = FALSE>>=
+
+# Specify the figure size (for determining font size)
+ff4_ow = 6.25
+ff4_fw = 13
+ff4_fs = fs * (ff4_fw / ff4_ow)
+ff4_ls = 0.5 * (ff4_fw / ff4_ow)
+
+# Create the lime explanation visualizations
+pfM_3qb <- plot_features(bullet_explain_perms_clean[1:3,]) + bullet_explain_plot_theme
+pfM_3eb <- plot_features(bullet_explain_perms_clean[7:9,]) + bullet_explain_plot_theme
+
+# Create the explanation scatterplots
+eoiM_3qb <-
+  plot_explain_scatter(
+    bullet_explain_perms_clean[1:3, ],
+    alpha = 0.9,
+    weights = TRUE,
+    line_size = ff4_ls
+  ) +
+  bullet_eoi_plot_theme +
+  guides(linetype = guide_legend(override.aes = list(color = c("darkorange"))))
+eoiM_3eb <-
+  plot_explain_scatter(
+    bullet_explain_perms_clean[7:9, ],
+    alpha = 0.9,
+    weights = TRUE,
+    line_size = ff4_ls
+  ) +
+  bullet_eoi_plot_theme + 
+  guides(linetype = guide_legend(override.aes = list(color = c("darkorange"))))
+
+# Join the plots
+plot_grid(
+  pfM_3qb,
+  pfM_3eb,
+  eoiM_3qb,
+  eoiM_3eb,
+  nrow = 2,
+  rel_heights = c(0.2, 0.3)
+)
+
+@
+\caption{Plots of LIME explanations (first row) and explanation scatterplots (second row) for case M in the bullet test data for two tuning parameter values: 4-quantile-bins (first column) and 4-equal-bins (second column).}
+\label{fig:figure-F4}
+\end{figure*}
+
+\begin{figure*}[!thp]
+<<figure-F5, out.width = '6.5in', fig.width = 12, fig.height = 10, fig.align = "center">>=
+
+# Specify the figure size (for determining font size and line size)
+ff5_ow = 6.5
+ff5_fw = 12
+ff5_fs = fs * (ff5_fw / ff5_ow)
+ff5_ls = 0.5 * (ff5_fw / ff5_ow)
+
+# Create the explanation scatterplot: case M, kernel density
+bullet_es_M <-
+  plot_explain_scatter(
+    bullet_explain_perms[16:18, ] %>% mutate(case = "NM"),
+    alpha = 0.75,
+    title.opt = TRUE,
+    line_size = ff5_ls
+  ) +
+  scale_fill_gradient2(
+    low = "grey50",
+    high = "darkorange",
+    midpoint = 0.5,
+    limits = c(0, 1)
+  ) +
+  theme_bw(base_family = ff, base_size = ff5_fs) +
+  theme(
+    aspect.ratio = 1,
+    strip.background = element_rect(fill = "white", color = "white"),
+    strip.placement = "outside",
+    strip.text.x = element_text(size = ff5_fs),
+    plot.title = element_text(size = ff5_fs)
+  )
+
+# Create the explanation scatterplot: case NM, kernel density
+bullet_es_NM <-
+  plot_explain_scatter(
+    bullet_explain_perms[13:15, ] %>% mutate(case = "M"),
+    alpha = 0.75,
+    title.opt = TRUE, 
+    line_size = ff5_ls
+  ) +
+  scale_fill_gradient2(
+    low = "grey50",
+    high = "darkorange",
+    midpoint = 0.5,
+    limits = c(0, 1)
+  ) +
+  theme_bw(base_family = ff, base_size = ff5_fs) +
+  theme(
+    aspect.ratio = 1,
+    strip.background = element_rect(fill = "white", color = "white"),
+    strip.placement = "outside",
+    strip.text.x = element_text(size = ff5_fs), 
+    plot.title = element_text(size = ff5_fs)
+  )
+
+# Join the plots
+plot_grid(bullet_es_M, bullet_es_NM, nrow = 2)
+
+@
+\caption{Explanation scatterplots for LIME explanations using kernel density simulation for the cases M and NM of the bullet comparison test data.}
+\label{fig:figure-F5}
+\end{figure*}
+
 \end{document}

### 2021-01-06 README.Rmd
removed supporting figures file

@@
 
-- [figures](support-info/figures) contains the figures generated by the supporting information document.
 - [support-info-references.bib](support-info/support-info-references.bib) contains the bibtex information for the references in the supporting information document.
@@
 The data used in the manuscript for the bullet comparison examples is described below.
-Note that this text is also included in the file [data/readme.txt](data/readme.txt) that is submitted with the manuscript.
+Note that this text is also included in the manuscript supporting information and the file [data/README.txt](data/README.txt) that is submitted with the manuscript.
 

### 2021-01-06 code/03-submission-steps.Rmd

@@
 7.
-Manually delete `figure/` and `figure-static/` from the figure file paths in `paper.tex`.
+Manually delete `figure/` and `figure-static/` from the figure file paths in the submissions folder `paper.tex`.
 For example, change `\includegraphics[width=6.5in]{figure/figure-01-1}` to `\includegraphics[width=6.5in]{figure-01-1}`.
 
-8. Compile the file `paper.tex` to make sure it compiles correctly (especially references). (If using texShop, make sure to compile using LaTex, then bibTex, then LaTeX twice more.)
+8.
+Compile the file in the submissions folder `paper.tex` to make sure it compiles correctly (especially references).
+(If using texShop, make sure to compile using LaTex, then bibTex, then LaTeX twice more.)
 
@@
     # Remove the paper files that may have been generated during compilation
-    file.remove("../submission/paper.aux")
-    file.remove("../submission/paper.bbl")
-    file.remove("../submission/paper.blg")
-    file.remove("../submission/paper.log")
-    file.remove("../submission/paper.synctex.gz")
-    file.remove("../submission/paper.pag")
+    file.remove(paste0(submission_folder, "/paper.aux"))
+    file.remove(paste0(submission_folder, "/paper.bbl"))
+    file.remove(paste0(submission_folder, "/paper.blg"))
+    file.remove(paste0(submission_folder, "/paper.log"))
+    file.remove(paste0(submission_folder, "/paper.synctex.gz"))
+    file.remove(paste0(submission_folder, "/paper.pag"))
 
@@
     file.remove(list.files(
-      path = "../submission/",
+      path = submission_folder,
       pattern = "converted-to",

### 2021-01-06 paper.Rnw

--- 2021-01-06 paper.Rnw
@@
 Throughout this paper, we distinguish between interpretability and explanability of models.
-We define {\it interpretability} as the ability to directly use model parameters to understand the relationships in the data captured by the model: e.g., a linear model coefficient associated with a predictor variable indicates the amount the response variable changes based on a change in the predictor\sout{ variable}.
+We define {\it interpretability} as the ability to directly use model parameters to understand the relationships in the data captured by the model: e.g., a linear model coefficient associated with a predictor variable indicates the amount the response variable changes based on a change in the predictor.
 In contrast, we define {\it explanability} as the ability to use the model in an indirect manner to understand the relationships in the data captured by the model: e.g., partial dependence plots depict the marginal relationship between model predictions and predictor variables \citep{friedman:2001}.
@@
 This causes the observations that are further away from the prediction of interest to be given larger weights than the scenario on the left.
-Here, the explainer model does not capture the linear trend near the prediction of interest, but instead, \sout{the explainer captures} a more global trend.
+Here, the explainer model does not capture the linear trend near the prediction of interest, but instead,  a more global trend.
 Without an assessment of this explainer model, the slope incorrectly suggests that the predictions decrease as the feature increases near the prediction of interest.
@@
 
-Without an assessment of the LIME explainer model, the user is putting trust in another black-box \kge{algorithm} \sout{procedure} to explain the complex black-box model.
+Without an assessment of the LIME explainer model, the user is putting trust in another black-box algorithm to explain the complex black-box model.
 In this paper, we stress the importance of assessing the LIME explainer model.
 To do this, we lay out the set of claims about LIME made by \citet{ribeiro:2016}, and we provide a toolkit of visual diagnostics  for the assessment of these claims: (1) \emph{explanation scatterplots}, (2) \emph{feature heatmaps}, (3) \emph{assessment metric plots}.
-Using these visual diagnostics, we demonstrate problematic examples of LIME explanations where the claims about LIME are not met and the explanations are highly dependent on tuning parameter values without a clear way to identify a set of tuning parameter values that produce the "best" explanations.
+XXX Using these visual diagnostics, we demonstrate problematic examples of LIME explanations where the claims about LIME are not met and the explanations are highly dependent on tuning parameter values without a clear way to identify a set of tuning parameter values that produce the "best" explanations.
 

### 2021-01-06 paper.Rnw
small edits

@@
 \autoref{fig:figure-01} demonstrates a simple example in which the explanation quality varies drastically when different weights are used.
-Other concerns \sout{with} LIME have been raised in the literature: \citet{laugel:2018} and \citet{molnar:2019} discuss the difficulty specifying a local region with LIME due to both an unclear definition of \sout{what is} a "local region" and how to apply LIME to achieve an appropriate local region.
+Other concerns  LIME have been raised in the literature: \citet{laugel:2018} and \citet{molnar:2019} discuss the difficulty specifying a local region with LIME due to both an unclear definition of  a "local region" and how to apply LIME to achieve an appropriate local region.
 \citet{laugel:2018} also present examples of LIME explanations that are clearly global and not local.
@@
 To do this, we lay out the set of claims about LIME made by \citet{ribeiro:2016}, and we provide a toolkit of visual diagnostics  for the assessment of these claims: (1) \emph{explanation scatterplots}, (2) \emph{feature heatmaps}, (3) \emph{assessment metric plots}.
-XXX Using these visual diagnostics, we demonstrate problematic examples of LIME explanations where the claims about LIME are not met and the explanations are highly dependent on tuning parameter values without a clear way to identify a set of tuning parameter values that produce the "best" explanations.
+Using these visual diagnostics, we \hh{identify situations in which LIME does not meet its claims.
+In some simple examples, we  demonstrate shortfalls in LIME explanations where} the explanations are highly dependent on tuning parameter values without a clear way to identify a set of tuning parameter values that produce the "best" explanations.
 
@@
 An adaption of the Python package in R has been implemented and made available by \citet{pedersen:2020}.
-In both implementations, a ridge regression model is used as the explainer model, and the user \sout{is asked to} select\kge{s} various tuning parameter options: the number of features to return in the explanation, the simulation method, the feature selection method, and how the weights are computed.
-\sout{The discussion of parameter choices and implementation details of LIME in this paper are based on the R package.} See Appendix~\ref{lime-details} for an overview of the options available for the tuning parameters \kge{based on the R package}.
+In both implementations, a ridge regression model is used as the explainer model, and the user  selects various tuning parameter options: the number of features to return in the explanation, the simulation method, the feature selection method, and how the weights are computed.
+See Appendix~\ref{lime-details} for an overview of the options available for the tuning parameters based on the R package.
 
@@
 \item \emph{Feature Heatmap} (Section \ref{feat-heat}): Comparison of features selected by LIME across applications of LIME with different tuning parameter values.
-\item \emph{Assessment Metric Plot} (Section \ref{assess-metric}): Comparison of performance metrics for LIME across applications of LIME with different tuning parameter values. 
+\item \emph{Assessment Metric Plot} (Section \ref{assess-metric}): Comparison of performance metrics for LIME across \sout{applications of LIME with} different tuning parameter values. 
 \end{enumerate}
@@
 
-\sout{Since 4-quantile-bins} \kge{When quantile bins} are used to simulate data, LIME converts continuous predictor variables to indicator variables identifying whether the variable value falls in the same quantile bin as the prediction of interest or not.
+When quantile bins are used to simulate data, LIME converts continuous predictor variables to indicator variables identifying whether the variable value falls in the same quantile bin as the prediction of interest or not.
 The indicator variables are used as the features in the ridge regression explainer model.
@@
 We introduce the explanation scatterplot here under the \emph{lime} R package default method of 4-quantile-bins.
-\kge{See the supporting information for} \sout{Appendix \ref{exp-scatter_plus} addresses the} explanation scatterplot formats \kge{under} \sout{in} other LIME simulation scenarios.
+See the supporting information for explanation scatterplot formats under other LIME simulation scenarios.
 
 The explanation scatterplot applies the concept of plotting the model in the data space discussed in \citet{wickham:2015}.
-The \kge{visualization} \sout{plot} is built by plotting the LIME simulated data for the top two features identified by the explanation in a scatterplot and coloring these points by the predictions from the complex model.
+The visualization is built by plotting the LIME simulated data for the top two features identified by the explanation in a scatterplot and coloring these points by the predictions from the complex model.
 The point size represents the weight assigned by LIME.
@@
 First, consider the claim of localness.
-The weights decay relatively slowly outside of the intersection of the \kge{two quantile bins} \sout{2-quantile-bin} suggesting that the LIME explanation is highly influenced by points outside of the bins containing the prediction of interest.
+The weights decay relatively slowly outside of the intersection of the two quantile bins suggesting that the LIME explanation is highly influenced by points outside of the bins containing the prediction of interest.
 However, it is difficult to say if the claim of localness has been violated, because a definition of a local region is not specified.
@@
 The explanation scatterplot raises awareness of the unclear definition of a local region with LIME.
-\sout{Nevertheless, it is possible to say that the weights assigned to the simulated data do not capture the local region identified by the intersection of the quantile bins.}
-
-Now, consider the claim of faithfulness: It can be said that the majority of the points in the $x_2$ quantile \kge{bin} support a prediction of blue, which is captured by the bar supporting a prediction of blue in the LIME explanation, and a similar statement can be made about the $x_1$ quantile-bin.
+
+Now, consider the claim of faithfulness: It can be said that the majority of the points in the $x_2$ quantile bin support a prediction of blue, which is captured by the bar supporting a prediction of blue in the LIME explanation, and a similar statement can be made about the $x_1$ quantile-bin.
 These statements validate the explanation produced by LIME.
@@
 
-This example explanation \kge{scatterplot} only includes two features.
+This example explanation scatterplot only includes two features.
 In situations where more than two features are included in a LIME explanation, the explanation scatterplots can be extended to a generalized pairs plot \citep{emerson:2013} that includes all pairwise combinations of features.
@@
 Explanations produced by LIME are likely to be affected by the choice of tuning parameter values.
-A hypothetical example of this is shown by Figure\sout{s} \ref{fig:figure-01} \sout{and \ref{fig:figure-02} }where the method used to weight the observations influenced the explanation.
+A hypothetical example of this is shown by Figure \ref{fig:figure-01} where the method used to weight the observations influenced the explanation.
 As of the time of writing this manuscript, we have encountered no recommendations for how to specify the parameter values besides for the default settings in the \emph{lime} R package.
@@
 Vertical lines of color represent explanations that are dependent on the tuning parameter values and may not be local since the same feature is chosen regardless of the location of the observation in the feature space.
-See \kge{the supporting information} \sout{Appendix \ref{feat-heat-ex}} for hypothetical examples depicting \kge{the extreme cases of} feature heatmaps\kge{.} \sout{with the extreme cases of horizontal and vertical lines.} \kgc{Remove?}
+See the supporting information for hypothetical examples depicting the extreme cases of feature heatmaps.
 
@@
 \caption{\emph{Feature Heatmap}.
-An example feature heatmap \sout{of the explanations} from the applications of LIME \sout{with different tuning parameter values} to the \data \ test set.
+An example feature heatmap  from applying LIME to the \data \ test set using different tuning parameter values.
 The vertical striping indicates that the LIME explanations are not consistent across tuning parameter values.}
@@
 \caption{\emph{Assessment metric plot}.
-This example assessment metric plot \sout{contains metrics computed on} \kge{is from} the applications of LIME to the \data \ test set.
-The kernel density simulation method\sout{s} performs well across all three metrics.}
+This example assessment metric plot  compares different applications of LIME to the \data \ test set.
+The kernel density simulation method performs well across all three metrics.}
 \label{fig:figure-05}
@@
 The plot is faceted by metric, and the metric values are plotted on the y-axis.
-The \kge{point} color\sout{s of the points} represent the rank of the simulation methods performance based on a particular metric (darker indicates a better metric value and lighter indicates a worse metric value).
+The point color represent the rank of the simulation methods performance based on a particular metric (darker indicates a better metric value and lighter indicates a worse metric value).
 Higher average $R^2$ values are better, and lower average fidelity and MSEE values are better.
 This example only includes one tuning parameter: the simulation method.
-If more than one tuning parameter is considered, the assessment metric plot is extended by adding additional facets\kge{, point shapes,} or levels to the x-axis.
+If more than one tuning parameter is considered, the assessment metric plot is extended by adding additional facets, point shapes, or levels to the x-axis.
 
@@
 Average fidelity and MSEE are similar metrics, but MSEE only takes the prediction of interest into account and not the full simulated dataset as average fidelity does.
-This suggests that 6-quantile-bins produce an explainer model more faithful for the prediction of interest while 2-quantile-bins produce an explainer model more faithful over all simulated data observations \kge{(weighted by proximity to the prediction of interest)}.
+This suggests that 6-quantile-bins produce an explainer model more faithful for the prediction of interest while 2-quantile-bins produce an explainer model more faithful over all simulated data observations (weighted by proximity to the prediction of interest).
 
@@
 @
-\caption{Assessment metric plot for the applications of LIME on the bullet comparison data test set.
-There are discrepancies in metric performances, but overall, 4-equal-bins with a Gower power of 0.5 appear to perform the best.}
+\caption{Assessment metric plot comparing LIME results from applications to the bullet comparison data test set.
+There are discrepancies in metric performances, but overall, the 4-equal-bin implementation with a Gower power of 0.5 appears to perform the best.}
 \label{fig:figure-10}
@@
 
-\kge{Additional examples of the visual diagnostics and more info on the bullet matching data may be found in the Supporting Information section of the online version of the manuscript.} The code \sout{used to produce the manuscript} and \sout{the} data \sout{from examples in Section \ref{application}} \kge{associated with the manuscript} are \kge{also included in the online Supporting Information section and} \sout{available} in the following GitHub Repository: \href{https://github.com/goodekat/LIME-diagnostics-paper}{https://github.com/goodekat/LIME-diagnostics-paper}.
+\kge{Additional examples of the visual diagnostics and more info on the bullet matching data may be found in the Supporting Information section of the online version of the manuscript.} The code \sout{used to produce the manuscript} and \sout{the} data \sout{from examples in Section \ref{application}} \kge{associated with the manuscript} are \kge{also included in the online Supporting Information section and}  in the following GitHub Repository: \href{https://github.com/goodekat/LIME-diagnostics-paper}{https://github.com/goodekat/LIME-diagnostics-paper}.
 

### 2021-01-06 paper.Rnw
last?? edits

@@
 Plots for 4-equal-bins and 4-quantile-bins are included to depict tuning parameter values with good (4-equal-bins) and mediocre (4-quantile-bins) performance based on the assessment metric plot.
-\kge{Additional examples of explanation scatterplots including explanations for a known match and explanations produced using the kernel density simulation method are included in the supporting information.} \sout{Explanation scatterplots for a known match, referred to as case M, and for the kernel density simulation method applied to both M and NM are included in Appendix~\ref{bullets-plus}.}
-
-\kge{Figure~\ref{fig:figure-11} (top left) shows that w}\sout{W}hen 4-quantile-bins are applied to case NM, LIME explains that the values of mismatches, rough correlation, and distance are important and support a prediction of the class true\sout{ (Figure~\ref{fig:figure-11} top left)}.
+Additional examples of explanation scatterplots including explanations for a known match and explanations produced using the kernel density simulation method are included in the supporting information.
+
+Figure~\ref{fig:figure-11} (top left) shows that when 4-quantile-bins are applied to case NM, LIME explains that the values of mismatches, rough correlation, and distance are important and support a prediction of the class true.
 However, this explanation contradicts the random forest prediction which correctly assigns the observation  a non-match.
@@
 
-Figure~\ref{fig:figure-11} (top right) shows \sout{the LIME explanation for case NM} \kge{that} when 4-equal-bins are used\sout{.
-Here}, the features \kge{LIME} identifie\sout{d}\kge{s} as important are distance and mismatches, which support a match and matches, which supports a non-match.
+Figure~\ref{fig:figure-11} (top right) shows that when 4-equal-bins are used, the features LIME identifies as important are distance and mismatches, which support a match and matches, which supports a non-match.
 This explanation is more faithful having at least one feature supporting a non-match and has a better linear fit, but the most important feature identified by LIME still supports a match, contradicting the random forest.
@@
 Even though an explanation will be interpretable if  the complexity of the explainer model is appropriately chosen, a lack of understanding of the explainer model could lead to an incorrect interpretation of the explanation.
-For example, the visualization of a LIME explanation from the \emph{lime} R package \citep{pedersen:2020} (\autoref{fig:figure-03} left; \autoref{fig:figure-11} top) is a simplification of the explainer model, which could lead to misinterpreted LIME explanations.
-\kgc{Clarify?} Supplementing \citet{pedersen:2020}'s compact visualization of the explanation with an explanation scatterplot that shows a more detailed visualization of the explainer model promotes a more complete understanding of the explanation (\autoref{fig:figure-03} right; \autoref{fig:figure-11} bottom).
+For example, the visualization of a LIME explanation from the \emph{lime} R package \citep{pedersen:2020} (\autoref{fig:figure-03} left; \autoref{fig:figure-11} top) \hh{provides an (over-)}simplification of the explainer model that could lead to misinterpreted LIME explanations.
+\kgc{Clarify?} \hh{XXX better?} Supplementing \citet{pedersen:2020}'s compact visualization of the explanation with an explanation scatterplot that shows a more detailed visualization of the explainer model promotes a more complete understanding of the explanation (\autoref{fig:figure-03} right; \autoref{fig:figure-11} bottom).
 
@@
 These diagnostic visualizations are a starting point that already highlight seemingly common issues with the LIME claims.
-Additions, such as visualizations of the step-by-step process of the creation of LIME explanations and interactivity \kge{would}\sout{,} enhance the assessment process.
-For example, a diagnostic plot that provides a summary of multiple LIME explanations, such as the feature heatmap, could be \sout{displayed and} clicked on to reveal more detailed figures\kge{, such as an explanation scatterplot, for a prediction of interest.}\sout{ associated with individual prediction of interest, such as an explanation scatterplot.}
+Additions, such as visualizations of the step-by-step process of the creation of LIME explanations and interactivity would enhance the assessment process.
+For example, a diagnostic plot that provides a summary of multiple LIME explanations, such as the feature heatmap, could be clicked on to reveal more detailed figures, such as an explanation scatterplot, for a prediction of interest.
 
@@
 
-While it would be ideal if LIME could be used as a method to provide easily understandable explanations for black-box models as \citet{ribeiro:2016} claim, \kge{there is still work to be done to achieve that} \sout{that dream is not yet a} reality.
+While it would be ideal if LIME could be used as a method to provide easily understandable explanations for black-box models as \citet{ribeiro:2016} claim, there is still work to be done to achieve that reality.
 The examples using diagnostic plots to assess LIME in this paper show frequent instances when the claims about LIME are not met.
@@
 
-\kge{Additional examples of the visual diagnostics and more info on the bullet matching data may be found in the Supporting Information section of the online version of the manuscript.} The code \sout{used to produce the manuscript} and \sout{the} data \sout{from examples in Section \ref{application}} \kge{associated with the manuscript} are \kge{also included in the online Supporting Information section and}  in the following GitHub Repository: \href{https://github.com/goodekat/LIME-diagnostics-paper}{https://github.com/goodekat/LIME-diagnostics-paper}.
+Additional examples of the visual diagnostics and more info on the bullet matching data may be found in the Supporting Information section of the online version of the manuscript.
+The code  and  data associated with the manuscript are also included in the online Supporting Information section and  in the following GitHub Repository: \href{https://github.com/goodekat/LIME-diagnostics-paper}{https://github.com/goodekat/LIME-diagnostics-paper}.
 

### 2021-01-06 paper.tex
last?? edits

--- 2021-01-05 paper.tex
@@
 
-Without an assessment of the LIME explainer model, the user is putting trust in another black-box \kge{algorithm} \sout{procedure} to explain the complex black-box model.
+Without an assessment of the LIME explainer model, the user is putting trust in another black-box algorithm to explain the complex black-box model.
 In this paper, we stress the importance of assessing the LIME explainer model.
 To do this, we lay out the set of claims about LIME made by \citet{ribeiro:2016}, and we provide a toolkit of visual diagnostics  for the assessment of these claims: (1) \emph{explanation scatterplots}, (2) \emph{feature heatmaps}, (3) \emph{assessment metric plots}.
-Using these visual diagnostics, we demonstrate problematic examples of LIME explanations where the claims about LIME are not met and the explanations are highly dependent on tuning parameter values without a clear way to identify a set of tuning parameter values that produce the "best" explanations.
+Using these visual diagnostics, we \hh{identify situations in which LIME does not meet its claims.
+In some simple examples, we  demonstrate shortfalls in LIME explanations where} the explanations are highly dependent on tuning parameter values without a clear way to identify a set of tuning parameter values that produce the "best" explanations.
 
@@
 The explanation scatterplot raises awareness of the unclear definition of a local region with LIME.
-\sout{Nevertheless, it is possible to say that the weights assigned to the simulated data do not capture the local region identified by the intersection of the quantile bins.}
 
-Now, consider the claim of faithfulness: It can be said that the majority of the points in the $x_2$ quantile \kge{bin} support a prediction of blue, which is captured by the bar supporting a prediction of blue in the LIME explanation, and a similar statement can be made about the $x_1$ quantile-bin.
+Now, consider the claim of faithfulness: It can be said that the majority of the points in the $x_2$ quantile bin support a prediction of blue, which is captured by the bar supporting a prediction of blue in the LIME explanation, and a similar statement can be made about the $x_1$ quantile-bin.
 These statements validate the explanation produced by LIME.
@@
 \end{knitrout}
-\caption{Assessment metric plot for the applications of LIME on the bullet comparison data test set.
-There are discrepancies in metric performances, but overall, 4-equal-bins with a Gower power of 0.5 appear to perform the best.}
+\caption{Assessment metric plot comparing LIME results from applications to the bullet comparison data test set.
+There are discrepancies in metric performances, but overall, the 4-equal-bin implementation with a Gower power of 0.5 appears to perform the best.}
 \label{fig:figure-10}
@@
 Plots for 4-equal-bins and 4-quantile-bins are included to depict tuning parameter values with good (4-equal-bins) and mediocre (4-quantile-bins) performance based on the assessment metric plot.
-\kge{Additional examples of explanation scatterplots including explanations for a known match and explanations produced using the kernel density simulation method are included in the supporting information.} \sout{Explanation scatterplots for a known match, referred to as case M, and for the kernel density simulation method applied to both M and NM are included in Appendix~\ref{bullets-plus}.}
+Additional examples of explanation scatterplots including explanations for a known match and explanations produced using the kernel density simulation method are included in the supporting information.
 
-\kge{Figure~\ref{fig:figure-11} (top left) shows that w}\sout{W}hen 4-quantile-bins are applied to case NM, LIME explains that the values of mismatches, rough correlation, and distance are important and support a prediction of the class true\sout{ (Figure~\ref{fig:figure-11} top left)}.
+Figure~\ref{fig:figure-11} (top left) shows that when 4-quantile-bins are applied to case NM, LIME explains that the values of mismatches, rough correlation, and distance are important and support a prediction of the class true.
 However, this explanation contradicts the random forest prediction which correctly assigns the observation  a non-match.
@@
 
-\kge{Additional examples of the visual diagnostics and more info on the bullet matching data may be found in the Supporting Information section of the online version of the manuscript.} The code \sout{used to produce the manuscript} and \sout{the} data \sout{from examples in Section \ref{application}} \kge{associated with the manuscript} are available in the following GitHub Repository: \href{https://github.com/goodekat/LIME-diagnostics-paper}{https://github.com/goodekat/LIME-diagnostics-paper}.
+Additional examples of the visual diagnostics and more info on the bullet matching data may be found in the Supporting Information section of the online version of the manuscript.
+The code  and  data associated with the manuscript are also included in the online Supporting Information section and  in the following GitHub Repository: \href{https://github.com/goodekat/LIME-diagnostics-paper}{https://github.com/goodekat/LIME-diagnostics-paper}.
 

### 2021-01-06 paper.Rnw
updates during meeting (final version for resubmission!)

@@
 To do this, we lay out the set of claims about LIME made by \citet{ribeiro:2016}, and we provide a toolkit of visual diagnostics  for the assessment of these claims: (1) \emph{explanation scatterplots}, (2) \emph{feature heatmaps}, (3) \emph{assessment metric plots}.
-Using these visual diagnostics, we \hh{identify situations in which LIME does not meet its claims.
-In some simple examples, we  demonstrate shortfalls in LIME explanations where} the explanations are highly dependent on tuning parameter values without a clear way to identify a set of tuning parameter values that produce the "best" explanations.
+Using these visual diagnostics, we identify situations in which LIME does not meet its claims.
+In some simple examples, we  demonstrate shortfalls in LIME explanations where the explanations are highly dependent on tuning parameter values without a clear way to identify a set of tuning parameter values that produce the "best" explanations.
 
@@
 This explainer model suggests that a random forest prediction of `blue' for this observation is mostly supported by the prediction of interest having a value of $x_2$ that is greater than \Sexpr{str_split(sine_poi_lime_default$feature_desc[[1]], pattern = " ")[[1]][1]} but somewhat contradicted by the prediction of interest having a value of $x_1$ that is greater than \Sexpr{str_split(sine_poi_lime_default$feature_desc[[2]], pattern = " ")[[1]][1]} and less than or equal to \Sexpr{str_split(sine_poi_lime_default$feature_desc[[2]], pattern = " ")[[1]][5]}.
-%\kgc{I decided to leave the values here.
-I actually prefer it this way myself, but I cut out a lot of text from this subsection in other ways.}\hh{XXX }
 
@@
 
-To provide a more detailed view of explanations obtained using different tuning parameter values, we consider explanation scatterplots for one prediction of interest referred to as case NM (a known non-match) shown in Figure~\ref{fig:figure-11} along with the visual explanation plots from the \emph{lime} R package.
+For a more detailed view of explanations based on different tuning parameter values, we consider explanation scatterplots for a prediction of interest, a known non-match (NM), in Figure~\ref{fig:figure-11} along with the explanation plots from the \emph{lime} R package.
 Plots for 4-equal-bins and 4-quantile-bins are included to depict tuning parameter values with good (4-equal-bins) and mediocre (4-quantile-bins) performance based on the assessment metric plot.
@@
 
-Figure~\ref{fig:figure-11} (top left) shows that when 4-quantile-bins are applied to case NM, LIME explains that the values of mismatches, rough correlation, and distance are important and support a prediction of the class true.
+Figure~\ref{fig:figure-11} (top left) shows that when 4-quantile-bins are applied to case NM, LIME finds the values of mismatches, rough correlation, and distance are important and support a prediction of the class true.
 However, this explanation contradicts the random forest prediction which correctly assigns the observation a non-match.
-The explanation scatterplot (Figure~\ref{fig:figure-11} bottom left) clarifies the reason for the highly unfaithful explanation.
+The explanation scatterplot (Figure~\ref{fig:figure-11} bottom left) clarifies the reason.
 Case NM falls on the boundary of regions for each of these three features where the random forest predictions transition from below 0.5 to above 0.5.
@@
 Even though an explanation will be interpretable if  the complexity of the explainer model is appropriately chosen, a lack of understanding of the explainer model could lead to an incorrect interpretation of the explanation.
-For example, the visualization of a LIME explanation from the \emph{lime} R package \citep{pedersen:2020} (\autoref{fig:figure-03} left; \autoref{fig:figure-11} top) \hh{provides an (over-)}simplification of the explainer model that could lead to misinterpreted LIME explanations.
-\kgc{Clarify?} \hh{XXX better?} Supplementing \citet{pedersen:2020}'s compact visualization of the explanation with an explanation scatterplot that shows a more detailed visualization of the explainer model promotes a more complete understanding of the explanation (\autoref{fig:figure-03} right; \autoref{fig:figure-11} bottom).
+For example, the visualization of a LIME explanation from the \emph{lime} R package \citep{pedersen:2020} (\autoref{fig:figure-03} left; \autoref{fig:figure-11} top) provides an (over-)simplification of the explainer model that could lead to misinterpreted LIME explanations.
+Supplementing \citet{pedersen:2020}'s compact visualization of the explanation with an explanation scatterplot that shows a more detailed visualization of the explainer model promotes a more complete understanding of the explanation (\autoref{fig:figure-03} right; \autoref{fig:figure-11} bottom).
 

### 2021-01-06 paper.tex
updates during meeting (final version for resubmission!)

@@
 This explainer model suggests that a random forest prediction of `blue' for this observation is mostly supported by the prediction of interest having a value of $x_2$ that is greater than 4.834 but somewhat contradicted by the prediction of interest having a value of $x_1$ that is greater than -0.302 and less than or equal to 4.844.
-%\kgc{I decided to leave the values here.
-I actually prefer it this way myself, but I cut out a lot of text from this subsection in other ways.}\hh{XXX }
 

### 2021-01-07 code/03-submission-steps.Rmd
prepared all files for submission
final prep for resubmission

@@
     # Specify date of submission folder
-    submission_date = "2021-01-06"
+    submission_date = "2021-01-07"
 
@@
     unlink("../figure", recursive = TRUE)
+    unlink("../support-info/figure", recursive = TRUE)
     unlink(submission_folder, recursive = TRUE) 
-    unlink("../support-info/figure", recursive = TRUE)
     ```
@@
 
-10. Knit this document to make sure the md version is up to date.
+11.
+Use latexdiff to generate a pdf showing the differences between the this submission and the previous one.
+To do this, (i) run the R code below, (ii) run the code `latexdiff submissions/2020-10-07/paper.tex submissions/2021-01-07/paper.tex > submissions/2021-01-07/diff/2020-10-07-to-2021-01-07.tex` in the terminal (changes dates in the code as needed), and (iii) knit the generated tex file to make sure the pdf with the changes looks good.
+
+    ```{r}
+    # Create folder to place the diff
+    diff_folder = paste0("../submissions/", submission_date, "/diff")
+    dir.create(diff_folder)
+
+    # Create folders within diff to store the figures needed
+    dir.create(paste0(diff_folder, "/figure"))
+    dir.create(paste0(diff_folder, "/figure-static"))
+
+    # Copy necessary files into the diff folder needed for the diff to work
+    file.copy("../references.bib", diff_folder)
+    file.copy("../WileyNJD-AMS.bst", diff_folder)
+    file.copy("../WileyNJD-v2.cls", diff_folder)
+    file.copy(list_of_generated_figures, paste0(diff_folder, "/figure"))
+    file.copy(list_of_static_figures, paste0(diff_folder, "/figure-static"))
+    ```
+
+12. Knit this document to make sure the md version is up to date.

### 2021-01-28 paper.Rnw
added GitHub link for limeaid
removed limeaid reference and specified link as urls

@@
 
-All runs of LIME in this paper are executed in a forked version (https://github.com/goodekat/lime) of the R package \emph{lime} (version \Sexpr{packageVersion("lime")}) by \citet{pedersen:2020}.
+All runs of LIME in this paper are executed in a forked version (\url{https://github.com/goodekat/lime}) of the R package \emph{lime} (version \Sexpr{packageVersion("lime")}) by \citet{pedersen:2020}.
 The forked version is functionally indistinguishable from \citeauthor{pedersen:2020}'s implementation but allows us to export internal values relevant for an assessment of the explainer.
-The code for the diagnostic plots is stored in the R package \emph{limeaid} \citep{goode:2020}.
+The code for the diagnostic plots is stored in the R package \emph{limeaid} available on GitHub (\url{https://github.com/goodekat/limeaid}).
 

### 2021-01-28 paper.tex
added GitHub link for limeaid
removed limeaid reference and specified link as urls

@@
 
-All runs of LIME in this paper are executed in a forked version (https://github.com/goodekat/lime) of the R package \emph{lime} (version 0.5.1) by \citet{pedersen:2020}.
+All runs of LIME in this paper are executed in a forked version (\url{https://github.com/goodekat/lime}) of the R package \emph{lime} (version 0.5.1) by \citet{pedersen:2020}.
 The forked version is functionally indistinguishable from \citeauthor{pedersen:2020}'s implementation but allows us to export internal values relevant for an assessment of the explainer.
-The code for the diagnostic plots is stored in the R package \emph{limeaid} \citep{goode:2020}.
+The code for the diagnostic plots is stored in the R package \emph{limeaid} available on GitHub (\url{https://github.com/goodekat/limeaid}).
 
